\chapter{The Showdown Between Humanity and Ximen Qing (9)}

It was a tempting proposal, in a way.

Of course, not the unexpected maternity leave.

She would pretend to comply as if she had no choice, only to backstab him later.

Should this be called a honey trap?

But it wasn't much of a honey trap since Qing hadn't done anything.

To think that he would come up with a whole family plan on his own and present it to her.

At least, it was clear that this guy had never been in a relationship before.

Dou Wusan had said he would uphold his honor, and in truth, he meant it.

However, Qing did not believe him.

After all, hadn't he said that he'd gnaw on his own leader until there was nothing left, not even bones, and then offer the remains to the bandits of the forest?

Hadn't she said that herself?

And yet, here he was, in front of his target.

He said he would hide her well and let her escape if she bore his child?

He didn't even keep his word to his own boss, so what? He would keep his word to her?

However, was there a need to take a detour when there was an easy path?

In fact, if she wanted to run away now, she was confident that she could.

If she used her Ethereal Steps to their fullest, she could hide in the forest, and just as she had set fire to the stronghold, once she was hidden in the forest, she could escape at any time.

But avoiding the difficult and challenging path meant postponing the work for later.

And she did not know what kind of trouble that might cause.

So, since they were already sworn enemies, she had to take care of them here.

Just as she had crushed those psychic parasites during the Demonic Cult incident, she had to take care of at least two Unrestrained Realm Masters before leaving, which was why she was setting fires and provoking them.

Unrestrained Realm? To be honest, they were fast. Faster than she expected.

But Qing was incomparable to what she was back then.

So if it was one-on-one, she wasn't lacking in confidence.

But he said he had laid out an elite squad.

And there was another Unrestrained Realm Master, the Supreme Commander, nearby.

Even for the Transcendent Qing, that was a bit much.

Two Unrestrained Realm Masters against one Transcendent was too much. What a bunch of cheap bastards.

Let's make this easy.

If it doesn't seem right, then I'll just stab him and run.

"……What if it's a daughter?"

It was practically half an acceptance.

Dou Wusan grinned.

"I said a son. It has to be a son, no matter how many times we have to try."

"What if only daughters keep coming out?"

"A son."

"Geez, aren't you being too unreasonable? Let's call it off if there's no son within three tries?"

"A son."

"Originally, the gender of a child is the father's responsibility, you know? It's chromosomes? Anyway, that's how it is. Since a woman always provides the same foundation, whether it's a daughter or a son is all your responsibil-"

"A son."

"No, is a son some kind of neutral country? Fine, let's say it's a neutral country. So, it can't be that you're just going to make a baby now, right?"

"Of course not. First, we must hide in a safe place. However."

Dou Wusan said, taking out a dark pill from his bosom.

Wow. Poison! Poison, yes, poison is an excellent method.

Qing inwardly cheered while outwardly frowning as if she was horrified.

If he was going to tie her up with ropes, she would have just let him, and if it was chains, she would have just ambushed him and broken a limb or two before fleeing.

But poison was a different story.

"Poison? Wow, that's really old school. Do you want me to give birth to a child so you can have the antidote?"

"It's not very harmful to the body, just a Qi-Dispersing Poison, so you don't have to worry too much. I have to take this precaution too, you see. It won't be a problem even if you conceive."

Qi-Dispersing Poison was a mystical substance that dispersed the Inner Qi in one's dantian for a duration.

It made sense that such a medicine existed even when Inner Qi was some kind of cosmic energy, or whatever.

However, it was difficult to use effectively compared to its performance.

If one's Inner Qi began to disperse, one would immediately recognize the poisoning and either stop breathing or throw away the tea they were drinking.

Before the opponent's Inner Qi could be emptied, they would realize, so unless they were trapped in a sealed room and gassed, or forced to consume it…

Qing had already taken it several times before.

Of course, due to her constitution, it didn't work on her.

"Geez. You've really made up your mind, haven't you? Give it here."

"How can I trust you? Open your mouth. Your husband will feed it to you himself. Come on. Ah."

Oh, he's really going all out, isn't he?

Qing felt a shiver crawl up her spine, but she had no choice but to open her mouth.

Then, a bitter taste entered her mouth.

Qing tried to close her mouth, but a strong force held her jaw open.

"No, no. I have to make sure you swallow it all."

Dou Wusan looked inside Qing's mouth.

The Qi-Dispersing Pill slowly dissolved and disappeared.

Only then did Qing manage to swallow the saliva that had filled her mouth.

This is quite the sight, isn't it?

Dou Wusan chuckled and placed another Qi-Dispersing Pill on her tongue.

"Ugh."

"I doubt one would be enough for someone who has reached the Transcendent Realm, wouldn't it?"

And so, she swallowed again.

Then, another one was placed.

Qing's veins bulged on her forehead.

This fucker. If he's going to feed me, why doesn't he just put them all in at once? Why is he putting them in one by one?

Is he enjoying watching the inside of someone else's mouth?

After swallowing a whopping five Qi-Dispersing Pills, her jaw finally regained its freedom.

"Ugh, that's so bitter. Do you have any alcohol? I saw you carrying one around earlier."

"You said you saw me carrying one around? Ha. You're telling me not to fill water flasks with alcohol even though I've been telling everyone not to."

Hmm. Qing recalled a time in her early working days when she briefly worked as a construction worker.

Mr. Kim, who sipped soju from a water bottle, another Mr. Kim who proudly and openly consumed soju from a small glass bottle of an energy drink.

And yet another Mr. Kim who secretly drank from a soju bottle.

It seemed that whether it was there or here, alcoholics were unstoppable.

And Dou Wusan was the same.

"Here. It's strong, so be careful."

Qing asked, feeling bewildered.

"Didn't you just say something about not filling water flasks with alcohol?"

"I'm a Master, am I not? What problem could there be if a Master drinks a bit of alcohol?"

"Hmm."

Qing raised the water pouch without making contact with her lips.

Since it was indirect, she didn't mind. But more importantly, it was just dirty.

As the fiery and strong liquor entered, it washed away the bitter taste with an even more bitter taste.

"Whew. You really do drink some good alcohol, being a Master and all. All the other bastards were drinking alcohol that was already all watered down, saying it was real alcohol."

Dou Wusan smiled at that.

I can't find a single thing I don't like about her, from head to toe.

"Of course. Because I am a Master."

Thus, Dou Wusan's method of abducting Qing was very simple.

Qing wasn't cross-dressing as a man, but she was dressed as a bandit leader. As such, she had tightened her chest and wore many layers of clothes, making her look taller and bulkier.

On top of that, Dou Wusan had her wear a fur hat that covered her face.

So, with her unusually pretty eyes, it created an oddly unpleasant-looking bulky figure.

"Commander, what's with that guy?"

"That guy? He's a candidate for the new Heavenly Tempest Star."

"Did you say Heavenly Tempest was defeated by that guy?"

"Isn't he quite bold? He said he wanted to join the Green Forest and challenged me right away. Hey, this one is ranked twentieth, the Swift Star. He'll be your senior, so why don't you greet him?"

Dou Wusan's expression was full of laughter.

However, Qing found it all childish and ridiculous.

Do you think I won't do it just because you asked?

Qing bowed deeply and spoke in a hoarse voice.

"Aigo, Senior, it's an honor to meet you. This junior, Heavenly Tempest, greets you profoundly. Cough, my throat is a bit bad, but seeing Senior really makes my heart swell with awe. Cough, cough, cough. This insignificant sore throat dares to try and stop my admiration for Senior. I must ask, would it be permissible to ask if I may one day have the honor of treating Senior to a drink until my cock falls off?"

At that, the one called Swift Star chuckled.

"Keke, this guy is quite something, isn't he? I approve. If he defeated Heavenly Tempest, then he has the qualifications, and personally, I like him much better than that arrogant bastard."

"Aigo, Senior, such words are an honor for three, four, no, even ten thousand generations."

"Sure. Let's meet again later."

Dou Wusan's expression turned strange.

What is this? Is this for real?

The hierarchy of the Divine Maiden Sect must be incredibly strict, huh?

The way she talks is like she's had a lot of experience in an organization, hasn't she?

"I'm going to take this new recruit to Liangshan Marsh and see how capable he is. If the Supreme Commander looks for me, send someone right away and tell him I'll be there soon."

"Yes, Senior."

Thus, Qing followed Dou Wusan with light steps.

----

Liangshan Marsh was the stronghold of the Green Forest's most elite combat unit.

And since any faction's most elite unit was treated well, the Green Forest had set up a separate base in a hidden valley at the foot of Mount Tianzi, even naming it Liangshan Marsh.

As such, Qing followed Dou Wusan along the path.

Since she was acting like she had no Inner Qi, she pretended to be out of breath. But this guy just kept going through the beastly paths without slowing down.

"Huff, huff, can't you slow down a bit, phew? I can't use Inner Qi, you know. Shouldn't you carry me on your back or hold me in your arms or something at times like this?"

"What if someone sees us and gets suspicious? I'm not such a considerate leader that I would carry a new recruit on my back."

Ah shit. What a shame.

If he had carried me or held me, I could have just broken his head right then and there.

And so, they traversed the mountain path for who knows how long.

Qing's acting was always accompanied by serious immersion, just like when she had acted like a cripple in her previous life.

I have no Inner Qi. I can't use Inner Qi.

And if I have no Inner Qi, I'm weak…….

So, ah fuck, this is so tiring. Huff, huff.

Finally, after a long and arduous journey through the mountain path, Qing entered Liangshan Marsh.

Wow, I can't believe I missed this place.

It was only ten minutes away from where I first set fire, but since it was in a valley, I obviously couldn't find it.

Qing followed Dou Wusan through Liangshan Marsh, her ears perked up. Hmm. No signs of anyone around?

Speaking of which, I'm curious about something. How did this fucker suddenly appear, avoiding my senses?

Qing couldn't resist her curiosity.

And the atmosphere now felt like she could ask without worry.

"Hey. I'm pretty sensitive, if I say so myself, but how did you learn that stealth technique?"

"I picked it up along the way."

"Oh. Isn't that some kind of Divine Art or something?"

"You could call it that."

"What is it? What is it?"

"It is said that if you want to survive in Wulin, you should hide thirty percent of your skills. If you're too interested in other people's martial arts, you won't live to see old age."

He was telling her to mind her own business.

What a shame. This doesn't work on him, huh?

Normally, people like this, if you just praise them a bit, they'll just blabber on and on about their stories, whether they're true or not.

He's not an easy one, is he?

Thus, Dou Wusan entered a secluded warehouse, then opened an iron door leading underground.

As Qing followed him down, an indescribable, foul stench, ugh, what is this?

"Ugh, the smell."

"My apologies. But this is the only soundproof place."

"Huh? Soundproof? Is this place soundproof?"

"If you change your mind and scream, it would be troublesome for both of us, wouldn't it? Now then. Lean against this."

Dou Wusan tapped on something next to him.

It looked like a vaulting horse often seen in school gyms.

However, instead of a pommel horse, there were two shackles.

On the opposite side, a steel frame that obviously looked like it was meant for inserting one's arms in order from wrist to upper arm.

Qing frowned deeply.

No, these bandit bastards, from the young masters to everyone else, have such a strange view of women that they even made a dedicated restraining device. Wow. Just wow.

And now that I look at it, there's even an expensive mercury mirror in front of the restraining device.

It was an arrangement that showed a determination to watch the woman's face while doing the deed.

This is not right.

This makes it impossible to ambush.

Qing frowned even more intensely.

Let's try talking first.

"You're going to tie up a person like a beast and do the deed? No, before that, what is this even? It's obviously made for this function, isn't it?"

"When there are only men around, one needs some time to relieve their sexual desires, don't they? Surprisingly, it's not easy when a woman decides to resist. Of course, you can make them beg for it by beating them, but they say it leads to a quick death that way. Ah. For reference, I've only heard about it. I've never done it myself. I don't enjoy such carnal pleasures to begin with."

He was shamelessly denying it.

Qing was dumbfounded.

However, it wasn't the time to be dumbfounded.

If she got tied up here, she really would have to take that unplanned maternity leave. 