\chapter{Forbidden City Diary (4)}

The list of officials kneeling before Namsamso was incredibly diverse.

Well, after filtering out the pyramids, there were only a few high-ranking officials who were no different from the most powerful people of the time, such as the second and third rank officials.

In each of the six ministries that lead the administration of the country, namely, the Ministry of Personnel, the Ministry of Taxation, the Ministry of Rites, the Ministry of War, the Ministry of Justice, and the Ministry of Public Works, there was one minister, and one left and right minister, each one of a lower rank.

There were six separate departments for science, military, military service, military service, and military service, and the 7th rank Do-geup-sa-jung and the 7th rank Gyeop-sa-jung were high-ranking officials who, although extremely low in rank, hold the power to veto the policies of their respective departments and to prepare the budget, and were actually treated as 3rd rank Jong-sam-pung-geum.

Of course, not all of them participated, so it was clear that some of the pro-Emperor faction, especially those who were extremely close to the Emperor and dared to call themselves close associates of the Emperor, did not show up.

Of course, it would be natural for them to be happy about the crown princess ascending to the throne.

Still, more than half of the pro-imperial faction expressed their opposition to me.

Even among the pro-imperial faction, most were afraid of the growth of imperial power, or wanted their daughters to be attached to the crown prince, or were wary of the appearance of the crown princess, having already been brought in as the emperor's concubine…

However, it was not easy.

How could it be easy to lie down on a stone floor without any shade in the middle of summer?

How many high-ranking officials have already collapsed from the heat and been carried out?

Even in the midst of all this, the prince didn't say a word or even respond, which shows how firm his will was.

Minister of Personnel Yoo Woo-young lets out a long sigh.

``Oh, it seems the prince was completely captivated, and since he has avoided women until now, didn’t they say that a late affair was even more frightening? What should I do about this?''

"At times like these, we must clearly state our intentions. The Crown Prince was a man of discerning reason and goodness."

The recipient of the words was the brother-in-law, Minister Oh Chung-hyung.

Not all of these came out for political purposes alone, and this was a representative example.

Whether the wife was the first wife, the second wife, or the concubine, was the favor bestowed upon the first wife normal?

If only the author were a commoner, how could he possibly be given the favor of such a stern person?

When conflict arises between people, it was necessary to clearly determine right and wrong in accordance with the laws, principles, and etiquette of the country, and to make adjustments according to the circumstances of both parties.

However, when conflict arises among martial artists, they were a people who consider it honorable to draw their swords and harm the opponent, and they consider it shameful to resolve it amicably with words.

``Besides, since the Empress was also against it, wouldn’t the Crown Prince eventually back down?''

Oh Chung-hyung says this and looks to one side.

Women kneeling in a line along the awning in the corner of the wide front yard, where there was some shade.

The one at the very front was the beautiful Lady Seo, and the title of beautiful woman refers to the position of leading the ladies (female officials) within the Forbidden City.

And the work of these ladies, unofficially called the Naegungbu, was a work that has been entrusted to the Empress for generations.

So, the fact that they were here means that the Empress has also expressed her opposition to the Crown Prince's misdeeds.

Of course, even if we leave out all the other obvious disadvantages, what mother in the world would want a martial artist as her daughter-in-law?

That was when.

``Yes, Your Majesty, please eat.''

The prince, who had left Namsamso, returned, so without any command, everyone took notice and said, "One, two—"

``Your Majesty! Please listen!''

Then, each faction submits a petition that has been prepared in advance.

"Your Majesty! The wedding was a matter of national importance. Please step aside for now and leave the discussion to us!"

``How can you allow an unmarried woman to stay in your bedroom? This was a great offense even to a woman!''

The prince was furious.

Why on earth do these people bother to tease others in this sweltering heat, even while they're drying up? I don't like women like that either!

The prince's expression suddenly crumpled.

Meanwhile, the expressions of the officials who saw Lady Deokseong following behind the crown prince were filled with shock.

``Your Majesty!!''

``How could I, my wife, not be able to do it!!''

``Kwaaaaah!! Touch!! Absolutely touch!!''

The volume of the voice rises to a higher level.

Well, Lady Deokseong was no ordinary person.

She was the wet nurse of the Empress's children, and her affection was no different from that of a mother and child, and she was a woman whom the Empress herself openly says she loves more than her own sisters.

Why else would the Emperor have given him a palace and exiled him instead of exiling him?

The crown prince was the one who will ascend to the throne, and the wet nurse was a powerful relative whose mere existence can influence state affairs.

So, Lady Deokseong also knows this and rarely goes out of the Suan Palace to jeer, and even if she does, it was limited to the occasional teas with the Empress.

In fact, it would have been normal for Lady Deokseong to have achieved a special exit from the palace a long time ago.

In the style of the hometown of Qing, it feels like this.

\begin{quote}
	※※Deokseong Madame Retirement
	※※ Upon leaving the palace
	\#\# One hundred hero-level workers<< were given
	※ Super★Giant Manor
	※Free gift
	◎◎Immediate retirement: Guangdong/ Guangxi/ Guizhou/ Sichuan/ Fujian/ anywhere to a remote☆faraway place from the funds※※
\end{quote}

This was not only a way to commend his hard work, but also a proper procedure for exile, a banishment from the palace.

But, isn't it true that he himself tearfully pleaded and said that when the princess leaves the palace to get married, how could he send her off alone to a faraway land? He said that he would follow her and take care of her, and that was why he was forced to stay behind and was unofficially exiled to Suan Palace.

Of course, since it was not an official exile, even if Lady Deokseong left Suan Palace, it would not be an act that broke the laws of the country.

The person the prince had just brought in was this very person.

If you have something to say, why didn't you just talk at Suan Palace and end it? Why did you bring your wife back?

Please keep my future wife by my side.

That is, the prince has made up his mind!

You have decided to make Heavenly Blossom Sword the crown princess!

``How could a martial artist, ugh, squeak……!''

The loyal subject Oh Chung-hyung, unable to overcome the shock, endures the pain and collapses, foaming at the mouth, from the delayed exhaustion.

Listen, O Minister! Brother-in-law Minister! Come to your senses! Come to your senses! Listen! Bring him in quickly, bring him to the ceremony! Quickly!

The prince's teeth clenched violently as he passed through the chaotic front yard.

These people don't know how to read others' minds, and no one can fathom what's on their minds. Seriously, I feel like dying…

If there was any consolation, it was the pitiful look in Lady Deokseong's eyes that reached the prince.

Now, it was Lady Deokseong who realized that the prince was not infatuated with women, but rather the result of a delusion driven by madness.

If only the prince hadn't been so overly compassionate in his eyes.

``Madam, I will take good care of you.''

"Don't worry about it, and don't pay too much attention to their opposition. The misunderstanding will naturally be resolved later, won't it?"

``……Okay. Well then, thank you for your hard work.''

The prince, with a grimace, retreats into his quarters.

Lady Deokseong watched his back until the very end, then quietly bypassed the main building and headed towards the attached hill.

It's been a really long time since I've been to a healing place.

A place where young grandchildren once played.

The young prince was crying and holding onto the hem of his clothes, and the young princess was awkwardly looking away and sweating profusely.

yes.

It's really annoying to see a child grow up, but who can stop it?

Just as the young prince has now grown into a respectable man and was now a respectable young lady, it was only natural that the young princess has now grown into a respectable lady.

The mother also acknowledged the prince's growth, but said that the princess's growth showed that she had changed as a person. So, isn't it likely that she has now realized this and was trying to become closer to him again?

Perhaps because it was such a painful experience, he knew it would remain in his arms forever… …

A look of pride appears on Madam Deokseong's face.

Perhaps this will be the end of this strange fascination.

I don't know if Heavenly Blossom Sword was a wicked schemer who took advantage of this gap, or if she's just a poor woman who got caught up in it.

First, we need to seize the initiative, press hard, and then find out what's really going on.

So for now.

Mrs. Deokseong holds the door to the Hillbangjeon.

It would be natural for a maid to ask her master's wishes before entering, but what could be more difficult than showing her superiority and showing that she was not just an ordinary maid?

Madam Deokseong knocked on the door without saying anything.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Aekyung's teachings, the introduction to them, had a tendency to be similar to martial arts.

Lunhyeol, Qing-i clenched her fist at Gaby's native pronunciation of India. "Chakra, oh, chakra!" But wasn't that a Japanese thing? A ninja, a nine-tailed fox? Anyway.

But contrary to Qing's thoughts, the wheel blood did not refer to the energy itself.

If I had to say, the wheel blood was a concept that corresponds to the central plains' dantian, and the spiritual power that Qing understood as a chakra was prana, which was a separate energy of India.

Anyway, there were seven Dantian points and ring points in the Cheonchuk style, from the pelvic floor to the crown of the head.

Unfortunately, it was not possible to open it step by step from the bottom.

One door open! Another door open! This wasn't it…

When you train one of the six acupoints, the other six acupoints will grow together.

However, the upper one was the higher level of the ring.

So, if you train the top, the bottom will grow quickly and achieve quickly, but if you train the bottom, it will be slower.

That is, seven connected gears.

The closer to the head, the larger the teeth, and the lower the teeth, the smaller the teeth.

The large gears were difficult to turn, but even if you turn them just a little, the smaller gears that follow them will turn very quickly.

Small cogs were easy to turn, but to turn a large cog once, the small cog must turn dozens, or hundreds or thousands of times depending on the diameter.

``Then wouldn’t training the Ilcheonryun be the fastest way?''

"Hehe, Mama. The Ilcheonryun was the circle of blood that connects with the universe, forming the true self within it and reaching extinction. If one could directly cultivate this, it would be granted not to humans, but to Buddhas, and among Buddhas, only to Buddhas who have reached the complete universe."

"hmm."

``Even the Buddha, who was the most superior among humans, only trained the wheel of light (Ajna Chakra, the six stages), so even that was an impossible power for ordinary people.''

``I see.''

Qing was somehow indifferent.

Well, this isn't what I wanted.

Why do you suddenly call it a martial art similar to a martial art, a martial art of the Heavenly Kingdom? Why am I taking this kind of lecture?

But Myeongnyun, um, Myeongnyun, I want to eat ribs… …

In response to Qing's reaction, Gabya pretended to be deadly again.

``That was why we criminals want to train our ring acupoints through the second ring acupoint, the ring of passion (Swadhisthana Chakra).''

``Passion Wheel.''

Qing's eyes sparkle again.

Passion Wheel? The name itself was unusual.

The second acupoint of the human body, the genitals, was located in the genital area.

``That is, it trains the blood circulation through pleasure, and this pleasure was not only physical, but also mental and spiritual, so it was connected not only to my own joy, but also to the joy I get from giving joy to others.''

"Oh. It's a bit strange to suddenly turn to pleasure here, but it's strangely convincing."

``Haha, so in the teachings of Aekyung, the postures for a man and a woman to enjoy each other’s company and achieve great joy were recorded. So, if you were familiar with these postures, you will understand what I am saying, right?''

The position has been revealed! Yes, this was the Kama Sutra!

Qing's eyes were very bright.

If I had studied with this attitude in the past, I probably wouldn't have been struck by lightning while playing video games. It's a passion for learning.

``So, what about the position? Do you have a book?''

"Hehe, Ma'am, you're more blunt than most women. Is that because you're a woman of the martial arts world? However, a woman's shyness was also a great charm, so I'll teach you about that later."

Gabiya's smile deepens.

It was truly a blessing that my mother was so eager to learn and did not hesitate or hesitate.

Gabiya's mission did not end with winning the Crown Princess' favor and becoming her confidant.

Aekyung was a study that brings and gives great pleasure.

Giving the Crown Princess paradise pleasures under the guise of teaching and making her addicted to pleasure.

I can't live without you, so I beg and crave for your touch!

Captivating and enthralling them with complete passion!

However, even in India, the sects that study Aekyung were treated as extremely evil witches, so how much worse would it be in the Zhongyuan?

So, the unwavering enthusiasm for learning in Qing was bound to be welcome.

If not, I would have had to spend a long time trying to persuade her with the miserable reality of the concubines who were favored by the crown prince and those who were not.

"Hehe, Mama. Then, today, let me introduce you to the eleven most basic positions."

``You can introduce me to more people.''

``Hehe, don’t be impatient. Mama, would it be alright for a celestial maiden to dare invade your bed?''

"then."

Gabiya rolled up the blanket and tied it tightly with a string somewhere.

"Now, consider this a man. The Heavenly Lady will introduce you, focusing on the movements of a woman. This was the first Pan-gyo."

Gabiya lies on the bed with her knees bent and her legs spread apart.

Maybe because it's my first time, I guess it's a bit boring.

How many people from the Qing Dynasty have not seen such an attitude on the screen?

And then what about the angle, and what about the pelvis, and if there were enough pillows, how can I use them to create a more enjoyable radiation?

``Oh, your legs there?''

``Haha, this was a position that requires some training? But since you were a warrior, I’m sure you can do it.''

Gabiya was also excited by the students' passionate attitude towards learning.

So, holding onto the blanket and squirming, adding appropriate moans to it, and even adding a plausible scream.

``Haaah, haaah, Mama, if the man gets desperate and increases his speed at this time, you should bounce your hips to match him, and also match him with a loud scream right next to his ear, so that the listener will hear it as a thunderous, huge scream, like this, hwaat, hwaat, hwaat, hwaat……!''

Gaby was also good at manipulating the man's role blanket, oh, that's plausible.

Covered in a desperately quilt, Gabiya let out a breathless, gasping, wet moan as if she were about to suffocate.

``Huh, huh, ugh, ugh, huhhhh……!''

That was the moment.

Knock knock.

It was a door that suddenly opened as if possessed by an automatic door.