\chapter{Forbidden City Diary (5)}

It was said that in Qing's hometown, there was once a time when such a story was a hot topic.

Do you know why wars break out? Yeah. Because we let our guard down.

Yes. If you let your guard down, no matter how strong your defenses or how many countermeasures you employ, they will fade. Even the most sensitive person will be swayed by distraction and fall victim.

Qing was immersed in Gabya's performance for a long time. "I'll show you something, the fantastic Kama-Sutra!" She was watching and listening, gulping and enjoying the performance.

The door opened and then, oh my!

However, unlike Qing, who was watching comfortably while lying down, Gabiya was not in a very comfortable state.

Originally, sexual intercourse was one of the most intense exercises, and so the human body was designed to squeeze out all its strength to the limit by covering it with a sexual desire that rises like wildfire.

It's a copy of a sexual intercourse position, so the intensity was just as intense, or rather, the intensity was even more intense than that of two (or more) people demonstrating the intense movement of working together.

So, was the door open or not?

I was just rolling up the blanket underneath me and squeezing it together, busy demonstrating some amazing hip movements that were somewhere between intense and soft, or both, as if sliding my pelvis forward and backward, up and down.

Of course, without even stopping to talk.

``Haha, hot, huh, ahh.''

With this background music, Qing keeps making eye contact with the unfamiliar woman.

``…….''

``…….''

``S, Shang-gong, ha-ha, I, above, ha-ha! Eww, keuheuuuu……''

Gabiya's body trembles.

It was the climax, the climax of acting that took all of one's strength.

And when I looked at Mama as if to ask how she was doing, she had a strange expression on her face and was sweating profusely.

Aren't you looking somewhere else without any reward for your hard work?

Gabiya's head followed his-

``Whoa! More, Madam Deokseong……!''

Thanks to that, I learned the name of the Qingdo woman.

More like Mrs. Deokseong.

Are you saying that you need to add an article to this person?

That virtuous lady, that virtuous lady's eyes were colder.

Then he looks at Gabiya and says a stern word.

"get out."

``Yes, yes……!''

Gabiya runs out in a hurry.

With a bright red face, he seemed to be in a state of panic, even hugging the blanket. No, what am I supposed to cover myself with… … .

And if you're going to run away, you should've gone together. Are you saying you're going to run away alone in this awkward situation without any sense of duty?

Take me too.

But Gabija had already jumped out.

And even if Qing runs away now, where will he go?

So what?

Qing looked at Madame Deokseong.

Qing gulped at the sight of his wife pouring out a dark, clumpy energy.

Qing tries to smile.

``Hehe, uh, hello.''

Madam Deokseong looks at him silently.

It was an incredibly awkward time.

``Uh, uh, could you please say something…''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was often said that there were no parents who do not recognize their children.

That was the feeling of a parent, a deep soul connected to a soul, it was natural to recognize my child, created with flesh and blood.

They say that it was a miracle created by the boundless love of parents.

But was that really true?

When people remember someone, it's not just their face or appearance.

A smiling face. The angle of the eyes as they smile and frown, the shape drawn by the wrinkles around the eyes and cheeks, the sound created by the sound colliding with the inside, whether it's a sniffle, like snot leaking from the nose, or a hollow, insignificant laugh, or a hearty, booming laughter.

What's it like when you're flustered? What's it like when you're happy? What's it like when you're sad? What's it like when you're down? What's it like when you're angry?

Of course, people cannot remember such detailed details clearly.

The overall impression formed by these details.

People were made like this, so to know was to notice this part.

So, it was not wrong to say that parents' ability to recognize their children was a miracle and supernatural power created by boundless love.

How many people, other than parents, can hold someone so completely and clearly in their hearts?

And then Madame Deokseong entered the room.

In fact, I didn't even notice such trivial details as the bizarre witch on the bed doing something outrageous.

Just that face that I saw when I entered the room.

Eyes wide with surprise, mouth gaping open in a daze.

A short gasp, and a look of embarrassment as he immediately averts his gaze.

Lips tremble, not knowing what to do.

Here a mother looks at her child.

Although I did not give birth to him, he was a child whom I raised by breastfeeding him and holding him in my arms like my own child.

Madam Deokseong's eyes tremble.

Here was a child I never knew I lost. What the heck.

My heart feels like it's going to break into a thousand pieces.

That was the moment.

Madam Deokseong flinched at the strange expression on the familiar face that was still watching her.

Isn't it the awkwardness and wariness of looking at a stranger?

``Princess Yeonsul?''

``Ah. Are you perhaps someone sent by the Empress? Um, um.''

The expression that followed was relief, followed by embarrassment, and then a look of surprise again.

``Oh, I guess you didn’t see the scene just now. It’s not like there was anything weird going on. I was just curious because you said you’d show me Aekyung. Is it really just pure curiosity? Honestly, how can I resist? So, if you could keep it a secret, hehe.''

The sound of that awkward, headless laughter makes Madam Deokseong's head spin.

You really were a princess!

Who else in the world but Yeonsul would commit such a crime in the middle of the Forbidden City?

Showing Aekyung? How on earth could Yeonsul resist that? I can clearly see her clinging to him, her eyes sparkling, begging him to show her quickly.

Finally, a tear fell from the wife's eye.

Qing was embarrassed.

No, was this something that needs to be done until the end?

No, what did I do before that, I was just looking at something a little, a little embarrassing.

Mrs. Deokseong cried.

And then Qing confessed.

"Oh, that. I'm Ximen Qing. I don't know much about Yeonsul, but do you think she looks that similar? I didn't mean to deceive the Empress or anything, but even if I said no, she wouldn't listen, and she was so sad…"

It's not that they look alike, but to Lady Deokseong, it sounds like she's saying it herself.

furthermore?

"Let's get this straight. You have no memory of your childhood, and you regained consciousness in a cave near Geonpyeong six years ago. Is that what you're saying?"

"yes."

``And then, begging, ah, how, while begging and wandering, you were picked up at the Shinnyeomun and came to this place……''

``Yes. I learned martial arts before.''

``Would it be okay if I sent someone to investigate?''

``Ah. Back then, it wasn’t like this. If you were to ask the Geonpyeong kids, or rather the Geonpyeong people, about the beggar they called ‘Changmyeonyeokguinyeon’…''

Mrs. Deokseong staggered.

Changmyeon was a face with bedsores, and Yeogwi was a devil who spreads plague, so I think I know what Changmyeonyeogwiyeon looked like.

Although you say it might not be you.

The more I listen to it, the more it fits perfectly.

And how could I not recognize this face, this sturdy physique, this voice?

Now that I think about it, I wonder how I ended up being fooled by the palace's fake magic.

Yeah, I thought it was suspicious from the beginning.

Even though they were entangled, their faces were different, and even though it was the aftereffects of the fever, their voices were different, and at best, there was only one body, an obscene and vulgar body.

Besides, how can a person's personality change so drastically?

It was Madam Deokseong who had just erased from her mind the thoughts she had lamented while fighting in the hill battle as if they had never happened.

``Princess, my goodness, princess. Ahhh…….''

``……? What I didn’t just say-''

"How much hardship must you have endured? Your complexion was so pale, and your hands were so cold. My goodness, it's freezing."

"hey?"

``Still, I’m glad you came back here.''

Madam Deokseong suddenly stops talking.

I'm glad you're back, but where have you been now?

Healing room. This was the prince's inner chamber.

Suddenly, the image of the ladies of the palace, including the beautiful woman kneeling in a row in the front yard, flashed through my mind.

Why would they come? The Empress must have sent them.

Why did you send it? Because you had to stop the wedding.

Why did you stop it?

Lady Deokseong's face turned pale.

``Oh my god. How could…!''

``Madam? Are you listening to me?''

``This was not the time for me to be like this!''

Madam Deokseong suddenly got up with a pale face and quickly ran out of the room.

It was so urgent that the door wasn't even closed.

Even the flustered Gaby left and closed the door behind her, as if it were a habit that the palace maids had become accustomed to.

It meant that it was so urgent that I even forgot about that.

And in the room, Qing was alone.

What was it? What the heck?

And then, gurgle.

Oh, it's time to eat.

If this was the case, who will take care of my food?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Your Majesty, it's the princess. Princess Yeonsul. How can you not recognize your own blood relative? This isn't an impersonation. Isn't that the princess Yeonsul?"

At Lady Deokseong's words, the prince was furious.

No, what on earth was the Thousand Flower Sword?

What kind of cunning tongue did he have that led him to the state of Mara, who even deluded the Buddha? (It was true.)

How could you deceive me so thoroughly in such a short time?

``Lady Deokseong, please calm down.''

"Is that really what you're saying? At this rate, you two were going to get married, oh my gosh!"

``Haa… Please, please calm down. What on earth did that woman say? Did she call me Yeonsul, or call the nanny ‘nanny’, or act cute?''

"No, he said he didn't know, but he doubted it. He didn't even recognize me, so he was so flustered by a stranger calling him by an unknown name that he didn't know what to do."

The prince becomes even more frustrated.

``No, he has lost his memory and doesn’t even recognize his nanny. How can he become a shaman?''

"Well, isn't that natural, since the princess has lost her memory? How could someone who has lost her memory recognize her nanny?"

``No, then why on earth was that woman a witch?''

``Prince, don’t you recognize the magic of the swan? She was the wet nurse who raised and fed the swan with your own hands.''

Mrs. Deokseong's expression becomes sharp.

"Now that I look at it, it's a shameless fake from the palace. It's clearly the work of those nefarious people from India. Something about it was suspicious from the start. No one recognizes you, saying you lost your memory. How can memories disappear so conveniently?"

``No, that woman lost her memory too!''

``When the princess woke up, she was in an unfamiliar place. Oh my, how could she wander the rich world without a single penny, a beggar? Aah, aah, oh, my, how difficult it must have been for her…….''

Mrs. Deokseong trembles, not knowing what to do.

Anyway, Mrs. Deokseong was a woman who didn't know how to listen to others.

The prince becomes more and more frustrated.

In fact, even if you ask why the Heavenly Blossom Sword was a real magic, there was only one answer that comes back.

I saw it as a nanny and it was true.

If the answer I got was at least that I didn't know, I wouldn't feel so frustrated or suspicious.

But no matter how much I think about it, there's no way the palace's magic could be fake.

Both of them lost their memories.

But the palace's magic was something he remembered from time to time, so he would occasionally bring up scenes from the past that came to mind.

Heavenly Blossom Sword said he had no memories at all.

Both have different faces.

The palace's Yeonsul had a tangled face, and Heavenly Blossom Sword Yeonsul wasn't that beautiful.

But wouldn't it be logical that after recovering from such a terrible illness, the scars would remain?

Rather than leaving a trace, it would be logical to say that it becomes more beautiful.

Even Heavenly Blossom Sword said he didn't know whether I was a magician or not!

The prince grabbed my bangs.
