\chapter{Forbidden City Diary (2)}

There were six palaces to the east and west of the emperor's residence, namely the East Six Palaces and the West Six Palaces.

This was the residence of the royal ladies.

However, the women of the imperial family were not only concubines, but also the empress dowagers, crown princes' wives, and princesses, who all resided in these twelve palaces and their vicinity.

Once you settle down in the palace, you don't really have to move out of the room, so it's not like you can just arrange them in order of rank, right?

So, who writes what does what, that doesn't become a measure of the power in the struggle.

But still, there was a rough grading system.

Among the six palaces of the west, Seunggeon Palace was considered the most important palace in the west.

Seunggeongung Palace was the residence of the most favored concubine for generations, but at the time it was being used as the residence of a princess.

And the left rear concubine's room attached to this Seunggeun Palace.

The rooms on either side of the rear hall were called back rooms, and were usually used by the maids who serve the master of the palace.

And to the left was the left rear room, and inside it, thick, eerie smoke swirls.

A maid opened the door and cautiously went inside-

``Oh, Your Majesty, what, what was that? What’s that smoke?''

The maid waves her hand in fright.

Despite the thick smoke in the room, there was only one woman sitting cross-legged.

The features of the forehead and nose were distinct and clear, and the corners of the eyes were slightly droopy, giving a languid impression.

It was also a characteristic that the woman of India showed.

A woman sitting cross-legged answers with a somewhat innocent smile.

"Oh, it looks like the incense isn't fully dried. What can I do? I can't ventilate. I'll just have to inhale it. You came at a good time. Let's clear the smoke together."

If you can't ventilate, just drink it.

This was truly a groundbreaking ventilation method.

But the maid seemed to be used to it, so she checked again to see if there was any air leak in the closed door, then sat down next to the lord and held his hand tightly.

And sssup, ha. Sssup, ha. Sssup, ha. Just the sound of someone breathing heavily in smoke.

It was a sight that made you wonder how he could possibly fill the room with smoke after drinking so much.

But that was only for a moment, and soon the smoke in the room began to swirl and clump together into thin threads, seeping into the nostrils of the two women.

It was a strange scene, as if time was flowing backwards, as if the smoke from burning incense was being blown away.

The air in the room gradually cleared of turbidity. It was an amazing air purification performance.

The spirit who had been breathing heavily opens his eyes quietly.

``[So, what kind of person was your new mother?]''

He was fluent in Sanskrit and Indian languages.

``Oh my, don’t be ridiculous. You have such a strong prana that the colors streaming from your eyes must have opened all seven chakras.''

"[They say it's the ultimate martial arts. They call it the Great Circular Heaven? However, the Zhongyuan' chūqi merely imitates our yoga, falling short of the spirituality of the ling blood.]"

For reference, yoga was also called yoga in the Chinese language.

``[So, was the new mother interested in Aekyung?]''

``[Yes, his eyes were really sparkling.]''

The corners of Ling Zhou's mouth slightly rise at that.

``[If you think about it, it makes sense. A mother's power comes from her favor, so how could she refuse a way to captivate a man? Well then, kindly. Inform me.]''

``[Yes, Your Majesty.]''

The maid answered with a bashful smile, then suddenly tapped my thigh.

``[Oh, right. Now that I think about it, I thought the new mother looked familiar, Princess Yeonsul’s portrait! She looks exactly like that!''

It was a sharp eye.

The lord tilted his head at that.

``[Really? I heard rumors that your Majesty was a peerless beauty. If she resembles the portrait, then yes, I suppose the Crown Prince would have been drawn to her.]''

But that was it.

Well, isn't it natural for a woman to be painted more beautiful than she actually was in person?

In this way, a picture of beauty was created that was full of the ideal tastes of the people of the Zhongyuan, which were mostly similar.

When I think about it that way, the rumor that the Mama, who looks exactly like Princess Yeonsul's portrait, was the best in the world was definitely not in vain.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In front of Namsamso's Dangyeongjeon.

To the north, officials in official attire were scattered about in the wide courtyard.

One person lined up side by side took up a fairly large space, but the front yard of Namsamso was so wide.

So, they all kneel down and shout in time to the beat of one, two, three.

``````Your Majesty, this iss not acceptable!!!''''''

``````How can you give your bedroom to a woman who doesn’t know how to be human!!!''''''

``````Please heed our voice!!!''''''

So, it was a blood-curdling petition demanding that the Heavenly Blossom Sword be brought into the healing battle and that it be immediately withdrawn and kicked out.

Why were they kneeling under the blazing sun on a sweltering, humid day after a hot summer rain, arguing about other people's love lives?

Of course, as an adult, it was a situation that could be very concerning.

If we take away the part about the prince's circumstances and the emperor's coercion, wouldn't the picture be really difficult?

The first time I saw Heavenly Blossom Sword, I saw that she was a peerless beauty, the most powerful beauty in the world in this era. As soon as I saw her face, I gave her my room.

It was a situation that anyone could clearly see as if the prince was possessed by beauty and was acting like a strong man.

So, the prince's expression turned sour at the sound of the petition outside the door. He turned sour, really sour.

Considering that the prince was usually gentle and had a flawless personality, his expression was so seriously rotten that it made one exclaim, "Has he been hiding his true colors until now?"

If Qing saw this, she might feel a little strange.

But, the future power itself, can't the crown prince bring one of his own to the bedroom?

If he wanted, he could gather all the beauties of the world in one place and, what was this, in the Eastern sense, he could have fun in the Abang Palace, the Abang Palace of the Six Forests? Isn't he the kind of person with power?

Of course not. (There were emperors who did that, but usually their countries were ruined.)

This was not only the Zhongyuan.

For the subjects who served the dynasty of the entire world, the king's marriage was a momentous event that could not be overlooked.

Because the king's woman was a power in herself, she belonged to the royal faction that supported the king's authority, commonly called the royalist faction.

In other words, the more women the emperor has, and the more women the crown prince has, the greater his power becomes.

Of course, the ultimate dream of all officials was to marry into the imperial family, so just as modern people mutter, "I want to win the lottery," the officials of the Zhongyuan also harbored the wish, "I wish my daughter would enter the palace."

The Emperor was no longer at an age where he was interested in women, and he already has the number of Marquis Jeong and Marquis Seo, so there was no need to add more.

But what about the prince?

It would be best if my companion were my daughter.

But if not, she should never be the daughter of a powerful family.

Even if the daughter of a powerful family was involved, she must be from our faction, not the opposing faction.

As such, it was a time when a huge fight was looming over the crown prince's wife.

At this time, a woman suddenly rolled in. Was she a martial arts master? Did she suddenly catch the prince's eye? Did she suddenly take over the inner chamber?

Naturally, regardless of faction, everyone had no choice but to pour out and shout out their resolute opposition.

``Use it.''

The prince was furious.

I don't want to be like this.

What brother in the world would want to marry a woman who looks exactly like his sister?

I'm doing it because I'm told to, really, ha.

The prince also had many worries.

The shape of the eyes that look like they would roll out if you hit the back of their head, the overall look that was so ugly that it was stubbornness itself, a very sullen and disobedient impression, and the pale, grayish complexion that looks a bit sick despite the activity that was not unique to wild boars.

Doesn't this look too familiar?

Of course, I didn't believe the absurd rumor that the Heavenly Blossom Sword was a real magic trick, as my mother said.

I remember my younger brother who was sick for a long time.

The sight of the wooden Buddha's face, which was too much to bear with my eyes, was so utterly devoid of abscesses, cracked, and torn, and yet countless lumpy tumors, like the skin of a toad, were oozing pus.

Even if things get better, how can your face still be so normal?

Even now, the ugly scars of the practice remain, so I walk around covering my face.

Even surviving a disease that even the gods shook their heads at and retreated from was nothing short of a miracle.

It's a shame, but if you managed to survive with only a small scar on your face, you could say you were lucky.

Moreover, what you were saying about the current Yeonsul being fake was that Yeonsul's actions do not seem like Yeonsul's?

So, does that mean that Yeonsul has to live his whole life doing 'Yeonsul actions'?

When I was young, I was just immature, and Yeonsul was just extremely immature, but I can't express it as immature, so I was just so immature that I went to the trouble of being a fool, isn't that all?

It may have been because he was a small child with a body as big as a bull that he frowned even more.

If he had been of an ordinary, small and simple build like everyone else, wouldn't there have been any expressions like 'like magic'?

No, but it would have flown anyway.

The current practice was just a matter of iron.

Even more so because I was almost dead.

Sometimes I miss the old days of martial arts, but I don't think I lost, and I think it was fun back then.

Yeonsul was now past the age of marriage, so he can't remain a child forever.

Although the actions of the current Heavenly Blossom Sword were similar to those of a magician, didn't the Emperor always say that the princess's behavior was no different from that of a lowly barbarian?

That is, it would mean that lowly barbarians act like Yeonsul, so it would be natural that Heavenly Blossom Sword's behavior resembles Yeonsul's reckless past days… … .

However, what the prince was worried about was not the absurd claim that the Cheonhwa Sword was the real magic and the palace magic was a fake magic.

When and where on earth did Mother see the Cheonhwa Sword and mistake it for her daughter?

And if you want to clap your hands, you have to touch both palms together.

My mother wouldn't have immediately thought it was a magic trick when she saw the Cheonhwa Sword.

There must have been a wicked scheme to exploit the mother's delusion and gain some great advantage, as the Heavenly Sword was clearly suited to him…

Well, since the mother was the mother of the country, I have to win the favor of the queen of the nation, ah!

A thought suddenly crossed the prince's mind.

\textit{It was said that Mother stayed at Divine Maiden Sect and performed a ritual for about a month before bestowing all the land in that area.}

\textit{Since they officiated the ancestral rites for the Empress, it was natural to grant them the land around it, but I heard that she gave them too much.}

Bang! The prince slammed the table.

That's definitely true!

\textit{This wicked woman must have tricked and deceived my mother, who was still not of sound mind.}

\textit{Of course, there's no way my mother would go mad. And she's still so sane.}

The prince's eyes looked fierce.

\textit{I will reveal the truth about this pretender.}

\textit{And I will make sure that those who dare to mock the royal family receive a thorough punishment.}
