\chapter{Forbidden City Diary (6)}

Qing sits hunched over with both feet on the pillow, his chin resting on his hand, and he stares blankly into empty space.

The face of a beautiful woman with a sharp and stubborn face.

But with a dull expression, as if bored or empty, without any emotion.

Because his chin was propped up, his eyes were open wide, and a blue square shape that no one else could see was reflected in them.

Now, looking at the status screen doesn't cause me to have a seizure, but I can't help but feel this subtle discomfort that sinks my mood just by looking at it.

What was your true lineage?

What about the fake princess?

This was a screen that has been postponed and ignored until now.

If there was a volunteer who imitated a deceased child to comfort an elderly person with dementia, everyone would applaud them.

A good story, yes, anyone can see that it was a good story.

But what if the dementia patient was the wife of a wealthy family and wants to leave her fortune to a volunteer?

From then on, could it become a good story?

And before that.

Indeed, can it really be right to impersonate a loved one who has lost someone and console them for their loss, even if it was done with good intentions?

And I, if this body was indeed that of the princess called Yeonsul.

According to the Empress Mama's words, Princess Yeonsul was already dead, or, as the saying goes, brain dead.

It was not entirely uncommon for brain-dead people to miraculously regain consciousness.

Even if the odds were slim, it wouldn't have been impossible. In the past.

But now, that can never happen again.

Because I'm here.

Blue's perspective.

Death by sexual assault, was the body snatcher not responsible?

It's been a while since I've felt the heat from my hometown, but I don't feel any better.

I don't know if baseball was the fans' responsibility, but isn't this clearly my responsibility?

Now, I don't have any doubts about whether you're trying to manipulate me by questioning the status window, but then what kind of concept was a fake princess?

Did those Indian witches literally set up a stand-in, saying, "Oh my, the resurrection failed?"

Or, if there was some kind of magical technique to block the flow of energy and make people fly around in the spirit world, there was no guarantee that there was no spirit.

Even if he had already been to the afterlife and lost his memories, what if he had really transferred Yeonsul's soul into a new body and sent it back?

Then what about the judgment of the status window?

It could still be fake though.

Because it's true bloodline. After all, I'm the one who occupies the body with the blood of that great emperor flowing through it.

But, even if you think about it, what will happen-

That was the moment.

-Mom, aren't you going to the market? I'd like to bring you dinner.

"oh."

The voice of Madam Deokseong, who had run out in a flash, and the news was very welcome.

``Yes, please.''

-Yes, Mama.

And then, knock, knock, knock! Multiple doors open in succession to the left and right, and maids carrying huge dinner tables come rumbling in.

The smell of food there, wow, wow!

I was already hungry, and since I was left alone, I must have been so hungry that I even looked at the status window that I had never looked at before.

Gulp!

A sound that resonates with all its might in response.

While the maids were startled, Lady Deokseong's eyes become moist.

Yes, that sound! Why had I forgotten it? She was the princess who would shout so proudly, as if the heavens and earth were shaking, just a little after mealtime!

If Qing had heard the inside story, she would have wanted to ask what kind of princess she was and why such a princess existed.

First of all, I was so hungry.

Even without that, Qing had to eat at least four meals a day.

Of course, I'm not saying you only eat four meals.

Because you can eat green onions all day long.

At least four meals, originally three, but thanks to the unprecedented and miraculous power of Saengsimgyeol and Jinjueonga, which increases the amount of food consumed, you have to eat four meals, one more meal.

Qing gulped.

Wasn't Qing already obsessed with thoughts he didn't want to think about?

Thoughts were rebellious creatures that, if you don't try to think about them, will just bloom like dust and fill your head, making you keep thinking about them.

To get rid of it, you have to turn your attention to it for a moment and completely forget about it.

And for Qing, there was no ventilation method as effective as eating.

So, a hearty meal begins.

Mrs. Deokseong, who was left behind to serve the meal, looked dumbfounded at the sight of her voracious appetite, as if she was chomping down on the plate, let alone serving it.

In fact, rather than being completely absorbed in something, it was more like being overcome by a kind of deep emotion, or memories, or nostalgia for the past.

Princess! Yes, this was how you should eat, princess!

You've become more cheerful than before!

This was my princess, my magic!

Affection gradually appears in Lady Deokseong's eyes.

It's a gaze that seems to drip with honey.

They eat everything without being picky, but their top priority was spicy, sweet, and salty meat, followed by sweet and salty meat.

I prefer vegetables that were crisp and juicy, lightly blanched, don't eat too much of hard ones, and enjoy soft ones less (though I don't dislike them).

And most of all, that ball!

The adorable sight of a squirrel stuffing its cheeks with food and munching on it, just like a squirrel stuffing seeds into its cheeks.

And when I eat something and it tastes good, I get really excited and the corners of my mouth rise without me realizing it, and my eyes arch gracefully.

Qing, who was inhaling it so mindlessly and eating it properly, suddenly came to his senses.

I was so hungry that I lost my senses for a moment.

Qing glanced around and put down the ribs he was holding in his left hand.

``Ahem.''

Ximen Surinryu beauty, beauty recognition.

Pick up a grain of rice the size of a soybean, and about forty grains was appropriate. When using chopsticks, turn your wrists widely to put them in your mouth. When chewing, your jaw should not move up and down greatly, and you should never move it left or right… …

It was a very perfect meal for a beautiful woman.

However, even though he has already revealed his true colors enough, he was only now acting calmly.

Then it was Lady Deokseong's turn.

``Mom, here’s some grilled pork. Okay.''

``Oh, I can eat it.''

``Okay. Ah.''

Jeok-i was a dish made by mincing meat, mixing it with starch powder, skewering it, and grilling it. It was the original ancient tteokgalbi.

Looking at Madam Deokseong, who was right next to him and holding out a skewer, Qing felt a very familiar sense of foreboding.

This person, isn't this the Empress Dowager dressed up?

The part where you were anxious because you can't feed them was the same, and the part where you don't listen to others was the same.

What would happen if the two of you talked?

I wonder if they were just talking about different topics and talking about what they want to say.

Anyway, Qing was weak to favors.

I wonder if this was the expression on the face of a mother bird looking at her baby bird eating its prey with its mouth open.

Well, it's uncomfortable. And, well, it tastes good…

Qing eats the food like that.

Even though he didn't say anything, his foresight to put the galbijjim, which he had saved for the last point, in last was amazing.

Should I say that he was very skilled?

``Mom, I’ll bring you another serving.''

``Oh, I’m starting to feel a little full now. A whole table would be fine, but maybe some fruit or snacks would be nice…''

It's not that I can't eat, it's that I'm starting to feel full.

It's not that I can't eat it, but I'm saying that one serving was too much, so bring out some fruit or snacks.

It's a sight that makes you wonder what else you're talking about after eating so much.

However, Madam Deokseong answers with a very satisfied expression.

"Oh, ma'am. According to the palace's rules, the lower classes follow only after their superiors have eaten. Of course, I, the servants, shouldn't dare to think that way, but how can human resentment be controlled? I'd like to prepare another table and serve it to the lowly ones as well. Is that alright?"

"ah."

The food left behind by Qing was entirely for the maids of the Hillbangjeon.

In fact, the greatest pleasure for the palace maids was cleaning up after these luxurious dishes!

If you scrape it clean like a radish, the maids will have to swallow their tears and eat only cold rice dipped in soy sauce.

So, wouldn't it be nice to serve them another meal and win their favor?

The expression on his face was painful.

I've been scraping everything clean so far… … ?

Somehow, the expressions of the court ladies who were clearing the table looked very gloomy.

If you feel sad about eating, how sad will you be?

For this reason.

A warm breeze blew through the kitchen after a long hiatus.

Although they did not dare to make a sound, the palace maids expressed their joy by dancing silently over a dinner table that was practically new.

That was when.

``What were you guys doing without any brains? Huh.''

Gabiya, a tan-skinned woman from India, appears and gives a hard time.

Since Gabya was a court lady who serves the king directly, she was considered to be of a higher status than the court ladies who were attached to the palace but have not yet served their master.

Then, he fills my plate with the most precious dishes and then walks away, acting proud.

The remaining maids extend their thumbs between their index and middle fingers to see him off.

It's not known where this hand gesture originated, but surprisingly, it's used for the same purpose in almost every culture.

Perhaps it could be said that it was a miracle created by the subconscious of humanity, the empathy that shit was shit for everyone.

Meanwhile, at the main battlefield of the Hill Defense Battle, a familiar sight unfolded.

It was the sight of Qing lying down with his head propped up on Lady Deokseong's thigh.

``But Mama, beware of that bitch, that Indian witch.''

``Are you talking about Gabi?''

At that, Madam Deokseong ground her teeth.

Hmm. I'm scared.

"Yes, that girl. I don't know what her purpose was in approaching Mama, but she must be hatching some truly heinous plot. I don't know what method she used to appear before Mama, but it must have been some evil Indian sorcery. What kind of dirty tricks did she use to attach such a monster to Mama? If I were to catch her…"

Aduk paduk.

Qing carefully raised his hand.

``Oh, I picked it. I thought I’d take a look at Aekyung…''

``This damn bitch, how dare she seduce such an innocent mother? She must have known that she would be vulnerable to such a spectacle, so she must have been using her tricks.''

She was a woman of virtue who was good at changing her words.

Instead of asking questions, Qing carefully asks a question he has been curious about.

``But, the Empress was like that too. What exactly was the Indian witch?''

``Those women claim to be monks of the Cheonnyeo Temple in Cheonchuk, but aren’t they the very women who opened a Buddhist temple in the Dongyuk Palace and settled there? Ha, how could they have allowed such a strange temple to be built within the Forbidden City?''

For your information, in the residence of Lady Deokseong, there was a female Buddha statue obtained from the strange temple Cheonnyeo Temple, and she offered Buddhist prayers to it morning and evening.

Well, until I met Qing, until I offered my prayers this morning.

The Cheonnyeo Temple was a group of very wise monks who saved the life of Princess Yeonsul.

And now?

These guys, how dare they deceive me… …!

Madam Deokseong was the quickest to erase unfavorable memories.

Anyway, Lady Deokseong reveals what she knows to Princess Yeonsul, who has lost her memory.

The princess was sick, and even the gods were shaking their heads. The world was in jeopardy, and her life was becoming increasingly dangerous.

At that time, there were women who came to the palace to treat the princess, and they called themselves the monks of the Cheonchuk Cheonnyeo Temple.

And when the unconscious princess was carried out by the monks, wouldn't she have walked on her own feet when she returned?

So when the Emperor asked if there was anything they wanted, their leader Asiya answered,

Our sect was persecuted in India and driven out to the Zhongyuan, but even here, there was no safe place.

But there exists a palace in this world that was the safest and most impenetrable, and we dare to seek refuge in its forbidden territory.

If you accept us, we too will repay your kindness for the rest of our lives as court ladies according to the palace's rules.

It was said that the Emperor bestowed a plaque on one of the rooms of the Dongyuk Palace and granted the position of Dharma Master to their leader, a nymph named Ashiya.

And, as a court lady, she kept her promise to devote herself to the Forbidden City (though she couldn't have broken it), but now she's spreading like a poisonous mushroom here and there in the Forbidden City, plotting something.

The back part has a lot of mixed feelings.

Anyway, the outline of the lecture was like this.

So, the leader of the Indian women was Ashiya, a woman called Asya in the Indian language.

And the worries she had before eating.

He was also the person who could resolve the question about the status window.

\begin{quote}
	[Lineage Mission - Roots]
	
	[You have encountered your true lineage.]
	
	Drive out the fake princess and reclaim your rightful title as princess.
\end{quote}

Here, the rightful monarch refers to the title of princess.

He was not saying that he was succeeding to the throne and that he should sit on a high chair.

Qingdo understood that much, so rather than trying to be a fiery filial piety, or rather a frost filial piety, he wanted to first understand the series of circumstances.

And if there was a person connected to him.

That was when.

Just as a tiger comes when I speak, and when I speak of Cao Cao, Cao Cao comes running, and when I talk of ghosts, ghosts appear, a sound was heard at an amazing time.

-mama……

A very timid voice quietly drifts in from beyond the door.

-Uh, was Madam Deokseong inside… …

Is Madam Deokseong that scary?

Well, it was a little scary.

``I think the lady has something urgent to do.''

-Oh. I see! Mama, was it okay if a celestial maiden comes inside?

"uh."

``Haha, mama.''

The door opens and Gabiya comes in, shaking her hips with that usual deadly sway.

Then, following Qing's gaze, he looks over his head and asks again with a puzzled look.

"mama?"

Qing answered him, waving his hand.

``Oh. There’s a bug. Don’t worry about it.''