\chapter{Forbidden City Diary (11)}

Even the ladies of the palace learn to be like the fairy princess.

However, even though it was called the Fairy Gong, it was not a type that has the effect of accumulating energy through full-scale internal energy study, but rather a type of pupil-type, aesthetic gymnastics.

It's only natural that the palace ladies, who have nothing else to do, would gather in a group in the backyard every morning and wave their hands and feet around.

However, swordsmanship was clearly a skill intended to harm others.

In the Forbidden City, where even the trees were uprooted to prevent assassins, they were teaching swordsmanship to a princess who was about to marry into a distant country anyway?

Of course, Qing was neither sharp nor sharp enough to notice these contradictions.

Didn't you just say you couldn't learn? Something like that.

``Oh. That’s it.''

The currents startle Gabija.

Gabiya was unresponsive. She appears to be a corpse. Of course, judging by the subtle rise and fall of her chest cavity, it seems she has some kind of life attached to her.

With a miserable face, his eyes were rolled up and empty, unable to even close, and he just stared into space.

The current didn't just stop at examining it, but approached it, poked it, opened the front flap, and slung it over his shoulder.

``Let me put this aside for now and then I’ll tell you.''

``Oh, you’re going to put it in the dorm? I’m not going to bury it somewhere dark.''

``Hey, there were plenty of better ways to bury it.''

Is Qing really that long? Just kidding… …I guess so?

Anyway.

``Mama, hehe, princess. Oh, Mr. Beom Gi-do-wi, do you remember him? Mr. Beom Yak-gong Gi-do-wi. The one who was in charge of your bodyguard.''

The prayer committee said that the position was responsible for protecting the royal bloodline.

Of course, Qing has no way of knowing.

"no……."

``I see…….''

The shoulders of the ocean current slump.

But that too was only for a moment before he returned to his smiling face.

"The princess asked me to teach her. Why, don't you remember? You kept nagging me for almost a month, demanding I quickly master swordsmanship…"

The King of Yuansui, eight years old.

It was a time when Yuansui, who was not a princess, was surprisingly an ordinary child who was not outstanding.

One day, for some reason, the eyes of the Yuansui Lord, who saw the long sword of the escort, sparkled and shone dangerously.

So he kept saying, "Teach me swordsmanship," "If you teach me swordsmanship, I'll reward you," "If you don't teach me swordsmanship, I'll jump off of here," "I won't eat until you teach me swordsmanship," "Of course I ate well, but I just lay in bed and it seemed like I was sick because you didn't teach me swordsmanship," "I think this was lovesickness or something," and he kept nagging me thousands of times a day, "Swordsmanship, swordsmanship! Absolutely swordsmanship! Swordsmanship even if I die! More than food… … That's not it!"

"hmm."

``That’s why we trained together.''

I heard that the person in charge of the prayer committee had come up with a plan of his own.

If you want to learn how to wield a sword, you must first master the basics.

Perhaps he thought that he would soon drop out because he couldn't endure the arduous basic training.

But he said he endured it all.

For almost three months, he ran when told to run, sat when told to sit, and lifted when told to lift, giving it his all. I guess people were impressed and thought, "Ah, this was no ordinary persistent kid."

The secret teaching of swordsmanship began.

The Yuansui Lord began to grow tall and strong, like a bamboo shoot.

So, ten years old.

The legend of the mighty, powerful, and gigantic princess of Yuansui began with the title of princess… …

The Empress clearly said that from a young age, the body of a grown adult was like that of a grown adult.

After hearing this, I feel like there must have been someone else who was the culprit.

``What kind of swordsmanship was this? But you wouldn’t have taught me just anything, would you?''

"Hey, you still remember, don't you? I heard about the Cheonhwa Sword, too. I heard you're still renowned as a master of the Moon Sword. Even though you've lost your memories, you must have never forgotten the training that was ingrained in you."

"uh?"

"You said you'd become a blue-haired woman after reading the "Wolnyeo" chapter of the "Oyewolchunqiu," and you wore only blue skirts every day. That's why you even insisted on wearing a tiger-shaped skirt in the first place."

Moon Sword? You learned the Moon Sword?

When I first fell into this primitive, ancient, uncivilized world of the Zhongyuan, the only martial arts I had.

It was a hidden element of the Martial Arts Dictionary, and was also the basic martial art when you enter the name as Acheong.

If Princess Yuansui had mastered it.

It was said that the Beom Gi-do-wi passed down the true copy of the Wolnyeo Sword Method, Wolnyeo Heart Gyeol, and Wolnyeo Sanbo three-part bundle.

Well then, I guess it must have been Princess Yuansui who was the previous owner of this body.

If it matches up to this extent, um.

Then suddenly a thought occurred to me.

``Hmm. So that person named Beom Gi-do-wi was also close with Princess Yeon-sul?''

"Of course. She's practically my own daughter. Oh, hehe, the girl's got a cube again. Well, that's what I mean, hehe, you know? Oh, he's been promoted to the position of Jang In-Gido-Wi and was in charge of the Hwanggeukjeon. We'll go see him later."

``Somehow, I feel like I’ll see it anyway……''

Qing trails off with a sour expression.

Somehow, somehow, I have a feeling that another burdensome character will be added in the not-too-distant future.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The palace maid carefully places the tea table in front of Qing.

Carefully. Very, very carefully.

Could it be because of the abundance of snacks on the plate?

A typical tea table might have a couple of pieces of sweets to accompany the tea, but the Qing tea table was full of nothing but sweets, mountains of sweets.

The cookies were piled high on the plate, and the steepness was very precarious, so I was careful not to drop one, so I put it down-

Bam.

One of the round cookies lost its balance and fell, rolling around in front of Qing.

It was a fried Korean sweet called yakgwa (yakgwa).

It was the moment when Qing picked it up without thinking.

``Oh my God! I have sinned against you! Please forgive me!''

Bang! The maid roughly banged her head and trembled, begging for forgiveness.

``Huh. It’s fine. I thought it looked a bit dangerous from the moment I entered, wondering who built it.''

Then, thump! This time, the maid next to him blocks her head.

``That, that, Lord, I committed a sin worthy of death! That, the plate was small, so I couldn’t help it…!''

Qing blinked her eyes.

No, what was it? Is someone going to eat it?

For some reason, today, the palace maids at Healbangjeon can't even make eye contact, and if they do, they all tremble and lower their heads.

What the heck? Why am I like some kind of symbol of fear?

Well, the maids saw the miserable state of Gabiya when she was brought in last night.

Wasn't it a horrific detail, with eye makeup smeared all over her face, her mouth glistening with thick saliva, and her eyes rolled back open and she passed out?

The palace maids were not very pleased with the behavior of Gaby, who immediately acted like a superior just because she was an exclusive servant.

But those miserable words were accompanied by an inevitable sense of deep compassion, and at the same time, a sense of relief.

Rather, isn't it a good thing?

And then an indescribable horror.

A palace maid's realistic dream was to be in a position where she receives the favor of a powerful master.

And the most realistic fear was the daily persecution under an evil and cruel master.

Even once you become a slave, you cannot leave of your own free will, and you will have to endure such terrible treatment forever.

Moreover, these terrible mothers sometimes hire people to deliberately harass them.

In fact, it was common for the lonely concubines of the Dongyuk Palace to harass the palace maids in order to appease their frustration at not being visited.

They say that the number of cases decreased significantly after the Cheonnyeo Temple was built, but it was still a place where ominous information was exchanged, such as someone being beaten in the palace, someone getting hit and having their cheeks swollen, etc.

So, if I make a mistake, I might end up like that every day.

Even that tiger-like ocean current was so fierce that it made my eyes swell and my throat hoarse. It was Mama.

If Qing found out, he would be very upset.

First of all, Haeryu was crying alone and Qing didn't touch him at all.

There was only a small misunderstanding with Gabiya, and it was true that there was some ambiguity as to whether I can say that I cried or not just looking at the result.

but.

``Hehe, mama.''

After the maids left, Gabiya filled Qing's teacup, then quietly took the seat next to her, hugged her arm, and clung to her.

I didn't mind the soft, fluffy feel of the fabric touching my biceps, but, um, why was he doing this again?

``Gabi?''

``Yes, Mama. It’s Gabi.''

It's not Mama, it's Mama-ah. The sound was drawn out and mixed with a nasal sound that was probably meant to be cute, and it's quite burdensome.

``Isn’t that a little uncomfortable?''

``I still have trouble controlling my body. My muscles were sore. Someone tormented me so much. Ugh.''

Gaby whispers in his ear, blowing a painful groan as if blowing a whistle.

Qing shut his mouth tightly.

Yeah. I did something regrettable… … .

Qing turns the conversation around.

``By the way, what was the event at Cheonnyeo Temple like?''

Haeryu left his seat because His Highness the Crown Prince had called him, and Gabya had just returned from attending the Cheonnyeo Temple event that morning.

And currently, the evil karma was forty-two points.

What kind of event were you doing that you're suddenly accumulating good deeds and returning?

``I’m sorry. Since this was a royal event, even if you were Mama, I can’t speak carelessly.''

``Imperial event?''

"Yes. But if you're really curious, for the next event, I could personally ask Your Majesty about it. Is it okay to speak to Your Majesty?"

"Your Majesty? Ah. If Your Majesty was attending the event, then well, there's nothing I can do."

Qing was easily convinced.

If it's an event attended by royal family members, it's only natural that you can't talk about the details carelessly.

If it had been when Gabiya was receiving the award, it might have been suspicious.

The child knew that his intentions were somewhat impure and that he did not intend to cause any harm.

And, there was something else I actually wanted to ask.

"Oh, right. Do you happen to know anything about Princess Yuansui? I heard that when she was seriously ill a long time ago, the Cheonnyeo Temple showed her effective treatment."

"Ah. That happened before I entered the palace. The Lord healed Princess Yuansui, and in return for that, he granted us, the Lord, a place to stay."

After receiving the signboard of the Heavenly Maiden Temple, Ashiya, the leader of the Heavenly Maiden Temple, called together the sisters of the Heavenly Maiden Temple who had fled from India.

Gabya entered the palace after that and began her life as a court lady, which was why she was still playing around in the empty palace without a master to serve her.

"Thanks to you, I got to serve Mama. Is this fate, a connection? The evidence of that connection, the bloodline between Mama and me, etched directly into my mind, oh. Even thinking about it makes me dizzy…"

It was Gabiya who was leaning her head back while making an unknown sound.

This guy surprisingly doesn't know anything…

It's like pretending to be deadly but being secretly sloppy, I thought it would be like this.

However, one thing was certain: we cannot overlook the 'evil witches of Cheonnyeo Temple' that the Empress Majesty speaks of.

So, did Ashiya change the lord? Then why did I wake up alone in a cave?

What if the real soul was real?

Then, wouldn't it be possible that the princess in the Forbidden City right now was the real princess?

The real princess of magic said, 'Abandon ship!' and escaped from her body, boarded a new body, and I entered the remaining shell.

Then, it might be just a few minor misunderstandings that overlapped, and we might be able to return the truth to the old acquaintances who miss Princess Yuansui.

I just need to live my life without being entangled with the royal family anymore.

Then everyone lived happily ever after.

How great would that be?

hmm.

If the Empress doesn't dare to cheat you and make a fuss about it, well, I don't think so.

``Hmm. Well then, could I possibly meet that Ashiya?''