\chapter{Forbidden City Diary (10)}

Qing's eyes narrow.

The impression of the blue was ever-changing.

It was because of the expression on his whole face.

She was a fresh-faced beauty with a slightly chubby face when she closes her mouth, making her look like she doesn't listen to anyone.

When she was happy, she blooms dramatically and was the pinnacle of gorgeousness, but when her heart was filled with murder, her beauty, which rivals the best in the world, disappears into a devilish smile that extends all the way to her ears.

When you don't know, your eyes and mouth become infinitely distorted, 'that expression'.

When the Ximen Surinryu beauty smiles with a subtle, awkward smile, she can unleash a destructive power that can stop the hearts of all people in the Zhongyuan, regardless of age or gender.

And at certain moments, a breathtaking sensual innocence takes over, a look that bewitchingly evokes the cruel innocence of a child poking and tearing at bugs.

Mo Joo-hee, daughter of Murong-mo, was the type of person who makes someone's heart beat as if it were going to burst, creates a warm heat in the lower abdomen, and makes them cross their legs and rub them together without realizing it.

Right now, at this very moment.

If we were to look at the cross-section of Qing's head through the virtual staging method used in Qing's hometown, we would see the upper part of the brain, which was a round room that spreads out into an area.

The upper room was covered in vivid, hot pink wallpaper, creating a splendid, almost eerie atmosphere.

If you look closely at the bright pink wallpaper all over the upper floor, you will see that it was not wallpaper, but a flow of some kind of fluid, a sticky dripping of paint from the wall.

The proof was the peach-colored raindrops falling one by one from the ceiling of the upper hall.

Below that, a tiny Hwanhee Jinki was wrapped around her body with only a few strands of gold thread and a few sheets of transparent cloth.

Hwanhee Jinki stretches out his finger with a serious expression, picks up the sticky, peach-colored drug seeping from the wall, and puts it into his mouth.

Hmm. Hmm. Wiggling thin eyebrows.

Hwanhee Jinki, who had been savoring it for a while, soon nodded.

Then, in a fit of excitement, he starts dancing, jumping around inside the upper chamber.

That was the moment.

The door creaks open and another little girl, a dishwasher wearing a Buddhist robe, steps into the upper room.

Then, as if they had encountered a natural enemy, the peach-colored drugs all retreated, keeping their distance.

Hwanhee Jinki, who had his face crumpled, spreads his palms with a determined expression.

Since ancient times, pleasure has been considered a spiritual liberation, a passion that allows us to forget all our evil thoughts and become absorbed in something, and it was the best way to bring peace to the body and mind.

The upper stage was already covered with murderous intent and was filled with the most ominous colors.

We must actively utilize these opportunities.

The old man frowns, then shakes his head and turns around to leave.

And then, the dance line of Hwanhee Jinki, jumping, spinning, and jumping again, continued on and on… …

Gabiya closed her eyes tightly.

I should have anticipated this situation!

The women of the Zhongyuan were a shy and stubborn people, and were very reluctant to touch their own naked bodies unless they were bathing.

But isn't Mama very open-minded and even passionate?

Moreover, even though Mama did not show any resistance to these actions, she also seemed to be unaware of these matters.

As his breathing became increasingly rougher, a trembling sensation was mixed in, and even though he was trembling, his expression was filled with doubt.

With such a body that was so obscene, with such an honest body that responds so faithfully, yet you were so innocent!

A woman who was just sensitive and doesn't even know what kind of pleasure she was experiencing!

It's easy this way.

So, it was a big mistake to decide that we could proceed boldly like this.

If things were as they were, the direction method would start with extending the hand little by little from the hand, neck, and back, and the process of breaking down the guard and making it a natural thing was in progress, but I was impatient.

Because I think things will be easier this way.

More than anything, I want to see the disheveled appearance of your majesty, who was not even aware of my pleasure!

but.

Even though I knew that Mama was a martial artist, and a renowned martial artist at that, I didn't really understand what that meant.

When people get excited, they tend to forget even the pain in their bodies and their actions become rough and bold.

Even if the ladies of the palace were in a state of irrationality, they were opponents that Gabiya, a true yoga practitioner, could easily subdue.

But a martial artist? A master at that?

Besides, what on earth was the identity of this dependable court lady?

How can one subdue an orthodox yoga practitioner with pure physical strength alone?

But Gabiya's closing of her eyes did not mean resignation or giving up.

Quite the opposite.

It was to organize the disorganized body and mind and to extend energy from the seven acupoints.

Yeah, even if Mom did that, she would just be an outsider who doesn't know how to use directions, and would only follow along based on her experience of receiving them once.

Of course, even for oneself, it can be dangerous to pour out that much direction.

Isn't this a special product that was personally prepared by the Lord himself, that promotes blood flow, relieves fever, and awakens the sleeping senses to make them more sensitive?

However, for a yoga practitioner, pleasure was a part of the training to reach extinction, and pleasure was not dependent on the body, but was controlled by the mind, which was the practice of the celestial spirit.

Not becoming excited by physical stimulation,

The clumsy hands of an outsider cannot invade the hands of a true practitioner!

So Gabiya calmly builds a wall in her heart.

The body was finite, the mind was infinite, everything we see, hear, and feel was dependent on the mind, so my mind was clear and transparent, and cannot be invaded… …

Gabiya was now standing in a quiet garden.

A tranquil garden with a lotus pond.

The high walls surrounding her rise high into the sky, unwavering and unwavering.

And the sun was warm and a cool breeze caresses my cheeks-

That was the moment.

Boom! Dddddd!!!

The walls shake with a huge vibration.

As the stone dust flew up, Gaby's new form staggered, and a gasp escaped from its mouth.

Oh, why?

Bang! Bang! The loud noise of the wall pounding again.

As the surface of the lake ripples and the water gushes out, lotus flowers float up all at once and bloom in full bloom, painting the entire area in red and white.

Gabya, who had collapsed, unable to control her body, saw eight pillars towering high beyond the castle wall.

Eight unusually white, long, and beautiful fingers stretch out endlessly, casting shadows.

What the heck, what the heck? Why!?

Gabiya observes her body again.

Eight fingertips dancing across the skin, your own vitality responding to them as it pleases, this was resonance, the resonance of prana.

In each area that he touched, his own energy moved as if it were yearning from within, and he felt a dizzying ecstasy, as if he was directly stroking the connected acupoints.

Gabiya's heart sinks.

This was the stage of unity, of unity! The stage of unity where you embrace the other person with your spirit and heart, embracing them with your own bloodline!

But why! How! I did not open my heart to Him!

Gabiya twists her body wildly.

But I can't resist the limbs that were held up and down, the walls were collapsing, the garden was shaking, and the thunder and lightning were loud and dizzying.

Suddenly, I recall the basics of the ancient yoga practice, the practice of primitive yoga, which, despite being more primitive, produced countless people who passed away.

Exactly, seriously.

If you treat others with sincerity, it will lead to true pleasure through your mind and spirit.

Surely, Mama, would treat me that way?

I, the Heavenly Maiden, simply cannot endure it… …!

If Qing could read Gabiya's mind, she would have thought, "What the hell were you talking about?"

Even Qing had a secret plan.

The life-saving techniques of the Hwanhee Palace, learned with no selfish motives and with only the pure desire to defeat Eonyeonyeong, the ruthless destroyer of the world!

The ultimate weapon, Joyful Yoyo Gong!

It was the Joyful Yoyo Gong, which was operated with the internal energy of the Girl's Joyful Gong, and had the ability to make even a stone woman faint.

It was a remarkable scene where the best health-giving techniques of India and the best health-giving techniques of the Zhongyuan were dramatically combined in one place, as the best of the best manufacturers in India were poured into it.

Gaby's face was covered in tears, her characteristically lethal eye makeup melting away.

``Mom, ugh, I, stop.''

"Okay, can you hold on? What the hell was this? What kind of drug did you put on me? Do you want me to explain exactly what this is?"

``That’s, direction, and, hauk.''

Gabija blew.

According to Gabiya's desperate explanation, which was on the verge of losing her breath, the effect of the direction was as follows.

One. It dissolves and removes waste products that have seeped into the skin, and instead, it penetrates with medicinal properties.

It refines the skin, making it clearer and stronger, heals wounds, and has a miraculous effect on various skin diseases.

Two. It warms the body's blood and increases its circulation, raising body temperature.

Thanks to this, the body becomes full of vitality, the root cause of illness was burned away, muscle pain was relieved, elasticity was increased, and it protects against injury.

Third, it awakens and sharpens the senses.

It was a supernatural ability that brings greater results to practitioners who awaken the wheel of passion through pleasure.

``This is, all, everything, everything.''

"Huh? That's it? What about the side effects? Like addiction? Are you still lying?"

``No, no, there isn’t, there isn’t.''

``Hey, aren’t you going to say it straight?''

``Really.''

``Ha, look at this poisonous thing?''

``Ugh, I, no, can’t, ugh.''

And time passes.

As time goes by, it goes by.

Qing slowly moves away from Gabiya's thigh.

Gabiya just sat there, her face drooping, her lips dripping with foam, her eye makeup smudged, and her eyes darkened with only the whites of her eyes remaining.

``Uh. Um…….''

I guess this really was a good medicine.

Um. Well. Um.

Then what if I didn't do anything bad?

I put a lot of good things on my body, and, uh, it helped me a lot with my Yeolrakryun training, right?

Gabija was all blown up.

In addition to the effectiveness of the medicine, the question of why I was prescribed it was also raised.

It was to capture the heart with pleasure.

I just wanted to ask you to rebuild and revive Cheonnyeo Temple, as I have become a precious servant who can entertain you as much as I can.

The current was indignant.

At first I thought, was this right?

And why did our princess become like this?

Even in the past, he was a master of tightrope walking who never crossed the line even when joking, but how difficult must life in the martial arts world have been for him? Now, even his eyes have lost their charm. What should I do…?

But after hearing Gabiya's confession, his expression suddenly became grim.

How dare this lowly barbarian woman do something to the princess?

``Mama, what should we do with this bitch? Should I report her to you immediately and have her hanged and slaughtered?''

The first mama was Qing, the second mama was Empress Mama.

"Hey, that's okay. It's a little annoying, but I didn't mean anything bad…"

The part where he says he was trying to make you crave pleasure was a bit annoying.

But, because Qing already understood that pleasure was a concept that combined training with Gabya.

Well, there were some impure intentions, but does that mean there was no malice?

``This girl. Mom was so kind.''

Gabiya, who was unconscious and passed out, may not agree with that.

No, but what was this guy that he's so exhausted?

Even though I used the Blissful Maiden Art, I never touched the embarrassing part once, but it was flapping, flapping, um, it was over because I felt it intuitively.

Well, but this bed… since it's summer, I wonder if it'll dry quickly if I hang it outside. What should I do tonight?

``Ugh. What. How kind.''

Then, as if asking what the current was talking about, the current turned its head around and protested.

"Really. It's been like that before. Even when you were bitten by that damn dog during your swordsmanship training, you were bleeding profusely, yet you secretly prayed to God that even a beast could bite—"

``Huh? Wait. What does that mean?''

"I hope your memory returns. A long time ago, a few years ago, wasn't it? There was a lion cub being raised in the King's Hall. What was the snack? Anyway, the princess tried it and…"

A lion dog? Qing's ears perked up. Is there a lion in the Forbidden City?

Of course there was. It was a fortified city that raised not only dogs but even an elephant, but Qing had no way of knowing.

But now there was a sound that bothered me more than the lion dog.

Qing interrupts the old story of the incoherent ocean current and the story of how he was bitten while stealing dog treats and asks again.

"No, let's not talk about being bitten. Swordsmanship training? Did Princess Yuansui learned swordsmanship? But isn't the royal family can't learn martial arts?"
