\chapter{Forbidden City Diary (1)}

Your Highness the Crown Prince, a thousand years, a thousand years, a thousand years!

A loud roar echoed from all directions.

Well, because His Highness the Crown Prince personally took it.

Of course, you should kneel down, bow your head, and chant the three thousand-year-old hymns with your forehead barely touching the ground.

Thanks to this, the onlookers did not witness Qing's disgrace.

Instead, wouldn't you have just said "stop shouting" at this point? How long must we keep shouting in unison, time after time?

Well, the prince, who should have been gesturing to stop, was furrowing his brow and looking down at the guest with a very displeased expression.

From Qing's perspective, what the heck, who was this guy that makes such a face from the first time we met, if you saw his face you should say something like hello, welcome, welcome to the palace of the Zhongyuan, why were you acting weird? No, didn't you just click your tongue?

``Tsk.''

The prince clicks his tongue and taps his forehead, his bangs, with his finger.

Bangs? Qing unconsciously raised his hand and touched the front of his head. "Oh, the cotton thread was flipped over. My front looks brighter."

The world was a mess because the cotton wool that touched the stone floor while I was sleeping got soaked through, so I can't see very well, but anyway, the area under my feet was bright even without looking thanks to the spatial perception of the Awakening Divine Skill's current detection.

Only after Qing had finished organizing the cotton thread did the prince raise his arm, which was bent at a right angle.

The cries of the millennia finally cease.

Everyone was silent as if nothing had happened, and only the sound of rain falling filled the silence. Then, the prince spoke.

``Young hero Ximen Qing, welcome to the forbidden realm of the Purple Palace.''

Huh? Where were you going? Qing's eyebrows twitched.

However, the womb refers to the heavenly palace where the Emperor of Heaven, the master of the heavenly world, resides, and the forbidden area refers to a forbidden area, a sanctuary where no one except the Emperor of Heaven can set foot.

And if you combine the two, the Purple Forbidden City, that was the origin of the Forbidden City being called the Forbidden City.

"You must be tired from the bad weather. First, go to your quarters and get your body and mind in order. Listen, Ximen Qing, ahem. This guy, ahem."

Suddenly the prince opened his mouth, and then opened it again.

For some reason, I feel extremely reluctant. Rather than being reluctant, I feel like I've lost. I guess my pride was greatly hurt.

But what can I do?

In the Zhongyuan, the crown prince was not a person who holds any real power.

They only have the authority of absolute power in the future, but their actual role was to obey and follow the emperor's orders.

``Guide Ximen Qing to the Hill Defense Battle.''

Healing battle!

To the south of the Donggung Palace in the Forbidden City was the Nan-gong Palace, which served as the crown prince's residence. It consisted of three large palaces and was called Namsamso.

Among these three buildings, Hillbangjeon was where the Crown Prince's concubine resides.

However, was it true that a marriage in the Zhongyuan was something that takes place by one's own will?

Wouldn't it be a very important event, requiring permission from the elders of the family and connecting the two families?

So, it was not something the prince can just give up healing.

If we combine these two, the prince's remarks end up meaning exactly like this.

I really like you.

Stay close to me.

That's a truly one-sided crush!

The prince gritted his teeth.

Of course, Qing doesn't know about such circumstances.

How could Qing know how many buildings there were in the Forbidden City, their names, and what they were used for?

Even when the emperor changes, the purpose of the residence changes depending on the emperor's residential preferences and the degree of favoritism of the existing residents, so it was only natural that those who were not palace officials would not know about it.

The prince shudders once, then turns his body around with his fists clenched tightly.

I feel like I've never felt such great humiliation in my life.

And as he walks out with brisk strides, the embarrassed eunuchs follow behind him.

The voices of the eunuchs can be heard faintly from over there.

"Your Majesty, what on earth were you talking about? Bringing a woman from the martial arts world into Namsamso. Your Majesty, please change your mind. Your Majesty, a woman's beauty was fleeting, like a light passing by on horseback. No matter how much you catch my eye—Shut up! What do you think of me? I have eyes too! But Your Majesty… …

It seems like the prince shouted.

If it weren't for the rain, I could have focused my mind and eavesdropped with my superhuman hearing.

The sound of rain falling on the stone floor was so refreshing, it's not easy, and I don't really care about eavesdropping on small talk.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

If you throw a huge rock into a lake, it will make a big ripple, the water will swirl violently, and the surface of the water will boil and create chaos with big and small waves.

And since this boulder was thrown into the Forbidden City, the news that the young hero Ximen Qing, who had come to receive the Emperor's praise, had been defeated in the battle spread throughout the city in less than half a day.

You might wonder why the security of the Forbidden City was like this, but the speed at which rumors spread was proportional to population density.

And the palace was bustling with people.

The Forbidden City was a complex of buildings, with over ninety palaces, and over nine hundred buildings remaining, totaling just under a thousand, gathered within the massive walls.

Thus, the number of rooms inside the Forbidden City reaches nine thousand.

The owners of the rooms, the people who manage them, the eunuchs and court ladies who reside in the castle, the high and low officials and their families, and the resident messengers—how many people were there?

Besides, isn't this truly an unbearable topic of conversation?

It was said that the prince greeted the woman of martial arts who had come running at the emperor's summons and told her to go straight to the healing room.

That woman was called Heavenly Blossom Sword, you know? Cheonhwa among flowers. She's a master, a master, and a total beauty.

A woman as vile as you, how dare you… … to His Highness the Crown Prince!

You were hopeless in the first place, weren't you? No matter how much you try to act, do you think His Majesty will even look at you once?

"Hey, why were you saying that? You might say I look unusual. You've probably only ever seen beautiful women, so you might say I have a unique and distinctive look."

You fucking bitch, you're even more of a bitch, man.

In fact, the palace maids' dreams were only one of two things.

To stand out to the Emperor and receive His Majesty's favor.

To stand out and receive favor from His Majesty.

However, the Emperor's women were subject to a very strict hierarchy and discipline, and the palace maids see and hear the life of a concubine that makes them shed tears every day, so they were not popular unless they have very, very ambitious aspirations.

Princes were the best.

Afterwards, when I leave the palace as a prince, I can leave this stuffy and dangerous Forbidden City.

And His Highness the Crown Prince, what can I say?

Even though it was called the Western Marquis' seat, after ascending to the throne, he will be given the second best seat among the Western Marquis' palaces and the Eastern Six Palaces on a first-come, first-served basis.

The reason it's the second was because the best position in the Dongyuk Palace belongs to the youngest wife, Bin.

So, the palace maids were 80% jealous, but at the same time, they were 80% perceptive.

Are you destined to become the crown princess?

If He were to take this opportunity to reclaim my life, wouldn't my life be truly bright?

For reference, there was no title of crown prince in the Zhongyuan, but there was a title of crown princess.

The next emperor was not the crown prince, but just the crown prince.

However, the crown prince's first wife was the crown princess.

Is the Crown Princess the problem? The Crown Prince has already fallen for it, so how much favor will she have? Don't you know favoritism was more important than official rank?

So, the maids who came out to greet the guests and the maids who managed the Namsamso meet right in front of the Hillbangjeon and exchange fierce glances.

Why were you guys here? This was Namsamso.

I know where everything is, so I'll come and see you. What the heck.

Isn't it only natural that we should serve you when you receive it? What do you know?

We were the masters of hospitality, the pinnacle of hospitality. What, patience?

The eye of that typhoon, that black hole that sucks up all the attention of the Forbidden City, was now shining brightly for the first time in a while.

By the way, how many people were actually in the bathhouse?

How many hands do you have right now?

Head, Shoulders, Knees, Toes, Knees, Toes. It's not a human barrier, nor was it a lucky sculpture that will grant you a long and healthy life and a son if you touch it, so why were you all flocking here and making a fuss?

``How about the water? Would you like more hot water?''

"Oh my, how can your skin be so fine? Wow, it's like white jade. No, isn't the white jade like your skin?"

``Oh, it’s torn. No, it wasn’t silk, it was hair. Oh my, how soft it is. I thought I was touching a fingernail.''

Well, the maids were also having a chat.

Still, compared to our Shinnyeomun disciples, they were a bit lacking.

"Your Majesty, this was a bottle of UnaeXiangjoyeok. Since you, a female knight I admire, have come, I have specially brought it from the Seoyuk Palace. It was a treasure of which only a few bottles were presented each year. Isn't the UnaeXiangjoyeok truly gentle?"

Even the palace maid who whispered quietly while rubbing the perfume that gave off the rich scent of milk.

I don't know what the West Six Palace is, but anyway, isn't that embezzlement? Is that okay?

But, um, I feel good… … .

How many people were there who soak their hands in hot water, warm their palms, apply perfume, and gently rub all over their body?

Ah, it's melting, it's melting…

Then soak it in hot water.

Apply the essential oil again and start the full body massage again.

If you stay still, you will be washed, dried, and dressed, and when you come to your senses, you will be resting your chin on a soft, comfortable bed (a chair with a floor-standing mattress) and getting a scalp massage, hair care, and nail care all at the same time.

You could say that the fate was indeed good.

That's why Qingdo may feel wronged.

Because there was nothing else to do but enjoy these luxuries.

Since I'm in the palace, I have to do at least three days like this and just enjoy the luxury.

The exact reason was that it was a process of purifying the body and mind before meeting the emperor.

Isn't it natural to first meet and greet the owner when visiting someone else's home?

However, the Emperor was someone you cannot just go and pay your respects to just because you want to see him.

First, you need time to calm your mind and body and shake off negativity.

So, the massage was also unlimited.

Because the palace maids took turns in order of their fierce competition to serve the prospective queen.

``Well, I’m a little hungry…….''

"Oh! I'll prepare something for the girl right away! Shall I bring you some food, some porridge, or some sweets? No, pretend you didn't hear that. I'll bring you everything!"

``No, why were you asking so much? Thank you…''

It was a question that never turned down a snack.

Anyway, as always with Qing, when you enter a friendly environment with friendly people, you become very relaxed.

Yum yum dried snacks, dried meat, dried fruit, lumped snacks, lumped meat, lumped fruit, fried snacks, fried meat, fried fruit, constantly mumbling, 'Are you cool?', 'Oh, over here, were you talking about my waist? Oh my, how thin it is, it's really a pretty face, it was meant for a young lady!' and listening to such banter, I'm so tired.

Then, after about this angle, another maid comes in and takes her place.

I was startled for a moment by the sight of the snack table spread out all over the room, but it was the shackles of the rotating shift where I had to serve people with a coquettish expression and tone of voice.

Among them, there were several attempts to gain favor.

First of all, the main thing was the basics.

A palace maid who gives gifts, saying that they were precious, even though her salary doesn't seem to be much.

Or a palace maid who spits out information.

The Empress was very, very strict, so if you show even the slightest bit of dishevelment, even a single strand of hair sticking out, she will spit out fire, so you must be careful.

But the Empress was strict? I don't think she's like that at all.

The concubine has more power than the Emperor's second wife, so if you wish, I will tell you to pay your respects to the concubine.

These days, there was a fierce fight between the concubine and the noblewoman of the Crown Prince.

Besides these circumstances, the prince's favorite foods were sweet, salty, and soft meat.

The prince knows how to eat. Yes.

Or, what color does the prince seem to like, what kind of hobby was reading, what kind of route does he usually take for walks, and when can you see the sun?

Information I never asked about and was never curious about.

And, again.

Qing sees the new maid who has taken over.

The Zhongyuan was actually, surprisingly, a fairly conciliatory multi-ethnic society.

To be exact, except for the Han Chinese, everyone else was barbarian, so you could say they were treated equally. The Zhongyuan was a community rather than a race, and was united by villages, cities, and castles, so except for a few minority groups who were looked down upon, the masses get along well.

So, it's not particularly surprising that a court lady looks like a painted Indian beauty.

``Mom, there’s a really good lesson.''

Of course, Qing was not a mama yet.

But from Qing's perspective, it seems like some of the palace maids call her Mama quite naturally.

``Studying?''

``Oh dear, how can I explain this? It’s so good for women, it’s so good for women, but I don’t know how to express it, and it’s hard to tell you directly…''

``If you say it like that, I’ll be even more curious. What was it?''

``Uh, have you ever heard of Aekyung?''

``Aekyung?''

``It’s a study of India. It’s truly good.''

The maid explains with a subtle smile and a truly strange laugh.

Aekyung.

In the homeland of Qing, it was the very study that comes to mind as a synonym for India, the very study that was known to people all over the world, and in the Indian language, it was pronounced as 'Kama-Sutra'.

"As you can see, Your Majesty, the girl was a descendant of the Heavenly King. And the Girl's Sutra, which the court ladies study, was a study derived from Aekyung, a part of Aekyung's pursuit of pleasure. If you master it, you will be able to command any man in the world. If Your Majesty was interested…"

You're trying to control a man? What were you using to control him?

Of course, Qing has no interest in such things.

But of course, Qing was interested.

Kama Sutra? No, how can you resist that?

\begin{lstlisting}
	The chapter's title is a reference to 'Countryside Diary' (전원일기) , a South Korean drama that was aired for a whopping 22 years (October 21, 1980 - December 29, 2002)
\end{lstlisting}