\chapter{Forbidden City Diary (3)}

The constant changing of maids and the never-ending massages were an extreme form of treatment that even the most luxurious people cannot match.

Qing was bored. Very bored.

A situation where you can't go outside the healing room.

Besides, the scenery that was visible was usually bleak.

A wall seven feet high surrounds the palace, and the floor was paved with stone without a single grain of dirt, creating a desolate landscape.

It wasn't just Hillbangjeon that was like that, but most palaces were like that.

Because the Forbidden City was built in a desolate manner.

In fact, there were no trees in the palace, except for a garden deliberately created in a corner.

Because if there were trees, invaders like it.

And in terms of architectural techniques, it may be because a building that completely removes natural objects presents an artificial sense of wonder and oppression.

Anyway, thanks to that, Qing was bored.

Especially since I am originally prone to boredom.

Well, what the heck was this? Of course, they treat us like guests, but it's ambiguous whether they're being nice or rude.

Then, this time, an extremely old court lady came in and spoke while showing off her neatly combed hair.

"Mama, have you noticed any of the children you've been serving? They're all homeless, and I'm sure they'll be delighted to serve you. So, if you could tell me without hesitation, I'll take action."

Ah, so that's how it worked.

Somehow, everyone came in and acted cute for a couple of minutes before changing shifts. It must have been a time for self-promotion, like, "Please pick me."

But if you invite guests, does your overtime pay drop significantly?

Or was it that the maids' work was really hard, so serving guests was the best?

Otherwise, he wouldn't have been so enthusiastic and worked so hard to give me a massage.

Well, that's not for welcoming guests.

In fact, the only person who thinks of her as a guest was Qing, and among the palace maids, isn't she already a powerful crown princess?

It was not yet known whether she will become the Crown Princess or a Lady, but since it was not a political marriage but the Crown Prince himself fell in love with her and gave her his own room, his favor will undoubtedly be great.

The palace maids, who considered keeping their mouths shut a virtue, were divulging all sorts of information to Qing as part of this self-promotion.

``Then, would someone named Gabiya be okay?''

``Gabi…are you talking about that child?''

The old maid's expression was cloudy.

``Umm, Mama, Gabiya was a woman from India. She has many shortcomings in the palace’s rules. She has a narrow circle of friends. She doesn’t quite understand the proper etiquette when it comes to serving her master. She has a bad reputation…''

In the court's language, this was almost like cursing someone.

The palace's rules were inadequate, and accidents often occur.

The circle of friends was small, news was slow, and connections were poor.

The way she treats her boss, she's a very arrogant woman.

The rumor was not good. The rumor was not good.

``Well, I guess it’ll be okay, right?''

But Qing was not a lady of the palace.

Was she a bit lacking as a maid? But what's the problem? Since when did you start living with a maid?

And I'm so bored I could die, how can I stand Aekyung?

Thus, the self-proclaimed Kama-Sutra master, Gabya, greets Qing with a strange smile.

"Hehehe, it's an honor for me to have found the Heavenly Maiden again, Ma'am. When you say you've called the Heavenly Maiden, does that mean you're interested in Aekyung's studies?"

``Not that I’m interested, but I’m just curious?''

``Haha, please lower your voice.''

This guy keeps snoring, suspiciously.

In fact, if others saw Gaby, they would think that she was more of a lewd and alluring woman than a suspicious one.

But, in Qing's view, um, this kid, I feel a little bad about thinking like this…

This guy was acting really deadly.

Qing was already the epitome of obscenity, a person who had as her sister the obscene demon king of the world, who was made up of lewdness and coquetry.

Even the lewdness of the rare was a fragment of the same essence as human nature, which comes out naturally without being conscious or decorated.

Even without trying so hard to let out a strange laugh, twisting your body as if claiming it was fatal, and putting effort into a lewd smile.

But isn't Yi-mei the perfect female demon herself?

So what was the lewd power of Gabiya?

Well, I'm trying really hard… … , this was that kind of salty feeling.

Not knowing Qing's feelings, Gaby continued to laugh and talk.

"Mama, there's no reason to be so ashamed of your interest in Aekyung. Aekyung isn't just a simple art of vainglory. It's a profound study that leads to nirvana through the process of vicissitudes. It's a journey where passion reaches all the way to the Sahasrara Chakra (the thousand wheels), freely managing communication with the universe."

``Oh, that sounds plausible.''

``However, dealing with this kind of passion was not an easy task, so I will just give a brief introduction today.''

``You don’t have to do it simply.''

``Hehe, please don’t be impatient. We have plenty of time.''

Gabiya's alluring smile deepened.

It was a smile that seemed fatal to Qing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

To the south of the Seoyuk Palace, there was a large palace centered around which were luxurious residences, which were called Janyeong Palace.

Just north of this Janyeong Palace, Suan Palace.

It was the place the prince was heading to.

When the prince entered Suan Palace, a beautiful old lady bowed respectfully.

``Madam Deokseong, how have you been?''

``Yes, Your Majesty. It’s been a while.''

enN1WnIzcFhHMVJuR0JvdkNPc013M09wMVFUdkdvQjAyUWd4UkV6elFZUWRjcDlhemN4MUtnRlV6Z3ZvOEhNOA

``I’m sorry, I should have visited you more often.''

``What was there to be sorry about? But, why were you suddenly here?''

``That’s-''

It was the moment when the prince was about to speak.

"Ah! Look at my mind. His Majesty was here, and I haven't even offered you a single refreshment. Could you please wait a moment?"

``No, wait-''

It was a question, but Madam Deokseong immediately got up and disappeared without a trace with quick steps, so 'Wait' would have been more accurate than 'Would you please wait?'

The prince lowers his outstretched hand in embarrassment.

And how much time passed?

As the doors opened to the left and right, four maids entered the room carrying a huge table setting.

``Madam, this was definitely a tea table…''

"How can you be so thin? No matter how vast the Crown Prince's knowledge is, and how arduous the task of assisting in state affairs is, you should always eat hearty meals. With your cheeks sunken, what were the people at Dan-gyeong-jeon supposed to do? I must tell my mother to strike a stern warning."

``No, I’m eating well.''

"Come on. Eat. Your face was half gone. I am ignorant and unfamiliar with the affairs of state, but I know how to eat whatever fills my stomach."

The wife keeps shoving food into the prince's mouth.

The prince was still eating it up.

``No, ma’am, why were you peeling the fruit?''

"Isn't it supposed to aid digestion after a meal? Well, the peaches were ripening nicely this year. First, have some plums."

``No, I’m so full I could die-''

``Oh, let me peel the watermelon for you first. It’s refreshing, so sip it like you’re enjoying a drink.''

``I haven’t even eaten yet, what were you talking about-''

``Look here! Is Hwachae still far away?''

In fact, even though she was an old woman, it was an attitude she could not dare show to the prince.

The prince dared not protest against this, so how could Lady Deokseong be so impudent?

``No, nanny.''

``Here, eat. You have to eat to live.''

Because she was the prince's wet nurse!

A woman born of low birth and sold into the palace, now granted a magnificent title by the Emperor and living alone in a large palace within the Forbidden City.

This was truly a success story of the Zhongyuan.

So the prince became so bloated that he even loosened his golden belt.

``Phew… I can’t eat any more.''

``How dare you, with such a narrow mouth, take on such a difficult national task. Alas, I am so worried. Alas, what should I do?''

``No, uh. Okay. That’s why I came here.''

"Oh, come to your senses. The Crown Prince himself has come to visit, so he must have something to say. So, what's going on?"

"Well, doesn't your nanny know by any chance? Why, ever since Yeonsul got sick, your mother has been somewhat, ahem, uneasy."

``What kind of presumptuous remark was that?''

``So, it’s a spell, a spell!''

At that, Madam Deokseong's expression hardened.

After Princess Yeonsul recovered from her illness, the Empress's favor was not what it used to be.

Even though he was told that he could catch the flu, he looked after the princess so desperately, but after he got better, he never called her and did not want to see her again.

Even if you ask her why, she will complain that the story doesn't seem like a story, or that something was strange about the nanny.

But that was a long time ago.

After spending a long time abroad offering prayers, he must have been awakened by the Buddha's miraculous power. Of course, it was natural. If the Buddha had seen Mama's sincerity, he would have taken care of her.

It's been a while since you've occasionally called Yeonsul over to have tea and walk around the garden together.

Although she was an empress who practiced the basics of military strategy, which was to keep the enemy close and watch, it was something that would make someone who didn't know the situation sigh in relief.

``You haven’t been feeling better lately. On the contrary, your madness has gotten much worse.''

``Madness, Your Majesty, how can you say such a thing?''

``It’s all because of that woman, Heavenly Blossom Sword.''

"yes?"

Madam Deokseong's eyes widened at that.

Why on earth was there a Heavenly Blossom Sword here all of a sudden?

I don't know much about the Cheonhwa Sword, but it was said that the prince fell in love with it at first sight and hid it deep in the depths of the Hill Defense Hall despite the continued opposition of his officials.

He was secretly hoping that if he did well, he might be able to take care of the grandson's child someday.

"Listen. The Thousand-Haired Sword, that thing, defrauded Mother. It was by claiming to be a magician and impersonating her, that it clouded Her Majesty's mind. Therefore, since Her Majesty doesn't believe the magician's magic was magic and instead regards the Thousand-Haired Sword as the true magician, I will now reveal the truth and condemn that terrible sin…"

As the prince continued his explanation, Lady Deokseong was shocked.

Oh my god, how could this be? How could this be? This was ridiculous.

The prince was mad!

This thing doesn't dare to talk about bloodlines, so I can't bring myself to say it out loud, but my son, whom I hold dear to my heart, my son, was mad!

Even the heavens were indifferent, how can the prince so firmly believe in such absurd delusions!

Well, that sounds crazy to anyone who hears it.

What mother in the world would believe a stranger who claims to be her daughter's bitch?

Moreover, Yeonsul was so beautiful and has such an extraordinary body, where else can you find a woman like her?

And when and where did you meet the Heavenly Blossom Sword, the martial artist of the Zhongyuan, who was said to be a terribly lowly butcher, and fall for it?

How could a mere woman named Heavenly Blossom Sword know the circumstances of the palace and commit fraud to her advantage?

Even if he was a fool, how could he dare to commit such a heinous crime against the royal family, violating even the laws of nature?

Even if it doesn't make sense, isn't it too absurd?

"Madam? I'm fine. Please don't look at me with such pity."

"Don't worry. Even if you ever leave the palace, I will follow you and take care of you. Even if you go to Yunnan or Qinghai, or even India or the Western Regions, I will follow you."

``Nanny, listen to me.''

"Oh my, if it was so hard, why didn't you come to me every time? I was so indifferent. If you hadn't come, I should have. Oh my, I was so indifferent."

``No, just a little!''

So the prince begins to explain again, step by step.

So, please, nanny, take a look at the Cheonhwa Sword.

In my mother's eyes, I'll look like a bad brother who fights with Yeonsul every day and doesn't get along well with her, so she won't listen to me and asks, "What do you know?"

Your Majesty, you should speak directly. Fighting? You always get beat. Fighting was something that happens when two people were on opposite sides—

Eight, you're telling me I should have been sincere to a woman younger than me?

Even then, the princess was already more mature-

Stop it! If you act like this twice, you'll become a general!

Ahem, anyway.

Look at the nanny. Since the nanny breastfed and raised Yeonsul-i from the beginning, how could the nanny not be able to distinguish between the real and the fake?

And when the nanny tells the mother, won't she listen attentively, and once doubt sets in, won't the mother quickly realize that she's been deceived?

``If Your Majesty says so, I guess I’ll have to bring in a new queen after a long time.''

The compassionate gaze looking at the prince didn't change much.

There was also a more dangerous murderous intent lurking there.

``If that was true, it was a serious crime that requires the destruction of the entire clan, the destruction of the ancestral graves, and the beheading of the author.''
