\chapter{Forbidden City Diary (9)}

The hospitality of the palace's guests was truly extraordinary, so why doesn't the number of attendants increase day by day?

Of course, unlike Gabi, who was directly nominated and chosen, Lady Deokseong seemed to have more business with Princess Yeonsul than with welcoming guests.

So I thought it might be the same this time too.

``Yes, please come in.''

Then, the door opened carefully, rolling around.

A court lady comes in with cautious movements.

And, wow… … !

The moment I saw it, I couldn't help but exclaim in awe at its majestic appearance. Wow! Actually, I couldn't help it.

The clothes were really about to burst.

The clothing of the Zhongyuan rarely directly reveals the lines of the body.

If you try, it will only be slightly visible when you tie a belt, and even then, there has to be a certain amount of volume above and below it to stand out.

Of course, in cases outside the standard, such as Mo Qing or Mo Chunfeng, it will be very obvious.

But there was a new court lady, Haeryu, whose body was prominent in a somewhat different sense.

The jacket was so small that it clung to his body, and the well-toned muscles that bulged out on the inside of the jacket did nothing to hide his chiseled lines.

With well-developed latissimus dorsi and a thin waist, she doesn't have a muscular body, but rather a beautiful figure that retains the curves of a woman.

Actually, the jacket was small.

It was Haeryu who was wearing a small vest on purpose.

This was the reason why Haeryu was difficult for the palace maids to touch even after losing the master's favor, and the secret to her not being directly harassed.

Overwhelming power!

Because if you mess with me, you'll probably get hit!

Hae-ryu entered the room with his head bowed and his crown placed between his two raised hands, a somewhat humble posture that did not match his dignified appearance at all.

Then he carefully raises his head, and when his eyes meet Qing's, he flinches in surprise.

Qing-i, who saw that, said, "Hmm."

It seems like she's also an acquaintance of Princess Yeonsul.

Why does it keep increasing, it's embarrassing people…

Qing waves her hand awkwardly.

"hello?"

The current suddenly brought him to his senses.

If Mama were alive, she would have grown up so beautifully by now, for there was a woman who truly resembled her right in front of her.

The prince would not have brought him into the palace without knowing.

If so, wouldn't you have prepared a substitute to replace the current fake?

His Majesty clearly said so.

You said to find evidence of someone who dared to impersonate the princess under the Heavenly Sword, so why did you summon a famous master from the Zhongyuan?

The current looked at Qing with a stern face and burning eyes and slammed its knees!

"Girl, I will do whatever you ask me to do, without hesitation! What should I do, girl?"

Qing tilted her head at the sight.

Oh, weren't you an acquaintance of Yeonsul?

For someone who was familiar with Yeonsul, his attitude was quite plain, so I guess he was just a strong and passionate person.

But, it's still a bit spicy anyway.

What should I do?

I know something about the palace.

Even if I ask you to do something… … .

Qing, feeling embarrassed, scratches her cheek.

The pupils of the ocean current dilate.

Well, an afterimage that exactly overlapped with Qing's appearance passed by.

And then, a great realization strikes the ocean current.

Ah! You really prepared thoroughly!

Yes, if you want to be a stand-in, you have to have the sincerity to learn even the smallest habits!

Your Majesty has been preparing to punish that wicked fake bitch for a long time!

If your body was in good health, your mind will be at ease.

It was natural that the developed body would gradually lose its utility and become pure as it gave the brain a rest.

So the ocean currents were rather full of enthusiasm.

Revealing the identity of the fake to the world and punishing him was Haeryu's long-held wish, and it was also his long-held wish that he could not immediately destroy the fake Yeonsul and follow him to death.

If you can't take on such a great task, what good will it do to live and train?

``Please don’t do that, just order me to do something!''

``Huh? No, you can say that.''

``Please don’t do that…! Just tell me!''

The current crawls, grabs the hem of the blue skirt, and cries out earnestly, very earnestly.

That's right, the physical fight between the one who doesn't have to order and the one who asks to order was like a meow.

Also, how stubborn was he? He would never back down unless told to do something.

Suddenly, a magnificent inverted triangle of the ocean current, stretched out and held on, enters Qing's eyes.

And the muscles that stick out like a bulge follow from there.

Well, you seem to have a lot of strength… … .

``Oh, well then. If you could give me a massage…''

The light of the ocean current flashed in his eyes!

"Massage! The girl has a knack for it! Take off your clothes and lie down right now! Take off everything, even your underwear!"

It was a rather powerful order to strip.

and.

``How were you, Mama? Are you feeling refreshed?''

``Oh, I think you could do it harder.''

"Please lower your voice. It's too much to handle. Um, was that all?"

``Just a little more?''

``Is this much?''

The force with which it was kneaded was very strong.

In fact, even if he had used his internal energy to crush it rather than brute force, would it be enough to damage Qing's human-transcending, man-year-old iron-like muscles?

As a result, Qing was satisfied.

Yes, if it's a massage, it has to be like this.

Gabi, she said she was giving me a massage, but she just gently scratched my skin. Of course, that gave me a strange sense of pleasure, but it was a bit much to call it a massage.

A Korean restaurant should serve Korean food. If they just serve bread stuffed with meat, no matter how delicious it is, it doesn't feel like you've had Korean food. Hmm, Korean food. I want to eat it…

``Oh, it’s refreshing.''

``It seems that the mother was satisfied, so the girl was also very happy.''

The current wipes his forehead with a proud expression.

"Huh, then, would it be alright if the girl stepped aside for a moment? I'm not quite ready to serve you, so I'll tidy up my clothes and come back."

Is getting a massage something that usually requires a lot of effort?

In the middle of a hot summer, after a long time, I worked out with all my might, so of course I was drenched in sweat, and my sharp muscles were visible through my soaking wet shirt.

``You’ve worked hard, so for now, get some rest. I’ll call you later if I need you…''

"Your Majesty was truly kind. Well, the girl will be looking forward to the moment you call her."

The ocean current bows its back.

It was a movement that looked incredibly restrained, perhaps because the muscles were clearly visible.

And then the way he slowly backs away was incredibly cautious.

Road,

As the door closes, Qing lets out a long breath.

Well, he seems like a nice person, but he's a bit too passionate, it's a bit burdensome…

Still, I wonder if it was the effect of receiving a proper massage, or if it was a pleasant feeling of fatigue that spreads throughout the body.

Qing jumps onto the bed without a moment's hesitation.

The blue was drooping.

My body was tired. The bed was soft.

He flailed his arms and legs on the round bed, stretched out his body, lifted his back, and trembled, stretching unusually.

The gentle pouring of water feels really good.

Well, at least it's fortunate that the court lady named Haeryu doesn't know Princess Yeonsul.

Madam Deokseong was also a bit difficult to deal with.

Even if this body was the body of Yeonsul, I am not Yeonsul, and I have no intention of becoming Yeonsul.

Isn't it something that I don't want to do, can't do, and shouldn't do?

So, I hope there won't be any entanglement with Yeonsul's old relationship…

That was the moment.

Knock!! Bang!!!

The door opened with a loud noise as if it was going to break.

It wasn't that it wasn't broken, but that the door leaf, detached from the frame, slowly fell backwards.

Qing's eyes were wide with surprise, and the backlight cast a shadow on the shape of a muscular man, making him look even more muscular because he was black.

``Current? Is it a current?''

Sniff! Sniff!

A harsh, nasal sound like the belching of an angry bull.

A kind of tense, huge spirit, like a bull about to charge a bullfighter.

And then, bang! A heavy leap that sends the body flying with a loud footstep.

``Mama!!''

``Ugh.''

The sound of the blue waters suffocating beneath the current.

Of course, I just lost my breath.

Qing was lying on a soft bed, and even though it was actually on a hard stone floor, her body was not one that could be injured by the weight of a single palace maid.

In fact, if you really wanted to avoid it, you could have rolled your body over and avoided it.

But Qing couldn't bring himself to do that.

``Ugh! The girl didn’t recognize Mama even though she was right in front of her. Ugh, how upset she must have been! Mama, Mama…!''

Ohhhhhhh, Hae-ryu was hugging Qing tightly, burying his face in her especially soft part and crying loudly.

The rough breathing was not a warning of a bull's charge, but an outburst of emotions made rough by the shedding of tears.

``This bitch was so foolish that she didn’t even notice me while I was giving her a massage, huh, mama, huh, you’re alive, euaaa……!''

He said to her, "Miss."

This guy was also a friend of Yeonsul.

It wasn't some kind of hidden landmine dug in the ground, but this kind of despicable time difference attack, making people feel safe, and then a surprise attack.

``Eww! Eww! Eww, eww, eww!''

Miss, and why was he crying like this?

I have a feeling that I shouldn't leave it alone.

And if that's the case, shouldn't you have asked if it was okay to cry first?

Qing's hand, which had been unable to grasp the direction, had no choice but to gently stroke Haeryu's head and back.

It's a little damp, I haven't washed it yet…

It was an ocean current that embraced him with all its might, as if it would never let him go again.

Well, but this woman.

The back muscles were really awesome.

The perception of a beat behind the current was actually a very simple principle.

It's been a while since I've had a refreshing, sweaty massage.

How long has it been since this happened?

It's been a while since my old mother used to praise me, saying that the massage I give her was the most refreshing in the world.

That disgusting fake sorcery made the weakling scream and start a fight as soon as it was applied, and even the weakling had tears in her eyes.

From then on, I think I already knew it was fake because of the strong suspicion.

Yes. It's been several years since I took care of Mama.

I dare say this outrageously and irreverently, and I'm ashamed to even mention it, but I'm closer to you than my own sisters, so how could I not know what's real and what's fake? I could tell at a glance…

``Hmm? Isn’t that the ocean current?''

At the voice heard at that moment, Haeryu bowed with a face full of joy.

``Ah! Madam Deokseong! How have you been?!''

"You're still so energetic, it's truly a sight to see. So, what brings you here? Oh, by any chance, Haeryu, have you also come to serve Mama?"

Mrs. Deokseong asks with a smile.

If it's the place where the mother is, shouldn't the first thing that comes to mind be Hae-ryu?

``Yes, Your Highness the Crown Prince, uh, ahem.''

The ocean currents take notice.

I'm not sure if I should say this or not.

Madam Deokseong whispered to him.

``Your Majesty? Didn’t you happen to say that Princess Yeonsul was a fake?''

``Yes, that’s right. His Majesty asked me to help Mama gather evidence to punish the fakes over there.''

"Your Majesty? Ah, Your Majesty, you've finally opened your eyes. Indeed. Couldn't flesh and blood recognize flesh and blood? And you two were so close."

``Huh? Did you? When did you do that?''

"This was it. They say brothers grow up fighting. Ah, I should be grateful to Your Majesty. I was already anxious because that Indian girl was hanging around. I'll be reassured by you. I'll leave the princess in your care."

``Leave it to me, okay? Princess?''

``Huh? I’m talking about Yeonsul Mama. Didn’t you just come from seeing me?''

``Huh? The person I met. ……Ah. Ah!''

"Hey, where were you going? Heh, you're still full of energy. Well, Mom always runs around with you behind her."

With such a belated realization.

With boundless joy and delight, he discovered that Princess Yeonsul, who he thought was dead, was actually alive.

And then, with self-reproach, he didn't even recognize himself.

It was as if the inside of that huge muscle mass was filled with tears, and the tears poured down endlessly.

It was a very loud wailing, a current that wets the front of the blue with tears and sweat.

``Hehehe. Mama. You may have lost your memory, but still, hehe, it’s nice to see you like this…….''

And then, with his eyes swollen shut, he held onto Qing's hand tightly and showed no intention of letting go.

Blue was a bit uncomfortable, but… um. I can't say anything to a kid who's like this, um.

``So, how hard it was for me. That fake bitch took all the palace maids away… Chuhwa went to the Eoseobang, Jangmi went to the Gyeongbang… All those bastards who were like Bulyeosi came flocking in, and those Cheonchuk bitches…''

The current tells me everything that happened to me in great detail.

The way he spoke was different from when I first saw him. His pronunciation was long and drawn out, his voice was loud and nasal, and he seemed to be full of charm.

``It’s all because of those barbarian bitches from India. Dongyuk Palace was in chaos right now, and those bitches were really blatantly acting up, and, you know what? Those bitches put drugs in the incense, maybe Choi Eum-Xiang? That’s what I think. I was so focused on the training method we used to do together with Mama, and, oh, that’s right, I kept working hard, because if I exerted myself too much, I could still fall asleep like I was going to faint. Hehe, but now hehe. Oh, that’s not it, on days when the incense was really strong, all the crazy bitches in the palace maids’ bedrooms were like, Ahem, this mouth, this bad mouth, hehe, anyway.''

Qing's ears, which had been uncomfortable for a while, perked up.

It's uncomfortable, but there was a sound I just couldn't ignore. Huh? What?

I don't know why, but I have a feeling this was important information that I absolutely cannot pass up.

Qing said to him with a serious expression.

``Let me elaborate on that story a little more.''

``Ah, I’m not very good at talking, you know, ah, you lost your memory. In fact, it’s been so long since His Majesty visited the East Six Palaces, right? That’s why the ladies were lonely, and the palace maids were like that. Those barbarian bitches from India were after that, trying to win over my favor, using some kind of directional magic? A directional massage? What kind of directional magic was that? Just using some directional magic makes the sound boom, huh. Hehe. So, who am I? No matter what, it’s still so suspicious, so when I go to the Cheonnyeo Temple, I sneak out, you know? That Jaehwa, ah, Jaehwa was a female doctor at the West Six Palaces. When I asked what kind of medicine this was, she said, ``You crazy bitch, were you asking me to make an aphrodisiac?'' Oh, I’m using the cube equation again, hehe. Anyway.''

There were a lot of shortcomings in the speech area.

Besides, it wasn't a story I wanted to hear!

What on earth happens in the maid's bedroom on a day with such a strong scent!

But, before that curiosity.

Why was it that a sound suddenly comes to my mind and I can never ignore it?