\chapter{Forbidden City Diary (8)}

There was also a hierarchy among the concubines, with a set hierarchy from the queen to the concubine.

However, what takes precedence over the ceremonial order stipulated in these national laws was the favor of the emperor.

Of course, the Empress, the mother of the country, was an exception, as it was rare for the Empress to be favored unless the Emperor's misdeeds were quite a mess.

If the concubines were like this, what about the palace maids?

The hierarchy among the court ladies serving a master was also determined by the master's favor.

In that sense, the court lady Haeryu was a fallen person.

The palace maids of Princess Yeonsul's residence were changing one by one before anyone knew it.

Of course, the existing palace maids did not disappear, but they all went out to work as managers or supervisors of empty buildings.

It's a sweet position with little work, little responsibility, but high compensation. It could be called a real honor.

Thanks to this, there was no other palace maid left who had served her since she was little.

In this situation, it's difficult to deal with, and the existing palace maid who doesn't seem to be particularly favored, and who doesn't even treat her kindly, so what can you do about her treatment?

It was difficult to provoke, so there was no direct harassment, but it was a situation where the person was secretly or openly ignored.

However, humans were social animals.

Even if there was no direct bullying, how can it be easy to be left alone in this kind of bullying?

Nevertheless, it was a current that endured steadfastly and continued its lonely struggle.

Yes, it was a struggle.

What was the struggle for?

It's a real fight for the princess of Yeonsul.

We must expose the identity of that evil fake.

Didn't that fake, that bitch dare to steal our princess's death?

We will erect a tombstone for our princess Yeonsul, whose death was unknown!

If anyone heard this, they would think this bitch was seriously out of her mind.

Besides, was it just crazy to suspect my master in the palace and call him a fake bitch?

It was a serious crime that requires immediate decapitation.

Even more so because the owner was a princess who has lost her memory.

So, some might say that it was only natural that Hae-ryu lost the princess's favor.

So then, how on earth did this court lady named Haeryu end up suffering from such a horrible and horrific delusion?

It all started with small discomforts that I wasn't even aware of.

Mom, you only eat one bowl of rice… …?

Ma'am, were you being cute to the Crown Prince?

Mom, since when have you been this classy…?

Since when have you been so modest, feminine, and even elegant?

At first, even the currents could understand this sense of discomfort.

Because you lost your memory, because you died from such a terrible illness, because even your beautiful face was left with a big scar… …

But when I saw the three hidden moles spread and connected under the plump flesh while I was bathing.

The sense of discomfort that had been building up in the ocean currents until now suddenly exploded.

This was a fake dot that has been drawn.

This bitch, somehow, was a fake, fake bitch!

So, he risked his life to see the Empress, a lowly subject, without fearing the laws of the country or the nobility of the palace.

Likewise, the Empress, who had been feeling a great sense of unease, exploded at this terrifying discovery.

It was a situation similar to a chain reaction of madness where the mental power level went beyond the limit and went crazy.

If others knew, this bitch was the root of all evil! She was the one who spread the madness! It would have been a shocking thing.

So the Empress gives a special order.

"You, stop crying! Times like these were especially difficult to avoid. You must stick close to the fake and continue collecting evidence. Do you understand what I mean?"

"Yes, Mama. Even if it means risking the girl's life."

So, with only one last mission left for the current palace maid, I'm determined to somehow find clear evidence that the fake was fake!

And today.

"Your Majesty! I know that for a girl to dare to make such a request was a grave crime worthy of death! However, the girl's only wish was to serve you, Princess, for the rest of her life. Please, please, have pity on me and revoke this order. I sincerely hope so."

It was a sight to see a mere court lady dare to rebel against the crown prince, the embodiment of future power.

In fact, it was common for a court lady to change her affiliation.

In the first place, in the political world of the women of the Forbidden City, if the power of a concubine was deemed too high, it was common practice to scatter her dedicated maids with the intention of cutting off her limbs.

The future of the palace maids whose masters changed like that was naturally the end of happiness and the beginning of suffering.

There was also the territoriality of the existing palace maids, and usually, the palace maids who dispersed like this were assigned to those who did not have a good relationship with the existing master.

Still, it rarely happens that I refuse to go.

Because it was because of the reasonable way the money was answered.

Let's say you say, "From now on, you were a court lady of that palace," and the court lady in question asks to be married.

Bad answer.

Sowon: I have sworn to serve my current master with all my heart and devotion for the rest of my life, so I cannot serve another master.

Answer: *Explaining why you need to hire another owner*

-There were more than one or two people with stories, and it takes a long time to persuade them all.

-Actually, it's a stretch, so there's not much to explain.

-I thought I could communicate and I climbed up.

-As a result, the financial hierarchy collapses.

-It feels like they were forcing me to do something while ignoring my personal wishes.

Good answer.

Sowon: I have sworn to serve my current master with all my heart and devotion for the rest of my life, so I cannot serve another master.

Answer: Then die.

-It'll be over soon.

- Helps establish the hierarchical order of the treasury.

-As you wished, I made it so that you could serve only one master for the rest of your life.

-Respect individual opinions.

So, Hae-ryu's petition was actually a life-threatening plea, a plea that was truly death-defying.

If the prince was even a little upset, he would have been in a position to have his balls blown off.

How dare you disobey me?

Fortunately, the prince was satisfied.

Yeonsul: It looks like there was a blessing in that form.

You've put a good spin on the topic.

If he's willing to risk his life for the sake of the practice, he might be a bit foolish, but he's the perfect person for this job.

The prince lowers his voice.

"Listen carefully. The reason I want to use you was for nothing other than the sake of Yeonsul. There was someone in the palace who dares to pretend to be Yeonsul, a fake who dares to claim heavenly bloodline as their own."

"omg!"

The current couldn't hide its surprise at him.

enN1WnIzcFhHMVJuR0JvdkNPc013M2phOHM5THNIQjZUTWZXWE1kTUhmmbmFqSTgzWUp3RG9FWnE5OVo3R0MxVA

``Your Majesty, you knew, you knew!''

"Well then. How could I not know? Is there anyone in this world who doesn't recognize their own flesh and blood? I recognized him at first sight."

``Ah. That’s so fortunate. Really…''

"That's why I called you. I want you to contribute some of your strength to uncovering the true identity of that wicked fake."

"Your Majesty! Your kindness was truly invaluable! What can a girl, a girl, do? Even if you tell me to carry a bundle of firewood and jump into a pit of fire, I will do so! Just give me the order!"

Kindling was a term used to describe firewood that provides sparks to start a fire, and was synonymous with the world's most flammable substance.

If you jump into a fire pit carrying this kind of embers, even a small spark will start a huge fire.

The prince nodded in satisfaction.

"I will appoint you as a handmaiden to the Heavenly Flower Sword. Under the Heavenly Flower Sword, you must find the evidence that dared to impersonate the princess of the noble royal family. Can you do it?"

``You can do it! Let me do it!''

The current answered briskly.

What was there to fear for the princess?

But why all of a sudden, under the Cheonhwa Sword?

I don't know for sure, but I'm sure you all have your own thoughts!

So, this time, the prince, with the ocean current on his tail, crosses the front yard of Namsamso.

Of course, the front yard was still full of officials, both high and low, lying down.

The country's subjects looked into the ocean currents.

Of course, the first concubine of the royal family was the one who appears first and serves as an indicator of the king's arrival, so it was natural that her face should be memorized.

So the subjects were even more shocked.

Are you saying that since there aren't enough nannies, you're going to bring in a concubine to take care of the princess?

And that very same Sibi whom the princess cherishes like her own sister!

``No!!! Your Majesty!!!''

``Please contact me!!!''

``Kwaaak! Tongchoook!!! Zu …

By the way, Tongchok means candle.

Just as you light a candle to examine a dark place, please urge us to examine the hearts of those below with a bright candle!

But the prince has no intention of giving in.

Rather, the only mission was to somehow uncover and stop the evil fakes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Hmm. What should I say? It's so refreshing, it's so refreshing.

Yi-mei, Yi-mei's breasts were so big. When was the last time I saw Yi-mei, ugh, ugh.

Qing clenched and unclenched his hand.

Even if it's not rare, Chunfeng.

Hmm, or maybe Gunyeong.

Miss, why were you doing this?

It was natural for anyone to have a legitimate desire to touch someone's chest.

Because that's human nature?

If I had to be specific, it's the pursuit of motherhood? Something like that?

But today, suddenly, I don't know why, but I feel like I can't stand it. Why?

Is it because Yi-mei appeared in my dream last night?

Should I say I'm a little restless?

Once I think about it, it just won't leave my head, so even when I force myself to think about something else, I just want to say, "Hmm, hmm, I want to chew on something…"

So why can't I concentrate in the morning?

If I had something to do, I would try to concentrate to forget it.

I can't even get outside the hill defense wall.

I'm thinking of swinging my body, but from the beginning, the old man, the Taegam of the Byungpaldang? He'd repeatedly told me not to practice martial arts or anything just because I was bored.

Among the things I could do, the most productive one was cultivating my inner strength.

But when I sit cross-legged, fold my hands, and close my eyes, I realize, hmm, was I this fond of flesh? I don't know how to calm down at all.

If Gabiya had been there, I could have studied the amazing culture of India while watching the Aekyung demonstration.

The court ladies from India were allowed to offer Buddhist prayers at the Cheonnyeo Temple ceremonies, and this was a supreme right that no one could stop, as it was permitted by the Emperor.

Of course, even if it could have been stopped, Qing would not have stopped it.

Freedom of religion must be guaranteed, right?

Or maybe I should get a massage.

But if the maids said they would do it, it would be okay, but it would be a bit strange for me to call them over and ask them to give me a massage, saying that I am the boss.

Is massage usually something that requires a lot of effort?

Come to think of it, Gabiya's Indian massage was a bit disappointing.

It's a bit odd to say it's not that great after receiving such a good massage, but what kind of massage was it where they just apply oil and gently rub it with their fingertips?

And it's not the back that's the main part, it's the front part.

If it's a massage, you should knead it hard to tone the muscles and then pull and push the bones until they bend.

But I couldn't say much because of my sincerity.

Because I am a squirrel in front of favor.

That's understandable, because while giving a massage, you rub it three times and ask once every time.

How were you? Mama, how were you here? Don't you feel something? Breathe naturally, if you feel like a sound was about to come out, don't you have to hold it in? T-It's not good to hold it in, was it? Uh, Mama? Are you okay? Are you feeling good? T-How were you here? Here? Here? Oh, where am I? How were you here? Mama, I feel like I'm getting a heat surge inside, and I'm having trouble breathing, oh, not really. I see. Yes…

They say you can't spit on a smiling face.

I couldn't bring myself to tell Gaby, who was so diligent, that I couldn't just give her a strong, throbbing massage using the Chuna therapy.

But it was said to be a massage with a history of six thousand years.

Perhaps it was not a problem with the Zhongyuan style of chiropractic, but rather a problem with the skill of the practitioner.

Now that I think about it, I kept asking myself if it was okay here, what it felt like here, and if I was out of breath and my body was so hot that I felt like my voice was going to leak out without me knowing.

I think it might be because Gabya was a beginner at Indian massage.

But who was good at it from the beginning? But I'm a friend who tries hard…

Still, it was said that there was a strangely pleasant feeling, as if it was ticklish but not really.

But when I think about the time I got a massage, I feel a little ticklish, was the room hot? It feels like the heat was rising a little.

Something, even though I'm surrounded by cold air, it feels like my skin was burning, hmm.

Oh! Is this the effect of the direction method?

Maybe the effects of a massage from India take half a day to show?

That was the moment.

An unfamiliar voice was heard from outside.

-Mama, starting today, I am Haeryu, the girl who will be serving you. Mama, may I greet you?