\chapter{Forbidden City Diary (10)}

For the palace maids of the Hillbangjeon, it was not at all pleasant to constantly have new exclusive troubles.

Because the Crown Princess will eventually have to settle down in the Hillbangjeon, the number of her dedicated concubines will naturally increase.

And according to the strict rules of the palace, the rank of a dedicated maid was much higher than that of a palace maid who manages the facilities of an empty house.

If that was also the Crown Princess's exclusive right, what will the future be like?

If so, then this honor should be given to the palace maids who were originally part of the Hillbangjeon.

Because the palace maids in the Healing War weren't lucky enough to be assigned to the Healing War, but rather they were people who got into the Healing War through wealth or high-level political maneuvering.

With a grand dream of serving the Crown Princess.

Gabi was chosen, but there was nothing that can be done.

Didn't you win through a fair competition while showing off to your mother?

Madam Deokseong was not someone to be talked to or anything like that.

Because the weight classes were completely different.

Wasn't she a living legend in the world of palace maids, having originally been a palace maid and now occupying the position of master of a palace?

But not this time.

Who? Haeryu? A girl who's the same age as Princess Yeonsul and a longtime childhood friend, but who's been neglected lately? But she's a little scary, you know?

Huh, I guess I was scared.

Moreover, even if the princess's servants were favored for a long time, they were actually sold to a distant land with their masters not long after, so they were not considered very high in the hierarchy.

So this time, as a first-year court lady who has been taking care of the healing room for a long time, I will make sure to instill a good habit.

Still, since it was Mama's exclusive concubine, you could say that it was a crude and pointless plan.

If the exclusive maids were to compete for favor, it was only natural that there were many things that the building's maids would be disappointed with.

So naturally, factions were formed, and they push and pull each other, and they keep showing their faces to Mama, and if they were lucky, they can even become exclusive…

You might say, "What kind of childish politics was this?" But these were palace maids who have to live their entire lives in the palace, and alone at that.

The only goal in life was to achieve this level of improvement, or it will be even harder to sustain.

And so, a new exclusive, Hae-ryu, appears!

``Sisters! Please take good care of me!''

``Huh? Yes, yes.''

ZGVPdDc2cnQxMFU0bVlrbnZITXlVaWI3WjFUYnRwemlpQWZSbmlQOFVodzBEQ1dMSkhjd2tFV2EvSHJjalVKVA

The palace maids glance at each other.

Hey, what's up, you want to get some rankings?

You were the one who said you were going to take control from the beginning?

No, that guy looks like he's going to get beaten to death.

Hey, Chohwa, Chohwa was coming forward! Come on, Chohwa! A few sharp words—

"Please speak comfortably. You're a full-time employee. Oh, and do you need any guidance?"

Wrong. That girl's eyes were so rosy.

You said you were a palace maid, but what a tiger-like bitch!

The fist was always closer than the law.

The highly developed muscles originally gave off an intimidating feeling that made it difficult to even make eye contact.

So what? It's a change of strategy.

Now that it's come to this, I should follow in the footsteps of this dependable Haeryu-sama, even more than Gabi, and secure a chance to stamp my face on Mama… …!

however.

The return of Haeryu, who had left with a brave heart, saying he would pay his respects to Mama, was shocking.

Her eyelids were swollen and bulging from how much she had cried, and they were bright red like ripe apples.

``Are you okay? Are you okay? Did you get scolded by your mother?''

``No, no. It’s just, that’s not it.''

The voice there was completely locked and dry as the main sound, so anyone can see that this was not just a cry.

Wouldn't it be like crying and crying and crying so much that you're completely exhausted?

The palace maids exchange glances.

Exclusive, would it be better to quit?

If he can make even the general Haeryu shed tears, how strict and scary must he be?

If you're like the villainess who just appears in the book.

It was the moment when the infamy of the Cheonhwa Sword began to blossom.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was shocked.

According to Haeryu's words, the court ladies from Cheonnyeo Temple were relieving the loneliness of the court ladies with some kind of stimulant drug.

And then, somehow, it wasn't someone else's business.

Somehow, I didn't feel like I had slept at all, and I felt like I had a dirty dream last night.

Even after waking up, all I can think about was my heart.

It was a morning where I couldn't sit still because I felt a warm burning sensation under my skin even though I was turning my head.

Gaby, you gave me some dirty drugs?

I believed it!

Even though she was a suspicious woman from India!

I had thought of a way to contact the Indian sorceresses that the Empress Majesty had been cursing at, but anyway!

I thought he wasn't a villain because his bad deeds were ordinary!

Hmm. Now that I think about it, well.

Even if your evil deeds don't reach 100 points and you don't pass the beast test, you can still do some strange things.

If you think about it, it was suspicious from the beginning.

Just gently scratching, what kind of massage was that?

And even though it's a massage, they keep asking me why my body doesn't feel hot, whether it feels good here, or how about here, and that it's not embarrassing to raise your voice, so speak up as much as you want.

How could you! Trust me!

What about the memories of those three days, the long time we spent together until now!

Well, it's been a few days since I've seen you.

Yeah, well.

So, Gabiya's betrayal isn't really that shocking.

If it's more shocking than that,

You think the medicine works on me?

The blood poisoner was a god and I was invincible?

But, if you think about it, it was the same when I was really into cherry blossoms.

After sucking on the cinnamon, you feel like you're drunk, you feel light and bubbly as if your weight has disappeared, and you feel good and excited.

Hmm, thinking about it makes me want to eat cherry blossoms again… … .

The mechanism of action of the poison was the non-action of the poison.

Even if poison enters the body, it does not take effect.

And because this poison contains all substances harmful to the body, even if a piece of iron was stuck in the body, there was no swelling, let alone infection.

Because the physical characteristics of the blood poisoner were in the realm of humanities, not science.

There was no formula to classify poison and non-poison through any definition.

He said that what was harmful to literature and emotions was poison.

Now it was time to clean up.

Because I understood the characteristics of sorcery while talking about sorcery with the Kunlun School's sorcery enthusiast, Duan Lun Jinren.

So, why did I take this drug and, to put it bluntly, get horny?

That must mean it's harmless.

If you think about it that way, it's a bit ambiguous.

First of all, this stimulant, it sounds strange to call it a stimulant, but it may be a drug that was completely harmless to the human body.

Or, it may be a harmful drug, but since the blood poisoner was not poisonous anyway, the harmful effects may have been omitted and only the non-harmful effects may have appeared.

This was a pretty important issue.

If you used harmful drugs, you can't just leave it like this.

Not only did you dare to poison me, but I heard that Dongyuk Palace was already in chaos, so this was no ordinary problem.

But what if that's not it?

It could have been done out of pure kindness.

According to Aekyung's teachings, the second ring grows through sexual pleasure, and accordingly, all seven ring points grow.

Even if you do not reach Nirvana through the completion of the Ilcheonryun, isn't it said that the growth of the ryunhyeol provides clarity of mind and health and longevity without illness?

Well, let me just ask you this outright.

But as was often the case with conspiracies of this kind, even if you ask, the answer was always the same.

I feel wronged. I did nothing wrong.

Even if there was no fault, he will claim innocence, and even if there was a fault, he will deny it and claim innocence.

Then what should I do… … .

"Hehehe, Mama. This was the Heavenly Maiden Gabiya. The Heavenly Maiden's event was long today, so I'm only just getting back now. Is it okay if I come inside?"

``Hmm. Come in first.''

Gaby pretended to be deadly, her waist swaying.

Then, Qing's eyebrows furrow slightly.

Above Gabiya's head, the number was forty-four.

When he came in last night saying he was going to burn incense, he must have been in his forties, um, late forties.

It's gone down? Where did you accumulate good karma?

Suddenly so special?

``Mom? Are there any more bugs?''

Gabya raised her head and looked into the air.

This was the reason why Qing described Gabiya's seductive gestures as fatal.

He pretends to be really deadly, and every now and then he makes these kind of fierce gestures, so you can tell at a glance that he's trying to be deadly somehow.

It was Qing who felt her heart soften at the sight.

Well, it's one thing to accumulate good deeds, and another thing to pretend to be deadly but still look clumsy.

``Did you say there was an event at Cheonnyeo Temple? What kind of event was it?''

"Oh, that's right. Right! Are you interested? If it's alright with your Majesty, oh, you can't leave the palace right now. Would you like to pay your respects to the Emperor and then come with me?"

``Yeah. Let’s go for a spin. I’m curious.''

``Oh, how happy we are! Our temple was dedicated to Aditi, the supreme heaven, the primordial earth, the world itself, and the mother of all celestial gods.''

It was a human characteristic to speak quickly, have bright eyes, and show a happy expression when a topic of interest came up.

``So… this was in the Vedas, the oldest scriptures… the priests of India deny this, but we were the ones who were truly authentic…''

Thanks to this, Qing was suddenly forced to listen to the doctrines of a religion he had no interest in.

So, Huh, Huh, Qing, who had been yawning without realizing it, quickly closed his mouth.

It's not polite to speak passionately in front of someone.

But the aftereffects of yawning brought tears to my eyes.

"Ah! The celestial maiden was so excited. I apologize. Oh, I didn't light the incense first. Hehe, don't worry. I'll keep the incense burning to prevent bugs from reaching you, Ma'am. And would you please lie down on the bed for now? It's a little late, but I'll give you today's incense treatment."

"uh."

Qing tried to stop him, but stopped.

Come to think of it, there was no guarantee that the scent was the ultimate scent that Hae-ryu spoke of, was there?

Could it be that my state this morning was just like being horny?

It was normal for a man to be unable to control his emotions once they were set in his mind.

I had to be absolutely certain that Gabiya had given me the drug, and then I could consider whether it was harmful or not.

This guy has such low karma that he will start to doubt with certainty when he was around eighty or ninety, but it was not that high and it starts to decrease from there.

So the way to find out was simple.

You can try receiving it again today.

So, this was the Indian massage session.

He rubbed his hands diligently in the right direction, and his warm palms scanned Qing's entire body.

And at first, I thought it was like gently spreading it out and pressing it in like a massage.

As expected, with the tip of my raised finger.

Hmm. Hmm.

Something. Something something.

"ha……"

``Hehehe, Mama. Are you feeling better? Okay, relax.''

This, um, feels, a little bit.

What should I say?

It's ticklish.

Something. It's like I'm out of breath…

"Hehe, Mama. It's okay. Naturally, this was where you're weak, right?"

``Wow!''

``Whoa!''

Qing suddenly sits up.

Wow, sir. This was some hot medicine!

``This isn’t it!''

``M, Mama? Why were you saying that……''

``Current! Now!''

-Mom!! I'm going!!

With a force that borders on chaos, a muscular woman bursts into the room.

She was wearing a single skirt pulled up to her chest, and since it was already late, she was wearing pajamas, revealing her chiseled shoulders and arms.

``M-Mama? How-''

``Catch the current!''

``Yes, Mama!''

Gabi, arrest on the spot.

The charge was unlicensed practice using illegal drugs.

I personally experienced the effectiveness of the medicine.

It's a dirty drug.

Next, isn't it time to find out whether this was a harmful drug or not?

That? Simple.

Qing picks up the jade bottle containing the incense.

"Come to think of it, I can't keep this wonderful treat to myself. I'm thinking of learning this six-thousand-year-old massage, known for its skin beautification, constitutional improvement, and longevity."

``That, that’s something a celestial maiden can teach you……''

"The best way to learn was through practice, right? It seems like Gabiya's having a hard time anyway. Okay, do you want to lie down?"

``That, Mama……''

"Or, why don't you like it? Is it some strange drug you don't want to touch?"

``Huh.''

Gabiya took a deep breath.

``What a strange medicine! That’s just a fragrance, a fragrance made with real Indian secret techniques!''

``Then, it’s not some strange medicine?''

``Of course! Absolutely not!''

"Then it's okay? Okay. Lie down. Haeryu, can you help Gabya lie down comfortably?"

``Whoa, I can lie down-''

The current grabs Gabiya's arms and pins them to the bed.

Qing sits on Gabiya's thigh, unties the knot, opens her jacket, and holds up the jade bottle with a mean expression.

``Okay, were you sure you want to apply it? Can I apply it?''

``Okay, just a moment.''

``Why? Not? Because it’s a strange drug?''

``It’s too precious a medicine to use on me…''

``Hey, between us. Don’t give up.''

Qing slowly tilts the jade bottle.

Then, Gabya's eyes turned to Qing with a sad expression.

And then, gulp gulp, it was Qing who poured the contents into his hand like he was pouring alcohol.

Then, Gabiya shouts urgently.

``Mom! Not that much…!''

``Why? Why can’t I use it a lot?''

``That’s it, that’s it……''

``Okay, let’s get it right?''

Qing slowly raises her hand as if she was about to turn it over.

But, despite that, Gabiya just closed her eyes tightly.

If you want to try it, do you mean try applying it?

Qing's smile was truly cruel and sinister.

\textit{You thinkt I wouldn't do it?}