\chapter{Forbidden City Diary (7)}

The red number above Gabiya's head was forty-seven.

Qing averts her gaze as if nothing happened, but, um, isn't it a bit too low to call her a witch or a sorceress or something evil and wicked?

If Gabya's evil deeds had reached 100 points, a perfect passing score, that is, a passing score for a beast, Qing would not have treated her kindly.

If she were a bad girl, I would have pulled out her joints right away, hung her upside down, and stripped her naked (if you've ever had a dislocated bone, you know how horrible torture this is) and made her confess everything she knew.

Well, that's too bad…

Since she couldn't possibly know about Qing's evil thoughts, Gabiya tilted her head for a moment.

It was a rather cute gesture, unlike his usual deadly charade, but that was only for a moment.

``……? Ah! Hehe, if a mosquito bites you, it’ll be a disaster. But. Didn’t the celestial maiden know this would happen and come burn incense to offer you, Mama?''

Gaby shows the wooden box in her hand.

There must have been something in the palace that wasn't luxurious, but this wooden box was particularly luxurious.

``GaraXiang?''

``Isn’t it true that Kara was the most expensive agarwood made from the hardened sap of the agarwood tree?''

Among the agarwoods, the color of the agarwood must be black like marble, smooth and shiny, and it must not have even a single scratch.

Therefore, it was called the heavenly treasure because it was the most precious thing under the heaven.

It was a sacred tree called 'a fragrant jewel tree in the Pure Land', as mentioned in the Buddhist scriptures.

It was called GaraXiang because it resembles that scent.

``They say that one box of this was worth two thousand won, so it’s an incense more expensive than gold.''

If you try to do it, it's only the amount of one bowl of rice, so how much was two gold coins worth in gold?

By the way, what was GaraXiang?

It's a name that somehow doesn't seem to have any scent.

Anyway.

If you were burning expensive incense instead of mosquito coils when bugs come out, incense was originally created to repel bugs.

Qing has been living in the Zhongyuan for several years now, and now it's become a thing to burn incense on a summer day.

However, the sight of someone burning high-quality incense catches my eye every time I see them.

The incense powder was ground very finely, like a pancake mix, and poured into a tightly packed incense burner that resembles a maze.

Afterwards, rub it well with a brush, push it in between, and carefully lift the incense burner. A long maze of incense powder will remain inside the incense burner.

A single stroke drawing that fills all the space, the longest form of line.

And when you light the end, the neatly arranged incense powder slowly burns and spreads its fragrance.

Looking at that sight, I secretly wonder how good the scent will be.

Finally, the fragrant natural scent of garaXiang, the fragrance of heaven, wafted into Qing's nostrils.

``Oh. Is this GaraXiang? Me again.''

``Oh, have you ever taken care of it before?''

``Isn’t that the same scent I always smell when I go to my friend’s house?''

``Huh? That can’t be true.''

It's the scent I always smell when I stop by Seolga Store.

Even if Seolga Sanghoe was doing well, there's no way they'd burn an incense stick worth two gold coins for the price of a fist.

Of course, Seolga Sanghoe has that kind of capacity.

And even if he didn't have that kind of capacity, he had the full will to squeeze out whatever he had and somehow give the world's most precious person the world's best fragrance.

However, Qing does not know.

So, what I'm thinking is.

Well, isn't this something you're trying to get me to do?

Just to show off, saying it's expensive, saying I'm giving you something precious like this.

But was Qing's sense of smell an ordinary sense of smell?

It soon points out a slight difference.

"But, sniff sniff, was it a little different? Strangely, a little richer, should I say? A little, um, what was it? It's a little sweeter, maybe…"

Qing possesses a sense of smell that surpasses that of humans.

If we were to compare it to that excellence, it would be between three and four times that of ordinary people.

By the way, it was said that a dog's sense of smell was ten thousand times stronger than a human's, so it was unfortunate that Qing's sense of smell was not even as good as a dog's.

Gaby's face brightened.

"Ah, as expected! Mama. Garam was the finest of all agarwoods, isn't it? If you've smelled agarwood, you might think it has a similar scent. How on earth did you, Mama, come to smell such precious agarwood?"

``Is that so?''

But why does he speak like this?

I have a lot of money, too. If I really wanted to, I could buy a whole bunch of cigarettes and light a chemical warfare device in my room.

Of course, I'd rather order one more dish than spend money on that.

Why would you burn gold to burn incense? It's literally the same as burning money.

But even in my hometown, there was a big difference between those who can and cannot drive expensive imported cars. So when I hear people ask me how I can drive a foreign car, I get angry.

Suddenly, the old maid's words come to mind.

That girl lacks manners when it comes to serving her master, well, definitely. She seems to lack a lot.

But whatever it is, it doesn't matter.

Since when did I become your boss?

If you burn expensive incense, you can add some color.

Just looking at the potato that was being held out, what was it?

Spring potatoes were delicious. Don't you have them at home?

Even if you say things like "dog's paw," a favor was still a favor.

But that doesn't mean that the sincerity of burning incense in the middle of the night, and the heart of preparing it with the best ingredients, will disappear.

``And Mama, hoo hoo, hoo hoo hoo……''

Suddenly, Gabiya starts to laugh very, very deadly.

What was it? I have to say something.

Then, licking my lips, he took out a jade bottle from his bosom with a fatalistic gesture and thrust it in.

``This was the famous fragrance of India.''

What do you think of the expression on Gabiya's face when she says that? It's an expression of absolute confidence, as if she really wants it to death.

Qing answers him.

``Hmm. Is that it?''

"Oh, mama, the direction, the direction of our India. Not the inferior or fake ones from the Zhongyuan, but the real India, made by India's people using India's secret methods! You should be even happier."

The direction refers to the oil used in Chuna, or massage.

And among them, the direction of the Heavenly Axis was considered the most precious.

Because the massage culture of India, this practice of rubbing and applying fragrances, was a product of an ultra-ancient primitive civilization that has been in use for over six thousand years.

In India, it was called Ayurveda, and in the homeland of the Qing, it was called aromatherapy.

This was a miraculous treatment method that even appears in Buddhist scriptures.

According to Buddhist scriptures, Shakyamuni Buddha was saved twice by receiving massage in this direction.

This acupuncture treatment saved the life of the Buddha, once when he had a bowel obstruction due to a twisted intestine, and the second time when his wounds were festering, boiling with fever and pus, and his body was rotting.

Besides this, there were countless great people from India who were healed through this type of massage, including Indian mythology, great emperors, generals, poets, etc.

Because no one in the world was curious about the great people of India.

In response to Gabiya's passionate praise for Qingdo's direction, I thought, "Hmm, the name of Cheonchuk was really strange."

``So, the Heavenly Maiden was going to give you a massage that contains the essence of six thousand years of India.''

``Hmm. Thank you?''

"Oh, my, how wonderful this is. Especially for women, if I may speak of it this way, it makes their skin as clear as white jade, clear…"

Gabiya's words were blurred.

What was the best beauty treatment to make your skin as clear as white jade?

Because Qing's skin was already in the best condition a woman can have.

Especially those hands, those long fingers with white, transparent skin, were truly the best hand that penetrates the heart of the Zhongyuan people.

``Besides that, it also removes fat, and, um, anyway, it’s also very effective for beauty purposes…''

Gaby's speech gradually loses confidence.

"You're already perfect, but, still! Wouldn't it be better if you groomed yourself even more? I have to, or rather, I want to, do it for you."

Qing snickers at him.

What was this? Is this a new type of incantation?

I'll give you a big score for novelty.

Well, he may be a bit awkward and clumsy when it comes to speaking, but he doesn't seem like a bad kid.

"Since you've prepared it for me, I should try it at least once. Oh, I like it when they press down hard. A massage needs some pressure."

"Oh, come on, Mama. That's not a massage. Isn't that just a primitive, uncivilized, force-intensive massage, pressing and pulling like that? What I'm about to give you isn't that. It's a real massage."

Hmm. A good kid, right?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

People have an instinctive tendency to avoid their own mistakes.

In Qing's hometown, it was a psychological fact that had already been sufficiently verified through countless cases.

For example, a type of parent that was once popular.

Like a member who kills a child without using medicine.

Even after the child's condition worsened and he became severely disabled, they still did not use any medicine.

Because the moment you start taking medicine, you have to admit that all of your child's conditions were your fault.

Because I have to admit and accept the truth that my child has suffered irreparable harm due to my own wrong beliefs and my own incompetence.

Even if it doesn't go this extreme, you can tell just by looking at the boss you hate at work or the common bastards and bitches in the neighborhood.

Even though I did something wrong, I got angry because people have a cowardly nature to try to avoid their mistakes.

If I get angry because of it later, from then on, it's the world's fault, it's not me, it's the world that made me like this.

Or blame others. Everyone else does this, so why was it only me?

Of course, just because you don't admit it yourself doesn't mean others were like that, so there was no one who was so crippled that they were confident in themselves and look like a cripple to others.

In this extension, the prince can never give up and must not give up.

Why were you asking me to admit now that Heavenly Blossom Sword was the real Princess of Yeonsul?

So then, what on earth will the prince become?

He was a fool who brought his younger sister into the bedroom without even recognizing her and said he would take her in as a companion, and he was a destroyer of natural decency.

Without parental permission (as seen by others).

Despite the opposition of countless officials,

Above all, you're proposing to Yeonsul?

As goosebumps appeared all over the prince's body, an unbearable, enormous power surged from his body and ran wild uncontrollably.

So, as this rampant force exploded from the largest muscle in the body, the prince's feet violently kicked the blanket away and writhed.

No!

The prince suddenly gets up and wipes away the cold sweat that has formed.

I don't know what tricks that wicked Ximen Qing used to fool my mother and my nanny, but he can't fool me either.

But, since my mother and nanny have already fallen for that witch's tricks, this can't go on.

Someone, someone with the vision and authority to prove that this fake was fake.

In that moment, faces flashed through the prince's mind.

What if we leave out the somewhat dangerous and politically entangled characters?

So the next day.

``Brother, were you asking me to hand over my maid right now?''

A woman wearing a cotton robe, a woman dressed in fine silk, spoke.

However, the silk garment had the image of a flying phoenix clearly imprinted on it.

For your information, only concubines and princesses were allowed to wear clothing with phoenix designs within the palace.

"I'm sorry. But, don't you know the situation right now? The opposition from all the ministers was so strong…"

"So, you intend to reveal your will by attaching my maid to that woman? Isn't it enough that Lady Deokseong has joined the fight?"

Since the nanny has already entered the healing battle, isn't that enough to show her determination to make the Cheonhwa Sword her own?

The prince scratched the back of his neck, which was exactly like someone else's habit, but anyway.

"Ahem. I have my own circumstances. I'm sorry to you, but I know you cherished her like a sister."

Absolutely not, the courtiers lay down and said that they could not allow a woman who had been living off the land of the martial arts world to become the crown princess.

However, isn't this always a voluntary act of loyalty?

So, it was impossible for the prince to come forward and shout, "I will do as I please, so kneel or lie down, do as you please!"

Because that was an act that tramples on that loyalty.

All the prince could do was continue to raise the status of the Cheonhwa Sword.

It was a way of indirectly informing the officials that I had absolutely no intention of changing.

… … was an excuse.

In fact, he only wanted to take the court lady who had grown up with Yeonsul.

If it were that child, he would be able to sense the fakeness of the fake, and then of course he would join in revealing the fake's true identity.

But since he couldn't say that, the prince continued to make excuses in a pitiful manner.

"But since he's a child you're close to and cherish, you want to take him with you even more. And it wouldn't be a bad thing for him either. Heavenly Blossom Sword was said to be an upright and cheerful person. And also, after I finish my work, I'll send him back to you so you can come and take care of him—"

"great."

It was a surprisingly refreshing answer.

The prince was ready to get his shins kicked once because his old temper was coming out.

So, I can't help but be surprised and ask back.

``Huh? Are you okay? Really?''

The woman wearing the veil, Princess Yeonsul, answers in a voice that seems slightly scorched by the fire, but with a gentle tone.

"If that's what you really want, Brother, how could I be stingy in welcoming my new sister-in-law? I might be able to become close with her through Ryu-ah. Your Majesty? Are you, were you alright? Are you feeling a twitch, a puff, a puff coming up in your face? Th-what?"