\chapter{Convalescence (8)}

Anyway, the search for Yun Yuanying continues.

A kind, gentle, and mischievous boy.

The child was very kind, had a good work ethic, and was not bad at anything, so he had a good reputation.

Despite his weak body, he was assigned to patrol the Wulin Alliance, so he was a natural at fighting, and even though his body was not up to par, he was already at a level that was unrivaled among his peers.

He was a very friendly child who enjoyed meeting people and visiting guests, so he was friendly with everyone and had no rough edges.

He was gentle and quiet, but surprisingly, he was also a mischievous boy, and he would always play little pranks that didn't hurt anyone's feelings.

If you notice your secret lover, you might make separate plans to get them together, or you might make homemade snacks with a strange flavor, or you might serve them cold tea.

He has a serious expression on his face, and when you ask him to hurry, he makes you laugh out loud, saying things like there's a hole in his shoe or he doesn't like the pattern on his clothes.

This was the result of an investigation into what kind of person Lee Sang-yeon was.

That's why, when they heard the news of Yun Yuanying's betrayal, no one believed it.

Qing thinks, Hmm. was it the same person?

Not kind, not gentle, and not playful, um.

Calling people to Oragara and making them go to the wrong place, then having them take a bath and shower, and then having them detain the Blood Cult guys in the meantime, was beyond the pale of a joke.

Are you some kind of divine empire of the Western Regions?

Is there anything that doesn't fit?

But people were bound to change.

There's also our grandfather, who was once a notorious hemp head, and our Heemae, who tormented the disciples as if it were nothing special.

Just look at Miss Moyong.

The woman who always used to be a troublemaker and cause trouble was now acting dignified and quietly taking care of her group.

However, just because there were people who change for the better, there were also those who change the opposite, so it was not something to be taken into consideration.

He's not the kind of person to do that.

I was really good when I was young.

Well, that might have been the case when I was young, but it's not the case now anyway.

Well, who knows.

A person may have changed drastically due to some shocking incident.

But that doesn't excuse the current evil deeds.

Moreover, while secretly, no, openly showing favor, he has an attitude of not caring about my life or death.

Even if I die, you'll keep me alive as a zombie. As expected, your goal was my body. This was incredibly impure.

Hmm. I don't know. I should eat.

But? How can this be!

"What? What was this dog?"

Bae. Qing sticks out his tongue.

A large fish bone was sticking out of the bright red tongue, too big to be chewed and swallowed.

It's a solid bone attached to the spine, so it's almost like a dagger.

"Ahem, I didn't mean to."

Qing's eyes narrow at him.

No, how dangerous were fish bones?

Is this a meal or an assassination attempt?

Qing sticks out her tongue in protest.

It was physical language that tells people to put away things they cannot eat quickly and put something to eat.

Mount Paengdae was breathtaking.

Of course, Qing was in need of rehabilitation due to fractures all over his body, muscle ruptures, and ligament damage.

In particular, when moving the arms, all the bones, muscles, ligaments, and other parts of the neck, back, and shoulders work together, so it was better to be as still as possible.

However, this does not mean that the patient was in pain or unable to move, but rather that he or she was able to carry out light daily activities.

No, really. No matter how comfortable it is, how can you keep sticking out your tongue?

"Don't you think you should at least maintain some basic dignity as a woman?"

"Oh. Okay."

Peng Daesan lets out a deep sigh.

Even a dog raised by Sega wouldn't do this.

Dogs know how to whine for food, but they don't ask you to clean up something they don't want to eat.

A showdown between a dog and Ximen-Qing, the dog wins!

Paengdaesan picks up his chopsticks and quietly retrieves the thorn.

"Look at me. This was why men were no good. They lack delicacy. Delicacy. Qing'er, you didn't get pricked while chewing, did you? Ugh, how surprised you must have been. were you okay? Should I feed you?"

At the fuss of Tang Lan-ah, who was about to start eating rice, Paengdae-san's eyebrows twitched.

He can't even stab a needle or sew a muscle, so he's relying on someone else's hands. How could a fish bone, which was not even a permanent weapon, pierce that sturdy mouth?

"No. I'll do it."

Following Iri, who came out straight away, there was also Gong Sun-Yaoyi, who appealed with her moist eyes, although she didn't say anything.

However, in this regard, it was a firm request.

"No. It'll mess things up. The closer you were to each other, the more strict you have to be in these matters, right?"

But even in difficult times, she was a woman who would not be pushed around anywhere due to her persistence.

"Well, aside from the meal, what about the bath today? Aren't you going to shower? What about night duty?"

The look in his eyes becomes sinister.

It's a teasing look that's used when teasing someone.

"Mountain? How was it? were you interested?"

"No!" "No!" "No!"

Tang Lan-ah, Gong Sun-Yaoyi, Xue-i-ri.

Huh. Did that dog just scream?

Is this the maximum vocal volume? More importantly, Gunyeong also knows how to make a loud noise. I thought people from the North Sea had a vocal volume problem.

I tried to tease them a little, but everyone was making a fuss, so I guess I'll have to give it a break.

However, it was a bit unfair to Qingdo.

No, what? Even if I bring it up, were you really going to make me take a bath or something?

What if rumors spread?

Do you have to block your friend's wedding?

"Well, then, I guess there's nothing I can do today. I'll just wash my face and go to bed alone, so you all know that."

"but."

"It's all your fault, isn't it? If you pretend not to know anyone, I'll just poison you and get you kicked out."

Xue-i-ri already had a history of rolling on the floor, clutching her aching stomach, sneezing with a runny nose and tears streaming down her face.

Tang Lan-ah isn't just pretending to take out poison. He really uses poison!

If only I had stopped him whenever he showed signs of trouble, he would have ended up pouring out all sorts of petty poison, and Xue-i would have suffered a lot.

Of course, there was also a positive reaction.

I don't use poison on Mo Yong and Ye Han.

They say that children grow up fighting, and that even enemies have their own relationship, so if you're completely distant with them, they won't do anything bad.

Xue-i-ri wasn't just being taken advantage of, so she was taking revenge by coldly throwing away Lan-ah's meals and snacks.

I don't know if cold tea was a revenge, but cold soup, um. Cold beef soup, cold duck noodles, cold mala soup were kind of like that.

But Tang Lan-ah has a resentful expression.

I have martial arts to practice today, and I think it's a good idea to sleep alone.

According to the dedicated accounts of two second-rate scholars.

(For reference, the first-class bookworm was the highest-ranking intellectual in the province who was doing business in that land.)

Saengsimgyeol was said to have the effect of revitalizing the heart. One side effect was said to be an increase in appetite.

Why was that a side effect?

Wouldn't it be better if you could increase the number of meals you could eat in a day? If you eat four meals instead of three, wouldn't the daily pleasure increase by about 30%, or even 3333, and infinitely?

Is this enough to be considered a new skill?

Such a noble function on a red theme?

Jinju Eonga loved zombies so much that he not only created them but also tried to imitate them himself. That was Eonga's secret weapon, the Gangsi Gong.

However, as the side effects of the Gangshikong were a decrease in heart rate and metabolism, this was supplemented through Saengsimgyeol.

Although Talmyeongjeongsim was a martial art rooted in Buddhism, it was said that it was not treated as a true martial art because it was strong and had a rough flow.

Even if you just look at the way he practices it along with the Taoist method, it was not a Buddhist teaching of Jeongjong.

However, the very idea of having to escape from the natural order and go against the grain was also following the unwritten precepts.

According to Buddhism, people in this world, the world of Saha, were beings who must suffer endlessly within the shackles of eons.

Therefore, accumulating merit and reaching nirvana was itself an act that went against the order of the world.

That was why Buddhist practice was difficult and tiring.

Isn't this a battle between the laws of the world and the individual?

How difficult it is, as evidenced by the fact that only one person in the entire world, Shakyamuni, has attained nirvana.

In Buddhism, Buddha was merely a title for one who has attained liberation. There were many Buddhas besides Shakyamuni, but there was only one Buddha who came from the Saha world.

The current owner was a renowned master of Sapa and one of the ten greatest masters in the world. The family has developed over time, so the exact details may not be accurate, but whatever.

So, in the middle of the night, the sound of suppressing and holding back the agguk and euguk lingered faintly, so while I was at it, I simultaneously uploaded six Taesanhyeoljo and Waegeom that were only on reserve.

That is, the brain drain was six times greater.

In fact, the reason I haven't mastered it yet and just left it alone was because I don't think it would be of much help to me to master it further unless I study.

Even if you try the Talmyeongdo Unga Kwon Taesan Bloodline, it's red, so there's no need to use it since you already have the divine skills.

The abstract black was completely blue.

Now that I've entered the realm of Hwagyeong, I feel like this martial arts spear isn't going to be of much help at higher levels, and might actually be a hindrance.

Why, in video games, isn't it more powerful to increase abilities by integers in the early stages, but in the later stages, isn't it much more powerful to increase them by multiplying them by coefficients?

The thought that's already coming to mind was that after I reach the point of life and death, I'm worried that even if I learn all the internal energy methods in the world, I won't have enough internal energy.

The same goes for martial arts.

I can use my power as soon as I get used to it.

But what harmonizes with my imagination? What can I truly use properly? What cannot be explained with a martial arts spear? A true martial art? The embodiment that can melt true intent anywhere, with any weapon, in any posture, was limited to the five forms of the Moon Lady Sword.

So, there's no need to use it, but if you just roughly learn it, you'll become stronger and your body will become more toned. However, I think that as your physical abilities increase in level, they will gradually lose their meaning.

Above all, when facing an enemy, you can fight more easily with a broader understanding.

More efficient at identifying enemies than increasing my means.

Isn't this nothing?

Is this okay? Can't you use a little more force?

Wulin will be absurd.

Now, a woman who has just reached the level of a monk was looking at a life-or-death mirror and doing this and that. If someone hears, they will think that she has been entrusted with some life-or-death mirror.

And you could yell at her, "Do you think it's thanks to you that I've been hanging on to my life until now, you shameless bitch?"

Of course, Qing will answer confidently.

Well, it's all about blood poisoning, isn't it all due to one's constitution?

So, anyway, there was a new member in the Danjeon.

A little boy who can't sit still and keeps turning his head around distractedly. He's so nervous.

What was it? The smell of the heart?

The demon's eyes suddenly glowed with a gleam.

Saengsimjin-gi, who had been turning his body around to look around, soon smiled brightly and energetically and clung to the elephant supporting Yongsangbanyagi's palanquin.

It seems like there was a connection between strength and vitality.

While the Magi were lamenting about him, another member of the family appears through the Danjeon door.

Oh! This time it's our turn! It's really magic!

The magicians welcomed their kind for the first time in a while and started making a fuss in a cute and cheerful manner. After all, they looked just like magicians.

He has a serious expression on his face, his attitude was rough, and he looks like he's chewing on something, so it seems like a dark murderous aura was rising from him.

The robes worn by the monk were torn and tattered, and he looked like a rebellious monk who had broken his precepts.

So this time it's really magic. It was already sad that Sega was pushed back, but Jeongsun was also no ordinary person.

So, the leader of the magician faction, the bicycle magician, welcomes the magician and approaches him with open arms-

puck!

The bicycle rider, who had been kicked badly, lies pitifully on the floor, constantly asking questions.

Then, Talmyungjin-gi clicked his tongue loudly.

Wouldn't you go to the Buddhist camp and squat down in a bad way, resting your elbows on your knees?

Of course, no matter how much the spirit of Talmyungjeongsim has continued to develop viciously in the Sapa Madu family for a long time, its foundation was unwritten martial arts.

I'm so sad about this, I can't live.

The magicians all lower their heads.

That was it. Hehe… … !

A mocking laugh.

The heads of the magicians all bounce up at once.

----

Qing was lying sprawled out in a mess, with saliva stuck to the corners of his mouth as a result of the aftereffects of the brain massage.

The guest room door opens carefully and silently!

An uninvited night guest slowly melts into the dark room and quietly heads to bed.

But Qingdo was not easy.

In a situation where you're already feeling dizzy, your brain spinning, and you're shivering from an indescribable, strange uneasiness, how could you not notice the intruder?

Besides, even though he killed it to silence the sound, it seems he was not an expert in infiltration, so he cannot avoid the attention of the Hwagyeong expert.

"Irene?"

"yes."

"Go over there and raise your hand."

"yes."

Qing bends her elbow and points.

As Xue-i-ri walked towards the place, feeling like she had already been caught, Dang-nan-ah, who was already standing with his hand raised, stood far away and waved his hand.

"No, I told you I'm going to go to the market tomorrow for breakfast, buy some gifts, and then leave right away. I need to get some sleep before I leave. Why on earth would you crawl into someone else's bedroom at this hour?"

"I'm just worried about Qing'er."

"It's not a man."

"What were you doing? were you talking strangely? If you're not someone else, then what were you?"

"Third party, don't interfere."

"What!? Who was the third party?"

"You. You vile poisoner."

"This was really……!"

"Come on. You guys want to keep fighting? You want to keep your hands up until I get out?"

"No, what he's saying was strange."

"No. No. I was wrong. I won't do that again."

"Hey, if you do that, what will I become-"

"Ha. Lan-ah was still the same. But Iri listens well. Iri, come here. Hmm? Iri, come here? was that okay? Iri, come here, um, come here…"

"No, why only me-"

In the eyes of the protesting child, the outline of Xue-i-ri, who was raising her fist as if to show off, suddenly appears.

"No, look at that! That's just words—"

"Are you going to keep yelling at me all night?"

At that, Tang Lan-ah's lips stick out.

It's literally like a duck's bill, if you cut it, it'll fill three plates.

Qing'er haaaaaah.

"There's still one empty seat next to me. Do you want to come here or stay?"

The child falls into a serious conflict.

Go? Don't? But that damn bitch was just being too hard on herself. Isn't that what Qing'er does to me? How can she do this to me? It's exciting, exciting. Even if Qing'er isn't here with me, she should have treated me better when she was. Do you think I'd even blink an eye if she cried and regretted it after I left? Even if she got on her knees and begged me, saying that she needed me and that she was truly my most precious friend, would I forgive her or not? No, I can't. Because I keep treating you well, you think I'm easy, but Qing'er, you're really not like that…

"Lan-Ahya? My side feels a little cold. Can someone warm it up for me?"

"Oh, really? Then there's nothing I can do. What would Qing'er do without me?"

The little girl heads straight to bed, smiling brightly.

And so the last night in the Wulin Alliance deepens.
