\chapter{Convalescence (3)}

Having finished Qing's apology journey, the group's destination was to return to the Wulin Alliance.

Before leaving Hangzhou, there was one bit of good news.

"Um, this……"

"Ah. Moonlight Sword, you're back!"

It was a moonlight sword sent by messenger from Wolgungru.

"Hmm? What about the money pouch?"

"That's because the guest broke the bathroom floor, and we had to waterproof it with the highest quality wood, and that's the cost. In addition to the broken part, we had to tear out the pillars, so we had to hire people. And because of that, we had to sell the highest quality guest rooms at a low price, which would be a loss. Also, since it's a high-rise building, we can't just use any carpenter, and the cost of materials alone was gold. In many ways, our loss was huge, so we hope you can be considerate of our circumstances. Yes, we have to make a living too. No, I'm not blaming the guest, I'm just stating the truth…"

He kept saying that he wanted to use it for repair costs, but then he blurted out that he wanted to use it for repair costs.

From Qing's perspective, this could not have been more regrettable.

It's not that I don't want to pay for the repairs, but the fact that I have to be treated like a criminal when I demand compensation that I should have, even though I'm an innocent victim.

"Hey, it's okay. I broke it to save myself. Is the money enough?"

"No, that's enough. It's fine! It's not unusual for a guest to experience a loss, was it? We're always prepared, and we're happy to help. Furthermore, if you become famous, you can use the room as a special feature, saying it was the one where the most beautiful woman in the world, Hang Ah Hyeon Shin, stayed. So, we have a way to make up for it…"

I was thinking of giving him a large allowance, even if it was just a receipt, but he strongly refused.

He was a swindler who only took the money with the intention of returning after seeing Nyong-nim's face in the middle of the night, and he didn't even feel sorry for her because he didn't know that she was a beggar and her stomach was dripping with oil.

Rather, I'm grateful that you gave me back the sword.

They were talking about selling the name of the Qing Dynasty and doing business, but since trademark rights did not yet exist in the underdeveloped laws of ancient Zhongyuan, it was not something that could be allowed or denied.

If you do something that tarnishes your reputation, you will be hit with a real sword.

The good customs of Zhongyuan were a society that encourages revenge and private punishment as good stories.

The famous Gou was also known as a swordsman who killed a corrupt official, but he was afraid of the government's pursuit, so he changed his surname to Guan Yu and found a new family.

"You were so kind, even to a lowly Hakka like us. were you not only beautiful, but also have the most beautiful heart in the world?…"

It's really touching to see him so moved.

What kind of beings were these innkeepers of Zhongyuan? They were truly remarkable people, broken and broken, yet rebuilt and persevering.

Of course, it will be a little different from what Qing thinks.

Qing did not know that he was planning to expand the bathhouse, paint it with gold and silver leaf, name it the Cheonhwaseonnyeotang, the most beautiful woman in the world, and promote its beauty benefits to make a business out of it.

If I had known, I would have just given him the receipt and told him to just pay for the repairs and restore it to its original condition.

This was why you shouldn't look down on those who stay in Zhongyuan.

Lan-ah, I-ri-do, Ye-wa, and Mo-yong-so-jeo all beg to take Qing's hand, so Qing was truly in a difficult position.

Of course, I can understand Qingdo's feelings.

Isn't it a very old human nature to want to be liked by celebrities?

It was human nature to divide my brother's right arm, left arm, right foot, and left foot into five parts and rank them according to rank, and to always have a series of maids following behind the brilliant stars and proudly hold up their arrogance.

In a master's house, even slaves were slaves of the master, because the master's authority was directly reflected in the servant's authority.

So what about these guys?

Why can't we understand the feelings of those weak and feeble subordinates who open their eyes wide, glaring at each other, and keeping each other in check, in hopes of receiving the Great Harmony Sutra's Evolution, Transcendental Evolution, Giant Evolution, Million Evolution, and Super Harmony Sutra?

This was the true generosity of a master.

But does that mean I'm hurt?

So let's take turns doing it every day.

It was a broad and grand calculation, like the Qing Dynasty's Hahae, that the honor of serving the youngest and greatest warrior should not be monopolized by one person.

San-i also secretly looks around and gives me a somewhat suspicious look, as if he wants to join in and help me.

But the reason why we can't say it out loud was because men and women were different.

Well, still don't say anything.

It was truly an honor to have served the master of Hwagyeong, and I cannot afford to give it to my first friend, not even to others, not even to the mountain, for a day.

It's not like I'm going to act like a woman, squealing and whining. I couldn't do it even if you told me to.

It's a little sad that I missed the chance to tease and exploit San-i, and I'm also a little upset that our friendship only goes so far as to discuss the shallow embarrassment between the sexes.

But I can't say that I can be the first to say, "Help me."

In fact, Sword Friend also volunteered to take up the job.

However, because the purpose was so impure, and because the intention to stick around all day and talk about swords was too transparent, it was rejected.

So today's guide was Murong Zhuxi.

I ate with Miss Murong, and went back and forth while holding her, and I used her as a prop for a while. Although the ride, or rather the sense of approval, was a bit poor for a woman, oh well.

It's too harsh to compare them to the professional pedestals, Heemae and Halpa, as they were still beginners.

Qing observes Murong Zhuxi's face while thinking useless thoughts.

That fluffy, fluffy hair, I wonder if it really was fluffy on a person's head, but when I look at that curly, thick hair, the word fluffy doesn't really fit.

And below that, Murong Zhuxi, whose face has subtly changed as she reaches her peak.

It seems like the head has gotten a little smaller, and the eyes, nose, and mouth have become more distinct. The eyes definitely seem to have gotten bigger.

Murong Zhuxi was going back and forth for no reason.

However, the posture was somewhat unique.

Should I say that my heart was pounding?

In fact, everyone has noticed, but no one was saying anything out loud.

Although he tries hard to be cute, the way he walks around with his chest puffed out was so cute.

But it seemed like walking around with her shoulders back all the time was causing her muscles to ache, so she sat by the bed and rolled her shoulders to relax them.

Well, then what?

"Um, Miss Murong? You seem a little different. What was it? After a complete transformation, what should I say?"

"Oh! No, that's not it. Just a little, just a little. Hehe, does that look like it?"

It was Murong Zhuxi who returned the question with a bright smile, blooming brightly like a sunflower in full bloom.

To be honest, it doesn't seem like much.

A facelift was not a full body plastic surgery that makes you look pretty or feminine.

It was a process of transforming into a body optimized for the martial arts you have learned.

So the arms were longer, and the curve below the waist, which was already dramatic, was even more curved, making it impossible to look away from the sight of it, making it impossible to hold back exclamations.

But since I'm swinging my dual swords, I guess the chunk of flesh hanging from the top will be a hindrance…

It's actually annoying and useless.

Qing smirked mischievously.

"As expected. Your face has become much prettier."

"Oh, you…"

Murong Zhuxi immediately becomes gloomy.

"And has your body attitude changed a little?"

"Ah. Hehe. Hehehe."

Murong Zhuxi, in full bloom again.

"Hey, thigh, can I just poke you once? Wow, it looks like even a needle won't go in."

"Oh, you're over there…"

Gloomy again.

"Oh, and the upper body too."

"Ah! I see, right!?"

"Ah! Right. Your arms have grown longer, haven't they? A warrior needs long arms, after all. Wow, that's great. Congratulations, Miss Moyong."

"Oh, yes……"

It's cute how you're getting gloomy again.

"Um. Uh, maybe. Somewhere else."

"Huh? Where were you?"

"Ugh, uhh, not the lower body, not the arms, not the face, isn't there something else that's changed? Definitely, please."

"Um. Um. Um."

Qing was very excited.

I don't know why I feel like teasing small, cute things like this.

The only exception was Lan-ah, who was short, but she looks surprisingly mature every time she takes a bath, so I don't think she's cute.

Murong Zhuxi's face darkens with anxiety, impatience, sadness, and despair in real time.

Just as Qing was about to open his mouth to give her the answer she wanted, he decided to stop teasing her.

Now, Murong Zhuxi, who had a desperate expression on her face, struck first at that moment.

"Oh. That, I guess it's because the clothes were thick. Now, if you look closely—well, not really, but if you look at it like this, you can clearly see the difference, right? Right?"

It was Murong Zhuxi who suddenly pulled down her vest and took off her small apron-like undergarment, dudou (dudou), hanging around her neck.

Then he leans his head against the bed and leans forward.

"Oh."

\textit{Hmm. I didn't mean to do that.}

\textit{It's a pleasure to my eyes, but I feel a little sorry for her desperate appearance.}

\textit{Did I tease her too much?}

Qing, who has reflected a little, matches the rhythm.

"Ah, breasts!? This can't be happening! Miss Murong! Breasts, breasts!"

"Ah. Ahhh……! Really……! Sob."

A drop of dew fell from Murong Zhuxi's enlarged eyes.

People shed tears even when they were very happy.

It's not to the point of being a total bluff, but it's not a lie.

There was something from nothing at all? Level.

Or maybe that's why it's great.

There was something from nothing, that is, how can it not be amazing to create something from nothing?

Metamorphosis, what the hell were you?

Is this a miracle of universal reality transformation?

"Wow! So lovely! So dainty and delicate! Wow! So pretty! So feminine! Just my style! How cute!"

Qing was good, he was good, he was praised as soon as he says something.

If it weren't for the cracked bone above my elbow, I would have clapped my hands to the beat.

Murong Zhuxi's face turned bright red. But the corners of her mouth rose towards the clown.

"If, uh, if it's your taste, ma'am, would you like to touch it…?"

"Huh?"

"Oh. That's not it! Just! No! No! I didn't mean anything else, because we're women! There's no problem! I was just bragging, no, not bragging, but confirmation, something like that. It just came out like that, so don't worry about it."

And then she suddenly turns her head and looks for the chest cover she had just thrown off so cheerfully.

By the way, it fell over the bed when thrown forward, so you won't be able to see it no matter how hard you look for it.

What was this creature?

You dare to show off the cuteness of a timid little animal that trembles in front of me?

Are you trying to do it with me now?

Qing's eyes narrow and take on a sharp shape, and a sullen smile appears on his lips.

"Oh my. Miss Murong."

A somewhat cold voice.

It wasn't the warm, sweet voice that Qing usually has, but rather a strange voice that somehow resembled someone else's.

In that moment, Murong Zhuxi was frozen in place.

Gulp! The sound of swallowing heavily.

A small head that creaked like a rusty hinge and turned towards Qing.

But surely, finally, really, etc., big, sparkling eyes full of anticipation.

"What? I called you, but you're not answering?"

"Yes, yes. Jesong, I'm sorry."

"Why do you do something you feel sorry about?"

"Ugh, I'm sorry."

"Again?"

"I, I was wrong. I was wrong, so then, I, I. Punishment-"

"Okay. What did you just say to me? Did you ask me to touch your breasts? Oh my god. Why?"

"No, no. I just, I'm so excited—"

"fizzle."

At that, Murong Zhuxi shut her mouth tightly.

As Qing reached out, he slowly approached, and Murong Zhuxi's red face turned even redder than his own, as if there were heaven above heaven.

Qing's hand, which had been gradually getting closer, suddenly stopped.

"Ah, ahh……."

Murong Zhuxi lets out a sorrowful, heartbreaking groan.

"Hmm. What should I do? This time, Lady Murong did great deed. She's also defeated many blood demons, hasn't she?"

Surprisingly, the person who cut down the most blood demons was Murong Zhuxi.

The blood demons were also afraid of Gong Sun-Yaoyi's increasing swordsmanship and could not approach him recklessly. So, they rushed at Murong Zhuxi, who seemed easy to catch, and ended up getting slaughtered.

The real hole was Lee Ri-hwa and Zhuge I-hyeon, but one of the two numbers had huge muscles and gave off the appearance of a master of external attacks.

After all, the short and lanky Murong Zhuxi must have been easy to defeat.

"Okay. So, let's speak clearly. What do you want me to do? Can you say it clearly, out loud, with your own words?"

"I, I. My chest, my chest-"

"Hey, just kidding, just kidding."

At that moment, Qing'er hehe, her expression softens.

"Dudu flew over to the other side of the bed. But seeing it with my own eyes definitely makes a difference. Congratulations, Miss Murong."

"Uh, yes. No, no. I'm not sure just by looking at it, but if you could check a little more thoroughly, I'd like to ask you to confirm that for me, since I'm not sure myself…"

It was mean to not want to do something when asked to do it.

Qing said this with a mischievous smile.

"My arm isn't fully functioning right now. Later, when it's fully healed."

"Oh, then you promise, you promise?"

"Well, okay. Promise."

Although Murong Zhuxi received a definite answer, she was actually just upset inside.

Anyway, Qing wouldn't have brought it up first, and neither would she, so even if it was a promise, it was just an empty promise. In the end, Murong Zhuxi couldn't keep up with either the reward or the punishment.

So, just ride my heart, you're going too far, really.

Anyway, after that, the soldiers marched back from Hangzhou to Suzhou.

The regret of the Hangzhou people for not being able to see the face of Heavenly Blossom Sword was immense, but in fact, the influential literati among them had already flocked to Suzhou in the past, seen Heavenly Blossom Sword, and had their tastes forcibly reformed.

The boasting of the literary men's writing skills was, in other words, like praising the beauty of the Qing Dynasty, so much so that even without revealing their faces, the beauty of the Qing Dynasty spread far and wide as if it had been seen without even being seen.

But Qing doesn't know.

Don't you know your own business, you ignorant bitch? I was so lost in the chaos of Qingdo that I couldn't even think straight, so I guess I should give you some consideration this time.

So, back to soju.

There was a canal in Shuzou that leads to Kaifeng.

So, I plan to arrive at the Wulin Alliance by boat in one go.

"\textit{Sobs}, Madam, I cannot serve you to the end despite your inconvenience. I, Wang Ssangryong, will be so resentful that I will remain with you for eternity, and even after I die, my wretched body will not be able to rot."

"Oh. Preservative treatment."

\textit{If only he didn't act like this, he would truly have the air of a great general.}

\textit{Why is it that whenever I have a private conversation, his strong shoulders became narrow, his stiff back bent, and his once dignified expression disappeared into a sly, eunuch-like figure?}

"Oh, don't be so humble. Thank you for everything. You even readily mobilized your troops. And you even held onto the official line until the very end."

"What a shame, what a shameful thing to say……!"

At the end of the monologue, the sight of Wang Ssangryong shedding tears was truly impressive.

She thought, 'He was truly a very kind person'.

Heavenly Blossom Sword was just a simple woman of Jianghu.

The scene where the general personally saw them off was not good for either of them, so Wang Ssang-ryong left first.

Still, it was Wang Ssangryong who secured the safety of the ship and ensured its opening.

The vessels on the canal were truly invincible, a moving sanctuary that no one but nature can touch.

Of course, nature can be tampered with, and government ships sometimes run aground and were wrecked, but how can humans overcome Mother Nature?

So, towards Kaifeng and the Wulin Alliance.