\chapter{Convalescence (10)}

Tang Lan-ah looked very uncomfortable.

Of course, since Tang Lan-Ah doesn't pay attention to others' feelings, his thoughts come out clearly.

"What, why were you following me? Aren't you going home? Don't you have a home?"

"Miss Ximen. Uh. Uh."

"No, why were you saying that? And what, you don't have a home? You have nowhere to go?"

"My heart. None. None."

It was a rather sad piece of personal history.

The little girl who felt him frowned sharply, even though she was the famous villainess of Sacheon-

"Are you a beggar?"

"uh."

Hmm. No. I guess I underestimated Lan-ah too much.

Come to think of it, I seem to remember hearing someone say, "Is Qing a beggar too?"

Ah. I think I also asked if my mom was gone.

Of course, I don't mean it maliciously-

"No, if you're a beggar, why were you following me? were you trying to cling to Qing'er? Qing'er, did you hear that? I told you this was what she's like? Her intentions were incredibly impure."

It's full of malice.

Well, a bad-tempered dog really does bite.

"Use it, it can't be used."

"Black."

"Don't make such a sad face for no reason."

Actually, if it was a really sensitive issue, Xue-i-ri wouldn't have responded by telling you to bark.

And what, Gunyeong was actually a beggar.

Seriously, how would he have survived if it weren't for his face?

"This leech thing was one thing, but what was this leech? Why were you chasing me?"

Then Paengdaesan shrugged his shoulders.

"They say the martial arts scenes along the Yangtze River were so spectacular. It's just a coincidence that our routes overlap."

The Three Gorges of the Yangtze River, the Qutang Gorge, the Wuxia Gorge, and the Xiling Gorge, boast the best scenic views along the Yangtze River.

Among them, the rocky cliffs of Mt. Wushan as seen from the Yangtze River were well known for their beauty, and Mt. Wushan's most beautiful peak, Mt. Sinnyeo, was considered to be particularly spectacular.

And on the other side, where it cannot be seen from below, there was a shrine dedicated to the priestess of Musan.

"Are you a pervert? Why were you spying on other people's sects?"

"I guess I can just be a pervert."

Did Tang Lan-ah's verbal abuse last for just a day or two?

In fact, it doesn't even work.

"You heard, Qing'er! Did you hear that? She's a pervert! A dirty, dirty rascal. She said it herself. I knew it the moment I saw that shameless face."

"When I first met Lan-ah, I think she said, ‘You're my husband.' She was just gently beating up Cho-ryeo—"

"What, no? I really hate guys who were that snobby."

Well, if you say so yourself.

Tang Lan-ah was of the Dang clan and lives in Sacheon.

There was a shrine gate on the way to Sacheon, so Tang Lan-ah was confidently going home.

However, I thought that Qingdo Xue-iri would naturally follow, because Gunyeong was a beggar and if it weren't for the Wulin Alliance mission, she would have continued to kill and settle down at the Divine Maiden Sect.

But I didn't know that San-i would follow me.

Well, didn't you grumble that your son wouldn't come home even though you were a little kid?

It's not that strange since I seem to like wandering around.

And there were many people who tried not to go home at all costs, so even if the party was over, my party wasn't over. Let's go for a third round, let's go for a fourth round. Can I go to your house and sleep over? I'll have a hangover cure in the morning. Wow, there were more than a few people who said that.

Aside from the pitiful heads of the times who don't want to go home and hold onto their subordinates' trouser legs, and the real ones who just want to go home.

There were people who feel bored and stuffy just staying at home, so they have to go outside.

Surprisingly, they were also very strange creatures who lose stamina when they were at home.

Wouldn't a normal person lose energy when they're outside and only recover when they're at home?

It was a limitation of human nature to be able to go out once or twice a day.

How can that be? I really don't understand.

Anyway, slowly, with the background music of Tang Lan-ah whining, whining, and complaining to Qing.

The carriage reaches Zigui. Zigui?

What the heck? was the groom trying to kidnap me again?

No, he was really a very kind person to the point of being suspicious.

It's been half a year since I've seen Zigui so unfamiliar.

The land around Zigui belongs to the Divine Maiden Sect.

And the land of the Divine Maiden Sect was granted directly by the royal family.

The Xuega Sanghoe, which manages such land, does not even need permission from the government to build a building.

Just building houses one after another and expanding the city, even the laborers were suspicious masters who had acquired superhuman abilities through martial arts to build houses, so how much more so?

This was the Demonic Cult's extremely evil plan to relocate the capital.

The sacred city that will receive the sacred fire in the future was not Cheonsanshinshi, but Musanshinshi.

Anyway, he was a coachman with a thorough professionalism and excessive kindness who acts like a loyal servant rather than a coachman.

Strangely enough, he stands proudly with his chin held high, and some people look at him with eyes of admiration, as if they were dying of envy.

Of course, Qing doesn't know this because he's busy chatting with his friends in the carriage and chewing on snacks that come in all day.

And so we arrived at Xuega Sanghoe.

The group getting off the carriage stopped.

"What was it, some kind of witch?"

Isn't there a woman waiting for the group, the epitome of obscenity, oozing a sexy aura just by standing still?

"Yi-mei!"

"Are you back? Oh, you're hurt again? were you okay? You have to be careful."

Jian Buxi approaches without hiding her worried expression and accepts the invitation very naturally.

"Huh, huh?"

The little boy who passed the favor without realizing it made a stupid sound.

It was a natural movement of logistics, like a servant receiving a load of luggage and flowing water.

Even the series of movements of embracing Qing were so skillful that it seemed like a craftsman, or rather a master, had been made. Even at a glance, Qing, who was being held, was clearly leaning against it with great comfort.

It was a very natural posture that no one on duty would ever do.

This was the quality of the original pedestal!

It was the ultimate comfort that the chicks, who were barely ahead of their time with enthusiasm, and the on-duty workers who were only experiencing the job could not show.

"Oh, right. If Yi-mei was here, what about her? She's not here, was she?"

"Huh? You mean your nephew?"

"My nephew was a piece of shit, anyway, him."

"My nephew was taken away by the priestesses. He wasn't supposed to be allowed out, but I guess he came out."

"Oh. I guess so."

Qingyi sighs in relief.

"Oh, you guys, was this our first time meeting? This was my, um, so, huh, my older sister, uh, okay."

For a moment, Jian Buxi's eyes widened, and then her strange face blossomed brightly.

A smile as bright as a child's, blowing away all the sexiness so far.

Hmm. If I like it this much, what will I become…?

"Hmm? I saw you when you went to the opening ceremony."

"Huh? was that him? No, but doesn't she look like some kind of worldly prostitute? She's a bit blind and stupid. Hmm, when she smiles, that's exactly her face."

"That's because you've completely transformed and become much prettier."

Meanwhile, Xue-i-ri bows her head.

"Hello. This was Xue-iri. Can I call you Unnie Kyeon?"

"Huh? Yeah! Sister-in-law, I like her. She's kind. She's pretty, has nice hair, and pretty eyes. Hmm? Does she look a bit like Xue?"

"thank you."

"oh."

The little girl seemed to have realized something and had an expression of "Oh no."

Qing's impression was different.

That's right. He could speak normally too.

Qing already knows why Xue-i-ri answers every question without fail.

Xue Ga-nom told me that if you don't do that, the barbarian bastards from the North Sea won't even answer you, so he slapped you in the face.

The reason why the words were short was the same.

He got beaten up for talking too much despite being a lowly person.

"This was San-i, Paengdae Mountain, the most handsome man in the world. Have you heard of Yi-mei?"

"Ugh. I haven't heard of it. But I should have. Oh! was he going to be your brother-in-law? Will I have a brother-in-law too? Can I see my nephew?"

The word 'Jian Buxi's' 'eung' was positive and 'eueuung' was negative.

However, the twinkling eyes and the chuckling Qing shatter the expectations.

"Hey, what a disgusting noise, my friend."

"Hmm."

Doesn't Sanido express his agreement with his unique low-pitched voice?

That was when.

The main building door creaked open!

"If you're here, why don't you just come in? Why were you just standing there? You don't look well. What the hell was that little bitch doing that you have on your face? Tsk tsk."

"Gramps!"

Because he wasn't feeling well, he simply greeted her with a smile. Choi Riong's lips softened.

But that too for a moment.

The moment his eyes fall on Peng Daesan, his expression lights up, and his once kind face suddenly becomes round and sinister.

A truly ferocious expression, as if the great demon of old was nowhere to be found.

"Gramps?"

"Hmm. No. I prepared some food. Let's eat."

He thought of Qing.

It's strange. It seems like Gramps starts eating food whenever he sees my face.

Hmm. As expected, it's Gramps. Gramps was the best.

The restaurant of Xuega Sanghoe was large.

It was built grander than the main building and larger than the warehouse, which was an incongruous layout for a manor that was not very large.

If someone were to see this, they might be impressed and say, "Wow, that's truly wonderful. Since it says 'family,' I guess that's how the company builds relationships by eating together!"

In fact, the interior of the restaurant was not very spacious, and a large banquet hall of unknown purpose takes up most of its space.

Every time I see it, I wonder why it was built like this.

According to Xue Ga-nom's explanation, the original purpose of a business was to entertain guests, and as an extension of that, they tried to be a bit extravagant and extravagant in order to gain the upper hand.

Certainly, it could be a preemptive strike.

It was a very luxurious banquet hall, where you can tell that the banquet hall was decorated with gold by inviting a discerning guest, but without feeling vulgar at all.

And there was a beauty with an exotic vibe, who was more handsome than beautiful.

"You little shit! Wow, how come you're getting prettier? Now you're just going to be the best in Gangso?"

"I knew it was a curse the moment I saw it. You even came this far?"

"Yeah. But, you've become prettier."

"Well, it looks good. Then that's enough."

"Oh, Xue Ga-nom, did you manage to commit suicide? was Xue Ga-ryeon dead? She's gone now?"

"You buried him well. Oh, don't be ridiculous. They say he visits his grave every single day, cries for an hour, and then leaves. It's so out of character for a guy who used to suckle prostitutes' breasts and fuck them until his dick was worn out. Because of that, he's stuck in the store, unable to leave, for fear of being noticed."

It's a very sinister and suspicious conversation.

"Speak nicely. What were breasts and what were dicks? In front of the kids."

"Tch. Do you even make friends with your own group? It's not fun, it's not fun."

The three of them all have frowning expressions, so there was no sign of Xue Ga-nom blushing and saying "Mother" as he had hoped.

It seems like this handsome old man still hasn't gotten rid of his sexual harassment instincts.

"This was Xue Ga-nom. The most intelligent man in Jiangsu Province, the most beautiful man in Jiangsu Province, my Jang Ja-bang, my advisor. Iri's uncle, uncle? was that uncle, or not? was it a little further? Cousin? Fifth cousin? Sixth cousin?"

"You're my uncle." "No."

The two men look at each other.

And then Xue-i-ri once again.

"no."

"Well, what's the point of calling me uncle when you haven't done anything for me."

Xuega shrugged.

"What? were you a eunuch? You seem to have a faint hint of tangible blood in your veins. were you a man? was this your family a family of eunuchs?"

"Oh, it's just that I learned martial arts incorrectly. And anyway, there were some women who have the Taeyanghyeol bloodline."

"Hmm."

Anyway, the table, filled with sweet, spicy, salty, and savory flavors, prepared according to Qing's taste, was still steaming.

Qing, I originally didn't have any thoughts.

Peng Daesan was a bit questionable.

I knew when they would arrive, so I prepared the food here. I thought it would be ready just in time for the carriage to arrive.

But Qing doesn't know. As always.

Instead, a quick word in passing.

"Oh, right. I took a picture of Hwagyeong?"

"……?" "……?" "Wow! Congratulations!"

Only Jian Buxi offers her congratulations.

He lacks common sense, and he would have believed anything Qing said, so even if he had taken a picture of Hwagyeong, Hyeongyeong, or Saengsa-gyeong, his reaction would have been the same.

"Hey, you didn't tell me in advance. You're making such a shabby arrangement for such a big event. Tsk."

"How shabby. Even in the palace, you wouldn't be able to eat like this. And what, so unsophisticated? Just because we've achieved a bit of a good look, you're throwing a feast or something?"

"What else can't you do? If you knew, you could have set up a meal in the square. When exactly was that?"

"When was it? The day before September 24th? was that right? Oh, it was the day before yesterday? But why was that?"

Why, why would that be?

Another anniversary for the future Musan Shinshi.

However, Choi Riong pretends not to know.

"Huh. Why would this old man find out about it two weeks late? He should have sent a letter or something. How can a woman be so indifferent?"

"I haven't decided whether or not to tell the world yet. And I'm only a Hwagyeong, so what's the big deal? What's so difficult about this? Isn't it something that anyone can do? It's like picking up a coin on the ground. Oh, um, would it be hard for someone who's not a Hwagyeong to understand? You know how I feel, Gramps, right? Oh, that's what I meant."

"Wow! Sister-in-law, you're really amazing!"

It's a very proud and arrogant Qing.

Since my friends were already used to it, I just listen with one ear and let it out the other as if it were the beginning again and pretend I'm not listening.

The strangely rotten expression on Xuega's face makes me even more excited.

\textit{Oh my, I can't get enough of this.}
