\chapter{Convalescence (5)}

Cao Xuanliang was the leader of Wulin.

If time permits, I will stay up all night praising the Cheonhwa Sword for as long as I can. I am ready, willing, and determined to shake off the old man's scorn, saying, "You were doing well, you were the honored granddaughter of all."

But was the position of leader really one where you can live however you want?

So, I have a duty to hear in detail what exactly happened.

Although the exchange of questions and answers unintentionally resembled an interrogation, she was polite and never lost her smile. Oh, she's so pretty. Please, just one granddaughter, great-granddaughter, or whatever.

There was no need for Mujae, so I will be a pretty child with this kind of personality.

With such a personality, Cao Xuanliang didn't even know what I was praying for.

Anyway.

"So, we can see that the Blood Cult doesn't really have Essence Absorbtion."

"Yes, according to the circumstances."

"That's enough gain. You don't need to worry about being falsely accused of possessing the Essence Absorbtion. A Wulin Alliance  investigation team has been dispatched to Mount Lao, and they plan to bring along some ronins and appropriate factions to investigate."

"Oh."

\textit{Is that also feasible?}

\textit{Come to think of it, instead of just breaking my way through, I could have presented evidence to show where those blood cult bastards were eating, sleeping, living, setting traps, and giggling.}

Of course, there was a huge difference in weight between what Qing said and the results of the investigation by the Wulin Alliance and other third parties.

"There will still be those who attack, but since you were at your level, it won't be a big problem."

But those who didn't believe won't believe.

Even in Qing's homeland, the world's equality can be seen by looking at the prospective murderers who were campaigning to kill their children by never using medicine.

However, this was a realm of disability, not intelligence.

If you believe in the theory of Ximen Qing's absorption of spirits, then it's not like Qing would have to suffer that much.

"Ah. And I met Yun Yuanying, the former Alliance patrol. You may not believe it, but Yun Yuanying seemed to have already surpassed the Profound Realm."

It was a very surprising news, but Cao Xuanliang wasn't particularly surprised.

Well, you have to say something believable to be surprised.

However, Qing was already a master of the art of painting, so it was not something that can be taken lightly and cannot be ignored.

"You're saying that child, Yuan'er, um, that word just slipped out of this mouth. She was such a good child, what  could've happened? Ugh. So, Yun Yuanying, that child has reached the Life-and-Death Realm?"

"She herself said that she has not reached the Life-and-Death Realm, but she naturally summoned hundreds of sword-shaped energy swords, and although she was not a perfect master, she showed off telekinesis, and she played with such a master without a care, and then she threw her into boiling water and brutally killed her. I have seen this with my own eyes."

Yun Yuanying might feel unfair.

'Oh my, I helped you so much, what were you talking about?'

But Qing didn't lie.

Cao Xuanliang's expression became serious.

That's unbelievable.

If it had been said by that guy or any other reviewer, I would have said that you were mistaken and fooled, and I would have never believed it.

If the externally typed swordsmen were determined to deceive, Cao Xuanliang can also come up with all kinds of tricks.

Capturing a super-duper martial artists aerial vehicle with a melee weapon? Wouldn't it be possible if the two of them worked together?

But you can trust Heavenly Blossom Sword's words.

First of all, this child was not so naive as to be fooled by other people's tricks.

Isn't this a timeless tale of a man who achieved greatness at the age of twenty-one?

And it was simply unimaginable that such an upright, righteous, and just Heavenly Blossom Sword would ever lie.

In addition to the imperial family sharpening their swords, now they have to worry about the minions of an unknown blood cult. Has peace been too long?

If there was any consolation, it was this.

"She's definitely affiliated with the Blood Cult, but she definitely has ulterior motives. She's a very dark and nasty woman. Oh, sorry. Anyway, she cooperates, but she also secretly backstabs me. Um, it seems like she's hostile to me. She must have some other agenda."

It's a relief to hear that.

Cao Xuanliang lets out a long sigh.

\textit{How did that good kid end up like that?}

\textit{Boiling a person alive? What a miserable and horrible way to die.}

\textit{When I think about how shocked and hurt Heavenly Blossom Sword must have been to see that sight, my heart aches.}

(The opinions of the people who were at the scene may differ)

"So, do you happen to know anything about the magic used by jiangshi or something? It seems like it's not a realm that can be reached through normal means. was there some way to achieve that realm?"

This was something that would make magicians burst with fear.

If such a means had existed, magic would have dominated the world long ago, and study would have been replaced by the study of magic rather than ignorance.

But what about the current magic?

If you do something, you will be treated like an evil and mean person, saying, "You wicked sorcerer!" and you will be treated like dog food, not cold rice, but even dog food that was given in abundance, so you will be treated like less than dog food.

In fact, if we trace the origins of martial arts, it developed from a combination of Buddhist asceticism and Taoist health techniques.

Also, if you look closely, Buddhist asceticism originated from the Indian Confucianism (Yoga), so martial arts was also just a branch of sorcery.

But the martial artists' claims also have some merit.

In fact, isn't there a well-established path to personal perfection, worldly attainment, and ultimately enlightenment?

The mindset of those who choose to take a detour and learn magic instead of following the straight and correct path was usually extremely evil.

To manipulate others by bewitching their will, to manipulate corpses, to curse them to death, etc.

The sorcerers protest that such things were the aberrations of some unscrupulous and evil sorcerers.

But common sense dictates that we don't refer to a component that makes up the vast majority as a part. It doesn't even make sense.

So, even if you ask Cao Xuanliang, he doesn't know anything about magic.

Just hearing the name, it sounds like something like Kangsi-sul, soul-taking, or shamanism.

I thought that even the art of corpse transport was a magic created to relieve the dignity of the deceased and the grief of the bereaved family, but in the end, seeing that child made me realize once again that magic was indeed an evil thing.

You can't criticize the leader of Wulin and the eldest elder of the Jeongpa, who has lived such a long life, for not knowing this and being so ignorant.

To begin with, the mastery of the current situation was a level that cannot be achieved by leisurely playing around and cramming in such miscellaneous knowledge.

It was natural that the higher the level of a martial artist, the less knowledge he has of anything other than martial arts.

and.

Originally, the higher-ups didn't need to know.

Just use someone you know!

"Well, yes. When it comes to sorcery, isn't Kunlun the best in the world? The Kunlun sect probably knows the details."

"Oh, was the Taoist priest of Kunlun staying in Meng right now?"

"Ahem. That's because they're originally from a remote rural area, ahem, it's far away."

"Oh, that's the part I need to go to……"

Instead of answering, Cao Xuanliang quietly turns his head and pretends to suddenly gain some new insight from the pattern on the wall.

Ah. was this the angle I have to go to myself?

But if you go from the Divine Maiden Sect, uh, it's beyond Sichuan and Gansu provinces, and if you're like this and want to take a carriage, um. It's far…

That was when.

Cao Xuanliang claps his hands!

"Ah. Right. If Chunbong was that kid, I guess I'll know."

"It wasn't Bongchun, it was Chunbong. Akkabi. You mean Hyeonhwa? Oh, even Zhuge didn't know, but I wonder if he knew her as Miss Chunbong?"

"Well, he's a kid who enjoys reading books and has mastered all sorts of miscellaneous books. And somehow, he's… well, he's a good kid, but I have a feeling he might like such evil magic."

"Oh. I did have that feeling."

Wasn't she a beauty with pea-sized pupils, four hundred white eyes full of whites on both the top and bottom, angular eyes, and sharp teeth, who looked like she was about to curse?

Why do you seem to be so knowledgeable about magic?

It was a sad story that would make Sima Chunfeng sad to hear.

Or maybe he could just pretend to lament with a dirty smile, saying that he's so great that he expects magic from him.

So, Jinang Hyeonhwa Sima Chunfeng.

"Oh. Wow."

As soon as I saw Qing, I tried to hold back my exclamation ten million times, but in the end, I failed to hold back.

\textit{Why am I the Three-Headed Beauty?}

\textit{Isn't there a real Three-Headed Beauty here?}

\textit{Or is it? It's a bit ambiguous to call her Three-Head since they're bigger than the head.}

Anyway, despite his tall stature, he was a very vicious Sima Chunfeng with a large chest.

Is that a watermelon or a heart?

Is that a watermelon?

Aren't there two watermelons hanging?

Humanly speaking, we need to check that out.

I demand the truth from Sima Chunbong.

There's a rumor that it's a watermelon, so please cut it open and prove it.

Sima Chunfeng bursts into laughter at the sight of Qing blatantly staring at his chest, as if to pierce it.

"Hahaha! Heavenly Blossom Sword! Even you, Heavenly Blossom Sword, can't help but admire this Jinang Hyeonhwa of Wulin, the shining, greatest intellectual of all time, Bone Samarang! Ah. The fate of the accomplished! How cruel it can be."

Qing'er, oh. Right. That's the kind of kid he was.

I only remember the unsophisticated names of Wanggasum and SaBaekAn. Come to think of it, there were other strange aspects to Lady Wanggasum, or rather Lady Sima.

"If it were you, you would understand this sadness, this loneliness, this sadness of one who shines alone among the foolish things."

"Ah. I understand that. Still, we hang out together because we're friends, but, oh my, with the peak and the super peak, this isn't even a nanny who takes care of children. The great warrior of Hwagyeong has to look after the super peak and the little brats."

Sima Chunfeng flinched at that.

"Heavenly Blossom Sword, just now? Did you say Hwagyeong, Johwagyeong? were you saying you've attained the enlightenment of harmony?"

"That's what happened. I haven't made it public yet, though."

A busy duel unfolds in Sima Chunfeng's mind.

This was after it was objectively proven that Sima Chunbong was a better person.

Height. Heavenly Blossom Sword was a bit taller, but it's not good for a woman to be tall, so Sima Rang Seung.

Nevertheless, when sitting, Samarang's head was higher, which was a qualification for studying in a more advantageous environment while sitting at a desk, Samarang Seung.

Martial Arts. You could say that Heavenly Blossom Sword won, but in reality, this wasn't an objective or fair match.

Because even though Heavenly Blossom Sword was superior in martial arts, his intelligence cannot compare to that of Samarang.

Martial arts was just about being stronger, right?

If we look at specifics like knowledge and wisdom, proficiency in the job, and engagement in organizational culture, wouldn't it be an incomparable advantage?

For this reason, isn't comparing Heavenly Blossom Sword and Sima Lang in terms of martial arts skills too harsh a standard for Heavenly Blossom Sword?

So, let's approach it from the perspective of achievements and fame that were not related to one's age, but rather martial arts.

Compared to the achievements of Sima Lang, who was the youngest deputy military commander and will soon become the youngest general of the Wulin Alliance, it was on par, so it was roughly a draw.

But Hwagyeong?

The weight of the youngest super-peak, the youngest Hwa-gyeong, and the twenty-one Hwa-gyeong martial artist were different.

If you want to be here, Samarang must be promoted to the position of Commander-in-Chief of the Wulin Alliance right now.

Well, I guess I have no choice but to admit defeat this time.

First, when I get back, I'll have to ask my father to retire immediately. He'll go fishing in the quiet countryside with his uncle, who's the deputy commander.

She was truly a fiery filial daughter, Sima Chunfeng.

"Ahem. Good. I guess this was enough for me to be recognized as my lifelong rival by Samarang! Hehe, hehe. Hehe. So, what was the reason why Your Majesty the Heavenly Sword so desperately and earnestly wanted to see Samarang?"

"I didn't look for it like that……"

"You're not being honest! Hehe, fine. I'll pretend not to know and fool you! So, what kind of wisdom do you want to ask of me, Samarang!?"

Do you usually say that you ask yourself?

Qing decided to do something like that.

"I was wondering if you knew anything about magic."

"Oh, oh, oh. I don't know why you're interested in such a visit to the Left, but since you've come to the right place, ask me anything and gain my brilliant wisdom."

"Hmm. Do you happen to know someone called Shihyeol Dokin?"

At that, Sima Chunfeng laughs loudly.

Because the original impression was strong, no matter how you look at it, it looks like the final mastermind was the one who will end it all.

Anyway, seeing the confidence in that smile, I thought maybe I was right in asking-

"Good. Heavenly Blossom Sword. Your victory."

"Huh?"

"Okay, if you want to hear the three words I don't know, I'll admit defeat and tell you without making any excuses."

Ah. He doesn't know either.

It was when Qing was about to ask him the next question.

"But! It was said that Confucius never spoke of supernatural beings. This means that he should not mention such strange things that deceive and obscure reason. It was not a problem that Sima Lang did not investigate it deeply. Rather, it was a great loss to the world for the highest intellect to be absorbed in such a thing, leaving aside other important matters. It was natural that he should not know about it. It was not right to say that he won by it or that there was something he does not know about it. Therefore…"

Sima Chunfeng shot Dudada's horse.

It's not a lame excuse, but rather a different kind of self-defense.

I'm so martial artists that I don't even breathe.

While Qing waited for a long time, the cloud pattern engraved on the bed was so neat and repeating, even though it wasn't machine-generated. What do you call this? Phew, phew, phew. Whatever. Hmm, it's really pretty.

"Huh, okay. Do you have any other questions?"

"Is there perhaps a method in the art of spiritual awakening, especially the secret art of the Unga, that can forcibly elevate a person's level?"

"Please don't attack me with magic. I've already admitted my defeat, so adding more would be fatal and wrong."

That means you don't know.

Well, I guess I'll have to go to the Kunlun sect and ask.

Yeah. I have to see Jeolgeombyeok anyway… … .
