\chapter{Convalescence (11)}

If you eat rice, fruit, snacks, and fruit again, and then eat more, you will find that more fruit keeps growing out of nowhere.

It was a cycle of endless snacks, with the belief that there should be no food left on the table, and snacks that were always sneaked in while you were fighting and eating them.

What the heck? Snacks automatically appear on the table?

Of course, the culprits were the workers of the Xuega Sanghoe waiting in line at the restaurant.

It was a solemn act of the new believers of the Xuega Sanghoe, who had been given a rank through a strict personnel evaluation, offering tribute to the sage god Cheonma Jonhou who had descended into the world of our priestess.

The Qing Dynasty's stomach was not infinite, and even if he stops by the store, he doesn't stay long, so those standing in the back of the line were anxious.

What if I end up ascending to the sacred mountain of the Cheonmasingyo, the spiritual root of the Cheonnyeonsingyo and the home of my heart, Shinnyeo Peak?

No one knows when Shinnyeo Peak became the sacred mountain of the new religion, but in any case, the shrine was in the heart.

How could the sun in the sky, the home of the divine veins, the fire burning in that temple, be objects of worship?

My faith was in the Sun Goddess Mother, the God of the World and the Wise God, and in the Heavenly Demon Lord.

The faith of the new followers in the Heavenly Demon Lord of Jincheon, who conquered the land of Zhongyuan at an astonishing speed in just a few years, which the previous Jinma (who had been confiscated from Heaven) could not overcome even after being defeated four times, was a miracle that was stronger than ever.

Clearly, the Heavenly Demon Lord will also guarantee the future of the new religion, and will either plan some grand strategy or, with his supernatural powers of foresight, foresee the future and provide majestic guidance.

So the Heavenly Demon Lord said:

"Oh, right. Xue Ga-nom! What breast size do you prefer? Do you have a preferred size and shape? Centered upwards? Downward? Long or round and plump?"

"Sorry, but at least it's not yours. Don't you know the saying, 'too much of a good thing'? Excessive breasts were problematic. I like a woman who's a little shy and bashful."

"What were you talking about? I learned how to make amazing yuyu this time, so I wanted to make it look exactly like what I wanted. Now, Xuega-nom, you should be excited."

"It's awkward to say it as if I wanted to run it myself. What good would it do if I ran it myself? I should run it to someone else so I can at least get a handle on it."

"Huh. You know how I feel? I feel the same way."

"Still, it's a bit inconvenient to try to put a bundle of silk in it. It keeps sagging and changing shape. But right now, the business was closed. It got caught by some vicious guy."

I don't know what business has to do with the heart, but Qing doesn't care anyway.

"Ah. I've just started a new business. I'm sure you'll be happy to see some faces. Come take a look around."

"Huh?"

So, Zigui, Boyeol Medical School.

The doors to the large manor were wide open, and a fragrant scent of medicine wafts from inside.

Hmm, why does the smell of boiling herbal medicine taste so good?

It's strangely mouth-watering.

This was the impression of Qing, who had been eating nonstop until a moment ago, chewing his food whenever he spoke, or perhaps talking and eating at the same time.

And then there was a female doctor, scurrying across the room. Her posture was upright, but there was a strange sense of incongruity. As she moved forward, her left and right feet moved, each movement synchronized precisely, creating a strange sense of incongruity, as if she were not even human.

And Qing knows the person who walks like that.

"Huh? Lang Lang? Isn't it Lang Lang? What were you doing here?"

"Are you my friend, Heavenly Blossom Sword? It was Langlang, and you were most welcome."

"What, a medical uniform? You decided to study medicine?"

"It's incredibly entertaining. Humans were truly miserable creatures in pain, and Lang Lang, in front of them, gains a great sense of superiority, a level of satisfaction that's enough to satisfy an omnipotent councilman."

It's not something a doctor should say.

But I completely agree with Qingdo.

Langlang looks at Qing that Gyeonpohee was holding.

"Oh. A very serious injury. Do you want to seek medical attention? That's good. I'm Lang Lang, my skills were very, very limited, but I'll do my best. First, I'll make an incision and try to scrape away the bone. Heavenly Blossom Sword, prepare a Go board. I've prepared a hundred different Go records for this occasion, so choose your favorite. By the way, this was Lang Lang's first experience, his first procedure. He's very nervous. I'll be gentle, so Heavenly Blossom Sword, just follow my instructions."

"No, what was this idiot doing? And why does he speak like this?"

"That's correct. This Langlang was objectively a quack in medical knowledge. But who was this young woman who displays her vulgarity with such utterly rude and foul language?"

"What the!? I was just going to take a look at this-"

"Ugh. I'm going to put poison in there. And you didn't see a single thing."

"But, this kid was clearly weird."

"Use it. It can't be used."

"Indeed, I understand. were humans also beasts, animals raised by the Heavenly Flower Sword?"

"Miss, this was really-"

Qing sighed as he watched the little girl show her teeth.

"Roughly. Similar."

"Qinga? You're only doing this to me again. What's a beast? A beast, and raising it? Hmm? Qingga, you're going to raise me? Isn't that okay? Should I just be an animal? Hey! You!"

The child immediately turns on the twin flames.

Because Xue-i-ri quietly approached Gyeonpo-hee and rubbed her cheek against Qing's shoulder.

What was it? A cat imitation?

Well, let the two bicker.

An old doctor with wrinkles all over his face welcomes Qing.

"Ah. was that the Heavenly Blossom Sword? How did you get so hurt? Hmm, was this Hyang-i, the Tang family's medicinal herb? It looks like everything's been taken care of. You should just lie down and recuperate. It's no use wandering around like this."

"You'll get better soon anyway since you're already healthy."

"You're still young, but you still need to take care of your bones. Don't you understand why they say "bone disease"? By the way, friends? Those were some good friends, aren't they? They're full of guilt. Ahem. No, they're good friends."

"They say it's a joke."

"Ah, Dok-hwa! If you ever get back to the Tang family, tell them I'm well-versed in their medical books. To be able to perform such great medical techniques? I thought my Tang family was truly ruthless. Keuheum, no, Nam A-dang Ja-gang. It's only natural for a general to be poisonous."

"That, Qing'er? Who was this person?"

"You were the elder of the priests."

The expression on Tang Lan-Ah's face becomes subtle.

The treasure of the four pillars? The head of the four pillars?

Then what should I say when I get home?

The Madou of Sapa said that he saw the book well, so it seems like he was asking for a duel rather than thanking me?

"How have you been, sir? You said it was a new business, so why bother with the medical treatment? Isn't it a waste of time?"

"What do you mean? Thanks to you, I'm doing well. What a luxury, after all this time. They say fate was mysterious, and I don't know what I would have done if I hadn't met you."

"Well, it's been a while."

Next to me, there was this guy, Yo, Yo, Yo, who was awkwardly nodding in greeting. I think he was the son of the yoga shop owner, but what was his name? I don't know.

It seems like it's difficult for Yomin to understand.

The doctor just set up his own clinic and was very happy, so he didn't really think much of it.

I never knew Heavenly Blossom Sword was such a precious girl. How could she have grown up to be such a good person and acted well in front of adults?

But what kind of family stole and kept the medical books of those demonic bastards? Isn't that a truly remarkable family? I said.

In Yomin's eyes, it's just that cult.

But I don't think I'll go anywhere, and I'm being treated well, so I guess it's okay.

In fact, to Yomin, there was no difference between Sapa and the Demonic Cult. From what I've experienced, I think they were just good people who have been falsely accused, but with a bad reputation.

It's just a little sharper, but it's true that like a teacher, there was also a disciple.

Originally, sufficient warmth was the way to make people round and round.

Because he was the eldest disciple of the medical staff and the youngest member of the charity medical staff, he received unprecedented respect and admiration.

"Your Majesty! Details of the servant, Mr. Yeom, now! Oh, Miss!? Excuse me! Please continue speaking!"

One of the members of the council was trying to announce something urgently, but upon seeing the question, he suddenly bent down and politely stepped back.

Is Mr. Yeom important now? It's unfortunate, but it's about finding a good grave site.

But the judge didn't think so.

"It seems there's a critical patient. Let's have tea later. I repeat, I'm doing well thanks to you. I brought you some of that special malic tea last time, so I'm sure you're saving it."

It seems like his taste has changed a bit, isn't he the type of person who only seeks out expensive luxury cars?

The fact that they even brew and drink malic tea, which was not considered expensive, was unique, and this was proof that they were changing from a hobby of the nouveau riche to a true tea lover.

For your information, malicha was a green tea with a little malic acid added to give it a flavor. It was called jasmine tea in Qing's hometown and was the tea served instead of water in Chinese restaurants.

Somehow, when you say Malihwa to the Korean people, it feels a bit hazy, but when you say Jasmine, a Western language, it feels completely different.

"Ahem, come here more often. And spend some pocket money, too. That way, it's more fun to give. How come you never hear about losing money on the battlefield? While you're recovering, I'll come often and make you some herbal medicine. I've even opened a pharmacy, so I should use it now and then."

Leaving Choi Riong's regretful words behind, the sun was slowly setting, so it was time to depart.

Shouldn't we eat dinner at Divine Maiden Sect?

Since it was the Divine Maiden Sect, the sanctuary of Geumnam, Paengdaesan said that he would unpack in the city and go on a martial arts tour.

Instead, Gyeonpohee, a skilled pedestal and authority on the water supply, joins the party and heads towards Musan.

Go up past the entrance to Musan, Geumnammun Gate, and climb again to reach the entrance to Sinnyeo Peak.

And as you pass the large rock, the main gate of the Divine Maiden Sect, the mysterious sect of women that people were so curious about, comes into view.

"Ah! The sunset suddenly explodes! What the heck, did the sun explode!? Did the descendants somehow manage to pierce the rest of the sun!?"

"No, you idiot! It's not the sun, it's the Grand Prince!"

"Ah! What the heck! The sun couldn't possibly explode and produce this much dazzling light! It wasn't the sun that was pierced, but my heart! Welcome!"

"Ah, Grand Master Taesasukjo! Welcome back! Representative Dang and Xuehwa too! And hey, Grand Master Taesasukjo's sister, you're being lewd again today! Dirty!"

"How obscene! As expected of the Grand Prince!"

I don't know why I'm there too.

By the way, you seem close with Yi-mei?

Gyeonpohee often stops by the main temple when she goes to the market or when she sends goods from the Xuega store.

Although she had the unique characteristic of being a sister of Qing House, for some reason she had quite a number of followers among her disciples.

"Ah! As expected, the priestess appeared last night and covered her eyes, and when the Grand Prince approached, she didn't dare open her eyes!"

"How can you be beautiful even with a medicinal cap on? Isn't it true that even the medicinal cap becomes beautiful? This isn't the medicinal cap that you put on, but the medicinal cap that has attached you to the Grand Master. Oh, I want to be attached to the Grand Master too! Can I be attached to you as your disciple!?"

Qing snorted at him.

"No, you guys aren't even standing guard, and you're just thinking about the squabbles all day? What the heck, Yeonseo and Sarang, you're the only ones standing guard all day? Did you even get a job as guards at the main gate?"

"We're also amazed! No, no! was this fate? A destiny born to welcome the Grand Prince! Ah, the girl was born for this moment."

"What were you talking about? If the Grand Master of the Royal Family says we were the guards of the main gate, then from now on we will be the guards of the main gate."

"Oh, that lowly girl doesn't even know that, and I'm like, "Ah, haha, I'm fired."

"Oh, me too, ah. Hehe, I'm so touched."

If we leave them alone, our chicks will keep chattering all night, so as usual, I cover their mouths with candy.

But, didn't these guys become more rounded?

It seems like I gain a little weight every time I come back.

"Sassukjo, you're back!"

"Oh my, you're a private tutor? Oh my, your pretty face was covered. What's this?"

"Your Majesty the Great! Your Majesty the Great!"

Seeing the Divine Maiden Sect family members welcoming her with enthusiastic smiles as soon as they saw her, Qing's heart also felt full and plump, as if she was lying down quietly.

Ah, I'm home, I thought.