\chapter{Convalescence (7)}

Zhuge Lixian and Sima Chunfeng search for books, their internal energy burning brightly.

It's not just a matter of finding a book.

A serious matter that affects the family's honor!

While the two proud geniuses were fighting, Qing sat there eating lamb jerky.

From Peng Daesan's perspective, um. What the heck.

Do you chew and swallow?

Does that make you feel the taste?

Maybe it's not because it's delicious, but because you just want to shove something in your mouth and swallow it.

What kind of woman would eat food like this, so the expression "eat it like it's not eating" was exactly right.

The sight of him hastily shoving it into his mouth and swallowing it without even chewing, how should I put it, was just watching, what do you call this kind of sight?

Yes. It's a blessing. It's a blessing to eat.

What a beautiful sight this is.

Paengdaesan watches over Qing with a pleased smile.

Why do you sinful women just take off the amount of food that will melt in your mouth without even chewing it, pretending to be careful and doing useless jaw exercises?

If the Jade Kirin's Guardian Guard and the followers of Saengsa had known, it would have been a thought that would have caused a frenzy of eating like dogs to sweep across Zhongyuan.

Then, suddenly, hiss.

"Now you're not even telling me to try it?"

"What were you talking about? Mountains don't eat things like this."

"Hmm?"

"I don't enjoy snacks, and if I do eat them, they're a bit greasy and don't stick to my teeth. And since I'm bored, I only eat things with a subtle sweetness. Don't you just hate things with a strong flavor that lingers in your mouth for a long time?"

Peng Daesan, who was hit hard, only wiggled his eyebrows.

No, you noticed that? How?

For your information, the taste of the Yuksaenghyangma Yeonyukgan was exactly my sister Paeng Choryeo's taste, and even though I raised her, Paeng Choryeo doesn't know what my younger sister's taste in snacks is.

However, since they both agreed on the idea that siblings should eat well, wouldn't they have gathered all the things that Pang Cho-ryeo, who was anxious about not being able to feed her snacks, disliked and put them in front of her?

There was even a nagging question about when I would ever have grandchildren.

The decisive reason why Peng Daesan leads that army of women who were just so disgusting and yet often leaves Sega and wanders was because of harassment, not bullying.

"Ahem. Even though it seems like I'm just mindlessly eating, I'm expressing my deepest gratitude with every bite. What's wrong, San? Haven't I been able to reach you until now? Wow, what's wrong? This was disappointing. How could this be?"

"Huh. That's great."

Pengdaesan smiled faintly and thought that it was worth it to go out in the middle of the night and steal the supplies by paying a bribe.

So, does that mean you knew that I had been buying you snacks all this time?

Ahem, Peng Daesan Mountain turns its head.

With his earlobes red, Pang Dae-san pretended to turn his face and look at the bookshelf for no reason.

"Anthropological Development Theory Based on Sword Forms Based on Records from the Sui Dynasty"

"Is that the book you were talking about earlier about the party and records?"

"Huh? Oh! Ah! That's it! I guess I was confused because the title was so long."

"Are you confused? I was wondering what kind of snack you were looking for and reading the records of."

"I don't trust reviews of food. No matter how much I read, they'll only say it's delicious. If you get your hopes up and try it, you'll only be disappointed."

It's a mysterious sound that's ambiguous as to whether it's wise or not.

anyway.

If you were a master of the art of painting, you can easily take a book out of the bookshelf with just a point of your finger.

Just like this.

"Mountain! Let's go!"

As soon as Qing takes hold of the book, the martial arts spear immediately reveals its presence.

He made a fuss, shaking his head and begging for the door to be opened, and Qing said, "Okay, I'll consider it a loss and open it for you."

Unga-kwon. Red. Raw heart, red.

Suddenly, Yun Yuanying's words flash through my mind.

They say that it was a martial art that was so amazing that even empty words cannot describe it.

It was really a lack of martial arts skills… … .

"It's obvious that this was a book only a swindler would read. was it some kind of hidden secret?"

"Yeah. I heard it's called Unga Kwon and Saengsimgyeol? Do you know?"

At that, Paengdaesan's expression hardens.

"Jinjueonga. It seems Yun Yuanying told you."

"Yeah. Just in case. There's a world of difference between knowing what kind of martial arts you're dealing with and not knowing what kind."

"It wasn't a particularly impressive martial art. It was a one-point breakthrough, a martial art that focused on the destructive power of a single strike by flexing the muscles throughout the body. Since the powerful training wasn't passed down through the qigong system, they had no choice but to focus on external attacks."

"Huh? You know me well? Oh, we know each other?"

At that, Paengdaesan's eyebrows twitched.

"I used to hang out with my older sister often."

"Oh, and Choryeo? Then Sani must have played with them too?"

"Hmm."

"You're not denying it?"

"You know my personality, don't you? This was completely unrelated to my intentions."

"Oh, well, you didn't particularly dislike Sani, did you? Your sister's friend? Wow, your sister's friend. Right. First love. Why, even though her personality seems to be a bit off, she's still pretty."

"Absolutely not. Absolutely not. And we've known each other since we were kids, so, um. Other than that, nothing happened. Nothing. Perfect. Nothing untoward. I swear on my family's name—, ahem."

"Oh. So, you're childhood friends?"

"Not a friend, but, well, if I had to say, closer to a distant cousin."

"Oh, childhood friends, like family? Oh my."

"No, that's not it, um."

"What's wrong, San? were you hot? were you sweating? were you sick? You were a little upset after lunch earlier, did you end up poisoned?"

"Yes, that's right. That woman really was a poisoner. was there really a woman in the world who actually poisons me, even though I know her face—"

"Lan-Ah, enough gossip. Anyway, what kind of person was Nyeonyeong? She used to be like, "Oh my gosh," and turn people upside down. I heard she was really timid. She was even afraid of things like squirrels."

I wonder if a coward would kill a living person without blinking an eye.

Peng Daesan carefully chooses his words.

"Rather than being afraid, I guess it was more like disgust. They're similar."

"Huh. Why do they look similar?"

"Why aren't there people who were sometimes afraid of bugs? Would a drone be afraid of bugs? To be precise, it's probably someone who shudders at the thought of them."

"Oh. Now that I think about it. That's true, San-i too."

"Why was my name there?"

"Why? You hate women."

"It's either those women who follow me around with nothing to do and make demands as if they've entrusted their hearts to me, or those who don't, but otherwise I don't really care."

"Don't all bug-hating people say that? They just dislike the ones that stick out and cling to them, not the ones that live quietly, hidden away. Well, anyway. So what? What about people? Nyong-nim, has that guy always been a bit persistent and sneaky, and you've always had a bad feeling about him?"

"Not really. He was just a kind, gentle person. Despite his frail health, he knew how to overlook those in need. And he was easygoing, always adapting to others and getting along with everyone. Ahem, I'm not trying to be biased, but that's just how I saw it."

It's like I'm looking at someone with a suspicious look.

What the heck? What really happened between you two?

I think it would be fun, but what if I ask Choryeo later?

Yes, your first love, the blood sect's mine.

I guess it would be fun to tease, but I think this was definitely crossing the line.

It's not something to joke about because it's sensitive, but I guess we'll just have to leave it at that.

"What? You said you were nice? You're not a good fit? You're just acting coy because you're in front of a mountain, aren't you?"

"I think if you ask anyone, you'll get a similar answer."

Qing tilted her head at him.

"Really? Then just ask."

Sima Chunfeng and Zhuge Yihyeon looked upset at not winning, but on the other hand, they looked relieved that they did not lose.

There's something you should ask them first.

"Do you know about the martial arts called 'Talmyeongdo' and 'Talmyeongjeongsim'? was this perhaps a demonic art? A righteous mind that takes life? The meaning was a bit strange since it involves 'Jeong'."

"Ah! Sister! You know about the Talmyungjeongsim! The Talmyungjeongsim's Talmyung was not that—"

"Hahaha, the Cheonhwa Sword was also true. A mask was not something to be taken away, but a mask to befriend. The right study to escape fate, originally-"

"Muipa! Originally, it was a martial art known as Muipa, but it was destroyed during the First Great Battle of Jeongsa-"

"Originally! So you could call it Jeongjong's study. Hmm. Someone keeps interfering with their superficial knowledge, so even the most tolerant of Samarangs feels a bit downgraded."

Zhuge Lixian was startled by that.

And then he apologizes with an apologetic expression.

"Oh, Sima Chun! Bong! Sister. It seems this younger brother has failed to understand Sima Chun! Bong! Sister's feelings and has been rude. Please, Sima Chun! Bong! Sister, as an elder, could you please show some tolerance, even just for once?"

Then, the tendons on Samachunbong's forehead were popping out, wow, one, two, three, four…

Well, Zhuge also had a secret temper.

Of course, rather than just being kind, you should also know how to get angry when you need to.

Well, that has nothing to do with me.

Ta-da, surprisingly, neither Talmyeong nor Talmyeongjeongsim were magic!

Then you have to learn it.

Isn't it true that as the level increases, the internal energy becomes relatively weaker?

Later on, when you get to Hyeon-gyeong, you can say that you have Hyeon-gyeong-level internal energy, but then Hyeon-gyeong was at Hyeon-gyeong's level, so what's there to brag about?

Come to think of it, isn't that the Mu-Gong-Chang guy a scammer or something?

In front of the truly strong, nothing seems to matter and people were just scared and their brains were in disarray.

Wulin can be very, very, seriously unfair.

How can there be such an ungrateful bitch in the world!

"Okay. Hey, does Unyeonyoung know by any chance? What kind of person was she before she betrayed you?"

"If it were Sister Un, she was a graceful person. Honestly, I still can't quite believe she betrayed me. It's just that she was naturally weak. Ah! Speaking of Unga, isn't she a family known for her strong bones? I imagine she suffered a lot of abuse at home."

This was Zhuge Lixian's testimony.

"Well, he wasn't this Sima Lang's match, was he? Huh? Hehe, Heavenly Blossom Sword, you're telling a funny joke, aren't you? Why would someone as brilliant as us remember such a commoner? Hmm. According to this Sima Lang's brilliant reasoning, alas, Sima Lang, you sinful genius! Perhaps, upon learning of Sima Lang's presence in the Jeongpa, you were frustrated and threw yourself into the Blood Cult, a place where you could shine, Heavenly Blossom Sword? Where were you going? This Sima Lang hasn't finished speaking yet…!"

I asked for nothing.

This guy talks a lot when you ask him anything, but he doesn't know anything.

This was why I am ranked last in the bookstore rankings.

But, well, wouldn't the wisdom bag itself have great potential?

When you feel better later, should we take a bath together?

I wonder what's inside that. No matter how I look at it, it's a watermelon, but I can't believe it unless I see it with my own eyes.

"Unnie, no, you mean Unga-nyeon? Well, she was a bit mature, you know? Whenever there was a fight at the Yongbong branch, she would always step in and break it up. Oh, of course, you're a hundred times, no, a thousand times more mature than her. And on top of that, you're so cool, it's chillingly cool. Hehe."

Murong Zhuxi, who insists on saying something obvious.

"no."

"Hello? Was my question a yes or no question?"

"It's not Gunyeong. No."

"Why, when you know it's not true? Um. No. I guess it was my fault for asking."

Xuegunyeong.

"When? I've never met you, and even if I did, you're the only one I have, Qing'er. Whether it's a one-night stand or a two-night stand, just try to catch the eye of that traitorous Blood Cult bitch."

Tang Lan-ah first came out of Sacheon during the martial arts competition.

Of course, I have never even seen her face once.

"Yeah, you know, maybe, um. No."

"……?"

Come to think of it, there's no need to ask Yehan.

Even within the family, he was a training fanatic who would always stay locked in the training hall.

"Yun Yuanying? He's not a swordsman."

"Hmm. I knew it."

"As expected of Sword Friend! We're on the same page! Want to spar?"

"The bones haven't even healed yet……."

After a thorough investigation, I was able to come to a fairly meaningful conclusion.

Is it really okay for the Half-Geom Double Sword Society to remain like this?

Our members were quite sociable, and we're not a group of loners.

Even though Changbin, a regular member and a ghost member, was absent, would it be worth asking him to hear his answer?

Uh, um, sir, um, I don't really know, yes, that's right.

What, since it's so awkward, I'll just say some weird nonsense that's neither polite nor informal.

Suddenly, a tendon bulged out on Qing's forehead.

No, but where was this kid stuck?

The chairman returned from the brink of death with dignity, and set a dazzling record as the youngest Hwagyeong, a record that will be remembered for a long time in the history of martial arts in Zhongyuan, and achieved such brilliant achievements, yet his face was not shown even once.

Just look at this guy, he's so striking.

We need to create a designated seat in the middle of the Bonghwanghoe banquet hall and have Jo Hyung sit next to it.

Thus, the Changbin Dojo, which had been practicing the mysterious and miraculous art of Jahashin Sword in the harsh mountainous terrain of the volcano, was startled.

What the heck, suddenly there's a very ominous feeling… …!

The ultimate goal of a Taoist was to achieve enlightenment through the supernatural powers of heaven and earth, which open the upper chamber to the world.

So, isn't Changbin's achievement of already unconsciously reading a vague ray of hope and sensing something ominous, truly remarkable?