\chapter{Convalescence (2)}

Qing was badly injured.

In fact, if it weren't for the Blood Poison constitution, She would have already died.

If she's lucky, she might wake up in her hometown after that, or maybe this time she'd go to the medieval Western Regions for a new adventure, and the legend of the shabby Western Region beggar might continued.

Well, that's something no one knows.

Anyway, the body that was not infected was this tough and strong.

But that's it.

With the help of the Soo-Ma-Gong, there was not a single part of the body that was healthy except for the part below the elbow, which was the strongest in the world.

First of all, there was one big wound.

From shoulder to the top of the opposite knee.

As expected, one of the three heads of the five-headed sphere was cut in half, and this time, it was the same head that was cut off last time.

That was Tang Lan-Ah's assesment.

"Still, be grateful it didn't get cut off there. If the angle had been just a little higher, or if it had been just half an inch deeper, one side would have been just for decoration."

"Anyway, I'm already hearing all this useless nonsense. Hmm. But I'm not. From shoulder to thigh. Wouldn't it be cool to leave a scar? Should I leave it instead of applying Jechangsan? It'd be manly, like a veteran who's been to the gates of the afterlife…"

Tang Lan-ah's fists trembled.

I've never felt so resentful of my own low standards as I do now, for there's no place on my torso that I can hit, and the rest of my body was so hard that only my fists were hurt.

This was what a bitch who just came back from the dead says, so it's really frustrating.

I quickly escaped from the Blood Moon Manor, took up a position in the infirmary, and stayed by his side for four days, receiving absolute convalescence.

After three full nights of suffering, I finally opened my eyes and was told the rest of the story. was that what I heard?

By the way, when I left the Blood Gate and joined the military, the sound of drums and thousands of cannons were all lies.

Of course, how could the military reach Hangzhou from Suzhou in one night, and how could they even finish dismounting the cannons in that time?

The military were walking men.

There was no way to sweep them away like the Daldan (Mongol) barbarians and Dalja bastards who rode horses, so Wang Ssangryong rode alone and came running out of breath.

First, he raided the Cheonhoso in Hangzhou and conscripted all the drums in the village to surround the Hyeonramun Manor.

First, to stop the fighting by striking the North, and then to bring Madam safely.

When Qing heard this, he realized that the general was indeed a great general.

A brilliant bluff!

Of course, if you listen closely, it was a moment when the demon explorers could easily escape from the blood demons regardless of whether Wang Ssangryong came or not.

Still, Wang Ssangryong did his job well.

Even if they hadn't chased him all the way to the Blood Moon Manor, wouldn't Hangzhou still be a place full of evil men?

It was thanks to Wang Ssangryong and the soldiers stationed around him that the conditions for safe treatment were created.

"Hmm. General."

That guy might go out for a drink at night.

Isn't that the name of the person who watched and reported it again?

But in the end, I guess I've achieved a certain level of honor, so I guess I can be promoted to general again.

When Qing seriously considers exemption from the traitor Wang Ssangryong.

That was the moment.

Urrrr!

A loud noise rings out.

A loud noise, as if lightning were striking, as if the earth were tearing apart, as if a mountain were collapsing!

His expression hardens into a grim one.

But, Tang Lan-Ah doesn't even show any sign of surprise.

Rather, isn't it that he responds calmly as if he knew it would happen?

"Oh, Qing'er, are you hungry? I'll gave you some porridge since you've been lying down for too long."

"I, I, I feel like I'm going to die. Rice, something, meat, sweet and salty meat, stew, galbijjim. And just something simple like beef, pork, chicken, and duck. Fish was fine."

The little girl slapped her.

"Hey, you've been starving for so long, what's with the grease? Hmm, maybe fish would be better. Something like porridge."

"No, meat, meat……"

"Huh. Okay. Just wait a minute."

The little girl heads out of the room.

Beyond the screen that had been erected to block the sickbed, the sound of a door opening with a creak, followed by the sound of the door closing with a creak.

-Excuse me, what's her condition, ma'am?

-How's Qing? I heard she seemed to have come to her senses.

-My sister… …

-She's still unconscious! She needs to rest, so why don't you go back instead of loitering around?

\textit{It looks like everyone was gathered in front.}

\textit{But what the heck, am I actually unconscious?}

\textit{That, something. Like those scenes.}

\textit{Was I was talking on my own, and Lan-ah was talking nonsense to the unconscious body?}

-Lies. I heard everything. What you're saying.

-What the heck, this is. Should I make you drool too? You seem to be hearing things now, don't you? I'll just stick a needle in your ear. That'll clear it up.

-No. No. Liars should have their tongue cut out.

-What? Are you done talking?

-Short story. You're ignorant. You've said it all.

-What, you, are ignorant of this kind of thing, I… …!

It refers to the punishment of cutting off the tongue.

A punishment imposed on a criminal who falsely accuses another person or claims that the police did something to him. If paid in money, it was equivalent to two gold coins.

Originally, the punishments in Zhongyuan could be exchanged for silver and gold, except for treason.

Anyway, after listening carefully to the bird's sounds, it seemed like Lan-ah was trying to block the visitation.

Well, actually, the best way to keep a patient healthy was to do nothing and just sleep, sleep, sleep, sleep, so I guess she was worried.

\textit{But I want to see the kids' faces.}

\textit{I also need to checked to see if there's any injuries on them.}

So Qing took a deep breath and-

"Hey guys-urg!"

The end of the call was truly painful, because the act of screaming basically puts pressure on the chest and causes chest pain.

A rush of happy faces poured in, accompanied by the sound of the door being slammed shut.

"Young Lady Ximen." "Young Lady!"

The first to rush over were Gunyeong and Mo-yong, who hung onto the bed as if they were about to collapse. Ye, who stood quietly and cautiously made eye contact, and Lan-ah, who had a look of obvious displeasure in her eyes.

While San-i and Zhuge-i were watching from a suitable distance, there was a guy who suddenly pushed the women left and right and clung to the bed with a loud bang.

"Sword Friend! Sword Brother! What the heck! That technique! Was that the Nine Solitary Swords! Was it the sword technique left behind by the Great Emperor Mucheon? What was its name! What kind of image does it hold! In my life! Like that! No! Such a beautiful sword! What on earth was that? I'm so confused. It feels I can't even pwopely spiek en sung its name en lyk Imgommaa craii-"

Nan-gong Shencai, who had been shouting passionately, suddenly began to speak slowly and his pronunciation becomes slurred.

Then, he slowly leant to the side, and Xue-i-ri, who was next to him with her eyebrows furrowed subtly, immediately stepped aside.

Nan-gong Shencai falls to the floor with a bang.

A single needle stuck out from the back of his neck.

There was Lan-Ah with her eyebrows raised and her hands outstretched behind him.

"Hmph, can't you see there's a patient recovering? You don't even know basic manners when you come to visit?"

"Hey, hoik, eeeeee, wooingie……"

It was Nan-gong Shencai who bravely asked for the name of the technique even after being poisoned.

Everyone just looked down at Nan-gong Shencai, who had collapsed, as if they had found some scattered food waste or human excrement.

"Young Lady Ximen-" "Young Lady-" "Hey. Qing-"

Words suddenly poured out at the same time.

And then they turned their heads and met each other's eyes, and their gazes exchanged, and it seemed as if they finally reached a silent agreement.

"Qing-" "Ximen-" "Young Lady-" "Sister-"

There was no agreement at all.

But even so, isn't it obvious?

Since they were going to ask if she was okay, if she was sick, and things like that, Qing decided to answer in advance.

"I'm fine. It hurts everywhere, but not too much. It's bearable. My Qi and blood flow were a bit damaged, but it'll get better if I leave it alone. There aren't any fresh wounds, so I'll be fine with enough rest. So, there's no need to worry."

The group looks visibly relieved, and Qing speaks again.

"Ah. But honestly, my heart was aching a little, no, a lot, seriously, and there's a bigger problem than that right now…"

Everyone's expressions become serious and they all look at Qing at once.

Then, Qing's expression turned sly.

With an extremely annoying expression.

"This body, Unrestrained Realm."

Tang Lan-Ah had a rough idea of when the first flower bloomed with a halo, but the rest them were oblivious, each occupied with their own task.

At that time, as everyone were about to congratulate her-

Qing struck first.

"Oh, you don't know what Unrestrained Realm is? Unrestrained Realm\footnote{化境;Huajing} is short for Cration Realm\footnote{造化境; Zaohuajing}, but do you know it's also Principle\footnote{思想; Shixiang}? It's the power of the mind that bends the world. From now on, my will is the law, the true state of martial artists beings who bend the laws of the world. Can you imagine how many things I can accomplish? Of course, you can't imagine. How could you, who aren't even Unrestrained Realm, understand?"

Everyone's expressions turned sour.

Except for one person who was paralyzed and fell down.

"Ohh!Esekspektt Sordbro!"

It was a bit slurry, but she understood it's a compliment.

Qing smiled kindly at her friends who looked at her in disbelief.

"Ah. Of course, I'm a peerless master, and even if you guys tried, it's only at Transcendent level. But even so, you're still my precious friends, and I'll respect you as members of our Half-Sword Double-Saber Association. What should I say? Oh, right. I don't have any sense of superiority. No matter how different our realms are, we're friends."

And then, huh, she started acting annoyingly.

"Of course, you guys who can't even understand me can't understand me."

After Qing said that, she laughed out loud really good, but then, ah, pain came over her chest and she groaned in pain, and then she couldn't hold it in anymore and burst out laughing again.

Everyone's eyes were cold as they looked at this ridiculous scene.

'Either laugh or be sick, just do one thing.'

They really wanted to slap some sense into her, but they couldn't lay a hand on her, who's wrapped in bandages all over her body, using her physical condition as a shield.

Either way, Qing was very satisfied.

\textit{Seeing their annoyed faces, isn't it worth the pain?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It's not like the teasing lasted just a day or two.

If you think about it, even when she reached the Transcendent Realm, Qing spent several days just shining the starlight of Sword Force and saying things like, 'There's nothing like this in that house.'

"Oh. Is it a little dark? Yup. Here, it's sparkly."

Small lumps of light the size of soybeans floated above Qing's head and shoulders, scattering faint starlight.

Force Compression, the symbol of an Unrestrained Realm martial artists.

In fact, the power of Kang-Hwan was quite poor, and the process of releasing the true energy into the air and concentrating it to form a solid was extremely difficult, and it consumes a lot of true energy and requires great concentration.

It's much more powerful and convenient to just put your true energy into the weapon and throw it.

So, although it was a powerful technique that any master of Hwagyeong could use, it was also a technique that was not used in actual combat.

Usually, it was used as a silent threat to show off before a fight, saying, "I'm Hwa-kyung, so I won't fight on my own."

If you really want to use it, there were often cases where you can use it as a substitute for a memorization weapon when you have nothing to throw in your hand while keeping a distance.

So what, everyone was like, haaah, I get it, they're excited, so let's just let them enjoy it.

Actually, it's quite a feat.

Qing was exactly 18 years old last year.

Myoryeong means a woman in her early twenties.

So, the exact age was exactly twenty.

So this year was twenty-one.

Hwagyeong at twenty-one?

The youngest person to reach the peak of their power at the age of twenty was recorded in the history of martial arts, but twenty-one?

What kind of realm can you jump over in just one year, or to be precise, in just a little over a year since it's already the middle of autumn?

Actually, I can't believe it.

Is that Hwagyeong at twenty-one?

How can you believe that?

Even if I had seen Kang-hwan with my own eyes, I would have thought that she had somehow imitated Kang-hwan's appearance.

That one move that Qing showed, the legacy of the Great Emperor Mucheon, as he himself revealed, that one moment of Dokgo Gugeom's first technique, that magnificent moment, I wouldn't have believed it.

But I've already seen the realm of great ideas that turn the world upside down, so, um, was that right?

Even at its peak, it was a blue that was filled with hundreds of thousands of strong energies that fill the world of countless changes.

It was reasonable to suspect that she might be a woman who could be used even at the peak of her powers if she were prepared to die.

But the group knows the blue.

He often talks nonsense, and at the same rate, he talks nonsense, so half of what comes out of his mouth was empty nonsense.

But even so, there was no case of telling a lie, so it was not a lie to say that he reached Hwagyeong, and there was no reason to do so.

So, um. The world was so unfair.

By the way, if someone heard this, they would be shocked, astonished, and upset, and their true feelings would explode.

The direct descendants of the Five Great Families and the Ten Great Families, and even the daughter of the Ice Palace, were born into the best families and the most precious bloodlines and grew up without any shortcomings, so what's the point of being unfair?

(Of course, Xue-i-ri has the right to feel wronged.)

"How is it? Is it a little brighter? Still dark? Ah, there's nothing I can do. This master of Unrestrained Realm, the peerless master of Unrestrained Realm, Unrestrained Ximen Unrestrained Qing, will specially bestow this."

A giant dumpling was stuck in Qing's mouth.

"Stop talking and eat quietly."

"Ah, this was it, oh my."

It was Qing who never bragging about her realm until the end.
