\chapter{Convalescence (12)}

Tang Lan-ah and Xue-i-ri go to the guest house to unpack their bags, and Qing'er heads to the ambiguous cliff at the corner of Sinnyeo-bong.

In Qing's memory, it was small, well, not exactly cozy, but still my home.

Even with my eyes closed, the sight was still vivid.

Around the corner, there was a small, somewhat lacking house, and a little boy taking the obvious place.

As expected, Chen Changming, swinging his sword alone in the empty courtyard, looked at Qing with the feeling of an exclamation mark, a punctuation mark that did not yet exist in Zhongyuan.

And as Ododo begins to run, Qing gets down from the human palanquin itself, Gyeonpohee, and stands on his own two feet.

As Qing spread his arms wide, the little one's expression also brightened. Although he had good proportions, his short legs moved even busier due to his short height.

"Sister!"

"Little one!"

And then suddenly.

Jian Buxi catches Chen Changming.

Although Chen Changming was struggling, Jian Buxi was a master who was about to reach Harmony Realm, and even a first-class player cannot resist her.

Moreover, I cannot help but have a reasonable suspicion that the Geon-Gon-Dae-Na-I that Hee-Mae has mastered was a martial art specialized in changing the direction of force, and was created to provide the ultimate riding comfort when transporting me.

"……? Ugh, what is it, let go."

"Haha, it's a shame, but due to national law, a master of the Hwagyeong and a first-class swindler can't dare to embrace. Instead, I'll give you a cute Yi-mei. Be content with Yi-mei."

"What? There's no such law. Eek, let go of me."

"Am I cute? I've never heard anyone say that."

Jian Buxi tilted her head.

Qing confirmed with sincerity.

"Well then. Isn't Yi-mei the second cutest girl in the world? Don't be disappointed by this. This was also amazing."

"Is the first one me?"

"No. It's Xiang? The kid's face is surprisingly thick. No, come to think of it, she's always been thick."

"……? Who is that?"

"Yi-mei. Could you please lower your posture a bit? It's not fair to be on the same level as a first-class master of Hwagyeong. Oh, that's even more true."

When Chen Changming stands on tiptoe, he starts to tremble at the height his feet touch, and then, with a shocked expression, he finally asks a question.

"What? You're on Hwagyeong? Harmony Realm, Sister? Really?"

"Yep. This is called Force Compression. It's so shiny. It can even be used as a lamp in the dark."

"Oh, congratulations, no, let go, let go."

I thought she might be listless or something because she wasn't helping in Mount Lao, but she's fine and focused on training.

Qing reflected a little on that.

How much did you underestimate Jang Myeong-i to do this?

Wasn't it me who was making fun of her?

Qing unpacks, or rather, watches Gyeonpohee unpack, and asks.

"Come to think of it, what about Master?"

"He's gone."

"Hmm. It's weird to say that. Did he go back to Taiyuan?"

"Oh. My sister asked if I could send a message, so I asked if you wouldn't send it."

"Well, then, you must be reading it by now."

It was resolved well, and now that the master and the disciple have reached the same level, the saying, "A blue fish comes from a blue pond, but was bluer than a blue pond, and ice comes from water, but was colder than water," was said for this disciple.

Since the Master was no match for the duel, wouldn't the disciple win if they fought? As expected, the Yangtze River's back wave pushes the front wave, and so he sent a letter telling him not to worry.

"Oh. Right."

"Huh? What's right?"

"You're right, Sister. Grand Elder is incredibly angry. She even said she should have broken your legs to keep you from leaving."

Qing said confidently, huh.

"That's why I risked my life to climb the mountain. But if you saw me climb the mountain, you'd melt away."

First, Qing gave greeting to the Sect Leader.

In fact, since Qing was an outer disciple, there was no need for her to first greet the Sect Leader.

However, there were rules within an organization, so if Qing went to Ximen Surin first, what will become of Sect Leader's authority?

Of course, Wang Ju-hee of Cheondun Sword was a person who has always been hidden and has no presence, just like her nickname (though she had recently establishing presence through relief), and she was not the type of person to establish authority in a position that she had shoved on by force.

She's the kind of person who would nod her head and say that the teacher comes first even if Qing passed her.

But Ximen Surin cared about her disciple's authority, so if Qing found her first, she would surely scold her, saying that even if he leaves the sect leader behind and heads first, and even if the sect leader was not easily visible and has no presence, he was likely to forget about him and that it was a matter of etiquette and manners.

"Ah! That is an accomplishment. Oh dear, if I'm not careful, I might get caught up with our Youngest Sister."

"Hehe."

"Master is waiting, so you go ahead and see her. Ah, Physician Tang? I'm sorry to ask this after such a long time, but could you spare a moment of your time? Young Lady Xue will be heading straight to the training center, right?"

"Oh." "Yes."

Only then did Tang Lan-ah recall the excessive workload she'd experienced during her last visit to the Divine Maiden Sect. Now that she thought about it…

But what can we do about what has already happened?

Even if she had known in advance, she still would have followed the Qing, so what, she should just do her duty.

So, Qing'er Bo-mu walked confidently, or to be exact, with a confident mind, but her body still a bit unwell, so she walked slowly towards Ximen Surin's moat.

Inyoung suddenly appeared and clicked her tongue in displeasure and spoke in a stern voice.

"What a mess, how can a grown woman act like a little child? What a disgrace!"

"Oh, Master! Ugh!"

Qing tried to run out with a bright smile, but a sharp pain came over her and she couldn't breathe.

Pain was originally meant to relieve muscle tension, but in an unexpected situation, the tension just dissipates.

The moment my body tilted, I was hugged.

Qing, held in her master's arms, was faint.

"Hehe, Master. This disciple Ximen Qing comes to see you."

"……What on earth can I do with this burn?"

Ximen Surin sighs deeply.

I put a long bandage over my eyebrow, cheek, bridge of my nose, and from the side of my eye to my chin on the other side, so the swelling has gone down and it seems to have gone down.

With that face, he was groaning and groaning as he climbed the hill, looking like he was in pain, so how could he just sit there and wait?

I was momentarily upset that I should scold him, but after seeing him injured, I blurted it out without realizing it.

There was no such useless bitch in the world.

How in the world can a master care for a sick disciple? Should an old master hold his disciple in his arms? What a miserable thing.

Not knowing that speed, the disciple just hehe.

It's a mess because I'm so happy that I was hugged by my master.

"Master, has anything changed for you, disciple?"

"With her face completely covered, how could anyone recognize her even if she changed? What kind of rascal would disfigure a woman's face like this? They deserve to be wiped out."

Ximen Surin's answer was very blunt.

He was angry and his temper was boiling, but he couldn't bring himself to say anything to his sick disciple, so he naturally let out a cold voice.

The veterans of the previous generation may feel very wronged.

I got beaten up because I was asked if there were men and women in the martial artists area and if I was really being ridiculous for avoiding my face and chest during the duel.

If she's still a bitch even if you hit her in the face, then she's just a bitch who wants to beat up people.

"Not that. It's like energy."

"Hmm?"

Ximen Surin's steps stopped.

"Have you been tempted by the Demonic Gate?"

"Hey, Master, would your disciple be able to enter that gate?"

So, Hwagyeong? Hwagyeong? A disciple who reached Transcendent Realm last year suddenly reached Harmony Realm?

There was no precedent like this one.

What was a knight? Even before knighthood, there was a precedent for strange things, so it was called a knight. It was something that had never happened before in the world.

But more than that, what kind of predicament did he have to be in to suddenly appear like Hwa-gyeong?

Now that I've held him in my arms, I know that not a single bone or blood clot remains intact. I can't even imagine how horrific it must have been.

What kind of hardships did you have to endure to get to this point? I feel so depressed that I can't breathe.

"It all started with a single treasure map. Tihs disciple was in Taiyuan, absorbed in my studies, studying the scriptures and sayings—"

"Let's go up first."

As usual, Ximen Surin entered the room carrying her disciple, passing through the wide open main gate.

And when I asked her the whole story, she proudly stuck out her chest, and it seemed like her chest was always sticking out, but somehow it was sticking out more.

However, because it was so prominent, one side was bulging and it was obvious that something was stuck on the inside, making Ximen Surin's insides boil.

What kind of nonsense broke my heart again?

"When Disciple was in Taewon, I was burning with passion with the teachings of the Hundred Schools of Thought, so I asked all the scholars to listen to my interpretation. While this disciple was studying so diligently, uh, um, what was it, a demon or a fiend? Anyway, I met some rascals who were plundering on the border, and I cut them down, and suddenly, a treasure map appeared. Master, do you know what a treasure map is? Oh, you know treasure map. Senior Sister even wore underwear made of it. Anyway, that treasure map was…"

Qing was babbling without knowing the speed.

She was very eager to show off her heroic deeds.

Not even noticing the teacher's anger slowly rising.

Then, Essence Absorbtion Demonic Art!

Ximen Surin's rage bar filled up to the brim in an instant.

\textit{This little wench knew just how vicious Essence Absorbtion Demonic Art is, and how terrible the desire to obtain it!}

\textit{And that bastard Tian, I told him to teach her some academics, but why was he bringing along this precious disciple?}

But for some reason, the full bar began to tremble and eventually began to lower the water level.

\textit{Calm down. Calm down. Isn't the child in pain?}

\textit{And even though she couldn't tell the difference between heaven and earth, she is still a woman of chivalry, so her spirit should be praised.}

\textit{But am I supposed to do about it? Even if I punish her, she'd just rolls around in pain and still won't listen.}

In any case, it can be said that Qing's decision to come straight to the Divine Maiden Sect was a very effective one.

Patient shields have always been a timeless strategy!

Then the Blood Cult appeared!

Rage Bar Threshold Breakthrough!

But it persevered!

Life-or-Death duees! The legend of seventeen against one!

How much anger could the rage bar held? It's already full.

But the kid was sick, phew.

But I persevered again!

A midnight escape! The tumultuous chaos of the Hangahyeonsin!

Ximen Surin's fist trembled and his appearance was like a silent sob, so how mysterious was the expression "a fist crying"?

But my friends came to my aid and I persevered for each other, and I achieved a miraculous realization and achieved growth.

"……That's how I reached the Harmony Realm."

"Me, you, us. Hmm. This teacher is glad you've made some really good friends."

Fortunately, the anger level has subsided at the Samyang section, so at least one big worry has been relieved.

This girl was always yearning for human kindness, but seeing the harmony, I thought she wouldn't go to extremes and lose herself.

"How did Master achieve the three yangs?"

Ximen Surin smiled brightly at her.

Isn't it the moment that all teachers in the world most eagerly await, to have a conversation with their disciples about the three yangs of enlightenment?

"Living as a woman, I witnessed the absurdity of the world, and I saw pitiful women suffering without even realizing the injustice it inflicted. So I knew that the cause is this era. And so, wasn't it my calling to rise up?"

"Ah. Yes."

"Now that you, disciple, have entered Harmony Realm, aren't you a true master of your time? As a female warrior, shouldn't you also consider the women we should protect? Originally, women weren't treated this way. During the Spring and Autumn Period and the Warring States Period, those who called themselves teachers used malicious language to deceive us…"

\textit{Ah. This. I asked the wrong question.}

Although Qing immediately regretted it, it was already too late, Ximen Surin's mouth was open, and the words that had been piling up were finally coming out at this moment.

\textit{So where am I? Who am I?}

\textit{They say time is relative, and it really is. Did even Mr. Al, with his charming tongue, found the expanding time and space by listening to naggings?}

But humans were creatures that save themselves.

Kkwarrung! The grand protests from Qing's stomach, the roaring cries for food, cut off the epic poem of Ximen Surin.

"…I guess it's important for Disciple to eat well since she's sick. Oh, right. Has your scar healed well?"

"Ah. That's right. Master, look at this."

Qing'er, who dared to take off her clothes in front of her teacher and show her scars.

Ximen Surin's expression hardens at that.

From the shoulder to the opposite thigh.

It was horrifying to hear, but the thick, swollen scars of the incision that remained clearly were indescribably gruesome.

Oh my gosh, how much it must have hurt.

It was a moment when Ximen Surin's heart was filled with emotion.

However, even if there were no scars, it would naturally be a sight that would make a teacher's expression harden.

If a disciple exposes his body to his master, wouldn't there be a huge problem, regardless of whether he was a man or a woman?

"Master, isn't this cool?"

Ximen Surin's eyebrows twitched.

Rage bar, breaking through the threshold.

"Hyang-i, ah, there's this really cute kid named Zhuge Hyang-i, and Hyang-i was also really cool. He seems like a veteran with a lot of experience, and he seems like a master."

Ximen Surin's eyebrows twitched.

\textit{What exactly is the appearance of a master?}

\textit{Just like the Sapa guys, there are a lot of idiots who deliberately cut their own faces, so the disciple's words are just at that level.}

\textit{And even if she say it's cool in empty words, what's the point of preserving the scar?}

\textit{Is this bitch planning to show off her scars by showing off her naked body to everyone?}

Ximen Surin's fist cried out bitterly.

\textit{Endure, endure. It's not too late to punish after she recovered, so endure for now.}

"So, if I don't erase the scars and leave them as they are-"

Dismissal!

What a mess!

The sound of a rage stick exploding!

The pent-up anger surged up over Qing's head!

Taak!!!

It was a majestic eruption, a primal destruction, a splitting apart of the most powerful force in the world, the fundamental unit that forms the foundation of the universe, the sun.