\chapter{Convalescence (4)}

When the Wulin Alliance heard the news about Mount Lao's bloody death, it was none other than the news that had been relayed by the Hanlin Academy's Scholar of Study.

This was news that sent shivers down the spines of the Wulin Alliance leadership.

Essnce Absorbtion Demonic Art, Blood Cult, and the Heavenly Flower Sword.

Essnce Absorbtion Demonic Art was an important matter.

Blood Cult was also an important matter.

But above all, the Heavenly Blossom Sword Ximen Qing was the most important, the most crucial matter.

Because, rather than asking for help, wouldn't that Heavenly Blossom Sword have asked for no involvement?

It was the will to escape alone to prevent a bigger bloodbath and a possible expansion into a civil war.

How wonderful and mature this is.

Now twenty-one, when a man was twenty-one, he was drunk on the power of a reckless child and was full of pride.

This was the reason why young people in Wulin got into all sorts of trouble in their early twenties, past their prime.

It was common for a brat who looks down on others with a haughty attitude and cannot tell the difference between heaven and earth to run wild with his meager strength and then break down and cry and tell the truth.

But look at the Heavenly Blossom Sword.

Even though she was a young genius who had broken many records for the youngest person to reach Transcendent Realm, she never showed a single shred of arrogance.

(The opinions of Qing friends may differ)

She was a model student who was good at studying (kung fu), and when she saw adults, she greeted them first with a polite yet cheerful smile, asked how they were doing, and chattered away in her beautiful voice without showing any signs of difficulty.

This was why these days, the elders were constantly talking about how their dream for the rest of their lives was to have a granddaughter (or great-granddaughter) as beautiful as Heavenly Blossom Sword, and they were constantly jabbing their children and disciples in the ribs.

There was no other child in the world as pretty as this one.

Even the appearance was pretty.

On the other hand, when making friends, there was no distinction between those from prestigious families and those from ronin backgrounds, so wasn't she friendly with everyone regardless of background or faction?

However, she hated the wicked and did not turn a blind eye to injustice, so she was a young but dignified knight.

What kind of organization was the Wulin Alliance?

Wouldn't it be a gathering of warriors who pursue harmony among the martial artists people who walk the path of righteousness and contribute to the peace of the world?

The appearance of the Cheonhwa Sword was said to be the very spirit of the Wulin Alliance.

This was the news I heard at a time like this.

So, it was inevitable that chaos would break out in the Wulin Alliance right away.

Rather, if Qing had urgently called for help, saying, 'Help! Help! Save the Cheonhwa Sword! The intentions were good, but the results were bad!', the Wulin Alliance would have felt differently.

'Even the Heavenly Blossom Sword is just a child, so she doesn't know what to do and what not to do, and ends up causing a big accident.'

'They say she's the youngest person to reach the peak, but isn't the scale of the accident unprecedented?'

Instead, the opposite happened.

'The world could easily be dyed in blood, so please, Wulin Alliance, do not make any hasty moves.'

'Since it is my own fault, I'll take responsibility for it.'

'I will somehow finish it myself and return.'

How can adults remained silent when they hear such words from a child they were supposed to protect?

However, as was the case with large organizations, the event did not happen in a flash.

Even if you go out with a small number of people, isn't it the nature of martial artists to rush in if something seems easy?

The leader called together the masters and assembled a battle group, and the number of warriors gathered was ten battle groups, three hundred in number.

Three hundred masters might seems small, but this was similar to the total mobilization order for the Orthodox faction.

Three battle groups, totaling about a hundred men, headed to Mount Lao to investigate the Blood Cult's traces, as per Heavenly Blossom Sword's statement.

And the two hundred men of the seven battle groups decided to head to Hangzhou to rescue Heavenly Blossom Sword.

So, Murong Chengyik, a peerless master who happened to be in the Wulin Alliance, had rushed to the scene after hearing the news of his runaway daughter's accident, but was at a loss when he heard she had run away again. The ninth rank of the ten greatest masters in the world, took over as leader.

Thus, a large-scale rescue force of the Wulin Alliance, led by Murong Chengyi, set out from Kaifeng!

A speedboat advances along the canal.

However, just as they neared Suzhou, they saw a high-ranking official's ship passing by. It was as if they were holding a banquet on board, with drums being beaten and musicians singing.

As expected, those government officials were like that.

Even when the world was in danger, they seemed so carefree and relaxed.

They didn't know that the sound of the drum was the sound of the victory banquet.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Kaifeng was a city that was once engraved with the shame of a great warrior.

Because back then Qing was only at Peak Realm and a Transcendent Realm.

\textit{What's the big deal about hitting the Peak Realm? Embarrassingly, flower petals are fluttering and people are even congratulating me.}

\textit{Wow, if only my feet were okay, I'd want to kick the blanket over my face.}

\textit{How could people satisfied with just Peak Realm? Or with Transcendent Realm?}

Anyway, Kaifeng!

In Kaifeng, there was the pride of Kaifeng, the Wulin Alliance.

There was one carriage that goes to the martial arts alliance.

After the guard at the main gate of the Wulin Alliance confirmed their identities, he opened the door wide and ran out in a hurry, quickly leaving the place behind.

The carriage heads to Mucheon-gak, the most precious guest house of the Wulin Alliance, the highest guest house for VIPs, without a guide.

They were the arrogant, haughty Mucheonggak squires.

This place was famous for stubbornly turning away guests who come in without a word, but this time, they greeted them with a bright face as if they were waiting.

'Hey, why were you welcoming me like this, when I'm a special guest? How have you been? You're not going to make a scene with a guest who's just trying to make a fuss, were you? If you were, just say so. I'll give you a real hard time.'

"Hey, what's the big deal? Why are you welcoming me like this? How have you been? It's not like there's a guest who's making fuss,right? If they were, just say so. I'll give them a serious piece of my mind."

Who would dare to make a fuss in the middle of the Wulin Alliance?

However, since even the words spoken were truly beautiful and thankful, it was only natural that the servants would give the top of Mucheongak without even noticing.

So, Qing's group unpacked their bags and sent a messenger to say that they had arrived to the Wulin Alliance and would pay their respects to the leader.

But? The leader?

"Child!"

"Ah! Ximen Qing, a disciple of Wulin, greet the leader. How have you been?"

Qing tried to force herself up while lying on the bed.

"Oh my, child, don't get up and just lie down. What the hell was this?"

She tried to held it in as best she could, but when a master like Cao Xuanliang sees it, she could't help but show its true colors.

\textit{This foolish girl!}

\textit{Even though she pretended not in pain, her eyes trembled and she secretly took a deep breath. I feel sorry and thankful for the way she tried to act okay in front of adults.}

Cao Xuanliang was amazed.

\textit{I barely managed to organize and send out a rescue team, but where did all those punks go? Were they rescuing people or just sightseeing?}

\textit{She came back on her own two feet, so what the heck?}

Still, Qing insisted on raising her upper body.

Since Cao Xuanliang tried to stop her, she couldn't even get up and greet him properly, so she scratched the back of her neck with an ambiguous smile full of apology.

Cao Xuanliang let out a pitiful sigh.

Except for her thin, white hands, all her exposed parts were wrapped tightly in bandages, even covering her neck and face with medicinal bandages.

"Hehe, it's a wound that will heal with just rest."

Still, Cao Xuanliang sighed in relief because she was okay.

In reality, the voice was not hoarse, so there was no sign of illness.

And above all, if you pray very earnestly, it was said that even after three days, the great man will grow amazingly and rub his eyes without realizing it and see again.

This pretty girl was already showing off her incredible skills, so much so that even a master of the Tanscend…

"Huh? By any chance? I'm not blaming you, so don't be shy and please answer me. Were you enticed by Demonic Descent?"

Cao Xuanliang's logic was simple.

Twenty-one. And since she reached Transcendent Realm last year, it's impossible to reach the state of harmony already.

In fact, if you jump just one step from the Early to Middle-Stage Transcendent Realm in one year, wouldn't you already be an unprecedented and miraculous knight?

But it was possible if you entered Demonic Descent.

\textit{Isn't the child's appearance this miserable?}

Cao Xuanliang knew how much of a weakling the martial arts people could be in front of the divine power, how willingly they would abandon humanity and become monsters worse than beasts.

So, in that bloody fight, in a situation where even friends were involved, the desire to seek strength at the crossroads of life and death was what leads one to desperately push oneself through the gates of the devil.

Even Cao Xuanliang himself, wouldn't he have been tempted by the devil?

\textit{When I decided I really had enough of getting beaten by a mad dog every three days, I reached the gate of the Demonic Descent. How shocking was that bloody and brutal scene.}

\textit{And how deadly that temptation was.}

If the Female Mad Dag was not a woman but just a mad dog, Cao Xuanliang would have also been possessed.

After thinking about it, he realized that it wasn't an environment where he could beat a woman just because he was in a bad mood, and he also realized the absurdity of the world, so he rejected the devil.

"Oh, that's not it."

"I'm not blaming you at all. Overcoming the state of mind was difficult, but you're only twenty-one years old, and you have sixty or seventy years left, so it's not something you can't achieve. In fact, your speech was remarkable, and your character was upright yet gentle and kind, caring and cherishing others. There's nothing to worry about."

It's a mistery who on earth that had that personality, but Cao Xuanliang's words were kind and full of sincere comfort.

It was hard to believe that the highest elder of the Orthodox faction would be so kind to a Demonic Adept who could explode at any moment.

"It was truly embarrassing to say this in front of Leader, but this girl has achieved a small feat, and by good fortune, she has reached the enlightenment of harmony."

A wave of Qi spread throughout the room.

It's not a dangerous technique, it's just a simple sound blocking technique used by extremely skilled practitioners who blocked out sound by spreading a curtain with their True Qi.

"Ahem, I'm not doubting you, but then, could you tell me what your Three Principles, your Three Yangs were like?"

"It was me, you, our. Because I exist, my friends exist, and because my friends exist, I exist. That's how we come together to create the world. Hehe, it's a little embarrassing…"

The Harmony Sutra was a state that can only be reached by clearly understanding and accepting with one's heart the Three Yangs that each person holds within themselves.

"Good! I am the human, and the other was the earth. However, the other was also the human, so you too can become the earth. In this way, they all come together to form the sky, and your world expands and expands, able to embrace the whole world."

It was of little help to impart the enlightenment of the Three Yangs to those below the level of Unrestrained Realm. In fact, it was somewhat of a hindrance.

You have to realize it yourself. If you focus on and get lost in other's Three Yangs, you will end up wandering around for a long time and just keep reciting three plausible things.

That's why Cao Xuanliang asked while blocking out the sound in the room.

Then he was shocked.

\textit{Unrestrained Realm? Unrestrained Realm? At twenty-one years old?}

\textit{What was I doing when I was twenty-one?}

\textit{When I was just about to reach Peak Realm, I was drinking heavily and playing around with women, and then, right, I was drinking heavily and saw a beautiful woman and started hitting on her. I should have known she was a fucking madwoman.}

\textit{Anyway, Unrestrained Realm?}

\textit{Does this, does this even make sense?}

\textit{No, common sense is, to begin with, limited in experience and limited in what I have seen, so I can only see a very small part of the world and am therefore narrow-minded.}

\textit{And yet, you're saying you've redefined the world through your own eyes and reached a state of harmony? Does that make sense?}

\textit{Maybe she lied about her age, since she's really deep, dignified, and mature for a child. But even if she lied about her age, she'd only be around four or five years older. It'd make more sense if she were in her mid-to-late thirties.}

Cao Xuanliang's eyes trembled violently.

"Alliance Leader?"

"Huh, ah. Right. Right. Oh, what a great fortune for Wulin, truly extraordinary, no, truly congratulations?"

"Thank you. I'm still lacking in many ways."

"No, don't say you're lacking. Even humility can become rude if it was excessive. If you're lacking, then who in the world is not lacking? Unless you intend to make fools of all the people in the world, then don't even think of such things."

"Yes…"

Qing's answer becomes gloomy.

Cao Xuanliang was like 'Oops'.

"Ahem. That's not it. Hmm, yes. It's really good to see you like this, and hearing such good news makes me think Orthodox faction's future look secure, and my heart was filled with satisfaction. I can't express how satisfied I am."

"Thank you. It's all thanks to me, the great genius of the century, the great Chohwagyeong."

"Huh?"

Cao Xuanliang looks dumbfounded for a moment, but then realized that it was the kind of joke he really liked, and laughed heartily with a kind smile.

"Yeah. You really listen well. But, um."

Cao Xuanliang had a serious expression on his face.

"Have you made your achievements known to the world?"

"I wanted to do that, but Zhuge'er, ah, Young Master Zhuge Lixian said it would be better not to do that, so I told only my close friends."

"Yeah, that Beastly Sage kid, may have been a bit, no, seriously, talkative, but he had a lot to say. That was a good choice."

Even he, who was ranked among the top ten masters in the world, was envious of this amazing achievement, so how could those who were not like him feel?

It would be fortunate if it just ended with jealousy.

There were many forces opposing the Orthodox Wulin.

Now that she's truly on the path to becoming the next world's greatest, would they really leave this young master of Hwagyeong alone?

She's not just becoming the best in the world.

She was the sprout of an absolute powerhouse beyond the standards of the past, like the great master Mucheon.

Also, since the Great Emperor Mucheon didn't just cause ordinary trouble, everyone in the world knows what kind of disaster an untouchable, absolute power can cause.

Even if she doesn't go that far, will the government just leave this child alone?

\textit{Now that I think about it, this child was also the one who discovered the fact that the royal family was sharpening its sword in Wulin.}

\textit{It was truly a great blessing for the Orthodox Wulin.}

Cao Xuanliang's eyes become even more profound.

Of course, he didn't think it would be a big problem even if it was widely known.

Unrestrained Realm at twenty-one, isn't that absurd, ridiculous, and pure nonsense?

No one would believe it, but whatever.

"Whether or not to make this known to the world is up to you to decide after consulting with your Master. As an outsider, I have no right to interfere."

"Eh, how come you're an outsider? You're the highest ranking member of our faction, and if I were to be more precise, you're my Martial Uncle."

Cao Xuanliang's heart skipped a beat at the sight of Qing's smiling eyes!

Anyway, there was not a single word that was not lovely.

\textit{How unfair is Heaven! How could it give birth to the Cheonhwa Sword and then to Yeo Gwang-gyeon!}

\textit{How could that bastard have such a pretty disciple!}

\textit{This is absolutely ridiculous! This can't be happening!}

\textit{Is it true that disciples must be beaten up?}

\textit{This won't do, I'll go and get some ironwood right now and whip it, no, just one whip wouldn't be enough to beat up that kid, I'll have to carve them from different types of woods.}

Of course, Cao Hakche and the Cao Yangyang might feel wronged.