\chapter{Convalescence (9)}

"My lady, if this keeps happening, when will we ever meet again? Hehe."

Oh my, was this aegyo?

Although she acts like an adult to others, perhaps because of that reaction, she acts like a child in front of Qing.

It's not that it's not true, but it seems like she's really sad and regretful about breaking up.

If you tell him not to go, he'll run away and come after you.

However, Murong Shengyi whispered to him and said that Murong Jia's true power was in his left and right swords.

A sword in the left hand and a katana in the right, a dazzling swordsmanship that sheds a faint moonlight and a Taoist technique that was like the upright sun that shines down straight down.

Until now, Murong Zhu Xi herself has said that she does not want to use the Tao, and the Tao itself was not a very feminine weapon.

I was worried that if I went through a complete transformation, I would end up with muscle growth only on my right side, which would lead to an unfortunate situation where I would end up with one arm.

So, this was Murong Zhu Xi, who used the sword technique instead of a similar straight sword, and used it in the true dual-wield manner.

However, now that we have reached the peak of our power, it was the right time to properly complete the vision of the Left and Right families.

The so-called super-climax special map.

So, Qingdo can't do anything about it.

"You can always travel together, right? So, when it's important, you have to train hard."

"yes……."

It seemed like he didn't want to let his shoulders slump, so Qing spread his arms and said, "Well, I guess there's nothing I can do about it. I'll have to cheer him up a little."

It seems that Murong Zhuxi was carefully holding Qing's body, as it was in a bad condition.

Qing whispers in his ear.

"Don't slack off, work hard. If you achieve something, maybe I'll give you a reward."

"Gulp."

The sound of Murong Zhuxi swallowing heavily.

Looking at his expression, it feels like there were swirls in his eyes. was this motivation or not?

My mouth was wide open, oh my, my mouth was watering.

Is this okay? I feel like I've become more stupid.

But soon, a firm determination emerged from beneath his thick, curly hair, so it must have clicked.

Actually, I don't know what the Qingdo reward is.

What on earth was the reward for Lady Moyong?

I just thought that since Murong Zhuxi was strangely obsessed with rewards and punishments, she would not work hard if I did this.

There was one gaze that was constantly looking at him.

It's Miss Su-bak, no, Miss Sama, who came out to see me off.

To others, it looks like a fierce beauty glaring at her with resentment.

Qing just smiles and opens his arms.

"Would you like a goodbye hug, Miss Sima?"

"Haha, so this means we should engage in a friendly competition as rivals? Of course, Lady Ximen still has a long way to go. And even if it's not even a hug, since we're not even children! Well, fine, Samarang, I'll gladly join in on your childish antics."

Even though he said that, he spoke quickly in the middle of the conversation, as if he thought he might say something, and his steps were as expected, full of pride.

Yeah, I don't think he has any friends either.

In fact, if it weren't for his strange words and actions, Samachunbong had a surprisingly good reputation.

If only he didn't keep complaining about his shortcomings at the end of every sentence, Samachunbong would surprisingly like to help others, but for the same reason, he was considered a good person but not one to be close to.

Just one hug like that.

For the first time since his departure from Wulin, Qing felt an unfamiliar feeling of being overwhelmed by something heavy and oppressive.

Although the rareness was great, it was in a position where Qing was crushed because it was originally soft.

What was so hard and heavy?

It's definitely watermelon, watermelon.

It was a regret of eternity that I cannot confirm it with my own eyes.

"Come to think of it, it's problematic to think you'll remain defeated forever. Heh, Sima Lang, the next time I see you, you'll be the highest authority on Zhongyuan' sorcery. So, you'd better rub your eyes and prepare yourself to meet the future authority on sorcery. Heh heh."

"I'm going to ask the Kunlun sect, so you don't have to do that."

"Uh-huh. Heavenly Blossom Sword, you're trying to walk the path of the apostle, intoxicated by the sweetness of a fleeting victory? Of course, silencing Samarang was a great achievement, and it must have been the most thrilling moment of your life. But you won't be fooled twice. Hehe."

It seems he was really upset that he didn't know anything even though he told him to ask anything.

Well, I told him to do as he pleased.

Anyway, if there was someone in the martial arts alliance who knows a lot about sorcery or witchcraft other than Kunlun, it would be a good thing, so there was no reason to stop them.

And so, with the two people seeing them off, the carriage of the Qing party slowly started down the road.

The destination was Hubei Province.

The most famous martial arts school in Hubei Province is, of course, the Taegeuk Wudang, the Wudang School.

The Divine Maiden Sect was famous simply because it was a mysterious sect of women. What if you asked ordinary people to show you just one of the Divine Maiden Sect's martial arts?

Since it's a priestess's gate, except for cases where it's a priestess's sword and you have to guess correctly, maybe one in a hundred people will answer.

But these days, six or seven out of ten people will answer confidently right away.

I know that! Heavenly Blossom Sword, Wolnyeogeom!

Of course, of course it was wrong.

Anyway, the rumor that she was the youngest and most beautiful divine dragon in Wulin and that she was very beautiful has this much ripple effect.

Moreover, these days, the Divine Maiden Sect suddenly becomes a landowner and offers generous terms, so tenant farmers flock to the area and several small villages were formed.

This was usually a characteristic of large sects that enjoy absolute support within the region, and it was also their main method of capturing public sentiment.

So, as a neighboring shaman, I am a little, no, very concerned about this aggressive expansion of the Divine Maiden Sect.

Indeed, was Wang Ju-hee of Cheondun Sword really aiming for hegemony in Hubei?

It was a well-known fact that Cheondun Sword was Yeo Gwang-gyeon's puppet, so does this mean that Yeo Gwang-gyeon means this?

Could it be that the legendary women's country, the Yojikyung, was planning to enslave men and establish a female-dominated society?

Of course, the current Moonju Cheondun Geom Wang Zhuji has no thoughts.

Because I had never managed the suddenly expanded land and had no one to manage it, I just left it to the youngest sister of the owner of Xuega Sanghoe.

So, they don't know that the Divine Maiden Sect tenant farmers believe in a somewhat bizarre form of the Shinnyeo legend and bow down to a god who doesn't exist in the thief world.

The daughter of the goddess Yohee succeeded her grandfather, Yeomje, and appeared as the sun, moon, and stars, a god who controls the sun and the moon.

For reference, the sun and moon were combined to form Ming, which was the sacred fire.

This sacred light, the sun-worshiping religion, has similar names such as Baehwa, Baehwagyo, Myeonggyo, Ilwolsingyo, Shingyo, and Magyo.

In any case, thanks to this, Jagwihyeon has also grown rapidly day by day, and the small town that was originally the first ferry crossing on the Yangtze River and was only involved in logistics was currently experiencing a period of miraculous growth, with buildings being erected in one day and new streets being built in two days.

It's truly a miracle on the Yangtze River!

And the destination of the Qing party was none other than Hubei Province! And within Hubei Province, it's none other than Zhuge Liang!

Hubei Province was a long and narrow province, and the powerful clan that holds hegemony in the east was none other than the Zhuge Clan.

Above all, to the right, a cool waterway stretched out to Hefei, Anhui Province and Nanjing, Jiangsu Province.

So, it was a route that Nan-gong Shencai and Gong Sun-Yaoyi can take together on their way home.

So, Hubei Wuhan. Zhuge Liang.

"Ah, Gaga!"

"Oing."

Qing's eyes widened.

What the heck, a very, very cute creature was approaching.

A cute little creature with a clean expression, a round face, and flapping its tiny limbs.

"Hyang-ah! Ugh."

Qing, forgetting her condition, hugged me tightly, and then the muscles and bones in her entire body screamed in unison and it stung!

I can't breathe and I'm sweating profusely in an instant, but it's okay, I'm okay, I can do it, I can do it… …!

Qing forces a smile.

"Gaga? Hehe, the scent has gotten a lot heavier? The girl has been working out hard on her muscles. Here it is. It's already come out this much."

Zhuge Hyang shows me his arms.

Soft arms with no muscle at all.

Why do arms fold? Even Hyang-i can fold her arms? Wow, that's amazing. She folded her arms really well. Should I praise her?

What on earth does that mean?

More than that, between the small lips of Zhuge Hyang who was smiling brightly, there was a gaping front tooth, oh my!

There's a gaping hole where his front teeth are, so this rascal has really sharpened his sword!

Is there such a thing as a monster that was harmful to the heart?

It's just that Zhuge Hyang was at an age where his baby teeth were falling out.

Even though he has no front teeth, he smiles brightly and looks like a fool, which makes him twice, no, ten times cuter.

So this unity!

Xue-i-ri, who was holding Qing, who was holding Zhuge Hyang, crosses the Zhuge family.

"No, put the kid down. A kid who's not even healthy enough was hugging a grown kid…!"

Now, he's a rascal who even gets jealous of his children.

But, since he originally had a rather ugly personality and was a child, I don't think it's something to be taken for granted.

Zhuge Xiang's expression darkens at that.

"Are you feeling unwell? Gaga, were you hurt?"

"No. I'm fine."

I'm not sure if it's sincere or not to ask if I'm hurt even though I have a bandage on my face.

Of course, Zhuge Xiang really doesn't know.

The children of the Zhuge family, who were strategists who worship power, tend to play a bit too aggressively.

When he called for everyone to gather to play, one of the three of them took turns putting a poultice on their face, so Zhuge Hyang must have just fallen over somewhere.

And then I met the lord and greeted him.

I also met Zhuge's mother, who was still rugged and strong.

Zhuge's mother, Daeungdaenyeo Hwang Bo-ran, looks at the Iron Sword and the Moon Sword and her eyes light up.

"Hmm? The Heavenly Flower Sword? What was this? Such a beautiful weapon? To wield such a weapon, you must be a giant among giants. The government didn't just ignore it, so it must be something the Sapa's Madou would wield. Ah, I see. was it a trophy? The Heavenly Flower Sword, despite its thinness, was magnificent."

Hmm. When evaluating people, do you usually use the expression "thin"?

"Mom, that's not it."

Zhuge Lixian whispered to his mother.

When measuring the thickness of two people, it was impossible to convert it into the common unit system of Zhongyuan, so the most appropriate one was fragrance.

If we assume that Il Zhuge Hyang was as thick as Hyang-i's waist.

Zhuge's mother was Zhuge Hyang, who only has one arm.

And since Zhuge inherited that blood so strongly, so strongly, that even though there were only two people attached to him, his vision felt full.

Then, suddenly, Hwang Bo-ran's eyes lit up!

"My goodness, being thin and thick isn't always the answer. Of course, that does happen sometimes. It would have been nice if my body was in good shape."

And then, haha, he laughs heartily.

"It's been a long-time dream, isn't it? To have fun lifting weights, throwing iron weights, and feeling your muscles tearing apart, all with a girl who's like a daughter."

"Ah. Yes."

"He's so weak, so why were all the kids so weak except for Ahyeon? She can even lift the Heavenly Blossom Sword well. A man isn't all about muscles. We need to properly examine whether it's water muscles or real muscles. Oh my, I was just fooled by those temporarily inflated muscles. But he came to see me and lifted a stone weight every now and then, so I thought it was cute. Oh my, what am I saying, nonsense, hahaha!"

And then he patted his son's back with a hearty laugh, what the heck, Taehyung all of a sudden?

In the evening, the Zhuge family held a grand banquet.

"Gaga! Gaga! This too! Can you have this too!?"

The pork that you can eat by dipping it in with chopsticks was Dongpo pork that was served whole without being cut.

Hmm. The shape of the pork belly was very well preserved.

Even if you cook it moderately, it will be enough for three people, or about one pound, based on the standard pork belly restaurant standards.

But I can't disappoint Hyang-i.

Qing took a bite and said, "This was physically a bit, a bit short on space."

The sight of someone dangling a whole string of pork belly from their mouth and mumbling about was definitely not something you should show to the elders at a banquet table at someone else's house.

"Good! You're eating so heartily!"

"Yes! The baby was truly blessed."

However, the aesthetic sense of the Zhuge family was different from that of ordinary people, so the elders did not hide their joy and delight.

But, somehow, your eyes were a bit ticklish.

What was this? This tight-knit family atmosphere.

I'm not being sarcastic, but were you really looking at me like I have honey on my face?

He was a blue who never stops when he says he was good at something.

In the past, even Xue-i-ri would ignore them and pretend not to be in the group.

Eat well and sleep well.

Hyang-i's sleeping habits were surprisingly annoying, so she was kicked with her fists and feet, and an unfortunate incident occurred where Qing couldn't sleep.

It's okay. It's okay if you don't sleep for a day or so.

The master of Hwagyeong was only for one night.

The next day, we leave for Zhugese.

"Gaga! Come again!"

"Sister, I'll come see you later!"

On the way, we stopped at the ferry crossing on the Yangtze River and saw them off.

"Sword Friend, when you get better, definitely stop by! I'll stay up all night to talk to you about the swordsmanship of Grand Master Mucheon. Hehe, just imagining it makes me excited. I'll never let you sleep."

I must not go near Anhui Province.

Qing made a big promise.

"Miss Ximen? You should definitely come visit sometime. Um, if you're going to do it, around the 15th of May or the 15th of October. No, the 15th of May would be ideal."

It's a fairly specific date.

"Huh? Yes, was there any event going on then?"

"Other than that, it's either hot or cold. October was sometimes windy and rainy, so it's only cool for about ten days in May…"

Nanjing was a land that was terribly hot in the summer and cold in the winter.

Of course, it was only the homeland of the Qing Dynasty and the capital of the country, but it was harsh enough for the people of Zhongyuan, so if you were to name the city with the worst weather, this was the place that always comes up.

"Well, I'll definitely come visit when I have time."

"Or I can come and find you."

Gong Sun-Yaoyi smiled faintly, and the two held hands tightly, creating a heartbreaking scene.

Although it didn't look very good because Qing was being held by Tang Lan-Ah.

For reference, Tang Lan-ah was quite short and Qing was quite tall, so the shape was even more awkward.

And only then did the group head west.

Sweet home within the house, towards the Divine Maiden Sect.
