\chapter{Convalescence (1)}

Qing collapsed and smiled with all her might.

Why, just looking at media like movies, I can't help but think how cool it was to play a role where someone burns themselves out to overcome adversity and then falls down with a satisfied smile.

So, I thought that Qing had finished it off in a pretty cool way.

This was why mass media abandons people.

You should have known that the way you imagine yourself was very different from what others see.

Blue's imagination: Lying down as if dead, but with a relieved smile of positive imagery that everything was accomplished and done, conveying the will to leave the rest to his friends.

What my friends saw: Oh my, this bitch was going to get slammed! She's really going to get slammed!

The blue knees give out and the legs fold.

Of course, the one with the most weight, the huge, massive butt, was the first to hit the ground.

The torso tilted in the cold and the back of the head was hit.

The legs were bent in the shape of a sickle and the arms were spread out at subtle angles, so if I had to describe it, I would say that it expresses the character swastika with its body.

What a smile, as soon as I lay down, I coughed, and vomited a word of blood, so the blood overflowed and flowed out in all directions, east, west, south, north, eight, sixteen, thirty-six, three thousand six hundred.

The blood that couldn't come out seeped into the airway and made a loud noise with the sounds of gasping, gurgling, and gurgling.

So, the little girl screamed and clung to him, and he squeezed his mouth open, pulled out his tongue, and turned his head away.

And then this time it was trembling!

The convulsions spread throughout her body, and she started jumping around like an epileptic and making a lot of noise like a crazy bitch.

The expression on Qing's face as he listened was bitter.

"Oh, um. I guess I was a little ugly……."

"To be honest, I don't even know how Qing'er was still alive. It wouldn't be strange if she died a long time ago. No, it's strange that she's not dead."

The little girl cried the whole time.

She cried while pulling out the prayer of the blue dragon, she cried while barely inserting a needle into her trembling body, and she continued to cry while manipulating the doctor to administer medicine and stitch up the wound.

Tang Lan-Ah's medical skills were not at the level of a female doctor like Qing, but she was one of the most skilled among women.

And judging by Tang Lan-Ah's medical knowledge, Qing was already dead at that time.

If your body was trembling and your heart was pounding, it means that your body was already lacking blood.

According to the medical book, how should we treat the condition in which the blood was lost, breathing was shallow but very fast, the heart beats slowly, the whole body trembles, and the patient becomes delirious?

One, it stops the bleeding quickly.

Two, pray and offer your sincerity.

Even if it weren't for that, with such serious injuries, it would be more difficult for a person to live, because the human inside was inherently vulnerable to the poison of the world.

No matter how I live, the future was clear in my eyes.

The fever will rise and the wound will rot and yellow pus will flow out.

This was the beginning of a realm of faith where all medicines were ineffective and one must overcome them with sacrifice and sincerity, such as cutting thigh flesh and feeding it, cutting off a branch and feeding it blood, or boiling it and feeding it.

So Tang Lan-Ah cried.

however?

"Oh, my body is actually quite though."

"Quite though? It's fortunate I was there, otherwise you would have just died."

"Of course. I could just collapse then because I believed in you, didn't I?"

"Haa. I really can't live like this. I can't live like this. Anyway, after you collapsed, those blood demons suddenly stopped moving…"

The lower-ranking blood demons had no intention of approaching Qing's surroundings, so with a glimmer of morale and a surge of hunger in their eyes, they continued their work towards the Sapa warriors.

The most hostile food beggar in the world, just a bite of my heart.

But the rest, the blood demons whose souls were so subservient that obeying orders took precedence over their own lives, were the same.

Changsanya's orders were to cut off, break, or capture that woman's limbs. I don't know why he did this to his little master, but he did so because the orders of a higher power took precedence.

However, Changsanya, who gave the order, was split in half and died, so there was no need to follow him any further.

And the only one left in command was the fallen little master.

But the little master has fallen, and now the hierarchy has been readjusted, and the big master was in no position to give orders.

"Then?" "Now, what do you do?" "Free time?" "I'm hungry." "Me too." "Me too." "Me too."

And the prey that the great master cares for (the prey that the great master has chosen) cannot be touched carelessly.

So, all of a sudden, my head turns around.

"Is there food over there?" "Heart." "Heart!" "Me too, I'll eat too!" "Heart, let's see the heart!"

"……Suddenly, everyone rushed towards the Sapa bastards. Thanks to that, I even had time to deal with Qing'er. You really think you've been blessed with so much luck."

"Oh, I kind of expected it."

As Qing tries to scratch her cheek, Tang Lan-ah lightly slaps the back of Qing's hand.

Then, I gently and carefully scratch Qing's cheek with my fingernails.

"Your bones aren't even intact. Why do you keep raising your arms? Where were you? Does it tickle here?"

"No, it's not that it tickles. It just."

"Anyway, you knew that if you defeated the Blood Cult leader, the Blood Demons would attack?"

"No. That's not it. It seemed like he was just following orders, so I thought, Changsanya? If I just killed him, he wouldn't just stand there and not move."

"Ha, you believed that and fell down after just one stab?"

"No, well, even if it wasn't, you guys were here. We held off San and Sword Friend well, so if they join us, there won't be any problems."

It was quite surprising that they had to rush into the Sapa guys, but it was a good thing anyway.

In fact, what Qing was really worried about was the reaction of the Sapa guys.

Even the most hopeless and hopeless of the five great families wouldn't dare to harm them, but isn't there always a chance?

So what if those kids run around like crazy?

What can I do about that?

I have no choice but to trust and leave it to you.

The best Qing could do was to prevent the immediate annihilation by the Blood Cult.

The rest of us can only trust that our friends will somehow take care of it.

I feel like there was no solution,

These guys were pretty damn good, and they're kind of hanging around the edge of the uninhabited area, so they should be able to handle that without me. Don't you think?

Hmm.

But even though they were all young, they were only at the peak of their power. It's really embarrassing.

I guess that's because I'm a doctor of Oriental medicine, but wow, what do you mean by super-climax? How dare you attach a symbol of super, transcendence to something so super-climax-like?

And then he'll have an epiphany and start talking like, "I'm at the peak, I'm at the peak, I'm at the peak."

Wow, my goodness.

If I were you, I would be so embarrassed that I wouldn't even be able to show my face.

Tang Lan-ah tilts her head at the somehow ominous gaze.

"Anyway, thanks to that, I was able to buy some time and quickly get Qing'er on board……."

With the Sapa vs. Blood Cults dueling for their hearts' contention, it was the perfect time to step down, the perfect moment.

But that doesn't work.

Because, the state of the blue was so critical that it was impossible to lift or move it.

Fortunately, Gong Sun-Yaoyi had brought a generous amount of Jinwon tonic elixirs and golden elixirs.

So, while Gong Sun-Yaoyi was melting the strong elixir by some means and feeding it to him…

"for a moment."

"Huh? That, that thing you fed me, I didn't know that, because I was bleeding, but that woman did it? I, I didn't do it."

"So. Did I steal the elixir? Yeah, Jinwon must have been seriously injured too. No, just take care of your own life. were you okay?"

Tang Lan-ah's stomach was bursting.

With your whole body wrapped in bandages and your throat hanging open, was this the time to worry about others and lie down?

It seems like he has learned a little bit of medicine somewhere, but he seems to be asking me about Qigong medicine, which was a completely different type of medical vision that has been passed down through generations.

"Hmm. That woman… well, she's fine…."

The little girl was roughly swayed.

But would it be as convenient as a pouch that you can just take out, use, and then refill?

Of course, doing something like that will shorten your lifespan.

However, since the human body has the inherent tendency to regain health, it was possible to slowly recover to a certain extent through long-term nourishment and nutrition.

In fact, the root cause was damage caused by continuous overtime work, hard labor, mental shock, drug abuse, excessive sexual desire, etc.

Doesn't the saying that vital energy was damaged and that vital energy was restored mean referring to the very source?

However, the act of artificially extracting and using it was not a good thing. No, in fact, it was a taboo that made me think it was just crazy.

In that regard, I have no choice but to acknowledge Gong Sun-Yaoyi.

If Gong Sun-Yaoyi continues like this, won't he end up like those old people who don't know martial arts, with a hunched back and a lot of small illnesses hanging from his back, his bones getting worn out, and suffering from epilepsy, incontinence, and all sorts of old age-related ailments?

I don't know if it's possible to take a picture of the current situation and then re-establish the origin by going to Banrohwan-dong, but I can't tell anyone that the current situation was no joke.

If Gongsun Yo-ye doesn't want it, and the weak-minded Qing finds out, it will only make her feel uncomfortable.

And he was the only one who risked his life?

I risked my life too?

"anyway……"

Because Qing's muscles were so strong, sewing and tying were Xue-i's job.

The clock was very unstable, so they stab you in several places and put needles in the board, and a disaster occurs where drops of blood leak out.

On that subject, she suddenly became skilled at sewing wounds, so I thought she was not a martial artist but a woman who made a living by sewing.

The noble and dignified lady of the Ice Palace had probably never even touched a needle, but to Tang Lan-ah, it was a miracle that made him wonder if this was a talent.

"Huh. Isn't it funny that a woman named Muin has a talent for sewing? I told you, she's like that. Well, I knew it all along."

Listening to it makes me feel a little sad.

Gunyeong, that kid was not very good with his hands, so how much sewing must he have done… … .

But if I try to package it positively, well, well, I guess there's one thing I'm good at.

Sewing was good, isn't it? There were no noble or base professions… right?

"Anyway, I've finished the urgent matter……"

Those were the times when the three women were busy saving Qing, and the three men were on guard, glaring menacingly at their surroundings.

Meanwhile, the number of magic explorers had been halved and disappeared.

However, it was unfortunate that all of the dead and fallen were of low level. If we look at the faces of those who were flying and crawling and breaking the blood demon's skull, there were five masters of Hwagyeong.

"Hey, how's Qing?"

"There needs to be a properly equipped hospital! If we can move him gently, make him a stretcher, something like a stretcher! And a thin blanket!"

"I'll be back, brothers!"

So Zhuge Lixian leaves the place in a hurry.

So after a while.

It was a muscular man who had somehow managed to make a neat stretcher out of nowhere.

"Well, how about it, Sister Tang? This was about it. If you need any further guidance, please feel free to let me know and I'll take note."

In my opinion, it looks like it would sell like hotcakes even if I sold it.

In fact, wasn't the Zhuge family a famous bloodline not only for their intelligence but also for their dexterity?

"I'm going to carry Qing'er, so you hold her legs, and Gong-son, hold her head there. You have to support her buttocks, not her bones. Okay, here we go, one, two."

The boy was placed on a stretcher, his arms and legs neatly arranged, and secured with a cloth.

Ready to get out.

"Okay, that's enough. Let's wake him up too."

Now, all you have to do was sneak away while the Blood Demons and the Magic Explorers fight.

That was the moment.

-Can't these guys stop fighting right now!

A voice that rings out loud.

Even though it doesn't have much internal energy, the voice was incredibly powerful, so if it's a talent, it could be considered a great talent.

As a general leading an army, he should naturally have this level of vocal power, so Wang Ssangryong's voice was incredibly loud.

Drums bang bang! The sound of drums resonates from all directions.

The high-pitched sound of the drums being struck from all directions was one of the military's old and fatal techniques to let you know that you were already surrounded.

True military wisdom was winning without fighting.

Of course, the name ‘kill' does not suit a technique that breaks the will to fight and does not shed blood.

"Thousands of cannons already surround you! The laws of the land were so strict, why were you causing such a commotion under heaven?"

Of course, the blood demons don't know the law of the land, so they keep attacking.

The magic explorers couldn't just give up and let their hearts be torn out, so they just kept fighting.

So what if I hear the sound of a drum?

Besides, even if it wasn't Wang Ssangryong, he had already finished preparing to escape.

The drums were ringing, and there was no drum like this drum.

And amidst the loud beating of the drum, a man who has transcended his limits opens his eyes.

He was a newly born warrior who has stepped out of the frame of the peak and reached the starting point of a superhuman who refines his inner heart into starlight and emits it.

And so, the newly born superhuman, Murong Zhuxi, raises two swords up and down in a cool manner.

One was as bright as the sun's light, the other was as cool as the moonlight.

The sun and moon were the foundation of the world.

With the sun above and the moon below, the principle of heaven and earth coming together was enshrined, and Murong Zhuxi shouts with a clear will.

"I'll protect you, my lady! I won't let anyone pass until they step on my corpse! Now, charge!"

"……." "……." "……."

Of course, no one jumped in.

Ding ding ding!

The back drum was in the middle of a loud noise.