\chapter{Convalescence (6)}

We must rescue the Cheonhwa Sword.

No matter what bloodshed blocks my path, I have no regrets about losing my life.

The future of our martial arts world was being fought alone in a lonely battle against the enemy, so why would it be a shame for an adult to sacrifice himself to take care of a child?

If it comes down to it, I'm ready to even fight a war.

With such a solemn resolve, finally disembark!

Heavenly Blossom Sword Rescue Operation, Begin!

"Are you referring to the Heavenly Blossom Sword? Oh, you're a little late. They boarded a boat and headed to Kaifeng about half a sichen ago."

Heavenly Blossom Sword Rescue Operation, End!

"But, why did you all come so far to see the Cheonhwa Sword? As expected, I had no idea that the fame of Ximen-shi, the most beautiful woman of all time, Wutou Fangzheng Chang'e Huashen Luoyan Xi Shi, would spread so quickly. This is the true power of Jiangnan, leading the culture of Zhongyuan. Haha!"

"……?"

The Jeongpa warriors, who had rushed into Suzhou city to gather information as soon as they got off, returned with dejected expressions.

But what on earth was Ximen-shi, the most beautiful woman of all time, the Wutou Fangzheng (Five-Head Fragrant Beauty), the Chang'e Huashen (Chang'e Incarnation), and the Luoyan Xi Shi (Falling face Xi-shi)?

It was not Fangzheng\footnote{方正}, but Fangting\footnote{芳婷}, fragrant and beautiful, so her five heads were fragrant and beautiful.\footnote{Both fangzheng and fangting spelled the same in Korean, bangjeong (방정) }

'Chang'e incarnation' meant the incarnation of Chang'e\footnote{Chinese moon goddess}.

It was not Luoyan\footnote{落雁; falling geese; referring to the story that Wang Zhaojun (one of Four Beauties) sorrowful face was so beautiful that even flying geese forgot to flap their wings and fell down} but Luoyan (落顔)\footnote{Falling face} that means to lower one's face, meaning that even Xi Shi \footnote{another of Four Bauties} lowered her face in shame\footnote{reference to two of Four Beauties, Diao Chan (moon hiding in shame) and Yang Guifei (flowers wilted in shame)}.	

They were saying she was the most beautiful woman of all time.

Ximen-shi?

In Zhongyuan, the term '-shi' was an extremely respectful title given to divine beings, such as immortals. Since it was difficult to say their names carelessly, they only call them by their surnames.

Leaving behind countless questions, the Wulin Alliance rescue team quietly boarded their boast and left through the canal they came in through.

And so, the Wulin Alliance.

"This brat! A-Xi!"

The former leader of the Heavenly Blossom Sword Rescue Squad, Lee Geom-il, Murong Chengyi, called out to his daughter in a stern voice.

\textit{I was relieved that the troublemaker had become more mature these days, but I never thought that she would cause such an accident.}

\textit{Essence Absorbtion Demonic Art? Did she not even know how much the cursed flesh was desired by so many people and rushed at it so recklessly?}

\textit{The part about it being for a friend was good.}

\textit{But if it was for your friend, you should have stopped her.}

\textit{Even if you couldn't dissuade her, you should have at least informed the elders of her family, her allies, or any Orthodox member.}

\textit{How can you go that way without anyone knowing?}

\textit{If she had made one mistake, I would have lost the most precious daughter in the world forever, so this time, I will give her a hard and severe scolding!}

"Ah, Father……!"

"Hey! Even if you're so reckless, you still-"

\textit{Scold her firmly! Scold her. Scold?}

"Hmm? Daughter? Why are you so pretty today? No, it's not justbecause you're my daughter? A complete transformation, oh, you've reached a new level! Superb, superb! Oh, my goodness, wife, are you seeing this from heaven? Our daughter, our daughter is ansolutely stunning! Only twenty-five, this young thing, sob, you should have seen our daughter become so dignified."

A teardrop formed in Lord Murong's eye.

Lord Murong sometimes sheds tears.

Wouldn't he be a famously pure man who, having become the head of one of Five Great Family, missed his first wife and didnn't even consider remarrying, let alone having three concubines?

"Um, Father? I'm embarrassed, so stop…."

"What is there to be embarrased for? You are admirable, my daughter! The sun, moon, and stars have helped you. How can you compare your complete accomplishments to the help of heaven?"

"No, I'm really embarrassed, so please, okay?"

"What were you ashamed of! This celebration, ha, was a blessing in disguise. You have made a good friend. I am truly satisfied with your efforts. Since you have borne fruit like this, this was how important a friend is. Since you risked your life and served with all your heart, my daughter deserves the same! Ha, this was a celebration for the family, no, for the entire land of Liaoning, there was no other celebration like this!"

"Dad, seriously, stop it. It's so embarrassing. It's just having reached Transcendent…"

"What's this about 'just Transcendent'? Transcendent Realm at your age? Is that normal? Let's go back right now and throw a grand feast! I'll empty our treasury and treat everyone in Liaoning to this wonderful event! Such a wonderful event—"

"Ah. Lord Murong! How have you been?"

"Oh, Heavenly Blossom Sword. Yes, I've heard of your exploits. Well, yes, you're truly exceptional. As a proud great swordsman, I too respects your deeds. However, you must be aware of your position and—"

At that moment, Murong Chengyi's eyes widened.

\textit{Huh? Why can't I read her realm?}

At Profound Realm, you could roughly tell with with a simple gaze or intuition what someone's Realm at up to Transcendent Realm.

And what if that didn't work?

It means that they have climmbed beyond that.

The experts in the field all know each other's faces, or even if they don't know each other's faces, they know their characteristics, so if someone doesn't know, they're usually young, so how can they not know the realm?

Then it would be at the Unrestrained Realm. Or maybe it's a Demonic Descent.

Either way, twenty-one was ridiculous.

Well, if you're twenty-one, you should bow down and accept it.

There's over a quarter of an hour left, but I can't seem to get out of that trap.

Only under the condition that it was achievable from the start.

"Hmm. Daughter. Should we keep the party a little more modest?"

Murong Zhuxi lowered her head deeply.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

To Qing, her friends were invaluable, and she was always ready to sacrifice herself for them.

Look, even now, sacrifices were being made like this.

To the chicks who were barely imitating the martial arts, who were barely imitating the martial arts, she was giving them the opportunity to serve the great martial arts master!

For those poor lowlifes who were still struggling and struggling in the midst of the climax, unable to even find the simple harmony of the three yangs, what joy could there be as great as holding the Cheonhwa Sword?

It was a question that made me tremble at my own broad tolerance.

In that sense, it can be said that Lady Murong was in a truly pitiful situation.

A golden opportunity to hold the Million Evolution Super-Chojohwagyeong Grassland Flower Sword, but on the day of her turn on duty, she had to devote time to her family.

\textit{But family is a serious matter.}

\textit{There's nothing I can do.}

\textit{Well, I'm a little jealous.}

\textit{I hope my mom and dad arre doing well.}

\textit{My younger sister, who was like a little devil, surely will take care of them.}

\textit{Instead of eating two chicken legs at a time, give one to them, you pig.}

\textit{Even if Mom and Dad tell you to just eat it, you're should at least pretend to refuse, you stupid pig.}

Anyway, well, don't be so gloomy.

So, since the pedestal of the day was absent due to unavoidable circumstances, it was not possible for him to just lie in bed.

Of course, it's not impossible to walk alone.

But, like Xue-i-ri the other day, I'll have to grit my teeth and groan and writhe, so why bother leaving the comfortable seats?

So, this was a situation where a soldering iron stand was needed.

"Oh, then me." "Me." "What? Why you guys, leaving Yeoui behind?"

So, Ye, Gunyeong, and Lan-ah were making a fuss over who will do it.

This was the pitiful struggle of those low-ranking officials who want to bring Hwagyeong's martial artists forces close to them.

However, surprisingly, the parts that cause friction between friends were always the smallest things.

Just like the year of the pig in his hometown, he always eats chicken legs alone, he makes people wait five minutes for him out of Qing as if it were natural for him to smoke cigarettes alone, he secretly takes small amounts when splitting the bill for drinks, etc.

Rather, after getting really upset and having a huge fight, they soon get drunk and pretend it never happened.

But these small things that hurt you accumulate and lead to distance, so it was a great lesson in dealing with friends.

The closer you are, the more you should pay attention to the little things!

So, it was not right to take sides in a half-day special like today.

For that reason.

"That's it. Today's Crutch is San!"

"……A crutch."

Even though he said that, Qing didn't miss the fact that Peng Daesan's eyebrows didn't flinch.

When he's upset, his eyebrows were always the first to react.

In fact, 10\% of the reason why Qing always floated Force Compression and said, 'Ah, Unrestrained Realm is really nice, it's a shame I can't express it in words,' at the end of every sentence, was to encourage her friends' motivation to practice.

By the way, the rest of the reason was because it was fun.

For this reason, whenever Ah Jin-ja Hwa-gyeong was talking about something or other, Paeng Dae-san pretended not to listen and stuffed food into her mouth. It seemed like he was pleading to be listened to as well.

They say that even the wishes of the dead were granted, so what about the wishes of the living?

However, this was nothing.

He was really useless as a Crutch.

"Aww, ugh. San, won't you support me properly? I'm a patient. Don't you know about fractures all over my body? Can you tell me what bones look like? If I pull on a cracked stick, will it hurt or not? My butt was going to fall out. Oh my, I'm dying. Ugh."

"Um, I'm sorry. Um."

"Ugh, San! A little. It needs to support the weight. Don't hang it, support it. Am I a laundry? Hanging it?"

"Hmm."

"No, what's the 'hmm' sound? Yout think it'll just work out if you just lower you voice? Anyway, you haven't mastered the basics. Put your left forearm forward, parallel to the ground. Hmm. Okay. That's how you'll sit down."

Qingi moves from a sitting position to a hugging position.

"Okay, let's go. Our destination is the Alliance's library."

"…"

"San?"

"……Okay."

Mount Paengdae had a complex expression.

A heavy, full sensation spread through the back of his left arm, the veins bulging in his clenched fist with his palm facing down, how much strength he was exerting.

But I still feel secretly hurt.

How can this guy, with his butt clinging to the man's forearm, think that I'm a woman?

Or maybe you don't look like a man.

Maybe it's the latter.

When I see these guys who don't care even after seeing this,

"Oh, Sister. You're going to the Jangseogak. The Jangseogak of the Wulin Alliance—"

"This library was established by the first leader himself, and initially he sought to share the enlightenment he had gained. However, depending on his level, enlightenment that was too high—"

"Wouldn't truths that don't fit their original purpose be poisonous? So, the reason we divided the reading levels in the Wulin Alliance's library isn't to discriminate based on origin or rank—"

"The spirit of the Wulin Alliance was to help everyone study—"

"But the current situation was not something that can be considered as such, and the viewing level was also-"

"Haha, how funny. A member of the Five Great Families, who enjoys the greatest benefits, criticizes the viewing level?"

"Sister Sima? Although the Sima family was not one of the Five Great Families, or even one of the Ten Great Families, hasn't it long inherited military power and managed the Jangseogak itself?"

"That's because the Bon family already has experience in governing the world."

"It's only three generations."

"Haha, we've been running it for three generations. Even though they've taken advantage of the blessed land of Shu-Han, they went on a northern expedition and they've wasted your time without leaving anything behind. How can they possibly be in charge of the Wulin Alliance's military affair?"

Somehow there were crakcles in the air.

Zhuge Lixian was always polite and kind, but today he has become a mean-looking muscular man like a master of the Sapa's external attack.

And Samachunbong originally had a dirty impression.

"San. Can't you kick them out?"

"I couldn't even handle a single stray word."

Zhuge Lixian and Sima Chun-Bong were spewing out useless information that no one asks about or was curious about.

Aren't they engaging in a useless knowledge war, cutting off each other's words and claiming to know more?

Zhuge Liang and Sima Yi were long-time rivals in Zhongyuan, and it seems that their rivalry arose because their characteristics overlapped, with each being more about intelligence than martial arts.

Let's just think of it as white noise.

"By the way, do you read books too?"

"What? San? You looking down at me? A general must read five cartloads of books—"

"Du Fu!" "Je Baek-hak-sa-mo-ok!" "Nam-asu-dok-o-geo-seo!" "Han-woo-chung-dong's story!"

"-like I said. I'm a graduate of the Hanlin Academy. I'm just a book hunter, you know? Any book I get my hands on, I'm done for that day."

"Yeah. I knew it when I fought with cooking. I knew it when I fought with books."

"Huh? were you laughing? were you kidding me right now, Chojohwagyeong Chojohwageom?"

"What about that damn Hwagyeong and that Grassland Flower Sword?"

"Well, that's supposed to be a joke. My ears were going to fall off. Hurry up and go."

Jangseo-gak with that kind of excessive background noise.

After the Jangseo-gak guard readily let the group in, um, books, um, books. It was full of books.

Perhaps because of the fire, the five-story brick tower was completely filled with bookshelves.

Of course, books were good.

If it was going to be like this, I wonder if it was really necessary to build it out of bricks since it wouldn't be fire-proof anyway.

Hmm. You want me to find a book in here?

What kind of beach were you looking for sand on?

Come to think of it, I think this was also a bad trait of Nyeonyeong, who ate a lot of food. But.

There was always an answer.

"Oh, what was the title? It was an unusual book. Anthropological Development of Swords Based on the Form of the Confectionery? Ah, I can't find it. Hmm. Someone who frequents the library should be able to find it."

For reference, the name of the secret weapon hidden by Yun Yuanying was a theory of anthropometric development based on the shape of the sword, based on records from the Sudang era.

Perhaps it got a little sweeter during the adaptation process.

"Sister! If it's Jangseo-gak, wouldn't it be the place where I, the younger brother, eat, sleep, and stay whenever I visit the Wulin Alliance?"

"I, Samarang, was born, raised, and fed in this library. I am a tadpole who has barely spent a few nights here, and I don't know my place or my place as a frog. Haha!"

And then they shot each other a look and then disappeared.

"You're good at manipulating people."

"No, really? I gave them both a chance to prove themselves. I'm like this. I'm so thoughtful and considerate."

"It's not consideration, but a strong desire to cut, isn't it? If you're joking, it's rather amusing."

"Oh, San. were your lips a little chapped today? Lips, lips, um, your lips were a little dry. Um, was eating prohibited here? Do you have any snacks?"

"No eating or drinking allowed."

Well, it's really annoying and repulsive to think that you're going to eat something in a library, let's say a library.

His shoulder was hunched.

"There's no one watching me, so it'll be okay."

Peng Daesan put his pocket on the desk.

Then, Qing's face brightens so much that it lights up the dark library.

Pengdaesan stared blankly for a moment, then sniffed, sniff. Qing's nostrils widened and his throat twitched.

"What was it, oh, meat liver, sniff, oh, incense, and something spicy, a little bit of pepper, and oh, this was lamb, lamb."

"Do you usually detect it by smell?"

"Wow, it's tender meat? Did you bring this for me to eat?"

Yukgan was a term used in the hometown of Qing to refer to jerky.

Dried meat was tough and tasteless as a travel food.

On the other hand, the tender meat was pounded gently, seasoned, and grilled several times, so it was quite a rare and expensive snack.

Why would Peng Daesan, who has no interest in snacking, bother to buy this expensive meat?

Then, Mount Paengdae goes, "Ahem."

"I picked it up on the way here. I'm scared someone might see it, so I'll just eat it."