\chapter{Inspector's Method (4)}

Qing had never been one to hold back on her words.

A natural ability. An innate sense for reading people's inclinations, determining how far she could go, and grasping what was known as the line.

Of course, even without that, this wasn't a question that required wit.

"Elder, isn't the liquor a bit spicy? It seems to be getting spicier. Did you order something special?"

"Hmm? Is your liquor spicy? Did you put in a bit too much ginger? That's all because you're young. Once you grow older and suffer through a spicy life, no matter how much ginger you put in, it just tastes sweet."

"Oh, did you live such a spicy life?"

"No? That can't be. My life up to now has always been full of love and joy. That's why I don't eat ginger. It's spicy. I truly can't understand why you would eat such a thing."

\textit{What's this now?}

\textit{He doesn't eat ginger because it's too spicy, but then why does he load up my drink with it?}

\textit{Of course, ginger tastes good, so it doesn't really matter.}

\textit{If you live as a beggar and eat whatever you can find, ginger would just smell fragrant.}

\textit{He really is the type to say whatever comes to mind.}

Qing fully understood why the Leader of the Diancang Sect asked the Elder to please keep his voice down.

"No, this isn't the spiciness of ginger. Um, it's familiar somehow, but what is it? Is it poison? No, that can't be."

It likely wasn't poison.

If it were, she should have felt it immediately after eating the poisoned food; there wouldn't be a way for it to become more toxic in real time while eating.

And, more importantly, the elder in front of her, was a Profound Realm Master.

If it was truly poison, the elder would have detected it first; he wouldn't be so at ease picking out carrots.

By the way, he doesn't eat carrots either.

A person who truly doesn't know the taste; carrots aren't the most delicious ingredient, but they're not tasteless either.

Just as Qing thought this, he tried to avoid the carrots in the stir-fry to get to the lamb.

"Hmm?"

Ji Yun seemed to raise his eyebrows for a moment, then suddenly slammed his palm on the table, creating a thundering sound!

A resonating crash that left an echo.

From Ji Yun's palm, a shape spread out like a round wave.

It was as if a blanket was lifted high and then slapped down.

The tablecloth expanded with the force of a great wave, undulating like a tidal wave.

And as it flipped over the plates on top, in an instant, there was a mess of food everywhere without a complete dish in sight!

It was truly the work of a miraculous table flip!

\textit{No, what is this? Using that high-level technique of Hyun-gyeong to flip the table, but what in the world did he just do?}

\textit{Even if he despises carrots, this is—}

"Come here and sit down. The food is poisoned. This, hmm, is extremely toxic. How could such poison exist? Ahem, there's no time for this. First, I need to push your poison out."

Ji Yun's grave voice cut through Qing's bewildered heart.

\textit{Ah. Poison. It is indeed poisoning.}

\textit{But how?}

"Come on, hurry. Show me your back."

At the same time, a terrible alcohol smell pierced his nose.

The reason a martial artist can drink heavily was that they can expel the alcohol effects caused by the intoxication in their bodies.

Of course, when drunk, they couldn't even thought of expelling the alcohol effects, and thus they received a lot of nagging to be cautious about drinking.

"Ah, Elder, I'm fine, so you detoxify first. As for me, I could say that I have already reached a level in detoxification; it may be out of line, but in that regard, it can be compared to Hyun-gyeong's level."

"That's not enough. This is the first time I've encountered such a strong poison. Hmm, I have never tried any other poisons, so it's hard to compare. Hurry."

Qing became slightly embarrassed.

She was grateful for the elder wanting to help detoxify her first.

Moreover, expelling one's own poisoning and expelling someone else's were not the same acts from the start.

Detoxifying one'd own poison was merely an extension of the management of essence within one's body.

But to dissolve someone else's poison?

That would require the techniques of a true master, an extremely difficult and delicate skill that would completely drain even the most skilled practitioners after doing it once.

Additionally, to expel someone else's poison while still being poisoned themselves meant that one would inevitably overlook their own poison.

Poison wasn't a sudden instant kill weapon that blows up when a certain level accumulated.

And a person's life wasn't like a video game where the health bar gradually depleted until it ran out.

Poison circulated through the body, collapsing organs and contaminating the marrow, destroying blood vessels and energy channels, so the longer it was neglected, the greater the aftereffects became, forming a terrifying weapon.

Yet Qing was prioritized first by Ji Yun.

However, perhaps due to Qing's somewhat unique constitution.

To someone like Qing, who saw poison as just a spicy seasoning, it was truly moving, but well, it wasn't necessary.

"Um, it seems manageable, but you should—"

"Hey! When an elder speaks, shouldn't you come quickly! This isn't a poison to take lightly! Hurry, there's no time!"

Ji Yun rebuked in a stern voice.

It wasn't the time to keep bantering 'senior first, no junior first', and it didn't seem like Ji Yun was about to back down either.

"Elder, actually, I—"

\textit{Um, there's no helping it; I must mention this now.}

Just as Qing was about to speak.

Creak! Bam!

The sound of the door opening roughly.

At the same time, a spicy smell rushed in, followed by a devious laugh.

"Hehe, patrons, what a fuss—"

Suddenly, the Lieutenant's words were cut off.

It was unavoidable.

In front of an elder, one couldn't keep covering their face, and didn't Qing's beauty shine brilliantly in the private room?

Once anyone took a look at Qing's beauty, they would surely be left speechless momentarily.

Thanks to that, the words came a beat late.

"Ahem, what's this noise? Even if there aren't any guests in this inn, making such a ruckus isn't acceptable, is it?"

It was a very flashy reappearance of the waiter, attended by his subordinates on either side.

"Y-you……! Ugh, wh-what is going on?"

Veins popped in Ji Yun's eyes.

It seemed the poison had suddenly worsened.

What could have affected him the moment the door opened with that spicy scent?

Just as Qing was trying to think hard.

"If you're curious, the poison you ingested is called Blood Gland Destruction Poison\footnote{滅腺血毒; Mie Xianxue Du}, a highly dangerous poison. Of course, the toxicity is one thing, but the process of the low toxin is truly cunning. Six harmless ingredients go in separately, meet in the body, and were molded into poison, and then finally, a finishing touch is applied by inhaling aroma to trigger the poison. Hehe, isn't it truly beautiful?"

Without needing to think, the waiter prattled on about it.

Just a moment ago, Qing had mentioned the Five Poisons Sect's leader, and yet, but it came up right away like this.

The type that rambled on about everything once they thought they had won.

\textit{Is this type more common than expected?}

\textit{However, judging from how he started talking right away upon entering, he seemed to think he had already won.}

Of course, logically speaking, that situation made sense.

Most people typically don't imagine nonsensical scenarios.

The enemy had Myriad Poisons Immunity, or perhaps one of Profound Realm's master was among the enemy.

Usually, such thoughts would be dismissed as paranoia, where people don't waste time on elements that converge towards the impossible.

Yet that impossible scenario had actually occurred.

"Tsk tsk. I don't know who your guest is, but that's too bad. He's innocent, but when you're next to a cruel person, they say you're bound to get hurt, don't they?"

"You, Blood Cult vermin…!"

Qing gasped, inhaling sharply.

\textit{Oh dear, elder. How could you say it out loud like that?}

\textit{You should just casually respond with something like, 'Are you one of the Five Poisons Sect folks?' or 'Who are you?' That'd be like admitting we know, which isn't the same.}

However, not everyone could think as cunningly as Qing.

On the contrary, the average person was closer to Ji Yun.

At that moment, the waiter's expression changed completely.

"So it's the dogs of the orthodox sects. No wonder, I thought you couldn't possibly conspire with anyone to eliminate the Five Poisons Sect in this town, but you're sniffing as if you're one of them, just as mad as dogs. Come on, I see that vulgar body of yours; you must be that Heavenly Blossom Sword? It fits perfectly, they said no other whores could compare."

Qing's expression soured instantly.

\textit{No way, how did my identity get exposed there?}

\textit{And which jerk said that? Is Three-, or Five-Headed Beauty not insulting enough?}

Well, wasn't it said that one speaks ill of the king when there's no authority present?

"Hehe, well. This is quite amusing. So, what will you do? Will you try to expel the poison in front of the enemy? Or since you're dead anyway, will you try to die together with whom you call the worst of the Blood Cult? Just don't think of it as easy; do you know about Poisonous Blood Human?"

Dying together, simply put, means 'you die, I die,' or a mutual death tactic.

To this, Ji Yun roared once again.

"Poisonous Blood Human! That cursed beast! How terrible are you people of the Blood Cult!"

"Hehe, no matter how terrible we are, we can't be worse than you Zhongyuan people."

"Zhongyuan people? I am of the great Bai ethnic group, and our Dali people are different from Zhongyuan."

"How long has it been since the Dali Kingdom was subjugated by Zhongyuan—"

"Subjugated? You Blood Cult folks can call it subjugation, but we call it yielding without strength!"

"……? Isn't that right? When you yield without strength, isn't that subjugation—"

"If that's the case, wouldn't you people of the Blood Cult be subjugated by Zhongyuan as well?"

"No, we are different! We will never yield, and we are liberators dreaming of the freedom of all oppressed people under the reign of Zhongyuan!"

"Then the Dali people are also Zhongyuan people?"

"You Bai people are collaborators stuck to Zhongyuan, even if you deny it now—"

"What about the other barbarians? Even the Dai Yue\footnote{Dai Viet, now modern Vietnam}, Birma, and the Jurchen, all pay tribute to the Son of Heaven in Zhongyuan. Are they also collaborators? Would you kill not just Zhongyuan people but all barbarians?"

"That's different! They are simply suffering under the oppression of Zhongyuan—"

"Then what about our Dali royal familiy? Isn't it the same?"

"It's not the same! You—uh, well! You collect tax to present to the Son of Heaven—"

"Aren't the barbarians doing the same? Did the tributes just fall from the sky? They're all taxes collected by those barbarians from their own people, aren't they?"

"No, that's different!"

The Lieutenant sounded frustrated!

\textit{What's this? Elder Ji Yun can rile up people?}

\textit{Is it right to say he riled up? Or is he just talking nonsense?}

Qing was left confused.

Ji Yun's sound transmission resonated in her ears.

—It may be tough, but bear with it a bit longer. When I send the signal, lie down immediately.

\textit{Ah, so he really was riling them up!}

It seems he was trying to lure them into a lull and then sweep them away with Hyun-gyeong's miraculous techniques.

When Hyun-gyeong surfaced among the enemies, the feeling was truly like being subjected to all the world's hardships, a sensation that felt bleak and frightening.

However, thinking that such a master was on your side, my goodness, there was no place more secure than this.

Qing sent a response.

—Senior!! I'm fine!! Shouldn't we listen to what they are saying? They seem to not hold their tongues!! It's an opportunity to uncover the Blood Cult's schemes!!

—Um, with that voice, it seems you're looking fine. You said you took down the Five Poisons Sect leader, did you pick up some antidotes from his corpse?

Ji Yun paused at the clear whisper piercing through his ears, loud enough that it felt like it could burst his eardrums.

On one hand, he was touched.

\textit{With a poison this dreadful even for Hyun-gyeong, how painful and hard would it be for a mere child like this, who was just at the level of Harmony Realm?}

\textit{Especially with enemies hovering in front of us; the pain would not just be pain; there must be a palpable threat to life sensed.}

\textit{Yet she still worried about the world's safety more than her own? How admirable, moving, and impressive. If only you'd be my disciple, you'd truly be praised as a blessing of the Orthodox sect.}

While Ji Yun was moved, he kept rambling on.

In fact, contrary to Qing's thoughts, Ji Yun was not particularly trying to take his time.

As Qing expressed, it wasn't that he was being attacked!

Ji Yun was merely being his usual self.

\textit{But why is this Blood Cult scoundrel so angry? How typical of Blood Cult bastard.}

There was a reason why the leader of the Diancang Sect asked Ji-Yun to keep quiet if he were to speak.

"Then what about the Miao people? Your Blood Cult has teamed up with the Five Poisons Sect; is that to say you are allied with that vile Zhongyuan people you so despise?"

"Miao people are victims! They are the oppressed! They groan under the oppression of you Zhongyuan people!"

"Hmm. Is it really so? It seems like they are living well? I know of a Miao person who started a business that is quite successful, and the tea plantations stretch beautifully across the mountains—"

"Grrr! Isn't it your Bai people who are living well? You are the ones who monopolized the wealth of Yunnan!"

"Well, isn't it because of abilities? Our Bai people are great. Now, let's end this. It's utterly pointless, you aren't making any sense as it is. Truly, you're like a true Blood Cultist."

"Who can't understand here, huh? Did you stuff some donkey's junk in your ear?"

"Hmph. Let's just treat it as it is, then what? Continue with the story; you mentioned something about the Poisonous Blood Human earlier, so what do you want us to do? There's no way you'd just keep repeating the same old story about dying."

"Grrr."

The Lieutenant groaned.

Qing nodded quietly in agreement.

\textit{I have a feeling that I'll get along really well with this Senior.}
