\chapter{Inspector's Method (12)}

The defenses of the Five Poisons Sect built by the Blood Cult were indeed like an impregnable fortress.

The layout of the building, which had been rebuilt for over five hundred years, formed the very axis of a formation, serving as an independent fortress that repelled enemies with traps and poisons, and furthermore, it also had the nature of a trap itself.

Each trap was interconnected, so if one got caught, another trap would follow, and even if one managed to avoid one trap, it would lead to another, making it truly horrific.

In addition to this natural fortress, a vicious and extreme trap had been imposed over the existing trap.

Where traps were originally designed, new traps were laid down, and even in places where traps did not exist, traps were placed, and the existing facilities were filled with deadly poison…

Such fortification of the main faction was tied to the history and strength of the sect, so it was not without reason that they refer to the history of the sect when speaking of its power.

Unless one was a martial artist of Hyun-gyeong, no matter how many enemies come, they would find it impossible to break through this terrifying defense.

Moreover, after the modifications of Jang Choi-ryang, it became even more vicious, making it impossible for both enemies and allies to enter without becoming ensnared.

This truly was an isolated paradise!

Isolated paradise means a remote island in the vast sea, and the main faction of Five Poisons Sect could indeed be called an island standing on land.

No one could enter, nor could anyone leave.

Originally, if one were to completely isolate the world with such traps, anyone would surely not be able to hide their anxiousness.

Firstly, the psychological fear would spread from the gradually diminishing food supply.

However, the members of the Blood Cult were at ease.

This was because the Blood Cult preferred isolated environments and lived to be cooped up.

The food supply was slowly decreasing?

Well, that was the same wherever one is.

Shouldn't they be thankful there was food to eat right now?

What if the food runs out?

Then, the weakest and the most useless would be the first to make a "noble sacrifice."

This was the mindset of the Blood Cult.

Due to the oppressive (justified) persecution from Zhongyuan, the Blood Cult had always been required to hide.

Jang Choi-ryang was also in the same boat; no, Jang Choi-ryang was more at ease than other members of the Blood Cult.

Now, while he may lack manpower, he was treated as a genius with brains bestowed by heaven, but before being taken by the Demon God, he was merely regarded as a foolish one.

Having also been persecuted by the Blood Cult, Jang Choi-ryang still preferred to isolate himself, thus the current situation of confinement within the Five Poisons Sect was no different historically than his previous seclusion.

No, rather, he felt more comfortable.

Out there beyond, there were only members of the first regiment that he recognized and other creations of his, as well as other fellow compatriots.

Had someone he didn't recognize appeared, clicking their tongue and muttering about being useless, the chances of them acting badly would have completely vanished.

So, even in this situation, Jang Choi-ryang unconsciously hummed while dedicating himself to his hobby of researching poisons.

This research was unusual.

Resolving the side effects of poison art by applying the characteristics of the world's most heinous poison, termed "Destruction of the Root!"

Destruction of the Root was truly a unique poison, thereby making it exceedingly perilous.

Once harmless constituents enter the body and combine, only then does the lethal poison take shape!

It seems simple, but it was truly a horrifying task.

The method by which an expert burns away poison was to have the substance act in the body first, so the body would reject it and recognize it as poison to expel it.

But what if the constituents were harmless?

No matter how skilled a practitioner might be, they cannot identify that this substance was a material for poison.

So what was the result?

Even the martial artist of Hyun-gyeong was completely deceived and fell into a state of poisoning.

Still, it does not lag behind notorious deadly poisons.

The Demon God must have been awestruck believing that even an immortal could be killed with poison, that even that ghostly immortal could be tricked and consumed by it, hence truly named the "Destruction of the Root".

Of course, there were weaknesses.

Firstly, since the taste and aroma of each component were incredibly distinct, if they were not used in a dish as a seasoning, even if it was not poison, it would taste strange enough to dissuade consumption.

Even if a dish was brought forth, if the counterpart was a picky eater, poisoning will not occur.

Certain ingredients also need to be infused with alcohol, placing those who do not enjoy liquor at a disadvantage. (Of course, there were hardly any individuals like that among Zhongyuan.)

Additionally, numerous processes must be completed, making the production complicated.

Above all, the outrageous cost due to the excessive amount of gold required!

A typical poison maker would continue researching to overcome this.

They would reduce the necessary constituents by compressing them, dull the sharply pungent tastes of every single component, and establish simple refining processes, perhaps even searching for alternative ingredients to enable mass production.

However, Jang Choi-ryang was not typical.

Like a genius of poison bestowed by heaven, he glimpsed another possibility in the world's most heinous poison.

It was research to eliminate the unavoidable dangers of those who have mastered poison art, the risks of poison itself.

Actually, poison arts were not complicated.

It involves gradually administering poison to oneself so that one can establish poison energy deep within the dantian, and as long as they mix poison energy into their operating inner arts, that would be poison art.

However, humans were not originally creatures meant to harbor poisons, hence innumerable side effects accompany this.

Firstly, poison was consumable, so whatever was used must be replenished.

If an issue arises in the dantian before all poison was used up, or if one's inner energy was exhausted, the poison will be released, ultimately leading to one's own death by their own poison.

Additionally, the stronger the opponent, the stronger their resistance to poison, marking a limitation of poison mastery.

As for the cost of raising a usable poison, it was often astronomical, rendering it almost economically unfeasible.

Of course, while the limitations of poison mastery were inevitable, its expensive and weak nature against skilled opponents cannot really be avoided.

And perhaps the side effects of poison mastery can be erased somehow.

How?

Through the separation of toxins!

Instead of lodging poison energy in the dantian, what if the harmless constituents could be separated and allowed to flow through the body?

What if they could be combined only when needed to exert toxicity, while remaining harmless at other times?

This was the new possibility Jang Choi-ryang glimpsed in the world's most heinous poison.

Moreover, it would also serve as a surprising gift for the master who had taken him in, who had regarded him as a "noble sacrifice" treated like a fool.

As one reaches the pinnacle of poison art, they will inevitably slip into a profound loneliness.

A poison artist embodies poison within their marrow, creating poison autonomously.

And that poison does not harm them, which eliminates the need to engage with poison mastery.

If the toxins dwell in every part of the body, then all bodily secretions including blood, sweat, tears, and the like will contain poison.

One cannot engage in any sort of interaction where a man and woman match movements, nor can they even use their own chopsticks in the shared meal without touching it with their own saliva.

Even if a mere conversation bubbles over, spitting could poison the other, and even the faintest breath, combined with weak poisons, could intoxicate a partner in a confined space while simply breathing.

But what if the toxicity could be separated and allowed to flow?

If one could eradicate that solitude of a poison artist, the inability to even pet their beloved disciple with bare hands could be entirely eliminated.

Hehe, surely the master will be pleased?

Surely, he will give tremendous praise.

In fact, this was a relatively old piece of research.

After completing the world's most heinous poison, Jang Choi-ryang had lost interest in further improvements and wholeheartedly devoted himself to toxic separation.

That was already a year ago.

The Demon God simply thought, "Another day for Jang Choi-ryang, huh? He completed it only to lose interest and dive into another study."

But in truth, it was a precious return of favor from a commendable disciple to his master, who treated him like a useless noble sacrifice.

The Demon God had indeed raised a decent disciple.

And in this moment!

Jang Choi-ryang's eyes opened wide.

His own poison energy had subtly diminished.

Was it perhaps because he had taken residence in the Five Poisons Sect's main faction completely isolated from the world, or perhaps even more so due to his own laboratory becoming double isolated?

Feeling distinctly at ease, he suddenly!

"Ah, ahhh…! Khehehe…!"

Jang Choi-ryang suppressed the laughter trying to burst forth and closed his eyes again, beginning to contemplate his body while separating the poison within.

The poison energy gradually melted away.

The poison energy, now separated into harmless constituents, flowed through his body distinctly identifying each component as they did not mix due to his hands having divided them.

And yet, he could merge them whenever needed to demonstrate toxicity—

It was truly a revolution in poison mastery!

This separation of poisons was a small step for a single human but a monumental leap for poison artists!

"Ihihihi…!"

Jang Choi-ryang burst into childlike laughter, picking up his brush with a bright smile.

And then he immediately began to write down this feeling, this principle, as an amazing gift for his master.

Then, tap!

Jang Choi-ryang let the brush drop as if throwing it aside.

And he leaped up, dancing joyfully.

The dance steps were messy, resembling more of a grotesque struggle than a dance.

But since Jang Choi-ryang's mental age had remarkably regressed, children were prone to dance spontaneously when they were excited, aren't they?

"Ihihit! Kihahhahaha!!"

As he exclaimed, dolphin-like, exuberant shouts poured out, and it was clear he was incredibly happy.

"It's done! It's done!! Master!!!"

At the moment when Jang Choi-ryang cried out in joy!

Bang! Crack! Boom, boom, boom, boom, roll…

With a huge noise, something rolled in under Jang Choi-ryang's feet.

He saw an unfamiliar sphere, the size of a baby's head made of metal, rolling in clumsily.

Jang Choi-ryang looked up.

There was a hole the size of that metal orb in the cover of the underground compartment above the ladder.

It seemed someone had dropped the metal orb from above.

Jang Choi-ryang tilted his head in confusion.

But why a metal orb? What purpose does it serve?

This was Jang Choi-ryang's last thought.

Bang!!!

Countless metal fragments swept over, turning Jang Choi-ryang's flesh into finely minced pieces.

Indeed, there was no way to endure a magic cannonball's explosion right under one's feet without profound martial arts.

Magic cannonball.

Referring to a shell filled with gunpowder with a fuse drawn out and its length adjustable to regulate the time of its explosion.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A signal flare flew into the sky.

The signalman shouts when he saw that.

“First shot, signal for a hit!”

That first shot wasn't even a hit, but it was a very close hit.

It was an amazing sniping technique that even descendants would admire and praise, and it was a sniping shot from a cannon.

But the observer couldn't tell until then, so it just fell in the middle.

The commander gave the order with great enthusiasm.

"All right! Prepare for a volley! Fire all rounds at the signal of the flag officer!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Boom! A loud noise rang out through the wall, and dust clinging to the rafters flew up like snow.

The members of the First Poison Squad frowned at that.

“What? An explosion?”

“I think Young Master blew something up again?”

"No, what's with all the explosions he kept making when making poison? Well, the results are astonishing, but shit, let's go. If he collapses again, we'll have to get him out first."

So the members of the First Poison Squad left the room in a hurry.

Jang Choi-ryang's residence and study was a small room in the Five Poisons Sect residence, a servant's room that hides a secret underground library.

Since everyone was divided into four buildings in the center of the Five Poisons Sect, the agents who came running after hearing the sound met each other in the yard of the Five Poisons Sect's Sect Leader's residence.

However, there have been several instances of the Young Master blowing it up under the pretext of experimentation.

So it would be the same this time too, since no one had a serious expression on their face.

"What, they're all here? Seriously. Who brought the antidotes? I was in such a hurry to get out that I forgot."

"Look at that guy, he's joking around trying not to go. I'll bet my balls that that guy has an antitote pill in his lap."

"What? If you're not sure, don't bet, don't you know? How do you know if I have the antidote or not?"

“You little brat. Look how long you’re talking. Aren’t you running away?”

“Who is running aw-”

That was the moment.

Kuung… … ! Kugugugugugugu… … ! Kugugugugugugu… … !

A dull sound echoing from far away.

Because the sound of a cannon is something heavy that flew in from far away and pierced into your ears.

But the members of the First Admiralty were at peace.

Because they heard it yesterday too.

“What? Another gunshot?”

"It was a mess all lunchtime yesterday, and it's like this again today. I guess those Zhongyuan guys are overflowing with gunpowder?"

By the way, they wer pretty flustered yesterday.

It was chaos, as they thought that the Orthodox sect bastards were collaborating with the government troops to fire cannons. They were about to abandon the main building and flee immediately. (It was a remarkable insight.)

But since no shells flew yesterday, it seems the soldiers were just doing gunnery training because the command post was nearby.

Well, yesterday really was just gunnery training.

To bombard the Five Poisons Sect headquarters located in the city, even though the Five Poisons Sect manor was as large as a fortress, to prevent collateral damage, they would first need to zero in and re-train their gunnery skills, which had become rusty from farming.

But today?

Soon, shells start raining down.

It was 鐵雨 (Tieyu), as in it was literally raining steels and irons.
