\chapter{Inspector's Method (6)}

Eventually, two of the Poisonous Beast, who had been as motionless as corpses standing beside the Lieutenant, moved and placed the antidote containing the Gu in front of Qing and Ji Yun.

Qing's physical body was that of a transcendent human.

With senses as sharp as her enhanced strength, she detected the faint spicy smell emanating from the breath of the Poisonous Beast.

\textit{Well, generally, if there's poison mixed into someone's breath, then you wouldn't really call that a person.}

\textit{These Blood Cult bastards sure come up with all sorts of things.}

Of course, the Blood Cult might hold some grievances.

When weaklings try to challenge the strong, it's common knowledge that victory can't be achieved with symmetrical methods.

If a swordsman wished to defeat a swordsman much superior to himself, simply improving in swordplay alone won't cut it, he needed to resort to other means.

Thus, in Zhongyuan, these other means were called sorcery.

A swordsman trained for thirty years might lose to a swordsman trained for just ten years.

In a just and fair world, the ten-year swordsman should never defeat the thirty-year swordsman. (Assuming both have equal effort and talent.)

That would be inequitable and unjust.

Thus the term 'sa'邪 refers to impure means that constitute sorcery.

The Blood Cult had always been weak, and therefore they employed sorcery.

The monsters were part of that sorcery.

Bloodthirsty creatures and their failed counterparts, those abominable creatures made from blood monsters, and the failures that came from cultivating those…

However, weakness does not guarantee goodness.

Many mistakenly believe that.

Anyway, Qing did not know, nor does she needed to know.

There's no shame in saying you didn't know, since you didn't necessarily wanted to know.

Qing consumed the antidote.

As soon as it touched her tongue, its bitter taste melted away, mingled with a cool medicinal fragrance and mint aroma.

\textit{What can I say, it's entirely the taste of Mincho 민초.}

\textit{Hmm, not a bad flavor.}

If someone who knows Qing heard that, they might wonder if there's ever any bad taste in what goes into that mouth of her.

The Lieutenant's lips twisted into a scowl.

Martial artists, especially the skilled ones, somehow carried an unfounded confidence that they could escape the agonies of Gu.

The pain inflicted by Blood Gu was absolutely a kind that no human could endure.

How many times has he seen a noble chivalry of the upright Wulin, weeping like a child and begging for mercy before the agonies of Gu?

And how electrifying those scenes were.

Now that he thinks about it, he hasn't had such amusements in quite a while.

Since the disappearance of the Lee Seon Blood Guild, it has been too long to remember.

And Heavenly Blossom Sword was the very nemesis of that Lee Seon Blood Guild.

He could tormentedly make them bear the weight of their fallen compatriots; particularly women could be made to experience a living hell worse than death in multiple ways.

Qing's eyebrows twitched.

\textit{That bastard has a sort of dirty look.}

\textit{Well, thoughts were free, and as long as he doesn't voice them, there's no crime.}

\textit{By the way, is this really the antidote? Or not?}

Qing could not detect the poison circulating within her body, so she couldn't tell whether the antidote was effective or not.

However, it was a medication infused with a semblance of natural energy, for in this primal ancient Zhongyuan, a plant called herbal medicine carries the cosmic mystery of Qi.

\textit{Hmm, a free elixir, how sweet.}

\textit{Although, calling it an elixir may be a stretch; it's quite short on energy. More like the level of adding wild mint fragrance? Still, it's quite nice.}

Also, if the wine bottle could think, it would surely have shouted out that it's something wonderful.

Still in a stupor, it looked at its kin who were curled up, smacking its lip, as if urging it to wake up sooner.

Anyway, Qing, unable to determined whether this was indeed an antidote, casted a glance at Ji Yun's complexion.

\textit{If it's truly doing its job, he should be showing more comfort. Ah, it seems the antidote is working.}

It wasn't just a change in expression.

"Mm. It's definitely effective. However, seeing as not all the poison was receding, it seems this was more aptly called a suppressant rather than an antidote. Along with the Gu, the belief is that you must regularly come to receive suppressors, or the poison will explode, is that not so?"

"Hehe, for a Zhongyuan guy, you certainly seem knowledgeable about poisons. If you're to make use of a slave bound by Gu, you must give commands face to face, right? Hehe, of course, you'll likely be careful not to raise suspicion. What, are you disappointed?"

The Lieutenant, now quite pleased.

Even so, Ji Yun was also in a rather merry state.

"I didn't have any particular expectations from a vile creature of the Blood Cult. If you don't expect anything, there's really no room for disappointment. But, Blood Cult bastard, when are you going to ask what kind of person this elder is?"

"Though you act nonchalant—"

"Of course, here stands the proud Heavenly Blossom Sword junior, yet by focusing solely on that, I feel somewhat treated like an old man from the back room. Well, sure, the really old seniors are simply playing around, but I'm still a vibrant active member."

The old seniors Ji Yun referred to were those like the Great Monk Wuxue, Jo Hyun-ryang, and Ximen Surin, who belonged to the Grand Elder hierarchy of Wulin Alliance.

In contrast, Ji Yun was of the Sect Leader hierarchy.

He was still in the thick of martial affairs, so calling himself a vibrant active member was completely the truth.

Moreover, the phrase 'really old seniors' was because, in fact, they were really old.

Still, it was indeed a statement that could draw complaints and beatings.

Qing began to feel a bit confused.

\textit{Elder, you're not the type who's been scratching enemies all this time, but rather the type who gets hit the moment they open their mouth?}

\textit{Nah, he wouldn't be, right? Surely not.}

"Hah, for how long are you going to keep pretending to be lofty, hehe, no, since you've brought the whip, don't blame me."

With that, the Lieutenant shot a glare at Ji Yun as if to make it obvious.

While wearing a bright smile, he was clearly hiding his sparkling eyes filled with anticipation.

However, that was only for a moment.

Before long, confusion adorned the Lieutenant's expression.

"……?"

"……?"

In the interim, Qing understood the situation.

The wine bottle was perhaps shaking like an epileptic, overflowing with an intense spiciness.

It was a fit of Gu.

These fits had occurred multiple times after a brief respite; they were perhaps trying to ascertain why everything seems fine.

"What have you done!? Why, how?"

"I might be late, but allow me to introduce myself. I am Ji Yun of the Diancang Sect, you vile creature of the Blood Cult."

The Lieutenant's expression changed in sequence.

First, bewilderment.

\textit{Ji Yun? That Ji Yun? The Flashing Sword? The eighth among the Ten Masters Under Heaven of Zhongyuan? Why him?}

Next was understanding.

\textit{Ah. Since he is a master of Hyun-gyeong, Gu won't work against him.}

And then astonishment.

His eyes were almost popping out, and Qing felt she gained insight into why a protagonist might hide their powers.

Ji Yun's arm moved.

His fist struck the ear of Posionous Beast down, and when he opened his hand, a pair of chopsticks sprang up in place.

The chopsticks in Zhongyuan were about three times longer than those in Qing's homeland, so the Posionous Beast fell to the floor like a broken puppet, sprawled across the cluttered table.

Following that, Ji Yun reached out.

One of the cooking chopsticks sprawled on the table lifted and flew into Ji Yun's hand.

A remarkable skill that moved objects without touching them, it appeared to be extremely convenient.

"Kill that bastard!"

The Lieutenant roared as he immediately turned around.

Knowing his lack of abilities and retreating honestly was exactly like the spirit of a scholar.

Suddenly, a grand stroke unfolded.

A single chopstick drew a line in the world, a single line, like 一 (one) character.

To Qing, it simply appeared as such.

Qing's Inner Qi enriched her innate capabilities to a level that comparing to a mere human became meaningless.

For someone like her, there was only a single letter, one that had had the process of writing omitted, completed before her very eyes, as if shining rays from the sun pierce through the clouds.

By the time she had seen it, the phenomenon had already arrived and occurred.

Sun-shooting Sword Technique. First Movement

The sun's rays are already there when people notice them.

There wasn't even a single sign of luck there.

This is because it has achieved the Sword Union with chopsticks, or, if we may say so, Chopsticks Union.

Because the person who saw that sight was instinctively afraid and had all their eyes drawn to the chopsticks rather than the person, they become unable to pay attention to the person holding the chopsticks, so that is all they saw.

“Kraaah!”

Thanks to this, Ji-Yun's appearance only comes into view after the commander collapses and screams.

Qing's heart was filled with joy.

\textit{Clearly, when Master was explaining Sword Subtleties in the past, she said that of Fast Subtlety, the best in the world is Diancang.}

“Kraaah!!”

If you write it down, it would be similar, but a completely different beast-like roar rings out.

The screams of the three remaining poisonous beasts.

\textit{Oh, right.}

\textit{I was so busy looking at the good stuff that I forgot about it for a moment.}

The moment Cheong drew his sword-

"No sword! The monster must not bleed! And hold your breath! Do not inhale its breath!"

It was Ji Yun's stern warning.

\textit{Oh, I see why you're using chopsticks.}

\textit{I guess he wasn't trying to show off that he could kill them with a prop like this.}

\textit{But honestly, killing a bad guy with something like a pencil is kind of cool.\footnote{John Wick}}

Of course, Qing was strong even without a sword.

Qing stretched out both hands toward the poisonous beast.

\textit{You said they shouldn't bleed?}

\textit{Well then, I just have to make it so that they can check their own back.}

With a loud, satisfying crack sound, the poisonous beast with its neck twisted collapses.

Even so, Qing's gaze was fixed on Ji Yun.

Well, how many opportunities you could have to watch the Hyeon-gyeong's fight without any worries?

\textit{Even Master's moves were always something I saw during sparring, so I had no choice but to dodge and block them to avoid getting hit.}

The first stroke was drawn twice more, leaving the screaming forms of the unknown parasites of the Blood Cult and the four bloodthirsty creatures remaining.

Qing stomped on the Lieutenant's ankle.

The overwhelming ecstasy transmitted through the soles of her feet, as the happiness of crushing flesh and crunching bones was simply indescribable.

However, the Lieutenant did not scream or anything; the chopsticks were plunged into the back of his neck, piercing his spine.

In other words, he was entirely paralyzed.

Ji Yun subtly shook his head.

"Don't vent your anger unnecessarily. Remaining grievances from a severed relationship only linger in one's body to stab oneself; if you have won, you must shake it off and forget it. When the hunt is over, you should loosen the bowstring; if left taut, it will eventually bend or break."

"Oh, just now, you spoke like a real Taoist."

"Mm? I am indeed a Taoist. Though my appearance may not suggest it, you see."

It's typically something one doesn't say.

Qing made an innocent smile.

"Ah. Right. Elder, your words were quite cutting. It isn't a virtue befitting a Taoist, is it? After all, can't stand teasing them? Honestly, that isn't a good habit, but I just can't help myself."

However, Ji Yun wore a puzzled expression.

"Hmm? What do you mean?"

"Huh? You were stirring someone's emotions with your words. I mean, weren't you employing the strategy of 'geogjang-ji-gye' to incite this?"

"Geogjang-ji-gye? I merely attempted to carry out a decent conversation. If it were possible to reform him, I planned to pursue it. However, as always, the Blood Cult's vile creature is filled with anger, tsk tsk, isn't that why I say all of you from the Blood Cult should be eliminated?"

\textit{You didn't mean to stir them up?}

\textit{A decent conversation? Reform?}

At that, Qing's eyes narrowed.

\textit{Are you serious about what you just said, or are you just joking around?}

Regrettably, it wasn't the latter; it was truly the former.

What a shocking revelation!

"By any chance, Elder, do you have experience with someone getting extremely angry in the midst of a conversation, or suddenly sealing their lips and leaving?"

"More than just once, truly. In this world, how many angry people are there? Even those who should be Taoists awaken their anger. It's quite a pity. As I said before, when the hunt is over, one should loosen the bowstring, instead, so many still remain drawing it taut, what a shame."

Hmm. Well, one would typically reflect on whether there's an issue with one's speech if faced with such things.

It was a never-ending self-positivity to assume the problem lies with the other rather than oneself, revealing a greatly self-centered worldview.

Perhaps that's the caliber of an elder who has even reached Hyun-gyeong. No, that must surely be the case.

In the meantime, Ji Yun, gazing down at the fallen Blood Cult members—more specifically, their worn out Five Poisons Sect uniforms—let out a deep sigh.

"Still, you were right about something. To think the Five Poisons Sect had truly become the den of the Blood Cult."
