\chapter{Inspector's Method (10)}

Three times a day, Qing supplied meals to the members of the Blood Cult.

The meals for the Blood Cult members were plentiful and, aside from the taste, constitute a superb source of nutrition that would put ordinary health foods to shame.

Moreover, it's even Qing's specialty dish (nutritional porridge) made directly by the Heavenly Flower Sword.

One could even say that the scumbags of the Blood Cult lead a life of luxury.

"That's quite some dedication. Isn't it bothersome?"

"Eh, I live for this kind of fun these days. I'm seriously considering dividing it into smaller portions, about ten meals a day. Hmm, I might get attached. Is this what it's like to raise a beast? If you nurture a weed, it becomes an herb, right?"

"If you nurture a weed, it becomes an herb…."

Ji Yun scratched his chin.

"Even if it's a weed, if you nurture it with affection, it wouldn't be inferior to a prized herb. Hmm, that's a good story. Naturally, a weed can't be compared to a prize herb, but one could use it as an excuse like a failed child or a failed student. Still, hmm, it's a thought-provoking topic worth considering."

If the Lieutenant heard that, he would go insane.

The Orthodox sect has someone inserting a funnel into a person's throat and pouring pig slop, saying it's fun; that they live for this kind of enjoyment.

Yet, the topic would just shift without a care.

Was the future of the Orthodox sect really alright like this?

"Now, you must be hungry, right? Ah, were you so paralyzed that you can't even feel hunger? Then we'll count it as hungry. Now, oh, the smell, hmm, this is a bit of a problem."

Lying on a bed with a hole in the butt area covered with cloth while there's a chamberpot beneath, and it would take a while to be emptied, well, what can you do.

Qing untied the gag designed to prevent self-harm, held the jaw open forcibly, and inserted the metal tube of the funnel.

"Alright, food is going in. Down it goes, gulllp, gulllp."

"……! …!"

"And, hey, we need to pull some teeth today, right?"

"……!!! ………!!!!!"

Only then did Qing carefully pour some water over the cloth covering his windpipe.

"Come on now, let's confess and find the light… no, let's seek death instead. Still no words to say? Will you live like this until you grow old and die?"

"Ugh, just kill me already."

At that, a smile bloomed on Qing's face.

A truly radiant smile that spread its glow like the rising sun, an incredibly charming smile like that of an unmatched beauty.

So much so that even the vicious scion of the Blood Cult was momentarily captivated, losing himself in her presence.

There he was, begging to be killed in such a pathetic state right in front of her.

Among all the reactions an evil person could have, this was Qing's favorite.

"Hey now, patient, you shouldn't say such things. I've taken such care to look after you so you won't die, and you dare say that in my face."

"Please."

"No, what would others think? They might believe I'm not trying to kill you personally. You're the one who is alive and struggling while I'm telling you that if you spill everything you know, I will grant you death, right? I clearly offered you death, yet you keep refusing it! No such thing as a free lunch in this world, you see? If you want to ask for something, you should first show sincerity. Our policy is pay in advance. Now, shall we start with some personal information? Name, title, specialty, hobby."

"……."

At that, the Lieutenant promptly shut his mouth.

\textit{Hmm, seems he still doesn't intend to speak.}

However, Qing didn't press any further.

After all, his cursing words were growing weaker, and he was ultimately in a state where he would likely open his mouth.

Just look at it.

As Qing lifted the gag once more, wouldn't he panic and hurriedly open his mouth?

"No, wait a minute. What's happening with Five Poisons Sect?"

"Ah, discussions are forbidden here."

"Wait, uhh, uh uh."

Qing again clamped the gag on, blindfolded him, and adjusted earplugs to fit snugly before binding them under his chin.

Why? Wasn't it said that the hardest emotion for a person to endure was boredom?

Of course, Qing thought that was a silly notion.

If you had a severe stomachache or a headache that feels like it's crushing your brain, you would think that you rather endure boredom than suffer pain.

However, she could agree that boredom was unbearable, so that's why she had prepared these measures.

After all, the body was devoid of sensations.

You can't speak, see, or hear anything; what would it be like to just breathe alone in such oppressive darkness?

And teething pain would be an added bonus.

Qing might not know, but seeing his wicked enemy and still wanting to share even one more word was quite awful indeed.

But still not opening his mouth, perhaps that means it's bearable since it's not pain after all.

It was then.

Creak! The sound of the door opening.

"Sister! Ugh, what's that smell?"

Despite being dressed, the remarkable presence of his well-developed muscles was evident. Especially those shoulders, a double width compared to Qing's, with trapezius muscles towering like mountains.

A man, clearly bigger, at least a head taller than Qing, held his nose as soon as he opened the door.

Yet Qing calmly raised her palm.

"Oh. Is that Zhuge? You've arrived? Then all the Diancang Sect members must have come too?"

"Yes, Sister. However, Sister Jian stayed back to care for Ciyu. But I heard you captured a Blood Cult member—is it truly like this?"

"Yes. I think he'll open his mouth soon."

"Indeed, as expected of you, Sister. If you can make him yield without using cruel methods, we will obtain reliable statements."

It was so absurd that Zhuge could say this without flinching.

Is the future of the orthodox sect really alright like this?

Of course, the things that Qing generally exhibited were exceptionally cruel.

It would probably be humane enough, relatively speaking, if there were some other stench instead of the thick smell of blood.

Just like the expression 'a frog is slowly boiled', the level of Qing's cruelty might be gradually increasing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

-Fourth Senior, it is certainly beneficial to the world, but it doesn't seem like something the main branch can handle alone. And what about Five Poisons Sect? Isn't the headquarters of such a long-standing sect practically a death trap?

-Ha. It's been a long time since Diancang shot its bow, and its arrows are already rusty. Why are you saying such pitiful things? How can arrows fly without considering their own merits? Should we just leave those evildoers alone?"

-No Fourth Senior, who would let that happen? What I'm saying is, this isn't something the main branch can take on alone.

-Let's say we send a messenger to the Wulin Alliance. When will the support arrive? It'll take at least two months. Do you know what the Blood Cultists will do in the meantime?

-Rather than asking the Wulin Alliance, wouldn't it better to asking for support from the Sichuan's Wulin? At the very least, we should secure the Tang Clan's support in dealing with the poisons."

The sounds of bickering spilled out from a side room.

Not that she was eavesdropping.

It was simply something that she heard because of her acute sense of hearing.

However, standing around awkwardly would make it seem like she truly was eavesdropping, so Qing knocked on the door.

Upon entering, she saw Ji Yun and an elderly Taoist.

She heard him called Ji Yun as an older brother, so he must've been an Elder within the Diancang Sect.

Though he looked significantly older than Ji Yun, who boasts a youthful vigor and shows off the mature charm of middle age.

We should take into account the fact that Gilwoon has achieved the realm of Hyeon-gyeong, and thus looked very young.

"Oh, Heavenly Blossom Sword. You've come. This is Ji Lian, my fellow disciple."

At that, Qing flinched.

Ji Lian Zhenren? Is there truly a person who bears that name? Now that I think of it, although it's a Daoist name, does indeed belong to someone real!

The strongest bandit, Zhu Jilian, meets Ji Lian Zhenren!

As one might infer from Ji Yun name, the generational name of the Diancang Sect's leader hierarchy was 吉 (Ji).

The character 連 (Lian) that followed it was a character often favored in Taoist and Buddhist circles, making it quite reasonable for a disciple's name of that generation, after all.

"Ximen Qing, a junior of Wulin, would like to offer greetings."

"Haha. I've heard from my Fourth Senior. You have accomplished some esteemed deeds. The entire Yunnan's Wulin owes you a great debt."

To this, Ji Yun snorted in disdain!

"A great debt, you say? And the guy who knows that are whining about not being able to invade because he's afraid of the Blood Cul? Can you believe this? This scoundrel are scared and claim he can't attack."

"No, Fourth Senior, when did I ever? And stating it in such a manner, ahem."

Generally, elders tend to be stern in front of subordinates but were usually relaxed amongst their peers.

It's a casual and relaxed atmosphere among themselves.

Thus, even with Qing present, if they keep addressing each other casually, it would be detrimental to someone listening.

Even Qing found it somewhat embarrassing.

\textit{Well, I can understand why the leader of the Diancang Sect might have cautioned Ji Yun. Really.}

\textit{Now that I think about it.}

\textit{He said the Sect Leader always insisted on keeping his mouth shut, but since he didn't do it this time, doesn't that mean it is intentional?}

"Hah, Yunnan is our land, and it is also our responsibility to protect it. Why should we seek the assistance of Wulin Alliance to deal with the Blood Cult that has settled in our land?"

"No, Fourth Senior. Are the Blood Cult scum just only a problem in Yunnan? Also, is it reasonable to propose charging in without a thought? Five Poisons Sect is not just any sect, it's a defensive establishment nurtured for over six hundred years, and they employ poison. Are you even dissatisfied with the idea of ​​asking for support of Tang Family?"

"Our Grand Diancang has never backed down from an enemy for only its own safety."

"No one is suggesting that! I'm saying we should proceed carefully and safely—"

"Are there not arrows that were too afraid to leave the bowstring?"

\textit{Oh, what a splendid line. It resonates quite deeply.}

However, Qing found herself agreeing with Ji Lian Zhenren.

\textit{No matter how dedicated the intention of an arrow may be, shouldn't we conserve as much as possible if we can?}

\textit{That's why even after announcing to live as Ximen Qing in front of the Emperor, I still went and borrowed a cannon from the law enforcement,}

\textit{Even thinking back, it feels like a shameful act but—}

"Excuse me, elder, about that—"

Qing was now hearing booming cannon sounds from far outside the city; the military were in the middle of live-fire training.

Having calibrated the cannon and adjusted its sights, they would soon be ready to surround the city and bombard Five Poisons Sect, and she was about to say that.

"This won't do. I need to ask the disciples of Diancang directly."

"Fourth Senior! No, wait!"

"Elder! Just a moment!"

However, to capture a master of Hyun-gyeong here, the abilities of these two were utterly insufficient.

After all, how could a mere Harmony Realm block the path of a master of Hyun-gyeong?

Moreover, it was due to Diancang Sect martial art pursuing great speed, and given that Ji Yun himself was particularly quick among the already swift masters of Hyun-gyeong.

Zhu Ji Lian (Qing) sent a warm, comforting glance towards Ji Lian.

As the elder Ji Lian shook his head with a sigh, his expression turned grateful, as though he appreciated being noted.

Is yet another elder about to fall prey to the merciless hands of the elder killer?

But before that, first—

Qing and Gil-ryun dashed out simultaneously.
