\chapter{Inspector's Method (7)}

As soon as they gathered their opinions about the suspicious Five Poisons Sect, it was the disciples of the Blood Cult who rushed in.

They wore the Five Poisons Sect uniforms and broke in under the pretense of having attacked Five Poisons Sect, so even a ten-year-old child could now understand that the Blood Cult and Five Poisons Sect had become one and the same.

"What a lamentable situation. Hmm, since Five Poisons Sect will be destroyed by our Diancang Sect, you should hurriedly head to the Tang Clan of Sichuan. By the way, there happens to be a prestigious daughter of the Tang Clan in Kunming, so it's good timing. Time iss of the essence."

At that, Qing was taken aback.

"Oh! Is something going on in Sichuan?"

"Hmm? How would I know about anything happening in Sichuan? I'm not from Sichuan. For matters of Sichuan, you should ask someone from Sichuan. The matter lies not in Sichuan but with you."

"Me?"

"Since you've been afflicted by Gu, you must obtain the antidote from the Tang Clan. Ah, but this is a secret. If it is discovered that there is an antidote to the Gu you're currently affected by, won't the Blood Cult scoundrels start cultivating other parasites as well?"

"Oh, I knew about that, but um, let's focus on Five Poisons Sect first and then check the Absolute Sword Wall. After all, that's the way back."

"If that Gu explodes, it will be hard for anyone, no matter how skilled they are, to survive; actually, you won't endure that since you are only at the level of Harmony Realm."

This was the same thing Qing often mentioned to her friends.

'You probably couldn't comprehend something as simple as Transcendent Realm.' 'Ah, it's so lonely as a Harmony Realm master.' 'Everyone else are a weakling at that level, so it's hard to take my eyes off you.'

Indeed, now Qing also suffered the same feeling.

Well, a master of Profound Realm might feel that way.

And frankly, those beneath Profound Realm were all similar; there wasn't much difference between them, be it a Third-Rate or Harmony Realm; it's merely a matter of distance, right?

However, the divide between Profound Realm and Harmony Realm was about ten thousand times greater than the gap between Third-rate and First-Rate. (Though Qing's personal opinion might differ.)

"No, before that. Aren't you in pain? When the Gu reacted, didn't it glow intensely? I've heard it's a pain beyond what one with normal senses could tolerate. Then again, if you managed to endure it, it seems it wasn't a big deal."

\textit{Hmm. Elder is just like this.}

\textit{He just speaks whatever comes to mind, lacking any malicious intent, perhaps just a born flaw in his manner of speech.}

\textit{But now, it may well be too late to change it.}

\textit{Moreover, with someone of Profound Realm's caliber, whether it's words or the noise produced from their mouth, what difference does it make?}

"Ah, is that the case? I felt nothing at all? Ah, mine must have some sort of flaw. Wow, ah. I didn't even feel it. I am completely fine?"

Her speech cut off abruptly, with an awkward glance that couldn't look straight into the elder, and even a bead of sweat perched on her forehead.

It was an absurd lie that even a dog wouldn't believe.

Of course, Qing was a master of gauging intentions.

There was no reason to speak a lie that wouldn't pass.

He seemed like a person who could be convinced.

"Oh, is that so? You're quite fortunate. Indeed, even precious elixirs will rot if not managed properly. Truly, it is a stroke of luck, and also a great fortune for the Orthodox Wulin."

"Hehe. Why go that far?"

"Excessive humility isn't proper etiquette. Even if it's merely the level of Harmony Realm, no one had never reached that level by your age. Your well-being isn't just your own; cherish it as a precious resource for the next generation of the Orthodox Wulin."

\textit{Especially during such turbulent times.}

Ji Yun added, thinking about it.

\textit{With the Blood Cult writhing, it would mean that blood would soon be spilled again in Wulin.}

\textit{After all this bloodshed, there might emerge even greater chaotic times afterward.}

\textit{The elder masters like us already have little time left to live. Before we go, we must remove the obstructions and leave the future in good hands.}

\textit{And that would be quite the reassuring junior to entrust that future to.}

"Hmm. Since it's confirmed that Five Poisons Sect is a lair of the Blood Cult, there's no need to pretend to be a gentleman in midnight. However, this one, hmm, we should keep him for now, and then throw him in the Repentance Hall to extract information."

"Ugh! Ughh!"

The Lieutenant, whose body was beneath Ji Yun, gurgled out muffled sounds.

Qing's eyes sparkled.

\textit{What's this? Some mysterious technique of Profound Realm?}

\textit{If you could simply seal a mouth this easily, there would be no need to go through the hassle of performing tracheostomy as well.}

\textit{To be fair, while making holes isn't too troublesome, it would be quite a bother to cover up every time they want to speak afterward.}

"Rather, it's a type of sealing acupoint, but it's still beyond your capability. Come back when you reach Profound Realm, and I will gladly teach you."

The implication was that it's still unattainable.

\textit{Hmm, just what are the limits of Profound Realm's abilities?}

That would be known only to those of Profound Realm…

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The leader of the Blood Squadron, Jang Choi-ryang, is a very, very cautious person.

In other words, they say he is very timid.

And now.

The deputy commander who went out to deal with the unknown Odogmunju acquaintance did not return even after a day or the next day passed.

So, Jang Choi-ryang's caution reached its peak.

"Daeju, what should we do now? If the vice-president had failed, the true identity of our school might have been revealed."

"I, I told you not to go. What should I do? What should I do?"

Isn't the worst way to answer a question the way it was originally asked, by asking another question?

Thanks to that, the subordinate was left speechless.

From now on, isn't it the leader, the lord, who has to decide what to do?

No matter how much of a dummy he was, he simply made good poison and gained the favor of the poison master, rose to the position of the main lord, and was effectively leading the unit as the deputy lord.

In times like these, shouldn't we be furious and order revenge, or decide to withdraw because it's dangerous?

First, the subordinate says something like that.

"Revenge? Revenge, ah, not now. The enemy, I don't know who that woman is. The deputy leader was hit, and four, four poisonous beasts went with her. That formidable master, right? That, that, mad dog, isn't it? Did the information leak somewhere? So, what should we do?"

“Calm down. And didn’t you say that Yeo Gwang-gyeon is currently in Cheonghae?”

“Well, that’s right. Here, Cheo, Cheonghae, it’s close.”

"It's not close at all. So, are you preparing to retreat?"

"Oh, no. That's not good either. The, the, the, the, the Master said to guard this place, but if you run away."

Jang Choi-ryang showed caution again.

The burden was a cautiousness that was bursting at the seams.

"Then what should we do? The worst-case scenario is that rumors about our school being here will spread far and wide."

“That, Master, Master has to come back, and when Master comes, Master said to guard it.”

"So, you're saying we'll just keep waiting? There has to be some kind of solution."

"No, just, just stay still, ah, no. The enemy, the oppressors of the Central Plains, prepare, prepare. Ah! Yes, prepare. Traps, formations, what do we have? One geun of residual salt, one and a half geun of Jakryulunsan, four geun of Balsimdok, three geun of Charyeonsimbun, two and a half geun of Usadok. No, because I used it to assemble yesterday, two geun and a bag..."

From Jang Choi-ryang's mouth, the names of the bloodletting and poisonous substances and their amounts continuously flow out.

As if reciting a well-organized ledger.

It means that all the poison stocks are stored in the head, so it is a useless but genius aspect.

“If you set up a formation, then the formation, yes, since there is a formation already prepared in the Odokmun, how about modifying it further? If you set up a Changsangsang in the Nine Palaces, a Uha in the Palgons, and a Cheoyeong in the Palgeon, then it is a Saengmun, no, not Cheoyeong, but Ocheonse……”

If someone knowledgeable in martial arts had heard of it, it would have been a skill that would have made them open their mouths in amazement.

If it is the stronghold of an old sect, there is usually a defensive formation set up.

Isn't it a kind of mental calculation in my head to add one more jin on top of the existing jin without damaging it?

Even though Jang Choi-ryang was an open puppet, he was also the reason he maintained his position as the leader of the first battle group under Dok-ma.

So, the subordinates also do not urge him any further and quietly wait for Jang Choi-ryang to finish his calculations.

“That, that’s right! This is it!”

Soon, Jang Choi-ryang unfolds a piece of paper, picks up a brush, and begins swinging it around excitedly.

How much time has passed like that?

Jang Choi-ryang points to a wad of paper.

“We, we, will guard this place, because the Master told us to, so we set up the formation, poison, and traps, and if the enemy comes, we will kill them all.”

The subordinate looks down at the paper on top.

A detailed map showing the terrain of a part of the open space to the west of Jeong Yak-jeon.

A design of the ship and traps with clear instructions on what to install and how to install them, with precise dimensions.

However, I know it's complicated.

“How powerful is this formation?”

“Two hundred. Two hundred can stop it.”

"What two hundred men? Two hundred masters? And if they come from the Jeomchang faction, the Flash Sword might come out himself."

“Oh, anyway, I can’t stop the situation, if the teacher isn’t here, but still, but still, so, okay, just wait a minute.”

Jang Choi-ryang's hands and feet tremble and his fingers wiggle wildly.

It looks like he's been calculating like that for a long time.

And finally, we come to a conclusion.

"Without Hyeon-gyeong, we might win. The odds are 70-75. If Master comes, we'll win. But, with one Hyeon-gyeong, two Hwa-gyeongs, twenty Cho-jeoljeongs, and the rest, half of them, we'll kill at least half of them. At least."

His subordinates also accepted it neatly.

In fact, no matter how great the formation, how terrifying the traps, and how outrageous the mercenary tactics—

This is just plain stupid.

If you win once, more enemies will come, and if you win there, even more enemies will come.

So, in reality, you are destined to be surrounded by enemies and die, and in such a situation, the Dokma should not return.

But now that it's come to this, it's okay if we lose, because it won't be a meaningless defeat.

If only we could make the oppressors of the Central Plains shed so much power and blood.

Revenge will be carried out by the remaining compatriots.

This was the poison that made a blood sect a blood sect, a blind hatred that even used death as a tool.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As the nighttime reconnaissance was canceled, the only thing Qing could do was to watch whether the Blood Cult scoundrels would try to escape while waiting for the arriving disciples of the Diancang Sect.

And perhaps just holding on to the life of the captured Blood Cult member to prevent them from dying.

"Now, it's time to eat?"

Shh, shhh. The sound of air leaking.

After all, the Lieutenant, who had a hole pierced between his collarbones, had entered a state of silence.

According to Ji Yun, it was a simple technique where he merely executed a small version of the sound-sealing method to effectively seal that mouth.

\textit{Hmm, is it really that easy?}

Just sealing a sound was already quite a marvelous feat in itself.

Qing could also seal the sound.

By manifesting her immense inner energy to envelop the whole area, that would suffice.

However, that would bring about an overwhelming sense of presence.

Even ordinary citizens ignorant of martial arts would be able to sense an incredible pressure from afar, similar to how a master's aura works.

So Qing did it in her own way.

There's no need to use difficult and miraculous methods; she just had to prevent air from getting into his vocal cords.

Just making a little hole with a finger would finish it off.

What's more, it requires no inner energy at all, as it's a remarkable tactic that can be used without any martial arts training!

By the way, upon seeing Qing's method, Ji Yun was greatly impressed.

"Indeed, we should employ this in our Repentance Hall. It's exhausting to put a gag on every time just to command them to humble themselves; every meal time it must be taken off at the cost of annoying those dimwits who sometimes try to speak up."

Qing haD released poison in the Diancang Sect's Repentance Hall!

\textit{It seems they prevent speech entirely to keep them from speaking…}

\textit{Thinking about it, it only makes sense that you wouldn't let a bunch of captured scoundrels talk freely to kill time.}

\textit{I've heard that the Shaolin Temple holds a strict regime, even digging caves into cliffs to isolate each prisoner into their solitary confinement.}

\textit{If you think about it that way, isn't the Kunlun School's Repentance Hall treating beast too humanely?}

\textit{They even occasionaly provides special treat.}

\textit{Indeed. Special treats.}

Qing looked down at the meal in the bowl.

It was an unexpectedly thick and murky something.

\textit{Just mashed everything together and mixed it into a meat soup without cooking it properly; well, it can't be called porridge. So what should I call this? Umm, a liquid food?}

\textit{But it has meat, fish, and grains, so isn't it a special treat at least?}

\textit{Since nothing rotten was included, if I had one bowl of this when I was a beggar, it would truly have brought me to tears while enjoying it.}

\textit{It even has its own funnel.}

That's right. It was a funnel.

A generic term for a tool that's fitted over a narrow entrance to conveniently pour its contents inside.

And in the room, in front of her, there lay a bloodthirsty creature of the Blood Cult, paralyzed and rolling its eyes around with its spine dislocated.

When paired with mealtime, what sort of scene does that create?

There's no need to explain it.

Moreover, Ji Yun was also thoroughly impressed by this idea and deemed it worthy of immediate implementation.

It must be very regrettable for the prisoners of Diancang Sect's Repentance Hall, but then they should have lived a life without regrets so that they would not have been caught in the first place.