\chapter{Inspector's Method (3)}

Qing revealed the suspicion of madness that merchant Jong had.

Ji Yun stroked his chin.

"Hmm. That's a bit dubious. That isn't a certainty, was it?"

It seems that the merchant Jong was indeed a killer, but it's unclear if this was a hereditary trait.

It could merely be a vile hobby of a wealthy local authority, and merchant Jong might have learned this hobby from his father.

"Moreover, from what I heard earlier, the child realized the futility of the bond of desire on his own and chose to end his karmic ties with forgiveness, so even if he has madness, he must have already learned the ability to restrain himself. Heh…"

A deep sense of regret permeated Ji Yun's voice.

\textit{Well, but isn't this something that shouldn't be spoken with regret? Or should the less virtuous side have grabbed a knife and killed the cheating man and woman themselves?}

\textit{Hmm, thinking about it, that seems much more manly and fitting of a martial artist.}

"Well, anyway, the story is quite touching, so let's examine the potential, and if it seems fine, we can accept him as a trainee and keep an eye on him."

In the local terms of Qing's homeland, the Diancang Sect was like a major corporation within the region.

The Five Great Families were thorough family businesses; only family or adopted children could join, so they were excused from outside recruitment.

As a reference, a trainee could be thought of as an originally non-existent level in the Four Disciples hierarcy.

What was this level?

It's the ranking established within the sect between master and disciple.

The Sect Leader and Elders center around this, and their disciples were referred to as first-level disciples.

These first-level disciples teach their own disciples below them, forming the second-level disciples.

And the second-level disciples teach disciples, resulting in the third-level disciples.

Later, when the Sect Leader retires and one of the first-level disciples takes over the position, the hierarchy rises a level.

The Sect Leader's rank becomes the Grand Elders rank, the first-level becomes the Sect Leader rank, the second-level becomes the first-level rank, and the third-level becomes the second-level rank.

Then, these second-level disciples take charge of the disciples they will teach, leading to the birth of third-level disciples.

So, it used to be like that.

The Martial Alliance was originally a social club of Orthodox sects, but as it solidified into a coalition, the different rankings of these sects began to intertwine.

Even among peers, some were upper-ranked elders while others were underlings, and if this applies to the whole generation, then what happens?

And not only that, if there were two or more ranks misaligned?

Thus, in a tacit agreement (definitely not officially), the ranks also began to align with each other.

No matter how much to protect the lineage, one might argue that this was a lineage-less act.

On the contrary, the higher the ranks and the older the martial artists, the more satisfied they were with this behavior.

Especially the Sect Leader's ranks.

The Sect Leader and Elders take on the actual duties of the sect. Yet, they also have the grave responsibility of teaching the most important members of the sect, the first-level disciples.

Until when?

Until the Sect Leader dies or was unable to perform duties due to senility.

But now, all they have to do was endure.

If they can withstand for about fifteen years during which the rank was divided, from then on, a lazy and blissful life will unfold before them.

Thanks to this, trainees were now born.

They were those too young to enter the third level, who were taught while waiting for generational change, in other words, a promising talent cultivation system.

"Wow, you are going to take him in to the Diancang Sect?"

"As long as the talent isn't lacking. No matter what, he'll be a disciple of the great Diancang, so we can't just take anyone without discretion."

\textit{Hmm, so you're saying that outright…}

\textit{Well, no matter how much every sect may think that internally, they would outwardly say that they value righteousness over cultivation.}

\textit{Yet from what you say, can I even trust this person with the kids?}

In fact, from the perspective of the Jong brothers, bowing deeply to Qing and even promising to serve her like a mother wouldn't be enough to repay such tremondous grace.

After all, the Diancang Sect was no ordinary sect.

In Qing's homeland parlance, it's a giant corporation.

Not just any giant corporation, but one of the top giants in the world.

To pass through the CV's screening based solely on connections to the CTO and directly go for an interview was significant.

Thinking about guanxi culture of Zhongyuan, it's no different than saying that they would accept him even if he was talentless.

A truly amazing connection! An absolute case of nepotism!

"By the way, hmm. The Five Poisons Sect has fallen so miserably. What a regrettable matter."

This made Qing slightly cringed.

In fact, the Five Poisons Sect had been decimated long ago, and the culprit that eliminated the lineage was none other than Qing herself.

Qing stealthily gauged the mood.

"Oh, um. You regret it? I hear that their deeds are worse than any other Unorthodox."

"Hmm? Thinking about it, I don't regret it."

"Really?"

"I misspoke. Not in the sense of regret, or am I right?"

"Do you regret it or not?"

"Hmm. To think I would have to erase such a long-standing sect myself, isn't Five Poisons Sect one of the oldest sects in Zhongyuan?"

"Is Five Poisons Sect that old?"

"In the past, Five Poisons Sect was called Five Poisons Alliance, an alliance of the five Miao tribes of the Sichuan. They always said they need to reclaim Sichuan that was taken by Zhongyuan people. When Five Poisons Alliance still in Sichuan, this was during the early Song Dynasty, so it must be at least more than six hundred years old, right? At the very least, so aside of Shaolin, there were no current sects older than that."

As a side note, the monks of Shaolin always proudly state that it has been a thousand years, but it was also a humble expression.

Shaolin Temple's history has been more than a thousand years since the starting point of the previous Shaolin Sect.

However, saying 'one thousand one hundred years' or 'one thousand one hundred and one years' sounded a bit strange.

Ji Yun grinned and added, "Or the original Diancang Sect."

\textit{Hmm, is that what you wanted to brag?}

Among the various martial sects, the oldest sect was certainly Shaolin Temple; after all, all martial arts started from the original Shaolin Sect.

On the second place was Diancang.

However, Diancang was originally a sect of the Bai people in Dali, outside of Zhongyuan, so it was not officially part of Zhongyuan's Wulin.

"Therefore, I must also be cautious. To end such a long history is indeed, whether friend or foe, quite regrettable? Hmm? Or not? Simultaneously, it would be historic, yes, if I, Ji Yun, were to put an end to that ancient history of Five Poisons Sect, I would be quite pleased."

Qing understood the personality of the greatest swordsman in Diancang, who had reached Profound Realm.

\textit{Elder Ji Yun is the type to speak first and think later.}

It was an inappropriate thought that she suppressed, but even if she hadn't, Ji Yun would have burst out laughing.

After all, what thought does an arrow need? Once released, it should fly directly to the target.

"However, I must confirm it with my own eyes. Hmm, how about tonight? Since the night of the new moon is approaching, it's perfect for sneaking over the wall."

\textit{In addition, overflowing with vigor!}

\textit{Let's infiltrate Five Poisons Sect tonight and see if it's a den of the Blood Cult or not.}

\textit{Well, that's a truly good idea.}

\textit{This elder seems to really match with me.}

"Then, as we need to stay up late tonight, I'd better drink heartily and sleep early? Do you drink?"

\textit{Wait, such a good idea?}

\textit{It's not that he just matches with me, but he fits me perfectly.}

"Hey! Waiter! Waiter! Hmm? Is it rural out here? Damn waiter doesn't respond when called. Even if they can't come right away, shouldn't they answer quickly? Waiter! Waiter!!!"

"Elder, you haven't open the curtain."

"Oh right. It's a habit. Whenever I goes somewhere with our Sect Leader, he'd begged and pleaded for me to keep my voice down."

"Ah. Yes."

\textit{If it's Ji Yun, the elder of Diancang, I can understand why he would earnestly request that.}

"Waiter!"

-Yes! Coming right away!

If there's the cat of Mr. Schro in the Western Regions, then there's Waiter currently in Zhongyuan.

When the guests call, an immediate answer returns, but whether the waiter actually come or not was uncertain until they appears.

\textit{However, considering the uniqueness of the current situation where the inn isn't doing well, we can expect that they'll hurry this time, right? Am I right?}

Creak!

\textit{Indeed.}

Qing was somewhat smug while the waiter scrubbed his hands with a friendly smile.

"Hehe, esteeemed one, what would you like me to prepare for you?"

But, the waiter's face?

It wasn't the usual waiter.

"Oh, where's the waiter who was here before?"

"Haha, it's been quite calm in the town lately. So, we must share the work. In times like this, should some work while others take a break?"

"Um."

Qing looked at the waiter, quickly surveyed above, and wondered, '\textit{Who is this guy?}'

In fact, waiter was ranked among the worst five professions in Zhongyuan, making it into the bottom tier.

These bottom five refer specifically to the carriage driver, boatman, porter, waiter, and human trafficker, all notorious for a high correlation with criminal activities.

Thus, it's pretty common for there to be bad apples among waiters.

\textit{But still, isn't this exceeding the limit?}

In fact, even those with high misdeeds were typically found in cheap inns or suspiciously secluded lodges.

But here, it's a top-notch tavern in Jinping, such high-class establishments rarely see them.

This was also why Qing always opted for the best taverns in the region.

Qing's eyes narrowed.

"Looks like this waiter must have some talents? No birthmarks or anything?"

The higher-class inns prioritize birthmarks, so whenever Qing sees waiters, they always have a noticeable mark or two on their face.

\textit{But why don't you have one?}

"Oh dear, guest. Birthmarks are something you're born with; but you're saying my waiter skill isn't something I was born with? Thank you very much. Hehe."

The slick and smooth way he brushed it off shows he's definitely born a waiter.

Of course, Qing wasn't a wicked assassin who would just kill those with high misdeeds.

Just because someone had high misdeeds doesn't mean they have to die.

But still, she remained cautious.

However, misdeeds were only visible to Qing.

Ji Yun waved his hand.

"Alright, just check on the liquor. Ah, bring out some Three-course Tea as well, and a suitable amount of white and yellow liquor, and gujiu\footnote{穀酒; rice wine}, you understand?"

"Yes, I'll bring it right away."

Soon after, the waiter, grunting and groaning while carrying a liquor tray, awkwardly set it down on the table.

"Well, since you've come to Yunnan, you must experience the customs of Yunnan. This is Three-course Tea\footnote{三道茶; Sandao Cha}."

Technically, it's not really Yunnan customs but the customs of the Dali people.

This tea was the first thing served when entertaining guests, made by steeping high-quality green tea from the Tea Horse Road three times.

The first brew was bitter.

In Zhongyuan, they usually discard the first brew, but the Bai people drink it without throwing it out.

Of course, it's naturally bitter.

"Is it bitter? That is the taste of youth. Bitter, astringent, and difficult, it's the taste of youth."

The second brew of tea was enhanced by adding honey, walnuts, and various things to enjoy a rich flavor.

This represents middle age; a family settled in that achieves abundant happiness.

The third brew tastes bland since it has been steeped twice, making it normal.

This was the faint and dull taste of old age.

"Here lies all the essence of a person's life. Oh, did you finish? Then, where should we begin? Hmm, what will you have? White liquor? Yellow liquor?"

Ji Yun poured the rice wine into a bowl, mixed it with yellow and white liquor, and stirred in honey and dates.

\textit{Ah, the elder likes bomb shots.}

For some reason, the more she looked at him, the more she felt like he wasn't just an elder from an Orthodox sect but an uncle working in the local area, quite real.

"Alright, alright, for the first three cups, don't refuse. Even if it's not, Heavenly Blossom Sword was said to be famous for drinking capacity, so today I must investigate if that rumor was true."

"Heh, with the liquor here, it'll only suffice for a couple of bowls, right?"

"Haha, good. Well, I should say something, so here."

Ji Yun raised his cup for a toast.

"To Five Poisons Sect."

"To Five Poisons Sect."

This was the toast made by someone who intends to erase Five Poisons Sect from the world.

However, it's not out of a malicious intent, rather, it's purely for the long history of Five Poisons Sect. It was just sounds strange.

But the one receiving it was the very person who wiped Five Poisons Sect from existence.

If there were indeed a hell, it would be a sight to see the tears of blood shed by Five Poisons Sect.

But, well, it would also be just fine.

They were indeed deserving of shedding such tears.

Regardless, Qing hurriedly drank her bowl.

He could only express it as hasty; Ji Yun blinked in disbelief.

"Were you that thirsty for liquor? Didn't say a word."

Qing felt unfair.

He just got too anxious about the waiters's Evil Karma.

The bad things highly associated with misdeeds done by waiters often involve poisoning alcohol or food.

After incapacitating someone, they'd either sell it or use it for meat, among other sinister uses.

Thus, the reason Qing rushed to drink that bomb shot was somewhat precautionary.

氣味. Qiwei (smell).

The act of sampling the food of a noble person to see if it contains poison was known as a 'smell hint.'

\textit{Hmm. There's no poison.}

\textit{After all, he may not know my identity, but I'm sure there's a rumor that I'm a master since I've caused a lot of ruckus, so he likely wouldn't be trying anything funny.}

Qing felt relieved.

Thus, the pouring and drinking continued.

\textit{Next, I'll the side dishes. All the snacks belong to me.}

The elder drunk plenty.

However, there war something peculiar about these snacks.

Initially, they were just ordinary Zhongyuan dishes, but as she ate more, a gradually pronounced spicy flavor began to emerge.

\textit{What is this? How has an entirely non-spicy dish grown spicy?}

Even the liquor felt as if it was getting spicier by the moment.

"……?"

Qing tilted his head.

It was not just a feeling.

The liquor was truly spicy!

\textit{What is this? Why is the liquor spicy?}