\chapter{Inspector's Method (9)}

The Magistrate was taken aback.

\textit{A cannon? Borrowing a cannon? What on earth is she planning to do with a cannon? Well, of course, if you've borrowed one, it's obvious you intend to shoot it.}

In fact, the real question was not what to do with the cannon, but rather who it would be aimed at.

The only thing a cannon could do was destruction, so if you're borrowing one, it would naturally be to fire it.

However, cannons weren't an ordinary matter.

The law enforcement office also operated cannons.

However, the purpose of those cannons was for defense, to hold out until military support arrives in the case of an unexpected invasion.

Since the state meticulously monitors the quantity of shells and gunpowder, no matter how esteemed Magistrate is, he could not simply take one out and fire at will.

Of course, the Inspector's request was also not an ordinary matter.

Thus, the Magistrate fell into deep thought.

But time was running short.

Hadn't the high-ranking official first opened his mouth and said 'favor'?

Showing prolonged hesitation would indeed be a blow to the dignity of a high-ranking official.

"Um, we have four General Cannons assigned to our jurisdiction, thirty shells, and about ten pounds of gunpowder."

"Wait. General Cannons? Not just regular cannons?"

General Cannons\footnote{将军炮; Jiangjun Pao}, if categorized, were more like direct-firing artillery in Qing's homeland.

General Cannons were weapons that shoot primitive ancient pellets forward.

A multitude of metal fragments fired in a fan-shaped pattern, capable of literally turning a person into minced meat.

They were primarily meant for defense, to sweep away incoming foes.

Behind city gates, behind the main gates of law enforcement, set up along narrow routes to eliminate advancing enemies.

The cannons Qing was thinking of were the ones operated by military authorities.

Artillery capable of launching various types of primitive ancient bombs, primitive ancient chemical shells, and primitive ancient flame projectiles far away with gunpowder were far more effective for offense than for defense.

However, there was no reason for such offensive weapons to be operated by law enforcement office.

Despite this, the Magistrate felt relieved.

It seemed she wasn't looking for General Cannons but instead wanted the regular cannons; if so, she would have to visit the Provincial Military\footnote{都督府; Dudu Fu; Military Provincial Commander Commission}'s office next.

Since the Provincial Military's office operated under a completely different command system from Magistrate, it would not matter for him whether they lend her a cannon or not.

"The regular cannons are owned by the Provincial Military's office, so it would be difficult for me to help. However, if you wish, I can send a message to them."

"Um, is there a nearby military camp?"

"Hehe, if you go just a little west, there's Western Army Central Command. Fortunately, since the southern barbarians are right on our doorstep, the Western Provincial Military'd office has plenty of cannons."

As the Magistrate explained, a trace of doubt began to swirl in his mind.

\textit{Something feels a little off, doesn't it?}

\textit{Is the Inspector really unaware of the difference between General Cannons and regular cannons, coming to ask for the regular ones at the law enforcement office?}

\textit{And is it possible that she didn't even know the location of the military camps?}

Moreover, due to the strict division between the civil service and the military, an Inspectir did not have any role in overseeing the military.

This was because there was a separate position, the military inspector, meant for overseeing military affairs.

Given the clear division of ranks between civilian authority and military authority, no matter how authoritative an inspector may be, it would take significant connections to gain cooperation from the rigid military's office.

"Umm, I guess I need to visit the Central Command then."

At that, the Magistrate felt relaxed.

Passing the dubious inspector off to the miltary's office was certainly a relief, and anyhow, since there was some suspicion, he could conceal his intentions and present the sincerity later.

With that thought, he suddenly grew curious.

"By the way, what brought you to ask about the regular cannons…?"

"Ah, the vicious scum of the Blood Cult have made hideouts in the city. Since they are nasty fellows, I was wondering if we could shoot a cannon at them and take down whoever pops out."

The Magistrate tilted his head.

\textit{The Blood Cult? That Blood Cult? The one committing treason? Why all of sudden?}

"Are you talking about the Blood Cult? Do you mean those treacherous scoundrels are hiding in the city…?"

"Ah. Five Poisons Sect has joined hands with the Blood Cult. It seems too dangerous to attack directly."

In an instant, Magistrate's heart sank.

Indeed, Five Poisons Sect was akin to the largest noble clan of Jinping County, so the sincerity sent to him wouldn't be negligible.

\textit{I received sincerity from traitors, traitors!}

The Blood Cult was an extremely treasonous organization.

They were the real deal, publicly declaring their intentions to assassinate the Emperor and bring down the country, truly despicable traitors.

To have received sincerity from such a Blood Cult?

It was a major crime that could easily label one a traitor.

"Is this, is this a confirmed fact? What the hell, the Blood Cult, those Five Poisons Sect are living just fine, what do they gain from partnering with …?"

"It is a fact already confessed by the Five Poisons Sect leader, and we have also captured the vile scum and monsters of the Blood Cult."

At that, the Magistrate jumped up from his seat, shouting urgently.

"The Blood Cult! I cannot allow this as a magistrate! We must head to the Provincial Military's office! I will lead you there immediately!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

While urging the driver, the Magistrate couldn't shake a slight anxiety.

This was due to the fact that he did not have a particularly good relationship with the Provincial Military office.

For the Provincial Military office to establish a military camp, two conditions must be fulfilled.

First, it should be a point where quick deployment was possible in case of national emergency.

Second, it must have wide arable land.

Among these, if one were to emphasize the crucial factor, the second, fertile land for farming, was of utmost importance.

In this respect, the regional government and the military authorities had a fundamentally troubled relationship.

Officials needed to secure a share of the land's output, but once a military camp was established, it took away all the surrounding lands, effectively robbing the yield.

Let alone that.

The military authorities continued to extort supplies under the pretext of protecting the country.

Thus, getting along with the military would ultimately be detrimental for the officials.

The closer they are, the more they would be taken advantage of.

Consequently, it was only natural that the military also has no good feelings towards the officials.

Once the military steps in, they would eliminate the bandits surrounding the area, so aren't they heroes who greatly contribute to the security of the area?

Even so, the regional government treated them like beggars and tried to be stingy by not giving them any supplies.

Of course, this fundamental issue originates from even higher up, where the high officials in the Imperial Palace in Beijing, as well as the personnel in the regional government and the Provincial Miltary's office, were engaged in power struggles to outmaneuver each other.

Thus, even if one was an inspector, or rather, especially since she was one, her chances of obtaining cooperation from the Provincial Military's office would be even slimmer.

The stiffness in the voice of the central command was evident even before they arrived, almost as if the Magistrate could hear it in his head.

'Are you the Inspector? However, the inspection of the military is not the responsibility of Imperial Censor, and military affairs are also under the jurisdiction of the Ministry of War.'

There was no reason for an inspector to interfere, especially with the operation of firearms.

Military affairs were about obeying orders, and the firearms that protect the country could not be mobilized privately.

Since it required the order of the commander, not the permission of the headquarters, bring the order.

And as expected.

"You're the Twelve Province Inspector General, Lady?"

Perhaps he was in the middle of training his body, but the commander, with his shirt exposed, looked Qing up and down in a sullen manner.

He was already on the wrong track with the commander.

\textit{The Chief Inspector has come, so it would be insufficient to merely treat her with courtesy and respect.}

\textit{Moreover, what kind of shameful behavior is this in front of a woman?}

"Look here, Commander. Even though we are of different authorities, that Madam carries out state affairs under the Emperor's command—"

"Hmph. Military affairs also follow only the Emperor's orders. Indeed, that is why we must be even more rigorous. I'll tell you in advance: we cannot move our troops without orders. So, what brings you here?"

"Umm, I was hoping you could help me with some artillery."

"Ha, cannons? Do you think cannons are just the kind of celebratory fireworks you fire on New Year's Day? Gunpowder and shells are specially controlled items by the government, military supplies that can never be released without an order. Even if you're a Minister, it's the same."

The commander's words were firm.

Well, the commander had nothing to kneel down to.

Thanks to the Empress being the daughter of the Minister of War, the military's influence was at an all-time high.

A mere inspector general was not someone who can speak ill of the military.

Qing's shoulders slumped.

\textit{This looks like they'll never lend it to me.}

\textit{Well. Even if it's Diancang Sect, if you were to storm into the Blood Cult's den without backup, the damage would be immense...}

"Listen, this isn't the time to be saying that-"

It was at that moment that the Magistrate was about to begin persuading him.

Suddenly, the commander's eyes wavered.

A thought suddenly popped into his head.

"Excuse me, are you by chance the Inspector General, Lady Ximen Tianhua?"

"Ah, I hadn't introduced myself."

In truth, Qing didn't introduce herself on purpose.

She knew all too well how cowardly and despicable it was to call herself a martial artist but then resorting to the Empress' plague and the Inspector's badge whenever it suited her.

She had many reservations about exposing her name and deliberately held back.

\textit{Still, what else can I do?}

\textit{It's much better for me to bear the ridicule than for the Diancang Sect warriors to shed unnecessary blood.}

Selfish as it is, she thought she might as well be selfish about it.

\textit{But how did he figure it out when I didn't mention it?}

\textit{Hmm, it must have been from the Empress…}

"Yes, I am that Ximen Tianhua. I had temporarily set aside the badge due to unavoidable circumstances. Well, I can retrieve it later."

"Ah! I apologize! Please excuse me!"

The central commanding officer immediately stood at attention, adopting a military demeanor.

As if nothing had happened, he stood rigidly in a precise military posture.

It was a standard of discipline rarely seen even among the new recruits.

This was due to the intent that had come down from higher-ups.

'If Inspector Ximen Tianhua seeks cooperation, treat it as your top priority.'

The command was specially given by the Minister of Military Affairs, so cooperation with Inspector Ximen Tianhua should be treated as equivalent to the command from the Minister of Military Affairs.

The current Empress was the daughter of the Minister of Military Affairs.

It was an order secretly delivered by the Minister of Mlitary Affairs after hearing the truth about his granddaughter from the Empress.

Of course, it was not wrong that the words of the princess were equivalent to imperial decree.

"Preparing immediately! Fifty fire cannons total, currently forty-nine ready, one under repair due to training damage! Fifty slingshot cannons, all ready! Thirty General Cannons, all ready! Two thousand five hundred iron pellets, one thousand two hundred flame pellets, three hundred poisonous flame pellets, currently the available amounts! If more were needed, I will promptly request support from the governor's office!"

Here were the types of cannons and shells of Zhongyuan.

If categorized in a manner reminiscent of Qing's homeland?

The fire cannon refer to mortars, small artillery pieces that military personnel can easily carry.

The slingshot cannon refer to larger towing artillery that must be pulled by beasts.

Iron pellets were buckshot, which explode upon falling to create a steel storm around them.

Flame pellets were incendiary rounds that ignite sticky oil and burn uncontrollably.

Poison flame pellets were chemical shells, a hidden weapon that emits toxic fumes.

"Um, you just said you couldn't lend…"

"It seems I was foolishly short-sighted because I did not think carefully! As His Majesty governs the nation according to the Will of Heaven in governing the nation, wouldn't cooperating with Inspector be an act of loyalty to the nation? I will assist with no reservation! Just give me the command!"

The Magistrate's eyes widened in astonishment as he stood next to Qing.

\textit{Wow, the usually rigid commander has show such military discipline, without a doubt, the Inspector truly is an incredibly powerful figure!}

\textit{Indeed! I had faith in you!}

\textit{Upon first meeting, I could tell right away she is someone extraordinary, it was like her aura blazed so brightly that I couldn't keep my eyes open.}

\textit{Even without her official seal, I have never once doubted her!}

\textit{When I get back, I'll be sure to offer my sincerity first!}

An essential skills for high officials in Zhongyuan was the ability to manipulate memories.

By virtue of being a high-ranking official, one was expected to possess the ability to alter their own and their subordinates' memories.

Anyway.

Qing has successfully acquired the cannons!