\chapter{Inspector's Method (11)}

When Qing and Ji Lian Zhenren rushed to the special room, it was already after Ji Yun Zhenren had begun to speak in front of the lined-up members of the Diancang Sect.

"It was a long time ago, and even before that."

A long time ago, or rather, very very long time ago, this was a preface commonly attached when a Zhongyuan person tells an ancient legend.

"Ten suns rose above the earth, and the land burned day and night. Amidst the chaos, countless demons ran rampant, and the world fell into despair. Thus, everyone offered sacrifices and sought help from the celestial beings, but there were no immortals who responded to their cries. The ten suns were not simple suns; they were the sons of the Heavenly Emperor."

A hint of confusion appeared on the faces of the Diancang Sect warriors as they listened to the story.

This was because it was a story that everyone in Diancang Sect should know.

"Then, a righteous immortal stepped forward with a bow, and his name was said to be Hou Yi."

Because this was the tale of Hou Yi, the immortal who shot down nine of the ten suns.

"Hou Yi shot down nine suns and also pierced through the great demons that had run rampant on earth, and finally, peace was restored to the world."

The expressions on the faces of the Diancang warriors swelled with a sense of pride.

After all, it was only natural for the Diancang, who considered themselves descendants of Hou Yi.

However, Ji Yun's words were not yet finished.

"But what fate did the one who saved the world face? Indeed, it was a truly tragic and lamentable thing."

After that, Hou Yi became quite pitiful.

Having killed nine suns, that is, the nine sons of the Heavenly Emperor, it was only natural that the Heavenly Emperor became enraged and exiled Hou Yi.

The once immortal Hou Yi was cast down to the earth and became a human.

Having married the wrong husband, his wife, Chang'e (the most beautiful woman of heaven), was also exiled with him, demoted from an immortal couple to a human couple.

Unlike immortals, humans age.

One day, shocked to see the wrinkles of Chang'e's face, Hou Yi immediately sought the Queen Mother of the West to beg for an elixir of immortality.

Originally, this was a treasured item that should never be given to humans, but the Queen Mother said, 'We are old friends, after all', and gave him two rejuvenating peaches.

It meant that the couple should each eat one and live long and happily.

However, the effect of these peaches was astonishing.

Eating one grants immortality, but eating both allows one to become true immortal, as they were treasures made from the essence of the heavenly peaches.

And when Hou Yi's wife, Chang'e, saw the peaches, she gulped.

Having been expelled from the heavenly realm, a place already easy to live in, Chang'e, who was fed up with living in this terrible mortal realm, was immediately dazzled by the two peaches.

Then, she gobbled both of them up all by herself and ran away.

Hou Yi was suddenly betrayed by his wife and lost the elixir.

As a result, Hou Yi fell into despair and spent his days drinking.

Then one day, a boy came to him and asked to be taken as his disciple, and with no one to cling to, Hou Yi took the boy in as his disciple.

However, this disciple had a remarkable dream.

He wanted to become the Greatest Archer Under Heaven!

How does one become the Greatest Archer Under Heaven?

By killing the existing Greatest Archer Under Heaven!

Instead of thinking about raising his own skills, the disciple only thought about killing his master and eventually aimed at Hou Yi in secret and shot at him.

Hou Yi caught the arrow with his teeth and blocked it.

No matter how much Hou Yi was drowning in alcohol, his past skills as an immortal were still intact.

Seeing this, the disciple cried and begged for forgiveness.

With his own disciple crying and begging, Hou Yi, feeling equally pained, thought, 'Let's just pretend it never happened', and forgave him.

Meanwhile, the disciple genuinely repented, thinking, 'Ah, I did a great wrong. How could I dare to oppose my master with a bow? I can't win.'

Thus, he thought, 'I should face him with a club instead of a bow'.

What a truly Zhongyuan-like notion!

So the disciple quietly snuck in at night and smashed Hou Yi's head while he was sleeping.

That was how the succession of the Greatest Archer Under Heaven! title went.

Truly, a Zhongyuan-style succession!

This was a legacy far ahead of the famous son of a bitch who was known for inheriting the throne much later, by eight thousand years(?).

"Although Hou Yi saved the world, he met such a miserable end. He was betrayed by the wife he loved and killed by the disciple he had raised like his own child."

Hearing this, Qing tilted his head in confusion.

\textit{How could Ji Yun Zhenren stop speaking when he was telling such a story?}

But if Qing interrupted here, sspecially in front of the warriors of the Diancang Sect, it would be an act of rudeness that would offend not only Ji Yun's but also the Diancang Sect's dignity.

So then she just listened, but why did Ji Yun stop the story of Hou Yi there?

If it ended there, only Hou Yi would seem pitiful, wouldn't it?

In fact, there was more to the story after that.

After his death, Hou Yi returned to the heavenly realm.

The Heavenly Emperor, thinking carefully, realized that it was entirely his fault for not raising his sons well.

Thus, he summoned Hou Yi back and granted him a position in the heavenly realm.

'You have died, so you are no different from a ghost. Ghosts understand the minds of other ghosts well. From now on, you shall govern the ghosts,' he said.

Having seized power, Hou Yi commanded ghosts to chase after that wretched disciple of his.

The disciple suffered throughout his life, tormented by ghosts, and eventually died alone on the street.

Meanwhile, his wife, Chang'e, who had taken the elixir alone and ascended, had long since been exiled to the moon due to her sins.

Thus, the bad guys received punishment, and the good ones lived happily ever after.

Of course, as immortals were typically unaging, it was understood that Hou Yi still eats and lives well in the heavenly realm.

"However, even so, Hou Yi was a hero. Even if his end was tragic, no one denies him. Rather, there were chivalrous warriors who rise, claiming to be the descendants of Hou Yi, thus the will of Hou Yi has passed down to them, and the arrows piercing the suns have reached our Diancang Sect."

Ji Yun Zhenren's voice filled the surroundings.

Hyun-gyeong's voice was soft yet penetrating, filled with a majestic charm.

It was a voice that wielded cosmic mysteries.

"I will ask you. If all that remains for you is this terrible future, will you not save the world?"

"No!!"

"Will you ignore the cries and moans of the world because you feel it is unfair that your own body may be hurt and suffer?"

"No!!"

"Right there, the human filth of the Blood Cult have set up their lair. Five Poisons Sect has fallen from grace, and they are in collusion with the Blood Cult. Right there at the main hall of Five Poisons Sect, their vile plans are being devised that will plunge the world into despair."

The voice of Ji Yun Zhenren gradually became passionate.

"Of course, it will be dangerous. We know well how a long-standing sect fortifies its nest with our own long history. They even use poison. So during this operation to eliminate the Blood Cult, someone here might die, or someone might suffer a terrible end due to being poisoned."

Tension filled the faces of the Diancang warriors.

"Perhaps we may have to wait for the support from the Wulin Alliance."

However, we do not know the Blood Cult's schemes.

We do not know what the Blood Cult was plotting right now, nor can we predict what they will do once they realize they were cornered.

While waiting for the Wulin Alliance's support, how many innocent civilians will die, and what kind of calamities will plunge the world into despair? We do not know.

"I will ask you again. Will you ignore the cries and moans of the world because you feel it is unfair that your own body may be hurt and suffer?"

"No!!!"

"Yunnan is the land of our great Diancang and the history of our great Diancang. The filth of the Blood Cult has intruded into our land and history that we must protect, so who will exterminate this pest?"

"It is us!!" "It is Diancang!!" "I will do it!!" "Me!!"

"Yes, this is the way of the descendants of Hou Yi, the Sun-shooting Hero."

\textit{Ah, so this was how he builds up a case.}

\textit{I thought he was just saying whatever he want, but he was quite a significant orator.}

With their loud responses, Ji Yun smiled.

\textit{Indeed, Ji Yun Zhenren, with his middle-aged demeanor, was shining beautifully. Hmm, I also want to age like that.}

\textit{But now I've completely blown it…}

In any case, it was an eloquent speech that left a significant impression on Qing.

And she understood the reason why Ji Yun Zhenren insisted they must attack immediately.

Because they did not know what the Blood Cult would do.

As the proverb goes, a cornered rat will bite the cat, no one knew what the Blood Cult, now surrounded, will do.

To put it bluntly, if facing death, it wouldn't be surprising for them to commit massacre throughout the city.

No, considering the Blood Cult, they were indeed the type to do so without hesitation.

Thus, the Diancang Sect pledged to shed blood.

Even if it meant facing an unfortunate end, well, not an end? Middle age? Regardless, even if a future awaited them similar to the tragic times Hou Yi faced, the Diancang Sect would willingly shoot forth like arrows, even if they broke.

Truly, was this not chivalry?

\textit{Hmm, suddenly, I feel immense respect.}

\textit{However.}

\textit{If that is chivalry, I cannot be a chivalrous warrior.}

\textit{If this were Hubei instead of Yunnan, and Divine Maiden Sect instead of Diancang Sect had arrived, and I were in Ji Yun Zhenren's position,}

\textit{Even if I die, I would never let Divine Maiden Sect charge.}

Qing felt the same for the Diancang Sect.

In an instant, the warriors of the Diancang Sect stood like arrows and began to unleash their auras.

"Tonight, we will draw our bows. Prepare yourselves."

Ji Yun Zhenren turned with a hidden smile, and Qing hastily followed behind.

"Um, Elder, I have something to say."

"Are you also planning to suggest we wait for support from Wulin Alliance?"

"Well, it's just that-"

"I appreciate your concerns, despite not being a matter of your sect. Hhowever, even so, I cannot change my mind. This is also for the sake of our Diancang. It would be best if we could wait for support and nothing happened. But what will happen if the vile things of the Blood Cult unleash a massacre?"

"No, it's not like that-"

"Sometimes, there are times when we must protect our souls and spirits even if it means shedding blood. If we turn a blind eye to the calamities we could prevent for our safety, then Diancang will no longer be able to claim to be the descendants of Hou Yi."

"Elder, just let me-"

"That would be a great sin, both to the disciples of Diancang and to the future heirs who will carry on the greatest pillars of our sect. Didn't I, Diancang, and our orthodox warriors train in martial arts to be worthy of that future?"

Splendid words kept cutting off Qing's attempts to speak.

Subtly, the Diancang Sect had suddenly become the greatest pillar of the orthodox sect.

"No, what I mean is-"

"And there's no need to worry so much. Certainly, I wouldn't push my disciples into danger, would I? If I go in first and smash everything, I can surely break the formation. Even if it doesn't work, I intend to dismantle at least some of the traps and mechanisms."

Certainly, it doesn't seem like Ji Yun Zhenren intends to push his disciples straight into the flames, but rather seems to want to take on the risk himself.

"Yes, I am embarrassed to make such a request to fellow Daoist, or rather a junior, but could you keep an eye on the disciples of our Diancang? If you are watching them, I can feel a bit more at ease."

It was as if Qing was unable to speak.

Qing quickly brought up the main point.

"Cannon!"

"Huh? Cannon? Why suddenly a cannon? Could it be that the Blood Cult even uses cannons?"

"No, Elder, we're the one who's going to shoot. The Blood Cult is not just our Wulin's enemy. When I explained the situation to the magistrate and command post, they readily accepted."

"The magistrate said they would fire a cannon?"

"Yes. Since the Blood Cult might come out, they will block the main routes and deal with them. Oh, and we borrowed the heavy artillery."

At this, Ji Yun's eyebrows twitched.

Qing felt a bit tense.

\textit{Hmm, as expected, I'll get scolded for reasons like not crossing the boundaries of the government. However, wouldn't it be safer if no one got hurt?}

Then, Ji Yun's angry voice flowed out.

"No, if such a good method existed, you should have revealed it sooner. Why only bring it out now? I wouldn't have to spend days persuading and worrying. All this grand talk would have been for nothing."

"Well, I don't know if it would work or not. And if you step forward, there might be problems."

Sighing heavily, Ji Yun appeared to be reconsidering going back on his declaration.

\textit{After all, he had posited that we should all shed blood so nobly and dramatically, hmm, right.}

Qing had insisted on living as a martial artist, and that she would live as Heavenly Blossom Sword, not as Princess Yuansui.

While that sort of theme thickens, she also being thick-skinned and exploit the power she obtained as a princess.

The image of the greatest martial artist in the Diancang Sect seeking cooperation from the magistrate must be strong enough to be a significant representation.

Whichever side bows to the other would become an awkward situation for both.

\textit{However, hmm, as the speech were eloquent, it seems that he considered this for several days.}

\textit{No wonder it seems like he were hiding something when I come visit after feeding the Blood Cult.}