\chapter{Inspector's Method (8)}

'Just seeing you eat makes me full.'

This describes the phenomenon where witnessing a loved one eating delicious food satisfies one's mental gratification.

Sometimes, the reverse may also hold true.

Of course, it would be more accurate to express that the Lieutenant drinks rather than eats.

Well, what's the difference between eating and drinking? If you chew, it's eating, and if you swallow without chewing, it's drinking?

It goes in through the mouth, so isn't it all the same? Is there really a need to strictly differentiate between eating and drinking?

The Lieutenant's eyelids fluttered.

This was about the extent of the Lieutenant's responses.

He couldn't even turn his neck because Ji Yun embedded chopsticks in his nape, and he couldn't speak beacuse Qing made a hole in his windpipe.

Thus, the meal occurs in a very peculiar silence.

Originally, there would be a significant flaw in such forced meals, as the process of opening the esophagus could lead to suffocation.

However, just piercing a hole in the windpipe solves everything, so there were no problems at all.

Once the viewing experience comes to an end with a rather enjoyable dining time.

"Well, esteemed scion of the Blood Cult, do you not wish to talk? If you want to say something, like you wish to abandon the Blood Cult and seek the light, raise your hand."

Qing looked down at the Lieutenant.

Anger-filled eyes gaze back up at Qing.

Though it seems there's much to say, the Lieutenant did not raise his hand, hinting perhaps that even though there's much to be said, he chose not to voice it.

Of course, that wasn't the case.

"Ah, right. You can't raise your hand."

Since his neck was pierced, he was in a state of full paralysis.

"Then, um, if you have something to say, try to blink your eyes vigorously instead."

Yet still, the Blood Cult scion glared fiercely.

Qing clicked her tongue and pulled the Lieutenant's collar up to cover his neck, pouring water over it with a gurgling sound.

The structure meant that the water-soaked fabric obstructed the air passage in his throat.

"Kill me, just kill me."

A voice strained and sounding metallic flowed out, the tone of one with an almost hoarse throat.

It seemed that the covered cloth allowed some airflow through, but there's no need to mind the voice, so it was what it is.

Qing exaggeratedly extended her arms.

"Ah, do you want to die? Is that such a hard life you wish to end? Well then, here's a wonderful benefit for you! If you spill all the information you know right now, I can grant you a merciful death! Yes, without pain, straight to the end! Isn't that amazing?"

"It's useless. Stop with your tricks and just kill me."

"Hey, why such a sad response? You will suffer every foul ordeal, living a long, miserable life, and only then will you die alone in despair? Ah, this is the true meaning of living long in sickness."

The notion of living long in sickness was a sickly curse.

"You vicious girl, you hypocrites call yourself righteous, only put on a façade in front of people, but what you do behind their backs is no different than a Demonic Adept—"

"Demonic Adept? Where would you find a kind Demonic Adept like me? I'm trying to send wicked people to hell as late as possible, you know?"

"Wicked? Ha, who do you call wicked people? We merely aim to liberate those oppressed by you ruthless, sordid scum of Zhongyuan. Who exactly is truly wicked and who will fall into hell?"

Well, that's the logic of the Blood Cult scum.

At that, Qing beamed a wide smile.

"Then why did you kill innocent waiters and chefs? Were those people also the opressors? Or were they the oppressed?"

"……."

The dish was the chef's handiwork, but it had poison in it.

He didn't voluntarily mix in the poison, someone must have coerced him into doing so. So presumably, if he wishes not to die, that's that?

And then it was a swift cut.

Before they reached the chef, the waiter must have intervened, so the waiter also received the cut.

However, they were people who didn't need to die at all.

Here, it was right in frontyard of Five Poisons Sect, and since he wore the Five Poisons Sect uniform, they could have just shut their mouths without being needed to told.

"Thinking about it, I'm getting a bit angry. Hmm, I think I'll need to pull out a few teeth. After all, you won't have any use for them for the rest of your life, right?"

"Wait a minute—"

Qing has now obtained four front teeth from the Blood Cult scion!

With the front teeth gone, he somehow appeared more innocent, not at all resembling a Blood Cult member.

Qing doesn't know much about teeth, but she vaguely remembered a story from somewhere where someone died after having all their molars pulled out.

Since she still had plenty of time to head over to the Diancang Sect's Absolute Sword Wall after finishing business here, she could slowly pull them out.

With that, today's interrogation ended.

There wasn't much of a result, but it was quite entertaining.

When she stepped outside, the Jong brothers were seated awkwardly, their legs shaking.

While bending their knees yet straightening their backs, they were directing their spines toward the sky, arms hanging parallel to their thighs.

It was a lower body strengthening method from Zhongyuan, called Horse Stance.

Surprisingly, the Jong brothers' talents were rather commendable.

At this point, they appeared to have talents worthy of being picked up on the street even without Qing's request.

"How is it? Shouldn't he opened his mouths a bit?"

"No. He asked for me to kill him, so I only pulled out his front teeth. It was quite funny, but you know, he wouldn't need his teeth anyway."

"Thinking about that now, if all the teeth were extracted, then there would be no need to bother with gags. If you're going to pull them, why not pull them all out at once?"

"I've heard that pulling too many at once could lead to death. It would be a shame to kill someone after all the effort it took to capture them alive."

It wasn't something to be said in front of the kids.

However, while practicing Horse Stance, you wouldn't be able to hear what others were saying.

With your thigh muscles feeling like they were tearing apart, there's no way you would have the energy to eavesdrop on someone else's conversation.

\textit{Still, it seems like they're gritting their teeth and enduring valiantly, which is quite commendable—}

Suddenly.

Before her thoughts finished, the younger one, Jong Mun-yeok, stood up, trembling, and rushed over, throwing himself against Qing's waist.

"Ugh, Sister, my legs hurt."

"Yes, yes, you shouldn't overdo it."

What can a little kid do?

For a nine-year-old this year, even practicing a that way might feel like receiving some punishment.

\textit{Jong Mun-woo seemed quite desperate; indeed, the child appeared much younger than anticipated.}

\textit{At fifteen, he is slightly late to embark on a journey of martial arts, so he should work hard.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At the time when the teeth collected by Qing reached the first small molar from the Lieutenant's canines.

The scouts of the Blood Cult's first elite unit had also completed the preparations for defense of the manor.

The three elements of defense for the manor were as follows:

A wall, formations, and traps.

In this regard, the Five Poisons Sect manor had a significant advantage.

The fortress walls built high in one go had an impressive radiance like a tall city wall.

The formations that Zhang Chaeyang had honed as a hobby had reached a masterful level, simply beyond the realm of mere pastime.

In reality, it's easy to say that it's just a hobby, yet because Zhang Chaeyang had some mental issues, his hobbies had turned to poison and battle formations; every moment of his life was dedicated to those interests, save for when he was eating, sleeping, or relieving himself.

Finally, for traps, poison was essential.

Physical traps might typically be avoided or withstood by martial artists due to their physical abilities; thus, it's the consensus that when preparing traps against martial artists, poison remains of utmost importance.

And the first elite unit specializes in handling poisons.

Even without that, the legacy of Five Poisons Sect had left many poisons thoroughly stocked in the warehouse, so they were truly overflowing with it.

In such an environment, Zhang Chaeyang squeezed all his abilities to finish what he crafted.

It was the moment when another exceedingly dreadful lethal formation came to birth.

Namely, Absolute Extermination, Immortal Extermination, Seongyeongmyeoljin!

With aspirations to kill even Buddhas and immortals and obliterate the world, even the ambition of killing eternally was wrapped within such a horrifying name.

Even if it wasn't merely an ambition, it was a dreadful name.

Zhang Chaeyang always came up with names like this.

"Hehe, even if Master arrives, hhh, it will certainly be a challenge, a challenge."

Zhang Chaeyang does not lie.

Even if Poison Demon returned, it would indeed be a great deal of trouble wrapped up in the formation.

When the Master was very much lost, he hoped to unseal it just as a surprise; perhaps he would get some praise for it?

This was the reason for Zhang Chaeyang's chuckling laughter.

You might question where there would be a master willing to praise a debauched disciple created merely to make someone lost in the formations, but it could be said it was the fault of Poison Demon, who raised an oversized child with boundless positivity.

"Is this truly alright? I'm not very knowledgeable about formations, but…"

"Then, of course, don't say anything. Not knowing, not knowing, I'm just messing around, hehehe."

In fact, the absolute formation would be challenging to rate by any true formation masters.

After all, it was a formation that entirely lacked entry points.

The reason formations were complicated and difficult was that they must be an atrocious and perilous space for the enemies while remaining safe for oneself and one's allies.

But if there were no entry points whatsoever?

That would mean that once you go in, there would be no method to come out, regardless of friend or foe.

Especially in a defensive situation like this, it was especially so.

He had gathered everyone into the core structure of Five Poisons Sect compound and set the formation around it; thus, it would tend to trap both enemies and allies within that perilous formation.

Of course, he had positioned the central structure in Five Poisons Sect main hall, so it could be dismantled whenever needed.

This was precisely the part that his subordinate was worried about.

"Then, we also would be isolated…"

"After all, if the Flashing Sword of Diancang Sect shows up, we can't withstand it."

It was the blind spot or weakness of the formation.

If they were to break through with sheer force, then inevitably the components constituting the formations would get damaged and eventually break down.

Before that, the formation would either kill the martial artists or, before the martial artist met their death, would tear down the apparatus.

However, if a skilled formation master, or someone at the level of Profound Realm decides to destroy, it'd be turned into total ruin in an instant.

"Nonetheless, even if the Flashing Sword comes, when they break the formation, they will already be poisoned, so we must all combine our strengths and fight. Then, we might win. Could we? Is it possible to win?"

"We will surely overcome it."

At that, the poison glimmered anew in the eyes of his subordinate.

The formation itself was not a bad one.

Generally, in the old sects, it would be prudent to stock up considerably on provisions, and since a well was present, they could endure for a long time.

Moreover, no matter how late it was, Poison Demon would return within a month.

If, prior to that, the Orthodox guys invade?

If the Lieutenant claims that without the Flashing Sword, it would provide an opportunity to decimate the elite of Diancang Sect, and if the Flashing Sword does show up, it could still inflict meaningful damage.

Revenge would be carried out by Posion Demon and the Blood Cult comrades, and afterward, the death would not be a mere death but would remain a noble resistance of which to stake one's life.

\textit{Still, what is this ominous feeling?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The magistrate's waist bent like a bow.

Not backwards, but forwards.

Her head was almost about to touch the ground, so one might say it resembled Five Points Prostrate.

Of course, he couldn't truly do Five Points Prostrate.

Bowing carelessly would mean charges of treason.

"Hehehe, to be graced with your presence, what an honor of three lifetimes it is."

The magistrate's ignorant laughter was part of a sort of etiquette.

Originally, it was a survival tactic for eunuchs to hide their masculinity before the Emperor to be perceived as harmless figures.

As such, it had now become an act of submission displayed by the officials in front of their superiors.

It was essentially the same as a dog exposing its belly before its owner.

To package it positively, it could be termed as an act of lowering oneself humorously to elevate the dignity of the other.

Moreover, the Inspector was someone of considerable status.

She was one of the highest powers capable of denigrating a provincial lord typically referred to as Magistrate, transforming him into merely some petty, lowlife figure.

"Hey, that's too excessive to say three lifetimes."

"Then, I shall say it's the glory of this lifetime. Hehe. Madam seems to want to hide her precious self, and so last time, I dared not treat you with a proper formality…"

"Oh, no need to worry about that. Sure, the beggars are rather wild, but it seems the local affairs are not bad, so Magistrate must be managing well."

"Hehehe, you flatter me."

The magistrate took a deep breath of relief inwardly.

\textit{It didn't seem there is any issue that warranted a visit, then perhaps she come to appreciate my sincerity.}

Sincerity, or in other words, a bribe.

Yet, finding himself in the position of having to give a bribe, the magistrate's spirits was lifted instead.

After all, when would he get another opportunity like this to offer respect to an Inspector face-to-face in this backwoods?

"Um, then, I should offer some tea for you. As we've received some exquisite aged Pu-erh, may I step away briefly to personally prepare it…?"

In this context, the important part was 'exquisite' and 'personally prepared.'

In managerial language, it meant 'Please wait, I will bring you very precious sincerity.'

However, the Inspector shook her head.

"No, I came to ask Magistrate for a favor, so I cannot impose such labor on you."

A favor.

This word sounded different in the ears of officials; it transformed into the word for 'order' when it entered their ears.

Thus, the Magistrate lowered his voice.

"Whatever it is, you may speak freely. If it's something within my power, I will assist in any way I can. However, regarding a favor…?"

With that, the Inspector also lowered her voice.

"Magistrate, I'm truly sorry to ask for such a favor, but could I borrow a cannon for a moment?"
