\chapter{Inspector's Method (5)}

At this point, Qing quietly chimed in.

"Now, let's stop. It must be quite hard to suppress the poison, isn't it?"

The reason it was a question was because Qing didn't know.

Well, she heard that one could do this and that with their Inner Qi, but surely one had to have experience suppressing poison.

She would rather not lie, even if she might deceive somewhat.

There's no particular reason to adhere to this, yet somehow it just feels wrong to cheat, it's more the feeling of not wanting to do so.

\textit{Hmm, why? Is it because I'm the lie itself? No, let's not think about it. I almost fell into a funk for the first time in a while.}

Fortunately, there's a perfect distraction right in front of him.

"Anyway, let's stop the chit-chat. If we keep talking, we might really get poisoned."

"What? You lot were already poisoned! And it's you guys who are the ones talking!!"

"Anyway. Does it really matter? So, if you have something prepared, stop dragging your feet and show it quickly. You're not planning to kill us right away, were you? So, what was it?"

"……Be careful with your words. I could very well kill you all right now."

The Lieutenant growled.

Indeed, he had something prepared.

But now that he was being pressed, he felt a sense of defeat, this wasn't the atmosphere he wanted.

"No, I'm being careful with my words. How else am I to be careful here? Should I speak even more formal? Ah, oh esteemed Blood Cult Waiter! May I gently inquire about the plans you have prepared for us?"

"Speak even more formal? If we're doing this, should we not go all out? Aren't you surprisingly petty?"

"Hey, Elder, if you elevate it to that level, it would be treason, wouldn't it? This isn't something to joke about."

"Well, yes. That's true. But if so, how do I answer? Should I say, May I ask? So what's the answer? Yes, then can I ask? Yes, can I? Should I say can I ask once more…"

It was a horrifying sight, two mouths spewing out terror.

The Lieutenant yelled sharply.

"You bastards! Do you want to die!?"

"Of course not. Is there anyone in the world who wants to die?"

"I can't say no. There must be people who truly want to die."

"But Elder, those people actually, I believe, fervently wish for hope to live, that's all. They just genuinely believe in their thoughts as they face extremely tough and difficult situations."

"Oh, how wise and fitting. I really wouldn't have expected that from you; surprisingly, wonderfully deep in cultivation? I've heard that even a stray dog might have something to teach, and I truly am impressed."

"What's this? Is that a compliment? Is it really a compliment? Although Confucius said there was something to learn even from a lowly person, saying it about a dog seems a bit off. It doesn't feel quite right."

"Do you think Confucius's personality was just an ordinary one? If that wasn't the case, he would have said it like that. Since it's awkward for his disciples to wrote it down, this saying would have been refined."

Bam!

The sound of a table being slammed down.

Once again, it was the Lieutenant's extreme measure to cut off the flowing conversation.

Of course, it was also full of personal rage.

"Enough! Hehe, you bastards look like you get along quite well, but let's see how long that lasts. Hehe."

Qing and Ji Yun thought simultaneously.

\textit{He's forcing that laugh.}

"The Blood Cult, huh? That sounded forced just now, right? Of course, it's not a bad attitude to think that laughter brings fortune, but somehow it feels pitiable. To think that in my life I would feel pity for a vile creature of the Blood Cult. It's surprising."

Ji Yun didn't just thought abou itt, he was also saying this aloud.

With that, Qing felt an inexplicable feeling of defeat.

\textit{Ah, I'm still lacking by a long shot. I need to strive harder…….}

And then, a sense of pride surged.

\textit{Even if I fall behind in martial arts, I can't possibly lose in battle of wits.}

That's an intangible poison recognized by Tang Family, so it shouldn't be defeated in battle of words, for the honor of the Tang Family that guaranteed it.

If they heard, they would feel wronged and bewildered, but they did say it was an invisible poison.

"Shut up! You bastard dog, don't look down on people! Let's see how long you can keep that calm look, look, here, I have the antidote."

The Lieutenant slapped a pill down on the messy table.

Then placed a jade bottle next to it.

"This was called 'Dan-ae Jeol-yeon', a deadly poison. Of course, it can't be compared to Myeolseonjidok, but still, 'Dan-ae Jeol-yeon' is a blood poison, making it tricky to suppress. That is to say, no matter how skilled you are, if you were poisoned by Myeolseonjidok and drink this, you will never survive. And this—"

"Wait. I have a question. No matter how skilled you say, but what if it's a master of Hyun-gyeong?"

"Well, it would take a long time to detox, but a master of Hyun-gyeong isn't common, and no, what the— shut up! I'll just tear your mouth off!"

"Geez, why treat just me like that?"

"Isn't it because you seem easy to deal with?"

"No, Elder, that's not how it should be. In Wulin, they say to be cautious of the elderly, children, women, and beggars. They can't just take me lightly."

"How would a vile creature of the Blood Cult know such things? That's why, to a person, learning is important—"

"Dammit! Just shut up!! I might just kill you! When I give the chance, be quiet! Please! Huh!? Just be quiet!! Did I ask for anything grand!! Shut up! Please! Shut upppp!!!"

Finally, the Lieutenant exploded.

Given how long he managed to hold it, one might say he held up quite well.

"Ugh, damn it. Had it not been for Heavenly Blossom Sword."

Qing and Ji Yun faced each other.

Qing conveyed through a look.

-Elder, I don't think we should provoke him any further here.

Ji Yun replied with a knowing glance.

Then opened his lips immediately—

Qing desperately shook her head.

\textit{No, you don't understand at all.}

Seeing this, Ji Yun closed his mouth again.

"Here is the poison and the antidote, and you lot must choose one of them. However, there is only one antidote, so one of you will end up desiring death while suffering terrible pain."

\textit{Ah, so this is what you wanted.}

Qing immediately understood.

\textit{You're saying they'll only save one and now need to kill each other; such a display would unfold before them. And amid that, the villain would smirk in satisfaction.}

\textit{What, wasn't there something similar?}

Yet, it seems like he chose the wrong opponent.

"Give the antidote to Heavenly Blossom Sword."

"No, hey, waiter, bring that poison over here right now. That's mine."

"What do you mean? If you want to die, it's best to go in the order you were born. What's the meaning of living by sacrificing a junior? If you do that, I'll die anyway. Your master would beat me up to death."

"Hey, even if there's an order when coming to this world, surely there's no order in leaving it. You're old, you should only eating good things."

It was a heartwarming scene of each side offering the antidote.

Yet it felt oddly casual, as if they were sharing some precious medicine, when one was immune to poison and the other was a high-level expert who can detoxify.

However, Ji Yun's case was a bit different.

Indeed, a brutal poison was present, and adding another poison would be overwhelming, even for a master of Hyun-gyeong.

In addition, the number of vile creatures of the Blood Cult was four, and one vile beast.

The vile creature was merely a peak in experiences, but the strength of the Blood Cult's 'Poisonous Blood Beast' was, quite literally, a beast flowing with poisonous blood.

No matter how skilled a master of Hyun-gyeong may be, if they fight in this condition, he would have to accept becoming crippled from the aftermath of the poison.

\textit{Yet, coming face to face with the Heavenly Blossom Sword, isn't it worth it to put trust in her?}

\textit{For the sake of the Orthodox Wulin, Heavenly Blossom Sword must be sent away alive and well.}

\textit{Although the worst-case scenario would be losing martial arts or one's life, that child wouldn't betray the kindness of the Diancang; so that would be okay too.}

Ji Yun resolved himself.

Once the Heavenly Blossom Sword took the antidote, he would immediately be dispatched to take care of those vile creatures.

Without even realizing that his neck was already under an azure blade, the Lieutenant let out a heavy sigh.

"I knew this would happen. You Orthodox bastards, ha, filthy beasts. Your kindness is always directed only at yourselves."

With that, the Lieutenant pulled out another elixir from his robe.

Now, there were two antidotes and one deadly poison.

"Here, there's one more antidote. Enough for both of you."

"What is it? Could it be that you're moved? Seeing how we're each willing to give our lives, it's such a nice sight? Waiter, are you perhaps a Spirit or something? If I throw in an axe, would it come back as a golden axe or a silver axe?"

"Is there a story like that in the legends of Zhongyuan? But why would you throw an axe to the Spirit in the first place? However, hmm, was it a wicked intent repaid with virtue? Indeed, it even went as far as to forge an axe out of gold and silver and return it. Though it's the same shape, the intentions behind it were different? A killing sword versus a noble sword. Hmm, that's worth pondering."

\textit{No, can it actually be like that?}

\textit{Well, they say you see what you want to see, and it seems like a master of Hyun-gyeong finds the Dao even in nonsense.}

"Ha. Now that it's settled, you lot, just eat the antidote."

The Lieutenant appeared utterly drained.

Upon that, Qing felt slightly disappointed.

\textit{Hmm, the Elder may be adept at the skills of wit, but he dragged it on endlessly.}

Too much was worse than not enough.

In moderation, you need to understand the characteristics of swearing and cursing, differentiate between them according to the situation, and use them appropriately to control the level of cursing, in order to continue to provoke your enemy.

\textit{Hmm, it seems the elder isn't quite sharp with his tongue as I am.}

And based on the principles of 'Ikjo'—there were times one must say what the adversary longs to hear.

So, right now.

"But, now you offer the antidote? Doesn't that seem suspicious? How do I know what's inside, how do I know if this is medicine or poison?"

At this, the Lieutenant's drooping shoulders regained their posture.

His eyes sparkled once again, and a devious grin returned to his lips.

"Hehe, the antidote is genuine. However, it is merely packed with Gu\footnote{Poison parasite. Qing raise one in her gall}. To suppress poison with poison, it seems that there is no better tool for dealing with you Orthodox garbage than yourselves. Hehe."

Now the Lieutenant was even laughing maliciously, fully revived.

Seeing Ji Yun's lips parted carelessly, Qing urgently blocked with sound transmission. 

-Wait!! Elder!! Hold on a second!!

Then she assumed a hostile expression.

"Hah, I might rather die than eat poison?"

"Well, for you filthy bastards, this is the only way to live. If you don't eat it, I'll just kill you here immediately."

"T-these filthy…!"

"Hehe, do you finally realize your situation?"

The Lieutenant was ridden with confidence, thoroughly uplifted.

"The pain that Gu brings is a hundred times worse than the anything you can imagine. Right now, you might be acting composed as some heroic figures, but do you think there has ever been one among such people who has not begged for mercy, shedding tears while clinging to others' pant legs?"

"That's something you won't know until you try."

Qing put on an indignant expression.

Thus, the Lieutenant's face swelled with triumph.

"Hehe. But you there, why have you gone silent? Seem like you don't feel like flapping your damn mouth?"

"Mm. Living is definitely better than dying. So, is it okay to eat it now?"

"Hehe, you are good at pretending you're calm, but ultimately you're just a bastard desperate to live. Hehe, hahahaha!"

The Lieutenant now burst into genuine joy, a triumphant roar escaping him.

However, one fundamental rule of Zhongyuan applies here.

Gu did not work on Hyun-gyeong.

Before the Gu can even do anything, all of it would be incinerated with the dignified technique of Samadhi True Flame.

Thus, there was a hint of pity in Ji Yun's gaze as he looked at the Lieutenant.
