\chapter{Inspector's Method (1)}

"Are you sure? Can you really just let them go?"

"Thanks to the Benefactor's rescue, both my brother and I are alive, and I know they have suffered as well, so I've put away my grievances."

"Oh, that's quite mature, really quite adult-like, isn't it? They say that despair raises a man; you've turned out to be quite the man!"

At that, Jong Mun-woon gazed at the distance, feeling a bit shy, suddenly puzzled.

"…But was there really such a phrase? My learning iss still short, so it's embarrassing, but who said that?"

"Huh? You don't know? It's from Cao Zilian, Cao Hong. The brother of Cao Cao."

Jong Mun-woon tilted his head, pondering.

'Romance of the Three Kingdoms' was essential culture for the people of Zhongyuan, and it's a rare legal source of entertainment, and even if read for fun, it was treated as a remarkable hobby that counts as reading.

Naturally, Jong Mun-woon had read it a few times.

But could he recall such a phrase?

Moreover,Cao Hong wasn't even Cao Cao's brother!

"Well then, what do you plan to do going forward? If you've given up the inheritance of the family, do you have somewhere to go with your brother?"

"There's my maternal family in Dali, so I plan to go there. However, before that, Benefactor, I have a modest request."

"Hmm? What is it?"

"Umm, if by any chance, you were to take in a disciple…"

It was a difficult request to voice.

Well, of course, being a little kids, they wouldn't be able to escape the allure of sword-fighting, and seeing this esteemed martial artist, it only makes sense they'd want to be his disciple.

"Hmm, I'm sorry, but due to the nature of our sect, I cannot take in male disciples. Our faction is exclusive for women; it's a male-free environment."

Technically, since Qing was an outer disciple of the Divine Maiden Sect, there wouldn't be a problem in taking in a male disciple.

However, having already received treatment as a senior member of the Divine Maiden Sect, she couldn't say she's fine for this reason and treat them as outer disciples at this moment.

"Ah…"

Jong Mun-woon's shoulders drooped slightly.

It was just then.

"Um, Great Expert, if you happen to have time, how about a cup of tea?"

It sounded like the usual flattery, but there was a certain cunning in the voice that did not align with the man's malevolence.

In response, Qing acted as if she recognized.

"Oh, Magistrate! It's a pity, but since the law enforcement office and Wulin were too close, it would be better for this girl to withdraw now."

"But, Great Expert, your insights were excellent, and your discussions were profound; even martial artists struggle to witness the hardships of the common folk during their travels. If you could share what you observed with me, this Yang Mo would wash the ears."

The term 'washing the ears' (洗耳) refers to the act of listening closely, implying that the speaker intends to pay great attention and remember the message conveyed.

"You've already listened to the voices of the common people, and your judgments were just and fair, so I believe there's no need for this girl to add anything further."

The magistrate's face lit up brightly.

To anyone observing, it would appear he had not been rejected at all but had successfully played his cards right.

Indeed, what the Inspector had meant was that she had seen well and was satisfied, so for the magistrate, this sort of litigation was far less important than the indpestor's mood, and had been afraid of it.

"And you, hmm, at such a young age, looking after your younger sibling, how truly beautiful that brotherly love is. If you have nowhere else to go, come visit the law enforcement office. Even though it's government offfice, there's no one with accounting duty, so they still need someone to manage the family estate."

"Oh. Is there such a method?"

Being a manager of a family estate that has relinquished inheritance.

Of course, since the owner was in the law enforcement office, it would feel somewhat like a professional manager, but still, this was commendable.

Moreover,

"Furthermore, I have heard your story, so take a suitable amount of assets with you. How can I send you out empty-handed in this perilous world?"

Or he meant to say to take a decent amount of financial backing with them.

Qing was impressed.

\textit{Despite being a magistrate, he seemed to possess quite a bit of kindness, didn't he?}

This was how high-ranking officials in Zhongyuan exhibit crisis management skills!

The chief inspector bringing in a rescued child would incur no losses, only potential gains.

The secret to making it to the position of magistrate lay was not missing even the minute details.

"Hehe, no, haha, Great Expert, should your heart change, and you wish to share your insights, please do not hesitate to find me. I will take my leave now."

Having established a connection, the magistrate left.

"Well. You still need to gather some money."

"I have given up on the inheritance—"

"Oh no, you can't say that! Is that how your heart feels? Your resolution? Anyway, such decisions cannot be made lightly. How sorrowful iss a person without money? Money should be earned when one has the means to do so!"

Thus, returning to the office, she grabbed a few notes, and since it was the merchant's office, she opened a drawer to find some gold pieces.

No matter how much he relies on his maternal family, he should at least take something or have some emergency money.

After gathering a rough amount of money, Qing carried the smaller Jong Mun-yeok, who had fallen asleep on the office's upper seat, on her back.

"Come on, let's head to the inn, ah. That's right."

"Benefactor? Did you forget something?"

"I'm hungry. I've been feeling peckish since a while ago, and I almost forgot."

Jong Mun-woon tilted his head.

Didn't she have a meal before coming?

He seemed to have eaten quite a lot too!

"Let's go and eat."

\textit{Hmm. What should we eat today?}

In fact, as they're provided food anyway, there isn't really much to worry about, but still, it would be good to have at least one dish that fits her taste.

\textit{Ah, I should've asked for beef to be boiled thoroughly, so tender that it melts in the mouth.}

\textit{Then what would they have today?}

Was there a moment more delightful than heading back to the inn where the food tastes good?

Qing found herself humming without even realizing it.

Jong Mun-woon, too, unconsciously listened closely.

It was a very exotic tone, distinctly different from the music of Zhongyuan, yet the melody was so pleasing that it seemed to stick in the ears.

Indeed, the song Qing hummed were already renowned pieces that had captivated innumerable people in his homeland.

It was just the moment filled with excitement as they entered the inn.

Suddenly, a sharp pain pierced her chest, constricting her breath and sending chills down her spine.

A murderous aura that was dreadfully overwhelming.

It emanated from a figure seated at a table on the first floor, facing away from them.

From the sword leaning against the table, it seemed to be a swordsman.

"Benefactor?"

Qing glanced at Jong Mun-woon.

His puzzled expression seemed to question why.

There was a steady, ragged breath from the chin resting on the shoulder.

This finely honed murderous intent didn't affect Jong Mun-woon or even the sleeping Jong Mun-yeok on her back.

Qing swallowed.

The figure seated with their back to them seemed to fill the vision like a towering mountain.

\textit{He's at least at Late-Stage Harmony Realm.}

\textit{No, even more than that.}

\textit{However, somehow, the Evil Karma? Just seven points?}

\textit{It is likely someone from the Wulin Alliance or perhaps a senior figure from the Orthodox faction.}

Qing hesitantly opened her mouth.

"Um, Elder?"

"Hm. In a situation like this, you should let the children flee first. Why are you addressing me with a pitiful voice like a beggar? You're letting all the steam out."

Their previously overpowering aura vanished as if it had never existed.

It looked like there was an attempt at a test or a mischievous prank.

After all, how could Qing not see the evils of a person?

If a fearsome master exhibited only seven points of wickedness, one wouldn't necessarily feel alarmed.

The middle-aged man raised his arms on the backrest and turned to look at Qing.

\textit{Wow, a handsome middle-aged man!}

One could easily guess that his past was quite extravagant, possessing a gentlemanly appearance reminiscent of Qing's homeland.

"But then, why have two children? Not just the daughter, but also an adopted son? Or is picking up kids your hobby? Hmm? Are they our children?"

The man's gaze softened even further.

\textit{But what did he mean by 'our children'?}

\textit{Did the Jong brothers have another hidden birth secret?}

Looking at Jong Mun-woon, the younger boy couldn't hide his bewildered expression either.

Then the man suddenly laughed in a hearty manner.

"The term 'our children' means the Bai people's children. Though the folks from Zhongyuan might not know well, people around here can tell which ethnicity you belong to at first glance. So I roughly understand the situation. Bai people's offspring? Are they doing terrible things to those kids?"

"Um, did you know?"

"Isn't it obvious? Because of this, we're in quite an uproar. I've tried to send students to block it, but the human sentiments are rather indifferent. It's truly the end of times, the end of times."

The middle-aged man clicked his tongue.

Then, looking at Qing again, his eyes sparkled.

"Then, ho-ho. I heard the news, but you've truly achieved Harmony, haven't you? I thought my seniors were merely teasing their juniors, but wow, excellent! Our children should be like that too. Oh, what was it—"

At this point, Qing had roughly discerned the middle-aged man's identity.

Achieving Harmony referred to achieving the state of harmony, that is, reaching the level of Harmony Realm. Qing had kept the fact of reaching Harmony Realm a secret in the Alliance.

If he had heard the news, it meant he was someone in a position to hear updates within the Alliance.

Given the esteemed level of cultivation considered, he must be the high-ranking expert, Master Ji Yun, Flash Sword of Diancang Sect.

"Ah, right. I suppose this isn't the place for such talk? I ought to speak separately."

"Oh, then, Elder, have you had your meal?"

"What elder? I'm not old enough for you to address me as that. Hm, it's a bit early for meals, but it's certainly better to eat while I can."

However, hmm, despite his dignified demeanor, he was a very easy-going elder.

So they went to the private room.

Without questioning or prying, they ordered a bottle of Baijiu, gulping it down.

With a pleased smile, Ji Yun looked at Qing.

"Indeed, they said next Greatest Under Heave and such, wow, Senior Ximen has picked up a dragon. Yes, I am Ji Yun."

With that came sounds of deep breaths from both sides.

For indeed, Ji Yun of the Flashing Sword was one of the Ten Masters Under Heaven, being the best in Yunnan and also the best of Bai people.

He was a pride of Yunnan and a pride of the Bai people, particularly for those belonging to both communities. He was like a heavenly idol.

"Is it really you, Master Ji Yun?"

"Wow, Flashing Sword! Four-Child Sword Technique!"

"Yep. Hm. These kids—no, you two, stay a bit upstairs. I have important matters to discuss."

The two looked somewhat regretful, but what could they do? They exited for the time being.

"Now, what's going on? What about those kids?"

"Oh, that's it. I happened upon a group of beggars trying to commit terrible acts, so I intervened. The truth is, their father was a dreadful murderer and had two wives; one had passed first, their biological mother."

"……?"

"And the second wife was unfaithful, and the partner was, believe it or not, that sworn brother of his. So…"

"……??"

Qing was not particularly gifted in storytelling.

However, as people grew older, they'd understood that even disjointed tales could provide a semblance of context over time; such was the wisdom of age.

Upon hearing the story, Ji Yun clicked his tongue.

"It's said that this area is infested with Blood Cult; how truly heinous. I wonder if those beggars were merely the lackeys of Blood Cult? Should I have killed that man instead of just checking?"

"Uh? What do you mean?"

"No, along the way, a beggar was trying to stab someone dead in broad daylight. I killed him instantly, and now that I think of it, that couple seemed suspicious as well. They suddenly collapsed, wailing loudly, while saying they wanted to live righteously and sought out heavenly deities, thanking the Buddha and the Primeval Profound Ancestor. They might have been in the know."

"Ugh, that beggar was always a problem."

"Is it merely a matter of calling them beggars for no reason? Thus, looking at this, your news doesn't seem like foolish banter, but it still requires further verification."

And so, Ji Yun asked with a serious expression.

"Is it true that Five Poisons Sect has turned into a den for Blood Cults?"
