\chapter{Inspector's Method (13)}

It was a sound they had never heard before.

It was like dozens of whip cracks tearing through the air sharply.

It felt as if dozens of whips were being swung at the same time, or perhaps it resembled the urgent chirping of thousands of birds, or the sound of mosquitoes passing in a line by my ear.

As the members of the First Poison Squad lifted their heads at the strange yet instinctively piercing sound, they suddenly spotted black dots in the sky.

\textit{One dot, two dots, three? Four? What is it?}

It seemed like the slightly raised dots were coming down, but then they gradually grew more distinct in size.

And in an instant, they fell with a bang!

With a tremendous noise, the roof of the elder's residence ahead exploded with roof tiles flying in all directions.

No, it wasn't just the elder's residence.

With a series of collision sounds, fragments that made up the buildings began to burst into dust and scatter everywhere.

\textit{What in the world is going on?}

\textit{As if a cannonball are coming.}

"Uh…?"

A dumbfounded sound escaped the team member's mouth.

\textit{Cannonball? Shell? Really?}

In that moment, a black iron cannon fell through the door of the elder's residence with a bang.

It looked heavy at first glance.

How high must it have fallen from to bounce up to waist height?

The team member, staring blankly, watched the large iron object approaching in an arc as it came closer.

Felt as if time had stopped, flowing slowly as if it were almost about to halt.

Suddenly, the team member's mouth opened.

"Everyone—"

The word 'evacuate' couldn't come out in time.

………!!!!

With a huge bang, the team member's world began to shake and turn upside down.

The team member was hurled and slammed into the ground.

Like being thrown into an uncontrollable force, as if thousands of blades were pushing them away.

Beeee……!!

The loud tinnitus filled the surroundings.

The team member attempted to rise, but the strength slipped from his supporting hand and he collapsed, trying to move his hands and feet to get up, slipping and floundering on the ground, looking pathetic as he writhed.

Beeee……!!!!

The dry ringing in his ears felt like it would burst his eardrums.

It was as though someone was forcefully blowing a whistle into his ear, creating a loud, fierce noise that inflicted a terrible violence.

"……! ………!"

The face of a colleague was flapping its mouth in front of him.

Before long, a trickle of blood was running down from his forehead, dripping down his chin along the wrinkles around his mouth.

The team member opened his mouth to speak.

'Hey, you're bleeding.'

\textit{Did I say that? Or not? Is it just that the tinnitus was so loud that whether I spoke it out loud or just thought it?}

As he stared blankly, a rough hand gripped his shoulder.

At that moment, a sharp pain surged through him, as if hot metal were being pushed into him, and he came to his senses.

"……Get a hold of yourself……"

Though the voice was still drowned out by the noise, the occasional words that came through and the strong hand pulling him were clear in their meaning.

He had to get out of here immediately.

\textit{But where to? Outside there's surely the formation—}

It was at that moment.

The eaves of the buildings in his line of sight suddenly exploded without any sign or sound.

No, there must have been a sound. It just wasn't heard due to the muffled ears, as if he was submerged, and only the piercing tinnitus hitting his brain.

In that instant, a strong force shoved the team member.

As he fell backwards, he caught a glimpse of the face of the person who pushed him.

Suddenly, time seemed to stretch infinitely.

Number Three of the First Poison Squad was the superior he hated and feared the most.

If you greeted him, he would scoff and say if that was what greeting meant, why don't you do it properly, and would kick you in the shins, and if you accidentally passed by without greeting, he would gather the juniors and kick you in the shins.

Behind him, brilliant light flared up.

In the brilliance stood the terrible face that he had never even dared to look at, slowly covered in shadow.

Then, a pain like breaking his tailbone, yet the team member stared blankly ahead, forgetting even that pain.

It was the figure of Number Three enveloped in flames.

It was the result of being doused by the primitive ancient firebomb, the Hwa-bi-tan, that spreads sticky burning oil all around.

\textit{Why? Didn't that bastard hate me?}

\textit{If I were to die, it would be because I dried up due to the annoyance of that bastard during the operation, a superior I was terrified of.}

\textit{Why did that bastard save me?}

\textit{Was all the harassment until now merely a part of military discipline, just a show for the others without any ill intentions?}

\textit{Or did he come out beacuse as the most senior person present, he saw someone in danger and stepped forward?  But if he knew it was me, would he not savd me, or did he know and still decide to save me?}

\textit{Fuck, does that really matter right now?}

Gritting his teeth, the team member sprang up.

\textit{Water! I need water! A well! The well…!}

The team member dashed out.

The building was breached, burning oil splattered all around, dazzling his eyes, and the earth continued to shake as tremendous explosions followed.

He turned halfway around the leader's office towards the well in the courtyard, frantically drawing up water, hurriedly cutting the rope of the bucket and lumping it onto his back, urging himself to hurry.

The team member splashed water onto Number Three, creating a thick cloud of steam.

But that was all, as Number Three remained limp, just gasping for breath.

The team member tried to lift Number Three.

In that moment, Number Three grabbed the team member's wrist.

'Get lost, you bastard. I'm done for, go leave…!'

Judging by his lip movements, that must have been what he said.

For the first time since joining the First Poison Squad, the team member rebelled against the terrifying superior, Number Three.

The team member draped the fallen Number Three's arm around his neck, rising up to navigate through the now darkening sky, towards the most horrific place.

He didn't know where it was but it was towards somewhere safe, towards the outside.

The roof tiles came crashing down, and the sound of the iron bomb's explosion revealed its presence with every small earthquake, the flames began to spread everywhere, heating up the surroundings like a hot spring, the sky was covered in smoke, and suddenly he saw someone's arms and legs on the ground, hollow eyes staring vacantly…

The number of colleagues following the team member began to increase, one by one.

Some were regaining their senses, while others were just terrified, chasing after the person in front.

Yet still, before this unprecedented disaster, they relied on each other, pulling and pushing each other, slapping faces to bring them back to their senses, moving towards the outside, towards the exit.

It wasn't just the members of the First Poison Squad.

The common people working with them lent a hand. The faithful, yet unarmed soldier, the loyal dog blood family members lifted the patients, and the well-trained beasts led the way.

Fortunately, the formation had lost its efficacy by this point.

The core element forming the formation had been destroyed, buildings were on fire, holes had been made, and pillars had collapsed, many had already crumbled, and the formation had lost strength from the start.

Moreover, many of the traps had been dismantled as well, and what remained were rapidly breaking down and burning away, so there was no way to withstand the bombardment of shells.

Of course, it was impossible to avoid all traps, but even so, the Poisonous Beasts forerunning and leading took the hits, thus the damage to the team members was minimal.

Thus, helping each other to stand as they finally revealed a passage through the smoke that was leading outside.

In everyone's eyes, the joy that shone from relief caused their lips to curl upward slightly, some reddening their eyes, while others seemed to lose strength as they staggered.

Several comrades rushed in to unbolt the door.

Creeeeak, the door leading outside opened wide, allowing escape from this hellish place.

And outside—

"The members of the Blood Cult have emerged!"

Blocking the front path were a series of martial artists.

The familiar and hated uniforms belonged to the Diancang Sect.

"Damn it! Poisonous Beasts, Poisonous Humans, kill them!"

At this, the beasts leapt out on all fours, while the Poisonous Humans, sprang up in zigzag pattern to follow behind.

Then the members of the First Poison Squad exchanged glances, deciding to disperse. 'Let's meet again alive'. And just as they were about to scatter to the left and right—

Boom! A massive roar pierced through, as if thunder had struck right in front, the air quivering from the tremendous noise.

In an instant, a bloodstorm swept in.

The creations of the First Poison Squad that were charging ahead were instantly transformed into a mist of blood.

And the damage didn't stop there.

The team member fell to his knees, trembling, looking down at his own torso.

His body was already dyed bright red, without strength, crumbling, with his dantian breaking and releasing a terrible pain.

\textit{How… how could this happen?}

The team member looked up again.

Amid the martial artists of the Diancang Sect, a massive cannon, still puffing smoke from its mouth, revealed itself.

The Great General Cannon. The strongest weapon of the regular army, radiating thousands upon thousands of metal shards forward, ready to tear through the very fabric of space, revealed its might.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In truth, the Magistrate, while coordinating with the Diancang Sect, had never believed in the justification of needing to clean out the lair of the Blood Cult.

From what the Magistrate knew, the Emperor saw the Wulin as a disease that needed to be eradicated, so perhaps the Inspector, carrying out the Emperor's wishes, was taking this opportunity to establish that justification.

Moreover, the Five Poisons Sect was a sect of those impure Miao barbarians, and those people were spouting terrible things like driving out the Han people and recovering Sichuan.

So even if she were to obliterate it, there would not be much backlash from the Wulin. Rather, far from protest, even the Diancang Sect would mobilize their famous Sun-shooting Sword Technique swordsmen to assist.

So, it was just like the usual power struggles of the central authorities.

That's what he had thought.

Until he saw the monstrous creatures, running on all fours and with their waists bent backward, charging out from the doors of the Five Poisons Sect.

"Th-They are real Blood Cult creatures! Fire! Fire!"

The Magistrate hurriedly urged the soldiers.

And boom!

Originally, magistrates was not a figure who would poke their head into dangerous situation.

In fact, magistrates were characters who did not appear even when there was no danger, a power behind the scenes that existed but did not exist, and a governing philosophy that ruled but did not rule.

But even that stiff commander is forced to obey the orders of the Inspector like a new recruit, so how could he stay in a corner to protect himself?

Such a person had no right to hold office in Zhongyuan, let alone take a high-ranking post.

Thus, being so close to the Inspector, Jihyun had no choice but to be startled when facing the monstrous creatures of the Blood Cult that were emerging in real-time.

At this, Qing, who had been listening from the side, tilted her head.

\textit{Real Blood Cult people?}

\textit{Are there fake Blood Cult members too?}

\textit{Anyway, cannons volley is enough to take care of those monsters? Honestly, I'm not quite sure if those monsters were dangerous or not, since I'm poison-resistant, and so I can't gauge the poison monsters well.}

\textit{In any case, the four cannons of the Great General Cannons were enough to sweep away the remnants of the Blood Cult that had emerged through the rain of shells. }

\textit{Um, I didn't notice it back in Sichuan, but seeing it like this… it's terrifyingly horrific…}

"Load quickly! Load the cannons! Hurry! We don't know when those traitors might unleash their monsters!"

Hearing the Magistrate's urging of the artillerymen, Qing looked at the Five Poisons Sect engulfed in flames.

While the destruction of the Blood Cult's lair was a refreshing sight, it was chilling in another sense.

What if it were the Divine Maiden Sects instead of the Five Poisons Sect?

In reality, when one reaches the level of Hwa-kyung, and becomes proficient with the arts of self-defense, the fear of shell blasts would naturally diminish.

If it wasn't something exploding right in front of you, mere fast-moving fragments were not threatening to a master of Hwa-kyung.

When one feels a shell fall, simply raising one's Qi to protect oneself and departing swiftly would suffice.

Nevertheless, masters of Hwa-kyung were not just some common weed that you pull out from the ground.

Even in the Nine Sects and Ten Great Families, how many genuine experts can be found in a single sect?

What of the remaining disciples other than Huakyung?

What about the shrines housing the tablets of their ancestors?

The documents recording the history of the sect and the manuals that organized and studied their martial arts techniques?

If they were to unleash such a bombardment, the individual masters might survive, but the sect itself would be as good as destoyed.

The defenses a sect had evolved over generations were fundamentally created to stand against other sects.

Naturally, how could there be any way to withstand a rain of bombardments right from the start?

The best they could do was prepare shelters underground, like the Tang Family did during the Sichuan incident.

\textit{Wait, shelters.}

\textit{Surely, the Five Poisons Sect would have prepared such, right?}

\textit{I really should taste the upcoming slaughter. Not that I'm craving for blood, but since I am immune to poison, I'd slice them thoroughly so the members of the Diancang Sect wouldn't be at risk.}

Thus, Qing fiddled with the hilt of her sword, grinning.

However, what Qing did not expect was that the Five Poisons Sect did not reveal their most critical secrets even while allowing the Blood Cult to take over.

Therefore, the Blood Cult nest was completely destroyed.