\chapter{Inspector's Method (2)}

The Blood Cult was very closed in nature.

Moreover, it was excessively cautious, which could also be described as being very fearful.

This was because they have been oppressed for a long time.

Of course, when one thinks of the various atrocities the Blood Cult members have committed to survive all this time, they were certainly deserving of such oppression.

For this reason, not only the righteous factions and the law enforcement officials, but even the unorthodox sects, and even the Demonic Cult, would tremble at the mention of the Blood Cult and seek to eradicate it.

In order to continue surviving like cockroaches amid such persecution, the organizational culture had to become closed and cautious.

Furthermore, among the various sub-factions of the Blood Cult, some were even more severe, particularly those less capable in combat.

The Blood Mist Corps was no exception.

To say it simply, the Demonic Poison was strong, not that the Blood Mist Corps was strong.

Just a few years ago, after the complete extinction of the Blood Mist Corps' subordinate force in Sichuan, they had lost many (involuntary) collaborators in Wulin, greatly diminishing their influence.

Thus, even Zhang Chuiliang, a disciple of the Demonic Poison and the chief captain of the Blood Mist Corps, moved very cautiously.

In fact, Zhang Chuiliang had always been a person filled with a significant amount of fear.

"Chief! We've suffered at the hands of Jahaeng and Uyeol. I, I will tear the Midwesterners apart! Just give the order, Chief! I will make that wretch wish she were dead!"

"Um…"

"Chief? It's not 'um', right now we need revenge—"

"I heard, you know? What if Master finds out and gets angry? Hah. That's why I told you not to send them out. We lost precious people trying to create unnecessary local collaborators. This was entirely your responsibility, Deputy Chief."

"Chief! This was not the time to discuss responsibility—"

"Enough. Let's not touch it unnecessarily. If that girl was indeed an old acquaintance of the Blood Mist Master, she might be known among the Midwesterners. If we budge, what if the identity of our school gets exposed? Master isn't here."

"Chief! Jahaeng and Uyeol were dead! Those bastards, one of our elite members was dead!"

"I, I'm upset and frustrated too! Jahaeng and Uyeol treated me so well."

His childish tone was quite childish for a middle-aged man, with words spoken in a rather awkward manner.

However, thanks to his genius mind regarding poisons, he had become a top disciple of the Demonic Poison.

"Then what should we do? Can we take revenge without using poison? If we use poison? If the Blood Mist Master was a well-known woman, then if she gets poisoned right in front of the Blood Mist Corps, even those Midwesterners will know who the perpetrator is. Should we withdraw our revenge then? But, Master had said to guard well."

"Chief! Jahaeng and Uyeol were dead! One of our elite was dead!"

"I, I'm also sad and angry? Jahaeng and Uyeol played with me so well."

For someone of his age, that childish way of speaking and awkward pronunciation felt quite young.

Yet somewhere along the line, his genius regarding poisons made him one of the top disciples in the Demonic Poison.

"But then, what should we do? Can we take revenge without using poison? If we use poison, if that girl was a master, what if she doesn't die from the poison? It's truly frightening."

"Then I will take matters into my own hands. Instead, how about using the Exterminating Poison?"

"……Not the Exterminating Poison. It's the Ultimate Evil Poison of the Ancient World."

The Deputy Chief's eyebrows twitched.

The name, Ultimate Evil Poison of the Ancient World, was something even a ten-year-old child would hesitate to invoke.

However, it was not too hard to remember.

"Cough, then how about we use the Ultimate Evil Poison of the Ancient World to test this?"

"Still. Still. Umm, should we? You're trying to take direct action, right? It's still dangerous, so take that Poison Master with you. If it gets dangerous, you can just leave them behind and escape."

At this, the Deputy Chief smiled warmly.

Though he was often infuriating and disgusting, he could not help but soften up at times like this.

He wasn't necessarily lacking, just slightly short of something.

"Yes, if it's dangerous, I will somehow escape."

With that, the Deputy Chief bent his head and walked out of the office of the Blood Mist Corps.

Gone was the warm smile; he was now the Deputy Chief, who had lost subordinates, and instead took on the actual role of a leader having to deal with the hatred, which only deepened his expression.

And, in truth, he had confidence.

The creator of the Exterminating Poison, Zhang Chuiliang, had—though he may not be trustworthy—his talent with poisons was highly regarded by the Demonic Poison as being even more potential than his own.

Thus, the Exterminating Poison, of which the Demonic Poison spoke with praise, "Truly, a poison that can even kill a celestial being has been born!"

And thus, the long and ridiculous name that simply cannot be refused.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"I'm almost certain."

In response to Ji Yun's question about whether Five Poisons Sect has turned into a den of the Blood Cult, Qing answered.

Yet, Ji Yun shook his head.

"Almost isn't enough. You must be certain."

"Umm, then, I am certain."

Still, Ji Yun shook his head.

"Even being certain is insufficient. Has a shot that leaves the bow ever returned?"

"Umm. Never, right?"

"Exactly, and you are holding the bowstring."

The most famous martial arts technique of the Diancang Sect is, of course, the Sun-Shooting Sword Technique, and among the Sun-Shooting Sword Technique, the most powerful last move was the legendary Hou Yi Shooting the Sun\footnote{后羿射日; Hou Yi Sheri} .

Here, Hou Yi refers to a character from Zhongyuan mythology, who, in the past, was said to have destroyed nine suns when there were ten suns that caused the world to be akin to a sauna or an oven, rendering it impossible for people to live.

Once he could no longer withstand the parching heat, he drew his bow and shot at nine suns, leaving only one.

The sword technique inspired by how Hou Yi shot through the suns was none other than the Sun-Shooting Sword Technique.

But if that's the case, shouldn't they have practiced archery? Why wield a sword while claiming to be a descendant of Hou Yi?

Of course, if they had practiced archery, they would have been swept away by the authorities long ago.

In any case, perhaps because of this, the Diancang Sect particularly liked to metaphorically present archery.

This was characteristic not only of the Diancang Sect but also of the broader Bai tribe.

"Our Diancang's actions are similar; just as the arrow that has left the bow does not return, so too does the blade drawn by the Diancang never return."

Ji Yun raised his voice determinedly.

"Our main branch intends to completely erase Five Poisons Sect. Thus, for us to draw our blades, it must be a thorough fact that Five Poisons Sect has collaborated with the Blood Cult. Therefore, is your assertion such a fact?"

"Since you mention it, um…"

That sounded very burdensome.

With the Diancang Sect stepping in, it meant that Five Poisons Sect would have to be completely erased from the world, meaning that the decision depended on what she said.

\textit{Still, isn't this a bit cruel?}

\textit{Having finally caught the Blood Cult's tail, and now that they come to help, they say I shouldn't kill them?}

At that, Ji Yun chuckled.

"I'm just saying this for effect. Isn't it magnificent?"

"Huh?"

"So that's why I came here first. From now on, it's a matter of finding out. Yes, I've heard the general situation. But initially, it's at the level of saying Five Poisons Sect is connected, not claiming it is a den of Blood Cults, and that is indeed somewhat a weak assertion."

"Ah, that's because… it might be a bit more certain now…"

"Hmm? Have you discovered more in between?"

"Rather than discovered, you could say it's a confession. The Five Poisons Sect's Sect Leader confessed it himself, you know? A commotion broke out in Sichuan before. They lost all elite disciples back then, and because of that they decided to collaborate with the Blood Cult for revenge against Sichuan's Tang family."

Ji Yun's expression became slightly perplexed.

"The Five Poisons Sect's Sect Leader confessed in his own words? When? How?"

"Um, well, you know, when he thought he had won, he started blabbering without even being asked."

"Ah. Hahaha, that's right! Yes, there are indeed such people. I understand what kind of mindset it might be, but it's truly foolish, isn't it?"

Ji Yun's eyes widened.

There were indeed people like that.

Why? To make those who were on the brink of death even more miserable; simply killing them isn't satisfying, so they blabber away their actions and future plans.

The Five Poisons Sect's Sect Leader spoke of his own plot.

Why? Because he thought he'd won.

Being victorious wasn't enough, he wanted to further grieve by spilling his secrets.

And then, right before him was the Heavenly Blossom Sword.

Would he kindly informed her of the fact they had allied with the Blood Cult, before suddenly changing his mind, 'Hey, this remains a secret, okay?' and just let her live?

"You defeated the The Five Poisons Sect's Sect Leader?"

"They said he has became a Poison Human, and thus he ended up vomiting blood and dying alone."

"Ah, so, hmm, was this the extent of it? Really?"

"Yes?"

Ji Yun's expression became serious.

"Heavenly Blossom Sword, by any chance, your adopted daughter, could you leave her with Diancang? I will take her as my direct disciple and nurture her well."

"Huh? Ciyu? Although she is my daughter, frankly, Ciyu isn't particularly talented."

"No, at a glance, she carries overwhelming killing intent in her eyes. Since the Heavenly Killing Star is right before me, I wonder if your daughter is the Earthly Killing Star of the current generation?"

"Ah."

"Oh, Godmother sent a message, telling me that you were born under that star. It seems she's being preemptive because I can sometimes leap out like a hasty arrow."

"Ah…"

"Seeing this, it certainly becomes clear. The best disciple must be of the Heavenly Killing Star, or if that's not possible, they must born under the Earthly Killing Star. After all, arrows are meant to kill enemies, and so are martial arts. Therefore, killing intent is the crown jewel of innate talent"

Yet, it was somehow a troubling thought.

"But, isn't it said that it is terribly dangerous? That if the Heavenly Killing Star arose, children born that year would all have to die?"

"I too believed that such a sacrifice would be appropriate to avert the great catastrophe upon the world. But seeing you now, it seems not so. With such an excellent swordsman like you here, well, originally, isn't it true that people are meant to be cultivated through learning?"

"Well, it is a bit more serious than you thought. I really want to kill villains whenever I see them, and peel their skin off and sprinkle salt on them."

"Right, I have those moments too. Like when the Dali royal family tried to force a marriage, or when I saw those guys talking about Bai Pox and all. I often think about those things. The important thing is that neither you nor I were like that. In any case, we endured it, didn't we?"

\textit{Hmm, you also sometimes have such thoughts, huh?}

"Furthermore, looking at you now, I can see it clearly. It's not about moral governance but rather law governance; truly, it is overwhelming force that makes people humane—"

"Huh. Wait a minute. Why are you suddenly jumping to that conclusion?"

"Hmm? Isn't that right? With her nature, Godmother wouldn't teach you by using nice words, right? You must've learned how to restrain your true nature while being beaten so terribly, hadn't you?"

He sometimes had moments of impulsive bursts, as he was often heard to say.

This was practicality in action, demonstrating a consistency between words and deeds.

Still, the notion that you were beaten growing up sounds more like just that.

"No, that was…true. I mean, it's true."

Qing felt a sense of grievance.

\textit{No, though Master did unleash nuclear bombardments from time to time, well, could it be at least called as something akin to the rod of love? This certainly makes it sound as though I had been tortured severely.}

\textit{No, it was true, but how to put it—affection?}

\textit{…Umm, it must be affection, right?}

Still, one thing was certain: she was absolutely not to leave Ciyu with someone like this elder!

"Anyway, Ciyu isn't the Earthly Killing Star; she was subjected to bad deeds by the Blood Cult, and that's why I took her in."

"Hmm. Such a story. For a young unmarried girl to make a decision to descend is undoubtedly difficult; you truly are the chivalrous one among chivalrous heroes. For someone youthful, you truly have a deep soul, indeed. As expected, a pillar that will lead Wulin in the future!"

Ji Yun's gaze softened further.

But that didn't last long.

"Indeed, this is all part of Godmother's teachings. Hmm, but I couldn't possibly spank such a little girl. Still, it means the Earthly Killing Star must exists out there somewhere; should we take a look at what fresh seeds of Earthly Killing Star might be around? I wish I had a disciple who would be called the world's best talent…"

In truth, Qing was unaware, but there was somewhat of a painful academic tendency surrounding the major sects centered around the Nine Great Sects and Five Great Families.

The Heavenly Blossom Sword had released poison upon an Orthodox sect again!

It was at that moment.

A thought flickered through Qing's mind.

"Ah, chicken instead of a pheasant\footnote{Korean idioms, 꿩 대신 닭, roughly meaning 'substituting with similar items'}…Sorry, but what do you think about the madness? A disease that leads to slaughter."
