\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (3)}

Reasonable malice strikes the Blood Cult!

The blood sect technicians who had been waiting at the third entrance of the second Daedonghyeol passage suddenly stood up from their seats.

Of course, a group of people with knives appeared in the engine room, so it was only natural to be on guard.

"Who, who are you!"

Then Qing answered.

Frowning, as if in disbelief.

"What are you doing? You don't know who I am? You little brats. Hey, what's your name?"

"Uh, why was your name…?"

"Why, why? I'm asking the old man, Guisan Manbak, if there's a fool who can't tell his upside down, wouldn't it be better to just take his brain out and turn him into a zombie? Why?"

"omg."

"Okay. Pick one. Do you prefer a zombie or a blood demon? No, do you need eyes that can't recognize your precious body? Should I pluck out your eyes too?"

"No, it's not!"

"So what's your name?"

"Uh, that. There. Hmm."

The nameless blood cult technician rolled his eyes.

Judging by the reaction, it seems like you are a high-ranking person.

Aren't all the high ranking members of the original blood sect people who have gone astray somewhere?

I thought to myself, "Fuck, I messed up and got screwed," and a cold sweat broke out all over my body.

He was a technician who couldn't do anything, like a guard at the main gate who greeted him with 'Oh, it's me.'

As expected, this was how people live.

Then Qing's expression softened and he chuckled.

"You rascal. I was just kidding. So, how's the grand plan going? Anything unusual?"

"No! But, uh, uh, your Majesty……"

The Blood Cult technician hesitated.

Then, the woman behind him, who was short but unnaturally large in the middle, let out a beastly roar!

"Kyaaaaak!"

"Eek!"

"No! You little punk! Stop! Sit down!"

"Kyaaaaak!"

"No. Stop. I'm not eating. It's a pain."

"Kyaaaa……"

Then, a short woman crouched down with her face flushed red.

Hey, was this really an imitation of a zombie?

Murong Zhuxi wanted to die.

When he dies, the cause of death will be something like, "I can't bear the immense shame and I'll die of shame."

Of course, it was Murong Zhuxi's fault for immediately raising her hand and claiming to be a zombie impersonator who felt like a pet following its owner.

"Oh, my pet was a bit spoiled. Sorry. But what did you just say?"

"No, it's not!"

"Yeah, yeah. Oh. Yeah, I heard you can see something pretty interesting if you come here. Show me right now."

"yes?"

"Something interesting. Show me."

The Blood Cult technician completely abandoned his doubts.

I don't know who I am. I deal with a ferocious monster who calls Guisan Manbak "old man," enters the engine room naturally, and acts like an animal.

If there's someone there who asks to see something fun, then anyone would think they're on our side.

However, there was only one thing that's on my mind.

Miss, I have to report this, but who on earth was it? How would you know if it was me? …

Behind him, Tian Yuxue's eyes trembled.

No, does this really work?

The Blood Cult was such a den of idiots, and I wonder if the people who fall for their tricks are really stupid.

This was the thought of Tian Yuxue, who had been criticizing Qing for having such strange thoughts, saying that it would be impossible for him to take the lead in suggesting suspicious circumstances (doors, traps) that Qing had claimed.

The wise man with a nose who cried out to know yourself two thousand years ago must have done so for nothing.

"Now, would you please come this way? If you look here, you'll have a clear view of the situation down there."

"Where. Wow. What was this? The eye sockets are so small, yet you can see so clearly? What, how? Is this amazing?"

"A wide field of view was achieved through seven different spec reflectors."

"I don't know what it's, but it's amazing. I didn't know the Blood Offering Corps' technological prowess was this great. I saw it again."

There was a saying in Qing's hometown that praise can even make a whale dance.

It was a random sentence that was created in the process of translating the title of a book written by a Western writer and has nothing to do with the original title.

However, it's a famous saying that anyone who hears it can immediately understand the meaning contained in the words, and it has achieved the feat of becoming known all over the world as an old traditional Korean proverb.

Even a whale that can't understand a word dances in front of praise, so how much more so would a technician of the Blood Sect who can understand a word?

"According to the exact principle, when an object's image was reflected and hits a curved surface…."

Qing ignores the explanation and looks through the observation window.

The stone chamber where people gathered was visible through a very wide field of view, but the image was not greatly distorted. Considering the technology of the underdeveloped Zhongyuan, isn't it truly amazing?

"Let's see. The red one was Gwangryongseong, the blue clouds are Hyeongasancheon, and the green stripes are Suwangseong. Aren't those Sapa guys all gathered in one place?"

"Yes. Fifty-nine people have gathered in three groups, halved from the first group. And here, we plan to halve the number again."

"Wow. That's interesting. Let's go ahead."

"yep!"

Then, two technicians came flying in from one side, holding a signboard.

The writing there says something about thirty people fighting and such.

Qing-i looks at Tian Yuxue and was single.

Look, I was right, how could these primitive, uncivilized, ancient people have created a system that could sense the number of people and then divide them in half? That was a sly laugh.

At that, Tian Yuxue's expression suddenly turns sour.

As the signboard sinks into the groove in the floor, Qing quickly looks into the observation window again.

Since they have already killed each other once, wouldn't they immediately gather together and draw their swords when they see a sign with the same meaning this time?

However, the composition was really interesting.

The Sapa sect splits into three groups and the rest into four groups, but the rest are far too few in number.

That means that the numbers of the three Sapha sects each exceed fifteen.

Only thirty people can pass, but if only two Sapas unite, the number will immediately exceed thirty.

So, what will happen to these Sapa guys from now on?

Qing's heart pounded.

"No, you guys were just watching this fun among yourselves? Wow, you guys. I was wondering why you'd been digging for twenty years, but now I have to admit it. It was worth the time."

A smile appeared on the lips of all the Blood Cult technicians.

Of course, each of us couldn't take our eyes off the observation window.

Then, I thought someone from each faction came forward and started talking-

"Oh, they fight! They fight!"

"Yeah! Kill them! Kill them all!"

"Kuuuuu, those damn bastards……!"

The excited technicians' cries continue.

Surprisingly, the first group to be attacked was a coalition of powerless ronin and minorities.

Representatives of the three factions agreed to start by getting rid of the trash.

Since the difference in number of warriors was almost five times, it was not long before the minority warriors were wiped out, and only the warriors of the three factions remained in the cave.

Indeed, what choice will the Sapa bastards make now!

Qing swallowed hard.

Miss, I need a delicious cookie made from dried corn heated and pressure-dense!

That's right, it's radish! It's radish!

Feeling regretful, Qing chewed on the jerky he had previously harvested as spoils of war.

Then at some point!

The red and green robes unite to attack the guys in blue cloud patterned uniforms!

The situation was that Gwangryongseong and Suwangseong had joined forces to attack Hyeongasancheon.

The Ten Great Elements of the Apostles refers to the ten most successful sects in the Apostles.

And among them, the five from the top are written as ~천, and the sixth to tenth are written as ~성.

In political terms, those who use the surname ~cheon are the Five Great Families, and those who use the surname ~ are the remaining families after subtracting the Five Great Families from the Ten Great Families.

It seemed that the two factions, which were less powerful than the Hyeon-ga-san-cheon faction, had joined forces and decided to kill those warriors at this opportunity.

Considering the unique tyranny of Sapa, it could be that he simply did it because he did not like Hyeon Gasancheon.

"Yeah, good job! Kill them all!"

Qing shouts in excitement.

Chen Changming tilts his head at him.

The way she was screaming at me to fight and kill me while banging her head against the observation window was because she somehow couldn't tell the difference between her and her older sister's blood relatives.

Doesn't it seem natural that Qing was in her own place?

It was during that time.

"Wait! Twenty-eight! Twenty-eight! Door! Open the door!"

"Open the door!"

As the number of people dropped below thirty along the way, the blood cult doors rushed out and headed towards a large pulley on one side of the engine room.

It was proof that the Blood Cult's cutting-edge technology was returning to the world's most efficient internal combustion engine: human power.

Just before the technicians could turn the pulley, Qing shouted sharply.

"Wait! Stop!"

"yes?"

"It's been so much fun, what are you doing? Let them kill each other."

"Well, if the number of people at the gate decreases too much-"

"Ugh. There's another checkpoint, right? It doesn't matter if a few more die here, right? If you're going to do it, you have to finish it all. Why stop in the middle?"

"Oh, but the rules-"

"Hey! You dare to compare yourself to me? Hey, Ddaengchil? Are you hungry? You want to eat people?"

"Kyaoo!"

"Eek!"

"Hey, can you see how red his face was right now? He must be so hungry that his face looks like it's going to explode, ugh, why was it so red! Hungry beast, ugh, miss, ugh, teeth, taste, some, teeth……."

Qing, who had been crying from the middle, couldn't hold it in and burst out laughing.

No, what kind of beast makes that yapping sound?

Hahaha, the hungry beast (Murong Zhuxi) looks at Qing, who was bursting into laughter, with a gaze that's half resentful and half sad.

"Sorry, Ddaengchil. Hehe, whatever you want later, phew, I'll give it to you, so calm down."

At that, Murong Juhee's eyes sparkled.

Qing regretted it for a moment.

Did I say that for nothing? What's going on? You wouldn't suggest switching roles for revenge, would you?

"Excuse me, sir?"

"Ugh, the thought of you being torn apart by my pets was so funny. Come on, won't you let go? I'm having a blast watching this, where are you talking? You guys have no sense of propriety."

The technicians then step aside obediently.

Because the technicians also wanted to see more.

If someone high up in the Blood Cult had ordered it, that would be a good excuse. The fact that everyone pretended to be sorry but quickly clung to the observation window was proof of that.

Although I missed a few scenes along the way, the fight between the Sapas was truly a sight to behold, and I have no regrets.

But Qing was still hungry.

Aren't these teenagers gathered here the ones who divided their territory among themselves and raided the villages as if they had conspired to establish a base?

"Okay, let's go to this battle. Um, twenty people. Okay, put down twenty people and come down."

"yes?"

"Look at it now. There are about twenty-five of them down there, including the Gwangryongseong and Suwangseong. If twenty of them go down, won't we have to kill each other this time? Can you put up with this? Don't you think it's not fun?"

The technicians' eyes trembled at that.

"That, that's such a brilliant idea!"

"Ugh! I, I can't stand it."

"But the number of people… was this okay?"

Qing drives a wedge into him.

"I take responsibility. Let's do it now!"

"Yes!" "Okay!"

Then, the excited technicians took a new signboard with only the numbers blank and wrote on it.

Everyone seemed to be in a hurry, as their hands flapped their fans to dry their writing with incredible agility.

Tian Yuxue thought to himself.

It's a good thing she's a Taoist priestess. If she really was a witch of the Blood Cult, it would have been a huge disaster for Zhongyuan.