\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (1)}

Can you imitate or store a human voice using only the organ?

It was too advanced a technology to have appeared in the primitive Zhongyuan era (passing necklace) of an uncivilized ancient era.

This meant that even if you were a technician of the Blood Cult, you couldn't insert a voice guidance message like "the door will open when the stone gate opens."

Not only was there no guidance voice, but in fact the stone gate could not even open by itself.

It was a thorough home-made industry, a manual door that's raised by hand using a pulley.

The Blood Offering team's technicians clung to the stone gate and began to open it, turning it slowly and diligently.

You might say it's too manual.

However, we must take into account that the Shingajjimyo was a tomb dug into the mountain.

This meant that if you wanted to attach one device, you had to dig out a space of that size.

Since people are going to be doing the work anyway, it's more efficient to just sweat it out than digging a mountain of rocks.

Even as the Blood Offering team's technicians sweat, the battle continues.

The sound of stone grinding against stone echoed, but how could the sound of the grindstone be of much use when swords were flying everywhere, their sharp blades dancing?

However, for the warrior of the Iron Blood Sword Heaven, who was called Muldae by the Apostle Brothers, the sound struck him like a bolt from the blue.

"Door! Door! The door was opening!"

They are making a big fuss just because one stone gate has opened.

But we also need to understand the position of the person behind the mound.

Because I was suffering from the swordsmanship of a monster (Ximen Qing, Jeongpa Taoist priest) who looked like a monster wearing human skin, or in the Chinese expression, wearing a hat.

Most of the upper body of the muldae was stained crimson, like a checkerboard, and Qing was truly enjoying the slaughter without any selfishness.

The sound of a millstone heard at this time.

I could see the door slowly rising over there.

It was a ray of light and the greatest salvation for Muldae!

"door?"

"Yes, the door! The door was open-"

"No need!"

What are you talking about all of a sudden?

For Qing, the door was no longer in his sight.

What matters was that the bastard in front of you was wearing the Iron Blood Sword Heaven's martial arts uniform.

Aren't they the ones who committed clan genocide (fortress villages are almost clan villages) in an innocent village just to occupy a comfortable break room?

He said he was trying to save that dirty life, but he couldn't sell it, so now he's selling the poor door.

And then, huh? A door? What door? A stone gate?

Qing's eyes, which had been hazy and immersed in pleasure, become clearer.

The murderous intent that had been engulfing his mind vanished, and the sage's characteristic half-empty, half-dazzling, half-Taoist gaze took its place.

In other words, Qing returned to perfect normalcy.

The smile that was overly bright and burdensome soon subsided.

Thanks to this, the human face was restored to its original position, and the monstrous sense of discomfort disappears as if it never existed, creating a dramatic scene where the evil spirit and evil woman of hell transforms into a pure Taoist priestess of the Jeongpa.

The sight took my breath away.

Ah, it's over. I survived… …!

It was at that very moment that Muldae was about to breathe a sigh of relief.

My heart aches!

"Ugh, why……?"

Muldae, who confirmed the blade stuck in his forehead, asked with trembling eyes.

"There used to be a village on the slopes of Mount Mount Lao, but it's gone now. Why? Those damn bastards called Cheolhyeolgeomcheon wiped it out."

"Because of those country bumpkins……"

At the same time, the blue blade pointed downward.

Qing's beliefs were consistent.

The knife must come out in the opposite direction from where it entered.

The body of the mulberry tree, cut straight from the pubic bone to the groin, fell to the floor.

For reference, Qing was in perfect normal condition.

I poured out everything inside me on the floor, desperately trying to open the door as my breath suffocated and my vision became blurry.

And one last word.

"The door was open……."

Even though the door was open, it seemed like he was quite upset that he was dead.

Even if you tell them why they're dying, they're still blaming the door, so what's wrong with the Sapha guys?

Qing swung his sword and sprayed the clinging blood.

Well, who would be standing there anyway?

Suddenly, an unknown person covered in blood, internal organs, fat lumps, and other waste turned his head with a shocked expression.

"Fuck, who, ugh, my throat was so sore. Am I going to get phlegm?"

After confirming the culprit, he naturally turned his neck and pretended to relax his muscles.

It was a natural thing.

Pride was pride, and it was another matter to argue with a bitch who laughed while chopping up people alive.

Of course, it would have been the same even if Qing had been a rather timid and feminine participant.

"Look here, my friend. When did you achieve unity? I thought you were catching up, but did you really have to be so far ahead? You truly are a divine presence worthy of my sword friend!"

If a master who has achieved the union of the divine sword throws filth, what can you do but just take it?

If you talk back to me for no reason, you will get hit with a knife on top of the dirt.

"Huh. What's so difficult about that? If I catch you, that's about it, huh? Come to think of it, how do you unify the divine swords if you use twin swords? Are you left with just two swords?"

"That's only natural. Dual swords are two swords wielded as one, meaning the two swords function as a single weapon."

"Is that what you call unity? Or was it even possible? There's only one consciousness."

"But isn't there only one weapon?"

"It's a twin sword?"

"Didn't they say that twin swords are a single weapon? So, sadly, twin swordsmanship can be said to be a martial art with flaws."

"What did you say?"

Murong Zhuxi turned on the twin flames.

If he wasn't the eldest son of the Nan-gong family, it would be a severe insult that would immediately lead to a life-or-death decision, and it would be such abusive language that the head of the Nan-gong family, whose drinking capacity increases by leaps and bounds by the day, would have to personally come forward and apologize.

But, as was the case from the first time we met, Nan-gong Shencai was not the type of person to be picky about what he says.

It may be because, as the eldest son of the Nan-gong family, he had a childhood where he didn't have to be picky about what he said.

Or maybe he was just born this way.

"Isn't that right? The basics of a martial artist are one weapon and one pseudo-martial art. Whether it's a sword, a half-sword, or a long sword, isn't the technique used left-handed? If the power of a weapon was ten, then the pseudo-martial art, the so-called "boxing technique," would be around three. So, wouldn't the combined power of a martial artist with a weapon and left-handed combat be thirteen points?"

The conversations of experts are in themselves intangible treasures.

This was because the conversation between a master who has reached the peak of his power and a master who was just a master at the peak of his power was a valuable conversation that you should listen to with all your heart, regardless of your pride.

The Sapa warriors, who had been pretending not to hear, tilted their heads, nodded, and some even looked indignant.

Those who are nodding.

I understand black, but what was a half sword and what was a long sword?

(The correct answer was sword, sword, and spear)

Those who nod.

Yeah, yeah. Parktu-sul was a similar martial art.

Just as a dancer was a pseudo-dancer.

But even three points seems too generous.

Shouldn't we give it one point, or maybe half a point?

And those who are indignant will be those very same people.

But what can you do if you are angry about a similar unmanned subject?

"But if you hold a pair of swords, you only have two weapons, so it's only ten points, so isn't it worse than having one hand empty?"

"Wow. That's convincing."

Qing nodded.

Murong-ju-hee had a very sad expression on her face.

Actually, when it comes to swords, Nan-gong Shencai's words are mostly correct, aren't they?

So, Qing nodded and poured it in.

Nan-gong Shencai only said the right thing about swords.

As for the rest, I'll just say the right thing.

"In that sense, the ultimate martial art was the double sword. Since you wield different swords on each side, wouldn't that be ten points out of ten, and twenty points on each side?"

Look at this.

In the end, the conclusion becomes strange.

"Then, isn't having two weapons always better? Then why does everyone use both weapons, leaving one hand empty?"

"That's because the world's people aren't geniuses like me. Does it make sense to wield a different sword in each hand? It's such a rough and tumble path that I'm afraid to give up and compromise."

"Hmm?"

Qing's eyes lit up.

Because he was the type of person who never misses a chance to tease anyone.

"Is that difficult?"

"It's not difficult. Swordsmanship, after all, was designed to counter all four directions. Naturally, its path extends out into the world. Using two swordsmanship techniques to harmoniously advance without interfering with each other is, in fact, nearly impossible. However, something that's close to impossible is, in fact, impossible—"

"Huh. Give me the sword."

Learning the martial arts of the Qing was to touch the primal fear beyond the universe, which was forcibly struck into the head and body.

In Qing's hometown, it's a serious mental and physical contamination caused by the great old state window that extends its reach even to the unconscious realm known as near-memory. - This was what Qing considers.

Anyway, it seems that the brain-crushing learning method of Qing, which involves eating raw food without even preparing it, was too much trouble to distinguish between right-handed and left-handed people.

I just hit all the left and right hands.

Moon maiden sword (Jin) on the right hand.

The Baekpalsura sword in the left hand.

The world's first great martial arts, passed down through the generations by the only one successor, and the vicious magic of the ten greatest magicians in the world unfold simultaneously.

Of course, the Moon Lady's Sword can be unfair.

If you want to spread it out together, you should at least use purple swordsmanship to match the level. Why are you bringing in gold when it lowers the level?

But originally, Qing had a habit of making someone feel wronged just by breathing.

However, if that were the case, everyone would have to carry two weapons.

Clash! The two swords clash fiercely, ending the short sword dance.

"Huh. It's not easy."

"Wow! Amazing! But I'd say it's still more of an imitation. Yanggeom involves dismantling each of the primary techniques and reassembling them so they fit together. Yet, the true meaning of each technique must remain intact. It's a highly sophisticated discipline. You simply took out two primary techniques that complement each other."

Qing's eyes trembled.

It's a real ghost, a ghost. A sword ghost.

Plus, the whole sound.

"And Sword Friend? Wasn't that ferociously vigorous swordsmanship just now the Baekpalsura Sword, one of the ten greatest magic arts in the world? How did you master such a ferocious, most ferocious of magic arts? What a wonderful swordsmanship! Show me more in detail when we spar later."

"……?"

I wonder if you're going to find out about this? I feel a pang of excitement for a moment.

Conclusion? Why?

But Nan-gong Shencai can understand everything.

No, I couldn't understand it, I was just amazed.

Indeed, the black rain!

How could a true swordsman pass up such a renowned swordsmanship?

Swordsmanship before the ten greatest magicians in the world!

In kendo, which was the practice of swordsmanship, there was no good or evil, so there was no right or wrong!

Of course, if it weren't for the black rain, it would have been a disaster.

It's just the reappearance of the Wulin Gongjeok Surama Sword.

But in the old days, during the Spring and Autumn Period and the Warring States Period, Zhong Ziqi died and Bai Ya stopped playing, so this was called a friend who knew the sound, and it was called Ji-eum (知音), which refers to the highest level of friendship.

Even though he was a close friend who only knows the sound, he was like that, but if he was a swordsman who knows the greatest sword in the world.

That was when.

"Hey, are you just going to keep talking? Shouldn't we get moving? Everyone's waiting."

Okay, Lee Hye-hye intervened.

"Huh. Now, shouldn't everyone just go their separate ways? The door's open."

"Hmm?"

Qing looks around and frowns.

"What? Why are you all listening to everyone else's ramblings? Those who need to go, go. Those who need to rest, rest. Those who want to care for the injured, stay. You should figure it out yourself."

The crowd felt a little aggrieved.

In fact, no group can be without a leader.

This was because it's human nature to implicitly choose someone as the leader even if no one specifically steps forward.

In this very place, wouldn't there be a terrifying female demon head who displayed overwhelming power and even more vicious murderous intent, and who even severed the head of the Taesan Demon Army?

The door was open, but everyone was watching closely and listening to the useless talk about Yanggeom.

Qing waved his hand.

"What are you doing? Doing things."

The soldiers looked at him awkwardly and then disappeared beyond the stone gate.

Some people helped the injured person cross the stone gate, while others sat down next to the injured person with a look of disgust on their face.

"We're going to take a short break. Judging by the way we're going back, I don't think there's any need to rush."

Since we're going back anyway, I don't think it'll make much of a difference whether we rest or go first.

Anyway, it's obvious that everyone will be waiting when another room comes out to divide the number of people.

Otherwise, they'll either set a trap for us or did something like this again where we kill each other.


\vfill
\begin{lstlisting}
	The chapter title is a chinese idiom. 说曹操，曹操到  Shuō Cáo Cāo, Cáo Cāo dào. The story was Emperor Xian of Han was facing a rebellion by his own generals, and some minister was recommending writing a summmon to Cao Cao to suppress the rebels. Before the letter was delivered though, Cao Cao had already sent his army to protect the Emperor, and succesfully destroyed the mutinous generals. Thus, Cao Cao was conferred a higher title.
	
	The English equivalent was 'Speak of the Devil, and he shall appears'
\end{lstlisting}