\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (10)}

Around the blue, warriors with clenched fists stand like guards.

In the treasure room behind me, those who were collecting pieces of the magic absorption technique also turned their blades with expressions of enthusiasm, as if they were burning with thirst.

Thanks to that, Qingdo was able to catch its breath.

Wow, this works.

This was a real liberal arts degree, so I survived!

If he had been a scientist, he would have rationally assessed the strength of both sides and then, after making a rational judgment that there was no hope, he would have committed suicide.

Yes, this was the triumph of emotion, this was the greatness of the Moonpungdang Moon Department!

Qing looks at the sturdy backs of the warriors protecting him and closes his eyes gently.

Once again, a massive wall of blood rises in a remote, blood-soaked wetland, revealing an entrance created by a strange flow of fluid.

No! Third attempt.

This was the fear of the devil.

First of all, an easy realization.

After all, isn't the original purpose of martial arts to kill people well?

The martial arts that are good at using people are the best martial arts.

In fact, it's a common saying that everyone from third-rate martial artists to the absolute rulers of the martial arts world say, so the moment you truly understand and agree with it, the door to enlightenment opens wide.

But there was something even more frightening than that.

That constant temptation!

After thinking about it again, I realized that even after giving up and thinking that it wasn't quite right, I realized that I could always continue to reach the level of being a demon.

Unlike normal harmonious enlightenment, where once you are interrupted and lose your enlightenment, you have to endure until the next inspiration comes, once you know it, you can enter the state of enlightenment at any time.

Isn't that truly an irresistible temptation?

Just close your eyes and jump through the door, and you too will become a Unrestrained Realm appealer.

It was the realm of a true superhuman who can break the laws of nature and step into the realm of martial arts.

Although it's a side effect of being influenced by martial arts.

-… … .

Even though it's a monster without eyes, it feels like it's looking down at me with a cold gaze.

What, are you upset? Are you upset?

So what are you going to do?

Qing rushes in and jumps into the pool of blood beyond the door, drawing a childish curve like a dolphin.

A viscous liquid that envelops the body.

The smell of rusty iron filling my lungs was so ecstatic that it felt like it was stabbing my bladder.

And the sounds outside that can be heard through closed ears.

-Behind there! Behind there! There's a witch again!

-Wait! Stop! You can't go any further than this!

-Protect the super-brained, beautiful girl! Absolutely protect the super-brained, beautiful girl! Protect at all costs!

Qing smiles in the blood.

The guards are strong.

Since you're protecting the witch of the Blood Cult, you're a blood guard?

And since blood was red, it's red?

Blood was red, so Hong, no, this was a bit much.

-Damn it! You can't stop me right now! That bitch was about to get in your mouth! If that bitch, who's already wrapped in magic, loses her mind, she'll definitely pass on her martial arts! She doesn't even know how to master the Subsimgong! She'll try to suck out your hearts right away!

Qing got angry.

What do you see people as?

There's no way our red mercenaries would fall for such childish fabrications and propaganda… … , ma'am.

Suddenly, an inner instinct sounds the alarm.

If your lower abdomen feels cold, it means that there was an attack targeting your lower abdomen.

After sensing danger to the body, consciousness naturally comes back to life.

It wasn't a sudden (omitted) sudden response, but an instinctive reaction that couldn't be helped even if Grandfather Mucheon Daeje came.

Qing felt a rough pull on both ankles from outside the murderous sea, and then, with a whoosh! She was roughly dragged horizontally, as if something had been pulled out.

When I opened my eyes, a single raindrop was flying towards me.

The blade caught in the arm that Qing swung and spun tightly, bouncing off.

"This was really too much! Are we even doing this to each other? Aren't you going to learn the divine technique? Are you abandoning the absorption method?"

Then, one of the guys answered.

"Are you threatening me with your divine power now, my young lady? Since everyone in the martial arts world was of the same faith, didn't you say we should all establish a world under the death penalty? So why are you threatening me with your education like those oppressors who have stolen your divine power? Or was this simply a lie to avoid a crisis?"

Then, a hostile gaze was fixed on Pavabak.

What the heck, why was this guy so persuasive?

Qing came to his senses.

"That, the great swordsman……?"

"I am just an ordinary person named Jong Jeong-pil."

Qing waited for a moment.

If you say you're ordinary with your own mouth, you're definitely not an ordinary person.

And as expected.

"The world was yours!" "Dokgo Sword!" "Dokgo Sword!"

A nickname with three letters? He's no ordinary guy.

In the first place, weren't the five strongest ronin among the Cheonhaorang?

That old man Yura Dal was also a Unrestrained Realm, and that fat guy over there was also a Unrestrained Realm, so we can guess that this kid was also a Unrestrained Realm expert.

Then, the fat Povidone opens his eyes wide.

"Jongjeong's younger brother? Why younger brother?"

"Brother Jang."

"Hmm, Au? Why don't you come here instead? Don't you have the ability to acquire it without having to beg for divine powers like that? Huh?"

This was Dokgo Geom Jong Jeong-pil, who smiles bitterly at him.

"Brother Jang. For my entire short life, I've wandered the martial arts world alone, without anyone to accompany me. A solitary wandering sword, Dokgo Sword. Do you know why? Because I couldn't find the reason for my birth. So, untethered to any worldly connection, I wandered, searching for that reason. Because I felt like if I were drawn to human principles and bound by time, I wouldn't be able to find my true purpose."

"Hmm."

"And now, I have finally realized the mission of this era. Now, my younger brother, only the future shines through. A future where all martial artists unite and cultivate a common martial art. A future where everyone shares enlightenment, not as their own but as the world's, and where we reach the ultimate goal of martial arts, not alone, but through the power of all! And so, the future of the world's martial arts world, where the world's martial arts world was truly not under the heavens, but a future where everyone ascends to the heavenly realm together!"

"No, little brother. Did you go crazy from listening to all that nonsense…?"

"No, Brother Jang. My mind was clearer than ever. My ideals are set on the future, and my eyes are fixed on the present. So, here and now, I will use this moment, the moment when the world's most precious divine art, free from the shackles of ownership, becomes everyone's, as the first stepping stone to my long-cherished dream!"

Qing broke out in a cold sweat as she watched his back.

What the heck, why did a real communist show up?

And it's not just any red, it's a Unrestrained Realm red.

It was when Qing was whining and beads of sweat were gathering inside his face.

Jong Jeong-pil, who revealed his ambitions and became a true communist, looks back at Qing.

Qing felt a sense of crisis.

The atmosphere can't get any redder!

"Ah, yes. Jongjeong Daehyeop. Um. That. Thank you for enlightening this flawed girl. This transcendent beauty, Choi Kang-nyeo, the most beautiful woman of all time, almost made a grave mistake. I thought being born with such exceptional beauty, exceptional intelligence, and overwhelming talent was my biggest mistake, but now I see I almost made an even worse one."

"what?"

"Why did Heaven give birth to this most powerful woman, this brain-killing beauty, and then give birth to another woman! This Yun Yuanying, by her very existence, was a great sinner who brings to mind the absurdity of the world. Being too talented was also a sin, a sin. Ah, I am truly a beauty who endangers the world. Yes, I, Yun Yuanying, the most powerful woman, I am truly a peerless beauty."

Originally, nonsense had the effect of soothing hostility, preventing hatred, and greatly refreshing the atmosphere.

Even though he was treated as a cripple due to minor side effects.

"No, really. The young lady isn't ugly, but she's not that beautiful either. Please come to your senses and-"

"So, let's share the divine power here and lessen the penalty for your sins! Everyone! Are you ready?"

"……?"

"Are you all ready to be reborn as a new person through the new power?"

"Yes!" "That's right!"

This time there were a few responses.

The Qingi entertainment instructor screamed as if possessed and put his palms to my ears.

"All of us! As revolutionary disciples for a new era! Let's overthrow the evil practices of the old system! For everyone! Through independent study! Through uneducated study! Let's all become immortals of the Dengxianqing! Are you ready to scatter that immortal world?"

"Right!" "That's right!" "Yes!" "I'm ready!"

In this martial arts world, the only thing you can do to get a response was to have a street vendor beg you for alcohol.

The entertainment technology that transcended the times was like a divine skill of the highest order.

As cheers pour in like a roar, Qing finishes by raising both fists!

"Now! Look! Let me show you something! This was the mystery of the Divine Power!"

Then, Qing closes his eyes, and a five-colored aura of unpleasant colors flows out.

"Oh! That's the new one!"

The blood red earth spreads out in my mind, and for some reason the sky was pitch black. What the heck, where did the mercury sun go?

It was a bad omen that completely emptied the space.

It feels empty because there was nothing there.

Qing runs towards power without caring about anything.

So, the fourth attempt at Mine Island.

Step through the door and plunge into the sea of ​​murder!

However, martial artists are not disabled.

At least Jongjeongpil wasn't a cripple.

"Go! Hey, girl, no, you bitch, you bitch, what the hell kind of name was that! Anyway, you bitch! Are you trying to trick me again?"

Qing's eyes widened at him.

"Ah, Kkabi. I'm almost there."

"You, now that I think about it, you have no intention of sharing your new skills. You were just lying to buy time—"

"Come on! Focus! My first meal! Sanjeongjinhon!"

Isn't that a terrifying name for a herbivore that scatters the mind and extracts the soul?

And that's his first meal.

It was not in vain that he was known as the most vicious magician.

"What, all of a sudden!?"

"Concentrate from the silver lining, let the dragon spring float, and stand on the ground! The divine art begins with standing upright, so everyone stand up and follow along!"

For your information, the terms Eunbaek and Yongcheon all refer to acupuncture points on the human body.

At this moment, everyone straightens their posture.

Whether you are a person who wants to monopolize or a dreamer who dreams of sharing, shouldn't you at least keep this in mind?

"From the Dantian, it should reach the Gwanwon, Junggeuk, and both Chungmun without being biased to the left or right. It should flow forward three times, seven times, through the Blood Sea and Yanggu, concentrating below the Blood Sea, passing through the Seol-an, and extending to the Haegye. The Yanggu then divides into the Yangryongcheon and Dokseok, four times, six times! It flows in this way, the true energy of the Haegye and Yangryongcheon passes through Taechung and into the Yongcheon, and the true energy of Dokseok flows into Johye, matching its speed with the Yongcheon!"

It was a fairly detailed commentary.

Everyone in the room held their breath, listened to the words, and then turned their energy to follow suit and took a standing position.

"From Yongcheon to Jokshim, from Jokshim to Seungsan, as you circle, the true energy exerts its power, applying strength to the calves. Passing lightly through the Eunmun Gate of Wei Zhong, it then applies its power again to Seungbu. The remaining true energy returns to the Dantian! Thus, the true energy circulates, adding strength to the front and sides of Yongcheon, solidifying Seungsan and Seungbu! This was the first step to draining the opponent's soul, the step of standing with the right posture!"

The unmanned people are standing there, taking the basic stance of an unfamiliar method.

This was a pose where you lift your heels and tighten your calves and buttocks.

By the way, the butt was different from the hip.

The protruding part behind the pelvis, that's, the round part that's attractive in women and dirty, filthy, and messy in men, was called the pubic bone.

And cut the buttocks in half, the lower half was called the buttocks and the upper half was called the hips.

So, the part that's usually called the buttocks was actually the upper part, the lower part was called the buttocks, and the whole thing was called the buttocks.

Afterwards, Qing recited the acupuncture points on the upper body one by one and taught the true energy, causing several warriors to exclaim in admiration.

In fact, blindly believing and following the instructions given by others was one of the worst and most despicable ways to commit suicide.

If you do it wrong, your blood vessels will become tangled and you will become a cripple who can neither live nor die.

But when I listened, the energy flowed naturally along the path, and those who tried to follow it also realized that this kind of careful operation of the bet was no ordinary, exquisite skill.

So the basic posture.

Standing with your heels raised, shoulders relaxed and shoulders still, the unique feature was the flow that flows to your head to increase your gaze.

"……So, after standing upright, walk straight ahead, but never let the movement of the divine energy cease. Your feet should be light and silent, and your heels should move one inch. The important thing here is……"

The unmanned forces try to follow the method of the swordsmanship, but as expected from a high-level martial art, it's difficult to properly find the center.

Those with a higher level of skill could also realize that the divine skill contained a considerable level of subtlety and gentleness.

So, those who reached the peak were able to imitate the divine technique quite convincingly using phrases that were only passed down through word of mouth.

It feels a bit strange that both the person doing it and the person watching it feel uncomfortable. Is this right?

There, those of lowly status are not gentle and do not have the body to follow them, so suspicions creep in.

"Is this right? It just won't work."

"Hmm. Should I give you a demonstration? It seems like it wouldn't be easy to do with just the blood vessels and muscles, right? Okay. Here's how it's done."

He then shows off his first skill, a proper technique.

A step forward with your heels lifted.

A smooth vertical movement, one inch at a time, runs up the back of the lower body.

So the place where the movement reached was the cheekbone.

Since you are already lifting your heels, your pelvis was tilted, your buttocks are wide, and your hips are narrow.

Besides, was Qing's cheek just a cheek?

The scale of the super-large jackpot was as grand as Mount Tai, setting men's hearts ablaze.

The huge thing moves from side to side, surprisingly gracefully for its mass!

It sways gracefully and elegantly, drawing an infinite double circle.

There, the peculiar sound of the hem of the clothes rustling softly echoes, so when you look from behind, you can't take your eyes off the buttocks.

When viewed from the front, the moist, sad, regretful, and somehow appealing eyes that seem to desperately desire something capture the attention.

When her innocent yet lewd eyes look at the men, their hearts sink.

The way she walks, shaking her breasts and buttocks, was like no other prostitute in the world, but it's also elegant and pure, and has a noble air.

The sound of snow falling softly.

It's the sound of clothes brushing against bare skin.

That faint sound was the most beautiful sound in the world, gradually fading away into the silence where I can't even swallow my saliva for fear of it being cut off.

Dalgi, who descended to the human world, was a peerless prostitute and also the most noble woman.

The witch slithers between the stunned men.

So, towards the outside of the passage.

The first duty of Tangseontal was to eat the first meal. Sanjeongjinhon!

To scatter one's mind and extract one's soul.
