\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (4)}

When a new sign appeared above the signboard, updating the number of survivors, the expressions on the faces of the remaining Sapa men in the hall were truly a spectacle.

It's so much that I want to keep it as a drawing and look at it over and over again.

The warriors of Gwangryongseong and Suwangseong are split into two groups.

There are twenty-seven people left.

Seven more people must die in this place.

Qing watched the scene with sparkling eyes and excitement, mumbling.

Indeed? How will it turn out?

Should we kill four, three, or three and a half of our own family members to make up the number of people?

Or are you going to take this opportunity to fight again and try to pass the loss onto your opponent?

Either way, it's a bit annoying.

However, the former would have the entire expedition team's morale sapped, and they would have to suffer fatal losses among similarly powerful forces.

Qing thinks that even though they are men, they have a sense of duty. Even if it means dying, they should stick together as family who eat the same food and fight.

Hmm. As expected from the Sapha kids!

The Sapa guys moved, and Qing was amazed.

None other than taking care of the injured!

Isn't it just a waste of time to take care of a seriously injured person who will only end up being a burden even if you take him with you?

How can one not be impressed by such an efficient choice that prioritizes functionality and beauty?

"Wow, they don't just abandon those injured Sapha kids, they kill them and leave. Even those kids usually emphasize loyalty and loyalty between sects. I get goosebumps."

"Hehe, isn't this loyalty that's completed through death?"

"Oh. Just kidding."

Qing was a little surprised.

Are they now feeling close because they saw the same thing in the same space and enjoyed it together?

Is this the close friendship between blood cult members?

I guess I'll have to try saving half of it.

Then let's see if they fight among themselves or if I come forward and say I'll die.

Anyway, the attention of the Sapa guys who had reduced the number of people to twenty by dealing with the wounded was focused on one side.

It was towards the stone gate that showed no sign of opening.

And the eyes of the Blood Cult technicians were also focused on one side.

It was towards the blue.

I looked at the Blood Offering technicians with half anticipation and half regret, and Qing just blinked.

What the heck, why? Why aren't these kids opening the door and staring at me?

"Uh, can I open the door now?"

"What are you going to do if you don't open it?"

"Hehe, that's, um, no. Then."

The Blood Cult technicians, for some reason, looked a little lethargic and headed towards the pulley.

I don't know why, but it seemed like it would be a novel-like passage that said, 'I take reluctant steps…'

And since his entry into the martial arts world, Qing has been acting as he pleases without paying attention to others based on his strong power, but isn't he originally someone with extraordinary insight?

"Wait! Should we do it again? How many people this time? Fifteen? Ten was too few."

The faces of the Blood Offering technicians brighten as if nothing had happened.

"Fifteen would be good!"

"If you cut it in even numbers, you might be able to split it evenly, so you have to cut it in odd numbers!"

These were two giant sects that cut down even the injured for the sake of a great cause (to find the world's most evil magician for personal gain).

A new signboard fell down with a thud in front of those ruthless men.

Sorry. Let's do it one more time.

Chair grab, fifteen people. Go!

"Fight! Fight!"

"Be a man and fight back, you little shits!"

In contrast to the heated atmosphere in the engine room, the stone chamber below was filled with sorrow, as if a funeral had been held.

It was true that he actually had a funeral.

If you were fifteen, then when you first entered the stone chamber, weren't there at least fifteen people?

It would have been okay if they had told us to kill everyone except my brothers from the beginning.

After making a dirty compromise, even cutting down the injured while holding back tears, you're going to kill five more?

Besides, the numbers of the two are ten to ten.

If two people lose, the maximum was mutual destruction, and even if you are lucky, how many people can stand?

So, to Qing, it seemed like his jaw was moving very hard, but he was going to finish taking care of the remaining injured people.

Hey, Kim Saege.

It was a rational choice from Sapa's perspective.

If I kill the wounded and the porter (the youngest) to fill the gap, wouldn't my safety at least be guaranteed?

But what if my life was in danger when it's a ten-on-ten fight?

Moreover, although the perpetrators were unaware of it, there was a secondary effect that caused great disappointment to the onlookers.

The blood cultists look at Qing again.

It's a desperate look that asks if we can do it just one more time.

They were Blood Offering technicians who were really arrogant and didn't take responsibility.

"I was supposed to stop here. Okay. What's the catch if I open the door later?"

"After passing through the corridor lined with traps, of course, there are no people of interest to eliminate with traps, so there's no need to activate them separately."

A faint tinge of tension appears on Qing's smiling face.

Person of interest to be eliminated.

So what I'm saying was that these kids are blatantly targeting me.

"And after the survivors joined together-"

"What!? Are you telling us to kill each other again? Are you so uncreative that you can't even use it? Are you going to curse me and say that the only thing this house knows how to do was make us kill each other? Aren't you planning it properly?"

"Hehe, that's not it. The next chamber was named the Wailing Chamber. It's the chamber where the highest level of the Blood Offering Corps's energy was concentrated."

After two fights, the gathered survivors find themselves in a place that resembles a kind of charnel house.

And there are friendly words on the wall.

The divine power you desire was somewhere among these.

But to open the ship, one must sacrifice a human brain or heart.

So those ugly, sword-wielding bastards will have to offer up their hearts and brains to open the sacred box where the Divine Power sleeps.

It would be fun to see them kill each other to open the box, but wouldn't it be equally satisfying to see them fight over the heart and brain that have already been released?

At the sight of the gruesome plot, the group's faces harden.

Except for Qing.

"Oh. That's really bloody."

"Hehe, thanks for the compliment."

"Okay. Let's open the door. The next attraction was also a delicacy. Why should we fill our stomachs with food instead of cooking?"

The Blood Cult technicians looked extremely regretful, but as Qing said, it was a waste to waste it here when there were more interesting things to see.

So the technicians get stuck in and turn the pulley.

As the heavy stone door opens, a rumbling vibration reaches the engine room.

Then, Qing claps his hands and focuses everyone's attention.

"Okay, everyone. Did you see what those Sapha kids did just now? Those damned men, you know. They don't even know how to fight like a man and make a life-or-death decision. Do they even deserve to be called men?"

"doesn't exist!"

"You have to take all your dicks off!"

The Blood Cult technicians burst into laughter and actively chime in.

Qing smiled with satisfaction and continued speaking.

"Right? So, from now on, you guys, kill each other like men. I'll spare all of you, but exactly half of you."

"……?"

"yes?"

"Didn't you hear me? You little brats, hiding in a safe place like this, manipulating the situation, you're in for a real treat, right? Now it's your turn. Come on. I'll spare you half. Fight! Be a man!"

The Blood Offering technicians blinked their eyes.

What? Is this some kind of joke? Should I be laughing now?

Those blood cultists are completely incomprehensible to me.

Qing sighed deeply and threw away his sword.

As the saying goes, a square peg makes a round hole.

The wrist of the technician standing next to the blue falls to the floor.

"Huh? Eww!"

The Blood Cult technician falls, clutching my precious wrist, screaming.

Qing stood beside him, his blade flashing.

Although it may be a bright expression of the blue, the pale starlight of the strong spirit's originally a vicious blade that makes the heart of a person feel cold when seen.

"Did I say I'd kill everyone? I'd spare half of them. I'd spare half of them, and then you don't even move a muscle, saying, "Oh, thank you, we're going to kill each other from now on." You just blink and look around, do you think anyone would notice?"

"Why, why are you doing this……!"

"Why are you doing this? Is there a reason to subdue those ugly Blood Cult members?"

"……!"

"You bastard! You weren't one of our followers!"

"You're fooling us!"

But the blue was dignified.

"When did I ever say I was a member of the Blood Cult? I was just asking if you knew who I was."

Although the group behind me lowered their heads as if they were embarrassed.

Anyway, isn't it true that lying was lying?

The more we do it together, the more we put it out there, the more embarrassed we become to put it out there.

But only Qing was confident.

Did I fool you? You guys were all alone, beating drums and janggu, and running wild with excitement.

"Okay. Quick. The Sapa guys were fun to watch, but it wasn't fun at all because I couldn't hear them."

Qing smiled eerily.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing didn't say they would kill everyone.

She said she would spared half of them.

Qing was a person who tried her best to keep her word.

As a result of the technicians' scuffle, only three people remain.

And, true to his promise, Qing spared only half of the remaining men.

That means the other half was dead.

She only took out the intestines, but she didn't kill them anyway.

Whether they live or die would probably depend on their subsequent medical treatments.

Of course, what kind of medical treatment would the Blood Offering technicians, who are good at handling machines but don't know how to handle the human body, possibly perform?

They would definitely die.

Qing was a female doctor recognized as a person of merit and had some knowledge of Oriental medicine.

According to the Yellow Emperor's Classic of Internal Medicine, the foundation of Zhongyuan medical book, how should we treat diseases caused by infection?

The correct answer was to drain the pus, clean the affected area, and then pray with all your heart.

If your prayer reaches heaven, you will live, if not, you will die!

From the Qing's perspective, it's truly uncivilized, but for the medical level of the time, Xhongyuan was at the forefront of medical advancement.

At least, Zhongyuan medicine was the essence of statistics that emerged through millions of experiments.

The nose-sniffing people in the western region were in a situation where if a loud voice was shouting, that was the cure.

Stomach hurts? Get an anal resection.

Headache? Get anal resection.

Heartache? Soak the patient in water!

We were using some very creative and experimental treatment methods, like Moore.

In fact, at this point, it's confusing whether this Qing-i was a Taoist priest or just a lucky cult leader who got into the Jeongpa.

Of course, Qing was lucky.

First, the group witnessed the Sapa guys wreaking havoc in search of the Absorbing Magician.

No one in the group considers the Sapa guys as human.

And the evil spirits of the Blood Cult are not originally human.

The perception of the martial world was that bugs can be saved, but the scum of the blood sect cannot be saved.

So, it's not like the Qing was spreading evil tricks against the Blood Cult.

Of course, it's something that a person should do, but the method was understandable to the extent that it's a bit extreme.

So, Qing was still barely able to maintain his dignity as a Taoist priest.

Of course, it's not like Qing was just wandering around the engine room, beating up evil cultists who have unfortunate pasts but aren't innocent.

The pleasure derived from bloodshed was merely a secondary pleasure derived from actions aimed at achieving a goal.

Qing did not forget his goal.

The immediate abolition of the Essence Absorbtion!

So, it was necessary to go around and secure an escape route for later, and cross-check the information that the technicians had given through various testimonies.

And only then do we head to the central control room, to the head of the Blood Offering Corps.
