\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (8)}

The warriors who had gathered to find the Absorbing Magician felt as if someone had slapped them in the face for no reason.

It's so absurd that it feels like I've been beaten up.

What did you just say?

Usually, a girl with a super brain killer in her own mouth, no, does she even call herself a girl in the first place?

And can you say things like "beautiful, elegant, noble" with your own mouth?

Of course not.

Are you saying that with your own mouth?

A nickname that would suit such a shameless woman would not be 'Super-Brainless Pretty Girl', but 'Thick-Faced Crazy Bitch', or 'Iron-Made Madwoman'.

Everyone was dumbfounded and speechless, just gaping.

It was a rare sight of unification in the martial arts world.

Meanwhile, Qing rolls her eyes diligently.

Where are you jumping?

Where was the direction where the easiest guys are gathered?

Looking back, I think it was a good thing that the ladder broke.

Still, the group will escape safely through the disguised exit dug by the Blood Cult technicians.

I'm just losing weight.

Well, wouldn't it be okay if we do it somehow?

Qing had a good feeling for no reason.

Just like when I wore a military uniform in the past, I would gladly lie down and sleep on any dirty ground.

Qing, who was wearing the mask of Yun Yuanying, had a surging boldness that seemed to boldly ignore any gaze of the world.

That was a transformation, yes, a transformation!

"Okay! Everyone! The Fantasy Chariot Tournament! Let me show you something!"

Qing fired without giving the new explorers time to think.

If you give them time to think, they'll just attack you in droves.

The method of dealing with the majority has been known to everyone for two thousand years.

Divide and rule!

Qing lightly grabbed the knife with both hands, using only his thumb and forefinger, and tore it in two!

"Huh, what, what are you doing!"

"Come on, tearing up a book isn't that hard, was it? Let's go!"

After Qing clumped the torn book together, he grabbed it from side to side and made a crunch!

I was half shocked and half swallowing a groan.

Half of the warriors were shocked by the atrocity of tearing apart the precious sacred art.

And half of them were sick of the ignorant force with which he tore the paper with two fingers, two fingers in total, like tearing a pancake.

"Well, it would be a shame if it ended here, right?"

"no way……!"

Qing tears the booklet open with a crackling sound, leaving no room for her to open it.

In the haste, they clenched their fists instead of their fingers, which made them less surprised, but everyone gasped in shock at the sudden tearing of the knife in real time.

"Wait! Stop! What are you doing!"

Qing shouts urgently as someone lifts their foot, unable to bear it any longer.

"You want power!? If you want it, I'll give it to you! Pick it up carefully! I'll put all the secrets here!"

And then Qing's hand drew the sign "Manse".

The fragments of the emergency light scatter beautifully in all directions like plum blossom petals, then slowly descend, making a rustling sound.

What a beautiful sight!

"Damn it! What are you guys doing! Kang Pae-cheon! Secure the emergency supplies!"

"Emergency! It's emergency!"

If you sprinkle silver in a box on the author, this kind of return to the father will be created!

They all rush in, bending down and stooping to pick up scraps of paper.

In the meantime, there was pushing and hitting, squeaking, and finally, the weapon was pulled out.

Qing's eyes lit up.

now!

Qingyi thumped hard on the ground.

Black mold grows and footprints appear on the stone floor.

The first step of the Cheonma Gunrimbo was three steps and one hundred miles.

The miracle of the Heavenly Demon using the Shukji method was that the blue was shot out in a long line.

The supernatural swordsman Wang Woo-ram was picking up a secret weapon that had fallen on the floor.

Having acquired about one thousandth of the magic absorption technique, it was worth it to reach the depths after passing through all the traps and vicious arenas.

Then, suddenly feeling ominous, Wang Woo-ram raised his head and saw the soles of shoes filling his field of vision.

That was the end of Wang Woo-ram.

Bang. Wang Woo-ram's head was smashed like a watermelon by the rough Pacheon Magic that rose from Yongcheonhyeol.

Why was this kid suddenly raising his head?

Since there was one guy in this position, the original plan was to step on his back and reach the second acceleration.

But then suddenly the guy raises his head.

Thanks to this, the stepping foot becomes vertical instead of horizontal.

Naturally, the long trajectory drawn by the blue movement also turns at a right angle and soars into the sky.

And fuck!!

The crown collides violently with the ceiling!

A flash of lightning struck Qing's vision.

A familiar pain, like losing your soul!

This was truly a creative honey chestnut!

For years, the hard, unparalleled stone head has been sending crumbs of stone flying in all directions.

The blue roughly fell to the floor.

My head feels like it's broken, isn't it really broken?

But escape, escape comes first.

Qing gritted his teeth and jumped up, trampling the innocent floor and breaking it, and returned to his original position.

The new Qing was shot out like an arrow again.

The moment Qing, who had been galloping alone through the slow passage of time, took a second step and soared with even greater speed—

A force suddenly grabs my leg!

What if you stretch out like you're flying and your legs get caught?

The scream of "Ugh," was short-lived, and the floor was rapidly approaching Qing's vision.

The blue was thrown to the ground at the same speed it was running at.

Bang!!

This time, the forehead hits the floor roughly.

A small hole forms and a sharp pain like a nail was driven into my forehead.

Creation nuclear honey chestnut my ita!

"Ugh."

It feels like I've been hit with a nuclear bomb on both sides of my head and forehead, and it's stinging, painful, and throbbing.

What, what a bastard!

The corners of Qing's eyes rise fiercely.

An ominous color that had never been seen before suddenly burst out, and the angry eyes, like evil spirits, suddenly turned towards my feet.

A whip wrapped around the ankle.

And along the long, flowing line, there was a young boy who was barely able to keep his feet on the world lying flat.

"Huh, huh?"

The man was still out of his mind.

Qing's enthusiasm for him soars.

That kid didn't know how to catch the thing he threw, so he fell over!

It was as if I had my feet tied by a blind whip.

"Ouch! Got it!"

As if he had suddenly come to his senses, the man wrapped the whip around my wrist tightly and pulled it violently.

As Qing was being dragged while lying on the floor, a sword suddenly appeared, held in both hands.

Qing rolled her body.

Bang! The blade of the great sword collides with the ground, sending up angry sparks.

In that moment, Qing's eyes flashed.

He raised his upper body and grabbed the whip.

It was a force that even Xiang Yu would respect.

The man flew through the sky with his hands outstretched.

The noise of people getting entangled in a mess.

Qing jumped up and screamed!

"Do you think people look funny when you tell these kids to just get out of here?"

A beautiful hand, almost transparent, with long fingers drawing four lines.

The tip of the finger breaks the shoulder blade, breaks the spine, and comes out through the side.

The other hand was gently gathered and stretched out straight, and it naturally digs into the warrior's chest like a sword being put into a sheath.

"Oh my!" "Oh my!"

Unmanned people running towards someone, shouting.

Everyone lives with relationships and the accumulated relationships, so taking someone's life means accumulating a lot of resentment.

"Oh! You should know that today was the day for a group memorial service!"

From Qing's eyes, a color blooms that resembles all the colors of blue, red, purple, and green, yet was not the same as any of them, a color that does not exist anywhere else.

The most ominous starlight in the world.

In response, the Sosu Magician, the Heuksal Magician, and the Bicycle Magician move and wiggle.

They were evil spirits who had their roots in murder and were created solely with the evil intention of harming people.

The blackened hand seized hers and struck her, shattering her bones. The slender fingers on the other side dug into her flesh, sending a serrated force through her body, sending flesh flying everywhere and blood gushing out.

A purple lightning bolt extends across time and space, reaching the enemies.

A hand passes by like a whip at an enemy who flinches.

After gently stroking the nape of his neck, a huge scar remained, as if bitten by a beast, and blood gushed out like a fountain.

The world of Qing begins to shrink.

Thud, thud, thud, the world shrinks into a circle like a fire going out, the ground beneath your feet dripping with blood, and above your head, a purple evil star fills the sky, revealing its insides made of boiling, five-colored mercury.

And the universe began to flow.

With every blink of an eye, a malevolent star rises, fills the sky, and disappears into the distance. The starlight dances dizzily until an ugly dawn breaks, and a malevolent star rises… …

The movement of celestial bodies on a remote star made of blood, as if time had been accelerated tens of thousands of times.

In the meantime, enemies arise.

Enemies made of blood.

However, unlike the movement of the celestial bodies, which flow like ten thousand years in a day, the enemies are slow, as if one day was stopped like ten thousand years.

Is there anything easier than dealing with a stopped enemy?

At this moment, what kind of emotion was Qing feeling? A boiling elation? How should I describe it?

Then suddenly.

ah.

Qing realized the true nature of this emotion.

This was what they call omnipotence.

Then the evil spirit answered.

-Do you want power?

In an instant, blood spurts before Qing's eyes.

It was a huge wall of blood that rises to the far end of the sky and blocks the way ahead.

Then the boiling, ugly sun reaches out and splits the barrier left and right.

And beyond the barrier, there was only the bloody, calm deep sea spread out wide.

At that moment, Qing realized that he was at a crossroads.

Ah. This was the mouth, the mouth.

Martial arts are the skills to kill others.

And the way to become a demon, a mine, was to throw yourself into that sea of ​​murder.

Then a face passes by.

Ah, Master, I miss you.

If you go over the wall like this, you will probably use up all the nuclear warheads you have, five thousand times more, and provide them infinitely.

The corners of Qing's mouth slightly rise.

"You want power? Isn't that such a boring line?"

Then the evil star splits open, revealing countless teeth jutting out from between the gaping planets.

It seemed like a laugh, or a sigh of regret.

Have you given up on kindness yet? The world was cruel, fate was an illusion, and flowers that bear fruit will eventually wither and rot. In this world, only fear can set you free.

"Who can be fearful for a thousand years? Those who rise by the sword fall by the sword. If you get stabbed in the back of the head in your later years and fall, was that freedom?"

Human nature was evil and weak. Kindness was easily shaken by gain. Therefore, the more we love and feel comfortable with someone, the more easily we betray them for personal gain.

"Well, what can I do if I get treated like that? I've decided to accept that."

Then the evil spirit shines.

This also seemed like a mocking laugh, or a sigh of regret.

The star that had been shining so vaguely finally begins to fade.

How long do you intend to deny your fate? I will leave the door open. Come whenever you wish. I will be waiting.

"Is that okay? What kind of mine was this? There's absolutely no reason for him to come back? Absolutely not!"

In an instant, the world of Qing was put back into place.

The crowd of people surrounding Qing looked at him with surprised eyes, and a middle-aged man with a sword thrust out shouted among them.

"You bitch! You're a wicked witch from the Blood Cult! Just how much magic have you mastered?"

"omg."

Qing was surprised.

"Magic, it's not magic, was it?"

"It's not magic! It's a black magic field with a small number of magicians, a wheel-turning magician, and a bicycle magician!"

"No, that's not it, God, um? No."

Qing tried to deny it reflexively, but then he thought about it and realized that he was not Ximen Qing, but Yun Yuanying.

"Haha! Now you understand! This was the power of the real woman, the super brain-killing beauty, the strongest woman, Yeon Yeon-yeong! A power as strong as the real woman's beauty! The most beautiful woman in the world, no, all time! Ohohohoho! If you take her for granted because of her beauty, you'll get a big scolding! Get out of the way right now!"

The expressions on the unmanned soldiers' faces suddenly turned sour.

Putting aside the nonsense that sounds like it would make your soul go out just by hearing it, what on earth was that laughter?

"She's a witch of the Blood Cult. Then there's no reason to hold her in the palm of your hand."

A middle-aged man, Jun Ki-chung, the lord of Jeolnakseong, raises a strong and fierce sword.

And on the right, a fat king of similar height and width was raising a banner, and on the other side, a skinny lama was holding a banner on his long staff.

Behind them, several unnamed unmanned men are aiming their blue weapons at them.

You can tell Unrestrained Realm's strength just by looking at her.

Let's say the amount of light itself was different.

Unrestrained Realm, the three idiots who were digging the door at the west gate, why are they all gathered together instead of fighting each other?

How many peaks are there now?

Why are you and I both using our power?

This was not it, this was not it.

Qing quietly closed her eyes.

Towards a deep image, somewhere in the heart.

To a world where blood flows, evil spirits fill the sky, and people open their mouths to look at the blue.

"Strength! I need strength! Give me strength!"

-… … ? Didn't you just say you didn't need it and that you would never come back?

"Okay! It's urgent, so hurry up! Hurry up and cheer up! Miss, give it to me!"
