\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (2)}

Arrows on the walls, thorns on the floor.

And then sometimes-

Qing's head snaps up at the sound of a loud noise coming from above.

The ceiling rushed towards the blue.

Since the sky was still, it could be interpreted that the ceiling was falling.

The blue fist rises upward. Boom!

The steel fist of the minority magician, no, the fist of eternal iron, delivers a powerful blow to the rock that dared to leave its place.

Crumbs of stone rise, followed by broken rocks and pieces of stone strewn across the passage.

Amidst the dust blowing in all directions, Qing spits out the stone fragments that entered his mouth.

Qing was being treated unfairly.

"Isn't it strange? Why are you targeting only me? Isn't it like someone was just watching and then triggering it just for me?"

Tian Yuxue laughed at him.

"Huh. Who's going to watch from where?"

Qing looks around at his group.

Everyone looks like that's going a bit too far.

It was a moment when truth was suppressed.

The lips of the Qing who had not received consent suddenly stick out.

"No, it's obvious you're only after me."

If you stand in front, it's a trap.

If you stand behind, it's a trap.

Even when he took his place in the middle of the group, he almost got splattered with arrows.

Thanks to that, Qing walked ahead, staying far away from the group.

Five projectiles flew from the wall.

The ceiling collapsed three times.

It fell to the floor four times.

"That's just bad luck. Who would watch, how, or where?"

"But. So many people have passed by before, so why does the trap only appear when I pass by?"

Isn't this a passage that the survivors of the previous grotto battle have already passed through?

Why are you pouring out traps only on me now when you were fine before?

Does this make sense?

"It's strange and coincidental, but isn't it better than hearing that a vengeful spirit lingers in a cave over a hundred years old, hunting you down? And even if that were true, why would they hunt you?"

"Hmm."

"Just think of it as bad luck. It's probably because there was an old trap that was a beat too late to trigger when you came along."

That makes sense, but isn't it still a bit strange?

Thanks to that, only the group was comfortable.

"Miss, this somehow feels malicious!"

The new blue one that had been grumbling suddenly goes out again.

His companions were like, "Hmm, we fell again."

It's not like it's the first or second time you've lost your temper.

This was how scary it's when people become accustomed to something.

Why do the Blood Offering technicians keep setting up traps that don't even work?

Not just to get my temper up.

It was not the outburst of a technician who has been denied his rights for twenty years.

Because there was still something big left.

In fact, no matter how creative a trap engineer may be, the trap he can create was only as good as it gets.

Shoot, drop (the target), or drop (the target).

So what was important was the placement.

Inflicting an unexpected fatal wound in an unexpected situation!

This can be said to be the very essence of a trap.

One last shot in this situation.

This kid must be dealt with at all costs. There were even vicious traps created to eliminate him unconditionally because he was a hindrance to the great undertaking.

A Blood Offering technician runs ahead and waits on the upper level of the trap-laden passage.

Looking into the passage through the observation window with multiple reflectors, he sees his target standing proudly in the lead and immediately detonates the trap.

Thud! The iron sword I had so desperately needed exploded with a loud bang, like gunpowder exploding under the immense tension.

A target that flies straight ahead at him.

But before the target hits the ground, thud!

The floor splits open and the target disappears into a thorn trap.

And then again, thud!

The ceiling collapses, and a massive boulder digs into the thorn trap, filling the void.

"That's right! You fucking bitch! What's wrong? A poor-made trap? Can't even catch a single mouse? Ha! Don't underestimate the engineering! This is the pinnacle of engineering technique, you damn bitch! Hahahaha

The Blood Offering technician detonates the light.

If I were to lie on steel spikes jutting out from the ground and be crushed under a thousand-pound rock, what could I do, no matter how great a master I was?

Beyond the observation window, the group, pale and frightened, are seen collapsing or rushing into traps, looking helpless.

Then, suddenly.

Suddenly, everyone clung to the thorn trap and began to cut and cut the huge stone with their knives, pulling the pieces out into a corner.

Why? Why don't you feel a little more sorrow?

The Blood Offering technician feels ominous.

"Even if we clean it up, all we'll find was a corpse riddled with holes…"

Then suddenly, a piece of shattered stone flies out from under the hole.

Suddenly, a head pops up, holding onto the rope thrown noisily.

A deep blue flower blooms in both eyes.

"Huh!"

It felt like their eyes had met, and the Blood Offering technician fell backwards and landed on his butt.

"Next, there's the next trap……"

The last resort and the final resort.

There was a drop trap that drops you into a natural cave dozens of meters below ground.

If you can't kill it, you should at least get rid of it.

The Blood Offering technician quickly runs away, emptying the room and heading towards the next trap.

As he kept falling for traps, he became accustomed to the sound of arrow traps exploding.

Bang, the moment the first protest sounded, I thought, "Oh, another arrow was coming," so I stepped forward and launched myself with a powerful lunge.

The floor rattles as you pass by fiercely, revealing a densely packed thorn trap.

Hmm. Oh, my. The floor was opening up.

It was natural to panic and not know what to do when you are caught in a drop trap.

But if you perceive that it doesn't do much harm, then it becomes nothing more than an annoying obstacle.

Well, it was already a white uniform with red polka dots embroidered all over it.

Qing twisted her waist in a counter-movement, and she quietly folded her hands in front of her chest.

Because my chest was already tied up so tightly, if I got stabbed, it would turn into a red top instead of a polka dot pattern.

After a dizzying free fall, groan.

My shoulders and the sides of my thighs are tingling!

And then, the blue rolled over the thorn blanket and slipped through the gap between the blades.

After lying down a few times, I found that it was much better to fall between the bars and get up than to press my body weight against the bars.

It was at that very moment that Qing was trying to get up from between the bars.

Vision darkens rapidly.

And then bang! A deafening roar.

Only then did Qing's spine tingle.

If you were lying on the bars of a self-defense weapon and got crushed, wouldn't you have ended up as a corpse with the bullets piercing through it?

My heart sank for a moment.

Sister! Hey! Hey, what should I do… …!

The amazement mixed with the watery sense of hearing of the Qing was captured.

It was a wish I hated more than death to worry someone.

Qing shouted urgently.

"Don't panic! I'm fine! Just move the rock away!"

It was a sound of the Buddha's body hitting a rock with a loud noise, just in case he couldn't hear.

Then, at the sound of people moving busily, Qing felt relieved for a moment.

How much time has passed?

As I was lying face down between the bars, the ceiling resting on the thorns suddenly split in half and a bright light burst out.

When Qing turned her head, her worried eyes sparkled in the shadows cast by the backlight.

A deep blue flower blooms in Qing's eyes.

It was a moment when the fever suddenly rose.

I somehow survived because it happened to me, but what if the kids got hurt?

For a moment, the miserable fate of his friends impaled on skewers flashed through Qing's mind.

He grabbed the string that was hanging down.

Two little kids running towards me as soon as I got up.

I can feel the vibration of the baby trembling in my arms, as if I was very surprised.

Qing patted the two little ones on the back and hugged them tightly.

"It's okay. I bounced it off. I'm fine."

Rather, it was a sight of the trapped party offering comfort.

But what else can Qing do if she gets angry?

All you can do was vent your anger by throwing a tantrum and destroying traps.

But what can you do in this situation where you're seething with anger right now?

All the trap pups were searched.

So, Qing bangs! With an angry fist, he hits the wall where the arrows are sticking out.

I used to wonder why people would get so angry and bang on the wall and do stupid things like self-harm, but after actually experiencing it myself, I understood why.

Thump! Thump! Thump! The continuous outstretched fists create holes in the wall, and the shape of the wound resembles a spider web with multiple layers.

And then, bang! Crash!

The wall, unable to hold on, crumbles down, revealing a dozen or so iron oars fixed in a small room hidden beyond it.

"Hmm?"

Well, since there was an iron oar, the iron oar must have flown.

However, a box placed on one wall caught Qing's eye.

I went closer and looked inside, and it was full of iron bars.

Qing, who was picking up one of the dogs and looking at its surface, suddenly raised the corners of his mouth.

"Master, look at this. It looks like a spare iron. Isn't there a lot of dust on it?"

Tian Yuxue frowns sharply.

If it's a one-time-use trap, there's no reason to keep a spare iron.

The fact that there was a spare iron means that the iron oar was brought out to be reloaded.

Of course, it could have been brought there when the Shingajimyo Shrine was built.

But if it's an arrow that's been left for over a hundred years, wouldn't it be normal for it to be covered in dust?

After Tian Yuxue removes the iron bars at the top, shiny new iron bars appear underneath.

"I told you, it feels like someone was watching and setting a trap."

"Hmm."

This was Tian Yuxue, who has been criticized several times.

Perhaps because he had nothing to say, he changed the subject.

"I heard there's a separate entrance to come in to reload. Hmm. I think it's over there. You probably have to climb down a rope ladder or something."

Tian Yuxue points to one side of the ceiling.

Anyone could see that it was an artificially created hole.

Qing jumped at him and dove into the hole.

I reached out to the left and right, touched the wall, and climbed up through the hole.

How much has it risen?

It's about the time when the area below appears as a small square.

With a thud, Qing, who had his head stuck at the end, firmly pushed both walls with his feet to secure his body, and raised both arms upwards with all his might.

Then, with a heavy feeling and a creaking sound like metal being twisted, the ceiling opens.

-What's there!?

"Just a moment!"

As the blue sky rises, a stone chamber with a rather lively feel comes into view.

From the start, isn't it suspicious that the lights are on and the view was bright?

Next to the hole I came up through, there was a pile of rope ladders driven in with stakes.

The Blood Offering technician was looking into the observation windows next to the next trap.

However, it's not that far away, but there was no sign of it appearing.

He thought she must've been very careful to protect herself after being badly hit by a trap.

"Hmm. It's past time to come…"

The technician muttered to himself.

There was one voice answering him.

"Really? It's past time for someone to come?"

"Well, that girl-"

The Blood Offering technician, who was about to continue answering, suddenly stopped talking and froze.

Originally, it was called a monologue because there should be no response to what was said.

"That girl? Who is she? Is she someone I know?"

It's a voice that somehow has a bleak and murderous quality to it.

The Blood Offering technician turns his head with difficulty, like a rusty engine that creaks.

There was a woman there, smiling brightly, revealing her pure white teeth.

The Blood Offering technician felt his heart sink.

Because the woman's eyes weren't smiling at all.