\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (12)}

As soon as Qing turns his back, a stern voice follows him.

"Yun Yuanying! Come back immediately! Your words have opened my eyes and given me a mission. Your revolutionary thinking was truly like that of my teacher! Do you truly intend to turn your back on the revolution? Are you truly only trying to avoid crisis with your lies? If not, then return immediately and declare your intentions to your comrades!"

"Huh, Heuk-i, what the hell was Hilki-eun-ga, algeun-ga, hahi! Hehe, that's right, kid!"

Qing, still holding venom in his mouth, answered with a roar.

He said that if there was no enemy, it's better to reveal it or not, and now was the time to do so.

"Stand there!"

"Stand there!"

"Stop, you little shit!"

The voices of the three fools selling the door are in unison.

Just like when they were knocking down the door at the west gate, they were three of them moving side by side as if they were one body.

Qing glanced back and thought, "That fat, fat piece of flesh was just too much of a rip-off!"

Well, it's not really a scam.

The Diamond Indestructible God Skill was so hard and solid that when it collides with an enemy, the enemy will only be hurt.

Because the meat itself was soft and squishy, ​​hitting it with a chunk of meat doesn't have much effect.

Qing's countless battles and experiences have not given him insight into martial arts.

If you just try it out, it doesn't seem to have any particular power other than blocking your breathing.

It wasn't that Povidone was carrying a sword for show.

So one, two, three, four.

Well, did you get rid of those two?

Qing unconsciously performed a ritual to pray for safety.

And since Qing was a Taoist priest who had eaten ancestral rites food, it was also a very spiritual ritual!

"I'll kill you!"

"Kwaaaaak!"

Thanks to that, two men jump out screaming between the flowers.

One of them was spitting blood and the corners of his mouth were covered in blood.

Another one was shedding tears of blood from his left eye.

However, both of them were in a state of full-blown rage, their eyes wide open.

The Mine of the Horse!

This was the crucial difference between real and fake flowers.

If poison enters your eyes or a small amount of poison seeps into your danjeon, it's normal to immediately sit cross-legged and turn your back to protect your body first.

But once anger truly rises, the murderous intent takes over the body and it rushes at the enemy without knowing how to take care of itself.

At that ominous aura, Qing swallowed without realizing it.

"Gasp, gulp."

A fiery poison that burns the esophagus!

The remaining venom sloshed down Qing's throat.

Since humans were not originally designed to hold liquid in their mouths, it can be said that they held it in for quite a long time.

It seems like he's excited to ingest some deadly poison after a long time.

A strange, yet not bad, subtly refreshing sensation, like a parasitic salamander perched on your stomach, shaking your intestines. What was this, Miss?

A bottle of alcohol has this kind of talent? Are you joking around right now?

It's been a while since I've had a drink, and my stomach feels like it's been stabbed.

Below that, it's shaking and shaking.

Meanwhile, the two masters who were thought to have been defeated evolved into mines and closed the distance while spewing fire from their eyes.

The sight of a person and a weapon flying towards the target, blinking and changing into one of two depending on the focus.

"This was really going to be crazy!"

It was the very moment when Qing shouted.

Thud!

An arrow shot out from the wall with the characteristic explosive sound of a bowstring returning.

The one-eyed mine that was running straight at him was hit by it and bang! The arrow blocked by the self-defense device flew in all directions.

Instead of bouncing off the arrow, the one-eyed mine lost its bearings and crashed into the wall, rolling along the floor.

The blood-spitting side that increases its speed even more, the blood-spitting mine!

Then suddenly, with a loud bang, it fell down.

At the same time, the trap door opened again and the lid slammed shut.

Ah! Master! Children!

Now that the Blood Cult bastards have been dealt with thoroughly, who will be the one to trigger the trap?

Qing raised his thumb and, not knowing where the observation window was, signaled by sticking it out in all directions.

The unmanned aerial vehicles chasing after them can't understand what on earth they're doing.

But since fools are not naturally suspected, if you think about his words and actions, it seems like he was mocking them in some way.

Qing runs out again, and the three masters throw Kang-Hwan repeatedly.

"Kwaaak!" "Kill me, kill me, kill me, kill me-"

The one-eyed mine roars, the trap lid explodes with a bang, and the blood-spitting mine follows with an eerie muttering.

Meanwhile, (former) Dokgo Prosecutor Jong Jeong-pil was the only one who followed along lightly.

So, Qing also loses his mind.

Aiming at the limbs, the strong ring keeps flying.

When the killing spirit suddenly rises, the mines fly in and swing their blades, causing the sleeping dead to slide and roll forward… … .

It was an indomitable race where you overcome the wind and fall seven times and get up and run wildly and bewilderedly.

Run, Ximen-cheong!

If the ground hadn't opened at that exact moment, arrows had been shot, and rocks had not fallen, they would have been caught and decided long ago.

It was thanks to the fact that the Blood Cult left behind a lot of unused traps to control the number of survivors.

Qing jumps up and down, rolls around, jumps up and rolls around again.

Jump into the sky, step on the ceiling, thump thump, step on the ground, step on the wall, thump thump, thump, thump, push the ground, thump thump.

Flapping, flapping, flapping, shrug shrug.

No matter how much I say, I'm starting to feel out of breath.

Isn't this extreme physical training where you jump up a couple of steps, fly, roll on the ground, jump up, jump up a couple of steps, turn like a swallow, kick the walls left and right, fly, jump on all fours, go forward, go forward, go forward, go forward again, and repeat this process?

There, he would sometimes beat up those who caught up with him, and when he was bored, he would catch a piglet weighing over 300 pounds that rolled by, spin it around like a shot put, and throw it at them!

And so the series of chases continued-

Suddenly, the sky widened to the left and right and Qing jumped into a large stone cave.

Beyond the vast cave where still-warm corpses were strewn, five passages were dug.

A color comes to Qing's face.

Ah, here! The cave where we were told to kill each other!

There really isn't much left now!

Even without that, sweat was pouring down my face and it was already dripping down my chin.

How could I not be happy that there isn't much left after overcoming that much discomfort?

"Damn it! That bitch! I'm really going to run away!"

"The man from Jungwon was so stupid! The entrance was blocked! The woman who turned around was blocking herself with a wall!"

"You stupid idiot! Haven't you seen her use her strength? She's just trying to break through the door and escape!"

"I'm not a cult member! And you fat pig are stupid! If you break the door, the passage will collapse, \#\#\#!"

Amukhaprap suddenly starts cursing at them.

And Jun Ki-chung and Jang So-nam also open their eyes wide and open their mouths.

Weren't those three people who had been busy cutting at the west gate and had destroyed the passage?

What if the stone gate inside was like that too?

"Stop it! That bitch was trying to collapse the passage!"

The three masters of similar skills begin to run at an even faster pace.

I am starting to urgently display my skills that I have been hiding until now.

However, Qing also squeezes out his last bit of strength as he approaches the exit.

As I push myself past my limits, pain throbs through my ankles, knees, and hips with each step.

But was now the time to preserve your body?

Once you get out of the Shingajimyo, you can throw away your Inpimyeongu and return to Ximen Qing from Yun Yuanying, even though the mountains are full of obstacles on all sides.

The three idiots, Qingqing and Qingqing, follow closely behind as they enter the passageway across the stone cave.

However, the movement of the blue was much more comfortable.

The first reason was that the two mines that had been following them, causing chaos in the Shingeomhapil and Shindohapil, disappeared at some point.

The blood-spitting mine fell down, panting and exhausted from the weakened danjeon where the poison had spread, and the one-eyed mine fell down as the poison had spread along the way.

There was no way that Qing would know these facts.

The second reason was the structure of the secondary passage that's subtly curved there.

Because if I just stuck to the inside wall that was bent, I could automatically escape the straight line of the three idiots' strong attack.

As Qing runs desperately, a stone gate was revealed on the other side, blocked by lightning.

But then what do I do now?

To cut a stone gate, you have to stop, and to feed the government, you have to stop yourself in the process of converting all the speed into power.

then?

Pierce with your body!

Finally, Qing steps on the final awakening.

Qing, stretching his body like an arrow, raised both his fists forward and flew into the sky.

"No!" "Stop!" "\#\#!"

He shakes off the three idiots' single blows and Qing's two fists break through the wall.

Finally, beyond the wall, beyond that-

Bam!

However, Qing's grand plan was only half-effective.

Because, compared to the shoulders that were hunched over with both arms raised, the hips were excessively wide and the muscles attached to them were very thick, along with the fat layer.

Thanks to that, only the upper body was outside the passage.

Lower body? Inside the door.

Who can I blame for that?

If you want to complain, should you complain about that huge butt?

"Miss, why isn't this coming off?"

The upper body of the blue rose protruded from the stone wall, or to be exact, it was a blue rose that only rose above the temple due to the thickness of the stone gate.

And the three idiots who were chasing after Qing are dumbfounded.

I let out a scream without realizing it as I saw Qing breaking through the wall, and what I saw was the lower half of his body sticking out of the wall.

That's the lower half of the body that's rolling its feet.

Looking at her plump butt, I think she looks fit.

"Hmm?"

"What was this?"

"Fortunately, the passageway doesn't seem to have collapsed. Hmm. For now, let's try pulling it out."

"Do you need to pull it out? Just ask me like this. Hey, you brainless beauty, can you hear me? Can you hear me?"

-……yes.

Somehow, a dead voice was heard.

Jang So-nam asked with a chuckle.

"So, you plan on staying put?"

-I wasn't planning on doing that. Um, it's a little embarrassing, but could I go over there?

"Well, that's up to you. Okay, let me ask you something first. What's the secret to the Absorption Technique?"

-Even if I say it doesn't exist, you won't believe me. But what can you do if it really doesn't exist?

"Really? Well, that could be the case."

He was surprisingly a man who was convincing.

However, the reason I was convinced was not because of faith, but because of logic based on what I saw.

"Isn't this girl stealing the emergency supplies?"

"Didn't you see the corpses in that room? Not just the dried ones, but the ones with their hearts ripped out. They'd been dead for a day? Or two? It was a stone chamber, so I'm not sure, but they didn't die immediately."

"Ah. I see."

Jun-gi-chung nods his head to him.

What if this girl somehow led people into the treasure room a day or two early, and killed the rest to monopolize the divine power?

There would have been ample time to memorize and destroy the new technique.

"You Zhongyuan bastards. You only speak what you know. What was that, you rude bastards?"

The two pretended not to hear.

"What was that, you little pig!"

Even though Amukhaprap was rampaging, he was still ignored.

In the meantime, Qing's voice was heard.

-Excuse me, I'll go over there first.

"Come out slowly. If you do something stupid, you'll spend the rest of your life without legs."

In that case, the waist gradually grows from the lower half of the body, wiggling and squirming.

The legs that were floating in the air and flailing around touched the ground and came out again, groaning -

-Oh, my arm was stuck. Excuse me, but could you please break down the wall a little?

That was only natural.

When I entered the wall, I had my arms raised and my shoulders rolled up, but now, isn't it like they're all spread out?

"……You do all sorts of things."

When Jun-gi-chung was so dumbfounded that he just shook his head.

Whenever Qing was polite, it's always at my disadvantage.

And we must always keep in mind that this cowardly behavior was always a process of building momentum.

There are two ways to break through a wall: by pushing with your fist pressed against the wall, and by pulling your fist in and pushing with all your might to hit the wall.

Which of the two would be more destructive?

Qing had pulled out his buttocks as far as he could and had both legs planted on the ground, so he was ready to kick forward.

That also meant the car was ready to launch.

Since they are greedy for the divine power anyway, they wouldn't go so far as to threaten my life, right?

It would be good if you tried and succeeded.

If you fail, at least apologize.

So, both arms of the blue one shouted "Manse" and then violently poured down, and from the soles of the lower body's feet beyond the wall, a wave of heavenly magic soared.

bang!!

A loud noise and a terrible pain in my pelvis.

The body of the blue dragon at the same time!

Qing rolls on the floor and suddenly stands up.

"Haha! You idiots! You live there! I'm going home! I'm the super brainless, beautiful girl, Choi Kang-nyeo-nyeong, Unyeon-yeong!"

-Hey! It's you again!

Turning his back to the roar coming from the gaping hole, Qing runs out again.

The sound of banging on the stone gate follows, so I guess they'll break it down and chase after me soon.

Haha! It's already too late.

In a moment, you can go out and run into the mountains.

Qing runs away laughing.

The passage gradually becomes darker.

The brightness of the passage itself remained the same, but to Qing, it seemed to be gradually getting darker.

Because a bright light was coming from the open passageway in the distance.

And so, at last, Qing throws himself out of this disgusting cave of blood sect and into that bright light.

"Come on, you arrogant world! I'm back!"

Qing waves his arms with a roar of victory!

It's the kind of nonsense that always comes out when you're in a good mood.

And as if in response, dozens of pairs of eyes look at Qing.

Well, that was only natural.

Wouldn't many people want to go into a cave that's dangerous and suspicious to anyone and look for treasure?

Or would there be many people waiting outside and trying to steal it?