\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (11)}

Some people have endured great humiliation for a greater cause.

That famous Hanshin crawled under the groin, under the other man's dick.

King Goujian of Yue ate his enemy's feces.

The assassin Ye Yang covered his body with lacquer to turn his skin inside out and swallowed hot charcoal to burn his vocal cords.

And Qing flirted and wiggled her buttocks in front of countless men.

It was truly a disgrace worthy of being recorded in history. If I were to leave behind a four-character idiom from the past, it would be something like "尻颭沽嬌" (Twerking).

Still, it was a task that could be accomplished by covering one's face with a veil, stealing the name of Qing, and borrowing the power of the super brain-killing beauty, the strongest girl, the most beautiful girl, the most beautiful girl, the most beautiful girl, the most beautiful girl, the most beautiful girl, the most beautiful girl, the most beautiful girl, the most beautiful girl, and … and the most beautiful girl, the most beautiful girl, the most beautiful girl, the most

It's Yun Yuanying who was embarrassed, not me!

The lewd and obscene prostitute here who was performing the duty of bathing in a brothel was not me, but Eon Yeon-yeong!

I barely managed to endure the goosebumps and the shame of wanting to die through self-destruction or personality splitting.

However, the problem was that it was unrelated.

The self-proclaimed super-brainless girl was really just a self-proclaimed one, and her face with the human mask was nothing special.

If Qing had claimed to be a super pretty girl with a straight face, everyone would have accepted it without a word.

The original appearance was that of the most powerful force on earth, but on the other hand, no matter how seductively one wears a human mask and acts, the power was bound to be clearly different.

The original body parts of a woman that make men angry are her breasts and buttocks, but didn't she just wrap them up tightly to disguise them?

The blue hides the heart! The heart hides the strength!

How could others know what you have hidden?

So, the power of the Tangseontal duty of shaking the breasts and shaking the cheeks was bound to be halved.

For that reason, the attempt to escape, even enduring the humiliation of the Ximen Qing, could be said to be truly bold.

Because she used a means with half the power while hiding her beauty.

Wasn't it a situation where there were even a few women in the seats?

In fact, women also like dirty things, and they were like, "Oh my god, what was that? It's so manly. But I also need to work hard to learn the new skill, so I covered my mouth and watched with my eyes focused.

So it seemed that Qing's bold attempt might miraculously succeed.

If it weren't for the presence of Povidone Jang So-nam, the master of Unrestrained Realm who was in charge of obesity among the best in the world, this place would have definitely been successful.

"That, that bitch! That! That!"

Jang So-nam was a master of Yukpo Sam.

Yukpo Sam was a martial art that boasts indestructible power, or defensive power, of the level of the Diamond Indestructible.

If the Diamond Indestructible provides absolute defense based on the principle of strong and hard, the Yukposam provides absolute defense based on the principle of soft and capable steel.

But compared to the Shaolin monks who practice painful training by beating, breaking, and destroying their bodies every day to attain the indestructible Vajra, what about Yukpo Sam?

Just eating delicious food all day long while you're awake and sleeping when you're not eating was not training, it's just like experiencing paradise in the human world.

If you compare it this way, you might think that something like the Diamond Invincible Shingong was just a struggle, while Yukpo Sam was a much more arduous study suited to a new skill.

But that's not all!

Surprisingly, Yukposam doesn't just provide physical defense!

When Yukpo Sam reaches his limit, his body transforms into a turtle-like shape.

The flesh attached to the torso was round and forms a round flesh above the elbows and knees, making it look like short arms and legs are attached.

Anyone who sees it can't help but exclaim, "Wow! Turtle! Grow! A male! Anyway, it's something similar!"

If even the long limbs are barely visible from the joints, then what will happen to the man's dick?

So, the person who was left behind was not a ghost, but a ghost.

The resignation of those who have given up completely also brings their defenses against women to their limit!

This was the mental defense function of Yukposam!

It must be a truly terrifying effect.

"Isn't that thing running away? It's just slipping away!"

"I'm not running away! This body, Yun Yuanying, was so suffocating in a cramped space! Even the super-brained, beautiful girl, as a manly woman, should live in a spacious place. Why should I be huddled in a semi-basement like this? Everyone! Don't worry and focus on your training! I will never run away!"

Bang, as soon as Qing finished speaking, the floor was trampled and shattered, scattering black, mold-like spores.

daily report.

Boom! This Bo.

"That girl was running away!"

"Catch him!"

"Just give me the new skill and go!"

And bang! Sam Bo!

The new form of Qing, which has reached its maximum speed in Sambo, continues to stretch and cut through space.

After that, the pursuers rush in, filling the passageway with noise!

However, they were entangled and had difficulty gaining speed, when suddenly, a terrible scream erupted: Kwaaak! Aak! Kwaaak! Six people suddenly jumped out and increased their speed.

The three stone gate destroyers of Unrestrained Realm, who were born on different days but are not particularly close, are destined to destroy the same gate together.

"You bastard! Are you going to betray the revolution? Are you going to abandon the oppressed and weak of the world? Stand right there! Stand right there!"

The real Hong In, who appeared two hundred years earlier, suddenly shouted.

Qing glanced back and thought, "What the heck, it's not like some Unrestrained Realm master was self-dividing, and yet there are still two more guys whose names I don't know?"

"Damn it! Kang-hwan! Throw Kang-hwan! Aim for the mouth and torso! The legs! Aim for the legs!"

"This was really too much! I told you not to run away! I told you to go somewhere bright and continue! Yun Yuanying hates the dark! She hates narrow places!"

"A lie even a dog would believe! You crazy woman! Stop right there! Stop! Stop! Stop, you punk!"

The blue one runs.

Qing looks behind him.

Jump up and avoid Kang-Hwan.

Looking forward, then back, looking forward, then back, the flying Kang-Hwans, shedding light, draw various arcs and approach.

Then, Qing kicks the ground and runs up the wall.

3D lightness!

It could be said that this was the appearance of a master who has reached the extreme of light-hearted study, but since he keeps jumping up and down like a rabbit, his speed keeps dropping.

"You bitch!"

Jang So-nam's voice bursts out loud.

Qing looked back, and, ugh, no, shit, what the hell was that, what kind of martial arts was that-

I thought the already round thing was suddenly fired as if from a cannon, but it was rushing forward in a complex straight line, bouncing up and down, left and right, and bending!

"No way! Does that make sense!"

This was the absolute good that separates the supernatural and the supernatural realms, the power of thought.

Martial arts touch the mind and bend the laws of all things, so you can bounce your body like a ball and launch a powerful attack.

Because it's a force that touches the thought, it ignores the angle of the bounce and does whatever it wants.

Then suddenly, a man with a long arm bounces off the right wall behind the blue and rushes in like a shell.

I know that that crazy lump of flesh can't be cut and that hitting it will only make it ripple.

Then what?

Squeak!

He stops abruptly, scraping the floor of the blue.

Then, the large body of Jang So-nam passes precariously in front of Qing.

The rotating place was where the man's body touches the front and his eyes meet Qing's.

At this time, time seems to pass slowly.

At that moment, both of Qing's hands stretch forward.

The outstretched hand shoots into the flesh!

And the greatest evil force in the world, no, the greatest evil force in history and the past, grabbed hold of the flesh.

The soft and squishy ladder wraps around both palms, and for a moment, it feels like…

This was soft and chewy, this was like… … !

And then a feeling of self-loathing started to creep in.

Qing grits his teeth and steps forward.

Since you caught a heavy object flying to the left, the load of mass plus acceleration was naturally applied to your body.

but-

"Euryaaaa!"

Qing turns his body with all his might, accompanied by a scream that scratches his vocal cords.

Boohoo! Boohoo! The mass of Unrestrained Realm's stairs circles around Qing at a fierce speed, and with each turn, its speed increases. Boohoo! Boohoo!! Boohoo!!! The air roars.

And then there was a point where Qing suddenly realized something.

Ah. If I turn it any further here, my arm will fall off.

So Qing let go of his hand.

Because arms are precious.

Wedge!! Povidone has been fired.

At this very moment, a new record has been set for the fastest human movement by any means, in both the East and the West.

An unprecedented record that would not be broken until the advent of flying vehicles!

Amukhaprap moves his lips roughly as he watches the fat guy flying towards him.

"Mother- keuk!"

It was unclear whether he suddenly missed his mother after leaving home in a foreign land, or whether he was interrupted mid-way while trying to curse his parents in a foreign language as a foreigner who does not know how to speak the language properly.

This was because the skinny lama, who was nothing but bones, dug deep into the flesh of the fattest man in Zhongyuan and became one with him, flying backwards.

The Amuk Haprap was so light that it couldn't slow down at all, so it flew straight into the treasure hunters who were chasing the Qing after the masters.

Bang!!!

People fly like corn against gravity.

Like a Western sport where a ball was rolled over a triangular obstacle course, people were flying with exhilarating screams.

"You bitch!!"

"Ugh, ugh! Ugh!"

An unknown martial artist with a strong sword thrusts his sword vertically, as if he were going to split the blue in half.

For a moment, Qing's eyes flashed.

And then, as if to say, "If you want to go, go," he takes a step closer and presses his forehead against mine.

Did Qing suddenly choose death?

Or was it a display of the pride of the world's greatest stone head, who believes that he can easily block anything with his head as strong as Mannyeonhancheol and his self-defense skills?

Neither.

The master was startled and withdraws his strength.

What he wants was the secret of the absorption method in Qing's head.

There was no ability to see the soft brain inside and read it with the tongue.

What's there to fear from a blade without a blade?

The left hand of the blue man blocks the Tao, and the right hand, pulled tightly, thrusts towards the exposed dantian!

The master flies far away with his body shaped like the Chinese character for "hye" (匸).

It could be said that the future was destined to be bleak, as he was hit squarely in the dantian by a properly charged small-scale magic attack without paying attention.

And then the first fool, Jun-gi-chung, clings to me with his sleeves fluttering.

When Qing shook his left hand, which he had been holding tightly, the sound of an arrow being carried was loud!

"Memorize!"

Jun Ki-chung, greatly surprised, swings his sword.

The sound of glass breaking.

Meanwhile, another master of the flower garden approaches.

Chaeng, chaeng, do and bare hands keep clashing.

Now, it's not the Jeongpa Taoist Ximen Qing, but the Blood Cult's minority witch, the brainless, beautiful girl Eonyeongyeong, so she was a minority magician who uses it without any regard for others.

Of course, it was a look I hadn't seen before, but whatever.

"Ugh, up, groan."

"What! If you're going to speak, speak properly!"

For a moment, Qing's lips curl into a round shape.

It looks like it's stretching out forward as if it's exploring a lover's lips.

And in between, sizzle!

Like a water gun, a stream of liquid shoots out and hits the eyes of the master of the flower garden.

"Ugh! You cowardly bitch! Aaugh! Dirty!"

It might be a reward for some, but it didn't seem to be a reward for this master of the flower garden.

"Haha! This was so funny!"

Qing proudly shouts.

It was a sound that was completely incomprehensible because there was still something left in my mouth.

Still, the Unrestrained Realm master should have understood.

Haha, if I had known that this was blood poison, I would have plucked out my eyes and thrown them away like Mr. Hahu Mo.

Wasn't there another dangerous guy?

Yeah, commie!

As Qing turned his gaze, he slowly approached while holding his weight, and then came the Dokgo Sword Jongjeongpil, no, not the Dokgo Sword anymore, but the Red Sword, or the Red Wi Sword, or the Red Wi Sword, the Social Sword, the People's Sword, the Musoyu Sword, etc., the red one slowly holding his weight and approaching.

Why hold the weight?

Do you think you're some kind of ultimate mastermind or arch-enemy?

Anyway, isn't it something to be thankful for?

Qing turned her back without a moment's hesitation as Jongjeongpil approached her.