\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (6)}

Amazing fact!

Qing was the most vicious of the vicious.

If you kill them nicely, you can kill them nicely, but unless it's urgent, there's no way to kill them nicely.

If you've ever been treated badly by a blue person, you probably already understand.

Actually, everyone knows this, so why are you surprised?

But no one survived after being attacked by the Qing.

So, the disgusting habits of the Qing are always closer to surprising.

In any case, for that reason, the attitude of the Blood Offering leader, Amharong, was not to Qing's liking.

Why, if this body has worked hard to get here, wouldn't it be better to pretend to be in pain, crying and screaming in anger, 'Why can't I be happy!', to make the torment less enjoyable?

This was unjust.

If I've put in this much effort, shouldn't I be rewarded with something?

And even though the pain, sorrow, and screams I create are a thrilling reward that sets my whole body on fire.

"Is that even a threat? Even those ignorant robbers are willing to spare your life if you hand them over. Tsk tsk. Getting robbed by such a worthless bitch. How can I live in such shame?"

"Can't you at least pretend to be upset?"

"I'm eighty years old. I always thought it would be today or tomorrow, but it's actually today."

The dark dragon walks out calmly.

Qing raises his sword in a flash.

"Sir, you don't seem to understand the situation. If you've lived long enough, you should at least pay the price. Lady Muyang, give me some salt. I'll skin it and pickle it thoroughly."

"Have you ever considered joining the Blood Sect? It's a place like this where you meet all kinds of talented people."

"Miss, can't you stop right now? Do you want me to break your leg club so you'll realize how precious your leg is?"

"You asked for the suction magic? Stop whining and just wait."

As Amharyong said that, he grabbed the handle of the iron door on the floor in the center of the central control room and started to whine.

"These kids, rainwater got into the iron gate, so I told them to oil it, but they didn't listen to me until the very end. Even if they put a latch on it, it wouldn't be as sturdy as this."

Qing narrowed her eyes.

I'm confused as to whether this old bastard of the blood sect was just trolling or if he's really in a state of despair.

What if it's some kind of suicide trigger?

Why, don't secret bases like this have suspicious self-destruct functions?

"You're not joking around right now, are you? If you pull that, the entire stone chamber will collapse and we'll all be buried underground."

"You poor girl. Why would we bother digging up a perfectly good mountain and causing such trouble in the first place? My job was to gather the bad guys and give the worst of them the power of absorption magic. Now that I think about it, even magic has its masters. With the perfect vicious witch here, the future of the martial arts world will be truly worthwhile."

No? Are you going to burn it?

You guys totally picked the wrong person.

You've been digging the ground for twenty years, so how happy would you be if the magic burns down?

Qing suppressed her urge to answer.

The Zhongyuan's ancestral rites were far more primitive than the Qing had imagined, and they didn't use any special fuel like the mysteries of the universe—the energy of heaven and earth—but they were still unknown territory to the Qing.

So let's put it aside.

Wouldn't it be nice to see the expression on the old blood cult members' faces if they were burned in front of them?

The dark dragon struggles for a long time, clutching the iron door handle, before finally collapsing on the floor, gasping for breath.

"Oh my, ugh, I can't eat this because it's so hard. Just kill me. My days are numbered. Why should I exercise for glory?"

"Miss, please step aside."

Qing takes a step forward, but a small force tugs at his sleeve to stop him.

When Qing looked back, there was no one there.

Why? Because I'm a kid.

When I looked down, I saw Chen Changming, with a very anxious expression on his face, appealing with his big eyes.

"It's dangerous."

"What can I do? If I go downstairs now and look for the magician, there'll be a lot of Sapa guys swarming there."

"but."

"And if you open it gently, you'll feel it all. If something feels off, just let it go, so don't worry."

Originally, I was a person who took great care of my own safety.

Even if you cut a person's torso with a knife, how can you be so sensitive that you can distinguish the sensation of each organ being cut? Wouldn't you be able to feel the tactile latch on an iron door?

Qing calmly grabs the handle on the floor and lifts it up.

The heavy, rusty iron door creaks and screams, piercing my ears.

The thick iron door, which must have weighed about 100 pounds, was covered in rust, so there was no way a second-rate old man could open it.

I opened it carefully and, huh?

It seems like there are no devices?

Finally, the iron door on the floor opened wide.

A small square of light pours in from beneath the exposed vertical passage.

It's quite high. Is there no elevator or anything?

Unfortunately, all the rope ladders hanging from the wall are of a primitive level… … .

Qing suppressed her regret.

"Okay. The soul-absorbing magician you've been searching for was down there. The door's open, so kill him or leave him alone, that's all you need to do."

"Huh. That's a funny joke. You go down first. I'll just leave you there and come back. Then, won't those bastards who got away with it take their anger out on you?"

"Is that what you usually say? You're the worst bitch in the world. The magic I've diligently prepared for has fallen to a villain like you. Well, twenty years of preparation paid off. Oh."

The dark dragon that had been babbling continuously finally got kicked once.

The female dragon, clutching its side, groaned and groaned as it squirmed on the floor.

"You're a blood cult scum, and you're saying nice things about your age. Do I look funny? You keep getting angry? You old man, do you want to die? If you want to die, you should beg more politely. Even if you ask me to kill you, I have to worry about whether you'll kill me kindly. Now you're just sitting there laughing."

At that, Tian Yuxue groaned.

It was a truly frightening sight to see a young woman kicking an old man.

Even though he knew that his disciple was a renowned Taoist priest of the Jeongpa sect and that the old man was an evil servant of the Blood Sect, he still had such thoughts.

In Qing's hometown, there was a psychological phenomenon called a "crawled dog."

This was because people have a natural tendency to feel pity for the weak.

In human evolution, protecting the weak was more advantageous for survival or something like that.

"Kuuuuu, why are you so angry?"

"I tried not to see any blood today, but it won't work. I'll just wait and see."

"Have you never heard that there was no one more scary than someone who says, ‘Let's wait and see'?"

"Okay. Just go down."

"Okay, let's go. Let's go. That green-haired girl was really ill-tempered."

"Wait. Okay. Mr. An. Mr. An was free now."

Qing untied the rope from An-ssi's neck and put it around Am-ha-ryong's neck.

"If you come down and do something stupid, you'll know, right?"

"For a woman like this to become a vampire witch? The world's future was truly bleak. Hehe."

The dark dragon begins to crawl into the passageway, laughing hilariously.

It was a poisonous creature that didn't groan even once, even though it was clearly visible that he was trembling and gritting his teeth as if his side was hurting.

Qing looked down at the sight, and suddenly grabbed the leash hard.

"Cough. Ugh, ugh."

The female dragon, who lost her rope ladder and was hanging by her neck, desperately reaches out.

The moment Amharyong's hand was about to touch the rope ladder, Qing shakes the rope and makes it fall.

Of course, the dark dragon, who had returned to the principle of pendulum motion, slammed his body hard against the wall and held on to the rope ladder with difficulty.

Qing looked down and smiled sadistically.

When Murong Juhee saw that expression, her expression became hazy, but fortunately, everyone else was too busy staring at Qing to notice.

"You keep telling me to kill you or let me live, but I guess you do want to live after all? I thought you'd just give up and give up because you kept saying you'd live all your life."

"Damn it, bitch, squeal."

"If you just talk, they won't understand. I've already experienced this before, so please take care of yourself. You know what I mean, right?"

"……."

This time, it was the female dragon who kept her mouth shut, as if she was quite upset.

Qing followed him into the vertical passage and went down the rope ladder about four steps-

Boom!

Suddenly, the rope ladder falls down without any strength.

The blue hanging there was also a body that, as a member of the world with mass, could not shake off the temptation of gravity.

However, gravity found Qing too funny.

At that moment, Qing stretches his arms and legs left and right.

As both feet and hands touched the wall, I was pushed away and then stopped in place. A strong force can resist gravity!

And then thump!

"evil!"

The weight on his back caused the tendons in his arms and legs to snap, causing him to groan in pain.

"Um. Sorry, buddy. Are you okay?"

"If you're sorry, can you come up quickly?"

The culprit was Nan-gong Shencai, who was climbing the rope ladder after Qing.

However, the line was quickly cut short, and only Nan-gong Shencai could survive. If the entire group had boarded Qing, it would have been impossible to guarantee that even the strength of the Yeohangjeok would have withstood it.

Of course, Qing could have held out because she was just a strong, ignorant woman.

Nan-gong Shencai stretches his arms and legs left and right, climbs the wall, and returns to the top in a somewhat ugly manner.

Miss, it was a trap after all.

Perhaps it was designed to boil over when a certain amount of weight was applied.

It's clear that the old man's schemes are no joke.

I just pretended to want to live because I was afraid that if I let my weight go down, people would get suspicious and not come down.

Even though I knew that if it broke anyway, I would fall too.

But you held on, right?

Miss, you can't just let that old bastard die.

Qing looked down.

"I'll go down here and retrieve the magic!"

Qing shouted like that and then slightly relaxed the strength in her limbs.

It was Qing who was pushed down the wall with both arms and legs.

It's the perfect thing to get your skin peeled off.

But it's impossible to harm the beautiful palm of a minority witch to this extent.

However, the shoes are hot, ah!

The blue folds its legs and sinks downwards, supporting its weight with only its arms.

Although the load on the arms increased, the advantage was that the body stood up straight after the legs were folded.

The blue slipped and finally landed lightly on the ground.

"Ugh. What's that smell?"

There are levels of stench, and the worst of them all was the stench of a rotting corpse.

The stench was so terrible that it felt like my nose was going to fall off, and Qing looked around, covering his nose.

On one side, there was a fancy box that looks expensive at first glance.

And the source of the smell was the dozens of corpses lying all over the stone chamber.

Most of them are dried up and twisted corpses.

Among them, there are a few ordinary corpses with holes in their hearts here and there.

What room was decorated with corpses?

It was when Qing was frowning and looking around.

"Keuk, keu, that fucking bitch, her lifeline, she's so tough."

"Oh! Old man! You're alive!"

Qing expressed his joy at the dark dragon lying on the floor.

It was a female dragon with two free legs, as if it had fallen gently because it was lucky.

Judging by the blood spreading from the corner of his mouth, it seems like he won't live long.

Qing smiled brightly at him.

I was going to show you how to burn magic, but it would have been so disappointing if you had fallen and died.

"You thought I was going to learn the magic of absorption? Damn, you were wrong. I'll burn you to the ground. Such evil magic should never be allowed into the world. Do you understand what I mean?"

"Keuk, keuk, ugh. Huh, do you really think you can do it? Is the absorption magic just a simple magic? It's a martial art that can make you the best in the world."

"Huh. I'll be watching you from there, whether I burn you or not. Okay. Opening soon!"

Qing hums a tune as she opens the box.

Of course, that doesn't mean I let my guard down.

I carefully open the box, feeling the sensation in my fingertips to see if there's another trap laid, and feeling if there's anything that feels off.

But surprisingly, it opens smoothly. What was this? It's fine.

There was a book of emergency supplies inside.

Judging by the unique crimson texture, the four characters of the Absorbing Law are written in crooked, bad handwriting, as if written in blood.

Next to him, a splendidly decorated dagger was neatly placed on a red silk table. Qing picked it up without thinking and was startled.

What kind of dagger was this heavy? It seems to weigh about ten pounds.

How can a dagger weigh ten pounds?

Upon closer inspection, it was just a simple dagger-shaped ornament, adorned with all sorts of jewels, without even a sharp edge.

Just by looking at it, you can tell that it's not something worth a few pennies, so just get it.

And then, finally, Qing puts his hand on the emergency bell.

A frivolous notification announcing the registration of a new martial art sparkles.

It was also evidence of a complete emergency.

Qing opened his martial arts window.

The name of the newly registered martial art sparkles.

[Heart Absorbtion Technique]

There were two deep furrows between Qing's eyebrows.

"Huh?"