\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (7)}

What the heck, was the status window broken?

For a moment, goosebumps ran down Qing's body.

The status window was broken, so that won't work.

If you're in a daze and want to try the medieval Western Regions instead of martial arts this time…

It was a moment when Qing's eyes trembled wildly.

A soft cough wakes Qing from his confused mind.

Qing's head suddenly turns.

"Hey, Grandpa, what's going on? You said it was a Essence Absorption technique, but why did you put Heart Absorbtion technique in it? You just changed the cover, right? Right?"

"Kuuuuu, keuhuk, heuuu, dagger, what about the dagger?"

"Shit, I'm asking first. Why answer a question with a question?"

"Haha, have you ever seen the Heart Absorbtion Sutra before? I wish I'd realized it later and screamed, but now that I've figured it out, I guess I'll go see it myself before I die. So, hey, how are you feeling right now?"

He was relieved.

In the first place, there was no absorption magic, and the answer was that a sub-heart magic was prepared with a cover change.

The status window was broken, what a terrible thing.

In that moment, cold sweat poured down my face and my whole body became damp, and I stopped just before a panic attack.

"Whew. I've endured it for ten years. Then I should say so. Me again."

For reference, in the phrase "ten-year-long-term", "sam" means "to reduce" and "su" means "lifespan". Ten-year-long-term means that my lifespan has been reduced by ten years, and it's an expression of how surprised I am.

"Hmm?"

At that, the dark dragon's eyebrows flickered.

"Shit, then the Essence Absorption didn't even exist in the first place. Why did I come here and suffer for nothing?"

"You've put decorations on your head, so don't be fooled by the nonsense. Think about it, and just live with it. You ignorant, foolish girl."

"What was it?"

"What's with the killing? If we really had the Essence Absorption Art, why bother digging up a rock mountain and set up traps?"

Qing, who was impatient, decided to just listen to the parts where Amharyong was having a hard time speaking.

"Well, it's the Blood Cult, right? Was there a reason the Blood Cult was acting so strangely?"

"You idiot. A divine technique guaranteed to be the best in the world? If we teach it to our disciples, wouldn't we be able to conquer the martial arts world with thousands of demons?"

"Oing."

Qing blinked with that expression.

This old man was incredibly persuasive.

Qing recalled the testimonies of the technicians.

He could have cleverly kept his mouth shut, saying, "Go fuck yourself (that's what Qing wants)," but there are many people like the weak, the bold, and the funny, who wouldn't have been able to come up with such a great plan.

Maybe it was the result of them all coming together out of revenge and deceiving the Qing.

Or maybe only this old man, who was a big shot, knew that the absorption magic was fake.

Anyway, the important thing was that I was fooled.

But it doesn't mean that Qing despaired or anything, so what can we do?

I had no choice but to return empty-handed.

"What? Then why did you dig the ground and sit there when there wasn't even any absorption magic in the first place?"

"Aren't you and your friends, young and old, the only ones who know that our blood sect was entangled? If you say it's not the Absorbing Demon Lord, but the Subsim Lord, and that it's a conspiracy hatched by the evil servants of the blood sect, who would dismiss it as such?"

"Ah. So that old man was the type who would spit out everything before he died. What if I taught him everything? Now that I know, I'll run away—"

Thud! Thud! Thud! Thud! Thud thud thud thud! Thud thud thud thud!

A loud noise cut off Qing's horse's tail.

A sound like something heavy was falling.

When Qing raised his head and followed the sound, he saw that the vertical passage from above was completely blocked.

"How? We cleared out all the Blood Cult guys."

"I weighed down the box. What do you think? It's so shiny, I couldn't help but reach for it."

"Ma'am. I wonder why a ten-pound dagger exists in this world."

I was just paying attention to the feel of the trap as I opened it, but I didn't know there were traps that would activate by reducing their weight.

Besides, if you think about it, isn't it a very simple and basic trap?

A trap that even the primitive people of long ago could easily use.

"No, what the hell was the problem? Are you even talking about something childish like, 'I'm going to destroy the world,' like an old man?"

"Kuhaha, as I get older, I seem to be able to let go of old grudges. Even though I still feel bitter, I don't feel like I'm gritting my teeth and not knowing what to do like I did when I was younger. I used to think that saying "time heals the wounds" was irresponsible nonsense, but that's not true either."

"But?"

"At first, they were tools to be raised and used. I thought it would be better to raise them as disciples than to train a dog."

When the organ-building technicians took on disciples, they carefully examined their intelligence and selected the smart ones.

Because organ transplantation was a realm of pure talent.

No matter how much you teach a fool, he will only repeat existing techniques and not be able to create something new and more advanced.

So, Amharong had no expectations at all from his disciples.

But that only lasted a day or two. He'd been digging rocks for at least twenty years, and after seeing Jang Je-ja for over forty years, he'd grown attached to him.

"Revenge? I never cared about that in the first place. I just thought, if I lived like this and died among my disciples, that would be a blessing in disguise. Heaven was cruel, but I thought, 'It's not so bad after all.'"

The dark dragon bursts into laughter.

"So, I can't help but think that even if I die, I have to make sure that at least one of you doesn't die a pretty death."

The words spoken in a strange manner and the hatred contained within them were quite chilling.

So Qing was happy.

No, this old man, even though he pretended not to know, was shedding tears of blood inside.

"Hehe. You should have said something sooner. If you had, instead of killing them all, you could have dragged them all before Grandfather and sliced ​​them up piece by piece."

"What a shame. I missed out on such a wonderful sight. Hehehe…"

"But did you know that? Actually, Grandpa's disciples aren't dead yet."

"what?"

The satisfied Amharong's eyes opened wide.

"Just killing the Blood Cult's filthy worms seemed too merciful, so I just roughly killed half of them and left them to die on their own. Even now, Grandfather's disciples are desperately searching for their Master. I hope he comes and saves them. Master, save me. Please. It hurts so much."

"You! You bitch! Ugh! Ugh, how, how can you wear human skin!"

"What can't you do? I've seen those Blood Cult kids do their tricks many times, and even if I kill them, I wish everyone would applaud and praise me for my good work."

Qing thought of the blood demons she had seen in Gwangju.

Those miserable downfalls that devoured their own mothers.

They were really funny guys.

Those murderous bastards who think they are the most pitiful people in the world.

Those scumbags who think that if they are pitiful, they will be forgiven no matter what they do.

"Grandpa was trash, and all his children are trash. For those who threaten to harm everyone in the world, isn't even death a mercy? What's wrong with a disciple? If you truly cared for him, you should have abandoned the blood cult and told him to take in a wife and children and live a normal life."

"You, you bitch, ugh……"

Amharyong was the worst conversationalist.

Even if you don't speak politely, you should at least pretend to listen when someone talks to you.

"Kill me, I'll kill you! You bitch!"

An old blood cultist with a mangled leg waves his arms with bloodshot eyes.

Even without that, his old body, which was already vomiting blood with its internal organs bursting, was rapidly worsening as anger grew, and his complexion turned dark and he appeared to be dying.

Then suddenly.

"You, you won't die a pretty death. Heh, heh, go ahead and wait…"

It was the moment when the Blood Corps under the Blood Cult was completely annihilated.

There might not be total annihilation, as there are still those who are still alive and writhing above.

Qing-i smiled brightly, ah, that was a good sight.

A bad guy's end must be miserable.

I'm sick and tired of being so evil all the time, always going first and waiting.

But still, every time I hear it, my ears are filled with ecstasy and a heat surges through my body. Ah, I really live for this taste.

Qing looks around with eyes full of evil intent.

The old man was dead, and the magician who absorbed the essence never existed in the first place.

But it's not like there's no income at all.

If I keep going like this, I'll end up collecting all the teenage magicians.

It was while Qing was looking inside the stone chamber to see where he should go.

A violent vibration occurred all around, and stone dust fell down.

Walls collapsing from eight directions simultaneously.

Beyond the open stone chamber, which was wide open in all directions, treasure hunters and warriors fill every direction, sending out astonished looks.

Qing, who was looking around at the bamboo, met my eyes and only then spoke.

"Ah. Shit. I'm done."

The masterpiece of the Gonghyeoldan, the Bloody Ramdaegye Fisherman's Journey, was originally intended to cause great discord in the martial arts world by using the non-existent magic of absorption as bait.

So, the final ending, the ending that marked the end of the grand plan, was the climax of the story that everyone in the Gonghyeoldan had been waiting for.

It's not like Amharyong did anything special for Qing.

If the box was opened, it means that someone has gotten their hands on the fake magic absorption potion, and of course they will want to run away safely with the secret.

In the meantime, should we just leave that suspicious vertical passageway right above our heads?

So, when the ten-pound weight (dagger) disappears and the engine was activated, the vertical passage leading to the central control room was blocked.

Then you'll probably try to run away now.

If you run away safely, there will be no bloodshed in the world of martial arts.

And it's not fun to watch for the Blood Offering technicians either.

So then, all the stone gates and passageway partitions of the Shingajimyo will collapse, giving all the treasure hunters inside a final chance to seize the Absorbing Magic.

Then, the technicians of the Blood Offering Corps were going to hold a celebratory feast while watching the most exciting scene of the Blood Offering Corps, which they had invested twenty years into.

The leader of the Blood Offering group was dead and the technicians under him were dying.

And Qing was the first to open the box and pop his head out into the main character's seat, which was the target of all treasure hunters.

Suddenly, all the doors collapsed, and even the stone walls that we didn't know were doors collapsed, revealing a room in the center that anyone could see.

And there was a woman with round eyes looking around.

And in that hand was a book.

Book? Book!

"It's an absorption magic!"

When someone shouts, everyone adds a word about magic or secrets, and the atmosphere becomes like a noisy market.

In the center of it all, Qing takes a deep breath.

"for a moment!!"

Qing slowly chose his words, facing the gaze pouring in from all directions: front, back, right, left.

Qing slowly sweeps her hair.

It was fake hair attached to the face mask.

Qing's heart gradually calms down as he feels the softness in his touch.

Qing was now in a state of being turned over by the iron iron!

In other words, his identity was hidden.

Inpimyeongu was invincible and Ga-myeong was a god.

Qing's confidence soared.

Let's see.

Now it says that this was an absorption magic, but even if it's actually a sub-sense magic, would they believe it?

Only then did Qing realize the purpose of the corpses displayed in the room.

It was not only to set the mood with the skinny corpses and to inform people that there was a magic absorption device in the box, but it was also a decoration to convince those who saw it later when the door opened that it was a magic absorption device.

And another kind of corpse.

The purpose of the corpses with holes in their hearts could also be realized.

It was to block out the truth even if it was discovered that the absorption magic was fake.

This isn't a magic absorption technique, it's a sub-spirit technique!

Shut up! What you learned must be the Subsimgong.

Do you think I'd be fooled into giving you something like the Subsimgong while stealing the secret of the Divine Power?

That corpse with a hole in its heart was proof of that!

The corpses are so fresh they could jump up at any moment. Aren't they the victims you killed to gain divine powers?

Then, no matter what you say, it will be understood.

He reached a conclusion.

Anyway, it's time to turn the human face inside out.

Because if you somehow manage to shake them off for a bit and then secretly take off your disguise, that's it.

Well then, um.

Qing took a deep breath after gathering her thoughts.

"Haha! You idiots! You're too late! The divine power was mine! The most beautiful woman in the Blood Cult, and the self-made nickname, the Super Brain-Slaying Beauty, the people of the world call her the Carnivore! A crazy carnivore? Anyway! The most beautiful, elegant, and noble woman in the world, an unparalleled face genius, a martial arts genius, and anyway, the strongest genius, Yeon-yeong, was the owner of the divine power!"