\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (5)}

After (physically) asking several of the Blood Offering Technicians, it was confirmed that the treasure room containing the Absorbing Magic's secrets could be accessed through the central control room.

The problem was the inaction of the Guisanmanbak Amharyong.

What a second-rate review.

This was a big problem.

The Blood Offering Association leader was well aware of his own weaknesses, so the security of the central control room was not ordinary.

"Heh, the plan has already been set in motion, and the Lord can control the rest on his own. You will witness the entire world drowning in blood, consumed only by ugly desires."

"Hmm. This one still has some mouthfuls."

Torture wasn't a panacea, so there were some who burned with rage until the very end, suffering.

But even so, it would only be my loss, and I would die more painfully if I kept at it, so Qing didn't really keep that in mind.

For Qing, the torture itself was enjoyable enough that spitting out information was a secondary factor.

Even if you keep your mouth shut, it won't harm the Qing.

Like this guy.

"Hahaha! I'll go to hell and wait for you!"

Qing looked down at the Blood Offering technician who was continuously bleeding.

The expression of a pitiful, downcast expression, as if saying that he was speechless, was clearly reflected in the eyes of the Blood Offering technician.

"There are definitely guys like this. They think that if you bite your tongue, you'll die."

"……?"

"If you bite your tongue, only your tongue was cut off. Do people die just because they don't have a tongue? Is the tongue a brain or a heart? Do you think with your tongue and circulate blood through it? Did you go mad after digging the ground for twenty years?"

The Blood Offering technician looks up at Qing with an expression as if he has been abandoned by the world.

"Ah, ugh? (Aren't you dead?)"

"You're dead, right? When was the last time you brushed your teeth? If you crush your flesh with that, of course you'll get abscesses. Your tongue will rot away, and you'll die from a fever. Or, if you're lucky, you might survive and become mute."

"Ugh (like that)……."

The eyes of the Blood Offering technician became aggrieved.

Those eyes, as if shouting, "Why, heaven! Why does this world deceive and mock me to the end!"

"Hey, ahhh! Keuk, keuee……"

It was a blood cult technician who was shocked not only by his eyes but also by the blood that gushed out from his tongue while he was actually trying.

When you cough, your blood pressure rises, and when your blood pressure rises, blood gushes out, gushing, gushing, thick stuff pouring out to the beat.

During the involuntary consultation process, Qing was able to hear about the Blood Cult's principles of operation.

There was no grave without an excuse, and each of the Blood Cult technicians had their own reasons to hate the world.

So, since the world hates me, I will hate the world too.

Isn't it too much to say that I will destroy the world since I was destroyed by the world?

Who was the enemy who took my family away!

It's Zhongyuan!

So I will wipe out Zhongyuan people!

It's a huge leap in logic, but I guess there are a lot of people like that in the world.

Just looking at the future that hasn't happened yet.

Where does my suffering (poverty) come from?

It was the people who had it, the people who were educated, the parents and ancestors who passed on poverty to me that made me so miserable.

So, the rich (the rich deserved to die) beat their teachers, doctors, technicians, and parents to death and destroy and burn everything their hateful ancestors left behind!

I am innocent and there was a reason for the massacre!

When people see someone who was so confident in himself, they click their tongues and say,

Tsk tsk, you crazy guy.

Once again, the hand of the Ximen Qing, which punished the poor seed of the Blood Cult, was full of mercy.

I threw him away with his limbs roughly twisted, so I hope he lives as long as possible before he dies.

So in front of the central control room.

A sturdy iron gate blocked the group.

The rough construction seems to scream that this was no ordinary door.

Unlike the stone gates that were security in themselves, weighing thousands of pounds and being over an inch thick, this was an iron gate designed as a real engine.

If you force it open, the passage will collapse forever.

It can be said that it contains the essence of the organ system that the Gonghyeoldan has built up, and that it cannot be passed through unless it's opened from the inside.

The Blood Offering Technicians were indeed exclusive, but they didn't seem to be able to commit fraud with common statements, so I'm hesitant to try it.

What if the passage collapses while you're messing around?

Then, the Qing party will not be able to see the face of the Blood Offering leader.

To get the emergency supplies, you have to go around the lower level passage.

Then, the Blood Offering Leader will realize that the outside was not normal and will immediately open the way to the treasure room.

Among those who were wandering around looking for the magic below, the secret will go to the lucky protagonist.

Then, there will be great difficulty in achieving the original purpose of recovering and burning the emergency supplies.

"Hmm. What are you going to do now?"

"I had a method in mind."

Qing explained the plan he had come up with.

Tian Yuxue frowned at him.

"Will that work?"

"It's okay to try, right? Sword friend, I'll ask you."

"Leave it to me."

Nan-gong Shencai nods his head solemnly.

Then, he raises his sword and glares at the iron door, then, with a snap, he retrieves the sword at the speed of a ray of light.

Then he raises his fist and bangs fiercely on the iron door.

Knock knock knock knock!

"Master! Master! We've got a big problem! Now, oh no, something big! Something big!"

It's a very urgent sound, as if you're about to suffocate.

This was also the moment when Qing discovers an unexpected talent in Nan-gong Shencai.

What the heck, why was this guy so good at acting?

I don't know why they pulled out the black one and put it back in for no reason.

Nan-gong Shencai gave a passionate performance, repeatedly knocking on the iron door.

If someone were to look around the door, it would be a scene so realistic that they would think something really big had happened.

Isn't it?

Actually, isn't it true that something big has happened from the Blood Cult's perspective?

It was the moment when Qing's expression gradually changed to 'that expression'.

"What the heck! Hey, man! How many times do I have to tell you to follow the procedure through the sound tube and report to me! Do you think the iron gate will fall down just like that? You little brat, it's open, so come in!"

I thought I heard a nervous, rasping voice, but then I heard the sound of metal clashing.

It was the moment when the essence of the Gonghyeoldan organ was dismantled.

"No, this works? Are you saying all the Blood Cult members are idiots?"

"Hey. Wherever people live, it's all the same, right?"

What good was the facility no matter how good it's?

In the end, it's people who operate it.

Surprisingly, Qing's plan worked.

It wasn't an irresponsible attempt to do something, thinking, "If it works, great, if it doesn't, don't do it."

They were so relaxed and careless, thinking it was a safe place, that without me knowing, the security of the guardhouse, or rather, the engine room, was completely breached.

In fact, the lower man's laxity was the same as the upper man's laxity.

If the leader of the Blood Offering group had maintained good discipline and practiced and preached the importance of security, the members would not have been able to act that way.

In the military, it's said that this was military discipline and was emphasized as the basis of all military.

Tian Yuxue sticks out his tongue after hearing Qing's explanation.

On the one hand, I feel happy too.

Yeah. It's because our child doesn't think, but he's really smart.

How could heaven have given such a beautiful head to such a girl?

"I've got one disciple who's really good. I'm retiring, so from now on, you do the real work."

"Hey, if the master was so upright, how could a disciple dare to do that?"

"That's what I mean."

-I told you the door was open! Did you knock so loudly that your ears went out!? Who's complaining that you were in big trouble and now it's been resolved!?

Just listening to the lines he said before, I think he's an old man with a bad temper.

You could have just told them to stop knocking, but you said you wouldn't knock the iron door down if you kept knocking like that.

Just by looking at them, you can tell if their hearing was damaged because they are beating loudly instead of telling them to come in quickly.

Even if I say so, there are people who do such dirty things.

When Qing opens the iron gate, another iron gate appears at the end of a passage about half a meter long.

Just in case he noticed and was trying to trick her, Qing quietly approached and pushed open the iron door.

However, it was an iron door that opened smoothly with a creaking sound of the iron plates.

And finally, the person who created this great underground city by digging the ground for twenty years, pointing with his finger without getting a single drop of dirt on it, appears.

Even if you don't know it when you're born, the impression you make in old age was made up of the expressions you've accumulated over the years.

Indeed, a grumpy old man locks eyes with Qing and makes a displeased expression, asking, "Who the hell are you?"

"What? Who are you-"

The dark dragon's words suddenly cease.

Looking at the group of people following behind Qing, he frowns on one side of his face and lets out a deep sigh.

"Those idiots. I told them to watch those martial artists down there and open the door for me, but why did they open the front door to their house?"

"Wouldn't it be a bit odd for Grandpa to say something like that? I wonder who those idiots learned from to open the door."

Who opened the door to the central control room?

"It's because I'm cruel that I ended up like this. But we've been eating and sleeping together in a tunnel for twenty years, so just bear with it a little longer. Just bear with it a little longer, and the day will come when I'll take revenge on the world. Oh yeah, oh yeah. I took pity on you, but this was how it ended up. Who can I blame?"

It seemed like everything had already been put down.

Qing scratched the inside of the single-minded person.

"Who are you going to blame?"

But it didn't work.

"Of course, it's the heavens. That damn heaven was impatient, unable to devour me until the very end. I simply wanted to wipe out all those bastards who spoke Zhongyuan language and were worse than any beast. That would be far more beneficial to both the heavens and the world. Why are you interfering with me like this?"

Is this the right thing to suddenly say?

It sounds like a very attractive argument, but it was actually born out of the wrong era.

This was because the people of Zhongyuan in this era were superior to the world average in terms of human nature.

At least the people of Zhongyuan in this era are great people who embrace Hongmogui (white people) and Haegwi (black people) as the same people.

Because anyway, the red (white) ones, the black ones, the border tribes, the Dongi Malgal, etc., they are all the same barbarians.

Surprisingly, the treatment of barbarians in Zhongyuan was not that bad!

At least they didn't display them like rare animals, or stack them up like luggage, carry them around like pack horses, and then throw them out in the field, thinking, "I used them for a long time."

Anyway, Qing puts her hand on his waist.

"No, what the hell was the problem? Why are you so impatient because you can't do it?"

"Ha! How could a well-bred woman like you know our sorrows?"

Amharyong continued speaking with a sneer.

"Do you even understand what hunger is? Have you ever been so hungry that you chewed and swallowed a passing bug raw?"

"Uh…yes."

"…You were?"

"Hehe. I'm also from a poor family."

Amharyong's mouth suddenly became speechless.

Since the branch of logic that was originally intended to branch out ended up breaking as soon as it started, it was only natural that I was at a loss for words.

If there was one person who can stand tall in the face of the Blood Cult's hatred and resentment towards the world, that person was Qing.

A miserable time that still occasionally comes to me in my dreams.

Those cruel Zhongyuan bastards never showed even a single act of kindness to the Qing.

Of course, Zhongyuan guys may have something to say too.

What good was it for to show mercy to a beggar woman with such a sick face, so twisted and distorted that it would be nauseating to just breathe in the same space as her?

So did Qing hate Zhongyuan guys?

Have you been gritting your teeth, vowing that you will wipe out all these wicked, filthy, vile, primitive bastards and slaughter them all?

No.

Rather, what Qing wanted was warmth, which she thought might exist somewhere in this world.

Even though she carried the evil spirit of a Killing Stars.

So Qing wandered.

And, Qing no longer seeks warmth.

But it still lingers.

The pig-like woman was also very greedy, so in order not to lose the relationship she has tightly embraced, she wanders the world to fight against the status window, which was an existential crisis and a cosmic fear.

So the wanderer who wanted to settle down said with a bright smile.

"Well, if you just surrender the magic of absorption, there will be bloodshed. It's a death sentence no matter what. So, why not just give up your life cleanly and without any pressure?"