\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (2)}

If I had my way, I would chew it up and eat it without any cavities, but it's a good-for-nothing bastard.

Because there were two minors in the group, it was necessary to refrain from showing any violent scenes.

If Chen Changming had known, he would have been wronged.

I'm an adult! I'm not a child!

If Murong Juhee had known, she might have felt even more wronged.

No, you even gave me practical training!

But Qing doesn't care.

All the tangible and intangible assets that Qing has accumulated in the martial arts world up to now are golden towers built on the grievances of others!

What was this guy doing, rolling his eyes lewdly, drooling profusely, shaking his body, and then learning martial arts!

Where on earth does that strong and powerful physical ability come from!

Why does she have three heads and such a great lower body and pretty face!?

If you feel wronged, you can just be the main character.

Anyway.

The person who caught the Blood Cult Blood Corps technician was Qing.

The Qing had the right to do whatever they wanted.

There's a child, so be gentle. Don't show blood.

I just took out all the joints.

Isn't it gentle if you don't see blood?

Anyone who has ever dislocated a shoulder knows the excruciating pain it can cause.

Because in this world, the only pain worse than the pain of a dislocated shoulder would be kidney stones.

The experience of extreme pain causes screams to flow from the mouth and corresponding liquids to flow from the eyes, nose, and mouth.

The Blood Cult technician, who was not pitiful at all, was left with his limbs stretched out in the face of the unreasonable violence that was suddenly inflicted upon him, and tears and snot flowed down his face.

The mouth was blocked, so screams and spit are excluded.

Because asking questions before torture was a low-level, low-level strategy.

"Well, you know what I mean, putting yourself in their shoes, right? I believe by now you can understand the pain I endured in that horrible trap. Don't you?"

The blood cult technician's blood pressure rises with injustice.

The only pain Qing had suffered from the trap was the red ladybug pattern on her uniform, and even that was healed without a scab thanks to her superhuman resilience.

"Well, it's probably best to answer honestly. I refrained from bloodshed because I have a minor, but thinking about it, I think I can raise this tough martial artist to be strong."

"Sigh. I'm an adult."

Chen Changming was pounding on his chest, but even if he got a massage, it would hurt more than this.

Looking at Chen Changming's reaction, it's clear that although Qing's words and actions are somewhat lacking, the core itself was clear.

Since I don't see blood, I guess I have some room to play around.

"Name, affiliation, age."

"Ugh. I have nothing to say. Kill him."

"Is this crazy, Mr. Ahn?"

"Yes, yes!"

Ahn, with a pale complexion, grabbed the torso of the Blood Offering technician and lifted him up, then began to shake him up and down.

Since the joints were already completely dislocated, the Blood Cult technician responded with what seemed like hundreds of exclamation marks, satisfying Qing.

"Kwaaak! I'll tell you! I'll tell you!"

"Again. Name, affiliation, age."

"……I am Qingshinwan, a member of the Blood Cult Blood Corps. I am thirty-seven years old."

"Lies! How can you be thirty-seven with that face? You can tell at a glance that you're over fifty! Have you lost your mind, Mr. Ahn?"

"Kwaaah! I'm thirty-one! That's right! That's right! That's right!"

But pain takes precedence over truth.

"I am fifty years old……"

It was Qingsinwan who had aged rapidly from digging caves in the rock for twenty years.

You might wonder how someone who was thirty-seven can look over fifty.

However, anyone who has been to the military camp, the homeland of the Ximen Qing, can understand it with difficulty.

The men who are called supply officers of the Korean military are usually around 35 years old, but on the outside they are grandfathers who are already approaching their 60th birthday.

When people suffer, they tend to age quickly.

Not only was he wronged for losing his youth, but he was also falsely accused of lying about his age, and ended up being half a century old.

Qing opens her eyes slightly.

"I don't think I'm fifty years old… Well, age isn't really that important, so let's move on."

The blood pressure of the Blood Offering technician soared again.

You're saying that you tormented people like that over something that wasn't even that important?

"You were the one who set up the trap, weren't you? What on earth are you planning?"

"Ugh, heh, you stupid bitch. Don't you know how things work out? Since the name of our school was mentioned, if you're not an idiot, you should know how things work out."

"Idiot? How can you call me that insulting? I'm smart, but if you really want to talk about intelligence, I'd say I'm highly intelligent."

"There was no such thing as a highly intelligent person-"

"Okay. It was all a blood cult trick, right? Somehow, Jang Bo-do was being spread around too artificially."

At that, Tian Yuxue's eyes become gloomy.

Lectures, deciphering maps, sleep.

It was thanks to the memories of last summer, when I silently performed only three actions.

Of course, unlike Qing, who was a high-intelligence person who only harmed others, Tian Yuxue was a true great teacher of the world and was highly renowned.

As soon as I heard the name of the Blood Cult, I immediately realized the truth, but after hearing it with my own ears and confirming it, I was filled with anger all over again.

And beside him, the cold-hearted Murong Juhee was a bonus.

Because Murong Juhee was already a mortal enemy who cannot live under the same sky as the Blood Cult.

Qingsinwan was completely stripped bare.

Not in a roundabout way, but in a real, physical and one-dimensional sense, I was completely stripped.

Because all the joints in the body are out of joints, the taste of the water bursting while swaying and fluttering was special.

On the way, Tian Yuxue and Murong Ju-hee exchanged blows and robbed him of everything, and Murong Ju-hee, who had been quietly standing in line behind them, also had a blast getting rid of the evil sect's entrenched members.

As a result, it seems that a fairly satisfactory amount of pain was passed on to Qingsinwan.

Pieces of broken teeth kept sticking out of his mouth, a sign that his teeth had broken from clenching his jaw so much that he had to grind them down. The whites of his eyes were completely red and bloodshot, which was typical of people whose pain reaches its peak when their blood vessels burst.

As a result of the hard work, the Qingsinwan's limp joints are strangely bent and spread out on the floor as if melting.

Amazing facts I've discovered so far!

The Blood Cult's Blood Offering group dug the Shingajji tomb for a full twenty years.

This was a great undertaking, no, it's not a great undertaking to build such a facility by digging into the inside of a perfectly good rock mountain.

Isn't it a great undertaking, usually called a great history, a new history that shakes the world?

"No, twenty years? Why on earth would you go to such lengths? What grudge in the world could you have that would make you dig the ground for twenty years?"

At that, Qingsinwan bursts out in laughter.

"I, my parents were tenant farmers who lived off the land of the detestable Mount Hua Sect bastards in Shaanxi."

"Mount Hua Sect? The Mount Hua Sect without a volcano?"

The expressions of Qing's group harden.

\textit{Why was the name of the Mount Hua Sect mentioned?}

\textit{I wonder if the world-renowned Mount Hua Sect has committed some heinous and atrocious act.}

"One day, those so-called Taoists of the Mount Hua Sect kicked us out. They said the same land yielded less than half the crops. Do you know what the life of a tenant farmer was like? We're poor, stuck on someone else's land, without even a single piece of land of our own."

It was not any other farmland, but the farmland of none other than the Mount Hua Sect.

Rumors spread that they had been kicked out because their harvest was less than half, and no landlord in the world would want to hire away tenant farmers who couldn't farm.

In dire poverty, her father was beaten to death for stealing someone else's dog, and her infant brother starved to death for not being able to drink milk.

The mother went mad with her dead child in her arms, and wandered around carrying a black, rotten piece of flesh until one day she never returned.

In the solemn atmosphere, Tian Yuxue asked with an ambiguous expression.

"Wait a minute. Doesn't that sound odd? Less than half the crops from the same land? If there were problems with water or soil, or if something like locusts swept through, all farmland should yielded half as well. Why are you saying only your farm are getting half the ususal yield?"

Qing didn't know farming.

Even Nan-gong Shencai and Murong Juhee, children of noble families, naturally didn't know how to farm.

And even though Chen Changming suffered from illness during her childhood, she was a daughter of a very wealthy family, thanks to her mother's efforts to raise her.

But although Tian Yuxue was from a wealthy family, he wandered around in his youth and has seen and heard things here and there, so he was picking the hole in the story.

"That doesn't matter! Those bastards who pretend to be the best virtuous warriors in the world, those poor, homeless people, were kicked out just because they stole a few sacks of cheap grains! They left them to die miserably on the streets! My father! My mother! My brother who couldn't even walk properly! Those damned murderers! Hypocrites! I'll watch Mount Hua Sect burn with my own eyes! I swore I'd burn that proud Mount Hua Sect down!"

Didn't this kid just say he stole it?

The group's eyes grew cold.

In fact, the Orthodox factions known for their land ownership tend to collect very generous rents.

For the sake of appearances, they were afraid that rumors would spread that they were exploiting tenant farmers, so they were careful about what the world thought.

The difference between the righteous and the evil was that they are aware of the world's opinions.

At least, it's not for nothing that they say that if you cultivate the land of a Taoist priest, you can eat three meals a day to your heart's content.

How dare a man who ate the land of the Taoist priest who already left him so much to eat dared to steal the grain produced there?

It's not even just ordinary sect, it's Mount Hua Sect.

If they could steal from martial artists who wielded swords, how easy would they think of a landowner without a sword

Of course, no landlord in this world would want to use them.

Besides, aren't the Mount Hua Sect the pride of Shaanxi Province, and the swordsmen that Shaanxi Province loves?

If rumors spread that someone had embezzled the grain from the Mount Hua Sect, no one would want to hire them, even as a day laborer, let alone as a tenant farmer.

"As far as I know, the Mount Hua Sect leave behind quite a generous amount of grains. They're praised for not letting anyone starve while working on the Mount Hua Sect's land."

"Don't be ridiculous! Those Mount Hua Sect bastards, that vast land, that endless expanse of land, doesn't it all belong to them! They have vast granaries that tenant farmers like us wouldn't have even after tens of thousands of years! Even a few sacks of oats aren't even worth a single grain of rice that we tenant farmers can afford!"

"Uh, um. So, since the Mount Hua Sect is so rich, you can rob them a little?"

"So, are you saying that someone born a tenant farmer should spend their entire lives farming other people's land? Is wanting a small piece of land really a reason to die such a miserable death?"

Qingsinwan shouted as if spitting out blood.

Qing tilted her head at him.

\textit{What the heck? Why was this kid so confident?}

"Wasn't it your family was annihilated not because they wanted their own land, but because they stole the grain from the Mount Hua Sect?"

"It was only seven bushels of grains! It was only seven bushels of grains!"

For reference, one bushel was worth 240 jins.

Seven bushels was one thousand six hundred and eighty jins.

In Qing's homeland terms, one thousand six hundred and eighty jins was just four kilograms shy under one tonne\footnote{1,000 kg}. 

"Well, to sum it up, your family stole seven bushels of grains, and that's nothing compared to the rice stored in the Hwasan warehouse. They made an entire family perished over something so trivial. Is that right?"

"Yeah! Those hypocrites! I'll kill them all!"

"Uh, um. Okay……"

Qing was speechless and stammered.

By the way, silencing Qing's speech was a huge achievement that could be boasted about to descendants for a long time.

What the Boold Offering's technician did was just such a feat.

Then what should have the Mount Hua Sect done?

Are you saying that other tenant farmers were idiots that they faithfully paid their rents?

If they dared swindling Mount Hua Sect, what will become of the other regular farmland owners? Then, it's clear that a third and fourth grain thief will appear.

In fact, the Mount Hua Sect was quite merciful in that they didn't beat them up and just drove them out unharmed.

People often make the mistake of thinking that being weak or poor equally means being good.

And the suffering they endured was the most regrettable in the world.

You might think it's absurd, but you could easily find people like this in either Zhongyuan or Qing's homeland.

She reached a conclusion.

"Just rip out his entrails and go kill the other blood cultists. Ah right, Changming should get out. This is no sight for children."
