\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (9)}

Colorful lights swirl around the blue sky.

The five lights of fire, water, wood, gold, and earth, but red was like blood and blue was the color of rotten water.

The green was sick, the iron has lost its luster and turned gray, and the yellow was stained and stuck together.

Originally, the Ogijowon was a harmony of five auspicious colors, but the colors that unfolded before my eyes were extremely ominous and ugly.

As the unmanned people hesitate and step back, each wondering what kind of harmony this was and what the hell was going on, and the fundamental fear of the unknown and the unknowable, the expressions of the three Unrestrained Realm masters harden.

Because I know what it's.

Because the fear of the unknown does not affect those who know.

In fact, most of those known to the world as masters of the Unrestrained Realm are not Unrestrained Realm, but rather are demons who have entered the Demon Realm.

Unless you completely lose your mind and get drunk on killing, the two don't seem to be much different anyway, so if you claim to be Unrestrained Realm, you become Unrestrained Realm.

But they also have excuses.

The famous disciples of the Jeongpa school have been practicing proven techniques since childhood by opening up all the blood vessels in their body (extending in all directions and not being blocked), and then taking elixirs as baby food. So, they can reach the Unrestrained Realm level through proper methods.

Where would our Sapa and Ronin have the chance to find elixirs and learn new techniques to reach the true realm?

So the three of them recognized the current situation.

A witch from the Blood Cult suddenly falls into the hands of a demon right before your eyes!

The three of them are shouting in unison.

"Kill that bitch!"

"You can't just leave it alone!"

"Suffocate this mad woman! Now! Urgent!"

If it were the hometown of Qing, there would have been no such attack during awakening or transformation.

Attacking during awakening or transformation was a serious crime based on some sin, and was probably an evil act prohibited by international conventions, and a great taboo that breaks the rules themselves.

However, in the primitive and ancient Zhongyuan, such stories had not yet developed, so if something seemed suspicious, they much preferred to kill it quickly.

The three masters' powerful swords are fired in a hurry.

The new blue version of him staggers and falls over, spilling onto the floor.

"Kwaaak!"

Kang-Hwan, who had passed the suddenly turned off target, attacks the Ae-Man warriors.

Still, the intended goal was successfully achieved, so it's an acceptable loss.

The five flavors and colors disappear into Qing's body.

The color that goes in before forming a circle.

The horse riding was cancelled.

Qing, who was forcibly dragged out in the face of a life-threatening crisis, screams in despair.

"Lady, wait a minute! What's that lethal attack you're making right now? Wait a minute! Just wait a minute!"

"Shut up! It's not a good idea to make fun of people, was it? Is now the time to achieve such a level of levity?"

"Not fatal! This was sick, sick, sick, \#\#\#, \#\#\#, what was it in the Chinese language?"

Amukhaprap asked, but who would understand what the chief said?

Amukhaprap himself.

And the blue one with a universal interpretation function.

"Ah! That's a strategy! A strategy!"

"Ah, the art of war! Thank you, madwoman! Instead, I'm gifting you with a surprising number of people!"

The old monk's skinny palms turn towards the blue.

Then, a palm swells up and a hand shadow made of blood-red energy rushes towards Qing.

However, it was a projectile with an ambiguous speed that was neither fast nor slow.

"You repay kindness with enmity!"

Qing turned around in indignation.

Then the blood turns towards the blue!

I thought it was a bit slow, but why does it have a guidance function!?

Qing was startled and lies down on the floor again, melting.

The shadow of a red hand passing by precariously.

Before Qing could catch her breath, the room suddenly became dark.

The fool of the three Unrestrained Realms. The round pig that carries the fat one among the Sapa Munju, Ttungtaeng, and the barbarians, Povidon Jang So-nam.

A huge, round lump of flesh with equal length, width, and depth.

When the buried limbs are spread out, something like a turtle or a turtle falls down like a meteor.

Miss, I'm going to go back.

Qing stretches his sharp, erect fingertips forward.

Seven seconds of the minority magic, Yohotamgan. Double left and right.

A wicked fox covets the liver.

Qing was the very herbivore that could tear out a person's heart with his bare hands.

The vicious scorpion that eats human flesh as if it were its own home was caught in its long fingers.

Finally, a huge belly fat covers the blue!

The vicious minority of the Ximen Qing, one by one, slammed into the front of the side, poof!

A young, strong hand shot into Povidone's belly.

It dug deep into my wrist, but I could still feel the tough skin on my fingertips.

The principle of softness overcoming strength, a sufficiently thick belly fat blocks minor attacks.

"madam-"

Boom! Ughhhh… …!

Povidone's belly bombardment covers the Qing, and a huge pit's dug with a loud noise.

Stone fragments flying in all directions.

A massive mass of belly fat weighs down the blue.

A strong pressure pressing down on the torso.

"Ugh……!"

Qing lets out a painful sigh.

I can't breathe, I can't breathe… …!

Qing pushed away the mass of flesh that was weighing down his body with his superhuman strength, but his hand was buried in the flesh and the weight did not decrease at all.

What kind of martial arts was this… …!

Even though Qing struggled, pushed, struck, and scratched, all he could do was get buried in the soft flesh, ripples would form, and he would slip, ugh, his breath, his bones, his bones… …!

It was a chest pain that has been left behind because the chest has shrunk.

The ribs cry out for help in excruciating pain from the immense weight pressing down on them.

The chest pain was so crushing that my lungs can't expand, so no matter how hard I try to breathe, it's all in vain.

The blood in my whole body feels like it's going to pound and break my blood vessels, and the pain of suffocation feels like my whole body was being twisted and squeezed.

"Ah, huff, huh, huff, breath, breath……"

The blue that was fluttering around like that's now drooping.

Only then did Povidone Jang So-nam roll out of the way, swing his arms and legs around like a puffy ball, and then stand up on two feet.

The two masters run towards him with bright colors, but stop in their tracks when they see Povidone's heavy body blocking their path.

"Hehehe, where are you going? I caught this crazy witch. Isn't that right? As the law of the martial arts world goes, since I caught her, she's mine."

"I'm sorry, but the situation was so serious that I can't help it. However, yes. Since I've reaffirmed my reputation as Povidone, take the witch and hand over the magic absorption. Even if she's not a magic absorption master, isn't she a woman who's mastered magic quite well?"

The expression on Jang So-nam's face suddenly turned sour.

And there was one lama who interferes.

"Wait! I've contributed to you too. I've made that mad woman lie down. I, too, must have divine powers!"

The monk Jang So-nam cleanly ignored the lama.

"Huh, why are you acting like this? How many eyes are there watching here? Why are you acting so petty? It's because the leader of the clan was acting like this."

"Treasures should be passed on to those who can protect them. I fully understand that Povidone's reputation was not in vain. But even so, can you alone shoulder the burden of martial arts achievements?"

"Ahem."

"So, Povidon, take that crazy witch and, whether you support her, roast her, subdue her, or bury her, extract her magical powers and train her, while we take the absorption magic. In return, if you wish, you may stay at Jeolnakseong. I will treat you as my honorary heavenly warriors."

"Hmm……."

Povidone's eyebrows twitch.

Not a bad deal, I guess.

It would be a good idea to give up the life of a ronin and settle down in a proper school.

If it's Jeolnakseong, it's a sapphire that's ranked among the top ten in the world, so if it's a sapphire with a thousand victories, then it's not bad to be treated as an elder.

Then Amukhaprap suddenly shouted.

"Wait! I demand a reward! You wicked Zhongyuan monkeys, do you dare to covet the offerings presented to the Buddha? You little peppers that can't even be squashed! I'll make you a pepper without seeds!"

In that case, the Jeolnaksungjon Jun Ki-chung and Povidone Jang So-nam make eye contact.

As if there was some kind of connection, Jun-gi-chung stealthily takes the seat next to Jang So-nam.

This was it.

The moment when Amukhaprap's fleshless face turned bright red as if it were going to burst-

"Hey!"

"Your Majesty! Behind! Behind!"

"That bitch! That bitch, doing that again!"

Jun-gi Choong and Seong So-nam turn around in a hurry.

The sagging fruits, with their whites exposed on the floor, and the chests, which are about to form rings of ominous color, are reflected in the pupils.

"You bitch! Where are you getting your ass kicked again!"

Junki-chung jumps up and raises his sword.

Then, the blue pupils that had been upside down suddenly roll back into focus.

Failed to pretend to be dead. What a shame.

Qing rolls his feet, touches the ground with both arms, spins around three times, and lands sharply.

Qing screams as he watches the sword destroy the innocent floor.

"Young lady, this was really too much! How can you be so cruel and attack a weak woman three to one! Hey, you cruel little bastards! And you're still men?! You barbarian bastard, you're right! Get rid of the peppers, get rid of the peppers!"

"This bitch……!"

Junki-chung shouted, but Qing looked not at him but at the fat guy in question.

What kind of flesh was this bulletproof flesh?

Qing screams as he sees the man's legs slowly lowering and bending.

"Wait a minute! I think there's been a bit of a misunderstanding. I scattered the secrets of the Absorption Method over there, but, um, you picked them all up?"

The treasure room had a completely different atmosphere, as if it were a different space.

Because the explorers, each holding a piece of the secret weapon that Qing had torn apart, were engaged in a breathtaking battle of wits, each aiming for the pieces of the secret weapon.

"Anyway, I don't have the emergency kit anymore. If you want the Jeong-seong magic, how about trying to collect the pieces there?"

"Well. I doubt a woman who has collected all the magic arts would have torn up and thrown away a magic absorption technique like that."

"Miss. You lack faith. I, Yun Yuanying, am absolutely not the type to lie. I am a completely pure woman who has never told a lie since birth, the embodiment of purity, the embodiment of purity. That was the real Yun Yuanying, no, Eonyeonyeong, no, Yun Yuanying."

"How can that girl who used to call me a transcendent beauty be so innocent? All the innocence in the world must have dried up."

"Why! I could be a super-beautiful girl too! To me, I'm the most beautiful woman of all time! Everyone's standards of beauty are different! How can you be so insensitive? Won't you respect my standards too?"

"A woman who has completely lost her mind. Her mouth was pierced, and lies are flowing out. She will go to hell and have her tongue pierced."

"Will you keep your mouth shut, barbarian? Can't you see the people talking amongst themselves? How dare you barbarian interfere in a conversation between people? Does your master permit you to do so?"

"\#\#\#\#! \#\#\#\#Hello\#\#! \#\#\#\#\#\#\#\#!"

A torrent of curses pour out that are too difficult to even utter.

Of course, Qing understood.

But since I wasn't the one being cursed at anyway, it didn't affect me at all.

You're cursing Yun Yuanying, not me.

"Then how about it, lady, come over here and take a look? Is there anything urgent?"

-Don't talk nonsense. I know you haven't torn the secret of the divine power.

The sound of Jun Ki-chung's voice rings in my ears.

When Qing looked at him, he held out one of the scattered pieces of the secret weapon and showed it to her.

There were only two letters on the torn piece of paper.

I'm sorry.

"madam."

Still, it seemed like he didn't want to spread the word secretly, as it would involve those who were holding the world's best sculpture competition.

Qing's eyes shine.

Really? If you don't like it, then I have to do it?

Qing, who had been holding her breath, suddenly lets out a loud noise.

"Oh! The preface to the Great Absorption Law! Qi flows throughout the world, and when warriors tame it and embrace it, it's called "Naegi" and "Jin Qi!" However, the natural Qi of heaven and earth was as fierce as a wild horse! It was as ferocious as a wolf or a tiger! It was also as timid as a wild hare! So, absorb the true Qi into your body! Taming it's as daunting and difficult as moving Mount Tai!"

The heads of the warriors who had been fiercely fighting over the emergency piece suddenly turned.

"If that's so! Why bother gathering the energy of nature? Doesn't the docile nature already exist, tamed by humans? After all, the world was a dog-eat-dog world, and the fittest are the ones who prey on each other to increase their power. This was the way of nature without action! When a true Taoist person achieves enlightenment, this was called the Great Law of Absorption!"

In fact, this was the preface to the book of Seopsimgong.

There, only the name of the last sub-shimgong was changed to the absorption method.

"That crazy bitch!"

"Stop it! Stop it!"

The unmanned soldiers rushed towards him.

Qing jumps up, his eyes flashing with a spinning soul fire, and he swings his black and white blades with his left and right hands, looking around in all directions.

The drones that were rushing in stopped for a moment.

"The absorption method was in my head! Everyone! Listen to what the real woman has to say!"

The Qing's enchanting tongue dances.

These so-called experts here already have their own renowned divine skills, but they are so greedy that they want to covet them!

But why did you venture into this dangerous territory?

Isn't that the desperate desire to risk one's life to find the divine power and leave one's name in history?

In that case, it would be better to have this Yun Yuanying!

I will teach you the secrets of the Absorption Method here!

Look at the one who tries to stop this!

Those guys named Unrestrained Realm!

And the ten greatest natural forces in the world!

They already have it!

Isn't this a trick to monopolize the divine power and further elevate the walls they have already built?

So, our sad people!

Even though I know that it's a ridiculous probability of one in a thousand or one in ten thousand!

Desperate people who have gathered together, risking their lives!

"Everyone, please protect me! Then I will summon the divine power!"

The boiling shouts of the Ximen Qing shook the stone chamber.

"Who owns the sacred art? Doesn't it belong to all of us? The sacred art was the property of all, not to be owned by any one person or group!"

"Hey, shut that bitch's mouth!"

"What are you doing! Kill him! No, you can't kill him! Just spare his life!"

"Look! There's a ghost haunting this place! The ghost they so fear, the new future where everyone shares divine power! Fearing a future where the wealthy can no longer exploit, they're trying to silence us and block the utopia where everyone shares divine power!"

There were some unmanned people whose eyes were becoming increasingly uneasy.

Even the unmanned people who belonged to the teenage nature were like that, so even if they risked their lives to obtain divine skills, wouldn't only those high ups be able to learn them?

He lets out a roar that's hoarse, but still full of strength.

"I will lead the way and share the world's greatest divine power! Let us all fight together against these vile oppressors! There was no sin in revolution, and there was a justification for rebellion! Revolution was innocent! Let's all rise up and seize the future! The four seas are the same, so let's all unite the world under the death penalty!"

Then a thunderous cheer followed!

"That's right!" "The revolution was innocent! Cho Ban-yuri!" "That's right!" "The new power belongs to everyone!"
