\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (2)}

There was a rule that the winner treats the loser well.

An important ritual to appease the spirits of the dead.

A noble act of continuing the legacy of the deceased.

Go ahead and explore the loot!

In the first place, it was rare to find someone who came to this place with a lot of gold and silver, but instead, there were quite a few snacks like jerky and rice balls that made Qing smile.

It was during that time.

As I put my hand into the bag on the corpse's back, I caught something large and hard.

The feel of a waterproof oilcloth.

Oh, what was it? No way? Is it a fancy snack?

Qing quickly takes off the packaging and then her shoulders slump.

Hey, what was this? It's an emergency.

High-end sweets, my ass.

Then the martial arts spear sparkled.

It was a renewal notification that served as a guarantee that the product was genuine and without defects.

It was a martial arts window that sparkles in the corner of your vision until you see it, begging for it to be opened.

Qing opens it and touches it to examine the untouchable, pre-registered martial arts that have not yet been brainwashed (physically).

Taesan Bloodline. It was a method with a red border.

The hope I had was disappointing.

It's not purple, it's not gold, it's just red.

When I think about it, it feels a bit unfair.

If you're going to imitate them anyway, shouldn't you synthesize these useless third-rate martial arts (actually, the red ones are also worthy of being called divine) and level them up?

Otherwise, you have to just use these miscellaneous items as materials to strengthen them and stuff.

Moon Girl Sword and Gu. How cool would that be.

If you strengthen it, the sword will shine. No, the sword still shines, but it will shine brightly in a golden color. Huh?

It was a thought that was very outrageous.

Anyway, Qing already has the best martial arts skills in the industry when it comes to tearing things with his fingers.

Qing, who quickly lost interest, tore off the corpse's intact clothes.

Although Qing was a swordsman, he was not so good at handling the sword that he completely abandons his duties as a swordsman.

Even if you only cut pork that has been cleaned and bled, the knife will glisten with grease, so what would happen if you cut live, raw meat?

So, you need a cloth to sharpen your knife.

"Okay, Changming, go clean your sword."

While he was at it, he tore off several and gave them to his companions as if he were doing them a favor, then sat down and began to quickly clean the blade.

But that was it.

Originally, you should wipe off the blood and clumps of fat and then apply oil again with an oil cloth.

Whether it's oil or human oil, it's oil anyway, so it just needs to be clean, right?

Qing, who boldly omitted the latter part, looks around.

Over there, two sword wielding guys are diligently cleaning their swords.

Whether it's a dual sword or a double sword, there's a very fatal flaw.

He who wields two swords must endure twice the trouble.

In fact, the biggest reason to keep one hand empty was for distance control.

If you equip a weapon in one hand and a fighting skill in the other, you can deal with enemies whether they are near or far.

There was a reason why twins are not mainstream in the martial arts world.

But Qing doesn't know anyway.

I'm not really interested.

I don't really want to use one more sword when I have the Tathagata Shinjang or Cheonma Guangzhoun that can attack from a distance.

Since lunch was already lacking, Qing munched on some rice balls he had picked up as spoils of war while the group sharpened their swords.

It would be nice to rest like that for a while and then rest for a long time, but was that how people live?

Finally, as they prepare to leave, Lee Hye-hye, who has crushed the man in the corner, does not seem to have any intention of going.

It doesn't really matter whether Lee Hye-hye goes or not.

But wouldn't it be a bit awkward if you suddenly came out from behind and asked to fight?

"We're about to leave. Isn't Miss Jo going?"

"I'm not Jo So-jeong, no, Jo A-yo was a nickname?"

"It feels strangely stuck in my mouth? So, what about Miss Jo?"

"So, I'm like, no, that's okay. I came here for nothing, even though I'm a magician. Why would I bother with magicians? I'd rather just go back, but since the road's blocked, I'll just rest and go later. After a day or so, this mess will probably be over."

Lee Hye-hye's expression as she spoke was clearly one of genuine fatigue.

Qing answered him.

"Then you can just go back now. I tried poking the door when I came in, and even though I reached the other side, it just spun around. You can just cut through it and leave."

"Huh? Really?"

"But there might be traps along the way. There might be traps you missed on the way back, right?"

"It's just a trap of that level."

"It might collapse, so I could just tear it down and run out. There are five ways out anyway, so it's okay if one of them collapses."

"Why are you telling me that? Well, from your perspective, it would be much better to eliminate your competitors."

Lee Hye-hye shrugged.

"I won't say thank you. If you just go away quietly, it's not a bad deal, right? I'm telling you because I don't want you to have to carry a bug behind you."

But it seems the three slaves had different thoughts.

"Thank you for your kindness."

Three slaves, led by Ilno, bow their heads politely to express their gratitude.

"No, hey. If you guys do that, what's going to happen to me? I'll be the only shameless bitch."

"Haha. Was I rude? Then please punish me. I'll gladly accept any punishment. Today, I'll be whipped."

"Then I will do it too."

"Hmm. That's good."

At that, Lee Hye-hye's expression suddenly changed.

"Fuck, why are these kids clinging to me? Can't they just get out of here?"

"Are you kidding me? Then beat him up and drive him out. Do whatever you want with him."

"No, for you, that's more like, oh, my fate……"

Lee Hye-hye has a genuinely disgusted expression, but the three slaves only respond with eyes that sparkle with affection.

After thinking for a moment, Qing took out the Taesan Bloodline's secret weapon and held it out.

"This was a secret weapon that Taesanmagun's thugs had. Are you interested?"

The master said that the method was inherently cruel, but it's not really a magical technique.

What's the big deal about just a red martial arts skill?

Lee Hye-hye's eyes widen as she checks the letters on the emergency kit.

In fact, to Qing, it's just red, but to the ronin wandering the world, a red border was the Divine Sword that they dream of and search for their entire lives.

Even though Lee Hye-hye knew that it was a limb, she was still skeptical when he called her a demon.

"Huh? Taesanhyeoljo? What, what should I do?"

"I'll give you some, so live well. It's a little overdone, but I'll let it slide because of the others. I heard Lady Jo was a good person. Okay."

Lee Hye-hye had a very sour expression.

"Well, you don't seem to know much about it, but isn't there a divine technique like this among the dharmas? It's said to be the divine technique that produced the greatest master of the Unrestrained Realm."

From the moment you explain something without just swallowing it, you can say that you have already become a human being.

Qing smiled brightly.

"I'm a swordsman, so I'm a bit picky."

"No, pronounce it a little differently. It's called ‘Jobeop.' It's called ‘Jobeop.'"

"Even if Kwon-beop was Kwon-beop, isn't Jo-beop also Jo-beop? Jo-beop was Jo-beop. Anyway, Jo-beop should go to Jo-beop, or rather, to Jo-beop's family, to be of use. I wouldn't have any use for it if I had it. I should live by giving back to others in return for my gratitude. There are people who are glaring at me, begging me to take them away right now."

Qing nods to the unmanned unit guarding his injured comrade on the other side.

Lee Hye-hye scratches her head as if she can't understand, and then finally snatches the emergency kit away.

"I'm Lee Hye-hye. I don't owe anyone anything. I'll pay you back later. Just pretend you know me when you stop using a fake name. Okay. Let's go. Hey there. If you're planning on going back, don't just watch and come closer."

So, Joa-yone sends the group back, and Qing grabs the leash.

"Okay. We should go now. Mr. An. What are you doing?"

"Oh, if you could send me too…"

"No, Mr. Ahn was not allowed."

"Why only me……"

"If you let go of Mr. An, who'll step on the trap? Come on. We've got a lifeline, so don't worry. Let's go."

Well, it's way over the limit.

He's not the type of guy who would suddenly become a new person if you let him go.

So, with Mr. Ahn in the lead, we walked through the passageway past the stone gate that had been open for a long time.

"Miss. Miss. An. Shouldn't you go a little faster?"

"Uh, there might be a trap, right……"

"Everyone who was supposed to pass has already passed, so what kind of trap was this? I put it in front just in case."

"That's the problem, isn't it……"

"You're a lifeline, aren't you? I saved An-ssi from near-death several times."

That speed gain only lasts for a moment.

When I told him to walk briskly, he seemed to start walking briskly, but then he slowly slowed down and started to stumble again.

"This won't do. I'll have to take a knife. If they come within my reach, I'll stab them."

"Oh my gosh, please, my legs are shaking because I don't know where something might pop out."

"Miss, traps don't activate until you step on something or press down on something. Where are the traps that activate on the fly?"

The anger that had been harassing An suddenly disappears.

There was a trap that was triggered right away!

Suddenly, a variety of screams erupted from the blue figure that had suddenly disappeared below: "Sister! Young Lady! Hey! Black Rain!"

It's urgent, so whatever the pseudonym or whatever, it's just pouring out as it was called.

Where the blue had been, only a hollow floor remained.

The four of them look down urgently.

Above the sharp, sharp blades, wouldn't Qing sit with a proud expression and look up at me?

"Uh, unnie…? Are you okay?"

"It's okay. I'm fine."

Chen Changming sighs in relief.

Qing has already achieved the perfection of his nerves by overcoming the harsh winter and taking off his clothes in the face of the great nature of Ximen Qing.

This means that as soon as you recognize danger, your self-defense energy automatically rises.

Add to that the superhuman strength of the body, and you have a primitive gravity-dependent trap that can be withstood with just your body.

If you dug it down about ten meters deep, it might be okay, but it's only going to fall about the height of a person.

"Hey, you should keep an eye on it."

"Miss, what kind of trap was activated without warning?"

So, are there any traps that are announced and then activated?

It's perfectly fine to spout nonsense.

When Tian Yuxue puts down the rope, Qing quietly comes up.

Qing sticks her huge butt out to Chen Changming as if nothing happened.

"Look at me. Isn't there any blood?"

"Hmm. A little. A little."

"Miss. It feels a bit warm."

Qing rubs her buttocks, which were hit hard by the blade of a spear.

There were red circles dotted on the white cotton pants, resembling ladybugs sitting on them.

Unless you're under the elbows protected by a small magician or have thick leather soles, it's inevitable that you'll get a small scratch when you're thrown at the blade.

"If it's bleeding, isn't there a hole in your pants too?"

Chen Changming grabs the blue pants and stretches them left and right.

"It's not a hole. I don't have an attitude."

Mr. Ahn looks at Qing with eyes that make him wonder if he was even a human.

What the heck? Is the blade dull? Why was it still intact? I wish I were dead.

Qing twists her waist and looks behind her.

Suddenly, the white cotton pants turned into polka-dot pants.

But it's not like I can change clothes.

Just wearing it's pointless.

"Miss. This was so disgusting. What kind of trap was this? It won't catch a single rat."

There was someone watching the situation, and that was the technician from the Blood Offering unit.

The technician was speechless.

What the heck? Why was that girl okay?

Although it's a cheap, disposable trap, it's a terrifying trap filled with scrap metal.

Even if you say you've reached a certain level, does that make sense?

What body was made of steel?

Anyway, he was a person of interest.

So, for the sake of restraint, didn't one person remain and activate the trap like this?

-What kind of trap was this? You can't even catch a single mouse.

The grumbling coming from the sound tube made the tendons on the technician's forehead bulge.

A beggarly trap? Can't even catch a rat?

It was a trap that has been carefully laid one by one.

Isn't this a trap that you've invested a whole twenty years, most of your life, into?

Wouldn't this be more lethal?

These were precious traps that were created with great difficulty while worrying about how to make it more horrific.

Isn't that the sound of making a mockery of all your past efforts and your past life?

Ah, ah.

With this grinding sound, a venomous look appears in the technician's eyes.

\textit{Okay. Let's see how long you can last in that damn trap, you four.}
