\chapter{Shuocaocaocaodao: Speak Cao Cao, Cao Cao Arrives (13)}

The culmination of twenty years of hard work by the technicians of the Blood Supply Group, the true beginning of the Blood Lantern World Fishery was when the secret was leaked.

Watching the martial artists fight each other in the caves and the temples, relieving our resentment was just a small reward that comes from the process.

If the plan had been fully implemented, the fight between those trying to escape with the secrets and those trying to steal them should have spread from this narrow Shandong Peninsula to the entire Zhongyuan.

Bloody Battle, as the name suggests, was a bloody battle, a prelude to a bloody battle.

So how?

When the treasure chest was opened, it's designed to emit another spectacular display of fireworks.

And so, in the still bright late summer-early autumn evening sky, unseasonable fireworks flew.

In the sky where the sun was shining brightly, the weak flames created by man have no power at all.

But still, its presence was outstanding.

At night, fireworks are not visible because they are covered by the black sky, but they actually emit a thick cloud of smoke at the same time as the fireworks.

Even in bright daylight, once a fire started, you could tell what had happened by the pungent smell of gunpowder that filled your nostrils and by the smoke you could see with your own eyes.

Just like right now.

"That, that!"

"It's a divine power! It must have been stolen!"

"Shingong? So, you're saying you're bringing it out now?"

Whether they had planned an attack from the beginning or arrived late and wandered around the mountain, the signal that they had given by poking them in the ribs with their naked eyes was enough to cause the unmanned soldiers scattered throughout the mountain to rush in.

Fortunately, there were four stone gates, but now there are three, so people are spread out.

Of course, from the perspective of the unmanned people in front of the stone gate, it was somewhat ambiguous. Should they say that the probability of the owner of the new skill appearing has increased significantly with the decrease in the number of stone gates, or should they say that it's regrettable that there are more competitors?

Among them, the south gate of Singajjimyo.

In front of the crowd of people gathered, half anticipating and half wary, a woman suddenly appeared and spread her arms out in a magnificent manner as if worshipping the sun.

"Come on, you arrogant world! I'm back!"

"……?"

A cold silence flows through the room.

In the uncomfortable silence, Qing lowers her arms as if embarrassed.

A heat surged up to his face, and then suddenly the face mask he had turned over gave him courage and strength.

Don't give up, cheer up! This was nothing!

Because you are not Heavenly Blossom Sword Ximen Qing!

The super brain-killing beauty, the strongest girl, was Yeon-yeong!

"Everyone! Run! Jeolnaksungjon! Povidone! And that, what the heck, those sly barbarians! They're going to kill us to silence us, to monopolize the divine power! They're on their tail right now! Everyone, run!!"

Qing says this and takes his foot off again.

"Hey, wait a minute! Stop!"

"This isn't the time to be like this! Run away! Everyone, run away! They're not Unrestrained Realm, they're Mine! The crazy Mine was chasing after you!"

"Povidone!? The Povidone of the World of Heaven was a mine!?"

No one was particularly surprised that Jun Ki-chung, one of the leaders of the Ten Great Apostles, or some strange barbarian, was a mine.

The fact that Jun Ki-chung was a barbarian was a fact known to everyone who should know, but there was no evidence. He was a barbarian, so it's only natural.

"Run away!"

Qing screamed and dove into the crowd.

"You fucking idiot, you fucking idiot! You're the one who's the one! Why don't you cut off his leg?"

"You barbarian bastard, you should have cut it off, why did you just watch!?"

"The head of Zhongyuan bird was a magnificent ornament! Follow the great Buddha! The Buddha was merciful! The throne was merciful!"

"What!?"

A fever rises in Jun-gi-chung's head.

Why didn't you cut off my leg?

Well, it can't be cut!

Even if the existence of the secret was unclear, didn't you personally experience the fact that the divine power was in the mind of that woman who had turned around through a single taste?

And when reading the human level, the correct way to build a relationship was to treat them with delicacies from the mountains and the sea and treat them with peerless beauties and gently seduce them.

Because, learning the rules that others teach you was almost like suicide.

Even if you twist just a few points of the blood circulation points, there may not be any problems at first, but as the problem deepens, it will return as a source of great trouble.

Even if you are lucky, you are a loser whose dantian was destroyed. You can be possessed by a demon and run wild, and either be defeated or die a miserable death with the veins of your entire body twisted.

Unless something cosmic like Qing verifies whether or not one's martial arts are complete.

When Qing tried to escape from his grasp, he had no choice but to aim for his legs or arms and throw a steel ring.

But even if you get hit with a small bean-sized bullet, it will probably leave a hole, and it will be at a level that can be sufficiently treated and recovered, right?

But wasn't it just stuck against the wall, with its huge, heavy buttocks wiggling around?

Why would you go out of your way to inflict harm and incur resentment?

So, wouldn't Jun Ki-chung have been wary of the men chasing him from behind, and wouldn't Jang So-nam have tried to persuade them by telling jokes?

Even Amukhaprap knew the truth, so he kept his mouth shut and watched, but after the self-proclaimed brainless killer girl ran away, he started asking why she didn't cut off his leg.

"Oh yeah! I'll send this idiot to Buddha today! This kind of idiot would probably wish Buddha would just disappear from the world! What kind of savage bastard would betray Buddha in the first place? Even Buddha doesn't consider savages human!"

"Idiot! Buddha was a true barbarian!"

"Go! Even if he's a cult monk, he's a Buddha, huh?"

Jun-gi-chung, who was about to lose his temper, flinched.

Come to think of it, was Buddha really a barbarian?

If you look closely, the Buddhist scriptures came from India?

Oh my goodness, have we been worshipping the barbarian gods as Buddha all this time!?

Junki-chung was in confusion!

"Taeho, Taeho! Hold on! Now was not the time for us to fight amongst ourselves! And there's no need to get angry at those barbarians! Let's just break down the door and chase after them!"

Taeho was the nickname of Siman Taeho and Jun Ki-chung.

At the right time, Jang So-nam stopped Jun Ki-chung.

Jun-gi-chung suddenly came to his senses and turned his body towards the wall.

So the three of them slam the door at the same time.

It was an astonishing scene of three people who had formed a bond that wasn't meant to be while cutting down a stone gate together cutting down a stone gate together again.

If the first barbarian prince to attain enlightenment about 2,500 years ago had seen this, he would have smiled his characteristically mysterious smile and said, "This was the law of dependent origination, this was the arising of causes and conditions."

However, it may be a bit of a stretch to say that we are doing this together.

They're all just digging a space for me to pass through, so they're not really cooperating.

So, even if three people dig a stone, the speed was not exactly the same for all three, but each person was pulling out their own strength.

Then, the sound of light footsteps follows.

It was (former) Dokgo Prosecutor Jeong Jong-pil.

The expression on Jang So-nam's face as he looked back was rotten.

"No, Jong-jeong, stop acting cool. Why are you so relaxed by yourself?"

"Brother Jang. I've been pondering the eloquence of my brainless, beautiful girl. Isn't this a grand idea that couldn't have emerged if it hadn't been cherished from the beginning? You may have been blinded by the new powers and temporarily lost sight of the spirit of the times, but don't you think it will eventually return to us, the oppressed?"

"Jong-jeong, brother? Did you get a head injury?"

"My mind was clearer than ever, and my heart has finally begun to truly beat. The girl with the most brains was clearly just wandering, but if I add my sincerity to that, she too will find her lost path. Towards the straight path that leads to the world. Together, the martial arts community will advance, forward, forward."

"that-"

At that moment, "Warrrr!" The sound of the stone gate collapsing made Jang So-nam turn his back in shock.

If you were to say that the round hole in the middle was the size of a buttock, wouldn't everyone be surprised? Each person would make a passage to escape from the hole on either side and jump over it.

"Oh no! Leave me alone!"

The man in the place hastily backed away and then rolled fiercely toward the larger of the open passages on the left and right.

Kkwarung! A large hole opens in the stone gate, and the flesh that gave Povidone its nickname slips out.

Qing's escape attempt was easily thwarted.

No matter how realistic the acting is, would you just let someone come out of a burning shrine?

"Wait! Stop!"

Then the blue stopped.

The unmanned vehicle that shouted "Stop" was a little flustered.

I don't know how to really stop when you tell me to stop.

However, the attitude of the unmanned person softens slightly at the sight of the blue person stopping obediently.

"What happened inside?"

"I, I don't really know. They keep making them fight each other, traps keep pouring down, the girl wanders around, and then, at some point, the mines start slaughtering people, and no one can return alive…"

"Mine……!"

"Yes, Mine! They're chasing us! If we don't all run away now, right now…!"

"Calm down, calm down for now. So, those minions, you know, Jeolnaksungjon, Povidon, and that squeaky-faced barbarian—no, who the hell are these barbarians?"

"What kind of fish cake, fish cake samhap? A wicked demon who stretches out his hand and bursts people with bloody water—"

"Great man! Amukhaprap! Are you talking about the monster Amukhaprap!?"

The unmanned soldiers, who had been pretending not to hear and pricking up their ears, shouted out the nickname and name one by one.

What, was that a famous barbarian?

"Yes! That's right! That was the name!"

The reason why Qing was stopped from escaping was nothing special.

If you run away from here, it will be suspicious and they will try to chase you even harder.

But if you match the rhythm and start a fight between the three idiots here and the unmanned people, it won't be too late to sneak away.

Rather, if we run away while our feet are tied together, we will be given ample time to throw off this mask and disguise ourselves in Ximen Hall, or rather, to return.

Then this commotion will be over!

"earthly-"

"Hello!" "You little bastard from Jungwon!"

At that moment, two mines jump out and shout.

But for a moment, he covered his eyes from the dazzling sunlight and blinked a few times with his eyesight to adjust, and then he hesitated when he saw the crowd surrounding him.

Then Qing suddenly shouts.

"Brothers and sisters of our church! They are enemies! Attack them all!"

Our school? Our brothers and sisters? An attack?

While the drones were momentarily dazed-

"Go! You bastards! You're the evil ones of the Blood Cult! Ugh, you barbarian! Let's join forces this time!"

"agreement!"

Since communication between blood sects was impossible, isn't it common sense in martial arts to attack them as soon as you discover them?

Amukhaprap knocks on the empty air with a paw.

Countless red handprints are imprinted in front of him.

It was as if someone was stamping their hand on transparent glass.

"It's a big deal! Get out of here!"

"The monster was attacking! Kill it!"

Some shout to dodge and others to charge, so some drones run away, some turn their backs, and chaos breaks out as they clash with each other.

Amukhaprap stretches both hands in the air, which was dyed red with blood.

Then, countless handprints spread out and shot out, rushing towards the unmanned people.

"Kwaaak!" "Damn it! Kill them!" "They have a new power!" "Kill them!"

Qing slowly heads outward, pushed and shoved by the chaos.

Again, this body, another one.

Even if you try to be a little humble, you can't be because you're so objectively outstanding.

Well, I guess the guys who came looking for magic are in their right mind.

As Qing slowly leaves, he soon reaches the outside and stamps his feet briskly.

It's also noticeable to run too far ahead, so you'll have to blend in with the crowd.

And now that Yun Yuanying was leaving, the teacher and the kids will be waiting upstairs, right?

Ah, I should go home now.

I miss you, Master. I miss you, Master.

Qing smiles mischievously.

Yun Yuanying was now over!

Super brainless beauty girl, business was closed!

"Oh my. Is this the end of the impersonation? Hmm, that was quite entertaining."

Suddenly, a soft, gentle voice whispered in my ear.

"But it's too bad it ends like this, isn't it? The tragic end of a girl with a brainless mind. Oh, yes. That would be good."

Goosebumps run down the back of Qing's neck.

Because it's not a voice that's being transmitted, it's a real whisper.

Because it's a voice that's kind but carries a clear malice, like a face that's smiling but not smiling at all.

"Which ending would you prefer? Disemboweled, smashed, burned, or flayed? Oh, you don't have to choose. I like them all."

