\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (4)}

Xue Ganom looked just as gaunt and hollow-cheeked now as he did a week ago, all skin and bones.

\textit{Yet why did he somehow seem prettier?}

Qing's powers of observation were exactly what you'd expect from someone of her background.

She was confident she wouldn't notice if someone was secretly living in her house for at least a week, even if furniture moved and food gradually disappeared.

\textit{But if even I can tell, there must be some dramatic change, right?}

\textit{What is it? Why does he look prettier?}

\textit{Did his nostrils get narrower?}

\textit{His head shape seems a bit more slender too.}

Qing scrutinized Xue Ganom's face closely.

Finally, she spotted the decisive difference.

Right, the eyes!

Originally, Xue Ganom had long, narrow eyes with tiny pupils like grains of millet, looking every bit the squinting villainous mastermind in the shadows.

\textit{But now those eyes... Like, what the... I mean, like...}

\textit{What man has eyes like that, for fuck's sake.}

Qing thought with utter disgust.

\textit{Those eyelashes, what the hell...}

Of course, Qing didn't just think this to herself.

After all, she was not one to hold back.

"Did you glue on fake eyelashes?"

Xue Ganom replied calmly.

"It is a side effect."

"Sure, the Blissful Maiden Art is a Fairy Art, but is it that potent?"

\textit{After all, hadn't the Sutra itself state that the Blissful Maiden Art had been created by a Fairy?}

\textit{But still, was that really how the Appearance Stat would turn out when increased?}

Even if Qing had chosen male as her gender, her Appearance Stat would have remained the same.

In that case, if Appearance increased, she would have become handsome, not pretty.

Xue Ganom resolved Qing's doubts.

"It's because I originally cultivated the Supreme Yin Jade Maiden Divine Art."

"The Supreme Yin Jade Maiden Divine Art?"

As stated multiple times before, when Qing didn't know something, the whole world could see her ignorance at a glance. As such, Xue Ganom explained.

"It's a nasty Demonic Art that turns you into a woman. I tried to replace it with the Ice Sura Demonic Art. I did not realize your Blissful Maiden Art was an orthodox Daoist teaching. I thought the Bliss Palace was just a den full of lustful harlots."

The Blissful Maiden Art was a Divine Art that suppressed the Demonic and converted them into pure True Qi.

It was also a martial art that followed the Daoist principle of the Golden Mean.

As the Blissful Maiden Art suppressed and embraced the Ice Sura Demonic Art, purifying it, the original Supreme Yin Jade Maiden Divine Art that had been replaced was revived.

Jade Maiden meant a woman as pure as jade, implying purity both inside and out.

Supreme Yin referred to the purest and greatest cold Qi, Orthodox Yin.

The cultivation of a righteous and pure beauty.

This was the very definition of walking the Orthodox Path.

In other words, it was a selective symbiotic target for the Blissful Maiden Art.

"Uh, so what does that mean exactly?"

"It means the Ice Sura Demonic Art I had gone through great difficulty to learn has scattered, and the achievements of the Supreme Yin Divine Art I had abandoned have returned. No, in fact, they have even surpassed what they were before."

\textit{Right. That's how it's supposed to be…}

\textit{I'm the abnormal one, I guess. Just me. Alone.}

Qing suppressed a sudden surge of emotion.

What had occurred to Xue Ganom was the natural characteristic of Inner Qi for these primitive, uncivilized natives of ancient China.

Compatible True Qi is absorbed into the highest one, while the rest that can't be absorbed dissipates.

Only Cultivation Techniques of the same level could coexist symbiotically without rejecting each other.

If not that, there were a few mysterious Cultivation Techniques like the Blissful Maiden Art that remained separate.

One couldn't just learn anything they wanted like Qing did.

Incompatible True Qi fighting separately and circulating through meridians regardless of the owner's will?

In Zhongyuan, this phenomenon was called Qi Deviation.

The reason Qing was fine was due to her Character Settings.

Because it was a character's body.

\textit{Not a person.}

\textit{I'm not a person.}

That's when it happened.

Suddenly, True Qi flowed out from Qing's Dantian.

It gently caressed all of Qing's Pressure Points, slowly flowing throughout her body, conveying warmth.

It was the ever so great compassion of the Great Tranquil Zen Art.

In the Imagery that followed, it somehow felt like a gentle smile, thus instantly unraveling her melancholy heart.

\textit{Right. I think, therefore I am.}

\textit{Among the four races that exist in the world - yellow, red, blackie, and ching chong - I guess I exist as the fifth. The one and only Ximen Qing.}

Qing asked with a grinning smile.

"Wow, so you escaped impotence in one go? You can take off that eunuch badge now? Are congratulations in order?"

"Unfortunately not. In the Northern Sea, the Supreme Yin Divine Art is also called the Barren Woman Art."

"Aw man, then you're basically saying nothing has changed, huh. Sorry to hear that."

Qing offered sincere condolences.

\textit{To think my friend is still impotent!}

\textit{Hm. It's actually kind of funny, but... Yikes, no, stop it Qing! You gotta manage your expression.}

\textit{Think sad thoughts…}

\textit{Wait a minute. Does that mean I'm impotent too?}

A look of desolate sorrow appeared on Qing's face.

Xue Ganom cleared his throat awkwardly.

"Ahem, I have already escaped impotence. It is just that I am extremely slow and insensitive now. But since it is still a sensation I have not had in a long time, these days even the slightest touch makes my dick stand up. In fact, it's standing right now, so if you want-"

"If you're going to ask me if I want to watch, you might actually go from Xue Ganom the Impotent to Xue Ganyeo the Woman. You see, every male fucker's dick I see should be cut off. That's my policy."

Qing spoke in a low voice with a shudder.

\textit{No wonder his sitting posture seemed oddly awkward.}

Xue Ganom looked very satisfied at her reaction.

He seemed to think his sexual harassment had finally worked for the first time.

After all, Xue Ganom had always been someone who made comments that were clearly sexual harassment as naturally as flowing water.

Qing simply despised this weird, misguided camaraderie between men, but she didn't bother voicing objections that would fall on deaf ears. After all, he didn't know she was a man.

Xue Ganom, smiling for the first time, pulled out a book from his chest.

"Anyway, take this."

As soon as Qing received it, the Martial Arts Window flickered.

It meant it was a Secret Manual.

The title was written on the book, so there was no need to check the Martial Arts Window.

It was the Secret Manual of the Supreme Yin Jade Maiden Divine Art.

The Blissful Maiden Art was already growing at a fierce pace.

Qing's Inner Qi Cultivation Techniques had clear growth limits.

The Heavenly Ice Sura Demonic Art alone wasn't nearly enough, so a new Divine Art to make her senses number was welcome.

"Wow. A Secret Manual! Are you giving this to me?"

"I am just giving one as compensation for the one I received. Hm."

Xue Ganom seemed to hesitate before continuing.

"If you happen to meet someone from the Northern Sea Ice Palace or the Snowy Mountains, please pass it on to them. You do not need to go out of your way to find them. If you just happen to meet them, then yes. That in itself is enough."

"Why don't you give it to them yourself?"

"I have already forgiven the Ice Palace, but they probably have not forgiven me. So it is better if we do not cross paths."

"Ooh."

Qing marveled at Xue Ganom's magnanimous character.

\textit{Doesn't this broad-mindedness indeed befit the most shining intellect of Zhongyuan?}

\textit{His only flaw is making those sexual comments that feels like it would come from a creepy old man, but since I actually enjoy those kinds of jokes, it's not really a flaw at all.}

But right then.

"Well, 'forgiveness' might be too grand a word. After I killed those damn bastards and bitches, set fire to the palace, and stole their Secret Manuals, I felt quite refreshed. People who have completed their revenge sleep well at night, you see."

Qing saw Xue Ganom's Evil Karma.

It exceeded 400, making him a Great Demonic Adept.

Of course, in this neighborhood, the Evil Karma of Demonic Adepts who lived quietly tended to be higher.

After all, it was the kind of place where you gained Righteous Karma for killing your neighbors.

When Qing first met Xue Ganom, she let him live because he seemed both amusing and useful.

Since then, she grew fond of him as she came and went, and found him handy, so she never thought of killing him.

To Qing, Evil Karma was nothing more than a qualification.

Anyone with three digits or more was simply someone who could be killed.

From the start, Qing's elimination of evil people had little to do with world peace or righteousness.

The reasons Qing started eliminating evil people were:

First, to gather Practice Points and become a Master to survive.

Second, for financial abundance.

Third, because it was fun.

During the roughly ten days she went berserk, fun had briefly become the top priority, but survival was still above that.

The reason she immediately cowered and became submissive to people with suspiciously high Evil Karma like Yun Yuanling was ultimately a desperate struggle to survive.

She had never played the role of an executioner going around looking for bad guys to kill, and she had no intention of doing so in the future.

Though Qing didn't clearly realize it yet, a new, imperfect category of ‘friend' had wedged itself into her current classification of how someone was either ‘human' or ‘an evil person'.

Qing spoke to her friend.

"Ah, right. So, I was meaning to say. I've had some realizations lately."

Xue Ganom brightened up.

He thought she was finally showing the clear, refreshing gaze befitting a Female Expert of the Orthodox Faction.

It seemed he thought she was going to stop her meaningless killing spree.

"Oho. That is welcome news. Then, now-"

\textit{Our hearts, our minds seem to have connected!}

Qing happily continued Xue Ganom's words.

"I need to choose who to kill more carefully. I've been killing way too indiscriminately up till now, right?"

"...?"

Xue Ganom doubted his ears.

\textit{Did I hear that wrong?}

Regardless of what he thought, Qing continued.

"So, could you make me a list of bastards crucial to the Demonic Cult? So that when the situation arises later, I can poke holes in their group."

This was the biggest point of reflection for Qing after regaining her senses.

It's good and all to search for escape techniques.

But fundamentally, ensuring survival at the moment of escape was the top priority.

"Um. I am sorry to change my mind, but could I get that Secret Manual back now? If you die stupidly, the manual will fall into the Demonic Cult's hands. I do not want to get mixed up in that."

"Hey now, haven't you heard about 'no takesies-backsies'? Are you really a man if you don't keep your word?"

"Even when I could not be considered a complete man, I poured water on myself every night because I wanted to live. How much more so do you think my survival instinct would be now?"

\textit{Indeed, Xue Ganom, there's nothing I can say to refute that.}

So Qing got straight to the point.

"So actually, in about a month? Or so..."

Qing spilled everything she had learned.

About the Alleged Supreme and the Heavenly Demon Tomb.

She planned to pretend to cooperate obediently, then smash the Heavenly Demon Spirit and escape, so she needed to take out important figures in advance to prepare for that moment.

Qing readily admitted her shortcomings.

That was why she was so shameless in seeking advice from her friend who had such a brilliant intellect.

Xue Ganom, who usually didn't hesitate to use derogatory terms for the Demonic Cult, nodded at Qing's plan.

"Indeed. You are quite cunning when it comes to those kinds of things, I see. Even if you escape now, those Demonic Cult bastards won't give up on you since you are the key. But you are not strong enough to face them head-on, so you want to inflict as much critical damage as possible before running away. Is that right?"

"Exactly."

"Hmm. Let's see."

Xue Ganom stroked his chin.

"The best method would be to make allies for yourself."

"Like you, Xue Ganom?"

Xue Ganom's eyebrows moved up and down once each.

"Well, you are free to think what you want."

"What? Aren't we friends? Are you abandoning your friend? You don't want to be friends anymore?"

"Friends cannot always be on the same side. Not betraying trust is the virtue of true friendship. Blindly taking sides regardless of the circumstance just makes us bad friends who hold each other back."

It was a fair point, so she couldn't say much to retort.

As such, Qing just frowned.

"Agh shit. You've got me there. Fine, explain then. So what do you mean by making allies?"

"Well, you are young and beautiful with big tits, so you could seduce a few Demonic Adepts and..."

"Rejected."

Qing shot down the idea swiftly.