\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (2)}

"Thousand Spiders Ten Thousand Poison Hand? Is that a Poison Art?"

Qing swiftly called forth the Martial Arts Window.

\textit{Thou Sand Spi Ders Ten Thou Sand Poi Son Hand. Search.}

As she did so, a majestic Purple Border appeared.

"Thousand Spiders Ten Thousand Poison Hand, is it…"

The 'Spiders' in 'Thousand Spiders Ten Thousand Poison Hand' meant something very literal.

It was signifying all the poisons possessed by a thousand poisonous spiders.

It was a Poison Art famous for its brutal training method, where one would take an antidote in advance and let a poisonous spider bite their finger.

But suddenly, she had a thought.

Didn't the Strategy Guide say that Poison Arts were trash?

Thanks to the Strategy Guide, she had survived until now.

Because it never spoke nonsense.

"Your realm is extraordinary for your age, but there are many strong enemies to face. As such, is there any means better than poison?"

But Xue Ganom did not speak nonsense either.

Qing regarded him as the greatest intellect she had met in Zhongyuan.

Qing wavered again at his words.

Hearing it like this, it sounded tempting.

Well, in the game, poison might be weak, but in reality, what could be stronger than poison?

It wasn't exactly like the game, so listening to the opinion of a native might not be a bad idea.

"Anyway, who has time to collect poisonous spiders one by one? If someone offers to give you a Secret Manual, just ask for the Great Tranquil Zen Art. It suits you better than a Poison Art."

"Great Tranquil Zen Art..."

This, too, was a Purple Inner Qi Cultivation Technique.

Qing obviously didn't know, but it was a martial art known to every martial artist in the world.

It was a Divine Art known for its ability to clear the mind and protect against inner demons, the purity of its essence in hardening the heart and mind was renowned as the most pristine of all martial arts.

However, in the 'If you could learn one martial art, what would it be' game, the Great Tranquil Zen Art had a different meaning.

It was a way of saying, 'Get your head out of the clouds and come back to reality.'

Of course, there was some sincerity mixed in.

After all, if she continued accumulating the sinful karma of slaughter, she might end up as the Great Demonic Adept of the Orthodox Faction, determined to slay all the bad guys in the world.

"So, Xue Ganom's choice is the Great Tranquil Zen Art?"

"Yes. Learn it right away, if someone offers it."

Qing didn't know much about anything.

And lo and behold, sarcasm didn't work on someone who fundamentally couldn't understand it.

"The Yijin Cleansing Method takes a long time to show effects, but the Great Tranquil Zen Art works immediately, right? Is that what you mean?"

Qing understood it in a different way.

Xue Ganom looked at Qing with a pitiful gaze.

It was the look of realizing that his friend was even more ignorant than he thought.

"The Great Tranquil Zen Art is a Divine Art that keeps your mind pure. It means to stay grounded and not get lost in delusions."

"Agh shit, come on, you should have just said that right away!"

"I just told you, did I not? And I should have known how ignorant you were first. So that I could stoop to your level for you."

It seemed like he had a hard time outright calling her an ignorant bitch.

Qing just frowned, having nothing to say.

\textit{As expected, of Xue Ganom. He was not an easy ‘nom'\footnote{bastard} to deal with.}

What do you do when you're at a loss for words?

Change the topic, of course.

"By the way, you said you wanted to learn the Blissful Maiden Arts, right? Can men learn it too?"

"The orthodox Dual Cultivation Techniques of Daoism originally does not discriminate between men and women. It's not something to be proud of where you learned it, but as far as I know, it sharpens the body's senses, so I thought it might help heal this body of mine."

"Is it that uncomfortable?"

Xue Ganom quietly pointed to his head.

His hair, still wet, clung to it.

"Ah."

Qing made a sound that didn't really mean anything in any specific way.

Then, Xue Ganom calmly shared an even sadder story.

"More than that, I have no feeling in my cock. I might just have a Śarīra\footnote{Buddhist relics found among the cremated ashes of Buddhist monks} come out of me after I die. At this point, you could say I am not truly living."

"Ah. Oh, no."

Qing exclaimed in pity.

\textit{Oh my goodness! How could this be!}

\textit{Xue Ganom was impotent! A eunuch!}

"Then, can you not even do it alone?"

Qing clumsily mimicked a hand motion up and down as she asked.

Xue Ganom spoke with a disappointed expression.

"Can't you at least pretend to be embarrassed? At any rate, even if I try to enjoy it mentally while scratching at my cock, it doesn't work at all."

"Ah, so you wanted to see me embarrassed?"

No wonder this uncle kept making lewd comments bordering on sexual harassment.

Qing's eyes narrowed.

Though she felt indignant, she also felt a pang of sadness at his calm confession.

Honestly, it would've been better if he just vented his anger; but rather than that, he seemed resigned, as if he had accepted his fate.

Qing, once a man herself, could fully empathize with his sorrow.

Moreover, Xue Ganom was a great helper.

He pointed out who to kill and gave good advice, after all.

"Then, I'll recite the Sutra for you, so listen carefully."

"What? Wait."

"Well then, here it goes. The Sutra says: '\textit{Thepathofmutuallifeleadstosupremejoy; therefore, thepleasureofloveisthedelightofthehighestform, theecstasyofthecloudsandrain.' As such, this means that as people enjoy the principle of mutual life, that love becomes...}"

Xue Ganom, who was about to say something, closed his mouth and focused as the Sutra poured out.

Understanding the meaning as it came, he, with his naturally sharp mind, memorized it quickly.

Xue Ganom memorized the Sutra in just three tries.

Sitting cross-legged and entering meditation was proof.

Proof of his sharp mind, worthy of being recognized by Qing as one of the great intellects of Zhongyuan.

Then he spoke.

"Don't come for a while."

"What? Are you saying you don't need me anymore because you've finished getting everything you want from me?"

"That is not it. I need some time to organize this rare opportunity, don't I?"

Qing frowned.

But since he was going to work so hard to overcome his impotence and escape his eunuch status, she felt it was inappropriate to complain.

Besides, she had taught him something valuable, so it was only fair to give him time to practice.

Qing looked visibly disappointed.

Seeing this, Xue Ganom spoke seriously.

"Take this chance to rest for about a week. Slaying those of evil is good, but it is also important to take time to calmly organize what you've gained. You are in a very dangerous situation right now."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A week had passed.

Now, no one in the Bliss Palace dared to touch Qing.

Everyone knew that the person living in the small room at the top of the disciples' quarters was a much greater Master than expected.

There were even rumors that a Shrine Maiden of the Main Palace served her humbly, crawling on their knees.

The Shrine Maidens of the Main Palace, who once looked down on the Bliss Palace disciples, calling them filthy prostitutes, were the ones spreading these rumors.

And as with all rumors, someone claimed to have seen it, but it was unknown as to who exactly it was.

It was a rumor that would surprise Teacher Kang.

In that humiliating scene, the teaching session included only Qing, Teacher Kang, and Soyeong, a Shrine Maiden in training as well as a maid.

Upon hearing such a rumor, she might even think that some spirit must have seen it and spread it.

For the record, Qing wasn't interested in publicizing Teacher Kang's dedicated enthusiasm for education.

Recently, Qing had also risen in status, gathering under her the likes of Jian Buxi, who had daily assemblies from those both above her in rank and below.

So, the disciples of the Bliss Palace did not dare to approach Qing.

Saying that it was fortunate she was crippled.

Since there was no need to worry about being bitten if they kept their distance.

She was practically treated like a mad dog.

Despite this, Qing had a rather busy week.

After all, a lack of information did not mean the targets to kill disappeared.

Besides, couldn't she tell who should be killed by the number hovering above their heads?

Honestly, the information was only needed to kill the more useful villains efficiently.

Otherwise, she could just torture them based on their Evil Karma, extract their martial arts, and then kill them.

Thus, she spent the past week going out at night alone and coming back exhausted to sleep.

Although it was fun, it was a big failure in terms of acquiring martial arts that could be used for her escape.

She only gathered these miscellaneous White and Blue… things.

This was the clear difference between knowing the coordinates and blindly sifting through sand.

And as she fell asleep like that, she would wake up around noon.

She would have lunch with Crutch No. 2, and sometimes Crutch No. 1 would visit, so she would eat with him.

In the afternoon, she received special massage treatments and snack tributes from Teacher Kang.

She adjusted the pace since it seemed they were progressing too quickly, which actually seemed to make Teacher Kang more at ease, thus kinder.

In the evening, she would go out for dinner with Crutch No. 2.

And only then did she have some rest and free time.

During her free time over the week, she watched Jian Buxi practice the Lustful Immortal Disrobing Dance.

The Lustful Immortal Disrobing Dance was the main Joint Attack Technique of the Bliss Palace's Second-Grade disciples, and Jian Buxi, having reached the Second-Grade, had received a copy of the Secret Manual.

Qing didn't know it, but the group performance of the Lustful Immortal Disrobing Dance by the Bliss Palace disciples was notorious in Jianghu as a particularly vicious Joint Attack Technique.

Disciples of the orthodox Nine Sects, who inherited the long-standing traditions of their sects, were particularly weak against women.

They couldn't help but be mesmerized by the clearly high-level sorcery of beautiful women gracefully undressing and dancing.

During the four Great Wars Between Orthodox and Demonic, countless disciples of the Orthodox Faction were either slaughtered by or drained by this technique.

This backward Zhongyuan lacked proper entertainment.

As such, Qing summoned her to train as a form of amusement.

However, the movements were clumsy and disjointed; she even got her limbs tangled while undressing and fell over, creating a complete shitfest.

Frustrated, Qing put it as a One Star on the Martial Arts Window and learned the Sutra and movements herself, so that she could provide detailed guidance.

As a result, she discovered that Crutch No. 2 had a catastrophic lack of talent for dancing.

Rather, it was Qing who had her achievements soar, as her coaching and observations counted as training.

In just one week, she achieved the level of Three Stars.

"No, what? Senior Sister. Can't you do it more like yareyare? Like delicately? Like shalalala? More flirtatiously, you know? Like this?"

Qing gently shook her hand, shalalaing as an example.

It was a deadly hand technique that enticed the opponent, starting from the shoulder, bouncing through the elbow and wrist, and ending at the fingertips.

Jian Buxi tried to follow the movement after hesitating a bit.

"Uh, shalala... Like this?"

What she showed was closer to a rough martial arts move than delicate.

\textit{The fuck? What kind of movement is that supposed to mean?}

\textit{Does she mean to burst someone's heart or some shit?}

Qing narrowed her eyes.

\textit{What the… I've shown this so many times, and she still can't get it.}

\textit{Seduction, my asshole. Isn't she unfolding some Praying Mantis Fist shit or whatever?}

\textit{Are you kidding me? Is it really this hard to just watch a proper disrobing dance?}

\textit{Ehhh? Hm, Crutch No. 2 is just useless.}

\textit{A First-Grade disciple would probably dance better, right?}

\textit{Should I just pick up someone else instead?}

\textit{There's no use keeping her except for spectating her ‘finishing touches'.}

\textit{But honestly, since the ending is always the same, I'm already kinda bored of it.}

\textit{All she does is get on top, wiggle her waist a bit, and then it's just over when the person underneath stops breathing.}

\textit{And no matter how I ask her to do something different, she says she can't do any other positions.}

\textit{Also, Crutch No. 1 buys me better and more food as well.}

\textit{Do I really need two crutches?}

"Uh, Junior Sister. I'll work harder, so..."

"It's not about effort anymore. Your talent… Can I even call this talent? If you can call having no talent at all a talent, then yeah, that's the talent you have."

Jian Buxi lowered her head.

Her body trembled slightly, and her shoulders shook occasionally.

Qing frowned deeply.

\textit{The fuck? Is she crying?}

\textit{Why is she crying in the middle of someone else's room?}

\textit{If she wants to cry, she should go to her own room to 'Wahhhh'.}

\textit{This makes me seem like the bad guy.}

\textit{Besides, did I say anything wrong?}

\textit{I just told the truth. I said she can't do it because she literally can't. It's not like praising her and saying, ‘Oh my, oh my, you're doing well, your skills are improving so much,' would magically make her improve. Wouldn't that just be a waste of time.}

\textit{Fucking hell, all she learned was how to act out some useless melodrama.}

Qing looked at the number above Jian Buxi's head.

There, a number she was always thankful for could be seen.

-136. It was still okay to kill her.

\textit{Well, she's useless now, so I might as well just get some Righteous Karma.}

Suddenly, Qing felt a chill down her spine.

\textit{Just get what?}

"Eup."

Suddenly, her stomach turned over on itself, and the dinner she had eaten tried to make a grand escape in the opposite direction.

The half-digested food, unstoppable even by a Master's abilities, surged up her esophagus with the force of some historical revolution and erupted magnificently.

"Junior Sister? Junior Sister! Are you okay?"

"My... eup, back, back."

At those words, Jian Buxi touched Qing's back.

Her strength was less than that of a five-year-old who hadn't even started kindergarten.

\textit{Either rub it or thump it hard. Fuck, just do one of them.}

\textit{Does she think my back is as fragile as tofu?}

\textit{It's not going to break even if she hits it a little harder.}

\textit{Isn't this a pretty good excuse to beat the shit out of a nasty Junior Sister's back?}

\textit{It isn't like I'm that fragile. How considerate is she?}

Finally, after vomiting all her dinner, her gag reflux stopped.

Moreover, it only stopped because there was nothing left in her stomach. The fact that her stomach was trembling violently mea- Ah. This feels like stomach cramps.

"Junior Sister? Are you okay now?"

"Not okay... Pass the water."

"Ah, wait. Here."

Jian Buxi brought a cup of water to Qing's lips.

Qing shook her head.

"No, just give it to me. Why are you doing that? Who said I needed to be fed water?"

"Oh."

Jian Buxi handed over the cup.

Qing used the Heavenly Ice Sura Demonic Arts to chill the water.

Soon, frost formed on the surface of the cup.

She gulped it down in one go, the cold water sending a piercing chill through her insides.

Her foggy mind started to clear up.

Then the aftermath of the dinner eruption hit.

The stomach acid and chunks that had gone up her nose delivered a pain that felt like her entire head was being squeezed.

"Hiss, this is killing me..."

"Junior Sister? Are you okay?"

"I feel like I've heard that several times."

"Uh... then. Um. Will you be okay?"

"I need to rest today. Senior Sister, you should rest too. You've had a hard time today as well."

Crutch No. 2 looked genuinely concerned.

Qing repented, reflecting deeply upon her previous callousness.

\textit{Yeah sure, the kid isn't particularly kind. She's incompetent, dumb, and not very helpful, but at least she's caring.}

\textit{I must've actually gone fucking mad.}

\textit{I should have rested when Xue Ganom told me to.}

\textit{Why have I been so diligent with my work every night?}

Feeling sorry, Qing added one more thing.

"Let's practice together starting tomorrow. That way, Senior Sister will improve too, right? It's originally a group dance, after all."

"Huh!? Eh? Huh? Okay!"

Jian Buxi's mood shifted back to a cheerful sunshine-like state.

She wasn't kind. She was incompetent, dumb, and not very helpful, and now it seemed Qing had to add simple-minded to the list.

"If you feel sick, you should rest. I'll have the Junior Sisters take care of this. Did it get on your clothes too? Make sure to take them off."

Even while being so caring, she didn't offer to clean it up herself.

Why? Because she wasn't particularly kind.

At any rate, Qing nodded in agreement; after all, she didn't care as long as she wasn't the one to do it.

As Jian Buxi left with that, Qing, now alone in the room, summoned the Martial Arts Window.