\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (5)}

Xue Ganom looked unconvinced.

His expression seemed to say, 'Why can't she do it? It's not that difficult, is it?'.

"You do not seem desperate enough, is it? But should you not do whatever it takes to survive, even if it means crawling between someone's legs? Only then can you plan for the future."

This referred to Zhongyuan's idiom ‘crawling between the crotch', meaning to endure humiliation.

It was famously associated with Han Xin, considered one of the greatest generals in Chinese history, though his later years were quite miserable despite achieving his goals through such means.

"Is that not better than dying? There are a few lecherous Demonic Adepts who might be to your taste."

Haa. Qing sighed deeply and spoke.

"Forget it. People have something called dignity, you know?"

Xue Ganom's face visibly hardened.

His blank stare and remorseful wrinkles suggested he was recalling something from the past.

Then, shaking his head, he apologized.

"I apologize. You are right. After living like this for so long, I had not considered that."

"Ah. But I do have a close grandpa figure. He's called the Purple Lightning Demonic Warlord, that foul-mouthed old man."

"You mean that pitiful old geezer?"

Xue Ganom looked Qing up and down.

"Well. I suppose that makes sense."

"Why do I suddenly feel really offended?"

"I heard the Purple Lightning Demonic Warlord's daughter died around your age. But apparently, she was so nasty and rude that she could rival the Three Great Evil Women. Maybe that's why he feels close to you."

"This is kinda weird. Why do I keep feeling worse? My hand is strangely itching to do something."

Qing waved her pale hand that was glowing white.

Only then did Xue Ganom shut his mouth.

"I have ears too, you know? I've already heard the old man's gone senile. But you gotta at least try to talk things out to know, right? It's pointless to just decide 'this person won't do' without trying."

"But the Purple Lightning Demonic Warlord is a hardcore Demonic Cult follower who's lived his entire life as a devout cultist. No matter what tricks you pull, I do not think he'll help you."

Qing waved her hand, changing the subject.

"Forget it. Can you just look into the killing, burning, and stealing approach? From what you said earlier, it seems you're quite the expert in that area."

Xue Ganom chuckled.

"Of course. I have spent every waking moment fantasizing about the world's destruction. Is that not the mark of a true specialist?"

"Ooooh! That's reassuring! How brilliant!"

"Considering how you pretended to have a leg injury and left only traces of the White Hand Demonic Arts in your killings, you seem quite meticulous yourself."

"That's because I'm just a superior person. But you're pretty awesome too, Xue Ganom."

It was a scene of two Great Demonic Adepts patting each other on the back.

"As a Divine Maiden Sect disciple, you'd use a sword. Can you handle a dao or spear by any chance? Even if you are not proficient, being able to imitate the traces left behind should be enough."

"Of course I can. Who do you think I am? Just tell me what you need."

Xue Ganom nodded.

"Then, first, we should burn down the Taiping Group of the Inner Palace Department. So, basically..."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After returning before dawn and closing her eyes with a peaceful mind, it was suddenly lunchtime.

Qing's body and mind felt incredibly refreshed after a good night's sleep.

\textit{Wow, what's the deal with this Great Tranquil Zen Art? The effects are insane.}

\textit{But, hmm. It's not entirely good.}

Usually when one wakes up, their mind should be foggy, their limbs weak, and their throats dry.

Then there was the pleasure of enduring your thirst while rolling around in bed, enjoying the lingering drowsiness.

But with her mind snapping to full alertness like this, it felt like she was missing out on at least one percent of life's pleasures, if not as much as half.

So Qing spent time in bed with wide-awake eyes.

Whether drowsy or not, she ended up lazing about anyway, after all.

Not long after, someone barged in, nearly breaking down the door.

It was Qing's worthless Senior Sister, Jian Buxi.

"Junior Sister! Are you going to eat?"

Normally, people don't ask if you're going to eat right after you wake up.

Because usually, people don't look for food immediately upon opening their eyes.

But anyone who lives with Qing for three days would start asking about food instead of greeting her.

After all, Qing was the type to look for food as soon as she opened her eyes.

Jian Buxi closed the door, walked briskly to the wardrobe, and opened it.

She gathered underwear, inner palace attire, and outer palace attire, hugging them before heading to the bed.

Qing responded with a series of familiar wriggles, raising her arms and legs.

Jian Buxi matched her movements, dressing her.

Her actions were natural and skilled, as if she had done this many times before.

"What's for food today?"

"Dried fish in thick sauce with eggplant soup?"

"N-No..."

Chinese cuisine, with a few exceptions, was just a list of ingredients and cooking methods.

Qing, usually strict about meals, showed rare cleverness at times like this.

"Dried fish in thick sauce" meant dried fish cooked in a thick, simmered sauce.

Qing knew a similar dish from her hometown called "braised pollack."

Qing's eyes trembled pitifully.

"How, how can such a reality exist..."

"Junior Sister!? Are you okay!?"

"I'm not okay. Mark today's date. I don't want to forget next year that today is when we have to set up an annual memorial service for all the Bliss Palace cooks."

"Hmm... Then, shall we eat out?"

It was welcome news, but Qing shook her head.

"I'm planning to eat with Gramps today. I have some things to discuss with him."

Jian Buxi's shoulders drooped, and she glanced furtively at Qing.

"If I'm being a bother..."

To be honest, she was being a bit of a bother. Or rather, annoying.

Even as the youngest, Jian Buxi had always been everyone's plaything in the Bliss Palace, but now she was completely ignored as well.

In professional terms, she was considered ‘outside the ranks'.

There were open rumors about how she got her Second-Grade Disciple position through connections despite her lack of skill.

However, this didn't exempt them from Jian Buxi's bullying, making life miserable for her subordinates daily.

Things might have been different if the dim-witted Senior Sister had handled herself better.

But her excessive bullying, which didn't discriminate, earned her contempt from above and both contempt and fear from below.

\textit{So while I can understand her desperate clinging day after day...}

The truth is, when Qing was losing her mind, she took advantage of Jian Buxi's situation and treated her like a servant.

If she made even one mistake, Qing would get all serious and say she didn't want to see her face, or mutter to herself about replacing her with someone else, showing clear disappointment.

Basically, in the end, this was all karmic retribution.

The triangle of conscience in Qing's mind spun wildly.

Although it was almost a circle by now, because her basic settings when it came to conscience were so small they were practically the size of a bean, there was still a part of her that scratched at this miniscule conscience.

"That's not it. Let's eat out together for dinner."

"Okay! And let's train together after dinner too!"

\textit{Shit, she's trying to push for this now?}

However, it was a rather awkward time to refuse.

After reluctantly nodding, Jian Buxi left the room with a sunny expression.

Qing was left alone, waiting for Cui Liweng to visit.

Grumble.

Suddenly, a thought occurred to her.

\textit{What if Gramps doesn't come today?}

Fortunately, Qing didn't have to experience one of the most terrible things a human can endure in this world - skipping lunch.

Cui Liweng, who had sneakily eaten lunch alone, came by to invite her for tea.

"What? While someone was starving here waiting, you went and ate by yourself? Gramps, I didn't think you were like that."

"Did you make an appointment in advance to wait? You are barking nonsense as if it is perfectly normal for me to wait for you."

"That's not important. What's important is that I'm hungry."

"Tsk. You cruel girl. Where did you get such a temper from?"

The OG Crutch grumbled as he picked Qing up.

It was a comfortable ride, befitting the original; the great sensation of a true Demonic Adept carrying her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Meals are more enjoyable with company.

Why? Because the number of dishes increases.

Moreover, Qing could outpace any competitor in devouring dishes anyway.

What mattered was the variety.

In that respect, Cui Liweng was a good dining companion.

This old man, despite looking like a complete skeleton in faded old clothes as if he couldn't afford to eat, had a suspiciously large sum of money.

\textit{What the hell? If you have money, what's the point of looking like that?}

\textit{So it shouldn't matter if I spend a bit of his money, right?}

Qing demolished the meal like it was a battle.

The scene of which she treated her food could be described as total war.

Cui Liweng kept nagging, but it was just the usual ramblings of a foul-mouthed grandfather, so it didn't have much impact.

"Even a pig would eat more gracefully than that."

This was Cui Liweng's comment as Qing's meal was wrapping up, after he had ordered all sorts of desserts for her.

"Come on. If I eat more gracefully than a pig, is that something to be proud of? Comparing yourself to a pig isn't something to brag about no matter how you eat."

"Hoho. That mouth of yours."

"Anyway, Gramps. I can't live like this anymore. I'm planning to cause some a shitstorm and run away. Choose now. Who will it be? Me or the Heavenly Demon Divine Cult?"

Qing suddenly threw a curveball.

Cui Liweng flinched visibly.

"Child."

"There are bad guys everywhere. What's this ‘law of the strong'? A law of nature? Nah, that's wrong too, but even if it were right, so what? Shouldn't humans live by human laws instead of the laws of beasts?"

"That will not last much longer. Soon, when the Heavenly Demon descends upon this land, he will liberate Zhongyuan. Under his leadership, a new world of equality for all people under the heavens will open up."

"But isn't that bastard the biggest problem? That Alleged Supreme, isn't he the worst scum of humanity?"

"That's..."

Cui Liweng seemed at a loss for words, his mouth opening and closing.

Finally, Qing had no choice but to say something unpleasant.

"Do you know that scumbag is planning to fuck me? Look at him giving me all these Fairy Arts to learn. I'd rather die than go through that. I'll seriously just bite my tongue and die."

For reference, people don't die from biting their tongues.

Humans weren't evolved to be that fragile.

Of course, there was a small chance of choking to death if the severed tongue retracted and blocked the airway.

But how would Qing know that?

Cui Liweng sighed deeply and spoke.

"Haa. Child. You do not need to worry about that."

"About what?"

"The current Supreme and the future Heavenly Demon Supreme who will complete the Divine Art by accepting the Heavenly Demon Spirit are completely different beings. Once he completes the Divine Art, he will no longer have any interest in you."

"How do you know that, Gramps? Your words aren't making any sense. His interest will disappear? Does learning the Divine Art suddenly make him like men or something?"

"That's..."

Cui Liweng suddenly seemed at a loss for words, mumbling and avoiding eye contact before continuing.

"...I cannot tell you."

"Wait, what? Really? He becomes gay, I mean, a \texttt{homosexual}?"

Qing asked in shock.

She was so surprised that she even spoke a Western term.