\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (8)}

Jian Buxi, who was helping Qing put on her sleeve, spoke.

"Junior Sister, did you hear that story!?"

"I can't know what story you're talking about unless you tell me first."

"The Taiping Group was burned down! I heard it turned to ashes!? All the prisoners escaped too!"

Qing had only burned two buildings.

And all she had done was release the prisoners locked in the underground prison.

It was just that the prisoners celebrated their sudden freedom with a fire show in the middle of the night.

"Ah. Is that so? That. Is. A. Huge. Prob. Lem. How. Unfortunate."

"Huge problem? No! I'm happy!"

"Why is Senior Sister happy about it?"

"I borrowed some money from the Taiping Group before, you know? The interest piled up so much that I made several pledges, but now they've all gone up in smoke!"

"Pledges?"

"Yep. I think it was how I had to perform comfort activities for Divine Cult fighters in the future Zhongyuan Liberation War? Oh, and demonstrations of new medical techniques at the Medicine Hall, and being backup personnel to continue the lineage if the Divine Veins are in danger of extinction. Top priority food supplier in case of isolation? There were lots of things."\footnote{Holy shit, how more pitiful can a human being be?}

None of the items sounded trivial.

It was literally mortgaging her entire future.

Qing asked, just in case.

"Do you know what all that means?"

"I don't know. But they said it wasn't anything too difficult."

Qing nodded.

\textit{Sheeeeesh wow, it was worth the effort to burn it down.}

\textit{They weren't just any old sons of bitches, huh.}

\textit{Maybe I should've stayed longer and burned more shit with the prisoners.}

"But how much did you borrow to make such pledges?"

"Here. Lift your butt."

Jian Buxi answered while helping Qing put on her palace skirt.

"About thirty silver sycees?"

"That's quite a lot, isn't it?"

Qing didn't ask out of any particular curiosity.

It was just an extension of the usual conversation between acquaintances.

But immediately after, Qing was put into a rather uncomfortable position.

"Yeah. My mom was sick."

"Ah, the price of medicine for your mother..."

"But then they suddenly raised the interest to 30\% per month, you know? They clearly said it was 30\% per year when I borrowed it. But everyone said it was normal, so I guess that's how it is."

This was how the Divine Cult governed its followers.

Tian Shan Divine City, being barren and without any special products, largely depended on the income of loyal special forces who went on external missions.

The Divine Cult had numerous businesses set up in Zhongyuan.

It was a cult sustained by special experts like professional black market merchants, grave robbers, robber gangs, human traffickers, drug criminals, loan sharks, and gambling dens, all united by the power of religion.

Thus, money and goods flowed in from outside and went to the Divine Cult's officials.

By that, it meant they flowed to the combat units and affiliated sects.

So if you didn't want to meet a miserable end as a debtor in Tian Shan Divine City, you had to learn martial arts and join a combat unit.

This achieved the first of the two teachings emphasized by the First Heavenly Demon: the great total armament of making all cult members into martial artists.

"So, is your mother alright now?"

"Huh? She's dead though?"

"Mm. Oh. I'm sorry."

Qing, feeling even more uncomfortable, closed her mouth.

However, Jian Buxi just smiled brightly.

"It's okay! My mom and I were practically enemies, you know. She always hit me, calling me a stupid retard who's mentally disabled, a useless bitch who only wastes food. I might be a bit dumb, but I'm not dumb enough to like someone who hates me."

Qing broke out in a cold sweat.

\textit{Shit. Isn't this becoming more and more of a problem?}

\textit{I swear, there's not a single thing I like about this neighborhood.}

Qing awkwardly offered comfort.

"Uh. That must have been tough."

"No, no. A useless bitch deserves to be hit, right? So I paid her back in kind. She was sick but didn't do anything, so she was useless. She made such a fuss every time I hit her. Going on about how I owe her for giving birth and raising me."

"Hmm."

"I repaid the grace of giving birth by borrowing money in my name for her medicine, right? And if she didn't raise me properly, then the grace of raising me is invalid!"

"Hmm. Well. Yes. You did well."

"Hehe, I did, right?"

Jian Buxi was someone who definitely got her revenge.

Still, considering she took care of paying back the supposed grace of giving birth, she really wasn't that bad of a kid.

But she wasn't exactly good either.

\textit{Wait a minute. If it's like this, then maybe…}

"Senior Sister? If you have any resentment towards me, could you tell me now instead of hiding it? Let's not have any of this keeping things bottled up and getting back at me later."

"Huh? What are you talking about! There's nothing like that!"

"Really?"

"Yeah! Junior Sister is the only one who's ever been nice to me anyway! You're more like a mom to me than my own mother! When I was little, I was so envious of other people's moms. You know, chasing after and beating up anyone who bullied their child, always giving me tasty things and nice things. But now I have a Junior Sister who does things like that too. Hehe..."

\textit{I thought she was just a slightly dim-witted crutch.}

\textit{But turns out she was a daughter taking care of her uncaring, aged mother.}

Qing felt even more uncomfortable.

This was why if people weren't careful in their daily lives, they could become a piece of shit in an instant.

Just like that, the worn-out triangle in Qing's conscience was spinning wildly first thing in the morning (It wasn't actually morning).

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing is no longer the Qing of the past.

She is now the rather unorthodox successor who has inherited the great Buddhist teachings of the Great Tranquil Zen Art through some half-assed, despicable method!

So she was no longer that scoundrel who made her teacher do all sorts of menial tasks including massages, and only played a single verse of the Heavenly Heart Harmony whenever she felt like it.

Qing reflected on her past behavior of disregarding educational authority and thought.

\textit{Right.}

\textit{Madam Kang is trying her best to teach me in her own way, so I shouldn't treat her so carelessly.}

\textit{Hmm.}

\textit{But.}

\textit{Isn't she just trying to use me for their own benefit rather than teaching me to improve?}

\textit{Isn't she on the same level as those rebel bastards raising child soldiers?}

\textit{Madam Kang is a real fucking bitch after all.}

\textit{Calling Madam Kang a teacher would be an insult to the roughly less than 6 billion teachers in this land.}

\textit{I mean, the range of error is a bit wide, but since I don't know the population of this world, I just went with the maximum.}

\textit{That's right.}

\textit{Come to think of it, I didn't really do anything wrong.}

So Qing just did as she always did.

After casually picking her nose and gesturing to clean the room with her toes, she diligently played one verse for her today as well.

Madam Kang shed a veritable bucket of tears because she was so moved at the performance and quickly ran away.

Maid Soyeong respectfully bowed at the waist and followed with a very refreshed expression.

Madam Kang's expression was becoming more and more rotten, while Maid Soyeong's was becoming brighter in contrast.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And then, it was time for dinner.

After that, an ordeal awaited Qing.

She had to take time out of her day to perform the Immortal Disrobing Dance with her Crutch.

At first, Qing truly felt self-loathing at the thought of having to perform a Immortal Disrobing Dance.

But the Crutch's disastrous dance moves had a devilish charm that made viewers clutch their chests in frustration, stand up, and shout to ‘Do this like this and that' while participating.

Jian Buxi's Lustful Immortal Disrobing Dance made people burst with awkwardness, pity, and frustration instead of lust, so it could naturally be called a truly malefic dance.

At any rate, Jian Buxi seemed to be enjoying herself despite achieving absolutely nothing with her completely new reinterpretation of seduction.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After that, she went to bed early.

And then she woke up, shuddering at the heaviness of the unwanted desire for a killing spree. But at the same time, she was inexplicably brightening the night with a wide smile and hopping along with excited steps.

After entering the courtyard and skillfully pushing the rope once with her foot and pulling it skillfully. Hm?

\textit{Wait. Didn't he say he'd remove the rope?}

And so Qing flopped down in the small room (living room).

But today something felt a bit...

As usual, Xue Ganom appeared, dripping water.

"You are here"

"What's this? Didn't you say you'd remove the water bottle?"

"On second thought, if it becomes known that I helped you, assassins might come. Being wet is better than being dead."

"What the? You don't trust me?"

"A wise person always prepares for the worst. I need to stay alive to plan for the future."

\textit{Indeed, Xue Ganom, there really isn't anything to refute when it comes to you.}

As always, Qing changed the subject.

"By the way, ventilate a bit. This old man, bachelor, widower musk is no joke. It wasn't like this last night, though?"

Then Xue Ganom somehow looked triumphant and raised his chin.

"What the heck? What are you trying to say with that?"

"Well, it is a man's house, so of course it smells like a man. I guess you are a woman, after all. Are you getting all hot and bothered?"

"You know, since you're not impotent anymore, can't you stop with the harassment?"

"I was never truly impotent, though. Come to think of it, you are right. As I was born a man, I was indeed improper. I apologize."

It seemed the joy of regaining his masculinity was far greater than Qing had thought.

\textit{Well, since he escaped the eunuch label, I can understand that elation, but still.}

Qing looked at Xue Ganom's long, slender eyelashes and forcibly swallowed the words that had come up to her chin.

There was no need to say words that would cause unnecessary hurt.

"Anyway, as you said, I left plenty of traces of the Blood Shadow Thunder Lightning Dao Technique, burned down Taiping Hall and the records office, and released the prisoners from the underground prison."

"I heard the news too. But do not be complacent. The Taiping Group is merely the weakest among the Demonic Cult's combat units."

Xue Ganom spoke as if he were one of the Four Heavenly Kings of the Demon King's Army.

"As you said, the Demonic Cult's determination to recover the Heavenly Demon Spirit will be extraordinary. They will surely mobilize all available combat units."

"So?"

"But the Taiping Group has burned down. If we burn down a few more combat units in the same way, the Demonic Cult members who were suppressed by force will cause an uproar. The very existence of the city will become unstable. They will have no choice but to deploy an elite few, as they need to prepare for the Great War Between Orthodox and Demonic."

\textit{Oing? Wot? An elite few?}

\textit{Teacher Seol, you never mentioned this before.}

\textit{If you suddenly switcheroo shit like this, I can't guarantee my trust either. You understand?}

With these thoughts, Qing asked grumpily.

"Wouldn't an elite few be more dangerous? Even I, the great Ximen Qing, might feel a bit uneasy if there are Transcendent Realm Masters crawling all over the place."

"Isn't a small elite force still better than a large elite force?"

Qing immediately understood the short, logical rebuttal.

He was indeed the owner of a brain worthy of being called the greatest intellect in Zhongyuan.

\textit{As expected of Xue Ganom! I believed in you! Your performance and capabilities are definitely guaranteed!}

With that, Qing's eyes sparkled as she asked a question.

"So, who should we kill and what should we burn today?"
