\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (9)}

"I went to console them because the Taiping Group had burned down. But when I returned, our Interlunar Crescent Team was on fire. I burst into tears as soon as I saw it."

This was the testimony of Si Miping, a survivor of the Interlunar Crescent Team.

Of course, they were tears of relief.

He had bought drinks to console a friend who lost his job, and ended up saving his own life. This truly embodied the saying that one should be generous to others.

However, this didn't work on Shi Hengheng, the Divine Cult's top investigator who was ruthlessly impartial without blood or tears.

"You should have been on duty at that time, right? What is this about consoling?"

"H-How did you..."

"Someone who survived by being in the outhouse at the time of the attack testified. He said the night watchman was not even at his post. No wonder we couldn't detect when the villain attacked."

Shi Hengheng cast a cold gaze.

"I shall pass judgment on-site with my authority as a senior investigator. Abandoning your post is no different from aiding the enemy. It is the death sentence for you."

"W-Wait a moment! Investigator!"

"Do not feel too wronged. I also sentenced the warrior who was in the outhouse to death for desertion, as he hid instead of fighting back. You two will hang side by side."

"Investigator! This is unfair! Is it really a capital offense for a ten-man leader to drink during night watch when everyone does it? Investigator! Investigator!"

"Do you really not know your crime?"

"If we don't drink during night watch, what else are we supposed to do? Should we stay wide awake in the middle of the night, guarding an empty entrance just in case someone attacks, like new recruits do? That's something you don't have to do after six years!"

Si Miping truly felt wronged.

Wasn't it common sense for a ten-man leader with over five and a half years of service to drink during night watch?

Shi Hengheng shook his head.

This was what happened to normal people when they were stuck between unnecessary military discipline, harsh treatment, and superiors who allowed it.

As Shi Hengheng left the temporary detention center, he ordered.

"Take them to the underground pri- No, we do not have one anymore. Just kill them and hang them in the streets."

"Yes, Investigator."

The reply was extremely polite.

And for good reason - Senior Investigator Shi Hengheng was recognized by the entire Divine Cult as the best investigator.

The arrest rate for cases Shi Hengheng handled exceeded 100\%, reaching an astounding 420\%.

A miraculous record of arresting ten culprits for every ten cases he took on, plus an additional thirty-two self-proclaimed criminals!

The identity of these thirty-two self-proclaimed criminals was unknown, but they were executed for obstructing the investigation, so their motives would remain forever a mystery.

The verdict was harsher because they stubbornly hid the truth and spread lies by insisting they were the culprits even under severe torture during the investigation process.

"Still, this is a clever and bold crime that pierces through one's psychological weak points. This is no ordinary criminal."

The day after the Taiping Group burned down, the same culprit attacked the Firewind Team under the Outer Hall Combat Division.

No one imagined they would attack again the next day using the same method.

It was only natural that the Firewind Team fell victim.

And then the night before last, which was yesterday.

The Interlunar Crescent Team was hit by the same method.

Despite using the same method for two days, they carried out a third massacre on the third day.

Truly a divine move that no one could predict!

Shi Hengheng acknowledged that this time he had finally met a true worthy opponent.

\textit{The culprit cowardly snuck in at night, massacred everyone while they slept, and then set fire to them.}

\textit{A real man should settle grudges honorably in broad daylight before everyone, even if there was a vendetta.}

\textit{How could they use such a petty method...}

"Ah! I see! I've solved one puzzle!"

"Investigator? Have you figured something out?"

"The culprit could be a woman. Because this is not a man's method. Haven't I ordered to round up all the men who recently flowed into the Divine City? Round up the women too."

This was the sharp deduction of the top investigator with a 420\% arrest rate.

\textit{But wasn't the White Hand Witch originally a woman anyway, and weren't the traces of the Blood Shadow Thunder Lightning Dao Technique from an insider?}

Wa Sunja, who was the assistant investigator, prosecutor, and executioner, thought this but didn't dare to voice his opinion.

Who would dare to even cough in the face of the legend with a 420\% arrest rate?

"Yes, Investigator."

"Investigate thoroughly. The honor of the Taiping Group is at stake. You remember what I always say, right?"

"Yes. 'Torture knows the answer'. I have firmly engraved it in my heart."

Shi Hengheng nodded with a cold expression.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"These days, there are so many corpses hanging in the streets! The stench of rotting bodies is so terrible it's hard to breathe! And the insects swarming around! So, let's go watch together!"

Qing tilted her head.

\textit{Wait, isn't that a bit strange?}

\textit{How does that lead to that kinda conclusion?}

\textit{Isn't the premise and conclusion too disconnected?}

"Why would we go watch stinking corpses swarming with insects?"

"To throw stones at them! If you hit a limb and make it fall off, you get one coin. If you hit the neck and make the body fall, you get three!"

"Ah. I see. Is this a traditional Divine Cult game?"

"Yep!"

Jian Buxi answered with a radiant smile.

Qing thought to herself.

\textit{Damn, these Demonic Cult bastards really do all kinds of shit, don't they?}

\textit{Now, they even desecrate corpses?}

This would make the Demonic Cult feel wronged if they heard it.

Qing didn't know, but this was actually a custom that flowed in from Zhongyuan.

However, it would be unfair to blame Zhongyuan either.

The act of desecrating criminals' corpses for enjoyment was a human nature practiced quite naturally in both East and West.

It was practically a guidebook written by rulers in uncivilized times.

It had an excellent effect in cultivating citizens' law-abiding spirit and fostering community consciousness.

Qing looked at Jian Buxi with a disgusted expression.

"Senior Sister."

"Yes?"

"Do you perhaps... not want to go to Zhongyuan?"

"I don't want to!"

It was an immediate answer, as sharp as a knife.

\textit{I thought she'd say she wanted to go…}

\textit{Well, if she doesn't want to, there's nothing I can do.}

\textit{People live their own lives.}

\textit{I can't force her to come along either.}

Instead of forcing her, Qing asked for the reason.

"Why?"

"Why would I go to that terrifying Zhongyuan?"

Jian Buxi asked back instead.

Qing wasn't at a loss for words.

However, this Crutch of hers had originally received brainwashing that made her think of Zhongyuan as some kind of hell on earth.

So Qing answered simply.

"Because I'm going?"

"Then I want to go too!"

\textit{Looks like this brat is destined for a short life.}

\textit{She's the type to follow along obediently if offered candy.}

\textit{To think that someone, who only knows Zhongyuan as a very dangerous place, will be so thoughtless, hmm.}

\textit{Come to think of it, she is a pretty absent-minded kid. Who has nothing in her brain.}

\textit{Still, that heart of hers is a bit admirable.}

Qing gave a warning instead.

"It's a secret, so don't go around talking about it anywhere."

"Okay! I absolutely won't tell anyone!"

And then in the afternoon, it was again time for an authentic Chinese massage with Alleged Teacher Kang.

Qing had wondered why there were so many Alleged Ones, but thinking about it, the Demonic Cult members were Alleged Divine Cultists to begin with.

Since the head honcho was an Alleged Natural Realm, it's only natural that those below him would have strong opinions of their own. They were all a bunch of wannabes.

There were only about ten verses left of the Heavenly Heart Harmony.

If she stalled for time, that would last her about two weeks.

After that, it would be time to head to the Heavenly Demon Tomb.

As Qing was organizing her thoughts, she suddenly realized it was an important moment and hurriedly spoke up.

"Ah. Right there, right there! The waist! Teacher, could you press a little harder? Why is an old person so weak? Because of you, I'm losing strength too and can't play the flute. Ah, yes. That's it. Perfect."

Feeling satisfied with Teacher Kang's attentive touch pressing firmly above her tailbone, Qing continued her train of thought.

Xue Ganom said he planned to escape before then.

\textit{Maybe I should tell him to take the Crutch along then.}

\textit{I could tell them to meet in Sichuan?}

\textit{After all, we'll have to stop by the Emei Sect anyway.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

'Today is the new moon, so it is a good opportunity to kill the Sura Demonic Sword. I have heard he is an extremely sensitive and cunning Demonic Adept in the Late-Stage Transcendent Realm, soon to enter the Unrestrained Realm. Of course, it is dangerous, so whether to kill him or not is your choice.'

'What? You want me to fight a Transcendent Realm Master? Xue Ganom, do you want to fight me that badly? Why? Wanna have a go now?'

'The Sura Demonic Sword is the leader of the Sura Sect. If the leader dies, they will have to hold a funeral. Is this not a chance to take out another sect after the Royal Demonic Path Sect?'

So Qing pondered all day.

And came to the conclusion that it might be worth trying.

'I heard the Sura Demonic Sword can only fall asleep after seeing a virgin's blood, due to side effects from his Demonic Arts.'

'So you're saying he kills one virgin every day?'

'Not every day. Even the Demonic Cult could not find that many virgins. So I heard he kills one every two weeks, on the full moon, and sleeps for a whole day.'

'Ah. So we sneak in while he's sleeping?'

'Well. Everyone knows when the Sura Demonic Sword is vulnerable, so the protection around him will be exceptionally tight.'

'Then what am I supposed to do?'

‘You will have to figure that out. I do have some ideas, but I am not sure if you can pull them off.'

Xue Ganom wasn't affiliated with the Demonic Cult.

He hadn't planted any spies or informants either.

If Xue Ganom had that level of ability in the first place, he wouldn't have a big brand that said ‘toilet' stamped on his forehead.

Nevertheless, his strategies based on bits and pieces of information he had picked up here and there kept working out perfectly.

He was truly someone only Qing would consider the greatest intellect in Zhongyuan.

As a result, there were no detailed aspects to the plan.

Qing had to figure things out and resolve them on her own as a martial artist.

That's why Qing was sitting on her butt near the back gate of the Sura Sect on the night of the new moon.

She came because he said it was a good opportunity, but…

\textit{Is this right?}

\textit{Is this really okay?}

Qing kept sighing deeply.

And after some time had passed.

She saw a black-clad figure approaching, carrying a large sack on their back.

It was a strange sack.

A fascinating one that kept wriggling and bulging as if something was inside.

In precise academic terms, this was a model example of what's called ‘kidnapping'.

And now it was Qing's turn to replace the contents of the sack.

Of course, it's not that Qing didn't have her own beliefs.

\textit{If it doesn't work out, I'll just run away, and if I get caught, I'll reveal my identity and threaten them, right?}

\textit{I might get cursed at a bit, but it's not like they'll throw me away, right?}

\textit{They won't not open the Heavenly Demon Tomb, right?}

\textit{If I succeed, I kill one Great Demonic Adept, and if I fail, I just get shat on a bit, right?}

\textit{There's really no reason not to do it...}

\textit{Xue Ganom said that seeing a virgin's blood didn't mean that kind of blood.}

\textit{Something about hymen blood or whatever.}

\textit{Anyway, he also said it wasn't that different since they kill them after the deed anyway, but…}

Qing stopped thinking.

\textit{Fuck it, I don't know. I don't care. Whatever happens, happens.}
