\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (10)}

A stone flew and hit the black-clad figure's forehead.

The figure swallowed a curse, threw down the sack (accompanied with a muffled "eep!" sound), and drew their sword, pointing it straight ahead.

"Who's there?!"

But there was no answer.

As the black-clad figure stared at the shadows ahead with tense, trembling eyes...

Tok. The light sound of something falling to the ground.

Then strong hands suddenly wrapped around their neck.

The figure struggled, but with their blood flow cut off, they soon lost consciousness as their eyes rolled back from lack of blood to the brain.

Qing carelessly tossed aside the black-clad figure and opened the sack lying on the ground.

"Mmph."

"Shh."

Qing put a finger near her mask, then lightly pointed outwards.

At this simple gesture indicating she would free her, the woman who had been kidnapped nodded urgently.

Qing untied the gag in the woman's mouth and the ropes binding her arms and legs.

The woman bent over sharply three times, bowing as if to show her gratitude, then ran off silently into the darkness of the moonless night.

Qing gathered the gag and ropes and put on the sack herself.

She laid down and wriggled, reaching out only her hand to grab the sack string and clumsily tie it.

As she carefully pushed the tied string out through the opening and took off her mask, putting on the damp, unpleasant gag and messily tying ropes around her arms and legs...

The black-clad figure who had briefly lost consciousness came to.

They immediately jumped up upon opening their eyes, looked around quickly, then sighed in relief seeing the kidnapping sack still wriggling on the ground.

After all, though there had been an unpleasant incident like an attack, all's well that ends well, right?

The figure decided to take this surprise attack to their grave, and picked up the sack again.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The first Sura Swordsman believed human nature was no different from that of beasts.

So he thought, humans have flourished enough to rule the world by wielding swords.

Then wouldn't savage beasts be even stronger if they wielded swords?

What if a bear held a sword? That would be sick as fuck. Let's make it happen right away.

Thus, the Hundred and Eight Sura Swords was created as a martial art to awaken humans' hidden bestial nature.

However, the Sura Swordsman underestimated human bestiality.

Once bestial nature seeped in, people instinctively craved blood, losing their minds as soon as they picked up a sword, leaving behind only a Killing Fiend.

But still, they were incredibly strong.

Of course they would be, as beasts who wielded swords.

And so the Hundred and Eight Sura Swords proudly took its place as one of the Ten Great Demonic Arts, and the term 'Sura Demonic Sword' came to refer to those who mastered this art.

Throughout history, numerous Sura Demonic Swords tried various methods to erase this side effect.

The most moderate method that emerged was based on the idea that a satiated beast doesn't hunt.

If they saw blood in advance, couldn't they suppress the explosion of bestial nature?

It was in the realm of philosophical thought that if you eat before you get hungry, you won't be hungry even as time passes. 

There couldn't possibly be any fallacies in that, right?

But surprisingly, it worked.

And so the Sura Demonic Swords came to periodically crave blood.

However, since human bestiality was not free from individual hidden desires, each Sura Demonic Sword throughout history had slightly different tastes in seeing blood.

The current Sura Sect Leader Cho Deungnam's taste was one of the cruelest in history.

It was said he would take a virgin's hymen in a bestial coupling, then tear the partner to shreds afterwards.

Because it was so horrific, the ritual was carried out in secret in a special chamber sealed tightly on all sides.

No one except the Sura Demonic Sword himself knew exactly what that cruel coupling looked like.

And now a new sacrifice has been thrown into that special chamber.

Rip!

The sack was torn open heroically, revealing the outside.

Qing looked out with surprised eyes.

"Huff, huff."

And her eyes met directly with the guy wearing a pitch-black mask.

Qing was so startled she cursed without realizing.

It was that curse from her homeland that served as an all-purpose swear word, exclamation, and expression of shock. \texttt{Fuck!}

"Mmph!"

Thanks to the gag in her mouth, the curse didn't leak out.

"Heuheu, stay still. If you just listen to me veryyy well, you might be able to return alive. Your Inner Qi is blocked, so you must feel uncomfortable, right? That's because of the Qi Dispersion Poison, so there's no need to worry too much."

Qing quickly looked around.

It was a room sealed on all sides.

Clearly ominous restraints gleamed, well-polished but stained dark red with all the blood it had veritably absorbed.

Several shackles attached to chains hung on the walls, and various tools like whips and clubs were strewn about on a platform.

Qing immediately regretted seeing this sight.

\textit{Shit. I fucking knew it. This really ain't it.}

\textit{This isn't some mere 18+ adult content. It's a slaughterhouse.}

\textit{I should just get out of here right away.}

Qing decided to immediately reveal her identity and leave.

She pushed out the gag in her mouth and spoke right away.

"Elder, I have something to tell you."

"Shh."

As the tip of a dagger rose to her chin, Qing stopped mid-sentence.

"You have such beautiful looks. I did not know the Divine Cult still had such a virgin left. I must give a big reward to the person in charge."

"That-"

"Shh. Enough. If you wish to live, keep your mouth shut."

Qing wanted to live, so she closed her mouth for now.

Then surprisingly, the masked figure started untying her arms and legs.

Of course, it was just loosely tied bindings that could be easily undone, only appearing intact on the outside.

Qing tried to talk again.

"Actually, this girl is- ugh."

But her words were cut off as the masked figure took off something similar to a cloth that was wrapped around his body.

\textit{Shit, my eyes!}

Qing's expression became one of genuine disgust.

It would have been better if he was just naked.

Back home, Qing was used to seeing naked men in bathhouses without batting an eye.

But wearing a black mask, and then…

No, it was an outfit too horrible to even describe.

The masked figure's exposed eyes widened.

"Huk! That expression! Perfect! More, despise me more! Look at me more as if you are looking at trash! Hurry!"

"That-"

"Good, there is no need to worry too much. Why do you think I covered my face? If you satisfy me, not only will you be able to return safely, but you will be able to leave with plenty of gold."

"This girl is-"

"Here. Take it."

And he held out the whip in his hand.

Since it was clearly meant for her to take, Qing reflexively grabbed it.

"This is...?"

"Huff. Huff. Use that to strike this body. Hurry! This body is an amazing Master, so there is no need to worry!"

And then he turned around.

\textit{Fuck, my eyes!}

Qing frowned again.

The sight of his sagging buttocks crisscrossed with leather straps dealt serious damage to her mental health.

If Qing had been an ordinary virgin from Zhongyuan, she wouldn't have known what to do in this outrageous situation.

But Qing, who had lived through the ocean of information that was the internet and was a witness to the flood of all kinds of sexual preferences, immediately understood the situation.

This guy's just a fucking pervert with that kind of fetish.

"What are you doing! Hurry!"

Crack!

Qing decided to go along with it for now and casually swung the whip.

Made of soft leather braided into multiple strands, it was more like a switch meant to cause pain rather than a weapon.

"Huk, your strength is quite impressive! But it is still not enough! More, harder!"

Crack!!

"Harder!"

CRACK!!!

"Good! More, moRE, MORE!"

CRACKKK!!!!

"Haaah... more, more!"

Qing shook her head slowly.

What was it again? Brutally rape a virgin and tear her to death?

No, more like he'd rather be known as a brutal Great Demonic Adept rapist murderer than have this pathetic appearance revealed.

After all, isn't this a neighborhood where brutality isn't particularly frowned upon?

The Zhongyuan were conservative.

So if this side of him became known to the public, he wouldn't just be socially buried, becoming ignored and canceled. No, it would be a form of social suicide. Or perhaps even beyond that.

So he'd probably silence her after enjoying himself fully.

Qing's guess was half right.

In any case, blood had to be seen to suppress the bestial nature of the Hundred and Eight Sura Swords, so after satisfying his sexual desires, it would lead to a time of cruel slaughter.

"What are you doing! Quickly! Quickly!"

Qing looked down at the Sura Demonic Sword rubbing his body on the floor.

\textit{I see, I see. Alright. If that's what you want.}

In the Demonic Cult, where total armament of all believers had been achieved, there were no civilians who didn't know martial arts.

But it seems he thought the Qi Dispersion Poison or whatever had completely scattered her Inner Qi.

He probably thought a woman without Inner Qi couldn't do anything to a martial artist at the upper end of the Transcendent Realm, no matter what she tried.

Qing's hands moved busily.

The relentless whipping was fierce beyond measure.

As lines kept appearing on the Sura Demonic Sword's exposed back, at some point he stretched his body and legs stiffly and started trembling.

"\texttt{Fuck!}"

Qing at least knew the basics of whipping after playing with Teacher Kang.

The basics meant injecting Inner Qi to make the whip stiff or bend it depending on which spot she desired to hit.

Qing drew up a huge amount of True Qi from her dantian.

The jumbled True Qis of Orthodox, Unorthodox, and Demonic surged like a tidal wave in response to her will.

Qing's Inner Qi had already reached the upper levels of the Transcendent Realm when she left the Divine Maiden Sect.

Adding all sorts of Demonic Qi on top of that in the Demonic Cult, its sheer volume alone now approached the Unrestrained Realm.

Five-colored Whip Qi wrapped around the whip, standing straight as a blade, and uncompressed True Qi overflowed as Whip Threads.

No, it was now beyond what could be called threads.

The True Qi spreading in all directions with the thickness of a thigh was almost like a forest fire.

"Wait, this is-!"

Though the Sura Demonic Sword was in the Transcendent Realm, his body and mind had just reached climax from being whipped.

As such, during this time when body and mind had simultaneously lost strength, if he could respond quickly, he would truly be a superhuman beyond humanity.

Unfortunately, he had not yet entered Demonic Descent, so...

"Too late."

The whip became a blade and swept across the floor.

Deep claw marks were carved into the floor.

If knife marks could be left on a cutting board, it was needless to say what would happen to the body that was on top of it.

The Sura Demonic Sword's torso was sliced thinly like sashimi.

In fact, since it was sliced through, bone and all, one could say it was a somewhat… different cut of sashimi.