\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (6)}

Cui Liweng was dumbfounded.

All he meant was that the interest in Qing would disappear.

Qing wasn't some representative of Zhongyuan women, and the idea of showing interest in men made no sense.

But he couldn't give a detailed explanation either.

So he had no choice but to let her misunderstand.

And Qing misunderstood to her heart's content.

\textit{Wait, martial arts can change sexual preferences?}

\textit{They called it the Heavenly Demon Divine Art, but isn't it actually a Demonic Art?}

\textit{Shouldn't they rename it the Heavenly Divine Demonic Art?}

\textit{Or maybe the Male Divine Demonic Art, or just outright call it the Homosexual Demonic Art?}

\textit{Hmm. Or maybe not?}

\textit{Come to think of it, this was a world where learning martial arts could make people prettier, more sensitive, or duller - all sorts of things could happen.}

\textit{Maybe there's some kind of hormone regulation or something?}

\textit{Even so, it's still a truly Demonic Art.}

"Well, let's put that aside for now. But what's this about liberating Zhongyuan? With that son of a bitch in charge, there's no way in hell it'll be equal for all. Won't he just create a living hell?"

"That too will naturally be resolved once the Supreme completes the Divine Art. Do not doubt it."

"Why? Does a person suddenly become kind or something? Ha! About that... Hmm. I guess it could make sense."

Qing's words took a turn at the end.

Come to think of it, hadn't Qing herself changed after learning the Great Tranquil Zen Art?

Maybe that Alleged Supreme was in an even more serious state than Qing.

\textit{Then, does that mean he won't be interested in me?}

However, what had to be known was that kindness and sexual orientation weren't related.

\textit{Is it a martial art that turns you into a nice homosexual?}

\textit{You become kind in exchange for becoming gay?}

Then she wondered why she was even pondering such nonsense.

\textit{So what?}

\textit{Whether that son of a bitch becomes kind or not, whether he sleeps with men or not, what does it matter to me?}

Then Cui Liweng spoke.

His tone was almost pleading.

"Just endure a little longer. Once you open the Heavenly Demon Tomb and the Supreme completes the Divine Art, he will not stop you from leaving then."

"Oing? Eh?"

Qing blinked.

"What? He'll just let me go?"

"The future Heavenly Demon will not keep non-believers under him. As long as you do not oppose the Divine Cult, he will be merciful."

Qing growled.

"Gramps, do you know that Alleged Supreme tried to gouge out my eyes just because I talked back once? Whether it's a Divine Art or a Gay Demonic Art or whatever, he'll still be a creepy motherfucker after learning it."

"You dare! How dare you speak such blasphemy?"

The Purple Lightning Demonic Warlord cut off Qing's words.

A purple light flickered between the old man's body and the world.

Purple Lightning Demonic Qi.

Unlike Qing's True Qi, the original owner's Purple Lightning Demonic Qi had the dignity befitting one of the Ten Great Demonic Arts.

It was because the Purple Lightning Demonic Warlord's Purple Lightning Demonic Qi had already completed its final evolution into Purple Lightning Force.

Since this usually appeared when the Purple Lightning Demonic Warlord was angry, Qing felt a surge of emotion, as if feeling wronged, and argued back.

"What? Are you getting mad at me now? Just because I insulted some stupid martial art? Why are you flashing around like that? Are you going to fry me with lightning or something?"

"Enough!!"

"Kiyaaak!"

Crack! Everything went white, and a shrill scream escaped involuntarily.

She couldn't even tell where she'd been hit.

It felt like her bones and muscles were melting all at once, enveloping her entire body in an instant.

Fortunately, the pain subsided quickly.

But it was enough to snap her back to her senses.

Qing originally had a habit of submitting to the strong when she met them.

This hierarchy of strength included not just cultivation realms, but also relationships.

Cui Liweng had shown such a soft and weak side to Qing that she had gradually started pushing boundaries, resulting in this situation.

But after getting hit once, she realized that the Purple Lightning Demonic Warlord was actually a Master of the Unrestrained Realm.

Moreover, he was actually an absolute fucking beast of a Master who could turn Qing into a crispy fried dish just based on his mood.

\textit{Ah, I went too far.}

\textit{What was I thinking, acting so recklessly?}

Qing reflected on her past behavior and forced a smile.

It was a smile packaged in subservience.

"Hehe. Elder. Why are you getting angry? I was just shocked, so my words came out harshly. You know I did not mean it, right?"

"I-I apologize. It was not my intention."

"Aoooo, of course. I have learned about this too. Elders sometimes have moments of depression, right? I do not mind."

"No. Child, that's not... This is..."

Instead, Cui Liweng, who had struck her, looked like he was the one who had been hit.

Qing's smile was not unfamiliar to him.

Her face and eyes weren't smiling, and her trembling pupils looked towards him but focused on his forehead or between his brows, not meeting his gaze directly.

As one grows old, they gain the wisdom to clearly name such an expression.

In this world, it was called fear.

The old man's cloudy eyes wandered through a different time.

There were eyes that always looked at Cui Liweng.

The saying that you can tell a person's character by looking at their eyes doesn't come from the Righteous Qi of Daoism and Buddhism or the malefic star filled with Demonic Qi.

People's eyes move first when they see something familiar, unconsciously curling at the corners, their gaze sticking and not letting go.

When seeing something frightening, the pupils tremble.

When looking at something hateful, the eyes lose their luster, and their color becomes colder than the north wind, with a sharp, harsh malice, forming shapes as deadly as daggers.

That's why round eyes that look at the world kindly are called 'stares', while those that look at hateful things are called 'glares'.

Cui Liweng had learned through experience that fear exists in the process of stares turning into glares.

The body growing cold in his arms, a life he never thought would be so short, the clear hatred in those eyes that couldn't be closed even in death, that he couldn't bring himself to close.

"Huk."

Cui Liweng's complexion turned white.

No, it turned blue, and eventually he rolled on the floor, his eyes rolling back as his body trembled.

The wide-open glare whispered in the old man's ear.

\textit{I hate you. I despise you. I wish I had never been born.} "Gramps? Why are you suddenly like this?"\textit{ Get lost. Please. I'm begging you. What do you want?} "What's wrong with you? Why are you suddenly acting like you're at a funeral?" \textit{My last sight of this world shouldn't be your horrible face.} "Come on, snap out of it! Gramps! Gramps!"

\textit{Father, you must live a long life.}

\textit{Because I don't want to face that mug of yours in hell.}

And then Cui Liweng's trembling stopped.

"...It is fine now."

"Are you okay? Have you come to your senses?"

"No need to make a fuss. It is just the result of my old age."

"You looked like you were about to kick the bucket, yet I can't even make a fuss?"

"I cannot go yet. I must see our Heavenly Demon rise to greatness and the entire Zhongyuan become a peaceful land under the Divine Cult's rule."

Qing picked up Cui Liweng, put him back in his place, and then dragged her legs back to her seat.

Then she diligently cleared out all the fruit.

It seemed like this might be the last time she'd get to eat for free, so she wanted to eat while she could.

Cui Liweng just smiled bitterly and stared blankly at a corner of the table for a long time.

The table emptied like that.

Qing was debating whether to end the meal or not and whether to ask him to take her back or not.

\textit{Is the worthless Senior Sister now Crutch No. 1?}

\textit{No, a single item doesn't need a number.}

\textit{Should I just promote her to The Crutch?}

That's when it happened.

Cui Liweng brought up a story that hadn't been asked about.

"You must have heard that I had a daughter."

Qing replied reluctantly.

If it had been before getting hit, she might have sassed back with ‘I heard she was the one of the rudest bitch under the heavens', but not now.

"Well. I've heard some rumors that your daughter was quite... unique."

"Yes. She was an unfilial daughter."

"Uh, if it's a heavy story, you don't have to tell me."

Hearing the voice filled with deep resentment, Qing quickly tried to cut him off.

She didn't like melodrama, after all.

However, Cui Liweng shook his head and continued talking on his own.

"She was always desperate to leave the Divine Cult. When I stopped her, from some point on, she started seeing her father as her mortal enemy. But how could the daughter of a Great Guardian leave for Zhongyuan?"

"You were a Great Guardian, Elder?"

"I was, once. Until my daughter stabbed her heart and killed herself."

"Ah."

\textit{Shit. This is getting all deep and heavy.}

"She killed herself in the prime of her youth without ever truly blooming. She died still considering her father her enemy."

Qing couldn't answer and just looked on with anxious eyes.

"If this old man betrays the Divine Cult now, how could I face my daughter after death? She would immediately confront me."

A shadow fell over Cui Liweng's aged face.

"She would ask why I made her life so miserable for the sake of the Divine Cult when she was alive, only to betray that very cult I cherished so much for the sake of some girl I didn't even know, after I had killed my own daughter. How could I possibly answer that?"

Qing just scratched her head awkwardly.

Xue Ganom was both right and wrong.

He was right that trying to persuade him would be pointless, but wrong about him being a devout cultist.

He was just a pitiful old cultist who felt he had to be devout lest his dead daughter's death be in vain.

\textit{Ah, shit. How can the living even win against the dead?}

From the start, Cui Liweng's words were that kind of refusal.

"I shall let you go after the Heavenly Demon Tomb is opened. Even the Supreme will not be able to treat you recklessly if I stop him. I hope you can endure until then."

Qing sighed deeply.

"I understand. If that's what you say, Elder."

Of course, it was just lip service.

First of all, there was no way she could trust that Alleged Supreme bastard.

He was the type to immediately enter the Demonic Descent Realm after learning the Gay Demonic Art.

If he suddenly decided to kill her then, what could she even do?

It would be too late for Gramps to try and stop him then.

She couldn't stake her life on someone else's mercy.

So she couldn't let that Alleged Supreme bastard achieve Demonic Descent.

Moreover, she couldn't bear to see that either.

She had to interfere at the crucial moment, destroy that Heavenly Demon Spirit thingy in front of everyone, and see his face contort.

And there was a second reason.

Even if she returned home safely, it would still be a problem.

In the end, that bastard who would turn from the Alleged Supreme to the future Heavenly Demon would gather all the Demonic Cult scum and come after her.

What about her sweet home in the Divine Maiden Sect that she had just obtained?

Moreover, what if rumors spread that Ximen Qing gave the Heavenly Demon the Gay Demonic Art?

It seemed like she wouldn't be the only one getting destroyed.

Also, even if she wouldn't get destroyed by the cult, she would definitely get whipped in the ass by her Master.
