\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (1)}

Qing, who had developed a hobby of night walks, visited Xue Ganom's house every night.

Thanks to this, Xue Ganom was drenched with water once again today.

Yesterday and the day before, he just stared with a reproachful look, water dripping from him.

But today, for some reason, his gaze was trembling with hesitation.

Qing asked with a sour face.

"What the… What's with that look?"

"You said you were not a Demonic Cult disciple. But were you actually a witch from the Blood Cult?"

"Oing? Ehh? Blood Cult?"

‘That expression' patented by Qing was so convincing that anyone would fall for it if seeing it for the first time.

In Zhongyuan, no one could express the ‘I don't know shit' look better than Qing, after all.

"Did you not wield the White Hand Demonic Arts?"

"Oh! You know about the White Hand Demonic Arts! Yeah, nowadays, it's hella. Really. Truly. So. Strong."

Indeed, the White Hand Demonic Arts had evolved significantly.

It was thanks to the Heavenly Ice Sura Demonic Arts.

The White Hand Demonic Arts were notorious for spreading the sinister White Hand Venom Penetrating Power, causing permanent aftereffects.

However, Qing's True Qi didn't have any cold attribute to balance that.

It was like driving a vehicle that required premium fuel with diesel.

But now, she had Heavenly Ice Demonic Qi.

Though it was not exactly premium fuel, it was at least akin to gasoline.

"So you are not from the Blood Cult?"

"No?"

"But you're the White Hand Witch?"

"I'm not that either, though?"

"But you did learn the White Hand Demonic Arts?"

"Oh! You know about the White Hand Demonic Arts! Yeah, nowadays, it's hella. Really. Truly. So. Strong."

"Am I hearing things... I think I heard that earlier too..."

Xue Ganom muttered as such.

Qing frowned.

As Xue Ganom flinched, Qing sighed deeply and said.

"What's with you? Why are you so on edge?"

"Given that every name I provide ends up found brutally slaughtered, can you blame me for being nervous?"

Xue Ganom thought Qing was just a clumsy robber.

But in reality, she was the Great Killing Star under the heavens.

And also the White Hand Witch of the Blood Cult, at that!

If the Demonic Cult were the bad guys, the Blood Cult was a gathering of the world's absolute scum.

There was a hierarchy even in wickedness.

Xue Ganom seriously considered escaping from the Demonic Cult.

Being involved with the Blood Cult never ended well, after all.

It was better to die than to be entangled with them.

Pain didn't scare him, but the Blood Cult did.

Qing showed a hurt expression.

"I promised not to kill you, though."

"In general, informants do not live long."

"That's harsh. Given our relationship."

"Yes. Now that you bring it up, we need to clear that up. What exactly is our relationship?"

\textit{Oing? What? Wait, he kinda has a point, right? What kind of relationship do we have?}

Qing thought for a moment and found a suitable word.

"Friends?"

Xue Ganom's eyebrows twitched up and down.

"Friends, friends, you say. I do not even know your name, but you are my friend, huh?"

"Ximen Qing."

"Your sect?"

"Divine Maiden Sect."

"Who's your master? Where did you learn your Demonic Arts?"

"A neutral country, somewhere over the rainb- I mean, my master's name is spelled with Su and Rin, with her surname being Ximen. And I learned Demonic Arts here and there."

Xue Ganom's eyebrows soared and came back down.

"Ximen Surin? The Godmother? The Divine Maiden Sect's, no, you did say Divine Maiden Sect, yes. A disciple of the Matriarch, no, a Ximen of Ximen. So you're saying you are a named disciple? No."

Xue Ganom's babbling was a fascinating sight to watch.

However, even that was brief.

Once he calmed down, Xue Ganom asked again.

"What in the heavens is going on in Zhongyuan these days? Is there some great plague spreading, about to destroy everything?"

"The Zhongyuan is fine, though."

"Too bad. I thought the world was finally ending."

Xue Ganom said that and turned away.

"Ehh? Hello? Where are you going?"

"I should treat a friend to a cup of tea, of course. There's a folding table by the cupboard, so set it up."

"Oooh, are there snacks too?"

"Look at the state of the house. Isn't it praise-worthy enough that I can even offer hot water? But you are looking for snacks as well? What snacks are you even talking about? It is not like you are a child."

Xue Ganom scolded her and went outside.

Qing looked around, took out the folding table from between the cupboard and the wall, and unfolded the legs.

She also took off her uncomfortable mask since it was her friend's house.

Then she sprawled out carelessly.

Lying down as soon as you visit a friend's house was a solemn etiquette of true friendship.

After a while, Xue Ganom returned with a teapot and cups.

He looked at Qing's girlish face and spoke.

"Turns out you aren't not a kid. You actually are one."

"A kid? Who are you calling a kid here?"

"If I had married early, I'd have a daughter your age. Doesn't that give me the right to call you a kid?"

Xue Ganom was logical.

Even Qing found people in their twenties to be childlike, so how much more so would it be for a middle-aged man like Xue Ganom?

\textit{Wow. Can't argue with that.}

As Xue Ganom set down what he was carrying on the low table, he asked.

"So, what is the problem?"

"Yeah, that! Remember that patrol leader? He was completely useless! After all that talk about having some peerless Qinggong!"

"I only mentioned there were rumors he possessed it. Hm. But that's not what I was asking about."

"Then what?"

Xue Ganom looked at Qing.

"I am talking about you. Do you really have nowhere to belong? You seem to be in quite a severe state."

"What do you mean by that? That's so out of nowhere."

"Why is a young Great Demonic Adept from a prestigious sect like you attaching yourself to a ruined middle-aged man like me?"

"Who are you calling a young Great Demonic Adept? You're going way too far."

"I can roughly guess the title they call you. Probably the Tri-Headed Witch? Or since the Godmother herself passed on her surname to you, you are probably a part of the same big family known as the Orthodox Faction. Then, perhaps you are called the Tri-Headed Demonic Virtue."

"What the hell, why do you keep nitpicking about my boobs? Should I rip them off and stick them on you? Maybe then you'll understand the pain you've been amusing yourself with at my expense?"

"You've got a sharp tongue for someone so young."

Xue Ganom sighed deeply.

"My point is, it's good and all to be a virtuous person, but do not let killing intent consume you. You have a good background and a good figure, and though, unfortunately, you have vulgar breasts, there must be many friends in Zhongyuan who would appreciate you. Is that not so?"

"I mean, that's true, I guess?"

"So why come all the way to this remote Demonic Cult to perform your acts of villainous retribution? From my perspective, you are not in a normal state."

From Xue Ganom's point of view, Qing had long since awakened to the Killing Star.

Though given she was a disciple of Ximen Surin, she seemed to be barely holding on through orthodox Daoist Cultivation Techniques.

When a person has no one to trust around them, they become slowly filled with loneliness and go mad.

So, could such a young girl truly have found someone to open up to in a den of villains?

They had met in an act of robbery, as perpetrator and victim, no less.

Considering that, could a mere few days of conversation really lead to such attachment?

No. And she must surely have already been mentally breaking down before they even met.

How did he know? Because Xue Ganom had followed a similar path, committing horrific killings before fleeing here.

He was an unwanted orphan who had been abused at the Ice Palace and now lived in hiding in the Demonic Cult on the opposite side of Zhongyuan.

He had indiscriminately killed his teacher, Senior Brothers, Senior Sisters, and Junior Sisters, and then stolen secret manuals before fleeing. And as he did, he often reflected on whether he may have been a bit too excessive.

At any rate, Xue Ganom had accurately diagnosed Qing's condition.

Qing had unknowingly leaned on him out of deep-seated loneliness.

Her loneliness had persisted since she first started her Wulin journey.

In truth, it hadn't been all that long since she had first received affection in Jianghu.

As such, it was only natural for her to cling to those who showed her affection.

It was also an extension of her disgust for those who only focused on her Constitution, not Qing herself.

Overwhelmed with emotion, Qing raised her voice.

"Agh, shit. Do you think I'm here because I want to be? I was kidnapped, so I was just venting my frustration a bit as I planned my escape."

"Ah, so you were kidnapped. I did not know that. My condolences. I thought you had come to slay evil. Kids your age often say such things, do they not?"

"Well, I mean, I thought about visiting here to train later, but I didn't want to come now, okay?"

"An escape, you say... So that's why you asked about Demonic Adepts who had Qinggong Techniques. You planned to learn them for your escape."

Qing seized this moment to ask.

"So, about that… If Xue Ganom could learn just one martial art in the world, what would it be?"

"The Blissful Maiden Arts, of course."

The answer was immediate.

Xue Ganom continued.

"I ran away to this place hoping to somehow steal and learn it, but it turns out it's an esoteric doctrine that only the Palace Leader learns in the Bliss Palace."

"Agh shit, I wasn't asking what Xue Ganom specifically wanted to learn, you know? I meant something useful for me."

"I am fairly sure you asked what I would learn. Hm. If I had to choose just one, you say. This is one of those games about hypotheticals that kids your age play, I see."

Surprisingly, it was a rather widely known game in Zhongyuan.

It was a direct result of the undeveloped play culture that existed in this primitive, ancient, and uncivilized Zhongyuan.

Xue Ganom stroked his chin, pretending to think, and finally concluded.

"If you need to escape an immediate crisis, there's nothing like the Essence Absorption Demonic Arts. Of course, you'd have to flee far to the west rather than staying in Zhongyuan, since all the martial artists would be after you with weapons drawn."

"Pass."

Of course, Qing thought that as long as she didn't get caught, it didn't matter what she learned.

After all, dead men tell no tales!

The rejection wasn't out of fear of future repercussions.

Qing had already searched for the notorious martial art with the kickass name of Killer Among Killers.

But it didn't come up.

She could only speculate that it was either exclusive to the natives of China or had to be learned through Special Missions, like the Nine Swords of Solitude.

"If it weren't for the immediate crisis you are in, it would be the Yijin Cleansing Method. It's the greatest Divine Arts for nurturing muscles and meridians, one without any equal under the heavens."

"Ah, that's two votes for the Yijin Cleansing Method. My teacher also mentioned it."

"Of course she would. Any teacher who cares for their disciple would dream of such, would they not? However, it is difficult to reach the Grand Star and the effects appear slowly, so it is not suitable for immediate crises."

Qing was now certain of one thing.

If she didn't learn it this time, that would be where she would spend the two thousand points.

"So, what if I need immediate results?"

"As you know, the only thing that can be immediately useful is pure Demonic Arts, is it now?"

"What if I somehow achieve the Grand Star for a martial art?"

"Indulging in fantasies is not a good habit. Live in reality."

Xue Ganom didn't hide his disdainful look.

"Agh shit, whatever. I'll figure that part out myself, okay? Just tell me."

Xue Ganom thought deeply once again.

Then he abruptly spoke.

"Thousand Spiders Ten Thousand Poison Hand. That's right, there was the Thousand Spiders Ten Thousand Poison Hand."

\vfill
\begin{lstlisting}
	The chapter title is a reference to Ronald Knox’s Ten Commandments for Detective Fiction
\end{lstlisting}