\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (11)}

"Whew..."

Qing sighed and tossed the whip aside.

Inside the room was just one messy corpse, its torso and innards sliced into pieces.

Qing looked around in disgust at the sight. Fortunately, the cloth the Sura Demonic Sword had wrapped around himself covered the lower half of the corpse.

"Hmm. Good. Yeah, this looks a lot better."

An old man's flabby ass.

It was better to cover it up for the sake of the mental health of whoever discovered it later.

\textit{But hmm, it looks a bit plain.}

\textit{Maybe I should add a little more decoration?}

Qing's eyes lit up as she looked around again.

She gathered some thick wooden dildos and placed one in each of the corpse's hands, then scattered a few more around.

\textit{Good. Now he looks more like the epitome of a pervert.}

Qing nodded, then reached into her chest to pull out a crumpled mask and put it on.

She looked quite suspicious in summer palace attire with only her face masked.

Carefully pushing open the only iron door, a dim cave lit by candlelight was revealed.

At the end was a ladder. She carefully pushed open the trapdoor at the top and peeked out to see the interior of a luxurious room.

\textit{Alright, I don't sense anyone nearby.}

\textit{Oh! Could this be a treasure room!?}

Looting the treasure room was the protagonist's natural right.

Qing used Black Shadow Stealth to completely suppress her presence as she ransacked the room's drawers and closets.

However, it was just the Sura Demonic Sword's bedroom.

The porcelain, scrolls, and silk clothes looked expensive at a glance.

But there was no way to convert them to cash even if she took them.

So the only loot was an old Secret Manual found in a box under the bed.

The Martial Arts Window flashed, revealing the registered name.

Hundred and Eight Sura Swords.

At the same time, a mission window popped up.

\begin{quote}
[Strange Fate Occurrence - Heaven's Equal\footnote{Shin Pil (신필)}, Remembering the Grand Dragon]

Description: [You have gathered one-third of the Ten Great Demonic Arts under Heaven.]
\medskip

Killer of Killers) Achieve 10 Stars of all Ten Great Demonic Arts and reach as well as the Grand Star of the Yijin Cleansing Method

[Upon completion, you will learn the Ultimate Martial Art: Northern Abyss Divine Art]
\end{quote}

"Ooh. Ultimate Martial Art."

Qing marveled unconsciously before thinking again.

\textit{But isn't that word a bit much?}

\textit{Using such excessive words actually makes it seem weaker.}

\textit{Besides, I've never even heard of the Northern Abyss Divine Art.}

\textit{If it were such a powerful martial art to be called 'Ultimate', Xue Ganom, Peng Ganom\footnote{'The guy from Peng family' a.k.a Peng Daesan}, or that oh-so-incredible person of the Ximen family would have at least mentioned it once.}

\textit{Also, why ten Demonic Arts and the Yijin Cleansing Method?}

\textit{What's the connection between the two?}

\textit{Hmm. I have no idea.}

For now, Qing burned the Secret Manual over the oil lamp.

After all, such a cursed Demonic Art that turned people into masochists shouldn't exist in this world.

Anyway, Qing had already registered it through her cheats.

Whether the manual was burned or not didn't matter to her.

Qing tossed the burning manual onto the huge, ransacked bed.

It was an expensive bed filled with feathers and finished with the finest silk from Zhongyuan.

The treasure of a bed worth dozens of gold pieces caught fire.

\textit{Now, all I need to do is escape. Then, it would be a pretty fulfilling day.}

Qing took a deep breath.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Xue Ganom had asked her to stop by and report the results, whether she failed or succeeded.

It was a different reaction from usual, where he would tell her not to come back and splash water on him meaninglessly. Or to just go wash her feet and sleep, instead of staining the floor with blood.

So even though it was a bit of a risky time, she returned, pulled the rope, and entered Xue Ganom's tiny place.

As usual, she was about to lie down when she unexpectedly encountered Xue Ganom sitting up, not sleeping.

"How did it go?"

"Who am I? Ximen Qing. Greatness itself. The adjective of 'Great' exists solely for me."

"Looks like you succeeded, then."

Then Xue Ganom stood up abruptly.

"What? Where are you going? I just got here."

"I'm going to unpack. I had prepared to leave immediately if you didn't come."

No wonder the originally cramped room seemed a tiny bit wider.

He was planning to bolt right away if things went south!

Qing asked incredulously.

"Didn't you say something about planning for the future if I got caught?"

"I tend to take a longer view. When a storm is coming, one should first seek shelter, shouldn't they?"

"But your friend was in that storm."

"If you had intended to drag me along to the underworld, we couldn't really be called friends anymore, could we?"

\textit{He really never loses an argument, does he?}

\textit{But this time the logic is a bit weak, and it's a context I'd heard before.}

Qing frowned, not impressed.

\textit{Come to think of it, all he does is talk smoothly.}

\textit{This guy has no loyalty. No loyalty at all.}

\textit{The greatest intellect in Zhongyuan my ass.}

\textit{From now on, all he is to me is the greatest intellect in the neighborhood at best.}

Xue Ganom's evaluation dropped several levels.

He was originally overrated to begin with, but even so, the drop was like a stock market crash.

"Anyway, you accomplished a difficult task. Judging by your expression, it seems nothing unpleasant happened either."

"Wow. In all my life… I can't believe it. Did you know? Okay, you see…"

Qing immediately spilled the beans about the Sura Demonic Sword's sexual preferences.

Xue Ganom nodded calmly, surprisingly.

"There are quite a few people like that."

"What? There are a lot of bastards like that?"

"Well, not to such a blatant level. But aren't all those types the same? I am referring to those who overwork themselves in Outer Arts training until their muscles tear."

"Aren't those just people who exercise hard?"

"Think about it. Those types always eat only bland foods like dry meat boiled in water or practice bigu fasting\footnote{Some Daoism practice to reach immortalism, basically avoiding five type of grains}. They treat fine dining as if it were a sin, but does that mean they enjoy any other pleasures? No. They just torture their bodies, enjoying the pain, then hobble around from the aftereffects. Not satisfied with that, they divide their body parts by days, repeating their ascetic practices without missing a single day."

"Huh? Now that you mention it..."

"They already feel pleasure from masochism, so they do not need fine food, and for the same reason, they do not seek other hobbies. They always make excuses about muscles, but what is the need for muscles that are built in such a manner?"

This was Xue Ganom's opinion.

Though Xue Ganom had no muscles at all and had a thin, stick-like body… It was obviously a very logical inference that had nothing to do with that, obviously.

"Ah! Indeed. That's true."

Qing marveled.

\textit{As expected of the neighborhood's greatest intellect.}

\textit{His observations of people were sharp as well.}

\textit{Who knew there were so many masochistic perverts in this world!}

"You have enough strength as long as you can handle weapons without Inner Qi, so shouldn't you focus on gathering even a little more Inner Qi to develop your dantian instead?"

"That's right. The more Inner Qi, the better."

"Of course. Hmm. Somehow, we got a tad sidetracked, huh."

Xue Ganom cleared his throat.

"It seems you have done all you can. It would be better to rest well and refine your martial arts until the day you go to the Heavenly Demon Tomb."

"What? That's all? I was just getting warmed up."

"You..."

Xue Ganom sighed deeply.

"Do not underestimate those Demonic Cult bastards too much."

Among the poisons of Zhongyuan, there was one called 'Gu poison'.

It was made by putting all sorts of poisonous creatures into a jar and sealing the opening.

The poisonous creatures would then eat each other.

In the end, the survivor would absorb all the other poisons, gaining a powerful Poison Qi.

The Demonic Cult, along with the total armament of all its followers, created a city similar to a crucible of Gu poison while stubbornly yelling about the law of the strong.

The weak had no voice in this unreasonable society, while the strong were treated as justified under the name of 'might makes right' no matter what they did.

The Demonic Cult had no intention of developing the Divine City from the start.

All they needed were capable individuals for conquering Zhongyuan and a large number of cannon fodder.

The series of processes that made Qing click her tongue at how chaotic things were was actually the result of pursuing extreme efficiency.

To quickly produce a large number of Masters.

"Either way, proper high-level martial artists do not even live in dormitories within combat units. You may have slaughtered a few powerful Demonic Humans, but they were all just careless due to the long peace."

"Hmm."

"It is most likely that from tomorrow on, you will need to be prepared, even when going out at night. All the Masters of the Demonic Cult will pour out looking for the murderer, after all."

\textit{Well, if that's the case, it can't be helped, even if it's disappointing.}

Qing nodded.

She had never lost out by listening to Xue Ganom.

Even if his loyalty was a bit questionable, his intelligence was based as fuck.

And to be honest, she wasn't having as much fun after learning the Great Tranquil Zen Art.

As expected of a Buddhist Divine Art!

Of course, in the perspective of the Great Tranquil Zen Art, this was utterly ridiculous. If it could speak, it would definitely shout about how it felt wronged.

After all, Qing was just bored from playing around too much.

There was a certain threshold in human psychology where no matter how fun a game was, you would become less excited once you got used to it.

As such, Qing completely gave up her lingering attachment to night walks.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Divine Cult's top investigator, Shi Hengheng, had a gleam in his eyes.

"Hehe, you little rat. You won't be able to run wild anymore."

With the death of the Sura Demonic Sword, even the Secret Pavilion took the stance that they would no longer stand by idly.

They gave Senior Investigator Shi Hengheng disposition authority equivalent to their version of First Grade.

It was an enormous authority that allowed him to request cooperation from those below the level of combat unit's Vice-Captains and First-Grade disciples of sects.

"Investigator, is this plan alright? Mobilizing so many Masters for night patrols is..."

The adjutant looked at the night patrol plan for the city, which was so densely packed it was hard to make out.

This was more like a Net of Heaven and Earth than a mere patrol.

And it was composed entirely of Masters of the First-Rate Realm or higher.

"Keke. Hasn't every crime so far happened at night? That means if we catch all the suspicious people at night, the culprit will be among them."

Shi Hengheng glared with bloodshot eyes.

"Just one more time. Try to run wild just one more time. That will be the day of your funeral."

Unfortunately, this strategy only held true if the culprit actually went out at night stroll.
