\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (7)}

A true man must have a great task he must accomplish, even if it means enduring any humiliation.

This is exactly what Xue Ganom meant by the story of Han Xin crawling between someone's legs.

When Han Xin was young, he was a braggart who always carried a big sword to act tough.

A local thug who disliked this sight blocked his path, spreading his legs and thrusting out his belly, saying:

'If you know how to use that sword, cut open my belly. If you're just carrying it for show, I'll let you off if you crawl between my legs.'

Han Xin was furious.

But he couldn't risk getting a criminal record for murder, which would prevent him from becoming an official.

In the end, unable to give up his dream of being a civil servant, Han Xin crawled between the thug's legs.

Then there's also the story of King Goujian Tasting Feces.

This is about King Goujian of Yue, the one helped by the Yue Maiden.

After losing a war against King Fuchai of Wu that had the continent at stake, Goujian became a prisoner in Wu.

Though Goujian was grinding his teeth in anger, outwardly he acted like a submissive and obedient slave.

When Fuchai fell ill, Goujian even ate Fuchai's feces and personally diagnosed him, saying there was no major illness since the taste was normal!

(A diagnosis through eating poop is a surprisingly legitimate study of traditional medicine)

Moved by this, Fuchai released Goujian.

Or perhaps he just didn't want to keep such a disgusting feces-eating man as a servant.

Afterwards, Goujian met the Yue Maiden and led an army armed with the enhanced version of the Yue Maiden Sword to destroy the State of Wu.

And here was another beautiful man/woman who had to endure such humiliation.

It was none other than the pretty girl named Ximen Qing, who had once been a military veteran.

Han Xin crawling between legs and Goujian eating feces were nothing compared to the humiliation Qing would have to endure.

\textit{I... I...!}

Qing looked down at the weapon in her hand.

The long handle, the sharp bridge of the nose, the gracefully heavy blade body with blood grooves carved into it.

And the single-edged blade.

Qing trembled with humiliation.

\textit{To think that I have to use a Half-Sword...!}

That's right.

Qing was holding a Half-Sword.

But this too was a sacrifice for the greater cause.

It was a noble sacrifice for Qing's dignity, petty revenge, and amusement.

Incidentally, it might also somewhat guarantee the peace of Zhongyuan's Wulin from the vicious claws of the Demonic Cult, but honestly, she didn't really care much about that part.

Though she would get a lot of Free Practice Points as compensation...

It was ultimately Xue Ganom's idea.

Just a mere act of a White Hand Witch causing havoc would be a bit boring.

So let's frame one of the three major outer sects of the Demonic Cult, the Royal Demonic Path Clan.

Qing looked down at the Half-Sword.

\textit{Hmm. But. I think I kinda… Just a teensy bit? Like it a little.}

Qing's pure strength had now surpassed human levels due to her collection of all sorts of martial arts.

She was probably the strongest person not just in Zhongyuan, but across the Five Oceans and Six Continents.

How to put it? For such a Qing, swords felt too light.

The Blood Shadow Thunder Lightning Dao Technique especially used a huge dadao\footnote{A type of dao/ Chinese saber}.

It was a weapon rarely seen in Zhongyuan.

Even with the non-interference between the government and Wulin, it was still awkward to openly carry such a large weapon around.

The national law prohibited carrying such private weapons, after all.

And also, it was inconvenient.

It was a heavy weapon weighing twenty catty just in iron.

How inconvenient would it be to always carry around something so big and heavy?

But for Qing, it was just the right weight that felt good without being burdensome.

Qing looked down at the fallen Taiping Group member.

He was an unfortunate villain who would never get up again, punished for neglecting his patrol duty and lying down on a mat in an alley.

Of course, the biggest cause of death was that he happened to be carrying a dadao.

"Your weapon's fucking sick, you know? Don't worry too much, I'll use it well tonight and return it."

The Taiping Group member didn't answer.

Because the dead don't speak.

Qing gauged the west direction.

\textit{The main building of the Taiping Group was supposed to be that big building with the blue roof over there, right?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Taiping Group under the Inner Palace Department of the Heavenly Demon Divine Cult was mainly responsible for maintaining public order in Tian Shan Divine City, and also handled fire fighting, taxes, and loan-related products.

However, there were constant opinions that Tian Shan Divine City's public order was too perfect to need the Taiping Group to protect it.

This was because there had been no violent crimes in Tian Shan Divine City for several hundred years.

For reference, robbery, murder, rape, and human trafficking were not considered violent crimes in Tian Shan Divine City, and were simply seen as the victim being stupid or careless.

Therefore, it is a clear fact proven by records that Tian Shan Divine City is a heavenly utopia perfectly free from terrible crimes.

Xue Ganom was ultimately an outsider who had flowed in.

So the strategy of first burning down the public security force and throwing the city into chaos was truly something that would make Divine Cult members sneer if they heard it.

What's the point of burning down people who don't do anything anyway?

It would just mean people could commit robbery, murder, rape, and human trafficking without having to be discreet about it, instead of doing it bit by bit while being cautious.

Stupid Zhongyuan people might call that chaos, but for Divine Cult members, well...

For this reason, the Taiping Group, too, was perfectly peaceful.

In fact, the Taiping Group had never even conceived of the idea that someone might attack them.

The patrollers were everyone's friends, easily befriended with enough money for a good night out.

It was even a time when everyone was confused by the sudden night shift and various illnesses were going around, so people were holed up in Taiping Hall saying they couldn't come to work.

And so, in this Divine City where night shifts had become a rather vulgar joke, a woman was crossing the small martial arts training field of the Taiping Group.

To the left of the main gate was a five-story building.

This was Taiping Hall, the dormitory for Taiping Group warriors.

The night guard watching the front of the dormitory saw a figure approaching, dragging a huge dadao.

A black outfit covering the entire body.

In Zhongyuan, it was called night-walking clothes.

The night guard was startled and stood up, but then sighed in relief when he recognized the dadao being dragged.

In fact, there was no one in the Divine City who wouldn't recognize it.

The ridiculously large dadao with red tassels was the weapon used by direct disciples of the Royal Demonic Path Sect.

If it's a Royal Demonic Path Sect member going out at this hour, then it's probably…

The night guard acted friendly.

"Fourth Senior Master, you are back already? You should at least pretend to patrol. If you return early like this, the entry log will be messed up."

Then the black-clad figure answered.

"Cry. Cry to prove your innocence."

The night guard asked back, confused by the sudden words.

"What? Senior Master, are you drunk? Why should I cry? I am a man."

"Who said I was telling you to cry?"

Qing snapped and then said again.

"Cry, Hell Sword."

The Hell Sword drew a circle as round as the full moon.

Blood Shadow Thunder Lightning Dao Technique First Move, Blood Full Moon.

It was a simple move that just swung the dao vertically from behind, striking down like lightning.

However, when combined with the Blood King Demonic Qi of the Blood Demon King Divine Art, it truly created a scene of a blood-red full moon rising above the ground.

The blade body lodged into the crown of the head, piercing vertically and coming out between the legs.

The crunching sensation transmitted through to her hands.

The feeling of forcibly cutting, crushing, and tearing with a weapon was a whole new world.

"Ahh... This feels sooo good..."

The taste of tearing rather than cutting.

\textit{This is also quite a delicacy, you see.}

Qing, who had shuddered once, strode forward.

It was the moment a Killing Fiend entered Taiping Hall.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Shi Hengheng, a senior investigator belonging to the Inner Hall's Taiping Group, was continuing his lonely struggle alone today as well.

It was because the vicious villain, the White Hand Witch, had snuck into Tian Shan Divine City.

Recognizing the seriousness of the situation, Shi Hengheng requested the dispatch of the Heavenly Demon Defense Squad's Combat Unit and proposed a special night shift for the Taiping Group.

However, the thoughts of those in high positions seemed a bit different, as they authorized the night shift formation but ordered to capture the White Hand Witch alive if possible, or surround and stall for time if not.

In essence, they were coveting the White Hand Demonic Arts.

Shi Hengheng, as one of the few conscientious members of the Taiping Group, was furious, but he had no choice but to follow orders.

Today too, he was staying up all night, trying to deduce the White Hand Witch's hideout by connecting the victims on a map of Tian Shan Divine City.

"White Hand Witch. Where are you hiding? It is clear that you must be somewhere in the East District..."

There was some progress.

The witch was definitely in the East District.

Speaking of the East District, she must be hiding somewhere in the red-light district, among the prostitutes.

That's when it happened.

A subordinate came in, making a fuss.

"It is terrible! There's a huge problem! A fire! T-There's a fire!"

Shi Hengheng looked at the subordinate as if he was pathetic.

"Firefighting is also the duty of the Taiping Group. Even if it's been a while since we've had to put out fires, seeing you panic like this makes me think we need to reschedule fire drills."

"That's not it!"

"What do you mean that's not it? What are you doing? Why aren't you waking up the warriors in Taiping Hall and dispatching them with firefighting equipment right now?"

"The fire is in Taiping Hall itself!"

Shi Hengheng frowned hard.

"What? Damn it! Ring the bell and gather all nearby warriors! What are the rest of the personnel at the main hall doing? Tell them to gather at Taiping Hall with firefighting equipment immediately!"

And so, the night of the Taiping Group was awakened.

All the personnel on night duty gathered, carrying fire sand, oil cloths, and water buckets, struggling to put out the fire in Taiping Hall.

Even citizens of the Divine City who were peeking around to watch the fire in the middle of the night were caught on the spot and made to carry water buckets, sweating profusely.

As Shi Hengheng was directing this process, a chill suddenly ran down his spine.

\textit{How could there be no one coming out when there's a fire?}

Normally, when there's a fire, it's human nature to jump out even if it's a thousand-li cliff outside the window.

But how could there be no sign of people when the entire building was burning brightly?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At that time, Qing was in the Great Hall of the Taiping Group.

This was the center of the Taiping Group, and also where all the main tasks like command briefings and paperwork were carried out.

'It should not be difficult to deal with the warriors sleeping in Taiping Hall. They are those with no discipline to begin with. Once all eyes are on the fire, set fire to the records office. What? You are asking where the records office is? I do not know that either. Figure out that much on your own.'

So Qing figured it out on her own.

She spared one person from Taiping Hall, ripped out his jaw, tore off his ears, and grabbed the one remaining ear to ask.

Upon doing so, he kindly changed jobs to become a guide.

As a reward for that guidance, Qing personally guided him to the underworld.

See? Qing was kind enough to repay guidance with guidance.

Qing casually tossed the porcelain bottle Xue Ganom had given her.

Along with a Clang, the resin-mixed oil splashed cheerfully between the ceramic pieces.
