\chapter{Heavenly Demon Divine Cult Serial Murder Case: \texorpdfstring{$\#$5:}{No.5:} No Chinaman Must Figure In The Story (3)}

Qing learned a new Cultivation Technique.

Her True Qis waited with bated breath for the mysterious new addition still lingering in her meridians.

Lately, only wicked things had been rolling in.

It was so bad that even the Blissful True Qi, meant to drive out the Demonic, was struggling - huffing and puffing daily like some pitiful murderous laborer chasing after surviving demons.

The Heart Cleansing Mirror of Zhu Xiang was too busy erasing the Heavenly Slaughter seeping into her Upper Dantian (brain) to maintain discipline.

Meanwhile, the Yue Maiden's True Qi just stood by, muttering 'Heheh, but well, what can be done anyway? Demonic Qi is Qi too, you know.'

In contrast, the Demonic Qi camp was having a field day lately.

Demonic Qi, by nature, gains strength from evil intentions and cruel actions.

Her Upper Dantian was on the verge of being stained with the karma of slaughter, thus about to give birth to a Killing Fiend.

'Just one more big chunk of Demonic Qi rolling in would do the trick, huh'. That was the expectation and assumption held at the current moment.

And so, as the first breath seeped in as True Qi, circulating once through every nook and cranny of her body, the gates of her Dantian opened.

The new addition to the family revealed itself with a ‘Ta-da!'

It wore a benevolent smile, with a subtle halo of radiant flames behind it, said to burn away the world's darkness and illuminate truth.

'Buddha has arrived!' 'We knew it!' 'We believed in you!'

The Daoist members of the family unanimously cheered.

It was the arrival of the Great Tranquil Zen Art, one of Buddhism's two greatest teachings.

When Buddhism uses the character for "tranquil," it doesn't just refer to sound.

It describes a state of perfect serenity, like a water surface void of any wind, with not a trace of delusion in the mind.

And in Buddhism, the method of pursuing enlightenment through such a tranquil mind while unifying one's spirit is called 'Zen'.

The Great Tranquil Zen Art was an Inner Qi Cultivation Technique created from this Buddhist enlightenment.

It was truly the very definition of an Inner Qi Cultivation Technique: a method of cultivating study within the body to govern the mind.

It was also famous as an esoteric doctrine of the Emei Sect.

Any sect worthy of being among the Nine Sects and One Union would have at least one representative Divine Art.

Just as Shaolin had the Yijin Cleansing Method, Mount Hua had the Violet Mist Divine Art, and Wudang had the Wisdom Sword of Cosmic Harmony, when people thought of Emei, they thought of the Great Tranquil Zen Art.

And here, at the edge of the world in this land of evil, one of Buddhism's greatest teachings had descended upon a deranged murderer.

Through some fascinating yet despicable method, no less.

For reference, the leader of the Emei Sect is called the Grand Abbot in Zhongyuan speak.

If that very Grand Abbot, Dingtie Yuan-ni, knew about this, she'd weep tears of blood, rendering her sixty years of mental cultivation utterly meaningless.

After all, what use is peace of mind when your sect's esoteric doctrines have been stolen?

The Emei Sect was like a temple among Wulin sects.

And the Emei nuns were martial artists akin to Buddhist disciples.

Whether Shaolin or Emei, these so-called martial monks were actually just depraved monks with a cult-like nature!

Of course, it's also true that among martial artists, these depraved monks generally had the most respectable characters.

At any rate, that's how Qing gobbled up the Emei Sect's Divine Art in one gulp.

As the Practice Points required were too burdensome, she raised it to Six Stars, an efficient point where huge amounts of Ability Points start coming in.

She didn't completely max it out, keeping some in reserve in case she needed to pull more fuckery later.

Just this achievement alone was enough to blow away her recent inner demons in one go, bringing a subtle vitality back to Qing's eyes.

It was a miracle - her dead fish eyes were sparkling again.

In fact, even though she'd now regained her senses, this time she'd truly fallen off a cliff before soaring back up via a mystical dragon's whirlwind.

Of course, one could say she was actually holding up quite well despite being the owner of the Heavenly Slaughtering Star.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Somewhere in the sky, the most ominous star emitted an uncomfortable light.

But that was it. That was the sole extent of how it felt

A lonely malefic star that had existed for eons as if it were a single day - human will is but a fleeting moment before it.

Mere insects like humans cannot dare to go against the will of stars.

It was just a momentary tantrum.

In the end, it would bloom blood and tears all over the world.

Famous Daoists of Zhongyuan saw this starlight.

It was the moment they realized that they were too late. That a Heavenly Slaughtering Star that had grown too far to stop and existed somewhere in the world.

It was like when Fan Zeng and Xiang Bo of the Chu-Han Contention era read Xiang Yu's fate in the sky.

And like when their more brilliant junior, Zhuge Liang, heir to the lineage of geniuses, read the Mandate of Heaven from the sky.

Reading the flow and energy of the heavens like this was a symbol of wisdom.

As martial studies had developed a lot since then, there were many interpretations of miscellaneous skills.

Almost anyone who could strut around saying they knew a thing or two about the world could read at least scraps of the heaven's flow.

But what could the Daoists even do about it right now?

After all, the actual owner of Heavenly Slaughter was passed out cold at the edge of the world.

They were just planning to circulate letters among themselves, boasting things like ‘My, oh my, it seems something big has happened, what do you think about it?' ‘By the way, when did you see it? With the power of my Dao, I saw it around the start of the hour of the Ox.' ‘My, it seems you are still lacking. For me, it was the end of the hour of the Rat.'

Of course, it wasn't because they had nothing better to do.

They were creating a network so they could gang up on the owner of the Heavenly Slaughtering Star when they appeared.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ximen Surin also saw this starlight.

From the uncomfortable color of the malefic star, she knew her cherished disciple had overcome a great crisis and let out a sigh of relief.

Ximen Surin lit a candle in the middle of the night, left her quarters, and climbed a peak. It was to offer a sacrifice of gratitude at the Daoist temple enshrining the Flame Emperor.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There was also someone capable of seeing this star in the Demonic Cult's territory. It was Zhi Shengzhu, the Secret Pavilion Leader.

Zhi Shengzhu smiled as he saw the malefic star in the sky.

\textit{So, Heavenly Slaughter has arrived in Zhongyuan.}

\textit{The time for the Divine Cult to reclaim its long-lost aspiration is not far off.}

\textit{When Zhongyuan is drenched in the blood of the Heavenly Slaughtering Star's victims, the Divine Cult will soar to greatness!}

\textit{This must be a revelation sent down by the Heavenly and Demonic Gods themselves with one heart and mind!}

If the Heavenly God and Demon God had seen this, they would have beaten their chests in frustration until their ribs broke.

After all, the dumbass was just sitting there watching, not realizing his own house was on fire.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing opened her eyes.

"Wow. Something, something's definitely different."

She opened her eyes naturally, feeling refreshed and full of vitality throughout her body, without a trace of lingering sleepiness.

As soon as she learned the Great Tranquil Zen Art, she passed out cold.

She'd lost consciousness after shivering from the sensation of her brain being kneaded.

In actuality, it was because the Buddhist Divine Art had scattered the Heavenly Slaughter, causing her fatigue to explode, but Qing didn't know that, and honestly, it wasn't like that was wrong either; it could be said that her brain got absolutely mind-fucked.

Moreover, the room was clean, with no trace of the grand volcanic eruption that had occurred previously, meaning she hadn't even noticed the evil cleaner thoroughly vacuuming the room on Crutch No. 2's orders.

\textit{Yeah, it really was dangerous earlier, huh.}

She was right about to charge up like a quarter of her White Hand Demonic Arts.

For reference, it was a quarter because Jian Buxi was so insignificant and weak.

She thought it might be fun to hit her with exactly a quarter of her usual strength, thus being able to watch her writhe and die while coughing up blood.

Wouldn't it be satisfying for a lewd performance specialist's final act to become a performance itself?

Qing shuddered as she recalled her thoughts from yesterday.

"Wow, this... It wasn't for nothing that they kept going on and on about Demonic Arts. So this is what it means to become evil, huh."

Qing, who regarded the Strategy Guide as her life's benefactor, blamed the poor Demonic Arts getting their assholes torn apart in her Dantian, not realizing the Heavenly Slaughtering Star held the overwhelming majority share in causing her to almost lose her mind.

\textit{Right, from now on, I should treat my worthless and incapable Senior Sister a bit better.}

\textit{I'll teach her the Blissful Maiden Arts too. It originally belonged to the Bliss Palace anyway, so returning it to their disciple is the right thing to do.}

\textit{And opportunely enough, we even agreed to train together.}

\textit{Training... but that training is… that kind of training, isn't it...}

\textit{My mouth is my own worst enemy...}

Qing's expression crumpled.

\textit{Um. A verbal promise made by someone incompetent in the mind while in a state of mental lapse wouldn't be legally valid, right?}

Unfortunately, the modern system of what defined 'mentally incompetent' that Qing had picked up in law classes had long since been completely abolished.

And in Zhongyuan, such laws never existed in the first place.

If you mismanaged a disabled family member, your entire household could go up in smoke - it was so common it didn't even count as an incident.

As such, both the principle of personal jurisdiction and territorial jurisdiction guaranteed Qing's promise.

Qing looked outside.

The world was still pitch black.

After spending ten whole nights taking walks, her body had already memorized when to open her eyes.

Qing got up and approached the window.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Due to the ominous string of murders over the past ten days, even the Divine Cult had started night patrols.

The enemy didn't discriminate between Masters and novices.

Nor did they distinguish between the rich and poor.

So it was time for the cult's patrollers to take the lead in guarding the nights of Tian Shan Divine City.

Of course, the exceedingly greater concentration of patrol routes around the residences of dignitaries was purely coincidental.

After all, in Tian Shan Divine City, everyone was, officially speaking, equal. Except for the two representatives of the deity above even the Heavenly Demon.

However, these new patrols didn't particularly pose any difficulty for Qing.

The Brazier Street was sparsely patrolled as it was the street of heretics, and the night patrollers' work ethic was poor due to the additional shifts without overtime pay.

Above all, Qing's Black Shadow Stealth had already reached Four Stars.

It was only natural that her progress was rapid after training diligently every night for nearly ten days.

Black Shadow Stealth was a Red Movement Technique she'd received as a reward for her dedicated service in personally peeling the skin off an unnamed ninja during the night and bathing his exposed flesh with poison.

As Black Shadow Stealth essentially meant ‘diving into shadows', the effect of the technique was roughly similar to its namesake.

Of course, it wasn't a method where she could actually move through shadows like the ninjas in novels, but merely a concealment technique that allowed one to hide within shadows.

It can't be called too exaggerated a name, though.

Originally, martial art names should be embellished. After all, it makes those who learn them later feel proud that they had it.

If it were called Imitation of Pseudo-Buddha's Palm Technique instead of Buddha's Palm, who would want to learn it?

Thanks to this, Qing was able to safely arrive at her friend's house on Brazier Street.

Qing habitually pressed the thin rope under her feet a couple of times.

And after sprawling out in the small room (living room) with an ‘Aoooou, I'm so tired', Xue Ganom, who had the unique hobby of having his hair washed in the middle of the night, would appear from the even smaller room (bedroom).

Xue Ganom pushed open the door with a creak and immediately fired off:

"Do you really have nothing better to do in the middle of the night?"

"Ah. I'm glad to see you too. Has it been a week now?"

"I am not particularly glad to see you, though."

Xue Ganom shook his head slowly.

Qing glared at him with narrowed eyes.

\textit{What the hell? I taught him that ever so precious Divine Art that I so easily obtained, but he treats me like this?}

\textit{Is he trying to say that now that he's learned it, he's done with me?}

\textit{I didn't think he was that kind of person. The nerve of some people.}

"To be honest, thanks to you, I can wake up sufficiently without even having to pour water on myself. But do you know why I still keep the water bottle?"

"Because it's surprisingly refreshing?"

"Because I am afraid of you. Because I feel like the next time we meet, it will not be a person, but a Slaughterer in human form strangling my neck. That is why I asked you to stop your killing spree for at least a week, but you just had to... Hm?"

Xue Ganom suddenly stopped his nagging.

"Hm? Something is different. Huh?"

"What is? By the way, Xue Ganom, you've changed a lot too. What's this? Are you wearing makeup these days? Why have you gotten prett-"

Xue Ganom cut off Qing's words and said what he wanted to say.

"Your eyes. That's right. Your eyes have changed. How did those rotten fish eyes suddenly become human? Did you have some kind of enlightenment? Well, I guess there is finally some good news."

And then he immediately turned his back.

"What the? Where are you going?"

"I am going to put away the water bottle now. From now on, you can just shake me awake. You realize you could just come during the day, right? Why do you always sneak in in the middle of the night? Good heavens, the nerve of people these days."