\chapter{Journey To Mount Hua (2)}

However, the mans spirit could be regarded quite highly. As in, he refused to back down.

'My version of sparring is like this!'

-was how he shouted, so Qing couldn't really say anything in response to that.

In the end, it was really just a training of pure swordsmanship only, without any practicality to speak of.

To Qing, it seemed like they were just killing time. Or perhaps, wasting it?

Additionally, it came with the bonus of bodily fatigue.

What even is the point of sparring like this?

Yet strangely, it was quite a beneficial time.

"Young Lady Ximens skills are extremely excellent."

"It's not worth mentioning the obvious. It's exactly the reason why we don't praise the sun for being extremely diligent in rising and setting."

"That confidence! What a great attitude for a swordsman! I have learned something new once again."

Nan'gong Shencai nodded and continued speaking.

"However, Young Lady Ximen's sword is far too honest. A swordsman's sword should be free."

"...?"

Qing tilted her head.

The fuck did it mean for a sword to be free?

{\itshape Does it mean the sword should find its freedom and leave its owner to wander around by itself, just like Master's sword did?

Do you think I would still be at the Peak Realm if thats possible?}

"Well then. You only need to see it once. Then, I am confident you would understand. This is the Third Movement of the Azure Heaven Sword, called Diffractive Wind."

The sword that was swept down flowed as if brushing the ground, rotating twice with the body and slashing horizontally two more times.

And then, he demonstrated the same movement several times more.

However, even though the move remained identical, it was not exactly the same every time.

It had the elasticity of a snake biting its prey.

The repeating movements had the oppressive force of a rolling boulder at times, the leisure of a gliding crane at others, and then the bustling energy of a swarm of ants.

"Ooh."

"Do you see? Even with the same movement, the nature of the sword changes depending on what is infused into it. Young Lady Ximen's moves are so refined that, aside from our Nan'gong Clan, there is no other art or skill that can follow its intricacies. Yet, it always maintains the same appearance."

\textit{Yeah, okay. Sure. He's valid and all. But why does he seem more like a Master than me?}

It seemed to have bothered Qing a bit, as she smirked mockingly at him. 

"What a pity. It would have been a bit more impressive if you had said that after winning at least once."

"Heh, being lacking is not something to be shameful of. The only thing to ever be embarrassed about is not trying to improve oneself."

"Sorry. If you say something as mature as that, what does that make me..."

Qing immediately apologized.    

"It is alright. Are we not sword brothers, after all?"

Nan'gong Shencai smiled, revealing his healthy white teeth.

\textit{What's with this bastard? Why is he so weird, but also so chill? }

"From what I can see, it would be better for Young Lady Ximen to practice the principles by using just the two movements of the Three Powers. What is your opinion?"

"Three Powers Sword? That one? The stabbing, slashing, thrusting, and whatever?"

The Three Powers Sword was embarrassing to even be referred to as swordsmanship.

It was merely three basic movements considered to be the fundamentals of the sword.

Slashing down vertically, cutting horizontally.

And the third varied by region.

Some said to thrust, others to cut diagonally, and yet others to sweep in a circular motion.

For example, it was like the three main dishes of a restaurant.

The first two were fixed and the last one was sneakily included as their local specialty.

In other words, the first two were completely genuine.

The movement where one slashed down vertically was called the Pressure of Mount Tai.

Though it seemed to have an excessively grandiose name, referring to how it would swing down with the force of Mount Tai, it also had to be considered how greatly it had penetrated into the very essence of a sword. 

The movement where one cut horizontally was called Total Annihilation, meaning to sweep through a thousand enemies with a single slash.

This, too, was grandiose but easy to visualize.

"So...Hmm. Why don't Young Lady Ximen try to face me using just those two movements? It's about embodying the Sword Forms, so we shall do it without using Inner Qi. Using just purely the strength of the sword."

"Hmm?"

Qing scrutinized Nan'gong Shencai's expression.

The corners of his mouth were subtly twisted.

Qing caught on right away.

{\itshape If I use only two movements and don't even use Inner Qi

Then, how can I possibly win?}

It was clear at first glance that it was a scheme to try and win at least once.

\textit{Do you know how long its been since I was that impressed by someone? Huh? Do you? But now, you ruined it. Look at this little fucker yapping.}

However, Qings stats were already teetering at the very edge of the human limit.

If every single person in the world did not use Inner Qi, Qing would have long been heralded as the Greatest Under Heaven, with titles such as the Female Xiang Ji\footnote{Courtesy name of Xiang Yu, a general of Chu-Han Contention period}. 

And shortly after, Nan'gong Shencai spoke with a broken wooden sword in hand.

"Now that I think about it, not using Inner Qi seems to make no difference in enhancing the pure strength of the sword. It appears that using Inner Qi is practically essential. Ahem."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Apparently, Darius, the King of Persia, once said-

\begin{quote}
	The most precious of all possessions is a wise and loyal friend\footnote{Herodotus, The Histories Book 5 Verse (Chapter?) 25}.
\end{quote}

Qing, the External Elder of the Divine Maiden Sect, agreed with him.

But to add onto that, if that friend was wealthy, then they would become even more precious.

Nan'gong Shencai was a very energetic man.

If asked to name his most manly quality, it would be that he always dined at the most famous places when in a city.

Normally, if one abruptly visited a city's most famous restaurant and demanded 'Hand over them food', you wouldn't get a 'Yes, right away.' in response.

Usually, there were fully booked months in advance through reservations.

However, Nan'gong Shencai was a Nan'gong.

Originally, big clans were either local Gzoku or their descendants.

Among them, a few clans had particularly strong control over their respective regions.

And the Nan'gong Clan just happened to be the owners of Anhui Province.

As such, restaurants in Anhui were more than happy to welcome the young master of their province.

It was an absolute honor; how could they dare talk about reservations in the face of him!

Qing's habit was to always be infinitely happy in front of food.

It was a natural disposition.

The obsession born from a persons deep-seated resentment about food was not any ordinary obsession.

Qing had fought with beggars, strong beggars, rats, bugs, and even stray dogs over discarded food.

Naturally, Qing harbored a grudge against hunger.

Had there ever been more comfortable days since coming out into Wulin? That was how great it was right now.

Of course, the Divine Maiden Sect was an exception because it was home.

Home was obviously comfortable, after all.

At any rate, she wasn't just satisfied with the gourmet food.

This thing called sparring turned out to be much more enjoyable than she thought.

"Very well! Let's spar since we're full! Let's go, Sword Friend!"

"Indeed! To think of sparring right after eating! You truly deserve to be called my sword brother!"

Nan'gong Shencai was sincere about the sword and possessed a talent for teaching that he himself was unaware of.

Qing absorbed the pieces of enlightenment that he brought greedily. She sucked that shit out to its very marrow.

And then, finally.

At the end of a spar, Qing exhaled deeply.

"Hooo"

Qing finally reached enlightenment.

She understood the difference between Sword Image and Sword Form.

She realized that infusing one's Image of a Movement to manifest a Form was different for each individual in the world, even if they all mastered the same martial arts.

It was a long-awaited moment of enlightenment!

Achieving the Transcendent Realm meant interpreting and adapting martial arts entirely as ones own.

To put it a bit radically, it could even be called a remodeling of martial arts.

It was the starting point of that process; she had just taken the first step in interpretation.

In term of enlightenment, Qing has entered the Early-Stage Peak Realm.

Only now had she truly understood the enlightenment that should have been reached a long time ago!

The gap between skill and martial knowledge had finally narrowed a bit.

It was because Qing had learned martial arts in a shoddy manner. Once could even say illegally, given the universes rules.

Since she just used whatever was crammed into her head without any foundation or basics, how could enlightenment or whatever possibly matter? 

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Fifteen days passed.

Qing reached Huangchuan\footnote{a county in Xinyang, Henan}, the southernwestmost edge of Henan Province.

Qing thought.

How could a city be named Huangchuan? Isn't that way too ominous?

{\itshape Having succeeded in the county of Huangchuan, I shall now bring Mother and Father to the Land of the Dead (Huangchuan).

  It doesn't exactly have a nice ring to it, huh.}

Unbeknownst to Qing, there were more than one or two cities named Huangchuan in Zhongyuan.

If villages were counted as well, there were easily over a hundred. 

This was because so many of the rivers\footnote{chuan} in Zhongyuan were yellow\footnote{huang} and muddy.

Basically, people settled next to these rivers, thus forming a name such as Huangchuan.

However, the Huangchuan in Henan Province was special.

After all, it was the largest city among the many Huangchuan's.

After stopping at the stable to send the carriage back, Nan'gong Shencai paid the remaining fee. And then, as if it was only natural, they sought out the best inn in Huangchuan.

Indeed. Just as expected from the so-called best inn.

Even from afar, an extraordinary crowd was visible.

It was like some human mass had literally formed a wall around the inn.

Qings eyes sparkled.

"Oooh. How can an inn be so popular? Look's like something to look forward to, right?"

"No matter how good of an inn it is, can it truly attract so many people? That does not make sense. There must be something special happening."

"Something special?"

Nan'gong Shencai's eyes flashed.

"Clearly, a distinguished swordsman must be present. Everyone must have gathered to catch just a single glimpse of their exceptional sword techniques. Does that not make more sense? Otherwise, it is hard to explain such a large crowd."

"...Right. Sure. If you say so."

Qing just heaved a deep sigh.

"Now that I think about it, I cannot seem to hold back either. I must go meet them and ask for guidance."

Nan'gong Shencai, unable to hide his excitement, strode ahead.

Qing shook her head.

{\itshape What kind of monster are you, Sword? No, seriously. What is up with the Way of the Sword?

  I can't begin to understand how it completely changed a perfectly normal, rich young master in to this.}

Qing lamented while following her precious bank.

But soon, Nan'gong Shencai stopped in his tracks.

When Qing caught up to him, she saw that his face was so clearly marked with disappointment.

"Why? What's wrong?"

"It is just full of women here."

"And? What about it?"

"I have seen this dratted scene several times before. It seems a swordmaster isn't here after all. I had my hopes up with my heart racing, even if just for a short while..."

\textit{Ah. This wall of women.}

Qing was also reminded of something when she saw this.

\textit{I see. So this is how it looks from the outside, huh?}

"Ah. You're right."

The scene inside became roughly clear.

\textit{Meh. Well, I'm sure some littering contest is taking place or something.}

Nan'gong Shencai sighed deeply.

"It seems that inside, there is a Junior Brother I know. He is a foolish punk who uses the dao instead of the sword, but still, he is not an individual of evil. Just a bit dull-witted. As such, I am thinking of at least giving my greetings. Would that be alright?"

{\itshape Do all rich young masters know each other or something?

 Well, I guess it makes sense for kids of chaebols to stick together.}

When Qing thought about it, it actually seemed quite obvious for them to.

"Of course, it's fine. No problem at all."

Then, Nan'gong Shencai beseeched her again. 

"To be frank, this punk can be quite harsh to women, so he might be rude to you, Sword Friend. But still, he is not a bad Junior Brother at heart. Please be a little forgiving and understanding, Sword Brother. It is also fine to not pay much attention to him."

Instead of replying with words, Qing only gave a smile in response.