\chapter{Journey To Mount Hua (3)}

The Zhongyuan, too, had societal phenomena similar to the modern era, making it difficult for a dragon to rise from a shallow stream.

The term Rising Stars referred to the young Masters who would become the main figures of the next generation.

However, all these young Masters came from prestigious backgrounds or were descendants of great clans. 

Of course, it was largely due to the growth system of focused investment where ones meridians were refined through Marrow Cleansing from birth, fed elixirs in the form of baby food, and taught to wield weapons as soon as they could walk.

However, the biggest obstacle was that it was not easy for young Masters who were not from prestigious backgrounds to be properly recognized.

If rumors spread that a new Master named Qing had slaughtered the Demonic Cannibal, people would not believe it at first.

'He wouldn't have fought alone, right?'

'There are Masters in the Forts of the Yangtze River Waterway as well, so they wouldn't have let him fight alone.'

'It was probably a lucky finish after a joint attack, wasn't it?'

'Isn't it likely that the Demonic Cannibal wasn't in peak condition?'

'He mastered the Flame Demonic Arts, didn't he? That cursed and venomous Demonic Arts could have messed with his brain, preventing him from making sound judgements.'

'What? A woman? A female brat, you say?'

'She must have offered her body to the Masters of the Waterway Forts in exchange for some fame. Kekeke.'

That would be the general sentiment.

Of course, rumors about Qing did not actually spread.

Bu Xiayun, the Waterway Fort Commander, was an old senior of Jianghu and was well aware of these characteristics in Wulin.

For the sake of his benefactor, it was best that rumors did not spread.

Thus, it was all thanks to him erasing traces and controlling the mouths of his people.

Of course, it did spread quietly, but those reliable in the Waterway Forts remained silent, treating them as mere rumors.

But what if a rumor spread about a son from a prestigious family defeating the Demonic Cannibal?

For instance, if rumors circulated that Nan'gong Shencai had defeated the Demonic Cannibal, people would react as follows.

'As expected of the Nan'gong Clan! I have always believed in you!'

'This is the power of history and tradition!'

'We should send a congratulatory bottle of liquor to Lord Nan'gong!'

'The future of the Orthodox Faction is indeed bright!'

'I knew that Sword Lunatic would cause that kind of trouble!'

This showed just how difficult and daunting it was for a young, unknown Master to make a name for themselves, even if they really were a dragon that had risen from a shallow stream.

Of course, this basic trend wasn't really the main problem.

It was because across all times and places, those in power had always tried to kick away the ladder to the top in order to maintain their tower.

It was for the sake of perpetuating a world of Wulin dominated by major sects and great clans.

In such a situation, the only peers the Rising Stars had were themselves. 

Moreover, these Rising Stars were showered with all sorts of love in their own yards, thus growing up while doing whatever they wished.

In the end, the young Masters were always affirmed in their lives as Wulins upper class.

It was the perfect environment for the birth of a strange bastard whose only positive trait was that he was kindhearted.

And in fact, that had indeed happened.    

"Little Brother, Little Brother Peng. About that young lady over there."

Changbin\footnote{昌彬; lit. 'prosperous elegant'. Changbin in the original text}, The Drunken Sword.

This title was given to him after he, in a drunken state, single-handedly wiped out a band of thieves attacking a civilian home.

He was the most anticipated talent of the Mount Hua Sect, as well as the most Senior Brother of the current generation, thus named Chang.

"No, Little Brother, I am telling you to look at that young lady, you see?"

"Haaa. What now?"

Peng Daesan replied with a voice filled with annoyance.

Regardless, Changbin whispered subtly.

"Look at that lady wearing the shockingly red palace dress. The third one from the left. Is she not exceptionally beautiful?"

"If you like her that much, why don't you go talk to her?"

"Ah, alas, there is a sun that such flowers specifically came to view, so how could a bee like me possibly be heard if I spoke?"

\textit{Why were all the Rising Stars like this?}

Peng Daesan showed his disdain clearly.

"I am not interested. Nor is it my problem."

"Ah, is our relationship only worth that much? Don't be like this. It's lonely drinking alone, you see. I only said that because I'm feeling lonely. Lonely, you hear me?"

"So am I not a person to you? Am I some statue?"

"Haha, am I expected to consider a man a person?"

Peng Daesan sighed deeply again.

{\itshape To think that a bastard like him was the Eldest Brother of the Hidden Dragon Assembly.}

The future of the Orthodox Faction was looking quite bleak.

For reference, the Hidden Dragon Assembly was the name of a gathering of Rising Stars from the Orthodox Faction.

It was also a venerable social club passed down through generations.

"Big Brother Changbin. Why don't you just keep chugging the alcohol you were drinking and stay quiet?"

"Ah! Oh my! My arms about to fall off because there is no one to refill my glass. Look here, Little Brother. Alcohol, by nature, should be enjoyed with beautiful women. That is what deepens its flavor and makes it all the more enjoyable."

"Are you spouting that nonsense again?"

"Ahhh. I just want to drink with women!"

Peng Daesan sighed deeply once again. 

Among the many Rising Stars of the Hidden Dragon Assembly, this bastard would easily be his least favorite.

\textit{He was a good person, sure. But all he did in every waking moment was drink and talk nonsense.}

If it weren't for the fact that he was so kindhearted, there would've already been a massive fallout between the two and Peng Daesan would have already cut ties with him.

\textit{Moreover, despite saying all this-}

"Oooh, Little Brother! Look over there!"

Changbins fuss interrupted Peng Daesans thoughts. 

\textit{It was probably about some beauty again.}

Peng Daesans expression soured and showed no hints of recovery.

"No, look. Younger Brother Nan'gong is coming."

"...I'm going to lose my mind. Seriously."

The only person that could be referred to as Younger Brother Nan'gong was the Young Sword King, Nan'gong Shencai.

And he was known to be the weirdest among all those in the Hidden Dragon Assembly.

Being with the bastard he disliked the most was troublesome enough, but now, the weirdest bastard had also made an appearance.

It was the perfect definition of adding fuel to the fire.

"Hmm? It seems Younger Brother Nan'gong found a woman, huh? True to his name as the Sword Lunatic, it seems he only considers women who carry swords as worthy. Eek, they're coming this way."

Peng Daesan suppressed his irritation.

\textit{Of course, they were.}

After all, they knew he was here.

This was why Peng Daesan always ended up running into people he disliked.

The persistence of women was already enough to make him sick with disgust.

They threw trash, made all sorts of bizarre attempts at physical contact, and conducted endless surveillance that left no room for privacy.

Peng Daesan had plenty of reasons to detest a congregation of women.

And one of the reasons was because Peng Daesan's whereabouts always became known.

As soon as he entered a city, within half a day, the news would spread like wildfire, saying 'The Jade Qilin is here!'.

Then, women would flock to him.

And when that happened, passing members of the Hidden Dragon Assembly or seniors from the Wulin Alliance would say, 'Ah, Jade Qilin has done it again, just like his name suggests', and promptly show up to meet him.

\textit{...But, huh. The Sword Lunatic was bringing a woman along?}

Even Peng Daesan had to admit he was curious about this. 

After all, the fact that the Sword Lunatic was accompanied by a woman was surprising in itself.

What if the Hidden Dragon Assembly voted for the person least likely to be involved with women?

Then he would win by a landslide every single time.

Nan'gong Shencai, the man crazy about swords, really didn't seem to care about anything other than swords.

For reference, when saying other than swords, it meant everything else. Literally.

Despite Peng Daesan never making eye contact with women, he was quite, no, very curious about the Sword Lunatics woman.

His head turned slightly.

She was a pretty young girl in simple martial attire called a dobok.

She appeared to be about twenty years old.

Her intricately braided hair was black, her skin was pale without makeup, her eyes were large, and her lips were delicate.

Her only flaw was that her chest was too large, making her outfit look awkward, but she still fell into the category of being a passable beauty.

And she wore a sword at her waist.

"She's carrying a sword, huh?"

"Of course, she is. She's with the Sword Lunatic, after all."

"That does make sense."

Peng Daesan agreed with Changbin.

This agreement was quite a rare occurrence, though.

"Big Brother Changbin. Doesn't she look quite familiar?"

"I am not sure. She appears to be a stranger to me, though?"

"I swear I have seen her before. Is she someone's younger sister?"

"Well, that does make sense. That lunatic isn't exactly known for being close to women."

While they whispered among themselves, Nan'gong Shencai approached and waved his hand.    

"I came to see Younger Brother Peng, but it seems Big Brother Changbin is here too?"

"That's right. How have you been?"

"Of course, as always, I am fine. Why would I not be? And you, Younger Brother Peng?"

"I've been well too."

"I see. That is good. Being well is best. Well then. This is Young Lady Ximen. Despite her appearance, she is an impressive swordsman."

'Ah. Of course. He isn't called the Sword Lunatic for no reason.'

'Just as expected. Of course that's the case. The Sword Lunatic? With a woman? What a joke.'

Peng Daesan and Changbin exchanged knowing glances.

It was a very, very rare agreement between them.

"Greetings, Esteemed Experts. I am merely a young girl, given the name Ximen. It is truly nerve-wracking to meet such renowned and virtuous experts whom I have only heard of in rumors. Could you, perhaps, please look kindly upon me even if I make a mistake? "

The girl greeted them with a coquettish voice.

Her face was only passable, but her voice was absolute in its refreshing clarity.

As soon as Peng Daesan met her eyes, she immediately fluttered her eyelashes flirtatiously. When seeing the smile in her eyes, one could practically imagine a tail wagging behind her.

Peng Daesan instantly lost all interest upon seeing the overwhelming affection in her actions.

"I am Peng Daesan."

Peng Daesan stated his name bluntly.

It meant that he didn't wish to engage in conversation any further with her.

"I am Changbin of Mount Hua."

Surprisingly, Changbin, too, responded with just a short answer.

"Ah. I see! You are the Jade Qilin, Peng Daesan!"

The sight of the beaming smile that followed was despicable.

Peng Daesans voice dropped an octave.

"What about it? Are you saying you came without knowing, then?"

Peng Daesan retorted sharply.

The girl immediately made a crestfallen expression.

"Ah...Did this young girl do something wrong?"

"Young Lady Ximen. Do not take it to heart. Younger Brother Peng is usually not one to be warm-hearted. It is not just you. He would be the same even if the Five Flowers of Wulin were in front of him."

Nan'gong Shencai consoled his sullen sword brother.

But even while he did so, his words were rather ridiculous.

Peng Daesan would act the same even if prettier women than her approached him? What kind of consolation was that even supposed to be? 

Nan'gong Shencai's words were basically implying that with her looks, she had no shot whatsoever.

It was a statement that would make any woman feel like shit upon hearing it.

Despite saying such dogshit, Nan'gong Shencai was actually quite shocked inwardly.

\textit{It seems that even Sword Friend is ultimately a woman}.

It was intriguing to see her become so demure in front of the Jade Qilin, but when considering her usual demeanor, it also sent chills running down his spine.

"Moreover, this fool uses the dao\footnote{Saber/ Chinese sword with one edge}. An exceptional swordsman like Young Lady Ximen should not bother with him. Just consider him nonexistent."

It looked like Peng Daesan would have to continue frowning for the entirety of today.

Making such statements right in front of peoples faces was exactly why Nan'gong Shencai was known as the Sword Lunatic.

But well, it wasn't all that polite to so heartlessly kick away a woman brought by a big brother he knew.

It would be better if she just lost interest in him by her own choice.

However, it seemed she had no intention of doing so.

"I have heard that Great Expert Peng has an exceptional eye for beauty."

"I possess no such thing."

"Don't be like that. What do you think of me? If you were to score me, how would this young girl fare?"

"Haaa. Look, Young Lady."

Peng Daesan sighed and quietly tried his best to speak nicely.

"I do not like you. If you need someone to talk to, please speak with Dao Master Changbin over there."

At this, Changbin, who was quietly drinking beside them, jumped up in surprise.

"No, wait. That's not...Do not mind me. Younger Brother Nan'gong, pour me a drink."

"Ah. Right. Here, have a drink, Big Brother."

Changbin was a man who did not lie.

And he had always said that the presence of women made liquor taste even better.

So, the moment a woman joined a drinking session, he focused solely on the alcohol.

According to him, he acted like that because it tasted way too good.

He was an extraordinary figure indeed; one who enjoyed the elevated taste of liquor so much that he couldn't even speak, merely chugging away in silence.

And now that a woman was present, it seemed any role that Changbin had in the conversation had come to a close.

Meanwhile, the girl continued to pester Peng Daesan.

"So, Great Expert Peng? What do you think of me? If I may ask?"

"Stop. Enough. Pay me no mind. I am only tolerating this for the sake of Big Brother Nan'gong. I would rather not say harsh words to you, Young Lady."

Peng Daesan's voice lowered even further.

It was clear that he was on the verge of exploding in anger.

That was when the young girl spoke.

"'Vi voud vwather nvot sway hvarsh vords tvu yvu.'"

Peng Daesan looked at her in utter surprise.

"Look at you always lowering your voice when you talk. Well, to be fair, what else would I expect from you?"

Suddenly, the girl placed her elbow on the table and rested her chin on her hand, slouching her whole body in a twisted manner.

"Hey, San! You haven't changed at all, huh! But still, I'm kinda sad, you know? I can't believe you've forgotten my face, just because we haven't seen each other for a bit over half a year. It feels like just yesterday that our San'ie was getting all teary-eyed about saying goodbye. No, wait. Or maybe you actually did cry a bit?"

"...No way."

"Why? Can you not recognize me just because my face changed a bit?"

Peng Daesan was astonished.

Only then did Qing smile with satisfaction.