\chapter{Journey To Mount Hua (4)}

People sometimes had something to say but were too overwhelmed to actually speak, resulting in only their lips moving without producing sound.

That was exactly the case with Peng Daesan.

Qing giggled.

"How could you do this to me? Does our friendship only amount to this much? San?"

"Ha..."

Qing believed that pranks should be enjoyable for both parties.

It should only slightly annoy the other person, without crossing the line.

If the other person had their feelings hurt, it was no longer a prank; rather, it became a quarrel.

Therefore, it was right to clarify things at this point.

Acting all womanly and feminine would only irritate him further.

This precise judgment of the so-called line was Qings true talent, inherent from birth.

\textit{Let's just let him get his shit together for now.}

Qing changed her target.    

"But why is this friend drinking all alone? Can I have a glass too?"

Qing reached for the stacked glasses on the table.

Dao Master Changbin flinched, before hurriedly grabbing the liquor bottle.

He then held the bottle with both hands in a very polite manner, trembling as he poured the drink.

"Uh. Here."

"Wait, what. Why are your hands shaking so much?"

"N-No, it's not that. I just have a bit of a case of hand tremors."

Hand tremors?

{\itshape What the heck? What's all that about? Wasn't he a Master?

  Well, I guess not every party can consist solely of martial artists at the Peak Realm.}

Qing casually moved on and tapped the table lightly.

"Here. Now it's your turn to take a drink."

"Ah. Yes."

Changbin hurriedly emptied his glass and offered it forward.

Sure, he mentioned having hand tremors, but it seemed quite severe.

In fact, it was difficult to pour the drink because he was trembling so much.

However, Qing was a Late-Stage Peak Realm Master.

One of the greatest traits of a Master at such a level was the ability to pour a drink neatly, even into a shaking glass.

It was said that beyond the Transcendent Realm, at the Unrestrained Realm, one could even pour a drink into a flying glass.

This was why Masters were so revered since ancient times.

"It's nice to meet you. Here's to our pleasant meeting. Cheers."

"C-Cheers."

Qing downed the clear alcohol.

It was a strong white rice wine, made of distilled liquor.

\textit{As expected of rich young masters. This ain't any ordinary drink, huh?}

The fiery liquor burned its way down her empty stomach.

Qing shivered.

\textit{Kyaaa, that's good.}

Long, slender fingers picked up a piece of dried fish.

The love that Zhongyuan had for beautiful hands had been famous since ancient times.

A beauty's qualification invariably included the shape of her hands.

After all, as the saying went, 'Slender hands made jade fingers and white arms'.

Peng Daesan, staring blankly at those white fingers, suddenly came back to his senses.

\textit{By the way, were her hands always like that?}

There was something he was reminded of from her suddenly increased beauty and the shape of her hands.

Overhaul Rebirth.

When ascending to the Transcendent Realm, the body was reconstructed and ones inherent beauty also improved by leaps and bounds.

"Have you reached the Transcendent Realm already?"

Qing, munching on the dried fish, replied.

"Not really? I just had a minor enlightenment."

It really was a minor enlightenment. In fact, everyone present already knew and had it before.

After all, it was the enlightenment necessary for reaching the Peak Realm.

Qing had basically cheated her way through, thus skipping past it. As such, she had taken an unusual path, achieving the state first and only gaining the enlightenment later to fill in the gaps.

Only Qing, who did not know of this fact, felt proud of herself.

\textit{Iyaaa\footnote{Onomatopeia for squeeing}. Is it that noticeable when someone obtains enlightenment?}

Of course not.

"I thought you underwent something like Overhaul Rebirth. If not that, then what is it? Did you master some Anti Aging Facial Technique?"

\textit{Anti Aging Facial Technique?}

Qing gave a puzzled look.

It was an expression that was innocent and pure, yet also dumb, as if she didn't know shit. 

"Ah."

Peng Daesan murmured softly.

It had been a while, so he had forgotten how ignorant she could be.

"Anti Aging Facial Technique is... No, forget it. I just asked because your face seemed to have changed."

"Ah. It's because I learned a few martial arts. Apparently, they're supposed to make you prettier."

"You learned Fairy Arts? In such a short time?"

"Wow! You know about Fairy Arts!"

"Haa. There you go again with that talk."

The benefits of the easily attainable Fairy Arts were only limited to whitened skin and teeth, brightened eyes, and pointless fat removal. 

Of course, these were key to the beauty standards of Zhongyuan, making its function quite remarkable.

It was also a type of knowledge that beauties in Zhongyuan attained.

However, Fairy Arts that actually cultivated the form of beauty itself was extremely rare. 

Perhaps only the esoteric doctrines of the renowned female sects in Wulin could compare.

The Divine Maiden Sect, the Fenghuang Sect, the Heavenly Flower Hall, the Bliss Palace..

Or it could be the unintended side effect of the Northern Sea Ice Palaces Demonic Arts, which could make even men appear feminine.

"I got a proper master this time. Since she recognized my genius, she kept requesting me, so I couldn't help but become her disciple."

"How could you speak such insolent words? No, forget it. Your teacher must have taught you because she understood as well. At any rate, you said you have taken a teacher?"

"Yep. She's called Ximen Surin. She even gave me her surname, you know? That's why I'm Ximen Qing."

"Keugh."

Suddenly, there was the sound of someone choking on their drink next to them.

"Keugh, ack, keugh."

When hard liquor that had an alcohol percentage of over 50\% went down the wrong hole, it didn't matter whether one was a Master or some alcoholic savant; it would result in a pathetic sight regardless.

Changbin coughed violently, his eyes reddening.

Yet even while doing so, he somehow managed to palm his fist in a respectful salute. 

"Young Lady, are you referring to the Godmother? Elder Ximen Surin, who is currently serving as the Grand Elder of the Divine Maiden Sect?"

"Ah! You know our master!"

"Wait, well, uh, please, be informal..."

"Ah. Look at this guy. You're from a Daoist Sect, aren't you?"

Qing looked at Changbin with a hint of wonder.

Ximen Surin had once told her to just mention her name if any arrogant, dumbass Daoist or Zhongyuan bastard caused trouble. 

That even their Sect Leader wouldn't dare to mess with her disciple.

"Wait, Sword Friend. Did Sword Brother truly learn from the Sword Queen, who is known as the Greatest Swordsman Among Women?"

"Huh? Did I not mention it?"

"You did not. Indeed, I had thought Sword Friends swordsmanship was extraordinary. But to think the heir of the Greatest Sword Clan Under the Heavens and the disciple of the Sword Queen would meet and become brothers of the sword. What an amazing connection of fate!"

"Is it really that special? If you start assigning meaning like that, every connection would seem extraordinary."

"So, has the Sword Queen truly reached the realm of Sword Intent?"

"Sword Intent? I dunno. Ah. But she does fly around on her sword."

The utter terror of a sudden nuclear noogie air strike was something one could not understand without experiencing it themselves.

"Sword Flight! Has she truly reached such a realm? Ah. Oh my word. I would not wish for any more in my life if I could go and see such a lofty Sword Style even once."

"Wouldn't that be a bit difficult?"

Nan'gong Shencai gasped for breath as if he was about to keel over and die.

As Qing just casually responded, ignoring his state, a gruff voice interjected.    

"Big Brother Nan'gong. Did you not see that we were in the middle of a conversation. So, you have placed your name in the ranks of the Divine Maiden Sect?"

"Nope. External disciple. I mentioned I had some circumstances, so joining them was a bit tough. But Master said it was fine, so..."

"Hmm."

Peng Daesan let out a sigh.

It seemed the story of the Godmother pleading for her to become a disciple was not a lie.

If such a respected figure of Jianghu went as far as to make an outsider her disciple, then-

But when thinking about it again, it did make sense.

A female martial artist reaching the Late-Stage Peak Realm at such a young age.

If even half of what was known about the Godmothers temperament was true, her testimony was quite convincing.

"But why are you traveling with that bastard, no, Big Brother Nan'gong of all people?"

"Because he's my Sword Friend?"

"What in the Heavens is this Sword Friend exactly...No, never mind. There is no need to explain. I roughly get it..."

"We were going to go see Mount Hua. Sword Cliff? Heard its worth seeing, you know? And I'm also curious about Mount Hua itself."

"Wait, you cannot just mention something like that so casua...No. Nevermind. No. Wait."

Peng Daesan's eyebrows twitched.

"What about the other companions?"

"There's none, though?"

\textit{She had no other companions?}

Peng Daesan frowned.

"You are traveling together alone? Just the two of you?"

"That's right?"

"I know all too well what kind of personality you have, but how can you travel alone with a man as a woman?"

Qing chuckled and replied.

"From what I can see, our Sword Friend over here doesn't care about any of that. I bet he thinks that in this world, there are only those with swords and those without, you know?"

"That is correct. In this world there are only two kinds of people. Indeed, my Sword Friend, no. Rather, our minds and hearts have reached a point of connection where we could even be called Zhijian."

"Oooh. Zhijian."

This referred to the ancient story of a concept called Zhiyin.

It was about the legendary connection between Bo Ya and Zhong Ziqi, famous for having the most profound friendship in Chinese History.

Their understanding of each other was so deep that they could communicate through music alone, without the need for words.

Since then, the term Zhiyin, which meant someone who perfectly understood music and sound, had been used to describe the closest of friends.

"Do not beat around the bush."

Peng Daesans voice dropped an octave, as he tried to regain the reins of this conversation.

Qing raised her hand. 

"Wait! Stop! What's this? Are you still upset? Sad? What was the point of staying there anyway? Black Shadow Association? Was that what they were called? Anyway, it's not like I could just fight to the death with them. The weaker side had to dip, you know?"

"That was not what I was talking about..."

Peng Daesans voice returned to normal.

When thinking about it, why did he have to care?

{\itshape What did it matter who this insane woman traveled with?

Besides, as she said, the Sword Lunatic was probably the most harmless man in the world for a woman.

Even if they traveled together, they would probably just spar all day.

He was originally someone who didn't have anything else in his head besides that.}

"At any rate, you said you are heading to Mount Hua?"

"Eung."

"Good timing. It works out well. I was actually on my way back to Mount Hua with Big Brother Changbin."

"Hmm? Are you saying we should go together?"

Peng Daesan's eyebrows twitched.

"Why? Do you not want to?"

"No. I'm obviously fine with it, but..."

Qing turned her head.

Changbin was desperately waving his hand and subtly shaking his head, but upon noticing her gaze, he sheepishly bowed, lowering his eyes.

"Just ignore 'that'. His lifelong wish was to travel with a woman, so think of this as fulfilling one of his wishes."

"No, wait, Little Brother Peng. What do you mean 'that'? I am still the eldest of the Hidden Dragon Assembly, am I not? Your words are a bit-"

"Just enjoy the liquor you so rave about. It is bound to taste better with a woman present, no?"

"Keuheum."

For some reason, he made a sound that seemed like an attempt to regain his spirits.

However, that was all he did. In the end, Changbin just quietly picked up his glass.

"So, have you booked an inn?"

"No. We came here because we heard it was good, but we found that the women had built a wall. So, I thought this must be where our San'ie is."

"You are saying you haven't booked, then. Let's go find one now."

And then, he called over the server to even arrange for a room for her.

{\itshape Truly, what else are friends for?

On top of that, look at him flexing that hes a rich young master. Nice one! Thanks, San!}