\chapter{Journey To Mount Hua (1)}

Qing was always bold, confident, and proud.

But this time, she felt that she had disgraced herself. It was her first mistake since the start of her Wulin journey.

{\itshape Do you even know how sincerely and kindly I lived?

To be fair, strictly speaking, it wasn't my fault this time either.

It just so happened that the Taiping Sword Sect acted like utter thugs right when my mind was foggy.

And then, some clueless sparring fanatic piece of shit provoked me, didn't he?

But still, I was a bit excessive this time.

Yeah. I also have a very tiny bit of fault.

And because of that, my perfect morality has been shattered.}

For that reason, Qing was depressed.

Honestly, Qing knew that feeling a sense of exhilaration from cutting people was not normal.

{\itshape But what else can I do?

It feels so very good. I just cant explain myself.}

So, she had been careful with her actions.

She only enjoyed cutting and tearing apart bad guys.

Qing was just slightly unusual, but ultimately an ordinary person.

As such, her solution to such times was also ordinary.

\textit{A city full of bad memories, huh? Better leave then.}

Qing's decisiveness was unmatched in Zhongyuan.

Because, after all, she had nowhere else to go.

On her way, she stopped by the Taiping Sword Sect.

The martial artist guarding the gate asked what business she had, so she graciously handed over the five spoils of war. Or perhaps, trophies.

"This is...?"

"I picked them up on my way here."

"...?"

What in the world did she mean by picking up the swords on the way here?

And not just any swords, but five from the sect.

The warriors brain froze momentarily and by the time he reached out his hand, Qing had already walked away.

"Young Lady? Where are you going! Just a moment.!"

As he was stuck guarding the gate, he could only cling onto Qing with his pitiful voice.

However, Qing was like the wind, so she could not be held back.

After that, just one problem remained. Where to go?

Qing thought.

{\itshape First off, it seems I don't get along with water.

Somehow, I've never had good luck whenever I'm involved with rivers.

Both the abrupt Final Boss appearance and this place as well.

It seems I have some water-related misfortune written in my fate.}

It's a shame to give up on the Yangtze River Free Pass, but theres no need to ignore the wisdom of the ancestors that said defying ones fate won't end well.

Besides, Qing didn't have much history of traveling in luxury.

After all, since when had she started looking for escort groups and what not?

Just as Qing was about to set off on foot-    

"What the. Why are you following me."

"No, it is not that I was following you per se. I just did not have anywhere to go, so I ended up here unintentionally."

"That doesn't mean you'll get a spar, you know? And why don't you have anywhere else to go? What nonsense is that? I can't believe youre just leaving aside your nice, wealthy home and saying something so privileged."

"Well, the thing is...Hm. I am thinking of running away from home. If I return now, I doubt I will be able to guarantee my life."

Three days had passed since the incident.

It was only natural for rumors to slowly reach the actual ruling clan of the Anhui Province, the Nan'gong Clan.

And the current lord, Sword King Nan'gong Dalu \footnote{大爐, lit. 'great furnace'. Daero in the original text}, was a man as straight as an arrow.

If the rumor that his son harassed a woman during broad daylight reached him, the consequences were quite predictable.

Qing asked in utter incredulity.

"Nah, what? Then just go on your own way. Why follow me?"

"Young Lady. Isn't it too harsh to act so coldly? As a fellow swordsman, I mean. Those who pursue the path of the sword are akin to comrades, wherever in the Four Seas they are."

Qing frowned, narrowing her eyes.

{\itshape What is this sudden talk of comradeship? What? You want me to give a standing ovation or some shit?

How do I shake off this lump?}

Then suddenly, an idea struck her.

\textit{Why do I necessarily have to shake off this wealthy young master?}

With that, an enlightenment came.

\textit{Ah! I've lost my roots! My original resolution! The absolute basics!}

In the first place, Qing had rarely traveled with anyone. But when she did, she had always enjoyed the benefits that came with it.

{\itshape Come to think of it, I wonder how San'ie is doing?

Well, I'm sure he's just going around, attracting women with every breath he takes.

At any rate, there was enough value in associating with this wealthy young master.

I was too caught up in the annoyance of sparring.

A few bing bong bonk slap here and there?

That's easy shit. I just need to get it over with.}

Of course, there was an essential process beforehand.

It was to establish a proper relationship.

The longer one had to be with someone, the better it was to make the identity of the relationship crystal clear.

At best, he was just a baby in his mid-twenties.

It was not okay to have him follow her around, using honorifics all the time.

For now, Qing tried to casually bring up the conversation, as if to throw in bait.

"If we're comrades pursuing the path of the sword...then we could be sword brothers."

"Sword brothers!"

Nan'gong Shencais eyes widened into saucers.

"I have never heard such moving words before in all my life. Sword brothers, sword brothers, you say..."

"So, we're sword brothers, okay?"

"That is exactly what I have been wishing for! Sword brothers. How excellent."

"Then, if we're training together as sword brothers, there's no need to be overly formal or keep our distance, right?"

"Hm..."

Nan'gong Shencai pondered for a moment and then nodded.

"That does make sense. If you wish, let us do so."

\textit{What the fuck? It's that easy?}

Qing felt a sense of disappointment towards this utterly ridiculous and easy-to-convince person.

However, her disappointment was premature.

Nan'gong Shencai's title was the Young Sword King, but he also had another moniker. The Sword Lunatic.

It meant that he was a crazy ass motherfucker who was obsessed with swords.

Qing had underestimated Nan'gong Shencai far too much.

"...As such, the sword is indeed the most noble weapon in the world. The fact that Jiutian Xuannu, the Dark Lady of the Nine Heavens, descended to the Yue State to bestow swords, and that Lu Dongbin, uses a sword, proves by principle that the sword is the Greatest Weapon Under the Heavens, second to none. Isn't that so?"

"Uh. Yeah. Sure"

"People often talk about the Hundred Day Spear, Thousand Day Dao, and Ten Thousand Day Sword. Of course, if the one speaking is closer to being a spearman or a dao wielder, the order of Hundred and Thousand might switch, but the position of the Ten Thousand Day Sword, which states that swords require tens of thousands of days of practice to master, is unquestioned. This proves the superiority of the sword once again and that we swordsmen, unlike those who handle other kinds of weapons, are the true martial artists."

\textit{Ah shit. I got myself into a fucking mess. I shouldn't have involved myself with him.}

The incessant bragging about swords from her side seemed like it would never end.

Sword brothers. The words that meant they were friends bound by the axiom of swords had deeply resonated in Nan'gong Shencai's heart.

Thinking he had finally found someone who truly understood him, Nan'gong Shencai began to share his special affection for swords.

\textit{Holy fuck, damn. He talks a lot.}

Moreover, Nan'gong Shencai's praise for the sword presented a significant problem for Qing.

It wasn't just a simple level of 'I like swords. I like them so much I cant control myself.'

It was more like the sword was the only weapon in the world worth considering, and all others were not even worthy of being called weapons.

Thus, the only real martial artists were those who wielded swords and those who used any other type of those so-called weapons were not true martial artists but mere pretenders, trying to appeal that they belonged in Wulin when they actually didnt.

After all, he was currently making an assertion that was roughly similar to such sentiment.

"Ah. It seems I have talked too much by myself. What about you, Young Lady? You must have a deep philosophy about swords as well."

"Uh, well. For starters, they're convenient?"

"Exactly! That overwhelming, unbeatable convenience cannot be ignored. After all, a spear can only stab, and a dao, pretending to be a sword, can only cut, so their mysteries are shallow and insignificant. Meanwhile, a staff fails to embody the will of a weapon in the first place, which is the intent to cut the enemy, and using a bian is..."

For now, Qing cut him off.

"Alright, alright. I know, you know, the sky knows, and the earth knows\footnote{Anecdote of Yang Zhen, an official from Eastern Han dynasty, rejecting bribe. Here Qing's use it in its another meaning, which is being sarcastic} that swords are great, so let's save that discussion for another time. Putting that aside, is there somewhere worth going to?"

"Hm."

Nan'gong Shencai rubbed his chin in thought.

Then, he suddenly slapped his palm with his fist.

"Then, what about Mount Hua?"

"Mount Hua?"

"I have gone to see the Absolute Sword Wall of Mount Hua before. There are no words to describe it other than how truly incredible it is. If it is the Divine Maiden Sect, the Mount Hua Sect would surely share the Absolute Sword Wall with you."

"Even if I'm an external disciple with no ties to the sect?"

"That should not matter with the empyrean presence you exude, Young Lady. After all, it was like that when I went."

"Hooo?"

{\itshape Mount Hua, huh? I wanna go see it!

When would I ever have the chance to see Mount Hua with my own eyes?

I'm worried that it might be a bit dangerous, but this guys been there and back. 

And since the Mount Hua Sect was mentioned by Teacher several times, it must be a famous sect. What was it again? Nine Sects?

If a sect had established itself to that extent, maybe its not all that dangerous.

How can I resist the allure of lava, which is more powerful than fire?}\footnote{Huasan/ 'Mount Hua' can also means 'volcano'. Misunderstanding on Qing's part.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There was no need to talk about how decisive Qing was and Nan'gong Shencai, needing to escape Anhui immediately, had no time to hesitate.

They bought a carriage and a coachman with Nan'gong Shencai's money.

Likewise, they purchased plenty of snacks.

And also a generous amount of wooden swords for sparri-

Qing frowned.

"Why buy so many wooden swords? If you resell them, do you get a profit or something? Is this some local specialty? A place famous for wooden swords?"

"Oh no. It seems Young Lady Ximen is not quite aware yet. A few spars are enough to break a wooden sword. It is much better to have plenty than not enough. Isn't that so?"

Even considering that, it seems to be a lot, though.

However, since he was spending his own money, there wasn't really any reason for her to object. Qing just accepted it as it was.

Sparring was undoubtedly a hassle.

But when thinking about how she would have to sit in the carriage, listening to his endless praise of words, she found herself thinking it wouldn't be so bad to beat this little fucker's ass like a drum.

\textit{Oh well. Let's just beat the shit out of him.}

After all, the difference in skill became far more apparent in sparring.

Dishonorable tactics and means were prohibited.

Targeting dangerous key acupuncture points was also prohibited.

And if one intended to use any dangerous moves, they had to be declared in advance.    

As such, even if Qing said it was just sparring, the outcome was pretty clear.

He was just a mere Early-Stage Peak Realm rookie, who could barely maintain Sword Qi as it blinked into existence and out haphazardly.

In reality, it would be more of a lesson than a spar.

In that sense, sparring with Nan'gong Shencai was sometimes helpful and sometimes not; it was quite vague as to which one it was.

So, to explain, this was how it went during the first spar.

Qing picked two out of the five approaching sword strikes to hit away lightly.

After the two real movements were deflected, the momentum of the remaining feigned movements wavered and disappeared.

Qing pretended to take a step forward and kicked Nan'gong Shencai's ankle.

Nan'gong Shencai let out a grunt and leaned forward, thus sticking out the crown of his head.

\textit{Ah! This is my time to shine!}

Qings left hand clenched into a fist with the middle finger slightly protruding.

{\itshape Master, your disciple is finally going to do her part.

Please watch over me from the heavens.}

Bonk!

In that moment, Qing felt a deep satisfaction swelling from within.

\textit{So, Master has always kept such a good thing to herself, huh?}

With that, victory and defeat had been decided, but Nan'gong Shencai refused to accept it.

"Young Lady, is that not far too petty?! That is cheating!"

Nan'gong Shencai exclaimed, seemingly aggrieved.

"Ehh? Me? What did I do?"

Qing genuinely didn't understand.

"How can you resort to other attacks besides the sword!"

The response that returned was quite strange.

It meant kicking was prohibited and so were nuclear noogies.

"...? I don't understand what youre saying."

"In a spar of swordsmanship, only swords should be used. Did you not know that?"

Qing blinked at the absurdity.

"What kind of dogshit is that?"

"...? Why are dogs defecating relevant here?"

"Nevermind."

Qing protested in a serious manner.

"You're not going to say we should only use words even in real combat, are you?"

"In real combat, it cannot be helped. If my skill is lacking, I may have to resort to other methods. But this is sparring, is it not? It is training to improve our swordsmanship, so naturally, we should only use swords."

"Hmm?"

{\itshape Is that convincing? It seems like it might be?

It also does kinda seem like absolute dogshit, though.}