\chapter{Training Arc (2)}

"The basics are the right attitude."

Qing then adds his commentary.

"The sword iss the ultimate weapon, a tool for self-improvement, and a means for swordsmen to communicate with the world. Should these swordsmen, practitioners of the sword, truly display such depraved behavior like mere thugs!?"

"No!" "No!" "No!"

There was no intention of unifying it into a military unit or even into a Tanaka unit.

In the first place, what, what's so important about that in the military? Will using this character at the end of a military name increase the number of enemies or decrease the number of allies?

It's just a trick to force people to obey orders by crushing them with authority and oppression.

"A swordsman, as a representative of all martial arts, must possess dignity. Wash daily to cleanse both body and mind, trim your hair and beard, and keep your mind in order. Do you understand?"

"Okay!" "I will do that!"

Walk with your shoulders back and confidence.

Look ahead and do not drag your feet or walk around with your back to the ground.

As Qing's 'basics' continued, Nan-Gong Shencai and Murong Zhuji glanced at Qing with ambiguous expressions.

"You shouldn't sit or lie down in a rude manner. That's the attitude of a beggar, not a swordsman!"

The two of them pictured Qing eating a snack.

She was leaning her upper body to the side, her arms resting on the armrests of the chair, as if she were sitting or lying down, her legs spread out like a half-lotus position, her skirt stretched out tightly, and she was munching on snacks.

And you're telling me not to lie down? Whether it's grass, rocks, or dirt, as long as it's not mud, you'll lie down and cry out, "Oh my gosh, how can you say that?"

"Your attire must be neat and tidy. Wash and change into fresh clothes every day. Don't take them off carelessly just because you're hot, and don't walk around in disheveled attire. Do you understand?"

The ecology of Qing, the second.

She loosened her belt and fluttered her belly, saying she was full, and she's showing off her belly as if it's some kind of boast, afraid that someone would say she ate too little, so she shows off what she ate.

"Moreover, a swordsman's sword is like a companion that will accompany them throughout their life. Do not disregard it just because it's a wooden sword for training. Keep it within reach at all times and practice with it!"

The ecology of Qing, the third.

The things Qing did with her sword, hunting and grooming animals, scaling and gutting fish, picking up trash and throwing it away, stirring up bonfires for no reason and sending sparks flying, and occasionally digging the ground to gather herbs…

Even a beggar wouldn't abuse his staff like that, let alone a warrior who wields a sword.

However, Qing was not a shameless person who forced things on others without doing it herself.

Because Qing was not singular person.

The great ChoeolQing could not be defined solely by her identity as a swordsman. He was a master who transcended weapons, using kendo in all directions, and he also possessed impressive skills as a carpenter and a female physician.

Even though it looks bad, it still tastes good when cooked, so it was a master of various skills that was also known as a master of cooking!

Above all, she was a skilled beggar with a lot of experience, a professional beggar, so to speak, a real beggar, a true beggar.

Because Qing affirmed all of these, she could reveal all aspects of her identity without hesitation.

But what about the officials?

Isn't it about breaking away from your past self, such as a ronin, a third-rate wanderer, etc., and starting anew as a swordsman of the Wulin Alliance?

The laundry of Zhongyuan was only to be beaten to remove dirt. If that was so, I will endure my bitter heartache and become a laundry club that will remove the dirt of the officials!

This was precisely the noble attitude!

"Okay!" "Yes!"

The officials give their answers with great enthusiasm.

Of course, there were a lot of requests, but they were just to be clean, neat, and tidy, so I thought, what's so difficult about that?

Moreover, the image of the stylish swordsmen of the Jeongpa martial arts world was exactly as Qing said, so wouldn't it be depicted as a neat nobleman with a single sword wielding a sword and showing off his chivalry to the world?

So, after hearing the basics of Qing, my heart raced with the realization that I had stepped into the world of martial arts.

"This Instructor will simply ask you to follow the basics, and if you just stick to them, I will be more kind and gentle than anyone else. But, um, is this difficult? Is it hard to stick to it!?"

"No!" "No!"

The officials raised their voices and clapped their hands as if it were natural.

But?

Humans were not made to be defeated, but they were also made to feel comfortable in positions that were dirty, messy, and crooked, which were bad and harmful to the body.

So, the basics were actually extremely difficult, but it will take some time for the officials to realize this… … .

"Finally, work when it's the time to work, and rest when it's the time to rest. Focus on your training during practice, and rest comfortably when it's time to rest! As long as you stick to the basics, there won't be any interference with your rest! That's all for now!"

Saying that they won't interfere if you stick to the basics was equal as saying that they will interfere if you don't stick to the basics, multiplying both sides by a negative number.

Arithmetic was not an important subject in Zhongyuan, even more so for the martial artists, so how could the officials have noticed?

I guess that's just how it is.

So, Orogeomgyeol, first lesson!

"The swordsmanship you will learn was called Five Paths Swordsmanship. This martial art originated from the Absolute Swordsmanship of the Wulin Alliance Swordsmen's Club. It has been developed through countless swordsmen, including the foremost swordsmen of the Wulin Alliance, the Four Great Sword Sects, and the prestigious swordsmen of the time. Now, it was our turn to inherit Five Paths Swordsmanship!"

"Five Paths Sword Strike!" "Absolute Sword Strike!" "Four Great Sword Sects!"

Exclamations of admiration burst out here and there.

They'ver never heard of anything other than the Four Great Sword Sects, but anyway, aren't names like Five Paths Sword and Absolute Sword unusual?

"Its essence lies in the infinite expansion of the Aurora, through the combination of the five subtlety of Zhong, Kwai, Yu, Byeon, and Hwan. Therefore, it was a swordsmanship of ascension that can only be fully unleashed after mastering the five subtleties of swordsmanship. True power can only be unleashed by transcending one's own limitations and awakening the starlight, making it a significant challenge for practitioners just beginning their swordsmanship journey."

What were the feelings of the officials who hear those words?

Rather good! The Wulin Alliance was the best!

A martial art that only becomes powerful after reaching its peak, isn't it a type of rising technique called strong martial art?

Of course, it was difficult, but there were very few people who entered the Department of State Affairs without that level of determination.

No matter how hard it is, no matter how much pain it involves, like cutting bones and tearing muscles, I will learn and persevere.

Of course, that's just my ambition, but if I really had to cut my bones, I would just throw down my stones and run away like Guan Yu, who cried loudly.

"Therefore, this Instructor will focus on teaching the fundamentals of the Zhong-Kuai-Yu, ingraining and internalizing the principles, and mastering the initiation process through the perfection of three paths! Therefore, the swordsmanship you will learn is the introduction to the Five Paths Sword, the Three Paths Sword."

"Three Paths Sword!" "Three Paths Sword!"

\textit{As I have felt since coming to Zhongyuan, the reaction of the people of Zhongyuan is truly heartwarming.}

Next, Qing continues to introduce the swordsmanship.

The Samro Sword was made up of three sword styles, the Jungro Sword, the Kwairo Sword, and the Yuro Sword, which contain only the secrets of the Jungkwaiyu. The goal of the course was to learn all three sword styles and be able to freely use all the secrets of each style.

For example, the first stroke was a downward stroke followed by a slash to the right and then a slash to the left.

However, after embodying all three paths, you will be able to strike heavily, deflect the enemy's attack with a soft right slash, and then target the enemy's waist with a quick left slash.

Or, you can strike with a sword to scatter the enemy's center of gravity from the beginning, then cut the enemy with a quick sword and finish them off with a heavy sword.

After learning all of the phrases, "중중중 큐브 큐브 큐브 유유유", freely convert them to "중큐유 큐브 중중큐브 큐브 큐브 큐브 큐브 큐브 유유" according to the situation.

Thus, the swordsmanship using the three paths was completed.

It was his own interpretation that he had created through his research and association with the swordsmen of the Half-Geom Ssangdohoe.

Even though he was beaten and destroyed by the Great Emperor Mucheon, he was the best swordsman of the time, and at least Hwagyeong was the one who joined, making him the pinnacle of friendship and absolute swordsmanship.

Even though the group assignments created by the best swordsmen of the time were unfinished and purely out of interest, they were a divine skill that incorporated various rising groups.

How do you teach this to officials?

At the very least, it has to be super high so that we can at least imitate it in real life.

Of course, the reason was that the Wulin Alliance decided that even just imitating the form was enough to create a swordsmanship that was colorful enough.

Among teachers, the first teacher to take on a new role was usually the most passionate, and among homeroom teachers, the first homeroom teacher to take on a new role was usually the most passionate.

"First, you will learn the first through third forms. However, since the third form was a training sword for advancing to the fifth form, the names of the first forms have been modified to make them easier for you to understand."

And so, the moment when Qing proudly introduces to the world the first three recipes of the Samro Sword Technique, the culmination of his efforts!

The Three Route Sword Techniques, the first call.

Strong, weak, weak.

The Three Route Sword Techniques, the Second Invocation.

Strong, strong, strong.

The Three Route Sword Techniques, the Third Invocation.

Strong, medium, weak.

The Three Routes of Swordsmanship, first half.

Strong weak weak strong strong weak strong medium weak!

It was a truly intuitive Movement name.

Well, the name of the Five Paths Sword's first form was unnecessarily grand and difficult, so things like Five Paths Sword's first stroke, Sanhai Yicheon Hal, and Sanhai Yicheon Hal were just useless and fancy, and the name of the swordsmanship itself was Absolute Sword's Ultimate, so it's ridiculous.

Of course, the officials were a little disappointed.

Still, the strong-weak-medium-strong-weak was a bit… … .

But that was only for a moment-

"This Instructor will now demonstrate the swordsmanship. I will demonstrate three sword styles: the first, strong, weak, and medium swords, and the quick, strong, and weak swords."

"……!"

It was the moment when Qing raised her flute.

In an instant, the bright daylight turns dark.

The figure of the woman covered in cotton was nowhere to be seen, but a sword stretched high, piercing the sky.

The shadow of a sword so huge that it blocks out the sun and casts across the world.

The presence of the weapon surpasses that of a human, and it was a skill where people were invisible and cannot be seen, it was the union of the divine sword.

A huge blade reaching far beyond the sky falls to the ground.

The sound of the air tearing apart was like thunder, roaring and tearing at the eardrums, and a gust of wind sweeps past, shaking the hair of the people in the palace.

And before the world, split into slanted lines, could even heal, starlight rushed in from left and right.

Under the split sky, a world cut twice at the waist, a vision of a world flowing down the cut edge and falling into pieces and scattering, seems to be reflected in my eyes.

The mountains and seas were two thousand and one.

Shatter the sky that was split in two.

It was a legacy of absolute swordplay that was recreated solely through the secrets of the middle sword.

"……" "……" "……"

The officials in the room just had their mouths wide open.

In the silence, Qing raises his sword again.

The first episode of the series, which unfolds again, was a strong and weak episode.

This time, it's the number of the Kwairo Sword that contains the secret of Kwai.

But there was nothing to see.

Only the scream of the wind, a beat late, tells us that it has already been cut down.

It was a speed that could not be caught up to even by sight at a third-rate or second-rate level, because originally, power was the way to create speed.

It doesn't have the majesty of a heavy sword, but it has a fierce speed that the five senses can't keep up with.

Then, Qing slowly unfolds his sword again.

Slowly but gently.

As she flutters in movements that anyone could imitate, only then does the elegant figure of the most beautiful woman in the world dancing with swordsmanship come into view.

And after the demonstration, Qing played the flute, the flute?

Only then do the officials realize that the weapon Qing wielded was not a sword, but a flute.

So then, what about that giant sword that I saw and felt?

And then, Nan-Gong Shencai smiled bitterly.

The thoughts of a warrior in the mid-Hwagyeong period.

In other words, she had filled the unfinished and empty Five Paths Sword with her own thoughts, so now not only had Sword Friend increased her realm, but her sword insight had also greatly increased.

And then another thought comes to mind.

\textit{Do you have any intention of hiding the realm of Hwagyeong? Isn't it too obvious?}
