\chapter{Training Arc (3)}

In fact, Qing committed fraud.

It's not that the Zhonglu Sword was weak and strong at first, but rather that the Dokgogu Sword was strong and weak at first, and it has a lot of the Yua Dokjon mixed in.

The shape of the giant sword that seemed to reach the sky was not an absolute sword, but a legacy of the Great Emperor Mucheon.

It was exactly the same tactic as showing up with a foreign car worth hundreds of millions of won and luxury goods worth tens of millions of won, and saying that if you invest, you can become like them too.

If we look at the history of the absolute swordsman being beaten like a dog and disbanded (dang) for being territorial towards the Great Emperor Mucheon, it was an act that was almost like an insult to his seniors.

But Qing was confident.

It's not a scam, it's just some seasoning.

If I had to say, was it something like a white lie?

Because everyone was positively influenced.

The eyes of the officials were like a blazing fire burning with a supply of oxygen.

Well, honestly, even though they were the officials of the Imperial Academy, they didn't expect them to teach such incredible new skills.

But what the heck.

I opened the lid and watched the demonstration, and it was truly a miracle like no other in the world.

Absolute Sword? This terrifyingly mad swordsmanship, perhaps the greatest swordsman of the time, was forged by the collective efforts of the greatest swordsmen.

Half of the martial arts world was comprised of ronin and half were warriors from small sects, and the obsession these lower classes of the martial arts world have with divine skills was a blind pursuit that goes beyond imagination.

Naturally, I couldn't help but clench my fists and burn with the determination to learn even if my body broke.

In other words, they were the type of people who were easily scammed.

"Before that, I will announce the formation of the training teams. Team 1, team leader: Yang Qi."

Then, while saying, "Oh, I'll do it," Yang Qi, who became a first-class martial artist after being hit by Qing, gulped.

Can I encourage you?

"For the crew, Wan Talu, Zhang San, Ma Dazhe-"

Qingha's youngest brother, Mataja, smiles and says that things were going well for his close friend, Yang Qi.

Whether it was from Zhongyuan or Qing, the desire to be in the same group as friends was the same.

"……Xiao Yindiao, Zhang Feihu-"

"No!"

Then someone shouts, cutting off Qing's words.

It was a noise that caused the family to be destroyed.

"Guan Dao, the instructor clearly stated that he would announce the formation. The formation of the training unit was not a matter requiring Guan Dao's understanding."

"But, he's my enemy! He destroyed my family, and now, when it's shameful to even live under the same sky with an enemy, you're telling me to join forces with him?"

The noisemaker shouted, swinging his weapon.

Qing answered him.

"Xiao Yindiao, come forward. Lie down and stretch out."

"Yes?"

"This instructor clearly said we should stick to the basics, and pointing at someone with your finger was impolite. Isn't that the most basic of basics, something even a child would know? So, come forward and lie down on your stomach."

Xiao Yindiao was startled.

Because when the informal speech changed to formal speech, Qing became even more oppressive for some reason.

Of course, that wasn't what Qing was aiming for.

Well, I guess the instructor really does use formal language. I can't seem to get the hang of using informal language. It just came out of nowhere, so I guess I'll just keep going like this.

And, if you're a flute teacher, you should use polite language. Right.

"Hurry."

The noise level was rising and falling, but judging by the pale face, it seems like he was quite aggrieved.

But rules were rules.

Qing dragonfly was falling. Boom!!

"Ugh!!!"

The Ximen Surinryu training method, which can make anyone, regardless of age or gender, run around rubbing their butts in one room, was the pinnacle of learning through the body.

"The officials also take note."

Qing declares clearly, his eyes seeming to flash with a sinister glint beyond his face.

"Manners."

"People."

"Make."\footnote{The Kingsmen}

I don't know why he broke off one word twice and stretched it into three, but the madness contained in these three words was chilling.

The noise-making group, which had been making a fuss for a while, finally returns to its original position as if the radiation exposure on its buttocks has subsided.

But that face was so unfair.

"Xiao Yindiao. Continue."

"Yes?"

"This Instructor asked you to be polite, but I didn't forbid you from speaking. So, please continue with what you are about to say."

Anyway, I already know what you're going to say.

Because the person who stopped the somewhat petty revenge of the noise maker and the revenge of the family that was trying to carry out by feeding them mountain poison was Qing.

And the person who gave special recommendations to the two people who were already disqualified before even taking the test was Qing.

Because in Sima Chunfeng's pre-treatment, the noise-making group was eliminated in the cowardice category, and Jang Bi-hu was eliminated in the origin category.

The noisemaker hesitates, then reaches out to Zhang Feihou again.

Since he was a noisemaker who had learned his lesson after being hit once, he straightened up and pointed politely with both hands-

"Fuck, fuck! That bastard was a bad bastard! He's such a bastard, bastard! I'll kill him!"

Oh, I know that.

Before a fight, I have a very logical and moving speech in my head, but when I actually try to say it, all that comes out is, "Fuck!" It was that kind of principle.

Unlike the swear words that were filled with pure hatred, the attitude was very cautious and polite, which was a bit, um, I shouldn't laugh.

"Xiao Yindiao, come forward. Lie down and stretch out."

"Yes, yes? I didn't scold you…"

"A puppy from the same officer? It's clear that this isn't a show of friendship that can be tolerated, given the personal connection. What did this Instructor say?"

"It was manners that maketh man…"

"Okay. Bring it. Hurry."

The noisemaker steps forward again.

The body lying face down was trembling slightly, um, it wasn't like anything was breaking or exploding, so why was it trembling, pitiful.

Of course, I don't intend to see it that way.

Bam!!!

The noisemaker was possessed by the zombie again.

This time, the thigh. Because Qing's nuclear honey chestnut hasn't yet reached the level of Ximen Surin, hitting it again after hitting it already could cause problems.

The key was to hit back after hitting back, but it's a shame.

Since the thighs were lower than the buttocks, rubbing them makes the back bend and hunched, which makes things even more difficult.

But once you get hit on the thigh, you have to rub it, regardless of your face or your grandfather's face.

"Okay, Xiao Yindiao. Let's continue."

Then, the noisemaker pointed politely at the equipment and, after finding his words with difficulty,-

"Well, he's the eldest son of a sect called Ongajubang. Ongajubang violently seized our family's business, and as the current leader of Eom Chang-hyeon's sect, they continue to brutally exploit the common people. So, I believe I shouldn't be associated with someone as dirty—or, rather, unclean? murky? In any case, someone with that kind of blood flowing through their veins, and with someone who was the enemy of my family…"

The officials' gaze was fixed on Zhang Feihou.

Their gazes were all cold and indifferent, the kind of contempt that could be described as silent condemnation.

After equipping him, his expression turned pale.

But we have to let it go now.

Anyway, even if I tried to stop the noise here, it would spread to my dorm and to the officials I was close with.

Rather than gossiping like that, it would be better to make it clear in front of everyone.

"Zhang Feihu, if you have anything to say, please say it now."

Zhang Feihu, or previously Wen Feihu, looked at Xiao Yindiao and finally began to tell his story.

"My original surname is not Zhang, but Wen. As Young Expert Xiao said, I am indeed the eldest son of the Ongaju family. However…"

It's dirty blood, I admit it.

But he said he didn't like that, so he left home and changed his last name to mean he was cutting ties with her.

Then some nod and others frown.

And it didn't stop there, it was noisy.

Even if it's called isolation, was it convenient to erase the family karma and get rid of the resentment just because you don't like it?

But, if it means that the realm of those Sado-ryeon bastards was the one who exploits the common people, then if they abandon their position as successor and come out, doesn't that show their determination?

Qing stomped her feet on the floor.

"This Instructor will not force your judgment. Some may argue that the revenge of Xiao Yindiao is justified, while others may argue that Zhang Feihu is innocent!"

Qing stomped his foot again.

"However you are now officers of the Yizheng Martial Study Hall and trainees of the Sacred Swordsmanship Academy, like sailors sailing on the same ship. Therefore, I will absolutely not tolerate any acts that cause conflict within the Yizheng Martial Study Hall based on past grudges. Do you understand what I mean?!"

"Yes!" "Okay!"

"Is that all you can say?!"

"Yep!!" "Okay, I understand!!"

Now, I don't know about the rest.

The people responsible should resolve this between themselves, or fight or split up after the course ends and they should figure it out on their own.

Because I can't force them into a cycle of apologies that digs deep into their bones, like hugging little kids to make up and saying, "I'm sorry, I'm more sorry."

"Okay, let's continue with the formation."

Three training groups of nineteen people each.

The total number of students in the swordsmanship course was sixty-one, so after subtracting the three assistant instructors, one person remained.

The blacksmith waved his hand at him.

"Yes, Sword Jade-lady."

"Instructor, my group hasn't been formed yet."

"Sword Jade-lady Trainee is already well-versed in swordsmanship, so I would like to train you separately and make you assistant instructor. However, if Trainee does not wish to participate, you can join one of the groups."

"No. Rather, I wanted to ask you a favor. Thank you."

And the eyes of the Geomok-gun looking at Qing sparkle, um, it's really burdensome.

Anyway, one last piece of news to announce.

Actually, this was the main point.

"And, from now on, on the fifteenth and new moon days, there will be a competition for the King of All Weapons, where trainees will compete against trainees from other courses."

"The King of All Weapons!" "The King of All Weapons!"

The King of All Weapons.

It was a martial arts competition where trainees from three disciplines compete against each other, and the winning discipline was given the title of King of All Weapons.

The benefits of the King of All Weapons were as follows.

Two extra dishes were served with the meal.

Tea and snacks were provided at the accommodation.

You will receive a number of amazing and unique benefits, such as extending your monthly three-day leave period by one day to four days.

And most important of all!

You can attach the King of All Weapons to the training center's slogan!

At morning and evening roll calls, the winning weapon was Sword/ Dao/ Fist, the king of all weapons and the most superior weapon in the world! The honorable/ humiliating slogan must be shouted three times!

"However, this Instructor absolutely cannot tolerate the horrific noise of those who proclaim that the half-assed half-sword or the uncivilized fists of the thugs are the King of All Weapons. Do you understand what I mean?"

And then Qing's aura became fierce again.

"If that should ever happens, hehe, then even this Instructor won't be able to hold back her anger…"

Qing shook the flute gently.

The officials gulped at her.

\textit{Oh shit, if we don't win this, we'll be screwed.}

And here was the key:

The participants in the Manbyungjiwangjeon were decided by other instructors!

That means, of course, you end up picking an easy guy.

"Therefore, you can only win if you not only receive guidance from the instructor, but also push and pull each other and raise the overall achievements of all of you."

It was a system that was quickly created at Qing's suggestion.

Let's maintain internal unity by pitting the training centers against each other, and through that unity, let's teach and lead those who were defeated, and bring about high achievements for all.

By the way, the response of Sima Chunfeng, who wrote the details, was truly enthusiastic praise.

"Divide and rule! Create external enemies! This was truly the way of an emperor! Indeed, a brilliant idea worthy of being remembered as a tradition of the Royal Academy of Political Science! The Heavenly Sword! I've been feeling a little skeptical of your ignorant words and actions lately, and now you've proven yourself worthy of my adversary!"

With all this praise, the pocket of wisdom was jumping around so intensely, well, it still felt like my lifespan had been extended by about ten years.
