\chapter{Training Arc (5)}

Dealing with your body was never easy.

Even if you think it should move like this in your head, if you look at it from a third party's perspective, it just looks strange and creaky, different from what you thought.

Moreover, humans have a serious defect in feeling comfortable in bad posture.

Unless someone forces the head and torso into the most ideal posture, the most ideal habits for the joints and body measurements.

It was necessary to constantly revise and repeat the created attitude to become accustomed to it.

Then, when bad habits were formed in the womb, or when the body grows or muscles were built, the difficult challenge of having to change the habits that have already been formed was faced.

This was also the strength of the famous family.

With the data accumulated over a long period of time, you can quickly provide the best form for your disciple.

Also, the four-person system called Hangryeol, where the upper class teaches the lower class, allows for customized instruction one-on-one, one-to-few, or even few-to-one (this was why you must become a beloved disciple).

As a bonus, when disciples who have been taught and grown in this way reach the level of elders or elders, they will already have a certain understanding of their own educational policy.

What this means is.

This means that the officials who entered the Yizheng Martial Study Academy had never received education from such a prestigious school.

Hmm. Everyone has so many bad habits… … .

Even though I intentionally named the herb "Gang-Yak-Yak" to make it easy to understand, everyone was overflowing with enthusiasm, or maybe I was putting too much strength into my body.

"Attention, Zhonglu Sword! Swinging it hard isn't enough! Maintain proper posture and understand the fluid flow of each sword strike! Boo-boo-boo-boo! Don't you think something's off!? Boo-boo! Boong-boo! Two beats, Boo-boo! Boong-boo-boo! Repeat!"

"Boohoo! Boom Boom!" "Boohoo! Boom Boom!"

"Is that all you can hear? You can almost hear ants crawling in front of the instructor!"

"Boohoo!! Boong boong!!" "Boohoo!!! Boong boong!!!"

"Quick Sword, pay attention! Same here! Shake, shake, shake! Is this the world's best swinging contest just because you're fast!? Strong, weak, weak, strong, weak, I understand! I repeat! Shaak! Shake, shake!"

"Shaaaak!! Shake shake!!!" "Shaaaak!! Shake shake!!!"

"Euro Sword!"

"Yes!!!!" "Yep!!!!"

"Good answer! I understand the difficulty of swordsmanship! I think it's not about swinging, but about drawing a line with the sword and connecting it, protecting myself while leaving room in my wrists, and thrusting the sword! Swordsman, no, Assistant Nan-Gong, forward!"

With the middle sword, you can roughly understand the movement of the center of gravity, and with the quick sword, you can roughly understand the sword's strike based on its speed, but with the euro sword, it's difficult to understand without receiving the opponent's sword.

So, Qing shows an example of a duel.

"Like this, with your wrists and forearms relaxed! Position yourself right where you can block the enemy's sword!"

Bang! The sound of wooden swords clashing sharply.

"Strong, weak, weak. Be more relaxed on the strong side, and be more aggressive on the weak side! Assistant Nan-Gong, come in! Like this, slap! Slap!"

Knock. Knock!

The strong softness actually makes the swords clash less loudly, while the somewhat aggressive clash of the three-strike strike was shallow but loud.

"Do you understand!? Chuuuk, chuuk!"

"Chuu …

It was a theory of beats that I had unconsciously brought up out of frustration, but it was also a very easy-to-understand theory of swordsmanship.

Because if you want to swing your sword to the beat, you have to use less strength in fast beats.

So, in the principal's case, who had been using only strong attacks and wasting his strength, a rather plausible sound began to resonate through the strong and weak attacks.

"Oh, that's great! I remember the details!"

"Thank you so much!!"

The officials of the Yizheng Martial Study Hall were neither involuntary conscripts nor passive students forced into service by national laws such as compulsory education. (Of course, some were not.)

Each of them had dreams of great success, and they were passionate warriors who came from far away to this foreign land, burning with their passion for learning. How could their enthusiasm be anything?

Especially, I felt like I was learning from the easy introduction that the Half Sword Swordsmanship Club had put a lot of effort into, so I swung my sword with excitement without even realizing how difficult it was, and I answered the instructor's words with a loud voice.

As time goes by, you don't even realize it, and before you know it, you realize it's lunch time when you hear the sound of the temple bell ringing.

"Eating was also part of training. The benefits of eating well build your body and muscles, so there's no need to explain them. Is that right?"

"Yes!!" "That's right!!"

"Well then, officials, enjoy your meal."

"Yep!!" "Enjoy your meal, Instructor!!" "Okay!!" "I'm hungry!!"

How light it would be to go out to eat after a rewarding training session.

As everyone rushes out in excitement, as if they were about to fly, Qing and his friends look at each other and snicker with evil smiles.

Yes, enjoy your meal.

It's something you should eat deliciously…

The real training starts now.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The diet of the officials focuses on providing meat and rice very efficiently.

What does efficient mean?

Mass cooking using cheap ingredients!

And as with any efficient diet, it's not exactly delicious.

If it was the home of Qing, there may be an advantage in that it has the unique taste of mass-cooked food, thanks to the continuous improvement of varieties and the increase in the low price of ingredients, and the combination of advanced spices created by learned people.

Spices from Zhongyuan were expensive, and cheap ingredients were bound to have flaws in taste.

Moreover, in the Chinese culinary world, mass cooking was considered a low-level job that only aspiring chefs take on.

If you were a master, you must hold an iron pot and devote yourself to just one table. Making a large portion and selling it was a small meal that only street vendors do.

wherefore.

"Ha. I don't know if this was food, or, umm, pork porridge. Mumm, umm, no, even pigs wouldn't eat this kind of garbage."

A face with a guilty expression, and a posture that seemed somehow elegant even though they were sitting in the same chair.

It was the noble prince of Sacheon, Wan Talur.

The eyes of his crew members were fixed on him.

Why was that kid making a fuss while eating?

Well, I'm hungry.

In Qing's hometown, hunger was a side dish.

In Zhongyuan, there was a saying that when you were hungry, all food tastes like meat.

This was a passage that shows how much the people of Zhongyuan have loved meat since ancient times.

By the way, it was said that even Confucius, who was considered the greatest sage in Zhongyuan, would flip the table over if there was no meat on the table, and his picky wife even ran away because of his nagging.

Of course, Confucius's wife was not guilty.

Confucius actually flipped the table if the side dishes were not neatly arranged in a square or perfectly round shape, citing the need to purify the mind. He flipped the table again if there was even a single dish that did not use the finest ingredients, the most expensive and fresh ingredients of that primitive era, saying that choosing the best was good for the body. He even flipped the table again if the soy sauce that went with each meat and dish did not match the appropriate soy sauce.

He protected his heart and reached adulthood, and maintained his health to the point of living to the age of seventy, which was the longest lifespan of his time, but in the end, he was unable to protect his wife.

In the end, although Confucius's virtues and words were praised, there were many who criticized him at the dinner table.

Then he should have prepared and eaten the food himself, but he only chose expensive, precious, and very elaborate meals to eat while serving his wife and disciples.

Anyway, the Sichuan nobleman Wan Talu starts to act like a Confucius, as if he wants to make up for it.

Of course, only in words.

While eating very well.

"It's truly a mountain vegetable dish. Mumble, mumble. The rice was bland and dry, and, um, the meat was so tough and chewy that I can't tell if it's pork or beef. The soy sauce was red and spicy, so it's better without it. Tsk tsk. The soup was so thick that I'd rather just drink the water. Gulp."

Parkjusanchae. A poorly made wild vegetable.

Bland and dry. Tasteless and dry.

A bitter taste, like eating a candle.

A saying that means licking dry bones, like licking dry bones, without any taste.

Hongbulgamjang. Amy, soy sauce was salty.

Yeosu pitcher. Water mixed with water. Meaning plain water.

As he was rambling and even writing letters, the expressions on the faces of the members of the first training group of the swordsmanship instructors sitting around the table became rotten.

What the hell was this kid doing, even writing text messages and talking nonsense.

Then either don't eat it or eat it like crazy.

People eat, but the food loses its flavor.

Even the noise and equipment that had been farthest away and unseen before looked at the truth with one mind and one purpose in mind.

"Damn it, you dare me to eat something like this? Aren't you some trash that even a dog wouldn't eat! I can't possibly eat this."

Suddenly, Wan Talu puts down his chopsticks and throws a fit of anger at Barak.

The crew's gaze turns to the empty rice bowl. "That's a total sham."

Then he leans back in his chair, puts one arm over the back of the chair, and speaks arrogantly, lifting his chin for no reason.

"Ha, you lowly creatures, do you even know what it's like? Hmm, right. You there, Chief. A nobleman, I think? You seem to have some decent swordsmanship. Well, then. Why don't you try changing your fate?"

A vertical line was engraved between the eyebrows of Yang Qi, the leader of the daily training group.

But Wan Talu only smiled a guilty smile.

"Ah, yes. Well, that's understandable, since you probably don't know who I am. But you know, if it were me, you'd listen to me right now. A man would naturally want to establish a family under his own name, wouldn't you? I'm the kind of person who can bestow such a blessing."

"Huh. What brings such a noble young master here?"

"This was all about gathering people. All the useful ones were already tied up in that sect or something, so even if I were to recruit some servants, I'd need someone truly talented."

"There was no work."

"Really? Then, don't regret it later."

Wan Talu says this and stands up, turning around.

"Where were you going? I have afternoon training—"

"Haha. With your humble title as a team leader, do you think you're some kind of superior? I'll take care of the afternoon training myself, so don't hold on to the precious person and just finish eating some dog meat."

No, what kind of bastard was that?

The veins on everyone's foreheads bulged, but that was it. Because they couldn't cross the Sichuan nobleman.

He really seems like he has something going for him.

In Zhongyuan, having a backer was a personal ability that could be proudly boasted of, so not messing with someone who seemed to have something was also a basic principle of conduct for the lower classes of the martial arts world.

Yang Qi quickly erased Wan Talu from his mind with these principles of conduct and spoke to his crew.

"Hmm. Everyone. We've got about thirty minutes left before afternoon training. Perhaps our group should head to the swordsmanship hall to review beforehand? Of course, if you're tired, you're welcome to take a short break."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The afternoon class begins with the sound of the bell.

The instructor's appearance a beat late was a consideration for the students.

If the instructor stays in his position, the officers will not be able to enjoy a proper break and will feel like they have to leave first.

The reason why Qing showed up half an hour late was because of this thoughtful attitude, and it was definitely not because he had eaten a huge lunch, then took a deep nap, woke up to the sound of the bell, and headed to the swordsmanship hall.

Seeing them neatly seated in groups even though they were not specifically trained in the rules, I can definitely tell that they were different because they entered voluntarily and even completed the test.

And so, Qing speaks the first words of the afternoon class to the distinguished officials.

"Trainee who was lying down under the Geumgang statue in the front yard of the school office after the meal, please come forward."

What's special was special.

What kind of kid was lying down and sleeping right in front of the school office, or rather, the principal's office? Huh? The principal was there, and the school administration, with its own right to expel students, was swarming around. How could they be so bold?

For reference, the word 'damdaehada' means 'dam' (large liver), and 'dae' means 'big liver', meaning that the liver was swollen.

That's what the officials were talking about.

There was murmuring about what kind of crazy person would cause an accident from the first day.

Qing slowly counted to ten inside her head.

\textit{Oh, you're not coming out? Well, I guess there's nothing I can do.}

"Wan Talu. Come forward."