\chapter{Training Arc (9)}

Qing looked at Weifeng again.

Did that bald, timid guy have any talent for handling kids?

Or, perhaps, the Shaolin Temple was the best not only in martial arts but also in early childhood education?

Qing didn't know, but he was actually the strongest.

There were many children abandoned at Shaolin Temple, and many families with difficult lives abandoned their children in hopes of seeking Buddha's mercy.

When Shaolin monks go out to beg for alms, such incidents occur frequently, and it was also common for them to return with orphaned children dying in their arms.

Even though they were among the pseudo-religious, they were monks who cannot turn away from someone who was dying right now.

The recognition and support of the entire Zhongyuan, also known as the Thousand-Year Shaolin, also comes from these merits.

They played tag, and someone caught someone, and someone caught someone, and then someone caught someone again, and so on. The childish, rambling, and bizarre story, with no order or theme, resonated from both sides.

I heard that tag was tag, but oh, isn't this the so-called air tag?

Why, he has to ride on that playground equipment that kills him if he steps on the sand, and then run away.

Are the way kids play the same in Zhongyuan or in my hometown?

Come to think of it, I wonder if kids these days were still playing around, but those 'kids these days' won't be born for several hundred years.

When I think about the kids running around, I think it wouldn't be so bad.

It's a kind of free-for-all. Overcoming obstacles.

Just adding some fun to it?

"Changming, you worked hard too. How was it?"

"He really doesn't listen. I think the kids will hate him."

"Hmm. That's what kids were like. But what's this new cuteness thing? Why do you talk like that?"

"I'm not pretending to be cute. Changming was cute. It's a well-known fact."

"Oh. Jang Myeong-ah? Is that right? Are you trying to act cute or not?

"That's not how you do it."

"Be grateful that you have something in both hands now. Don't forget that I am the rightful successor to Master's signature nuclear honey chestnut."

"That's why I brought Xiang'er too."

As if he had expected it, Chen Changming spreads his thumb and little finger and makes a gesture of measurement.

On the way to the restaurant with the child in both arms, the instructors who had also completed the Taoist and martial arts classes joined them.

"Oh, Sister. I was wondering if Xiang'er would come back. So you were keeping her?"

Kwon Beop Assistant Zhuge Lixian stretches out his arm and makes a gesture to receive Zhuge Hyang.

But when Zhuge Xiang shook his head in refusal, he blinked with a slightly shocked expression.

"Oh. Instructor."

At that moment, the kids on the left and right tapped their bells to signal for them to come down, and then bowed to the bald man who appeared late.

"Hello, instructor." "Hello."

It was the boy's instructor, Monk Weifeng.

The bald man looked startled at the sight of Qing, then quietly joined the furthest group with a "ahem ahem".

Well, it seems he still has some grudge from losing at the Jamryongbimuhoe. He's not a bald, petty person for nothing.

Considering how the kids were doing their belly bows, it seems like they're following along well.

Anyway, since Qing was confident that he would forgive even his enemies for a moment in front of delicious food, what does it matter?

The important thing was rice!

While eating, the instructors chat among themselves.

"Oh, Qing-ah. Peacock tax? That's amazing! These things crawl all over the place. Why didn't I know about this method sooner?"

"Don't be too harsh. It's best to do everything in moderation, making sure it doesn't go beyond the level of training."

Advice from martial arts instructor Yu Wook-ah continues.

"Then, if something goes wrong, it's easier to just quietly increase the intensity. Show a stern displeasure. Then, your disciples will subtly observe your every move and try to behave appropriately."

"Oh. But if you want to roll at low intensity, you'll have to hold on tight and use it for half a day."

So, during dinner, there was a series of sounds that would make the officials sad to hear.

For the novice instructor, Qing, it was also valuable information that became his flesh and blood.

The swordsman's schedule continues even in the evening.

"Instructor Nan-Gong here was an excellent teacher, surpassing even me in teaching. It's no exaggeration to say that I, too, learned the fundamentals from Assistant Nan-Gong."

Nan-Gong Shencai nods happily.

Qing, who only knew how to use the herb method and had no knowledge of swordsmanship theory, has now become a master of the Hwagyeong method and was showing off his tremendous swordsmanship.

Of course, it was truly rewarding-

"As a result, the instructor has surpassed even Assistant Instructor Nan-Gong, and he was a master of education who surpasses even the teachers through his teachings."

Nan-Gong Shencai's emotions faded a bit in the words that followed, but anyway.

So, at the swordsmanship school, Nan-Gong Shencai's swordsmanship class for absolute beginners, "You can do swordsmanship too" began.

The reason why Qing didn't teach the basics of forensic science directly was because he had another schedule.

"Instructor, did you enjoy your meal?"

The eyes of the Geomok Army sparkled.

Hmm. It's dazzling. It's burdensome.

Unlike the half-melted and sluggish attitude of the already heavily trained beginner swordsmanship class, Geomokgun was extremely lively.

Well, it was because Geomokgun, who took on the role of assistant quite naturally and subtly, was the one who was being manipulated rather than the one being manipulated.

"First, I'll explain the original form of the Five Paths Sword. It'll be better to first understand what form it ultimately takes."

"It's what I was hoping for."

After all, since Geomokgun was a swordsman who had reached the pinnacle of swordsmanship and already understood swordsmanship theory, it wasn't difficult to reduce his progress.

We conducted training for assistant instructors like that for about an hour.

After washing up and returning, he goes to find Ciyu, whom he had entrusted to Paengdae-san.

What kind of magic did Paengdaesan use? He was teaching my daughter, Ciyu, who was really stupid, how to write.

"Wow, the schedule was tighter than I thought. How's the mountain? Is it worth it? How about the Taoist?"

Paengdaesan gently shakes his head.

"Don't be ridiculous. This was truly a sight to behold. My sister was so upset. She completely turned the class upside down before it even started."

Because the women came out with full makeup on from the first class, they experienced the ruthlessness of the guerrilla warfare and the ruthlessness of the guerrilla warfare before the instructors and assistant instructors were even introduced.

What were you girls doing with your faces painted on, thinking that magic was funny? And you guys were just sitting there snickering about how good it is? You need to get your wits about you before you even learn magic. Everyone, get down on your knees right now. Let's do it.

That's what he actually said.

Ah, so that's the type of instructor at Choryo.

However, it was said that Choryeo did not express any such regret or displeasure at dinner.

Even if it wasn't makeup, wouldn't the result have been the same?

Peng Chaolei had firmly urged Qing to take control of the government from the beginning so that there would be no more trouble later.

For reference, there were roughly three generations of male and female students in the Taoist school.

The sword was not originally a weapon suitable for women, as the weapon itself was heavy and was used to maximize its destructive power through brute force.

Still, there were a lot of women?

It was obviously something strange.

But it wasn't strange to add the jade giraffe to that, because the admissions office had to filter and filter out a lot of people to minimize the number of people.

Everyone, it seems that even the women who originally wanted to learn swordsmanship have almost turned around, and I guess you can say that seeing you, you were also a symbol of wanting to learn martial arts.

Qing thinks, well, if she's going to change her major just to see a man's face, then she's probably just doing it wrong as a drone.

If we switch the genders, and say the man switches from swordsmanship to following the woman he loves, well.

But he's still a fool.

Qing, holding Ciyu in her arms and heading to her room, looks at the moon to roughly estimate the time.

Around 8 o'clock in the afternoon?

Qing feels proud again.

The time I started class after eating breakfast was around 7:00 AM, so it was a truly rewarding day, completely dedicated to nurturing my students.

… … What the heck! I'm a person too, a person!

Qing's eyes went dark!

The first reason why the Yizheng Martial Study Hall opens in the summer was because the days were getting longer.

The second thing to note was that there was no need to burn firewood, because if you do, the area around the State Council Hall will become a hill or a mountain instead of a forest.

This, every day? Without missing a single day?

Only then did Qing realize how merciful the creator god of the Western regions was and how much he loved his creation.

At least your god worked six days and rested one day. How merciful of a divine being he was, to give the rascals a day to play under the pretense of worship.

The part about burning in a pit of fire forever seems a bit merciless, but whatever.

Compared to that, what about Zhongyuan?

Hmm…….

If only there was a place where I could play alone like in my hometown, I would at least try to cut down on my sleep.

If you don't have time, just don't sleep.

Isn't that simple?

However, the primitive and uncivilized play culture of ancient times was so boring that it was truly impossible to play alone.

The soul of Qing one was so used to the stimulation of the future that it was difficult to write alone, even if it was just playing with eggs, so the threshold for fun was seriously high.

Well, it worked.

I overlooked the diligence of the people of Zhongyuan… … .

But what if I regret it now?

Because I am a person who cannot afford to be idle, I feel a sense of useless responsibility that was becoming infinitely heavy for people who were friendly to me.

Qing clenched his fist.

All that's left was to really go out, go out.

From the first day of school, Qing dreamed of going out.

There were still twenty days left until departure.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

I desperately need to go out and take a vacation, but that doesn't mean I have any free time.

So the curriculum continues to progress.

After changing the training group for Jungkwaiyu, we practiced, had lunch, and had a quick snack.

Since the eggs were already fully hatched, one round of the three warm-up exercises was enough to recover and prepare them again.

And then the sparring continues and ends.

The beginners were staggering around with their bodies drooping for about half an hour under the guidance of Nan-Gong Shencai.

When Qing teaches the Five Paths Sword Technique to the ambitious Geomokgun, an early summer night arrives.

I went to find Ciyu, played with her for a bit, and then went to sleep.

And the morning of the sixth day.

After morning roll call, the trainees who were returning to their dormitories to eat breakfast and prepare to head to the principal's office suddenly stopped in their tracks.

Well, it's because of the person standing in the yard of the inn.

"Guardians, I am very disappointed in this instructor."

No, why again? It's disappointing again. The officials just swallowed their sighs.

It was a Qing raid on the official residence.

The training room smelled so musty, and no matter how much I thought about it, I wondered if these guys even washed their clothes properly, let alone wore them.

"The instructor clearly said to stick to the basics. Wash daily to keep your body clean, don't wear dirty clothes, and wash them to keep them clean. Are these basics or not?"

"It's basic!" "It's basic!"

"Did the instructor tell you not to rest? Or did he tell you to light incense and decorate each room? Is it really that hard to just stick to the basics?"

"No!" No!!"

But the officials feel a little wronged.

By the time class was over, I was already exhausted, covered in bruises, and every part of my body ached.

On the other hand, wouldn't the limbs be as heavy as water-soaked cotton, and if you lay down anywhere, wouldn't you be in a state where you could sleep soundly even on a bed of thorns?

Qing was excited by such a sight.

"The instructor isn't doing this to harass the disciples. Regardless of the swordsman's dignity, cleanliness was a part of training, fostering a healthy body and orderliness was a part of training, fostering a healthy mind. Should we neglect our training?"

"No!" "No!"

"If you know, get moving right away! Clean up! Sweep the dust, sweep the floor, and take out the beds and let them dry in the sun. Get going!"

"Do it!" "Okay!"

As someone who was cleaning in Qingdo County, I didn't know what it meant, so I just wanted to take it easy, but I wondered why it was so bothersome and annoying, and why I couldn't stand to see my subordinates having fun.

In fact, cleaning was a major problem.

There was a disturbance last night, and an emergency was declared due to bedbugs in the Taoist training dormitory.

Surprisingly, the bedbugs were found not in the men's quarters but in the women's room, and the scene was truly horrific.

So what?

I tried not to touch the dormitory as a human being, but if it wasn't midnight, I would have to force it to be purified.

And so, another day begins at the State Affairs Office.