\chapter{Training Arc (1)}

Yizheng Martial Study Hall was a huge estate hidden in the mountains.

It was a manor built like a maze, with walls built inside the walls, following the unique style of manor houses in Zhongyuan.

According to one theory, the people of Zhongyuan formed communities in villages and waged war, and this complex form was developed for the purpose of water defense.

A unique feature of the manor style was the door for passage.

The passageway, which anyone can enter and exit, was a round, doorless passageway.

Of course, servants were an exception to this rule, and the small side doors through which servants enter and exit were designed to be as out of sight as possible.

It means that if there was a gate in the wall, you must ask permission to enter.

And the size of the gate symbolizes the authority of the area.

So, what was the emotion when the officials faced the grand gate with the magnificent signboard of the Kendo Hall, the swordsmanship training center facing north?

My heart swelled with pride, and I realized that I had finally registered with the academy, that it was my first day as a member of the Jeongpa Wulin Alliance.

The chest of the person who had equipped the equipment of Eomchang was especially magnificent, because he gave up the good position of successor to the Sapa who had taken over the city and escaped.

In Zhongyuan, being born was not a simple family register thing that could be given up on one's own, but rather a huge stigma that had to be endured for the rest of one's life.

Nevertheless, the feeling of stepping foot into the Legislative and Military Academy with such confidence was indescribable…

-Go! The witch doctor! What kind of atrocity was this in the sacred Kendo Hall!

-Witchcraft? That's an exaggeration.

It was a loud voice coming from inside the kendo hall.

His roommate, Jang Sam, nudges Jang Bi-hu with his elbow.

"Oh, I guess there's a fight."

After equipping him, Jang Bi-hu answered.

"Let's go."

There was no one in Zhongyuan who refuses to watch a fight.

The two of them rushed in, and surely the vast training grounds of the kendo hall were already surrounded by enthusiastic observers.

When Jangbi-hu quickly joined him, he saw two men facing each other inside.

One was a young man named Cai Shengxia, who broke a test tube but was subsequently beaten by Heavenly Blossom Sword.

And one more.

"Hmm. Getting into a fight with the Sword King from day one. That guy's a real deal."

Zhang Feihou said, clicking his tongue.

The person frowning across from Cai Shengxia was none other than Nan-Gong Shin-jae, the sogeom king widely known as the Sogaju of the Nan-Gong family.

"I know that his martial arts skills were great, but he needs to know how to behave better…"

He said it as if he felt sorry for Jang Bi-hu.

Then, Zhang San answers with a suspicious, meaningful smile through his narrow eyes.

"If the opponent was unknown, it's okay to act casually and start a fight. But if the opponent was a celebrity, shouldn't we treat them with respect, even if it means inventing something new? Perhaps Azure Dragonhyeop was a brash person who doesn't care about fame or influence. So, Hyeongje shouldn't speak carelessly without knowing the context."

Jangbi-hoo felt a little embarrassed by the well-known but not put into practice theory.

It might have been even more embarrassing if it weren't for the extremely suspicious expression on Jang Sam's face.

But somehow, to be honest, it seems like the expression on his face was hiding some kind of hidden agenda.

Besides, his name was Jangsam.

The pseudonym I use when I don't want to reveal my name was Jang-sam, so it's a declaration that I won't go out of my way to hide my name.

Jangbi-hu, who was feeling a little embarrassed, asked the officer who was watching first about the situation to change the subject.

"What's going on?"

"Qing Dragon Hero challenged the Sword King to a duel. After a few rounds, the Sword King grew angry and declared it a sorcery. Qing Dragon Hero countered, saying that if skill alone doesn't cut it, then it's all sorcery."

"No, did you really say that? Didn't you mean to fight?"

"The Sword King really said that, and Qing Dragon Hero was polite, but it did mean that. Will we have a proper showdown? But no matter how great my martial arts are, I can't stand up to the Sword King. No, with such divine skills, why bother coming all the way here…"

It seems like it was a somewhat biased judgment.

Well, if it's the next head of the Nan-Gong family, a arrogant country warrior who has mastered a new art, it's clear whose side you should take.

That was when.

-What's the fuss so early in the morning!?

A clear voice that quickly enters my ear.

Despite the loud shouts, the voice was so beautiful that it was almost strange to hear it as it was not rough at all.

It was a sound that anyone who heard it once would remember the owner of the voice, so all the officials turned their heads at once.

The Thousand Flower Sword has appeared!

Qing was speechless.

First class, starting from the beginning where we haven't even been introduced yet, what kind of mess was this?

But, well, it turned out well, right?

"Nan-Gong Shencai, please lie down and stretch out."

"Hmm……"

Nan-Gong Shencai had a displeased expression, but he didn't say anything and just lay down obediently.

Well, Nan-Gong Shencai was just a strange person, he was definitely not stupid.

She didn't call him Sword Friend, but Nan-Gong Shencai, the disciple. That meant she was going to treat him as one of the disciples. He also realized if he didn't want to undermine the instructor's authority from the first lesson, he had to follow her obediently.

And through this, she also expressed her intention to treat everyone equally, including the Sword King, so he understood that even if he had something to say, now was the time to hold back and play along.

Qing took out something from her waist.

It was too big to be called a flute, and it was a very ugly thing, dark and lumpy.

The mere fact that he had created a flute from iron was a great achievement, worthy of praise from the world's ironsmiths. Even though it may have a rough appearance and an uneven surface, it does not in the least overshadow his brilliant achievement.

But what if someone you don't know sees it?

'Why do you carry around something like that even when you're not playing a flute?'

'Are you carrying it around to beat people up?'

And soon that doubt turns into certainty.

'Oh, it's clear that she's carrying it around to beat people up!'

Bam!! The terrifying sound that wakes you up in the morning.

"Ugh!"

Even the world's greatest Nan-Gong Shencai was completely out of his mind after being hit by a nuclear explosion that hit his buttocks. He jumped out as if he was being launched while still lying face down, rubbing his buttocks at high speed and imitating a jiangshi.

"Hoooo……."

Qing exhaled as if she had used a great technique.

Nuclear fusion was a skill that requires profound concentration. While her Master used it with great ease and naturalness, like picking up a side dish, Qing must be very careful to control her strength so as not to injure his muscles and bones, and must also be extremely focused.

"Gentlemen, there are countless martial arts in the world, and they are also overflowing with mysterious and incomprehensible martial arts. Therefore, you should not so carelessly dismiss others' martial arts as sorcery. Do you understand?"

"Yep!" "Okay!" "Okay!"

The answers were not yet unified, but they burst out with a loudness that matches their volume.

Of course, he came to his senses after seeing a terrifying blow that made even the most skilled warrior lose face and run around like he was possessed.

Only then did Nan-Gong Shencai, who had recovered from the shock and fear, look at Qing with slightly resentful eyes.

Ahem.

"However, let me make an excuse. Young Expert Nan-Gong here is the teaching assistant who will be assisting you in the progress of this course. He was a great help in the last swordsmanship course and also participated in the planning of the current course."

Qing continued speaking.

"From now on, within this swordsmanship course, all martial arts other than swordsmanship will be treated as sorcery. Assistant Nan-Gong have known this in advance, so it seems he's a bit impatient."

From the officials, there were murmurs like, 'Ah, so that's what happened'.

Even if he was the Young Sword King, how could he carelessly accused others of sorcery? There were no rumors of such a person, so it was somehow strange.

Of course, Nan-Gong Shencai was sincere.

Cai Sengxia was waving his sword and dancing around, so from Nan-Gong Shencai's perspective, it was neither swordsmanship nor dancing, but a terrible hybrid, a true sorcery.

Anyway.

Qing flashed the Fushen-di.

"This flute is called the Aegyo Bong. It is meant to be a disciplinary instrument, filled with the love of a strict teacher. It will be used to deliver a harsh lesson to disciples who make mistakes, with a heavy heart."

Aegyo Bong, if I had to explain it, was a love stick.

A cold sweat ran down the backs of the officials.

It was a moment when confidence turned into understanding.

'You really brought this to beat people up!'

And at that moment, Qing's momentum changed.

In addition to the unmanned nature of Hwagyeong, there was also the aura of murderous intent emanating from the master of a thousand lives.

It gives a chilling fear to third-rate, second-rate, and first-rate unmanned appealers, and to the most advanced unmanned appealers, it gives a tremendous sense of intimidation that was as great as they know.

A son-in-law who stops breathing in an instant.

It was fortunate that she was wearing veil, but if their eyes had even met, it seemed like a disaster could have occurred, causing the faint-hearted to collapse.

"Well, that's it. From now on, I will assume your duties as instructor. That means I'll throw away the courtesy of being a man to man. Anyone who's dissatisfied, leave immediately. From now on, there will be no mid-course withdrawals from my classes."

I thought it was something unusual, but no one really wanted to leave.

Of course, the Office of the State Councilor was the opportunity that officials dream of. No one would enter the office just to relax.

"Assistant Instructor Nan-Gong, Assistant Instructor Murong, Assistant Instructor Changbin, please step forward. These three are the assistant instructors who will assist you in your training."

Three men came forward and took their places on either side of Qing.

"Before we begin the lesson, I will first explain the rules of this course. Repeat after me! All martial arts except swordsmanship are sorcery!"

"All martial arts except swordsmanship are sorcery!"

"Is this all you can say?"

"All martial arts!!! Except swordsmanship!!! Are sorcery!!!"

"It is the best weapon among all weapons, and it is a weapon that is far superior to any other weapon in the world!"

"It is the best weapon among all weapons, and it is a weapon that is far superior to any other weapon in the world!!"

"Dao is a piece of trash that can only strike down!"

"Dao is a piece of trash that can only strike down!!!"

"Spear is a low-quality weapon used only by commoners who lack Inner Qi!"

"Spear is a low-quality weapon used only by commoners who lack Inner Qi!!!"

"Kwon is a weapon that is too shameful to even mention!"

"Kwon is a weapon that is too shameful to even mention!!!"

Nan-Gong Shencai's voice was unusually sharp, so why was he yelling so earnestly?

"Of course, those words are horrifying and terrifying thoughts that should never be said. But right now, you are all students of the Swordsmanship course at the Yizheng Martial Study Hall, and your time in school is to be solely dedicated to swordsmanship. Therefore, while you're immersed in your studies, you must dedicate yourself solely to swordsmanship with this mindset."

Therefore, the use of sorcery was prohibited in the Sacred Swordsmanship Hall, and anyone who uses it will receive a rather harsh lesson.

In the part where the lesson was sharp, the gaze of the officials was fixed on the copycat.

"Rule number two! The use of Inner Qi during class is prohibited until the instructor gives permission!"

Then there was a commotion. That's understandable.

How can you practice swordsmanship without using your internal energy? Wasn't the original importance of external energy in harmony with internal energy?

There were also some people who didn't stop at just being loud.

"Instructor. This is Sword Jade-lady of Sword Pavillion. The use of Inner Qi while practicing the swordsmanship is crucial. If you don't utilize Inner Qi, you'll just end up with a form that looks good—"

"Stop."

Qing interrupted the words of Sword Jade-lady.

"I haven't explained all the rules yet, so I will let it slide this time. If you have any suggestions for the instructors, please raise your hand first and ask for permission."

At that, Geomok-gun looked slightly indignant, but quietly raised his hand and asked to speak.

But Qing shook her head.

"I understand what Trainee meant. However, since this Instructor had also benefited greatly from this training, I will not accept your suggestions."

Nan-Gong Shencai nodded happily.

Sword Jade-lady seemed to think for a moment, then bowed and stepped back.

He said it was a huge help. It was his brother's training when he first entered the swordsmanship world, but after he gained control of his internal energy, he'd always practiced alongside swordsmanship. It seems like a new training method he'd never tried before was surprisingly helpful. So, of course, he had no complaints.

"Depending on your attitude, this instructor can become either a god or a devil. And that attitude was fundamental. Just the basics. You just need stick to the basics."

Qing brought up the basic theory.

It was the most difficult thing in the world to keep, that very basic thing.
