\chapter{Training Arc (8)}

The extremes of cruelty seemed to test the limits of human endurance. The faces of the officials were flushed, some on the verge of tears, others on the verge of screaming, and those who had already been tamed by the monks wore a look of resignation.

Pass the second Mabo and the second Waho.

And the second peacock tax.

I wonder if they were trying to claim that it was a posture where the bird shakes its legs and spreads its tail feathers, as the name suggests.

"One. Two. Three. Four. Again. One, two…"

The officials felt a deep sense of absurdity at the calm voice that recited numbers even though it seemed like they were about to die.

What was the meaning of this series of painful movements?

The pain was so intense that it felt like my back was stuck under a thousand-pound rock, I wished it would just be cut off. Whoever created this exercise, aah, curse, curse.

Save me, save me… … .

Each official was overcome by certain emotions depending on their personality.

The passive ones felt despair and sadness mixed together according to their personality, while the more enterprising ones began to feel anger, big or small, depending on their personality.

So the moment someone crossed the threshold, it was my turn to react violently, depending on my emotions.

In the military camp of Qing's hometown, the trainees were already completely psychologically suppressed, so they would usually burst into tears of despair and sadness.

Currently, there was one person in the swordsmanship hall with the lowest threshold for differentiation.

"Eww! What the hell was this!"

Hwaruk! Flames rise from the principal's office.

The surrounding officials, startled by this, jumped up, but as they tried to do so, their legs and backs gave out, and they began to crawl and drag themselves away, shouting urgently.

"Fire, fire!" "Instructor, Che Yaohong is burning!" "Fire, fire, it's possessed!"

Qingdo was surprised.

What is it? Why there's a fire all of a sudden?

And then, realizing that the figure engulfed in flames, the one who was stoking the flames, was none other than the conspiratorial woman Che Yaohong, he thought, "Hmm, what am I? Am I the source of a fiery rage?" Didn't I clearly have a fire this morning?

If it's a fiery anger, it should bring peace like a river, right?

There was someone who took action before Qing.

"Miss Chang, overcome it! I will help you!"

Before we knew it, Cai Shengxia, Azure Dragon Dancer, was creating a strong wind by following the rhythm of his movements.

Qing's expression suddenly distorted.

\textit{No, he's just sitting there blowing on someone who's on fire. Isn't this kid fanning the flames of a burning house?}

Qing's Fushen-di cuts through the air.

The same trajectory was drawn by the same dark, gloomy, iron-colored, rainbow that stretches on and on.

Bam!

"Ugh!"

Cai Shengxia held his head and rolled on the floor.

It was an inevitable, instinctive reaction.

It's like my head was split in half, so I grab it with my hand to keep it from splitting open, an instinctive response that I can't resist.

The strong wind at the fire scene cut off the oxygen supply in one room, and Qing turned around.

Hmm. Fire.

Honestly, I'm a bit like that too.

No matter how much of an expert you are, if you start a fire, you will still get burned.

It was the limit of a living being made of flesh.

But Qing was an instructor.

As the person in charge of this place, there was no time to hesitate, so regardless of whether it would work or not, I quickly deployed the technique while wrapping my body in the dizzying coldness of the Ice White God's Art.

Che Yaohong was still burning.

"Do you think I came here to do this!? You're a country girl! Even if you ignore me!"

"Che Yaohong's official residence!"

Calling someone by their first and last name together has the effect of bringing them back to their senses a little.

Che Yaohong looks at him with a start.

Before he knew it, two pure white arms, covered in frost, stretched out towards Che Yaohong's arms with a strange softness.

The season of Shinto, Muyeongshinsu.

Her thin, extraordinarily long and delicate fingers sink into Che Yaohong's clenched fist like water.

An irresistible, soft flow that slips through your fingers.

Soon, both hands were clasped tightly together, and a chilling cold air was felt directly on my skin.

A flash of reason returns to Che Yaohong's shrunken eyes.

"Instructor? I'm in danger, I can't control my anger—"

"Oh, anger management issues? It's okay."

Just as power creates light, fire creates an upward current, and as Qing cotton flutters and rises, a beauty that was roughly the most beautiful in the world was clearly revealed beneath it.

A rather gentle smile on that face.

Qing continued speaking with a gentle expression.

"Then you just need to learn how to control your anger."

"Huh? What-"

Since ancient times, there has been only one way to change anger management disorder into anger management ability.

Power! More power! Violence! More violence!

"Wow."

Ximen Qingryu Reader's Secret, Finger Jury.

A fearsome minority of the …

And the evil power of Qing was the strongest power since the beginning of mankind, and it was Ximen Qing's ultimate skill to tighten the opponent's fingers with the world's strongest fingers and the world's strongest evil power.

"100 million."

If it hurts too much, you can't even scream.

Che Yaohong's waist bent like a bow.

My hands were clenched in a fist, trying to shake off the foreign substance that has lodged between my fingers and was causing me terrible pain.

Anyone who has experienced it knows that fingers that were jammed tightly together will never come free.

Soon, Che Yaohong's eyes shot up into the dark sky, revealing the whites of his eyes, and the flames disappeared from his entire body as if he was claiming that nothing had happened.

What if anger arises from a trivial pain?

Just cool it down with the overwhelming pain!

"Che Yaohong's official residence. Are you alright?"

"Heo-eop, me, mu, what."

Che Yaohong came to his senses.

What was it? I felt like I was in excruciating pain, a terrible agony that left my mind blank and unable to think of anything.

But all that was visible were large blue eyes, filled with worry, as the cotton thread was turned over the top of the hat.

"ah?"

Che Yaohong felt a burning sensation rising from his head - a single ray of flame actually rose from the crown of his head - and he quickly lowered his head.

Then what you see were hands, two hands clasped tightly together, fingers intertwined, two hands clasped together as if they will never let go.

That pleasant coolness that seems to cool down the boiling blood-

Che Yaohong, who had always hidden his skin because of his martial arts skills, was more vulnerable to physical contact than anyone else in the world.

"Are you alright? Is Che Yaohong Guando?"

"I'm okay, I'm okay."

"Do you think it's going to catch fire again? Can you control it?"

"Because I can, give me your hand, your hand…"

I have a serious premonition that I might have to let go.

When we hold hands, for some reason my heart starts beating wildly as if it's going to explode, and before I know it, I'm covered in a cold sweat, my heart was pounding, and at the same time, I feel dizzy, as if my whole body was falling.

What was this, what was this feeling… …? Me.

Of course, the answer was fear.

Because during Qing's first official ceremony, he suffered the pain of losing consciousness from his unique ultimate skill, the finger thrust.

Subconsciously, I was still warning myself that my body was in danger, that the figure before me was nothing more than a vicious torture device in human form, that if it wanted to, it could crush my fingers alive and turn them into flesh, or even tear them out of my palm!

"Che Yaohong Guan Dao. Is it difficult to control the fire?"

"Well, when I get emotional, when I get angry, I can't control myself without realizing it…"

Qing smiled and thought about it.

So you're complaining of intermittent explosive disorder?

There were countless people in the world who claim to have intermittent explosive disorder, but in reality, ten out of ten were fake.

Because even in Qing's hometown, anyone who couldn't truly control their anger would have been in prison long ago, let alone in the martial arts world where people don't speak out, let alone use their swords.

Because he's already burning in the afterlife across the Jordan River. He's probably burning fiercely, both literally and metaphorically.

"If you feel like you're about to lash out again, call the instructor without delay. Understood?"

"Oh, I see, yes……"

"Then, the Che Yaohong official too?"

"Huh? No, really?"

"I'll lie down again. I'll finish what I was doing."

I'm finishing what I was doing.

Che Yaohong's face turned black and dead.

----

There was a brief commotion, though?

There were no casualties as the fire was successfully suppressed early.

Fortunately, there were no embers left, and Che Yaohong did not catch fire again.

However, with my superhuman hearing, I could hear him muttering curses repeatedly.

That's something I can overlook, even if it's not Che Yaohong, there were a lot of curses coming from all over the place.

The original free-range arm technique was supposed to be effective, so it means that it was effective.

Rather, I would say it was praise and compliments.

Thanks to this, the sparring class that followed was also very successful.

Because all the major muscles in the arms, legs, waist, stomach, and chest were toned, the muscles were limp.

When you apply force to a specific muscle, a stabbing pain immediately follows, so you naturally swing the sword in the least painful position.

Thanks to this, the level of swordsmanship also increased significantly.

Since there were many people there who were not familiar with sparring, the Euro Sword training group, which was on the defensive, was repeatedly beaten.

But I heard there were no casualties.

It can be said that the effectiveness of body stretching has been proven and even exceeded.

It works so well, I guess I can't help it.

It's really heartbreaking, and I really don't want to hurt my precious followers.

But sometimes there were times when I have to sacrifice my pain for the sake of others. Hate me if you want, but please remember this one sincerity, for the sake of all of you…

"Miss Ximen? You look happy."

"Huh? Me? No?"

"But you keep smiling and even humming. You look so refreshing."

"Oh, Miss Murong. You shouldn't slander someone like this."

"……?"

That was when.

"Unnie Gaga!"

"Oh, what's that voice!?"

Qing's head suddenly turns.

A very, very cute creature appears ahead!

Appearing with triple the cuteness!

It was Ziyue and Zhuge Xiang who were holding hands tightly on Chen Changming's left and right.

For reference, the cuteness score was one and a half for Zhugehyang, one for Ciyu, and half for Chen Changming, so it's three times the cuteness score in total.

Even though Ciyu was my daughter, I shouldn't be biased. Still, she's no match for Xiang'er.

Changming'er, Hmm, actually, half was too generous.

The reason the three appeared together was simple.

Because Chen Changming was in charge of the boys' department as an assistant teacher.

He applied for the forensic course and ended up being assigned to the juvenile department as an assistant instructor. He was deeply impressed by the way Monk Weifeng played with Ciyu.

I think you'll get along well with kids.

Well, to anyone who looks at Changming'er, who was so skinny, he looks like a child, um.

Meanwhile, the two little ones came running with their short legs and jumped up with quite a strong attitude.

However, it was too much to defeat Qing, and it was impossible for the two little ones to deal damage to the strongest and most powerful monster.

Qing, who was hugging Ciyu and ZhugeXiang from left to right, rubbed her round cheeks.

Looking left and right, what happiness!

"Is class over? How was it? Did that bald guy act mean?"

"It was fun." "Hehe, it was fun."

"Huh."

Both of their expressions were bright, to be exact, only Zhuge Xiang was bright, while Ja Yeo was somehow smiling gloomily.

To Ciyu, this was like a big smile, so it must have been really fun.

Really? Where did the youth self-discipline training with the reverse-current Se-su-gyeong go?