\chapter{Training Arc (4)}

The plan of Qing Dynasty was for the three training groups to learn the Zhonglu Sword, Kuailu Sword, and Yuru Sword at each stage, and then proceed with changing the techniques to cover all the way up to the eight-stage finishing.

In fact, it was not an efficient method.

Since several people were conducting three separate trainings, it was difficult to see them all at once.

Even if there were three assistants, each one will be assigned to a different person, and since there was only one person who was the best and he was not a great Jecheon Daeseong who can pull out body hair and use the clone technique, it was difficult to provide overall guidance.

Even if you teach them one at a time, in the order of Kang Kwai-yu, you still have to teach them all three anyway.

So why did you separate them anyway?

It was not for the purpose of dividing and ruling, as Sima Chunfeng admired.

The middle sword can be swung in the air.

The Kwailo Sword can also be swung in the air.

However, the Euro sword could not be swung in the air and had to be used in tandem with the sword.

Since it was a defensive technique aimed at self-defense, such as defense and spilling, inducing gaps and destroying balance, it can only be properly embodied by mixing it with a sword against a person.

So, the Jung and Kwailo swords should be trained together by taking turns sparring with the Euro swords.

However, in this case, the Euro Sword team would have to take turns fighting the two training groups, which would make for a very difficult and arduous schedule.

Qing had many thoughts on this as well.

Are you here to play? You won't do it if it's hard and tiring?

You just have to repeat yourself and suffer, you know.

The art of softness was originally evaluated as being half a weight class higher, so it must be difficult and hard, not easy, right?

It was a deep thought of Qing.

Just be tough. It's tough to begin with.

"Assistant Changbin will take charge of the middle class, Assistant Moyong will take charge of the quick class, and Assistant Nan-Gong will take charge of the euro class."

It was more reassuring to have Nan-Gong Shencai take on the most difficult part.

The Mo Yong family was famous for their quick swordsmanship, so teaching them how to use the sword would be perfect.

It's a bit of a shame that Changbin's achievements were so poor, but I think we can take care of that by raising Geom So-jeo well and having her join the teaching staff.

So, the real class begins!

- As soon as he did that, one of the officials suddenly blocked Qing's path. Then he raised his hand and asked to speak.

I wonder if there's any reason to raise your hand when it's right in front of you, but whatever.

"Geomokgun official map."

"Yes, Instructor. What should I do?"

It was a black jade army that has come out wearing a cotton turban that hangs on the ears and covers the lower part of the head, and looks like it was not from Zhongyuan but from India or Persia.

The large oval eyes, pointed tail, and unusually large pupils give off a somewhat sinister impression.

The expression was so proud that it looks like a cat that would scratch and throw a tantrum if you prodded it, but the look in its eyes was like a puppy wagging its tail.

It seems to be spewing out diamond-shaped light dots?

Hmm. Dog and cat. Just dog and cat… … .

"First, join the group and proceed."

Then, Geomokgun's shoulders slumped.

Normally, I would have wondered why she was doing this, but somehow, thinking of her as a female version of Geomchi, a female Geomchi, I think she probably wanted to learn herbalism directly from me.

In fact, when you reach the peak, you were still a lowly person, but it may be natural for a person not to want to train with imitators who were below the peak.

But the curriculum was supposed to be used for everyone, and just because there's a genius in the class, the teacher can't give one-on-one tutoring during class.

"Starting today, after work and dinner, I'll be personally training for about an hour to fulfill my duties as an assistant instructor. Of course, it's not mandatory, so you can refuse, Hmm."

Qing's words were cut off mid-sentence by the black jade army that was shooting out a diamond-shaped beam of light.

I know even without hearing the answer.

"Thank you, Instructor."

And then, it was the Geomok Army who bowed and retreated with a haughty attitude.

Anyone can see that his steps were so light.

Hmm. It's really easy to understand… … .

Again, the real class begins!

In fact, the teaching of the herbivore has already been decided by the assistants, so there was no need for Qing to intervene further.

They just walk around and pat down anyone who catches their eye.

"Made the pipe, spread your legs wider and don't turn your waist. More, more, stop."

"Hayatu Kwando, shoulders were out. Lock your shoulder blades and open your chest."

"Innkeeper, just now, the posture, um, like this, your elbows shouldn't be fully extended."

It was a good thing I brought the copy.

How convenient it was to just push and pull with a flute without having to touch it.

Qing, who was trained in swordsmanship by Shinto, could handle even sharp blades as if they were his own hands, so it goes without saying that he could even handle a blunt flute.

Qing walks around and gives instructions on the posture of the officials.

In fact, I was wandering around Qingdo for a bit.

I've never performed the duties of a Qingdo instructor before, and this isn't even my first class.

The assistants will teach the beginner's course, and I will take care of the detailed corrections, but I wonder if this was the right way to do it.

However, the officials' thoughts were a bit different.

He comes and taps the flute, pushes, pulls, and adjusts the posture, and without fail, the wooden sword gains strength.

Indeed, was this the flute that brings enlightenment?

I'm thrilled again. I'm moved again!

Qing simply took a quick look and took into account the body type, the proportions of the upper and lower body, the length of the limbs, and the position of the joints to determine the appropriate pose.

I thought so too, didn't I?

In fact, it was an amazing collection of experiences engraved in my mind through countless real-life experiences.

The ability to see the enemy, read their stride by looking at their body and weapons, and roughly estimate the distance and the force they can exert when they bend their joints and extend their waist.

In this respect, Qing was a natural fighter.

Martial arts was a learning method that was eaten raw by turning the brain and eyes of the amazing window of the universe.

But the martial arts learned in this way were actually no different from giving you a good weapon in your hand.

Like a pistol in hand.

A skilled hunter might take twelve lives with a single magazine of twelve rounds, but someone might empty ten magazines and not only fail to kill, but also end up dying after inflicting only collateral damage.

The reason why there were unmanned units that were quick to achieve but weak in actual combat, or vice versa, was because there was a big difference in this area.

In this respect, there were not many people in the peaceful martial arts world who had fought as fiercely as Qing in life-or-death battles, not only among the same age group, but even among middle-aged warriors.

But Qing doesn't know how valuable my correction is.

So, was this right? Shouldn't we be discussing something more high-level and fundamental, like discussing the herd?

But the crowd was like that, most of them were third-rate or second-rate, so honestly, I think it would be better to build up your body by lifting weights and running and crawling to build up your stamina.

So, I guess it's not like there's any particular point to hold onto for those who were already learning well on their own.

So when Qing light approaches, everyone suddenly gains strength and their swordsmanship grows.

Look here! Look at me too! It was a desperate movement, desperate for attention.

So, while wandering, boom! boom! boom!

The sound of the sword cutting through the air was truly heavy, the sound of a great heavy sword.

It wasn't a sound that came from the first second.

One-shot diet was strong, weak, and weak.

Once hard, twice softly.

Even though it was a heavy sword, it was important to control the speed and aim accordingly, so it was made that way.

And even if it wasn't the Samro Sword, the strong and weak were popular characteristics of the first martial arts technique.

It's very good to kill the enemy with one blow.

If you hit the enemy and their posture was disrupted, you can quickly pursue and kill them, and if you miss, you can quickly follow up with a follow-up attack and hide their weakness.

But if you hit all three sword strikes with Gangganggang, then it wouldn't matter if it was a herbivore that was originally made with Gangganggang.

Boohoo! Boohoo! Boohoo!

The sharp sound of the wooden sword again.

Since these three sword strikes unfold separately, it cannot be considered a single, connected attack.

"Che Yaohong's official residence?"

The owner of the sound was the concubine Che Yaohong.

"Let's reduce the force in the second and third movements, um."

Qing looked at Che Yaohong and swallowed his words.

Even the way to hold the sword was awkward.

"Guan Do, have you ever held a sword before?"

"that is……"

"I am not reprimanding you. Please answer with peace of mind."

"……yes."

Well, I guess there's no reason to use a sword when there's good fire.

Of course, it'd be twice as cool if you used a sword, but the breath of flame! Flame Jade! Hmm, it's pretty cool.

A fire sword would be stronger than a fire fist.

Honestly, if you were to fight her, this witch would be much harder to deal with than Azure Dragon Dancer, because no matter how skilled you are, the fire was hot.

"By any chance, were there any other classes in this course that teach people how to hold a sword for the first time?"

He shouts my name here and there.

For those from third-rate backgrounds, swordsmanship was a luxury, and there were those who used Taoism or martial arts.

"Well. The person in question will receive basic forensic training after dinner. However, it's not mandatory, and those who wish to participate were free to do so. And the Che Yaohong sword was like this, with the arms here, a bit wider, and the fingers resting on the handle."

Oh, this was too much for a flute.

Qing reached out his hand.

Startled, Che Yaohong quickly pulls out his sword, but he cannot avoid the touch of the hand of the master of the Muyeongsinsu, Qing. Soon, an unusually cool, yet smooth skin gently grips the back of his hand.

Due to the nature of the main character, the body temperature of the hot Che Yaohong was high, so the cool water of the water magic was as cold as an ice rink.

It's like putting your hot, burning hands into cold water.

In that moment, a flame burst into flames in my hand without me even realizing it. This was why the successors of the Zhujakmun were wrapped tightly in their armor.

But that was only for a moment.

The sound of frost forming.

"Che Yaohong's official residence?"

"I'm sorry, I didn't know, I couldn't control this very well."

Qing nodded at him.

As long as you don't attack, it's fine.

If you add the extreme power of the Ice White God to the small magic that provides the diamond indestructible power below the elbow, you can freeze the flames that rise up for a moment.

"It's okay. Just relax your fingers."

It was only then that Che Yaohong realized that he was holding the sword so tightly that it was almost falling apart.

It had been so long since I'd felt human skin. The descendants of the Jujakmun were unable to control their flames during their initiation stages, so the clothing that tightly wrapped and concealed their entire bodies was both a fireproof garment to protect themselves and a restraint to protect others.

Qing's eyes went dark.

It's a total mess from the tip of the toes to the position of the head, so I'm trying to keep the posture, but, um, why was this guy so stiff?

When dancing, it's soft and swaying, but it creaks like some wooden doll.

Hmm. It'll probably take a lot more than I thought.

Did I take the instructor's job too lightly?

There were more than a few things to be lenient about when trying to arrest someone who has no basic knowledge of forensic science.

There were more than one or two people whose names I was calling out earlier, but if I start from scratch one by one, I won't be able to get an estimate.

"It won't work. Officials who are holding a sword for the first time, or who are unfamiliar with the sword, will be excluded to the rear. Could Sword Jade-lady help teach them?"

How to hold a sword, how to swing it, the basic posture and precautions, even the swordsman of the highest level, Lady Geom, could handle it.

If you have talent, you should use it. It's reliable! Geomokgun!

Oh, was this how it feels to be a professor accepting graduate students?

I feel so omnipotent!

Even though he hadn't even been promoted to assistant instructor, he was already being treated very frugally.
