\chapter{Training Arc (6)}

Actually, Qing was a little bit interested.

If only he had an ordinary face, I wouldn't have noticed. I don't know how he could lie down so confidently when his face was completely sold out during the entrance exam.

I heard that they were complaining all the time about the food being terrible even in the cafeteria. Well, that's because everyone in the EYizheng Martial Study Hall has ears, and the people who prepare the meals there were all Wulinmaeng staff.

How on earth can you be so confident?

Of course, I heard Sima Chunfeng's speculation, but there must have been some hidden agenda. It seemed like he was intentionally trying to cause discomfort, so I don't think he did it without thinking.

So, I guess I should take this opportunity to find out what's inside me.

"Wan Talu, does Guando lie like that in front of the adults' bed at home?"

"Huh, that's right."

"But why were all the elders of the academy gathered here, ahem."

The answer came back so confidently that I didn't hear it well.

Because he was trying to argue that you do that at home too, and that you don't do that at home, so why do you do that outside?

Well, I got hit once.

"You just said you were lying down?"

"The old man said it was nice to see their precious eldest grandson looking so comfortable, so they even laid out a mat for him."

If it was a six, seven, or ten year old kid, that might be possible, but if it was a fully grown young man, wouldn't he deserve to be beaten with a club right away?

If an adult comes, you should get up first. Why were you lying down in front of them?

Even in Qing's hometown, it would be a question of whether one had completed home education, so how much more so in Zhongyuan?

Qing's eyes narrow.

Is this kid just talking nonsense and crying because he doesn't want to lose an argument?

Or, I was trying to figure out if he was really a precious child in my house who grew up without any manners and did whatever he wanted.

"So Traines is A Young Master. Ignorance is not shameful, so there will be no punishment. However, I will now inform you. What the official did was against etiquette. If you wish to rest in the future, please do so in the dormitory or in the dormitory yard. Now that you know, if the same behavior reaches Instructor's ears, I am prepared to take action."

"Huh. Well, even the most trivial things have a home, so they forbid even the most trivial things. After all, you're just commoners, and you can't even tell who's noble. If that's what you think."

If you can say you understand in such a way that it makes you feel bad, then you can call it talent.

Wan Talu turns around with a sly smile, one corner of his lips quirking up on his pretty face.

No, I tried to turn it.

"Wan Talu. Where are you going?"

"Didn't I say I knew?"

"I will take into account any ignorance. However."

A fierce smile appears inside the cotton.

"I'm sure the swordsmanship academy said we should be respectful of each other. Is this Instructor a friend of the Kwando? I don't remember ever allowing him to bow down."

"Uh?"

"Come and stretch out."

At that, Wan Talu's face turns white.

It was such a dramatic change that you could hear the sound of blood draining out of your body.

"Now, wait a minute. This won't do."

"Why not?"

"That, that's right. That's right! Do you know who I am and dare to beat me?"

"Hmm. That's interesting. Who is the official?"

"Uh, I. That! I can't tell you that!"

Do you know who I am? Who am I? This was a series of chaotic situations that continue without me telling you.

"Then this Instructor will do my best to not know. According to the official, if you know the official's true identity, you can't beat him. If you don't know, you can beat him. Bring the official to Wan Talu."

And then Qing swung his sword, Bboong Bboong.

Qing was a monstrous monster with such brute strength that even the Hangwoo General must bend himself to the NamQing or NamHeavenly Blossom Sword. He was a living, breathing, monstrous being.

The sound of this mighty, divine wind-splitting force, unfolding before your eyes, as if passing right by your ears, was so frightening that you can't help but feel it.

"Official. Do you have any final words?"

"Hey, wait a minute! This won't do!"

"How was it?"

"That's right! I've never been hit before! Not even my father!"

"Hmm. Hmm. Hmm."

He raises his seductive nasal voice.

It meant that I was thinking about it.

Wan Talu with wavering eyes-

"Fine. If even Chief Chun says he didn't hit me—"

Phew, Wan Talu sighs in relief.

It was too early a relief.

"This is your first experience. I'm honored to be the first to whip the official's whistle."

"Wait! Wait a minute—"

"Instructors, bring him here."

In addition to the three assistants, one more person rushed in. Oh, Miss Sword was not even an assistant yet, but she was very quick-witted and good at it. Hmm, Injae, Injae.

Wan Talu, with his limbs held in place, was dragged upside down in front of Qing.

Suddenly the atmosphere became heated.

"Let go, let go!"

"Don't move. If you squirm, this Instructor can't guarantee hitting the right spot. You'll end up a cripple."

"Okay, wait! I'll speak! I-"

"I didn't ask."

Boom!! Boom!!

In an instant, the expressions on everyone's faces become relaxed.

The sound of a blocked stomach being cleared!

Well, he must have been an ugly person to begin with.

"Ugh!!!"

A desperate scream rings out.

What was even more frightening was that your assistant had not yet let go of the hand that was holding your arms and legs.

Once exposed to radiation, rubbing the affected area to disinfect it was a human survival instinct.

Thanks to this, Wan Talu was hanging in the air with his limbs held in place, writhing and vibrating very violently.

"Keu-keu, keuh-keu. Ha-eu, huh. Keu-keu, ke-keu."

"Wan Talu, are you crying?"

"Ah, no, sh*t, who's crying, ugh."

"But, you still don't have manners, do you? Are you still not coming to your senses?"

"No, no……"

Only when Qing hat starts to shake does the assistants let go of the arms and legs they were holding.

Wan Talu falls to the ground, faces down, and then shows no sign of getting up.

What? Is he dead? Judging by the way his shoulders were shaking, I don't think he's dead.

In fact, Qing had a rough idea of Wan Talu's true identity.

Of course, it was only Sima Chunfeng's guess and has not been confirmed, but it was likely that he was a spy sent from the palace.

A child with a lot of guilt doesn't usually seem like someone from a wealthy family, but if he's the child of a famous martial arts family, there's no way you wouldn't recognize him.

Even though it was broken in this car test, it was a family with enough wealth to throw away the sword, so if it was a family in the martial arts world, everyone would have known it by now, so it must be a society other than the martial arts world, the upper class, or the government.

But in the third test, I was caught using the skill of the point window, so even though it was clumsy, it was called the light skill of ascending, Biunchukyeong or something.

The martial arts of the old faction and the five great factions have a painful past, having already been offered up during the time when the Jeongpa was the palace guard.

If he was from a noble family, even one of the highest ranks, then the use of the unexpected Jeomchangpa Shinkong would be explained.

'Didn't you send someone so incompetent?'

'Oh my, the Thousand Flower Sword.'

Then, Sima Chunfeng tapped my head, motioning for me to use my head.

There was a commotion as he was hugged and subdued, and then his side was destroyed, but anyway.

'Huk, huk, huu, huuuu, huuuuu, I won't bother trying to hide it. I guess it means that I am a special envoy of the palace, so treat me with respect.'

You weren't going to try to hide it in the first place?

This was what it means.

He's a spy, but I sent him anyway, so keep him. Why don't you like him? Really? Treason? Treason?

No matter how powerful the current martial arts world is, it's impossible to openly rebel against the imperial family. So, somehow, they have to pass.

It's like sending a spy with a label saying he's a spy, so I don't know if I should call this bold or petty.

But what was certain was the arrogance of the imperial family.

It was full of the intention of, "I sent it, so how dare you refuse?"

There was some good news though, and it's a completely different thing to try to hide something and to make it known.

Even in the imperial palace, it was not an act that was right to be made known to the world, and if a high-ranking official's child were to study at the Imperial Academy, it would be a great loss of face for the imperial palace.

This was because the very act of sending them to the martial arts world to teach them instead of teaching them themselves was tantamount to acknowledging the superiority of the martial arts world.

So, I can't say it out loud, but I think it will come out as if I'm telling you to do whatever you want.

anyway.

So, Qingdo came to a conclusion.

Since we don't know his true identity as a spy of the imperial family, shouldn't we treat him the same way as Guando?

"Wan Talu. Stand up."

"Sniff."

"Guan Do, are you crying now?"

"I told you not to cry, you know……."

After getting hit once, Wan Talu was now using polite language, albeit a bit gruffly.

I thought it would be a bit more open, but it's only one room, so it's a bit disappointing.

After all, power breeds courtesy!

And I feel stronger than anyone! More powerful than ever!

That was the greatest power of martial arts, the phenomenon that even distorts reality, when will we ever again be hit by the club imbued with thought?

The maximum amount of pain possible without harming the body! (Additional damage to males)

It was a human-centered ideology of nuclear fusion that values the lives of others.

However, as I lay there, face down, looking at that trembling back, I felt a little bit of pity.

Was it a bit much? But it's still Anna.

I think you said you were eighteen this year.

I don't think he would have lied about his age, so let's see. If it's from his hometown, he's in his second year of high school? Hmm. Then he's a kid…

"Wan Talure, the crown prince. Rise."

Qing wakes Wan Talu and personally brushes the dirt off his body. As he does so, she whispered a word of comfort into his ear.

'Try messing with me again. I'll let loose. Seriously.'

"Hic."

Wan Talu, who hiccuped with surprise.

Well, every baby was a baby.

Even if you were clumsy, if you show off your skills and were shy or insignificant, people will treat you like a baby.

A rough and tumble delinquent isn't a child, he's just a juvenile delinquent. No, why was the concept of a juvenile delinquent even necessary? He's just a young, yellow-headed delinquent.

But luckily, he's under me.

Just as dough becomes chewier the more you knead it, people also become more kind the more you knead them. Hmm, I want to eat handmade noodles. No, sujebi.

Chureup. Qingi quickly gulps down the saliva that flows automatically like a dog's paw.

It was a more terrifying moment for Wan Talu.

This woman was now even swallowing her saliva to beat people up. There was no such thing as a dog butcher, no, a human butcher. The old men of the family kept nagging her so much, saying that these people were butchers who eat people too, so be careful.

Everyone felt relieved when the hated guy got beaten up, but after he got beaten up, he came back with bloodshot eyes and covered in dirt, so he looked a bit pitiful.

The leader, Yang Qi, pats him on the back.

"See?" Wan Talu said, shaking it off, but it was a relentless rejection, so Yang Qi gave him a wry smile and patted his back again as if to say it was okay, offering comfort.

I said that one of the leaders was chosen very well.

but.

Well, who am I supposed to comfort now?

Qing looked at Murong Juhee, Nan-Gong Shencai, and Changbin.

A gaze filled with a mysterious heat, or a gaze filled with some kind of evil madness, returns.

Because before the full-scale sparring class, we plan to do some 'simple' physical training.