\chapter{Training Arc (7)}

Before entering the martial arts world, Qing was a master assassin who had undergone two years of rigorous military training in his hometown.

Surprisingly, in Qing's homeland, men who came of age were given the opportunity to join the military and learn the terrifying art of killing through surprisingly systematic, scientific, and even entertaining training.

Above all!

The greatest lesson learned from the military in Qing's homeland was not just the art of killing.

It was a unique opportunity to learn truly important lessons, big life lessons.

How closed societies and rigid hierarchical cultures degrade humanity. How budget constraints in organizations degrade people. How behavioral goals that prioritize results over process create inefficient farces. How those who prioritize authority were seen as individuals with no other strengths to offer. And so on.

However, the biggest problem was the mysterious phenomenon of forgetting all the valuable lessons and terrifying killing skills that he had learned through his body within a month of graduating from military service.

Well, isn't that just a waste of time? Well, what does it matter now?

Anyway.

In the military camp of Qing Dynasty, the most rigorous and dangerous training was conducted once a year.

Guerrilla warfare was the art of breaking through the physical limitations of humans and reaching a state of extreme self-discipline!

This infamous training was so brutal and dangerous that it resulted in tens of millions of deaths each year, with only one in a thousand returning alive (probably).

And Qing gained new insight into this training, which he had overcome twice in the past.

I thought it was just a training exercise to make you guys really mad because you caught me, but, well, that wasn't it.

Surprisingly, there were days when even the most prestigious sect would catch me and punish my disciples.

Because for the safety of the disciples.

When a person receives an external shock, major injuries can be avoided if the shock was evenly distributed throughout the body.

However, humans have a sense of smell, and when they were in danger, they apply force to the affected area and harden it.

In this case, rather than being distributed, the impact was concentrated at one point, leading to major injuries such as muscle bursts and bones broken.

But what if you exercise your entire body evenly?

Even if you unconsciously tighten your muscles at the moment of impact, you will be forced to release the tension through the so-called "knock-knock pain."

then?

It can reduce a broken bone injury to a bruise, and a bruised bone injury to muscle pain.

In other words, it was set up for safety!

So, not only Qing, but all three assistants from prestigious families had been training under the harsh and vicious guidance of their masters and private tutors.

Because that was the tradition of the noble family.

And tradition was something that continues from the past to the future, how can we put it differently?

I can't be the only one who gets hit!

Of course, that's not the case.

Now, we have to proceed with the lesson through sparring, but since those skilled in swordsmanship were clumsy in both offense and defense, it was inevitable that there will be those who strike and those who get hit.

Furthermore, the one who gets hit naturally feels bad. As anger builds, it can intensify one's swordsmanship and lead to emotional attacks.

So, to prevent accidents, it was necessary to tense up the muscles throughout the body.

So, it's all for the officials.

It's heartbreaking, but I can't help but wish for the best for all of you with the loving heart of a parent.

Qing and assistant instructors looked at each other with evil smiles and sinister expectations.

In response, Qing said a loud word.

"In the afternoon, before the sparring class, let's do a quick warm-up!"

Some of the faces of the officials turn a muddy color.

Before sparring, warm up your body.

Those who already understood this meaning were those who came from small and medium-sized sects or had undergone systematic training thanks to having a good teacher.

'Oh, right. There was this. It was done.'

But only some.

This passage shows the background of the officials and the great opportunity that the Office of the Inspector General offers, given that most people have yet to realize the seriousness of the situation.

"The life of a warrior was in the lower body. Whether it's the quick sword, the middle sword, the strong sword, or even the circle, the change, the pae, the ja, the cheom, the gang—all these magical skills begin at the soles of the feet of the official!"

This was a common knowledge known to everyone, from third-rate martial artists to world-class masters.

However, surprisingly, there were few people who know about it and practice it properly.

Lower body training takes a long time and was difficult.

In Qing homeland, was there anyone who does not know that alcohol was a poison that has no positive effects and was simply harmful to the body, and that sweet and salty foods were also harmful?

But still, they drank well and ate well.

Knowing something doesn't make it easy to put it into practice.

"Look at Assistant Murong here. She has the best lower body I've ever seen. Isn't she truly amazing?"

At that, Mo Yong-ju lifts his chin.

She was a heroine who trembles like a gentle rabbit in front of Qing Dynasty, and she was the one who originally controlled half of the female warriors of the Phoenix Society.

"As a close friend, not an instructor, I want to brag to the whole world about this amazing lower body. Isn't that right, Assistant Nan-Gong?"

"That's certainly true. I can't acknowledge you for wielding a half-sword, but I can certainly acknowledge the training you put into your lower body."

"Assistant Murong, what is the great secret to training that great lower body?"

"There's no great secret to lower body training. Just Mapo, only Mapo, Instructor."

Murong Juhee answered.

Qing nodded in agreement.

"You've heard it all! Then, Assistant Murong, I'll ask you to take charge of the warmup."

"Let's all practice together. Let's practice Mapo!"

Murong Zhuji showed off the most ideal posture by taking a Mapo stance.

Mabo means riding a horse.

To be precise, it refers to the movement of bending the knees and placing the thighs parallel to the ground, then raising the arms and holding them parallel to the ground again.

Once you get used to it, add weight by hanging weights on your wrists and increase the load by carrying a backpack.

It was said that a warrior who has not trained in Mabo cannot be called a warrior, so everyone knows the movement without needing to explain it.

So everyone, bend your knees.

Hhowever?

Why isn't it ending?

In just half ke (seven minutes and thirty seconds), there were already many instances of knees shaking and thighs rising and falling.

"Don't raise your thighs! Look at the Assistant Instructor! I thought she was a statue! Thighs aligned with the ground! Assistant Instructors, assist with training!"

Then, as if they had been waiting, Nan-Gong Shencai and Changbin appeared.

"Don't lift your thighs! Lower them. Like this, like this!"

"Do-woo, why are your legs shaking already? Can't you steady your knees?"

Somehow, the two of them were in high spirits.

Of course, Changbin was passing by the female trainees as if he didn't even see them.

"Guan Do, raise your butt."

And even Geomok-gun, who secretly joined the teaching staff and took care of the government office.

Maybe she didn't like Mabo, but, um, since Lady Geom was slender and her legs were so slender that it seems like they might break if she were to get cold, it seems like Lady Geom should also get some Mabo.

But since he was a talented person who will become an assistant later on, I can't just point it out and diminish his authority.

That's how it is

Unlike the civilized people of Qing, who were extremely weak, aren't the warriors of this era primitive people who were stupid and use their bodies?

The third-rate officials show some signs of difficulty, but they follow along without making any noise.

But what about this angle?

"Stop! Stand up!"

It was only in this bay that the principal was scorched to the ground.

Oh my, this was how you learn swordsmanship.

Rather, what was truly amazing was that Lady Mo Yong, who doesn't even move a muscle, was holding on purely with her lower body without using any internal energy.

It was somehow amazing.

"The people whose names are called will come forward! Cai Sengxia Gwando, Wan Talu Gwando, Usurim Gwando, Kang Hwangja Gwando…"

Names flow out one after another from Qing's mouth.

These were excellent Mabo people who have maintained a firm stance for a long time.

Perhaps that's why the officials stepped forward with a somewhat smug look on their faces.

"Rule two of this swordsmanship school! You may not use your internal energy without permission! Now, line up!"

These were the officials who became absorbed in thought in an instant.

No, if you're holding on with your internal energy, then what kind of training was that? You have to tear that knot apart with pure muscle power to be considered training.

"I'll take it easy, so don't be nervous."

Pak, pak, pak, pak. Qings stand in a line and swing their flutes.

Since she actually hit them gently, not just with words, this level of trickery was not considered a mistake.

Certainly, the reaction was equally bland.

Not like it's a real shot, jumping out or rolling on the ground? Or like it's just a constant, swooshing sound? Or something.

"Guan Do, where were you going?"

As Qing speaks kindly to the officer who was walking quickly in a large circle, laughter spreads throughout the room.

But that was only for a moment.

"Okay, then, let's continue stretching."

The expressions of the officials were filled with shock.

Or resignation, or despair.

It was the expression of someone who had finally realized what it meant to warmup.

"Next, wow!"

Waho, meaning lying down tiger.

And it was also a famous training method.

Lie face down on the ground with your hands on the ground and support yourself on your toes. Your torso should be straight and not bent, and your elbows should be bent at right angles.

In Qing homeland, it was the lowered position of an exercise called a wide push-up, and as you get used to it, you gradually raise your palms and put weight on your fingers, and later add weight to your back.

"Hey, put your butt in."

"Get up! You can do it!"

There was no teaching assistant in the world that was this annoying.

Well, it must be very convenient since they don't do that.

So this angle again.

"Now, next was the peacock tax. First, let's watch a demonstration by a skilled assistant."

Then, Nan-Gong Shencai lies on the floor, spreads out both arms, then straightens both legs that were pressed together and lifts them diagonally.

One left, two in place, three right, four in place. It was the exact posture that would make a blue-haired man tremble if he saw it.

Free arm first movement, whole body twisting.

The most evil torturer to appear in Zhongyuan for the first time!

Actually, I don't remember the rest very well.

This, lying down and stretching out and then jumping up, there was also jumping and spinning, that's about it.

It seems like lying down training was too easy, or maybe it's because my limbs were already sore from overworking them.

It would be understandable to hesitate when told to lie down on the floor, but everyone immediately lay down on their backs without a word.

But, well, really?

How long could these primitive people endure the most brutal training on earth, embodying the essence of modern exercise science?

"One. Two. Three. Four."

Qing gives a command from the stage.

At first, I thought I was following along well?

"Ugh." "Ah …

Not even twenty times had passed before a groan erupted.

Well, he was already exhausted from the Mabo and Waho, so what kind of cruel act was it to do a free-range arm wrestling when he was tired?

Looking up from the stage, it was quite a spectacular sight.

About sixty people were lying down, their knees bent awkwardly, barely able to lift them, and they were groaning and groaning as they moved from side to side.

Ah. So this was what it felt like.

Life was a tragedy when seen up close, but a comedy in long shot.

This, um. kind of. how should I put it. was interesting… …

Haha, humans were like trash, you say?

Still, I've been given a lot of leeway.

The last command was silent, I didn't do that. Well, I personally feel a bit responsible for the solidarity.

"stop!"

"Ahhh……" "Hoooo……" "Ugh."

Sounds of deep relief here and there.

And then, while lying down, he gasped for breath and his chest rose and fell.

Qing gives him time to catch his breath by lying down for a while.

Because it gets harder after you rest a bit.

"Okay, now we've done one full circle. Let's continue our warm-up. Back to the beginning, Mabo!"

One full circle. That is, it's not over yet.

It was a moment when deep despair filled the eyes of the officials.
