\chapter{A Ronin Has a Ronin's Sense of Loyalty(17)}

Even though the bruises hadn't completely faded, her chest was being squeezed again, causing her to scream. Moreover, since it hadn't healed yet, the pain was much worse than last time.

Moyong Juhee growled in a choked, submerged voice, "I'm grateful that you saved me. But when I think about what you did, I can never, ever forgive you. You are the most horrible person in the world, a monster, a monster, you are."

"Argh, h-hand, hand."

Qing struggled, grabbing Moyong Juhee's hand that was squeezing her chest.

She tried to pry it off with force, but it wouldn't budge. When she tried to remove each finger with both hands, Moyong Juhee's other hand would assist, squeezing one area for each one she pried loose.

"It hurts, it hurts! It really hurts!"

"You, you know it hurts, too?"

"Let go, let go, it really, it really hurts, argh!"

When it really hurts, the screams are not loud.

Lightning struck in Qing's mind.

Unable to even scream loudly as she gasped and groaned, Moyong Juhee cried and smiled at the same time.

"Right, this thing. It's nothing but a weakness anyway. Ha! It's so useless. This thing, this thing, I don't need it anymore."

"Let, let go, it really, it really hurts, argh!"

At this point, even Qing was getting angry.

This bitch was even using her Inner Qi, so it was obvious she was trying to burst it on purpose.

As such, Qing had no choice but to use her last resort.

Qing squeezed Moyong Juhee's wrist tightly.

It was Qing's grip strength that could crush even steel.

"KYAAAAAAK!!" A sharp scream erupted as Moyong Juhee's hand fell powerlessly.

Moyong Juhee, whose wrist was grabbed, screamed.

"Are, are you making fun of me!? Did you think I would just act like a pathetic idiot, trembling at the sight of your teeth!? What. Yeah! I'm a pathetic idiot who got caught and had her teeth pulled out! Do you want to put them back in since you think they're so fitting?! I was barely able to forget about it!"

Ah. Qing's hand slowly lost its strength.

It was a well-intentioned gift without much thought.

But she realized that it had not only touched a raw nerve but had also completely torn it apart and sprinkled salt on it.

"I, I'm sorry. That was absolutely not my intention. I just wanted to comfort you."

"Comfort? How could that possibly be comforting! From the start, you're, you're strange! Every time I close my eyes, what you made me do still, ugh, ugh."

Moyong Juhee couldn't continue, covering her mouth as her stomach acid surged up.

Even now, whenever she closed her eyes, that moment was still so vivid.

The feeling of cutting through the flesh of a living person, the sensation of severing muscles. Unable to resist the forceful strength that compelled her, she squeezed with her own hands, thus hearing the desperate screams of the dying. That horrible sound between sobs and screams.

And then, the feeling of death as their breath finally stopped, like a delicate thread snapping, like an ornament falling off.

"Why, why did you do that? That, that wasn't something to do. No matter how, no matter how bad they were, I, ugh, I shouldn't have done that. Huh? Why, why, I, and, the worst thing is, do you know what the worst part is!?"

Pain makes people sick.

Moyong Juhee was utterly sick.

Qing's prescription was revenge.

Of course, it might have been helpful if it hadn't been so extreme.

But Qing was in a state where Heavenly Slaughter was rampaging.

Even the teachings of Buddha did not dare to stop Heavenly Slaughter, for although martial arts were meant to harm others, the image of Buddha was not one of mercy but of saving the world by embracing the world's killing karma.

But Qing only tilted her head.

What? What shouldn't be done? What's wrong with torturing and killing those Blood Cult bastards? Why is that not okay?

They were people who deserved to suffer enough.

"Uh… Young Lady Moyong. Those bastards deserved to suffer. Unlike Young Lady Moyong, who has done nothing wrong, the Blood Cult bastards were different."

"What does that matter? Why, why does that matter?"

"If I had just severed their breaths, it would have been like letting them off easy to burn in the fires of hell for their sins. But that's not the case, is it? Death is just an irresponsible end."

Moyong Juhee's body trembled.

To her, it was all just a terrible thing.

"You, you enjoyed it! You just did it because there were bad guys and you could be that cruel to them! You were grinning as you butchered people! Stop making excuses about sins and whatnot!"
Qing scratched her cheek.

"Hmm. I'm not sure what the problem is. So, if I had cried and reluctantly inflicted pain, it would have been okay? Even so, the result is the same. People who deserved to suffer died in pain, didn't they? Does it become a wrong act just because I enjoyed it a bit?"

Moyong Juhee looked at Qing as if she was looking at the most horrible thing in the world.

"You, you. You're a monster. That's what you are. You're just a blood-crazed killer."

"I won't deny the part about being a killer. But isn't calling me a monster a bit much? I have never once done anything that I am not proud of, haaa. Never mind."

Qing sighed deeply.

She's a sick kid.

There is no way a rational conversation can happen.

Is this like that Stockholm Syndrome thing, where a kidnapping victim sides with the kidnapper? Or is it just that she's so sick that anyone in pain makes her feel empathy?

"I'm sorry. I didn't know Young Lady Moyong would be in so much pain. I did such a terrible thing to you, and giving you the teeth was not my intention at all. I'm sorry. Um. Then, get some rest."

Qing spoke and then got up.

Well, if she doesn't like it, then that's that.

After all, the only thing Qing lost was a sore chest, so there was no need to stay any longer. Since she didn't know Joon and the Clan Leader, she could just part ways here, right?

That was when it happened.

"W-Wait!"

Moyong Juhee urgently shouted.

"What is it?"

"Where, where are you going?"

"I think it would be better if I wasn't around. Uh, I won't come by again, so don't worry and rest well-"

"W-Wait. Just a moment. Just a moment."

"Is there anything you need……?"

"There's nothing like that, but."

"Or should I just leave? It seems like Young Lady Moyong will feel more anxious if I am around."

"Wait a moment! It's not that."

Moyong Juhee grabbed Qing's wrist.

Qing looked down at her, wondering what she was doing now. Was she going to squeeze her wrist this time? But when she looked down, Moyong Juhee, with her head bowed, let out a small, clear voice that sounded like a mosquito's buzz.

"……Just stay a while longer."

"Yes?"

"It's because of you! It's because of you! The terrible memories keep coming back, so you have to stay by my side. I, I can't be alone right now. It's because of you, so take responsibility. Yes, you have to take responsibility. Stay by my side. Stay with me until I fall asleep."

Moyong Juhee's trembling grip on her wrist was conveyed.

Qing replied with a sullen expression.

"But won't you keep thinking about it if I'm here? Um. Should I call Nanah over-"

"It's because of you, I said! So you have to be here. No one else will do. Stay by my side. Stay with me until I fall asleep."

"But if I'm here, you'll just keep thinking about it. And didn't you say you hated me?"

"No!"

Moyong Juhee begged with a changed expression.

"I don't hate you. It's just a little, a little terrifying, that's all. I, I don't hate you. How could I possibly hate you? It's just that when I see you, I keep thinking about that time. I'm sorry. I shouldn't have been angry at you. But you made me do that. I didn't want to kill people like that, but you! You!"

"Young Lady Moyong?"

"No, no, no, no. I'm fine. I'm sorry. I'm sorry. I spoke too harshly, didn't I? I didn't mean it. Don't leave me alone. Please, please, I'm begging you like this……"

Ah. She's having a panic attack, huh?

Qing sighed again and sat down on Moyong Juhee's bed.

Then, the trembling transmitted through her wrist gradually subsided. After a while, her breathing became deeper, sinking into a deeper place.

The space occupied by Moyong Juhee on the spacious bed of the finest guest room was just a small area where she curled up.

Qing looked down at Moyong Juhee, who seemed to be still trapped in a box, and thought.

It seems like I've become a sort of panic button. It seems like it was too early to teach beginners actual anatomy.

Honestly, she's being all 'take care of me' and 'don't be nice to me', so it's going to be quite annoying to deal with her.

So, I shouldn't show my face to her, she decided.

-is what I thought. Um.

"What the hell. Why is she like that?"

Dang Nanah raised her eyebrows. At the end of her gaze, Moyong Juhee sat with her knees hugged to her chest, her head buried.

She had hobbled all the way to the training grounds on her uncomfortable feet and when they tried to greet her, she told them not to act familiar and pushed them away. But she didn't go anywhere, just sat there in a corner, looking pitiful with her head buried.

"I don't know, either. She seems to be in a lot of pain because of the Blood Cult. I think she's mentally ill."

"No. It's making the mood weird. It's like we're bullying and ostracizing her."

"I don't know. What can I do about her inner thoughts……"

She had been like this since the day after visiting her, and it had already been three days.

She would sit in a corner of the training grounds with her head buried, and when it was time to eat, they couldn't just leave her, so when they asked if she wanted to eat together, she told them not to act familiar.

She was acting so pitiful that it was uncomfortable to just ignore her, but they didn't know what to do.

As such, a somewhat uncomfortable spectator had been attending the half-sword doubles training ground every day, and somehow, the days passed by until the semi-final matches were tomorrow.

It was the night of Cheon Yuhak's return.

"Sigh, this wench is so thoughtless that her master has to go through all sorts of hardships. Aigo, wench, massage my shoulders. Aigo, I'm so stiff."

"What? What's going on? Why did you suddenly leave?"

Qing grumbled, but obediently massaged his shoulders.

"Ohhh, the hands of my disciple are truly wonderful. This is why people raise disciples. Keuheueu."

"And what's with sending a message and asking for money? Does it make sense that it costs five taels of silver to send ten words?"

"You brat. If you give the money in advance, do you think they will actually deliver the message? You have to tell them to deliver it first and then collect the money, so they don't run off somewhere else. And you have to pay five taels of silver for them to really open their eyes wide and run in a hurry."

"Hmm."

That made sense.

It was a message to not worry, so it didn't make sense to ask for five taels of silver.

So Qing just changed the subject.

"So, what did you do? Why did you suddenly leave for ten days?"

"Keuheueu. There's a person's head in that box over there, so don't be surprised. It's the head of the Blood Demon of the Blood Cult."

"Ooh. Why is he in there?"

"You brat, if you gang up on someone like that, how could you not know he had escaped through the ceiling? I didn't know much about the Venom Arts, but you have to catch the person controlling it far, far away, so I had to chase him all the way to Henan Province to kill him, what else?"

"Wow, you went far."

"Well then. Now, take that and tell those Ronin bastards that you got rid of the venom they were harboring. Tell them that the genuine Divine Thief appeared and stole the head."

"Um. Teacher. The matter of the venom has already been resolved. You were very late."

"What? I caught the Blood Demon?"

"I took care of the rest. The venom has already been removed."

Qing conveyed the events that had occurred while Cheon Yuhak was away.

"What, so wasn't this a waste of my energy? If I had known, I would have just rested. I'm so exhausted from chasing that bastard all over the place……"

"Well, it's not a waste of energy. Anyway, you did great. Wasn't the Blood Demon a master of the Unrestrained Realm? Did you catch him one-on-one?"

"Here, listen. So I……"

Cheon Yuhak began to brag.

It was a grand tale of a minor victory, but it was also a very neat ending.

At that moment, Seomoon Surin was once again feeling a sense of loss.

"These bastards. Even if they didn't know last time……"

After all, the Ronins who had returned to the Hall of Honored Guests had once again requested an audience with Seomoon Surin. 