\chapter{A Ronin Has a Ronin's Sense of Loyalty(7)}

Then, Gyeong Damgan made a strange laugh that sounded as if he was sobbing.

"But, little girl. I heard a strange story. You used the Black Slaughter
Demonic Palm? That a female warrior of the Orthodox Faction mastered
one of the Ten Great Demonic Arts? Do the fools of the Orthodox
Faction know about this?"

"Oh. You caught me. I guess my hands are stained black, so it can't be
hidden, you know? Here. Look. These are the black hands of the Black
Slaughter Demonic Palm."

Qing extended her fair and slender hands.

Those who mastered the Black Slaughter Demonic Palm had their skin
turn black, with a texture akin to tree bark. It was hard, rough, and
disgusting to look at.

So, when Qing dangled her pretty fingers as if to show them off, it was
clear she meant to say, 'Unless you're blind, do you really think these
hands are black?'.

"Hmph. It seems like the youth these days don't have their basics straight.
You should have at least said you mastered the White Hand Demonic
Arts."

Even Gyeong Damgan couldn't believe such words.

It was utter nonsense for a female warrior of the Orthodox Faction to
have mastered an evil Demonic Art, especially one of the Ten Great
Demonic Arts that was recognizable to all of Jianghu.

However, since several of his subordinates had simultaneously
testified to it, he couldn't just ignore it, so he tried to test her, only to end
up being embarrassed.

"Ugh. White Hand Demonic Arts is a bit…"

Startled, Qing shrank back slightly.

However, Gyeong Damgan did not doubt the White Hand Demonic Arts
in the slightest.

After all, the White Hand Demonic Sect was a branch of the Blood Cult,
so if they had accepted a disciple, there was no way Gyeong Damgan
wouldn't have known.

"Anyway, just you wait. You will pay the price for your insolent
actions."

They always say, 'Just you wait'.

Qing snorted and then prepared to act pitiful.

But Gyeong Damgan just let out a cackle and retreated.

What the hell? How anticlimactic.

Since she had nothing to do, Qing sat in the lotus position and
circulated her Qi. Although, she did lie down since it was boring, so it
was safe to say that she had finally started to look like a martial artist.

Hm.

My cultivation is increasing at a snail's pace.

It was only natural, seeing as she had only circulated her Qi for half a
day. It was already a mistake to expect some great achievement from
such a short period of time.

In truth, there was a reason Qing was neglecting her Inner Qi
cultivation.

Due to the collaboration between the Blissful Maiden Arts and the
Heavenly Glacial Demon Arts, Qing was in a state of automatic
cultivation, circulating her Qi every single moment of every single day,
regardless of whether she was eating or taking a shit.

Come to think of it, the Blissful Maiden Arts had already reached the
Tenth Stage while the Heavenly Glacial Demon Arts was at the
Eleventh Stage, with almost enough Practice Points to reach the Twelfth
Stage, thus being on the verge of acquiring a Special Ability from
mastering it.

The Heavenly Glacial Demon Qi, which was constantly being chased,
was more diligent than the Blissful Maiden Qi that did the chasing.

Moreover, the difference in the required amount of Practice Points
between Gold and Red techniques was quite signiicant.

The Blood Demon Divine Arts and the Purple Lightning Demonic Arts
had also risen by two stages each, so aside from the side effects, the
Blissful Maiden Arts had done a great service.

Meanwhile, the Blood Cult warrior tasked with the daytime guard duty
was dumbfounded, seeing Qing sitting in the middle of the cell,
circulating her Qi.

Originally, cultivating Qi was when a martial artist focused on their
meridians, thus becoming defenseless. For a warrior of the Orthodox
Faction to cultivate Qi while trapped in the secret prison of the Blood
Cult was unheard of.

She must be either incredibly bold, or rather, she had no fear or
thoughts, or perhaps she was completely ignoring them. It had to be
one of those, or a combination of all of them.

It was absurd and outrageous, as well as insulting to a member of the
Blood Cult that had once struck fear into the hearts of the Central
Plains.

Honestly, the position of a prison guard was typically reserved for those
of higher rank.

Because, after all, it was a position where one could torment the
prisoners as much as they pleased, as long as they did not directly harm
them.

The reason why the morning guard had blatantly trampled on Qing's
rice ball wasn't solely because his personality was utter trash.

It was because he could do so, and had always done so.

Other than that, they harassed prisoners with their words, urinated on
them, poked them while they slept to disturb them, and so on. Everyone
had their own preferences.

Tormenting the prisoners like so to mentally exhaust and sicken them
was Gyeong Damgan's intention.

But the scene he had witnessed in the morning was so shocking that he
didn't particularly want to provoke her.

Besides, just watching the beautiful face of a beauty with her eyes
closed made time fly by.

God damn, she really is fucking pretty.

While waiting for the day when her body would be disposed of, he
licked his lips, his stomach growling from hunger.

It was when the guard took out his lunch, a rice ball wrapped in
bamboo leaves, and unwrapped it.

Qing's eyes shot open.

A diamond-shaped brilliance, with its corners shrunk, sparkled in her
eyes as she stared at the rice ball.

"Excuse me, Warrior? What about this girl's meal?"

The guard, who was just about to take a big bite out of the rice ball,
frowned deeply.

Does she think this is some sort of restaurant or what?

"Lunch?"

"Yes? What do you mean by that? Even if you hate someone, you still
have to feed them, don't you?"

"You fool. Do you think we would give even a single meal to the likes of
you Orthodox fools? There will be no meals for you in the future, so don't
even say such retarded nonsense."

"No meals? What do you mean by that? Surely, in the morning-"

"Senior Ju, I mean, that guard, prepared that meal personally. If you're
hungry, you should beg for our mercy. Try to be all flirty and, hehehe."

It was all up to the guards whether to give food.

Qing understood this malicious system.

The guard continued with a sneer.

"Are you hungry? Then, how about sucking on this elder's cock? If I like
it, I might just give you a bite of this rice ball."

"Haaa. Men."

Qing sighed deeply.

Men were such sad beasts. How could they possibly resist this system
where they could do whatever they wanted as long as they didn't touch
the prisoners' bodies?

Just you wait and see. I have something to show you.

"There's nothing I can do about it, then. Could you come here for a
moment?"

"What? Really? So easily?"

The guard, who had stood up, reached for his waist, but then his gaze
fell on the red stain on the bars that vertically separated him from Qing.

In an instant, a chill ran down his spine, instantly extinguishing the
excitement that had surged.

"You, you bitch, trying to lure me in."

"My, you have quite the good eye."

Qing smiled brightly and said so.

The guard plopped down on his chair, his legs feeling weak.

"So, when do I get my meal? For reference, I have a deep grudge
regarding meals, you see? It would be best not to make an enemy out of
me over food. Let's just get along nicely, okay?"

It was a threat to give her food if he didn't want to die.

The guard momentarily agonized over it.

She was a wench who could twist a person into a metal bar.

Was it really wise to earn her resentment over mere food? Wouldn't it
be better to just give her what she wanted and let it go?

But only for a moment.

After all, what could a trapped wench do?

No matter how overbearing she acted, there would have been no
material that did not beg for mercy under the Deputy Leader's
methods.

Especially if the material was a woman, all he had to do was wait until
it was time for disposal.

"You stupid wench. Know your place. Yeah, go ahead and dance naked
for me. If I like what I see, I can give you this much."

The guard tore off a piece of the rice ball, as much as a single knuckle,
and held it out.

Qing sighed deeply.

Why are all the bad guys like this?

"Why can't they understand when you try to talk it out peacefully? Why
do they always make things so cumbersome?"

"Hmph. What can you do even if it's cumbersome? You talk too much for
a wench trapped in a cell……"

The guard suddenly stopped talking.

It wasn't a ploy to make her angry, but rather his speech was cut off in
surprise upon seeing the iron bars between them split open to the left
and right like willow branches.

Qing casually spread the bars like she was opening a curtain at the
entrance of a shop.

Originally, steel was strong against pulling or pressing forces, but not
as strong against bending.

And Qing's strength far exceeded the level that steel could withstand.
Qing immediately lunged through the open bars.

Although the width of the hallway wasn't that large, the guard quickly
reached for his sword. However, in an instant, his neck was caught and
he was choked, unable to breathe as he struggled.

But that was only for a moment.

Once the blood low to the brain was cut off, the difference between a
Master and a novice was merely how intensely they resisted before
fainting.

The guard was only a First-Rate expert, so he couldn't put up much of a
fight against an enemy who pressed down on him with enough force to
slam him against a wall.

Eventually, the guard went limp.

"Who doesn't know how to get out of here? I'm telling you to just talk it
out nicely, but you just had to make things difficult. People really love
getting beaten up."

Qing grumbled as she dragged the guard back into the cell by his hair
with one hand and gobbled up the rice ball with the other.

Then, she stripped the guard's top and tied his arms tightly behind him.

Afterward, she took off his pants and used them to gag his mouth
securely before approaching the bent bars.

Ugh. This is easy to bend, but straightening it back is a pain in the
ass.

After struggling with the bars for a long while, Qing nodded in
satisfaction after restoring the bars to an almost unnoticeable state.

Then, she noticed five more rice balls wrapped in bamboo leaves in the
pouch on his waist.

Well, to be fair, I guess it would be a bit stingy to share just six rice
balls for lunch.

Thinking this, Qing enjoyed her lunch, gobbling up the six rice balls,
which amounted to three large bowls of rice.

But why is there only salt and plain rice without any other ingredients?

Is the Blood Cult in financial trouble? How can a person live by only
eating rice seasoned with salt?

Still, the salty glutinous rice, imbued with a fragrant bamboo scent from
the leaves, was quite palatable.

After finishing off the one the guard had taken out and the five he had
stashed away, a total of six large bowls of rice, Qing then pressed her
finger into the guard's shoulder.

As she did so, her white and slender, elegant finger sank in without any
resistance.

It was as if a person's shoulder bone was made of tofu, allowing for a
very natural intrusion.

Suddenly, Qing's expression became dazed.

Wow……… This feels so good. It's like I'm going crazy.

However, the guard, whose shoulder had been pierced, did not seem to
feel the same way.

The guard's eyes shot open and he squirmed.

"Shh. Quiet. I told you to be quiet. Why, do you think these people will
come all the way in here to save you if you make some noise? Or will
they just stand there, kicking their feet, watching you die a miserable
death? If you understand, nod your head."

At that, the guard nodded vigorously.

Since he had been present in the morning, he knew very well that
calling out to his colleagues for help would be of no use.

After all, he himself was a colleague who was of no help.

"Mmm. Anyway, since I got my meal, I'll let go of any grudges. But you
made me go through all this trouble, so you should pay the price for
that, right? Choose just one of the most important things between your
right arm, left arm, and neck. I'll pull out the less important ones."

It was a truly horrifying threat.

After all, it basically meant she would pull out both his arms.

"I, I was wrong. Please forgive me……"

"Oh. You're being polite right away? I'm glad we can communicate well.
There's a way for you to leave here with all your limbs intact. Wanna
hear it?"

"Yes, yes. Please."

"Tell me everything you know without lying, and I won't touch a single
hair on you. Ah, except for your shoulder. I already touched that, so that
doesn't count. Anyway, if you tell me everything honestly, you can leave
here in one piece, okay?"

"Everything, you say……"

To that, Qing smiled brightly and freshly.

"Everything. What this place is, what kind of people all of you are, and
what your colleagues' martial arts are like, what you do here, things
about the Blood Cult, and everything else you know."