\chapter{A Ronin Has a Ronin's Sense of Loyalty(4)}

The martial artists, filled with excitement, cut through the night. It was Chun Yu-hak who was chasing after the mysterious scent of the East, whose principles were unknown. It was also a skill that Qing had to learn later. Then, Chun Yu-hak finally raised his finger in front of a secluded wall outside the city.

 "Is it here?"

 "Yes. Hmm. I don't sense any other presence, though."

 Qing closed her eyes and concentrated on the surrounding sounds. With her superhuman hearing, she listened quietly, but apart from the breathing of the nearby vagrant martial artists, nothing else particularly caught her ear. She measured the wall of the manor from end to end, jumped slightly, confirmed the modest structure of a single main building and one annex, and whispered again.
 
 "I'll jump over the wall with these people here. Can you keep watch just in case? What? I mean, there might be someone who will try to run, whether it's the culprit himself or some hidden accomplice."
 
 "Hmm. Isn't it better if I go with you? I don't know what's inside, so how can I send you alone?"
 
 "I can get away on my own, no matter what. It's all about striking swiftly. What if even a single rat escapes? And if there's a real problem, we need someone to ask for help from Teacher as well."
 
 "Tsk. I don't know if I should cause unnecessary worry for your Lady." 

If it were the previous generation, he might not have known, but Chun Yu-hak, who was middle-aged, did not know about the splendid past and true nature of Ximen Surin. Moreover, since the previous generation had kept their shameful history a secret, he had no knowledge of Ximen Surin. 

"So, where is he? Main building? Annex?"

 "The main building's main room. If it's dangerous, get out immediately. Don't do anything foolish, thinking you're doing a favor for some lowly people." 

This was how the vagrants of Zhongyuan were treated. But even if they weren't vagrants, but people of noble status, Chun Yu-hak's words would not have been any different. Whether they were of high or low status, he must first take care of his disciple. 

"Now, fellow vagrants. They say our enemy is over there. Main building, central room. I'll charge in from the front, so Young Master Ma will take the back and Young Master Wang will take the right……"

It was a simple strategy without much to be called a strategy. However, since the world only had six directions, if they charged from all four directions, the only way to escape was to sink into the ground or soar into the sky. Thus, Qing and the vagrants jumped over the wall. The manor, with only an annex the size of a mere storage shed, had an abandoned yard overgrown with weeds that was not very wide. They quickly crossed it and kicked in the door of the central room, only to find an old man sitting in a chair as if he had been waiting for them. Despite the sudden arrival of uninvited guests in the middle of the night, he showed no sign of panic, as if he had already known they would come. Then, he flashed his eyes open and spoke. 

"Hmm. In the middle of the night-." 

Boom. A group of vagrants suddenly burst through the back wall. It was Young Master Ma and his group, who were supposed to take the rear. At that, the old man looked as if he was about to say something, but changed his expression to one of nonchalance as if saying, 'I have never opened my mouth', and once again flashed his eyes open. 

"In the middle of this night-."
 
Then, Boom. Cutting off the old man's words, vagrants rushed through the right wall, lining up from side to side and aiming their swords. The old man brushed off the stone fragments that had fallen on his lap and calmly opened his mouth again. 

"If a person is talking-."

Boom. And then, the remaining left wall was also breached, and the vagrant martial artists gathered in one place, surrounding the old man in a circle. Qing thought. No, wait, but their teamwork is absolutely fucking terrible. Why can't they charge in all at once? Why are they staggering their attacks?

"……"

"……"

"……" 

The old man sat quietly as if waiting for something, and only after confirming that everyone had finally arrived, he finally brought up the main point. 

"Ahem. Indeed. I thought you would come since you have audaciously smeared yourselves with the Scent-Chasing Incense." 

"Ehh?" At that, Qing looked at the faces of the two people. 

"I thought it was a rather covert operation."

"Ahem." At that, the old man let out a chuckle.

"What do you expect from vagrant bastards like you? You can't expect anything to be done properly. Even after eating the Blood Strengthening Elixir, you can't beat a couple of kids in a sword fight." 

"Blood Strengthening Elixir!" "Blood Strengthening Elixir!" "Blood Strengthening Elixir!"

About three people shouted at the same time. And since there were many martial artists who had very shocked expressions, Qing thought, 'Hmm, is it some very famous medicine? The bad kind?'

"Seriously, isn't that old man too relaxed? What is his realm that he can be so leisurely? Is he at the Unrestrained Realm or something?"

"Hehe, you are a very amusing child. I am Gyeong Damgan. Indeed, you fools of the Orthodox Faction call me the Frenzied Demon of Blasphemy, don't you?" 

"Frenzied Demon of Blasphemy!"

"An evil villain of the Blood Cult!"

However, Qing could not exclaim along with them because a notification window was flickering and demanding attention in the corner of her vision. Yeah. I knew it would be like this. It's so noisy when I leave it alone. Qing reluctantly brought up the mission window. Some crisis and the Blood Cult, blah blah blah, and at the end, Heavenly Slaughter must kill them all. The end. She had already mastered the fact that the mission window was just noisy and had no substance. Whatever. I'll do as I please. Qing closed the mission window. 

"Hmm. Are you a famous person? Woo Soyeop, do you know him?" 

"He is a Demonic Adept of the Blood Cult……." 

"Is that all?"

"He's also said to commit all sorts of crazy acts."

"Well, his title is Frenzied Demon, so that would make sense." 

The knowledge of the vagrants was wide-ranging because they picked up bits and pieces of information here and there, but it lacked depth.

Frenzied Demon of Blasphemy. A bad guy of the Blood Cult. He uses Demonic Arts. His personality is extremely awful and dirty. The end. 

In reality, just being in the Blood Cult already meant that he was a bad guy who used Demonic Arts and had an awful and dirty personality, so it just meant that they had heard of someone named the Frenzied Demon of Blasphemy from the Blood Cult. It was to the extent that they had only heard of his name.

Qing missed Je Gali-hyeon. Then, she would have heard about the origin of his title, the martial arts he used, his realm, and even unasked-for related anecdotes.

Gyeong Damgan was being far too nonchalant, and the vagrants were already tense because they heard he was of the Blood Cult. They swallowed nervously and sweated profusely. But it wasn't like they couldn't handle one Demonic Adept with so many Masters gathered here. If it were like this, it would be bad. Qing used words to bolster their morale.

"Hey, old man. Can't you see what's going on? Can't you see that we're surrounding you right now? Do you look down on people because they are vagrants? Are you so relaxed because you think a bunch of vagrants can't do anything to you? What, do you think Masters don't get hurt when they get stabbed?"

This was the interpretation. This fucker is looking down on vagrants, isn't he? Even Masters bleed when they get stabbed, so don't be afraid.

At that, the vagrants' morale was restored. However, Gyeong Damgan just let out an unpleasant chuckle.

"Still, I can take more than half of you with me on my way out. What do you think, you vagrants who value your lives so much? Hmm. What is it? Why are you naturally joining in, child?"

"I'm also from a vagrant background?" 

"Was the Divine Maiden Sect originally composed of vagrants? Fine. Then, you should know too, child. If you all attack together, you might win, but do you think it will really end like that?"

At that, Qing answered without hesitation.

"Vagrants have the code of honor of vagrants!"

At that, the vagrants, with their spirits uplifted, responded in unison.

"That's right!"

"Vagrants have a code of honor!"

A thick killing intent formed in the eyes of the vagrants. It wasn't just words; at this moment, their hearts were truly burning. 

"Code of honor, you say? Then, how about this?" Gyeong Damgan flicked his finger.

"Ugh!" "Gaaah……!" "Aaaargh……!" The vagrants fell to the ground at once. They all clutched their chests, groaning in pain, their faces pale as they gasped for breath.

The only ones who were fine were Qing and one other vagrant.

Gyeong Damgan clicked his tongue.

"Tsk tsk, why would you swallow medicine given by a stranger without any suspicion? What if it contained Poisonous Gu?" 

"Poisonous Gu?"

"Don't you even know what Poisonous Gu is? Since you don't know, this old man will tell you. Gu is, hmm, yes. It is a parasite. It releases poison according to the will of its master."

Qing cursed inwardly. Ah, fuck.

There are all kinds of things in Wulin.

Remote-controlled parasites? How does that even exist? What? Do they control it by emitting psychic waves with superpowers or something? Now, the only one who seemed fine was the one who had left half of the pill uneaten, saying he had eaten a pill before. Ah, so that's where he put the parasite. 

"Now, child. You said something about a vagrant's code of honor? Are you going to let them die like this?" 

"Ehhh, you petty old man. Fine, let's fight then. One-on-one. Got it?" As Qing pointed her sword, Gyeong Damgan shook his head.

"Hehe, for reference, if this old man dies, all the Gu will die as well. And the poison that the Gu were holding will burst out at once. Then, what do you think will happen?" 

"Seriously, fuck, how can there be such a convenient ability? Then what do you want me to do?"

"Either this old man changes his mind and releases them, or you call a physician to cut open their stomachs and take them out. But the moment their stomachs are cut open, the Gu will immediately release their poison."

"So you're saying you're just going to toy with people's lives, huh?" 

"Keke, that is this old man's favorite thing to do. So, I will also give you one. If you obediently swallow it, I will spare the lives of these useless vagrants. Indeed, I will uphold the code of honor, just as you said. What do you say? Or will you watch them die?" 

He held out his hand, making nonsensical wordplay, and on it was a cloudy, marble-like object. As Qing focused on it, she could see something wriggling inside the translucent membrane.

However, Qing had eaten many bugs before. In fact, they were nicely packaged, so this was practically a luxury. Moreover, Qing had never worried about an upset stomach while eating all kinds of bugs. If it was harmful to the body, it was all blocked. It was a convenient ability that was practically cheating.

"Haaa, I'll swallow it, so stop tormenting them. Quickly. They're going to die at this rate."

At that, the groaning sounds instantly stopped and only the sound of ragged, gasping breaths could be heard.

"Hoho. You will swallow it? Do you truly not know what this means? Your remaining life is entirely in this old man's hands."

"In return, release these people's Gu. I, I will take their place."

Qing spoke resolutely. Her voice was that of an utter scammer.

"Young Lady, you can't!"

"Young Lady Ximen……!"

Sorrowful voices tried to dissuade Qing. But there weren't many of them? You bastards. So much for a vagrant's code of honor. Well, whatever. I should live my life first before worrying about others, right? That's what you'd expect from the code of honor of vagrant pieces of shit.

To be fair, Qing wasn't really expecting much either.

"I'm fine. If it's just me, and all of you can be safe." 

"Why, why go so far?"

"We are all fellow vagrants, aren't we? A code of honor. I already told you, didn't I?"

At that, the vagrants couldn't raise their heads, ashamed of their own behavior. They were ashamed that they couldn't say they would rather die than to hear her speak of a code of honor.

"Now then. Release these people."

"Keke, why should I? Would a wench like you be worth letting go of all these people? To think I'd have to give up so many just to have one ugly woman with a covered face. If I'm going to do that, my profits are-."

Gyeong Damgan's words suddenly stopped. After all, when faced with a radiant beauty that suddenly brightened up the room, it was only natural to lose one's words. 

"I don't know why everyone goes crazy just because I hide my face a bit. Now then. Is this enough? Isn't one beauty better than twenty dark, ugly men?"

Then, Gyeong Damgan burst into mad laughter. Mad laughter meant laughing like a madman. 

"Keuheukheuk! How remarkable! But what a pity. If you swallow it, I will spare these vagrants, but I never said I would release them."

"You petty-."

"The offer remains the same. If you swallow the Gu, I will spare the lives of these vagrants. If not, they die."

"Ah, fuck it. Give it."

As such, the Gu-like object flew through the air. Qing snatched it and swallowed it without hesitation. At that, the pitiful groans of the vagrants spread out.

However, Qing did not fear poison. But there was one thing she was concerned about.

It's immune to poison, but what about this? Will it die or not? If it doesn't die and stays alive, I can pretend to be controlled and then deliver a critical strike from the back. 