\chapter{A Ronin Has a Ronin's Sense of Loyalty(12)}

Meanwhile, the Guest Hall was filled with a somber atmosphere, as if
someone had died there. In fact, it was so quiet due to everyone's
sorrowful silence that one could hear even the sound of an ant crawling
on the floor.

Because of this, even the sound of breathing felt awkward, so everyone
was being careful to breathe as quietly as possible.

Then, Wang Nopil, a master of the Stone Throwing Fist, suddenly
spoke with a determined expression.

"We cannot just wait like this."

"Brother Wang. But what can we do? If the Poison Human is running
wild, we'll just end up as burdens, rolling around on the floor."

"Are you saying we should just sit here and wait? While we do not even
know what Young Lady Ximen is going through right now, are you
saying we should just sit here and breathe?"

"Then what? If we rush in there together, will it at least make us feel
better to suffer together?"

To that, Wang Nopil shook his head.

"No. But we can seek help from the Masters of the Wulin Alliance. We
have no choice but to go to them and beg them to rescue Young Lady
Ximen."

At that, Dorye, master of the Danyang Sword, intervened.

"That is out of the question. Young Lady Ximen is a woman. If rumors
spread, she will not be able to live with her head held high for the rest of
her life. I am sure that Young Lady Ximen must have had a plan in mind
when she told us to wait. For now, we must trust and wait for her."

"Ha. What is the use of one's honor if they are dead? Young Lady Ximen
is also a former ronin, so she will likely value her life more than such
trivial matters as hono-"

"If you think that way of Young Lady Ximen, then it must be all the more
likely that she had a plan, if she willingly let herself get captured, no?"

The two's opinions were divided.

Wang Nopil insisted on reporting to the Wulin Alliance immediately to
launch a rescue operation, while Dorye believed that they should trust
Qing and wait longer.

At that moment, Ma Yeongjeon of the Jidang Fist interrupted.

"Enough. What is the point in fighting amongst ourselves? Um, I heard
that there is an Elder of the Divine Maiden Sect that Young Lady Ximen
will be joining for the banquet. We should at least inform the Elder of
her sect."

To that, all the ronin agreed.

Thus, they sent a person to the Moocheon Pavilion to summon the
Elder of the Divine Maiden Sect.

As a result, Ximen Surin, who had received the ronin's call, was utterly
dumbfounded and could not even let out a chuckle from how absurd it
all was.

What do you mean, who is calling whom?

There was a limit to how far one could go, even if they had an urgent
message to deliver in secret.

In terms of age, status, and realm, Ximen Surin was a Great Elder of
Wulin, to whom the very act of being compared to mere ronin was a
great discourtesy.

Of course, the ronin could be excused for their ignorance.

Since Ximen Surin did not officially participate in the Wulin
Tournament, she was not even seated in the VIP seats of the Wulin
Alliance, let alone the Elders' seats, which could be said to be for the
Old, Strong Individuals.

As such, it was impossible for mere ronin to know who the elegant
noblewoman beside Qing was.

Even the disciples of renowned sects did not know, and when they
asked those who might know, they were simply told not to ask and not
to approach, so they just shut their mouths.

However, ignorance was ignorance and impudence was impudence.

It was also because when things were so absurd, one became curious to
hear what they had to say.

Thus, Ximen Surin ended up visiting a low-class lodging that she
would never have had any business with otherwise, for the first time in
her life.

"You called for me?"

"Yes. As you are an Elder of the Divine Maiden Sect, there is a fact that
you must know-"

"You called for me without even knowing who I am? That is
interesting. I am Ximen Surin, but are you planning to introduce
yourselves in front of an Elder?"

It was an old woman's mischief.

She intended to inject some manners into the pale and flustered
youngsters.

But alas.

Upon hearing Ximen Surin's name, everyone's faces brightened, and
their eyes lit up as if they had found salvation.

"Godmother! Please help us! The truth is……!"

Thus, the ronin all knelt and conveyed what had happened. They did
not hesitate to reveal their own faults, starting from the acquisition of
the Jamramdan to the Poison Human, the pursuit, and Qing's heroic
sacrifice.

"Y-You, you fools……!"

The rage of the Zenith Among Women exploded fiercely.

Ximen Surin's hair stood on end and a pressure as heavy as a
mountain weighed down on the ronin.

"W-Why, why did you not report it last night! My goodness, the Blood
Cult! Those bastards, they- No! Where is she? Where is she?!"

"I shall guide you immedia-"

"What do you mean guide me?! Why are you not rushing out right now?!"

Ximen Surin's eyes went dark.

It was obvious that her foolish disciple, who was kind and good-natured
to a fault, had stepped forward without knowing what the Poison
Human was or what kind of people the Blood Cult were, all to save
these useless pieces of shit.

Talking about how she would run away if things went south or whatever.

No. Not the Blood Cult. She can't just let this go.

What a terrible state her disciple must be in, having fallen to those
scoundrels, those hideous maggots that cannot even be considered
human.

Just thinking about it made her heart sink and her mind go blank, as if
her soul was being sucked out.

What the hell is that damned Divine Thief doing?!

Was it a mistake to entrust her to him, thinking that the lecturer of the
Hanrim Academy would have good knowledge and character?

Her disciple, who had brightly smiled, saying she would be back soon,
still lingered before her eyes, as if it had just happened.

"Ah. I was surprised since you suddenly left. It seems you ran into each
other. Ah. And these are the ronin."

It feels like she's…

"Master! That's right. Do you know about the Blood Cult? This disciple
has discovered their stronghold. They are truly heinous bastards.
So-"

"XIMEN QING! YOU BITCH!"

Thud!!!

Qing fell to the floor, unable to even scream, and clutched her head.

When it hurt too much, one couldn't even roll around and make a fuss.

Instead, they just froze in the position they fell in. Qing had learned
this fact through her body.

"Young Lady Ximen!"

"Young Laaaady Ximeeeen!"

"Young Lady Ximen! Are you alright?!"

Then, the ronin rushed towards Qing, who was lying on the floor, and
knelt.

Some of the more emotional ones even shed tears, as their gratitude,
relief, and worries for Qing, which had accumulated over time,
exploded all at once.

It was a bit odd to see men kneeling before Qing, who had collapsed,
though.

"H-How could you do this for us……"

"Hey, we're ronin, remember? What did I say? What do ronin value the
most?"

"……It is honor, Young Lady."

"Now. Then, you can all go. You know where the Moocheon Pavilion is,
right? It's on the third floor. You know Dokhwa, right? No, I mean,
Poison Blossom. For now, tell her to prescribe something to stabilize
you guys, so you can all sleep soundly for three or four days."

After urging the ronin, who couldn't take their eyes off her due to a mix
of emotions such as being moved, gratitude, and shame, to hurry up
and leave, only Ximen Surin, with her stern expression, remained.

"I cannot let this go no matter what. What were you thinking, doing
something so reckless? If you wanted to die so badly, you should have
told this old woman. I would have split you in half cleanly."

"Hehe, were you worried?"

"Was that a question?! When I heard that you had swallowed the
Poison Human and were captured by the Blood Cult, I almost passed
out!"

"I-I'm sorry. Ummm. I did not tell you this, but the truth is, my
Constitution is, um, well, I am completely immune to poisons."

"Completely immune to poisons? You mean you have a Myriad
Poisons Invincibility Body? You were simply born with it? That is the
most absurd thing I have ever heard."

"Hehe. Well, something like that. Ummm. It's, well. It's not considered
a good thing, I think."

Ximen Surin glared at Qing.

For some reason, she could not meet her gaze and was clearly avoiding
her eyes, indicating that she was hiding something she was reluctant
to reveal.

If she had been good at lying, she would have been fooled, but she was
so blatantly acting suspicious, asking her not to ask further, that it
made it difficult to press even when she was upset.

"Fine. Since you are immune to poisons, you swallowed the Poison
Human. Since you were confident you could escape no matter what, you
willingly let yourself get captured."

"You know me. If I get tied up, I can just untie myself. And if I get
blocked, I can just break through……"

Ximen Surin sighed deeply.

Since she did not act recklessly without any plan, there was no reason
to scold her further.

It was commendable that she had acted with such righteousness, but
she couldn't bring herself to say so.

"Alright, then. So, where are those Blood Cult bastards?"

"Well, there's a surprisingly large space under Kaifeng."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In Qing's hometown, there was once a time when the saying 'the dream
is grand, but the reality is shit' was popular.

It was the case for Gyeong Damgan, the Intellectual Rampant Mad
Demon.

He, too, had a grand dream.

In his later years, he hoped to burn the last flame of his life, carefully
refining the precious materials that he might never encounter again.

As such, he had more inspiration than ever before, making him all
giddy inside.

First, as a reward for acting so impertinently in the morning, he would
cut off the heads of one or two ronin and bring it to her.

Since there were twenty of them, he could kill about half. After all,
killing ten would still leave ten, so it would be fun to watch them suffer.

Then, if he provoked the ronin with misunderstandings, they would
shout things like, 'It is all because of you!' at the woman while
showcasing cruel and gruesome violence, as well as indulging in
depraved acts.

That would be a nice way to end this.

Yes, it would also be a good idea to use the captured Sword Flower first.

He would put her in the same room and place a luxurious feast and a
bowl of rotten rice mixed with urine, telling them to decide between
themselves which one to eat.

Would the Divine Maiden Sect's disciple make a concession? Or would
she reveal her ugly true nature, unable to endure?

A nice bed and a chamber pot would also be nice.

Since the Sword Flower had already half-collapsed, if he gently
persuaded her to direct her resentment towards the Divine Maiden
Sect's disciple, what a wonderful spectacle that would be.

What if he made the Sword Flower torture the Divine Maiden Sect's
disciple? Wouldn't that be a true masterpiece……

It was such a grand dream.

But the ronin were holed up in the Wulin Alliance and refused to come
out. As if they had all agreed to do so, they remained eternally
entrenched.

Even for the Wulin Alliance, which was full of idiots who had grown
complacent due to the prolonged peace, it was too risky to reach out to
them now.

Since two of the ronin were to participate in the next sparring
competition, should he just wait until then to capture them?

But since he had nothing to bring back, he returned with four innocent
heads to offer to the Divine Maiden Sect's disciple.

He planned to tell her that he had harmed two, so he was returning
fourfold.

Would she blame herself then? Would she be angry?

He wanted to see her tears, but he also hoped she wouldn't break.

As he was wrapping up the four heads and humming a tune, he heard
that the Sword Flower had escaped.

It was the moment when his wonderful plan was shattered.

"What?! You let a woman with the Poison Arts on her escape?! Is that
even possible?! You 병신s! Then what about the Divine Maiden Sect's
disciple?!"

"Uh. Um. She is still in the cell."

"Phew. That's a relief. She can never escape. Since she has a hostage,
kkkheuk! So, what will she do when I tell her that the Sword Flower
escaped? They had a falling out, didn't they? How will she react if I
mislead her into thinking the Sword Flower abandoned her?"

Then, his subordinate scratched the back of his head.

"Well, the Divine Maiden Sect's disciple was the one who helped the
Sword Flower escape."

"What?! But you just said she was still in the cell?"

To that, his subordinate hesitated for a moment before confessing.

"Well, she left and then came back on her own. She said she was
hungry, so she went out to grab some dinner……" 