\chapter{A Ronin Has a Ronin's Sense of Loyalty(13)}

Qing's tongue was a sharp blade certified by the Grand Elder of the
Tang Clan, capable of spewing forth the venomous whispers of hell.

It was no exaggeration to say that if the tongue was a blade, it had
reached the realm of the Formless Sword. After all, it had the power to
drive a person into Qi Deviation by simply turning their rage inside out
with just three inches of her tongue.

However, it wasn't as if Qing had returned with the grand intention of
assassinating the Blood Cult bastards through verbal abuse.

Rather, as a certain piece of shit from some fictional work said, it was
to keep friends close and enemies closer.

It would be annoying if these bastards ran away, after all.

Of course, provoking them was also fun.

"H-How, how did you……!"

"It seems the meals were rather lacking. I suppose the Blood Cult's
finances aren't doing too well, seeing as the hospitality towards guests
is so poor. What's going on? Are you all just a bunch of beggars? Ah. I
was just talking to myself. Anyway, this young lady could not bear the
burden, so I went out to eat."

"How did you escape is what I'm asking! Not why!"

"Ah! Then you should have asked properly. It's like you can't even talk
like a normal human being, just like a complete retard. Ah, my bad.
Don't mind me, I'm just talking to myself again. I keep talking to myself,
I'll be more careful. But to think an old man would eat shit through his
ass because of his age……"

"Wha, what! How dare you, you wench!"

"Arghhh……!"

Qing immediately pressed her knees to the ground, curling into a ball
and burying her head.

"Ahhh, ahhh, aaaaah, haaa, haaaah……!"

Since it was a forced sound, it only sounded like a moan to others, not a
scream.

There was even a Blood Cult warrior who readjusted his awkward
stance.

Of course, since Qing had her head buried, she didn't know and was
just thinking to herself.

Wow, it feels like I'm directly pouring alcohol into my intestines.
Feels fucking lit, you know? I might get addicted to this, hah? Is
this why alcoholics can't quit?

"Hnghh! Hngh! W-What now, are you feeling cocky? You may have
some skill in martial arts, but did you forget that your life is in my
hands? Hnghh! Hnghhhh!"

"Ugh, ugh, so infuriating. It is so infuriating."

"Yes, have you sobered up a bit? You have quite the talent, how did you
escape? And how did you know that bitch called Jian Hua was
captured?"

"Didn't I tell you there was a corpse here? He asked me to suck his
cock."

"S-Stop! What vulgarity! Do not say s-such things!"

Gyeong Damgan had a seizure.

This was because Divine Maiden Sect disciples had to be pure flowers. After all, only then could the joy of deflowering be fully enjoyed.

Qing's eyes lit up at his attitude.

"Hm? Why? Is cock embarrassing? Then, penis? Right. So, he asked me
to suck his penis, so I thought, why not give it a try."

"Stop! Why are you saying such things!"

"Why so demanding? So, he asked me to grind his cock, so I thought,
why not give it a try, and he came right away- Ahhhh!"

"Arghhh!"

Unable to endure the vulgar choice of words from a noble Divine
Maiden Sect disciple, Gyeong Damgan used his poison.

As a result, Qing stopped talking and, 'Ah fuck, why can't people let
me talk?', moaned instead.

"Haa, haa. Yes, if your goal was to scratch at my insides, then you have
succeeded splendidly."

"Did it work?"

Gyeong Damgan's eyes trembled.

Why did just three words make his anger surge to such an extent? It
was to a degree he couldn't understand.

At any rate, Gyeong Damgan understood the situation.

Some dumbass got swept away by his sexual desires, approached her,
and was thoroughly taken advantage of.

Since he had seen the tragedy of this morning, he could understand that
once captured, there would be no time to use his poison.

"Hnghh, then it is this old man's turn to do some scratching. Here. A
present for you."

When Gyeong Damgan gestured with his hand, a Blood Cult warrior
brought a box that had been set aside in a corner.

Gyeong Damgan opened the box as if showing off, revealing four heads
stuffed tightly inside, all with agonized expressions.

However, since there were no familiar faces, Qing just tilted her head.

"What is it? Do you know them?"

"Hnghh, they are innocent civilians. The very ones you killed."

"Oing? What, are these the guys I killed? Then they must have been
guilty civilians."

"You killed them. If you had not acted so impertinently this morning,
my mood would not have soured. And if that had been the case, there
would have been no reason for this old man to kill innocent civilians to
show you."

Gyeong Damgan was full of anticipation.

What will you do? How will you react?

In response, Qing reacted.

"Why are you blaming me for something you did?"

"What?"

"I mean, think about it. I didn't force you to cut their heads off with a
sword. You killed them because you wanted to, so why blame me?"

Qing was from the modern era and had already encountered many
such stories through various media.

It was a logic that few people sympathized with, so Qing, too, had a
hard time understanding it, even after experiencing it herself.

"Can't you understand? If you hadn't caused a scene this morning,
these people would have been alive and well, spending time with their
families. It is precisely you, because you acted so arrogantly, that these
people died."

"Oing? Why? These people died because you cut off their heads. Did I
ask you to cut off their heads?"

"No, you! Argh! Why can't you understand? Think about it! If you hadn't
killed my subordinate, wouldn't I have had to take revenge?"

"But you didn't even tell me about that. If you had threatened to kill
innocent people if I didn't behave, I would have considered it."

"Why are you making it sound like that!! Fine. You don't know these
people, do you? Then, what if I cut off the heads of those ronin bastards
you cared so much about? Would you still say the same thing?"

"Of course, I'd be angry, but that's not because of me. I'd give them a
grand revenge, but there's no reason for me to feel sorry."

"Why does it work like that?! Think! Think, use your brain for once! If
these were the heads of those ronin, imagine that those ronin died
because you acted so rashly!"

"Hmm. Even if I wasn't there, weren't you planning to kill them anyway?
So, even if they were the ronin's heads, how is that any different?
They'd die whether I was there or not, so it's the same, isn't it?"

"Why! Can't you! Understand! It's because of you! Because of you, you
bitch!"

"Why is it all my fault? Then, is it also my fault that you're a bastard,
is it also my fault that you ate your parents when you were hungry, and
is it also my fault that you're impotent?"

"No!! Argh!!!"

Gyeong Damgan exploded.

And then, he exploded once more.

"And where did you hear that I ate someone!"

"It's just my thoughts. Since you're such a son of a bitch, you're
probably capable of it."

Gyeong Damgan exploded for the third time.

"Impotent?! Who said I was impotent!!"

"Uh, so you're not? The members of the Second Coming of Yi Shen
Blood Cult all said that you were impotent, an impotent bastard with a
cock that doesn't even stand."

"Argh! Arghhh! Ugh……"

The elderly Gyeong Damgan grabbed the back of his neck.

This was the power of the absolute, the formless poison, the formless
sword, also known as the Heart Sword.

Then, he glared at Qing with eyes full of venom, before belatedly
activating his poison, as if he had suddenly realized something.

Feeling her insides warm, Qing leaned forward.

But since she had used her voice quite a bit, she decided to just pretend
to be someone who couldn't speak from the pain, instead of moaning.

A fairly ambiguous time passed.

The smallest unit of time in Zhongyuan' measurement was one
gak. It amounted to fifteen minutes in the modern era, so it showed just
how much of a primitive and uncivilized society this was.

About half a gak had passed.

Qing, who had been lying down, slowly raised her head.

"Hey. Isn't that a bit too long? I, uh, might end up passing out from the
pain if this goes on any longer, you know?"

"……?"

"Gu is also a life, you know? How can you just take away the
poisonous liquid they worked so hard to gather? You should be sucking
out the liver of a flea instead."

"You, how."

"Hmm. One. I'm enduring it through sheer spite. Two. I received an
antidote from a friend of the Tang Clan and ate it beforehand. Three. I
ate lunch and got rid of the poison while I was at it. Which one do you
think it is?"

Gyeong Damgan was momentarily at a loss for words.

The poison of a venomous insect gave extreme pain as if the person
was being burned alive. Those weak to pain could have their hearts stop
from the shock.

So, the first option was out of the question.

And since she accurately acted as if she had been poisoned, the third
option wasn't it either.

"Fine, it appears you are feeling quite confident because you ate an
antidote in advance, but do you think its effect will last forever?"

"You chose option two. Well. I won't tell you the correct answer, though.
But if the poison doesn't work, what's left for an old Demonic Adept? A
flimsy underground facility? Or an iron gate?"

Then, Qing took out a bundle of keys from her bosom, shaking them
with a jingle.

"You don't know when I went out and came back, do you? I have these
keys, you know?"

"Damn it! Chains, bring the chains!"

Gyeong Damgan shouted.

Qing watched as the Blood Cult warriors aimed their spears at her
while one of them brought chains and began to wrap them around the
iron gate.

The warrior wrapping the chains was trembling, hurriedly and
frantically trying to complete the seal.

Qing approached, causing spears to extend toward her.

Qing grabbed a spear shaft and pulled it towards her.

"No, wait, what are you trying to do with this? Are you trying to lock up
a woman who doesn't even know martial arts?"

Qing snatched the spears and tossed them back. Finally, she grabbed
the wrist of the Blood Cult warrior who was wrapping the chains.

"Let, let go!"

"You should ask politely. I might or might not let go, depending on how
respectful you are, but that's an order."

Qing pulled the Blood Cult warrior's arm.

As the warrior's shoulder came through the bars of the iron gate, he
slammed his head against it with a loud clang.

But the pain in his head was nothing.

Qing had already grabbed his shoulder and was digging her fingers into
the bone.

"Argh!"

Crack, crack, crackle. It was a sound that should not come from a
human body. It was also a sound that only the warrior and Qing could
hear.

The sensation of muscles, cartilage, and tendons tearing apart
transmitted to her fingertips, through her sensory-awakened fingers
and into her entire palm. Ah. Ahhh.

Finally, the warrior's shoulder was separated.

Qing, having obtained a large chunk of shoulder blade, stumbled
backwards while holding the warrior's forearm.

Then, she blinked with a blank, unbelievable expression.

In the cell, there was a continuous, desperate scream as the warrior
clutched his shoulder, which looked as if a tiger had taken a bite out of
it.

The sight of a human's shoulder being torn off alive silenced the
interior.

Amidst the silence, Qing staggered to her feet and looked at the
warrior's arm in her hand.

Wow. A makeshift club. A green-haired princess, right?

I've only seen this in a screen before. It doesn't look that great in
person, though. I wonder if it'll look like what I saw in the wild if I
remove some of the flesh.

"Now then. Is there anyone else who wants to wrap some chains?"

At those words, the warriors, their faces ashen even in the darkness of
the underground, hurriedly backed away.

Even Gyeong Damgan had completely given up.

"What cruel hands! Is this really something a righteous martial artist
would do?!"

"Ehh. Do you say it's cruel to catch mosquitoes or fleas? Where is it
written that it is cruel to catch pests? What human treatment did you
expect when you're just Blood Cult vermin?"

"Ver, vermin, you say."

"I've been watching how you guys roll, and, uh. I think it would be
disrespectful to insects to compare them to you. Maybe mosquitoes or
fleas are more beneficial to the world?"

Qing said as she casually opened the cell door and stepped out.

At that, Gyeong Damgan stepped back with a start. 