\chapter{A Ronin Has a Ronin's Sense of Loyalty(5)}

Jitan-Gwangma's title meant a madman who found meaning in sighs. In
other words, a mad, perverted bastard who was crazy about the despair
and sorrow of others.

And this was precisely why the Blood Cult was so dangerous.

The reason why the Blood Cult disturbed the world was not for any
justifiable cause like conquering Wulin or revenge, but simply for
personal motives.

At any rate, Jitan-Gwangma was most crazy about, and truly, the
meaning of his life, was the pleasure of pushing others into complete
despair and appreciating their broken expressions.

And among them, there were the best ingredients.

Those who were inherently good and righteous, yet unyielding and
refusing to lose their will, thus possessing a brilliant emotion called
nobility.

And now, Jitan-Gwangma was thrilled at the thought of having one of
the best ingredients in his life.

"Kheheheuk! Heuheukheukheuk! Indeed, it is amazing. Truly amazing.
Honor? To think this child would risk her life for the sake of honor! Is
this not a masterpiece!"

Gyeong Damgan burst into laughter like a madman.

"Yes, what should I do with this child? What would be the best way to
proceed?"

If he could thoroughly break that dazzlingly brilliant, beautiful child
and push her into the depths of despair, making her curse the world as
she wept, what an enjoyable, unparalleled experience it would be…

Ugh, I must calm myself. I must be calm.

Gyeong Damgan barely managed to speak, his expression distorted
from suppressing his laughter.

"Right, a promise is a promise. You rogues can now get lost. If you
attempt to eliminate me, you will only die in pain, so if you quietly
follow my instructions, you may be able to preserve your wretched
lives. Of course, you will have to follow my orders for the rest of your
lives, though."

How exhilarating it was to hold onto their lifelines and force them to
obey.

The rotting expressions of the rogues, who had intuited their fate,
enraptured Gyeong Damgan.

And even in the midst of this, the unwavering expression of the Divine
Maiden Sect's disciple, staring at him, pleased him even more.

Yes, you must be strong.

Be as strong as a brilliant yet solid diamond.

"Aaaagh!"

Once again, a scream spread throughout the area.

The Divine Maiden Sect's disciple also knelt, bending at the waist and
collapsing to the floor, as the Gu worms simultaneously released their
poison.

"Did I not tell you to listen to my orders? If this old man tells you to
leave, you leave. And if I tell you to come, you come. Like an obedient
dog."

Then, the Divine Maiden Sect's disciple spoke haltingly.

"I, I'm fine, so everyone, please leave. I will try to find a way somehow……."

"Kheheuk, Young Lady………"

At that, the rogues, with reddened eyes, left without being able to say
anything further, as they lacked the face to do so.

What a magnificent sight this was!

Gyeong Damgan felt a tingling sensation in his lower parts, which had
been numb his entire life.

Meanwhile, Qing had roughly figured things out.

Hm. So if these things release poison, it feels spicy.

Looks like the worms won't die if they enter my body.

The poison they release isn't harmful, and since the worms are
inside me, they don't seem particularly harmful either.

If the Gu worms were like a piece of chicken gangjeong that was
easily digestible, or if she didn't feel anything even when they
released poison, she wouldn't know when to act sick.

Fortunately, just when her solar plexus felt hot, the rogues suddenly
screamed.

Qing pretended to be in pain to match the atmosphere, and the madman
seemed quite satisfied.

"Keuheukheuk! Child. Yes. You need to be a bit more aware of your
situation. First, then. Yes."

The old man said, clicking his tongue.

"Take it off. Let me see your body."

Qing frowned deeply.

What a crazy perverted old man. He should age gracefully. What is he
doing at that age? Huh?

Qing suddenly remembered, wasn't Yongmopagwi supposed to be a
middle-aged man with a great nose? Why is he an old man?

Regardless, without any hostages, Qing had no reason to listen to him.

"You have quite the dream, don't you. If you give me fifty thousand
gold coins, I'll take it off. Payment upfront, please."

"Keuheukheuk! Good! At first, there has to be some resistance! It's no
fun if they tremble and obediently listen. But what if a child refuses to
listen?"

Then, it felt like a shot of liquor in her solar plexus, warm and fuzzy, as
the Gu worms released their poison.

Qing immediately fell to the floor, going heueok, haeuk, and pretending
to moan in pain.

However, unlike when Qing was genuinely in pain, retching and
making sounds of phlegm, her fabricated moans sounded more like
lewd groans, going ahk, heuut, aahk.

Of course, Qing couldn't possibly watch a video of herself acting, so she
was confident in her performance.

As Qing acted out her seemingly lewd act of pain, she thought.

This is pretty decent. It feels like I've had a drink when the worms
release their poison. Isn't this just fucking amazing? It's like an
unlimited supply of free alcohol!

As Qing was thinking about her favorite alcohol, her thoughts naturally
became sharper.

Unlimited supply? There's no way that's possible.

In the end, these tiny creatures can only make so much poison, right?

Besides, they are parasites in the end, so they have to eat something
to make poison. So the amount they can store must be limited since
they can't just keep making poison every time they eat.

Since Qing wasn't affected by poison, it wasn't a particularly useful
deduction.

On the other hand, if she had asked someone like Zhuge Ihyeon, she
wouldn't have had to go through the trouble of deducing it herself.

After all, it wasn't really a secret that was difficult to obtain information
on.

This was why people had to learn.

\todo{missing section}

"Good. Let's see how long you can act so carelessly."

As Gyeong Damgan said that and struck the floor, a hidden lid opened
after a moment, revealing a secret passage.

Naturally, the lid was manual.

Upon seeing the hand opening the secret passage on the floor, Qing's
eyes lit up.

There are Blood Cult bastards below!

Wow! The Blood Cult! Wow! Bad guys!

"Now, go in."

Gyeong Damgan gave the order.

Qing obediently descended the stairs leading underground.

As she entered the dark stairwell, the ominous purple light in her eyes
flickered.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

While Qing was subjected to the terrible Gu and kidnapped to the
frightening secret base of the evil Blood Cult-

Or rather, while the terrifying Qing, with a bottle of Gu worms
embedded in her, was infiltrating the secret base of the Blood Cult-
Cheon Yuhak wasn't just playing around.

As soon as Qing smashed the door of the manor with the rogues and
barged in, a figure quickly escaped over the roof and urgently fled.

"Tsk tsk. As expected."

My disciple is so clumsy.

Cheon Yuhak clicked his tongue and flew. If Qing had known, she
would have argued about who was actually being clumsy.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

What the hell? How can ancient China, in its primitive era, have such
well-constructed underground facilities? Shouldn't underground
levels be something that developed in the modern era?

Of course not.

Underground construction was one of the specialties that all humans,
who were somewhere between chimpanzees and monkeys in the
Middle Ages, engaged in.

And in Zhongyuan, cities near large rivers were basically a
series of cities built on top of the sediment that buried them during
floods.

Therefore, there were underground structures upon underground
structures, so using the heritage of their ancestors made it very
convenient to build underground bases.

Thus, in an underground prison that not even a single ray of moonlight
could penetrate, where only a tiny oil lamp illuminated the inside of a
cell, Qing lay down leisurely.

This place is really not treating its prisoners well.

How can they not even provide a single sleeping mat? I don't expect a
pillow, but shouldn't there at least be a tattered blanket?

It's cold, hard, and uncomfortable. How am I supposed to sleep in a
place like this?

Exactly half a gak later.

Qing was snoring. Drrrrrrng.

And within Qing, the exhausted baby Gu worm had finally regained its
senses.

Originally, plants produce their own poison.

However, animals that had poison, referred to as poisonous creatures,
had to eat something poisonous to make their poison.

Gu worms were the same.

Gu worms actually started as beneficial parasites that lived in the
human body, eating harmful substances. Only after methods to handle
specific species were developed did they become a means to control
others.

Meanwhile, although the Poison Blood Constitution prevented Qing
from being affected by poison, it did not purify and eliminate poison
like some mythical artifact.

It just meant that the poison that entered her body did not harm her.
Instead, it stayed in her body until it eventually decomposed over time
or was expelled.

And the poisons that remained in the body did not go anywhere else.

Thus, the baby Gu worm, having regained its senses, wriggled its hungry
belly and wandered through Qing's intestines, searching for
something to eat and fill its empty venom sac.

It was truly a gluttonous creature that was the very definition of a
parasite.

Then, it reached a certain spot and tasted a drop of bile, and oh my!

In all its worm life, it had never tasted such a divine crystallization of
poison.

The Gu worm wiggled its tail and greedily devoured the bile.

As it sucked on the bile, the color of the Gu worm very, very slightly
deepened into a more reddish hue.

Of course, this was something that Qing, who couldn't see inside
herself, didn't know, and likewise, something the Gu worm, which had
no eyes, didn't know either.