\chapter{A Ronin Has a Ronin's Sense of Loyalty(6)}
The greatest beauty that Gyeong Damgan considered was despair. The
moment when all determination was lost due to disappointment and
frustration with humanity, when one fell into a bottomless pit, that
moment was the very reason for human existence.

However, beauty was always precious.

Weak-minded individuals who collapsed with just a little bit of
torment were only a brief source of entertainment. But even then, his
threshold had risen due to his long artistic experience, so now he felt
hardly any stimulation.

Yes. Just like that thing over there.

If it hadn't been for the mission, he would have already discarded it as a
material of the lowest quality. But when one's hobby and job were one
and the same, the hobby would have to eventually yield. So, he was
keeping it around for now.

Then, while he was thinking about such things, a material that
surpassed the highest grade, no, even a special grade, came in. How
should I trim this to see an even more beautiful despair?

Gyeong Damgan's mind was only focused on that.

For now, he had decided on the finale.

Since the moment a woman broke was usually when her chastity was
violated by brutal violence.

If he made her suffer all day long at the hands of those bastards she
tried to protect, what kind of reaction would that child have?

Everyone had a different reaction when they broke; would the Divine
Maiden Sect disciple cry or would she scream in agony? Or would she
just give up, like a living corpse with lifeless eyes?

"Keuheuheuk."

Just thinking about it excited Gyeong Damgan, who couldn't suppress
a strange laugh.

So then, how should I torment her before that?

She's a tough one who can withstand the pain of the Gu poison that
would make anyone collapse, so she won't give in to physical pain,
will she?

Then how should I slowly break her spirit? How can I give her a thin
thread of hope so that she doesn't give up, but at the same time, make
her soul gradually wither away……

It was when Gyeong Damgan had thrown off his pants and was having a
good time with such pleasant thoughts.

The door burst open and a subordinate rushed in.

"Sub-leader! You need to come out now, hu-hurk!"

The subordinate, who faced cosmic horror due to the visual stimulus,
could not continue his report.

"……You bastard!"

Gyeong Damgan, who was sent flying, grabbed his subordinate by the
neck. The sin of disturbing his most enjoyable moment and the sin of
witnessing his superior's disgrace were punishable by death.

"Keo-eok………"

As the subordinate lost consciousness, he thought.

Fuck, the hand that's choking me right now… Fuck, fuck. It's dirty.
Fuck, this impotent bastard who can't even get it up. Why not use a
sword instead……

After throwing away the corpse that had once been his subordinate,
Gyeong Damgan locked the door.

It was originally the fault of the one who did that without even locking
the door.

As such, the Blood Cult martial artists were the ones placed in a
difficult position.

"When is the Sub-leader coming?"

"I sent the youngest, so he should be here soon."

"Why isn't he coming when I told you it's been a while since I sent the
youngest?!"

The Sub-leader did not appear and the youngest, who had gone to fetch
him, did not return.

"Argh!"

The Blood Cult martial artists could only helplessly watch the situation,
not knowing what to do.

The beginning of it all was during breakfast.

"Wake up, wench!"

"Agh. My body aches from sleeping on the cold floor. Ugh, I couldn't
even sleep well. What's going on?"

Qing grumbled, having slept soundly without waking up even once
during the entire night. The guard who had to listen to her even
breathing and cute snores all night was speechless.

"Now. Here's your breakfast."

"Oh. Breakfast right after I wake up. I like this one thing at least. So,
what is it? Is there anything good?"

Qing was polite to those who gave her food.

This was because if she was rude to them, she wouldn't know what
they would do to her food the next time.

"You really do have it easy, don't you? To think you're not even
thinking about us. Here. It's a rice ball. Take it."

"A rice ball……"

Qing examined the guard.

The size of the large rice ball in the guard's hand was generous and
satisfying, but he didn't have anything else in his hands.

No soup in the morning……?

But still, who am I to complain when they're feeding me?

"Thank you. I will enjoy it."

Qing politely thanked him and reached out her hand through the bars.

And it was just before her beautiful, long fingers were about to touch
the rice ball.

Thud.

With an obviously intentional gesture, the rice ball fell freely. The
round rice ball fell to the cold, hard ground and splattered.

"Huh?"

"Keke, did you think this was some kind of restaurant? Now. Look. This
is your future."

The guard crushed the rice ball with his foot.

The poor rice ball was left as a flattened, mashed up food waste on
the ground.

"You will only have this to eat. Kehe, this is truly the very definition of
the Greatest Beauty Under the Heavens. When will it be my turn, kehat,
what are you doing? Are you going to eat that?"

As Qing reached for the rice ball, the guard asked with a sneer.

The hand that was slowly reaching for the rice ball suddenly moved like
lightning and grabbed the guard's ankle.

"Uh? What?"

While the guard was flustered, Qing reached out her other hand and
grabbed his other ankle as well.

"This fucker is playing games with me since the morning. I hate those
who play with food the most, you know."

"Let, let go! What is this strength……!"

The embarrassed guard tried to shake her off, but his ankles were
firmly held, as if they were stuck to the ground.

Well, that was just how it was. After all, it was Qing's monstrous
strength that held onto him. What else could one expect?

"Hey? What do you think will happen if I pull you just like this?"

Qing was sitting on the floor, leaning her upper body forward with both
arms stretched out to grab the guard's feet. And between Qing's arms
stood an iron bar.

As the blood drained from the guard's face, he drew the sword at his
waist the moment-

Qing straightened her back and lay down.

The guard's legs flew into the cell like cannonballs, eventually getting
caught between the bars.

Crack! The sound of bones and iron colliding.

The guard's eyes rolled back and he foamed at the mouth.

But that was only the beginning.

As Qing massaged the guard's feet, her hands traveled up his calves.
Crack crack crack. The bones shattered and became limp like an
octopus' legs.

"KAAAAAAAAAAH!"

Qing trembled at the sensation of crushing the bones into tiny pieces.

Wow. It's been a while. This is… really… It's even better than I
remembered. Wow, this is what life is about.

Qing grinned savagely and spoke.

"Shh. Customer. Your legs are very stiff. If you don't loosen them up,
you'll keep walking or running, you know. How can a person just stand
and wander around when they should lie down or sit?"

"AAAAAAAAAAAGH!!!"

Finally, the guard's leg bones were ground into sand, so Qing tied his
two legs together into a knot.

"GYAAAAAAAAAAAAH!!!"

Not even an hour had passed, yet the guard's voice was already hoarse.
Hearing the desperate screams, the Blood Cult members rushed over.

"Wh-What are you doing! Let go, let, ARGH!"

Startled, the Blood Cult member who tried to separate the guard was
grabbed by the wrist.

Then, after banging his head hard against the iron bars, his arm,
softened by Qing's bone massage, was wrapped around the bars twice
before being pulled inside and tied sloppily.

As such, the remaining Blood Cult members could not dare to approach
the cell. Among them, the youngest, who was kicked in the shin and
told to bring the Sub-leader immediately, quickly ran off.

And now…

"Would you like to have the hostage back? Then, I shall relay my
demands. One plate of stir-fried meat, two bowls of freshly cooked rice.
And for the soup, um, something mild and clear? What is your cook
good at?"

"Shut up! Right now……"

"Eh, this restaurant doesn't treat its customers very well. Okay then, a
clear soup. A refreshing one with freshwater fish boiled thoroughly.
Then, I will return the hostage. That is all. I will repeat. One plate of
meat, two bowls of rice, and one bowl of clear fish soup."

Two different types of sounds seemed to ring in Qing's ears.

The sound of the Blood Cult members being dumbfounded.

And the sound of their patience snapping.

"You, crazy, where did they even catch such a crazy bitch, where is the
Sub-leader?"

"Well, the youngest's corpse is in front of the door……"

The second-to-last, now the youngest, member reported that fact.

"Is that the problem right now!? Why aren't you bringing him here
immediately! Can't you just run!?"

Fucking bastard. It's not like you're the one going.

The youngest member swallowed the curse and ran off again. But he
had no intention of knocking on that door, so he planned to just stand in
front of it and report when it opened on its own.

So, the second youngest also didn't return.

"Oh my. You ordered a while ago, but there is still no word? Are the
cooks planting the rice seeds right now? At this rate, I'm going to
become an old lady, you know?"

"Just, shut up!"

"Ah. I'm so scared. So scared that my hands are shaking and I might
just throw a fist. Wow, look at my hands shaking."

As Qing spoke, she grabbed the tied-up martial artist's hair and
smashed his head against the iron bars.

"Argh! Argh! Argh!"

The sound of the head hitting the bars, along with the screams, were
truly entertaining. Then, with a crunch, she felt a crack, so Qing let go.

The iron bars glistened red in the lamplight.

"Uh, what should we do? Where is the Sub-leader……!"

"Damn it! Just give her what she wants! Bring it to her!"

Thus, eventually, she received a satisfactory breakfast.

After carefully placing the tray that came in through the cell's serving
hatch, Qing approached the two Blood Cult members tied to the bars.

"Well, thanks to you, I had fun. In your next life, you should live
kindly so you don't suffer like this."

Qing's hand turned black, then, Pop! The head of the tied-up Blood
Cult member burst like a watermelon.

The headless corpse slid down the bars it was tied to with its arms.

The half-castrated guard, who was sitting with his legs halfway tied,
screamed, 'Hiiiiiiik', squirmed, and then, unable to even scream due to
the pain in his legs, just opened his mouth wide.

"St, Stop! You promised to release the hostage!"

"Me? I just asked if you wanted to have the hostage back."

After saying so, Qing squatted down this time and raised the Black
Hand of the Black Killing Demonic Arts.

At that, the tied-up Blood Cult member met Qing's eyes and pleaded.

"Save, save me please……"

"Three hundred fifty points."

"What is th-"

Pop! Similarly, a headless corpse slumped, tied to the bars by its legs.

Qing tried to wipe her face, then paused, stopping her hand.

Soon after, she wiped the debris that had splattered on her face with
the inside of her elbow sleeve.

"Ahhh. So refreshing after a morning workout. After all, exercise
makes one's appetite better. It's not good to eat as soon as you wake
up."

Then, she approached the tray that had been carefully set aside and
began her breakfast.

Even in the midst of all this, Ximen Surin's style of eating like a beauty
shined. It was quite a sight to see such a peerless beauty sitting
daintily, eating her meal.

As such, the Blood Cult members stared blankly at Qing's appearance.

They were dumbfounded, absurd, and in the midst of it all, she was
pretty, so…

It was when Qing had nearly finished her meal that Gyeong Damgan
appeared.

As soon as he showed his face, he cast his Gu poison instead of
greeting them. Qing, who was about to reach for the last piece of meat,
scowled at the rising sensation of alcohol.

Tsk. I told you not to disturb someone while they're eating.

Qing hastily chewed and swallowed the food, then rolled to the other
side of the tray.

"Aheuuuuk……!"

It was a slightly unnatural sight.

Gyeong Damgan felt a strange sense of incongruity, but he soon missed
it as a moan, like a mating call, tickled his ears.

"S-Stop, stoooop………"

The desperate plea satisfied Gyeong Damgan, who stopped spraying
the poison.

"You caused quite a commotion this morning, didn't you? Don't you
know how cruel a woman of the Orthodox Faction can be when she
turns vicious?"

"I heard you're a wandering warrior, not even part of the Orthodox
Faction? Also, old man, are you losing your mind already? Wait! Stop
the poison! Stop it. I said stop. A bit. Heuk………"

Gradually, Qing was getting tired of pretending to be in pain.

If it hurts, people don't usually scream, so she thought that now she
should just bury her face and tremble without making a sound.