\chapter{A Ronin Has a Ronin's Sense of Loyalty(10)}

Mo Yong Ju Hee had been holding back her screams the entire time.

Or perhaps she hadn't been able to.

The gruesome feeling of flesh being torn apart. The guard's endless
screams. Her ears were muffled as if she was underwater. Whether her
own screams were mixed in or not, she couldn't tell.

Dismantling a human body was dirty and horrific.

Even if it was her deeply resented enemy, whom she had wanted to kill
so badly, it still felt horrible.

And yet, the clean voice whispering in her ear was so sweet and
soothing in this terrible place, in this world that was full of only terrible
things, terrible times, terrible memories, and a terrible self.

"You did really well. Next, let's take a look at the torso. Shall we open
the abdomen? Like this, here."

A white, long, beautiful finger traced the guard's belly, cutting through
the skin as if a sharp blade had been attached to it. The skin split open
smoothly, revealing the insides.

Yellow, lumpy fat was exposed.

The finger passed through once more, and only then were the inner,
pulsating organs fully revealed, soon to be submerged in the shallow
pool of blood that had accumulated.

"Ugh."

"Oh my. Young Lady Mo, you have a weak stomach, don't you?"

"No, no, it's okay. I can endure it."

No, I can't look pathetic.

Mo Yongjuhee desperately suppressed her nausea.

If I look pathetic, Young Lady Ximen will… She came to save me, and
she's so warm… If I look pathetic, she'll abandon me. Just like everyone
else.

"Even if it looks disgusting, if you look closely, it's actually quite
endearing how carelessly it's made. It's called the Five Viscera and Six
Bowels, you see? The Five Viscera are."

"Urp, uweeeek……!"

Mo Yongjuhee could not hold back the rising vomit any longer. The
empty, pale stomach acid poured into the open abdominal cavity.

However, as the acidic liquid splashed onto the organs, the guard's
body convulsed as if malfunctioning, his already boneless and limp
arms flailing wildly. In that moment, it slapped Mo Yongjuhee's cheek
with a wet thud-

Ah, no……

"Hic, haah……. I'm sorry, I'm sorry. I'm sorry for making you dirty. I'm
sorry……"

"Oh dear. It's okay. It's okay. Yes, it happens. Those damn bastards, they
should have at least left a chamber pot."

Mo Yongjuhee struggled to get out of Qing's embrace, out from under
her thigh. No. No.

"It's okay. It happens. It's not your fault, Young Lady Mo. You have
nothing to be sorry for."

"Let go! Let go of me! No. I'm sorry, please let me go. I'm dirty. I-"

"Shh. Young Lady Mo is not dirty. You told me, didn't you? You said you
didn't do anything dirty or shameful. You endured well. You did great."

Such warm acceptance. Tears welled up in her eyes. Yes, if I just listen
to her, if I just listen-

"Now. He's about to die. Shall we watch this bug die together? This
an insignificant creature was the one tormenting you, Young Lady Mo.
There is no need to be afraid."

Mo Yongjuhee looked at the dying guard.

His limbs were twisted, with muscles exposed and bones showing in
places. His abdomen and chest were wide open, revealing his insides
while he barely clung to life, making gurgling sounds.

"Now. There. Look at his eyes. He's desperately pleading for help, isn't
it? Isn't it interesting? Such a wicked person begging for help so
humbly and earnestly in the face of his own death."

"Hiccup……!"

Mo Yong Ju Hee desperately swallowed her screams at the sight of his
desperate, bloodshot eyes begging for his life.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the distant past, Qing's grade for Liberal Arts Psychology was topnotch.

It wasn't that Qing was a particularly eager or studious student with
exceptional understanding, but rather that she had succeeded in
staying awake in a class notorious for its tediousness, where attendance
was 50\% of the grade and 50\% of the students failed because of the
attendance alone.

If the Liberal Arts Psychology professor could see Qing now, he would
be pounding the ground in regret.

Counseling a client involved unconditional acceptance, affirmation,
and empathy to heal their wounded heart.

The biggest taboo among them was to suggest a solution. If it were that
simple, they wouldn't have been hurt in the first place.

Qing got it all mixed up and did exactly the opposite.

In her own way, she was trying to be considerate.

Revenge often loses its satisfaction and leads to emptiness, which in
turn can make life feel futile, right?

So she thought that seeing the agonizing pain of her enemy would
provide the utmost comfort.

Humans tend to assume their own thoughts are universal, so she
believed that her gruesome anatomy lesson would be helpful to Mo
Yong Ju Hee as well.

"Young Lady Mo, are you feeling better now?"

But if such drastic anatomical methods were effective for healing the
mind, Mo Yong Ju Hee would have to have been born with an ominous
star like the Earthly Fiend Star or the Earthly Ferocity Star, if not the
Heavenly Slaughtering Star.

If Qing had allowed her to strangle her enemy, she might have felt
better. But the kindness she showed was just another form of torture
for Mo Yong Juhee to endure.

"Yes, yes, I, I did well, right? You told me to do this, so I did everything
you told me to. You won't abandon me, right? You won't leave me, right?"

"Abandon? Don't say such things. Of course, Young Lady Mo was a bit
of a pain in the ass, but-"

"I was wrong. I'm sorry. I'm sorry. I'm sorry. I'm sorry. I did wrong, so I?
No, you! It's all your fault! It's all because of you! If only you hadn't! It's
your fault! Take responsibility! Of course, you have to take
responsibility!"

Oh dear. Qing thought with an 'I knew it' expression.

She's still not in her right mind.

I can't even make jokes.

But if I do this, what am I supposed to be?

Qing sighed deeply.

Mo Yongjuhee shuddered.

Then, she crawled on her knees, scraping them, and clung to Qing's
legs again.

"No, no. It wasn't sincere. Please don't abandon me? Okay? I have no
one but you now, Young Lady Ximen. I, I did everything you told me to. I'll
listen to you well from now on. What should I do? What should I do?
Yes, that, you like breaking things, right? Shall I, shall I smash his
head? Or should I gouge out his eyes? Will you believe me then?"

"Don't play with dead bodies."

"Ah. Then, then what should I do? Just tell me and I'll do anything……"

Qing hugged Mo Yong Ju Hee tightly again.

"I'm sorry. It was a joke. I'll never abandon you, so don't worry. Shush."

"Yes. Yes. Yes."

Qing tried to sigh again but held it in.

Well, I guess it's understandable that she's terrified of being left
behind.

"Um. We should get back to the surface for now. Young Lady Mo, can
you wait here for a moment? I need to clear out some Blood Cult
bastards on the way out-"

"Let's go, let's go together! Don't leave me!"

"They might use Blood Puppets, and you'll be in pain again. Pain is
bad, you know. If you wait here for a bit, I'll clear the path quickly-"

"It's okay! It's okay, so let's go together. I can endure the pain. I'll
endure it, so don't leave me, don't leave me alone……"

Qing scratched her head.

Why is she being so difficult and annoying? Ugh.

"The poison from the worms doesn't kill you, even if it hurts. Can you
really endure it?"

"Yes! I can endure it. So-"

"Alright. Get up. Let's go out and talk."

Mo Yongjuhee grabbed Qing's hand and struggled to her feet. Then,
staggering and trembling, she took a couple of steps before stumbling.
Qing quickly caught the falling Moon Yong Ju Hee.

"Young Lady Mo? Your feet, those damn bastards, your toenails-"

"It's okay. I can walk. It just hurts a little."

"How can you walk with all your toenails ripped out? That's not
possible."

"No, I can walk. I can walk!"

"Calm down. Yes, you can walk, but it will hurt a lot. I'll carry you.
Here."

In the end, Qing tied Mo Yongjuhee tightly to her back with the guard's
upper and lower garments.

Mm. This is… the greatest invention of humanity that surprised the
entire world and drew admiration, the Korean-style baby carrier,

Podaegi.

I don't know why it's turning out like this, though.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

She had heard that the Commander had not been seen since last night
and that the Vice Commander had left in the morning, saying he had
business to attend to. As such, it was the perfect opportunity to
smuggle out Mo Yongjuhee.

Qing had a rough idea of the underground paths, but it wasn't easy to
navigate based on verbal descriptions.

Still, Qing wasn't particularly worried. After all, if she didn't know, she
could just find someone who did. Smart people should make use of
others, as was only right.

So, she leisurely concentrated on finding signs of people while strolling
around, until she finally located her target.

"Wh-Who's there! Here, ugh."

As Qing stomped her foot, a black shadow lurched and swiftly moved to
cover the Blood Cult warrior's mouth.

However, the Toxin Arts were not controlled with words.

The area around his solar plexus burned as if on fire, and if this
continued-

"Agh……!"

With the painful groan, Qing's head suddenly sparked with pain.

When a person's pain exceeds what the mind can handle, they
instinctively grab onto something and try to crush it with all their
might.

Even to the extent of damaging the tendons in their grip.

It was the monstrous strength that ignored the limits that the brain
usually imposed unconsciously to prevent injury.

Since Mo Yongjuhee was carried on Qing's back, there just so happened
to be a sizable handle in a very convenient position.

"Ack."

Qing's mind turned completely blank.

It was pain comparable to practicing the Nine Yin White Bone Claw.

There were more vital points for female martial artists than for male
ones.

Unable to even scream, she collapsed and writhed on the ground.

The Blood Cult warrior was dead, but the toxins were still alive,
continuing to send pain signals. It was a terrible agony that lasted for
about a quarter of an hour, until they finally realized their host's death
and calmed down.

This was karma.

It could be said that she was punished for forcing Mo Yong Ju Hee into a
horrific forced-killing experience.

"I'm sorry, I'm sorry. I'm sorry. Please don't abandon me, I'm sorry. I
didn't mean to. I'm so sorry. I really didn't mean to, I'll do whatever you
want, ah! Young Lady Ximen likes pulling out fingernails, right? If that's
what you want, I have ten of them……"

There's nothing I can do about this.

Qing peeked at her front.

I don't think it was ripped off. Is it just swollen, maybe?

It still throbs with pain. It hurts so much. Is this okay? It hurts a bit too
much, though……

"Haaa. It's okay. And who said I like pulling out fingernails? What kind
of terrible slander is that? Though I do like it, but. Still."

Qing tore off the Blood Cult warrior's sleeves and made Mo Yongjuhee
clutch them in a bundle to prevent a recurrence.

Thanks to one failed attempt, the second attempt was a success.

After a Blood Cult warrior was subjected to a parasite removal
procedure that involved a hole being drilled in his abdomen, he was
deeply moved and became a friendly guide, thus resulting in a real-time
job change.

"If you go this way, it's the northwest path. S-So, then, as promised……"

"Yeah, yeah. I'll keep my promise. But I didn't promise anything with
Young Lady Mo, did I? Young Lady Mo? Please do the honors."

Mo Yong Ju Hee reached out both arms and snapped the Blood Cult
warrior's neck.

With the neck twisted more than ninety degrees, the Blood Cult
warrior was discarded as Qing briskly climbed the stairs.