\chapter{A Ronin Has a Ronin's Sense of Loyalty(2)}
	
Afterward, the rogues got together to compare their notes, starting
with the physical descriptions.

Then, Chun Yu-hak took out paper and charcoal, sketching and
adjusting the image based on the stories that emerged.

"Oh? Were you perhaps an artist? To think you would come so
prepared. It seems the Young Lady was even more serious than we
thought."

The warriors' gazes toward her grew warmer.

Honestly, who in the world would go out of their way to take care of
rogues?

As freelancers without a sect who were often used as cheap swords or
as meat shields, they were quite sensitive to even the slightest bit of
warmth, especially since they were often subtly looked down upon as
robbers when they had no jobs.

Even if she was a slightly inferior disciple of the Divine Maiden Sect,
Qing was still a female expert of a renowned orthodox sect.

And here she was, not just running off to the Wulin Alliance to report
them, which would have been a perfectly understandable solution, but
actually taking care of them, saying that they shouldn't be harmed.

Naturally, they were moved by her kind heart.

"Hmph. I am always serious."

Qing naturally took the credit.

Even though Chun Yu-hak's eyebrows twitched, it wasn't the time to go
around calling her out for acting like a bitch.

Since everyone's accounts differed slightly, the reliability of the
composite sketch made from the testimonies of several people was not
particularly high, just like the case with the mole.

However, unlike the composite sketch of the mole, which was based on
testimonies from people who didn't really care and just took the money,
these independent warriors were quite sincere. As such, after discarding
a pile of paper, a portrait that everyone agreed upon was produced.

"Hmm. He has an ordinary pig's nose……"

The only characteristic of an otherwise ordinary-looking person was a
snout. Moreover, even after actually seeing such a distinct feature in
person, the warriors had no idea who he was. So, it was obvious that
they wouldn't recognize him from just a drawing. Naturally, Qing
didn't have the insight to look at it and say something like, 'Oh, this
person looks like so-and-so'.

"For now… He will definitely show up in front of you all again."

"How can you be so sure?"

"Uh……. Criminals always return to the scene of the crime, don't they?"

"Indeed!"

"The Young Lady's ingenious deduction truly shines!"

Admiration burst out from here and there.

The warriors, who had been thoroughly buttered up, were completely
won over.

Now, they were ready to clap and agree with any bullshit that Qing
spouted.

Again, rogues were a group of people fundamentally starved for
affection.

"Besides that, you are all practically caught in his trap. Since the
Stupefying Incense Pellet is an expensive item, it probably wasn't just
to extort money. More than likely, he'll try to blackmail you into doing
something shady."

At that, the warriors' expressions darkened.

As they listened, they realized how rash they had been to suddenly
accept and take a suspicious drug, just because it was called the
Shin-Tu.

However, even if the genre was changed to a Rogue's Regret and they
went back in time, the decisions made by these freelance warriors would
not be so different.

That was just how desperate they were for the Hidden Dragon
Tournament.

And the actions of desperate people were easy to predict, as well as
manipulate.

"If you can capture him, that would be great, but since he might be
dangerous, don't try to provoke him. Just do this instead. Here, take
one each. It's called Tracking Incense. You all know what that is, don't
you?"

Qing distributed the medicine bottles that Chun Yu-hak handed to her,
one for each person.

"When you meet him again, secretly sprinkle it on him. You don't have
to splash it on his face. Just a little on his pants or something is fine."

That was the conclusion they came to.

If they met again, they would apply Tracking Incense.

Even if one person failed, there were several people, so at least one
would succeed.

And afterward, they would gather and capture him.

After that, they would use appropriate methods to extract the purpose,
any potential mastermind, and ensure the secret didn't leak.

It seemed somewhat sloppy and there weren't any concrete details,
making it a rather simple plan.

However, considering it was Qing, this was a very brilliant idea. In fact,
it was to an extent where everyone should stand up and give her a
round of applause out of respect.

"Uh…… But, you see."

The Chair King, no, Rogue Wang Nopil, cautiously spoke up.

"But if we suddenly drop out, won't he think it's strange and become
suspicious? We managed to reach the Sweet Sixteen with great
difficulty and if we don't take the medicine, I think he will certainly find
it strange. I don't necessarily mean that I want to take the medicine,
but……"

The latter part of his sentence was quite pathetic because Qing's
presence became increasingly ominous.

"What, you want to eat the Stupefying Incense Pellet? What's the
point? Do you want to get your ass beat?"

If he ate one more, he would surpass a hundred points in Evil Karma.

He would change from a stupid, pitiful guy who was being used to a
stupid, pitiful, AND evil guy who was being used.

"Well, if you can get some other Stupefying Incense Pellet, then eat
that……"

"If you have something like that, don't ask for my permission. Just use
your own judgment. But if you're roaming around Kaifeng asking for
Stupefying Incense Pellets, don't you think anyone would notice
something's up? It's better to act like the guy who distributed the
medicine is suspicious and didn't take it. He'll probably show up again
asking why you didn't, you know?"

Qing sighed deeply and answered as such.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There was really only one person she could show the painstakingly
created composite sketch to.

"Jegalyi, do you perhaps know who this is?"

"Hmm. Is this some sort of test? Mmmm."

Jegal Ihyeon looked at the sketch for a while before suddenly slapping
his fan.

"Oh? Do you know who it is?"

"I do not know. After all, a composite sketch is not a very reliable thing.
However, this drawing's style does not look like art. I only know that
the artist's lines are unusual."

Jegal Ihyeon was still just a rising star.

If it was a name or a nickname, he could have listed some information,
but he wasn't confident in identifying someone from just a drawing.

"What the. Why did you hit your fan then?"

"Wouldn't it be alright for a person to hit their fan, Big Sister?"

Jegal Ihyeon answered with a grin.

Qing tilted her head.

What's going on? Why is he being a prick?

It wasn't enough to warrant a nuclear launch, so it was indeed the
flesh-and-blood rising star most anticipated by the Jegal Clan, known
for their deep schemes and intricate plots.

Honestly, finding the guy who distributed the medicine wasn't that
urgent of a matter for Qing, nor was it some lifelong vendetta she had
to settle in a bloody revenge.

It was more like, 'Since there's a bad guy doing bad things in my line of
sight, I should find him and beat the shit out of him'.

She also didn't like how the Hidden Dragon Tournament's reputation
was being tarnished because of the winner.

Thus, it wasn't like Qing was desperately waiting for the bad guy to
show up.

As such, while preparing for the tournament, she hung out with the
Half-Sword and Twin Daggers, enjoying the stimulation of blades
digging into her skin as if she was addicted. Eventually, she found
herself standing in the Sweet Sixteen of the Hidden Dragon
Tournament.

Her opponent in the Sweet Sixteen was someone Qing knew.

"……Mount Hua's…… Please……"

It was Changbin, who, come to think of it, never showed up when she
told him to come to the Mucheonggak.

Still, since they were somewhat close, she thought of herself as one of
the few women he could comfortably converse with. But for some
reason, he was speaking gibberish.

Qing giggled and greeted him.

"By the way, Changbin-ah. Why have you not once come to visit the
Elder's abode? I told you to come, didn't I?"

Changbin's tension eased a bit at her laughter.

"I-It's, well. It's a bit embarrassing, isn't it? To visit a place where
women reside, ahem, there might be rumors that are not so favorable,
or some such……"

Changbin mumbled his excuses.

In summary, it was as follows.

'It's not easy.'

"Ah. Sorry. I was a bit thoughtless."

She hadn't considered Changbin's fragile heart, which turned into a
scaredy-cat when it came to women.

If Qing had raided the Mount Hua Sect's guest house and dragged him
out, he would have followed her obediently. But it was clear that the
shy Changbin could not have come to visit her just because she told him
to come play.

"Now, come."

"I'll, g, go."
Changbin spoke neither formally nor informally, and charged forward.

The 'Hua' in Mount Hua Sect stood for 'Flower'.

In Qing's homeland, it was more commonly used to mean 'Brilliant', but
in the ancient times, 'Flower' and 'Brilliant' were used interchangeably
with the same pronunciation.

The meaning of 'Brilliant' was not used to describe luminescence in
ancient China, but rather the beauty that dazzled the eyes.

However, the actual Mount Hua that Qing saw was a stupidly tall rock
mountain, and it was acknowledged as the most rugged rock mountain
in the world.

Since they called that rocky mountain a flower, the ancestors of the
Zhongyuan had eyesight that was on par with the blind.

Therefore, the sword of Mount Hua resembled that flower, which was
actually a cliff that looked like a blade.

As Changbin's sword swayed gently, white sword qi bloomed like
petals along its path.

The sword qi that seemed to swim as if riding the wind were actually
petals. The true essence of Mount Hua lay not in the petals but in the
brutal sword force.

The gently curving sword suddenly fell with the trajectory of a
lightning bolt.

The splendid sword qi that fluttered like petals was just a trick of the
eye. If one did not focus on the sword, it was a terrifying technique that
would instantly sever one's neck.

Clang! Qing struck the lightning aside with her sword.

As she pushed the sword away, Changbin's figure swayed gently and
performed tricks.

I don't think Mount Hua's martial arts are very sly, do they?

Qing thought as such.

The swaying footwork was the Serpentine Willow Steps of Mount Hua,
which she had already experienced several times in her spars with
Changbin.

Changbin took a heavy step forward.

It was Mount Hua's Seven Steps.

Qing took a step back and leaned her upper body backward.

She had seen the Seven Ultimate Slashes of the Plum Blossom Sword
Technique a few times before, as it cut through the air in vain in front
of her shoulder.

However, the petals that had been driving along the trajectory
suddenly rushed towards Qing.

The martial arts of Mount Hua were not different in their illusion and
variation.

The splendid Plum Blossom petals of sword qi were both an illusion to
distract the eye and, at the same time, sharp blades of sword qi
themselves.

Qing's iron sword drew a large semicircle, igniting into the shape of a
setting sun. The fragile petals melted away as they touched the setting
sun.

Then, Changbin's sword transformed once again.

The meticulously moving tip of the sword drew branches of a plum
blossom tree extending along an elegant line.

The sword qi that lingered in space was a characteristic of the Mount
Hua Sect, and this time, the plum blossoms that bloomed on the
branches reached out towards Qing.

But, hmm. I think I can see the veins of the leaves.

It seemed as though the sword techniques of Mount Hua were too
visible to her eyes. It was because of that old man, the trace of the
Celestial Martial Emperor that existed alone amidst the scattered
raindrops of sword qi that filled the world.

One Leads to All. The thrust of an ordinary Three Essence Sword
pierces through the plum branches like a bamboo stalk.

Startled, Changbin quickly created distance.

"How?"

There were ways to omit the end of a sentence when using neither
formal nor informal speech. As Changbin asked as such, Qing replied
without hiding her laughter.

"Skillfully? Now then. You should try harder."

"Then, I'll, come."

Changbin's expression brightened as he charged again.

After all, despite everything, he was still a martial artist. The moment
when he could pour out everything he had was enjoyable.

A field of flowers bloomed, fluttered, fell to the ground, and then, as if
blown by an untimely spring breeze in late May, they rose again and
scattered in the stadium.

And finally, Changbin, who had stopped, bowed respectfully with a fist
and palm salute.

"Phew. I have lost."

Having unleashed all Seven of the Ultimate Slashes and even the
Fourteen Styles among the Plum Blossom Sword Techniques, Changbin
had a refreshed expression.

"The winner, Divine Maiden Sect's Disciple, Ximen Qing!"

This time, there was a considerable amount of cheering.

After all, wasn't it a duel of splendid techniques that lit up the arena
with flashes of light?

Since Changbin knew of Qing's skills, he had decided to go all out from
the start. And as he did so, Qing also responded by raising her own
sword qi.

For ordinary people, it was practically impossible to see such a
stylized duel between Peak Realm Masters who could unleash sword qi
like this.

Moreover, the martial arts of Mount Hua were originally quite
spectacular.

Cheer, cheer, cheer for the Dazzling Swordswoman! Dazzling
Swordswoman! Dazzling Swordswoman!

Though the cheering was for the cheering, the content was somewhat,
well…

Even if the same words were repeated, the emotions contained within
were closer to a heartfelt warmth this time.

Of course, Qing didn't care about such things before and she didn't
care about them now either.

After jumping down the elevated stage to the passageway below,
Changbin hesitantly spoke.

"Um. Young Lady Ximen? Does it not bother you? There is no reason to
hide that beautiful appearance……"

"It's not that I'm particularly hiding it. But if I suddenly take it off now
and go, 'Tada! I was actually a stunning beauty all along!', wouldn't that
be a bit embarrassing?"

"That is true, I suppose. Yes."

"Also, um. It's a bit, how should I put this? If you keep speaking so
formally, but then not, it's a bit, you know? It's like, do you want to or
not?"

"But since Young Lady is technically a Senior by generation, it is a bit
difficult to speak casually. Though it is also not quite right to use
complete honorifics, so um, it is not easy, so to speak……"

It was the delicate heart of Changbin, who found it difficult to speak
casually, yet did not want to use honorifics either.