\chapter{A Ronin Has a Ronin's Sense of Loyalty(11)}

Atop the stairs was a large door that clearly led to the surface.

It was a stark contrast to what Qing had expected, imagining it would
be some sort of secret passage's hidden door.

Although the door was firmly locked with a latch from the outside,

Qing opened it with ease and finally emerged.

In a welcoming gesture, the warm air of early June enveloped her body
as soon as she opened the door.

At that very moment of her majestic escape, Qing thought.

Hm. It's a bit cooler underground, huh.

Qing didn't really feel anything special as she had been captured in the
wee hours of the morning, had a short nap, ate breakfast and lunch,
before coming out in the late afternoon.

But for Moyong Juhee, who had not seen the sunlight for a long time
and had her heart broken in despair, thinking she would never see the
bright scenery again, it was a very different experience.

That was why the moment the warm early June air wrapped around her,
she sobbed with a stifled cry.

Qing smiled bitterly and looked around. It was the back of a building
and a wall, a backyard that could it about three people side-by-side,
though… it wasn't really a backyard, was it? What would you call such a
place?

As she turned around, she thought the camouflage was more exquisite
than she had expected.

No outsider would bother to enter the space between the back of the
building and the wall, and even if they did, upon seeing the stairs
leading down and a door made of roughly hewn wood, they would
likely dismiss it as a basement used as a storage room.

According to the Blood Cult warrior's testimony, those of the
Secondary Blood Cave Unit usually stayed above ground when not on
duty.

Then this manor must be a base used by the Blood Cult, right? she
thought.

Of course, the best method was to look around with her own two eyes.
Qing released the straps on her stomach and carefully laid Moyong
Juhee down before asking.

"Can you wait here for a moment? I'll just clear out the manor first."

"You're going to abandon me-."

"I'm not abandoning you."

"Let's, let's go together. Don't leave me alone."

Moyong Juhee pleaded, grabbing onto Qing's arm.

"I will never abandon Young Lady Moyong. I promise. So, can you wait
just a little bit?"

"No, no! Let's go together. Don't leave me, don't leave me behind."

"Young Lady Moyong. You won't have to wait long. It'll be a hundred,
just a hundred breaths before I return."

"No! No! Don't leave me. Huh? Okay? You, you, you can't do this to me.
It's because of you. Responsibility, right, yes. You have to take
responsibility."

Qing gently cupped Moyong Juhee's cheeks and met her gaze.

"Young Lady Moyong. Look into my eyes. I will never abandon you.
Okay?"

"Then, then we can just go together."

"I'm just going to clear out the manor interior for a bit. If there are any
Blood Cult bastards inside, you might get hurt again, Young Lady
Moyong."

"It's okay. It's okay if I get hurt, if I get hurt."

She was just acting like a child, so Qing was at a loss.

Hm. Normally, they listen to me if I do this.

Were movies just movies, after all?

Qing was about to sigh, but she held back when she saw Moyong
Juhee's desperate gaze, desperately pleading and looking into her
eyes.

Fine, let's try to soothe her up to three times.

"Young Lady Moyong. What are you so afraid of? It'll be just a moment,
just one moment. Are you scared something might happen in the
meantime?"

"But, alone, I, I was alone and I shouted so much, but no one came to
help……"

Moyong Juhee spoke incoherently.

From what she heard, it seemed like she was ambushed by the Spitting
Bat Demon, who was lying in wait outside the city when she was going
home alone without any guards.

To prevent her from escaping, her toenails were pulled out and she was
hung with a noose around her neck. She was hung at a height where she
could stand on the very tips of her toes; if she stood on her toes, she
would writhe in extreme pain, and if she writhed, her neck would be
constricted and she wouldn't be able to breathe, so she would struggle
and stand on her tiptoes again, causing the pain to surge once more…….

"They said they would let me down if I swallowed the Gu. I, I
tried to say, that I would swallow it, but, it hurt, because I couldn't
breathe, why did no one help me. Why did they laugh, and I, I was
dying."

The Blood Cult bastards had apparently watched her struggle in agony
and suffocation with laughter until the break of dawn.

"So I can't be alone. If I'm alone and get caught again, then. No. No."

Moyong Juhee sobbed, tears streaming down her face.

"I'm, I'm pathetic, right? I'm a stupid bitch who got caught wandering
around alone and suffered such a dirty fate. I'm a stupid bitch who
pushed away my guards just because I was being watched. I know, I
know I'm a good-for-nothing. I'm good-for-nothing as a woman and
good-for-nothing as a martial artist."

"No, you're not. Young Lady Moyong is neither pathetic nor stupid. It's
not your fault. Is it a crime to go home? It's all the fault of those Blood
Cult bastards. You have no sins, Young Lady Moyong."

"Really? Really?"

"Yes. Really. Can you trust my words?"

"Yes. I'll trust you, I'll trust you."

"And you're one of the Five Flowers of Wulin, you know? With such a
pretty face, you are a proper woman. Also, you have avenged yourself
as a martial artist. So please don't say such things."

"Yes. Thank you. Thank you so much……"

"Young Lady Moyong. Can you find the courage to wait just a little
bit? Just a little, a very little. I'll be back after just a hundred breaths.
Okay?"

"Just a little. You'll be back after a hundred breaths, right?"

"Of course. Just wait a little. Siiiiigh. Hearing about it makes me so
angry. I'll catch those bastards, so let's take our revenge together,
okay?"

"Yes, yes, okay."

Then, Qing gave Moyong Juhee a tight hug.

"You're so kind and brave. Young Lady Moyong is truly a strong and
resolute person. Okay? You trust my words, right?"

"Yes……"

"If the painful and difficult memories come to mind, trace back the
memories of when we returned the favor to those bastards. Wasn't
revenge sweet? I'll be back soon."

After saying so, Qing flew away with her Anti-Gravity Footwork.
Moyong Juhee counted, hugging her legs with her focus regained for
the first time in a while. Then, she suddenly had a question.

"Revenge……? Huh……?"

Moyong Juhee's focus scattered again and she began to tremble.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Unfortunately, there were only two Secondary Blood Cave Unit
members staying at the Blood Cult's base.

After a contest of truth where only one would be spared, the location
of the base used as a stronghold was thoroughly memorized by Qing
after hearing the testimonies that followed one after the other. Then,
she picked the final winner.

Thus, the loser of the contest of truth was Qing's portion and the
winner was Moyong Juhee's.

"Uh, um, I'm, I'm okay. You don't have to, so please do as Young Lady
Ximen wishes-"

"There's nothing to hold back on. Once you've suffered, you have to
return it in kind to release the resentment in your heart. Now. Just do
exactly as I do, okay?"

"Yes, yes……"

"Unfortunately, we don't have much time, so let's just peel off the skin
and hang them up."

Thus, there were two skinned corpses hung side-by-side.

Afterward, they washed up in the bath of the ownerless manor.

However, Moyong Juhee screamed and threw a fit at the mere sight of
water, burying her head and trembling uncontrollably.

As a result, Qing had to soothe her, wash her, soothe her again, pour
some water to wash her hair, which led to her throwing a tantrum and
flailing her arms, but she refused to close her eyes, so she ended up
screaming in pain, causing Qing to soothe her once again, before finally
washing her, thus using up all her energy.

After changing into clothes that were in the manor, she finally looked
like a proper human being again.

They had to return to the Wulin Alliance, but they couldn't enter
in the form of blood-soaked monsters, could they?

"I'm sorry, I'm so sorry. I'm sorry."

"It's okay, so stop that."

"But, the bruises, they're swollen and dark, what do we do……"

"I told you, I don't know why you keep fussing over it. I've been split in
half before, so a few bruises are nothing. They'll heal in a few days, so
stop feeling sorry. It wasn't your fault, Young Lady Moyong, since you
were in so much pain. So it's not your fault."

"Yes……"

Thus, while constantly consoling and soothing Moyong Juhee, who kept
apologizing and suggesting to pull out her nails or even hit her, they
finally returned to the Wulin Alliance.

Once there, they heard the sound of wooden swords clashing in the
backyard.

Qing's friends didn't even worry.

This was because Qing often disappeared for days due to Cheon
Yuhak's training.

They just assumed that she was training with the Godmother (since they
couldn't say it was the Divine Maiden's Teachings), even when she
didn't show her face for a day.

Qing, thinking how carefree they were, stuck her tongue out and went
up to the guest room of the Wulin Alliance to lay Moyong Juhee
down.

"Young Lady Ximen, don't go anywhere……"

Moyong Juhee said, holding onto Qing's hand tightly.

But due to the extreme fear, exhaustion, and relief from finally feeling
safe after so long, she soon fell asleep.

After asking a servant to call Tang Nana, Moyong Juhee's eyes were
bloodshot as soon as she saw her.

"What the hell? Isn't that Geomhwa? Why is she here? You, you, you
brought another woman again. No, you were so obsessed with her that
you even held her hand? Wow. You really are amazing."

"It's not like that. Nana. Young Lady Moyong is currently poisoned."

"Yeah, yeah. Poisoned. That's what happens every time Qing'er calls
me. So, what kind of poison is it this time?"

"Uh. It's the Secondary Blood Cave."

"Huh……?"

Tang Nana, who had her hands on her hips and was snorting, blinked
her eyes.

"Did you just say Blood Cave?"

"Yeah. Secondary Blood Cave."

"Are you joking?"

"Have I ever joked about something like this?"

Then, Tang Nana's expression turned serious.

"Goodness, what is this? It's the Blood Cult's poison."

"Mm. I know. It can't be removed, so I'm thinking of getting rid of the
Queen Poison. Then, she has to be put into a deep sleep. Can I ask for
your help? It's something that can't be made public."

She couldn't figure out what kind of bug would send signals with
supernatural powers, but the Queen Poisons could order lower-ranking
poisons to commit suicide.

Then, the venom within the poison would spread throughout the body,
causing the infected to die as well.

Moreover, there was even a suicide signal chain reaction for the
Queen Poisons, a sure-kill move that led to a massacre by using poisons
to transmit the order to die to the widest range possible.

The reason the members of the Blood Cave Unit were spread out evenly
across bases, with their lives at the mercy of their Captain and
Subordinates, was to act as human relays.

Therefore, it was necessary to put Moyong Juhee into a deep sleep with
the poison.

This was so that even if the Queen Poison received the suicide signal, it
would remain dormant and unaware.

Of course, this wasn't a method Qing had come up with.

It was a clever strategy suggested by a member of the Blood Cave Unit.

In response, Tang Nana sighed deeply and spoke.

"So the Blood Cult is involved? Then we should ask the elders of the
Alliance for help."

"That would cause problems for more than one or two people. I'd like to
handle it quietly if possible. Mm. I think the two of us should be
enough."

Moyong Juhee claimed that she had never done anything untoward, that
she had resisted until the end.

But if rumors spread that she had been captured by the Blood Cult,
who would believe her?

Even if Qing had heard the truth of the hobbies of the Secondary Blood
Cave Unit Leader, the Blood Wheel Demonic, and his subordinate, the
Spitting Bat Demon, it didn't change a thing.

Moreover, the Ronin would fall into a pit of dishonor in an instant.

They had tried to maintain the line while living without a sect, so
wouldn't it be unfair if they were to fall just because they ate some
bad medicine?

"There's another person besides Young Lady Moyong who's been
poisoned by the Blood Cave. Can you put them to sleep for about three
days?"

"You mean put the poison to sleep as well? Well, it's not that hard.
Mm. But Qing'er, you know a lot of details. It's surprising to see,
actually."

"What do you mean? I'm originally this kind of person if I put my mind
to it, you know?"

"Oh my."

Tang Nana slapped Qing's arm.

"Will you tell me what happened later? I'll prepare the medicine for
now. Gather the people you need to put to sleep beforehand."