\chapter{A Ronin Has a Ronin's Sense of Loyalty(3)}

As soon as they returned to the Cheonmu Pavilion, Qing hurriedly
changed her clothes.

She couldn't stand the feeling of being wrapped in armor. It felt like
being in a narrow room with hot steam pouring out, or like wearing a
thick mascot costume in the middle of summer. It was a horrible feeling
that made her feel suffocated.

"Haaa. I feel a bit better now."

Now that the wind was blowing through the hemp cloth, she felt like she
could finally breathe. At the same time, even without looking, she could
vividly feel the movement of the air within a narrow radius of about one
step.

As her senses were freed from being tightly wrapped and stifled, they
became even more vivid.

Ah. So this is what it feels like to be able to see in all directions even
without looking.

It was said that if one continued to keep their senses open, the range of
detection would gradually expand. Right now, it was only about two
feet, but that wouldn't be the case in the future.

Qing was once again realizing what Cheonyuhak meant by calling it a
trick.

It was a kind of physical improvement, one might say.

Ximen Surin's training was a way to draw out the senses for actual
combat, thus establishing Qing's combat style and leading her to the
next realm.

But the legacy of the Divine Thief was a way of bestowing mystical
abilities, rather than just martial arts.

If the lineage passed down by a single person relied solely on slow and
traditional training, it would have long been cut off and disappeared.

Come to think of it, wasn't there actually no particular gain when it
came to the principles of flexibility?

I think that was what I was originally trying to learn.

But now, only her joints had become softer.

Qing bent her wrist backward.

Her wrist bent a little over ninety degrees, and each joint of her fingers
bent further back gently.

Anyone could do this by pushing with the opposite hand, but it was
originally an impossible feat to do with the strength of just one hand.

Cheonyuhak could even touch his forearm with the nail of his middle
finger, so Qing, who had only received the Joint and Bone Breaking
Technique twice, still had a long way to go.

I should hurry and fill up the Flexible Softening of Joints, too.

Anyway, now… It's just boring.

But at least now I have a parasite to take the pain for me.

With that thought, Qing pestered her teacher with a light heart, asking
her to torture her.

"Teacher, when are we doing the Flexible Softening of Joints again?
Can you do it tomorrow?"

Cheonyuhak was dumbfounded.

The last time she brought it up, she was trembling all over and seemed
to have a clear, resolute determination.

But what was this?

Now, it was like she was asking for pocket money.

"You're one tough bitch, you know that? You don't even look afraid
anymore. Can you actually endure it? You know, just thinking about
what I went through back then makes my legs go numb."

"Eyy, is it that bad?"

"For now, let's deal with the Tracking Incense issue first. If that bastard
shows up while you're recovering, wouldn't we be left with no choice
but to just sit there and watch?"

"I just wish we could get rid of him quickly……"

"Why are you in such a hurry?"

Of course, she was in a hurry.

Since the Transcendent Realm was still out of reach, she had to
compensate in other ways.

The Divine Thief's training was more of a mystical body
modification or development than it was training. As such, she wanted
to finish it quickly.

"Teacher, come on~. If we finish it quickly, it'll be easier for Teacher,
and it'll be good for me too. Right?"

"In all of history, there has never been a bastard, no, a bitch, who
sweet-talks someone into torturing her."

Eventually, Cheonyuhak grumbled about how difficult it was to make
the Poison Brewing Elixir Chamber and then jumped over the wall.

Then, Qing also felt a sense of apology. After all, this made it seem like
she was just taking advantage of her teacher.

So, she decided to help with the potion brewing tonight and waited,
occupying Cheonyuhak's bed.

About an hour later, when she was just about to fall asleep, she felt
someone leap within a step of her through the subtle low of the air.

"Tsk. You're even stealing your teacher's bed now? You really are a
thief by nature, aren't you? But I must say, I've picked up a pretty
decent disciple."

"Hehe. I was just waiting to help Teacher. Did you already get the
ingredients?"

"No."

Cheonyuhak shook his head and spoke with a serious expression.

"The scent of the Tracking Incense is very strong. It seems that guy has
shown up."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Out of the eight martial artists who had reached the quarterfinal, two were
from independent backgrounds.

The quarterfinal's participants were Minor Hero Wang Nopil, who used a chair as
a weapon, and Minor Hero Majeon, who used Earth-Cleaving Palm.

In fact, by the time one reached the level of the final sixteen, the
martial artists of the Orthodox Faction were all Masters deliberately
nurtured by famous sects, so they could not be compared to those from
independent backgrounds.

The reason why two martial artists from independent backgrounds
made it to the quarterfinal was simply due to luck with the match-ups.

There were two matches where independent martial artists fought
each other, so two were bound to advance.

At any rate, it meant that they were among the top eight Rising Stars of
the current generation, so it was a joyous occasion for martial artists
from independent backgrounds, as if it was their own success.

As such, after the round of sixteen, martial artists from independent
backgrounds gathered for a get-together.

It was to celebrate the advancement to the quarterfinal and to console those
who had fallen.

The atmosphere was good and lively, but it instantly died down when
Wang Nopil and Majeon returned after saying they had guests and then
facing the guy who had sprinkled that powder.

When Qing entered the Jungjeong Inn with Cheonyuhak, the
atmosphere had already subsided and become quite chaotic.
Qing clicked her tongue inwardly at the sight.

If it was a get-together, they should have done it in a nice place. It was
a shabby place in a remote area that didn't do much business, and
moreover, it was an inn.

It wasn't a restaurant or a pub, but an inn. In fact, this was the level of
the ronin's financial situation.

Still, it seemed they had rented out the whole place.

Qing made a joke about the subdued atmosphere.

"Why didn't you invite me to the get-together? It's not right to exclude
me like this, you know? That's so mean. Are we not close enough as
fellow martial artists from independent backgrounds?"

"Ah. Young Lady Ximen. Th-That's… The place is a bit humble, so……"

"Humble, my ass. There's a roof, people cooking, and we even rented
out the whole place to avoid prying eyes. This is practically a feast.
Ah. Congratulations to Young Hero Wang and Young Hero Ma for
advancing to the quarterfinal."

Saying so, Qing poured them each a drink.

They both received the drink with serious expressions and gulped it
down.

"It's not something else, but the Tracking Incense was activated, so we
came to check. So, you met that guy, right? What did he say?"

"He gave me this."

Young Hero Wang held out another wooden box.

From its appearance, it was a treasure chest with elaborate red patterns
carved into it, clearly containing a precious item.

When Qing opened it, there was another bright red pill.

"What is it? Did he give you another Lust Arousal Pill?"

"He said it was an elixir this time. He said there would be some side
effects, but it would add ten years' worth of Inner Qi."

"He gave you an elixir? For free? Without asking for money?"

Qing knew how precious elixirs were.

"He said it would be fun if a martial artist from an independent
background won. He also asked me to reveal that I had eaten an elixir
given by the Divine Thief."

"Tsk."

Cheonyuhak, who was beside her, clicked his tongue loudly.

"If it wasn't for Young Lady Ximen's words, I would have suspected
nothing and eaten it. But now, I know it is no ordinary conspiracy. How
shameless can someone be to offer an elixir to a ronin? Lust Arousal
Pills, I can understand to some extent, but this…"

The martial artists nodded in agreement.

Qing clapped her hands together.

"Now. Since that guy just left, isn't now the moment when he's most
off-guard? If we strike before he prepares any other tricks, I think it
would be best to take him down tonight. What do you think?"

The martial artists' eyes lit up with a murderous glint.

Unlike the young masters and ladies of the Orthodox Faction, martial
artists from independent backgrounds were wild people who had lived
through blood and violence as a part of their daily lives.

What the fuck? Is this some kind of a joke? Are they trying to show off
by going there to fight or something?

As such, Qing tried to lift the mood.

"For now, let's just enjoy the afterparty. Is there anyone here who
doesn't know how to extract alcohol from their system? Then, I'll treat
everyone properly tonight."

Qing was loaded with money, as she had been earning without
spending.

Her friends were aghast whenever Qing held her money pouch. As for
Peng Daesan and Namgung Shinjae, they believed it was shameful for a
man to let a woman spend money, and Tang Nanah regarded Qing as
some sort of a poor person or a beggar.

So, after a long time, Qing opened her money pouch, ordered dishes
from a restaurant, brought in good alcohol, and threw a proper party.

Naturally, the atmosphere became lively.

When she went to the outhouse for a short call of nature, Cheonyuhak
clicked his tongue.

"What a foolish plan. In my entire life, I have never heard of such a
foolish plan to attack."

"What do you mean?"

"Since the Tracking Incense has been planted, wouldn't it be easy to
figure out who that guy is and what tricks he's up to if we just tail him
for a few days?"

"Eyy. That's true and all. But, you know. When a person's greed is
triggered, they can be shaken and make mistakes, right? If we want to
take care of it together and bury it, we shouldn't give them time to
think such useless thoughts."

Qing was very meticulous when it came to her own safety, if nothing
else.

Originally, Qing's plans always started with the premise of running
away if things didn't work out.

The enemy's location was identified and they could take their time to
spy on them at any time.

Attacking in a rush without properly investigating the enemy's identity
and strength?

It was a pretty foolish plan when she thought about it.

Why? Because Sun Tzu, who had delivered the single blow of 'Know
thyself and know thy enemy', before becoming the eternal and
immortal victor, had said so.

But there was a separate reason why she urged the martial artists to
attack immediately, late at night, despite such a fact.

If even one person was out of sight, who knew if someone might fall for
temptation and betray them?

Lust Arousal Pills aside, no martial artist could resist the temptation of
an elixir. If they were blinded by greed for the elixir, it wouldn't be
strange for them to do anything.

If just one person spoke, they would all become bastards who ate
someone's elixir.

Therefore, she gathered them all in one place, watched them under
the guise of an afterparty, and intended to finish things off before they
had time to be swayed by temptation.

Cheonyuhak clicked his tongue again.

"Even so, these are ronin you have never even met before and they
won't be of much help to you, so why are you putting yourself at risk
just to help them?"

After all, the ones who would get hurt would be the martial artists from
independent backgrounds who ate the suspicious Lust Arousal Pills,
not Qing.

So, in fact, it wasn't even her business. Naturally, Cheonyuhak, not
liking that his disciple was putting herself at risk for mere ronin, was
full of complaints.

To such words from Cheonyuhak, Qing responded with a playful
coquetry.

"Eyy, but you know. I can get out of there whenever I want. Didn't you
see my Ethereal Steps? Didn't you also say that no one can catch me if I
decide to run? Not even you, Teacher?"

"Hmph."

Cheonyuhak tried to say something but stopped.

And that was true, too.

How is it that this little girl is so skilled in footwork? If it was a short
burst, a short distance duel, then she could be caught, but in a long distance race of who could run farther, she was already practically the
best under heaven.

Thus, they drank and reveled until late into the night, and only at 2 AM
did the ronin collectively expel the alcohol from their systems.

Expelling alcohol with Inner Qi was a skill that any martial artist at the
level of a First-Rate Master could do.

However, if done carelessly, one would be told that they might as well
not drink in the first place. Therefore, it was a skill that required careful
use and a good eye.

Since over twenty martial artists had gathered, the alcohol vapor
formed a cloud as it was expelled all at once.

Finally, the martial artists from independent backgrounds returned to
their senses and their eyes regained their murderous intent.

It could also be said that it was a way for ronin, who made a living by
selling their swords, to prepare themselves before a battle.

"Then, shall we go?"

At Wang Nopil's interjection…

"Young Lady Ximen. Why don't you just let it be? It is the way of us
ronin to speak with our fists before a fight. If Young Lady could deliver
a few cool words, it would be appreciated."

"Eyy, that's a bit embarrassing……"

But in fact, a pre-battle speech was quite an important ritual.
It was to define 'us' and strengthen solidarity, as well as identify the
enemy to raise morale.

Qing scratched the back of her neck and chose her words.

"Mmm. They say that ronin wander alone like wolves, right? But
originally, wolves live in packs with the most outstanding sense of
loyalty among beasts. But, aren't we just like that? Aren't we the people
who repay even a small amount of money with blood and loyalty?"

She sure knew how to embellish the fact that they sold their swords for
pennies.

In fact, this was Qing's true specialty.

A glib tongue of deceit! The devil's mouth!

"Oooooh!" "That's right!" "Indeed!"

The ronin responded excitedly.

"There's a bastard out there who's trying to take advantage of us,
treating us like we're nothing, just because we're mere ronin. Can we
just stand by and watch? No, right? What do we do? We take care of it
the ronin way. Why? Because we are ronin."

"Because we are ronin!"

"Loyalty and the sword. That is what makes us ronin."

"Loyalty!" "The Sword!" "Ronin!"

The ronin, completely taken in, raised their voices.

Never in their lives had they heard such an inspiring speech that
stirred their hearts so deeply.

They even felt a sense of pride in their past as ronin, thanks to her
ecstatic eloquence.
Having confirmed that their morale was fully charged, Qing drove in

the final wedge.

"Let's go. Let's carve the lesson that ronin have their own code of honor
with our swords."
