\chapter{A Ronin Has a Ronin's Sense of Loyalty(9)}

"Oh my. Young Lady. Are you alright?"

"Why, why are you here so late?!"

Moyong Juhee burst into anger and threw herself into Qing's arms.

As she had suffered some kind of hardship, a foul stench wafted
through, causing Qing to frown for a moment. Then, she sighed deeply
and gently patted her back.

"Why are you so late? I, I, I wanted to die, but I was scared. It hurt so
much, and I hate pain. Why are you so late? So very late?"

In fact, Qing had only just learned of Moyong Juhee's capture through
some simple entertainment.

However, she couldn't just say that she had no idea she was even
captured and that no one up above seemed to know either.

Fortunately, although Qing's origins were not of Zhongyuan,
thus making her seem barbaric, she possessed a wide array of
miscellaneous knowledge.

Qing hugged Moyong Juhee tightly and whispered in her ear.

"I'm sorry for being late. It must have been very difficult, right? But you
held on well until now. Thank you. You did well. It was very impressive. I
was really late, huh? It's all my fault. Young Lady Moyong did nothing
wrong at all. I'm sorry……"

Listen to the client, empathize, agree, and comfort, but offer an
alternative. Offer an alternative? Or was it to not offer an alternative?
Her psychology class, which she had taken after failing to enroll in the
courses she wanted, was so long ago that it was all a blur.

"Hueuk……!"

Moyong Juhee finally burst into tears.

However, she still gasped, choking back her sobs, making her seem
truly pitiful.

It was when Qing had held her in her arms for quite some time, waiting
for her to calm down.

"……You. Are you Ximen Qing?"

"Young Lady Moyong? Are you feeling a little better now?"

Only then did Qing release the arms that held her tightly. Moyong
Juhee leaned her upper body back to check Qing's face and made a
dazed expression.

And then, as if a stage actor was changing masks, her face instantly
became full of vivid hatred.

"You, what the fuck? Why are you so pretty? You, you have everything,
you have it all, so why do you do this to me?! How could you do this to
me?! Because of you, because of you I, it's all because of you……!"

Suddenly, Moyong Juhee began to pour out resentment. Her voice was
distorted with tears, making it difficult to understand, but it seemed like
she had some sort of story.

After being utterly humiliated at the Dragon and Phoenix Banquet, she
thought the only way to regain her honor was to defeat Qing in the
Hidden Dragon Sparring Meet.

But after losing to a mere ronin, she became a complete laughingstock.

Even worse, she had overheard her own group whispering about her
behind her back in the stairwell of the Phoenix Assembly.

They said things like how she thought she was all that, how she
despised those who liked lilies, yet she lost to a mere ronin, and how
they only followed her around and acted as maids because, frankly,
they felt a bit better about themselves when they saw her, since even
they had something better than her……

In the end, Moyong Juhee, who now hated everything, left a letter saying
she would return home first and fled during the night.

Qing was quite dumbfounded by this.

Why is that my fault?

No matter how fearless a young lady of the Five Noble Clans was
(somewhat of a Master), if she secretly left in the middle of the night in
this harsh world, those Blood Cult bastards who had been watching
would have thought a delectable treat had just rolled in all by itself.

Moreover, if she left a letter saying she was returning home first, the
members of the Moyong Clan would definitely not think she had been
kidnapped, right?

"Young Lady, please calm down for now. My goodness, your face is a
mess. Those bastards must have some food, so……"

The guards were on twelve-hour shifts, so they brought twelve hours'
worth of food with them. It was the secret of the six rice balls.

It was when Qing was saying this and getting up.

Moyong Juhee, who had been pouring out resentment, suddenly
crawled on her knees, clung to Qing's legs, and hung on.

"H-Heot, don't go! No, please don't abandon me. I'm sorry. I'm so sorry.
I wasn't being sincere. Thank you for coming to save me. Please don't
abandon me. Don't abandon me. Please take me with you."

"I'm not trying to abandon you, Young Lady. That fucking, son of a, no.
That dirty, umm. That vile bastard."

"No! I'm not vile! I really held on and endured! I didn't do anything
vile! So don't abandon me, if you abandon me-"

"Kkeuek, what the! What the hell! Let go! What the fuck! What are you
doing! Let go of me, damn it!"

"KYAAAAAAAH!"

Just then, the guard woke up and shouted, causing Moyong Juhee to
scream in terror and bury her head in the ground.

"You fucking pig bitch! Fine! Let's die here today!"

"No! I'm sorry, I'm sorry, please, aack, aaack! Eok, heok, aaack!"

Moyong Juhee thrashed like a fish out of water. Her eyes rolled back
and she drooled and snotted, as if she was about to pass out.

Ah, I should have removed the venom first.

Qing hurriedly rushed over and pounced on the guard.

With one hand, she grabbed his neck and pinned him to the ground,
while the other hand plunged into the upper abdomen of the guard.

The guard, with his neck restrained, could only gurgle and squirm,
unable to overcome the strength of a peddler.

Qing felt around his intestines, focusing on the sensation at her
fingertips.

Hot blood flowed between her fingers, tickling the back of her hand,
and the man's heartbeat pulsed through his skin, thump, thump, thump.

For a moment, a shiver ran through her entire body, as if an electric
current was sparking, but… focus, focus…….

Finally, Qing carefully pulled out her hand.

In her hand was a venomous insect, a Two-Lined Blood-Threaded
Centipede, with two black lines. After confirming it was what she was
looking for, Qing threw it on the floor and stomped on it.

"Haeu, ha, whew, heok, heok……"

From inside the cell, the sound of Moyong Juhee gasping for breath
could be heard. Qing, after subduing the still squirming guard by
pressing harder on his neck, approached the cell again.

"I'm sorry, I'm sorry……"

"Young Lady Moyong. It's alright now. It's alright."

"I'm sorry. I'm sorry. I'm sorry."

Hmm. Her condition is really, really bad.

Qing looked down with a troubled expression at the back of her head
as she buried her face and rubbed her hands together, repeating how
she was sorry over and over again.

Pain could break a person.

That son of a bitch, Alleged Supreme, had broken Qing's mind
completely after beating her up.

But now, Qing no longer felt particularly annoyed or angry when she
thought about that time.

Qing knew the reason why.

"Young Lady Moyong. Can you come here for a moment?"

"I'm sorry, please, no more pain."

"Come on. It'll be fun for you too, Young Lady Moyong."

Qing picked up Moyong Juhee and headed out of the cell. The moment
they crossed the threshold, Moyong Juhee screamed and thrashed,
shouting how she couldn't go out.

It was a bit of a hassle, but Qing just stood still and hugged her tightly
until she calmed down a bit.

"I, I can't go out? Livestock can't go out. I, I'm, I'm."

"Young Lady Moyong. I am Ximen Qing."

"But, I don't want to be in pain. I."

"It's alright. Now. Look at that bastard over there, see? Now, he can't
hurt you anymore, Young Lady Moyong. And now, it's your turn to take
revenge, Young Lady Moyong?"

"Revenge."

Poisonous malice formed in Moyong Juhee's eyes.

Thanks to that, her focus returned quite clearly.

"That fucking son of a bitch! That fucking bastard!"

Moyong Juhee pushed Qing away and flew at the guard, strangling his
neck.

Qing was startled and tried to stop Moyong Juhee.

"Young Lady Moyong? You can't do that."

"Why not?! Because of this bastard, I! Let go! I'm going to kill him!"

"Young Lady Moyong. It's too wasteful to just kill him by strangling him.
He's already going to die soon anyway because I removed his venomous
insect. You have to make him suffer as much as possible."

"Huh?"

"Come on. Let's wake him up first, shall we? Watch what I do carefully."

Qing turned the guard over, undid the clothes that bound his hands, and
then firmly grabbed both of his shoulders-

Crack.

Though it wasn't a loud sound, when set to the background of a
person's shoulders crumpling like paper, it sounded louder than
thunder.

"Kkeuaaaak!"

The guard, shocked by the intense pain, screamed once again with all
his might. With his shoulders crushed and drooping, the way he
twitched despite his best efforts was truly a sight to behold.

As such, Qing skillfully wrapped his clothes around his mouth and
gagged him.

"I like to hear the screams, but since he's too loud, I'll just block it for
now. Hmm. Young Lady Moyong. Shall we start by pulling out his
fingernails? The proper way is to stick thorns under them before pulling
them out, but… Well, we have plenty of time to enjoy ourselves."

"Uh? I, uh."

"Come on, don't hold back."

Qing hugged Moyong Juhee from behind, held her hand tightly, and
explained the procedure kindly, allowing her to experience it firsthand.

"Grab it like this, and up, now, give it strength. Put strength in this
direction, slowly. The angle, a bit more. Now. See how it's lifting up?
There. Neat and tidy."

The guard's body bounced up and down.

Moyong Juhee, who had cowered at the terrible sensation touching her
hand, stared at the struggling guard as if possessed.

"Now. Isn't it easy? After all, he's just a guy like this. He just knows how
to handle venomous insects a little. But once you remove them, he's
nothing but a bug, isn't he?"

"Yes……"

"So, is there any reason to be afraid of something like this?"

Moyong Juhee shook her head.

"Then, take your time and enjoy. You can break the limbs one by one,
starting from the fingertips and toes. Here, look. The nail that's already
been removed. Use your fingers. Squeeze. Squeeeeeeeze. See how he's
squirming?"

In fact, Qing was a bit excited.

Originally, humans had a fundamental desire to share the things they
enjoyed.

"He's a bit loud, but I recommend loosening the gag. They'll scream
and beg for their lives, saying all sorts of things. How about it? Do you
want to try loosening the gag for a bit?"

In terms of Zhongyuan, it was a whisper of a demon. In Western
terms, it was a whisper of the very devil itself.

And Moyong Juhee nodded, as if possessed.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was now a semi-semi-expert on venomous insects.

The Two-Lined Blood-Threaded Centipede Senior had taught her
roughly the knowledge of a semi-expert.

It was a desperate lecture (in fact, their lives were at stake), but it was
too disorganized, so Qing's understanding had only reached the level
of a semi-semi-expert.

Honestly, Qing could remember things well if she listened and tried to
memorize properly.

After all, among Qing's abilities, her Wisdom had far surpassed that of
humans.

However, as is often the case with brain functions, even if one had the
latest hardware and spent a lot of money on it, if the person using it
was careless, they rarely paid attention and rarely inputted information
in the first place.

To use a modern expression, it was like buying the latest model after
spending a fortune, only to play Minesweeper on it.

At any rate, according to the entomology Qing had impressively
absorbed, venomous insects were quite a hassle to deal with.

Fundamentally, venomous insects had no lethality.

Because, with some exceptions, parasites did not seek to kill their
hosts.

However, when threatened, venomous insects would secrete venom.

Depending on the species, the pain varied, but it basically caused
excruciating pain that made a person roll on the ground and lose their
mind.

The lethal power of venomous insects came from not the venom itself,
but a special organ called the 'venom stopper'.

It was a deadly poison that a venomous insect would secrete as a last
resort right before it died, or a deadly poison that would leak from the
corpse of a venomous insect after it died.

According to the guard's explanation, this much was the same for the
ecology of ordinary poisonous creatures. They just lived inside an
animal's body, but they still had the basic characteristics of poisonous
creatures.

The unique aspect of venomous insects was their ranking and
synchronization.

Venomous insects were unique creatures that were ranked according to
the toxicity of their venom stoppers. When the higher-ranking venomous
insect was stimulated, it would transmit that stimulation to all lower ranking venomous insects within a certain range.

In other words, the way the guards inflicted pain with venomous insects
was to gently touch the venomous insects within them with their Inner
Qi, thus threatening them.

That was why those who practiced the Venomous Insect Arts practiced
vegetarianism.

Moreover, they didn't eat any stimulating spices. In the first place, they
didn't consume any food that would cause the venomous insects to
produce venom.

After nurturing venomous insects like that for about two years while
eating vegetarian, the toxicity of the body was completely removed,
thus making it so the venomous insects could not produce venom.

And once they reached that stage, they wouldn't be able to secrete
any venom.

It would only transmit stimulation in all directions.

That was the principle of how the Two-Lined Blood-Threaded
Centipede operated.

When Qing thought about it, she felt that if that was the extent of it, it
would be better to just die than to live a life of vegetarianism without
even being able to eat spices.

Power comes with a price, they say, but isn't that just too much to ask
for?