\chapter{A Ronin Has a Ronin's Sense of Loyalty(1)}

Surprisingly, Zhongyuan had a long-standing tradition of living
in an upright fashion. They slept in beds, and they sat on chairs.

The cross-legged position that martial artists often took, known as
the lotus position, was different from the 'Yangban position' that was
common in Qing's hometown, where both legs are crossed. Instead,
the lotus position was close to an acrobatic feat, where one places
both feet on top of the opposite thighs.

In short, it was an incredibly uncomfortable posture, and if you asked
why they bothered to take such a position, it was actually a penance to
prevent them from falling asleep during meditation.

The lotus position was originally a posture that originated from
Buddhism, and the root of ancient Buddhism lay in self-harm.

Therefore, for the independent martial artists of the Hyeon Gaek Hall,
the lotus position was an uncomfortable posture, but not one they
could not do.

Though they were from independent backgrounds, i.e. ronin, they were
not drifters with no roots who had no knowledge of Inner Qi cultivation.

Through the Wulin Alliance's strict character examinations, they had
established a name for themselves as righteous individuals in their
respective regions.

Thanks to that, only Dorae, who was lying on the floor, felt
uncomfortable.

"Young Lady Ximen? Is it okay if I just sit down too?"

"Ehhh. Just lie down comfortably. Comfortably. You deserve special
treatment, Young Fellow Do."

How can this be comfortable!

Except for a few, the independent martial artists of the Hyeon Gaek
Hall were all sitting in a lotus position in the room, so Dorae alone was
lying on the floor.

It was hard to tell if this was a special treatment or a special form of
torture. It was almost as if she was secretly being spiteful for being
handed such a wicked drug that used blood essence.

"So that means not a single one of you missed taking the Sleeping
Lapis, huh. Mmm. What can we do about something that has already
happened."

The independent martial artists averted their gazes.

Qing continued.

"Since human elixir has to be discarded after a ritual, come on. Take
them out. And if you have any recollection of how the guy who gave
them to you looked like, we can start with describing his
appearance-"

"This is not right. What right do you have to say that you're going to
collect them or whatever?"

"Huh?"

Qing gazed at the martial artist who had boldly stood up.

It was Young Fellow Wang Nopil, who used a chair as a weapon.

"What is it? So, you're going to keep eating elixirs that are made from
ground-up people?"

At that, Wang Nopil paused for a moment.

"Is it not an already created item? While it is unfortunate for those
sacrificed victims, wouldn't they rather have someone use them instead
of being discarded in vain?"

What the hell kinda logic is that?

Qing became irritated.

"What is up with this nonsense about meaning when you didn't do
anything good to begin with? And why are you speaking so proudly
when you're the one who gobbled down such a thing before a martial
arts tournament? Did you even think that a suspicious-looking,
crimson Sleeping Lapis given by some random guy was a proper item?"

"That's-"

"Everyone, speak up. Don't say you trusted him because he was a
'Hero', or any crap like that. Did that guy who called himself a Hero
even show a Hero Certification issued by the government? You're all
here being quiet in such an uncomfortable position because there's
something you're all ashamed of, right? Ah. Young Fellow Do, just keep
lying down. Stay comfortable."

At that, the martial artists averted their gazes, and poor Dorae
hesitated to stand up before awkwardly lying back down.

After a rough calculation, Qing realized that each pill had increased
their Evil Karma by thirty.

However, just because they ate it unknowingly didn't make them guilty?

It wasn't as if someone had secretly fed them while they were sleeping,
or threatened them with a knife and forced them to eat it.

From what Nanah had said, that crimson drug itself was ominous and
should have been avoided, yet they were the ones who had gobbled it
up, all smiles, just because they were handed to them by some
unidentified guy.

In the first place, 'Hero'? That was just an excuse. It was just greed to
get a good result in the tournament and the desire to believe that the
a good drug given by the 'Hero' would be of some help.

Was the source suspicious? Yes.

Was the drug suspicious? Yes.

Was the purpose for which it was used righteous? No.

As such, shouldn't they be held responsible for the spike in their Evil
Karma?

At that, Wang Nopil shouted in anger.

"You can't possibly understand, Young Lady! You grew up so well, eating
good elixirs since you were young and learning Divine Arts! How could
you possibly understand our feelings? You would never understand
how meaningful this tournament was for us ronin! Everyone, isn't that
so?!"

As expected, when it came to making people angry, there were two
methods. The first was to stop talking midway and the second was
-

However, the above methods only applied to ordinary daily
conversations and were not the secret of debates and quarrels.

In reality, there was a separate, greatest, and most powerful form of
attack that could both provoke people, while creating a sense of
injustice, frustration, and a desire to rebel; all while shutting their
mouths and causing their blood pressure to skyrocket.

And that was to take the moral high ground and call out the other
party's flaws and shortcomings, crushing them beneath your might.
Qing realized that she had messed up.

She had only been thinking of her own frustration; when she spoke in a
rant, the other party only rebelled rather than feeling embarrassed.

Therefore, she was only wielding a sword of words that was only for her
own pleasure.

If she wanted to persuade them, she had to guide them with
understanding.

Or, with money.

And the method Qing preferred was through force.

As such, Qing moderated her tone, pacifying them and changing her
approach.

"I understand everything, which is why I'm trying to solve this quietly
here. Honestly, instead of telling all this to the bigwigs of the Orthodox
Faction, I'm here. Isn't that so? Because I completely understand how
desperate you all are."

"Ha. Understanding. You're hilarious. What do you even know? How
could you, a disciple of the Divine Maiden Sect, possibly understand
the resentment of us drifters, who do not have a sect or any decent
background whatsoever?"

"Well, I was a ronin too. It was only a few years ago that I lived by
scraping up garbage and fighting with beggars for a spot to sleep."

"……? Then aren't you a beggar, not a ronin-"

"Ehhh. A ronin or a beggar. If you have a sword and take by force,
you're a ronin and if you don't and beg for food, you're a beggar, isn't
that so? We all slept on the streets, were beaten by beggars, and if by
some chance there was a piece of kingly meat from the discarded
garbage, we were all so happy about it, right? And also…"

After saying so, the resentment she had been harboring burst forth.

If not now, when was she ever going to express this to anyone?

Thinking that she had finally found someone who could understand
her, Qing began to spill out all her sorrow.

At that, the faces of the ronin became awkward.

"Uh. Um."

"And if you caught a rat, that would be a rare feast, and we'd eat it raw
because we didn't want those beggar bastards to steal it. Ugh, thinking
about it makes me so angry. I should have set fire to under the bridge
before I left Geonpyeong. Should I go back after the martial arts
tournament is over?"

The martial artists exchanged glances.

Even if they were ronin, they had never lived such a beggarly life.

Even if they sold their swords as day laborers at a third-rate martial arts
school, they at least had a place to sleep and were given cold rice.

"Y-You have been through a lot……."

"What's with that pitiful look? Isn't everyone from a ronin background
like this?"

"Young Lady, those are not ronin, but beggars. Ahem. No, what I
mean to say is that you have been through a lot."

Wang Nopil was about to say that, but he was poked in the side by his
companion and had to change his words.

Thus, Wang Nopil's instigation was thwarted.

Rather, after hearing Qing's sorrowful experiences, he was not so bad
off after all. In fact, he even felt comforted by realizing that her life as
a low-life martial artist in the gutter was not the absolute worst.

After all, if he was capable of spreading righteousness in his own
hometown with martial arts that were at least presentable, he couldn't
have been a complete loser, either.

In the end, wooden boxes were stacked in front of Qing.

When Qing opened them to check, they all had two pills each, with two
spaces that were empty.

It seemed they had been diligently taking two pills at each of their
two matches so far in the preliminaries.

"Hmm? What's this? Who is this person who only took half a pill? Did
they eat one and a half and go off?"

Then, Qing, who had discovered one pill that was only half, asked.

"That's because that one was originally a half. They said that people
who eat Sleeping Lapis for the first time should start with half a pill, so
one of them was half from the start. I've eaten it once before……."

The martial artists nodded in agreement.

They were originally wood boxes with three and a half pills instead of
four.

What the hell? They even controlled the dosage for the first time? For
someone who was trying to play a trick, isn't he too kind?

Even though it was a wicked drug, it was said to be a genuine Sleeping
Lapis that was very potent and had almost no side effects.

Thinking that there were all sorts of weirdos in the world, Qing brought
up the real matter.

"From now on, we must catch and punish those bastards who spread
these wicked drugs."

"The Hero, you say? How could we possibly……"

"When they deliberately spread such a terrible thing that uses blood
essence, would they be doing you a good deed whether or not they are
a 'Hero'? Isn't it either to ruin your bodies, or to ruin your reputation?"

"What do you mean by reputation……?"

"You all, the independent martial artists, have been performing well in
this tournament. If someone suddenly appeared and said those bastards
won by using elixirs made from ground-up people, wouldn't all your
faces be smashed into the ground, along with the Wulin Alliance's?
That's what I think, anyway. What about you?"

It was the view of Qing, an expert at killing dignity.

As the most prominent authority when it came to destroying one's
dignity, she could roughly see through other people's tricks.

The martial artists' expressions became serious.

There was no good deed without a reason behind it in this world.

They thought he was a bit odd and weird, but since the 'Hero' was the
same, they thought there was nothing wrong with it, and decided to
trust him.

However, after hearing Qing's words, they realized that their belief
was just an illusion, without any basis.

"As I said earlier, I understand your desperation. In my opinion, is there
really that much difference between a realm reached by being born
with blessed elixirs and a power obtained by reducing one's own life
span? I do not want to judge what is right and what is wrong. If only
that Sleeping Lapis wasn't a despicable item made by grinding up
people."

The martial artists nodded gravely.

"So, I don't want you to be pointed at or blamed by others if this comes
to light. You worked so hard to get here without any backing, right?
You're all famous righteous warriors in your respective hometowns,
right?"

If each pill was worth thirty points, then half of them would lean
towards Righteous Karma after subtracting sixty points of Evil Karma.

Since no one had more than 100 points after adding 60, it meant the
Wulin Alliance's screening process was definitely thorough.

After all, it was easy for orthodox martial artists to live righteously,
wasn't it?

But, it was a difficult matter to maintain one's Karma when they lived
difficult lives (though not as difficult as Qing's).

Therefore, they should not be condemned or pointed at just because
they were unable to resist a moment's temptation.

That, Qing thought, should not happen.

"So, shouldn't we catch and punish that bastard, or those bastards, who
distributed those drugs so that you can all sleep soundly?"

The martial artists nodded again.

At that, Qing spoke in a kind voice.

"So, let's put our heads together and think. How are we going to catch
them and fuck them up?"