\chapter{A Ronin Has a Ronin's Sense of Loyalty(15)}

Kyung Damgan answered weakly, his voice almost drained as if he had
given up.

"I don't know either. I haven't seen him since morning. Who knows if
he's passed out drunk or off enjoying himself with some suitable
material he found."

Material? What the fuck is he on about? This old man still hasn't
snapped out of it.

Qing clicked her tongue disapprovingly.

Regardless, it meant that she had come all this way for nothing.

Qing immediately believed and accepted Kyung Damgan's testimony
without suspicion. At least when it came to selling out his comrades,
Kyung Damgan was a very reliable figure. After all, the loyalty of these
guys was shallower than a puddle of mud on the road.

Moreover, the very concept of disappearance was quite vague in the
Zhongyuan.

People with roots in Qing's homeland might not understand this well.

In their countries, the government collected every piece of information
on every individual, even their fingerprints.

This was a feat of a police state that was fully achieved only by that
particular ethnic group in the entire world.

Foreigners would be shocked and cry out 'Big Brother' out of nowhere
upon learning this, a sentiment that those people could not understand
at all.

Even the people of Zhongyuan had not registered all the noncitizens (unregistered individuals who were called rats) who were not
officially recognized!

Therefore, in Qing's homeland, kidnapping someone and making them
work as slaves would never happen unless the police were complicit and
looked the other way.

Furthermore, in addition to the voluntary submission of personal
information, the entire population had real-time communication
devices that doubled as location trackers.

Thus, if someone suddenly became unreachable, it was immediately
noticed as strange, leading to the conclusion that they had gone
missing.

If the location tracker was simply turned off, great anxiety would
already be brewing in their hearts.

However, what about the primitive and uncivilized Zhongyuan?

If someone left home saying they were going to a martial arts
competition, it would take a month to get there, a month to watch, and
a month to return, so even if there was no contact for at least three
months, people would assume they were just having fun.

Then, after about half a year, they would start to wonder if it was time
for their return, and after a year, they would accept the eternal
separation, thinking the person must have been stabbed somewhere.

Moreover, even the basic postal system in Zhongyuan was the
exclusive domain of the government, relying on enormous sums of
money or connections to even deliver a letter.

It was a world where sending a single letter was impossible without
money or connections!

Therefore, even if Qing had been gone for three or four days, no one
would particularly worry. They would just think she went somewhere or
that their paths had diverged.

Even if Moyong Jujui had left a note saying she was returning home/

First, her family wouldn't have worried for about a week.

They would just think she had caused some trouble again and was
hiding out of shame.

Similarly, Kyung Damgan's words that he hadn't seen her since
morning also fell within this context.

She could be playing alone somewhere or have been given a separate
task by her superiors. It wasn't a big deal if the leader was absent, and
they would just click their tongues.

"Hmm. If you don't mind, would you be willing to remove the venom from
those who have been poisoned?"

"Keuheuk, just kill me. I'll take as many of my comrades with me to the
underworld."

"Aren't they enemies rather than comrades? You'll just get beaten up on
your way to the underworld, you know?"

"What afterlife is there after death? If the heavens intend to punish
evildoers, they should do it while they're alive. Who believes that
nonsense about being punished after death?"

"Hmm. That is true."

If heavenly punishment fell immediately upon committing misdeeds,
there would be no bad guys in the world.

The idea that one would suffer after death was just a pitiful selfconsolation of the living, wishing it to be so.

"Keuheuk, what now? If you kill me-."

"Ah. For reference, the Ronin are fast asleep after taking some strong
medicine. So, threats about the Queen Ant unleashing an unlimited
self-destruct sequence upon your death won't work."

Kyung Damgan snorted at this.

"I'll just remove the venom. Just let me live."

"Hmm. I agree with that sentiment."

Kyung Damgan's expression brightened.

Qing smiled refreshingly and continued.

"You don't have to worry about the venom, but I hope you live a long,
long life as a eunuch, okay? You shouldn't die, okay?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was said that the martial prowess of the Blood Demon of Mount Li, the
Grand Master of the Bloodworms, surpassed the Unrestrained Realm.

The informant did not know the exact realm, however.

It was natural for people in Jianghu to hide their true abilities, so
revealing whether they were in the Early, Middle, or Late-Stage was a
foolish act.

I wanted to ask Master to take care of the Blood Demon, but it's a real
shame she's not here.

Thus, Qing dragged the unconscious Jitan'gwangma, grabbing him by
his sparse hair, and headed outside.

On the way, she found Ximen Surin, who was inspecting the
underground stronghold of the Blood Cult, and smiled brightly.

"Master! I've caught Jitan'gwangma."

"Have you been hurt anywhere? There's not a single spot on you that's
not covered in blood."

"Not a single drop of it is mine. It's nothing to catch a mere
Transcendent Realm."

"Yes. Now you can easily handle a Transcendent Realm. Well done."

Even with Qing's entire body covered in blood, Ximen Surin simply
praised her calmly.

Seeing that, she felt a faint sense of nostalgia. The pleasant times of
her youth, when she would drench herself in the blood of her enemies
and slaughter the foes of the women of Jianghu.

"It seems the Blood Demon has already left. I don't know if she's just
away for a bit."

"Then I shall have to stay here a bit longer. But what are you going to
do with that wretch? Why haven't you cut off his limbs and thrown him
in a pigsty?"

Jitan'gwangma's evil habits were well-known.

It would have been natural if he didn't have the moniker
'Jitan'gwangma' if such habits weren't known.

"Well, I have something to try. I think it could help with my training.
Hmm. But I need Second Master to be with me."

"Hmph. No wonder he's called a genius thief. He must have found some
precious treasure to steal somewhere. Isn't there another woman
wearing inner garments made of treasure maps?"

"Or it could be a man."

When Qing made a joke, Ximen Surin pretended to lightly tap her with
her fingers.

"You brat. How could you make such jokes about your Senior Sister?"

The woman who wore undergarments made of treasure maps was
Cheondungeon Wang Juheui, the Sect Leader of the Divine Maiden
Sect.

Ximen Surin often teased Wang Juheui, asking how the most valuable
underwear in the world felt.

Since it seemed the Blood Demon might return, Ximen Surin decided to
stay underground. Meanwhile, Qing headed to the surface.

Along the way, she saw martial artists of the Blood Cult, who had their
limbs cut off but were miraculously still alive without any bleeding,
groaning and wriggling.

Qing considered finishing them off, but decided against it since her
master had left them alone. She didn't want to be disrespectful.

Besides, they were living relays for the Queen Ant's unlimited selfdestruct sequence.
It was necessary to keep them alive to get rid of them all at once later.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Mucheon Pavilion's bath had equipment to torture Qing, or rather,
to train her in the Oil-Flowing Continuous Striking.

And firmly fixed there was none other than the villain known as
Jitan'gwangma Kyung Damgan.

After tying his limbs with the same precious items Cheonyuhak used
to tie Qing, she brought a lit torch to his severed wrist.

"Eueueup!!!"

"Oh, come on. Stay still. Your blood will just burst out again if you
move, even after I've cauterized it with great effort, you know? You
should live a long life, so I'm treating you."

"Eueup!!"

"I mean, I just cauterized it a little and you're acting like you're dying.
It just stings a little. Honestly, old people are so dramatic."

Qing thoroughly cooked Kyung Damgan's wrist.

Since she directly applied fire, if one had to classify it, it would be a
direct-fire roast.

Ah. I want to eat some pork belly.

It wasn't appropriate to think about eating while roasting a person's
wrist, but the smell of burning meat was unavoidable.

Qing knew from personal experience that once properly bound to the
Oil-Flowing Continuous Striking training platform, even the slightest
movement was impossible.

The reason was that it was ergonomically designed to completely sever
the joints and tendons, so the subject wouldn't cripple themselves
during the procedure.

Therefore, Kyung Damgan could only scream beyond the gag.

"Oops, did you die!?"

Qing hurriedly checked Kyung Damgan's pulse.

The lifeline of a Transcendent Realm Master wouldn't be severed by
such a simple medical procedure as cauterization.

Qing was greatly relieved.

Then, she returned to the Mucheon Pavilion, where she saw a welcome
face after a long time.

"Oh, Grandfather! How have you been?"

"Yes, have you been well?"

The warmly smiling, gracefully aged old man was none other than the
Tang Clan's Grand Elder, whom Qing called Poison Grandfather.

Poison Grandfather asked quietly.

"Hmm. So, Surin is here?"

"Ah. Master is below, taking care of the Blood Cult's leader."

"I see?"

The Grand Elder's face lit up.

His shins, which had been broken after being kicked for making some
aphrodisiacs, still ached whenever it rained.

Upon hearing of Ximen Surin's arrival, he had avoided even looking
towards the Mucheon Pavilion.

But since it was about capturing the Blood Demon, could his sore shins
be a problem?

It wasn't easy to remove another's poison.

Qing had just stabbed and pulled it out, but she had only done so
because she intended to kill them.

If the worms were forcibly pulled out, the venom they carried would
spread throughout the body, as they would struggle and release their
poison.

Qing could do as she pleased since she only needed them alive long
enough to enjoy the moment, but…

But it was impossible to do the same to Moyong Juhee and the Ronin,
so the help of a master skilled in both poison and medicine was needed.

Thus, late at night…

Poison Grandfather, carrying a glass bottle full of live worms, returned
with a joyful spirit.

Qing watched closely as the master of human anatomy performed his
skills, which were indeed wondrous, befitting a medical expert who
specialized in using knives.

And the worms were surprisingly… um. Cute?

Qing had imagined something like earthworms or leeches, but what
was actually taken out looked more like translucent newts.

They had two lines running horizontally across their wide heads, which
was why they were called the Two-lined Bloodworms.

She wondered if such creatures originally existed and tilted her head,
but then she remembered that this world had mystical powers like
Inner Qi, where people could shoot sword beams and even fly.

So, it wouldn't be strange to have parasitic newts.

Then, she just needed her master to return.

Since she had a good training tool, she thought she might as well learn
the Oil-Flowing Continuous Striking technique.

She wanted to learn it now, especially since she would have to teach her
own disciples later.

Besides, the thought of severing joints and tendons until they were on
the verge of complete destruction was, well, just thinking about it was
so exciting.

However, Cheon Yuhak did not return.

Instead, an unfamiliar person appeared and delivered Cheon Yuhak's
message that he would be late, so not to worry.

Hmm. Why did you send the messenger collect on delivery?

Master has plenty of money, though.

Ten gold for the message 'I'll be late, don't worry, my disciple' is a bit
expensive, isn't it?

In the end, Cheon Yuhak was late, not knowing what he was doing.

As the tied-up Kyung Damgan grew weaker, Qing made a decision,
thinking he might die.

Moreover, while the Blood Cult martial artists, who were acting as
relays, were still alive, she needed to send the signal for the Queen
Ant's self-destruction.

Well, if I turn these knobs, I can figure out how it works on my own. I
don't necessarily need Master to teach me. I can learn it by myself.
