\chapter{A Ronin Has a Ronin's Sense of Loyalty(14)}

Qing opened her mouth to speak.

"In the first pl-"

"ARGH! AAAAAAARGH!"

"Hmm?"

Qing, who was about to continue, tilted her head sharply at the sudden,
desperate scream.

Her gaze caught a one-armed warrior. As their eyes met, the one-armed
warrior stiffened.

"No, wait, I'm trying to talk here. Jeez. I forgot what I was about to
say, you know. Seriously, just because his shoulder got lopped off, a
grown-ass man is screaming like a little bitch. He has no manners at
all. No manners."

Qing's body turned to face the one-armed warrior directly.

"Hiiieek."

"Are you going to be quiet now?"

The one-armed warrior then proceeded to shove his remaining fist into
his mouth, as if to seal it shut.

Qing smiled in satisfaction and continued.

"Since you made a mistake, you have to be hit ten times. Since you
were loud, if you make any noise, we're starting over from the
beginning."

The detached arm of the one-armed warrior swung with mighty force. It
was an unprecedented experience in human history for the onearmed warrior. Who else would ever get slapped in the face with
their own shoulder?

Smack! Smack! Smack! The unpleasant sound of flesh hitting flesh
resounded throughout the underground. The liquid that oozed out
from the end of the makeshift club splattered everywhere, and the
one-armed warrior desperately covered his mouth.

And finally, the tenth hit.

Qing tossed aside the detached arm, which had been reduced to just an
elbow after being torn apart. It wasn't very powerful, to begin with,
being full of padding like a cushion, and it wasn't sturdy either, so it
seemed unlikely that she would use it again.

"Hmm. I had something to say. What was it? Hey, Eunuch Grandpa? Do
you perhaps know what I was going to say?"

"Y-You, what are you."

The hope of ruining the most beautiful, virtuous, pure, courageous,
and perfect woman in all of existence was no longer present.

What stood before him was nothing short of the most vicious killer
under the Heavens.

"Ah. That's right. Where in the world did Eunuch Grandpa's boss go
off to? It has been ages and he still hasn't come back. I was told that
the Great Lord of the Secondary Blood Poison Altar was here, but only
his lackeys are here guarding the place."

"Who are you calling a lackey!?"

"Oh, why are you so angry? If you're the Sub-Lord, then that means
you're the lackey of the Great Lord, aren't you? After the Great Lord
takes care of his business, the Sub-Lord has to clean up afterward with
his tongue. So you're a lackey, aren't you?"

"Who told you such nonsense!! Such a vicious slander!! Where did you
hear such lies!!"

"Well, Eunuch Grandpa is angry right now. He must be angry because I
hit the nail on the head. What will you do if the deceased Blood Altar
member testifies that he clearly saw that scene with his own two eyes?
Since he faced the fear of death, he wouldn't have lied. He said he saw
the Great Lord and the Sub-Lord licking each other's private parts.
Ugh, how disgusting. Hey, you guys, your lords were mixing their
tongues together. Ugh."

Of course, the Blood Altar member had not said such a thing.

Since Qing tried to avoid lying whenever possible, she did not say that
the Blood Altar member said it.

It was just a bit of wordplay, but it was inevitable that the Blood Altar
members would look at their Sub-Lord like he was a piece of shit.

"That is all just bullshit! It's all lies!"

"I have never lied. I can even swear on my sect and my master's
honor."

"Hngh! It's a lie! That bitch is selling out her sect and master to tell
lies!"

"Hmm. That is a bit of a stretch, don't you think? Hey, you guys, what do
you think?"

The members of the Secondary Blood Poison Altar were greatly
shocked. Their expressions all looked as if the food they had eaten
was trying to escape through the way it came in.

They suddenly became the subordinates of disgusting perverts, so it
was only natural for them to be mentally affected.

"Hmm. So, where did your lover, I mean, Great Lord, go off to without
even showing his face?"

"If you keep spouting such nonsense……"

"See? You're trying to hide and protect him so desperately because
you're lovers, aren't you? If you weren't lovers, there would be no need
to protect the Great Lord. What has the Blood Cult ever done in terms
of loyalty to their superiors? It's all about taking over if you can, isn't
it?"

At those words, the eyes of the Blood Cult members turned to Gyeong
Damgan. It was true, after all.

It was a very cunning instigation.

Normally, it was impossible to reveal the whereabouts of a superior,
but these were people of the Blood Cult, who were all trying to screw
each other over. So why protect him?

"A-Are you really believing that idiotic nonsense?"

"You weren't such a reliable superior before, but now you're forcing us
to believe you?"

"Kaaaaaaargh!"

Gyeong Damgan's eyes rolled back.

Simultaneously, with a scream of 'Kkkeoeok', the Blood Altar members
collapsed, trembling and convulsing.

It was the suicide command of the Queen Mother Poison.

Qing also felt the wriggling of the parasite in her stomach.

The suicide command was a mysterious signal from a bug that spread
in all directions over a wide area without error.

He was going to kill all his subordinates gathered here just to get one
person, Qing.

Hmm. Goodbye, my parasite. I should have given you a name if I
knew we were going to part like this. Well, it's too late now, but
farewell, Sulbyeong.

Qing accepted her parting with Sulbyeong, who was finally given a
name right before its death.

But isn't the Poisonous Essence much more poisonous?

I hope it gives you a nice, final gift before you go.

Hehe, I look forward to it.

Perhaps it had heard her encouragement, but the wriggling of the
parasite gradually slowed down.

If it could have conveyed its meaning, it might have said something like
this.

I made it, you bitch. I survived.

Huh? Sulbyeong, you're not dead? Why?

For some reason, Qing could not understand.

Even experts in the field of parasites would not understand this
bizarre and miraculous case, so how could Qing, who was merely
equivalent to an undergraduate in the study of parasites, possibly
know?

It might have been due to the mystical properties of the bile from the
Poisonous Blood Human, or perhaps the poisons that had not been
removed had combined to create some effect that fostered the
parasite's independence.

Or maybe it was just because of Qing's warm encouragement.

At any rate, amidst the Blood Altar members dying in the most horrific
agony possible due to the explosion of the Poisonous Essence, Qing
jumped up in surprise.

My goodness, they don't care about losing their lives!

And they're wasting Righteous Karma! Besides, at this rate, I could
enjoy them for a week straight!

Qing hurriedly flew around, stomping on the heads of the Blood Cult
members and kicking them, doing her best to ensure that their
precious lives were not wasted.

Fortunately, since they were in pain and rolling on the ground, their
heads were in a good position to be stepped on or kicked.

Thanks to that, she was able to kill everyone before they died on their
own. After kicking the head of the last Blood Cult member until only
half of it remained, Qing lost her balance and tumbled, rolling on the
ground.

Since Qing's muscles were screaming and her joints were creaking, she
had no choice but to roll on the floor as soon as she finishes that last
soccer kick.

"You, you bitch!"

In the midst of the carnage that had unfolded in an instant, Gyeong
Damgan had no time to do anything. Qing had moved at a speed that
far exceeded what she usually displayed, having pushed her Inner Qi
and strength to their limits.

As a result, every time she zipped past, the head of a Blood Altar
member would disappear, be reduced to half, or would be sent flying
away from its body.

"Jeeeez. I didn't even feel anything because I was in a hurry. But
hey. Eunuch Grandpa, wow. So you're like, 'I can just recruit more
subordinates', yeah?"

"You bitch? How……"

"I don't know. I thought I was going to die, but I'm still alive? Ah, but
two, four, six……, who killed all the subordinates that just died? Was it
Gyeong Damgan who detonated the Queen Mother Poison? Or was it
the Secondary Blood Poison Altar who released the Poisonous
Essence? Or perhaps, you wouldn't dare accuse me, who tried to
reduce their suffering, of being a murderer, would you?"

"That's… well? Trying to reduce their suffering……?"

Gyeong Damgan paused.

It didn't really make sense, but it also kind of did, and it also sounded
like bullshit.

Meanwhile, Qing stood up, dusted off her clothes, and drew a sword
from a corpse's waist.

Sanie, I'm sorry. Choryeo, I'm sorry.

But I guess I'm just a swordsman, after all.

I feel at ease with a sword in my hand.

Qing swung the sword a couple of times.

Namgung Shinjae said that Qing's skill was at the level of 'Wielding a
Sword', grasping its weight and length to wield it like a familiar
weapon.

It was a bit of a cheap sword with an unbalanced center, but it would
be fine for a nameless mook to swing around.

Qing held the Moonlight Sword (No. 10) and spoke.

For reference, wooden swords and practice swords with blunted blades
were not recognized as Moonlight Swords. This was because, to Qing,
swords were tools for cutting people.

"Are you still going to keep talking?"

"Ha! Presumptuous! Let us see that meager skill of yours!"

Gyeong Damgan said that and rushed forward first.

Qing easily twisted and pushed away the oncoming trajectory, but did
not stop talking.

"Don't you usually offer to yield three moves as a senior of Jianghu?
Have you been eating your age through your asshole? Have some
shame, you know."

"Hmph. Do you think I am some kind of naive fool from the Orthodox
Faction!"

"Is that even a question? You just look like an old, ugly eunuch to me."

"You keep going with that! Eunuch! Eunuch! Eunuch! I am! Not an!
Eunuch!"

With each shout, a strike of his sword followed.

In comparison, Qing's manner of speaking was relaxed, as if she was
not in a fight against a Late-Stage Transcendent Realm Master who
used Sword Force.

"So, does your dick still work? When you're about to throw it away,
you shake your limp dick around. That must be so sad. The deceased
left a will, saying it was very pitiful."

"Argh! Die! Dieee!"

"Are you going to kill me with that? Try harder."

Even though Gyeong Damgan was a Transcendent Realm Master
without even considering the parasite, for some reason, he kept
getting pushed back by Qing's skill.

That's right, Qing's sword was a dreadful Killing Sword.

However, for nearly a month, she had sealed her Killing Sword, the
technique she was best at, and trained fiercely.

It was only natural for Qing's skill to have improved by leaps and
bounds.

Moreover, when using the Killing Sword, the Sword Qi imbued with
the Heavenly Slaughtering Star became harder and sharper the more
carnage she had accumulated.

When combined with her absurd output, it was not difficult to clash
against and counter the loosely compressed Sword Force of a
Transcendent Realm Master.

"Why! Why! Why! Die!"

"Hmm. Honestly, well. I did expect this, but… You're more
disappointing than I thought. It's no fun anymore."

In an instant, Qing's eyes flashed.

At the same time, Qing's sword drew the most absolute trajectory.

Below Heaven, the laziest sword, but this could be the virtue of an
emperor, for the ruler of all under Heaven must not move carelessly,
but when he does, he must shake Heaven and Earth.

Slash. Gyeong Damgan's sword, along with his wrist, fell to the ground
with a loud clang.

Gyeong Damgan hastily sealed his wrist's pressure point and wrapped
his severed hand with a towel.

Qing just looked down at that sight, and Gyeong Damgan muttered
incredulously.

"How, how is it that you are only at the Peak Realm……"

"Hmm. Curious? It'll cost five hundred nyang if you're curious. Anyway,
wasn't it obvious I would win from the start?"

"What nonsense is that! The difference in realm is-"

"Hey. When you lost your mind earlier, you used the parasite instead of
drawing your sword. You should have drawn your sword then.
Shouldn't that be the obvious thing to do when insulted as a martial
artist?"

"What does that even mean!?"

"You relied on the parasite, so your sword is shit now. When was the
last time you sincerely swung your sword?"

"Ah. Aaaah……"

Gyeong Damgan was also a Transcendent Realm Master.

He understood Qing's words.

When Gyeong Damgan lost his mind and his eyes rolled back, the
explosion that erupted was the suicide command of the Queen Mother
Blood Poison.

It should have been a moment to draw his sword, so it had been a long
time since he had forgotten his sword in favor of the omnipotence of
the parasite.

No matter how much of a Transcendent Realm Master he was, what use
was there if he wasn't even a swordsman?

Qing had already let go of her thoughts since then.

Transcendent Realm or whatever, it's already rusted all over, so I'm
obviously not going to lose.

Qing pointed with the tip of her sword and asked.

"So, where is the Great Lord?"

That was why Qing had returned to the underground.

She was certain there was supposed to be a head honcho, but she had
never even seen his face.

It wasn't to taunt the old man, but there was perhaps a slight selfish
desire to enjoy the fun of plucking out the limbs of bugs.

Originally, if she had just killed the first one, the rest would have been
exterminated by the automatic chain suicide command following the
death of the Queen Mother Poison.

But there was another Queen Mother Poison of the same rank that she
had yet to see, so she couldn't help but be concerned.

"I don't know either. He hasn't been seen since this morning. Whether
he got drunk and passed out or found some suitable ingredients to
enjoy by himself, how would I know?"