\chapter{A Ronin Has a Ronin's Sense of Loyalty(16)}

In truth, there was no difference in intelligence between the primitive
pre-modern humans and modern humans.

But there was a distinct difference between the two. Modern humans
were much physically weaker than their ancestors. Instead, they
gained adaptability to tools.

At the very least, modern humans could figure out how to operate tools
just by tinkering with them for a bit.

This was also true for Qing, who quickly learned the operation of the
Training Machine for Preserving Internal Organs, which Cheon Yuhak
had memorized after all sorts of scolding from his teacher, including
comments like, 'Ha, you can't even memorize this? I bet you'll cut off
your own disciple's limbs and sever their tendons later on. Aigo, is this
the end of the Divine Thief title? Ehew.'

As someone who had worked in manufacturing, she knew that as long
as she followed one simple rule, these non-electric, primitive machines
would not malfunction.

Do not force it. That was all.

Thanks to this, after turning and tightening various parts, Qing became
quite skilled at operating the training machine.

Unfortunately, due to her inexperience in operation, she had ended up
breaking three of her precious fingers. They weren't even cleanly
severed, which would have allowed her to enjoy the sensation of them
being slowly cut. Rather, they were broken in the opposite direction at
the joints.

"Ugh! Uuuugh! Uuuuuuugh!"

"Grandpa. Do you have something to say?"

"Ugh! Ugh!"

Gyeong Damgan responded fervently.

Qing pondered for a moment.

Hm, should I untie him? But if he bites his tongue, well, bites?

Qing soon slapped her palm with her fist and untied Gyeong Damgan's
gag.

"What is the meaning of this! You, martial artists of the Orthodox
Fa……"

Qing grabbed Gyeong Damgan's jaw, which was moving up and down,
causing the latter part of his sentence to be garbled.

"Come to think of it, I put a gag on you to prevent you from biting your
teeth or your tongue. But we're not exactly in a relationship where we
need to worry about each other's dental health, are we?"

Then, Qing shoved her fingers into Gyeong Damgan's mouth.

Gyeong Damgan bit down with all his might, but it would be ridiculous
if the beautiful hand of the White Hand Demonic Arts, feared by
everyone under Heaven, were to be damaged by mere teeth.

"Ah. What I'm going to do is… I'm going to pull out all of Grandpa's
teeth. Then, you won't get hurt even if I don't put a gag on you, right?"

"Ah, ah!"

"I'll give the extracted teeth to Young Lady Moyong as a gift. You like
pulling out people's teeth, don't you, Grandpa? I heard you pulled out
four of Young Lady Moyong's molars. Revenge should be a hundred, no,
a thousand times over, so if I give her all your teeth, it will be a
consolation, right? Now then. One."

"Argh!"

"Two."

"Arghh!!"

"Ugh, why are you licking someone else's hand? Are you a dog,
Grandpa? Oh, right. You are a dog, huh. Do you think your tongue can
push my fingers away? Just give up and accept that you're paying for
your sins in your old age."

"Argh!"

"Here we go. Four. Aigoo, this old man has such strong teeth. I wonder
why Masters have such healthy teeth. Is it the mysterious power of
Inner Qi?"

Qing pulled out Gyeong Damgan's teeth, one by one, skipping every
other tooth.

Originally, human teeth were called teeth, while animal teeth were
called fangs. In that sense, it was more appropriate to call Gyeong
Damgan's teeth fangs.

Qing thought they would be firmly held and easily extracted like a
prefabricated toy, but surprisingly, there were tough tendons, ooh.

As such, the roots of the teeth held on firmly, so when Qing pulled with
force, they were torn out with the flesh, providing a solid and
fulfilling sensation.

The instinct of living things was to disperse pain by struggling when
hurt, even if just a little.

Conversely, it meant that if one could not struggle, the pain would be
doubled.

"ARGHHHH! How can you be so cruel! You bitch without blood or tears!
How can someone like you be a righteous martial artist! You're like the
Killing Star of all under Heaven!"

Of course, Gyeong Damgan's pronunciation was very inaccurate
because all his teeth were gone, but this was what Qing heard.

"Aigo, kill me! Kill me!"

"Hmm. That's not right. It's not 'kill me'. It's 'please kill me'. Very
politely. 'Please, kill me.' Even if you beg and plead with tears, I might
not listen to you. Though, I won't listen to you anyway."

Qing said with a bright smile.

Gyeong Damgan was still unsure.

Was this the revenge of a martial artist from the Orthodox Faction,
who believed that evil should be punished with extreme pain?

Or was it merely an act to enjoy the suffering of others?

And now, he knew.

This bitch is just like me.

"Oh my. Now you're showing some fear. Hmm. Respect is indeed born
from fear, after all. Are you going to be polite now? Where did that
audacity go when you were talking down to a young lady who is barely
the age of your granddaughter? These old folks nowadays have no sense
of hierarchy, tsk."

It was almost a reversal of the relationship between the young and the
old.

Since she was just babbling whatever came to mind, even Qing didn't
know what she was saying.

She was just like a child, chattering away in high spirits.

"Please, please save me……"

"Aigoo. You still can't get it right. It's not 'save me'. It's 'kill me'. That's
what an old man should beg for. But I won't do it. Hehe. Are you upset?
But what can you do about it, Grandpa? You don't even have teeth.
Want to bite your tongue?"

"I-"

Qing interrupted Gyeong Damgan's words with a sweet smile.

"Think of it as a preview before going to hell. Ah. And this room has
great soundproofing, and I really love hearing screams, so don't hold
back and feel free to yell to your heart's content. Then, shall we start
playing in earnest, hmm?"

A noisy and enjoyable time passed.

Qing's understanding of the human body deepened.

She had completely mastered the limits of joints and tendons, the
resistance felt when reaching the limit of movement, and how much
more force was needed to completely destroy them after countless
attempts.

After all the joints of the Limping Mad Demon were disabled, Qing laid
down on the floor, exhausted.

But with just the joints disconnected, the bones and flesh were still
intact, so there was still much to enjoy.

Qing could confidently say that the Training Machine for Preserving
Internal Organs was truly the greatest device in Zhongyuan.

And then, Qing did as she pleased. The only downside was that the
Great Demonic Adept, who had been screaming pleasurably at first,
gradually reduced his volume.

Even after Qing poured salt water into his mouth to encourage him, it
was only effective for a moment.

"Please kill me, please, I beg you. Kill me, just kill me. I was wrong, I am
a sinner who deserves death. So please kill me……"

"Ehh, you're being noisy while I'm trying to rest."

"Guh."

"I told you I'd kill you, so just wait. Now that playtime's over."

"Thank, thank you."

Qing replied with a chuckle.

"Playtime is over, so it's time to start for real. I wasn't having fun
because there wasn't any blood. I'll untie you, so run away if you don't
want to be dissected alive. If you don't run, I'll take it as your consent
and start peeling the flesh from your fingertips."

The Great Demonic Adept of the Blood Cult, whose tendons were all
severed, could do nothing but wriggle, even after being untied.

"Eek, kill me, kill me, please kill me!"

"I already told you that at the beginning, didn't I? That I wouldn't listen
to you anyway. You've been torturing people your whole life, but you
can't even endure this? Come on now."

As someone who had endured, and for three hours at that, Qing was
entitled to say such words.

Qing smiled and drew the Blue Wave Sword.

It was a sharp weapon she had recovered with the help of a Blood Cult
martial artist.

And then.

I wondered why they always tortured people in the bathroom in
movies.

But now that it's over, it's so nice to just wash everything away.

Everyone really knows what's good for them.

Qing's eyes, as she left the bath, were clear.

It was a gentle gaze, like that of a Buddha who had attained Nirvana,
completely devoid of any lingering desire.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's next match was against Wang Nopil, the master of chair-based
violence.

However, after slitting his stomach open and removing the poisonous
salamander, he was unable to participate in the match and applied for
forfeiture.

"You don't have to forfeit. I could have gone easy on you. You could
have at least swung a chair around before going down."

"Hahahacough."

Wang Nopil tried to laugh like a real man but ended up clutching his
stomach. Laughing heartily consumed a lot of abdominal muscles, so
his incompletely healed stomach ached.

"Isn't victory and defeat determined only after a bout? Even if Young
Lady Ximen is a master of the sword, the outcome of a duel is-"

"Do you really need to compare a bamboo shoot and a bamboo tree to
know which one is longer? This is just a case of an honorable defeat."

"An honorable defeat?"

"You were going to lose anyway, but since you couldn't participate in
the match because of the surgery, you can say it was an honorable
defeat, right? If you hadn't had that hole in your stomach, you could
have claimed that you would have dealt with me in the Round of Eight
in the Hidden Dragon Sparring Meet."

At that, Wang Nopil laughed again and grimaced.

"You consider winning as a given, huh?"

"Well, isn't it?"

After finishing their visit with the ronin who had taken up residence on
the third floor of the Martial Union without permission, Qing climbed
the stairs to the top floor where she stayed.

Another uninvited resident was staying in the best guest room of the
Martial Union, which Qing and Ximen Surin were using.

"Young Lady Moyong. How is your body?"

"Eek."

Moyong Juhui shuddered and pulled the blanket over her head.

Then, she slowly lowered it, peeking out with just her eyes to look at
Qing.

Qing looked at Moyong Juhui with pity.

"What, what! What is that look in your eyes?! It's making me feel
uncomfortable, you know?!"

"It's okay. I understand everything. Here, this might help. It's a gift."

Qing handed over a neatly wrapped silk bundle.

Moyong Juhui, half in doubt and half in reluctance, unwrapped the
bundle, only to be startled and scream.

In the midst of her reaction, Gyeong Damgan's teeth, which had been
meticulously cleaned, scattered in the air.

"What are you doing! Why are you doing this to me!"

"It's… the teeth of the Limping Mad Demon. I thought it might be
somewhat of a consolation to Young Lady Moyong. Of course, I pulled
them all out while he was alive."

"I don't need this, this kind of thing! Why! Why are you doing this to
me! What did I do wrong! Just get lost! I hate you! I resent you! I don't
want to see your face!"

Moyong Juhui screamed hysterically.

No, it was an actual fit, in fact.

Qing's eyebrows twitched.

Geez, even after I saved her.

But she could understand.

After such a terrible ordeal, it was only natural for her mind to be
afflicted.

Qing offered her own form of consolation.

It was the same consolation her sworn sister had given her when she
was struggling in the Demonic Cult. After all, it had been a great comfort
to her.

Qing forcibly hugged Moyong Juhui.

"Let go! Let go of me! What are you doing!"

"It's okay. Shh. It's okay. Young Lady Moyong is not at fault. I took care
of all the bad guys. Think of it as a bad dream, a terrible nightmare.
You are a strong person, so I believe you can overcome it. Both in body
and mind."

"Let go, let go of me……"

Moyong Juhui's voice was damp.

"It's all okay. And no one will ever know what happened to Young Lady
Moyong. There are only four people who know, and they are all
trustworthy individuals who can keep their mouths shut. So rest assured
and focus on recovery, urk! Argh!"

Suddenly, while consoling her, Qing screamed in pain.

Qing's voice, full of agony, trembled thinly.

"Why, why……?" 
