\chapter{A Ronin Has a Ronin's Sense of Loyalty(8)}

"Are you, are you really promising to save me? Could you swear upon
the honor of your sect and master?"

"I told you, I always keep my promises. If you tell me everything you
know truthfully, I will promise you on my master and the Divine
Maiden Sect's honor that I will let you go safely this time. Only this
time. Are you telling me not to ever touch you again just because you
spilled some information?"

Qing made the promise while also adding a few words.

It was because she knew adding such a caveat would actually make her
words more trustworthy.

"No. Uh, first, I am Yu Sung-gwang, and I am the senior warrior of the
Second Squad, under the command of the Deadwood Venerable of the
Blood Cult."

"Second Squad?"

"The Second Squad is named after a type of venomous worm that has
two lines on its body. It is because the venomous worm we handle in
our unit is this very worm……"

The guard answered all questions truthfully.

From the organization of the Blood Cult to the structure of the unit,
and about himself and his mission, everything was laid out
haphazardly.

The main purpose of the unit that handled the Blood Venom Worms was
to infiltrate Wulin and secure key figures by feeding them these
worms.

However, simply feeding them the worms was not enough to feel
secure. After all, there were many ways to get rid of the worms.

Therefore, it was essential to completely break them down through
mental and physical torture after feeding them the worms.

This process turned them into obedient servants even after the worms
were removed.

"With the help of these now useless collaborators, we feed important
figures the worms, or extract information, or seek internal
cooperation-"

"Wait a minute."

Although Qing didn't particularly want to know the details, there was a
part that caught her attention.

"Useless collaborators? If they're useless, doesn't that mean they're
discarded? Is that your way of saying things?"

"Th-That is, the preferences of the Battalion Commander and Vice
Commander……"

The following contents were truly horrific.

The last step in breaking down the captured prisoners was to give them
to pigs, dogs, or beggars.

However, before that, they must not be directly tortured sexually. It
was the preference of the Battalion Commander and Vice Commander
to save the most precious thing to be taken away at the very end.

After experiencing such treatment in the end, neither men nor women
could ever resist again.

Qing briefly gave her opinion.

"Hmm. I suddenly feel like killing all of you."

"Y-You promised to spare me."

"The promise is still valid. I made it on the honor of my sect and my
master, so I can't break it. But the Blood Venom Worms? Can you tell me
more about that?"

And then, she heard a lecture directly from an expert about the
worms.

"So, I have told you everything I know."

"Hmm. But I don't know if you lied to me or not. So wait a moment. I'll
catch another one and cross-check."

"I have only told the truth-"

"Enough. Do you think I wouldn't know if you're lying to me? This is
your last chance to correct anything. I clearly said I would spare you if
you told me everything you knew without lying, right? But if you
deceived me?"

Qing's pupils narrowed.

It was a very sinister look, with the whites of her eyes showing on all
four sides of her pupils, and a subtle, ominous purple gleam flickering
within.

The Blood Cult warrior, who was called Yu Sung-gwang, trembled, his
breath catching in his throat.

He was overwhelmed by the true colors of the most evil star among all
the ominous stars, the lonely star of Heavenly Slaughter.

"If so, you will beg me to kill you. I'll start by peeling off your skin first.
Last chance. Anything you've hidden or lied about, anything at all?"

"That is, in truth……"

Some information was corrected, and some other trivial information
was revealed.

Seeing his desperate expression, it seemed like he was telling the truth
this time.

"Then, since you have told me everything, now."

"Alright. I have to keep my promise."

Qing nodded and then spoke again.

"But what is your father's name?"

The warrior swallowed hard.

"Why are you asking that?"

"You didn't tell me. I clearly told you to tell me everything you know.
There are still things you've hidden, aren't there?"

"Ah, no. My father is……"

And then, other family details that he hadn't even been asked about
came pouring out.

"Is that so? Then what are your favorite foods? What about your
dislikes? Are there any foods you can't eat?"

"Why food all of a sudden……"

"What are your hobbies? What is your ideal type of woman? Who are
your close friends, and what are your embarrassing childhood
memories? I clearly remember asking you to tell me everything you
knew, didn't I?"

Qing's eyes narrowed.

"Why did you tell me everything, but there are so many things I don't
know? You were planning to deceive me from the start, weren't you?
My goodness, you're trying to deceive me? As promised, since you've
hidden things, you must die."

"That doesn't make any seon."

The Blood Cult warrior's pants were shoved into his mouth.

Seeing Qing's radiant, wide smile, he finally realized.

She had no intention of sparing him from the start.

Demanding to know everything was an impossible request from the
outset, so it was obviously an unfulfillable condition.

"I don't know if this will be any consolation, but at least you won't be
going alone. So don't feel too wronged about being the only one to
suffer."

It wasn't much of a consolation, and the Blood Cult warrior struggled
desperately.

Then, Qing clapped her hands and spoke again.

"Ah, you said the soundproofing was perfect, right? Sorry. I'll take out
the gag. It must be agonizing for you. You should at least be able to
scream."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

[Omen, (Unknown)th Crisis]\newline
[You have encountered the evil purpose of the Blood Cult.]\newline
Actions to perform the mission\newline
………………

"Why are you stating the obvious only after I figured it all out?"

Why is it acting like it's the one who figured it out and is kindly
informing me?

Qing clicked her tongue and dismissed the newly updated Martial Arts
Window.

Well, whatever. It's a good thing to earn Righteous Karma as a bonus
for doing fun things, and to get additional Practice Points as a reward.
If they told me exactly what to do, I'd feel like I was being used, but
saying they won't interfere no matter whose side I take is just being
unreliable.

I can't bring myself to like that attitude, no matter what.

However, she felt no anxiety.

After all, Qing was currently feeling better and more refreshed than
ever before.

Qing took the key to the cell from the guard-who-was-no-longer-a-guard
and stood up twice.

The reason she stood up twice was because she stumbled and fell hard
while trying to stand up, so she had to stand up again.

This is what happens when you get an intense rush of blood to the
skin. Mmm. Seriously. Wow, it's fucking crazy. Seriously.

But well. It felt really good, so, it's fine, isn't it?

With unusually clear eyes, Qing, covered in blood, opened the cell door
and headed outside.

The guards took turns, one per day.

All day long, they would harass the prisoners, and at night, they could
either set up a cot to sleep or tease the prisoners to keep them awake
for fun. Either way, it was a very lax assignment where no one
bothered them.

Moreover, since they could rest all day the next day, it was said to be a
sweet gig that only those of higher ranks could take on.

It was a familiar culture, showing that organizations of this kind
operated similarly no matter where they were.

Since Qing was minding her own business, she had no reason to be
rough.

The poison was just an automatic purification parasite that sucked out
toxins, and Qing could escape whenever she wanted.

The only thing she was worried about was the lives of the ronin who
might have swallowed the poison pills without knowing what they
were.

As someone's had said, it wasn't that she had trapped them, but rather
that they were trapped with her.

Which movie was that from? Batman? Aliens?

The correct answer was Watchmen, but Qing couldn't possibly know
that. After all, her memories of her Korean heritage were fading,
occasionally coming to her in dreams, reminding her of those times.
And when she woke up from such dreams, she would be overcome with
terror and tremble for a while.

What if I go back?

Now, she was certain that she could never adapt to the modern world
again.

Agh, shit. Bad thoughts again.

Still, her body and mind were so refreshed that she could easily shake
them off.

Qing pushed open the iron door leading outside.

Creak! The iron door opened with a shriek.

They should really oil this thing. The facilities are so poorly maintained.

After leaving this Second Training Room, Qing checked the numbers to
the left and right, then knocked on the iron door of the First Training
Room.

Then, a small iron plate slid open from a hole under the door, and a
voice answered.

"What, who is it?"

At the same time, Qing pushed the iron door with all her might.

Creak! The heavy iron door moved effortlessly, unable to withstand her
monstrous strength, then thump! It hit something with a loud thud,
meeting strong resistance that struck Qing's wrist.

Qing quickly entered and closed the iron door, then pushed the hole
closed with her foot.

This would make it completely sealed. The deceased had said that no
sound from inside could be heard.

And then, alas.

The guard of the First Training Room was lying on the floor, bleeding
from his head.

"Ah shit, I hope he's not dead. What a waste."

Qing hurriedly checked the guard's pulse.

She preferred to dismantle the living, not to tamper with corpses,
which was a disgusting and disrespectful act against the deceased.

Fortunately, the guard seemed to have just fainted from a concussion.

Qing stripped him from top to bottom, tied his hands and feet to
prevent him from escaping.

Since the soundproofing was good, there was no need to gag him,
knowing that this was the kind of advice that could only be given when
one has learned that knowledge is power.

Taking the key to the cell, Qing opened the cell door. Then, she heard a
startled voice.

"Eek."

In the center of the cell, there was a small iron box from which the
voice came.

There was one in Qing's room too. She thought it was a toilet, but it
turned out to be a torture device.

It was said to force oneself into that small box, and the worms would
release poison every time one tried to get out, thus tormenting them.

Qing sighed and spoke.

"Young Lady? Are you okay?"

"I am not a Young Lady, but livestock. I am not a Young Lady, but
livestock. I am not a Young Lady, but livestock……"

Hmm. She seems to be completely broken, huh?

Qing scratched her head.

Operation Annihilation.

It was the purpose of the Blood Cult that Qing had learned.

Despite the grand-sounding name, the contents were quite petty.

It was a plan to ruin the Wulin Tournament and disgrace the Orthodox
Factions of Wulin.

It was a plan to capture the most famous figures, brutally break them,
and exhibit them during the biggest event held in the city where the
Orthodox Wulin Alliance was firmly established.

For the capabilities of the Second Squad, they couldn't handle anyone
too powerful.

In the first place, it was said that ordinary worms couldn't even affect
martial artists above the Unrestrained Realm, as they would just burn
away the toxins.

Excluding Masters, famous Rising Stars would be the targets. And to
maximize the shock, they naturally aimed for the Five Flowers of
Wulin, the beautiful flowers loved by everyone in the Orthodox
Factions.

That was why it was called Operation Annihilation, a plan to annihilate
the flowers.

The initial plan was to target the easy White Lily.

However, an order came from higher-ups not to touch her, so it was
passed.

The Poison Flower wouldn't work because the worms wouldn't have any
effect, so that was also passed.

They didn't even know if the Mysterious Flower would participate in
the Wulin Tournament.

Therefore, the remaining targets were either the Snowy Flower or the
Sword Flower, or both.

They were watching for an opportunity, as the Snowy Flower seldom
left her residence. Meanwhile, they caught the Sword Flower leaving
the city, apparently ashamed of her defeat by a ronin in the martial
arts competition, and were in the process of educating her.

"Young Lady Mo. I'm Ximen Qing."

"I am not a Young Lady."

Then, the top part of the iron box opened slightly, and the box shook
violently before falling to its side.

Between the gaps, Mo Yung-joo barely managed to squeeze herself out,
though it looked more like she was spilling onto the floor. 
