\chapter{Honestly, You Have to Understand This (2)}

Only Qing knew that Qing had made up her mind.

So, everyone else just continued on with their usual lives.

Taiping Sword Sect demanded legitimate compensation for their protection once again.

Owner Jin protested his chagrin.

However, the martial artists of the Taiping Sword Sect were, in fact, just the lowest members of their organization. They had no authority to decide whether to accept or decline the protection fee.

In the end, Owner Jin was forced to hand over the protection fee.

It was a future that had already been decided, so it was nothing out of the ordinary.

The anomaly occurred elsewhere.

From the moment he entered the bar, Nan Jiangding \footnote{南江碇. Nam Gangjeong in the original text}, the Third Captain of the Taiping Sword Sect, had been continuously concerned about a woman.

Since the time Xi Shi, the Most Beautiful Woman in History, frowned, the vast majority of people in Zhongyuan developed a peculiar sexual preference for frowning faces.

Naa Jiangding, being an ordinary martial artist, shared the same sexual preference. 

The sight of a woman, seemingly uncomfortable and tired of all that was in the world, tipping her drink into her mouth!

Moreover, she wasn't extremely beautiful, which made him even more drawn to her. After all, it seemed like he had somewhat of a chance if it was her.

If it weren't for the serious matters of his sect, he would have immediately rushed over to share her worries.

Just as he was thinking this, he saw the woman approaching him.

Even more, with a smile in her eyes!

Dream-like fantasies unfolded in Nan Jiangding's mind.

However, Nan Jiangding should have paid more attention to Qing's hands rather than her face.

If he had, he would have remembered the old bar saying that no decent person came at you gripping the neck of a liquor bottle.

'Good people do not come ones way and those who do come are not good.'

Good people would not come his way, and Qing, smiling slyly as she approached, was most definitely not in a state where she was a good person.

Unfortunately, Nan Jiangding's dreams of a happy future ended with a physical collision between his head and the liquor bottle.

It was a clash between a cheap porcelain bottle and a skull.

The outcome was exactly as anyone could easily predict.

Crack!

The shattered pieces of porcelain mixed the scent of liquor flew through the air.

Nan Jiangding staggered, soaked in strong alcohol, not because he was drunk, but because he was hit squarely on the head.

However, a martial artist at the end of the Second-Rate would not fall just from a mere battle.

The reason why it was described as just end was because the world was not leisurely enough to categorize every mediocre Second-Rate fodder into Early, Mid, and Late-Stages.

Nan Jiangding yelled in fury.

"W-What is the meaning of this?!"

"Violence. Disturbance. And also, um, making a scene."

Qing clearly explained her actions.

Normally, this was where swords would be drawn, but Qing's appearance granted Nan Jiangding a single moment of patience.

"Young Lady. Right now, you are being extremely rude to a disciple of the Great Taiping Sword Sect. Perhaps you have had too much to drink."

\textit{What the hell? Why is he not understanding?}

Qing cocked her head.

"I'm not picking a fight with the Great Taiping whatever thingy. I'm just causing a disturbance in a bar. "

Nan Jiangding pondered over how the two were different.

And Qing graciously provided the answer.

"You received the protection fee, didn't you? Isn't the protection fee supposed to be for protecting the establishment from people who cause violence, start disturbances, and make a scene?"

"...?"

Qing pointed her long finger at herself.

"Here. Trouble."

Qing folded her finger and pushed it forward. Nan Jiangding's chin turned slightly.

Then, the punch from Qings other hand drew a semicircle.

Nan Jiangding's turned chin was instantly corrected.

Though, the hit was a bit more powerful and ended up turning his head to the other side.

Nan Jiangding, hit in the jaw, staggered and collapsed, while Qing flexed her fingers and shook her hand.

"Now, then. Disturbance added. Are the rest of you just going to watch?"

Those words became a kind of signal.

Still, no swords were drawn, not because they were righteous or from the Orthodox Faction, but because underestimating female martial artists in Zhongyuan was not all that new of a trend.

In the first place, they were just sect disciples who went around collecting protection fees, so their martial prowess was not particularly exceptional.

Qing punched, struck, hit, and swung.

When she grabbed a wist and pushed, two fell crashing down.

When she poked the shin of someone charging from the right with the tip of her foot, he clutched at it with both hands and rolled on the ground.

"That is no ordinary capability! Everyone, draw your swords!"

Nan Jiangding, having overcome his brief concussion, charged in as he shouted.

Still, it was at the level of being cute, all the same.

Qing was fighting without even using her Inner Qi.

After all, if she used her Inner Qi, she wouldn't just be hitting them but literally making them explode.

Even without Inner Qi, Qing was already among the strongest under the Heavens.

WIth the achievements of the martial arts she had mastered and the accumulation of increased Stats, she had become one of the most formidable forces in Zhongyuan based purely on her physical strength.

To be fair, her basic stats were exceptionally high.

This was the reason Qing, with no prior knowledge and a soft-hearted disposition typical of modern people, was able to survive the early stages of the cutthroat world of Zhongyuan, where drawing swords was all but a common occurrence.

While Qing was skillfully navigating between swung swords and choosing where to strike, she suddenly noticed the crown of a man falling forward.

\textit{Eh? Can I also? Do a nuclear noogie?}

A montage of profoundly humiliating moments rushed through her mind.

{\itshape It is a favor that I can never repay to Teacher.

  So, this Disciple will carry that sentiment with her, thus bestowing such a favor to others.}

It was then that Qing clenched her fist, making her middle finger protrude amongst her digits.

"Stop! Stop!"

Nan Jiangding, who had already taken quite the beating, flailed his arms desperately.

His eyelids were already swollen and bruised.

"I am grateful for your leniency. I have realized my shortcomings, so please allow me to retreat."

She didn't hold back, though. She just beat the shit out of them.

Nevertheless, since he was someone who could at least manifest a pretense of wrapping Inner Qi around his body, his bones remained intact and he was still standing fairly unscathed.

"What's this? Isn't this your Taiping Sword Sect, ooooh, I managed to memorize this, huh. It's nice that its so easy to remember. Anyway, isn't this an establishment youre supposed to protect? You're just going to leave like this?"

"As I said befor-"

"Enough. Forget that."

Qing interrupted Nan Jiangding.

"I spared your life, so leave your sword here as compensation. I should gain something out of this too, shouldn't I?"

Hearing this, the warriors of the Taiping Sword Sect hesitated, at a loss for what to do.

Still, it didnt seem like he was the Captain for no reason, seeing as how Nan Jiangding stepped forward.

"Young Lady. A sword is as vital as life to a swordsman."

"Whatever. I'm a swordsman too, you know? Then shall we have a serious sword duel with our lives on the line?"

Qing gestured with her chin towards the table where she was sitting.

Seeing the Moonlight Sword (No. 8) peacefully resting there, the martial artists eventually let go of their swords.

The sight of the Taiping Sword Sect disciples leaving with their shoulder slumped was all too pitiful. 

"Hoooo."

\textit{It was somewhat f. u. n. But. This. FUCKING!}

As soon as the playtime ended, the throbbing pain and various discomforts like tingling, numbness, and stiffness aggressively returned, contorting Qings face. 

Moreover, it even felt a bit wet and sticky.

{\itshape  Did all women in the world live like this? Holy fuck!

  It's so sad that I haven't reached the Transcendent Realm yet. Seriously, it's gonna make me cry. }

As Qing searched for alcohol, she realized, 'Oh shit!'.

Why? Because it had already spilled along with what was once a bottle.

\textit{My liquor.}

"Over here, Server."

"Excuse me, Customer..."

It wasn't a server but the owner who approached her.

The round bottle in his hand exuded luxury, even from its packaging.

Qing waved her hands in denial.

"Haiya, you don't have to be so thankful."

"That's not it. Please take this and, uh..."

Owner Jin hesitated, unable to continue.

It was obvious what he wanted to say but couldn't.

He was probably trying to ask her to leave.

"Look, Owner. If I leave now, will you be safe? Those fuckers will definitely bring their mommies. If I'm not here, you or someone else will get beaten. Isn't that right? It's not like you're a newbie to this business."

Qing had learned this from her experiences.

The fuckers affiliated with martial art unions always ran off to cry out for their mommies or an existence of similar standing.

When Qing was living the life of a low realm fodder, she had no choice but to take a beating and flee.   

\textit{But now? I. Am. A. Master. An incredible Master.}

But also a Master in a very shitty mood.

"I'll clean up after myself and deal with the backlash, so just bring out the alcohol. Aghhh, fuck, so annoying. Shit."

Qings irritation spilled over.

Owner Jin placed the jug down with a ghastly face and quickly disappeared into the kitchen or somewhere similar. 

Qing peeled off the oiled cloth covering the jug.

As soon as she opened it, a strong scent of alcohol wafted over her.

Though it was a jug as big as a child's head, a Master of her caliber could pour it into a small cup, about the size of five beans, without spilling a single drop.

When she drank, it was so strong that she couldn't tell if it was alcohol or pure ethanol.

And she liked it for that very reason.

As she was drinking one cup after another without any side dishes to balance out the intense taste of liquor, an old beggar suddenly approached her and started to speak to her.

"Excuse me, Young Fairy."

"What do you want. I'm not buying. Go away."

Qing waved her arm dismissively.

"Hoho, the Young Fairy is quite heartless, isn't she?"

"Gramp. I've had some bad experiences with beggars, you see? Even if I'm heartless, you should be thankful I still respect the elderly, okay?"

"Hoho'"

"Otherwise, I might actually resort to attacking the elderly."

Qing was usually lenient towards old people.

By that, she didn't mean those who were just older in age.

She was talking about those whose ages were advanced to the point where they couldn't hide their wrinkles. Those who didn't have many days left.

"Cough, Cough."

The old man cleared his throat.

Then, he strangely fumbled around his waist. 

It was almost like he was asking her to take a look there.

When Qing glanced briefly, she noticed that, while his attire was utterly beggar-like, only the rope tied around his waist was conspicuously new and stiff.

Qing knew these kinds of beggars.

They were the extremely strong type.

In ancient China, even beggars had learned martial arts and those types wore such ropes around their waists.

Per usual, Qings knowledge came from experiencing it firsthand.

And also, per usual, Qings knowledge fell somewhat short.

But now, Qing was a Master.

No matter how strong, a beggar was still just a beggar. She was not afraid.