\chapter{Honestly, You Have to Understand This (4)}

The actions Qing enjoyed were as follows.

Murder, pulverization, torture, execution. Being covered in blood.

It was nice to do it with her own hands, but just watching was also fine.

All of these were phenomena that occurred during fights.

However, Qing didn't actually like the act of fighting in itself.

A fight where she couldn't enjoy her hobbies was nothing more than just labor.

It was annoying, exhausting, and difficult.

This was why Qing, when facing the Demonic Cannibal, could never truly enjoy the battle.

But now, she was asked to spar? Spaaaaaaar?

Why do that when there were so many great life-or-death battles to be had?

There had to be some enjoyment in cutting flesh and watching bones lay bare to justify the effort of straining her body.

Furthermore, before becoming the disciple of Ximen Surin, Qing had no experience with sparring.

After becoming a disciple, sparring was just an excuse for Ximen Surin's harsh punishment, thus Qing merely rolled around in agony.

As such, Qing was utterly sick of sparring.

On top of that, her mentality was in a very poor state at the moment.

Moreover, the young man wasn't an elder like Lu Gu.

There was no particular reason for her to show respect to him.

Qing wasn't an evil person, so she couldn't entertain herself with this lamb that walked straight into a wolf's den, but that didn't mean there was any reason for her to hide how pissed off she was.

"What's with this fucker? Just get lost."

The young man's expression turned dumbfounded.

After all, it was an insult he had only heard from close friends or relatives.

"Uh, tha...tIs that something you are saying to me?"

"Why? Is there anyone else here besides you?"

"How can you say such intemperate language upon our first meeti-

"Why? What about it? Oh, are you just bursting with etiquette and politeness by asking for a spar upon our first meeting? Do I look that easy to you? Because I'm a female brat wandering alone?"

After saying as such, a sudden surge of sadness welled up.

\textit{Do you think I wanted to turn out like this?}

In spite of herself, she spoke out.

"So, is it no problem for a young master dressed in such fine clothes to ask for a spar upon first meeting someone? And because I'm a bitch of unknown, shitty origins, you think it's fine for you to just come at me like that?"

Qing fired off a barrage of words.

It was the very definition of sudden, unexpected anger.

The young man was certainly rude.

But more than that, the timing was extremely bad.

Qings irritation was about to explode at any moment, like an active volcano bubbling.

So, obviously, if an earthquake shook it carelessly, it would spill out.

"Young Lady, it seems there has been a misunderstanding. I never had such intentions or thoughts."

At such words, Qing suddenly fixed her posture.

She straightened her slouch, stood tall with hands gently clasped together, and wore a soft and gentle expression, albeit with a slight frown.

As soon as her mouth opened, a beautiful voice mixed with a gentle flirtatious tone flowed out.

"Young Master. Thank you for offering to advise such an ignorant girl. The wild flowers of the mountains and fields are there but merely for the visual enjoyment of the guests. Do you really wish to pick them, only to have them wilt in sorrow?"

It wasn't that Qing couldn't be feminine.

She could if she had to.

The nuclear noogie truly was a great step forward in advancing the educational system of Zhongyuan.

"No, no, it is truly not that kind of rude trick-"

"I truly do go through all sorts of beggarly, pitiful situations. Just how much of a sin is it for a girl to just want to drink her fill and lie down quietly? What did she do so wrong that she has to be approached and made a fuss over by everyone and their mothers?"

In reality, the young man had a habit of immediately challenging unique swordsmen he encountered.

While staying briefly at the Taiping Sword Sect, he heard of a mysterious, unidentifiable female Master that had appeared, so he had come to watch.

Then, upon seeing the sword leaning against the table, he impulsively made a sparring request.

It was not because he looked down on Qing for being a woman.

However, Qing did have a point.

The requests for spars from a noble young master from a powerful clan had never been problematic before.

Who in the world could refuse a spar request from the Young Lord of the Nan'gong\footnote{南宮. Nan'gong in the original text} Clan?

"Uh, that...Young Lady? Please calm down a bit and-"

"Calm down? Do I look like I can calm down right now?"

Qing started her second outburst.

"Agh, seriously. You should experience it too! Want to feel what menstruation is like? Why don't you physically understand what a period is before you tell someone to calm down?!"

"Uh, uh..."

Nan'gong Shencai was completely flustered.

"Fucking hell, do you think it feels good to constantly bleed down there in spite of myself?! To have weights on my limbs?! To have my chest swell even more when its already so fucking heavy?! To not even be able to fucking sleep?! Thats why I'm trying to drink and rest, but now I'm asked to fucking spar?! Do you really think I'm in a position to spar right now?!"

After spitting out her frustrations, Qing stood up abruptly.

She picked up her belongings and slung them over her back, before fastening the sword that had been leaning against the table to her waist.

Additionally, she skillfully swept up five more long swords as spoils of war and walked away shamelessly.

The best instructor of the Taiping Sword Sect and First Sword of Anqing, Zuo Songmen \footnote{作松門; Jak Songmun in the original text}, was taken aback by the situation.

\textit{Why is she taking our swords?}

After all, one could not casually hand over swords marked with their sect's insignia to an outsider.

Zuo Songmen hastily reached out his hand.

"Young Lady? Wait, where are you going? We still have other things to talk abo-"

"I'm going to go shit out blood! What about it?!"

\textit{I shouldn't have reached out.}

Zuo Songmen immediately regretted his decisions.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Overwhelmed by emotions that were indistinguishable between anger and sadness, Qing just stayed cooped up in her room.

It did seem closer to sadness, though.

The things she had lost made her sad and her situation was miserable.

As such, she reluctantly tried to sleep with her uncomfortable body.

She faintly fell asleep only to wake up again and again.

Her drowsy mind could not tell if this was a dream, reality, or if she was truly awake or not.

She slept so much that she had a headache.

But then, she had no energy to get up, feeling utterly lethargic.

All she could do was just lay there, breathing in and out.

But even breathing wasn't easy.

The sun had risen and set, and then risen and set once again. How many times had it done so?

At some point, she woke up.

The sun was already high in the sky.

Her body felt refreshed.

To be precise, only her body felt refreshed.

Memories rushed back to Qing.

She considered this a kind of karma as well.

\textit{Ah, shit...}

Qing covered her face with her hands.    

\textit{Fuck. This is so fucking embarrassing. Agh, shit. Fuck.}

Originally, around this time, she would be in pain and turn sensitive.

But still, she had never shown such disgrace before.

Qing looked towards the corner of the guest room.

Six swords were present there. Even more, they were neatly lined up, in completely unnecessary fashion.

Besides the Moonlight Sword (No. 8), there were five spoils of war.

Was she actually a crazy piece of shit?

Why had she meticulously brought these along? In that haze of pain and annoyance?

Among the teachings of Ximen Surin, there was a rule not to steal matched weapons from members of a sect.

After all, if one took a weapon that a sect had collectively matched with each other, they would definitely come back to reclaim it.

It was only natural.

It was an issue of face for the sect.

From the perspective of modern Koreans, one might think, 'What's the big deal about losing face?'. But in Zhongyuan, losing face was no small matter.

From early times, what it meant to lose face was...Ugh!

Besides the issue of face, there were practical problems as well.

Killing someone randomly by the roadside and planting a weapon with a sects insignia there made framing someone very easy. Even if it was proven to be a false accusation, parts of the responsibility had to be shared in some fashion with the sect.

And besides that, there were several other similarly advanced applications.

As such, she must never steal weapons marked with a sects insignia.

When she responded to the question of how she had survived up to now with such lacking common sense, her teacher had given such advice in utter horror.

\textit{But in games, collecting item drops to sell was the absolute basics...}

Qing pushed aside the memories.

She sat quietly and reflected on yesterdays events.

{\itshape Honestly, it had turned into a bitttt of a violent rampage.

But, lets be real here. You have to be understanding of this.

Unless you lot experienced it yourself, you really can't say shit. Like seriously. This level of fuckery really, truly is the real fucking deal.}

Qing finished psyching herself up and left the room.

She intended to fill her empty stomach first.

So, she headed to the first floor.

And there she met the person waiting for Qing.

"Ah, Young Lady. Is your body feeling better?"

"...Yes."

After that fiasco, Qing stayed in her room for three days.

During that time, the rumors spread quickly through Anqing.

It was said that Nan'gong Shencai \footnote{神才 lit. 'godly talent'. Shinjae in the original text}, the Young Sword King, had challenged a woman who was menstruating to a spar, causing her great embarrassment.

'No matter the lack of sparring partners, how could he propose such a thing to a woman experiencing her period?' was what they said.

Rumors, by nature, tended to gain momentum and be added onto over time.

There were whispers that Nan'gong Shencai had deliberately sought to humiliate the woman, causing her to flee in tears.

Fortunately, since Anqing was close to Hefei and it was something that happened within Anhui Province, the rumors stopped spreading at a certain point.

Speaking ill of the Nan'gong Clan in Anhui Province could lead to ones head flying into the air even in broad daylight.

At any rate, Nan'gong Shencai had to take responsibility for the rumors.

Truth be told, Nan'gong Shencai felt a bit wronged.

Had he known, he would not have requested the spar.

But then again, it didn't mean he could exactly ask her about her state. After all, it was not the kind of question one could rightfully ask a woman.

Ultimately, a man should gauge a womans situation with subtlety, but how could he have known at first sight?

Nevertheless, thinking it was wrong to have immediately asked for a spar without formal introductions, he sought the help of an elder from the Beggars Union.

WIth the information-gathering capabilities of the Beggars Union, they managed to find the inn where the unnamed lady was staying.

A single woman who he didn't even know the name of.

Even Lu Gu didn't hear Qing's name and only knew some personal information about her.

Basically, it was an utter shitfest. Finding her, in itself, was difficult as well.

"Young Lady, I sincerely apologize for the other day. Had I known your condition, I would never have been so rude."

"Well...Whatever. Let's just forget it happened, then."

Qing, who was not feeling all that proud herself, nodded.

"Then, allow me to formally introduce myself. I am Shencai of Hefei's Nan'gong, the Greatest Sword Clan Under the Heavens."

"Oooh."

Qing exclaimed in admiration.

\textit{The Greatest Sword Clan Under the Heavens? Wow, look at them go.}

Noticing Nan'gong Shencai's expression, who seemed to question whether he had just heard correctly, Qing quickled added.

"I am Ximen Qing."

Qing spoke briefly since she didn't have much to say.

Also, she felt awkward due to the chaos she caused the day before.

To her surprise, Nan'gong Shencai then acted quite friendly.

"I have heard from Elder Lu Gu that you have reached the Late-Stage Peak Realm, Young Lady."

While Lu Gu kept secrets incredibly well, Qing had never specified that her realm was to be kept confidential when telling him.

Of course, Lu Gu wasn't playing some kind of trick or keeping up a pretense.

He had simply inferred she wasn't hiding her realm; if anything, Qing should be bragging about it, after all.

"What about it?"

"It is a bit embarrassing, but I am still at the Early-Stage. Therefore-"

Nan'gong Shencai's eyes sparkled as he continued.

"Young Lady, let us have a sparring match. No, I must ask this of you, on behalf of Nan'gong. Please."

Qing looked at Nan'gong Shencai, her eyes half-opened. 

\textit{Wait a fat fucking minute. Look at this fucker go. Seriously? Again???}