\chapter{Honestly, You Have to Understand This (1)}

Qing had always known nothing. However, the shitfest that occurred this time was particularly unfamiliar to her.

{\itshape Waterway Forts? What's that? Yangtze River? What's that? Dongting Lake? What's that?

Regional.whatchamacallit. Fucking civil servant positions are ridiculously complicated, huh. Fucking hell.

Demonic Cannibal? Sorry, I don't remember those weaker than me.}

All she had done was been lured by a free dinner, yet somehow she ended up becoming everyones hero.

Well, to be fair, it was a bit of an understatement to say she took down the Demonic Cannibal just because of a different bad guy. He was quite strong, after all.

It was all for the best. She shouldn't look the gift horse in the mouth.

The Forts of the Yangtze River Waterway was a wealthy business. And for that reason, the treatment of their benefactor was more than satisfactory.

Moreover, they even prepared a special event for Qing.        

Waterway Fort Commander, Bu Xiayun, had no time to dwell on the sorrow of losing his son.

After all, he had to prevent any backlash from the government.

Luckily, the Regional Inspector had become disabled.

It gave him a reason to tidy up relations.

After all, an exchange of Guanxi can only be possible if there was a flaw from above.

All accusations were directed towards the monstrous human named Yun Yuanling and a new backer had to be found.

As such, Bu Xiayun sublimated his sorrow of losing his son in another way.

Into hatred towards the evil traditionalists.

The name, traditionalist, was absurd from the start.

They were basically saying, 'Traditionally, we have always been thieves, so let us continue to live as thieves'.

Words must make sense to be considered words in the first place, shouldn't it?

But still, until now, they were someone's friend, as well as descendants of the previous generations Waterway Forts Seniors. As such, he chose to just watch from the side.

After all, he believed that they could change after experiencing prosperity and a dignified profession.

However, Bu Xiayun's trust was betrayed.

Now, the Waterway Fort Commanders conviction was solidified.

{\itshape I was too lenient on innovation and reform.

An overhaul begins with parting ways with the old generation!}

Coincidentally, it was the same idea as the epoch-making thoughts that others have also had in the far future or the past of a different time and space.

This was the strength of a group that had shared the same culture for a long time.

It's name? Red G!

Thus, with a single-minded determination, he was ready to break the back of tradition through the justification of a single piece becoming soaked in red.

The traditionalist scum were tied up and executed in a row.

And for the execution, the benefactor of the Waterway Forts volunteered to do it herself.

She had a nearly divine dignity when she nonchalantly sent peoples heads flying with a loose, friendly smile.

That was when it started.

When people began to show aversion.        

Qing read such an atmosphere and thought.

{\itshape These bastards seriously shouldn't be associated with, huh.

They were bastards who kept stabbing her in the back.

They said they'd take me to a nearby city but imprisoned me in the same room with a fucking nutcase.

They tried to sell me out after Yun Yuanling's identity was revealed.

Now, they seemed to hint that they wanted me to get lost.

Even though they talked about how I'm their eternal benefactor or whatever.}

Still, she liked the Dragon King Plaque they gave to her as a free gift.

The Dragon King Plaque represented the Forts of the Yangtze River Waterways commitment to treat its owner with utmost respect.

The highest respect river bandits could show was just one thing.

That under no circumstances would they charge a toll.

No toll was charged to ships boarded by the possessor of the Dragon King Plaque.

Unexpectedly, it might not seem like a big benefit to oneself, but in reality, that was not the case.

After all, the dream of every vessel passing through the Yangtze River was to have the Dragon King Plaque.

Forget boarding fees; the owner of the Dragon King Plaque was an existence that actually received hospitality, rather than needing to ask for it.

In essence, it was a free pass to the Yangtze River.

Qing was someone who didn't think too deeply about anything.

It was also because she was someone who shouldn't think deeply.

After all, that was why her executive ability was unparalleled.

Qing set off to the river on a boat she had acquired.

Meanwhile, she was engrossed in a certain thought for a period of time.

{\itshape Yes, that time.

When I used the Sixth Move of the Buddha's Palm, Cintamanicakra.

So, like, something was different.

Something, kind of like...

Kind of like that...}

It was a thought Qing kept revising.

\textit{Something. It was literally something.}

It was a frustrating feeling as if she was just about to grasp it, but couldn't quite do so.

It was much more ambiguous than the frustration of wanting to eat something desperately but not knowing what it was, felt during every meal.

She had used Buddha's Palm well at critical times.

But that time, the feeling was completely different.

\textit{It was like my Inner Qi, which had always moved like a machine, seemed to want to sing the end of the world and like, by itself, its amount was like, you know, something, like suddenly, so like, ah, fuck this.}

Still, she had a very strong premonition that she could grasp it if she thought about it a little more, just a little more deeply.

Qing felt frustrated to death, but in fact, this phenomenon was a precursor to a kind of enlightenment.

Qing's method of using Moves was akin to copy-pasting.

Forcedly imprinted Moves in the body and mind were unconsciously utilized.

However, Qings method wasn't all that odd.

Martial artists from prestigious families learned in this way as well.

After firmly imprinting Moves through tens of thousands of repetitions in their minds and bodies, they refined them through sparring and real combat.

Thus, they build up their own set of Moves, their own style of martial arts.

In Qing's case, the only difference was that she crammed the long process of imprinting, which normally took over ten years, all in one fell swoop.

And in the very present, Qing, the embodiment of ignorance, stood on the brink fully facing this faint wisdom.

It had begun.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qings manner of speaking was, as Ximen Surin put it, rougher than a colt gone wild.

Qing had never seen a colt gone wild.

As such, the expression didn't particularly resonate with her.

Of course, it was also that the Godmother, leading a mountain paradise for women, had incredibly strict standards.

But eventually, Ximen Surin came to accept it.

It was partially due to the fact that the surprisingly lonely, elderly woman had a soft spot for her ever so lovely disciple, who mingled without hesitation.

But the biggest reason was the insight that came with having lived a long life.

'I see. It is not that she can't speak in a feminine manner. It's just that she chooses not to.'

Qing was not particularly aware of this fact.

However, what should be kept in mind is that she had entered a world where her body, gender, and name had changed.

Moreover, it was a strange place where even the world itself had changed.

The manner of speaking that sounded so odd to the people of Zhongyuan was actually a mental barrier erected by the subconscious, striving to protect what was left of herself in memory.

For Qing, this actually made things even harder at times.

After all, it was a time that only came for women, known as menstruation.

Unable to bear it any longer on a ship, Qing immediately disembarked at the docked city.

When she rushed to a dry goods store, the female owner sent Qing a sympathetic look upon seeing her complexion.

It was the kind of empathy Qing did not wish to see or even know.

As such, she stocked up on a huge amount of cotton cloth.

\textit{Fuuuuuuuc.}

Every single joint felt painfully cold.

Muscles ached where they attached to the bone, making it hard to stay still, yet too tiring to move.

Even her fondness for gourmet food disappeared at these times.

Among the disciples of the Divine Maiden Sect, there were some who moaned in pain. Qings case was not of severe pain but of feeling mildly sick all day.

Her stomach hurt.

And her chest hurt even more than her stomach. Almost as if it was bruised.

And above all, this feeling of leakage was disgusting.

\textit{Ah. Seriously. I want to slaughter! Is there no Demonic Adept anywhere?}

For that reason, Qing was extremely on edge.

Shitty bastards who crossed paths with her at these times, unfortunately, ended up badly hurt even without starting a quarrel.

Staying cooped up in a room was suffocating, so she couldn't endure it.

That was why she came outside, but she just got annoyed again.

It was practically at the level of a mental illness.

What to do then, at times like this?

Watching bad guys perform in a kind of talent show was the best, but that was hardly possible in the city.

Instead, she might as well drown herself in alcohol and stay in a daze.

She had to reach the Transcendent Realm quickly!

According to Ximen Surin, once she underwent Overhaul Rebirth, the time of that month for women would pass just like any ordinary day.

\textit{But what the fuck am I expected to do? What am I. EXPECTED TO DO!}

Qing forcefully swallowed that screen with alcohol.

How should she put it? The bitter and tart, cheap liquor made it feel like her insides were burning, thus helping forget other pains.

As such, in one corner of the bar, a fuseless bomb was slowly heating up. 

That was why in today's case, it wasn't really Taiping Sword Sects fault.

Taiping Sword Sect had come to collect this months protection fees, just as they had always done.

However, it was after the Zhou Hu Union had attempted to expand the business by forcibly attracting new customers.

"W'eve already given this months protection money to the champions of the Zhou Hu Union."

"Is that so?"

A warrior of the Taiping Sword Sect paused to think, then asked.

"And what does that have to do with us?"

The owner was taken aback.

"What do you mean by that..."

"How is a private contract you made related in any way to our Taiping Sword Sect? After all, do we not have our own separate contract?"

"Then, are you asking for the protection f-

"Look here, Owner Jin. Sssssp. Something is quite strange. It almost seems like were extorting you. But isn't it only right for you to pay us, seeing as the Taiping Sword Sect is protecting you?"

Owner Jin's face fell as he replied.

"Then what about the protection fee I have already given to Zhou Hu Union?"

The warrior asked back with a puzzled look.

"Why are you asking me when you are the one who paid it?"

Flames of anger surged in Owner Jin's heart.

What was the point of all the protection fee paid so far if it was going to be like this?! Hadn't they diligently offered gold so that they would fend off bastards like the Zhou Hu Union?!

However, Owner Jin merely pleaded with a humble expression.

Since the one with the sword was ultimately king, Owner Jin, who did not have a sword, was at fault.

Moreover, such incidents would hardly make a case.

After all, it was commonplace in Zhongyuan.

In severe cases, there were stores that paid protection fees to four different martial arts unions at the same time.

Owner jin made a mistake by ambiguously setting up his shop on the boundary between two sects.

It was all Owner Jin's fault.

Upon seeing such a sight, Qing sincerely felt sorry for him.

Not just in the modern world but even within Wulin, the sorrow of small business owners resonated.

It was because of the Evil Karma of these mediocre, disagreeable warriors.

Taiping Sword Sect professed themselves to be part of the Orthodox Faction, and as such, they weren't all that bad.

The worst among them was about -56 and the best was about -3. Considering that they wielded swords, they lived relatively decent lives.

They were much better people than the men remaining on the wasen at the time of Ximens Stranded Records.  

As such, Qing pondered.

Qing had firmly set a standard that only those with a triple-digit number for Evil Karma deserved to be dealt with.

If there was even a single compromise, it would inevitably spread uncontrollably, turning her into a crazy, kill first ask later, mindless murderer.

{\itshape If that's the case If that's really the case

Shouldn't it be okay to just give them a little beating?

If someone does something bad, they should be hit, right?

Especially if they call themselves a part of the Orthodox Faction. Then, all the more so.}
