\chapter{Honestly, You Have to Understand This (3)}

"What about the belt. What are you trying to imply?"

At that, the old beggar sat on the ground.

It meant he wouldn't steal the liquor from her.

"Hmhm, do not be too stingy."

"Haaa. So, what is it?"

\textit{Since youre not gonna steal it, I'll let it slide.}

"This old man is a beggar called Lu Gu \footnote{僂谷. Nugok (누곡) in the original text}. At times, I am also referred to as the Keeper of Secrets."

Keeper of Secrets, Lu Gu.

Qing didn't know, but he was quite a famous beggar.

After all, his nickname literally meant he kept secrets well, a virtue not found among the Beggars Union Daoists of Zhongyuan.

Of course, the reason for keeping secrets wasn't because of some stale, old-fashioned value like loyalty.

After all, he openly stated he wished to know all the secrets of the world.

What this inherently meant was that he would become the most tight-lipped person in the world, so others should tell him their secrets.

Why else was it said that the king's ears were donkey ears?

It was a natural instinct for people to want to spread secrets once they knew them.

Countless numbers of people have confided their secrets to this beggar, claiming himself to be a living field of reeds\footnote{a quiet person}, and found peace of mind.

Unaware of such a background, Qing sighed deeply.

"Fairy, why do you sigh so?"

"Since now, even a beggar seems to want to exchange greetings. My fate really is... Ugh. Does this body really look that easy to approach?"

The old beggars eyebrows twitched.

Had this insolent youngster been a man, he would have been beaten up immediately and taught manners through the ways of Wulin.

However, she was a young girl. A sweet age of sixteen.

Beating a young girl was far too demeaning and shameful an act for an elder of Wulin.

{\itshape This wretched brat.

She truly is a coarse and insolent bitch, who thinks of Beggars as merely the beggarly trash that lives in the streets...

Mm?}

Lu Gu flinched.

{\itshape Of course she would think of Beggars as mere beggarly trash that lives in the streets. What else could she do besides that?

How can a mere beggar call someone else a coarse and insolent bitch?

Since when did I hold myself with such esteem?

When all I am is a mere beggar}

He touched upon the principle of Immortal Li Tieguai.

Suddenly, Inner Qi arose from within Lu Gu.

A good-for-nothing, terribly sloppy flow of True Qi, faltering and gallivanting.

But deep within, it was a generosity capable of easily embracing all of heaven and earth.

Lu Gu vaguely realized that he had entered the Late-Stage Transcendent Realm, taking a step into that world.

As such, he burst into laughter.    

Qing was unaware that she had inadvertently helped someone elses enlightenment when she couldn't even take care of her own.

All she did was keep a straight face in annoyance.

{\itshape What the hell? Does he have bipolar disorder?

Well, I guess it makes sense if one became old, all while being a beggar.}

After cackling by himself for a while, Lu Gus voice became kinder.

"Indeed, this old man overstepped. How foolish of me. After all, I thought everyone would know who I was if I just said my name, when I am just a mere beggar. What folly. I feel so ashamed."

"Why. Are you famous or something?"

"In a way, yes. After all, around here, there was hardly anyone who didn't know my name."

"What even is there to be so proud of for being some famous beggar?"

Qings response was sharp, as if to stab at his supposed arrogance.

Normally, generosity and compassion was contingent upon being happy. Thus, Qings current state was most definitely not conducive to generosity or compassion.

However, Lu Gu just looked pleased.

"That is right. Indeed. What pride is there in a beggar being famous? Even the beggars passing by would laugh in mockery."

If there didn't seem to be an impact when hitting something, it couldn't be considered hitting.

Seeing as he wasn't provoked no matter how much she scratched at his ego, Qing lost interest, feeling greatly disappointed.

"But still, Fairy. The Taiping Sword Sect is not all that rotten. Indeed, if we were to nitpick, they are among the better ones in the so-called Orthodox Factions."

"Well, yeah. Seemed like it."

\textit{If the Second-Rate bottom-rung riffraff's Karma was at that level, then sure, that could be the case.}

Qing readily agreed.

"And yet, did you truly have to beat them so harshly and even take their swords when chasing them away?"

"It's because they kinda seemed like the Orthodox Faction that I let them off. If they were from the Unorthodox Faction or whatever...You know, those disgusting evil fuckers. Then, not a single one would have left here alive."

\textit{Honestly though, it would've been better if that was the case.}

Qing smacked her lips in disappointment.

"Oho? So you would have killed them all if they were from the Unorthodox Faction? What a fearsome Fairy you are."

Despite his words, Lu Gus expression softened a bit more.

"But still, was there a need to get involved?"

"I was in a bad mood and they were an eyesore."

"An eyesore?"

Qing sighed deeply.

Still, it seemed slightly better than morosely drinking alone since she was talking with someone.

{\itshape Yeah, okay. I'll be quite generous today.

Consider yourself lucky. Old beggar.}

"If you're taking protection fees, you should obviously have to protect them from being extorted by other business entities too. The owner here is a pushover and...what was it? The other group?"

"They are called the Zhou Hu Union."

"Yeah anyway, them. Apparently, they don't seem like pushovers, so that's why they're not trying to bully or torment them. If so, how is it any different from specifically picking the weak to bully? If youre going to mob up and call yourselves a sect, fight like a man. Or if you're not confident in fighting, you should have just given up on the protection fees.

"That is true, but Fairy, you do not seem to understand how unions work in Wulin."

As such, Lu Gu told her.

If they were to fight, it wouldnt just be the sect falling into ruin in one fell swoop but a long period of bloodshed.

Moreover, as was often the case with medium and small sects, there were bigger forces backing them from above, and one wrong move could escalate into a large-scale war.

And if they gave up on the protection fees as Qing suggested, they'd just be sitting ducks as they lost their entire business.

Qing glared at Lu Gu intently.

{\itshape What's with this old man? Why is he shielding them, even at the cost of his own reputation?

Is he getting food from them or something?

Why does he fucking care who I beat up? Who does he think he is?}

"Ah, shit. If that's the case, why bother distinguishing between Orthodox and Unorthodox Factions, White and Black Paths? Either way, the bastards who wield swords will pick and choose to fuck over the people who don't. Taiping Sword Sect? More like, Taiping Business. Or maybe, Taiping Unorthodox Karma?"

"Heh! Keheueheheh!"

The old beggar suddenly burst into laughter.

What was so funny that he laughed until tears flowed, clutching his stomach and planting his forehead to the ground?

Qings expression gradually grew cold.

{\itshape This thing was just a crazy beggar, huh.

This is why beggar fuckers aint it.}

In the past, Qing had a hostile relationship once with beggars.

She had every right to detest them.

Qing stopped paying attention.

How many times did she fill and empty her cup, lifting and setting down the gourd?

Finally, the old beggar straightened up, wiping the corner of his eyes, and asked.

"May I inquire about the name of your teacher?"

\textit{Who does he think he is to ask about my teacher's name?}

Qing was about to snap back, but hesitated as their eyes met.

There was something warmly familiar about the old man's face.

Almost as if her teacher was looking at Qing.

Even though he had been confrontational all this time!

Qing, whose heart grew weak, obediently replied.

"Her surname is Ximen, with Su and Rin as her given name."

"Ah! Senior Ximen!"

Lu Gu acted like he knew her.

So, Qing tried to check if he really did.

"Do you know my master?"

"I've met her a few times before. About twenty years ago, this old man fought alongside her in Luling\footnote{modern-day Ji'an, Jiangxi}. So, does she still punch first, talk later if she doesn't like something?"

Qing was immediately convinced.

\textit{AH! He knows about the nuclear noogie! That r.e.a.l.l.y is...Ow.}

"Ah, so you were a Fairy of the Divine Maiden Sect."

"That's not the case. She said I was an external disciple."

"Ho, an external disciple, you say. That is truly quite rare, though.."

If she was a cherished disciple, there was no reason to place her separate from the sect.

When a teacher had the intention to pass on everything to their disciple, it would include the essence of the millenia-old philosophy of Zhongyuan people, as well as Guanxi. And this encompassed the background of the sect, internal ranks, positions, and more.

But given that it was the Divine Maiden Sect, something was a bit off.

Wasn't it originally a mystical sect that made it nearly impossible for disciples to leave?

Why did they give her the freedom to stay outside the sect?

"I see. You have stepped into the Peak Realm, Fairy."

Stepped into? What do you mean stepped into? I'm at the whopping Late-Stage, you know? This body, you see? A Master. Thats me."

Lu Gu was impressed.

"Perchance, how old are you this year?"

"I'm not exactly sure. Master said I'm about twenty, though."

"Senior has truly taken a prodigy under her wing!"

Lu Gu was even more amazed.

To think she was at the Late-Stage Peak Realm at such a young age.

She was truly a prime candidate for the next generations Greatest Under Heaven.

"!"

Realization struck Lu Gus mind like a bolt of lightning.

The leaders of Orthodox Wulin were once the Nine Sects One Union.

But now, people just referred to them as the Nine Sects.

One Union was conspicuously missing.

The Beggars Union, expelled. Eliminated. Fallen from grace.

It was all thanks to Senior Celestial Martial Emperor.

His disdain for the Beggars Union was well-known, after all.

The recent enlightenment helped Lu Gu understand the Celestial Martial Emperors disdain, though.

That they were bastards who were lesser than even beggars; it was still painful to think about, to this day.

Lu Gu recalled the way Qing initially looked at him.

It was a deep-seated disdain.

\textit{This is huge trouble. If we are unlucky, then once again...!}

He had to make a good impression.

Even if she wouldn't necessarily be the Greatest Under Heaven, at the very least, wasn't this youngster destined to be the next Zenith Among Women, after all?!

The impact that the words of the Zenith Among Women had on female martial artists was enough influence to genuinely change lives.

"Uh, that...Fairy, do you have some bad blood with beggars? Not all beggars are bad people, though."

"Oh, don't even start. They're all just pieces of shits."

Qing was ready to unleash a tirade of words.

How there were minimum requirements for human survival, yet this repugnant territorial nature of already-established forces try to take even that away. Also their villainy and how once they secured any semblance of a foothold, they carried out a battleground of an endless repeat of advance and retreat...

But just as she was about to begin-

The Taiping Sword Sect appeared once again.

Led by the welt-faced Nan Jiangding, about twenty martial artists burst in.

Just like how Qing described it, it seemed he had brought his mommy along.

Nan Jiangding pointed his finger rudely.

"There! It's that woman over there!"

Considering that he left out profanity like brat, whore, and bitch, his choice of words wasn't all that bad.

It seemed it was worth it to not spill blood and only beat him up a bit.

Qing wore a sly, reckless smile.

She was just starting to feel the itch for a second round anyway.

Qing slammed her hand down on the table. Tack!

She was about to stand up with extravagant gravity when a middle-aged man from the Taiping Sword Sect spoke up first.

After all, here in this place was a Seven-Knotted Beggar of the Beggars Union, the Discipline Elder.

"Is that you, Elder Keeper of Secrets?"

"Oho. It's you, First Sword of Anqing."

"If we had known you were here, in Anqing, we would have invited you to our sect, but we were uninformed and have made such a discourtesy."

"Forget it. It is fine. What kind of reception would a beggar like me expect anyway? Regardless, I am grateful for your words."

The atmosphere was quite warm.

\textit{Ehhh? If this continues, then my plans are gonna go to shit.}

Qing frowned.

"Elder. Are you, uh, perhaps companions with the Young Lady?"

"Hmhm. That is indeed the case."

Lu Gu gave Qing a wink.

It was a signal that he would take care of everything.

And in actuality, Lu Gu had that level of authority.

{\itshape What the fuck is up with him?

That old beggar is shitting the bed. When it was already fucking made!

Fucking hell, I shouldn't have interacted with him in the first place.

Why do the fucking beggars always have to get in my way like this?}

But despite Lu Gus efforts, it actually had the opposite effect from what he intended.

"From my understanding of your circumstances, while it may not be entirely your fault, there seems to have been a lack of consideration in certain aspects."

Qing filled her cup in resignation.

She did such an action completely absent-mindedly, but pouring liquor from a gourd the size of a childs head into a cup without spilling a single drop was practically a form of art.

And it was also a feat that only a Master could display.

Qing decided to just let them jack each other off among themselves and turned her attention completely away, downing her liquor.

Then, as the sound of footsteps approached, suddenly, a neatly dressed young man, clearly excited, spoke in a yell.

"Young Lady! Let us have a spar!"

Qing looked at the young man with half-opened eyes.

\textit{Who the fok is that guy?}