\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (8)}

There has never been a person in the world who could lift Qing and spun her around.

First of all, it was not customary for a man to hug a woman just because he was happy to see her (except for an old man or a crutch), and for a woman in Zhongyuan to hug and spin around just because she was happy to see her, it was considered very frivolous in terms of social sentiment.

Besides, Qing was a grown woman, and she was physically large as well.

But Peng Chaolei was a bigger woman, physically bigger, and didn't really care about face or anything.

So I guess it was pretty refreshing.

I guess it was fun.

As soon as the powerful reunion ritual was over, Peng Chaolei slapped Qing on the shoulder.

"But no, this kid. How come she never came to visit even once? You said you'd come over, but it was just empty words."

"Somehow my schedule got a bit tangled. I even went to Kunlun Sect."

"Yeah. I heard the story. This brat ran away from home and we haven't heard from him in almost half a year. Our parents let him off easy because he followed our Qing'er around. If not, they'd just break his legs."

"Did you hear what she said? Be thankful to me."

At that, Peng Daesan snorted.

"I thought you couldn't see me because you didn't even pretend to know."

"It hasn't been that long since we last met, has it? Since we parted ways in Chang'an? It was spring then, and it's spring now. You're going to get attached at this rate, really."

"You don't really have to worry about that because I'd lose interest as soon as you open your mouth- Ugh."

Crack! Peng Chaolei's huge palm hit Peng Dae-san's back.

They say that because he were raised on her backs, they were more like a mother and son than siblings.

"Ouch. That must hurt."

\textit{I've tried hitting the back with my palm, but is it really true that the power of the original mother's palm is different?}

\textit{Or maybe it's just because she's a muscular woman with the muscles of a beast that she looks sick.}

"Enjoy your meal! Oh, it's Sister Chaolei!"

Zhuge Xiang, who came to eat at the right time, jumps up and throws herself at Peng Chaolei.

Are you saying that the two of you knew each other?

In fact, Peng Chaolei was the first love of everyone in the Zhuge Family, regardless of age or gender. This was because the Zhuge Family had a unique aesthetic sense.

Ciyu, who came holding hands in a friendly manner but lost her friend, approached Qing with a slightly sullen look.

"Hey, did you wash your hands?"

"Ung."

"Let me see. You didn't wash properly. What, were you playing in the dirt? You hid dirt under your fingernails to show off? To show off?"

"no……"

Ciyu shrinked again.

But Qing wasn't scold ingher in the first place.

"So what? Washing was a matter of sincerity and feeling. The fact that you washed was what matters. It's not like you're going to eat with your hands."

It was a good lesson for the child.

"Yeah, digging the ground yields some good finds. At this time of year, you'd probably find something edible, right? There was a time when I spent all day digging."

It seemed as if Ciyu's face brightened a little, but soon it became dark again and shadows gathered.

It was not a metaphor, but a physical shadow.

A giant appeared, blocking the light source. 

Peng Chaolei's gaze at Ciyu sparkled in a way that belies her size.

"Oh, is this Ciyu sleeping? Let me see, my goodness, am I seeing my granddaughter? Am I Grandma?"

"Grandma?"

\textit{Huh. Why was Choryeo the grandmother? San was the uncle, so his mother is… Hmm, was she the grandmother? Or not?}

This was an unexpected expansion of Qing's family tree. 

Anyway, even though Peng Chaolei already had Zhuge Xiang by her side, it didn't bother her at all.

The face of Peng Chaolei, who lifted a child on each hand, was bright and innocent.

Well, if Choryeo likes it that much, then there's nothing Qing co do.

She even monopolized the two little ones and had them each sit on her sturdy thighs.

"Oh, Qing'er, you're an instructor? Yes, that's right. The ranks have to be right, so it's a bit much to encourage them. I heard about that. Congratulations."

"Hmm."

\textit{Why do people keep knowing my realm?}

\textit{Well, I did inform the Wulin Alliance, and Chunfeng was a high-ranking member of the management team, whether it's the deputy military commander or something.}

When Qing looked at Peng Daesan, he subtly avoided her gaze.

\textit{Hmm. But if I'm going to start talk about it, I guess I'll have to start somewhere. But is that okay? What about the level of security clearance in the Wulin Alliance?}

If you tell them that you were family or that you were a best friend and say, 'Hey, keep this to yourself', then soon the rumor about the Heavenly Blossom Sword Hwagyeong will spread throughout Zhongyuan.

Of course, it doesn't really matter.

They say I'm Hwagyeong, so what can they do?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The first entrance exam for the Yizheng Martial Study Hall.

The third category is, sabers!

In fact, no matter what anyone says, the most popular weapon in the martial arts world was the sword.

That was because the sword has been a symbol of authority and power since its origins, and has also been used as a tool with religious meaning.

So, beyond the martial arts world and beyond, the entire world revered the sword and considered it precious.

But what about the sword?

It's not like it's a spear…

Although spear was a close friend of the military, it has a somewhat awkward relationship with the martial arts people.

Before the time of the Great Emperor Mucheon, Wulin was concerned about the government's opinion, so it was difficult to use the ultimate weapons of the military, such as spears, guandos, and hand cannon\footnote{火銃; Huochong; lit. 'fire gun'}.

So, aside from the sword, the next most popular weapon was the dao.

What a convenient and easy weapon this is, all you have to do was swing it with all your might.

Even in Zhongyuan, there were more blunt-tipped types than pointed ones, so they were simple, crude weapons that had no stabbing power and were really just for cutting, with weights attached to the ends to cut like an axe.

It was so easy to handle, but once you hit the head, shoulder, or stomach, it has the awesome power to send you straight to King Yama.

Even the price was cheap!

A swordsmith that could make a properly balanced sword was rare, but dao was easy to make because the nature of the dao was to roughly grind one edge on a heavy piece of iron and attach a handle to it.

So, the last round of the primary exam was bound to have the largest number of applicants in the province section.

If you were truly learning proper swordsmanship, there were reasons to apply to Yizheng Martial Study Hall… …of course (connections, advancement, entering the mainstream), but it was not as desperate as that of the dao wielders.

But what are those daoist desperate about?

Ta-aang! With a sound like metal breaking, the applicants was helplessly swung around by the blade, which makes a whirring sound like a tuning fork.

"Haha, you're so weak-willed! Are your muscles just filled with water? Think of me as your enemy and charge!"

Peng Chaolei shouted heartily.

But, even if you say something like that.

The applicant was just feeling wronged.

Peng Chaolei's weapon was a large and heavy sword, and if you include the handle, it was honestly a giant sword as high as Chen Changming.

Such a revolt was a privilege previously granted to families who were close to the government.

The dadao of the Peng family, the moon sword of the Cao family, the long spear of the Yang family, the cavalry of the Murong family, etc. The martial arts masters who came from the military in the past were now using strategic weapons that the original martial arts people could not use because they were afraid of being noticed.

So, look at it from the applicants' perspective.

The famous female warrior Peng Chaolei swings a heavy iron lump that was guaranteed to cause serious injury even if it just brushes against them, so it was only natural that they would be intimidated.

Furthermore-

"Kyaaaaah! Young Lady! Sister! You're awesome!"

Even the cheers of the women, who already made up more than half of the audience, were as passionate as a tiger roar.

Even if we leave out the fact that Peng Chaolei was Peng Dae-san's sister, she was a very popular female warrior.

So, the test takers were left struggling to demonstrate their abilities in the face of the great ordeal of having to choose between physically dying if they get hit and socially dying if they hit.

"Hey, Little Brother. Can't you see the instructors up there? I told you, these aren't the most relaxed times. Is that all a man can dream of? You need to show them what you got."

"Yes, yes!"

Although he was a muscular and burly man, as was typical of daoists, he acted politely in front of Peng Chaolei, as if he were meeting a proper older sister.

"I think it's okay if you use a wooden dao and it breaks. Right, should we give extra points if it breaks? Is that okay, judges!?"

Even the judges gave a slight nod of agreement.

Only the staff member of the General Affairs Department who was present shook his head desperately, thinking of the unexpected expenses, but anyway.

In the end, the test taker's wooden dao snapped in half and flew high into the sky, and he exited the stage with a clenched fist and a look of triumph.

Finally he appeared.

"Kyaaaah…"

It was a passionate\footnote{熱火; Rehuo} cheer from the women who came all the way to Henan to see Jade Qilin.

Rehuo meant very, very hot fire, and with the current firepower, it must be powerful enough to overcome even lava.

However, their journey was in vain, as Jade Kilin had put on a bamboo hat with a veil and covered his face…

All kinds of screams erupt at this.

-Prince Peng, the girl has come from the land of Guizhou to welcome you, please understand this little carelessness and show me your face just once.

-I'm from Qinghai!

-I'm from Heilongjiang!

It was like the host of a banquet saying that he would give a gift to the person who came the furthest.

Moreover, it was as if all the barbarians from the remotest regions of Zhongyuan had gathered there.

But Peng Daesan completely ignored it.

'Aaaah', 'hey', 'yaaaah', 'please, please'. All kinds of pleas, screams, and laments were all mixed together, making it difficult to even understand.

Suddenly, the sound slowly died down.

The reason was that the young man who fearlessly entered the examination arena to face Jade Kilin was also of extraordinary beauty.

"I am Wan Talu from Jianyang."

This was the applicant who has a graceful impression that made you think, "This is what a noble person is like.'

'Chicken instead of a pheasant', they said. In the eyes of the women, a very handsome man has appeared, so instead of the covered face of Jade Qilin, they gulped and swallowed their saliva while looking at him.

"Oh. A person from Jianyang. This is interesting."

Next to Qing, Sima Chunfeng was showing interest.

"Oh, what is it? Sima-lang. Are you interested at him?"

"Oh, Heavenly Blossom Sword, haha, don't you know? Jianyang is a city located south of Chengdu. Now you get it, right?"

Qing responded with 'that' expression.

Sima-lang's expression brightened even more.

"Oh, oh, oh. Heavenly Blossom Sword? You didn't know? You think he's from Jianyang?"

"I don't know about Jianyang, but Kkanyang was delicious. Oh, isn't Ujaptang available today? I'm suddenly craving it."

"Oh, oh, oh, oh, Heavenly Blossom Sword, why are you beating around the bush like this, as if it's embarrassing not to know something? Hehe, you're so cute."

\textit{What is this? Is this a scheme where she try to bluff at me?}

Qing looked at her with a hopeful eye, but unfortunately.

"Heavenly Blossom Sword. Wherever you go, people from Sichuan always say they're Sichuan people, never mentioning their city's name. So, you could say he's already suspicious, right? Besides, with that face, he should have a decent name, but there's no specific info on him. Isn't that suspicious?"

"Oh, wow. That is really military-like just now."

Qing was purely amazed.

Sima Chunfeng's nose was high up in the sky.

But if she seemed military-like just now, does that mean she wasn't military-like normally?

Of course, it was like that for Qing.

\textit{Anyway, Mandalorian? He's already a man of considerable Evil Karma, so I was wondering if I should write another opinion that suggests something suspicious.}

\textit{It's a good opportunity, I have something to write about.}

[It's suspicious that he didn't introduce himself as a Sichuan person even though he's from Sichuan-]

"Heavenly Blossom Sword? Even if the profound views of this Sima Lang were a beacon in the darkness, a guide through the fog, a clear truth like salvation, how could you so brazenly copy them—"

[-is what Sima-lang concerned about. I strongly agree with her.]

"-Ahem. Yes. That would be right."

\textit{Did she just look at my evaluations all day?}

In fact, the judges thought that the sight of the two of them talking were quite normal these days.

Although they made a lot of noise, play around, and make a lot of noise, they both tended to write their evaluations diligently, and even the Military Department looked with happy faces, thinking that the annoying bitch finally have something similar to a friend.

That was when.

Suddenly, Peng Daesan Mountain took of his hat.

It's a surprise reveal of the face, the intention of which was unknown.

As a look of displeasure swept over the crowd, the women realized something new and began to reflect.

'Ah. Young Master, no, who is Young Master? To think that he was handsome after seeing something like this, I was blind for a long time.'

There were even many victims who were mentally and physically got weak and fainted.

The woman who witnessed this utterly harmful sight for the first time was shocked like never before, and the woman who witnessed it again realized that the Jade Qilin she had imagined all along was a deteriorated version that could not reproduce the real thing even a bit.

Of course, the biggest reason was the low threshold of stimulation due to the limitations of the primitive play culture of the primitive ancient Zhongyuan.

Wan Talu's expression changed dramatically.

He was confident about he appearance, so he came out in front of Pang Daesan without fear, but judging by his reaction, you'd  wonder if he knew it was hes defeat or if his pride was hurt. Only he know his true feelings.

And what comes next? It was a duel between the examiner and the applicant, without any need to describe the process.

Wan Talu lost in terms of both looks and skills.

Well, even Mount Pyeongdae was considered a lowly warrior by Qing standards.

It's just the usual spar between applicants whom level ranged just between Third-Class to First-Class at best and a real martial artist whom no applicants could hope to defeat.

At the victory of Peng Daesan, a shrill roar that seemed to tear the world apart and rip the eardrums of the crowd echoed.

But who would dare challenge Peng Daesan next?

"Me! I'm the Butterfly of Yichang!"

"I came first! Please teach me, Li Minlin of Macheng, Prince Jade, no, Prince Peng-"

"Hey, what the hell!? You're cutting in line!"

"Everyone, what a disgrace this is in the examination arena! Don't you think this is overstepping the bounds? You should be ashamed! Phew. The is was a disciple of Qingmen sect, Du Yue. She's a woman, so I can't reveal my face to public. But if later—"

"Yaaaah!!"

Oh, they're fighting, they're fighting.

The atmosphere suddenly changed to a battle royal with a lot of hair pulling.

Anyway, amidst this turbulent scheduling for facing the handsome examiner, the first entrance exam for Yizheng Martial Study Hall was also slowly coming to an end.