\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (4)}

"Well, what do you think? This is the true skill of Sima-lang— huh?"

Sima Chunfeng jumpe up from her sitting position, then hits the desk with her knee, landed on hed butt, and covere the famous wisdom pouch of Hodadak Jinang Hyeonhwa.

However, trying to cover up the mass that could not be handled with just two arms resulted in a natural backlash, making her look even more feminine.

"What, what, what, what are you doing!?"

Qing stared at her fingers.

\textit{What the heck? It was surprisingly resilient. How could it be that heavy? Is it some kind of fairy-like thing from the Sima family? Or was it because it's unmanned?}

"There is a place where the iron plate isn't placed?"

Sima Chunfeng sighed in response.

But the tips of her ears were still bright red.

"Heavenly Blossom Sword? I understand your competitive spirit. But in front of the world, even if we don't need to worry about the opinions of those ordinary people, we still need to save face—"

"So it's okay as long as it's not in front of people?"

"That's not what I meant-"

"Shh. Sima-lang, I understand your desperate desire to speak with the great Heavenly Blossom Sword, the one who transcends the realm of the Unrestrained Realm, and I understand the less great Sima-lang desire to monopolize the attention of the greater Heavenly Blossom Sword. But work is work. The exam begins."

"Urgh. Like that. Ha! You've got a leg up. Yes, I'll admit it. I let my guard down for a moment because of that cunning scheme."

Sima Chunfeng said with an indignant expression.

And yet, she muttered quietly.

"Three of you? Because you're three times as great? Wow."

It was possible that Sima-lang or Nimnimnim or Nimnimnimnim would appear sooner or later.

Anyway, fortunately, the judging of unarmed martial artists was more fun to watch than that of swordsmen.

How can it not be fun when mediocre people were hitting each other?

Originally, fights between low-level martial artists were much more fun.

It's kind of funny to see them using bare hands over a good sword.

It was during that time.

As an unusual candidate took their position, the atmosphere becomes agitated, and Qing, for once, let go of her bored gaze and looked down at the testing arena.

First of all, she was a woman.

Female unarmed martial artists were actually rare.

Although female martial artists were not that rare.

In the first place, it was natural for a female warrior to learn at least one unarmed martial art, whether it was a Hand Technique or a Palm Technique, in case she lost her weapon.

And well, Zhongyuan was a dangerous place.

So, if we expand the scope of martial artists to include people who have learned martial arts, we can say that female martial artists account for a considerable portion.

But what if we narrowed down the definition of a martial artist to someone who primarily uses unarmed martial arts, that is, someone who has given up a very convenient and powerful weapon of their own accord, choosing only disadvantages without any advantage, and a quasi-human ape of questionable intelligence and qualifications?

A female unarmed martial artist?

It was a simple logic.

It hurts when you get stabbed with a knife.

Whether the person holding the sword was a strong man, an eight-year-old boy, a slender woman, or an old man waiting for his day to die.

It hurts the same way if you get stabbed.

But the fist was a little different.

If you get hit by a strong man, it hurts a lot, but if you get hit by a woman, it hurts less.

What if that's an eight-year-old kid?

If you pretended to be sick for no reason, you could get a special massage from your grandson's little hands.

That was why female unarmed martial artists were rare.

Because the difference in weight class was so absolute.

But the reason this candidate was unusual wasn't just because she was a woman.

\textit{What is that outrageous outfit?}

\textit{Is that really tiger furs?}

Come to think of it, there's no way there could be fake tiger furs in this primitive, ancient Zhongyuan.

Because dyes were expensive, and making a finely crafted fake tiger furs would be much more expensive than buying the real thing, and the labor involved would be no small amount.

And in this heat?

Isn't this already a hot spring that makes you think this summer will be very hot?

She wore a leather jacket and leather pants, tied her leather shoes just below her knees, and put on a thick tiger furs coat.

It was still morning and a bit chilly, but she was the only one dressed in midwinter clothes, so of course she's going to stood out.

Yet, on her youthful face and her perfectly tanned brown skin, no beads of sweat were visible.

"I am Che Yaohong from Honghe."

Qing thought that the tanned skin might look rough.

Surprisingly, even though he was wearing such an outrageous outfit, he politely accepts the lottery ticket.

"Indeed, it's Honghe! I see!"

"Why?"

"Hehehe, Heavenly Blossom Sword, Honghe is a settlement south of Ainao Mountain in Yunnan Province. They must be one of the minority groups in Yunnan. It's been said since ancient times that there are more wild beasts than people in Yunnan, right? If that's what they wear, wearing bear and tiger skins, then that makes sense."

"Oh, is that a bear skin inside his coat?"

"Furthermore, Yunnan is a harsh, humid, and hot place, where people from Zhongyuan find it difficult to breathe. Wouldn't the mild spring of Zhongyuan be a coolness to that woman, not enough to make her take off her coats? Just like Snow Flowers, a North Sea native, always sits outside in the dead of winter."

Gunyeong liked to be outside in the winter.

Because it's hot inside because there's a fire.

They say that even the summer in the North Sea was colder than this, so even at Divine Maiden Sect, Xue-i was working hard to celebrate in the cold wind wearing summer clothes in the middle of winter.

That bastard, the resentment he had in his internal energy was not ordinary, so he sat there all day gathering energy.

Well, even if that's not the case, there's no place to use Gunyeong.

Since Ciyu and Xiang'er were best friends and stick together, there was no need for Gun-yi to take care of them.

It doesn't seem like she would be helpful for swordsmanship research.

The State Affairs Division seems to have similar thoughts, as they were unable to use the insect that came without being called and just left it to eat.

Anyway.

Even if we discuss Gunyeong's uselessness again, it's enough that she just has a pretty face and sleeps comfortably. Just breathing was a lot for Gunyeong, she's trying hard enough. To ask for more was just greed, greed. Just grow up healthy.

Qing quickly brushed aside Xue-iri's taciturn beauty that had briefly brushed past his gaze and returned to focusing on the test.

"I'm sorry, but this girl's martial arts are somewhat unique. Could we test them in the form of a demonstration rather than a spar?"

"Hmm, alright."

Examiner Huangfu Guang readily accept.

Well, it was a good thing because he was having a hard time sparring with a woman.

It would be awkward to spar with a young woman, who was as young as her daughter, in a situation where they were fighting with their fists and notn weapons.

Huangfu Guang stepped down from the testing arena.

The woman catched her breath.

Take a step forward, bend your waist, lower your upper body, then slowly raise your torso as if standing up from the top of your spine, while stretching out both arms.

\textit{What is this? Isn't that it? Ballet?}

\textit{Was ballet existed in Zhongyuan? Or is it originally a Zhongyuan folk dance?}

Of course, that's impossible.

At the end of a slow but elegant movement, a spark suddenly rises from the air and wraps itself around Che Yaohong in the shape of a multi-branched snake.

It was an untimely feast.

The sight of Che Yaohong, fluttering and flailing with flames, was truly like a vermilion bird.

Not a compliment, but the flames were pretty flashy so it looked a bit okay, but without the special effects it looks like a bit of a fluttering motion.

"Sima-lang. I think that's a hopi-"

"That's right. As I, the master, have already seen through it and told you, it's probably to effectively block heat through the animal's hide. After all, fire is the most dangerous force."

I don't remember hearing when it was said.

As Sima Chunfeng said, fire was dangerous.

Just as in the case of the Gwangseo Line, when a forest fire broke out, everyone, including the guards and others, ran away together. Is there any other way to do this than to act like a human in front of a fire?

Placing a bet might keep the heat at bay for a while, but only for a little while.

Fire crackle, fire crackle. Multiple flames leave long tails, creating complex trajectories.

They gather together like a hammer and strike the enemy.

\textit{Oh, a fire fist.}

Qing exclaimed.

The leg stretches out and a bright red flame shoots out.

\textit{Oh, flamethrower.}

Qing exclaimed again.

Previously, he would twist his body for about three breaths and perform some kind of avant-garde performance art, and then he would quickly raise both hands with their wrists clasped up to the sky-

Pfft! The loud sound of fire spreading.

It was a magnificent sight, with all the flames rising at once and ascending into the shape of a giant bird, making a great blaze.

Wow! It's flying!

The examiners, instructors, and onlookers all had their mouths agape and their expressions were blank.

\textit{Should I call this a martial art?}

\textit{Or should I call it a power show?}

\textit{Or maybe dance or performance art?}

Anyway, Che Yaohong, who had finished the demonstration, found her exposed face drenched in sweat as if it had been doused with water.

Even though she was wearing a thick tiger furs coat on a hot spring day, he was still dry and didn't sweat a single drop.

Of course, fire was hot…

"It's called Zhuquewu\footnote{Vermillion Bird Dance}."

Ohhhh!!

A beat later, cheers erupt.

The sound of applause was loud, and there were also several attempts to incite people by using nicknames like "Shin Gi-ju-jak" and "Ju-jak Jae-nyeo."

To Qing, the nickname Vermillion Bird had a strange connotation.

"Hehe, this was getting interesting. Perhaps it has something to do with Young Expert Chai's Azure Dragon Drance?"

"Oh, when I saw that kid, I thought she was going to perform one of four divine beast dance, but really-"

"Oh, oh, Heavenly Blossom Sword. That attitude is wrong. If you say things like, 'I also realized it' hehe, I understand your competitive spirit, not wanting to lose to Sima-lang's insight, but please refrain from making such dishonest remarks! No, that, please. Even if it's Heavenly Blossom Sword-"

Sima Chunfeng, with a bright red face, quickly coveeds her mouth and wisdom pouches.

Qing  blew the tip of her poking finger.

"Stop the obvious trick of trying to cover up your weaknesses with trivial tools. It makes you look weak."

"Ugh."

By the way, um, I guess it's safe to say that all four of the divine beast have a dance move, right? No, maybe there's a Yellow Dragon in the middle too?

Zhongyuan's divine beast had the five directions, including the center.

If that's the case, why don't they just group them all together as something like Five Direction Dance and say Sabibangmu Jujak's Breath? Why do they have to exist one by one?

In terms of swordsmanship, there were the eastern sword, the western sword, the southern sword, the northern sword, the middle sword, the east, west, south, and north, each separately.

If we just combine them into the five-way sword, huh?

Suddenly, a thought flashed through Qing's mind.

Five swords. Five directions. Five Swords Path.

Oh, isn't it okay?

They say inspiration ce unexpectedly, and this was a thought that struck me like a flying bird.

First, ask Nan-Gong Shencai, the best intellectual in swordsmanship.

Of course, there were still more important things to do than the Five Paths Sword, so I have to take care of those first.

It was a matter of punishing the destroyers of judicial justice who dared to evade just punishment.

As soon as today's examination was over, Qing hugs Sima Chunfeng's torso.

I felt the side and it looked like they had put in a metal plate and sewn it with cloth.

The feeling of a solid iron plate pressing against my side doesn't tickle at all.

Even while being captured, Sima Chunfeng lets out a leisurely laugh.

"Heavenly Blossom Sword? It doesn't work?"

"Are this your favorite clothes? They're not the first ones your parents bought you, are they? It's hot outside. Could I cut a hole in the side so you can get some air in?"

Sima Chunfeng's eyes were rolling at that.

"Oh, that's it. It's a piece of clothing I've decided to take great care of from now on? Uh, I don't think it should be damaged. Heavenly Blossom Sword? That's not it, is it?"

"Yeah. Then there's nothing I can do."

Qing's right hand slid through Sima Chunfeng's front like a snake, without any resistance.

Pickpocketing was a highly sophisticated technique that involves breaking into someone else's bag without the owner noticing, and the true nature of Divine Thief's Flexing Flex, which stood at the pinnacle of this technique, lies in this very digging.

Sima Chunfeng shuddered at the unusually cool and smooth skin of those fingers wrapping around her side.

Then, the left hand also takes its place.

"The idea was good, but you should have just come out wearing armor."

"Oh, no!"

"Right."

Then, Sima Chunfeng covered her mouth.

Because she couldn't scream so loudly.
