\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (7)}

I had a feeling that Sima Chunfeng, who always sat in the evaluation hall first thing in the morning, was nowhere to be seen.

Just before the exam began, a woman in unique attire strode confidently out of the main gate, drawing the attention of onlookers.

The front collar extends all the way to the shoulders and was buttoned up, cinching the neck tightly. Instead, the voluminous sleeves flutter in two tiers, and the skirt, without any pleats at the top or bottom, falls in a straight line.

It was a garment called Gijang, which was a form of satisfaction, but you can't tell the size even if you look at it.

but.

"Hehehe, Heavenly Blossom Sword. How were you?"

"Yeah. Did Sima-lang sleep well too?"

"I haven't been feeling well. Yesterday, I dozed off for a bit after dinner, and in the meantime, those incompetent idiots over there took care of all my work. Ugh, how can I endure this humiliation…!"

It means that while you were eating and taking a short nap, your colleagues finished all your work.

What? Isn't that a good thing?

There was no greater humiliation than having your job taken away from you by the self-proclaimed genius who will lead the future of Zhongyuan martial arts world.

The Wulin Alliance soldiers also knew this very well, so when they heard the words, 'I saw her laugh so hard she collapsed!', their eyes widened and they ended up taking care of her works in an instant.

Those who were humiliated for doing their own work, or those soldiers who take on so much work all at once just to make fun of others.

It's not entirely normal.

If a military or deputy military officer saw this, it would be astonishing why they didn't do it in the past and why they were delaying it.

But smart people especially.

Slow down your work pace and minimize the daily quota of work given to you.

Can anyone join the military?

Anyway.

Qing focused on Sima Chunfeng's clothes as he gnashed his teeth, saying, "Thanks to whom?"

It was a dress I hadn't seen on many women before, but it was really pretty. What was it? However, the stitching was a bit crooked, so I didn't think the tailor's skills were lacking.

This was a bulletproof vest.

The front part extends to the shoulder and then falls to the side, so there was no place to dig your hand in, and the chest was flat, so you can tell at a glance that the inside was a compression bandage.

The lower side seam was heavy and sags, so it looks like there's an additional sheet of iron added inside.

"Heh, what's wrong? It's called a gijang, a garment of satisfaction. It's not at all strange, was it?"

"Yeah. It's pretty."

"Oh. Hmm."

Perhaps he didn't know that compliments would come flying in so easily. Ah, ahem, ahem. Sima Chunfeng was feeling embarrassed for no reason.

Qing thought as he looked at the sight.

Well, I shouldn't stab you today.

It was absolutely not the case that Qing would reflect on himself after seeing him come out wearing the clothes of some kind of barbarian tribe to prevent himself from being stabbed.

How could there be a place selling barbarian clothing in a small town, let alone a big city?

Looking at the stitching, it looks like it was made overnight.

Well, if you don't react, it'll only get worse.

"Well, anyway, since yesterday was a busy day, I guess we'll have to get the work done quickly so we won't be able to have dinner together today."

As expected, it was Sima Chunfeng who was openly provoking.

"It's too bad. I wanted to eat together."

"……?"

"It's work, so there's nothing I can do. I have to eat and live with Sima-lang. What if I keep losing work?"

"Uh… Heavenly Blossom Sword. Then tomorrow too?"

"If you think of me while you're working, come over and play. I'm studying swordsmanship at the training center."

"Ugh."

While Sima Chunfeng was at a loss as to what to do, the first test, in the offensive and defensive division, began.

In fact, the reason why martial artists, commonly known as martial artists, abandon convenient weapons and use inconvenient limbs was not because their heads were uncomfortable.

Just because I can't find the right weapon technology.

The martial arts, swordsmanship, spearmanship, swordsmanship, and other martial arts that were floating around in the author's mind were of a slightly, or rather, quite noticeable, level.

That's the world's most powerful Shaolin.

It was said that wandering monks of the Shaolin school in the past were not stingy in teaching martial arts, so even if you look at the martial arts spear of Qing Dynasty, don't the martial arts techniques they picked up (stolen) during their wandering days, such as the Six-Hap Fist and the Seven-Star Fist, have blue borders?

Compared to that, the book on the author's secret weapon technique was so full of flaws that only one out of ten books will be registered, and even those were almost all bordered by white.

And if you want to learn without a teacher, it's easy to learn martial arts.

So, the vast majority of the martial artists taking the test here now were desperate martial artists who had gathered here to give up martial arts.

Of course, there were those who want to learn real martial arts, but if you lack the brain, your body will suffer, so what can you do?

They were all poor people… … .

Qing-i, with a somewhat sad look in her eyes, watches the sweaty confrontation between the two shirtless men bickering with Weifeng, and suddenly looks away.

Rather than saying I was blinded, was it more passive? Was I blinded by the inevitable pull of my soul?

Oh, Dan-Hyung. You've done a great job.

Dan-Hyung was a style of clothing that allows a woman to reveal her upper chest. A famous person who wore this style was Hae-eo-baek-hap Jin-seol.

Is it because the weather was hot that it's an early death?

Last year, short hair was trendy, but could it be this year too? Finally? Really?

Qing steals glances at the woman's chest from time to time.

In fact, since it was the body of a Qingdo woman, no one would say anything if they saw it openly, and she knew it well.

But if you keep looking away as an evaluator, you won't have anything to write in the evaluation report.

however!

And the next day.

And again the next day.

What the heck? Has the short-sleeved shirt trend really arrived already?

How did a trend suddenly spread like this in just a few days?

As time goes by, the density of short hair in the crowd increases, so now you don't have to peek, you can just turn your gaze and see at least one pleasing curve.

Now half of the onlookers were single-minded.

At this point, it's not the trend of single breasts that's the problem, but rather the mysterious gender ratio itself.

Because even if a man goes on a tour of Zhongyuan, he can just pack a bag and go, but it was not an easy task for a woman.

Strictly speaking, the number of people with the social status or wealth to go on a 'tour' was similar, whether they were men or women.

However, since almost all of the people who could wander Zhongyuan as half-vagrants and half-beggars like Qing in the past were men, it would be normal for the gender ratio of these onlookers to be overwhelmingly male.

But look.

The whole place was cotton, the whole place was my heart.

And the cotton yarn was strong, giving it an expensive look, but somehow it was plain and even shabby, a strangely balanced outfit.

Well, it's basic (important) that if you wear tight clothes, you wear tight clothes on the top, and if you wear tight clothes on the bottom, you wear tight clothes on the top, right?

Did you throw away your clothes because you put so much effort into your hat?

Shouldn't you not be putting pressure on the hat in the first place?

Sima Chunfeng also seemed to have noticed something strange.

"Looking at it this way, Cheonhwayang's popularity was truly amazing. It's the same this year as it was last year."

It didn't seem to be the case.

Cheonhwayang, Yang was a character used to describe shapes, and means fashion and customs.

In this case, it means the trend of Cheonhwa-yang and Cheonhwa-geom, because Qing Dynasty was the one who caused the craze for cotton yarn in Zhongyuan.

"Huh, this much influence. This time, I'll mark this as an official defeat for Bone Sima-lang."

It seems that he was more concerned about the fact that Qing was leading Zhongyuan fashion trend than the density of women.

But what about a formal defeat?

So, was there an unofficial defeat?

"Hmm. Isn't that right…? The Thousand Flower Sword's face was so striking and unique. Even if poor ordinary people wanted to resemble Sima Lang, they wouldn't be able to do it since there's nothing special about it. So, it's not like they've officially lost…"

Is it a fabrication of defeat, or rather a manipulation?

No, what the hell was defeat manipulation anyway?

"Well, um, wouldn't there be some innovative decoration that would evoke a sense of wonder, something unique…"

And then he ends up lost in thought, muttering to himself, "Is there something unique that I can follow?"

Qing had a strong feeling that Sima Chunfeng would come out with a unique outfit for a while.

Well, Chunfeng's strange behavior wasn't just for a day or two, so let's move on.

Qing had a theory that can explain this mysterious phenomenon all at once.

\textit{Oh, this.}

\textit{Isn't this the sign of Jade Qilin sightings?}

\textit{I think San will appear soon.}

An unusually high density of women.

A cotton shawl draped over the head like some kind of Yellow Turban bandit.

Beggarly clothes.

And when she told her to look at a woman lacking clothes in area on her upper body, he seemed to have made the effect .

But what if these three are combined?

\textit{I saw this when I was playing video games.}

\textit{Zombies coming out of a quiet, foggy village.}

\textit{However, looking down on this sunny day under the bright spring sun, I wonder where else in the world can I find such a view.}

Perhaps that's why the crowd seemed unable to concentrate on watching the test.

Even though Zhongyuan people likes to watch fights, the test was more of a demonstration than a fight, and there was no bloodshed, and it was not even a cool sword fight with blades flashing because they were taking turns with offense and defense.

Either admire the sweaty physiques of these men.

Or taking a peek of the real upper chest of a quantum mechanical beauty who turns her head and covers her face with a cotton swab.

Of course you'd choose the latter, right?

It was something that couldn't be seen openly, so for some reason the focus of the men watching the training was further away, towards the opposite side of the testing room.

And so, today's exam ended in a somewhat gloomy atmosphere.

As they were about to go out for dinner, Sima Chunfeng was looking at her with a look of regret, as if she was demanding something.

Well, even Chunfeng would know by now.

After eating together, she realized how lonely eating alone can be.

However, it was a bit cumbersome.

Qing leads Sima Chunfeng by linking arms.

"Well, what's coming up today? I told you it's the most anticipated moment of the day."

"Ahem, Heavenly Blossom Sword, why do you lead me as if it were natural for me to eat with you?"

"Okay, okay. Let's go. There's still food left."

As Sima Chunfeng pretended not to be able to resist and casted her gaze into the distance, she was led without any resistance, and Qing, feeling good at the thought of food, even hums a tune.

A melody Sima Chunfeng had never heard before. Or rather, was it simply a melody she had never heard before? This was a melody entirely different, with different roots, yet shaped by a system of its own.

Sima Chunfeng, the genius of the century who claims to have mastered two of the Four Arts of a Scholar, the forbidden arts of calligraphy and painting, becomes dizzy when she heard the melody.

Anyway, when she went to the restaurant, as expected, this was what happened.

\textit{You're already here!}

Qing, who was seeing the world for the first time in a long time, brings a bright smile to her face.

A natural smile of pure joy appears at the sight of the most beautiful woman in the world, who has entered the dining hall and opened her veil in the hot weather.

At that moment, Qing realized.

\textit{Ah. I didn't notice when I wasn't looking.}

\textit{I missed you more than I thought.}

\textit{I really, really wanted to see you.}

Qing ran out, calling out the name of the person she missed.

"Chaolei! When did you get here? How long has it been since I see you?"

Peng Chaolei, a very strong and sturdy magpie from Peng Family, an instructor at the Dao Study at the Yizheng Martial Study Hall, appears.