\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (3)}

Nevertheless, Orogeomgyeol was an outstanding technique.

"I should say it's really well done. I'm impressed!"

Since the people who participated in the creation of the martial arts were swordsmen of the most renowned swordsmen of their time, the level of perfection of the swordsmanship itself was quite remarkable.

It was Nan-Gong Shinjae's evaluation.

Although his level was low, he was an amazing swordsman who was recognized by even Qing for his keen eye for swordsmanship.

"It's strange. Even though their personalities were clearly different, they connect so smoothly. It'll be a great help in embodying various mysteries."

This was the sentiment of Murong Zhuji, who once practiced madly with a paranoid obsession for transformation.

Now I've let go of my obsession and even managed to get that tiny bit of fat I've been dreaming of, or rather, put it in my chest.

Among the members of Half-Sword Double-Saber Association, Murong Zhuji was recognized as the most mature member (even among the members, no matter how much, she cannot compare to Qing herself, who was a complete adult), so even though she was a bit shady, she was a great person who does her part with dignity even as a subordinate.

And above all, even to Qing, the only true master in this place, it was not a bad swordsmanship.

The reason the Oro Sword Technique was created in the first place was to create a perfect sword technique by approaching it in a way that had never existed before in the world.

It was the legacy of the absolute swordsmanship club that disappeared due to severe discrimination and absurdity.

"It's truly a shame that such a swordsmanship has disappeared, it's called absolute swordsmanship."

"If he had been beaten up by the best in the world and disappeared, it would have been worth it to disappear."

"A swordsman's greatness was entirely derived from his swordsmanship. Even if his temperament was a bit mischievous, it's not a major flaw. However, he paid the price for not recognizing a greater swordsman."

It was a shame that the Absolute Sword Association was disbanded, but it was okay because the person who disbanded it was the greatest swordsman in the world, Emperor Mucheon.

If the Great Emperor Mucheon had not been a swordsman, wouldn't Nan-Gong Shinjae have been indignant and cursed him, saying things like, "How dare a non-swordsman persecute a swordsman!"

Anyway.

There was no doubt that the Five Paths Sword was a study for ascension that was too good to be taught for free.

I think it's called Gyereuk.

Even if you have it in the Wulin Alliance, it was not a martial art that you have to learn by looking at the techniques of each school, and since you have already learned the subtle contents of each school's techniques, it was also difficult to just reveal them carelessly.

Because it was such an ambiguous matter, the Wulin Alliance decided to make a big decision and revealed it.

However, the problem is.

"How do you even teach this? At least you need to be able to vaguely sense the essence of it to truly unleash its power."

"I've thought about this for a long time, but Sword Friend's standards for swordsmanship are incredibly high. Even just imitating it is enough to demonstrate its power. Even just mastering its movement is a powerful technique, far more powerful than common, lower-class swordsmanship."

That was exactly what the Wulin Alliance wanted from Qing.

However, Qing became serious.

"No, Sword Friend? What the hell are you talking about? You're teaching swordsmanship to a swordsman, regardless of their rank. Are you trying to say something like, 'Let's just beat up a beginner and have them imitate it?' Have I misjudged your character?"

"……!!!"

"Just because you swing a sword, you're a swordsman? That's just playing with a sword. The difference between a swords playing and a swordsman lies in their passion for the sword. They don't treat the sword as a mere tool for harming others, but as a lifelong companion, constantly striving toward perfection. Possessing a noble attitude, regardless of skill level, isn't that the spirit of a swordsman?"

"Gasp!"

"Now, you're saying that those lowly, second-rate, first-class at best, insignificant, lowly martial artists who were barely at the peak of their abilities, were nothing more than mere mortals, low-level martial artists who were embarrassing to call low-level martial artists, and that you'll just teach them vague swordsmanship and give them immediate results, just give them sharp swords, and that's it?"

"Ugh!!"

"How can you hand over this unfortunate swordsmanship that never truly blossomed, this crystallization of the blood, sweat, and tears of countless swordsmen, to aspiring swordsmen, even those with inferior and pathetic skills, as mere tools? Mimicking it? Mastering the swordsmanship? How can a swordsman, of all people, say such things?"

"Stop, stop!"

Thud. Nan-Gong Shencai kneeled on the ground.

"Sword Friend, Sword Friend iss right. How could I? Swordsmanship is the world's most superior skill, the most essential culture in life, and the most noble act a person can perform. How could I have spoken so rashly about teaching swordsmanship? I am truly ashamed. Alas, I cannot even raise my head to look at the sky!"

Qing placesdhis slender fingers on the shoulders of Nan-Gong Shencai, who was kneeling before her.

"You should know this now. Anyone can make mistakes. Recognizing a mistake, feeling ashamed, and striving not to repeat it was what makes a gentleman—or rather, a swordsman."

"Sword Friend!"

"In that sense, Sword Friend just now seemed a bit like a swordsman."

"Ugh, that hurts my heart, but even if I had a hundred swords, I wouldn't be able to say anything."

"But the training, the swordsmanship, haven't even begun yet, so our research, our swordsmanship, to show those lowly, insignificant aspiring swordsmen the true world of swordsmanship, the sword world has only just begun, only just begun."

Cheong, who thought everything that came out of his mouth was just words, spoke. Honestly, Qing herself didn't know what she was saying.

"Sword Friend is right. It seems I've fallen prey to a terrible evil. How dare I speak out so recklessly in the midst of the most important task in the world, teaching swordsmanship."

Qing nodded and got back to the main point.

"Anyone can make mistakes, and the swordsmanship to overcome them and move forward is what makes swordsmanship so noble. But if not for Sword Friend, who in the world could dissect, analyze, and reassemble the legacy of these ancestors and pass it on to their juniors? That's why Sword Friend's swordsmanship is so noble."

Nan-Gong Shinjae's eyes burned brightly.

Qing gave him a pleased smile.

Starting tomorrow, there will be an entrance exam for applicants who have mastered martial arts, including martial arts such as Kwonbeop, Jangbeop, Gakbeop, Joppaep, and Geumnasubop.

That is, it meant that Nan-Gong Shinjae would not step forward as an exxaminer.

But, if I do this, I'll be stuck in the Oro Sword all day, right?

The so-called humanoid swordsmanship automatic research entity!

How great would it be if I could just receive the parts that were completed after the examiner's work report?

Since it's dark, if you fill in the missing parts and complete it, you can learn it with a martial arts spear.

I really want to eat honey cake, honey, honey, honey. I wonder if there's a place outside that sells honey bottles.

"So, Sword Friend, take a moment to calm down. Young Lady Murong, would you like to have some honey-sweetened bread?"

"Huh? I just had dinner……"

"Shh. Tell me you want to eat. Otherwise, you'll have to watch Sword Friend's miserable sorrow."

"Sword Friend! How could you have such considerate thoughts…!"

While Nan-Gong Shinjae was impressed, Murong Zhuji, who was urged on, nodded her head quickly.

"Ah, yes. I want to eat…"

"Then there's nothing I can do. Young Lady Murong wants to eat, so I'll have to leave for a moment. Okay. Let's go. Should I buy you some swordfish too?"

"Ah. I'll ask you to do what I heard."

"Aww? Your taste was unique."

"Well, it's because it's black sesame-"

"I'll pretend I didn't hear that. Anyway, check in. Young Lady Murong? Let's go."

Qing left the training ground, holding Murong Zhuji's wrist in a joyful manner.

And then, the only thing that could be heard was the loud sound of Nan-gong Shencai swinging his sword.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Yizheng Martial Study Hall's unarmed test has begun!

In fact, Qing didn't have to take on the role of examiner if she wanted to.

Because it's a bit odd for a swordsmanship instructor to be judging unarmed martial arts.

However, Qing was already sufficiently qualified as she was the successor of Tathagata's Divine Palm.

I received a request to come out and help, if you don't want to, don't.

So why did you come out anyway?

Instead, we've created a highly motivated humanoid automated research entity to study the Oro Sword.

Of course not.

If I postpone my work, my body will feel better, but my mind will be less at ease, so I had no intention of leaving my work, the Oro Sword Research, to him.

No, I just wanted to check it out.

Even among the swordsmen, there were a few yellow, or rather red ones mixed in here and there, so it would be no wonder that there weren't any in other departments.

Since Qing was the only one who could tell if the number was red or blue, she was the only one who could write a line on the evaluation form saying that the back of the person seemed a bit dirty, so let's dig into it.

Especially for the safety of the trainees and to prevent unpleasant incidents, it may be a bit boring, but that was the fate of a master.

From the morning, loud cheers of 'Wow!' erupted.

The crowd cheered as they saw a bald man, Weifeng, come up to the testing arena.

It wasn't strange.

After all, Shaolin was the true and undisputed best martial arts school in the world, and to those strange people who voluntarily gave up weapons, Shaolin monks were truly idols.

But what about Qing?

Sima Chunfeng, who was sitting next to her, also had an indifferent attitude and just kept chattering away.

"It is truly regrettable that the members of the Guangdong's Zhen Family are unable to participate."

Zhen family was busy with reconstruction and could not participate.

Originally, when it comes to martial arts, it was Tai Chi Chuan, but since there aren't many schools that focus on bare-handed martial arts like Jeoksoo Gong Kwon, excluding Shaolin, it was a representative one.

"Yeah, it's warm out there."

Sima Chunfeng's head was taut.

She definitely said it was a shame that Guangdong's Zhen Family couldn't participate, but why did the reply was the weather was warm?

If you don't know, you should ask.

However, Sima Chunfeng could not admit that she did not know, and even more so to his arch-rival Cheonhwa-geom, so she could only think hard.

Of course, when the weather was warm, women's clothing also becomes lighter, and when talking about women's clothing, you can't leave out the Wulin's Five Flower the Whit Flower Young Lady Zhen Sui.

\textit{Hmm. I hope Young Lady Zhen was doing well.}

\textit{Guangdong was far south, so it'll be much hotter there. Hmm, I should go see it sometime when it's hot. I also have to see the Dianchang's Absolute Sword Wall, so I think I'll stop by on the way there.}

"But, Heavenly Blossom Sword, hehe."

"What? What does it mean?"

"Haha, I must inform you in advance that I, Sima-lang, will not be able to join you for dinner today."

"Why? Are you busy?"

"Heavenly Blossom Sword must realize the duty of those who lead our time. Like beasts herding sheep, our mere presence leads these ordinary people."

"Huh? Do wild beasts usually herd sheep?"

"The ordinary people of the Military Division were born with a sad stupidity that, unless they are whipped by the presence of this Sima-lang, they will remain ordinary people forever."

Sima Chunfeng pretended not to hear Qing's question.

"So, I, Sima-lang, have been devoting my precious time to Heavenly Blossom Sword, but now I must fulfill my duty as Sima-lang, which I have not been able to do, of rebuking the laziness of those ordinary people."

"What? Are you not afraid of my fingertips? Should I take the time to examine and see if people can truly laugh to death?"

"If you think that Sima-lang will ever yield to such threats, you are very mistaken."

After following along obediently for a few days, it seems like she has forgotten the scary experience of laughing and crying and even tearing her muscles.

Without hesitation, Qing stretched out her finger and said, "Hit!"

Instead of digging in gently, the sound of hitting a metal plate resonates.

Because it really hit the iron plate.

\textit{No, what was that? Is there a metal plate added to the side?}

Somehow, it was too blatant a provocation.

"Keuheuk, ehehe, hehehahaha!"

Sima Chunfeng bursts into flames.

She was afraid of being poked in the side, so she put up a metal plate and smiled happily.

"Hahaha, what do you think, Heavenly Blossom Sword? Of course, you could wrap your arms around the steel plate and pierce it, but would that leave Sima-lang's side unharmed? Hahaha, that wouldn't be possible, would it? You know Sima-lang is a giant who will bring peace to the entire Zhongyuan!"

It's just a piece of iron. If Qing wanted to break through it, just break through it.

But then, instead of just evoking a reflexive laugh, Sima Chunfeng's side would have been covered in blood and her internal organs would have been exposed, a truly gruesome sight.

So, can you afford that?

Sima Chunfeng threatened with her own body, not someone else's.

Qing's eyes narrowed at her.