\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (6)}

After a noisy dinner.

It was a clear night with a bright moon shining so softly.

In the quiet of an era when human civilization has not yet conquered the night, only the crackling sound of a fire in a brazier was peaceful.

And then suddenly a woman stood there.

Originally, she was called the Moon Maiden, and Zhongyuan was a land where the figure of a sorrowful woman, pale and sad under the moonlight, was admired as beautiful.

It was the moonlight that transforms even ordinary women into beauties.

Moreover, the figure of a peerless person who was praised throughout the world was truly a paradise in a painting that makes even the moon turn its head in shame.

It would have been like that if she had just kept her mouth shut.

"I've thought about it, but the Five Paths Sword is completely beyond the level of the applicants. They're practically at the level of apes. They don't even know how to hold a sword? I feel bad for those low-level, or rather, pathetic people. I can't teach those pathetic losers, those little brats who don't even know how to crawl, how to run."

"Well, even so, that's a bit harsh……."

Changbin, who was dragged in by the scruff of the neck, carefully tried to state his opinion.

"What?"

"No, uh, it's called Xingwuyueshi. Actions ultimately don't stray from your thoughts, so I know it's a joke, but I thought it might be a good idea to be a little more careful with your words and actions…"

It was Changbin who wrote the text saying that he was a Taoist priest.

He's so excited.

"What? Who gave someone in Peak Realm permission to speak? Is that you, Sword Friend?"

"How could that be? Brother Changbin, could you please move over? A Peak Realm might get hurt like this."

"No, why are you becoming more and more strange……"

Even though Changbin was grumbling, he did not leave Nan-Gong Shencai's side.

Of course, he had to be next to Nan-Gong Shencai, since he couldn't be next to Qing or Murong Zhuji.

Of course, even if he wasn't next to her, Changbin was truly docile and like a lamb the moment a woman was in the same space.

"Anyway, the Five Paths Sword is too difficult. First of all, the illusory and transformation subtleties are just so-so. From what I've seen from the examiner's seat, the second- and first-class applicants would struggle with illusory and transformation subtleties. They're likely to just go crazy and change. So, I'll exclude those two."

In the past, Ximen Surin used the four basic techniques of the Kwaidunhwan as the basis, but the techniques mentioned in the martial arts were simply applied.

Since I'm studying swordsmanship, if I were to compare it to swordsmanship, there's the Yu and Byun swords in the Five Paths Swords, the Yugeom and Byeon swords. In addition, there were also Ganggeom, Paegeom, Cheomgeom, Jeolgeom, Nageom, and Chalgeom, etc. If you just put them together, you have everything.

However, Ximen Surin only used the four indicators of fast, slow, light, and heavy, and arranged the principles of quick, slow, and heavy, and other principles in between.

For example, there was softness between slowness and heaviness, and there was variation between fastness and lightness.

However, there was general agreement that the countless mysteries could be categorized with a certain degree of difficulty.

The easiest was Kang (strong sword), the medium was heavy, the quick was Pae (faithful to the movemente). The softer and more subtle was about half a level harder.

And since the difficult ones were illusion and change, these two were based on the premise that you must be good at bluffing and have perfect control over your body.

"So, I'm going to try rewriting the Five Paths Sword into three parts: Zhong-Kuai-Ruo\footnote{中快柔; Medium-Rapid-Soft}. I've thought of the first one. Let's take a look."

Qing draws her sword and raises it.

The posture of the first stage of the Five Paths Sword.

The front foot takes a step forward and touches the ground, thud!

Knees that bend in compliance.

As the torso sinks, the spine bends, adding weight to each joint, until each step feels like a thousand pounds of force reaching the shoulders.

At that moment, the sword flows.

All the muscles in his body contracted simultaneously, and he brought down the sword he had raised high, with a single blow. Boom!

The heavy sound of a sword cutting through the world.

A dull trembling wakes the silent night.

A fall that seems like it will shatter the earth brings about change at the end.

The rear foot naturally rose with the shift in center of gravity, turning a step outward. The bent torso twisted.

The blade or handle of the sword, which was pointed at the ground, was caught in the hand of the master, and turns round like a weight tied to a rope, and points far behind the leg.

A lowered posture and a back twisted to its limit.

It was a precarious shape, like a bow drawn to the end, and the moment it reaches its limit and stops, it was dizzying, like the danger was imminent, as if the heart has already been pierced.

Within a few seconds. Boohoo!

A world that splits from bottom to top, from right to left.

But the darkness doesn't stop yet.

The front feet that drag the ground as they move forward.

A large blade rotated from left to right, like a hammer tied once over the shoulder.

Last, the third strike. Boohoo!

A heavy sword was a heavy sword.

This was because it adds weight to the sword.

That was why the center of gravity of a swordsman swinging a heavy sword was located outside the body, and objects with centers located outside were bound to fall over.

Like a giant tree that falls down, its body also takes the form of a falling tree.

At this time, the sword was swung to raise the body that was about to fall and preserve its balance. Since the weight was entirely placed on the sword, it was called a heavy sword.

Thus, the sword technique of the middle sword was so great and wide that it cannot be stopped.

The body tilts and twists violently, and despite its black heaviness, it was as fast as a ray of light.

If it misses and cuts through the air, its body twists and becomes the starting point for another heavy slash, and when weapons collide, it has a violent temperament that forces one-sided dominance with its weight.

"Hoooo……"

Qing puts away his sword and takes up his stance again.

As before, he raises his sword high, and as before, he stretches out one foot and steps on the ground.

A steep slope that strikes again like lightning.

Wedge!

But this time, a sharp, cutting-edge sound resonates.

What's different?

Another thing was the center of gravity and its movement.

He stepped forward but made no sound, so his center of gravity was still firmly planted on his hind legs, on the center line of his torso, just as he was trying to close the distance with his enemy.

The weight not carried by the sword remained entirely on the body.

This frees up the arms below the shoulders, eliminating the need to swing them for balance.

Shoulders that draw a larger circle.

The elbows were drawn gracefully towards the torso, pulling the center of the circle drawn by the blade.

And the most important key, the strength of the wrist was applied to the swing to increase the speed of the blade, so the air that cannot dodge was split and you cannot help but let out a sharp scream.

The method of separation was also simple.

The center of gravity has barely changed, so it's just a stepping stone to turn the angle of the body.

He released his arms that were curved around his torso and swung his sword, breaking away.

At the same time, the front legs glide forward without a sound, and the third sword strike was continued without delay, and the sound was a waeakssang, the sword slicing through the air twice with a single sound without distinction between the second and third strikes.

A quick sword was a fast sword.

It was a culmination of techniques in which the waist, shoulder, elbow, and wrist move in four circles with only one purpose: to swing faster.

Even if it doesn't carry weight, speed was itself a power.

Of course, the people of this primitive and uncivilized era could not clearly define the operating principle of the world, which was that force was mass times acceleration.

But being hit by a faster blade, a faster fist, a faster stone or arrow hurts much more than being hit by a slower one.

Humanity has been aware of this strange and mysterious phenomenon for thousands of years!

It was truly an astonishing phenomenon that such a profound secret has been discovered so early on, and it proves that humanity was worthy of being the master of the world.

anyway.

The center of gravity of the sword was me.

Since the center of gravity was on me, the technique does not need to move towards the enemy, and was free to extend in all directions as desired.

Also, even if the enemy dodges or collides with me, it was only a light collision and does not cause me much damage.

So, the quick sword has a lightness that continues endlessly like a strong wind.

"Hmm."

Qing takes up his position again.

Three more sword strokes, taking on the same shape, but this time they were silent and silent.

The joints were not fully extended, and even the wrists were in a loose shape.

Thanks to this, the sword was not at a right angle, but rather tilted towards the forearm, and its speed was slow and leisurely, as if the blade was floating through the air.

It was as if he was trying to loosen up his body through gymnastics after working out twice.

"Okay. See? Sword Friend. Come in. Let me try it."

"Ha, good!"

Nan-Gong Shencai jumps up onto the training ground.

Nan-Gong Shencai appeared in a hurry, as if he was flying, shouting, "What's so urgent?" and "What's so good?" as if Qing had said it was first-come, first-served.

Then three thump thump thump collisions.

The third demonstration, which was like a slow-moving gymnastics, was a solid defense that protected the body when meeting the enemy, and took the enemy's attack and deflected it.

This was the essence of gentleness and softness.

Continuously seek to gain an advantage by fighting with less force, smaller movements, and slower speed than the enemy.

Less force means less recoil, smaller movements mean a more leisurely path, and slower speed means conserving strength and stamina.

So, it was a clever way to actively take a defensive stance when facing an opponent, and to always be prepared to exploit the opponent's weakness.

It was a demonstration of the three types of subtleties: Medium-Rapid-Soft.

Orogeomgyeol, a mixed stew of various dishes, has been unified into one quality, at least now it was no longer a mixed stew, but has been separated into Jeyuk-deopbap, Hoe-deopbap, and Dakgalbi-bokkeum-bokkeum-bap, the land, sea, and air.

Hmm. This makes me want to eat all three… … .

"Is that really how it is?"

Because the principles were unified, it was easy to teach and learn, and its power was even doubled.

But.

"Still, isn't it a bit disappointing? Having finally learned such an interesting swordsmanship, isn't separating it like this a waste of its unique character?"

"So, the goal is to have them master all three types, but there's not enough time to learn even one, so for now, I'll teach them what best suits their aptitude and interests. And then they can exchange the rest among themselves."

"All three? Hoo, ohhhh……!"

Nan-Gong Shencai's eyes sparkle like stars.

"I see. So you've kept the three types of swordsmanship as consistent as possible? So, if you master each style's details, each one individually, you can flexibly mix and match them depending on the situation! Isn't that right?"

"Yeah. That seems closer to what Five Paths Sword was aiming for. To mix mystical powers, you need to be able to flexibly change within the beginner's style, even if you're not a master like me."

The only downside was that it involves too much of the instructor's effort.

It's a huge hassle to modify a perfectly good swordsmanship into three different types and prepare them separately.

But, isn't that what a master was originally like?

Since I've already taken on the job, I can't just do it half-heartedly.

Let's put the changes and illusoriess on hold for now and study them later when we have time.

Since it was a swordsmanship that originally consists of five principles, shouldn't it be passed on to even the officials who have completed the three paths?

To this extent, she was already more than adequately fulfilling hier duties as an instructor at the Department of Political Science and Technology.

It seems that the standards for martial arts were too high, and this was due to the distorted judgment of martial arts level that even the red border was neglected.

It could still be said to be a sense of responsibility. However, Qing displayed that sense of responsibility in an odd way.
