\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (5)}

If crying was defined as the phenomenon of excessive secretion of body fluids flowing down the face due to stimulation of the tear glands, then Sima Chunfeng cried.

If you say that crying was entering a certain mental abnormality after crossing the threshold of sadness or anger, regardless of whether or not there were tears, then it may not be the case.

To the observer, there was no difference between the two.

This was the reason why Sima Chunfeng was lying face down on the table.

Qing looked at that sight and reflected a little.

\textit{Well, maybe I was a little too excited.}

After all that tickling, wouldn't Sima Chunfeng have breathed a deep sigh of relief after arriving at the restaurant?

Qing felt that the punishment for daring to avoid punishment was a bit insufficient.

'I think I left something in the guest room.'

\textit{I turned around, and with a hiss, the body I was hugging hardened. The signs of despair I felt throughout my entire body were really, ahh.}

\textit{It was so thrilling that I did three more rounds, but there was no more reaction, just a complete collapse, dead eyes and chattering teeth.}

\textit{I thought she'd really lose her mind if I did any more. What the heck, her mental strength… tsk, that's why I said I can't be underestimated.}

In fact, Sima Chunfeng's preparation was not bad.

However, her imagination was a bit lacking.

She couldn't think of a simple solution: wrap the plate around it and put your hand inside the plate.

Well, she never thought that would happen.

You could say it's a lack of experience.

Because there has never been anyone who has gotten along with someone so casually and wildly.

Qing was always making 'That guy has no friends' jokes, but it turned out there really was someone who was like that!

It was Xue-i-ri. And Sima Chunfeng too.

So, it was when Sima Chunfeng was lying there like a corpse - she really thought she was going to die - just barely holding her breath, completely exhausted and unable to control her body.

A young voice speaking to her.

"Are you dead?"

"I survived…"

From vocal cords strained to the limit, a completely submerged voice emerges as a hoarse, yet incredibly thin tremble.

Ciyu tilted her head.

"Are you crying?"

"No. I don't cry. I'm just so tired…"

"Eat meat. It will give you strength."

Ciyu puts the chopsticks holding the meat into Sima Chunfeng's mouth, who was lying on the table.

Sima Chunfeng was a little moved.

\textit{She is Heavenly Blossom Sword's adopted daughter, isn't she? How could she be so kind, unlike her cruel and merciless mother? Her eyes are a bit dead, though.}

"Ah. Truly, this Sima-lang, ah, this grace, ah, forget, ah, uh, say something, ah, ha-"

But somehow food kept coming into her mouth.

Why was it that she kept pushing in without stopping?

Was she really doing an experiment to see how much meat can fit into a person's mouth?

Actually, it was because of Qing.

Since Qing likes to fill both cheeks with food and chew, it was natural for Ciyu to also do so, and because the child thinks that what she likes was what everyone in the world likes.

Everyone was looking at Ciyu nursing the fallen Sima Chunfeng with a warm expression on their faces.

Qing thought as she looked at the sight.

\textit{No, she's picking out meat again.}

It was a process of pretending to feed someone but ultimately leaving only vegetables on her own plate.

It was a very sophisticated strategy for a kid who was only (estimated to be) ten years old.

\textit{Clever and intelligent, our little girl is so smart. It's not because she doesn't study, but she's smart. She'll become a great person.}

Qing was also pleased in another way.

It's not that Ciyu didn't eat meat at all, but she only eats the tough parts without any fat.

Chunfeng was also eating well although she looks embarrassed by the feast of meat filling her mouth, so Qing let it slide this time since Ciyu was making friends with everyone and it's all about connections and wealth.

Sometimes, a strategy worked and it gave confidence to the always-shrinking Ciyu.

Qing looked at the sight and said just one word.

"Alcohol."

Changbin, sitting between Qing and Xue-i, immediately stood up and poured her a drink. The bottle he held neatly in both hands was a truly humble sight.

If only his hands hadn't been shaking, he could have been considered elegant, but unfortunately, his artistic score plummeted.

Nan-gong Shencai was talking about Five Sword Path the whole time while Gunyeong's suppressed moans echoed in between while eating porridge.

For some reason, Young Lady Murong was watching Qing closely.

It seems that Ciyu was having fun, and Xiang'er joined in, busily stuffing meat into Sima Chunfeng's mouth.

Next to her, Zhuge Lixian, who was sitting in horse stance without a chair, was shaking, saying that everyday life was training.

Qing smiled happily as she sipped her drink.

After all, food tasted better when eaten together. Right.

And then one more thing.

"Alcohol."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The reason Cai Shengxia wanted to enter Yizheng Martial Study Hall was to continue his master's legacy.

When the four divine beasts dance together as one, the entire Zhongyuan will kneel!

Those who master all four martial arts and perfect the Four Guardian Dance would be able to become the best martial artist in the world.

However, it was impossible to search for each and every successor in the vast Zhongyuan.

Cai Shengxia decided to become famous first.

A successor with a competitive spirit will come forward and challenge you to a duel, and who won't?

Just as an awl in a pocket will pierce through and fall out, isn't it natural that he will rise to the top of the martial arts world?

He might also be able to find it with the help of the Aliiance.

But, hasn't a descendant already appeared who made the same judgment as him?

It's already been worth it to apply to Yizheng Martial Study Hall.

Cai Shengxia immediately delivered the letter.

-Somethingsomethingfourdirection, somethingsomethingknees!

As the successors of the Four Directions, they cannot escape this long-held fate, so this was a duel where their lives were at stake.

Of course, risking one's life was not such a grim concept, and it only meant that the loser must serve the winner as their lifelong master.

Some people might say that it was more brutal than a fight to the death.

So, on a bright moonlit night, Cai Shengxia quietly leaned against the deserted wall of the testing center and waited for his opponent.

How much time has passed like that?

Even on a rather chilly spring night, the attire was excessive. Of course, even on a winter night, a thick coat wrapped in a tiger skin might be considered excessive for a woman.

The successor of Vermillion Bird Dance, Che Yaohong.

"It's you. Azure Dragon Dance."

Although it was an informal speech, it didn't sound particularly rude.

This was because Che Yaohong's voice itself was so obviously tired, and there was a deep sense of self-mockery in it.

Rather than being rude, it gave the impression that they didn't even have the energy to be polite.

There was a certain decadent beauty to it, completely different from the fire fist and flame bridge demonstrations during the day.

"Oh, Miss Chang. Haven't you seen my skill demonstration?"

"I didn't recognize your face the day before yesterday. I heard you were beaten up badly, but you looked fine."

"…It wasn't that bad."

Cai Shengxia made his excuse a beat late.

The intention was to become famous overnight by defeating the famous Heavenly Blossom Sword, but since he ended up becoming famous anyway, it can be said that the goal itself was achieved.

It wasn't the image he wanted though.

Cai Shengxia, who has nothing to say, politely made a sword greetings.

"Then, in accordance with the long-held wish of Mu-maek-"

"Wait a moment."

To him, Che Yaohong held out her palm.

"You want the Vermillion Bird Dance anyway. So let's not waste our energy on unnecessary things and just teach each other."

"According to the long-held wish of Mu-maek, the loser must serve the master of the Four Directions—"

"I don't care. Serving or being commanded. Why should I dedicate my life to something called a long-cherished wish?"

"But, Lady Che, haven't you already inherited the martial arts of the Four Guardian Gods? How could you so easily reject the ancestor's long-held wish?"

At that, Che Yaohong let out a long sigh.

"I heard you can control the wind. That's great. Just look at me."

Che Yaohong raised her arm.

"Just because an ironsmith handles molten iron doesn't mean the iron isn't hot. I'm no different. I wouldn't go around like this just because I like it. I wish I could wear pretty clothes, or at least wear ordinary clothes."

"Clothes… you mean? For that simple reason-"

"Just that?"

A deep furrow formed between Che Yaohong's eyebrows.

And then, haaah, just a heavy sigh.

"You said let's fight. What happened when wind and fire meet?"

"You have to try it out, long and short-"

"I'm not saying I will win. Whether I win or you win, the city will suffer. If a fire breaks out in this dry spring, it'll burn like a raging fire."

"Are you threatening to set the city on fire now?"

Che Yaohong touched her forehead.

"I'm saying there'll be a fire, not that I'm setting it on fire."

"Oh, then let's move to a different place-"

"Where are you going to fight? In the mountains? It's better for a city to burn than starting a forest fire. In the fields? Is it okay to set fire to someone else's grains?"

"Uh, um. Well, then, why don't we wait until it rains and then decide once the world was sufficiently wet?"

"Do you really have to go that far… Well then. Anyway, not today. Think carefully. Don't waste your energy. Just teach each other and go our separate ways."

Then Che Yaohong turns around and slowly walks away with a tired look on his face.

That was when.

Cai Shengxia shouts.

"Don't be ridiculous! Isn't it Lady Che who wants to achieve her long-cherished wish more than anyone else?"

At that, Che Yaohong stopped.

"If you truly wish to give up, why are you suggesting we exchange what we have? And why did you come out of your seclusion and enter the Yizheng Martial Study Hall?"

"Haa……. I-"

"Lady Che is just so kind!"

Che Yaohong's expression was blank.

She had a look on her face like, 'What the fuck did I just hear?'

"I was short-sighted! YMy Lady, you're so kind, you couldn't possibly handle the destruction your own divine power would bring! Well then, let me! I'll help you!"

"No, what are you helping me with…?"

"To help you control the flames of the Vermilion Bird! I have a way to control the wind, and I'm sure the White Tiger and Black Tortoise also possess similar secrets! So, I will find a way to perfectly control the flames, so you canshed that thick fur coat, wear the beautiful clothing you desire, and unleash your divine powers to your heart's content!"

Cai Shengxia's expression as he spoke was firm and serious, without a hint of hesitation.

If there was such a thing as sincerity, was that how it looked like?

Che Yaohong thought about it.

'What the heck, this little punk.'

Would a truly kind woman would always be wearing a fireproof suit, ready to light a fire at any moment? It was a double-layered garment that she wore while sleeping, as well as a blanket and sleeping bag, just in case she was attacked while sleeping.

Che Yaohong would never hesitate to light a fire to protect herself, regardless of whether it meant burning a city, a mountain, or the entire Zhongyuan.

But in the end, that's what how you would get a nasty title.

You'd get nicknames like 'Pyromancer Witch' or 'Arsonist Maniac' and run away while being chased by the whole Jianghu.

That's why she applied to Yizheng Martial Study Hall.

To learn proper martial arts, not just martial dance.

But even if they teach it at Yizheng Martial Study Hall, how great of a martial art would they teach?

It's a martial art taught by the arrogant masters of Wulin Alliance.

Still, they would teach you much better martial arts than than learning it from a local martial artist or buying some dubious manual from the market.

That's also why she suggested to teach each other.

The wind doesn't start fire.

She thoght it would be a good idea to switch from the tiresome Verillion Bird Dance to Azure Dragon Dance.

\textit{In the first place, what did he know about being kind and all that?}

\textit{Guys didn't care what other people think, so they can just walk around with their shirts off.}

\textit{I'm sick of this body's state, with my hair short because I can't grow it out, my skin tanned and dark, and my torso burning because it's weird to show my face.}

\textit{Using martial arts itself was a great risk, so just living quietly and holding my breath was even more dangerous.}

\textit{It's a good thing no one messes with that crazy woman wearing a bearskin and a tiger fur coat, otherwise I might have become infamous long time ago.}

\textit{And what happens after you help?}

\textit{Since you'd shown you me favor, should I make you my lord and serve you for the rest of my life?}

\textit{A kid who has never experienced anything like that, he happily went on a tour of Jianghu with not one, but two women peeking out from behind the wall and glaring at him fiercely, hahahoho?}

\textit{What's the big deal?}

\textit{Some people can't make even one friend because they're afraid of getting entangled in something that could started a fire.}

Che Yaohong's clenched fist was trembling.

\textit{I feel like punching that smooth face with fire right now.}

\textit{But, that is also tiring… …}

As Che Yaohong turned her back and walked away, a firm shout still followed her.

"It's okay! Everything will be okay! I'll help you! Please, don't lie to yourself and suffer any longer!"

\textit{Haiyaa, what a pain.}

Che Yaohong shook her head slowly.
