\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (1)}

Qing's routine had become simpler.

When the sun rises, she went to work as an evaluator.

The first test was conducted twice, once in the morning and once in the afternoon.

Since the martial arts demonstration of each applicant took about one-eight of a shichen, you can watch the talents of sixteen people per session, or thirty-two people per day.

Of course, that's in theory.

In reality, the number of people taking the test per day was two or three times less than that.

Among them, there were always some weird guys who come out and try to get attention.

Martial arts were not gymnastics or dances that were designed to be swung around in the air, so they can only be properly performed when the opponent receives them appropriately.

So, the examiner can help the examinees to develop their martial arts skills to their liking, and sometimes even teach the examinees they like.

In other words, it was absolutely not a surprise mission, a competition to beat the examiner, or anything like that.

If that's the case, then let's have a duel where they kill each other, no, fight each other, and the winner gets the award. Why would they have examiners sit high up and watch in boredom?

Nevertheless, there were still some ignorant applicants who tried to win somehow, so here's another one.

The testing room was bustling.

It was because a peerless beauty, whose face was covered with veils, was called to the test.

Why was she wearing a veil when she's so beautiful?

Well, it's not a type of cotton shawl that covers the entire body like a woman's hat, but rather a type of cotton shawl that was hung on the ears and covers only the lower part of the face.

Qing tilted her head.

\textit{No, then what's the point of using a veil?}

But it actually looks prettier.

As the saying goes in Qing's homeland, if you cover your lower face, your appearance will go up by at least two levels, or at least that much.

The lower face has a variety of shapes, so it was difficult to be born with a beautiful face. Also, the human brain fills in the parts hidden from view by imagining them in the most ideal shape.

"I'm Sword Jade-lady of Sword Pavilion."

"Sword Pavillion!" "Sword Pavillion!" "Sword Pavillion!"

People in Zhongyuan have a habit of repeating words they know to show that they know them, so if they show off like this, it means that they were somewhat cultured.

Qingdo roughly heard of Sword Pavillion before.

It was a mysterious sect of female swordsmen in Hainam Island.

By the way, in Jianghu a mysterious sect meant that one stays in a corner of Zhongyuan and did not come out.

However, that doesn't mean that all the hermits in the corner of Zhongyuan were from a mysterious sect. If they didn't go out into Jianghu, how would you know if such a sect existed or not?

So how mysterious was it that their name became known even though they never came out?

But that's exactly why they're called the mysterious sect.

That didn't mean it was that great.

Either it produced a master whose name was known throughout Zhongyuan, or it was for a very simple reason.

All the members were women.

Just hearing about a sect comprised entirely of women made her curious.

Then, Sima Chunfeng, who had been silent til now, think it was the moment to spoke out.

"Kuhaha, this is getting interesting. If she inherited the Jade-lady title, she must be the eldest disciple of Sword Pavillion. There must be only one reason why that proud swordswoman of Sword Pavillion would show up, right?"

"Why is that?"

"Kukukukuku……!"

\textit{This guy, if someone asks you a question, you should answer, but why are you just smiling suspiciously?}

Qing was about to spread her fingers and prepared to retaliate.

Unfortunately, those fingers never dug into Sima Chunfeng's soft (perhaps due to his lack of muscle mass) side.

"That girl wishes to regain the title of Sword Queen, and so she requests a spar from Heavenly Blossom Sword."

"Huh? What was that?"

Qing's forehead furrows.

\textit{Another weird kid shows up and takes up my time.}

\textit{When I asked how long the first test would last, I got the desperate answer that it would be until evryone is tested.}

Even though the number of applicants was increasing in real time because the application for admission can be taken on-site, strange persons keeps appearing and wasting precious time.

"Sima-lang, can you explain the situation?"

"Oh, haven't you heard? This story begins with a chance encounter about fifty years ago…"

"I'm in a hurry. Hurry up."

"The previous Sword Queen was defeated by Godmother and gave up the title of Sword Queen. So, I guess her disciple was trying to reclaim it now?"

Sima Chunfeng gave a simple summary.

Although Chunfeng was quite strange as a person, she was at core a good person, so her high virtue was not without reason.

It seems like the sense of chosenness was coming out in a good direction?

\textit{Well, come to think of it, isn't Sword Queen the title for the best swordsman among female martial artists?}

\textit{By the way, what was Master's nickname? Godmother.}

\textit{Of course, it was a very fitting nickname that expresses both Master's kind heart and somewhat radical thoughts in just two letters.}

He said that he would hear it once in a while, especially not in front of his master.

Because Qing was just a master.

Sword Queen? So a man was a Sword King and a woman was a Sword Queen? Does that mean a woman can't be the Sword King and must be the Sword Queen? That's what I thought it meant.

Even the one and only Empress of Zhongyuan, Empress Wu Zetian, was only an empress, so it seems she wasn't that radical.

Since the original owner of the sword was different, she probably didn't want to hear it.

It's a bit unfortunate that I have to hear this from Chunfeng's mouth, but since you never said anything…

Anyway.

Qing doesn't avoided a fight that comes her way.

But, you have to choose the time and place.

It was the kind of thinking that a woman who doesn't care about time or place thinks when she picks a fight.

The original human nature was that if I do it, it was forbidden love, but if someone else does it, it was just an affair.

This was evidence that Qing was still human, that she has preserved her humanity despite her transcendent genius.

"I understand what you're saying, Lady Sword. However, the entrance exams for Yizheng Martial Study Hall are currently underway, making it inappropriate for a private duel. Could you please speak to me after the schedule oss over?"

Then, Geomokgun just looked up at Qing with calm eyes.

Then he said.

"The Sword Queens is originally the title of the most outstanding female swordsman, and has been in our Sword Pavilion for generations. However, forty years ago, my master was defeated by Godmother, and thus the title of Sword Queed was handed over to her. At that time, Matriarch promised that if any descendant of the Sword Pavilion ever sought to reclaim the title, her disciple would not shirk it. The Cheonhwa Sword must now keep that promise."

Qing felt wronged.

\textit{No, I've never heard of such a promise.}

\textit{Why didn't Master tell me about this?}

Well, Ximen Surin never promised!

A village girl from an island village she never heard of suddenly attacked her like a black widow, and then what?

'Ugh, I'm angry, but I'll yield the honor of the Sword Master. However, we at Sword Master will definitely reclaim it, so we'll challenge again.'

She just nodded her head because it was too troublesome.

Although the Geomgak faction did not normally interacted with the mainland sects, they always stepped forward to help when trouble arises in Zhongyuan, so they were classified as an Orthodox faction.

Also because they were both from a female-only sects, she felt a sense of closeness.

Ximen Surin never even thought that those words were a promise for disciples to fight each other.

"Then, after today's test is finished, shall we spar then?"

But Geomokgun shook her head.

"This is a spar that must be widely known to the public, restoring the honor of the swordsmanship. Furthermore, after the exams were over, the sun will already be setting, making it unsuitable for a spar. Furthermore, after the exams were over, you will be attending the Yizheng Martial Study Academy as an instructor, Heavenly Blossom Sword."

\textit{What? Isn't that your problem?}

\textit{If you come to me right away and say, 'I'll temporarily give up my title', it's like you're pawning something.}

\textit{No, even if you leave it at a pawnshop, don't you only could pick it up during business hours?}

"Or are you afraid of defeat?"

\textit{No, isn't that too blatant provocation?}

"Even though Lady Sword says so, it is not possible to interfere with the events of the Wulin Alliance due to personal circumstances, is it?"

In that moment, a shiver ran down Murong Zhuji's spine. Ah, this.

"Even the most trivial of matters, if personal matters take precedence over greater ones, the greater good will inevitably be forgotten. Lady Geom, as you say, I am here as an instructor and examiner of the Yizheng Martial Study Hall, so I cannot prioritize personal matters. Do you understand what I mean?"

"No, that's not true. The affairs of Orthodox factions are paramount, so no one in the world would point a finger at such a crucial matter."

"Since our opinions don't connect, it seems we'll never reach a conclusion. In that case, let's do this. If Lady Sword requests to take the test as a candidate, I will gladly accept. If I lose, you've already surpassed the instructors, so studying at the academy will be unnecessary. But if you lose, you should seek the necessary training at the academy. What do you think?"

"Very well. The Sword Master of the Sword Jade Army will request the entrance examination from Instructor Ximen."

Although she looked slightly resentful, her reply was immediate, as if there was no need to worry.

And then, he pulled out his sword and swung it into the air.

The soft starlight blooms and spreads out gently, making it a swordsmanship, and at the same time, the starlight branches out into many branches and was splendid, making it a swordsmanship that also has the wonderfulness of illusion.

"The study of swordsmanship, the ten thousand swordsmanship."

A ritual of preparation. It was a preemptive strike to announce that this type of swordsmanship would be used.

\textit{Ohh, Peak Realm. I also used to have something to believe in.}

Qing took out the Fushen-di.

Geomokgun's eyes sharpened, but Qing simply shrugged.

\textit{But it's a little bit strange.}

\textit{Just a Peak Realm?}

\textit{What on earth do you believe in to be so confident?}

Of course, her current realm was still a secret, but still, Qing was widely known as a Transcendent Realm master.

Well, Haenam Island was far, and it's an island, after all.

In the primitive ancient Zhongyuan, where the fastest way was to travel by boat, and the next best was to travel by horseback, how far could the rumor of last autumn spread?

So, Geomokgun was confident.

At least that was the case until sword and flute met.

It was a world of unimaginable, unpredictable force that sparked with a loud bang.

It was so admirable that she didn't let go of her sword, so the two hands holding the sword were pushed away and her waist was forced to turn to its limit by the recoil.

The sides were open!

Next, bang!!

Qing didn't see her as a woman.

It only depends on whether the mind was equipped or not.

\textit{If you were in a state of discomfort due to a hurt heart like Young Lady Murong back then, then I don't know, but if you lack etiquettes and manners, then it was a deficiency that can be filled with the embrace of love.}

"Ouch!"

With a painful gasp, Geomokgun's back arched like a bow.

It was bent sideways, not forward or backward.

In a shape almost like a shrimp.

Qing slowly backed away and created some distance.

Geomok-gun gasped for breath, then regained her composure and gave a serious look.

In fact, one nuclear punch to the head could have made her roll around.

\textit{But, um, the swordsman was a member of the Orthodox factions.}

\textit{At the very least, she had to fight until the very end before falling. If she fell in one blow, the reputation of the swordsman would be lost in that swamp.}

\textit{But isn't the sword not guilty?}

\textit{They said that he was a member of the political party and a member who stepped forward to help in times of danger.}

\textit{So, for the sake of the honor of the swordsman, she must be beaten so brutally until she falls down.}

\textit{Of course, then I would become the villain?}

\textit{Then, I will accept that resentment.}

\textit{I'm so kind.}

\textit{Since there were guys who keep coming up because i look easy, I should take this opportunity to clearly show them what kind of person Instructor Ximen is.}

\textit{It's a proven fact that you should never be rude to a teacher who wield the flute.}

\textit{Why do the kids who came to take the exam keep talking about how beautiful they were in the world? They're just out of their minds.}

Is it to vent all the frustration that has built up from those kinds of interests?

It's not about holding on to a jerk who can't back down just because he's sick and beating him up for a long time.

It's definitely not because the feeling of hitting that dancer last time still lingered on her hand.

But inside the veil, Qing's smile was nothing but a sinister one.