\chapter{Warrior Self Study - Martial Study Hall Classes Will Begin (2)}

Even when she was at Peak Realm, Qing never once struggled against her opponent in a one-on-one fight.

That bastard's half-joking, half-smiling rhetoric about transcendence, that unnatural pride of being half-way to the next level, was in fact half-sincere and also true.

But the current Qing was not at Peak Real,.

As a result, the Geomok Army was hit a lot.

It was a very even and brutal hits.

She had horrible experiences where she had been hit while stretching out her sword, hit while swinging it, kicked in the stomach, kicked in the shins, had her neck hit, had her thighs hit, and her legs gave out without her realizing it.

At first, the crowd was watching with excitement the fight between two female warriors who held the supreme honor of being the Sword Master.

A look of growing tiredness, a feeling of pity creeping in.

'Oh, that must hurt.'

'You're really beaing up the kid.'

Among them, only Mo Yong-ju-hee's heart was pounding, and for some reason, she couldn't take her eyes off the screen, swallowing her saliva.

Despite this, Geomokgun did not put down his sword.

This was called the 'downed dog effect', and people tend to support the underdog.

So, the crowd also clenched their fists and desperately hoped to strike that evil Heavenly Blossom Sword over there.

And then eventually.

"……I lost."

Huh. Already?

If Chunfeng had even half the guts, he wouldn't have said he lost already. But now he felt a little more relaxed.

If you let go of your body twice, you'll be able to catch people.

"So, we'll see you at our school from now on?"

"……Please send me a map."

The black-haired soldier turned around, stumbled, and limped away into the crowd, her left leg having been hit particularly hard.

It was a very lonely sight.

Perhaps the crowd's disappointment was shown by the lack of cheers despite the victory.

But Qing was confident.

No, just to this extent. How much would it cost if I lost?

Ximen Surin didn't bother to impart her swordsmanship to her already gifted disciple who already possessed perfect martial arts skills, so she focused on melting what Qing already had through sparring that resembled real combat.

To dismantle the Movement from its fixed form and apply its true meaning in battle.

So Qing rolled around every day.

A drop of sweat now saves a drop of blood later, and a scream now saves a death scream later.

So, Qing had rolled around with the magic of love, the near-death experience, and the secrets of nuclear bombardments.

This was the true nature of the training that Qing did while staying at the Divine Maiden Sect.

And Qing, who actively supported Master's educational policy, only took on the role of Ximen Surin this time.

No matter how much she was angry or in a good mood, she didn't necessarily beat up a good person just for fun.

It all becomes blood and flesh, and the more you suffer to the point of death, the more you mature.

I've already become a true teacher. Please teach me what was true and right. Wow.

And wouldn't the Geomok Army also learn well by studying hard?

If she had gotten angry and started whining after getting a few times, Qing wouldn't have beaten her so badly.

But I think that Geomokgun also gradually became more serious and began to seek proper education.

Because I felt like there was a question mixed in with every sword attack, like, "So, what if I swing it like this?"

Of course, she could just be a stubborn woman.

But, in terms of feeling, it felt like she was similar to Geomwoo, like a female Geomwoo.

Perhaps, seeing as he left satisfied?

Well, if not, then forget it.

As the limping Geomokgun walks, the crowd makes way for him, and for some reason, many pitying looks were fixed on him.

Of course, that was only for a moment, as the path I had just walked was soon filled in and I was out in the open space.

"Young Lady Sword? Are you alright? Even if you were the Heavenly Flower Sword, how can you treat someone like this? Such a law was unacceptable!"

"That's right! That's too much!"

"What should I do? You must be in a lot of pain…!"

Geomokgun came out into the world of martial arts and suffered two defeats.

Once upon a time, to Heavenly Blossom Sword now.

And once again, to this young man I met on my journey, Cai Shengxia, who had the amazing ability to draw out nature's spirits.

Geomokgun looked indifferently at Cai Shengxia, who had a worried look in his eyes, and the two women next to him who were making a fuss.

You must be in pain, Sister Sword, were you okay? Oh, how come, there's already a bruise on your arm… …! And you're limping like this. How could you beat someone up like this?

But there was a kind of sinister pleasure in the eyes of the women who spoke like that.

At first glance, it sounds like concern, but if I were to translate it, it's an expression of displeasure, like, "Wow, you're completely screwed."

Of course, this was nothing new.

It was just a journey to compete with this amazing new skill and gain clues to reach higher levels, but it seems that to these women, they were seen as rivals trying to steal their man.

So, after all that pretense, he's completely ruined, and it looks like he's going to completely embarrass himself in front of you.

He simply asked to meet his rival and fight as swordsman against swordsman.

To begin with, he's a lecher who pretends not to know the two women he likes and turns his eyes to another woman.

It's more of a problem if you're not pretending not to know.

"This was just too much! Even if you're an instructor, you can't treat someone like this. I'll just—"

"What are you planning to do right now?"

"Huh? That's…"

How to do what and how to do it.

What can even Chai Shengxhia himself did after getting beaten up?

"Oh, a protest?"

"Do I look that sick?"

Suddenly, Geomokgun's eyes gently opened.

Cai Shengxia stared blankly at her carefree smile, as it was the first time he had seen her smiling.

"You have seen it wrong, Young Expert."

"Yes?"

Geomokgun walks without hesitation.

Is this the expression "I have become a tattered rag" because there was no place that does not hurt and no part of me that does not ache?

But it doesn't hurt.

It's not a matter of the body, but of the mind, thanks to this incomparably refreshing sense of liberation.

\textit{The first place I came across was truly a terrifyingly wide and vast place.}

\textit{If we had set out along the coastline from Haenam Island, we would have returned to the starting point several times, yet we had only just arrived at our destination. How much wider the world would have been, stretching west to Sacheon, east to Gangnam, and north to Habuk?}

\textit{The first loss was special, but the second?}

\textit{The world is so vast, so it is only natural that there would be one or two masters who could defeat me.}

\textit{Heavenly Blossom Sword is not at Peak Realm.}

\textit{That overwhelming force, that restrained movement, that gaze that seemed to hold me in the palm of her hand and looked into me with such clarity.}

\textit{Above all, it wasn't a duel or a spar to begin with. It was a one-sided instruction and teaching.}

\textit{Because it was absolutely not something that someone of the same level could do.}

\textit{Although the method was quite rough and harsh, it was a teaching that contains a clear answer.}

\textit{If I could compensate for the precious experience that was worth a thousand pieces of gold by just being a little sick.}

\textit{If it weren't for the fact that the place I was hit was so painful that I couldn't concentrate any longer, it would have been fine even if it was all day long.}

\textit{But there is no problem.}

\textit{If I enter Yizheng Martial Study Hall to keep my promise, I will be able to continue receiving teachings.}

\textit{However, it was a little embarrassing and shameful.}

\textit{How shocked she must have been to see a young woman in her prime pick a fight and have a go at it.}

If Qing had seen into these inner thoughts, then perhaps she would have spoken out.

'Look, that's a proper female swordsman'.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's work was simple.

While the sun was up like this, I perform the duties of an examiner.

When the sun sets? Even after the sun sets, Qing was busy.

"Um, Young Lady…"

"Yes, Young Lady Murong? What's wrong?"

"Um, that's it."

Murong Zhuxi clenched and unclenched her fists, twisting her torso in a difficult and awkward manner.

Qing was laughing at him.

"Do you have a favor to ask? Hey, why? Between us. What was it?"

"Well, when you sparred with that swordsman today. Ugh, that was an incredible sparring match. It felt like you were teaching in a completely practical way."

"Hey, it's not that grand."

Qing continued speaking, scratching the back of his neck.

"How did you know? Lady Moyong has reached her peak, and her discernment has become quite human."

It was a speech that contained absolutely no trace of humility.

It would be quite shocking to hear someone like this girl only acting well in front of adults.

But, originally, social life was like this, if you treat your superiors well, your subordinates will naturally follow suit.

It was a big decision by the Yookchamgoldan to motivate their friends.

Of course, it was a way to only make friends feel good, cutting off their flesh and bones, not my own flesh and bones.

"Uh, well, me too, if I may ask you a favor, I'm learning something new these days, called Dujeonseong, but it's difficult, I'm really stuck, I'm so frustrated, I'm just so strict, so blocked, so, strict… Whew, Whew."

Somehow, the sound got quieter as I went further back, and since I had superhuman hearing, I could hear the gasps of breath coming from behind.

"Hmm. Sparring was like a real fight. They say vomiting now saves you from vomiting blood later. So crying during the fight won't help, right?"

"Ah."

At that, Murong Juhee's face turns bright red.

Qing tilted his head at him.

\textit{What is there to blush about in what I just said? I thought I said I'd just make you vomit instead of coughing up blood.}

\textit{Is it the part where she'd be crying?}

\textit{Young Lady Murong cried a lot in front of me, so it might be embarrassing.}

"But I'm a bit busy these days. If Young Lady Murong were to ask, I'd really like to join you. But first, I'm supposed to take the role as an instructor and teach a swordsmanship called Five Path Sword, so I'm currently researching it."

"Oh."

"So maybe next time."

Murong Zhuji nodded. 

\textit{Next time, and again, and again, isn't that the promise of a next time that would never return?}

\textit{No, no. Then, if you finish the research quickly.}

Murong Zhuji raises her head and speaks.

"Then, I, I'll help too!"

"Oh, that's good."

Mo Yong-ju, join.

In this way, the Wulin Alliance, which does not know how to save money, burned firewood and trained in the Five Swordsmanship in the bright courtyard of the temporary headquarters of the martial arts academy.

Because to teach, you must first know.

Surprisingly, Qing was a sincere person.

You could say that she was not sincere at all if you saw her fell asleep and snored loudly, and when she opened her eyes, she was out playing and having fun.

That was because it was a time when you could rest hard and play hard, but the root cause here was 'hard work'.

Even when she had to do something she didn't want to, she was faithful to that responsibility and didn't waste time. So, if you were to put her in the boring role of an examiner, she would watch the aplplicants closely and diligently wrote the evaluations.

This was a model of diligence: sleep when it's time to sleep, play when it's time to play, and work when it's time to work.

But weren't the times when you have to do that were severely limited?

Normally, I'm the type of person who takes the loss and doesn't do anything.

It's because I only do things to avoid being ordered to do something or to avoid a disadvantage that I can't bear.

That doesn't mean Qing was special.

Surprisingly, everyone knows one or two of these people, so they were quite common figures.

A very passive and sincere person.

A passive person who only worked hard when told to do so.

In any case, Five Path Sword Technique contains the five secrets of swordsmanship in one swordsmanship.

In fact, there were many martial arts that have different effects depending on the type of food.

One first was a strong sword, two first was a strong sword, three first was a quick sword, and so on.

The characteristic of these martial arts was that they were at two extremes: either completely basic or the highest level martial arts that required sword training from the very beginning.

If we're talking about basic martial arts, it's like the Moon Sword.

The Iron Guard, the eighteenth class of the military branch. And the lower-ranking martial arts masters of the prestigious Geopa and Sega families.

Thanks to this, the disciples were able to experience various mysteries through introductory martial arts and at the same time find the nature that suited them and decide on their career path.

In the latter case, it was a case of a master who had already reached a state beyond the realm of the mystical, compiling the enlightenment of his later years.

The secret of the highest level, like the Dokgo Gugeom of the Great Emperor Mucheon.

But Orogeomgyeol was different.

It contains many secrets in one recipe.

After a heavy strike, the sword was turned and released, and the speed was used to lead to a quick sword strike, and then a smooth finishing sword strike was performed.

It was a series of events that start from one meal and end from another.

It sounds good when you say it this way.

But it only sounds good.

If it were really good, the current martial arts world would be a hodgepodge of these kinds of tricks.

There was no such martial art because it was not good.

However, as an instructor, it was a martial art that Qing had to teach.