\chapter{Be Sure to Maintain Your Dignity When Going Out (7)}

The body of Qing was invincible, and the ultimate realm that all martial artists long for was swallowed alive from the moment he left the martial arts world.

In the past, I had a rough understanding of it through my own experiences.

To the point where you can eat whatever you want without getting sick.

It's because I ate all sorts of things that people shouldn't eat out of sheer hunger.

Perhaps it's because of my blood poisoning constitution. Ah, it's been a while since I thanked you, Strategy Guide. Thanks to you, I'm somehow still alive. If you ever enter this primitive era, I'll pave the way for you. Seriously.

Now I understand more clearly.

Thanks to seeking teachings from the shamanistic enthusiast, Danryun Jinin, I realized that this blood poisoner's purification action was not biotechnology, but a cosmic mystery.

Not because of the liver, but because of the thoughts.

What difference would there be if we injected poison into a body that was already dead?

To put it simply, let's call it a setting.

The setting was that Qing's body was already dead, probably died with Princess Yeonsul. And then, oh my, I'm possessing a body that's already dead!

So the poison doesn't work.

Because poison was a tool that harms the living, not the dead.

This makes it sound like the poison was an evil entity that has the will to harm people.

But if it's magic, it's possible.

This was how people have perceived poison since ancient times, and sorcery was an act of realizing this common, absurd perception of humanity into an idea.

It was the so-called universal magic theory.

To Qing, this sounds ridiculous.

But isn't there already an even more amazing cosmic mystery, a Qi, in this amazing pseudo-Central Plain?

In a world where people fly around with swords wrapped in rays and spitting out magic, how could there be any magic?

So, this status window, well, the central plains were wide and the outside of the central plains was wide too, so there might be someone else using it somewhere, or there might be something similar.

Anyway, whether it was poison or food poisoning, it didn't work, and the poison itself didn't disappear.

Since Qing's body was already dead, it was not detoxified, so it just piled up inside him.

Now, what, the poison-eating parasitic salamander, the bottle, was doing the detoxification for me, so if this was a coincidence, then it was a very coincidence.

If it weren't for the bottle of alcohol, my liver and intestines would have been filled with poison and overflowed into my blood, and I would have been bleeding toxic blood.

Is blood the only problem? Poisonous spit, poisonous tears, hmm, poisonous spit seems a bit okay.

But what's even more convenient was that you get to hear about the good things about eating something.

Even alcohol was like that.

When you drink it, the burning heat was hot, but it also brings back that feeling of alcohol that makes you feel better.

According to the interpretation of the single-minded Jinin, the feeling of being dull due to alcohol was the function of the body, that is, the white, and the feeling of being good was the function of the soul, that is, the spirit.

Since the setting was that the body was dead, but the soul was not dead, isn't the state of feeling good after drinking alcohol a part of the mental realm?

Anyway, that's why Qing likes alcohol.

Because it was a completely perfect food that makes you feel good when you eat it, but has absolutely no side effects.

So, the Qing leadership was cheerful and lively.

When pouring alcohol, pour it all down without leaving a single drop in the glass.

He never refuses when offered a drink, and readily offers a glass with a cheerful expression. He was a truly delightful drinking buddy, no matter when, where, or with whom he was with.

On the other hand, he really enjoys drinking alcohol.

When you reach the point where you can enjoy alcohol for its taste, you can enjoy the subtle sweetness and sourness of Hwangju, the harmony of sweet and sour, the heat and fragrance of Baekju, and the strong, sweet and sour taste of Takju, all of which were wonderful.

So, the beautiful smile of a peerless beauty after pouring a glass of wine, the beautiful exclamation of ``Kyaaah,'' the cheerful sound of the glass landing after being set down.

Anyone who sees Qing drinking alcohol can't help but swallow their saliva and think, "Wow, it looks really delicious. What kind of alcohol can it be that makes it taste so good?"

Even for those who don't enjoy drinking, it's a true alcohol promotion agent, or the best side dish you'll ever see.

So, what this means was that if you drink and ask for favors, you will end up drinking too much without realizing it.

As for Qing himself, he doesn't really have any recommendations other than the first drink, so he just tells everyone to drink according to their own tolerance.

If you drink it so deliciously, how can you tell others to drink it in moderation?

``Hehehe, my lady. Um, there’s something that’s bothering me.''

``Hmm? Young Lady Murong? Are you drunk?''

"No, I'm not drunk. You know that. I'm just a drunkard. I've never lost before, or rather, I lost. Hehe, I lost to you, young lady. Right?"

Hmm. I'm drunk. I'm drunk.

But Qing didn't really stop him.

Because for the high-ranking players (based on the Zhongyuan), there was a powerful awakening called alcohol discharge.

There was a skill that allows you to quickly regain your senses by simply expelling alcohol from every pore if you put your mind to it.

Of course, since it's a technique that would be quite ridiculed if done at a drinking party - if that's the case, why were you drinking? Or were you trying to spread the smell of alcohol? Don't you know that this isn't just a smell, it's the alcohol itself, and if you smell it, you'll get knocked out? Are you trying to get the rest of us to get drunk while you sober up? And so on - it's a technique that's only used in emergency situations or when going home, but anyway.

If you can quickly become sober even after getting drunk, there was no reason to discourage someone from getting drunk.

So, Qing was just fun.

In fact, it wasn't just Young Lady Murong who got drunk.

In the back, several chairs were placed together, and Seol-i-ri lay down very straight and fell asleep.

Thanks to this, Changbin, who was freed from the female barrier on the left and right, was now standing next to Paengdaesan, chattering away with a determined expression on his face.

Although Pangdaesan was getting along, his expression was showing his displeasure and telling him to go away.

And there's also the background noise that keeps coming from earlier, and the noise that just doesn't stop.

"This Sima-lang was truly unbearable. How can ordinary people be so insignificant? It's astonishing how they can breathe with such intelligence. If not led by more brilliant individuals, it's clear that we will fight each other and self-destruct in the future. Geniuses like us—oh, excuse me, excuse me. Geniuses like Sima-lang, lesser geniuses like Heavenly Blossom Sword, and prodigies like you—if not led by us, we pitiful beings who will perish..."

Sima Chun-bong sits hunched over, resting his chin on the table, his heavy pouch of wisdom resting on it, and continues his speech to no one listening.

The blue lips draw a loose curve.

This kind of atmosphere was also good.

It's not possible to be productive all the time swinging a wooden sword, so I guess this relaxed atmosphere has its own charm.

I guess it's fun to watch everyone get drunk while still being sober.

In fact, it was like this even before he entered the martial arts world.

Because when I entered a drinking party, my role was to send the party back to their senses until the very end.

To be exact, I'm not trying to get drunk, but whatever.

The joy of seeing everyone drunk and having fun while still maintaining their senses was something hazy, it's hard to describe.

``Why, Young Lady Murong? What were you upset about?''

"No, I'm not upset. How could I be upset with you, Young Lady? I'm always grateful, hehe."

And then followed.

``But, I feel a little sad. I feel sad.''

Hmm. I'm definitely drunk. This was an illogical phenomenon that can never be caused by pretending to be drunk.

``Hmm. What should I do? What’s bothering you?''

``Yeah, no, no.''

"no?"

``Yes. But, a little? A little?''

This was the endless cycle of sorrow.

Of course it doesn't matter because it's fun.

``So were you upset or not?''

``I don’t know. You don’t even know my heart.''

``If Lady Murong doesn’t know, how could I? Now tell me.''

``No. No. Hmm. Well then. Um, I need you to do just one thing. Could you please do me a favor?''

``Hmm. Have you heard? What was it?''

``Excuse me, ma’am, can I sit on your lap?''

It was a pretty cute request.

Why, did he secretly like the sight of Ciyu in his arms? Well, a drunk person's thoughts were baseless anyway, so analyzing them would be pointless.

Qing tapped my knee.

``Okay. Come here, then.''

``Hehe. To me, you were the best.''

And then he climbs up onto Qing's lap, swaying.

``Hmm. Young Lady Murong? Is this it?''

"lol."

If you ask someone to sit on your lap, don't you usually ask them to face the same direction?

But why were we facing each other?

Murong Zhuxi hugs Qing's shoulders and places her chin on the nape of his neck.

And then, somehow, I started to dream.

As if he didn't like something, he kept changing positions back and forth on Qing's lap.

``Hmm, this isn’t it. Why was that?''

``Isn’t that the wrong direction?''

"This isn't it. No. Change it. It has to be changed. Please change it, young lady."

And then he sat back down on the chair, his face flushed with alcohol, and he spread his arms wide.

``Okay. Here you go.''

``You want me to sit on Lady Murong’s lap? Wouldn’t that make it uncomfortable to drink?''

"Yes. Can't you? Oh, but why do you always say you drink, young lady? You drink, after all. But it's okay, young lady. You've thought about everything, right? I don't know about you, but hurry up. Can't you? Yes?"

``I don’t think the previous injections were like this.''

Well, in the past, she was a person who had accumulated a lot of resentment, and was the resentment itself, an inferiority complex about a certain part of her body.

Alcohol weakens self-control, so the accumulated emotions just burst out through the thin line.

But now there was no anger to explode.

Qing sits on Murong Zhuji's lap.

Oh, it's hard? Young Lady Murong's thighs were really round. She's just a huge muscle mass, wow.

Developed thigh muscles were great from front to back, not side to side.

Murong Zhuji's thighs were unusual when viewed from the front, but when viewed from the side, they really look like they could fly. Perhaps that's why they're a bit, no, a lot higher...

To pick up a glass, you have to stretch out your arms and bend down, so it's actually hard, high, and quite uncomfortable.

In addition, there was Murong Zhuji-hee who clings tightly to his back with her arms wrapped around his waist as if tightening his grip.

``What was this? Is this right?''

``Oh, no… It’s surprisingly light… It would be better if it were heavier….''

Actually, she's not that light because she's tall, but anyway, even Lady Mo-yong was quite the womanizer.

But what does it mean that it has to be heavier?

What weights were those? Perhaps they're meant to be used for thigh training. It seems like they're hard and exerting a lot of force, so I'm starting to have reasonable doubts.

That was when.

``No, Heavenly Blossom Sword? That won’t do?''

``Huh.''

"Sitting higher than the main Sima-lang, the seated height was clearly the main Sima-lang's victory. Hehe, I see. So that's what you were concerned about? But this was also the bitterness of defeat. The Heavenly Blossom Sword must not seek victory through such dishonest means, but must overcome it through effort."

His expression changed to "Eh" again.

What does it mean to win in the sitting height category, that is, in the sitting height category?

If you're tall when sitting, doesn't that just mean you have short legs and a long torso? And what kind of effort can you put into increasing your sitting height and lengthening your torso?

``What the hell was this-''

"I appreciate your efforts, but Heavenly Blossom Sword, please come down immediately. Let's have a fair fight. Those who were role models for others like us shouldn't engage in such despicable tactics, should we? Besides, it feels like Heavenly Blossom Sword was looking down on me from above, and honestly, it's a little uncomfortable."

``No, this is.''

Apparently, he needs to regularly destroy his sides to come to his senses. I never thought a system of body parts destruction would be necessary in a place like this.

It was the moment when Qing was about to rise from his seat to receive the appropriate punishment.

This time, Murong Zhuji, who was behind him, tightened her arms around his waist and applied the brakes.

``Young Lady Murong? Let go.''

``No, no. Just a little more, just a little more.''

A drunk person has no logic.

If you say it can't be done, it can't be done. So what?

Know that Chunbong was lucky.

Later, when I sober up, I have to buy Miss Mo Yong a drink of thanks.

Then I'll get in on the action too, and this situation will happen again, so if Lady Murong earns another point of kindness and buys me drinks to show my gratitude,

Oh. The drinking party was full of unlimited energy and unlimited drinking.

I was going to drink like that for a while, but, um, it was really uncomfortable.

The seat was too high, and the torso leaning against the back wouldn't stay still, so wouldn't it be constantly pressing down, moving left and right, up and down?

It wouldn't have been so bad if there was some cushioning material.

Isn't this the same as bones rubbing against each other? Front ribs against back ribs. What kind of ribs versus ribs was this?

"No, Young Lady Murong? Can't you stay still for a bit? It's a little uncomfortable."

But what kind of drunk person would listen to what you say?

There's no answer, and he just keeps pushing my back with his torso. What the heck, you said you were upset, but this was how you're taking revenge? It's so uncomfortable?

I was so absorbed that I didn't even pretend to listen.

But there was a way to everything.

``Oh, Young Lady Murong, I need to take care of something for a moment.''

Qing said, gently pulling away the arm that was holding my waist.

Although it was shown as being easily pulled away, it was an arm that Murong Zhuji had been holding onto with all her might, so it was a scene that showed that Qing's strength was not at a human level.

"oh……!"

``I’ll be back in a bit. San, take care of the kids.''

Qing says this and quickly leaves the top suite.

While you're at it, empty your bladder a bit too.

And as I was about to go back to my room, I suddenly heard a rather desperate voice.

-You can't do that, I'm not a prostitute, I'm a man, please, please... ...!

It was the sound of the good mood from drinking disappearing in an instant.

It was a sound that could barely be heard if you listened closely beyond the door, but Qing's hearing was beyond human, so how could he not help but hear it?

``What kind of bastard was this? Hmm.''

Come to think of it, it might not be a bad opportunity?

It's been a while since I've had a chance to taste some food. It wasn't the right time, but the time for cooperation and retribution has finally arrived.

Thinking about it like that makes my appetite come back.

Qing clenches his fist and flashes a sullen smile.
