\chapter{Be Sure to Maintain Your Dignity When Going Out (6)}

When people do something shameful, they naturally look around to see what others think and try to escape their gaze.

In that respect.

If we look at the circumstances under which certain conspirators hatch their sinister plots, we can see the honesty with which they perceive their conspiracy.

It was also common sense that most of the plots took place in tightly closed rooms and dark places due to the limited lighting in the central plains.

But a high (good) room in a high-class guest house.

All the windows that doubled as walls were wide open.

Everyone was sitting and lying down in a comfortable position, so when were they going to kill me? They have to kill me quickly. They want to finish it quickly and return.

This was a passage that allowed us to see the mindset and confidence of the conspirators as they embarked on their mission.

"They say gangsters will come out of the den tomorrow. This time, we'll take down our target."

Everyone's gaze was focused on him.

"What were you all looking at? Who would have thought a tiger would be so close? That incomparably cunning beast was just watching, lurking in the trees."

The person receiving the attention had a look of resentment.

This isn't an excuse, it's a face that comes out because I really don't think it's my fault.

First of all, the target's path was not identified.

In the first place, that gang of thugs was holed up in the mountains, so they were isolated and helpless, so it was impossible to know what kind of plots and schemes they were plotting inside.

Even so, I had only just managed to hear about this training or something the night before, and even that was only when I casually asked the porters carrying their food supplies, as if I had no interest in them, if there was anything interesting going on.

The worker didn't sell the information either.

Since I was just a worker, I had no way of knowing advanced information like their event schedule, so I just asked them about how busy they were and how their orders had dropped by a few days. When I asked them about it, they said they were all out training or something, and if they kept training, how would we make a living? That was all they complained about.

So, without any time to prepare, they quickly hid one person at a time along each descent route and waited for their target to appear.

Unfortunately, the target happened to pass by the path he was hiding on, and when he finally got the chance, the tiger got in his way.

Of course, the criminal may also feel wronged.

The tiger was just hiding all day, waiting for an opportunity to catch and eat it, so saying that a tiger suddenly appeared was an overreaction to the tiger.

It was the natural order of beasts to eat and be eaten, and it was not particularly unfair that he was killed by a monster with human-like strength.

However, it was too much that they just abandoned the tiger, saying that it was heavy and there was no time to sell it, even though it left its skin behind when it died.

anyway.

``This time, we have to handle it thoroughly.''

The middle-aged man emphasized in a serious tone.

It was exactly the kind of strict, dignified, and serious tone of speech that was expressed in the palace script of the Qing Dynasty.

"That, Youngban? But, would he come out? He'd know someone was after his life."

``Hmm.''

A middle-aged man groans at him.

If I had known they would come out this quickly, I should have prepared properly and dealt with them in one go instead of just stabbing them carelessly.

But since there was no information about the Walpaegul and the Uijeongmuhak Hall, how can we know if they were there the whole time or if they come out in the middle?

So when the opportunity came, what I was trying to do ended up going wrong.

"Still, I'm prepared just in case. You never know. That rascal might burst out without thinking, since he's never going to give up his drinking."

Not everyone seemed convinced, though.

"It wouldn't hurt to be prepared, would it? Hmm. Still, I doubt even the most thoughtless of people would come out and say they want to have fun right away..."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Finally, I'm going out! I've waited so long for this day! It's just a shame it's in the middle of nowhere. Ha, even if I had money, it's hard to spend it."

Even the most thoughtless of men, the nobleman of Sacheon, Wan Talu, spoke up immediately.

By the way, no one in the room asked me, but I was the only one saying this.

That means I'm looking forward to going out.

Then, one by one, a young man laughed and took his place on either side of Wan Talu.

``Hehehe, where in the world was there a city where there was no place to play, right?''

"Well, then, Confucius, you don't need to worry about that. And you said you stayed at Sopyeonggak when you took the entrance exam. You said it wasn't that bad, right?"

"Ha, you're so low-level. Sopyeonggak? Nosan Jeilru? Nosanhyeon, you're just a leader in some unheard-of, remote village. The food was barely edible, and the women aren't just ugly. If you go to the business district..."

And then he starts bragging about how splendid the night of business is, how magnificent the skyscrapers lining the lake are, and how beautiful the courtesans are, etc.

The office of the State Councilor's Office was a room for six people.

The remaining three, Bangjang Yangchil, Eomchang Lee Injo, Soeumjo, and Jangbihu, looked at the scene with expressions that said, 'That guy was acting like that again.'

The constant braggadocio of Wan Talu? The blatant assertion that I'm a master, a natural, a noble person? This was why this behavior has persisted until now.

While some people might frown upon such an attitude, others cling to it, hoping to gain something from it.

Roughly speaking, in the primitive, uncivilized statistical world of the Zhongyuan, if there were ten people, nine will frown and seven will cling.

If you add seven to nine out of ten, you get sixteen, so why was it called ten out of ten?

Well, six of them, both of them, will secretly feel bad about it, but from now on, they will laugh and try to please him.

"Hmm. Right, you, Team Leader. How about you? Team Leader, you've worked hard, so I thought I'd treat you to something hot while I'm at it. What do you think?"

``Hmm.''

The paint was slightly rough.

Until now, I had no idea if this guy was truly precious or if he was just a bluff that was always talked about in places like this (where you can't tell if it's true or not, so believe it or not).

But now that we're about to go out for real, wouldn't he say he'll take care of everything from the first night to the third morning, including eating, playing, drinking, and even involving a gisaeng?

Honestly, as a man, it was a condition that I cannot help but feel uncomfortable with.

But there was no such thing as free happiness in this world.

In other words, there was no such thing as a free lunch.

Looking at the two guys on either side of that dog's paw (which has now become his official nickname) who were eagerly licking it, this was a kind of warm invitation.

"Ahem. I appreciate your sincerity, but this time I plan to stay at the academy and train. I'm worried we're short on leaders, and even though I'd love to join you, I can't bring myself to do so."

It was a fairly gentle rejection.

Wan Talu was excited about it.

``Well, if you don’t like it, then don’t worry. Do whatever you want. What about you?''

After equipping him, Jangbi waves his hand.

Would it be a shame for the eldest son of the region's top sapa to be a womanizer again?

Rather, training was the priority, so after equipping the equipment, he planned to remain in the academy without requesting to go out.

And, saying that they could not fall behind their enemies, the Akmun Noise Unit also decided to stay.

"Well, even if I'm in a situation where I have nothing, I should at least try. Well, try your best. I need to relieve some of my stress now."

It was a truly beautiful Wan Talu story.

However, it was not the case that I refuse to go out because I don't want to drink with Wan Talu.

It's annoying, but that's all, and it's not something you should avoid at the risk of suffering losses.

The number of applicants for going out was not that many, at around one-third of the total.

In the first place, those who entered the Uijeongmuhakkan were passionate people with a purpose, whether it was martial arts or political sect.

Even if it was a three-day trip, wouldn't it be a schedule where you leave in the morning, arrive at Nosan County late in the afternoon, rest the next day, leave on the morning of the last day, and return late in the afternoon?

In that case, I think it would be better to practice.

Besides, what if I leave the room on my first outing and get labeled as someone who's lost their shit?

Or, as the instructor always does, there was also the aspect of being cautious because you might end up disappointed.

And above all.

As the number of trainees decreases, the time instructors and assistants spend caring for each individual naturally increases.

If I stay and practice during this time, I might be able to receive personal instruction, and on top of that, it would be a chance to get noticed as someone who works hard!

Yes, on the day of going out.

Those who had requested to go out rushed out after roll call, as if they were busy with something—it was only three hours to go down the mountain, so they had no choice but to be in a hurry—and the remaining officials gathered at the swordsmanship hall with burning passion.

"Wow! Such passion despite being rested. As a swordsman, you must already have a strong enough spirit!"

There was no sign of the disappointment specialist instructor, only Assistant Instructor Nan-gong and Assistant Instructor Geomokgun swinging wooden swords.

``Oh, Sword Friend, you mean Instructor Ximen? He went out.''

The remaining personnel should have first found out whether the instructor remained in the academy.

Well, it was a holiday to rest even if you stay during the outing period.

From a learner's perspective, they may want to learn and master as much as possible, but from a teacher's perspective, how was this any different from asking them to work even on holidays?

Do you volunteer to work even on holidays?

This was absolutely not sincerity.

It was evidence of a kind of mental abnormality or sick soul that should be expressed as madness or extreme insanity.

Of course, even then, there were still two assistants left.

Well, Nan-gong Shencai and Geomokgun were both madmen obsessed with training.

The other instructors were descending the mountain with light steps.

"Hehe, it's been a while since I've been out. Seriously, I searched all the restaurants."

Know that I'm going to eat everything.

I've lost Dugangju. I've lost Bopungju. I've lost Songharyangju. I've lost Ssanggyoju. I've really lost everything.

Know that tomorrow was the day when all the broads in Nosan County will be destroyed.

Although the school food was delicious, the ingredients and menu were limited.

Should we say that this was the limit of school meals?

Besides, of course, drinking was prohibited in the school.

What kind of disaster would it be if the instructor were drunk, smelled of alcohol, and injected drugs?

Of course, it may be said that it was a somewhat unfair measure for a government that would never take such a measure.

The footsteps of Qing, who was descending the mountain with Murong Zhuxi and Seol Iri on his left and right, could not help but be particularly cheerful.

Since there was no one in the group who was not an expert (based on the Zhongyuan standard), the descent was a breeze, and the group came down at a speed of just one and a half hours.

The destination was Sopyeonggak, the best inn, best restaurant, and best bar in Nosan County.

The first guest house in a small town with few tourists was like this, a trinity of all three, and as soon as you enter the majestic building, a stern face pops out to greet you.

``Are there six of you?''

"Yes. Let's see. Is there a seat at the top? If possible, toward the lake."

"Oh, of course. It's a rare place to be empty, but it seems to be empty today because the distinguished guest was eating there. Hehe, I'll take you this way."

If you were the best inn, you had the right to put the city's best landmark in your name.

The famous landmark of Nosan County was Sopyeong Lake, located to the west.

The highest point of the guesthouse, the one with a view of the lake, means that the guest was a very important guest, a big shot.

So, Jeomsoi's back bent and she couldn't help but let out a happy "Aigoo."

There were six people in the group.

Qing-gwa, Seol-i-ri, who was now naturally attached to Qing-i on his way, and even Sima Chun-feng, who was captured and kidnapped by Murong Ju-hee and Qing-i.

It was an amazing event with four of the six beauties of the Jeongpa martial arts world present.

And Pangdaesan Mountain.

He also suggested it to Peng Cho-ryeo, but he said that he was done for and should take his younger brother, and handed Peng Dae-san over to him.

And one more thing.

"Okay, okay, today Changbin has the top seat. Okay, here. This was Changbin's exclusive seat."

``Oh, that, I wish I could sit next to Pang Awoo.''

"Oh, what? You don't want to sit next to me right now? Or what? You don't want to sit next to Miss Seol? Which side? Just tell me."

``No, that’s not it. Well, there were more than just likes and dislikes in the world—''

"There's no such thing as gray in the world. Just pick a specific person. Do you like them or not? Well, if you really don't like them, there's nothing you can do. If you can't stand it because the drink tastes bad when you sit next to them, you have no choice but to change them. It's hard to sit next to someone you don't like. Then, sit next to the mountain. Then, who will sit next to you? Pick a specific person. Which of us would you rather not sit next to? Who do you hate the most?"

``This place was really nice……''

Bad member Changbin was on a thorny path again today.

So five people.

Actually, I gave them all the advice.

How could he not recommend it to someone with such a strong personality?

He even stopped by the governor and asked if he would like to come down for a drink this holiday. How lovely and special must the governor, Dagger Sword Master Yoo Seon-yeop, have felt seeing his sociable junior, who was about the age of his granddaughter.

Even if it's just words, how can they be so pretty when they come here to invite me? These days, even empty words were just empty words, so they whisper and hang out together secretly, afraid that I might actually come.

It was another moment for the old man killer to achieve his goal.

And the instructors of the two martial arts schools, Yuuk Ah Dojo and Jegal Ihyeon, stayed behind, saying they would do muscle training that they had been putting off during their vacation.

Qingdo readily agreed with him.

Well, there's nothing I can do about becoming a dancer. If I don't want to die, I have to train my body. What can I do?

Okay, let the banquet begin!
