\chapter{Be Sure to Maintain Your Dignity When Going Out (13)}

The Assassin's Ecology, Part 2.

I am not an assassin.

This was the type of person who cannot reveal himself openly and disguises himself as a commoner by covering himself with a blanket.

Someone who was pretending to run away or get caught up in the crowd and passed by Wan Talu suddenly pulled out a knife or an awl and ran out.

Because of that, Wan Talu was treated like a doll in the hands of a child, and was treated worse than that, so at least he could hold the doll's hand and swing it around.

``Ugh.''

Wan Talu, grabbed by the scruff of the neck, lets out a muffled cry and falls back.

There was an assassin there, his awl stretched out in the air.

As soon as our eyes met, he quietly, nonchalantly hid it with his sleeve.

Of course, just because I was calm, it didn't mean it became natural.

``Hehe, Nari, that’s not it-''

If not that, then what? After failing to stab our dog, how many creative excuses did you come up with to avoid the situation?

Qing was very curious.

But unfortunately, this was not the time to be excited about unexpected ideas while leisurely listening to excuses.

So what? I guess I should at least have some fun.

enN1WnIzcFhHMVJuR0JvdkNPc013L1VWWWZiYWRyRXRrakJ5cFpXbGJvcWZtVkhHSExjRTNkR2JSclY0Q1pJWg

"Arrest on the spot! No questions asked!"

Qing shouted firmly and extended his dagger (Samho).

The sunset-colored river draws a fan that vertically divides the world from bottom to top, and with a thud, the assassin's arm rolls across the ground.

The assassin's expression becomes blank as the weight of his arm suddenly becomes lighter, and he stares at the point below his elbow where it has disappeared.

``Ah!''

A scream that erupts a beat late.

It was the moment when I held the wound from which blood was oozing out with my remaining hand.

The reason why falling things have wings was because it was natural for what goes up to come down.

The blue dagger, still gleaming, once again draws a starlight trail across the world.

Again, with a thud, the left forearm fell and rolled on the floor next to the right forearm.

The assassin with half his arms cut off was at a loss and was swinging his short arms around, and, well, maybe his back was a little ticklish.

It was the moment when Qing grabbed Wan Talu's shoulder and pulled him up, urging him to move again.

The ecology of the assassin, three.

Civilized assassins, that is, the tool-using type.

Charuruk, this was one of the sounds that Qing hated, after the horn, it was the noise of the weights hanging from the net hitting each other.

A net that spreads out and flies in a refreshing way.

Qing immediately throws Wan Talu away.

Towards the net.

``Huh?''

A fully grown young man was caught in the net, so he was a very big fish among big fish.

The weights clanked and swung around, and in an instant, the wrapped Wan Talu fell to the ground with a thud.

Wisdom of life, what if the net flies?

It's good to throw someone nearby.

``Ah, what the heck, eek!''

Wan Talu, who was about to protest harshly, lets out a shrill scream as he sees a group of assassins descending on him while he was caught in a net.

Assassins falling, each clutching a weapon, the terrified expressions of their targets caught in the net.

In an instant, the target becomes a flesh-colored pillar, stretching out like a stick of candy.

And then, with a bang, the assassin's blade sinks into the hardened market floor.

It was the moment when the assassin was about to draw his sword.

A stinging, radiating pain down my side.

The assassin, looking down at the torso, doubts his eyes.

The wrist was deeply embedded in his side, its dazzlingly white flesh contrasting with the already spreading blood.

The assassin's gaze flicked upwards, and then he was met with the deadly beauty of a peerless beauty with a look of clear pleasure on her face. A serious ominous feeling spread through her entire body along with her sinister smile.

``Oh, no……''

``Okay.''

Crack! Qing vigorously pulls out the assassin's intestines. The red and blue entrails come out coolly like thick ropes.

Aaaah! The assassin lets out a terrible scream.

But to Qing, the world was just a sweet sound.

Qing, who had pulled out his intestines, stomped on the other assassin who was blankly watching this unrealistic sight, closing the distance.

Then, with the intestines in his hand, he circled the assassin's neck once, twice, three times.

Heuk, the assassin belatedly grabs his neck, but the raw intestines were more elastic than you might think and were incredibly tough.

Thanks to this, a dramatic embrace between two assassins entangled in their internal organs takes place.

``Dead!''

Several assassins rush in at this moment.

When Qing leads the assassin pack, isn't it a tragic situation of assassins stabbing assassins, or rather, a comical situation of pests catching pests?

Qing's arms swell.

The force of a thousand pounds pushing back one assassin plus another, the assassin who stabbed the assassin, the two assassins become entangled with each other and were crushed beneath them.

``Whoa! Whack! Whack! Whack!''

At that moment, an urgent scream rang in Qing's ears.

Oh dear, I turned my head and saw Wan Talu wrapped in a net, rolling left, then right, then right again to avoid the assassin's blade.

Qing lifted her knees high, and then bang!

It was the super-fast movement of the Samboilbaek Cheonma Gunrimbo, in which magic energy bounces up along with dust.

A terrifying speed that almost seemed to shatter space, leaving an illusion in its original place.

During flight, the blue's long legs fold.

The moment the heel was pulled close enough to touch that plump buttocks, it shoots out like an arrow released from a bow, drawing a delightful semicircle.

The sound of the legs cutting through the air was like a blade, or even more fierce than a blade, roaring.

Bam!!!

The blue foot was stuck in the assassin's pelvis!

A crushing blow, with such precision, that half of the pelvis was instantly shattered into small pieces of bone.

And with the remaining strength, he pushed the assassin forward, and the assassin, whose spine was bent to the side like the Chinese character for "廴", flew off into the distance.

Qing grabs the net and pulls it in to grab Wan Talu in a hurry.

Then, Wan Talu's body floats in the air.

Of course, on the other side, a masked man holding onto the net was looking at Qing with bewildered eyes.

``Kill him! Ignore the Heavenly Sword! Just kill him!''

At the sound of someone shouting, the remaining assassins rushed between the two at once.

As the Qing's net flashes, the area around Wan Talu's legs soars into the sky, and the wedge and blade pass under Wan Talu and graze the thigh of another assassin.

Soon, shouts of "Don't throw it, don't throw it" erupted along with harsh curses, and although it didn't seem to be from colleagues, the sound of something flying like a swoosh followed.

Qing lifts and lowers the net, pushing and pulling it.

If you lift it, it goes up, and if you lower it, it goes down.

When pushed, Wan Talu's buttocks will stretch downwards, and when pulled, they will stretch out again.

Up, down, sideways.

Various projectiles such as iron swords, daggers, short swords, and swords fly by in a chaotic manner.

``Whoa, woof, eww, uh!''

Even in the midst of all this, Wan Talu managed to dodge quite well by twisting his body and rebounding.

Meanwhile, some of them rush towards Qing.

But the saying that if you stay still, you'll get lost was true. A fly jumping into a blazing fire was probably safer than this.

Miss, I didn't mean to take your life.

But if it's urgent, there's nothing we can do, so what can we do but to die a comfortable death that doesn't suit our circumstances?

The blue elbow extends out like lightning.

A technique called the 'outdoor slam', where the elbow extends out as if to say 'don't do that' and digs into the assassin's ribs.

Then, the back of the hand, raised from the elbow, shattered the assassin's philtrum, sending pieces of yellow teeth flying out.

Nothing more than a spinning wrist.

With the help of the oil-type training, he swings his arm, grabbing the assassin's hair, and lightly turning it halfway.

How could an assassin with broken ribs and pierced internal organs hold out?

An assassin, dragged around helplessly, blocks the path of other assassins and those in the same industry, taking the blade in their stead.

``Whoa!!! Whoaaaaah!!!''

At that time, Wan Talu's scream was particularly urgent.

No, this kid doesn't talk, why does he just scream?

Of course, it's not that I don't understand, but when people get desperate, they don't speak and just raise their voices and scream.

When Qing turned his head, the assassin holding the net had suddenly drawn his dagger.

The assassin grabbed the Qing by the head, and the Wan Talu's neck was completely exposed.

Qing pushes the sole of Wan Talu's foot with all his might.

The 'with all your might' of the Qing was different from the 'with all your might' of the average person.

Wan Talu's body shot out like a steel bolt from a volley, its tip aimed at the assassin's chin.

``Ugh!''

A scream erupted from Wan Talu, who had been struck by the assassin's scepter like a ram banging on a gate.

Where would a scream erupt?

The assassin's forehead, which had been struck by the prince's crown, sunk about two inches, and he immediately rolled his eyes and collapsed.

Wan Talu was wrapped in nets and held up from above and below, so the support at his head disappeared and he fell into a very natural free fall.

Kong! The flat back of Wan Talu's head, perfect for pounding, makes a cute collision with the floor.

And then, jiik! It's dragged out, drawing a long tail on the ground.

Well, that's because Qing, who was holding onto the net on the bridge, started running aimlessly again.

``Catch him!'' ``Aim for the kid!''

Qing scratched her thin, white neck at the sound of blood clots rising here and there.

No, it wasn't a swarm of bugs, but where on earth were all these assassins hiding in this small city?

Like a damp mountainside rock being lifted, or like a midsummer scene with a bonfire lit in the middle of the night.

But, it was Qing who has temporarily put aside his immortal mindset.

There was no choice but to give appropriate punishment to those who rush towards me with the intention of dying.

Deeng! With the sudden sound of a bell, one of the assassin's shoulders explodes.

Blood, flesh, bone fragments flying everywhere, a severed arm falling to the floor, and then a knee being roughly struck, eliciting a desperate scream.

Starting with him, assassins, each expressing their individuality through their own unique costumes, rushed in from all directions.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

On the roof overlooking the author's commotion.

A group of men, their masks drawn down to their eyes, clatter across the rooftops, following the chaos below.

The man in the lead sticks out his tongue.

I thought that there was nothing I hadn't seen due to the nature of my job, but isn't this the true tragedy of a blind person?

He drags the targets wrapped in a net, sometimes dragging them to the air, sometimes picking them up and tucking them under his arm, and then swinging his sword at them as they leap into the air at the assassin's attack.

Then, he jumps up, grabs the target caught in the net, swings it around in a big way, hits the enemy with the sole of his foot, and then kicks off the ground again to advance. The subsequent movements were so natural that it seems as if they were coordinated in advance.

One of his subordinates sticks out his tongue.

"That woman has incredible strength. Did the Shinnyeomun martial arts have the ability to cultivate strength?"

"No way. Would a world-renowned beauty queen like you build strength? She'd probably be born with incredible strength and pour all her energy into it."

"Even so, Hiya, you're so murderous, aren't you? How can a woman be so vicious? What good was a world-class appearance if you're so vicious?"

The sunset-colored sword flashes three starlights at once, and its body splits into six or seven pieces, spilling out its contents.

On the other hand, it pulls out organs with its bare hands, tears off limbs alive when grabbed, and when it holds a weapon, its hands were vicious, causing blood to spurt out and create a bloody spurt.

Sometimes, when the time was right, he throws his weapon and pierces the enemy, and tears the enemy apart with his bare hands, taking the weapon and swinging it, throwing it, tearing it apart… …

The saying, "A Sea of Blood" was exactly like this, as blood flows everywhere you go.

"She's not only skilled in combat, but also cunning. Who would enjoy cutting people down? Yet, she deliberately and cruelly slaughters them. Isn't that the very essence of a military tactic, designed to instill fear in the enemy?"

The man looked at Qing with sunken eyes.

They chose such a vicious method, so it must be a ploy to deliberately tear off limbs and scatter internal organs to break the enemy's morale and fighting spirit.

Or maybe it means that he was the greatest murderer in the world who takes pleasure in tearing and killing people.

But that's not likely.

She was said to be a female sect member and a Taoist priestess, so she must have definitely received teachings on human life and such.

Look at that expression even now.

Grit your teeth, grit your teeth… …

The man's eyes were fixed on Qing's face, a beauty so magnificent that it could be considered the most beautiful in the world.

An angry expression with clenched teeth.

But for some reason, I got the feeling that the woman was desperately trying to hold back her laughter, as if she was forcing herself to create an atmosphere.

As expected, the corners of the mouth were moving in a twitching manner.

A frown formed between the man's eyebrows.

Did I see things differently? No, I don't think so. A woman claiming to be a member of a prestigious political party, surely not.