\chapter{Be Sure to Maintain Your Dignity When Going Out (10)}

Qing realized the man's true intentions.

You little shit, you're trying to kill yourself right now.

If it had been the previous Qing, he would have killed him in one blow and then hurriedly returned to Sopyeonggak.

Because I have to save the officials, my officials were my responsibility, they were the ones I have to protect.

But not anymore.

Because my friends were two rooms to the right of the room where the officials were playing with the women.

The officials' inaction was so poor that it can hardly be called inaction, but even so, when an attack comes, they draw their swords and fight.

If it were our kids, they would have looked into it, and since they were drunk enough to just give it to him, I guess they did a good job.

There were two climaxes and two climaxes, and there was no need to count the number of climaxes, but since Chun-bong was smart, he might be able to handle it from here on out.

I'm a bit hesitant to leave it to the kids, but they're clearly underage, so I guess they'll do it.

I'll do that much. Trust me, guys.

Of course, if a super-powered assassin unit were to come in like ghosts and cut off the heads of the officials, there would be nothing they could do, but then it would already be too late.

``So, you’re saying you have a colleague?''

"You're quite free. Do you have time to talk to me like this? That guy was yours, and the rest was irrelevant?"

The man chuckled. Qing shook her head.

"The instructors' dinner was in the room next door. I don't think there's any need to speculate on which side the funeral was held."

It's not the room next door, but the room next to it, but anyway.

The man's mocking expression suddenly changed.

It was a malicious lie.

"Well, I think we have a lot to talk about. If I had to say, I don't have much to say, but don't you think you have a lot?"

``Please spare my life, and I will tell you everything.''

``Huh.''

It was a very dramatic change in attitude from the man who had been forcibly laughing at the thought that other people would be okay in this situation because he was full of poison.

Even if you turned your palm over, it wouldn't be this dramatic, because after all, your palm was made of flesh, whether it's up or down.

"Cooperative attitude, that's good. Why did you target the Department of State Affairs?"

At first, I thought they were targeting this dog, but if that were the case, then there was no reason to attack the site where the poisoning attempt and world-class masterpiece were born.

Then maybe I was mistaken.

What if you were targeting the Department of State Affairs itself?

The incident where the Gaeppeuldagu guy was attacked wasn't because Gaeppeuldagu was Gaeppeuldagu, but because they were just targeting any guy who deserted from among the officials, and out of all people, there was one guy who ran away in a strange manner?

"I don't know. Here, here's a request form. Please take a look..."

The man fumbles around in his arms with his right hand, the only one of his limbs that was still intact.

And then, suddenly, he takes something out and stuffs it into his mouth.

"you!"

Qing, a beat late, slaps his wrist and kicks his forehead, knocking him down and holding onto his lower body.

Ugh, ugh, a man desperately clenches his jaw and holds on.

But Qing had no intention of taking a soft approach, so he said, "Crack, crack, crack!"

The man's upper and lower molars broke off, tearing and digging into his cheekbones.

The moment when the teeth break and fall out due to the terrible force pressing between the gums, and the lower jaw opens a gap on its own.

The blue fingers dug deep into the man's throat, tearing and tearing at the soft flesh.

``Keuk, ugh, ah, uh! Eok, uh!''

The man retches as the vomit surges in, ugh, ugh, finally the man's upper body bounces with a violent eruption, a great bounce.

Qing suddenly let go of both hands and opened the space.

And then the great backwash that followed.

Qing's expression as he looked at the sight was rotten.

Not only was it dirty, but the trickery was also extremely foul. Is this kid trying to trick you into drinking poison?

``Kuuuuu, this was it.''

It was not that it was not, but the tongue of the poisonous snake that spoke was swollen and purple.

It seems the poison I ate wasn't just any poison.

Still, the kind that makes you laugh out loud was probably the kind that works quickly and was painless. It also contains pain-killing ingredients.

Qing lightly steps on the area slightly above her dangling ankle.

As expected, there were no signs of pain that follow the touch, so it's just nice to look at.

On the one hand, it's cool.

You're drinking poison while using your brain?

And what kind of poison was this poisonous?

Are you trying to hide something? Or were you afraid of the consequences?

And above all, this was not right.

If he was caught trying to poison someone, he would have been tortured terribly, suffered terribly, and died a horrible death.

Do you dare to take it easy by drinking poison?

This isn't right.

Qing's eyes become poisonous.

But what can you do with someone who has been poisoned with a lot of anesthetic ingredients?

Then a great sense of helplessness came over Qing.

This was too much, really.

Is this how you become a villain? … … .

``Hehe, I’ll wait for you, Geoge. My daughter was definitely going to die, you damned Muggle bitch.''

Of course, the dying person may have different thoughts.

The man senses the end of his life and pours out curses filled with venom.

``Yes. Yes. Is that so? Ah…….''

But it bounced off.

Whether it's good or bad karma, or whether it's utilitarianism in principle or the idea of prioritizing the Chinese people and giving preferential treatment to the Zhongyuan people, does it feel like comfort after death was already guaranteed?

Why, when crossing the underworld, wouldn't a magnificent nuclear aircraft carrier come out to greet you?

``Hehehe, my dear Chae-hu, you’re going to be a nun. You’re going to be treated like a piece of shit, you little punk. You’re going to have to cut off your limbs and eat the damned thing. How long will you have to eat the damn thing until the day you die?''

There was no evil talk like this one.

It seems to be talking about the end of Lady Cheok, who was the concubine of the Yu family. It was an execution so gruesome that it was prohibited by national law.

Even if you become the emperor, it was a punishment that requires you to endure opposition from your subjects. What kind of emperor were you?

But thanks to that, Qing's mood begins to improve again.

I guess dying was a really unfair thing.

Is it something to be angry about if a dying person curses? Isn't it just him saying he's angry, or like they say in their hometown, "It's rude, but you're on fire."

Then, a bashful laugh burst out.

The man who saw that smile opened his eyes wide, but in the end, he couldn't even close his eyes and his pupils dilated.

What was so unfair that I can't even close my eyes?

Aren't I the one who's been wronged?

I did a good deed but there was no reward and I need to lose something to catch the bad guy.

Anyway, the dead guy has no business.

What Qing wants was a pleasant ergonomics with a living person, and touching a corpse was just dirty.

``Wan Talu? Just in case, I was wondering, do you know anything about the assassin’s identity?''

Then suddenly, Qing.

No, this kid was attacked by a real assassin and still came out, saying he was going out?

And after being attacked and coming out three days later saying it was good, he went so far as to play a role in which he forcibly took a woman who already had a partner because he was bored?

Is he a thinking man? Can we truly say that these were the actions of a man who knows how to think?

"Official. You requested leave even after being attacked by assassins? Do you, by any chance, wish to die? If so, I, the instructor, will allow you to leave without any trouble."

``Wh, what were you talking about!?''

It seems like it was a bit of a provocative scene for a child to see the polite speech coming out right away.

I don't know if I should call a young man who enjoys such situational drama a kid, but whatever.

``Let’s go back first. We need to go back quickly, so hmm, here we go.''

``I can go on my own two feet-''

"Wan Talu, Instructor Bon has two suggestions. One, hit and come. Two, just come. Instructor Bon prefers the first option."

``At least don’t carry me like a burden!''

It sounds like a burden and he doesn't want to go.

It seems to be the last pride of Wan Talu.

``Well, then there’s nothing I can do.''

Qing approached Wan Talu tentatively, grabbed his back, and with the other hand, placed his hand behind his knee and lifted him up.

In the hometown of Qing, it was called the princess hugging posture, which was a posture used to hold a precious person.

Then Wan Talu's face turned red-

``What the heck! Just carry me like a piece of luggage!''

``I do not give orders. I, the instructor, do not listen to anyone weaker than me.''

It was human nature to say that if you don't like something, you have to do it more.

Qing flies away.

Qing's footsteps as he returned to the main gate were more urgent than usual.

Of course, our members of the Half-Geom Ssangdohoe, plus Chunbongi, were trustworthy, but even so, since they will only react after the assassins have attacked the government office, it was inevitable that they will be a step late.

If by any chance there's a real expert among them, well, let's not think badly. It's a good idea.

You must have done everything yourself. You must have kept it well.

That was the kind of thing I wanted to think about.

What if someone got seriously hurt, or, as much as I hate to think about it, what if someone died?

Was it really the right decision to go after the assassin? Or was it just a rush, a chance to revel in the slaughter that had been a while coming?

So, Qing's lightness has no choice but to become faster and faster.

A master who could carry someone in his arms and move through the city at incredible speeds, like a whirlwind or a storm, was a huge nuisance.

Did you see that? Just now? I was like, what the heck? Something flew by so fast, was that a man inside the woman? What were you talking about? Wasn't that a woman inside the man?

What. This kind of thing.

Juru, who returned in such a hurry, tried to control his suddenly trembling heart and climbed up to the top floor in one breath.

"hmm……."

Qing let out a heavy groan.

I didn't want anyone to get hurt, and in fact, no one got hurt.

Because nothing happened.

Miss, I got hit, the raid was a piece of crap.

That was a lie as soon as he opened his mouth.

He asked to be saved, but then he drank poison and committed suicide.

My colleague said he would take care of the problem, but he lied again.

In this case, shouldn't we consider it right to target this bastard?

Still, if there was any consolation, it was the sturdy presence of the group seated on the other side while the officials sat respectfully on one side.

Even if assassins had invaded, they could have been stopped. As expected, the Half-Geom Double Sword Society was trustworthy! It was a time of reaffirmation.

As soon as Qing entered, the group jumped up and ran towards him.

They looked up and down to check if there were any injuries, and everyone seemed relieved to see that it was clean without a single drop of blood.

``Wan Talu, I need to talk to you for a moment.''

Now it was time to hear the truth about that dare, that dare to say, "Do you know who I am?"

For now, leave the officials in the room and tell them to not get drunk and just have fun since the situation isn't over yet.

Of course, it's not a dog's paw, and the attack was just the end of the war, so how can I let my guard down?

And among the academy instructors, Wan Talu stands proudly with his chest stretched out.

"Ah, yes. I've repeatedly warned you not to reveal anything, but given the circumstances, I can't help it."

I wonder if it wasn't the case that he tried to come out several times despite being told to do so.

``My name was Kang Dam-hyeon, and my father was Kang Cheom-ryang, the Minister of Justice!''

Qing counted. One, two. Now.

But there was no particular chorus.

They just looked at each other's faces and confirmed the rather serious expressions that came to their faces.

And only Qingman had that expression.

What? Who was Kang Cheom-ryang, and what does the Tongjeongsa do? Is he a high-ranking official?

What else was Tongjeongsa?

It's probably not a nickname, but since you said he's from the palace, he must be an official, right?

But was it a high position?

It seems like everyone knows except me.

Qing blinked his big eyes.