\chapter{Be Sure to Maintain Your Dignity When Going Out (15)}

Youngban's knees flash.

And then, as the soles of the feet hit the roof without mercy, the roof tiles shattered and a huge hole was created in the room.

It was a truly exemplary technique of the Thousand-Gun Chu, temporarily applying enormous force to the earth.

Yeong-ban's angry gaze, which had suddenly fallen into the house, scanned the inside.

Inside the house, which has a strong sense of life, there was a large hole in the wall through which people can pass, and the house next door was clearly visible.

Of course, the house next door also has an outer wall, so even if one side was open, you can't see inside. That means there's a hole in the house next door too.

Thanks to the sharp sense of the master, the characteristic sounds of people flocking to the house next door were picked up.

Youngban suddenly shouts.

``You b*tch! Where were you running off to!''

Yeong-ban shouts and steps on the ground.

Jin-gak was not just an act of stepping on the ground, but a descent that brings out power beyond one's own strength through the transfer of body weight.

Therefore, the outstanding Jin-gak was able to freely use the rebound force that tramples the earth to convert it into speed and power, and as if the body of the spirit was drawing a long tail, it escapes the village in one step at a terrifying speed.

And at the top, above the narrow beams of the ceiling.

One breathtaking beauty.

Wow, that kid was really fast. Qing was honestly a little impressed.

There must be some kind of divine technique I don't know about, some kind of lightness study that's unparalleled in the world. Of course, even so, it's slower than mine.

It's darkest under the lamp, and when searching a room, it's hard to find something hidden behind a door. And surprisingly, humans were creatures who don't look up when searching for something.

Moreover, Qing, who was a reserve fighter and a master of firefighting, decided to kill the sound.

Besides, on the other side, at the Qing entry point, there were still gold-blinded moths and assassins chasing after them, so of course there was no sign of life.

Originally, when you were upset and filled with anger, the middle process of thinking was completely cut off, so you suddenly react by thinking, "That kid was a bad kid, so I'm going to hit him."

Qing continues to hold her breath.

Not yet, not yet.

``Yeongban! It’s dangerous!''

Then one of them jumped down and escaped.

"Oh, Wiseman! Yeoltan as a member of the National Assembly! I will help Yeongban!" "Understood!"

After that, another guy jumps down and chases after my colleague.

It was a moment when the corners of Qing's mouth hung down so viciously that they touched his ears.

So, there's one left above?

By the time Youngban jumped over the wall three times and reached the house where Heavenly Blossom Sword had first jumped, assassins had already rushed in.

So the assassins stare blankly at the latecomers in the same industry. After all, what else could someone wearing black and a mask be but an assassin?

Only when Yeong-ban met that half-blinding, half-sad gaze did he realize something was wrong.

If the Heavenly Blossom Sword had escaped here, these scumbags wouldn't be able to stand by and watch so calmly.

So then? Where was the Cheonhwa Sword?

In an instant, a chill runs down Youngban's spine.

-Youngban! I'll help you! "Captain!"

His loyal subordinates call out to him and rush after him a beat later.

Yeongban turns around to check his subordinates, then sends out an urgent call and asks them to wake up.

-Oh, my lord, oh, my lord?

-I have given instructions to bring Jong Baek-ho to the hospital.

Aaaah, as soon as that sound ends, a desperate scream rings out from far away.

The problem was that it's a voice that feels somehow familiar.

``Damn it!''

The spirit rises up, gritting its teeth.

The front-facing rocket hits the roof, and with a loud explosion, the ceiling of the house was blown open.

In the sight of Yeong-ban, who had suddenly landed on the roof, the back of the figure quickly receded into the distance, and in his hearing, the terrifying scream of ``Keep going!''

Youngban hurriedly climbs over the roof.

Jong Baek-ho, still with his eyes rolled back and foaming at the mouth, but his pants were now soaked in crimson blood, and next to him was Oh Wi-sa, desperately clutching at the bleeding wound in his severed thigh and screaming.

Yeongban immediately takes off his mask and wraps it around O Wisa's thigh.

The rough treatment that reduced the circumference of the thigh by half made the scream of the shaman burst out again, but shouldn't the bleeding be stopped first?

Yeong-ban asks, wrapping his thighs tightly around her.

``Oh, my lord, where did the Heavenly Sword go?''

``Ugh, uhh!''

What comes back was an incomprehensible scream.

The moment Youngban raises his head in wonder.

``Huh.''

Yeongban takes a deep breath without realizing it.

The jawbone was torn off and hung dangling from the facial skin, and behind it, the tongue hung limp and dangled between the collarbones.

A horrific sight, beyond anything I could have ever imagined.

If you're going to rip the chin off, you should rip it all off, or just throw the lower jaw away, so the lower jaw, still attached to the skin, hangs by pulling the cheek and flips over, exposing the molars.

``Huh.'' ``Ugh.''

Two surprised sounds followed, the sounds of two subordinates running after their superior.

``This, this outrageous thing, how could you wear human skin and do something like this…!''

But it was still too early to be indignant.

Because there was another kind of noise that was heard in the ear.

-Beep, beep! Beep, beep!

A familiar whistle sounded, and it was an emergency call, a whistle signal to immediately stop all actions and assemble here.

Yeongban's expression becomes urgent.

This wicked woman stole my horn and was imitating it!

Calling together the leading group-

``We need to chase that woman right now-''

Yeong-ban was about to run out shouting like that, but he stopped when he heard a helpless groan.

This bitch, this woman, this fucking bitch was so wicked, why didn't they just kill her and leave her to suffer like this?

It was a tactic to leave the injured person alone so that someone else can take care of them.

If left alone, their lives would be in jeopardy. The witch was asking, "Are you going to abandon your companions? Leave them to die?"

Goosebumps run down Yeongban's spine.

That evil was evil, but isn't it actually a military strategy used in warfare, a sophisticated tactic to weaken the enemy's capabilities and morale by sending away sick prisoners?

You must not get caught up in this.

If we set aside a few people from our small crew to transport the wounded, we'd be playing along with that crazy woman's tricks. But.

Yeongban closed his eyes tightly.

``Seon Baekho was in charge of the two. Make sure they survive, do you understand?''

"insect!"

I couldn't bear to let my subordinate die.

Yeongban jumps up, gritting his teeth.

It was the teeth of the spirit who continued to suffer.

Qing didn't know, but there were levels to horns.

The purpose was to differentiate priorities through tone.

And the whistle that Jong Baek-ho blew was the whistle of Yeong-ban, the signal of the commander giving the highest priority order.

So, as the leader of the front line, Jang Cheon-ho had no choice but to follow the leader's signal.

At first it seemed like the rally signal was ringing, but after a while it stopped.

And after a while, the whistle's rallying signal began to sound again.

It seems like something has changed in the operation, the signal position was changing rapidly.

``Yeon Baek-ho, take the lead.''

The lead group, led by Yeon Baek-ho, the most skilled in light attack and tracking among the group, follows the signal.

The white tiger heads east.

The signal was moving from south to northeast, so I figured I could join them halfway if I continued straight east.

How far did he run following the rally signal?

-Stop, stop! Stop! It's a trap, it's the enemy!

The sound of someone screaming from over there.

In the lead group's view, the figure of Yeong-ban running towards them while screaming loudly was captured.

However, since it was impossible for a desperate cry from afar to reach everyone at once, was it a trap? An enemy?

That was the moment.

``Ugh!''

A wild scream erupted from the rear of the line.

Everyone's heads turned to see the gruesome sight of my colleague, Yang Baek-ho, being held captive by a strange man.

It was a sight where the abdomen was split open horizontally and the internal organs flow out.

``Wh, what!''

At that moment, the assailant throws the two white tigers.

Jang Baek-ho, who had been unconsciously accepting the attack with both arms outstretched, slipped out between the legs of the hidden villain, who was lying down, and swung his blade.

A scream erupts again, and Jang Baek-ho, who had been embracing Yang Baek-ho, collapses, clutching his own leg.

However, these were also elite soldiers who had been selected in their own way, so they quickly got into battle stance and flew around, the sound of their robes fluttering.

And, ttang ttang ttang!!!

The breathtaking sight of multiple swords being blocked by crossed wrists, amidst the loud sound of steel striking.

``Uh-huh!''

Even in the midst of the somewhat rough and rough sound, the tone was so outstanding that it was pleasing to the ears, and a strange shout resonates, and the woman spreads her arms.

Several swords springing up at once.

It was a shocking sight to see the strength of several men unable to handle one woman.

And at that moment, a vision suddenly descends on the woman's two wrists.

A bizarre illusion of a giant hand with five blades sprouting from the back of a woman's hand.

The shape of some indescribable hand, its long fingers reaching to a single foot, resembled human ones but did not, the claws of an eagle but did not, the sharp fangs of a beast but did not.

It was a twisted shape, but it was smooth without wrinkles, and its texture was like white jade. It was sharp and makes the heart flutter, but it was also a magic hand with a certain beauty that captures the gaze.

Although this was an article I have never seen before, anyone with knowledge of the Zhongyuan will immediately understand what this welcome is.

Magic ring number.

It was the essence of the world's most vicious resentment, the very form of that venom, wielded by a minority witch.

``Minority Witch!'' ``Why!''

Why did that damn witch suddenly appear?

It was an appearance that no one could have imagined.

The moment the witch stretched out her arms again-

``Hey, wait a minute! Stop, stop!''

Jang Cheon-ho urgently tries to dissuade the witch.

The Magical Circle was the image of the Magical Circle and the actual condensation of the existing strong energy.

Evidence that the minority witches had already reached the same level as the main and the main characters, and that they were too harsh opponents to face during a mission.

``Why, the minority witch, no, Mahou, were you interfering with the, um, main meeting?''

The act of calling a mine "Ma-gun" or "Ma-hu" instead of "Ma-in" was an expression of not wanting to fight.

It could be said that it was truly cunning to be a mine when killing and a demon lord when avoiding.

Anyone who sees the mine emitting a cool, strong aura right in front of their eyes will involuntarily let out a "Ma-gun Ma-hu" sound.

Underneath the hood that the witch had wrapped tightly around her, her blue eyes seemed to be watching someone.

It's about exploding with anger right away.

``No questions asked! It’s my circle!''

He tramples the ground while shouting.

It was a sudden rash that was completely incomprehensible.

Jang Cheon-ho immediately raises his sword, but the blade just towers in the air.

Because the minority witch was not looking at him, but at Yeon Baek-ho standing next to him.

Unfortunately, Yeon Baek-ho's martial arts skills were not as advanced as Jang Cheon-ho's.

The moment I blinked, something came into my eyes, stinging.

``Huh?''

Yeon Baekho lowers his head blankly.

A twisted illusion deeply embedded in my stomach.

And then, with a bang, something like a thick rope was pulled out. What was it? Is it my intestines? Is this a dream or reality?

``Hey girl!!! Thousand Flower Sword!!!''

At that moment, the angry voice of Yeongban awakens Yeon Baekho's spirit.

As I came to my senses, a sound surged up, a scream that came out on its own.

Yeon Baek-ho collapses, saying, ``Eww, save me!''

But the minority witch, as if she didn't care at all, lightly kicked the ground and flew away.

Then, a beautiful voice rings out in a loud noise.

-I'm not the Heavenly Blossom Sword! I'm the Minority Witch! I'm the Minority Witch! Because! I'm the Minority Witch!

And. A cry that strangely emphasizes the minority witch.