\chapter{Be Sure to Maintain Your Dignity When Going Out (11)}

The Tongjeongsa (司) was the department that managed the documents of the Zhongyuan imperial family, and the Tongjeongsa (使) was the official title referring to the head of this organization.

You might wonder if it was right for the document management director, and not even himself, but his son, to be so proud and proud.

However, the method of communication was either verbal or written.

In particular, the primitive ancient Zhongyuan did not have any means of long-distance communication, nor did they have the technology to transmit letters through personal machines.

Since the Emperor was only one person, his time was limited.

And the act of reading was much faster and more efficient than listening and understanding.

That is, most of the information coming in while observing the emperor's state affairs was in the form of written documents.

And the Tongjeongsa manages this document.

You can submit petitions you like, and discard petitions you don't like.

Even if you write a low-priced petition and submit it, you can manipulate information, so you have the ability to turn a traitor into a traitor overnight, and a traitor into a loyal subject for eternity!

On the other hand, since the imperial edict issued by the emperor was also a document, it was possible for it to be manipulated as it was the mouth that issued the emperor's words.

Of course, if you get caught like this, you'll die.

It was the destruction of three generations of families, of a whole family, where not only one person dies, but all their relatives were slaughtered.

However, the position of Tongjeongsa meant that the emperor could choose which information to take and which information to speak.

For that reason, this position, its power and prestige were very great.

In the Zhongyuan, bribes were not considered dirty money, but rather a legitimate side income earned through one's abilities. The fact that the Tongjeongsa was the highest-earning position in the palace shows his power...

This was Sima Chunfeng's explanation.

``Uh-huh.''

As the explanation progressed, Wan Talu's lips gradually turned up and his shoulders straightened.

Is this kid a Tongjeongsa?

I don't know if that river official manages the documents well, but at least my son seems to have been poorly managed.

Qing taps Wan Talu's head.

"Are you laughing? Thanks to you, I'm having a blast being an assassin. Don't you think so?"

``How dare some bastards do this to this body…''

``No one has any idea?''

``Hmph, a capable official usually has many enemies. There must be one or two who hold a grudge against their father.''

``The attitude of the officials was truly polite.''

Again, bang. Qing lightly smacks the back of the head. This kid has a pretty big head, and he's got a knack for hitting the back of the head.

Wan Talu's head jerks, then he stiffens his neck, glares, and turns on his twin flames.

"I'll say it again, once you've entered the Swordsmanship Academy, I don't care if you're the son of a Tongjeongsa or a Tongjeongsa father. You just have to stick to the basics, right?"

``What on earth make you so arrogant, you rascal.''

Pfft. Another hit to the back of the head.

When he sleeps, he always lies down straight and sleeps motionless like a corpse.

The back of the head was flat, so it's nicely pressed down, so, um, this feels good in the hand. It's not bad.

The look in Murong Zhuji's eyes as she looked at Qing with the corners of her lips slightly raised caused a slight earthquake, but fortunately or unfortunately, Qing did not notice.

"Arrogant? This was just a guess. It seems like the government was relying on Chief Chun, but was your father, who lives far away, using that document to stop the assassins here right now? Just retire him, whether he lives or dies, and let the government handle its own affairs. Do you understand that official duties were inviolable?"

"Ugh. This was what you mean by the thugs of the martial arts world. You try to solve everything with force, huh? The authorities turn a blind eye, so these mere thugs run wild, huh? Ugh."

"Use proper honorifics. And, then, those who sent assassins against you weren't officials, but martial artists? Assassins use money and power, not force. If you're going to kill, you should boldly reveal your name and act on your own. Wouldn't it be far more despicable to call an assassin from behind?"

``That’s…! Ugh.''

Wan Talu closed his mouth in anger.

To begin with, there was nothing more foolish than trying to deal with Qing with words. If you were to fight with that wicked tongue that can turn a person's internal organs over with just words, you would risk defeat in every battle.

"So, why did you come to the Legislative and Military Academy? Are you a spy, after all? It's a bit blatant for a spy, but you're trying to steal information about Meng?"

``That’s not it.''

Okay. Another slap on the back of the head.

"Hey, you want a man to be so petty and call me dayo dayo? If you're going to use honorifics, it'd be more manly and refreshing to use them clearly. You don't want to be hit and you don't want to use honorifics, so you're going to be vague? Either treat me like a man and continue to pay the price, or use honorifics neatly. Either way, you're either going to be neither here nor there, and that's more retarded, or you're going to be a jerk."

``Ahem. That’s not it.''

Wan Talu was a man who subtly showed his respect, perhaps because he didn't want to be a jerk.

If you look at it, it seems like it would be easy to handle.

At that time, Sima Chunfeng stepped in to organize things.

"Well. Now that things have come to this, there's no choice, was there? Prince Wan Talu, or rather, Prince Kang Dam-hyeon, must return home. His identity has already been revealed, so we can't continue to ignore it. If assassins continue to attack, the safety of the other officials will be seriously threatened. Therefore, we will skip the exit formalities. Prince, please head straight to Beijing."

It was a quick expulsion.

Of course, it was Sima Chunfeng who claimed to be the center of the school's operations, so it was natural that he had that much discretion.

"Huh. Do you think anyone wants to be here? Well done, this den of thugs, ugh."

"basic."

``It doesn’t matter anymore, it’s not even a government office!''

"Where the hell does that little brat keep using informal language? This was a warning from an adult, not an instructor. If you get caught doing this, you'll be in serious trouble."

And then, Qing, ahem.

"Well then, I'm planning on taking this guy to Beijing and back. Sima Lang, would it be alright if the instructor left for a moment?"

``Is it the Heavenly Sword itself?''

"If I die before I go to Beijing, won't it definitely be talked about later? That Tongjeongsa was a very high-ranking official, isn't he? I'd rather not give him even the slightest reason to blame me than have him harbor resentment over the loss of his child."

``If that’s the case, then it wouldn’t be a problem for the Heavenly Blossom Sword to visit, but for the ordinary people here.''

The corners of the group's eyes fluttered as they suddenly became ordinary people.

In a situation where there were two people who were considered the best in the martial arts world, and who would have broken the record for youngest peak if it weren't for Qing Man, following the treatment of commoners.

"Okay. If we just run all night, it won't take more than a few days. The teaching assistants were already capable of conducting the class. And if you assign Sword Friend, or Shencai, as temporary instructor, he'll teach you really well. Honestly, who else would be better at teaching than me?"

If Nan-gong Shencai had been there, he would have been deeply moved, saying, "As expected of Sword Friend!" But unfortunately, he was currently teaching at the academy, eagerly welcoming aspiring swordsmen who were requesting swordsmanship even on holidays.

Wan Talu's face turned pale at the sight.

You're going to run all night, right?

Because I am a Wan Talu who has already been a burden on the side and also been a girl who was quietly held in the arms.

Either way, from here to Beijing like that?

I'd rather risk being an assassin!

"No, it's fine. I can go alone. Sure, I won't go far, just stop by a small outpost on Pyeongjeongsan Mountain. Wouldn't I get a military escort? I'll take care of it."

Pfft. Another one.

"Yeah. You'll just open up and take a beating, right? That's manly and nice. But were you sure? Is that general close to your father? And you can guarantee he's not on the same side as the assassin?"

"that……"

Wan Talu trailed off.

Of course, I don't know. How much could a young man who was just playing around know about the politics of the palace?

"It seems like you don't understand your current situation. Wouldn't it be strange if an assassin burst in right now? Did you see him eat that thing all by himself?"

An anesthetic and a sedative that works so well were not usually rare items, and since he was trying to silence me by taking it, he must have some ulterior motive.

If I had to say, I could say he was a member of a prestigious assassin group.

That means there will be more of that guy's colleagues.

"You've already failed twice. If you go back to the academy like this, they'll think you'll just shut yourself away and never come out again. Actually, it's a bit absurd that you're still here after being attacked last time."

Qing shrugs.

"So what if you absolutely have to deal with it when you get out? You're going to go into this situation alone?"

"that……"

``It seems like you don’t understand the situation right now. Wouldn’t it be strange if the assassins all rushed in and said they’d kill you right now?''

It seems he's finally realizing the extent of his situation. Anxiety fills Wan Talu eyes.

``Well, then I’ll ask you to do that.''

And at that moment, from somewhere far away, a terrified voice said, "Fire."

``What was it? Where does the fire start?''

In that moment, everyone's expressions hardened.

A beat slower than the words, the spicy, burnt smell began to creep up my nose.

Knock knock, I hurriedly opened the door and saw the smoke seeping in, though it was still faint.

Oh, so that fire was here just now.

``Miss, they say words become seeds.''

Qing tapped the back of his head.

What kind of fire was this all of a sudden?

If the raiders thought it was their last chance, it wouldn't be strange if an attack came at any moment, just like the Qing said.

Qing quickly gives instructions.

The group all draw their weapons at once.

"No, no, those women with extreme temper might get involved. Young Lady Mo Yong, take care of the officials. The rest of you, help the inn guests evacuate. They might even attack civilians for destroying evidence, so everyone, stay on high alert."

Then Qing lifted the Wan Talu and placed it on his side.

Perhaps thinking that being a burden was better than being a girl, Wan Talu quietly put on his clothes with a look of resignation.

``What about you, my lady?''

"I'll be the bait, yelling, 'I'm here with this guy,' so when things were settled, come help me. Got it, everyone?"

Everyone nodded to him.

Then, suddenly, Sima Chunfeng said something.

"Wait a minute. Why were you giving orders as if the Heavenly Sword were a given? It's times like these that I see the wisdom of Sima Lang's heavenly wisdom—"

``Then Chunbongi, please take care of it. Then.''

``Wait a minute, Chunbong-''

Qing laughs and flies outside.

I always wanted to call Chun-bong "Chun-bong."

Yeah, this was the feeling, there's a massacre ahead.

This time, I will kill you, absolutely kill you.

Personally, I'm glad that they don't hide and come at us, and it's also good for the school.

They're the kind of guys who put poison in alcohol to catch a single person, and now they're even setting fire to a pavilion. If we leave them alone, they'll come up with something new.

However, wouldn't it be a good thing for the world if we tortured and killed such a vicious assassin?

So how can you not laugh?

I told my friends I would be bait, but wouldn't it be a good idea to attract their attention and gather them?

Bait can catch fish.

Qing leaps down the steps one at a time, but each step was a landing, and he taps Wan Talu's crown on the head.

``What was it?''

"What were you doing? You heard me. I'm trying to get attention. I have to shout that I'm here. I run, you shout. Or, do you want to switch?"

``Why that, no, haa.''

Wan Talu seemed to have lost his voice as he tried to protest something, or perhaps he had given up.

Then, the windpipe of the dog that was stuck in the side began to expand and swell.

and-

``Look-at-me-! Me- ah! Shit, why again!''

"Look, you shouldn't shout like that. What are they looking for in the first place? Shout out your name. Your name. Since the academy doesn't know your identity yet, you should shout out, 'Wan Talu. I am Wan Talu.' Where are you in Sichuan? Jianyang? 'I am Wan Talu of Jianyang'."

``……Jianyang. I am! Wan Talu! Jianyang, ugh!''

Wan Talu screamed.

That's right, if you squeeze the side of the blue tightly, the pain of a thousand pounds of terrifying force squeezing your waist was so great.

"Is that all you can shout? Even an earthworm passing in front of a guard or instructor would make a louder noise than that. You could almost hear the footsteps of an ant."

``What the hell were you talking about- Aah! I get it, ah, I get it!''

No matter how much you whine, you're just like a rat in a cage, or a dog stuck in your side.

Since your body was already trapped in a torture rack, you will have to obey unless you want to be separated into your upper and lower body.

Wan Talu's expression suddenly darkened as he understood this meaning.

And then, a loud and powerful cry.