\chapter{Be Sure to Maintain Your Dignity When Going Out (9)}

Everyone, who has never heard such a groundbreaking poem before, wonders if the poem I just heard was really a poem from the human world, and their expressions turn as if they were trying to distinguish reality.

It means that the expression on his face was one of bewilderment.

"Hey, Instructor? That kind of joke..."

"Put down your glass. It's quite poisonous. There, Mr. Gu, please return the wine to its bottle and gather the remaining glasses in one place. Keep the wine as evidence, and burn the remaining glasses, as they could be dangerous."

The poem seemed like a joke, but the instructions that followed were completely drained of oil and extremely plain.

The officials who saw that serious expression finally gulped, "Huh, was he really poisoned?"

Qing was about to run out in that state, but stopped.

But an attempted poisoning? Who were you targeting? Could it be you, the dog-eared bastard? Was his life truly threatened? The assassination during the march wasn't some empty excuse, a bluff, but a real event?

Moreover, since it was a precious drink, everyone should have a round of it, and it was a vicious plan to kill everyone in order to catch one.

If I leave this now, I might be in danger again.

``Wan Talu, was the assassin real?''

``How many times have I said it was real- huh.''

Wan Talu, who was about to vent his frustration, lets out a gasp.

It was the sound of someone being pulled by the back of their neck and held by their side like a piece of luggage.

And then Qing runs out of the room.

Not towards the hallway, but towards the open wall with a view of the lake.

``Eww-!''

A scream erupts from Wan Talu, who was suddenly thrown into a free fall.

Either way, Qing jumps from roof to roof, tak, tak, tak, tak.

The style of the pavilion in Jungwon was structured so that each floor had a skirt-like roof that became narrower as it went up, making it easy to escape in an emergency.

``-Ah! Aah-ah! Aah-ah!''

The Wan Talu, which sounded like a piece of luggage, felt its back tighten with each step it took.

The strange scream that comes out because of it.

Either way.

Qing, with a person on his side, slumped down in front of the guesthouse entrance, using his toes, knees, and one hand to do something cool.

Then, they try to escape by taking the quickest route and launch a re-attack into Sopyeonggak.

"Hey, Jeomsoi. Who was that guy selling liquor on the fifth floor? The guy selling Jagang, or rather, Jacheondugangju."

``What do you mean-''

"hurry."

Qing, the star of truth, twinkles.

The brilliance of the river was a cold, cold starlight, a threat that people instinctively feel when they see it.

"Oh my, Great Hero! I really don't know what you're talking about! This was the first time I've heard the name Jachundu Gangju in twenty years!"

``Ma’am, I thought it would be like this.''

Qing scratched the back of his head.

I don't think Jeomsoi really sold poison.

Well, his face, um.

Qing reflected a little.

I just thought of them as employees, I didn't see them as people, so I didn't really remember their faces.

Qing was trying to recall that face vaguely, as if he was half-remembering it.

``Put it down! What the heck! Am I a burden?''

Wan Talu shouted with a red face.

How embarrassing it would be to have a grown man (no, eighteen years old) writhing around on your side, not a child.

``The official was becoming rude again.''

``Knock them all out! Do you know who I am!?''

That was the moment,

A suspicious hat-wearing man sneaks out of the guesthouse under the gaze of the Qing.

Qing immediately raises his voice and calls out.

``Hey, wait a minute!''

Then, the sound of a footstep hitting the ground was heard!

The sound of doors being slammed one after another!

A hat that quickly disappears from its place.

``Stand there!''

Qing immediately follows and flies his body.

Wan Talu's back, which was screaming at him, also suddenly bent.

``I am Kang Tong-ak!''

It was the moment when the purification of Wan Talu, which was finally about to be revealed, was put on hold again, but I wasn't particularly curious or asked about it in the first place.

Rather, catch that kid.

People pass by in a chaotic manner on both sides of the blue sky.

``Hey, watch out!'' ``What, what was it!''

Sky blue eyes quickly scanned the area ahead, drawing a path through the gap.

Like a lightning bolt that breaks and extends with a powerful force, it runs between people, upwards, stepping on tables and hitting walls.

The back of the hat was rapidly approaching.

``Stop!''

If he had been told to stop, he wouldn't have run away. Ssatgat, who had identified his pursuer, dug into a narrow alley between the pavilions, or rather, a gap between the pavilions.

Qing immediately followed him.

The sun was low at sunset, and the shadows cast on the shaded alleyway quickly turn dark.

Qing's nerves were on edge.

A person who runs away from a crowded place was bound to cause a lot of trouble, so it was difficult to chase him.

But in these narrow, dark, and complex spaces, even one wrong turn can easily lead to losing the enemy.

On the other hand, you can hang around a corner or on top and hold your breath, and then attack by surprise.

If you slow down, you'll miss your enemies, and if you speed up, you run the risk of being surprised.

The man in the hat was hiding behind the corner, his sword raised high.

The sound of footsteps tapping on the ground was getting closer.

And when they finally reached the point, the true energy exploded from the man in the hat's dantian and raced through the blood vessels.

Now! The man in the hat brings down his sword.

Wedge! Just as both hands, gripping their swords tightly, fall to forehead level, a fearless woman suddenly leaps out from around the corner.

A perfect beat, as if they were in sync.

Or as if you were throwing yourself into a falling blade.

The woman's surprised expression.

A forearm that reflexively flashes up.

The corners of the man in the hat's mouth rise.

The sharp sword energy will slice through her arms and even cut off her torso. It will be a sufficient lesson for daring to follow the elders…

And, bang!

A sound that should not be made.

The man in the hat's eyes widen as if they were going to tear.

The weight suddenly lightened, the blade broken in half.

The man in the hat cannot understand the situation as the pain in his palm was throbbing.

Why does the blade, imbued with black energy, break when it collides with my bare arm?

Well, the arm of the minority magician was an indestructible arm.

It's not even a sword, it's just a sword energy, it can't even show the round transparent skin.

Qing immediately lets go of Wan Talu and slowly stretches out his arm in a strange manner.

It was an optical illusion, as if the arms were stretching and twisting like snakes, a cunning digging by the Muyeongsinsu.

And then, bang! He slaps the man's wrist.

A groan accompanied by a loud crash, the sword in half fell to the floor.

And from behind, there was a similar groan, like the groan of a Wan Talu being thrown down.

The moment the man grabbed my wrist, the blue-clad Muyeongsinsu who had struck me came out and quickly snatched my hat and took it off.

It was difficult to just recall, but seeing the face brought the memories back to me.

Yeah, this kid, this kid who sold alcohol.

The corners of Qing's mouth were torn apart.

A sinister smile that almost reaches your ears, a terrifying expression like that of a demon or evil spirit that you would fear seeing in your dreams.

Hey, this kid, was he a kid that can be killed?

Qing's other hand immediately grabs the man's wrist, the wrist opposite the one that was holding his.

And, Ajajak.

Sometimes there were sounds that can be heard through touch.

That special, oh, so sweet sound of bones crushing and breaking, bones breaking into tiny pieces and hitting each other.

``Ugh!''

The sound of a bursting scream adds to his hearing.

A double window that you can enjoy with your skin and ears.

Qing's wrist, which was trembling with the loss of its wick, was held high, still holding the lump of flesh.

The man raised his hand with superhuman strength, but even though Qing was tall, he was tall for a woman, so he couldn't lift her and her toes touched the ground.

Because the fact that both the torso and lower body were now completely exposed and empty was more important than the act of lifting itself.

The bridge of the blue draws a graceful curve.

A powerful kick that hits the opponent's calf with the shin.

A crisp, clean feeling of bones breaking.

The man's body, lifted by his wrists, soars like a hanging weight until it was almost level with the ground, then he was finally freed and floats in the air for a moment before collapsing.

Crushed wrists, broken shins.

After all, it's best to start from the outside and ruin each limb.

Because I can't run away or fight back.

``Ugh……''

"Hey, you can play with food. No? You dare poison my drink? I'll never forgive you."

Qing was whining.

If the man had been in his right mind, he might have felt wronged and asked if he was angry at that part, but he was in a state of shock and was struggling with excruciating pain he had never experienced before.

So that's what I was trying to say.

I can't get my head around this. What the heck? This guy?

Well, if you crush someone's wrist while they're still alive, it's hard for even an assassin, let alone an assassin's ancestor, to stay sane.

But Qing also knew an excellent first aid method that would bring him back to his senses in times like these.

Qing immediately places the sole of her foot gently on the man's intact ankle.

And then slowly, very slowly, apply force.

Ugh.

How on earth do I explain this bone-crushing sensation?

Whether you do it with your hands or the soles of your feet, this current seems to surge up from there, seeping straight into your spine, as if you suddenly have the urge to urinate.

Even when I wasn't in combat, I could concentrate and fully savor this sensation.

Haa, Qing, without realizing it, lets out a strange sound, a sound she's afraid others might hear, but-

``Ahhh!!''

A terrible scream that hides him.

"Are you coming to your senses? Let's see. Do you have one wrist left? If you become disabled, will you even think about talking?"

``Stop it! Stop it!''

See. As expected.

You come to your senses in one room.

"Wan Talu. Here you go. A familiar face, um, no."

Qing swallowed her words.

If it was a familiar face, I would have recognized it when I sold it to you. Since I didn't know you, I just accepted the poisoned drink.

"Okay, let's have a conversation. Who were you, and why were you after my official route?"

``You b*tch, you b*tch, do you know what you’re doing? Who dares to bother- AAAH!''

"Oh, I stepped on your toe. Sorry. No, don't make a joke out of stepping on your toe. I don't know, so I'm asking. Confucius said to ask if you don't know, and isn't it a virtue for those who know to tell you?"

``Foot! Foot! Aaak!''

You can't make a joke out of this.

Still, I thought we could communicate well.

If I had known this would happen, I would have brought Gae-pap-da-gwi with me instead. If I had left it behind, I would have enjoyed it slowly.

Only then does Qing remove the leg that was trampling on her crushed ankle.

``Ugh, ugh, ugh, what were you doing, why were you interrupting our event?''

"I'm an instructor at the Legislative and Military Academy, and instructors have a duty to uphold their own principles. Since you tried to kill me not once, but twice, if you don't know the full story, wouldn't it have been a third or fourth time?"

``Kuuu, keuuuu……. Ugh, gulp! Ouch, ugh! Ouch!''

The guy let out a sneer and then coughed roughly as if he heard a sound. As he coughed, he reflexively tried to cover his mouth with his hand, but the back of his hand, which was dangling, hit his wrist hard, causing him to cough and scream in excruciating pain. It was a total mess.

What the heck, were you an idiot?

At that sight, Qing let her guard down a little.

``What’s so funny?''

"It looks like we're all going to die trying to protect one guy. Ugh, I wonder if the guys in that guy's room were okay now?"

Qing's face, which had been showing a mischievous smile, suddenly turned cold, almost cold anger.