\chapter{Be Sure to Maintain Your Dignity When Going Out (17)}

The blood rushes to Yeong-ban's face like an evil spirit.

It was a sign that the bulging veins on his face would burst at any moment.

``Y-you-bitch-!''

What kind of minority witch was this?

A witch suddenly appeared at the point where the whistle stopped and harmed his subordinates? Even if it was a stretch, you had to have the sincerity to be a little bit of a stretch to even pretend to be suspicious.

Of course, it's absurd that the leading group, who don't know that Qing stole the flute, suddenly appears as a minority witch, but I just wonder how this could happen.

To Yeong-ban, who had been following Qing the whole time, it was just an imitation of a minority witch that didn't even eat a single grain of rice.

Moreover, Yeongban had to watch with his own eyes what his subordinates were being treated like, so it was only natural that his anger would reach its peak.

``I’ll kill you!!''

The spirit wave cuts through the men, scattering a harsh wind as it moves away.

``Youngban! You have to calm down!''

Following him, a rear guard member passes by a beat later, calling out for help.

A series of hordes left behind, the groans of the dying.

My guts, I have to pick them up and put them back in.

Save me, save me. Please help me.

Creak… … .

Two with their intestines out, one with his pants covered in blood and foaming at the mouth.

The expression of the leader of the front line, Jang Cheon-ho, was deeply stained with despair.

But I still had the judgment to the extent that I had to help Yeongban now.

"Jin Baek-ho, escort the injured. The rest will go to Yeong-ban."

However, Jang Cheon-ho, who gave the order, also has no idea what the situation is.

From the appearance of the minority witch who followed the sound of the household register, to the reason why the minority witch suddenly intervened, and why was Yeong-ban shouting the Heavenly Blossom Sword and chasing after the minority witch?

Above all, where was the goal going?

Wan Talu stomps his feet with all his might.

He wore a black outfit and a black cloth wrapped around his head, covering his hair. A mask was worn below his nose, revealing his eyes, which were covered in ash.

Anyone who saw it would see that he was a common assassin running away.

And since there were more than one or two assassins in this chaos, the civilians looked away with anxious eyes, pretending not to see them.

The assassins didn't pay much attention to their partner who was running off somewhere.

So, even Wan Talu, who was somewhat cautious at first, now rolls his feet and performs light attacks without hesitation.

Now that the threat of an attack has been overcome, I feel free enough to think about other things.

The rough hands of Heavenly Blossom Sword, who picked up the ashes from the brazier and rubbed them on his face, were a tough powder that covered his entire face with a rough ashes.

Thanks to that, my face still felt cold and hot.

"Okay, now change into these clothes and head to the inn. There were a lot of assassins out there, so if you pretend to be one, no one will find it suspicious. Now, go tell the kids—no, the instructors. I'll get out on my own, so you have to take care of the officials who came out."

‘… … Why, why were you doing this? Why didn’t you just hand me over?’

Taak! Wan Talu's head was thrown back.

It was a powerful blow that strained the back of the neck even though it was just a snap of the fingers.

Aaaah, Wan Talu clutches his forehead.

Qing clicks his tongue.

'This was a really funny kid. To be honest, I don't really like our dog poop.'

As he spoke, Qing's gaze seemed to glance upwards.

"I thought you were lucky. They let you off easy because you're eighteen and not even a statutory child yet. Hmm? Let's see. You didn't commit some mortal sin and were being chased, did you?"

Wan Talu jumped at that.

'How could that be! Ahem, I'm innocent... ... I haven't incurred such a great grudge that anyone would try to kill me.'

"You punk, I'm not sure about this. Anyway, this isn't it, right? Then I'll believe you."

'what?'

At that moment, Heavenly Blossom Sword smiles faintly.

A mischievous boy-like smile.

"I'm your instructor, and your guardian. It's only natural that you protect my path, right?"

'but-'

'That's it. And after experiencing the martial arts world for a while, I realized that someone with the ability to spread assassins everywhere like this has no reason to be wronged. You little punk, think you're lucky.'

I don't know how much an assassin costs, but to bring in this many would be more than enough gold to fill a cart.

It seems unlikely that anyone with the ability to raise such a sum of money would be treated so unfairly by a young, reckless young master whose karma was only somewhat high.

Moreover, from what I have seen so far, the Sichuan nobleman can be a funny bastard, a yellow bastard, and a rip-off bastard, but he was not yet a bastard.

Just look at that ridiculous situational comedy. Even if it's a taste that's forced, it's not forced, so there's still room for improvement.

"So, change quickly and hide under the bed. Even if they find out, they'll think you're a hidden assassin, so handle it yourself. I don't need to feed you that much, do I? Oh, my, groan."

Qing stands up, groaning for no reason.

It was evidence of mental aging, like the meaningless old man's actions and the constant mumbling of songs, but for a moment, Wan Talu's expression became blank.

Because I finally noticed Qing's face covered in blood after hearing his groaning.

The clothes had lost their original color in a single corner, and looked as if they had been soaked in blood.

And Qing had a bad habit of just taking weak attacks with his body and hitting them, so if he was strong, there was no need to go out of his way to dodge them.

To someone who didn't know, it looked like a rag, and there was even a needle sticking out of his chest.

'There, there.'

'Oh, it felt a bit tingly.'

'Hey, were you okay?'

'It's not a million years before I'm worried.'

'Don't underestimate it! Poison-'

"If there was poison, I would have noticed it by now. And I'm worried about the government."

The Heavenly Blossom Sword then broke through the wall and flew over to the house next door.

Wan Talu ran straight out onto the street.

The Cheonhwa Sword was hiding and told to come out, but seeing the instructor in that state, it was impossible for him to remain hidden peacefully.

How could a woman, who would cry and act so sensitively at even the slightest scratch, hide for the sake of her own body while her entire uniform was soaked in blood and her instructor told her to take care of herself?

Wan Talu ran straight towards the main gate, thinking that the other instructors would be there and that he should quickly seek help from the Heavenly Sword.

Actually, that Heavenly Blossom Sword was really exciting.

"Oh my, townspeople! An assassin was catching a witch! An assassin was catching a witch! Where can a witch live when she's so sad?"

Qing was running around.

Behind me, angry shouts resonate.

``Stand there! If you don’t stop now, I’ll kill you!''

It wasn't like Youngban was really expecting an answer.

It's just a reflexive cry that comes out when a person's anger reaches the top of their head, or in technical terms, when they get pissed off.

Qing responds to him with a question.

``Ah! If I stop now, will you spare me!?''

``You bitch!! I’ll kill you!!''

``No! If you’re going to kill me even if you stop, why stop? Wow, you really were doing a dirty job!''

``Shut up! Stand there, stand there! Thousand-Hwa-Geo-Eom!''

``I’m not the Heavenly Sword! I’m that famous witch! How can I be called the Heavenly Sword?''

``Shut up! Who were you trying to insult?''

``Is there anyone else chasing you besides you? You, you, you!''

``I’ll kill you!!''

``Oh my! That old punk was always talking informally! Hey, how old were you! You punk with no brains! That old punk has no manners!''

``Kuaaaah!!''

Yeongban's eyes suddenly roll back.

This was the ultimate formless poison, the terrifying poison that seeped into the human mind.

``Just because I killed a few assassins, a few bugs, and now a master assassin was chasing me! You little bastard! Ah, assassins were the kind of guys who'll stab their own mother if you give them money! Hey! How much was it? How much was it? I'll buy your mother's life! Let's see, three pennies would do!''

``You bitch, how dare you!''

``Are you ignoring three pennies? For three pennies, you can get dumplings and soup! Oh, do you have any change left?''

``Eww!!''

Yeongban let out a scream and increased his speed to chase after the minority witch(?).

The lower body was already moving at a speed exceeding its limit, and more energy was flowing out through the Yongcheon point, so the energy pulse was hurting and gradually getting damaged.

It was a pain that Yeong-ban couldn't feel, as all he could see was the back of the Cheonhwa Sword.

The back of the Cheonhwa Sword gradually gets closer.

One sheet of distance, half sheet of half.

Two, one, finally, Yeongban raised his sword and said, "Whack!"

In that moment, the ground beneath Heavenly Blossom Sword's feet explodes.

The back of the Cheonhwa Sword suddenly widened the distance in an instant.

Buung Yeong-ban's sword cuts through the air.

Then, a mockery reached Yeongban's ears.

``Wow! I almost lost! What a shame! What a shame!''

``Eww! Die! Die!''

"Miss, could you please be a little more polite? Then I might hold my breath and die!"

``Kwaaak!''

``Okay! I get it! I’ll hold my breath and die. Huff! Huff! Huff! Huff! Huff! Sorry! This won’t do!''

If someone heard me say that, they might say I was really excited, but I really was.

Wow, I can't even see it, but I can feel the anger, it's burning brightly behind my back, wow, I made that kid angry! I can control that kid's emotions!

``Kwaaaaak!!''

Youngban's hand flashes.

Like a Western god who sprays lightning, his arms stretch far behind his head, and he sprays the sharp blade with all his might, filled with fury and with fierce speed.

The blade, imbued with a powerful energy, rushed towards Qing's back in a straight line like light -

Thud.

A blue arm bent at an odd angle catches the blade flying towards my back.

It was an amazing feat.

How can a person's shoulder be turned like that, and how can an elbow be bent so far beyond the limits of its joints that it can grab a sharp blade?

How can you catch that fast throwing sword when you don't even have eyes on your back?

But it was possible to do so.

The joints were creaking with the oil-flowing movement, and the atmosphere read with the awakening technique was not wide, but there were no blind spots.

Moreover, the sword of a master has power when in the master's hand, but once it was out, it was just a projectile thrown with all its might.

Above all, it was a Qingdo master.

That was when.

Suddenly, Youngban's face turns pale.

Of course, even though Qing could sense the back of the head, he couldn't tell what it looked like since he didn't have eyes on the back of the head.

Qing, who was unaware of Youngban's condition, continues to provoke.

"What the heck! It's cheap! Use a good sword! Hey, you beggar! How can you call this a sword!"

``Go, how dare you! Hand it over right now! Do you know what kind of sword that is!''

``What kind of sword was this! It’s obviously cheap!''

``You, you! You!''

Yeong-ban's eyes turn bright red.

Qing tilted her head.

What the heck? Why did it suddenly get scratched so badly? Is that a sword you treasured so much? Or some kind of heirloom?

Qing's eyes flash.

The reason doesn't matter. What matters was that you've found the trigger.

``Look at this! It just snaps!''

Qing raises both arms, grabs the handle and blade, and folds it in half.

It seems that the sword was a sword because it holds on quite tenaciously until the handle and blade become level, but originally, it was not a master but a sewer who could break the sword, no, even a sewer was not needed.

Wouldn't it be possible for a strong man to break a sword blade without learning martial arts?

To begin with, the blade was weak against bending force, so if you bend it by applying weight, even a famous swordsman, let alone a famous swordsman, would not be able to withstand it.

Youngban was terrified.

``Stop it now! You bitch! Do you know what that sword is?''

"I don't know!"

As Qing applied more force, the handle and blade became closer than horizontal, almost touching each other, and formed a precarious shape that looked as if it would break at any moment.

At that, Yeongban shouted.

``Stop it!! You insolent bitch, that was a heavenly grace bestowed upon you by the Emperor-''

At that moment, crack. The blade snaps in half.

Aah! A shrill scream came from behind.

And at that same moment, Qing thought.

Huh.

Emperor? Emperor?

As Qing ran without stopping, he glanced at the two pieces of sword he held in each hand.

Oh dear, this was a disaster.

Please tell me a little sooner… … .
