\chapter{Be Sure to Maintain Your Dignity When Going Out (2)}

There is a story that I heard over and over again during my time in the military.

Military strength comes from the soles of the feet, and marching can be said to be the flower of training.

``Aren’t we going to do something like a march?''

Of course, the Qing did not have such firm values and the military policy of his homeland, which was to prioritize the march.

As always, I just don't have any thoughts.

It was just a random chatter that came up for no reason while eating.

"Oh, Heavenly Blossom Sword. A march? Isn't this a military base? After all, such training is meant to ensure the group operates efficiently under control. We're simply teaching aspiring sect members who dream of becoming a sect leader?"

``Hmm. Is that so?''

"You absolutely must do this!" It wasn't a claim, but rather a thoughtless remark, so Qingdo immediately agreed.

But it wasn't Sima Chunfeng.

Although I'm a little suspicious these days, isn't he Heavenly Blossom Sword, the one and only swordsman in the world who is skilled in both civil and martial arts?

There must be some reason for making such a claim, and it must not have been something that was just thrown out there without any thought.

It was the evil of overestimation.

"Huh, Heavenly Blossom Sword. Since you've mentioned it, let's share some more insights. We're the academy, so we call it Haengdo. What advantages do you propose for Haengdo training?"

"Huh? Hmm. Well, first of all, fostering camaraderie? There's no easier way to become close than through memories of overcoming difficult times together, right? And then there are times in life when you have to rush like that. Above all, it's good to do it at least once..."

Qing roughly took out whatever came to mind.

And when Sima Chunfeng heard it, it wasn't bad, was it? No, it's okay. No, it's actually good.

Sima Chunfeng was delighted.

"Heavenly Blossom Sword, could you elaborate? If that's true, it sounds like this would be a training I'd really like to try."

Distance? Can't you just walk a thousand li?

Is it taking too much time?

Hey, if you don't have time, you can just skip sleep. What if a person is tired from not sleeping for a few days? You can leave in the morning, eat breakfast, lunch, dinner, and late-night snacks, and then eat breakfast, lunch, dinner, and late-night snacks at the school building.

Yeah. Yeah. 3 days and 1 night.

Ah. Well, that's true.

It's too much for a third-rate person, but too easy for a first-rate person.

Well, well, let's divide it.

As a result, the pilot training for the Haengdo Islands was decided!

Let's try it once, and if it works as Qing said, we'll apply it to the next batch of officials next year.

In other words, Ximencheong has once again poisoned the martial arts world!

And then the real work of the military officers in the academic office began.

How can it be easy for more than a hundred drones to move at the same time?

Seeking various cooperation (bribes) from government officials.

I also need to look at the road.

Preventing various incidents that may occur.

Yes, on the day of training!

As Qing looked at the officials in their military uniforms from the platform of the Great Demonstration Hall, there was no other sight that was truly magnificent.

However, there is one thing that is a bit disappointing.

Well, the military inspection is the highlight of the march.

However, the officials are voluntary entrants and are also very enthusiastic, or rather, now that all three subjects are being run for safety, their enthusiasm has somewhat diminished and has come down to a level of enthusiasm.

In any case, unlike the military, these are officials who do not have the mindset of seeking comfort for their own safety.

Moreover, would those who dream of the grand goal of the State Affairs Academy, of sucking honey from within the fences of political factions, resort to mere tricks to lighten the load?

Besides, most of the luggage was prepared by the school.

Two water canteens, enough food for ten meals. Dishes and utensils for each person.

Weapons and spare weapons (the only advantage a martial artist without weapons had)

A sleeping bag, two blankets, a spare change of uniform, and a towel.

The training progressed like this.

Ten people form a group.

The number of people is adjusted according to each subject, but for now, one group is about ten people.

And each group returns to the Legislative Assembly Hall after reaching seven return points.

There are points added based on the order in which you arrive, but points are deducted if you are late, so you must return by the evening of the third day.

Ultimately, it ended up being a march to Dokdo at a commander training center, not a group march as Qing had mentioned.

Anyway, since Qing wouldn't have known about such a commander's lesson, if he just kept walking while carrying his luggage, it would be a march.

And above all, there is 'cargo'.

Each group is provided with a certain amount of sandbags and cargo, taking into account its level and weight class.

If this cargo is difficult, you can throw it away.

However, after the march, each group will be assessed for losses and points will be deducted.

These are officials who aim for promotion through high grades in the State Affairs and Military Academy.

So, the officers who were inspecting the battlefield were also filled with a sense of ambition, and their ambition was to be the first to return and receive a great score.

``Now, before training, the Lord has something to say!''

The atmosphere suddenly became cold.

In the dim dawn, the sky suddenly became quiet, and only the birds that came out to eat the early morning insects chirped.

The Dean of the Department of Political Science and Technology, Dagger Sword Commander Yoo Seon-yeop, walks out confidently.

It felt like someone wearing a pitch-black mask was playing some kind of ominous background music.

In that silence, Yoo Seon-yeop opened his mouth.

-You guys at the inauguration ceremony seem like yesterday, but already ten and two days have passed. I wonder if this is the transience of time. However, in the past, as in the case of Gwalmoksanggan (Gwalmoksangdae), Yeomong said, a man should change so much that when he meets again after three days of separation, he must rub his eyes and look at them again. As I, the governor, look at you Gwando, a gentle weight has already taken over your prayers, and a pure light has come into your eyes. I can only be amazed. I congratulate you on your achievements and am proud of you.

Wow!! Thank you!

-Okay, so I just want to ask you three things.

Wow… … .

The officials' eyes went dark.

Where on earth do you keep picking up and pulling out three things? And I have a foreboding, almost ominous feeling that, even though it's only three, it'll end up being four.

As it turned out, the premonition came true.

The officers were already mentally exhausted before they even started marching, so it could be said that this was a harsh treatment that added more difficulty to the training that was close to three days and one night of self-denial.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The first day of the march.

The footsteps of the officials are light.

A fifty pound load on one's back is not a light weight.

However, the physical abilities of the people of the Zhongyuan are completely different from those of the civilized people of the Qing Dynasty.

Isn't it common for most civilized people to hang on to something and support their own weight for less than half a second before falling?

Just hanging on is like this, so trying to climb up while hanging on under your own weight is a very harsh challenge that only one in ten people will succeed at.

However, if you are a middle-aged person with no physical defects, you can easily hold on to this angle by holding on to your own weight, and if you are bored, you can climb walls and cliffs, so you could say that your basic strength is different.

Even the scholars who only read Baekseo-saeng's writings enjoy intense hobbies like martial arts and horseback riding when they are bored.

If the common people are like this, even if they are only third-rate, they are historical warriors who use their strength.

So, this is about it.

Rather, it is about moving forward steadily, with a relatively busy pace from the beginning, in order to rank.

Qing was assigned to escort the first group of swordsmen as a security guard.

I don't think there will be any unpleasant incidents, since the land of Hanam is like the front yard of the Wulin Alliance with ten strong warriors.

Still, they didn't know, so they mobilized instructors, assistant instructors, and even school soldiers to take charge of escorting and monitoring, one person per group.

It serves as both an escort and surveillance, and a surveillance role.

No distractions during the march.

Since three days' worth of food was provided, any actions such as stopping at a village to eat during the march were also prohibited.

In fact, if you walk a thousand miles in three days, you will have to walk all night, so there is no time to do anything else.

furthermore.

``You were attacked by Madou, and one of you was seriously injured and is unconscious.''

"yes?"

"You decide who's injured. It'd be best to take turns. However, any unconscious patients must be transported on a stretcher."

Just carrying a pack and walking for three days without sleeping is something that any martial artist wouldn't be able to do.

One injured, unconscious, requires escort.

It was a situation given at the first return point.

Of course, an unconscious patient cannot lift any load, so in addition to the stretcher, the patient's load must also be shared.

It was only then that the officials' expressions became clouded, and it was only then that they realized that this training would not be easy.

``Good. Let’s just say I was injured.''

The nobleman of Sacheon, Wan Talu, steps forward.

It was a declaration that I would be carried out on a stretcher.

The atmosphere in the room becomes cold because it was not something that should have come out of my mouth.

A skinny guy can also have a thick face.

It was a time when Qing was once again impressed by Wan Taluian.

Jo Jang Yang-chil quickly steps in to mediate.

"If you think about it, it's not such a difficult situation, is it? We can all take turns getting some rest. For now, let's have Man So-hyeop take the role of the patient first—"

"What a bother. I'll just play the patient for the rest of my days. Well, isn't that a bad deal for you guys? We have an instructor, so I should show my hard work while getting some recognition. Hehe. I have nothing and I'm in a position where I feel like I should at least try hard."

I'm saying I have no regrets.

At that moment, from somewhere, a crackling sound of flames rising up.

``This little bastard was so upset and fell asleep.''

``What, what, what did you just say?''

"Why did you call him a piece of shit? The more I look at him, the more I see that he's a real rascal. A rascal needs to be beaten to get better. Wait a minute, let him go, let him go."

When the female protagonist, Chang Yo-hong, complains of anger management issues, suddenly starts to act out, the crew rushes in and tries to stop her.

I think if there hadn't been a blue light in the room, there would have been a huge fight.

``I think this instructor is a non-existent person.''

Actually, I feel a little sorry for Qing.

It might be fun to just watch the guy get beaten up without stopping him.

But, I was watching Qing's expression carefully and ended up hesitating and passing it over, so, um, it's a shame.

But the atmosphere is awkward, and that Wan Taluian guy is not ordinary and shameless, so I think that eventually, the time will come when it will explode.

And the explosion came sooner than expected.

The first evening, it was an early summer afternoon, the sun still shining brightly.

``Hey. It’s a dog. Get out of the way.''

``What? Are you talking to me?''

"If we assume it takes about thirty to get back, it'll be about three. Everyone's lying down, so get out of the way."

``You lowly bitch. Do you know who I am?''

``Ha! Who are you? Can you do anything?''

"Hmph. You're a person of such high status that I can't even imagine something like that. In fact, I should be grateful that you even bothered to talk to me like this— oh, what are you doing!"

It was Wan Talu who was thrown overboard after Changyohong overturned the stretcher.

Then he suddenly gets up, points his finger, and raises his voice.

``This, this lowly bitch, how dare you, you don’t even know your place- um.''

Wan Taluian pauses.

Well, that's because Changyohong was burning.

It's not a metaphor, but a real fire spreading through his entire body, and especially in his eyes, a deep blue flame is burning brightly.

``Eight, you can’t communicate with my lowly things, damn it!''

Then he turns around and walks off somewhere by himself.

But somehow, with the creaking and awkward gait of the joints, everyone had the same thought in their heads.

That kid is scared.

Then Chang Yo-hong said one more thing.

``Hey, you.''

The two men flinched at that.

One was a Wan Taluian who had been escaping, and the other was a member of the crew who had been pointed out.

``Are you a third-rate person? You look tired. Why don’t you lie down for me?''

``Oh, Miss Chang? Thank you for your kind words, but I’m still fine.''

"Who told you to lie down and be thankful? Don't waste your energy and drag your feet. You should lie down when you're less tired to recover faster. Don't you know that lying down after it's spread will only make it spread further? Don't you want to lie down quickly?"

``Okay, I’ll lie down.''

A third-rate crew member lay down on the stretcher with a somewhat subtle expression on his face.

What should I say, a rough kindness?

It's not that I'm happy that you're paying attention, but it's not that I'm not grateful either.

But, one thing is certain, it's a bit scary...

That's because it's what the blazing flame mine says, pouring blue flames from its eyes.

``But you little shit, where did you run off to?''

"Oh, Miss Chang. Calm down. Since things have come to this, wouldn't it be better to have dinner and then go, even if it's a little early? Regardless of his attitude, he's someone who wants to stick with the school. He'll be back soon, won't he?"

``Tch. I’m going to take care of that kid someday, really.''

The flames of Changyohong slowly die down.

It was at that very moment that the crew members each breathed a sigh of relief and felt at ease.

-Eww!!!

The sound of that dog's scream echoes out in a desperate manner.