\chapter{Be Sure to Maintain Your Dignity When Going Out (3)}

A scream of utmost urgency.

To Qing, who had mastered the screams of the evil spirits, it sounded like a real cry of urgency, not a sound made by someone falling or hitting something.

A scream that I let out without even realizing it, because I couldn't even bring myself to say the words, "Please save me."

In an instant, Qing's head spins around.

A raid? Or a grudge? He seems like a guy who's always been a stickler for grudges.

How dangerous was it? If it's enough to make you scream, it's probably not dangerous. If you were attacked by a truly dangerous one, you'd probably die before you could even scream, or your scream would have been cut off midway.

Have you ever run into a hidden Madou?

Or was it because of a grudge from before you entered? No, we know when you'll be coming out for training at our academy and where you'll be coming from, so we wait here.

Or maybe a wild animal, a tiger or a bear.

It might not be that dangerous of a situation.

A conclusion reached before even taking a breath.

It was intelligence that improved rapidly only at times like this.

``Yangchil, Wangpil, Seondu, Changyohong, Humi, drop your luggage and follow us while maintaining your formation!''

With a concise command, Qing immediately jumps up and runs out.

Boom! The sound of the ground being trampled.

For a moment, the ground shook and there was a rustling sound of leaves.

The front was blocked by trees, and the blue sees the line of progress and throws itself at it.

Tree trunks swaying sharply from side to side.

It was a process of running down a mountain, stepping on the ground, rocks, and trees, tilting them sideways, and drawing a lightning-fast line.

And at the end of it-

Grrr… … !

A giant flying beast, a tiger with a yellow body and black stripes clearly engraved on it!

``Eww!''

``This! How dare you cross my path!''

Qing's right leg was stretched out.

Left leg folded and level with right leg.

A human high-pressure kick fired at the speed of a typhoon slams into the tiger's side.

Wake up! With a shrill scream, as if he were about to repent, the tiger's massive body was thrown to the ground, rolling around.

People in Qing's hometown don't know this, but tigers were bigger than you can imagine.

The tiger's head was as big as the torso of a healthy adult, and it was a giant monster with one front leg as big as an adult's head.

If such a monster were to stare at you head-on, even a martial arts man, not a martial arts person, would scream involuntarily.

Daeho lowers his head and stares quietly.

A menacing aura that makes you want to jump in at any moment.

-Grrr… …!

``What were you looking at?''

Of course, this was the case for most martial artists.

To the unmanned being who had reached harmony, a cat was just a cat, even a tiger was just a slightly bigger cat.

What the heck, what can I do if I mess up?

The tiger held its breath and glared at Qing.

There was a wildness in wild beasts that allows them to quickly tell whether their opponent was afraid or not.

Some say that we instinctively recognize signs that a living thing was tense, such as olfactory stimuli or a stiff facial expression.

But to Daeho, the new food that had interrupted his meal was just standing there, facing him without any, not even the slightest, fear.

Should we retreat or attack?

It was a moment of conflict for Daeho.

-Instructor!

-Are you okay?

In that moment, Qing's head suddenly turns.

Tigers were far more dangerous creatures than you might think. Not to themselves, but to their subordinates.

If it suddenly accelerates, it boasts a crazy speed that cannot be imitated by human lightness, so even if it was blue, it can cause the heads of many inferiors, or even unmanned hopefuls who were not even inferiors, to explode before they can even react.

``Get back! It’s dangerous-''

At that moment, the tiger flies away.

In the world of beasts, launching a surprise attack on an opponent who has avoided eye contact was like any reaction engrained in one's instincts.

The newly appeared prey looked much more plentiful than the previous one, almost as if it were about to burst.

The tiger's huge forepaws surge forward.

It was said that the tiger's front paws have the power to shatter a cow's head in one blow.

And, Qing also had that kind of power.

Qing, who had just twisted his body slightly to avoid the front paw with just half a step, naturally ended up digging into the tiger's embrace and brought his clenched fist down.

On the tiger's forehead, in the middle of the king's pattern, a blue fist strikes!

-Wake up!

The tiger starts barking again.

And then I had a rare and unforgettable experience that I would never have again in my life: the unfamiliar and terrifying experience of being held down and manipulated by a human being by a huge body weighing two hundred and fifty pounds.

Qing grabs the tiger's front paws with both hands, lifts it up, and throws it to the ground.

And one more time. One more time.

Kwung! Kwung! Kwung!

When Qing finally lets go, the tiger lies face down, tucks its tail under its legs, and groans.

-Kkiiing… … .

The eyes, as large as its body, look up at Qing with a sad yet unusually bright sparkle.

``If you wanted to act cute, you should have done it before you pounced on me…….''

After all, you can't keep alive an animal that has tasted human blood.

It's not that tigers cannibalizing people was evil or that there's some kind of conspiracy, but there's no zoo where they can be kept.

The members of the Swordsmanship Training Group of the State Council and the Swordsmanship Training Group had never seen anyone so fast in the world.

Of course, if you accelerate as fast as you can on a flat, open terrain without any obstacles, you will be able to achieve that speed for a short time.

But isn't it an incredibly rugged mountain?

It would have been difficult to simply speed up in the dizzying, tree-covered wilderness without a path, but the sight of the instructor running at full speed and disappearing was a truly surreal sight that left me unable to even express my admiration.

But before doubting my eyes, following the instructor's footsteps was the priority.

The fact that the number of people in front and behind has been determined means that everyone should move together without scattering.

Since there was a third-rate unmanned island among the crew, they cannot even run, let alone fly, and have to chase after it at a hurried pace.

Thump, thump! Kkeung, uh-huh, ominous sounds resound.

And finally, it was the moment of catching up.

``Instructor?''

A tiger was lying down with blood foaming at its mouth, and a blue dragon was sitting on top of it.

In front of him, Wan Talu was kneeling, his hands raised in the air.

"Wan Talu. Is it okay to leave without permission during training?"

``No!''

``Did you know? But why did you do that?''

``I’m sorry, I’m sorry!''

It was a Wan Talu city with a strong military presence.

After seeing a martial artist swinging a tiger in front of his eyes and killing it with a single punch, anyone would be bound to be distraught.

"Is that all you have to say to apologize? Why did you do something you deserve to be sorry for?"

``I was wrong…….''

"No, isn't the instructor you just saw asking? Why did you do something you feel sorry for? Of course you did something wrong, and of course you should be sorry, but isn't he asking why?"

``I, I was so angry, I’m sorry, I’m ashamed…….''

``Hmm. I’m angry…….''

Qing pretends to think.

"Okay. People tend to lose their minds when they're angry, so that's understandable."

Qing nodded. Then suddenly.

``But, isn’t that not allowed?

The crew members held their breath.

It was an unavoidable reaction as I felt my breath catch in my throat without realizing it.

"I will answer."

"yes yes."

``Then why did you do something that was not right?''

The endless chain of events continues, each one so detailed that even the onlookers become astonished.

Why did you do that? If you apologize, will your academy life end? There must be a reason you're sorry, right? Oh, that's why. Yeah, that makes sense. That's possible. People can be like that, and they can make mistakes.

But, that won't work, right?

"Whew. We're in training, so I'll leave it at that. However, the Wan Talu Guard. This instructor was extremely, extremely, extremely disappointed."

This was Instructor Seo Moon Qing, a specialist in disappointment.

"Even if Guan Dao was nothing more than a first-class squire, he can still handle a tiger. Why would he let out such a desperate scream over a mere beast? I uphold the dignity of a swordsman, Wan Talu Guan Dao."

``That, that tiger, that wasn’t a tiger……''

``If a tiger isn’t a tiger, then what the instructor just saw sitting on isn’t a tiger, but a cat?''

Then Wan Talu made a voice of resentment.

``It’s true! It wasn’t a tiger, but some guy suddenly appeared and started swinging a knife, and here, I got cut by that knife. Look at this!''

Then, he puts his front porch forward, and no matter how much I look at it, it's dirty and covered in dirt, but it's in perfect condition.

``What do you see? Is the beast wielding a sword?''

Then, it was Wan Talu who looked down at the front of my head and groped it roughly.

``I was avoiding it, but some assailant, yes, an assassin, an assassin was after me!''

Wan Talu expressed his grievances with a look of resentment, and with a half-crying, hateful voice.

I was just walking around aimlessly when I tripped over a rock hidden in the fallen leaves, and then something sharp passed over my head, no, it almost brushed past me.

Then, an assassin in black attire suddenly fell from above and attacked. He was a first-class assassin, no, definitely a top-tier assassin who could use his sword skills very naturally.

``So I ran away, no, that’s not it.''

But since he was not easy to deal with, he divided hundreds of sums with him and eventually dealt a fatal blow to the assassin.

The assassin ran away, saying he would wait and see, and just as he was about to chase after him, the tiger suddenly pounced on him.

But I have already exhausted all my strength in the bloody battle with the assassin…

The expressions of everyone listening to the testimony became narrow and squinty, like the eyes of a man with long hair.

What kind of master assassin was this (it's not uncommon, but very rare), and why would such a renowned assassin target a dog?

And the guy who screamed so desperately in surprise at a single tiger fought a top assassin and split hundreds of points? And even won?

No, in the first place, there was no time to aim for hundreds of points.

Besides, tigers were clever beasts.

If you're going to hunt, why would you attack a healthy one instead of chasing a wounded one?

And you said you were trying to chase after the assassin, but then the tiger came out and you suddenly lost all your strength and couldn't deal with it?

``This little shit barely managed to scare a tiger and scream, and now he’s getting beat up, it’s not even funny. Ha, no, you were just saying that to make me laugh, right? Ha, shit, yeah, this kid was really funny, this kid.''

``Changyohong’s official route. Maintaining the dignity of a swordsman.''

"Your Majesty, you were so frightened by a tiger that you urinate on it. You must be a very interesting person. However, may I call you 'young lady' from now on?"

Qing nodded in agreement.

Even if it's the same thing, you have to say it with dignity.

"Who, who said I peed! And I'm sure an assassin attacked me—"

"Yeah, yeah. These days, assassins were taming tigers and driving them around? The world was really fucked up. No, what the, what the hell was that, vicious?"

``It’s so scary, my lady.''

Yangchil said something.

``Yeah. That. The world was so cruel.''

Then Wan Talu got angry.

``You bitch, how dare you-''

``Use it. Oh my. Dignity.''

Qing's sudden words.

Then Wan Talu tries to change his words.

``That, that young lady, eight, what was this…!''

Wan Talu jumps up and turns around.

Qing-i, um. I just told you with words, so you haven't come to your senses yet?

Do I really have to pick up the flute? Why should I have to pick up the convenient and fun fist instead of the tiring words when dealing with other people?

The moment when Qing quietly takes out the flute.

``What were you guys doing! Hurry up and keep training!''

Unfortunately, it seems like words alone were enough.

Qing-i licks her lips and puts the flute back into her belt. Hmm, too bad.
