\chapter{Be Sure to Maintain Your Dignity When Going Out (1)}

This can't go on like this.

Free time, free time, personal time for me, time for Ximen Qing as a free person, not as Ciyu's father, not as an instructor at Yizheng Martial Study Hall, but as a free person-

Yes, freedom, freedom is needed!

In fact, if I could just figure out how to handle the private tutoring time for Geomokgun, I would have plenty of time.

So how? There are ways.

Just ask someone else to do it!

``Oh, if you're a swordsman, then you must be a true swordsman with a long history. I can't help but help you.''

Nan-gong Shencai's beginner swordsmanship class is held for half an hour after dinner.

The training of the instructors of the Geomok Army lasted for one hour.

So what if we leave half of it to Nan-gong Jinjae?

You can get a valuable hour of free time, half an hour, just like in your hometown.

I searched through everything.

If I leave Ciyu to Sanhan to learn his letters for a while longer, I will have complete freedom. I will lie in bed very meaningfully and productively during this precious rest time.

``Instructor?''

Geomokgun had a very disappointed expression on his face.

But the blue is dignified.

Because honestly, in terms of teaching, Nan-gong Shencai is better than Qing.

It will also benefit the Geomok Army, who will receive a higher level of education.

It's also beneficial to be able to lie in bed and daze off for a while.

And it's also beneficial to Nan-gong Shencai, who is happy anyway, just by swinging his sword.

Wouldn't it be a world where everyone is not only free from hurt, but even happy?

"Your Majesty, I'm not lying when I say I learned from Assistant Nan-gong. Of course, if we were to fight in a real fight, I'd win ten thousand times out of ten thousand. But when it comes to swordsmanship and understanding, Assistant Nan-gong is superior."

"Hmm. Hmm. But, Sword Friend, if you fight ten thousand times, at least once-"

"Yeah. No. Even if we fought ten thousand, ten million, a hundred million times, it wouldn't be possible. If you feel wronged, you can even fight with the Sword and Cloud."

``Ugh…! This won’t do. Charge. Of course, without using your internal energy.''

``That’s funny. Are you going to use it?''

At the light attitude, Geomok-gun blinked.

Well, since Qing always said that and lowered her voice, I couldn't understand the part where it sounded beautiful despite being low, but anyway, thanks to her, I can now see Qing as a woman of her age.

"Oh, Miss Sword, you can speak freely. Now that all the officials have left, it's private time. You'll be joining the instructors, so there's no need to be so formal, right?"

``No. How could I, seeking instruction, maintain an impertinent attitude?''

Geomokgun was very firm. Hmm. Pumpkin. Yes, I want to eat pumpkin porridge. There's one in Jungwon too. Will they make it if I ask? They put honey rice cakes in there.

Anyway, yeah. I'm free!

``Um, my lady……''

"Come on, Young Lady Murong. Shall we go and just chill out together for a bit? Sounds good, huh?"

``No, that’s not it, um, let’s spar a bit…''

``Huh?''

It was a completely unexpected ambush.

That's understandable. The admissions office seems a bit reluctant to spar. I think they may have been a bit too squeamish.

But still, while she was in the admissions office, Murong Zhuji-hee had developed to the point where she could block something that was once a hundred times, but once out of twenty times.

A whopping five-fold growth. As expected, youth and warriors grow the more they suffer. Why didn't they say in Romance of the Three Kingdoms that frustration makes a man? (They didn't.)

``Hmm. Young Lady Murong, I have a favor to ask…''

``Ugh, over there, ugh…….''

"Why are you making it so difficult? Am I difficult? No, I'm completely comfortable. I'm completely comfortable, and it's practically a science. Just say it comfortably. Why?"

"Uh, if you could be a little gentler, ah! Of course! Being rough would be a big help, but that's not it. Since you're usually using the secrets of the middle sword, there's a lot of progress in the part where you grab the axis and rotate it, so I'd like you to also master the art of grabbing the axis of a counterattack. Um, there's absolutely no other reason for that..."

Qing was originally a hot-tempered person, and had a quick temper, so he liked to use the trick of pushing things forward with brute force.

And Master, Ximen Surin is also like that, so whether it's a sword, a dagger, a fist, or a foot, he has no choice but to swing it and unconsciously put weight on it.

Dujeonseong is a dual-wielding martial artist who uses one weapon to block enemy attacks and use it as an axis, and uses the other weapon to change direction and return enemy tactics.

So, since Qing uses a lot of strong attacks, the latter part is trained, but the part that focuses on sharp, flashy, and ever-changing attacks is not trained.

Hey. I was trying to rest.

Qing scratched the back of his head.

If Murong Zhuji had made her point clearly and confidently, I would have decided to rest today.

But look at the state of Murong Zhuxi.

Murong Zhuji had a face as pale as a peach blossom, her earlobes were red, and her body was hunched over, her shoulders hunched, and her fingers wringing.

Just looking at that, I can tell how much courage it takes to ask for something, so I can't just say, "No, I'm just going to lie in bed and do nothing today," and refuse.

``Hmm. Then there’s nothing I can do.''

``Ah, hehe, hehe. Please take good care of me.''

So, the sparring begins.

Since Qing's body is beyond human, he is eight times as heavy, two times as fast, and the two combined are roughly called strong, which is his advantage.

Although his strength makes him particularly effective at fighting, he possesses a monstrous body that can also excel in other abilities, such as incredible elasticity and flexibility.

Besides, this body is a master.

The blue wooden sword suddenly flows down in a meandering wave.

The mystery of the new voting, the invisible spirit, is an optical illusion created by the shaking sword filled with a soft, sticky feeling.

Additionally, this slow, sloppy, and subtle technique also has an optical illusion that makes it appear to move much slower than it actually does.

The blue sword trembled, but somehow rushed towards Murong Zhuxi at a speed that made his strength drain.

Since it was Murong Zhuji's first time, he thought she would be gentle and raised his left-handed sword, but thanks to that, his reaction was a beat late.

It was the soft sound of Qing's wooden sword striking Murong Zhuxi's shoulder.

``Ah,''

Murong Zhuji immediately sat down, slammed one knee on the ground, and grabbed my shoulder.

``Hah……!''

"Oh, Young Lady Murong. Are you okay? I didn't use much force, but did I miss it? No, it just didn't taste right."

``Oh, no. Good, good. This, this.''

Murong Zhuji's expression was like the faint but clear moonlight on a late night.

There's something shady and subtly lewd about her? She's smiling like the moon, not brightly like the sun.

``Ugh, could you please do a little more……''

So, let's continue the training.

Geomokgun was slightly disappointed.

In fact, the purpose of taking the entrance exam for the Department of State Affairs was not to get into the department, but to see if I could win by looking at the Cheonhwa Sword.

I lost the match and ended up entering the Department of State Affairs.

But it's actually good.

The instructor is fully qualified to be called the next best swordsman in the world. That young swordsman is twenty-two or so this year.

If the unmanned person who has already achieved harmony in that age is not the next best in the world, then who will be the best in the world?

What captivated Geomokgun more than anything was the Qing swordsmanship. A swordsman speaks with his sword. What does age have to do with anything?

Having the opportunity to learn from a master who has already achieved exquisite skill makes the journey to the distant heart of the Zhongyuan truly worthwhile.

I watched with some interest as I was defeated by the unique swordsmanship of a young man I met on the way, a strange swordsmanship that was neither dance, nor swordsmanship, nor blade, nor wind.

But now that I've seen the true swordsmanship, the swordsmanship that reached the heavens, I realize that swinging the wind as a blade was just a simple grappling technique, a sorcery that was difficult to defeat with swordsmanship.

But, that young man's name, um, I don't know.

Geomokgun was a man who was as persistent as he was when he got hooked on something, and when he lost interest, he would just as easily throw it away without even looking at it.

So, the only reason I entered the martial arts academy was to learn from one instructor, Heavenly Blossom Sword.

It's only natural to be disappointed when you learn from someone your age, not even an expert, but someone of the same level, instead of the instructor.

But since it's a matter of learning a new swordsmanship, it's only natural that even if you're not at the same level as them, you can still learn to that extent.

Only after memorizing this Oro Sword technique can you request a full-fledged training session with the instructor… …!

It was a rather regrettable feeling for Qing.

Of course, Qing doesn't know. How can one know what's on someone else's mind?

So, Geomokgun also endured and received the teachings of Oro Geomgyeol.

however.

``Hah……!'' ``Huh……!'' ``Ah……!''

Why is that sticky moaning sound that keeps breaking my concentration?

``Hmm? Why are you like that?''

"That. Assistant Nan-gong? Isn't that woman, that, Geomhwa?"

"That's right. He's a half-baked swordsman who wields only one side of the sword, the most prized weapon of all time. But his passion is still worthy of consideration."

``No, that. Is that how you normally make sounds?''

"Hmm? What do you mean? Isn't that just a slap in the face? It's natural to grow the more you suffer. That's a good thing."

Nan-gong Shencai nodded.

``Getting hit. No, ahem. Ugh, the moaning is a bit, masculine, I don’t mean it in a bad way.''

Because it was a somewhat embarrassing question to even say out loud, Geomokgun asked cautiously and stealthily.

Nan-gong Shencai just shrugged his shoulders.

``Hmm? Isn’t that just a normal moan?''

Nan-gong Shencai looks as if he is wondering what is strange.

Well, at the table of the Half-Geom Ssangdohoe, there is a person who eats while making really masculine noises.

Once you get used to that person and the meal, that kind of thing is just a normal, painful sound.

So, Nan-gong Shencai and Qingdo didn't think anything was particularly strange, so Murong Zhuji was unknowingly benefiting from Seol Iri.

"By the way, it seems the instructor is observing Geomhwa's swordsmanship. Are you someone who would normally readily offer swordsmanship lessons like that?"

"What good is there in sharing swords between close friends? And above all, it is the spirit of this organization, training together."

The eyes of the black-haired soldier flashed at him.

"If you say this is the meeting, does that mean you're a member of the Instructor's Sword Society? By any chance, have you joined the Sword Society called Absolute Sword Mastery?"

"That's not it. Our swordsmanship... Hmm. Ahem."

Nan-gong Shencai coughed for no reason.

Well, it wasn't a name I could be proud to tell others about.

Even more so, as a swordsman.

"Well, there is something like that. Rather than that, let's unfold the next chapter."

The eyes of the black-haired soldier flashed again.

Perhaps it is a secret, secret vision of some nameless sword!

Of course not.

But illusion is free.

If that's the case, then wouldn't it be impossible for someone who inherited the swordsmanship of Geomgak to fall into such a swordsmanship?

The eyes of the blacksmith burn quietly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

These days, the staff of the Military Academy, that is, the warriors of the Wulin Alliance Support Unit, seem to be very busy.

In fact, the main duties of the support unit soldiers are to guard the Uijeongmuhak Hall, and their secondary duties include miscellaneous tasks such as facility maintenance and repairs, and to draw lots to take charge of cooking at the government cafeteria.

But even if it's called facility maintenance, there's not really anything special to do.

Even if you say it's your turn to cook at the government cafeteria, since the food will be eaten by the government officials anyway, you can just make it roughly and serve it.

And as for security duties, the only annoying thing is being on night watch.

Surprisingly, the officials of the Department of Military Affairs did not stand guard or anything, as they were officials who had to work hard at military affairs.

But I've been quite busy these days.

Because there is a lot of work.

Why is there so much work?

Because the super large training was caught.

What on earth is this massive training that causes all this work?

It's a march, no, it's not a military march, it's a march!

This was because the movement of a large number of people required a great deal of effort, including advance planning, distribution, route setting, and prior coordination.

This was a sign of the harsh training that the officers of the Military Academy had to undergo.