\chapter{Be Sure to Maintain Your Dignity When Going Out (8)}

-Please, Confucius, I already have a lover with whom I have a future relationship, so please don't say such things. I am not a woman who sells her body...

-You bitch! How can a bitch who sells flirtation and laughter say she won't sell her body? If that's not deception, then what is? How dare you, you lowly bitch, try to deceive me!

-Please, I beg you, please… …

There's no need to listen any further.

Draw your sword right now, your sword, um, my sword.

Because he was standing to one side while drinking, only the body of the enemy was left standing alone.

Well, there's no need to take a sword with you when you go to the back room, and if you happen to drop it, what kind of disaster would that be?

It was an unexpected incident, so why did people in Qing's hometown lose their cell phones, precious objects more precious than the light, dreams, life, soul, and life itself of modern people?

So, in some ways, it was a wise choice, and a master of Hwagyeong was still Hwagyeong even without a sword, right? After all, I am the master of Soo-Magong?

This was the thought of the woman who immediately threatened the officials that the black sword was a companion in life, a tool and key to training to perfection, and that they should always carry it with them, whether they slept or ate, or else there would be punishment from the Aegyo Bong (a flute, a perpetually cold wind, it hurts a lot).

However, if you feel wronged, you should either become an instructor or take pictures of the scenery.

Just because a master of Hwagyeong left his knife behind, wouldn't he be able to cut down a single rascal who's making a fuss in a country town like this?

But somehow, the voice seemed familiar, a stern voice with a hint of guilt, a clear, low-pitched pronunciation, I felt like I'd heard it somewhere before-

Of course, that didn't matter.

Knock! Qing immediately opens the door.

Then, oh my, a short, low scream of surprise, followed by the sound of something moving in a hurry.

It was a noise made when two or three pairs of birds suddenly fall apart in surprise.

And then someone shouted, accompanied by the visual background sound of a sword being drawn.

``Who were you!''

And then, without even giving Qing a chance to respond, he continued talking on his own.

``Uh, Instructor Ximen?''

``What is it, Oruwon Trainee?''

The sound of a chair being dragged and falling over.

The faces that were hastily getting up from their seats were familiar, the swordsmanship officers, and the unfamiliar faces looked at me with expressions of being in trouble, so I could tell they were officers from other classes.

And at the very top.

``Wh, what were you doing! Hey! Even if you’re an instructor, was it okay to interrupt my personal life like this!?''

Ah. That's right. That voice. It was Wan Talu.

It's a pity that his voice was so clear and serious that it doesn't match his personality and conduct at all.

"Of course, personal maintenance time was guaranteed. However, only if you adhere to the basics. This guide clearly states that only the basics should be adhered to."

"That damn basics, what else? Would you say that even going out and hanging out with gisaengs was against the basics?"

This kid was acting so confident.

Qing's eyes narrow.

"Is it right to forcefully take a woman who refuses you, regardless of your sexuality? This instructor, by observing the evidence, destroys the root of that sin. It's about eliminating the root of a man's thinking, not with his head, but with his subordinates. Today, the Wan Talu lineage will be cut off."

It was the intense presence that erupted in an instant, the master's murderous intent that made one's ribs tremble, and his murderous intent.

Wan Talu was startled and waves his hand.

``Wait a minute, there’s a misunderstanding, there’s a misunderstanding.''

``Misunderstanding? I heard you clearly.''

"That's not it, no! You, you speak up. Hurry up."

This guy was trying to get away with intimidating the victim into giving false testimony? Such a despicable act!

Boom! The innocent floor of the building caves in, and splinters of wood fly.

The number of new Qing models keeps increasing, and then, boom!

``Ahhh!!''

Wan Talu falls, clutching his head.

One big slap to the son of a bitch's head!

After that, Qing gives a gentle smile to the woman kneeling next to the rolling Wan Talu with an expression that was incomparably gentle.

"You have nothing to worry about, my lady. That bastard won't be able to walk away on his own two feet, so come here with peace of mind."

The woman's expression became blank for a moment, and then she opened her mouth.

``Ah! Heavenly Blossom Sword! You’re the Heavenly Blossom Sword Daehyeop!? Oh my gosh, yaaaah! Wow, unnie, you’re so pretty!''

``Huh?''

"Guys, this was the Great Swordsman of Heavenly Flower! The disciple of the best female martial artist, the divine dragon of the martial arts world! The next best in the world! Wow, I really respect him!"

``Gyaaak!''

A celebrity suddenly appears.

The women who had been frozen by the commotion came up to me, squealing, saying, "You're so pretty," "Wow, look at your hair," "I think I know what they mean when they say you look like ebony." "What kind of soap do you use?" "Wow, the fragrance!" "You're really pretty, pretty, pretty." "Wow."

``Huh.''

Qing paused for a moment with that expression.

Even these were cute gisaengs who were causing a fuss.

And after a while.

``Oh, so, it’s a classic drama?''

A play that assumes a certain situation and plays a role that fits that situation.

In Qing's hometown, it was called a situation comedy.

``I told you it was a misunderstanding……''

Wan Talu, his face quite swollen, lets out a wet, half-sobbing sound.

Qing scratched the back of his head.

But this kid has a bit of dirty and messy taste… … .

Forced? With a lover? Oh my. Seriously.

"Oh, sorry. The instructor was a bit hasty. The acting was so realistic, man, the Wan Talu can even be an electrician."

Jeon-gi was a literary and artistic trend that flourished in Gangnam. The plays of the Zhongyuan were a mixture of song and dance, but Jeon-gi was a form closer to modern plays because such song and dance plays were rare.

An electrician was an actor who was usually called an electrician.

At that, Wan Talu's expression becomes even more distorted.

"You call me a lowly electrician, huh? How dare you insult me like that—"

``Huh, were you out of your mind? Haven’t you heard the saying, ‘There’s no such thing as high or low in occupations?’''

Everyone's expressions turn hazy at that.

Was there ever such a saying? Isn't it natural that there were noble and lowly occupations? Isn't it the natural order of the world that noble people do noble work and lowly people do lowly work?

Of course, there was still a distinction between noble and common in the Zhongyuan.

Of course, even in the Qing Dynasty, there was a clear distinction between noble and base occupations, although it was not said in words. Therefore, there has never been a time in human history when occupations were not classified as noble or base, and there never will be in the future.

``Ahem. That’s what the instructor thinks.''

One of the officials raised his hand and asked.

``Instructor, if there was no distinction between noble and base occupations, were you saying that those Hao guys and the government officials were the same?''

The Hao people were the five lowest occupations in the Zhongyuan. I heard of them in the Qing Dynasty.

What these five professions have in common was that they often engage in activities such as robbery, murder, theft, human trafficking, and cannibalism in addition to their main job.

"Ma'am, I'll just skip over it. And honestly, there's no difference between the two."

``Ah! So that’s what you mean!''

The official slammed his palm against mine.

The actions of the Zhongyuan officials were not much different from those of the lower classes of humans.

Suddenly, Wan Talu shouts!

``What kind of blasphemous talk was that! Governing a country was a noble duty, commanded by Heaven to govern all the natural laws of the world. How dare a mere barbarian dare to disgrace an official!''

what?

Qing tilted his head.

What the heck was this guy suddenly having a rash?

"Why was the Wan Talu government causing such chaos? Is the government an official? And the learner was very disrespectful to the teacher. Is the government really like that? Is that right?"

Only when Qing raised his fist did Wan Talu flinch.

Well, come to think of it, I thought this guy was a spy sent by the government.

Maybe he's the son of a high-ranking official?

Look at it now.

Qing looked around at the magnificent table set so high that it would make her legs break, and the officials sitting around it.

If you don't leave an empty seat when filling a table in the Middle Kingdom, you were second-rate.

A truly first-class dining table was one where plates were placed on top of each other, creating a three-dimensional effect through these layers.

There were seven officials, excluding Wan Talu, each with one woman on either side or two on either side.

Since it would be so embarrassing and shameful for the person sitting at the top to ask for a favor (this culture of saving face was something that the Qing Dynasty should learn from its hometown), he means to pay for all this luxury by himself.

The eyes of the gisaengs were bright and sparkling.

And the officials' expressions were awkward.

"Why were you all like that? Just keep doing what you're doing. As long as you follow the basics, the instructor won't touch you. Personal sexual misconduct isn't a problem, since you're not married, so what?"

"Instructor? So, were you saying married people can't enter the Giru? Why?"

Another guy spitting again.

It was the guy who asked about those guys earlier.

Oh my, our official was really curious, he's really curious.

In this Zhongyuan, even if you play with women in a giru, it's just a pastime that men usually enjoy.

Anyway, I came out to run some errands and wasted time.

I've tasted the taste of a real chestnut, but, um, I want to blow its head off. Compared to that, a real chestnut was just something I've stroked.

Ah, I want to break open a watermelon! Miss, I was looking forward to finally getting a taste of it, but it's really tempting. I've been holding back and forgetting about it.

This emptiness, this burning thirst, I need to quench with alcohol.

It would be better if there was even a hint of hee-mae, hmm, Chun-bong, um, if you try to slyly poke me in the side, it would be okay.

No, that won't do... ... .

Since Gunyeong was just sleeping, I took a room next to her and let her sleep, and once she fell asleep, she wouldn't wake up.

Hmm, I keep having bad thoughts.

But if it's Gunyeong, don't I have rights too? I fed him, gave him a place to sleep, bathed him when he was sick, clothed him, and even taught him divine powers.

Qing clenched and unclenched his fist.

It won't work.

I feel a little sorry for the officials, but I'll just have to hang out here for a bit and then go.

What do you say? Officials, it's not your job to be concerned. Come on, I like the instructor here, too.

Hmm, okay, let's do this. As an instructor who cares about his students, it won't hurt his dignity.

But now, these worries were closer to being ugly than dignified.

Anyway, Qing was a product of miracles, a peerless beauty on the outside, who would be a picture wherever she was as long as she kept her mouth shut.

That was when.

Knock knock. The sound of a knock on the door.

``Who were you?''

"Hehe, sir. It's truly an honor to have you visit our restaurant. A bottle of our precious Jachundu Gangju just arrived."

They said they came to sell alcohol.

However, what's secretly upsetting about Qingdo is, why were you leaving our room and coming here to sell alcohol?

You got the best seats, and how much alcohol have you sold in half a day since lunch?

Besides, what was Jacheondugangju?

Even for Qing, who had heard the name Myeongju somewhere and never forgotten it, it was a name that was incredibly unfamiliar.

However, Dugangju itself was a very precious liquor, and if it has the name Haneulcheon, it means it was the highest quality liquor. Just by hearing the name, you can tell that it was a really great liquor.

"Huh. Even a lowly merchant can recognize a nobleman. Come in. This was perfect timing. Just hearing the name makes me think this was a very precious drink, so I'll offer you a glass while I'm at it."

Suddenly, a dog barked in a strange way.

"Hehe, if not now, when else will you, Instructor, taste such precious liquor? In your humble Taoist life."

Well, it's still a dog's paw.

I thought that the fire-breathing woman, So-Jeo Chang, had given her a really amazing nickname.

And what about the simple life of a Taoist monk?

Surely you don't think Taoists were poor?

How can you be so ignorant of the ways of the world?

A Taoist priest was never poor.

Even the famous local temples were overflowing with offerings year-round, and their warehouses were bursting at the seams.

How about a hot spot for women all over the Zhongyuan, or, in technical terms, a nationwide hot spot for women, like Shinnyeomun? These days, the Empress Dowager's estate was overflowing, so it's practically unmanaged, and it's practically in ruins.

But Qing didn't bother to point it out.

And he didn't even shake it off and get up.

Let's say you've been hit by some kind of defenseless technique.

If you leave here and say you're done, you'll be criticized for being too proud, so it would be more generous to empty half the bottle before leaving.

Of course, I absolutely don't want to drink alcohol.

And it's not because of the bad hand chopping.

It can't be helped because of the reputation of the Zhongyuan.

Jagangducheonju, huh? Jadugangcheonju? Well, whatever, oh my, my mouth was watering… … .

Gulp gulp gulp.

It was the sound of alcohol flowing out of a high-quality liquor bottle, a typical Zhongyuan liquor, with a narrow spout that does not even allow a finger to fit through.

Qing swallowed her saliva and sniffed the scent.

The lingering scent of alcohol hits you and makes you dizzy.

Isn't this the kind of strong liquor that would make someone with a weak tolerance for alcohol intoxicated just by smelling it? It's the kind that evaporates little by little if left alone.

But compared to that, isn't the smell a bit strong?

I know it's a rare true liquor in the Zhongyuan, a type close to alcohol, but it feels a bit rough rather than elegant.

No, was this alcohol or perfume?

For a moment, Wan Talu smirks, a sinister smile on his face.

"It's a shame to just drink it, so how about enjoying a little entertainment? Instructor, try it first, and then write a poem about the taste. Then, we, the officers, will join you in the fun."

Hmm. Something like this.

This was exactly what Hanrimwon bachelors do.

Qing, a peerless beauty who had rolled in, received countless requests to shake hands and discuss the scriptures without any of the usual pretense.

But the way they always make fun of someone was by writing poetry and humiliating them with combative comments.

I guess it's the dark way of those who have been taught.

But who was Qing?

She was a woman who graduated from the Hanrimwon Academy.

That too, was the disciple of the master of poetry!

A master of memorization who has memorized and memorized all kinds of scriptures without any prior knowledge!

So, confidently pour yourself a glass in one go-

Wow, this taste!

This fiery cycle, as if all your internal organs were on fire! The spiciness of the Korean people, as spicy as a super-hot Qingyang pepper!

Qing cheerfully downed his glass!

With everyone's eyes focused on her, Qing pulls out a poem from between her bright red lips and her two alluring fleshy parts.

Purple Heaven Du Kang Wine

-The supernatural, supernatural sword of the supernatural world, the ...

Don't eat it.

I'm poisoned.

Catch that drinking bastard.

Right now.