\chapter{Be Sure to Maintain Your Dignity When Going Out (16)}

Qing sensed the entire situation: assassins constantly rushing in, men disguised as civilians launching surprise attacks, and even secret weapons flying in amidst it all.

I quickly realized that there were several people running after me on the roof.

Somehow, he didn't seem to have any intention of coming down and just kept chasing after me, so I pretended to be out of breath and scratched him gently.

I'm tired, but you still won't come?

Why, you're going to pounce on me after I collapse from exhaustion? If another assassin strikes first, won't you be left with nothing?

Then, they finally split into two groups and one group pushed forward, as if they were planning to attack from both the front and back at once.

But I have no intention of matching it with him.

Of course, even if the enemy was easy, Qing had no way of showing mercy.

Why would anyone go along with the schemes of these seemingly mysterious assassins?

Because I am a true master of Hwagyeong?

Hey, even Hwa-kyung dies if she gets hit by a sword. She has to get hit hard, no, really hard.

``Me, me, this was enough- ugh!''

Qing punished Wan Talu for his nonsense by grabbing his side.

You little shit, where have I seen you before? Why were you telling me to leave you behind?

I've been causing this mess all this time, so why bother if I'm just going to let it die? Of course, thanks to that, I'm enjoying the taste of it.

``Nonsense, huh? I won’t do that. Phew, I’m an instructor, and you’re a trainee.''

``Are you saying we should die together? Kk! Oh, stop, it hurts, it really hurts. Surrender! Surrender!''

``Be polite. And keep pretending to be tied up.''

Thump, thump, the sound of the hand stuck at my side tearing off the netting one line at a time.

It was a truly incredible feat, just fiddling with your fingers to tear off that incredibly thick net.

``Okay, did you hear that?''

"……yes."

Wan Talu answers.

This was the first time I've heard such an ugly answer, but

He was telling me to pretend to be tied up in a net and use it when the time was right. Did you really understand that?

Qing, while fiddling with the net and tearing apart the assassins who rushed at him, paid close attention to the movements of the rooftop runners.

Roughly fifteen? Sixteen? Or maybe fourteen? In any case, all numbers before and after that, except for five, accelerate forward.

Qing hesitates before him, pretending to be hesitant to deal with the assassin and secretly slowing down his pace.

Thanks to this, the leading group of rooftop teams that had overtaken them gradually fell behind, and the remaining rear teams were slowing down to catch up with the blue.

Of course, it was natural that the rooftop side didn't know that Qing had noticed them.

At that moment, a miraculous and surprising event was captured by the Qing's oil-fueled waiting detection system, where the corpse of Balchi suddenly rose.

Well, it's not a corpse.

He was an assassin who pretends to be a corpse and lies down, then stabs the person who passes by with a knife.

The creativity of the assassins should not be underestimated.

However, it seems he didn't know how to hide the red numbers above his head. Even if the assassin was the most creative, he wouldn't have thought that he would have the ability to see the numbers above his head.

If I hadn't known, I might have been hurt. It's a shame. It's a shame.

Qing thinks so and screams.

``Ahhh!!''

The assassin was confused.

The dagger aimed at Qing's dantian shows no sign of being embedded, as if pushing a rock.

Even so, Qing let out a scream, so it must have been a shallow stab, but despite the fact that there was no feeling of tearing through the skin at all.

At that moment, the assassin meets Qing's gaze.

At that time, neither the dazzling beauty of the most powerful candidate for the most beautiful woman in the world, nor the beautiful curve of her large eyes that seemed like they would pop out if you tapped the back of her head, entered my sight, because of the unprecedented color blooming in the center of those blue eyes.

The most vicious evil in the world, a color close to pure evil itself, without any impurities.

The assassin disguised as a corpse stands stiffly.

Because his skills were too weak to withstand the murderous intent of a thousand years, it was not the case that someone who was confident in his skills would pretend to be a corpse and pray for someone to pass by.

He closed the distance between himself and the assassin, whose arms were frozen solid.

And then, with his elbows pulled back, he attached the double swords to the assassin's body from above and below-

``Kwaaaaak!!''

Scream with all your might and thrust both arms forward simultaneously.

The assassin himself wanted to scream, but his nerves were frozen with fear, and he couldn't even utter a sound as his torso flew at incredible speeds.

The torso was backwards, and the limbs were spread out in the opposite direction due to the recoil, so when viewed from the side, it looks like an assassin falling in the shape of the Chinese character for death.

Still, for a moment, I felt a little relieved at the sight of Qing quickly moving away.

``You bastard! Where were you running off to? How dare you stab me!''

The angry tone of the blue voice as it shouts.

Assassins can be very wronged.

I pushed it away and it ran away?

But before he could even raise such a protest, Qing quickly picked up the net-wrapped Wan Talu and, bang! He shot up, digging a hole in the author's solid floor.

``Tsk.''

The leader of the group of assassins on the rooftop who were chasing Qing, called Yeongban, crumpled his face.

It seemed like an assassin had stabbed the Heavenly Blossom Sword.

Of course, if that were all, it would be a blessing in disguise. I would have thought that the money I spent on those human bastards was well worth it, and that it was worth every penny.

The problem was that the assassin threw himself at a civilian house as he fled.

Although Qing had pushed hard towards the house, it looked just like that to the pursuers who were occasionally peeking from the rooftop.

Didn't Qing keep screaming as if she was stabbed for him in the first place, and didn't she fly around pretending to be indignant, saying, "You stabbed me?"

It was a very painful mistake for Youngban.

Because, until now, the road to Minga was not a road for him.

Why did he think that Heavenly Blossom Sword would run away along the road? Because he thought that the houses on both sides were not the road, but obstacles blocking the road.

So, if you open up an alley and block the front and back, you can naturally guide them.

The bigger problem was that Heavenly Blossom Sword must have realized that the houses were not obstacles but rather surmountable passageways.

If you run away from now on by breaking through the doors, walls, and windows of houses instead of the road, the pursuit will inevitably become dozens of times more difficult than before.

It was his big mistake to momentarily forget that the gangsters called Wulinin were destroying houses as easily as eating rice.

Of course, if Qing had known, he would have laughed.

It wasn't that Qing ran along the path without a change of perspective. To be precise, it wasn't that he couldn't do it, but rather that he chose not to.

Because you shouldn't just go around digging holes in other people's houses.

The Qing Dynasty was a member of a highly civilized, advanced social system, and among all the primitive, primitive people of the Zhongyuan, they were the most socialized and common-sense people (though they were still a thousand years old).

But when there's nothing you can do, there's nothing you can do.

Collateral damage and property damage could be compensated for with even more gold, and in the first place, Qing had broken through the walls of other people's houses more than once.

Anyway, thanks to that, Youngban was in a difficult situation.

I had no choice but to stop running and watch with my nerves on edge to see which way this woman would jump out and run away.

"It was my mistake. I should have formed a circular encirclement instead of blocking from the front and back. Bring in the vanguard. This was going to be a difficult task."

``Your name.''

The subordinate answers and immediately shoots Hyo-shi.

A hyoshi was an arrow that makes a sound when shot, and was an ancient, primitive signal flare that flies into the sky making a loud beeping sound.

Then the servant put the family register in his mouth.

Beep, beep! Beep, beep! Beep, beep!

The signal bell was originally noisy and sharp enough to grate on people's nerves.

Because then, after hearing it, wouldn't you come to your senses and be able to understand the signal?

The creaking sound right next to them was so loud that everyone's foreheads furrow slightly, but isn't that inevitable?

That was the moment.

Beep!? The tone of the register was filled with questions.

Of course, if something grabs your ankle while you're blowing the flute with all your might, even the most virile of men would be startled and let out a gasp of shock.

But the confusion was short-lived, as the man playing the flute immediately drew his sword and struck my ankle.

Bang!

And then I got really flustered.

A crack? Is that the sound of a weapon and a human hand colliding? And that blade, imbued with black energy? Could it be that the grip holding my ankle isn't a human hand, but a piece of iron carved into the shape of a hand?

In that moment of hesitation, my remaining left foot was suddenly grabbed by a hand as white as jade that had emerged from under the roof.

``What happened-''

Before the surprised Yeong-ban could finish his question, the body of the man playing the flute fell down.

However, if a person standing on a roof was pulled down while being caught in a hole under each foot, where will the point of impact be?

The correct answer was below the pelvis.

And the piper, being a man, had two very, very precious spheres hanging from his pelvis.

Not from now on.

``Ugh.''

When the pain was too great, you can't even scream. The veins in the flute man's eyes turn bloodshot, and he makes a strange gurgling sound as if he's forgotten how to breathe.

That was when.

The flute man's body suddenly rises.

As if the hand that had been holding my ankle under the roof was pushing me back up.

No way. Daeyoungban's expression turned utterly shocked, and before he could even shout—

The flute man's body sinks again.

A thud, a crash that was even more horrible because it was sticky as my legs hit the roof.

``Kwaaaaak!!!!''

Only then does a desperate scream burst out.

A groan that would make the listener's bones shiver, a cry of the most excruciating pain in the world, a groan that could only be heard from the bottom of the abyss of hell.

And the man, now the man's torso rises again.

It seemed like he was already on the verge of fainting, his upper body bent limply and he was lying face down, hitting his butt.

``No! Stop it! Stop it!!''

Although Youngban shouts desperately.

The Qing were of the Korean ethnicity.

The Korean people were a people of three generations.

They were the type of people who need to be satisfied once, slightly lacking twice, and need to be satisfied three times to feel safe.

Additionally, Qing was also a person from the Zhongyuan.

The Zhongyuan people were a people who have been recommended three times.

If you accept an offer on the first try, you were a shameless person who doesn't know how to respect others. If you accept an offer on the second try, you were a fool who thinks you were too hot to do anything. If you accept an offer on the third try, you were a people who were recognized as a true gentleman with proper distribution.

``Ugh, ugh…''

The human's eyes, once filled with the flute, turn over, revealing the whites of his eyes, and foam spews from his mouth, imitating a crab.

Jong Baek-ho, your face has brightened since you said you were getting married. Are you really that happy? It's a shame to make a fuss about your future wife being pretty.

Hehe, Yeongban, what if you live in captivity or were a slave? If you meet a good person and live together for a hundred years, isn't that the happiness of life?

The awkward smile of the subordinate flashed through my mind.

The servant was full of enthusiasm and said that he would get married after completing this mission, so let's finish it quickly.

Yeongban urgently put his hand under his subordinate's shoulder and pulled him.

Below, the subordinate's legs were easily pulled out, as if he had already let go of his hands. However, the ankles below the knees were completely crushed, and the tips of his toes were hanging limply.

``This, this vicious……!''

Yeongban stutters as his anger boils over him.

How dare you, how dare you, this lowly woman of the martial arts world, dare to touch who, who dares! How dare you! How dare you!

We'll have to see if she's really a lowly woman, but anyway.

Youngban, I'm angry!
