\chapter{Be Sure to Maintain Your Dignity When Going Out (4)}

The attitude of the officers who were going out for the training was quite light.

Some people said that a three-day, one-night mobile training exercise wouldn't be so difficult, and that it would be easier if they could escape the horrific operational situation.

``Huh, it's already summer.''

``Whew, the air outside this world.''

``It's so refreshing……''

But reality and imagination were different, and while imagination was easy to come up with beautiful things, reality was a cesspool.

``It's hot……''

``……''

``……''

The officials who continued to walk past 2 a.m. were now completely silent.

Just because a person's body can withstand two days of no sleep doesn't mean they don't experience mental fatigue.

Besides, there was a long way to go, and this was only the first night, and I couldn't sleep even when the sun rose tomorrow. I would have to keep walking, not only tomorrow, but tomorrow night, and even in the morning...

It wasn't that difficult, but it was a series of uncomfortable situations, and the mental fatigue of those who knew that these situations would continue.

Of course, limited to first class and above.

Third-rate and second-rate warriors were starting to feel physical pain in their legs.

Perhaps the only silver lining was that I can see officials in the same situation both in front and behind.

When you go down the mountain, you will see the Hanam Plain, which was open in all directions and has some hills.

That is, it was a flat and even road.

The mobile road runs through rivers of various sizes, more than eight times its length.

In other words, you can get drinking water at any time, and since it was next to a river, it was less hot, and you can even cool off by soaking in the water when you get a fever.

And when you go down the mountain, you take a well-maintained road.

In other words, there was no reason to get into trouble with some evil spirit, a vicious criminal, or a robber in the Hanam land in front of the Wulin Alliance.

Each group was accompanied by an instructor, a student, or a warrior, so it was truly an incredibly safe training session.

Of course, just because they were a martial arts academy doesn't mean they will send their students into dangerous training, even if it means they die, and just because they get lost and fall behind, they don't just say, "We don't need weaklings!" and abandon them.

In the first place, such an environment was not created.

Training always puts safety first.

In fact, what educational institution would put its students in danger?

If you send trainees into a dangerous environment without a guide, or if you force them all into it and say that the one who survives was strong, then that was not an educational institution, but a jar of loneliness.

Even in the military during war, new recruits were trained in safe places in the rear.

So the moon sets, and the feet move forward.

Descend along the ridge north of Uijeongmuhak-gwan and follow the river to the northeast toward Icheon-hyeon.

Turn in front of Icheonhyeon and head southeast along the Yeoha River.

And when you reach Yangseonghyeon at the end, it was exactly halfway to the 500-ri road.

A group of martial artists with rotten expressions pass in front of Yangseonghyeon, a proper city-sized city surrounded by walls.

``Ah, it's a city.''

``Yang Seong-hyeon……''

``It's so hot outside, I wish I could have a glass of cheap beer….''

``I wish I could just eat a plate of properly stir-fried, crunchy vegetables, if not meat…''

Then gulp. Gulp again.

``I want to wash……''

``It's so stuffy I think I'm going to die……''

Some neat people were anxious to clean their bodies so that there isn't a single sticky spot here and there.

And right now there was a civilization that can solve all these needs.

There was a splendid human civilization right there, with rich food to eat for a fee, alcohol to wash it down with, baths to wash in, and comfortable beds to sleep in.

However, you cannot enjoy the benefits of that civilization.

Because entry into private homes was strictly prohibited.

How can I express this sad feeling?

Look at the desperate expressions on the faces of soldiers looking out the windows of trains and freight cars as they pass through civilized villages in their hometown of Qing.

But, since the instructor and the warrior were here, it was not something you can do by pretending not to be an official and buying something to eat.

So, looking at the street vendors with their bags open in front of the city gate, I can only swallow my saliva.

By the way, the instructors were the same.

The instructors who have already reached a certain level were not particularly physically tired, but they were mentally exhausted from being bored and not being able to sleep.

Besides, how can I take care of anything by myself?

The instructors said that carrying a backpack would look bad, so they kept their luggage simple. It was summer, so they only ate yesterday's rice balls, and now they're making do with rice cakes.

The Qing were particularly vulnerable to two weaknesses: boredom and hunger.

Since both of those weaknesses were hit, wow, city! wow, guest house! wow, tavern!

It was fortunate that Qing was wearing cotton.

If not, the peerless beauty, considered the most beautiful woman in the world, would have been watching with a longing expression, filled with desperate longing.

It would have been a major biochemical attack that would have caused a mass outbreak of the extremely vicious disease, lovesickness, for which there was no cure, precisely because it was the expression most loved by the people of the Zhongyuan.

Ah, really, eating fried pork, beef stew, pancakes, and bread by dipping them in clear soup, digging out the insides and putting the meat in, stuffing it all in my mouth until my throat feels like it's going to burst, and then clearing out my blocked passages with a big glass of alcohol, that's it.

But I can't go...

The officials were obviously training, so I can't buy anything to eat on my own.

But it's there, so why can't I have it?

There's so much gold, why can't I go?

Soldiers on the wall look down at the suspicious group passing by, carrying heavy packs on their backs.

I had heard in advance that they were passing by the training center at the State Council, but judging by their appearances, they looked like either peddlers or martial artists, and they looked like prisoners being dragged away.

So the group turns southwest with fixed gaze and steady steps.

And walk.

And walking again.

Keep walking.

I keep walking again.

Walk, eat some boiled porridge, take a break, and walk again.

It gradually starts to spread and sag from the bottom in reverse order of skill.

So what?

``Give it to me.''

``I can, I can…''

"We're not in the same crew. We're on a mission. We have to get there together, even if we die together. Even if we live together, we have to get there together. Give it to me."

High-ranking officials leave the burdens of low-ranking officials behind.

Because that's how the training was designed from the beginning.

The date was close to the full moon of June, and the heat has been rising since spring, so summer was just beginning and it was starting to get really hot.

I didn't know that the Jeongmuhak Hall, located in a lush forest on a mountain, with a wind blowing all year round, and even surrounded by a valley, was so hot that I came out into the world and realized that the world was such a hot place.

As the sun sets, groups of trainees begin to slowly enter the high hillside between the two mountains south of Pyeongdangsanhyeon, where the mountain range lowers down.

And on top of that hill stretches a gray, dull wall, that marvelous structure which the people of the Zhongyuan call the Great Wall, and which the Qing homeland calls the Great Wall of China.

However, it was not a particularly surprising building to the people of the Zhongyuan at that time.

If you live in Hanam, you can see it everywhere, and even if you were not from Hanam, there were magnificent city walls built all over the large cities. If you go to nearby Jeongju or Luoyang, you can admire city walls that were much taller, thicker, and more magnificent.

Compared to that, the Great Wall of China was quite inferior.

When it's sunset in summer, it's winter night.

According to national law, you cannot pass through the Jangseong Gate at this hour.

How could the commander of the Jangseong Military Base so coldly close the gates to the Jeongpa soldiers who were training hard and sweating?

It was not because of the golden box delivered by the Wulin Alliance, but out of respect for the swordsmen of the Jeongpa who worked hard for the country in areas untouched by the officials.

However, the military was not visible at the wide open gate, which was a wise military response.

I happened to be away from my post due to training, but the Jangseong Gate seemed to have become old and was open by itself.

I never opened the gate in violation of the law, and I had no intention of letting them through.

What kind of training was this? Ahem, it's like detox training for alcohol poisoning in case something happens. It's like training to train the liver, which was the most important part of the body, to the point that everything was due to the liver. Additionally, it's training to increase the harmony of the group.

Of course, if the leader takes bribes alone, it will not be a good thing, but if he uses his generosity when the money comes in, everyone will smile and stay on good terms for a long time.

The night, just three days before the full moon, was bright and the early summer heat has subsided, making it a good day for a walk.

The officials keep walking.

The moon shadows of the walking paths begin to tilt, and soon they begin to tilt westward, and finally, as dawn breaks, they arrive at the foot of Mount Bokwoo.

"ah……"

``The mountain……''

The officials who saw the mountain path going up muttered.

The State Council Academy was located on a high ridge of Bokwoo Mountain, which meant that from now on we would have to climb the mountain.

That's exactly six o'clock.

It's not that I didn't know, but this immense sense of frustration that was now washing over me was something that was simply indescribable.

After all, the last and the flower of the march was mountain climbing.

It's quite serious for a mountain climb.

In the gloomy atmosphere, the officials began to head towards the mountain.

My feet were heavy and my calves feel like they're going to explode.

Sweat becomes so sticky that it turns into oil, and whenever skin touches skin, it becomes sticky and uncomfortable.

The third-rate guys, the ones without luggage, were already pushed to their limits both physically and mentally, and had reached a stage where they could move automatically, where they could just take one step forward or backward and the other foot would move automatically.

It's a state where you just move forward without any thoughts, without any feelings, and you don't feel like you're alive.

Even the officials with a lot of luggage were dying.

The backpack of the central plains was not designed very ergonomically, so it feels like you were being crushed by its weight the whole time.

My shoulders hurt so much that they feel like they're going to separate from my torso at any moment, and because my shoulders hurt, my back was also sore, and because my back hurts, there's no place on my body that doesn't feel sore.

If I have stamina, my shoulders will hurt, and if I don't, my feet will hurt.

Of course, Qing was very relaxed.

It wasn't that difficult for the master of Hwagyeong, so now his eyes were sparkling.

Almost there!

I've ransacked the instructors' mess hall. Today was the day the instructors' mess hall was destroyed. I'll chew up every last grain of rice and barley in the warehouse.

Rice, proper rice, not rice cakes, rice!

Qing, who suddenly became more energetic, raised her voice and boomed with her beautiful voice.

``We're all here now! Are you tired, officials!?''

Well, it would be difficult, wouldn't it?

He came with a simple backpack on his back, so it shouldn't be too hard. He wasn't confident that he could get up if he collapsed, but he was confident that he could fall asleep within three breaths.

But if you twist it, you have to become an instructor.

``No!'' ``No!'' ``It's not hard!''

"Then, walk with your shoulders, your back, your chest, and your confidence! I repeat, you can do it!"

``You can do it!'' ``You can do it!''

``Is that all you can hear?!''

The correct pronunciation was "Mo-ok-sori-geu-geut-pa-ke-a-a-an-a-om-ni-kat-ah!" It's a sound that I've heard hundreds of times before.

The officials begin to curse him.

``You can do it!!!'' ``I can do it!!''

"I also send my support to the fellow swordsmen who were struggling right now! You can do it, swordsmen!"

``````Swordsman! I can! do it!!''''''

Then, a sound echoed immediately.

-The best in the world! The greatest swordsman! The only warrior king!

-Martial Arts Center! We! Will win!

It's not that Qing shouts spontaneously.

Making people shout all kinds of nonsense at the end of a march was a part of the training process that was originally scientifically designed.

Qing just sent a signal that he should start clearing his throat at this point.

The officials who entered the mountain path, whether in front or behind him, began to shout evil at each group.

Swordsmanship was the best, Taoism was the best, cheer up our officials, we can do it, we will win, etc.

At first, it was almost a cry of anger.

What nonsense were you talking about when you're already tired and exhausted, your soles feel like they're going to burst, your ankle bones were crushed, your shoulders feel like they're going to fall off, your body feels clammy and damp, sweat was pouring down your face, and you're so sticky and squeamish that you're getting really irritated?

But humans were also secretly simple creatures, and as they scream and suck out the air in their lungs, their anger was relieved.

At some point, everyone gets quite excited and starts shouting actively.

Well, soon this endless march will come to an end.

And. Finally. Finally. In the end.

As we cross the ridge, the dreamy manor and the massive buildings of the State Council Academy come into view far below, across the valley.

One of the officials muttered involuntarily without realizing it.

``It's home.''

At that moment, a thrill runs through everyone's head.

Home! I'm home!

After all this arduous training and self-discipline, I finally returned to the home I had dreamed of!

Even the voices of those who couldn't stand it anymore and shouted, "Home! I'm home!" were heard everywhere.

Qing smiles happily from inside the cotton swab.

Since when has the State Affairs Office been your home?

Well, from now on.

Because it was a training session just to hear those three words, ‘home.'

Walking? Everyone walks well.

Three days without a night's sleep? If it's unmanned, that's about it.

Camaraderie? We'll be seeing each other all summer, so wouldn't it be harder to not become close?

But it's hard for a place to become a home.

Love? Love? Something like that.

It was a training to change the mindset of considering the school as my home.

After hearing this, Sima Chunbong immediately began formulating a training plan, as he understood the importance of belonging to a group.

Without even knowing it, the faces of the officials broke into bright smiles.

Although he looks a bit tired, the sense of accomplishment he feels doesn't fade away.

As we passed through the main gate of the Legislative and Military Academy, the staff took our luggage and served us refreshing iced tea. Everyone hugged each other and jumped up and down, exclaiming, "We did it!"

No, I'm too tired to run around, so I'm just hugging her in a somewhat messy manner.

So, the training was successful.