\chapter{Be Sure to Maintain Your Dignity When Going Out (21)}

Jang Cheon-ho, who was running away with his back wrapped around his waist, felt an eerie fear he had never felt before at the sound of loud, thumping footsteps chasing him from behind.

Every time I looked back, a pitch-black shadow closed in on me. Each time, its size grew ever more vivid.

It was a lot more pressure than I imagined.

Was lightness a skill that could make such a big difference in the first place? Even if it was slow and fast, it was still a master at the peak.

It wasn't a skill that could close the distance by walking or running.

Jang Cheon-ho grits his teeth.

If things continue this way, it's only a matter of time before they catch up. If they want to slow down that destructive method even a little, they'll have to move to a more complex location.

Jang Cheon-ho's escape was pursued by people.

If there were too many people blocking the road and obstructing the view, no matter how much of a minority witch she is, no, was she really a minority witch in the first place? Is she even a person in the first place? The reason she says she was afraid of Mine was because she doesn't know what kind of magic she will use to go wild and become a monster with a fearful face.

However, Jang Cheon-ho did not choose to run away without any plan as he would be caught anyway.

``Daeyoungban, now. Jincheonroe.''

He, Young-Ban and Dae-Young-Ban, reach out to Jang Cheon-Ho's bag.

The heavy, hanging bag loses its weight and begins to flutter, and a dark-colored iron ball half the size of a head appears in Daeyoungban's hand.

Jincheon-roe was a powerful fire bomb that had the power to make the sky tremble when it exploded.

He stares intently at his adversary, who was chasing him with the Great Sword on his shoulder.

I don't think I'll be able to kill that monster with a single shot, but I'm sure I'll be able to inflict enough damage to make it impossible to continue the chase.

Within, Daeyoungban releases Jincheonroe.

The trajectory of the bullet was a rather unattractive parabola for a serious expression.

It looks more like it was missed than thrown.

But the more trivial some skills seem, the more noble they are.

The Jincheon-roe, which fell to the ground with a casual throw, does not bounce back up but begins to spin and roll away.

So the fireball gets closer to the mine.

I felt hazy and intoxicated by a dream.

In the dim, dark dawn, a vague consciousness, like a mind that was not asleep but not awake, wandering somewhere between dream and reality.

Qing was running. He was running.

I don't know why, but my body moved and ran on its own, and somehow this situation felt very natural.

What was this? Is this a dream?

The view crosses the dream world.

I run towards the back of a man I see on the other side, and although the gap doesn't seem to be narrowing, as was often the case in dreams, it doesn't feel particularly important.

And when I turned my eyes away from the man's back for a moment, the whole world was celebrating a grand festival.

A carnivore who kills and kills, drunk on blood.

Death unfolds with every gaze.

It was a delightful massacre by killers who showed their teeth and laughed.

Officials kill followers. They claim that by killing the evil demonic cult, they will ensure the world's well-being. They say that the demonic cult was a corrupt cult, and that killing them will benefit the world. They take pride in killing for the sake of the world.

The common people responded to him, so there has never been a time in the history of the Zhongyuan when the government and the people were so close.

The unmanned slaughters the followers. The old school Taoist priests and monks kill the demonic followers. How much merit will be accumulated by punishing these evil hordes who taunt the people? The Taoist priests laugh. The monks have always lived with compassion in their mouths, but were the demonic followers worse than beasts, beyond their reach?

The warriors of the Ten Great Sega slaughter the disciples. The Marums, representing the Emperor's land, hunt down and kill the unholy traitors. They deal with the traitors who dream of rebellion, cutting off their noses and threading them on thread, knowing that the rewards will strengthen the Sega family, and so they slaughter without pause.

It's our sin.

It was our sin to fight with swords and spears for all the peoples who were suffering under the rule of barbarians.

It was our fault for not allowing the seeds to slowly wither and become extinct under the abuse of barbarians.

The crime of attempting to save this Zhongyuan people, who were worse than beasts, was the very fact that the barbarians had devoured the Zhongyuan and attempted to annihilate them. This was a divine punishment bestowed upon this shameless people. The crime of forcibly saving this terrible people and establishing a nation.

A voice burrowed into Qing's ear, no, what was it? He couldn't hear it, was it me speaking? It sounded like a monologue from an electronic game.

However, Qing sympathized with him.

The cultists had the qualifications.

He had the right to wipe out all these primitive, ancient, uncivilized peoples, drench himself in their blood, devour their flesh, and cry out for revenge.

All the people of the Middle Kingdom were indebted to them, and the present world, life, and the existence of their descendants were all spoils stolen from them.

Before I knew it, the surroundings were covered with desert.

The question of when I ran to the desert was fleeting, because dreams were natural, they were called dreams. The question was fleeting, and because it was natural, it was like that.

The man's back was approaching briskly.

Here was a desert, and all around were the miserable corpses of cultists escaping from the Zhongyuan.

A prisoner's wounds fester and abscesses bloom, dying. A child starving to death rots in a swaddle, and the mother, clutching the rotten piece of meat, eventually collapses, unable to endure the harsh desert.

With every step, desert day and desert night intersect, leaving long trails of footprints, and every three or four steps, a corpse litters the path. It's a truly perilous path.

And then at some point.

It was Qing running through the middle of the Zhongyuan army rushing in and charging at the believers.

And Qing sees his birth.

It was a miracle that such terrible resentment met with justification.

When the followers of the doctrines had abandoned the future salvation they believed in and were left with only revenge and desperately longing for judgment, the judge of the world in the forgotten doctrines, the devil of pitch-black color who would shatter the rotten world, came into the world.

To the Zhongyuan people, the sky was originally black, the pitch-black color was the color of the sky, and the devil of the sky color.

The sound of a man declaring.

If you call us a demonic cult, we will gladly become a demonic cult.

There were no more people in the world, only shameless beasts, so they should be destroyed and destroyed.

Since our spirit and soul will never perish until the very end, it was the law that the world has brought about its own destruction.

Did you do something a little regrettable or not?

There was no grave without a story, so it was only right that Cheonma hates the Zhongyuan, and the reason why the demon cultists of Cheonsan live miserable lives simply out of hatred was the same.

The devil's plan from the beginning was not conquest, but destruction, to exact the punishment for the sins of those traitors who deserved to die.

Because the demon cult was nothing more than a tool to demand the blood money they deserved.

enN1WnIzcFhHMVJuR0JvdkNPc013eUtGTDFCM3paWDlyclo0cnVlcE4xWGJSVkc4QTdwSUkyZ0JWUVUySWNOeQ

That was the moment.

Roll, something was rolling towards my feet.

It was the head of a child who has lost his body.

In an instant, images from another world overlap.

A dizzying landscape where both sides were mixed together, as if two pictures were drawn on transparent paper.

It's an unfamiliar street, but somehow familiar. I don't know where it is, but it's Jungwon, Jungwon.

Qing looks at the head that was rolling towards me.

A dark metal sphere that appears to overlap the child's head.

This was my first time seeing it in person, but oh, this was a wall bomb.

Anyone can see that it looks exactly like a bomb.

It's a real bomb, it's a bomb that looks like it's going to explode.

Suddenly, Qing's eyes scanned left and right.

The corpses of the fallen disciples in the desert.

The common people of Zhongyuan have fearful expressions on their faces on the streets.

Qing's eyes turn towards the front again.

The back of an assassin running away.

Suddenly, bang, my legs hit the floor on their own.

A bizarre mine that stops for a moment.

And stretch your left leg back.

Qingi understood the body's intentions.

I plan to kick it like this.

A master can kick a lump of metal and still be fine, so if he were to kick a wall bomb and hit that hated Mr. Joo's subordinate, the massive explosion would not even leave a trace of flesh.

Then, this mess will come to an end.

There were probably a few wounded people with their heads still intact, and a few corpses. If we just find them and break their skulls, this situation will be more or less resolved.

If the government later says something, why don't you just ask for evidence? An assassin? An assassin of the Emperor sent by the government? Don't you know someone like that? Oh, there's evidence. Do you have evidence?

but.

Mine's body stops.

The trembling, unnatural stillness, as if someone had forcibly grabbed and held me.

Is a wall grenade something that, when it explodes, only deals damage to a certain area like a grenade in an electronic game?

Qing had finished his military service in his homeland, so even if it was a primitive ancient grenade, would he just harm two fleeing assassins?

Besides, this was not the hometown of Qing.

It was a world where there was cosmic mystery, qi, what seemed like mass hypnosis but was actually a real spell, and there were also organ-generating rituals that boasted ridiculous technological prowess.

Is the wall grenade really a primitive ancient grenade?

Qing's gaze fell back to the floor.

The author's wall-crawler on the dirt floor, the child's head on the red sand floor, soaked in the blood of the dream, appeals to the blue with its eyes.

At that moment, Mine's eyes turned blue.

The color of the clear, blue sky, not the sky of the Zhongyuan, but the blue of the blue sky.

Miss, even if those bastards spill something like a wall bomb, it's dangerous.

The situation would be over if you just kicked it.

Seriously, man, this fight was getting dirty.

Qing throws herself on the floor.

The iron ball rolling on the floor still hugs the head of the child in the dream.

The child's head screams.

\textit{\textbf{-Why, why didn't you see it too! Didn't you join in our outrage at our sorrow? Didn't you understand us?}}

\textit{\textbf{-But, how! How!}}

Qing smiled bitterly.

\textit{I never liked these uncivilized bastards from the Zhongyuan in the first place. Those piece of trash, I held a ceremony just a few years ago to make sure they were completely ruined.}

\textit{These Zhongyuan people were blinded by gold and abandon their human nature, do not hesitate to be cruel to those weaker than themselves, and commit reckless acts all their lives for the sake of saving face, but when you look at them from the outside, it was surprising how shallow these guys were when it comes to saving face.}

\textit{But I'm also a bastard.}

\textit{Even though I'm wearing the mask of a witch now, let's say I kicked a wall bomb and committed that sinless, yes, not sinless, very great original sin.}

\textit{If I do that and cause them to die and get hurt, how will I look at Master's face?}

\textit{I'd be ashamed to face my teacher, and I wouldn't be able to raise my head in front of my friends. How could I smile and agree with the elders, who were talking about the great blessings and agreements of the political faction?}

\textit{In fact, what's the big deal if fifteen people in the Zhongyuan die?}

\textit{I'm also a pleasure killer who enjoys killing people.}

\textit{And whoever gets caught up in it and dies isn't my fault. It's the fault of those assassins who used wall-crawler grenades, those scum of humanity.}

\textit{\textbf{-So why! Why!}}

It was the scream of a child, the scream of countless dead cultists, the scream of the magic that filled their bodies.

Qing hugged the child's head tightly.

\textit{Well, I'm a selfish person from the start, right?}

\textit{I understand your resentment, but I'm not making excuses or denying the fact that the civilian, military, and even the martial arts world carried out ethnic cleansing.}

\textit{But, more than that, my priority was to become someone that everyone at Ximen Qing can be proud of.}

\textit{I can even block grenades by flying my body. Wow, how proud I would be if my Master and Teacher knew.}

\textit{\textbf{-How, how can you be so heartless! Out of your selfishness, out of your petty desire to wear the guise of a virtuous person, were you willing to turn a blind eye to the injustice suffered by these countless people?}}

\textit{Well, to be honest, more than just appearances?}

\textit{You guys have nowhere to go without me.}

\textit{So, if you don't want to lose this body, I think you guys should protect it.}

\textit{Can you stop one wall bomb?}

The head of the child who was being held tightly twitched as if in shock.

\textit{\textbf{You tell me to take care of it myself, seeing our miserable state, how could a person, a bitch, no, how could we, us, do that?}}

Heavenly Demon True Qi stammers as if he was speechless.

I feel a little sorry for Qingdo though.

\textit{So what were you going to do, trying to escape from my body? Throw away the Heavenly Demon Spirit? Throw away the mental parasite? Throw away your leader? You're going to leave? I guess it's fate that I've been chosen by a wicked landlord.}

\textit{And what did you bring?}

\textit{You kidnapped a stranger and forced him in, so aren't you the ones who were occupying the place by force?}

At that moment, Tok,

A vibration, as if something was breaking or tapping inside the wall bomb.

In an instant, pitch-black magic energy from Qing's entire body heads in one direction.

As the center of the back panel was pushed out, the original shabby fabric was revealed, and all the magic energy was suddenly pushed into the front of the blue, and the overwhelming true energy like the sea formed a barrier in front of the long-term-

… … !!!!!

A huge explosion rings out.