\chapter{Be Sure to Maintain Your Dignity When Going Out (19)}

Contrary to Yeongban's urgency, Heavenly Blossom Sword's back gradually recedes.

As if the chase up until now was a joke, as if saying that he could no longer hang out with me, his back was moving away step by step.

The ground was hollowed out by the trampling of human feet. Dust rises like a bomb has exploded.

I can't even imagine how powerful this magic is.

Youngban does not know this lightness.

The original method of ascent was to resemble the wind.

As your level increases, you become faster and lighter, so look at the expressions that describe the high levels of lightness.

It was said that the portrait was like running on blades of grass without breaking, running on a snow field without leaving footprints, and running on water without leaving footprints on a wide plain.

But what kind of study was that majestic back view, that steadfast vanguard back view?

But with each step, a loud noise erupts, the earth shakes, pillars of earth rise, and stones fall down.

Just destruction to push my body forward.

The actions of a tyrant who tramples the entire world for his own purposes were the worst of the worst.

The Heavenly Demon Lord's Forest, the Heavenly Emperor's Fall.

The earth breaks and dust covers the sky.

We must kill them all.

We must kill all those who were entangled with the palace.

The skull must be shattered into pieces so that even its identity cannot be identified.

Because, because.

Perhaps, it was also the first pure murderous intent that the Qing had in the Zhongyuan.

Not because he's a piece of shit, or because he's someone you can kill, but because he's someone you have to kill.

why?

Because that damn traitor's limbs must not be left behind in the world, not even a single trace.

Because we have to completely wipe out those beasts of humanity, as if they never existed in the world.

From the Qing dantian, from the dark shadows of the lower, middle, and upper dantian, a sticky, black evil energy seeps out.

It's not just the danjeon.

A certain energy flows out from every corner of the blood vessels, the eight meridians, and all the passages.

Like sticky blood spreading across the floor, yet never stopping, a massive, irresistible flow that fills the inside.

In Qing's ears, in his mind, inside his internal organs, his heart beats wildly, whispering blood-curdling cries.

Tear those hypocrites to pieces.

We still haven't forgotten the grudge.

Chew the flesh of the abominable Zhou family, wipe out all of Zhou family's limbs, and wipe out all of that abominable group of traitors, leaving not a single one behind.

Some scenes flashed through Qing's mind.

The sight of people passing by.

Bruises covered his entire body, his clothes were torn and tattered, and what could be seen through the gaps where the wind was blowing was a shabby torso with skin and bone shapes sticking out.

That past.

There was a harsh time when the Mongolian barbarians conquered the Zhongyuan and treated all the peoples of the Zhongyuan like livestock.

No, they were treated more harshly than livestock, and this must be the reason why this dynasty lasted less than a hundred years.

The scenes keep flashing by.

A man who swings his sword, saying that if things continue this way, only the extinction of all Zhongyuan peoples awaits him.

At this time, a famous believer with the surname Joo stood up from his seat.

When they attempted to rise up against the cruel empire, a religious group called the Ming Cult rose up with tens of millions of soldiers, spears and swords, in support of their family's cause.

The blood of countless famous scholars flows through it.

The general was the one who gives orders, and the soldier was the one who jumps into the danger with a sword, so most of the blood that flows was from the Ming sect.

And finally, the Zhou clan won and a new dynasty was established, and the present country was a great legacy built on the blood of the Ming dynasty.

Thus, the Emperor Zhou declared to his comrades and soldiers, the Ming sect.

You have the name of a religion, but you deceive and delude people with empty doctrines. You were evil and treacherous villains.

How dare you misuse the name of Mingming? You were a terrible group of devils, yes, a demonic cult.

I will uphold my destiny and destroy all of you demonic cultists to establish justice in the world.

Qing's heart burns coldly.

It was the scene of the world's ugliest betrayal.

The disciples were dying. They were trampled to death under the swords of the Zhongyuan people they sought to protect.

A comrade who fought alongside him was stabbed in the chest, a close friend who talked about a hopeful future in the midst of an endless war brutally tramples his wife and daughters, and those who watch sit on the corpses of the father and son of the prisoners, laughing and raising their glasses.

The resentment of countless dead people cries out.

Yes, if you say we were devils, then we would rather be truly great devils, devils that cover the sky.

The most angry man among them engraved all his resentment in his heart.

Tens of millions of grudges coagulate, creating the most terrible energy and destructive force in the world.

A true magic crystal that covers the sky.

Heavenly Demon True Qi. Of all the hatreds in the world, it was the darkest, the most intense, and the sticky, unshakeable desire for revenge.

The blue pupils lose their color.

The original blue, the clear and clean sky blue pupils were just dyed in pitch black darkness, and even the ominous malevolent stars disappeared, leaving only a bottomless pit with no trace left.

Since the resentment of people has reached the sky and covered it, it was only natural that the stars do not shine.

And now.

What on earth has changed in the world?

The barbarians of the previous dynasties treated the Zhongyuan peoples as mere property and goods, like cheap cotton cloth and utensils that could be torn and broken and replaced at will.

What was the difference between the current emperor and them?

They block the mountain without hesitation, harm the civilians, and ultimately burn them to the ground, so they don't care if millions of innocent people die.

Their intrigues have caused assassins to overflow into the city and set buildings on fire, leaving civilians as mere property, easily replaceable.

If our end was betrayal, we will blame our eyes for not recognizing people.

This was the way of life. Isn't this the cruel world where those who deceive and were deceived were evil and those who were deceived were foolish?

But if our blood was shed in vain.

If the empire built on our blood was no different from before, then the dynasty of beasts that changed from barbarians to Han Chinese continues.

Then why on earth did our blood have to flow?

The blue dantian swells as if it was about to burst.

A huge energy composed of tens of millions of souls bursts out from within a single individual, filling all the energy channels beyond the dantian, filling the middle dantian, and filling the heart, and soon all the blood in the body becomes black with deep-seated resentment.

Somewhere in the upper chamber.

At the center of the entire dantian and blood vessels, immersed in pitch-black darkness, was a narrow cavity protected by a pale curtain.

All the spirits were stuck in a small space, their usual grumbling and meowing appearances were nowhere to be found, and all of them just had anxious eyes.

All the qi look at one platform.

Looking only at the back of the Wolnyeojinki, who was stretching out her arms straight while spreading her blue curtain.

The expression on Wolnyeojinki's face was always indifferent and unreadable, but now she was expressionless, just staring into the darkness beyond where nothing could be seen.

It smells.

The unpleasant smell of Mr. Joo, the smell of that vile collaborator, that traitor who deserves to be hated by all.

It was a stench that was unbearable, not just in the nose, but in the soul, a stench that permeated the spirit.

And finally, the terrible stench of a group of men visible on the other side, men who dare to come here with swords in hand, hits you.

The blue lips draw a curve.

Yes, you guys, you guys.

The black veins that had risen all over my body suddenly swelled up and cried out to get rid of those ugly things.

Qing pulls her arm with all her might.

The magic ring number could no longer be called a prime number, because the prime number uses white elements, so the pitch-black magic ring, which was already as dark as a hole in the world, could no longer be called a prime number.

Qing was shaking up the world.

A huge black dragon hovers above it, tearing through space with its four huge blades.

The guy was holding a knife.

The frost there, the blackness? Just a small amount of blackness? The corners of Qing's mouth curved into a sneer, and just like that, slap.

Your fingers naturally dig into the penis, and also naturally come out in the opposite direction.

The blade that broke into five pieces, the thing that crumbled into even more pieces, or rather the bones and flesh that was the thing.

``Wh. What-''

The sound of someone shouting.

Qing stands still, her eyes rolling around him.

And then, stretching out his arm that had reached down to his waist, he made a fist and pointed it at the enemy with only his sword in it-

``It’s dangerous!''

I was pushed back by the force that Jang Cheon-ho was pushing me with, and I fell over.

Jang Cheon-ho was about to shout, ``What was this?'' but stopped himself and couldn’t do so.

A single black line cuts through the air.

Pfft. A soft sound.

It was a sight to see the head of the five thugs who had pushed me being shattered in all directions.

What the heck? Jang Cheon-ho's thoughts were frozen.

Oh, the Wisa was a first-class warrior, a warrior on the verge of peaking. How could such a warrior lose his head to a single point of a finger, a single finger aimed from afar?

As Jang Cheon-ho blinked, Qing tilted his head, and instead of stopping, he tilted it further, until he was lying flat on the ground, looking at the body of the deceased who had collapsed.

As if he couldn't understand it at all.

I really can't understand it.

What the heck? Why was that bastard protecting my comrade and dying in his stead?

There's no way Mr. Joo's people would have that kind of obligation, right?

My master betrayed and murdered his followers, who were like family to me. How can those mere servants show such loyalty?

So, why us? Why us?

Above the head of the standing Qing, a blade draped in a vivid purple aura falls.

It was Jo Baek-ho's Hwang Eun-ja-ha-gong.

``I’m dead!''

Jo Baek-ho's shouting was not a foolish attempt to inform you that he was attacking you even though it was a surprise attack.

There were times when people just need to raise their voices to find courage.

But even if he hadn't shouted, the result would have been the same, so Qing, without even looking back, stretched out his left arm behind him and grabbed Jo Baek-ho's face with his huge hand.

Jang Cheon-ho shouts in horror.

"for a moment-"

The sound of a single life being torn apart was truly fleeting.

The headless body of the white tiger was falling to the ground, trembling, its nerves still trembling.

It was the moment when Jang Cheon-ho swallowed his saliva.

The sight of Mine blurring for a moment.

Boom! A sound that reaches your ears a beat later.

And then, before you know it, a huge demon falls from high above, blocking your view.

Jang Cheon-ho's blade embraces starlight.

A black beam of light coming in a straight line.

Against him, the swords, drawn in a somewhat slow circular pattern, barely collide and touch each other on the forehead.

And as a result, Jang Cheon-ho's torso bounces off and bounces twice before rolling on the floor.

He jumped up as if he were a swordsman using a sword, but Jang Cheon-ho's expression was one of complete incomprehension of what was happening.

``Checkup, dog!'' ``Dog!'' ``Dog!''

Meanwhile, the shamans, equipped with medical equipment, surround the villains and circle around them.

Although the number of people was insufficient to fill all five points inside, it was a type of Five Elements Examination that doubled its effectiveness just by filling the five points outside.

Jang Cheon-ho grits his teeth and flies.

Filling the empty spot of the swordsmanship, he stands in the direction of Mokyang and adds sword power, and the swordsmanship with the addition of a supreme master applies even heavier pressure.

Screening was a skill designed for many to deal with many people.

They constantly attack and attack the enemy, and they show the results of their long training by hiding each other's weaknesses and complementing each other, and by acting as if multiple bodies were one in both offense and defense.

With two blades flying at each other, it's impossible to focus on one.

If you try to engage in a clash of strength with your weapons, another sword will stab you in the back. If you try to strike away, another enemy will support your back and block it. You will also push each other's backs to double the power of your charge.

As the straight and curved lines arranged in the five elements were aligned, the sound of clashing loudly resonated without any respite as Qing repeatedly swung his two swords.

It was a constant assault like a torrential downpour pounding against a tent, but the expressions, the contrast between them, were strange.

The desperate expressions of the assassins using all their might.

But at the center of the storm, the enemy's gaze was just glaring with his eyes half-lidded and filled with venom.