\chapter{Be Sure to Maintain Your Dignity When Going Out (14)}

Flying dark clouds.

An ambush by assassins disguised as merchants and farmers. Even masked assassins rushing in from above, in front, behind, and from the sides.

This was also the reason why even a worn-out drone can still walk around in a dizzying situation that makes one lose their mind.

It's not even about targeting the blue.

The assassin's target was Wan Talu, so the moths rushed in with the idea that if they could somehow get through the Thousand Flower Sword and land a single blow on the target (poison was the assassin's friend), their lives would turn around.

Protecting others was much more difficult and challenging than protecting yourself.

An attack aimed at me will inevitably end up being stuck in my body, but an attack aimed at others will block my vision from the very beginning.

On the other hand, other people's bodies do not move as freely or as we think, like our own limbs.

So, the actions of the Qing Dynasty were truly divine and not at all lacking.

how?

Because it was very sensitive.

Blue can be sensitive if you want to be sensitive.

Originally, even before entering the martial arts world, Qing was very good at observing people's expressions and reading their minds, and he was also very good at understanding other people's personalities, so he was very good at social skills and perceptiveness.

It was the ability that became the source of the old man's murder.

But, what good was it if you only have the ability?

I'm not using it.

There was a kind of line, a limit to indifference.

In front of people he doesn't know well but needs to know well, or people he needs to look good in, he digs into their weaknesses like a ghost and gains favor.

When you become completely comfortable with someone, you become completely comfortable without any consideration for their feelings.

Or I'll just see him once or twice and leave it at that. Or, if I feel like he's a guy I can treat around like crazy, even though it might sound a bit rude, I'll just ignore him and act roughly.

However, human abilities were originally revealed in times of crisis.

Before leaving for the island, even if it was a crisis in my hometown, it was just a mistake that made me have to hear unpleasant things, or like having to go to a company dinner I didn't want to go to.

But in this primitive ancient Zhongyuan, things were different.

When we say crisis, we mean a real life crisis, a life or death situation. We were literally standing on the edge of a knife that was a matter of life and death.

And, above all, Qing was always treated as a troublemaker or a goalkeeper, and his target was Wan Talu.

Rather, this situation makes me feel a sense of crisis.

Even if I get hit a little or get stabbed somewhere, I just have to lie down for a few days and that's it.

A weak dog-like creature would be in danger of death if hit with just one poisoned needle. Wouldn't it be a truly dangerous target for protection who would die if hit with even one blow?

In a crisis, sensitivity blossoms and its scope expands explosively.

The eyes, left, right, up, and down, move at a speed that was difficult to do on purpose, and the head rolls, memorizing every single detail of the terrain, people, movements, and expressions without missing a single one.

That girl, she's keeping an eye on him, look at her, why was she slowly closing the distance in the middle of a chaos while pretending to be scared?

Why was the soup vendor on the main street, amidst all this chaos, carrying a carrying pole on the right? If you want to protect your precious soup, you shouldn't be carrying it in a back alley or in someone else's yard, but rather, you should first take care of your own carrying pole.

A stream of air, one arrow, two daggers, a bunch of needle-like things, the order of contact, left rear, left rear, right rear.

And then two, no, three assassin bastards jump in.

The net mass that was caught on the side of the blue mandala, and the well-packaged mandala were left as is.

A dagger passes just over Wan Talu's buttocks.

Qing gets his foot caught in the net and pushes it away.

They say your leg strength was three times your arm strength, right? Qing doesn't know if that's true, but he knows that legs were stronger than arms.

Before Wan Talu could even grab his nose, which was stuck on the ground, he swept across the floor in a huge circle.

A sweeping kick with someone else's body.

Wan Talu's body, rotating around Qing's ankle, collides with the assassin's calf from the front.

The assassin, lying on his side and floating, stretched out his neatly gathered fingertips, and, Whew, the damp and moist insides of the person, this ecstatic pressure of a foreign body squeezing them, and then the coolness of the fingertips passing through the squishy intestines, piercing through the hardness, tearing the back skin, and meeting the blood-soaked skin with the air followed.

Qing, who had pierced the assassin's stomach and all the way to his elbow, turned around.

A wedge, an arrow grazes and sticks into the ground.

The oversized decoration on his elbow slaps away the assassin rushing from the left, and swallows all the flying needles into his body.

Meanwhile, the national carrier reveals its true colors, swinging it with a large movement to try to pour the contents of the barrel over it.

But since he was already concerned about the target, the moment he threw the dagger that Qing had captured before, the relic of some assassin whose number he had forgotten, aiming at the porter's dantian, ah, aiming, Qing realized his mistake as soon as he threw it.

And the dagger that was shot gets stuck in a very terrible spot, below the dantian.

It was said to be the greatest pain a man can feel, and the trajectory of the soup cart, which had been drawing a large parabola, regains its freedom before reaching its destination, and with a slap, hot oil was poured onto the afflicted spot with a characteristic sound.

``Ugh!''

Thanks to this, one of the assassins was thrown over and rolls on the floor.

The moment when Qing's liver and gallbladder become slightly cold.

Miss, what's with the oil, you crazy bastard.

But it worked out well, so that's all.

At that moment, the last weapon he had captured earlier, a dagger, struck Qing's back, bang!

It wasn't a slur, it was a slow attack. It seemed like it didn't have enough strength to break through the compressed muscles imbued with the Qing's self-defense energy. It felt like a stinging wound had formed on the skin, but it was nothing more than a little bit of relief.

In the midst of all this, Qing focuses on the one remaining man and the expression on the woman who was screaming.

The assassin who was rushing towards me frowned and turned around, as if he was planning something for the future.

And the woman who was pretending to be confused and screaming as she passed by suddenly tripped over my heel and fell forward with a thud.

And on that collapsing landing site, there was a net-wrapped Wan Talu, and the falling woman has already pulled out a short skewer-

Qing pulls his foot back sharply.

The net snapped shut, sending Wan Talu's body sweeping the floor backwards, and the female guest, instead of hitting her target, slammed into the ground.

Taang, the sound of a crossbow being snapped.

In the midst of this, two more assassins rush in.

Oh, it's so endless, it's so endless.

Qing sticks out his tongue and stamps his left foot.

Just above Wan Talu's head, as he was sliding backwards, the net was stopped by Qing's heel.

Then he flashed it again, tucked it under his side, took a light step, then a heavy step, and bang!

Two steps containing the power of Jincheon Magic crushed the buttocks of the female guest who was trying to get up, and the terrifying technique that dug a hole even in solid rock trampled the person, causing flesh and bone fragments to burst out in all directions.

Leaving the explosion behind, Qing picks up speed again.

Wan Talu was completely out of his mind.

Well, when the body was just wrapped in a net and wriggling, it was thrown, pushed, sweeping the floor, spinning, falling, and being lifted again… …

My field of vision keeps changing so much that I can't focus on anything, and the only things that pass by in the scenery that passes by without me noticing were blood, veins, and bursting blood.

At first, Wan Talu shouted loudly, "Let go of this! Gently! Please! Get rid of the net first!"

If a person continues to be swayed, he or she will inevitably lose consciousness and become confused.

And then, I just swung it and it got thrown, and I lifted it and it got lifted, so I didn't even know what state my body was in.

And the sound heard in my hazy consciousness.

``Ha, gasp, huh, huh, ugh.''

Irregular, rapid breathing.

When a person was too out of breath, the breath coming in and out of the body collide, causing a choking sound to escape from the windpipe.

That would be the case.

Even if he was a fierce instructor at Ximen Gate, it would not be easy to swing a single man and fight against the enemy.

Excessive visual stimulation dulls a person's sense of sight. They become invisible, yet able to see.

And when a person turns off one of their senses, they tend to allocate the attention they had been focusing on to other things.

And since I was tied up in a net with my body spinning around, I naturally had no choice but to focus on hearing.

The sound of the West Gate instructor's breathing was so beautiful that even the sound of his breathing was not irritating to the ears.

There was a sensuality in the panting of a woman.

The instructor, who was once so confident and firm, was completely disheveled, unable to hide his breathing, which sounded like a scream that could not be suppressed even if he were to be killed by force.

Why?

Yeah, that's right.

Wan Talu's expression sank.

At this moment, my shaking body and the tied-up situation were gone, so what was left was a clearer mind than ever.

And then he opened his mouth with a solemn expression-

``Leave me alone.''

I bit my tongue hard.

The voice he hears.

``Ugh, I’m going to shut up. Huh, huh, and then, ha, I bite my tongue.''

But I already bit it.

Well, you shouldn't open your mouth carelessly when you're shaking like a burden.

"You're clearly tired. Let's get started. We'll get ahead and block the road. Yeon Baekho, take the lead and find a suitable spot. It needs to be somewhere we can force them into the alley. This was a beast hunt."

Unlike those lowly assassins, he couldn't reveal his true identity. He was driven to a remote location, as it wouldn't be a good thing for others to see.

If you block the roads in front and behind them and open up a back alley, they will run away there like a chased animal always does.

I don't even know if that's intentional.

Or even if they knew, what could they do? All a mere beast could do was run away and hope for some luck.

This was what hunting beasts meant.

It was also a shortened slang term in this group, a command close to a code.

``Okay, Youngban.''

The man called Yeon Baekho suddenly increases his speed.

And most of the group followed suit, picking up speed, so they seemed to have been running slowly, but they were quickly moving away.

Since he will be blocking the rear himself, it was only natural that there will be more people blocking the front.

A middle-aged man, who had been watching the people ahead, looks down at the bloody tragedy that continues below.

To this extent, isn't it a level of divine power that can be said to have been underestimated, or rather, to have been true to the rumors about the Cheonhwa Sword?

A middle-aged man laughs bitterly.

How can you evaluate the level of martial arts and achievements of a woman like that in the first place?

This divine power was a completely different aspect from the divine realm.

A woman who knows how to fight, how to battle, how to wage war.

enN1WnIzcFhHMVJuR0JvdkNPc013dzBTZHNJTU5nOHgvd1B6WGZoQVA1NG9aVUI3VWQrK3UxbG9ZbXJvYTBVag

What about those rascals who call themselves martial artists?

In fact, if you were to call their battles, they weren't really battles. They were just sword fighting, announcing their names, making a fuss, and keeping things formal.

This tended to be especially worse for those with higher levels of skill.

Even if you're just a lowly player, don't you know how to fight a proper battle? Even then, when a high-level player appears, they'll spread out their positions, set up a stage, and have a life-or-death battle similar to a battle of the greats.

But that woman was not Heavenly Blossom Sword.

He has no hesitation in slaughtering his enemies, and he has no interest in maintaining the ridiculous appearance of being unmanned.

They pick up, throw, and discard the enemy's sword, use their weapons roughly, swing their weapons, aim for the enemy's vital points, and use what martial artists call despicable methods. They do not hesitate to use any means necessary for victory.

She was a woman who knows how to fight.

And a martial artist who knows how to wage war was very dangerous.

Above all, it was even more so if he was a world-class talent who was rumored to be the next best in the world.

A murderous intent appears in the eyes of the middle-aged man.

Because she was a woman who must be killed.

A strange light appears in Qing's eyes.

It was a look that could not be seen by someone who was already exhausted and out of breath.

The term "breathlessness" refers to a state in which the body cannot provide the necessary breath even though the heart was beating hard and pumping blood.

So the lungs try to take in more air with more force, and even then, the heart works harder to circulate blood.

This was a process that only gets worse, and when it reaches this point, the person's mind becomes confused and their eyes cannot help but become clouded.

But Qing's eyes were calm.

Because, in fact, it's fine.

So I just thought to myself,

Look at those kids.

I pretended to be tired, so now it seems like you're finally trying to do something?