\chapter{Be Sure to Maintain Your Dignity When Going Out (18)}

In the hometown of Qing, there was a saying that even the king was cursed when he was not present.

However, the people of Zhongyuan do not curse the emperor even in places where there were no people.

Because if you get caught you die.

What if someone were to hear this and say, "That bastard cursed the Emperor?" The verdict would be handed down after the entire family was executed.

A family was the basic rule, but three generations of relatives were massacred on average, and if you use a little harsh language, you have to watch the destruction of a whole family, with even eighth cousins of your in-laws being beheaded.

Even because his own execution was the last.

Because Qing was not born a native of the Zhongyuan, he cannot understand these fears, the greatest taboos that flow through the blood of a people through long experience and witness.

However, as I could roughly guess, this fear of the people of the Zhongyuan continued and was still ongoing even in their homeland of the Zhongyuan.

The ruler of the Zhongyuan was always an absolute power, a real divine being who owned both the property and the lives of the people.

So, Qingdo's heart suddenly drops.

In the past, when I was a wanderer, I could have confidently declared that if the emperor or the ruler was not human, he was not a human but an animal, so beat him up.

Now, I have submitted my discipleship to the Shinnyeomun Gate. To be exact, I have not submitted my discipleship, but I am still an honorary disciple.

If a skilled person comes forward, what could the government troops not do to slaughter hundreds or thousands of people?

If you don't get caught up in tactics and fall down exhausted, if you jump out and hit well and launch a surprise attack, you could continue to kill government troops for decades, causing tens of thousands of casualties.

Of course, this was an impossible story in the past when the level of education was not high.

Even back when Hwagyeong Muin was the world's greatest martial artist, the government officials held a similar level of power to today's. No, back then, the Mongol barbarians were conquering the Zhongyuan, and their armies were cavalry, making them even more powerful than they were today. (That's why they all rose up and overthrew the dynasty.)

But the level of the masters was gradually increasing.

Now that there were only a few martial artists in each castle, and even after the peerless martial artist known as Mucheon Daeje showed off his martial arts skills, the government has become very afraid of the martial arts world.

However, the martial arts world has always been afraid of the government officials.

Where was the expert alone?

What about the master, disciples, brothers, and members of the sect?

Gosoo, don't run away to avoid my body. The temple will burn down in the bombardment, and your disciple will become a traitor and your family will be wiped out.

It was not something that can be protected by just a few superhumans.

So, Qing's heart couldn't help but sink.

No, what was it? A general's sword?

You broke the sword the emperor gave you?

Did you just break it?

If you say that this sword was cheap, it was the same as saying that the Emperor's grace was cheap.

negative.

No, that can't be.

How could I just throw away the precious sword bestowed by the Emperor?

And on the topic of assassins, what kind of thing was Cheon Eun-ssi doing? Do you expect me to believe that?

What kind of guy with a sword was committing an assassination?

anger.

Who was this kid trying to fool now?

Don't be fooled, never be fooled.

It seems like they're waging psychological warfare because they can't catch him with light swords right now. Even if the kid was an assassin, how dare he use martial arts to drag the palace into it?

I won't kill this kid nicely.

Adding the crime of treason to the crime of assassination, I'll make you chew and eat every bit of flesh you have. I'll make you chew and eat everything except your molars, really. No, even your molars. If you don't have teeth, you can chew with your gums or swallow them raw.

negotiation.

If it turned out like this, and I say I didn't know, then it was the guy who threw the general's sword who was at fault in the first place. Can't I just say that I didn't notice because the management was a mess?

I also have the Empress Dowager's jade tablet.

I said I was a princess, so wouldn't that be considered treason rather than just treason?

Then, Qing's eyes flashed.

Hmm? Wait a minute.

Am I a princess? Me? Me?

Aren't I at Ximen Market now?

I am now the world's greatest witch.

Five stages of acceptance, dramatic resolution in three stages!

Qing's expression changed suddenly.

Then, he raised both arms in a flash, and a strange mass of energy, a twisted demonic hand, was emitted from the back of both hands as if to show off.

"This was the very proof that the original woman has reached the realm of the Demonic Phantom! Because! The original woman was the Minority Witch! That Minority Witch!"

Suddenly, a small group of witches introduce themselves in a loud manner, and people's attention was drawn to them as if they were another spectacle in the midst of this chaos.

But that was only for a moment.

``Hahaha, what a sword! A sword given by the Emperor? Ha, the Emperor was such a beggar, how could he give me such a sword as a favor! Even a piece of dog meat thrown to a dog on the side of the road would be more gracious than this!''

``You, you bitch! You’re so rude!''

"How shameless! How pitiful that the Emperor must entrust the sword to a lowly mere mortal! He has a mere fool who can't even capture a single Great Demon Witch, and he calls him his subordinate!"

``Are you crazy!''

"Yes! I'm crazy! Villagers! Look here! This was the general's sword bestowed by the Emperor! If you force it, it will snap, but even if it were carved from wood, it would be stronger than this! Either the Emperor was poor and used a cheap one! Or, oh! This was an empty container! Don't you understand the Emperor's profound intention to break it while using it and then die as a traitor?"

``Everyone, shut up!''

Yeongban became confused and shouted.

Aren't there crazy sounds that come out that were beyond imagination, that you've never even imagined?

``Now! Look again! This was the Magical Hwanso!''

The twisted hand made of steel clenched into a fist, and the thumb thrust its sharp nail through the gap between the index and middle fingers.

In fact, this was a very old expression used not only in the Qing homeland but also in half of the world, including the Zhongyuan!

"And this too was a magic illusion! What on earth does the Emperor do, and what has he done for us? His officials commit tyranny! They feed their own stomachs by sucking the blood and sweat of the common people! The world was overflowing with tears of blood, yet what does the Emperor do?"

The civilians who had been trying to sneak a peek at the assassins' retreating spot also immediately turned their backs.

Because there were so many cases of trespassing everywhere, with people rushing into any house they saw, I realized that the sound I was hearing was a terrible sound that put my life in danger.

They say Madura was a crazy witch, but she really was crazy. I didn't see anything, I didn't hear anything.

But, um.

It may sound crazy, but it's not wrong.

The common people only expressed sympathy inwardly.

``The Minor Witch was calling! The Son of Heaven, you bastard! The Son of Heaven, you fucking bastard! I recognized this bastard as a yellow bastard from the time he was messing around here and there! At a time when management was more fearful than compatibility, how does a profligate, profligate bastard have the qualifications to be the Emperor! I hope you receive heavenly punishment and live a thousand years and ten thousand years! Long live! Long live! Long live!''

``Shut up! Please! Just a little!''

``"Minority witches don't listen! Minority witches curse the Emperor! The Emperor's little dog! Only those who agree, follow me!''

If the son of the emperor was a bastard, it would be like insulting himself due to his bloodline, but since he was just saying whatever came out of his mouth, there was no such self-reflection.

Youngban was very vividly aware of what it meant to turn around and what it meant to be delusional.

``Yes, yes, you bitch, Heavenly Blossom Sword! How dare you, Heavenly Blossom Sword!!''

Yeongban calls Heavenly Blossom Sword.

It seems like she's desperately racking her brains in the face of a crisis, and her intention was to loudly proclaim Heavenly Blossom Sword, who was now pretending to be a minority witch, as Heavenly Blossom Sword.

``Heavenly Blossom Sword!? That’s right! I am the Heavenly Blossom Sword! I am the world’s most beautiful witch, Heavenly Blossom Sword! That’s right! From now on, I will use the Heavenly Blossom Sword! I will stand on the heavenly flower! I am the Heavenly Blossom Sword! No, it’s not even the Cheonhwa Kwon, no, it’s not even a martial art! I am the Cheonhwasu!''

``No, what-''

It was the price of underestimating the blue beak.

Now that I have evolved into a minority witch who claims to be the Heavenly Sword, I am speechless.

And Qing didn't miss that moment of shock, that moment when he was speechless and dizzy.

``Okay, I’ll give you back the general’s sword! Here, take it!''

Qing throws the handles and blades on both sides high into the sky with all his might.

Yeong-ban was startled and immediately jumped up, stomping on the ground. At that moment, the Qing Jin-gak repeatedly struck the ground, and with a loud bang!! he immediately turned around and ran in the opposite direction.

Yeong-ban desperately reached out, and luckily managed to grab both parts of the general's sword, before he noticed Qing's figure disappearing behind him.

Why were you turning around and running here?

Why? Your subordinates must be chasing you.

At that moment, Youngban becomes lost in thought again.

Will his subordinates be able to handle the fact that Heavenly Blossom Sword was not a supreme being, but a demon who has mastered the world's most vicious magic?

However, Youngban had already launched himself, and had not yet learned the divine technique that would allow him to switch from a fully accelerated leap midway.

It was a moment of intense regret, not because I couldn't learn it, but because I didn't learn it.

The lightness that Yeongban chose when entering Hwang Eun-mu-go was not the Hwang Eun-je-un-shin-jong, which allows for changing direction in the air, but rather the speed, which was chosen with only speed in mind.

Meanwhile, a cheerful horn sound, beep beep beep beep, rings out. It's a strange horn sound that somehow makes me feel like I should be calling out the name of the country with four letters, "Dae-ae-myeong-je-guk" and "Guk-hyeok."

Yeongban's expression becomes more urgent.

That bitch was after my subordinate now!

Qing blows the whistle and draws the assassin dregs out, making their heads spin.

I hadn't thought about it before because of the sudden appearance of the general's sword, but now that I'd taken on the disguise of a minor witch, I'd regained my composure.

Why would an assassin suddenly deceive himself by saying, 'Oh my, the sword bestowed by the Emperor!'

My eyes rolled back and I threw away the general's sword and everything, and then I came to my senses, or maybe I was so out of it that I screamed without realizing it.

If you think about it, it was all that guy's fault.

Well, he broke the sword, saying it was cheap, but from the perspective of the person who gave it strength, even the old man's masterpiece, the Moonlight Sword (No. 10), was not this strong and resilient.

It was a masterpiece that could be said to be the best of the best swords, the most precious sword of all swords.

It's not like they gave you this sword to keep at home, so it's not a problem to take it out and use it in battle.

No, why would you throw away such a precious sword?

No matter how angry you were and how much your eyes roll back, that's not the case. Of course, when a person's eyes roll back, they might punch without realizing it, so that's possible, right?

Then that won't work, right?

It was all because of that guy.

He threw a knife and I just caught it.

It was a natural strategy to destroy the enemy's weapons, so I just broke the weapons.

If that kid hadn't started this mess by saying he'd commit assassination in the first place, I wouldn't have had any reason to go this far-

Then suddenly.

What a mess. Qing's eyes narrow.

Now that the streets were filled with assassins, the wealth of the palace could explain the mobilization of such a large group of assassins.

Since they were assassins who tried so desperately to kill the client by throwing themselves at him, they might have known the client's identity to some extent.

But why were you after the dog paws in the palace?

Even though the sprouts were a bit yellow, no, very yellow, almost rotten, were you making this fuss just to kill one 18-year-old brat?

Why? A common palace intrigue involving the Tongjeongsa Temple?

But if that's the case, the emperor could just point a finger at you and end the affair, so why would he order his subordinate to assassinate his son?

Maybe the emperor isn't the main character.

Perhaps the Tongjeongsa knew my son was in danger and forced him into the Uijeongmuhak Hall? Hmm, that seems plausible.

But there's no point in thinking about it now, what's the point of guessing on your own?

This was something that only a smart person, someone with the intellect of Seol Ga-nom, can guess. What am I, on my topic, even if I'm not as good as Seol Ga-nom, I wouldn't know if it were Chun-bong or Jegal.

Rather, I should do what I have to do.

What Qing needs to do now was not to uncover the secrets of the palace conspiracy surrounding Gaebaldaegwi.

What has happened has already happened, so we must act to protect myself, my friends, and our entire academy.

And in this case, the direction was clear.

We need to get rid of all the pairs.

Murderous mouth.

Now was not the time to run away and waste time.

The assassins who attacked the author were probably just guys who had received a small amount of money, but the fifteen or so guys running on the rooftops—these guys were definitely from the palace, um, the palace soldiers? Guards? Palace assassins? In any case, they were definitely some kind of palace guy.

And the dead cannot speak, so we must eliminate every single one of them.

We must eliminate them, not kill them.

Whether it's burning or burying the body, if we get rid of it so that it can't be identified, then even if there's any repercussions later, we can say, "Nothing happened, we don't know."

We need to completely erase that evidence from the world.

Qing's eyes have a cold chill.
