\chapter{Be Sure to Maintain Your Dignity When Going Out (22)}

At the moment of explosion, Qing had a feeling.

Ah, this, this doesn't seem right. Wait a minute-

Loud noise.

Mine's body shakes.

The tightly pressed waist bends like an old woman, the closed arms and legs spread out, and an explosive cloud of dust spews out through the gaps.

A thick cloud of yellow dust, like a desert storm, rises and obscures the author.

People lying face down on the floor without realizing it, or those who have fallen and covered their heads, raise their heads with anxious expressions.

All that can be seen in the thick sand and dust was nothing but yellow powder.

Between them, something black jumps out.

A mine rushes forward, its entire body covered in sand dust, surrounded by visible currents of air, and spewing pitch-black smoke from its mouth.

Maybe it's a predetermined outcome.

Jang Cheon-ho, who was running away with the Daeyoungban, slowly slowed down and kept glancing behind him, looking at the thick dust, and unconsciously muttered to himself, "Did I get rid of it?" This could have been the result of his fervent wish.

It could be said that this disaster occurred because the Zhongyuan were still ignorant of the mystery of language, the unconscious revival of the origins of humanity, which countless creations testify to with the same content.

Anyway, Mine was fine, no, it's just that it's so black that you can't see it well, but his shiny, shiny body was covered in blood.

It hurts so bad! Kill those bastards!

It's not that it wasn't, but Qing's eyes turned.

If your internal organs have been torn apart by oppression, and pieces of shattered metal have been deeply embedded in your muscles, leaving your entire body, thighs, and arms without a single sound spot, then of course you have the right to be angry.

The dog-like bird makes the fight dirty. How dare you use grenades in the sacred martial arts forest? This kind of hex, hex, you bastards, I'll catch you, put a bomb in your back, and blow you up.

No, that's not fun. I should have put bamboo in their front holes, filled them with gunpowder, and lit them. Once they've done it properly, I should make them cringe at the mere smell of gunpowder. Those bastards deserve to have their arms and legs cut off and thrown into the mud.

Daeyoungban and Jang Cheonho may be wronged.

No one threatened him with a knife to cover up Jincheon-roe with his body. Why did he jump in alone and write the poison, and then turn his eyes and look at him with murderous intent?

But there was no logic to an angry person.

And this fucking Heavenly Demonic Crusade, Heavenly Demonic Crusade? What the hell was this divine art? What kind of divine art was this if it can't even stop a grenade? The destruction of the Zhongyuan? If you get hit directly by a cannon, you'll be crushed and have to try again next time, and that's how it all came to this?

I knew this would happen after seeing how the Demonic Cult was going. Failing once was failure, but if you fail twice, you should know how to change your methods. If you failed three or four times, you don't know that it's the same ten or a hundred times, so that's why you're in this state.

The Heavenly Demon True Qi was very wronged.

It wasn't just any ordinary Jincheonroe, it was a real Jincheonroe manufactured in the palace, a super-powerful fire bomb made to kill unmanned personnel.

Even though I saved the people of the Zhongyuan who deserved to be chewed and eaten, I was so heartbroken that my teeth were gnashing and falling apart, and when I barely managed to save them, this was what they said when they came back.

Why should I be sad and do magic like this?

So, even the Heavenly Demon True Qi becomes angry.

It's all because of those kids!

As Qing and Magi exploded in anger at the same time, Mine ran forward with injuries that would not have been strange if he had collapsed at any moment.

It actually got worse.

Now, with black smoke rising from his eyes and mouth, he was hunched over, running at them on both feet and arms like an animal.

It was a total frenzy.

Jang Cheon-ho urgently increases his speed again.

Mine, now a demon with an almost beast-like appearance, was chasing after him.

The demon's gaze was completely lost, and the black threads inside his eyes grew and shrank, spinning and trembling.

Could this be the form of the world's murderous intent twisted and tangled together?

That was the moment.

Jang Cheon-ho's expression hardens.

It was none other than the voice of the Great Commander shouting in my ear, because of some order.

"It seems you're trying to act like a swordsman. If that's true, I'll give you another chance to become one. If you catch someone, seriously wound them, and throw them at them, they won't be able to chase you down. Find a suitable target. Young, preferably a woman."

``Daeyoungban! That means...!''

-Think of the greater good. The martial arts world raised that monster. We must inform the Emperor and have him subdue it. Do you intend to repeat that damned disgrace of the Emperor again?

Jang Cheon-ho grits his teeth and throws the Daeyoungban forward.

The surprised expression on the face of a young girl as the shot rocket spreads its body in the air and rushes forward, rapidly approaching her.

The sound of both hands being swung around, the blood spreading along the tips of Daeyoungban's fingers, and the feel of the person's yellow fat getting caught under his fingernails were disgusting.

``Ugh, eww!''

The girl who was attacked without even knowing English had no time to scream in pain, and was thrown into a dizzying trance as her body flew up, leaving her to let out a pitiful scream.

The girl's body flies away, spraying blood at the man who has turned into a black beast.

The mine, which had been spewing out black smoke, pulled back its huge, erected claws, and with a creak, the black beast's body trembled as if it had broken.

And then, with a human fluster that was noticeably different from before, I carefully caught the girl flying towards me with both arms outstretched.

``Ugh.''

The thin stream of blood that gushed out from his mouth made Mine and Qing's body tremble.

Qing's gaze turned towards the fleeing assassins, and then towards the girl. He raised his head again to see the backs of those murderous men two steps away. He lowered his gaze again to see tears welling up in the girl's eyes and threatening to overflow from side to side.

It was a trick whose intentions were so transparent that one could see right through it.

Hostage, were you going to leave me to die and come after me?

Qing's fist was clenched.

My hands were trembling, but those kids, but this kid, I have to catch those kids, if I don't kill them now, they'll die, but even if I kill them, there's no guarantee, if I let those kids go, countless kids like this might be created.

``Sigh……''

Crack! The sound of upper and lower teeth clashing with heavy force. You fucking dogs, I will never leave you alone. I will chase you to the ends of hell, and I will make you writhe in miserable pain until you die, never letting you die for a thousand years.

Qing moves her hands busily.

Qing was a martial artist, a carpenter, and a female physician, so her hands were busy examining the girl's wounds, tearing the hem of her clothes to wrap them, pulling out the loose threads, and preparing thread to sew them up.

Even in the midst of all this, his gaze alternated between below and ahead, as if he would never forget that fleeing figure, emitting a cloudy light filled with the most ominous colors in the world.

He looked at the girl again, grabbed the severed vein, froze it to stop the bleeding, and raised his head again.

Suddenly, the corners of Qing's mouth rise subtly.

The backs of the assassins running away as one, and in the distant focus, the welcoming faces running closer.

Changbin runs towards him and suddenly kneels down, and when he suddenly holds out his hand to interlock hands, the man in charge jumps up and steps on him. Is that a mountain?

Gunyeongi and Murong Soju, who were kneeling side by side in the same movement, trample Gunyeongi and fly up.

Wouldn't it be a healthy scene of martial arts where the lower classes serve as a stepping stone for the higher classes, or in other words, as a mat, and where the higher classes trample on the lower classes and soar?

The fact that they were able to breathe smoothly even without me was very satisfying to Chairman Bon.

Qing was at ease and her hands were busy.

Meanwhile, the sound of footsteps approaching me.

I raised my head slightly and oh, wow, Chunbong was racing, my heart was racing too, racing like crazy, oh my gosh, wow.

The moment their eyes meet, Qing screams.

"You're a slut of the righteous faction! You little witch! Even if I, the little witch, were to tear you to pieces right now, I wouldn't feel satisfied! But I, the little witch, can't bear to let an innocent girl die, so I'll just let you go! Just get out of here!"

If they just hugged each other here, wouldn't a deep connection between the Jeongpa's later indices and the minority witches be formed?

Qing's impersonation was a very natural performance that came from deep within, and anyone who heard and saw it could tell it was natural!

The joy of the present cannot break this thorough disguise.

Sima Chunfeng stopped at that.

``Uh. Um. Uh.''

The pause should be brief, Sima Chunfeng stutters like a broken person.

What the heck, was this kid smart? I thought he'd catch on quickly and get along with me since he's so intelligent, but he's just so awkward because he can't even get along with me?

``Uh, uh, um.''

Qing swallowed a sigh.

Chunbongi was smart but very reckless.

Qing suddenly gets up from his seat and lowers Sima Chunfeng's evaluation by three levels.

Now that the serious wounds have been treated, isn't it time for a real doctor with the tools and remedies to step forward?

``Where were you going?''

"The girl's life was in danger, so this witch seeks out the councilman! You woman of the righteous faction, if you won't obstruct my path, then step aside. If you have nothing better to do, how about taking care of those filthy assassins?"

``Ah, ahem. This Sima-lang is-''

Sima Chun-bong seemed to be about to hear something, but Qing cut him off.

Sima Chun-bong's expression suddenly turned sad.

"Let those savage beasts breathe! I will personally take their lives, you little witch! Unless you were going to fight me, you will not be so merciful as to grant them deaths! Argh!"

Qing left a message.

The message was to capture those bastards alive rather than kill them if possible.

In that way, the minority witch flies away with her natural minority witch speech and actions.

However, the scream that burst out at the end because he couldn't hold it in was something that everyone should understand.

Even though he was a strong-willed person, it was difficult to endure the pain caused by stepping on the law.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The physician was surprised.

First of all, how surprised would you be if a monster suddenly appeared by kicking open the door of the infirmary and actually kicking it away with his foot?

``What, what is it!?''

The second thing that surprised me was the sight of the monster putting the patient down. It wasn't that I was surprised by the bloody sight, since the doctor always saw bright red blood.

However, since the amount of blood was spread on the clothes of a doctor who has seen patients all his life, he could roughly tell how much blood had been lost.

``I’m sorry, it's an emergency patient. There are multiple abdominal wounds. We’ll move from the trachea to the central sac—''

He was surprised for the third time when the monster started reciting the details in the medical book.

But for a moment, the expression on the doctor's face became serious after hearing the details, and the doctor who finally received the patient's details clicked his tongue.

"How could a medical woman, so educated, bring a corpse to the doctor? With so much blood lost, is this a corpse or a patient? I understand your pity, but you have to let go those you can't save. You foolish fool."

"Huh? She didn't bleed much, and I stopped the bleeding right there. It's a wound, but it was cut with a sword, so the wound was clean."

``Tsk tsk, you’re bleeding while wearing that bloody armor, get a grip.''

``Oh, this. This isn’t the patient’s blood, it’s my blood. Ah. A lot, um.''

Only then did Qing start to spin. His head started to spin.

She ran over in a hurry, but when she finally looked down, her front was completely red, even though she was wearing two layers of clothes.

``Uh-oh, I'm in danger.''

Qing fell over to the side.

The physician clicked his tongue at her.

"Haiyaa, so the patient is brought by a corpse. Is Suyeong there? Close the clinic door right now and boil some water! Prepare some decoctions and bring in all the doctors! Now!"

The sound of someone shouting busily.

Qing's conciousnes faded away.