\chapter{Be Sure to Maintain Your Dignity When Going Out (5)}

The officials were given a very sweet break.

The Chinese people's aversion to cold drinks has been well known since ancient times, but what about the cold and sweet drink they drink after a long march of three days and one night on a summer day?

Kiyaa, kiyaaa, the sound of people drinking alcohol was loud here and there, was there really such a thing as cold tea that tastes this good?

Moreover, the cold tea was the work of Seol-i-ri, a famous Bingseolhwa from the Five Martial Arts Schools. The taste of a cup of cold tea served by a cold beauty with an expressionless face (who, in Qing's eyes, looked a little pouty because her luck was interrupted) was amazing.

Then take a short break until the power returns.

As each of them lay down on the parade ground without a care in the sand, the sound of snoring soon resonated through the majestic multi-window.

The last group of trainees returned around 5 o'clock, so unfortunately, the last group had no choice but to go straight to the training closing ceremony without even having time to rest, right after drinking a cup of iced tea.

And when we stood in a neat line and inspected.

That day, Guan Dao remembered the fear of being lectured by the governor…

"I, the Lord, am extremely proud of you! To have completed the training without a single dropout was proof that you all, together, have taken care of yourselves and achieved your goal! Moving forward together—this was the spirit of the Wulin Alliance!"

It was the spirit of the martial arts alliance that came out at the moment when I suddenly felt like I didn't want to do the martial arts alliance.

But that too for a moment.

"You must all be tired after your training. As a senior warrior, I am truly proud of you! That's all!"

It was a short speech, almost miraculous.

Could it be that today, too, they were beginning the same four lessons? The faces of the officials, who had been devastated by shock and horror, now show a great joy.

And then.

``Wow!!!'' ``Long live the Wulin Alliance!!''

A roar like thunder that erupted spontaneously even though Qing didn't shout it out, a roar like passion more than ever.

Then, Qing went up to the stage.

I have to announce the schedule for the future, but what the heck, when I think about it, I feel like I've become a bit of a host.

Of course, since he's the youngest among the instructors, it would make sense for Qing to take charge, but hmm.

"Thank you all for your hard work, officials. Before we conclude this closing ceremony, I have some news for you. It's about the opening of the Manbyungjiwangjeon."

It was a match of pride between the three Kendo clubs, a special event for the clubs, with not only pride at stake, but also special privileges such as special meals, extended outings, snacks, and tea.

And after today, the full moon will be over.

"For the sake of the exhausted officers and staff from this training, the Manbyeongjiwangjeon will be postponed to the last day of the lunar month, and this full moon will be replaced with an outing. Furthermore, to commemorate the successful completion of training without a single injury, all personnel will enjoy the privileges of the championship hall until the Manbyeongjiwangjeon begins. In other words, food will be served at your table!"

-Wow!!

Again, cheers like a firework.

Even without that, my body was gradually getting used to the arduous schedule of the academy, so wasn't it time that the poor meals I had been eating out of hunger were starting to taste really bad?

Those wishing to go on an outing must report to the head of each office by tomorrow morning. Each office head will report the status of outing requests after work tomorrow. Outings will be for three days, departing after roll call and returning by noon two days later. Do you understand?

``yep!!''

"Tomorrow morning, we'll rest and finish personal preparation, and then we'll resume class in the afternoon. Well then, that's it, let's disperse!"

I'm sure you're all tired, so I'll just tell you what I need to say and be done with it.

It was a training session that was swiftly implemented at Qing's suggestion. This meant it wasn't originally part of the school's schedule.

However, since the training results showed that he was more tired than expected, we adjusted the schedule and sent him out on his first outing and postponed the Manbyungjiwangjeon.

Even if it was a showdown between the training centers, it was still a situation where even the beginner's skills hadn't been fully taught, and the instructors had already conspired to ensure that the victory of the martial arts center and martial arts instructors was predetermined.

Anyway, the instructor has the right to nominate the participants in the Manbyeongjiwangjeon, so if the three of them work together, it won't be difficult to decide the direction of the match.

The swordsmen and the great swordsmen will be motivated by the humiliation of losing to those primitive people who use their fists.

The martial arts hall won, and their morale was high, thinking that they would win. It was a fair match fixing that didn't hurt anyone.

On the way back to the instructor's quarters, Peng Cho-ryeo, who had also finished guiding the group, stretched out and made a noise like an old man.

"Ugh, I'm so tired after staying up all night for the first time in ages. I need to cool off and go to sleep. What about Qing-ah? Should we shower together?"

``I'm going to heat some water. I need to boil it thoroughly.''

``A hot spring this summer? Isn't it hot?''

``Hehehe.''

Qing grabbed Paeng Cho-ryeo's wrist and led her inside the cotton swab I had turned over.

``What, why was it cool?''

``This was the ice ball.''

Far from being hot, it was Qing who kept me cool by emitting a cold air of Hansimgong the whole time.

The inside of the baggy clothes was basic, and the face was tightly wrapped to block the cold air, so it's like the air conditioner was on all the time.

Although he hadn't acquired the ability to unconsciously turn on the air conditioner while sleeping like Seol-i-ri, it wasn't that difficult for Qing, who already had the level of internal energy of a Talhwa-gyeong, to turn it on all the time while he was awake for three days without a night's sleep.

So, a hot bath without breaking a sweat and being fluffy was purely a personal preference.

After I returned to my lodgings humming like that, um, why was there no one to welcome me?

They say raising a daughter was all in vain, so when Dad comes home from work, he should at least pretend to come out and hug him.

How fun was Ambassador Wolbong's boys' class that you can't even see the tip of your nose?

Well, I guess there's nothing I can do if I'm hanging out with friends.

Since dad was dad and friends were friends, it could be seen as wise in that it was a priority to play with friends that you can meet and play with at times like this rather than family that you can see every day.

Even though our daughter was not smart, isn't she wise?

Yeah, what's the point of being smart? You have to be wise, right?

As Qing nodded and was returning to her room, she suddenly noticed the back of a figure crouching in the corner of the flower bed.

What the heck? Playing with dirt? Watching ants?

Qing was stealthily sneaking.

As a result of his training in martial arts, he was always able to move around without making a sound. If he tried to hide his presence, there would be no way for a kid like him to notice even if he died and woke up.

So, it was at that moment that Qing quietly approached, raised both hands, and made a "wak" sound to tease him.

``Hehehe.''

A child's soft laughter.

Over Ciyu's round shoulders-

Hmm. What should I call this?

A mole with a swollen flesh, but covered in blood.

The branches the child was holding were pressing down on his torso, and blood was seeping out from the wounds here and there.

There must have been a deep wound in the abdomen, and the purple-tinged intestines swelled like balloons and protruded outward, but only after the child picked up the branch did the swelling stop.

Well, it's a bit ambiguous because it's a mole.

Aren't moles harmful and useless creatures that ruin crops when they come out into the fields and kill trees when they come out into the mountains?

Besides, I know it carries some kind of deadly disease. I don't remember what it was, but I remember hearing someone tell me never to touch it with bare hands.

Well, now that I think about it, would it be a problem if it was a cat or a dog?

Anyway, the people of the Zhongyuan were known for being omnivorous, living up to their reputation of eating cats, dogs, and anything with four legs.

While Qing was momentarily distracted, a sound seemed to have escaped.

Ciyu was so startled that she threw the branch she was holding in her hand without realizing it and fell on her butt.

And then there's the expression on his face as he looks up at the blue.

It's as if if you were to draw despair, fear, horror, and similar emotions with a facial expression, it would look exactly like this.

It was definitely not the kind of expression a child would make.

``That, you know, no, no. No.''

Ciyu, who always speaks slowly and with a slightly awkward pronunciation, starts speaking incoherently and in an unexpected manner.

Qing Rin was angry at him.

``Isn't it fun to stab, cut, and torment?''

"no."

You were the type of person who only uses polite language when you were single.

Qing giggled and grabbed Ciyu under her armpits, pulling her into his arms.

``Isn't it fun? I'm having fun.''

He asked Ja-yeo to listen intently.

At that gaze, which seemed to be trying to determine whether he was sincere or not, Qing smiled bitterly and spoke in a gentle voice.

``You're not joking, were you? So, was it fun or not?''

``……It's fun.''

Qing nodded in agreement.

"Come on. There were people like us. What should I say? They're broken? A bit defective? Or maybe they're just a little mentally ill."

``Dad, too?''

"Well, there's nothing in the world more exhilarating than tearing flesh, breaking bones, and letting out screams. It's so thrilling that my legs tremble and my strength drains. Hmm, thinking about it makes me suddenly want to kill. I've been holding it in for quite some time..."

It's a crazy story that's scary to hear.

But when Ciyu was pulled out from among those chunks of meat, the crushed flesh and bones and entrails.

From then on, it was something I had been vaguely guessing, just in case.

So I hoped it wasn't the case, and I thought it wasn't the case.

Among the mothers, I was very relieved to see Hyang-i walking around Ododo and laughing so much while holding hands with her again.

The child has a gloomy atmosphere and a rotten look in his eyes, but he was surprisingly fine.

But, perhaps it couldn't be helped.

"Of course, I know how you feel. But, um, the world doesn't know. They don't even want to know. So, people like us, um."

People like us.

Qing tries to force a mischievous smile.

"You have to enjoy yourself and be aware of it to live a life of beauty. Look at me. Doesn't everyone love Dad?"

``Yeah. They all like Dad.''

Still, isn't it fortunate that it's in the Zhongyuan?

On the mountain, there were many man-eating beasts, and at the foot of the mountain, there were many people worse than beasts.

What these two have in common was that even if they beat him to death, he was not guilty, and rather, people were busy praising and praising him for his negotiating power.

Of course, there were differences between the two.

If you kill an animal by beating it to death, it leaves a bad aftertaste and was disgusting, so it can't be said that eating a person was particularly evil.

But, even if the villain puts in a lot of effort to torment the other person, it can be said that he feels that much more satisfied.

Anyway, it was fortunate that it was the central plains now.

If it were my hometown, hmm.

Because I just have to endure it for the rest of my life.

So what a blessing this is.

Because I don't have to tell you that you shouldn't do that, that you have to endure it and hide it for the rest of your life, that you have to endure and endure the burning thirst and thirst again.

"First, you need to choose your target carefully. If you harass a bad guy, everyone else will probably just ignore it, right? Well, in that sense, a mole isn't a bad choice. However, you should at least have an excuse ready in case you get caught. Like, you planted a precious plant and it ate it."

"huh."

"There were many villains in the world, and I enjoy tormenting them, and it benefits the world. People who were beneficial to the world were meant to be loved."

"huh."

"That's why you need to train in martial arts. If you become a master, you'll be able to confidently torment bad guys."

This was a scene that really teaches children something good.

But there's nothing I can do.

It would sound a lot better than the horrible words that you have to endure for the rest of your life, and I'll shave your head and make you a Buddhist monk, whatever.

Ciyu's eyes were so black and rotten that even if you look into them, you can't see what's inside.

But you have to know my heart to be my daughter? Qing hugs Ciyu tightly and pecks her cheek.

Soon, hehe, a rather dark laugh for a child bursts out.

"Okay. Let's go. The mole is dirty. You didn't touch it with your hand, did you? We need to wash it quickly."

Qing carries Ciyu and heads to her room.

It was a truly dazzling companionship of a real thousand-year-old and a half-millenial man.