\chapter{Be Sure to Maintain Your Dignity When Going Out (12)}

``What about Cheon Cheon-ho?''

"that is."

``No. I guess there’s no need to hear it.''

A middle-aged man frowns and smiles bitterly.

At Sobaekho Square, under the setting sun and the rising black smoke, a continuous shouting could be heard from the center of the square.

-I am!! Wan Talu!! You despicable assassins!! Why don't you come out right now!! Are you afraid of me!!

But who would be afraid of that sight?

The young man who was stuck next to the woman was screaming loudly.

Thanks to this rare sight, there were quite a few onlookers who choose to watch people instead of fire, wondering why that guy was carrying his name like a burden on the woman's side.

``What were you going to do?''

``Heavenly Blossom Sword. It was the ultimate realm.''

I heard a rumor that in a life-or-death battle on Mount Nosan, he defeated three martial artists of the same level, who had reached the pinnacle of their power.

"Aren't rumors always exaggerated? Those witty people of the martial arts world make a living at exaggerating things, trying to extort money. And if a beautiful master like that were involved, they'd probably go around spreading rumors about her as some kind of celestial goddess."

This was Qing's evaluation in the Gangho.

Whether they were jokesters or onlookers, they were always anxious to make their own spectacle more dramatic and create a more interesting story.

It's an even more interesting story to hear because it says that there was still a young and beautiful woman there.

There was no reason for the Wulin Alliance to stop the rumors about their dragon from being exaggerated, and it was even good for the Wulin Alliance's reputation.

So even if the Sapa and Ronin heard the rumors, they would not believe it outright that a woman in her early twenties was some kind of heavenly talent and was already at the peak of her powers and even skilled in actual combat.

Above all, I don't want to believe it.

If you were a member of the Wulin Alliance, even if you don't believe it, you were on our side, our Wulin Alliance family anyway, haha, it's really good, it's great, that's how you put it in words.

"How about we take this opportunity to issue a stern warning to those thugs of the martial arts world? If you'd just give us the order, we'll all—"

"no."

The middle-aged man shakes his head.

``If you show even half the level of inaction that rumors say, it’s much more dangerous for a master who was accustomed to actual combat than for a realm.''

"then."

"Let's relax a bit for now. Young, reckless people run wild and tire quickly. Send a signal. Let's see if these real assassins can handle it."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Beep! Beep! Beep! Beep!

The sound of a flute came out of nowhere. To someone who didn't know, it might have sounded like a child blowing something carelessly.

It was a signal sound that had a special meaning to some specific people, those who were classified as professional assassins.

``Captain, it’s the Heavenly Flower Sword, the Heavenly Flower Sword. But were you really going to do it?''

"Even so, isn't she just a bitch in her early twenties? She seems to be using martial arts or something, but don't you know that that's completely different from our ambush? If you don't know what you're doing, you'll die if you just brush against her with a sword."

``Who would say that? What were you going to do about the aftermath? How could the Wulin Alliance just sit still?''

"Let's wash our hands after this. Don't you know our guest was backing us up again? If this goes well, we can all grow old and die in a grand estate, listening to the sound of Nari's voice."

``Still, it would be a complete loss of face for the Wulin Alliance guys……''

"Life was a one-shot deal. It's a one-shot deal. Hmm. Should I do it or not? If my younger brother's intentions were completely opposite, then there's nothing I can do."

``Hmm……''

If you had heard the truth, it would have been absurd.

From the beginning, they were talking on the premise that if they came out, Heavenly Blossom Sword would be defeated.

And after a while, the one called Aura came to a conclusion.

"Fuck, let's do it. Let's do it. We should fix our fate while we're at it. They said they'd take care of things later, but they're just going to back out, and it doesn't seem like they'll just let us quietly leave. If it's going to cause problems even if we don't, we'll have to do it anyway, huh?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's ears suddenly perked up.

Beep, beep, beep, beep. The harsh sound of a flute was picked up by the hearing that transcends humans.

There were a few sounds that Qing hated the most in the world, and the one that proudly took its place among them was this signal whistle.

Who was it, what kind of guy was playing the flute?

Still holding the Wan Talu, who was screaming "Wan Talu, Wan Talu, my name was Wan Talu", on his side, his sharp eyes glaring in all directions, making the blue shiver.

Now that we have heard the whistle, isn't this a signal that the enemy was about to attack?

As expected.

``Wan Talu!!! My name is!! Mandal, evil!''

The Wan Talu who was shouting the name falls down with a splash, making a sound like a frog being stepped on.

At the same time, the sharp sound of arrows.

An arrow aimed at Wan Talu's head slices through the air and lands! The arrow loses its power upon impact and bounces back, spinning.

Qing quickly turns his gaze, but only catches a glimpse of the ambush attacker disappearing into the distance on the other side of the pavilion.

Miss, this was not good.

I thought the enemy would jump out and swing their swords, but if they were already hiding here and there and shooting at me with bows or crossbows, those deadly bastards wouldn't come out and fight properly.

So, how?

We have to move.

This was an entertainment district, so it's packed with three-story towers, making it the perfect spot for sniping.

But if the enemy can't snipe, they will inevitably appear in front of you.

``The pipe was moving.''

Qing grabs Wan Talu by the back of his neck.

"Ugh," Wan Talu said, clutching his neck and making a choking sound, about to protest that a woman could be so ignorant and cruel.

My head jerked back as a strong force pulled my body back, and I immediately shut my mouth as the iron bar brushed past my nose.

Instead, another outburst erupts.

``What the heck! Why! Why me!''

``So, I guess I should ask from now on.''

Qing answers indifferently and runs away while holding onto the back of Wan Talu's neck.

When I put it on my side, it was difficult to protect it because there were too many protrusions in the front and back, and when I put it on my back, it was like a shield on my back, so it was like asking me to shoot arrows.

If I hug her like a princess, both of her hands will be tied up, so it's difficult. Even a dog's paw has two legs, so I have no choice but to make it walk on its own.

Qing supports Wan Talu as he walks down the street.

Wedge, wedge, intermittently flying iron.

- It's an attack! - Everyone, run! - Aah! - Run! - Save someone!

I can only watch when my body was safe, but with arrows flying right now, all the passersby were in a state of panic.

As the screams of the Abigail continued along the Qing's charge, the location was revealed without Wan Talu having to shout his name.

That was when.

``Wait, wait, over there, over here, over here!''

At the entrance to the alley over there,

A man calls out to Qing with an urgent hand.

``This way, get out here!''

Are they school officials? Or were there two groups: one trying to kill Gaebaldaegwi and the other trying to protect him?

And the answer is?

He was an assassin.

As soon as the blue one approaches, the man extends his dagger as if it were nothing more than a matter of course.

The blue hand grabs the man's outstretched dagger.

The tip of the sword stopped precariously in front of the Adam's apple.

``Eek.''

Wan Talu gets his butt kicked.

"profit!"

The man was moving forward and backward, but his blue hand, gripping the dagger, barely moved.

``You did me a favor. I’ll return the favor.''

The moment Qing pulls the blade, I push it away with all my strength.

Bang! The dagger handle was lodged in the man's nose, and with a thud, the nose sinks down in an instant.

``Ahh! Whoop?''

The sound of a jaw being choked during a scream.

It was because Qing's hand had tightly grabbed the man's lower body.

At the man who was looking at her with surprised eyes, Qing smiled faintly, a somewhat sinister smile on her face.

The attempt was quite fresh and cheeky, but it taught me a lesson that this was how you can let your guard down and try to stab someone.

Then, I have to pay the tuition.

This feeling of cracks slowly spreading through the bones, if I just apply a little more force, yes, like this.

Break!

The thumb and middle finger, holding the man's chins on either side, meet somewhere between them.

It was a very surprising phenomenon that occurred despite the presence of a lower jaw in between.

``Gaaaah!!''

The bestial scream of an assassin who has lost his lower body.

The tongue, having lost its support, hangs limply and dangles past the Adam's apple.

``This was confusing people.''

The tip of the blue foot kicks the man's knee.

Qing's body was already a human weapon, a terrifying weapon that can be torn to pieces with a punch and turned to dust with a kick.

The blue man's shoulder blade was being crushed.

Qing gulps as he feels the unique sensation of something hard being crushed into pieces.

Phew, this was it, this was it. I feel like I can live a little now. I feel alive.

If you have a broken knee and a broken shoulder, you have paid your tuition fees.

There was no need to go to the extent of cutting off the breath, since he would have lived a miserable life and died anyway.

I guess I'll have to beg and beg to survive, but after experiencing it, I realized how cruel the people of the Zhongyuan are.

Qing realized the sublime spirit of respect for life in Kunlun's Chamhoedong.

If you kill them, they will suffer immediately and it will be the end, but if you leave them alive, they will desperately continue to live a miserable life and die painfully.

Could there be a more fitting end for a villain than this?

Qing suppressed the laughter that was about to escape her without her knowing, and grabbed the back of Wan Talu's neck, who was still sitting there in a dazed state.

``Come to your senses. Is it time to look around?''

Then I looked at the back alley for a moment and-

Back alley? If it's a dead end, no, that's better, because the enemies will just swarm in one place.

But, if this guy was going to stab the dog and run away from the beginning, he would have set a trap. It doesn't matter to me, but it could be dangerous for the dog.

Qing's mind, having tasted blood, was at its peak, his brain ablaze with the excitement of slaughter, and he was working on his tasks in earnest, unlike usual.

So, the assassin's ecological experience begins, heading out to the outskirts of the city and learning through firsthand experience.

First of all, let's be honest, men!

A man must raise his voice and shout out his purpose, and rush forward head-on. Even though he was nothing more than a pest in the human world called an assassin, he was the type who remains faithful to the code of conduct for a man.

"asleep!"

The man in black jumps down from the building and points his sword at it.

He flashes his dagger at her.

The moment the tips of the swords met, the most destructive starlight, Kang-gi, pierced through the assassin's sword, slicing it in half.

The tip of the sword splits like a cucumber pressed against a cutting board, and finally the handle splits cleanly, and half of the palm with the fingers attached falls to the ground.

There were two types of martial arts: Ihwajeopmok and Salyangbalcheongeun. The art of using the enemy's strength, cutting down the enemy with the enemy's speed, was Ihwajeopmok and Salyangbalcheongeun.

"Ugh."

The assassin turned around without even considering my palm. Excellent decision. But he was still my opponent.

The blue dagger cuts straight through the air.

This was something that an ordinary unmanned person would not have done because they would have been wary of losing their enemy's air power, that is, their weapon.

The dagger was stuck vertically in the center of the assassin's back.

The lower body trembles wildly as it falls down, a kind of reflex reaction where the nerves were going crazy after being stabbed in the spine.

After confirming the scene, Qing starts walking busily again.