\chapter{Be Sure to Maintain Your Dignity When Going Out (20)}

Hwang Eun-o Haeng-jin was a high-level examination that combines the five directions of fire, water, wood, gold, and earth, and the five depths of Yong-yang, Jung-eum, and Bing.

The mine located in the center suddenly lowers its head.

As if unaware of the danger of the examination, as if unaware of his own precariousness, when he was already trying to scout out the enemy, identify his weak points, and immediately break through to escape, he suddenly lowered his head weakly and looked down at his feet.

That was the moment.

The head, shoulders, and arms were all lined up, and long, thin fingers extend out.

The huge pitch-black demon sitting above it stretched out its twisted claws in the same shape.

The blood drains from the assassin's face as he points his finger.

In that moment, other assassins rushed in.

The three men who had taken control of Geumyang's defenses rushed in at once and swung their swords. Kagagang! Three swords lifted up the man's hand.

Mine's hand rises upwards.

Even after being hit by the swordsmanship of three masters, the fingers slowly rose with a dull weight, followed by a black ray of light slicing diagonally towards the distant sky.

The assassin, who had taken control of the ground, took advantage of the moment and struck the ground with a thud.

Then another assassin, moving to the soil's location, gives a forceful push to the center of its back.

And so, with the combined power of my awakening and my companions, the assassin's blade, literally fired in a straight line, aimed at the vital spot, the nape of the neck, where the black veins were clearly visible.

But, chin.

The assassin's body suspends in mid-air.

The white hand of the mine grabbing the sword, the minority of the minority witches, even in this midst, was so transparent that it seems dazzling.

And then, the sword cannot withstand the clenched fist and breaks into pieces.

Small pieces of broken iron fall from the palm of his hand as he opens it again.

The assassin retreats in terror.

But the new form of Mine doesn't react at all, as if it doesn't care about the person who steps down.

That's why the presence of Mine was tightening with even greater pressure.

Why don't you counterattack? You parry, deflect, and shatter the attacks directed at you, but you don't actually move or counterattack.

If you try to slow down your attack, the finger will immediately shoot a black beam of light towards you.

As if telling me to keep going.

It's like he's standing there, whipping everyone, forcing them to go on the offensive, as if telling you, you little shits, to keep throwing tantrums.

``Hold on a little longer! The spirit will be here soon!''

Jang Cheon-ho shouts.

In fact, it's something he's saying to himself, and people tend to fear the unknown, and Jang Cheon-ho was an enemy he's never faced before.

Is that a person or a ghost?

They say that a demon possessed by magic was dangerous, but isn't this something close to a supernatural being?

How long could he have endured like that?

If we calculate the total, it was in the tens, but since the number of assassins was a number, the attack power was also doubled.

In the end, it was only a short time, less than half an hour, but has there ever been a time when it felt this long?

And finally.

``You bastard! Thousand Flower Sword!''

Yeongban shouts and cuts through the air.

Yeong-ban, who jumped into the Five Elements Sword, immediately reached out and received the sword from his subordinate.

As you step through the gate, a bright purple energy surges from beneath the sword and covers the sword ridge, forming a sword river.

Not only that, it emits a soft purple color, dazzling and splendid like the last light of the setting sun, the sunset.

A precious color that stretches out like the sunset.

Purple sunset, this was called purple haze.

The vision of a great sect shines through the hands of a completely unrelated person.

Mine's hand points forward.

Still the transparent flesh of the white minority.

A palm spread out as if to block out the dazzling sunset shining upon me.

Finally, the purple sunset touches the white palm.

Phew.

The soft sound of skin being torn apart.

The sword that pierced the heart of the mine.

However, that was all, he was blocked from moving forward by the black blade that pierced his palm.

Yeongban pushed the sword he was holding with both hands with all his might and tilted his body, but Mine just lowered her head and silently raised her hand to block it.

Blood flows out of the pierced palm.

Black blood flowed down, forming a precarious clump under the palm, then quickly formed into a single drop and rolled down.

That moment.

Black spreads from the pierced area in the center of the palm.

A black that was even blacker than black, a blackness so foreign to the eye that it burst out and spread, covering the pure white hand, then rapidly contaminating the inside of the sleeve, and soon even the outside, running all over the body.

Mine, who had suddenly stood there, was just as dark as a pitch-black shadow.

It was a human-shaped abyss so black it looked like a hole in the world.

And then, the black mine opens its eyes.

Countless cracks appear in the pitch-black darkness of the entire body, and soon, all kinds of eyes open their eyelids in a flash.

Big eyes, small eyes, slitted eyes, round eyes, triangular eyes, sunken eyes. Some were like women, graceful and beautiful, some were like men, sharp and thick, some were like children, and some have sunken eyelids from old age.

Thousands and hundreds of eyes open at once, glaring at the world with bloodshot eyes.

``What, what kind of sorcery was this!''

Youngban screams.

Then, in an instant, the pupils gather together.

It was a chilling sight, with countless eyeballs rolling around in unison, and goosebumps running down my spine without me realizing it.

And then-

The Heavenly Demon True Qi was smiling. He has always been smiling.

In the pitch-black darkness, countless eyes glared at each other with their bloodshot eyes, shedding tears of blood, a muffled laughter that could only be heard as a sound, the saddest and most miserable laughter that forced itself to hide its tears.

The disciples open their eyes and watch.

The death of the teacher was their justice, and I had to just open my eyes and watch the merciless murderers being praised for killing my brothers and sisters.

Because it was a life that cannot be carelessly thrown away, a life that requires the duty to survive in order to avenge the deaths of family members, a life that requires the most terrible duty of revenge, a life that cannot be undone even if one dies.

So let's watch.

I couldn't even breathe, so I covered my nose and mouth, and I could only vividly remember the images of my dying brothers and sisters.

So, amidst the blackened, tainted hatred, only bloodshot eyes, shedding tears of blood, watched everything. Watching.

Countless deaths, countless grudges ask.

The country we built with our blood betrayed us and killed us.

So, what rights do we have?

Isn't it the potter's sole right to destroy what was wrong with the potter's work?

They had rights.

The right to shatter and destroy the Zhongyuan.

So the deaths of thousands and millions demand their rightful rights, so break them, for this was a just demand that even heaven cannot interfere with.

This was the right course of things, the just price that the sinner must pay for his sin.

You have built your nation with our blood and lived your lives, so we will destroy all your lives in the Zhongyuan and establish justice in the world.

If the sky breaks and collapses, the people on earth will be crushed to death, and so the heavens will fall.

The whole world owes us a debt.

The resentment that filled the inside of the Qing finally confronted the figure they had been searching for so long, somewhere in that vast abyss.

One who has a duty to take revenge.

This was the back of the devil, the judge who will exist forever and ever to carry out our revenge, the devil who will destroy the heavens, the devil who will cover the heavens, and the devil who will announce the end of the human world.

You were our avenger, you were ours.

We were your tools, we were yours.

Only then will we become one, and once again follow the laws of the world, the natural order of things that prosper and fall and the prosperous and decline.

The Heavenly Demon True Qi laughs.

Finally smiling.

The eyes that had been floating all over Mine's body suddenly turned upwards and disappeared.

All that remains were the bulging whites of the eyes.

Suddenly, something strange sprouted from the upper and lower eyelids, and it was a human tooth.

Thousands and hundreds of eyes smile at the same time.

Each of them silently opens their mouths with all their might, releasing the anger they have been holding back until now.

A cry that loses shape, a silent cry.

Mine's head suddenly lifts.

The mine's pupil splits in half, then splits in half again, and again, and again, increasing the number of splits in countless ways.

Something more horrific and disgusting than anything Yeongban had ever seen.

``You, you bitch, what the hell-''

The area around Mine's mouth opens wide.

Because the face was already dyed so dark that there was no distinction between shades, only the area around the mouth was visible.

Mine's fist hits Yeongban's stomach.

The body of the spirit bounced off as if hit by a running iron and rolled on the floor.

Then, with my remaining hand, I pulled out the sword that was piercing my palm-

``Hit, hit!''

Jang Cheon-ho was writing evil.

The assassins, who had come to their senses late, started moving their feet again and continued the examination.

Mine swings his arms.

As the magic wand disappeared, the eagle's claw-like fingers drew four black lines in the air.

Blood bursts out and spurts out.

The severed limbs roll across the ground, and then, with a bang, grab the fallen assassin's ankles and swing them around, smashing the assassin's head against his.

Jang Cheon-ho swallowed hard.

Mine cuts off his comrade's limbs.

Lift and swing your comrade's body to hit him, and induce the sword attack to stab and hit your comrade.

Slowly crush the head of the comrade who was shaking until it bursts, then grab it with both hands and crush it with a crunch.

As if, as if playing.

Jang Cheon-ho quickly supports Yeong-ban.

``Ugh, what the hell was that-''

"Youngban, you must evade! We will buy time, so evade!"

``How can I leave you- ugh,''

Youngban's eyes tremble.

The flow of true energy that was turbulent and wild, the pain that feels like some kind of extremely cold energy was seeping into the dantian and scratching, these were the symptoms of smallpox.

Yeongban forcibly suppresses the cold air that was in me and pushes me into a corner.

``I swear by the sword that my Son gave me that I will be before you.''

``Yeongban!''

``Even if we die, we die together, and even if we live, we live together!''

``Please forgive me.''

Jang Cheon-ho's fingers dug deep into the back of Yeong-ban's neck.

Yeongban's body stiffens like a corpse.

Yeong-ban just rolls his eyes and sends a look of anger, but Jang Cheon-ho grits his teeth, hugs Yeong-ban, and runs out.

Mine's eyes turn to the figure behind him.

Hehe, the mouth opens as if it's fun.

The moment you turn your torso and take a step forward.

``You can’t go!'' ``You’ll have to step on our dead bodies!''

The assassins fly off at once.

I would say it was truly a tearful expression of loyalty.

The second-best player in the group was running away with the best player, so no matter how good the spirit of the rest of the group is,

If all problems could be solved with just a determined mindset, why bother learning martial arts?

Thud! Mine stomps his foot.

The ground sinks half a meter in radius, creating a hole the size of a meter wide.

Before the eyes of the assassins, who were suddenly staggering as if crushed by the pressure, a black beam of light appeared.

Behind it, the figure of a mine with ten fingers spread out in all directions was reflected.

"ah."

It was a will left by several assassins at the same time.

Headless corpses fall one after another, kneeling and hitting my shoulder.

It was as if headless corpses were bowing down.

Leaving him behind, Mine leisurely lifts her torso.