\chapter{Be Sure to Maintain Your Dignity When Going Out (23)}

Grumble, groan, the sound of breathing like boiling phlegm echoes irregularly.

A pale woman lying on the bed, her beauty, even though she was bloodless, was truly unparalleled.

The room where the bed was placed was filled with a pungent medicinal smell that gave me a headache.

The original medicinal fragrance was fragrant, but too much of it was as bad as too little, so the concentrated medicinal fragrance that fills the room makes you feel like your nose was falling off.

In front of him, sitting expressionless, was an old man named Assemblyman Je, commonly called Je Elder or Assemblyman Je by the residents.

"I don't think there's any chance of him waking up. All his internal organs were ruptured. His liver, intestines, and all his organs were bleeding and clumping together. Ugh, tsk tsk."

My congressman shakes his head.

It was true that the medical practice of the Zhongyuan was primitive compared to that of the Qing Dynasty, and of course, it was not developed to a level comparable to that of the Western Regions at the time, but anyway.

"How strong was his bones? He's still breathing, but he's already a corpse. His swollen belly was full of blood, so prepare yourself mentally."

Those who listen to him have somber expressions.

Tears welled up in the women's eyes, and at the moment when a single tear was about to flow down along with a pitiful cry of "No" -

``Ugh, huh.''

A woman lying down, the sound of her breathing heavily.

Has Qing finally died? Sadly for some of Qing's enemies, it was simply a cry of pain.

The pain that hits you as soon as you come to your senses.

It's an intense abdominal pain that makes it hard to breathe and makes you start to sweat.

For a so-called modern person, a person from the hometown of Qing, it's a rare empirical fear, the kind that makes you think, "Wow, this was really going to be a disaster."

``Wow, I’m falling behind, ugh, man, man save me. What, wow, wow, wow. Seriously, wow, I’m dying.''

It was a common saying, "I'm dying."

It was a sound that someone with a very painful stomach would make. Although it was an expression that only older men would make, it was a groan made when the pain was so bad that it was an attempt to relieve the pain.

But.

When you're really sick, you can't even speak.

If you can hear these groans, it means you still have some sanity to hold on to.

``Qing?'' ``Miss Ximen!'' ``Miss!''

Suddenly, two people rushed in and tried to grab his hand, but it hit the air, and then they slapped each other's hands away, glaring at each other. It was Murong Zhuji and Seol Iri.

Suddenly, the atmosphere changed to a showdown between Geumnasu and Qing, and Qing's eyes were filled with pain.

What the heck, this was killing me. What were these?

``You’re crazy, stop it.''

Qing was about to throw up her hands but instead wrapped her arms around my stomach, and then not only did my stomach hurt but my chest also started to hurt, making it hard for me to breathe and I gasped again.

I grit my teeth and look around, and there were many happy faces.

But? An elderly man was looking at me with a questioning gaze.

Who are you? I don't recognize your face.

``Uh, uh, hello?''

It was a blue color with a fairly high pain threshold.

It seems like he'll fall behind, but it's not that bad, so Qing nods and says hello.

``Oh, how are you alive? How can you even talk?''

Qing blinked at him.

What? How were you still alive? Shouldn't you be dead? Or maybe?

``Oh, did I die? Or did I just come back to life?''

``No, that’s not it.''

Qing was relieved for a moment.

I guess it's not resurrection. No matter what, resurrection was a bit strange. If someone just died and came back to life, what would it be? They're not even human, were they?

Seeing Qing looking somewhat relieved, I, the member, am dumbfounded.

``How can a sick person with blood in his abdomen be so healthy?''

"Ah, so that's why I can't breathe. And I'm not fine. I feel like I'm going to die. Seriously, if you could give me some food..."

My lungs couldn't expand, so when I took a little breath, they filled up and I felt a sharp pain.

Qing stroked my stomach and thought, "Wow. This was all internal bleeding? How did I survive?"

If I were to consider the opinion of a doctor named Seo Moon Qing, who has a constitution that was prone to blood poisoning, then at least the blood didn't leave the body, right?

Thanks to my constitution, the blood that has accumulated inside me doesn't get contaminated, and to be exact, even if it does get contaminated, it's closer to not having any negative effects, but when I say it like this, it doesn't sound like a real person, anyway.

My congressman quickly reaches out his hand to him.

When Qing, seeing the shape of the hand, obediently held out his wrist and felt the pulse, the member's expression gradually became more and more frowning as if he could not understand.

``Why did you live? Mac, why were you okay?''

Everyone's eyes were on my congressman.

Why did you live? Is that something a member of the National Assembly should be saying?

My congressman coughed at him.

"Now that you're talking, I guess I don't need a slinger. But, how skilled were you? Seriously, if you're a master, you can still be fine even if your organs were completely destroyed."

``Couldn’t that be possible if you learned a special technique?''

``I’ve never heard of such a miracle.''

``Hey, the central plains were so vast. And yet, so many have exploded?''

``It’s not torn, but it’s not bad.''

Basically, a bruise was a type of bleeding.

Small blood vessels burst and pool under the skin, causing discoloration. The current condition appears to be severe bruising of the internal organs due to the pressure of a bomb explosion.

Come to think of it, isn't it all about tyranny?

``What about the fragments?''

"Well, patients don't usually ask that much, but the doctors said they removed the ones that were less stuck and protruding. The ones that were deeply stuck didn't fall out and the wounds didn't heal, so they left them alone."

``Somehow, I had a feeling I was going to fall behind.''

The abdominal pain was so bad that I didn't feel it much, but the muscle pain that came up here and there, I don't know if I should call it muscle pain, but it felt like my muscles were tearing, and the foreign body sensation seemed to be fragments.

``You seem to have learned medicine, so I guess you don’t need to explain much. Oh, where did you learn medicine?''

``Langzhongdaein took a quick look.''

My congressman's expression was one of relief.

Of course, the same goes for the medical community in the Zhongyuan, as there was no other guarantee of identity as certain as the relationship between the people of the Zhongyuan.

Some lawmakers save everyone, some save the rich, and some save the good. My lawmaker was one of the latter.

"Dear Langzhongdaein? It seems you didn't save my Madou. Well, I assumed you weren't Madou since you came running here asking for my life without even knowing what I was like. But you seem to know how to assess my condition, so you can talk to me."

My doctor immediately gathered people together and explained why he had treated Qing.

He said that he thought that if someone were to ignore his own pain in order to save others, he wouldn't be a bad person, and left the room.

And in the remaining room, Qing looked at her friends.

Somehow, he looked quite angry.

``Ouch, it hurts. I’m dying. Oh my.''

Qing lies down, joking.

Then, worried voices asking if everything was okay could be heard from both sides, and before anyone knew it, Murong Zhuji-hee and Seol-i-ri had turned to the other side of the bed and grabbed each other's hands.

Pangdaesan was quietly glaring with three very deep furrows between his eyebrows. Well, what would he do if he glared at me?

"The Heavenly Flower Sword? Don't you have something to discuss with Sima Rang? A so-called Soo-Ma-Gong? The world's best Heavenly Flower Sword was a Soo-Ma-Gong?"

The answer came not from Qing, but from Murong Zhuxi.

``A soju demon? How can you say that? It’s not a soju demon, it’s a goddess and a holy spirit.''

"Are you a goddess? No, that's not it. Wait, you already knew about the Golden Yang Sword? The Heavenly Flower Sword was a small-scale magic-"

``Goddess. Goddess. Goddess.''

``……I learned the divine water of the goddess.''

Everyone's eyes were turned towards Murong Zhuji.

It was a question as if he knew.

Well, that's because we hung out together in Nosan, wearing masks over our faces.

"The Divine Maiden was a martial art created by the Master, and it may seem like a minor magical art, but? Of course, it's entirely possible to misunderstand it. But the Divine Maiden was still the Divine Maiden, right?"

Sima Chunfeng understood right away.

It was true that it was a minority magic, but it was not a minority magic, but a goddess and spirit. The master also knows about it and has expressed his intention to block it in the name of the godmother.

Of course, whether it was a goddess or a sorcerer, it didn't matter, but Seol-i-ri only held Qing's hand tightly and looked down with a furrowed brow.

The highest observation level in Seol-i-ri's history, Ike, Gunyeong-i seems very angry.

Qing said, slowly avoiding eye contact.

"First of all, I'm sorry. But I didn't die, did I? And I was certain I wouldn't die. I never thought, 'I'll save everyone else after I die,' and I never will. I can tell you that with certainty. I have a firm survivalist philosophy that I will live on this earth even if I roll around in a dunghill. I want to make this clear..."

A tendon bulged on one side of everyone's forehead.

``You’re saying that now.''

The Pangdaesan Mountain produces a very low, very low, and infrasounding growling sound, similar to a hometown song.

Qing lowers her eyes, as if she was newly intrigued by the pattern on the blanket.

``I was sick for a few days, not even a swordsman, but I got hit by a flying piece of metal.''

"Heavenly Blossom Sword? The Jincheonroe thrown by the palace's master was nothing more than a piece of metal? A weapon merchant's fire grenade, applying the magic of dispatching troops? Don't you realize that the fact that the Heavenly Blossom Sword was still alive was a complete miracle? Do you even have the awareness that you were the leader of the times, the center of the entire martial arts world, no, the entire Zhongyuan, the entire world, and that you must lead the world in the right direction? The Heavenly Blossom Sword's existence was not only for the Heavenly Blossom Sword, but also for the advancement of the entire martial arts world..."

However, the part where the secret of dispatching troops was applied makes Qingdo reflect a little.

It was the art of filling the weapons with energy, filling them again and again, filling them to the brim, and then filling them again until they could no longer withstand it and broke them into pieces.

Of course, breaking it isn't everything, but the art of directing the explosion in one direction.

The broken pieces of the weapon were lethal just by the speed at which they fly, but the countless pieces that still contain the true energy and scatter in all directions all become dark weapons filled with the true energy.

So, in the same way, Jincheonroe was filled with true energy and was made by carving out each piece.

Did you really almost die?

Did Heavenly Demon True Qi put in a lot of effort?

That vicious demonic energy had disappeared without a trace, leaving only a small, fingernail-sized lump stuck in a corner of the dantian.

Somehow, the surroundings were warm, and other true energies were entangled and in chaos. The flow was very intense, and it seems like all the true energies were mixing together and hitting the wall where the Heavenly Demon True Qi was attached?

It doesn't feel harmful though.

The Heavenly Demon True Qi was laughing… … .

From then on, it was just a lot of useless nagging.

But thanks to that, the attitudes of others have softened a bit, um, but Chun-bong talks a lot, you have to understand that brainy people talk a lot.

``Ahem. Anyway, I’d like to reveal that I’m fine!''

Qing screams in excruciating pain.

Seol-i-ri lifted her finger, poking Qing's side, and looked at him with accusatory eyes.

No, Gunyeong, you too, Gunyeong… … .

``It’s bad.''

``Um. Sorry.''

Seol-i-ri squeezes Qing's hand without answering.

Qing tried to change the subject.

"Rather than that, um, so, yeah, right, how much of me, no. What happened to those assassins? Wait, the Imperial Palace? Come to think of it, the Imperial Palace? How did you know? Did you catch them? Did you catch them?"

A sudden thought strikes me and I ask.

Sima Chunfeng nods his head to him.

Well, if two of the three top-tier assassins join forces, it would be more problematic to lose the top-tier assassin who was injured among the wounded.

His expression becomes urgent.

"Did you kill them? Or, no, since you said it was the palace, those bastards must have been the ones who did it? Where were they now? That's right, those bastards were no ordinary toxic creatures, they're the kind of bastards who bite and die-"

``The measures have already been taken, and since this was a matter that cannot be judged from the perspective of Sima-lang…….''

Qing's expression brightened up very brightly.

Those kids, they were caught alive, right?
