\chapter{Towards that remote, rural village (7)}

Qing's body was now almost fully recovered.

To be exact, the bones have already been attached for a long time, but they were still soft and bumpy and swollen, so they were in the stage of a strong muscle that will gradually subside and become as hard as before.

In Qing's homeland, you can already lead a normal life without any problems at this point, but for the people of Zhongyuan, daily life was hard work, so there might be some difficulties.

Anyway, Qing can walk around on her own just fine.

Why would you just wander around?

Even though the skeleton protected by the Hosin Ganggi was weak, it was stronger than that of the common people, and above all, was the Qing's body just a body?

A monster that transcends humanity, a wondrous body close to a monster disguised as a human.

Compared to when it was in good condition, it was quite fragile, but it was at the level of an ordinary drone, so it can fly around very well.

But why were you still holding me in your arms?

Well, that's convenient.

Gunyeong's ability to support was growing, so although he can't compare to Jian Buxi, the best supporter in the world, I think he's now good enough to be recognized as a supporter.

The third pedestal. The youngest ever to hold the pedestal for the Transcendental Flower Sword, the Chojo Flower Sword, would be an achievement worthy of being recorded and boasted about for generations to come.

Even Gunyeong was still at its peak!

To be honest, I'm a little hesitant to bestow upon such a lowly servant the honor of holding the Heavenly Flower Sword, for fear of it becoming a climax.

What does it mean to have good friends? It's a privilege of being friends.

Of course, that doesn't mean I was so bad that I would feign illness and order my friends around just because it was convenient for no particular reason.

In the Demonic Cult, one had to first pretend to be paralyzed from the waist down due to dissatisfaction with the second half of the body, and since Gramps and Jian Buxi had not yet reached the level of family appealers, they were considered as Demonic Cult followers.

However, the reason why Qing used the exquisite technique of levitation without walking on his own feet was purely because of Jian Buxi.

Even when Qing was fine, she gets gloomy when I don't have her in my arms, so she asks me three times a day, "Sister-in-law, doesn't your leg hurt? Should I hold you?"

How could I let him walk on his own feet when he hasn't even fully recovered yet?

At some point, Xue-i-ri started to secretly pass it off as nothing more than a happy Gyeon-po-hee, who would spend the whole day, sleeping and awake, hugging her only younger sibling.

"Hmm. It's a bit much to go around now, isn't it?"

If that were the case, then even if I had skipped Sacheon and gone straight to Chang'an and taken a comfortable carriage, I would have arrived in Nanju by now.

Of course, I had to take Lan-ah too, and I had a meal with Jayu.

"I don't think it's worth taking unnecessary risks. What if we encounter a group of thieves when you're not in good health?"

"That's right."

"Yeah. Xiao-mei hasn't fully recovered yet."

Gunyeong, who agrees with that, and even Yi-mei?

"Hey, if I ever meet a proper warrior, I'll know. Even in my current state, I can easily defeat a swarm of rascals. Oh. By the way, a proper warrior was someone who knows how to manipulate thoughts in harmony."

"Tsk. That damn Unrestrained talk."

"Why? If San is feeling wronged, why not become an Unrestrained Realm master?"

Qing grinned, revelaing her snow-white teeth.

Peng Daesan sighed at the sight of such a pitiful sight.

"Hmm. Then, shall we try a majority vote? I can't be the boss and tell you what to say, where to go, what to do. So, let's decide democratically."

Despite being three to one in votes, Qing confidently chose the majority vote.

"Okay. Those evil, cruel, ruthless, nameless, thieves were so scary and terrifying that I feel like I'm going to wet my pants and my body was shaking. I should just abandon those who were suffering and resentful because of them, saying it's their fate, and let them continue to suffer. I should just throw them away and go. Like those lowly bastards of the Sa-pa, I only care about protecting myself and don't care about the plight of the common people. Those who want to cowardly run away from the thieves, raise your hand."

"…" "…"

How can you raise your hand when she said that?

It was a very petty, despicable, and even childish trick.

But even in the midst of all this, one person raises his hand.

"Yi-mei, could you put your arm down? I told you all this, so why would you do that?"

"But I still prefer the safety of my Sworn Sister. They're strangers anyway. Xiao-mei is far more precious to me."

Qing wiggled her eyebrows at her.

\textit{What was this annoying yet wholesome situation?}

"Yi-mei? How could you betray me? It won't work. This was really bad. As punishment, put me on your knees and reflect on it."

It's actually a reward for Jian Buxi.

With a cheerful laugh, Jian Buxi sat Qing down on her lap.

Qing raises his hands high, enjoying the soft texture of his plump upper body bouncing against his back.

"Well, Yi-mei isn't a member of the Orthodox faction, so that could be the case. Then, next. As a worthy successor to the Orthodox faction, you must not turn a blind eye to injustice, but stand up to the bandits with dignity and practice righteousness. Raise your hand."

"Wait, wasn't that wrong? Why did the conversation slyly shift to subduing a gang of bandits?"

"I won't take any questions. Please only ask questions that have been agreed upon in advance. Okay, again, raise your hand. Yi-mei, raise your hand quickly."

Peng Daesan, who looked like he had just licked a lemon, and Xue-i-ri, who had a faint wrinkle between her eyebrows, both raised their hands with sour expressions.

"Okay. Then, through a very fair decision-making process, everyone unanimously agreed to proceed with the Hanam trip. Bang bang."

And then Qing hehe, a smile filled with apology appears.

"Hey, don't be so upset. Even if the commoners resisted, there's probably a lot of skilled people among those bandits, and if you leave them alone, the authorities won't do anything. If I didn't know, I wouldn't know, but now that I did, it's a bit much to just leave them alone."

Qing slowly revealed her thoughts.

She didn't have any grand ideas about Orthodox value or anything, but she still don't want to pretend not to know.

Even though Master might hit her hard for being a bitch who hasn't even gotten better yet, she'll probably praise her and say she did a good job in the end.

And honestly, what kind of mere bandits would be a trouble for this Unrestrained Realm master?

If there had been a famous master, there would have been a lot of notoriety, not just rumors of a gang of thieves, but people would have said something about who did what and who did what, but since there wasn't, it meant that they were just average guys.

If those little bastards, who were nothing to her, were a great pain and threat to someone else, then isn't it worth enduring a little inconvenience? 

"What do you think?"

"Hmm."

"I know you feel the same way as Yi-mei. I appreciate your concern for me. I'm sorry for being unreasonable, but will you go with me?"

"If I say I'm not going, you're probably planning to run out alone in the middle of the night again. But at least you're saying it, so it's better than before."

This was what Peng Daesan said with a relaxed expression.

"To be honest, I doubt your meager skills will be of much help. I'm bringing you here specifically to witness the Great Unrestrained Realm prowess, hoping to glean even the slightest clue. Honestly, shouldn't I be getting paid for this?"

At that, Paengdaesan's expression suddenly changed again.

You could say this was the price to pay for daring to recklessly attack the formless and vicious beak of hell without even knowing the opponent.

Wasn't it the tongue that the Tang family recognized and the successor of the Zhuge family admired?

But that doesn't mean that in the middle of the dark night, we should go out to the battlefield with a high spirit of suppression, shouting, 'Where were the thieves? They're all dead!'

First, take a bath.

Because bathing was a serious matter.

Why was the price of water so expensive even though it was a city next to a river?

Of course, this was because the water quality of the river was poor and there was not much river water to wash your body in.

The saying that the people of Zhongyuan do not wash well comes from here, because there was not much river water to wash in.

Such clean water was only available in the southern part of Zhongyuan, Sichuan, Shandong, and Liaodong regions, and in other areas, it was only available in small streams or springs flowing from the mountains.

So clean water was expensive and precious.

So, rich and noble people tend to wash very well.

Bathing was a very important matter, especially for Taoist warriors.

This was because in Taoism, bathing was considered a kind of ritual, a sacrificial rite that purifies not only the body but also the mind.

This was exactly what the term "bath purification" means.

Usually, Taoist rituals were performed daily, however small, and before the ritual, one must wash away impurities through purification.

The reason why all Taoist temples were confined to the mountains was to obtain this pure water, so clean water was considered the most important ingredient not only for bathing but also for meditation and health.

So, in the luxurious inn of Nima, one of the only cities in the Nakigae steppe, there were three proper bathhouses.

That also means that there were a lot of guests looking for a bath.

I think it would be better to just build it big.

Because the people of Zhongyuan consider it unclean to bathe in a large group unless the water was running, it was quite natural to build several small baths.

Anyway, after a long time of resting, the group's skin became very smooth and shiny.

No matter how much you wipe it with a wet towel, it's not as good as getting it wet and wiping it off properly.

Although it was a bit lacking in the luxury of a luxury inn, I woke up after a good night's sleep on a comfortable, Jungwon-style bed for the first time in a while, and Jeomsoi quickly gathered supplies for the night's stay.

They had even prepared a makeshift tent, sleeping bags, thick cotton clothes, dry goods, and a large pile of dried dung from the cows to make a fire, all ready for them to carry like a mountain.

Of course, there were three. Blue was exempt.

Thanks to that, I left Nima not as a martial artist but as some kind of peddler or peddler, and headed towards the narrow valley at the foot of the Langipnap Mountain that blocked the way to the north.

Amazing miracle, Qing walks!

It's almost like a crippled person walking.

Although the luggage was full, it was nothing special for the group that was at the climax and at the climax.

But, it was not possible for Yi-mei, who has a mountain of luggage behind her, to continue to be a burden and balance the front and back, right?

It's a shame that Jian Buxi was gone, but even from Nima's perspective, the LangipnapQingsan Mountain was not an ordinary mountain, so I think it's necessary to conserve some stamina.

As was often the case with high mountains in the highlands, it was a wilderness where it was difficult to find trees.

This was why the majority of the load was taken up by firewood, as it was a village where there was no firewood to be found.

Although the peaks on the left and right do not seem that high, white snow sparkles from around the summit.

The path slowly climbs the mountain. If you look closely, you can see that the gravel has been pushed left and right, and there was a solid, trampled ground. This was the side path that the Gangjok people mentioned.

As we followed the road, we suddenly found ourselves on a rough, steep climb along a ridge, leaving behind a flat hill.

"Is this right? It seems like it would be much faster to just keep going straight."

"Don't stray, just follow the path. It wouldn't have been so twisted for nothing."

"It might not be the road. What if there's a landslide or something on that peak?"

"Wouldn't it be okay to turn back then? Anyway, there must have been something wrong with it."

"Hmm. San. Are you cold? Your lips are blue. Oh, now that I think about it, it's quite chilly."

Suddenly, Qing noticed the weather.

Since he has ice crystals in his dantian thanks to the power of the Ice White God, he can be said to be insensitive to the cold itself.

It's not that it wasn't, but as soon as we left the meadow and entered the foothills, the temperature dropped sharply.

In early December, the temperature in the mountains has already fallen below zero, comparable to Qing's hometown.

"No, it's not just that, the weather was quite… um. Everyone seems fine."

That's right, Qing was immune to the cold, Xue-i-ri was immune, and JIan Buxi was born and raised in the high, frigid lands of the Cheon-san Shin-si, the Cheon-san Mountains.

The warm land of Hebei was not like it was now, even on the coldest night of winter.

So, to Paengdaesan, the sight of three people with perfectly normal faces without a single blush from the cold was rather strange.

If it was like that during the day, how much worse must it be at night?

Pitching a tent at the foot of a sharp cliff blocks the wind, but you can't burn fuel all night.

"I guess there's nothing I can do. Do you want to share a sleeping bag with me? It'll be a little warmer if we share one. After all, we have body heat."

"What?"

Paengdaesan's expression was astonishing.

It's like, what did I just hear?

"No."

Xue-i-ri stands between Qing and Paengdae-san, making a rare display of firm resolve.

"But what if he catch a cold like this? You know what I mean, I've heard it before. There aren't any doctors here."

"If it's cold, you can put rocks in it. Attach a sleeping bag and have them sleep in the middle."

Xue-i-ri, a North Sea native who specializes in overnight stays in cold regions, was able to come up with a plausible solution.

In the end, they heated up a large rock, removed some of the heat, wrapped it in a cotton cloth, and placed it inside Peng Daesan's sleeping bag. And they placed his sleeping area in the center, and placed a special cover over everything to make it even warmer.

"How was it, were you okay?"

"It's warm enough, so don't worry."

"Don't do that. If it's cold, or rather, if it's chilly, you should say it's chilly. If you keep saying that, you'll get a cold, so there's really no answer."

"Didn't I said it's warm now?"

"Don't be like that. Don't be embarrassed for no reason. You're all dressed, so what?"

"No."

"What the hell were you, no, sorry. I'll take care of the fire, so just go to sleep."

It was a blasting device that emits ultra-low frequency sounds.

It's not that it's not true, but Peng Daesan was quite upset, but he can't understand the reason, so he just mumbles in a low voice.

Then Qing's eyebrows twitched.

\textit{No, what is it?}

\textit{Why were you so upset and lowering your voice when I'm worried about you? If you don't like it, then you don't. What's the big deal?}

\textit{I don't know if it's because I'm a woman, but I also don't want to share a sleeping bag with a man.}

\textit{But I thought about it anyway because it would be hard if you caught a cold for no reason.}

Qing was about to say something, but then, ah, that's enough.

If he didn't like it, then he don't like it.

If she keep suggesting something he didn't like, he might get annoyed.

Or maybe his pride was hurt because he was making a fuss about catching a cold despite being a Transcendent Real master.

You have to be a master of the art of painting to argue with a super-talented person.

Who am I? The evolution of the harmony of the super harmony of the harmony of the super harmony.

You have to be lenient and tolerate this much.

So Qing closes her eyes.

Since Qing falls asleep as soon as she closes her eyes, it doesn't take long for her to-

Eyes flashing.

\textit{No, but this kid is funny when I think about it.}

\textit{What the hell were you talking about? Shouldn't you be bowing down to me and shouting thank you while gilding the sleeping bag and giving it to me?}

\textit{What kind of guy is this?}