\chapter{Towards that remote, rural village (1)}

Peng Daesan didn't particularly like to see the world.

His personality had always been like that, mountains were just mountains, rivers were just waters, and buildings were just buildings. The way people lived were all different, so there's nothing particulary strange about them.

Was there any reason to go there and enjoy the scenery?

Despite this, Peng Daesan was still wandered around.

How did that happen?

At first, it was just that there were a lot of people in the house who were nagging him, so he couldn't stand id anymore and went out for a walk (to escape).

The young Pang Dae-san's eyebrows twitched because the women following him were uncomfortable, annoying, and irritating.

So, he headed to the mountains to see how far they'd follow him, and the sight of those vicious creatures was truly a sight to behold..

Their breath wer pounding and they were sweating like rain, but if he casted a glance, they pretended to be okay, only their face s flushed red.

Women who pretended to be elegant, sweating, holding their breath, and climbing mountains wearing nice (but uncomfortable) clothes ended up fainting one after another.

It was the moment when Peng Daesan understood the true joy of hiking.

So from the mountains to the fields, to the rivers and lakes, and then to the temples and historic sites.

Peng Daesan walked around with his face exposed, strided briskly, tried to join escort convoy for no reason (of course, he has never been rejected), and leisurely and slowly.

So, in fact, even if Peng Daesan covered his face with a hat and rode a boat to view the Yangtze River's Wu Gorge, there would be no particular feeling.

There were just cliffs rising to the left and right. The end.

It looked impressive, but that's all. What's so special about a still cliff?

"Divine Maiden, please grant me a handsome son like Jade Qilin…"

"The Holy Fire Pure Land, one's life to break the fate……"
 
However, what was unique was that there were quite a few people bowing and parying towards the Goddess Peak at the top of Wu Mountain.

There were even strange people who chanted, made wishes, and even prostrated themselves on the ground with two palms, two feet, and a total of five torsos, all of which were planted on the ground, all moved along with the flow of the boat towards the peak of the mountain.

It's quite authentic for a folk shamanism that exists in every neighborhood, and it seems like a sight he hadn't seen when he visited a few years ago.

Rather, the sight of those people was more interesting than the cliff.

\textit{Hmm, I guess I'll have to come back tomorrow and see it again.}

The next day.

The number of people bowing down to the Goddess Peak and praying has decreased.

\textit{I don't know if it's because it's an expensive ship, or if it was just a recent trend, so I'll have to come back tomorrow and check again.}

The next day again.

If you board a cheap boat, it will be creaky, noisy, and you will be tossed around by the rough currents.

\textit{If I look at it like this, I'll just get splashed with water. I guess I'll have to come back tomorrow and take a look.}

The next day was thick with fog.

\textit{I guess I'll have to come back and see again tomorrow.}

The next day was foggy again. Tomorrow then.

The next day, it was foggy again.

The next day was sunny, so Peng Daesan got on the boat, and observed those who bowed and prayed.

And the next day, and the next day.

"Little Brother, it seems you are quite fond of the Wu Gorge. The world's gorges were countless, but it was said that you can't say you've seen them all unless you've seen the Three Gorges of the Yangtze River. And the best of the Three Gorges of the Yangtze River is the Wu Gorge. A divine maiden, turning her back, stands atop a thousand-foot cliff, just like a man chasing a beautiful woman."

"…Who are you?"

"I'm an old vagrant named Yuan Hongdao\footnote{One of the greatest Chinese poets and scholars of the Ming Dynasty}. I'm thinking of writing a poem after observing the Wu Gorge, but the majestic scenery makes me feel like my vocabulary was lacking. So I'm looking at it again and again, trying to soothe my thoughts. So, when I see Little Brother keeps appearing on a boat after boats, like a backdrop, how could I not ask your opinion? What exactly about Wu Gorge has so captivated Little Brother?"

"No particular reason. Just so-so."

Peng Daesan had nothing else to say about Wu Gorge.

The cliffs that have stood firm for thousands of years won't suddenly changed overnight, and there was nothing to do, so he gradually got used to seeing them every day and he was just bored to death.

\textit{But why am I looking at something like this?}

\textit{Tomorrow, um, is there anything else to see nearby?}

\textit{Why bother staying in Zigui, a prosperous city but located in the countryside where there isn't much to see?}

\textit{I guess tomorrow I'll just head back home.}

"Just so-so! That's interesting! Even if it seems trivial, doesn't it have a certain charm that draws you in? Hmm, Hmm. That was a good story. Are you planning to take the boat again tomorrow? Then I'll ask you to join me drinking wine."

"Hmm."

Paengdaesan thought about it.

\textit{If an elderly person offered you a drink, it would be impolite to refuse.}

\textit{So, I guess I'll have to take the boat the day after tomorrow.}

He was trying to return home, but ended up being held back by an unexpected connection.

The next day, he drank with the old man.

The next day after that, he offered the elder a drink as a thank you.

And then the next day… …

"You punk, how long are you going to stick around and kill time? Tsk tsk. A man sitting here doing nothing but wasting time, what a good thing. Tsk."

"Elder Chui."

"Who're you calling Elder!"

Cui Liweng snorted.

\textit{Looking at him, he's a fly at first glance. He's not going anywhere, just going out on a boat and coming back. No matter how you look at him, isn't his intentions impure and utterly sinister?}

"Huh, why not swing your saber one more time instead of just foolishly watching the water? If I were that weak, I wouldn't be able to laze around. Anyway, those slick-looking guys were like this. There's no real substance to them."

Peng Daesan secretly had a nasty personality.

If it weren't for that, he wouldn't have gone on a trip through the mountains and rough terrain knowing full well that women would follow him, and he wouldn't have mercilessly left the fallen women behind and gone his way.

Besides, the word 'sleek-looking guy' was the word that Pang Dae-san hated the most, so he trained to avoid hearing that word. Before the appearance of Qing, wasn't he considered the best of the Wulin's Ten Great Families' youngsters (the best in general being Wolbong of Shaolin)?

As the successor to the Hebei's Peng family, Peng Daesan was well aware of his position and the power of his family.

This means that he was definitely not a great person who would listen to the disapproval of a mere village elder.

"Um, um. I'm sorry."

Paengdaesan slowly avoids gaze.

And yet, why was he listening meekly?

Qing introduced him as an old man who was taking care of her, but judging by the way he treated her, he was just like her own grandfather.

If he was your friend's grandfather, he was an adult you should naturally respect, so you wouldn't dare to strike him down.

"You're bowing your head just because an old man said something without any sense. Tsk tsk. I don't like it."

Actually, he probably won't like it either way.

If Pang Dae-san had been confrontational, Cui Liwen would have cursed him, saying, 'A guy like this, who charges without any respect or understanding, would end up dead somewhere'.

"Stop playing around and start training! Starting tomorrow, it'll be perfect if you come to the store and spar with Xi'er."

Paengdaesan wondered for a moment who that was, then realized he was referring to that lewd-looking woman.

They said she was Qing's Sworn Sister.

\textit{Are you saying that instead of just playing around, I should come and check out that woman's martial arts skills?}

"I will do as you wish."

Come to think of it, there's no reason to refuse.

\textit{Rather than just watching Wu Gorge while riding a boat, it would be more beneficial to teach someone….}

And that evening.

Peng Daesan rolled on the ground about twenty times.

He didn't know that he was being taught rather than teaching.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was an apperentice phyisician and knew some medical skills.

Even if she couldn't properly take the pulse or do acupuncture, it meant that she could do simple things like making prescription, suturing, wrapping, or draining pus.

So, after hearing her condition, it was possible to roughly calculate how long she'd recover.

Since her recovery was roughly three times faster, her bones should be fully healed in about a month.

So, if she leave now, she'd be completely healed before reaching Kunlun Sect.

Ximen Surin, who was stroking Qing's head, stopped.

"Where is this unwell woman going?"

"Hehe, if I stop by Sichuan and take our time, I'll be all better before the month ends. I won't be able to train at this rate anyway, so wouldn't it be better to get moving rather than just killing time?"

Ximen Surin, who was listening, was dumbfounded.

'Since I'm sick and can't practice anyway, I'm going to waste time traveling.'

Sounds about right. It's a perfect counter.

In the first place, convalescence was not a time to waste by doing nothing but eating, sleeping, and pooping.

Convalescence was the act of paying the cost of time to heal a sick body.

If you didn't do it right and the bone didn't heal properly or inflammation occured incorrectly, bedsores could form and pus could spread, causing lifelong suffering.

"What on earth was that weird logic?"

"Wouldn't it be okay if Lan-Ah would be there too?"

Ximen Surin looked down at the smiling face of her disciple.

The sick disciple crawled up every morning and evening to pay her respects. Even though she told her not to, she was very stubborn.

In the end, they reached a compromise that she should be brought to the door by a helper, and even if she did receive the greeting, it would be like, 'Well, my disciple was sick, so I won't have her train'.

\textit{I told her not to overwork herself and just lie down for a while.}

\textit{This time, this shameless bitch didn't even refuse, and instead, without a care, she slowly crawled over and lie down on her master's lap.}

\textit{I've never seen such manners in the world. Who is the master? Where did her lack of morality and education come from? It's dizzying and dark.}

\textit{But I can't just keep my disciple in check while she's injured. So let's dicipline her once she's being better.}

Quing may be aggrieved.

Even though she had finally gotten hit with a hydrogen bomb the last time, it was rare for her master to smile so brightly when she held Qing in her arms.

So why was Qing insisted to keep properly pay greeting to her Master? It was to soothe her mood.

In fact, when Qing lay down on her master's knee, the corners of Ximen Surin's mouth naturally loosen and her hands dropped down, and rustled Qing's hair automatically.

Actually, filial piety was nothing special.

Just linking arms with them when you go to the market was already filial piety. It's not something grand, well, actually, it's better to do something grand.

"Ha. If I tell you to rest, you'll listen, but since my disciple has already set her mind, what's the point of holding on to her?"

"Hehe. I'm really sorry."

Ximen Surin looked down at his disciple's face.

\textit{I don't know why she's being in such a hurry, but she's definitely not feeling well.}

\textit{So, holding her back out of concern will only make her more anxious. It's far better to send her out, even if it means feeling uneasy.}

\textit{But, there's a condition.}

"Take your sworn sister along. If that doesn't work, take that bastard Cui."

\textit{Cui Liweng might be superior, but his Qi reserve was still meager and his skills were also poor, so he was no different from the lewd sister who wacing standing the wall of Unrestrained Realm.}

\textit{If they're going to spend time together, I'd be much more at ease with a woman. No matter how comfortable it might be, a woman's handling of things is different from a man's.}

\textit{Since Cui was running a big business right in front of me and gathering experts all for the sake of my disciple, there's no reason to leave the child behind and call him out to disrupt his work.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"You're leaving already when you're not even feeling well?"

Chen Changming's voice was husky.

"I'm just going to meet the Kunlun sect masters for a bit. And while I'm at it, I'll also check out the Absolute Sword Cliff. Why, do you want to come with me? Should I ask Master?"

"No. I want to reach Peak Realm first. Then we can go on a trip. You promised."

Qing's smile deepens.

\textit{It seems that her experience in Mount Lao was an opportunity for her to realize her weaknesses.}

\textit{It's not like she was frustrated or immersed in her training, but I think she's grown up a lot.}

\textit{There's nothing we can do about things that don't work out, but that doesn't mean we should give up.}

Qing stroked Chen Changming's head.

"Our Changming is already an adult? Well, you're still look like a kid, though. What's that? Dwarfism? Our little one's a kid."

"What were you talking about? I'm twenty."

"Oh my goodness. The kid's already twenty? Hmm. But isn't twenty still a baby? She's still just babbling?"

Surprisingly, Qing was very sincere.

\textit{Isn't twenty years old a baby?}

\textit{What if I have to take care of this baby all the time because she doesn't know how to do anything properly?}

But it seems Chen Changming didn't notice.

"What were you talking about? You're only a year older."

"Yeah. That's the setup. Ah. Playing with a baby was hard."

"I'm not a baby."

"There will come a time when you'll be grateful when you hear people calling you a baby. So, enjoy it now."

"I'm not happy at all."

\textit{Well, I guess it has its own set of difficulties.}

Chen Changming was always found being carried around by fellow disciples who were much older than her.

That must be one of the reasons why she hide in Qing's tatched hut after finishing her training.

Anyway, pack your bags.

In the first place, there wasn't much luggage, and it was much more convenient to just buy and use things when needed.

There was no need to carry a full sack like in the days of wandering around, like the old man who gave you a red gift.

At that time, Qing had no money, and even if she had, there was nothing she could really use it for, but she thought she would be in trouble if she didn't have it, so she carried all her belongings around.

"Physician! Come again!"

"I don't want to come…"

Tang Lan-Ah who was thoroughly milked out of free examinations looked quite tired, but it was obvious that she'd stop by again next time she passes by.

"Snow Flower! See you next time!"

Xue Iri was strangely popular.

She claimed to be training all day, spent all day in someone else's hut, and only showed up once during breakfast mealtimes.

Isn't that so? Or is it because we haven't seen each other in a while?

The closer you got to Gunyeong, the more you knew her, the more insignificant she became.

"Grand Junior Master, have a safe trip!"

"Ah, Grand Junior Master, my sun, my light, my snack, if you go now, it will be eternal winter until you return. But since winter is coming soon anyway, isn't that a gain? So you should return before I suffer a loss!"

Leaving behind Siliang, who added more nonsenses until the end, Ximen-Qing, sortied.