\chapter{Towards that remote, rural village (4)}

"I don't know. Huh."

Then, he suddenly turned around and lay down, and when Qing looked down after raising his upper body, his snout was sticking out really far.

This was so cute that it makes me weak-hearted.

"I'm going to see the Supreme Lord. Aren't you going?"

"Huh. I don't know. Just go somewhere."

"Am I really going?"

"Go or not."

Oh, really. How can I put up with this?

It was a moment when Qing's patience was shattered.

Reach out straight and press down on the baby's upper and lower lips with your thumb and index finger.

This may be my own way of expressing my dissatisfaction, but the original version has a round and innocent face with an outstanding appearance from Wulin Ohhwa, so even if he sticks out his lips, he's just cute.

"Oh, really. If I cut the mouth off of this, I could make five plates."

"Moooo! Mooo! Mooooo!"

"This thing keeps acting cute. were you kidding me? You're not some seven-year-old kid, you're just sticking out your lips."

After I let go of his hand, the baby started crying.

His big eyes were so full of moisture that they seemed to reflect Qing's face, and looking at him, I couldn't help but think this.

Well, my face. It's pretty, but it's hard to find a mirror in this neighborhood, so even though it's my face, I can't get used to it.

"You're really going too far. You don't even understand my feelings."

A brief moment of useless self-praise, a moment of forced tears like the occasional Mancheonhwaru, not a real, moist sadness welling up.

Qing stroked the boy's head.

"I know how you feel, Lan-ah. You're worried that I'll have a hard time, that I'll get entangled with those tough guys again and get chased like last time, and you're worried that I won't notice."

"How can you do that when you know everything?"

"I know. I told you I knew everything, right? But what could possibly get involved there? There aren't many people living in Qinghai Province to begin with. And it's the territory of the Kunlun sect's Taoist priests. Who would dare come at them with a sword like last time?"

"But even if our mothers told us to stay, shouldn't Qing'er have asked me to go with her? What kind of fun would I have? I'm always hurting myself and eating my breasts. How can I just sit back and wait?"

"Back then, it was just a shameful past of mine, a weakling who was barely at the peak of his power. I'm a Hwagyeong now, right? Shouldn't I be worried about the youngest, greatest Hwagyeong, Heavenly Blossom Swordnimnim, who has reached the level of Lan-ah? Incidentally, the reason there were three of you was because I'm about three times as great."

At that, Lan-ah's face became a little more wrinkled, and her expression changed from sadness to bewilderment.

Then, Qing smiles gently and gently strokes Tang Lan-Ah's head.

"I want to go with Lan-ah too. But were we just going to hang out together this time? Shouldn't I get some favors from Lan-ah's family? Hey, even though it was the head of the household's birthday, they insisted on taking Lan-ah with them. I didn't see them that way, so it's disappointing. If that's the case, then the next time you try to go somewhere with Lan-ah, they won't look kindly on you."

"……."

"At times like this, I should have accepted the store. Even if my Lan-ah comes to see me later, you'll probably say, ‘Ah, Heavenly Blossom Sword, if it's Heavenly Blossom Sword, I should go see it,' and send me off, right? Right?"

"……huh."

"I'm doing this because I want to see our Lan-ah for a long time. Even if I had my way, I'd tie her up and take her away, even if she said she wouldn't go. Where would you run off to, you're my doctor? But? We have to see each other for a long time. Should we drain the pond and go catch some fish?"

It's a fishing rod. Drain the water from the nail and catch fish.

If you dry the nails, you will have a cartload of carp right away, but you will never be able to raise or catch any more carp in the future.

It means not to sell your future for the profit in front of you.

"I feel sad too, and I'm already feeling empty, thinking about this trip without my Lan-ah. Oh, I just kept thinking about it, and my heart feels like it's being torn apart. What should I do? What should I do without my Lan-ah? Am I going to die of loneliness? Oh, oh, I'm dying. Hurry, hurry, hug me. Hurry."

"Stop it. were you done?"

"Aren't you going to hug me?"

Lan-ah snorted.

But the corners of my mouth were twitching.

"No, really. Qing'er, what on earth were you talking about so fluently? Well, you know, you've got all sorts of bastards and bitches tangled up in you. Oh, not you, Sister Kyeon. Seriously, I'll fool you just this once."

This was the true power of the Qing.

The beak of fear, the formless poison acknowledged even by the Supreme Master, was not only used to cloud the enemy's reason and drive them mad with indignation.

If you make up your mind and open your mouth, you can melt even a person's heart, so you can say that you were at the realm of the tongue of the heart.

"Okay, let's go see Grandfather Dok, or rather, the Grand Master. Um, but what were you doing here? What exactly was this?"

"Uh. Uh."

It's the sound Xue-i-ri makes with her lips sticking out. What was it? Imitating a duck?

A moment when Qing ponders the truth.

"Where did this come from?"

Tang Lan-ah quickly took a step forward and grabbed Xue-i-ri's lips and shook them.

Xue, who always has a pale expression, leaves behind a rare sight of her expression suddenly becoming rotten.

----

Gramps Dok still has a fresh-faced demeanor.

However, we must not forget that he was a terrifying old man who pursues all kinds of ingenious and extreme poisons that aim for social death.

"Oh, isn't that the Heavenly Blossom Sword? Why were you looking for the old man in the back room?"

"Nothing else, I just wanted to ask you something."

"This was an old man's favorite moment. Okay, okay, what was it? Hmm, hold on. I'll get some tea out first. Hey, Mrs. Sacheon!"

Qing suddenly has a question.

Aren't all the ladies working at the party from Sacheon?

Is this a structure where you give numbers from the first to the hundredth house of Sacheon?

In reality, it was not a case of specifically targeting someone, but rather a gentle personality of the Taesang family leader who would appropriately address his subordinates with respect.

If I had to say, I would say that in Qing's hometown, it was a title such as aunt, madam, mother, etc.

"Okay, what were you curious about?"

"Oh, I was wondering if you knew anything about the constitution called Shihyeoldokin."

"Hmm? Blood poison? was that the blood you're talking about? The dead blood that you extract with leeches or something?"

"Yes, maybe."

"Hmm."

The Taesang family leader stroked his long beard.

And the Sachon lady kept pouring the well-boiled tea into the kettle until it was gone.

"I can't really pinpoint anything. I was wondering if there were any Germans who felt that way."

"ah……."

"But, those concepts? Names that seem to have some kind of meaning were actually nothing more than illusions. I think that's the case, too."

"Is it an illusion?"

"Hmm. Do you know what a poison is?"

For those who practice solo practice, there was a dream-like realm, a fantasy realm called Mandokjiin or Dokin.

It was the final evolution of the poison attack, in which the bone marrow becomes poisonous and the blood itself becomes poisonous.

Since poison was automatically generated from the body, unlimited poison attack can be used, and if necessary, all you have to do was spray blood, so it was literally like becoming poison itself.

"Wow, this was truly a weapon of massacre."

"Does it look good? But there's nothing like that."

"yes?"

"No. I just imagined it. If the poison seeped into your bone marrow, you should die. How could you possibly be alive and spewing out venom? Well, there's a theory that you could somehow create a poisonous entity before the cessation of the slaughter. But if that were possible, wouldn't an absolute being like the Poisonous Supreme Lord have emerged before the Great Emperor Mucheon?"

"Huh."

The Taesang family leader laughs heartily at that.

"Having something like this makes it easier to lure disciples, and since they say the higher the goal, the better, it's also good for motivating them. Why, even the most inexperienced people call it the "Gicheonkyung" or "Jayeonkyung"? Why do they insist on giving it a name when no one in the world has ever achieved it? It doesn't even exist in the first place."

"There were no Kicheon-gyeong or Jayeon-gyeong? Wasn't it achieved by the MuQingdae, or rather, the MuQingdaeje senior?"

"Senior, you were in the realm of life and death. Why was it called the realm of life and death? Isn't it a stage that transcends life and death, a stage where you ascend to the zen and become an immortal immortal in heaven? In the end, since you ascended to the zen, you were in the realm of life and death and simply ascended."

"Then why was there a natural landscape called GiQingyeong?"

"Didn't the Great Emperor Mucheon say that he had achieved the level of imposing his will on Heaven to those who questioned his realm? The orthodox martial artists seem to have interpreted that as the next level, but I believe he was originally a man of such strong words. His thoughts were so strong that they defied Heaven. Didn't he say something like that?"

"Then what about the natural scenery?"

"That's the same as being a poisoner. If you reject the path of life and death and strive diligently, won't you become a superhuman, able to control the natural world as if it were your own hands and feet?"

So, it was a disheartening argument that the term "shihyeoldogin" was created out of thin air.

However, as someone who was a blood poisoner myself, this was not a very convincing argument.

"Oh, you said you were going to Kunlun Mountain. were you going there to ask about that? Hmm, right. If it's about magic, that's a different story."

"Different? How so?"

"If we trace back to the origins of martial arts, it begins with the magic of the Invasions of Heaven…"

I'll skip the story I've already heard.

Qing took advantage of this gap to nibble on some snacks. "Oh, Koryo-byeong. Korean food was the best snack after all. This was seriously delicious. I couldn't even eat it back home."

Goryeo-byeong was a food called yakgwa in the hometown of Qing, and it was the original Korean Wave that was introduced to Zhongyuan and shook the entire country.

The bitter tea and sweet yakgwa go so well together, I'm full but still eating it all at once.

I omitted the part where Qingi knows about snacks.

"However, martial arts and sorcery have now become entirely different methods. When a warrior confines his energy within his dantian, it was said that he holds the world within himself. Therefore, once he reaches this state and achieves a perfect world, his will defies the world and bends it. This was called Sasang."

"Ah. You're talking about Hwagyeong."

Somehow, Qing was proud.

"Unlike that, sorcery exploits the world of all, not individuals. Since people also belong to the world, sorcery was about twisting the imaginations of many people and expressing them in the form of language, rituals, and so on."

"Hmm. I have no idea."

"Why, isn't there something called geomancy? Since ancient times, it was believed that the energy of heaven and earth influenced people, and geomancy was simply the formalization of that imagination."

"Hmm."

Qing recalled his experience at Cheonmachong.

And isn't there a lost and depraved version of the first Heavenly Demon hiding somewhere inside me right now?

Is that what alcohol is?

It's like a mental parasite. There were monsters that take over bodies in every neighborhood, right?

"Well, I've only heard that. When I was much younger, I wondered if it might be possible to use magic, since they said it was impossible to poison someone. But with so many charlatans in the world, people no longer believe in magic, and so now, they say all true Taoist magic has disappeared. All that remains were things that don't even seem like Taoist magic."

All that remains were the martial arts called Kangshisul, the great law, formations, and acupuncture techniques.

"Oh, was acupuncture also a magic?"

"Well, if you study medicine even a little, you'll understand. was it possible that someone can't speak, their muscles will collapse, and they'll sleep like the dead just because you press down on them?"

"ah."

"The same goes for alchemy. If you leave a yin medicine alone, will it freeze, and if it's yang, will it catch fire? However, if you mix it well, blend it, and apply your sincerity, won't a miraculous elixir like Daehwandan emerge?"

In the end, the conclusion was that you have to go to the Kunlun School and ask.

But it wasn't that there was no real income, because, well, something, this primitive, ancient, uncivilized Zhongyuan felt more and more convincing.

It would be plausible except for me.

Hmm. Thinking about it any further would be detrimental.

And now, why bother shaking your eyes at my ontology?

I'm here, and my friends were here.

Then that's enough.

I guess I'll have to eat some honey medicine.

I eat, therefore I am.

Qing skillfully changes the direction of thought.

"Oh, sir, but have you been touching anything poisonous lately?"

Gramps Poison's eyes gleamed at him.

It was a sign that someone who was asked a question about their hobby was about to pour out their words, saying, "I was born for this moment, for this explanation."

"Oh! Right. I've been perfecting a few combinations…"
