\chapter{Towards that remote, rural village (9)}

Their gazes collide.

Both the man and the woman had the same expression.

\textit{What the heck, am I seeing things?}

It was the thought that express the absurdity of meeting each others in the middle of nowhere.

With the sound of the hems of their clothes fluttering, three people landed next to Qing.

The impression of the man who had been bending over him suddenly changed.

"Xiao-mei, do you know him?"

"Huh? Yea, I know him."

"The Strange Monk?"

Peng Daesan muttered while pulling out his saber.

In the tension there, Jian Buxi and Xue-i-ri also naturally took a cautious stance.

The Strange Monk Amukhaprap, was the skinny one of two Fat-Thin Duo idiots.

The standoff between them continued for a while, when the grilled fat suddenly dripped, the bonfire flared up, and the meat caught fire.

"\#\#\#!"

The meat that Amukhaprap was grilling with the chief's curses - he put out the fire by waving his arm in the air.

"You damned bitch from Zhongyuan! You're burning your own offering, so even Buddha won't forgive you! Burning meat tastes bad! This karma will be passed down as a family motto for generations to come!"

And there goes the nonsense Zhongyuan language he's always been talking about.

Or rather, should we say that the language of Zhongyuan was quite brave, even though it was pure barbarian language?

Although he complained about the charred state of the meat, he also took a moment to carefully cut off the burnt parts and immediately turned the meat over the campfire again.

And then, without even a second thought, he just focused on grilling people.

Wasn't that an attitude of not caring at all?

When I first saw him, I wondered if this crazy, skinny guy was still obsessed with the magic of absorption and had managed to keep up with it.

"What are you going to do, Qing?"

"Hmm. I don't think we're going to fight."

Qing looked at the corpse rolling next to the Strange Monk.

It was completely sunken and in a horrible state, um, looking closely, it seemed to be a woman.

At first glance, it looked like she could be summarily executed if caught in the act.

Qing decided to start talking for now.

"No, what were you doing? Why are you roasting a person? Are you going to eat it? Is it okay for a monk to eat people?"

"Not a human!"

"I have eyes too, don't I?"

Qing said this and pointed to the corpse in a gruesome state with her hand.

Then, Amukhaprap suddenly burst out.

"Foolish woman! You should pluck out those useless, useless eyes! A human form that cannot be recognized as human. A person without a human heart, not a human, not a beast, not a beast, a dirty beast, a beast that was not good. This bitch was an ugly beast that eats people."

"So, does that mean that this woman here was a cannibal and not a human?"

"You only listen to what a bitch says and believe it. Why, you useless brain. Throw it away along with your eyes. It's a metaphor for devouring, so you ignorant bitch don't understand."

"No, then, what was it?"

"I salute your ignorance. However, I appreciate your understanding, foolish old man who has a vast mind. This beast of a year, a professional bandit, kills people to gain wealth. She lives killing people. She eats people. Do you understand this with your narrow-minded and narrow-minded intelligence?"

The language was a mess, but it's actually easy to understand. I can't say that he's good at speaking Zhongyuan dialect, but it's not like he's bad at it either.

"Oh, so this was a bandit?"

This was the body of a woman who had suffered a sudden decline in status.

Qing thought about it for a moment, but?

There was no reason not to believe it.

First of all, Strange Monk was a master of the Unrestrained Realm.

Even though he witnessed the Nine Solitary Sword's First Movement, he didn't know that Qing was the same realm as him, so he had no reason to lie and evade the situation when he thought he had the upper hand.

And after confirming the identity, he lost interest and returned to his enthusiastic approach to grilling, indicating that he didn't care whether anyone saw him or not. So, he wasn't even wary of spreading rumors.

It meant there was no need to tell lies.

"But even it's not a person, can a monk eat meat?"

"Only you Zhongyuan cultists don't eat meat. Even Buddha ate meat, so people grow tall and live long lives because they eat meat. You Zhongyuan cultists, not eating meat was a direct order from the emperor. You were blasphemous cultists who distort the Buddha's teachings for fear of worldly punishment. That's why you, a Zhongyuan Buddhist, are pathetic."

"Oing?"

Qing looked at Jian Buxi and about to ask 'Is this right?' when Jian Buxi tilted her head as their eyes met.

\textit{Well, why did I want to ask Yi-mei? She wouldn't know anyway.}

Qing's gaze shifted to the side, but looking at Xue-i's pretty face, she skipped her. Finally, her gaze met Peng Daesan's.

This was a process of confirming facts.

Since Yi-mei and Gunyeong probably don't know anyway, the only person who seems to know was Pang Daesan.

But.

"I don't have any interest in reading Buddhist scriptures."

"Aishhh, there's no one smart in this group."

Paengdaesan's eyebrows twitched slightly, but since it was true that he didn't know, he didn't react in any particular way.

"Well. So, this was a thief, an animal that doesn't deserve to be human, and since it's okay to eat animal meat, you're grilling it and eating it?"

"That's exactly it."

"Well, but don't most people not eat it? Regardless of whether they're animals or not, isn't it a bit dirty and filthy?"

"This was my greatness. Through my preaching, I performed the miracle of transforming an ignorant woman into a human being. It's the same as the greatness of Buddha, who guides sentient beings. I don't want to eat, but I'm hungry and have to eat to survive. It's an unavoidable, presumptuous tragedy, yet a sorrow that follows the laws of the world."

"Hmm. You're not going to eat it, were you? Then just throw it away. Yi-mei. Can you make some porridge?"

"Oh! You have realized the compassion of the woman of Zhongyuan. Take refuge in the Buddha immediately! I will give you the precepts immediately. Your Dharma name was \#\#\# \# \#\#\#\# \#\#!"

The expression on her face suddenly turns sour.

It sounded plausible when you don't know what it meant, but Qing had an all-purpose translation function so that all languages ​​can be understood.

"No. How can a person's Dharma name be 'Wise Cow'? Do you think I wouldn't understand if you spoke Xizhang language?"

"How can you understand this precious, profound, and most exquisite language in the world? It's astonishing that a person of humble and vicious Han descent can understand it! Yet, you still lack wisdom. This was the profound thought of accumulating wisdom equal to the vastness of your udders. Furthermore, the ox was a sacred beast."

The titles 'Zhongyuan woman' and 'ignorant bitch' were given a huge upgrade because they said they would give him food.

"Okay, let's put that 'meat' away."

"I worked hard to cook it, so let's taste it. Honestly, I've been curious about it for a long time. It must be so delicious that you Zhongyuan guys would go crazy eating it."

Unfortunately, they have nothing to say in rebuttal.

There must be one or two cannibalistic bastards in Zhongyuan.

"Just get rid of it. If you eat human flesh and you're unlucky, you might get a disease that makes holes appear all over your brain."

In a flash, Amukhaprap threw away the arm he had been so carefully and lovingly roasting.

"What's the fuss? I only told you to throw it away because it'll make you sick."

"I'm exceptionally unlucky. So I don't rely on luck. So, you, prepare your offering quickly. This was a once-in-a-lifetime opportunity to accumulate merit."

There was no reason why they cannot provide a meal to a starving person who has nothing to eat and was trying to eat other people.

They immediately took the pot out of they luggage, and since the milk had already been used up, they just dissolved the dried powder in water and boiled it.

Just tore up some beef and lamb jerky and put it in there and leave it until it thickened.

Whether it was true that he was hungry or not, Amukhaprap sat by the fire, unable to take his eyes off the pot, and gulped down his saliva.

Qing asked him a question quietly.

"Have you decided to give up on the Essen Absorbtion technique now?"

"I have seen your martial arts. There was such a thing as study, proof that divine techniques were unnecessary. Thus, you have proven the absence of divine techniques."

It's nice to hear that.

Qing's groups shoulders also slowly loosen and their tense expressions relaxed, so it seemed they had been tense all along.

But that was only for a moment.

"However."

The words continued, and their shoulders stiffened again.

Except for Qing, of course.

Now, being at the same realm, plus two Transcendent here and one ornamental bamboo lady, it's not like he was an opponent worth worrying about.

"You fooled yourself. You wasted my time. This was a foolish act you failed to prove earlier. But you paid the price for it with your own foolishness."

He was accusing Qing of tricked herself to trick him.

But the one who was fooled was at fault.

"That's a bit absurd, but I'll let it slide since you said you wouldn't blame me. But I heard there's a gang of bandits running rampant nearby. Did you catch just one? You were hungry, so you wanted to eat it?"

"The wisdom of a band of petty thieves. When they meet a master, they resort to lewd tricks. They pretend to be noble, asking for help and offering their bodies. However, they were only trying to seize the moment during intercourse. Since they have penetrated the truth, they present a precious, great man without delay."

"Ah. I see what you mean."

Qing examined the corpse of the thief woman again. It was dented here and there, probably from the Blood Handprint.

So the rest must have run away, and the Strange Monk didn't seem to chase them, whether because he was hungry or just not interested.

There's an old saying in Jianghu that you have to be wary of girls, children, old people, and the great Heavenly Blossom Sword, but isn't it the woman who was the most dangerous of these threats?

Qing had exprienced it before.

\textit{That demonic cult member, who called herself an ordinary villages, had such high bad Karma when she came running naked and begging for help, so I pierced her heart right away.}

\textit{Come to think of it, wasn't it too hasty to immediately kill someone without even knowing what kind of person they were?}

\textit{Of course, it's thrilling to kill villains, and it's fun now as it was then, but I guess I was too absorbed in it back then.}

\textit{And because I was desperate to exchange my Karma.}

\textit{And in the end, well, she was a human trafficker and it was a set-up for kidnapping, so I wasn't wrong, right?}

"Huh? Did she do that even after seeing a monk?"

"A woman's beauty cannot match her own greatness. I'm not a fool who rushes after her holes. Only a woman who was at least a crude imitation of you can make my penis stand up."

"No, that's not it. Is that okay for a monk to do that? Isn't it hindering the path to Nirvana?"

"Foolish you. Adultery was not a matter of choice. Adultery, perverted sexual intercourse, forcibly taking or eating another's female, were the characteristics of beasts. Humans were not beasts."

He's surprisingly sane despite being the one who chases her to get Demonic Art. But?

"Oing? You're saying it's okay for a monk to sleep with a woman?"

"Our Buddha permits. Of course, we have many Buddhas. Some Buddhas prefer eunuchs. The Zhongyuan Buddha does the same. However, you have been granted a precious opportunity to take refuge in our great Buddha. Our Buddha was a generous being who smiles with a contented heart despite your obscene behavior and tangled relationships with your husband. Furthermore, if you take refuge now, you will receive a particularly precious Dharma name for free. If the name of the U-Tsang\footnote{One of three traditional regions of Tibet. Xizhang is derived from its name} was difficult, it will be Zhongyuan name. Mingzhi Nainiu. This opportunity, the chance to leave this world of incredible mercy, was unprecedented."

Mingzhi, bright wisdom. Nainiu, milk cow.

"With such a Dharma name, I will surely take refuge from it."

"I cannot understand. This blessed Dharma name was truly precious."

It seems like he really thought it's a good Buddhist name, not an insult or sexual harassment.

So much so that Qing was momentarily troubled.

\textit{Is this a universal sentiment among the Xizhang people, or was it simply the Strange Monk's own? I guees I'd ask another Xizang monk later.}

"Xiao-mei, who is he?"

"Ah. I haven't even introduced yourself yet. This is my-Yi-Mei, hoooooo. You already knew the other two, right? This is the Strange Monk, um, what was it? Yumomahop?"

"Wow, you really like fishcakes\footnote{Yumo}."

"Oh, how did you know I like fish cakes?"

Everyone had similar expressions except for two.

\textit{What is this? What kind of conversation is this?}

Well, people tended to be very sensitive to the pronunciation of foreigners.

Even if it were Qing, those red-haired people in the West wouldn't call her Qing, instead calling her with the Westerners' characteristic rolling pronunciation of names like ching, cheng, chong, chang, and chink, and they would say it was the same.

The Strange Monk's real name, Amukharap also didn't really have anything to do with Yumo or Mahop or anything. Qing just roughly recited whatever she heard.

Before they knew it, the smell of porridge was already wafting in.

It doesn't smell that good because they couldn't put all the milk in.

He said he was hungry, so as soon as she handed him a large bowl, he quickly stuffed it into his mouth and expressed his admiration.

"Truly a paltry taste! Yet fiercely delicious! When hunger was intense, it was like a delicacy! The Buddha's words were always right! Your offerings were now transformed into merit!"

It wasn't clear if it tasted good or not.

But they understood that he was expressing his gratefulness.

There was three people who eat well, one person who talked, and one Peng Dae-san who sat with a tired expression.

It was a place where every meal was made with dried porridge, so much so that the smell alone would make him shiver.

But Xue-i-ri was a porridge lover who liked everything she ate, to the point of addiction.

Since Jian Buxi didn't eat much in the first place, she just happily looks at her sworn sister who ate well and passed on the jerky pieces.

"Well, so you're going back to Xizhang now?"

"That's right. Henan\footnote{Henan Mongol Autonomous County in Qinghai Province, not the Henan Province} was here, one day north. You too will be like that. I have already seen through your own wisdom."

"Even if you don't go to the Hui area, there's nowhere else to go anyway, right?"

Amukhaprap cleanly ignored her and continued to speak.

"So, another amazing opportunity. Receive this gift and accumulate merit. Your future, where you will be praised by the Buddha in paradise and be reborn as a human, will be decided here."

"Hmm."

She looked around at her friends.

\textit{I understand there was no hostility.}

\textit{Still, I don't really want to hang out with a Demonic Adept who was looking for Demonic Art. His Karma is also no joke.}

\textit{And my friends probably feel the same way.}

Then a thought suddenly occurred to her.

"Well, how about this? There's a gang of bandits running rampant in Henan right now, so we're trying to clear things out. If Yumomahop help out, wouldn't that be a chance to earn that virtue you keep talking about?"

Then the Strange Monk started hitting both of his thighs, just the skin on the bones without any flesh.

"How admirable! Why are you still in this world? Saving beasts is your karma!"

And then he continued speaking with a serious expression.

"But you were wrong. This means I am not helping you, lowly beings. You ware helping yourself. If you agree, you will have the opportunity to accumulate merit."