\chapter{Towards that remote, rural village (5)}

Originally, I planned to have a quick breakfast, set off, and then diligently climb the DaeXue Mountains.

So, three bowls of easy-to-digest porridge, one bowl of soup to avoid the boredom of just porridge, or rather, soup with noodles? Oh my gosh! But I always welcome these kinds of twists.

Eating only the main dishes feels empty and doesn't feel like a full meal, so I just have a simple breakfast with about five dishes.

And finally, let's go!

If you were to do that, wouldn't the head of the family, Dangtujuk, come out and stop you?

"Hey, you're not planning on crossing the mountain range like this, were you? How did you know you were going to make your way through that vast, snow-covered land?"

"Well, wouldn't it be okay if I just got my bearings? I can just get over the mountain…"

"Oh dear. You're not from Sacheon, so you might not know. It's not a land you can just navigate by looking at the stars and finding your way, like in some other place. Without a guide, even for experts, it's not easy."

"Hmm. It's past Cheonjasan Mountain."

"But there's no ice at the top of Cheonjasan Mountain. If you climbed a cliff over a thousand jang and there was no way back down, would you turn back? Even if you did that a few times, it would take several days. Of those, there were well over forty peaks that were two thousand jang tall."

But, unlike the memories of the Qingdo Cheonjasan Pass, I didn't just pick a direction and go straight, so I didn't come without thinking. I heard that there was a path that went up to Qinghae along the river.

The saying that Sacheon was a natural fortress was something that was said a thousand years ago, when the Yu, Jo, and Son families were wrapping up the world for the Sima family.

Isn't it now after roads have been paved here and there for people (and only people) to travel?

It's just a bit rough and dangerous, but it's for civilians, so what for the martial artists.

Even though they were embarrassing chicks who were just mere rascals, they still have their own tricks.

If it was a dangerous road to begin with, Master would have stopped me from going.

"I already found a good guide, so he said he'd be back around lunchtime."

"Well, thank you for your kind words, but-"

"Right! Since you're in Sacheon, shouldn't you try the famous Cheonhajeilsuksu's Mala Ultimate Soup?"

Somehow, it was a suspiciously desperate party.

But Qing couldn't sense that-

"omg."

I was so surprised that I didn't even have time to feel suspicious.

Oh my goodness! That's right, I forgot about that!

How can you come to Sacheon and not eat Mara Gunggeuktang? If you do that, then there's no point in coming to Sacheon.

When you think of Sacheon, you think of Mara Gunggeuktang, and when you think of Mara Gunggeuktang, you think of Sacheon. Sacheon exists because Mara Gunggeuktang exists.

Even in Qing's hometown, there was a city built for a bakery.

The bread was so delicious that people couldn't leave and settled around it, eventually turning it into a city. This was a fact from the watermelon story.

"Oh, but wasn't that person booked for a year? Or was it a season, not a year? If I were to leave now, I'd have to push someone away. I'm sorry, since you must have come expecting it."

He swallowed his admiration inwardly.

I felt it before, but the child was so dignified and kind that he was already an adult.

Our baby was the cutest in the world, but I wish she would learn from Heavenly Blossom Sword just a little bit.

How can such a mad dog have such a disciple? Where in the world was there such a law? No, isn't there?

It's because he's a disciple like this that he's holding up well under Yeo Gwang-gyeon. If he wasn't, he would have broken his dantian and run away a long time ago.

"I've made a reservation once a day in the name of the Dangga, so I'm taking turns trying them out at Danggata. Can't we just postpone our turn by one?"

This was not a lie.

After the previous chaos, I reserved one seat per day, so it was an extreme (extreme) daughterly love, telling me not to carelessly delay someone else's turn like last time and get involved in unnecessary trouble.

Why were you making fun of the reservations that have already been made? I'm taking applications for Dangga-ta and passing them around to let people try it out one by one.

"Hehe, then shamelessly. Swish. Gulp. Ah, my mouth was watering already."

The dangtujuk smiles at him.

Although not as cute as Ah-ah, isn't she a pretty cute child?

It's really nice to see her acting cute and cute, saying things like, "Even after preparing such a lavish meal in the morning, my mouth was watering," hehe.

"Gulp. Ah. Just thinking about it makes me want to eat it right away. You haven't tried it, have you? I told you it's truly the ultimate soup."

Qing's reluctance stopped there.

… … It's cute, right?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Malatang? It's not even a dish in the first place. Is it worth making such a fuss about?"

"No, I told you it's really delicious."

Pengdaesan had to listen to praises of malatang all morning.

In the first place, a true delicacy should be tasted without explanation, so raising expectations by making a fuss like this was the worst of the worst.

Thanks to this, he felt like he had already eaten a hundred bowls of malatang.

Although Peng Dae-san was not particularly picky about food, as the eldest son of a five-generation family, it could be said that he have a wealth of culinary knowledge.

These children of prestigious families, those whose taste threshold has been elevated to the heavens through precious foods since childhood, were the true gourmets.

It was different from the owner of a dog-like food sense, who was like a dog, who scrapes everything clean and eats it as long as it was good enough for humans to eat, and even licks the plate to clean it clean.

So, the true gourmet's evaluation is.

Mararani?

The horse was said to have a bitter taste in his mouth, making it numb and blurring his sense of taste.

The purpose of rinsing your tongue with tea during a meal was to enjoy the taste more richly, but how can it be considered proper food if you put in ingredients that ruin your taste buds in the first place?

I heard that there was a theory that people would boil the ingredients in water and add spicy seasoning to hide the spoiled taste.

So, any food with the two letters Mara in it was absolutely not a proper food.

It was a harsh assessment of Peng Daesan.

Anyway, the owner of the house said-

"I've found a brave guide, so he's probably already at the reservation desk. He'll be my guide in the future, so it would be nice if we could get to know each other over a meal together. Ahem."

That wasn't wrong.

No matter how much money was exchanged between employer and employee, if they become close, they tend to give each other a little more convenience.

Of course, that wasn't entirely true, because there were a lot of bastards who would turn into robbers if they were the guides of Zhongyuan.

The guide who saved me from the Tang family would never do that, but anyway.

So the door to the private room opened.

And then Qing realized why the head of the family had insisted on holding onto me and asking me to have lunch with him.

"Huh? Ziyou? Isn't it Ziyou?"

It would be a dizzying situation for an ordinary person.

I opened the door and there was the prince. He had already arrived and was waiting, so I couldn't tell how long I had been waiting.

But Qing was not an ordinary person.

If he was here as Ziyou, then he was Ziyou, not the Grand Prince Dexian.

In fact, even if it wasn't Qing's idea, he was of the same rank.

"What the heck, somehow. I was already worried about leaving without seeing your face."

"Did you even have that thought? I was quite disappointed that you didn't show your face even once."

"Well, what can I do? I can't just carelessly visit you."

Ziyou had to agree with that.

If the Heavenly Blossom Sword entered the Grand Prince mansion, it would only cause useless rumors to spread, and neither Qing nor Ziyou would welcome it.

"And you decided to speak like that?"

"Ah. Right. I see. I forgot. But-"

Ziyou was about to say something, but he stopped talking when he saw Peng Daesan entering the room a beat late.

"Hmm."

Paengdaesan's eyebrows also twitched.

The two men's eyes met uncomfortably.

"Ugh."

In the meantime, Tang Lan-ah let out a suppressed sound.

"Lan-Ah, stand up. This is Ziyou, my friend. Ziyou, you already knew Lan-ah, right? This is Jian Buxi, my um, Yi-mei, uh."

Jian Buxi's expression was bright and cheerful.

\textit{She like it this much, so it's worth sacrificing my hands and feet to summon goosebumps.}

\textit{Still, physiologically, it's kinda, ugh.}

Qing continued the introduction, shaking off the goosebumps.

"This is Young Lady Xue-iri, the Snow Flower. Oh, you know Jade Qilin, the most handsome man in the world? This is him, Peng Daesan."

"Ziyou."

"Peng Daesan."

Peng Daesan just answered each question as it was asked.

But the man next to Jayu didn't seem to think so-

"Oh no! Fire-"

"Sit down."

"Yes!"

But he just got his butt kicked in, so, as far as I remember, what was it? I think it was someone called a dog. Was he a Yangsang dog?

"I heard you're going to Qinghae. Yang Sang-gu here knows the way. I brought him here to work for you. He's a guy who's just freeloading anyway."

"Hehe, Young Lady, it's been a while. Treat this worthless little person like a dog, I'll do my best."

Akabi. It's one letter different.

Anyway, since they're all dogs, it's no different than matching them. It's just like matching them. No, it's just matching them. I matched them.

"By the way, are you feeling okay?"

"You know I'm strong, right? And I'm almost completely healed now."

"Is this really so urgent that you have to go when you're injured?"

"No? I just don't want to waste time just sitting around, so I'm going to get better on the way."

Ziyou's expression was now distorted by the feeling of what he heard.

This was also a common expression made by those who heard about Qing's efficient time management.

"What kind of dogshit is that?"

He was so flustered that even his tone turned informal.

"Why? Since I can't train lying down anyway, wouldn't it be better to borrow someone else's, or even a friend's, feet to get moving?"

"…?"

"Oh, anyway, how have you been?"

That was the time when the two of them exchanged stories, one woman looking at them with a quizzical expression, two women with no thoughts, and one man who looked very uncomfortable, and time passed in a daze.

"Oh, aren't you Miss Heavenly Blossom Sword?"

"How have you been, too, Master Chef?"

"Whew. It's not easy. I'm trying to come up with an Ultimate Ultimate Malatang that will surpass Ultimate Malatang, but I can't seem to get the inspiration."

"Oh."

\textit{Already at the pinnacle of malatang, you're still trying to surpass it. You have a mindset that truly deserves to be considered the best. Is that how you can be called the best in the world?}

\textit{I want to suggest something, but I can't think of anything. Why would I add anything to a malatang that's already reached its peak?}

So lunch.

"Oh. This is delicious. Here, Xiao-mei, this is the best. Cow? It's beef, right?"

"If it's delicious, Yi-mei should eat it too…"

Jian Buxi picked out the most delicious ones and put them on Qing's plate.

"This. It tastes strange. It's bitter."

Xue-i-ri doesn't seem to like the shape of her mouth.

I thought she would like hot soup, but the subtle furrow between here eyebrows suggests that the numbing sensation of malatang didn't suit her taste.

"Huh. Is the malatang bitter? Are you a kid? Should I order some sweets?"

Tang Lan-ah was chattering next to Xue-i-ri, who was constantly gulping down tea.

\textit{I don't know what eating malatang has to do with being an adult.}

\textit{Oh, is that so?}

'Do you find mala-tang bitter? You grew up so smoothly that you didn't have to worry about bitterness. After going through so many bitter things, you just think of refreshing beef soup?'

Of course, since Gunyeongi must have been very bitter, you might not want to eat it because it was bitter.

Anyway, since there were several dishes other than mala-tang, I guess I gave up early.

Hmm. It's delicious. Once you get used to it…

It's truly a sad thing that we can't share delicious food together.

Anyway, the spicy ultimate soup I had after a long time was truly the ultimate.

"Hmm. Why don't you stop by sometime? Yes, like last time, why don't you try use the veil? The guys at home were making a fuss about wanting to see you, so you should at least stop by sometime."

"Well. Master told me not to wear veil this time. But if I ever come to Sichuan again, I'll wear it."

\textit{Still, coming all the way to the neighborhood and seeing his face somehow gives me a warm feeling.}

\textit{To be perfectly honest, I didn't really think about it. 'Oh, right! I have Ziyou. Yes, I have a friend like that.' That's how it felt.}

"Should we elope now?"

"Oh, no. Lan-Ah can't do that."

"Can't you just tell me to follow you?"

"Then you'd really follow me."

"Tch."

Leaving behind Tang Lan-ah who was dripping with foolishness until the very end, it was a truly rewarding time, even though it was half a day late.

Although it's a bit questionable, now that we have a competent guide, it might actually be a win-win situation, shortening the schedule rather than delaying it by half a day.