\chapter{Towards that remote, rural village (3)}

The view of Divine Maiden Peak from the boat wasn't particularly impressive.

Because it's the mountain behind my house…

It looks small when you just look at it from below?

Among the Divine Maiden Sect buildings hidden behind the peak of Divine Maiden Peak, the only one built facing the Yangtze River was the Qing Mo-ok.

But since it has a fairly large front yard, it's obvious that you can't see it even if you look up from below.

If I just take a boat and climb up the cliff, I might be able to get home a little faster.

If I really wanted to climb up, I could grab the cliff and climb it, but it was a rock that jutted out in a more steep and jagged direction than vertical.

After passing the 120-mile long waterway with high cliffs on both sides, a brief moment of openness was felt through gentle ridges and sparse plains.

But that was only for a moment.

The waterway narrowed on both sides and the cliffs rose higher and higher, so this was the gateway to Gudang Valley, also known as Gudanghyeop in the central region.

The narrowest waterway of the Gudanghyeop was only twelve jang wide, and yet the highest cliff was four hundred jang high.

If you take a boat and look up between them, the oppressive feeling as if the earth was rising and tightening around you was a breathtaking view.

Then, after passing through the short Gudanghyeop waterway, which was about 40 li away?

Unfortunately, from then on, the height was a bit lacking and the cliffs were not very sharp, so it was a series of scenery that seems familiar but not familiar.

Then, after leaving the mountain, you enter Sacheon.

Of course, Sacheon was a large land to begin with, so wouldn't it compete with Qinghai Province for the largest area among the provincial cities in Zhongyuan?

There's still a long way to go.

The road from Junggyeong-hyeon, Sacheon-seong to Chengdu, the capital of Sacheon, was blocked by three long, narrow mountains, so it follows the upper reaches of the Yangtze River and heads towards Hapcheon.

How have you been so far?

I am in a very luxurious state of recovery, eating well all the time, eating snacks whenever I can, and spending time lying down or sitting down.

The food was so expensive that it breaks your legs, so no matter how much you eat, it's only a profit if you don't take taxes on this much logistics.

There were already a lot of snacks there, including dried fruit, pickled fruit, dried snacks, honey snacks, candies, and all kinds of meat, and the endless supply of snacks and snacks keeps coming out.

So, today, Qing, who enjoys a hearty meal and then lies down after eating, enjoys her rightful right today as well.

In normal times, Pang Dae-san would grumble, saying, "You should move a little after eating," but isn't it a patient's duty to lie down properly?

Tang Lan-ah gently strokes and pokes Qing'er's swollen belly, and even grabs it and pulls its soft belly fat, and then quickly comes to a shocking conclusion.

"What? Why don't I gain weight even though I eat so much? My stomach was just bloated, I haven't gained any weight at all."

"Maybe I just don't gain weight?"

"No way. I gained weight just by munching on a little bit of food from the side. It's unfair. How could Qing'er do this to me?"

It's not that it's not true, Tang Lan-ah has gained quite a bit of weight over the years.

Even though she originally had a round and cute face, her jawline, which was quite slender, has become much rounder, and her chest, which was secretly fleshy, has become a bit plumper.

In Qing's eyes, it's okay because she's cute. She was too skinny before, but she looks good now.

I was just trying to offer some comfort.

"are you okay."

The unexpected answer came from Xue-i-ri.

These two people were so cold that a chill rushes through them just by making eye contact.

The expression that a cold air was blowing does not refer to the air current between the two, but rather because Xue-i-ri actually blows out a cold air.

After discovering that Tang Lan-Ah, who grew up in the warm land of Sacheon, actually feels quite cold, Xue-i has been secretly lowering the indoor temperature.

Qing was immune to the cold, and Jian Buxi, who lived in the frigid frozen land of Cheonsan, was not strong against the cold, and Peng Daesan does not share a room with her and does not seem to be particularly sensitive to the cold.

Although it was originally strong against the cold, it was insensitive to the cold itself due to the effect of ice crystals.

What the? He noticed that the room was a bit chilly, and when I warned him that he couldn't use it, he didn't say anything and just shivered, saying he would endure it. Only then did he breathe a sigh of relief.

Does that kind of person agree with what I said?

What the heck, they say kids grow up fighting, and that even if you hate someone, you become attached to them?

After all, letting them fight was the right answer-

"What? What's okay?"

"Because it's not my body. Fat. Piggy. Fluffy."

"This was really……! Let's see."

By the way, Xue-i-ri doesn't gain weight either.

A big eater who secretly eats for a long time, and who keeps eating snacks next to her while maintaining a slim body.

Originally, people in the Ice Palace didn't gain weight.

In fact, it was purely the child's carelessness.

San-i goes out onto the deck every hour to swing his sword, and Hee-mae eats little, perhaps because of the poor food situation in Cheonsan Shinshi.

Gunyeong also spends most of the day with his eyes closed, meditating and concentrating on his energy. He doesn't pay any attention to the beautiful scenery or anything else, and was diligently working on improving his meager and pitiful internal energy.

But what about Lan-ah?

It just sticks next to Qing one, so when it's time to eat, it eats, and when it's time to eat, it sticks next to Qing one and chatters.

That thing over there was cool, wow, it's so pretty, it looks like a turtle, it looks like a crane, you must be really enjoying your trip.

Of course, from Qing's perspective, there was no better companion than this, so he was a precious friend who relieved the boredom of just lying down and hugging her.

Of course I gained weight because I played so much…

The child may feel wronged.

Even if you throw a secret weapon, you can't just poke a hole in someone else's stomach, and to cultivate dogmatism, you need the poison of a family's vision.

Just because you eat any poison doesn't mean it will be absorbed into your body.

Moreover, since poison was a consumable item, it decreases as you use it, so you can't waste it by swinging poison or poison stick.

Of course, it was just a cowardly excuse.

Just ten days on the boat.

Before I knew it, there was an endless horizon on both sides of the river.

The fertile plains of Sacheon, where it was difficult to find even a small hill, stretch out before you, giving you a sense of spaciousness.

Because Qing was from a different country, this side was more unfamiliar and comes across as a wonderful scenery.

In my hometown, the city was filled with skyscrapers that blocked out the sky, and even when I left the city, there were always round, tall mountains rising in the distance, so I never got to see the endless, level land.

So we got off the boat and finally arrived in Hapcheon!

If it takes ten days to come up the Yangtze River, it was like sucking the honey, so wouldn't it have been like eating through the sharp, insurmountable mountain range of the notorious Shu Han in just one day?

After five days of leisurely riding in a carriage along the well-maintained highway, the streets of the holy city come into view.

And it was a journey that took ten and six days to pass through the main gate of Sacheondangga.

Etiquette that was usually followed when visiting a friend's house.

First, I greet the master of the house, and for the evening banquet, I enjoy the fiery dining skills of Jin Gi-myeong-gi and Cheon Hwa-geom to the fullest. was this a human or a squid? I perform a devilish performance that pushes food in without even chewing.

And then, wouldn't Lan-ah's mothers (the concubines of that famous family) invite the women to have a cup of tea together?

however?

"Hey, listen up. Your father's birthday was early next year. were you going to Qinghae Castle now?"

"Oh, ah."

The little girl flinched at that.

"They say that no matter how you raise your daughter, in the end she's still someone else's child."

"My one and only daughter, so precious, so precious, I raised her so preciously, but now she's saying she's going to the countryside with a friend before her father's birthday. Oh, Heavenly Blossom Sword. I'm sorry. It wasn't Heavenly Blossom Sword's fault."

"It's because I don't have a good head. It's hard for Heavenly Blossom Sword to adjust it."

"I was already worried about my child's lack of friends, but thanks to Heavenly Blossom Sword, I'm relieved. But my child was still like this. He's so stubborn."

"Ugh, wouldn't it be okay if I just go and come back quickly…?"

"Does that make sense? How were you going to get into Sacheon?"

"Heavenly Blossom Sword, if it's alright, how about staying until New Year's Day? Well, then I guess we won't be able to cross the mountain range until next spring."

It's now past the middle of November.

From mid-December, it starts snowing and freezing right away, making it difficult to climb to Qinghae.

So if you're planning to leave, you should leave now, or go after mid-March.

Of course, when you return, you just have to come down to Gansu Province along the relatively gentle Nanning Hills.

To begin with, the road from Sichuan to Gansu Province, where the famous Shutu and Jiange were located, was the most dangerous road in Zhongyuan, so whether you head straight to Qinghai or go around to Gansu, both will soon be blocked.

Qing understood the mothers' intentions.

Even if you tell her not to do it, the wicked woman of Sacheon was not one to listen.

It's the head of the family's birthday and all, so it's obvious that they'll force themselves to go along.

So the reason I'm telling you too was so that if you go, you can leave our child behind.

Of course, it was more dangerous now, so I had a stronger intention to rest at the party this year and then go up next spring.

If I had to say something, I would say that instead of suffering by climbing a mountain in the winter, you should rest and have fun. If you really have to go, please stop this.

Of course, I appreciate your concern and the suggestion that I rest before going up, but in that case, it would be better to just take a boat back to Divine Maiden Sect and spend the winter there.

I've come this far, so why go back?

So what?

"Hey, you're not going to leave me behind, were you?"

"I'm going, but this is Lan-Ah's home."

"Oh, that kind of thing, that kind of thing? I'll go too! I'll go too! I'll go too!"

"But it's a family matter and… shouldn't you celebrate your father's birthday?"

"Father's birthday was next year, the year after, and the year after that, but this was the only time I'm going to Qinghaeg with you. Don't you know what's more important to me right now?"

"Huh? How about that, um. No."

Qing barely managed to chew and swallow the words that had reached her tongue.

\textit{I almost asked how she could guarantee that she would be able to celebrate his birthday next year, the year after, and the year after that.}

\textit{The thought meant well, but it's a bit ambiguous to say it.}

"You should stay home. Your father loves you the most, Lan-ah."

"Since you care about me, won't you understand?"

"Oh, I'm sorry to upset you."

"Tch, Qing'er, how could you, how could you do this to me! I hate you! I'm going to hate you!"

Then Xue-i-ri nodded to him.

"Miss Ximen. I'll go to the bedroom tonight."

The three of us took turns switching left and right, so it seemed like today was a really fun day for Lan-ah.

"What was this? Why'd you get to decide?"

"I'm not being sarcastic. You just said you hate Young Lady Ximen."

"I didn't say I won't sleep here, did I? Um, Qing'er? Can't you let it slide just this once? Just once? Okay? Just this once, and you can go with me, and I can take care of Father starting next birthday. Okay?"

And then, the voice of Lan-ah's mother flashed through my mind.

They say there's no use raising a daughter.

In fact, there were five of them, so it's impossible to tell the order of precedence between the second and third.

I was so blessed to see you.

There were five mothers who look at me with affection, and I am enjoying it five times more, but I am thinking of going on a trip with my friends.

In fact, since mothers were the ones who can see Lan-ah most accurately, wouldn't it be better to ask Qing to do it for you?

"No. I won't let you come along. I have no intention of letting you join. You should stay. No, this was Lan-ah's home. Anyway."

Qing answered firmly.