\chapter{Towards that remote, rural village (2)}

As always, we stop by Zigui first.

As per the master's strict orders, I have to take Gyeonpohee, and if that doesn't work, I have to take my grandfather.

Not only that, he entrusted the sword to the company.

The author, who was the master, was a master, and since he handles weapons so carelessly, even if it was a masterpiece that a blacksmith put his heart and soul into, it cannot be okay.

The Moonlight Sword (ten-ho) cut through stone walls and rocks, cut through the flesh and muscles that were strong enough to defend oneself, and even cut through the weapons of others, causing teeth to gradually fall out and cracks to spread here and there.

Just because it wasn't broken at all, it's enough to be considered a famous sword.

So, to find the weapon and the stand,

Xuega Sanghoe.

"Oh my gosh, miss! What a miracle!"

Even though his face was completely healed and he looked fine, he was sitting in someone else's arms.

The Xuega Sanghoe staff don't care at all.

Is it any wonder that the Great One rides on a man?

It was also a glorious place where if we receive an application for the pedestal of the Heavenly Demon Lord, everyone will rush to it and a bloody battle will break out.

And it's not a sight I've seen once or twice before.

"Have you come to see Mr. Choi?"

Qing tilted her head.

Isn't the abdication method a bit strange? Was there a abdication method in ancient China? It seems like there was some problem with the translation.

However, the act of pointing out the original law of oppression was proof of a small person.

Since he was a great man, I didn't bother to ask him.

"I'm going to see Gramps too, what about Yi-mei?"

"Ah, Net! I'm at the training ground right now. Can you tell me what's coming and going?"

"No. I'm training, so don't bother me. I'll go and see for myself."

"Yes, Miss. But, this…"

"Oh, hmph, hmph, figs, dried figs, right?"

"Oh, you really were a genius, Miss! You can see through the snacks in my pockets!"

It would be more accurate to say that he sensed it through rather than saw through it. In any case, it means that he guessed it right.

The sense of smell was comparable to that of a dog.

The upper-level employees who followed quietly approached, and as always, they shyly offered snacks and then quickly disappeared.

I'm a little curious about where the snacks come from and how they know when they'll arrive and how they prepare them.

The correct answer was that if Qing was at the Divine Maiden Sect, she prepares new snacks every day in preparation for when she comes. If she doesn't come, she can just eat them herself or give them to her friends, children, lovers, or wives, as it has the effect of making relationships harmonious, so it's not really a big loss.

Anyway, Qing doesn't know, he just eats it because it's given to him and it's delicious, so he just eats it.

The snacks that last a while were put away for now, and the snacks that go bad quickly were eaten up right away as soon as they were received, giving great joy to the upper-level staff.

As soon as you open the gate to the training ground surrounded by a high wall in the courtyard of Xuega Sanghoe, you see Gyeonpohee in a strange but cool pose on the other side.

Both arms raised high into the sky, both arms crossed so that the wrists almost brush each other, a graceful look.

The expression on his face was serious, unlike the always fierce Jian Buxi. What was this? Why were you so cool?

"Huh?"

Qing'er jumps out of Xue-i-ri's arms.

He took a few steps forward, then suddenly spread out both arms and grabbed Inyeong who was falling from above.

"100 million!"

It would have been nice if only my physical condition had been normal.

As if to accept it, he lowered his arms, shoulders, torso, pelvis, knees, and ankles with the elasticity of his entire body, and the bones, muscles, and tendons that had absorbed the shock of the fall protested in unison with intense pain.

Ximen-Qing, plus four days until recovery was complete.

But, I persevered!

He looks down at Mount Paengdae, which he holds in his arms with care, as if he were holding a precious young lady.

"Whoa, what the heck, why, phew. Falling from the sky?"

"…It wasn't to the extent that I would have been hurt even if I didn't accept it."

"Didn't you fall from quite a height? What the heck, the mountain? Even the sky was flying now? What the heck? Falling things have wings?"

"Hmm. Would you mind letting me down now?"

Qing chuckles at him.

If you ask them to get off, it's common sense not to give it to you.

"No. Keep doing that. Oh my, it hurts. Don't move. If you move, it'll hurt me. I'm still recovering. My bones haven't even fully healed yet."

Peng Daesan, who was trying to escape by force, flinched.

Whether or not Peng Daesan, who was held like a princess of the Western Regions, wears a arrogant expression.

"Xiao-mei!"

Jian Buxi, with her face as bright as a child, runs towards me quickly, calling out to me.

He threw aside the mountain of Pangdae that he was holding in his arms and welcomed him with open arms.

Stop. After taking three steps, Jian Buxi screeched to a halt and took two steps back.

"I sweated so much……."

"It's okay. My leg hurts. Hurry up."

Then, it was Jian Buxi who hugged Qing while letting out a meaningless laugh.

Well. This comfort is, after all, a consideration that even the pedestal appealers dare not imitate. It was the best ride in the human world, created through careful consideration to find a way to make carrying the Great Evolutionary Heavenly Flower Sword of the Super Flower Mirror as comfortable as possible.

It really supports you without any bulges, but the parts that touch it were soft and fluffy, and also, um, a little damp… … .

Instead, I could see the lewd face of Yi-mei, drenched in sweat, up close, so I guess it was a bit of a gain.

Wet white was about five times more obscene.

"This won't work. Yi-mei, go wash up and come back. Let's go to the Kunlun School together."

"Do you want to wash together?"

Although Qing was talking about the distant Kunlun School as if it were a walk in the back mountains, Jian Buxi seemed to have no doubts about that part.

"Unfortunately, I'll see you next time. I'll see the elders of my class and take care of Gramps, so hurry."

"Ung!"

Qing, who transferred to Xue-iri, skillfully controls people with his fingers.

"But, San! What, you didn't go home?"

"You! There's nothing more disgusting than a man with a foolish heart. You're just hanging around like a leech, just to get a glimpse of Qi—"

"Hmm. As I was about to leave, the elder recommended that I sparred with her."

"Ah. Gramps? Is that because Yi-mei needs practical experience? Ah, thank you for your hard work."

Paengdaesan's eyebrows twitched.

You're saying that's a woman who needs practical experience?

In fact, Jian Buxi didn't really need any practical experience.

Because she was a person who does not let her guard down when faced with an enemy, and was born with no limits to his abilities, he does not even know the concept of mercy.

As the youngest of the Hwanhee Palace, Gyeonpohee had never received mercy, and had never had the opportunity to learn such a concept.

"But you're going to Qinghaeseong like that? You're not even in good health?"

"Hey, if you rest on the way, you'll get better. Rather than lying around complaining of pain and wasting food, you might as well just ride the carriage and lie down. You're just going to be lying down anyway, right?"

"What the heck, you're a physician, so why you let Qing do whatever she want?"

"What? You want to do it with me now? You pervert who's been loitering around saying you want to see Qing, how dare you do it to me!"

"Anyway, I don't think he'll listen to me, tsk. I'll take you there until you're fully recovered."

"Look, look, this was what the goal is, isn't it? What's the difference between you and those bitches chasing me? You're just going to wait around, loitering around until I finally come out."

"I've heard all sorts of things. Did I seem like someone with nothing better to do?"

Peng Daesan was confident.

He just happened to sightseeing because he heard that Wu Gorge were the best among the mountains and rivers of Zhongyuan, and then he met an old poet and had a chat with him. As he was about to leave, the old man was holding him back to practice martial arts.

He thought I might see my friend's face once, but I thought he would rest for the winter and then leave.

Even though I was a bum, I had no intention of staying until then to follow my friend on his trip.

However, since the man cannot leave after losing, he can only do so until he can properly defeat his friend's sister-in-law.

"Oh. Really? It'll be more reassuring if San-i goes with you. Oh, San-i, you said you were good friends, and you really are? What, what, why were you acting so strange?"

And doesn't Qingdo welcome you like this?

It's a rural area I've never been to anyway, and a remote area I'll never get to visit in my lifetime, so it might be a good idea to take a look at it at least once.

A sick friend was going on a rough road, and you tell him to figure it out yourself, and it wouldn't be the duty of a friend to just watch.

"Hello, Elder Ban! How have you been?"

"Ah, Miss. I was wondering if I should bring you this, but you came just in time. As expected, you're a miracle worker."

"Hey, the person who left it should pick it up. Why were you even delivering it when I didn't even pay for it?"

Even the old man in the iron cage had suddenly become very gentle, which was the greatest proof that Xuega Sanghoe was indeed a good place to live.

Right now, the iron room itself was decorated with cute wooden and iron statues of goddesses and Buddhas here and there, so it looks quite smooth for an iron room that was decorated with hammers and iron furnaces.

"Okay, I've taken care of the black bird."

You're back, Moonlight Sword!

By the way, was this number ten or eleven?

While Qing ponders for a moment, Ban, the son of the old man, respectfully accepts what he was holding in his hand and hands it over.

"And this, I made it after looking at the Unwoldo you gave me earlier."

"Oh. Nanga Peak."

It was a typical hexagonal bar with a thicker, longer piece of iron at the end of the bar and large, heavy thorns lined up neatly on top.

"If you push the bottom of the sword open, you can connect it by inserting the bottom. Since the moon sword was a forbidden item in the coffin, I made it this way."

"Oh. The Iron Curved Sword, you're back! Hmm, but it's not a sword. What should I call it?"

"If I had to say, I think it should be called a sword tip or a sword breaking."

Instead of the blade of the Unwoldo, he carries a vicious long sword and a long iron hammer on his back.

"I think I should just call it the Nang'a Moonlight Sword. It fits perfectly in my mouth. was that okay?"

"Isn't it the owner who decides the name of an object? Do as you wish."

He was a semi-elderly man who doesn't say anything was okay.

Qing didn't even know that, and in a fit of excitement, he swung with all his might -

"Ugh."

Ximen-Qing, three more hours until recovery was complete.

After saying hello to my grandfather.

"Please take care of yourself until you get better. Don't run wild like a calf with its tail on fire."

I came to say hello, but I got nagged in return.

Qing was being treated unfairly.

Why did I run wild because I wanted to run wild?

Why doesn't the world leave me alone?

Three people nodding their heads from left to right.

Since Jian Buxi was the only one who didn't agree and tilted her head, I guess the only one who understood me was Yi-mei.

And he stops by Xuega-nom for a moment and gives him the chest he promised to make for him.

"Okay, Xuega-nom. Here, I've made Xuega-ryeon's chest. I've written down the instructions for making the filling, so if you're going to use it, you have to change it every ten days. Otherwise, it'll harden and turn into a stone chest."

"No, did it have to be this big?"

"If you're planning on returning as a Xuega later, wouldn't a larger one be advantageous? Disguise, after all, involves erasing existing characteristics and adding new ones, so having a single breast can prevent any potential trouble."

The guy looks surprised at that.

"You're thinking so deeply? Did you eat something bad today? I knew you'd be like this, since you eat anything that catches your eye. But what did you eat that makes you so smart?"

"What? A declaration of war?"

"Just kidding. Whatever you eat goes straight to those big tits anyway. Since the medicine doesn't reach your head, there's no reason to."

"Is it possible to pick a fight with a master of the art of painting?"

"But, um, it's quite heavy. About five pounds? How dare you carry that much milk? Isn't it heavy?"

"That's one of the best things about being a master, isn't it? Yi-mei?"

"Yeah. Yeah. That's right. It doesn't hurt even if I run."

Xue-i-ri and Dang-nan-ah exchange glances as if by a miracle.

Hey, you. Do you understand what that means?

no.

Peng Daesan, with an uncomfortable and embarrassed expression, tried to look away and showed the reaction that Xuega had been expecting.

In fact, I would say that I only suffered a loss because I didn't want to see the man embarrassed at all.

So, I chose a large merchant ship heading to Sacheon and boarded it.

Qing has the Dragon King's Seal, the sacred water of the Yangtze River.

It was a world-class treasure that possessed the unprecedented and miraculous power of exemption from tolls.

Therefore, it was not appropriate to say that you get on a merchant ship or that you get on for free.

Rather, it was more accurate to say that the Qing chose the merchant ship that would take them, so when the Dragon King's fleet appeared unexpectedly, the ship owners rushed to join them, causing a commotion or something.