\chapter{Towards that remote, rural village (6)}

After passing Dogangeon, the best irrigation, reservoir, and flood control facility in Zhongyuan, which I had visited before, the first gateway to Qinghae, Muncheonhyeon, comes into view.

To be exact, the appearance had been revealed before then.

From the castle, the mountains stretch out in the distance like a folding screen, blocking the view.

Somehow, I felt like I was ignoring the distance and not getting any closer, but after passing Dogang-eon and reaching the entrance of Muncheon-hyeon, Hmm.

Qing once again reflects on whether he had underestimated the mountainous terrain of Zhongyuan.

I don't think this was a terrain that I can pass through while holding on to, but I feel sorry and embarrassed, what should I do?

But it's not Qing's fault.

In Qing's hometown, the mountains were round and low, so it was not easy for people to change the perceptions they had developed in their childhood.

"Hehe, don't worry too much. It's been less than a hundred years since the new road was paved, so it's surprisingly easy to travel. It's not time to climb the mountain yet, so just relax."

Yang Sang-gu, who joined as a guide, looks like a person who will turn into a gang of robbers no matter how you look at it.

His laughter was light and evil, his gait was not straight but crooked, and he sways greatly, making a rattling sound. His speech was polite but somehow impolite, a frivolity that only a particularly light-hearted type of neighborhood thug would show.

"Hmm. I'm not the one riding. Hey, were you okay? Should I switch with Yi-mei?"

"Yes. No."

"Wow, this reminds me of when you collapsed from overwork the other day. For a whole week, Yeonpa hadn't been carrying you around. And you, too, were holding you, as if it were natural, with no shame whatsoever. I guess extraordinary people were different."

The intention was that the two would get along well with our troublesome king.

But what does that sound like to Qing? were you just shamelessly picking on me right now?

If Yeonpa had seen this behavior, he would have thought, 'This bastard was talking like a dog!' and immediately slapped his back and stamped the fearsome space-time stamp of Jeonryunmakyeop.

There was no Yeonpa here, and Yang Sang-gu was proud of having tied it together once, so even if there was no ill will, it was just that it was the way it was born and there was nothing that can be done about it.

I thought it would be better to have Yi-mei, a skilled supporter and one of the few in the group who could barely be called a true expert, handle the transport of Qing on the mountain path.

What can I do when Gunyeong vehemently denies it and insists on taking turns listening?

Fortunately, there was a road made of compacted clay that ran through a valley where two magnificent mountains met.

The men of the Gangjok tribe, carefully cruising the stream carrying goods on rafts, glance over, wondering why they were Zhongyuan people at this time of year.

So, on the first day, we followed the path next to the stream and went up the valley, so it wasn't a particularly difficult journey.

Then, as the riverbank appears quite wide, people seem to live anywhere, and a small village appears.

It will be Muncheon-hyeon, the only Zhongyuan-style residence and county magistrate in Muncheon-hyeon.

"If you go up the river like this, you'll reach Guchaegu. Wow, it's truly amazing. I've never been able to say, "Wow, really, wow," because I'm a bit ignorant, but if you pass Hwangryong Valley, see Ochaeji, and come down, wow, that's truly a breathtaking view."

"Hwangryong Valley? Ochaeji? Even so, isn't it just a lake in a valley? Oh, I'm not saying it's nothing. There were plenty of valleys and lakes here and there, after all?"

"It's not the valley you're thinking of. Thousands of ponds flow like steps, their waters a crystal-clear turquoise. It's one of the most breathtaking sights in Zhongyuan, known as the "Scenery of the Human World."

"Oh, the mountain? Have you been there?"

"Ahem. I just happened to hear that."

I thought he just picked up snacks, but it seems he listens to other people's stories too.

Qing thinks it must be quite famous, since even San-i, who lives in Oh Ha-buk, has heard of it. But what on earth was this staircase-like pond thing?

However, the road was rough and the hidden Guchaegu area at the top was a spectacular view known only to those in the know.

It was truly a strange thing that an outsider, especially one who has lived in a foreign land for a long time, would not know about this.

Unless you ask the witty talkers who also serve as sources of information about Zhongyuan if there were any breathtaking scenery worth showing others when traveling to Sacheon, you won't be able to tell them.

"Oh. I'm looking forward to it. I'll see you on the way, right?"

"Oh, Miss? That's the road to Geomgak. If you go that way, you'll end up in Hanjung."

"Huh. What? But why did you bring it up?"

"I just told you that there was something like that, right?"

"No, where in the world would you bring something up and then say you won't go? was that how it is?"

Qing was speechless.

When you go on a tour, isn't it like the guide says, "Oh, there's a really cool tourist attraction over there called so-and-so, but we're not going to go. I saw it and it was really cool, but you guys can't see it?"

If you're not going to go, you shouldn't have said anything at all.

Or, you could have started by saying, "There were other tourist attractions over there, and although it's not on our itinerary, I'll explain them to you, so you can go there later."

Can I trust this guide?

After staying a night in Muncheonhyeon, we started climbing in earnest along the valley hills to the east.

Even though I keep climbing and climbing and climbing the steep mountain path, always heading higher and higher, the only things I see on both sides were steep mountains with even higher peaks.

When I asked Yang Sang-gu, he said that the basic height was 1,500 zhang, and that there were several peaks that reach 2,000 zhang. What was this? 2,000 zhang? How can a mountain stretch 2,000 zhang?

Surely the white sparkling top of the mountain was a sign of eternal snow, a sign of the bitter cold that never melts.

As a result, it can be said that the consideration of freedom was of great help.

Isn't a guide just like a guide?

There was no reason for a master of light martial arts to try to make a little money by merely providing guidance.

Moreover, since no one in the group was as skilled as Yang Sang-gu, it would be a great help to be guided along a path suited to a warrior, at a pace that suited the warrior.

If I had to pick one person who would hold the group back, it would be Xue-i-ri, not Ga.

I can't run fast because I have to be careful not to shake while holding her in my arms.

There was no such thing as a separate lump of luggage.

As you pass Ihyeon and climb the mountain path of Maigang River, turning north, the wide open Nakigae Grassland suddenly appears.

It's not just a meadow, it's a prairie.

In Zhongyuan, it was impossible to even attempt to attach the character "大" to anything of a certain size.

But how wide was the prairie that was proudly called the prairie?

The unique unit of measurement of the Korean people, Yeouido, was equivalent to 11,100 Yeouidos, and if we calculate it in terms of Seoul, which was a larger unit, it was roughly 50 Seouls, the equivalent of 50 Seouls, and it was an area equivalent to 30% of the land of the country from which the Qing Dynasty originated.

"If you follow the river all the way up and around the mountain that blocks it, you'll reach Qinghae Fortress. Just follow the water, and you'll be able to do it without me, right? Even a child who knows nothing about martial arts can do it, so there's no need to ask."

It's a sound that was somehow incredibly rough.

The person himself was polite, but his speech was a bit sloppy.

"Well then, I will now take my leave. I would have loved to escort you all the way to Kunlun, but I have someone more precious to offer."

"Thank you for your hard work. Thanks to you, I was able to come comfortably."

"I think you must have been comfortable anyway, hehe, you were being too kind."

There was no part of the way he speaks that was not annoying, even until the very end.

The remaining path was easy enough for even a child to find, so those who were less precious can just go, even though they won't be walking in my arms anyway.

But from the saint to here, it's been ten and a half days already, and the person I've seen Yang Sang-gu-ja during that time has just had this kind of speech pattern.

Should I say that I don't mean anything bad but I'm being rude?

Qing, who had already become accustomed to that tone of speech, catches a glimpse of Yang Sang-gu and finally sets foot on Qinghae land (still in Sacheon) (though he has not set foot on the land yet).

It only took ten and a half days to cross six hundred li, so you could say that I am not worthy of being a martial artist.

The ground on which they stand was a thousand zhang high, so climbing the mountain for ten days straight, without even one person walking on their own, was quite an incredible speed.

The height of Mount Taishan was 500 zhang. If Mount Taishan were to be piled on top of Mount Taishan, it would be this high now.

The tall and rugged volcano was only seven hundred meters high, which shows how high the land of Qinghae rises.

So, the southern Hongwon grassland of the Nakigae steppe.

The buildings in the village that appear occasionally were single-story or two-story, square brick walls.

The relatively neat facilities were painted in white or yellow gold, and the upper part has a unique decoration of neatly lined white circles on a black-brown background.

Still, the first thing that catches the eye was the building, which was called a carpenter's building.

And the specialty of the Nak-i-gae steppe was the yak.

Boiled pork with mou meat, stir-fried mou meat with fish sauce, and sannae (yogurt) made with mou milk

Then don't go back to this taste.

however?

To begin with, since it was a prairie with not many guests, there were few specialized inns and restaurants, so wherever you went, you could find Mou boiled pork, Mou grilled meat, and Mou soup.

This was the problem of rural villages without cities.

There was no separate host or restaurant, so whenever guests came, the whole village would host a small festival to entertain them.

And since she was a pretty guest, isn't the amount of silver she offers just a small amount?

I tried to make it as grand as possible, but I couldn't even say I was tired of it because I was treated to meat instead of the usual vegetables.

Of course, I don't get tired of blue.

Because meat was always right.

But my friends were still wondering, what was this? were we supposed to hold a ritual with meat now?

If you stop by around dinner time, after dinner, you'll always see a jug of alcohol on the floor and all the neighbors gather around to drink it through straws.

Instead of pouring it into a glass, each person puts their own straw in, and after the guests take a sip in order of rank, the men take a sip first, then the women take a sip, and so on. After each turn, they add water and fill the bowl again.

It was a unique drinking culture where alcohol gradually turns into water and then disappears into a cycle that ends when it was no longer in effect.

As the alcohol level gets weaker, the intoxication doesn't get deeper, right? That must be a shame for heavy drinkers.

Perhaps because there was still no limit on drinking by minors in Zhongyuan laws, even the little kids come out and their eyes sparkle.

It's cute to see the future dream trees trying to suck as long as possible.

We go up the winding tributaries of the Baekha River, stopping at small villages like this, and sometimes tent villages where herds of sheep have come out.

A large waterway appears along the way, and it was the Yellow River, the source of the Baihe River, one of the four major rivers of Zhongyuan.

It's almost winter, so the grass was yellow and the ground was frozen, but the orderlyal scenery unique to the highlands still warms the heart.

As the Yellow River curved and turned sharply to the east, a fairly tall mountain stretched out to the north like a castle wall, blocking the road.

At the end of the Nakigae steppe, on the border with Qinghai Province, a small town called Nima, also called Nimajin, located on the riverbank, comes into view.

It was a city that serves as a logistics hub for Gansu Province, and was located on the banks of the Yellow River that flows into Sichuan, so it was bound to be quite prosperous.

In a city like this, there were high-class inns, and what do high-class inns have?

Right in the bathroom! Bath! Hot water!

So, although it was still a little early, I got a room, filled my stomach with some Chinese food for the first time in a while, and asked Jeomsoi for directions.

"Sir, was this your first time on the Qinghae Road?"

"Yes. Does that make sense?"

"Oh my, I wonder. I was wondering if it was possible since you said it was over the Langipnap Clearing."

"Uh, was there a problem?"

"The river tribes were easily traversed, so if you look carefully, you'll find the path. But there were no houses along the way, so you should be well prepared, right?"

There was a mountain path that the Gangjok use, but there were no houses along the way until they reach Hanam County in the northern part of Qinghae Province.

That means I have to stay overnight.

"Oh. Then, could you please help me prepare something?"

"Well, but the times were chaotic right now, so it's probably best not to go. There's a group of bandits taking up residence around Hanam County."

"A group of thieves?"

"These vicious, ruthless men demand not only money but also people as tolls to take them away. They seem like they're ready to kill."

Hanam County was the only city entering Qinghai Province from the south, and was also a gateway to southern Qinghai from Sichuan and Gansu.

A group of thieves were in that place.

Thanks to this, logistics have decreased and prices have risen, so the public sentiment in the area has become extremely unstable these days.

"I'd be happy to prepare it for you, and it would be a good idea to attach a letter of explanation, but how could I do that when the route was so obviously dangerous? So, it would be best for you to simply go down to Gansu. Since you're heading to Xinying, why not just go up from Nanzhou?"