\chapter{Towards that remote, rural village (8)}

When Qing opened her eyes, she was in a pitch-black tent. It was quite chilly, and her white breath spread.

The coldest time was usually just before sunrise.

If it's chilly to you, it means it's not normal weather.

Because it was a thin cotton thread that survived the winter, not only the strong wind but also people's gazes could pass through it.

Of course, the weather in Hubei Province was warm, so there was not a single day in the year when the water freezes, so it was hard because the temperature felt cold due to the sharp wind, but the temperature itself was not that low.

However, in Qinghae-seong, frost falls at night except for one season, summer, in June, July, and August.

So, Qing was tossing and turning in her sleeping bag, her eyes blinking with a particularly cold face.

Wow, it's still cold even though the wind was blocked.

It looks like it's in a freezer.

Then, suddenly, I remembered Mt. Paengdae, who was unusually cold for a man.

Qing carefully gets up from her seat and examines the sleeping face with her superhuman vision that pierces through the twilight.

It's dark so I can't tell the color, but her lips were particularly faded, so you can tell at a glance that they're pale.

Are Yi-mei and Gunyeong okay? Hmm. I guess they're okay.

The two of them were very cool, one was Dororong, and there was a faint smile on his sleeping face, which was comfortable, but doesn't Gunyeong's expression seem richer when he's sleeping?

Anyway, after being so stubborn yesterday, it looks like he's going to catch a cold, so I can't just leave him alone anymore.

So what? There's nothing I can do.

Qing'er rose from her seat like a ghost, without a sound or a trace. If she couldn't even do this, she wouldn't be worthy of being a prospective fighter.

The body of the cold-cold Peng Daesan must be warmed up.

how?

Qing knows how.

Well, you can just light a fire.

Take a handful of hay and spread it on the floor, then set two flat pieces of hay in a triangle and light them with a fire starter.

The fire quickly started up with a comfortable crackling sound, and after adding another layer of dry food, it quickly became smoky. As expected, when it comes to heating, well, what should I say, direct fire grilling was the best.

Direct grilling was definitely unbeatable.

It's also delicious when grilled.

Is it just meat? Have you ever seen a Chinese chef shaking a large pot, swirling its contents high and high? This isn't a show of skill.

This was also a direct fire grill, as it was a process of adding a smoky flavor by directly contacting the food with the fire.

Grilling isn't just the best for cooking.

When it comes to punishing the wicked, there's no method more effective than direct grilling. Therefore, burning at the stake has been practiced in every civilization around the world, and it's no wonder that direct grilling was the most preferred method among religious believers, regardless of their faith.

But now direct grilling was also used for heating?

How much stronger do you want to become?

Hmm. Looking at the fire like this makes me want to eat some fried chicken. With some sticky rice in my stomach. Somehow, the wings were almost like charcoal.

These friends were sleeping well because they were tired.

It's only natural that even though he's martial artists, he doesn't wake up to all the noise in the world because he's a light sleeper. If that were the case, then all martial artists people would have dull complexions from insomnia.

A shadow of a person rising from Qing space was captured.

Inyoung sits quietly next to Qing.

Qing leans forward naturally.

Suddenly, he lifted his arm and wrapped it around the back of her neck, and his long, slender, white fingers slyly inserted themselves into her chest.

The inside of the tent was red and swaying with fire.

The crackling sound of flames, the occasional sparks flying out.

And the soft, fluffy, most pleasant lump of flesh in the world, overflowing in the palm of your hand and oozing out between your fingers.

As I look at the fire and touch my pale chest, I wonder if there was such a luxury in the world.

Why was it that in Taoism, if you touch your chest in the morning, it was okay to die in the evening? (No)

Qing was very good at messing with his bad hands.

When I slightly clench my fist, the feeling of my fingers overflowing with sweat and getting buried in a blanket was so rare. Take it out, take it out.

Yi-mei smiled and whispered to him.

"My sister-in-law really likes breasts. Since I've lit a fire, should I boil some porridge?"

"No. If it smells like porridge, everyone will wake up. I'll wait a bit. It's too cold outside anyway, so I don't feel like going out early."

'Yeah. It was a little cold.'

"Are you cold? Aren't my hands cold?"

'Ugh, it's okay.'

Leaning against each other like that, they whispered for a long time.

The radish kimchi here was really delicious. Meat, meat was always delicious. Oh, what was that? The boiled pork, and the japswae-tang…

After a long conversation about food, the conversation turns to the unique customs of Qinghae.

But this was cow dung, but strangely, it doesn't smell and has strong heat. Isn't that a cow that's been herded? Oh, did you see the five-colored cloth tied to the rope? Doesn't that look exotic? What was it called in the first place? A plateau? A rocky mountain? I guess I like that kind of thing. It feels good.

Mostly, Qing was talking and Jian Buxi just says, "Yeah, yeah," and accepts it.

But, like a child, her emotions were transparent, so she smiled brightly.

So, from dawn to morning, it's quite a long time.

'It's about time to wake up. Should I make some porridge?'

'Okay. I'll do it. Sister-in-law, take a rest.'

It's not like it's anything grand to tell someone to sleep out overnight.

Just throw a few dried seeds into a pot, pour in the milk, and put it on the fire.

The savory scent of milk slowly warming rises, and since the dry ingredients themselves were seasoned, there was nothing more to add.

It was said that one of the most gentle ways to wake people up was through a delicious smell.

As the tent was filled with the rich, sweet scent of milk, the remaining two naturally opened their eyes and sat up.

The taste of milk porridge was far inferior to its smell.

The so-called smell scam.

How delicious would this kind of travel food be in the first place? It's not like we can bring a host with us, and even if we did, how would we travel with all the ingredients, cooking utensils, and cooking utensils?

Of course, it's possible if you travel by carriage, but it's nonsense in the first place when you're traveling across the mountain ranges of a deserted plateau.

"San, how were you feeling?"

"It's fine. It's not that cold."

Well, it must be warm since there's a fire.

Go out there a little while and see what happens.

Still, the body temperature that dropped overnight rose a bit with the direct grill heating, and with the addition of some boiled porridge, the temperature rose sufficiently.

Oh my, Gunyeong was even sweating.

"Sister-in-law, close your eyes."

Jian Buxi slightly wets Su-gyeon (handkerchief) and wipes Qing's face.

It was a very meticulous touch, being very careful not to use it anywhere.

"Come here, come here."

"no."

"No, bullshit, don't you want to come quickly?"

Then Qing calls Xue-i and rubs her face.

This was a rough hand movement that aims to remove even the dead skin cells.

Gunyeong likes to take a bath, but secretly hates washing.

Even though you eat porridge all the time and sweat like it's raining, don't you feel uncomfortable?

Xue-i-ri may feel wronged.

In the North Sea, if you touch the water, you will immediately freeze.

And then, other than the sleeping bag, we folded the floor, put away the dishes, and finally, the long-awaited tent setup.

As soon as I open the tent, a strong wind blows away the warmth.

The warmth of the past vanished in an instant as if it were a mirage, and on a harsh December morning in the Bin Mountains of Qinghai Province, a cold wave of freezing temperatures reached minus fifteen degrees Celsius in Qing's homeland.

"Hmm."

Pengdaesan was closing his thick fur coat without saying a word.

Qing'er's laughter was so good. It's because she lacks the realm. After laughing at her and saying that she's not cold at all when she's at Hwa-gyeong, she sets off again.

As I carefully examined the white frost-covered ground and followed the untrodden path, a cliff that seemed to extend more than twenty feet to the side came into view.

Looking at the direction, it was the natural barrier that I would have encountered if I had gone straight from the fork in the road yesterday.

"Didn't I say it wasn't meant to be that way? If someone had said so, we could've been in big trouble."

Pang Dae-san was muttering as if he wanted revenge for what happened just now, but his voice was trembling from the cold and it didn't do any good.

As you continue up the ridge, you climb up for about half an hour, but the path to the top goes down the ridge and then down.

"Wow. What was this?"

At the end of Animagyeongsan Mountain, in the distance, the huge mountain slope of LangilapQingbong Peak rises vertically, almost blocking out the sky.

Even though I am standing at the very top of the ridge, the sparkling snow far above was dazzling.

Fortunately, it didn't block the road.

The gentle ridge on the left was faintly marked by a path.

"Well, it's cold and we don't have many supplies, so let's go at a brisk pace. Haven't you been feeling a bit restless up until now?"

The gentle downhill slope was solid and the view was clear. Qing finally decided to pick up some speed on the martial artists downhill.

As Jeomsoi said, it was not that difficult since even people without martial arts skills can cross it.

When I was climbing a mountain, I thought, "If it's not too steep, then I'll break my legs."

After bypassing the high snow-capped mountains, a flat plain stretches out along the frozen river.

It was a small river, so it froze over in the winter, but there were clear traces of farming on both sides.

As expected, a small brick house can be seen in the distance.

There was no sign of life and the dust was thick. It appears to be a seasonal residence where people live during the summer and leave after the harvest.

It was now Yushicho, a little past five o'clock in Qing's hometown time, but they had also come across a brick building. They decided to stay here for the night.

Next to the fireplace, a pile of dried manure was piled up to waist height, and the writing on the wall caught the eye.

-You may use it, but please do not take it with you, as other guests may visit during the winter. We would be especially grateful if you could pay for your use.

It seems that during the off-season, they give it away to potential travelers.

Somehow the door wasn't locked.

I keep feeling this way: The people in this town were incredibly kind. The same goes for the people in the tent village I stopped by on my way here.

There were quite a few coins in the earthenware bowl, so it seems that the people using it were not very hard-hearted.

Pick up two silver coins and bury them deep inside the coins.

No matter how kind a person is, a hermit might become greedy, so don't let him see you.

Since we paid a lot of money, we should light a fire to protect the already fragile mountain from the cold.

I was able to rest comfortably for a day in a warm and cozy brick house, thanks to an unknown farmer who chatted away.

So, it's the third day of the overnight stay.

Hmm. I told you not to take it.

That's what I'm asking you not to just bring it and fill up your warehouse, and just in case, not to empty it at all.

I'm not saying you shouldn't pay a price and take a little bit, right?

It was not a forced judgment, but a judgment that could be made universally when viewed in context.

Still, I was a little worried, so I buried two more silver coins between the coins, and packed a generous amount of dried manure and went out into the cold morning air.

As Jeomsoi said, once you get over Langilap Mountain, you just have to look at the river.

If you follow the small river flowing west, you will see a valley hill to the north that looks easy to climb, so go over it.

Then, in the vast wilderness, you will see a strange river. If you follow it, you will reach Hanam County.

Of course, I'm not sure since I heard it from the merchants of the Gangjok tribe.

Or not.

Although it lost a lot of credibility in the ending, fortunately, it seems that Jeomsoi heard the right story.

Since we had gathered a lot of moo dung, we would wake up every now and then during the night and light a fire to keep the tent warm.

On the fourth day, I found the road, even though it wasn't maintained, so I thought I'd get there soon.

As I was following the road, it started to get dark and I was looking for a place to pitch my tent when I suddenly saw a puff of smoke rising from the other side.

Well-dried moose dung, unlike firewood, produces almost no smoke.

Still, a stream of smoke rose, which means there was a chimney that was collecting and releasing the smoke.

Qing's face brightened.

It bloomed quite a lot, if I had to put it into words, it bloomed brightly.

"Oh. I guess there's a cabin over there too. Or maybe a house. Come here, what does this mean?"

"Sleep indoors."

"Tsk tsk. Come here. You haven't slept out yet. That's it."

"as soon as."

"It means there was proper food other than that boring porridge!"

"No. The dried porridge was delicious."

He was sweating profusely, gulping down the boiling, simmering food that was somehow so delicious that his tongue was almost cooked. Did that suit his taste?

"Hmm. There'll be passengers, will that be alright? I've always said I'm not happy with people I meet on the road."

"Hey, maybe it's because there aren't many people? They're all nice people. And the hermit can make anyone kind, right?"

"Hmm."

Pang Dae-san was a man who pretended to be cautious, but had a subtly bright expression.

No matter how warm a makeshift tent is, it can't compare to a house surrounded by walls.

It's really cold, it seems quite cold.

But the most excited person was Qing.

Rice! Rice other than porridge!

A proper soup, not just thick barley broth!

Not dried meat, but juicy meat!

Qing was so excited that he runs off to study the technique of flying quickly.

Beyond the winding riverbanks and hills, ahead, lies hidden rice. Therefore, gluttony was effective.

So, Qing one was over the hill!

Unfortunately, it's not a house, but a campfire.

When Qing's eyes met with the man who had been grilling meat for a long time, Qing's face immediately darkened.

Unfortunately, they were grilling people, not juicy meat.