\chapter{Towards that remote, rural village (10)}

Xue-i-ri and Paeng-dae-san's expressions were unpleasant.

You might wonder who was in charge of suppressing the bandits and who was in charge of assisting them, but in reality, he was saying that he will be the main character in suppressing them.

Aren't the stories that Heavenly Blossom Sword and his friends were fighting off bandits and were helped by the Strange Monk, and a story that Heavenly Blossom Sword and his friends were helping the Strange Monk cut down bandits, completely different?

Of course, Jian Buxi has no idea about these high-level justifications, honors, or a kind of unintentional politics, and has no intention of knowing about them.

So, with the help of the Qing, they level the ground by digging it up and prepare to pitch a tent at the bottom of the steep hill.

Peng Daesan quietly asked Qing about this.

Then a strange answer came back.

"Huh? What does it matter who helps who? After all, if we just take down those harmful bandits, isn't it better for the world? What's the point of blowing up their names?"

And then a mischievous, sly smile.

"And doesn't this body already have a reputation? Of course, I don't know about San'er, who's just a super-handsome brat."

"That damned rant, ha. Do you think that's all there was to it? The Strange Monk is entangled with many favors and grudges in Jianghu. There's nothing good getting entangled with him."

"Or you can just say no. If they're going to attack us like that, saying, 'You beat up some thieves together, so now you're my enemy too!' Aren't they no different from Demonic Adepts in the first place?"

"It's not that simple. You don't know how narrow-minded and absurd human hatred can be."

How hurtful it must have been for the enemies of Amukhaprap to see a monstrous monk gain fame through such a righteous act.

If you say that you helped him, it was only natural that their heart would inevitably turn to hatred.

"San'er has had a hard time."

"I don't know why you came to that conclusion."

"There were those kinds of women. They gave their heart to someone they like, and then you don't reciprocate. They said 'How could you do this to me?' and gritted their teeth. San'er doesn't need to worry about those petty women. San'er says that's just how other people feel, so why bother considering the feelings of someone who doesn't really matter to you? They're complete strangers, right?"

Peng Daesan had a look of surprise.

She usually acted like an idiot, but once in a while she saw through people and said things like a proper Taoist.

"Ah. But why the favors and grudges? Did Yumomahop do a lot of bad things?"

Peng Daesan glanced at Amukhaprap, who was sitting cross-legged in front of the campfire.

"He's a cruel man with a volatile personality, making him unpredictable. If he doesn't like what people saying, he'll kill anyone, even innocent people, without hesitation, and then try to nip the buds."

The statement of 'nip the buds' meant trying to get rid of those who have the potential for revenge.

This includes family, friends, and acquaintances.

"Hmm."

"That's why I don't want to be with the monk. I don't know when he'll flip and attack."

"Hmm. Is that so? I'll go ask."

"What?"

"Why don't you pitch a tent?"

Qing put the Moonlight Sword she was using to dig the ground back into its scabbard and heads towards Amukhaprap.

"Excuse me, monk?"

"How can you interfere with Zen meditation?"

"There's a scary rumor going around. Did you really go around killing people just because you don't like them?"

I didn't ask without any basis, so it's not like I'm not confident I can fight and lose.

Above all, don't you get along well with that fat guy Povidone?

If you were going to be offended, you should have been offended a long time ago. Looking at the way you've been sticking with me all along, it seems like you're not the type of person to kill people just because you feel like it.

"Hmph. That's absurd. All those I killed died natural deaths. Those vicious and base Zhongyuan bastards who exploited the most precious U-Tsang bloodline on earth. But if I attack, I myself, not yet a Buddha, am a judge without mercy. Like the unstoppable wrath of Magagara, the Great Black Heavenly Avalokitesvara. Even if I hide in Zhongyuan, I cannot escape my own judgment."

Magagara, the Great Black Heaven, and the Wrath of Avalokitesvara were all gods of India, and of all the gods, they were the god with the most familiar sound to the Korean people: Shiva. Shiva.

"You wicked Zhongyuan descendants, especially those of Han Chinese blood like yours, are the world's most filthy, impure, and deceitful fate. You are not barbarians, but Han Chinese, the vile people who suck our backbones. I have judged you thus. Are you dissatisfied? But you have been given incredible fortune, to escape the vile Han bloodline and be reborn as a barbarian."

"So what? And what if you lump all Han Chinese together and call them bad guys?"

"Not all Han Chinese exploit the barbarians. However, all exploiters in Zhongyuan were Han Chinese."

"Hmm."

I knew that the people of Zhongyuan were treating barbarians, so I knew that I had seen and heard about it step by step.

Basically, they were easy to exploit, and the government officials unconditionally side with the Han Chinese. If even the the Han commoners were exploited by the merchants of Zhongyuan, how much worse would it be for the barbarians?

It was said that he went around looking for such scammers and killing them.

Qing saw the Evil Karma of Amukhaprap.

Peng Daesan said that he killed them all to get rid of the trouble, and Amukhaprap said that he only killed those who attacked him.

Qing thought that what San said was probably right, because she obviously felt that way too.

What if I made grudges and it causes harm to not only me but also our Divine Maiden Sect chicks, friends, and Xuega Sanghoe?

Perhaps, to the Strange Monk, those people were not Xizhang people, Hmm.

Was it just an unlucky Heavenly Blossom Sword?

I also wonder if things would have turned out like this if it weren't for Master, our Divine Maiden Sect, and our Jeongpa family.

"But what were you doing? Are those Zhongyuan guys practicing pitching tents?"

"What were you doing? Why were you pitching a tent? Shouldn't you be sleeping?"

The wide, sunken eyes of the Amukhaprap looked at Qing with questions.

"Fall asleep?"

"Come to think of it, your luggage was light. Don't you have a sleeping bag? How did you get here without one?"

"The U-Tsang is the U-Tsang's home. The sky was the roof, the earth was the foundation. Unlike the weak people of Zhongyuan."

"No, let's say there's a roof and a foundation, but there were no walls. So you've just been sleeping on the floor all this time?"

"You fool! Then you'll die! I'm not the general, that North Sea barbarian!"

\textit{What was it? Is it the hatred of barbarians against barbarians?}

"No, then how did you get here? Is there some kind of overnight stay method?"

"I'm a master. A master can survive with just five days of sleeplessness."

That means you didn't sleep.

Why were your eyes bloodshot? I thought it was some kind of side effect of the Bloody Palms martial art, but it's just because you didn't sleep.

It seems that the reason I had my eyes closed until just now was not because I was meditating, but because I was dozing off in front of a warm fire.

"Then, I'll sleep inside the wall tonight. was that okay?"

"You were actually a crazy woman? Even if you were a true Buddhist and holy master, why did you believe in him and sleep with him?"

"Why? You said something suspicious along the way?"

"That's crazy talk. I said I'm a prospective Buddha. There was no one in the world I can trust more than myself."

Qing asks back with a cheeky, mischievous smile.

"Then isn't it okay?"

"For that reason, San. That's good. It's cold, so sleeping together will keep you warm."

"I don't like it." "I don't like it!"

Pengdaesan and Goeseung spoke at the same time.

And then they looked at each other.

"I hate it." "I hate myself even more!"

Hmm. I thought it was a pretty good idea.

Since Pyeongdae Mountain was already shivering at night, wouldn't it be okay if two people shared a sleeping bag to keep warm?

Even with the skin attached to the bones, the two of them were stuck together and it doesn't seem like the sleeping bag will be too small.

"Then there's nothing we can do. Yi-mei and I will share a sleeping bag-"

"Use this."

"Oh! How can a North Sea barbarian know etiquette! It's a constant source of surprise!"

Before Qing could even finish speaking, Xue-i-ri handed my sleeping bag over to Amuk-hap-rap.

"Miss Ximen. There were no more sleeping bags here."

Qing was impressed by him.

What? You just called yourself by your own name?

What kind of confidence was that?

Do you commit such a crime just because your face was somewhat or very even?

There's no way this can be forgiven.

Since a beautiful woman can do anything, shouldn't she be entitled to be forgiven for things like third-person pronouns and pigtails?

"Hmm. As expected of a North Sea barbarian. It's okay to sleep on the cold floor."

"no."

"Ah. Sorry. No matter how close we are, isn't that a bit too much for the North Sea barbarians?"

"That's not it. And those North Sea bastards were truly uncivilized barbarians."

"I didn't say anything like that."

The subtle valley between Xue-i-ri's eyebrows.

But it was the easiest valley in the world.

"Come here."

Because it was a valley that disappears as if it never existed.

"Oh. That's too bad."

"Sister, I'm sorry."

"Ugh. It's good that you two get along well."

Jian Buxi just smiles happily.

This was the dignity of a family, on a different level from the friends who were after Qing's bed.

Thanks to the strange group, the average age has increased by about five years, but in fact, middle age in Zhongyuan was the most exciting time.

So today I walk through the wilderness again… … .

"It's truly horrible. I'd give it to an animal."

Now he was a barbarian who complains about food and whether he can live.

Of course, since there was nothing else to eat, he grumbled but emptied his plate cleanly.

So we walked and walked, had lunch and walked, and it was getting dark quickly, so we had dinner and were about to pitch the tent again.

"You weaklings of Zhongyuan, don't pitch your tents. Keep going and you'll reach us in the morning."

"It's so dark out here?"

"Foolish you are. If so, it's a sign of falling snow. Rather, it goes firmly like a bull's horn."

It was said that since it will snow, we will walk all night and arrive in Hanam County in the morning.

But what if night falls under a cloudy sky?

In this astronomy, even a Qing with superhuman eyesight cannot see anything.

On pitch-black nights without even moonlight, even Qing night vision was unavoidable.

So, if you go at night to avoid the snow and get lost, you might end up getting hit by some snow tomorrow and end up wandering around the city for a few more days before you arrive in the evening.

"You Zhongyuan folk were so fortunate! Here, a great starlight, your guide, pierces the darkness. The land of the West was like your own home, clearly visible even with closed eyes."

"You were lost, weren't you?"

The fact that Amukhaprap was trying to grill food on an abandoned road was because he was lost and wandering around, and was hungry and was about to abandon humanity.

Eating the dead because you're so hungry was not considered a crime even in the Qing homeland, but it's not something a lost soul should say anyway.

Then, Amukhaprap suddenly burst out.

"I didn't know it then! I know it now!"

"Hmm. What do you think, guys? The old man said he was confident. Honestly, I'd rather go. I don't even want to look at dried porridge anymore."

Paengdaesan quietly looks at the bonfire.

In the place where Qing had sat, there was a bowl of porridge that had been completely emptied.

What the heck? You ate two bowls, and then you threw them away because you didn't want to look at them?

But even Mount Paengdae has already taken the crane, so now, if you serve any dish other than dried porridge, it would be a delicacy without a difference.

"Hmm. One night should be fine."

Jian Buxi and Xue-i-ri were of the opinion that they should just do whatever they want as long as it doesn't put Qing in danger.

So, Qing rolls up some dried grass and attaches it to the iron blade of Nanga Peak to make a huge torch.

It's closer to a beacon than a torch.

A huge fire blazed across the wilderness, and a chill touched my cheek along the way.

"Oh. It's snowing."

Of course, Qinghai was a dry place, so even if it snows, it was only a little bit, falling one or two at a time, making it feel like a sleet.

Still, the huge flames of three torches and mou gunpowders were shining in all directions.

The snowflakes fluttering softly into the darkness beyond my sight were surprisingly charming.

Originally, snow was just a cursed byproduct of the heavens that I would have to clear away, but otherwise, snow was just a beautiful sight.

The fire burns and the light gradually dwindles.

The firewood I had collected by paying for it at the martial artists store was still overflowing, so once the fire was extinguished, a new one was lit, and the mobile beacon fire was continuously revived, crossing the Qinghae Sea.

However, the Nang-A-Bong, who took on the role of Nang-A in the combined weapon Nang-A-Moonlight Sword, can be very resentful.

What on earth does this crazy bitch know about weapons?! Even if it's a blunt weapon, not a sharp one! How could she light it on fire and burn it red? How could she possibly be ok with something like that?!

If Nanga Peak had consciousness and had eyes and a mouth, it would have cried tears of blood and cursed its master.

What can I do about the subject of weapons?

It's just the strange fate of a weapon that met a fierce master.

After five signal fires had died down and the sixth, a large fire rose high again, Zhongyuan-style walls finally came into view in the distance.

It was Hanam, the southern gateway to Qinghai Province.