\chapter{On the Plains and Hills, One Food and Two Hammers (2)}

Qing blankly looked up.

The words, ‘Jin Family Estate', which had once been written in gold, were now tilted and stained with blood.

The signboard was the face of a martial clan.

Since the face was already crooked, it was eerily quiet, with no sign of guards or even any sign of life, let alone the tightly closed main gate.

What's going on? Did I come to the wrong place?

Is this Jin Family Estate not the right one?

Well, there's probably more than one Jin Clan in Zhongyuan.

Although Qing didn't know, the surnames of Zhongyuan were the same if they used the same Chinese characters. So, there was only one Jin Clan.

A long time ago, there was even a guy with big ears who sold mats and claimed to be a descendant of the imperial family.

However, they didn't recognize people based on their ancestral hometowns, but rather on their current real estate locations. As such, it didn't really matter if they had the same surname.

It might make people feel a bit more familiar with each other than complete strangers.

"Aigo, child. You'll get into big trouble if you stay there."

Someone spoke to her, and when she turned around, she saw an old woman with a serious expression.

"Huh? Why?"

"It's been cursed, you see. Cursed. If you get involved, you'll suffer a disaster too. That family has already devoured hundreds of lives."

"Cursed? What did they do wrong to be cursed?"

For the Korean people, who were of Qing's blood, a curse was somehow associated with retribution for sins committed.

There are few ethnic groups who attribute the cause of misfortune to their own faults, so it could be said that they were a truly moral people in this respect.

However, in this primitive, ancient, and uncivilized Zhongyuan, a curse was simply a disaster that happened if one was unlucky.

"What do you mean, cause? There are tons of bastards who perform death rituals to bring down a prosperous family. If you get caught by a really powerful one, this is what happens. Tsk tsk."

"Hmm. What happened?"

"A slaughter. A slaughter has been firmly set. If you're associated with this family, you'll be cursed and face a funeral."

The old woman's eyes, as she spoke, held a strange glint, almost a kind of madness.

Just as Qing swallowed her saliva…

"Oh my, Mother! I'm sorry! I'm so sorry!"

"What? Who are you? I need to find my son."

"Mother! It's me, Dong! Dong!"

"Ah. The second one. Dong-ah, go find your older brother. It's already past dawn, Dongil must be hungry."

It was long past dawn, and the sun was already high in the sky.

At that, the man repeatedly bowed his head.

"Martial Artist, my mother has been mentally unwell since losing her eldest son. Please do not be angry and forgive her with your generous heart."

"Ah, it's okay. Shouldn't you hurry and follow your mother?"

"Thank you! Mother! Aigo, where are you going?"

"I was told to use the character ‘목' when naming my child, but he ended up working with wood, and now he's… Hmm? What? Hey, Dong-ah, have you seen your brother?"

She was a bit unwell, huh.

Qing looked back at the tilted signboard of the Jin Family Estate.

The old woman's eerie gaze, the curse, the slaughter. A shiver ran down her spine.

Just then, clouds rolled in, covering the sun and casting a dark shadow over the area…

Creak.

The door made a twisting sound and slowly opened.

"Whoa."

Qing involuntarily took a step back.

Cutting people was one thing, but she couldn't cut ghosts.

In a world where people could receive the mystical energy of the universe to fly around and shatter cliffs, there was no reason why curses or ghosts shouldn't exist.

As Qing clutched the hilt of her sword, a face appeared through the doorway. It was a neat, traditionally beautiful face.

No way. Is that ghost pretty or what?

"Who……? A veil?"

"Miss Jin! It's me. Ximen Qing."

Qing said, lifting her veil.

Jin Seol's eyes widened.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After greeting the weary-looking Clan Lord Jin, Qing was served a late lunch.

She had skipped lunch because she had hurried to get here.

The deadline for the Martial Alliance's dispatch was until winter.

And now it was early February.

So there were less than two months left.

The reason why it was said to be a little less than two months even though it was early February was because this year had a leap month, meaning there were two Februarys.

In the lunar calendar, an extra month had to be added roughly every two and a half years to keep the seasons from shifting.

So, because she had hurried to arrive, she reached the land of Gwangju just past lunchtime.

"What on earth happened?"

"While we were away at the martial tournament, the Blood Cult attacked our main estate. Because the Blood Cult was involved, the bodies were left unattended. Ah… I didn't realize the stench of decay would linger so much."

‘Chumul' referred to the fluid that came out of a rotting human corpse.

It was the number one liquid that carpenters hated the most.

Once it soaked in, not only the smell but also the dark stains of death never came out.

Therefore, when a person died in a room and the body was left unattended, the room had to be completely dismantled and rebuilt.

"The Blood Cult? Then, the Martial Alliance…"

"They said they would send support, but our family decided to hold off for now."

"Huh? Why?"

"It's not like we're in a position to receive guests, and we decided to request help once we've tidied up the estate a bit and are ready to welcome guests, but……"

The problem was, they couldn't tidy up the estate.

As soon as construction started, the workers kept dying, and it was said that the Jin Family Estate was under the wicked curse of the Blood Cult.

So, forget about construction workers, they couldn't even hire new servants.

The only people left were those who had accompanied them to the martial tournament to assist them.

"A curse."

At that, Jin Seol shook her head.

Anger rose on her pretty face, one of the Five Flowers of Zhongyuan.

"Where in the world would there be such a thing as a curse? It's the handiwork of those unorthodox bastards, but they don't even know that. Once this situation blows over, it'll seem like there really is a curse."

At first, they thought it really was some kind of curse.

So they called in renowned Daoist Monks, Buddhist Monks, and even shamans to perform exorcisms.

But the tragedies of the workers did not stop.

Then, they realized too late, only after seeing how the unorthodox bastards were accepting new disciples and spreading elixirs like crazy, even though they were just cheap ones.

They realized that the workers weren't dying because of a curse, but because of those bastards.

"Those bastards. They should be wiped out, down to the last seed."

Qing frowned deeply.

Jin Seol nodded in agreement.

"We were too late in realizing it."

The love of superstition among the people of Zhongyuan was a deeply ingrained instinct on a genetic level.

No, it could be said that Zhongyuan were superstition itself, and superstition was the Central Plains.

Look at Qing's homeland.

The Red People's private army had burned all the traditions and evil customs of the old era to open a new era.

But they couldn't even touch the superstition, which was the identity and pride of the Chinese people, so they carefully preserved it in their hearts and passed it down to their descendants.

So once the rumor that a place was cursed spread, who would dare to set foot on that cursed land?

"The, uh, Miss Jin? But the Martial Alliance's support unit is scheduled to arrive."

"What? Why?"

Qing explained the situation.

The incident in Guangxi.

The Martial Alliance's support unit arrived a bit late and the situation had already been resolved, so they were sent to the Jin Clan instead.

"How can we show them this mess?"

Jin Seol stamped her foot.

"Hmm. Then wouldn't it be better to break the superstition? If someone works and is fine, people will think the curse has lifted. Why don't you let the workers stay inside the estate?"

"We should have done that sooner."

Meaning, it was already too late.

At that, Qing asked.

"Then, the construction was halted? The materials must still be there, right?"

"Yes. We have high-quality materials just taking up space."

"Then, we can repair the estate."

Qing answered casually.

At that, Jin Seol's eyebrows formed a steep angle.

She wondered if Qing had even listened to what she was saying.

"Didn't I just say that we have no way to do that? Especially since carpenters are sensitive people. Even if we call them from afar, they refuse and turn back."

However, Qing was nonchalant.

"Well, there's a skilled carpenter right here."

At that, Jin Seol blinked.

"Where?"

At that, Qing pointed at herself.

"Me. Ximen Qing. No, Carpenter Ximen of Luoning."

In Zhongyuan, jobs considered lowly often didn't have distinctions between men and women.

A fisherman's daughter was a fisherwoman, a farmer's daughter was a farmer, and a carpenter's daughter was a carpenter.

It was just that women's bodies were not as strong and lacked stamina, so they didn't usually do it for long.

In Zhongyuan, a wife or concubine was also considered one of the jobs a woman could have.

So, the fact that the Heavenly Flower could do carpentry wasn't all that surprising.

"You said you could do carpentry?"

Jin Jagang, the Clan Lord of the Guangdong Jin Clan, did not look like a martial artist.

If anything, he looked like a stubborn scholar who had consumed a lot of ink, with a lean build that resembled a bamboo tree.

Qing's first impression was, ‘Wow! A professor!'

But surprisingly, his tone was gentle, and even when Qing asked him to speak informally, he shook his head.

He said that if speaking comfortably made the person comfortable, how could he be so impolite to a guest.

Jin Jagang's character could be inferred from that one statement alone.

"I can do the work of ten carpenters, so if the Jin Clan members can help a bit, we can proceed with the construction. I already checked the materials, and they're fine since they were well covered with waterproof cloth."

"I understand that I should not ask this of a guest, but I must ask you shamelessly. I would be grateful if you could help."

"Oh, it's nothing. But, Clan Lord. Wouldn't it be a bit boring to just proceed with the construction? So, I have a suggestion……"

Qing laid out her plan.

At that, Jin Jagang's eyes gleamed.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Jin Family Estate of the Guangdong Jin Clan occupied the best location in Guangzhou.

It wasn't just a figure of speech. It was located at the center, from where one could reach anywhere in Guangzhou city, with a small stream nearby and several wells due to the underground water veins. It had been the largest local power, practically having a better location than the government office due to its geomantic properties.

Therefore, the Jin Family Estate was located right in the center of Guangzhou, where people constantly passed by.

And on the Jin Family Estate, a notice was posted after a long time.

「Seeking workers to participate in the estate reconstruction project. The lead carpenter is the greatest carpenter in Henan, also known as the Divinely Skillful Carpenter, who is also a renowned shaman. As such, she is an authority regarded as the best when it comes to ominous construction sites. We hope many will apply without any hesitation.」

Below that, the notice mentioned things like the provision of room and board, generous wages, etc.

"The greatest carpenter in Henan? They even brought someone from that far."

"That much ignorance must be why they're laying hands on a cursed house."

"They say she's a shaman's daughter. Maybe she's a woman with some insight into that sort of construction. It might be worth a try? If you work for a month, you can take it easy for the rest of the farming season."

"Hmph. The Blood Cult's curse isn't just any curse. I bet there will be a funeral on the very first day."

"Well, I'm going to watch how things turn out first."

Of course, that didn't mean they could immediately find workers.

It wasn't like they had put up the notice for that purpose anyway.

There was a separate target audience for it.

"Sect Leader! Sect Leader!"

"What's all the fuss about?"

"The Jin Clan is starting construction again. They even brought a carpenter from Henan, no less. It's said that she's the greatest carpenter in Henan and a shaman, so she can overcome curses."

"Is that even possible? How could they send someone all the way to Henan and bring a carpenter back here so quickly? It doesn't add up. And what shaman would do carpentry? If there were such a quack, rumors would have spread throughout Jianghu. And are the carpenters of Henan fools? To think they'd let a carpenter woman be called the greatest carpenter."

From start to finish, it was utter nonsense full of flaws.

"The Jin Clan must be resorting to trickery, don't you think?"

"Hmm. It seems those orthodox bastards are resorting to lies when cornered."

The Sect Leader smiled and turned his gaze to the side.

There sat a pale scholar, who smiled back and spoke.

"If a shaman carpenter dies, no one in the world will take on the reconstruction. It won't be a problem, will it? Even if they can't buy that cursed land, who would want to buy it? They won't even be able to raise the money to move. Sect Leader, you might be able to buy it later at a bargain price."

"Hahaha, having a smart one below me really makes things convenient. So, shall we do the same as last time?"

At that, the scholar smiled gently, a smile full of kindness.

"Wouldn't it be better to do it differently? Kill her as cruelly as possible and hang her at the marketplace."