\chapter{On the Plains and Hills, One Food and Two Hammers (6)}

The Killing Moon Sect was one of the three great forces of evil in
Guangzhou.

One might ask, how could a sect be named ‘Killing Moon'?

It wasn't because the leader of the Killing Moon Sect was going through
a late puberty, but because evil sects tended to choose names that
sounded more intimidating than those of others.

If Qing were here, she would say that overly strong names often
sounded weaker, but anyway…

For an organization's name to be sinister and ominous was actually a
commendation among the forces of evil.

After all, it made one think that they were not to be trifled with from
the name alone.

At any rate, Guangzhou had been firmly under the influence of the
Zhen Family. However, due to the timing, during the three months from
the middle of the martial arts tournament to the return, there wasn't a
single Zhen Family member present in the land of Guangzhou.

Thus, a warring states period of Unorthodox Factions quickly unfolded,
and now three Unorthodox Factions, the Killing Moon Sect, the
Guangzhou Shipping Union, and the Golden Dagger Union, held a tight
grip over the land of Guangzhou.

Even after the direct descendants of the Zhen Family returned, they
were busy with funerals and unable to recover from their losses.

The forces of evil were eager to solidify their territories, their eyes
burning with ambition.

And right now, the target of their keen attention was none other than
the talk of Changan, the mysterious carpenter and shaman, the
Earthen Maiden.

The leader of the Killing Moon Sect, Li Wangchul, was displeased.

"I heard there was construction today? And that quite a lot of materials
were used?"

"It wasn't even enough for one building, Big Brother."

"But they still did construction work, didn't they! If we leave it like this,
they'll gather workers again, and then the servants, and before you
know it, we'll be left chasing chickens with a dog."

"Should I send the boys, Big Brother?"

"Fuck, can't you stop with that ‘Big Brother' shit? How long has it been
since our Killing Moon became a renowned sect of evil? And you're still
going on about ‘Big Brother'? It's Sect Leader! Sect Leader, got it?
When a fucking Chief Manager keeps calling me Big Brother at every
turn, what are the boys supposed to learn?"

A proper Sect Leader wouldn't call his disciples ‘boys', for starters.

"Yes, Sect Leader. I understand. Sect Leader. Big Brother."

"This son of a bitch?"

"It's just a force of habit, Bi-, no, Sect Leader."

Chief Manager Wang Wu quickly lowered his eyes.

Of course, it wasn't really a force of habit.

He was deliberately calling him Big Brother at every turn on purpose.

After all, wasn't it some random bastard who had suddenly wormed his
way into the position of second-in-command, claiming to be an advisor
or something?

So he intentionally called him Big Brother in front of the boys to show
that he was the Sect Leader's direct subordinate and that even the Big
Brother couldn't treat this younger brother lightly.

Thus, he could only feel a sense of loss and sadness when hearing him
being called Sect Leader.

This was not a good sign at all.

The sense of loss felt by the Unorthodox Faction was a far more
dangerous and vile emotion than what ordinary people thought.

"Tsk. Send the boys to do a hit. If you dismember them and throw the
parts in the marketplace, even the most brazen bastard won't dare to
show up for construction work at the Zhen Manor."

"Wait. It would be better for the Chief Manager to go personally.
Rumor has it that the Earthen Maiden possesses monstrous strength like
General Xiang Yu. If we send some half-assed lackeys and they fail to
capture her, things will escalate, won't they?"

It was that random bastard, Advisor Fang, who spoke.

Wang Wu glared at him.

"What? You're saying that to take down one phony shaman, the secondin-command of the Killing Moon, the Great Killing Moon Sect's Chief
Manager, should go personally?"

"From what I see of the current situation, if you send underlings, they
will send even lower underlings, and who knows how far down it will go?"

"What? What's with this guy, speaking nonsense just because he has a
mouth."

"Enough."

Li Wangchul maintained his gravitas.

"Advisor Fang is right. Since it is an extremely important matter, is it not
right for you to handle it? After hearing you out, I, too, feel uneasy
leaving it in the hands of another."

"Hmph. If Big Brother says so, then this little brother can't do anything
about it. Big Brother."

Wang Wu persisted in calling him Big Brother until the end.

With that, Wang Wu stood up, glared fiercely at Advisor Fang once, and
then turned sharply to leave.

After he left, Li Wangchul clicked his tongue.

"That bastard is a bit insolent, isn't he."

Advisor Fang replied smoothly.

"Is it not all an expression of loyalty? Sect Leader, you are truly blessed
to have such a good younger brother. However, now that you are the
leader of a region, you should maintain language and conduct
befitting a large organization. Considering his personality, wouldn't it
be better for both of you if he were to head the combat unit instead of
being Chief Manager?"

"That's what I'm saying. That bastard Wang Wu doesn't even know how
much you're thinking of him, Advisor Fang."

At that, Advisor Fang just smiled warmly and said it was nothing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the southern part of the manor district was the villa district, where
the luxurious summer homes of the wealthy lined the beach.

And one of those villas now had a peculiar decoration.

All sorts of colorful fabrics were attached to the eaves, fluttering in
the wind, and various talismans were stuck on the main gate, giving it
an ominous appearance as if to seal away evil spirits.

And on top of that, words were written in blood.

It was uncertain whether it was chicken or pig's blood, but regardless,
despite the eerie appearance, the handwriting was peerless, making the
whole thing even more bizarre.

Instead of the Peerless General Xiang Yu, it is the Shrine of Lady Yu.

It was a phrase that made passersby snort.

Instead of the Peerless General Xiang Yu, the Shrine of Lady Yu?

Lady Yu, also known as Consort Yu, was one of the top five beauties of
Zhongyuan, as well as part of the top three most beautiful
women of all time.

The ideal beauty of all Chinese men, Xi Shi, was ranked first, while the
remaining three of the Four Great Beauties of Zhongyuan,
Wang Zhaojun, Diaochan, and Yang Guifei, were ranked second.

And the third rank was filled with Lady Yu, Daji, and Feiyan.

To claim to be Lady Yu while wearing a veil that chased away flies was
simply brazen, even if it was just to cover her face.

"So, let's just rip off that bitch's veil."

"Heh heh, Boss Hammer. What's the point of looking at a woman with
her face covered? If you see something you don't want to see, it'll kill
the mood and you won't be able to get it up. Let's just leave her face
covered and share her around, yeah?"

At that, Hammer tapped the back of his head lightly.

Hammer was the right-hand man of Wang Wu, the Chief Manager of the
Killing Moon Sect.

It wasn't because his head was shaped like a hammer, with a flat
forehead and a protruding back. It was said that he was called Hammer
because he liked to crush people alive by smashing them with a
hammer, or something like that.

Since Hammer was boasting at the front, it meant that Wang Wu had
disobeyed orders and used his subordinates after all.

"Can't you see how big that bitch is? From the way she swings that
hammer, her muscles must be like those of a horse. Would you want to
embrace a woman who's all muscle?"

"I'd rather like it."

"You crazy bastard."

For the Unorthodox Faction, lewd banter was as natural as breathing.

After all, from the beginning, they were bastards who joined the
Unorthodox Faction to fulfill their lewd ambitions of freely wielding
what was between their legs.

They had a grand ideal of becoming stronger to do whatever they
wanted, especially to women. So, one had to wonder if they were
pathetic or just honest.

Thus, one of them climbed over the wall.

Despite having done so stealthily, the agile movement of lightly
mounting the wall was quite impressive.

The one who crossed over then opened the main gate.

The bells hanging from the gate jingled, causing the members of the
Unorthodox Faction to flinch. However, as it was the middle of a
winter's night, there was no sign of life.

"Why are there so many bells?"

"Those shamans are all like that."

"Ugh. Creepy."

The villa was a high-end one, so the yard was spacious, but there was
only one lonely building standing there.

"Hey, the youngest ones. Keep watch."

"Do you mean us?"

At that, Hammer tapped the youngest one's head lightly.

"You've grown up now, haven't you? You have lackeys under you now,
huh? I'll call for you when it's time to have fun, so keep a good eye out
for any suspicious bastards."

The monstrous strength of the Earthen Maiden was famous.

It was said that just seeing her drive a pillar into the ground by herself
made people nod, thinking that it was no wonder she served General
Xiang Yu.

Therefore, the members of the Unorthodox Faction called to capture
the Earthen Maiden were mid-level martial artists who had quite a bit of
experience under their belts.

Leaving two behind, the members of the Unorthodox Faction carefully
approached the villa.

The youngest and his senior, who had been watching them blankly,
nudged each other.

"You're going to raid the warehouse, aren't you? Let's go together."

"Are you really allowed to be a team leader? Always going against what
your Big Brothers tell you."

"…I'm not."

"Let's do our best. Okay?"

The youngest's expression was like that of someone who had chewed
on shit.

The new disciples had come in droves recently, so there were many
team leaders, but this bastard still acted like their Big Brother.

However, if one was dirty, they should have entered the sect first.

There was nothing that could be done.

The youngest took a deep breath.

It wasn't just to sigh.

He was trying to sigh to scratch that bastard's ears, who was pretending
not to sigh.

Warak.

Suddenly, a huge hand covered his mouth.

At the same time, his neck was constricted, blocking his airway and
preventing him from making any noise.

As the youngest struggled, something lifted him up by his torso.

His feet, floating in the air, kicked a few times before eventually
dangling limply.

Meanwhile, the one who had entered the warehouse let out a sigh of
relief.

Perhaps because the walls were surrounding it, as soon as he opened
the warehouse door, warm air came out.

Since it was already a cold night, he quickly entered the warehouse,
basking in the warmth and enjoying the sensation of his skin tingling.

"Why is there a fire in the warehouse?"

Indeed, there was a faint glow, as if there was a charcoal fire in a brazier.

"Ah, the warmth makes me feel alive."

This year had an intercalary month, so right now, February was the
time when the most severe cold would hit. Moreover, it was the coldest
time of the night.

Of course, Qing would just sniff and say that this wasn't even cold and
that the early autumn of Hubei was colder, but…

But for a native of Guangzhou, even this was cold.

So, with a joyful expression, he quickly entered and approached the
brazier, enjoying the warmth.

Then, he suddenly made eye contact with a man who was staring blankly
at him.

Not just one man.

As if waking up one by one, men who had been lying on the floor with
blankets rolled up stood up.

"Wh-Who are-"

"Enough."

A voice infused with Inner Qi blocked the Unorthodox Faction member's
words.

"I am called Jin Jagang. You probably know my name, don't you?"

Of course he knew. Who in Guangzhou didn't know the name of the
head of the Zhen Clan?

The Unorthodox Faction member's eyes darted around.

But no matter how much he looked around, there were only many
enemies, all with menacing expressions.

"Be quiet. If you make a sound, unfortunately, I will have no choice but
to kill you."

At that, perhaps hoping that a small sound would be fine, the
Unorthodox Faction member covered his mouth.

And then, thud, the warehouse door closed.

"Would you like to kneel?"

At those almost polite words, the Unorthodox Faction member quickly
knelt down.

Knees were originally light for members of the Unorthodox Faction.

"I'm thinking of tying you up. If you resist, it will be very difficult.
Would you like to resist?"

"No, no, I won't."

"Hmm. You listen well."

At that, the middle-aged man, Clan Head Jin Jagang, gestured with his
eyes.

Not long after, the Unorthodox Faction member was lying on the floor,
tightly bound.

And a little while later, the youngest was also thrown beside him,
limply tied up.

Jin Clan martial artists started to leave the warehouse one by one, and
finally, Jin Jagang, who followed them, paused as if he suddenly
remembered something, and said while holding the warehouse door.

"Ah, right. Did I mention that even if you don't make a sound, I would
kill you? I hope you take some time to reflect on your life while you
still have time."

"Eueup-!"

The Unorthodox Faction member tried to shout belatedly, but creak,
thud. The sound of the warehouse door closing was the only thing that
replied. 