\chapter{On the Plains and Hills, One Food and Two Hammers (9)}

The Civil Engineering Fairy had descended upon the construction site once more!

The return of the Civil Engineering Fairy!

This was a signal that the Civil Engineering Fairy had emerged victorious in the century-defining spiritual battle against the curse of the Jin Family.

As such, people with nothing better to do gathered to witness her prowess.

"Fairy?"

"Is it really the Civil Engineering Fairy?"

"Ahem, you people. Do you not see even though you have eyes? If I am not the Civil Engineering Fairy, then who am I?"

"Well, your attire… Um, it seems you were hiding your strength."

Jin Seol had stayed up all night to make new shaman clothes. Well, to be precise, she didn't make new clothes, but rather patched up existing ones with various fabrics.

As a result, the colorful fabrics that were once sloppily attached and fluttered about busily had melted into the clothes, harmonizing with the beautiful curves of the woman's body.

Except for the feeling of tightness around the chest and hips, it had become an excellent garment that accentuated Qing's grand, yet elegant figure.

Qing didn't really care much about clothes.

Still, she had to admit that Jin had perhaps taken the wrong career path. If she had become a tailor instead of a martial artist, she might have made a name for herself throughout Zhongyuan.

"Ahem, you people. Do you want to taste the might of this wondrous hammer? Can't you get rid of those impure gazes? I came out today to build a house, but tsk tsk."

However, today, people were not here to see the Civil Engineering Fairy's monstrous strength.

They were all eager to hear the truth of that night, the grand battle between the Civil Engineering Fairy and the curse.

"So, Fairy? We heard that there was quite a commotion in the middle of the night……"

"What's the big deal? Some ominous thing came to the shrine at night, so I just chased it away. No matter how vicious a curse is, it's still a human's doing. If the Great Deity, Xiang Yu, shouts just once, they scatter in fear, screaming in terror."

Qing spoke as if she had fully immersed herself in the role of a shaman.

Her voice was also crisp and sharp, making her look like a proper shaman.

"Fairy? Are you not cold? On days like this, instead of hammering in the cold wind, you should have a warm cup of alcohol."

"Hmm. Shall we?"

In Zhongyuan, paying for tea or alcohol in exchange for stories was an age-old tradition.

And so, a bowl of warm yellow wine was placed before her.

Originally, yellow wine should be drunk warm to truly appreciate its flavor.

After taking a refreshing gulp of the free alcohol, Qing began to tell her story.

"After finishing the construction for the Jin Family, I was putting away the materials when I suddenly thought, ‘Ah, perhaps an unwelcome guest might come today.' This is the intuition of the Greatest Carpenter in Henan. But who am I? Am I not the Greatest Carpenter in Henan? There was no reason to fear some evil spirit, so I went to sleep early, didn't I?"

The listeners tilted their heads.

What is this intuition of the Greatest Carpenter in Henan?

And what does being a carpenter have to do with evil spirits?

Do carpenters in Henan also beat up ghosts?

Is it because of the Shaolin Temple?

"Then, in the middle of the night, I woke up to the sound of an evil spirit seeping in. You all, do you know the sound of an evil spirit entering? It's like a chilly night breeze, but from far, far away, where human ears cannot hear, you hear the sound of footsteps, trudging along."

At that, the people swallowed their saliva.

"So, I quietly hid myself to see what kind of curse it was. Yes. Then, when the evil spirit crashed into the Shrine of the Beautiful Lady, the bell that wards off evil started ringing on its own, clanging loudly. It was shaking so violently that I thought the bell would break."

"So, so what happened then?"

"So I finally met eyes with those outrageous things and my goodness, I have never seen such eyes before. They were gleaming like beasts, filled with evil, not just any evil spirit that had eaten one or two people."

Qing lowered her voice.

"But, from here on out-"

"Waiter! Bring more yellow wine!"

"Do you like the dried fruit here Civil Engineering Fairy? Which ones do you like? No, I'll just order all kinds for you."

It was a common practice for storytellers to pause the story at this point.

In Qing's homeland, it would be similar to saying, ‘To be revealed in 30 seconds,' or ‘Please watch the commercials.'

As such, seasoned story listeners would place offerings on the cleared table.

Qing blinked her eyes.

"No, I didn't mean I wanted alcohol."

It was absurd, but… Hm. Still, I'm happy.

Qing emptied a cup of yellow wine in one gulp and set the mood again.

"I wasn't saying I was thirsty, but what I'm about to say now is so ominous. Do you know what curses are? Curses don't just appear on their own. Have you ever seen something that didn't exist in the world appear by itself? Curses are the same, they have a creator. It means someone wanted to harm the Jin Family so badly that they killed a person and created a curse with a poisonous heart."

"Who, who is it? Could it be… them?"

One of the onlookers added a beat.

Them, those whose name cannot be spoken.

There wasn't a bald, noseless sorcerer in Zhongyuan, so they were referring to the evil cults.

A characteristic of cities where evil cults held dominance was that ordinary people could not speak the name of the evil cults.

At this, Qing shook her head.

"Honestly, I don't know for sure either. I can tear those evil spirits apart with divine power like that of the Great General Xiang Yu, but even if I were to chase down their roots, do you think those cursed villains would tell the truth?"

"Then, is the curse on the Jin Family gone now?"

"No. It's not over yet."

Qing firmly cut them off.

"When a curse fails, it doesn't just disappear. It returns to its creator, the one who made the curse, you see. Haven't you heard the saying? If you want to curse someone, dig two graves."

The onlookers looked puzzled.

Qing also looked like she didn't know what she was talking about.

Huh? Is this not right?

It's not digging graves, but something else? Or is it not two, but three?

Wasn't it a famous saying?

This was because it wasn't a saying from Zhongyuan, but rather from those Japanese bastards.

"If you want to curse someone, you must dig two graves, one for your enemy and one for yourself. If the curse succeeds, the caster will also be harmed as payment for their deeds, so they must dig their own grave too."

"Then, even if the curse works, the caster is also harmed?"

"That's what's so scary about curses. That's why people have avoided curses and incantations since ancient times, calling them wicked. But the scarier thing is when the curse fails. Do you know what happens when those curses are badly hurt by a spiritual carpenter like me?"

"W-What happens?"

Qing finally revealed the main point.

"They take their anger out on their owner. So since I chased away that vicious curse, it will surely harm the one who created it. If there are any bastards in Guangzhou city who suffer a very, very great misfortune, they are the ones who cursed the Jin Family."

At that, the listeners' eyes lit up.

It meant that bastards in Guangzhou city would suffer a very, very great misfortune.

Wasn't this a premonition of turmoil, a forecast of great fun and spectacle?

The listeners' butts were already fidgeting, their mouths itching, eager to spread the news.

And Qing added fuel to the fire.

"But curses have a habit of recognizing those who know about them. You all heard about the Jin Family's curse from me, so if you're unlucky, you might suffer misfortune."

The people of Zhongyuan had a particular fondness for superstition.

"Gasp. Then what should we do……"

"I bet she's going to sell us talismans now, right?"

This was also a common transition for shamans.

Those who were faint-hearted or obsessed with superstition were ready to hand over their coin pouches, and those with a bit more fortitude thought that it wouldn't be a bad idea to buy one if the price was right, even if they didn't believe it.

Or there were those who would immediately get up and leave, saying ‘Hmph, I knew it' with a scowl.

At this, Qing clicked her tongue loudly.

"Who do you think I am, a merchant! Would I leave people to suffer misfortune after hearing my story! I told you because I have a plan."

"W-What is this plan!?"

"Spread my story far and wide. Once everyone in Guangzhou knows about the curse, then the curse will think its fame is natural and won't bother you. So tell everyone that the Jin Family's curse is broken, that the resentful curse is returning to its owner, and that they will soon suffer great misfortune. Do you understand what I'm saying?"

Fortunately, it wasn't an expensive prescription, and since they were already eager to spread the story they had just heard, it wasn't particularly troublesome.

"Now. I've had my fill of alcohol and snacks, so go and spread this news throughout the world and avoid misfortune. The more people who know, the safer you will be. Now. So go, spread this news to every corner of the world."

Thus, the listeners, acting as disciples, rose resolutely to spread the teachings of the Greatest Carpenter in Henan far and wide.

The common folk said, ‘Have you heard the news? It is an ominous and wicked tale, but it will be entertaining to your ears, and by doing so, you will also gain safety.'

At that, the listener would reply, ‘I have been eagerly awaiting such news in this long winter, so storyteller, accept my alcohol and share your tale with this poor, bored guest.'

The people's love for gossip and the desperate need to avoid curses combined, spreading the newly updated rumor like wildfire in the dry winter.

Thus, the talk of the town was none other than the curse.

And the question of whether the curse, as foretold by the Civil Engineering Fairy, would befall its owner.

Then, who was that owner, and if misfortune struck, just how great would it be?

It was a great topic to talk about during the idle farming season.

Some dismissed the Civil Engineering Fairy as a fraud and her words as nonsense, while others argued that since she had completed the Jin Family's construction without a hitch, there must be something to her claims, sparking impromptu betting pools.

There were many types of bets.

Bets on who would be struck by the returning curse.

Bets on when it would strike.

Bets on whether the Civil Engineering Fairy had divine powers and if misfortune would actually occur.

Thus, countless people in Guangzhou were waiting for a new incident, as well as the fate of their bets.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Naturally, such ominous rumors also reached the ears of the Extermination Moon Cult.

They heard that those who had cursed the Jin Family would suffer great misfortune because of their own curse.

At this, the Extermination Moon Cult Leader, Yi Wangchul, paced around the Cult Leader's Hall.

"What tricks are the Jin Family playing now?"

However, Advisor Bang remained calm.

"It's just a way of saying they will take revenge, like ‘An eye for an eye, blood for blood'."

‘An eye for an eye, blood for blood' meant taking revenge in kind, a mindset of a real man.

This was a bit different from the saying ‘An eye for an eye, a tooth for a tooth', which was a saying from the Western Regions at the time.

Back then, in the Western Regions, it was common for someone to be killed over a mere shoulder bump, so the saying meant to return only a shoulder bump for a shoulder bump, emphasizing the importance of human life while advocating for revenge.

Therefore, ‘An eye for an eye, a tooth for a tooth' was a law that encouraged forgiveness, not revenge.

But for the people of Zhongyuan, who considered such a timid mindset as something to be spat on…

They believed that if one wasn't ruthless, they weren't a real man. In Zhongyuan, revenge was considered an integral part of a person's character.

However, on the other hand, the saying ‘A gentleman's revenge is never late, even after ten years' was also highly regarded, meaning that one should hide their true intentions and bide their time.

So, for the Jin Family to openly announce their intention for revenge was, in essence, quite unusual.

That was why the Extermination Moon Cult Leader was so nervous, thinking that something big was coming.

If the factions clashed, the Guangzhou's evil cults could unite and win, but if they schemed in secret, his own safety would be at risk.

After all, the head of the Jin Family was an Unrestrained Realm Master.

What if he got drunk and started breaking things while I'm enjoying my hobbies with concubines, alcohol, and all?

"You have a point. If the Jin Family's bastards try something and it doesn't get found out, it will be rumored that the Extermination Moon Cult cast the curse. And even if it is discovered, the justification is clear, regardless."

But Advisor Bang remained calm.

Wasn't this a truly trustworthy appearance?

Yi Wangchul grabbed Advisor Bang's hands.

"So, what should we do?"

"Let us stay quiet for a while, as if we have closed our doors. Martial artists should also refrain from acting alone. Since they have already spread rumors about a curse, they will surely try to harm us in some way. If no harm befalls us, won't the Jin Family just end up looking ridiculous? However, if we do not step forward, it will be nothing more than a midnight ambush."

The idea was to temporarily halt the activities of the sect to make it impossible for them to ambush anyone in the middle of the night.

"But that ambush is the problem."

"The Jin Family is short on manpower. Moreover, each martial artist is a direct descendant of the Jin Family, so they are resources that absolutely cannot be lost. Therefore, if we capture one or two of them, they will surely retreat."

Advisor Bang was as calm as ever.

When the advisor maintained his composure, the leader also found peace of mind and courage.

"As expected! You've thought of everything! You are indeed my Zhuge Liang! No, you, Advisor Bang, are a step above Zhuge Liang to me!"

Yi Wangchul praised Advisor Bang.

It was then.

Hurried footsteps rapidly approached, and before he could even say ‘Come in', the door to the Cult Leader's Hall burst open, almost flying off its hinges!

"You bastard, I told you to get permission before entering, how many ti-"

"Big trouble! The Golden Coin-"

"Golden Coin? Why are they?"

"The Golden Coin Clan is ruined! It's completely destroyed!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing also heard the news.

"Huh."

Qing was just dumbfounded.

What? Why is the Golden Coin Clan suddenly ruined?