\chapter{On the Plains and Hills, One Food and Two Hammers (7)}

The shape of the woman, who had thrown a blanket over herself and lay on the bed, was bulging. 

Even if he knew she was a muscular woman and wore a veil, seeing that shape made a man's crotch bulge. After all, it was a man's destiny.

Mangchi's expression became utterly insidious.

"Hey, Earth-Building Fairy. Your men are here, so how can you just lie there?"

Mangchi called out to her, but the woman did not even stir.

Mangchi let out a snicker.

"Khehe, she's sleeping without a care in the world. Who's going to carry her away if she keeps doing that?"

As Mangchi said that, he suddenly threw the blanket away.

Then, poof. Unfortunately, it was just a blanket.

And also, cling-clang! Those are bells.

"What?"

It might be said that this was a very basic trick, but in fact, it was a trap anyone would fall for.

How would the Earth-Building Fairy know about the attack of the Killing Moon Squad and prepare for it? Even if she did, when would she know to vacate the bed?

However, before that, their instincts as members of an Unorthodox Faction screamed at them.

I'm fucked. I feel like something's really fucked.

Just as Mangchi raised his voice…

"Eugh! Everyone-"

-Ahhhhhk!

A desperate scream resounded from beyond the wall.

And on the south wall of the bedroom, made of wooden frames and paper, shadows of people were cast.

"Hyung-nim……?"

"It's a trap. Everyone, hide. We don't know who they are, but if they attack, we'll rush them all at once and escape amid the chaos."

Despite his dull appearance, Mangchi made quick judgments.

The Three Great Unorthodox Factions of Guangzhou were the Gold Coin Union, the Canton Shipping Company, and the Killing Moon Squad.

Since they were factions that ended in ‘Union' and ‘Company', they represented professions, so the Gold Coin Union was a usury business and the Canton Shipping Company was a shipping, shipbuilding, and fishing business.

Meanwhile, the Killing Moon Squad had purely taken over the underworld with force.

And Mangchi was the Action Leader of the Killing Moon Squad, which had conquered the back alleys of the underworld.

Thus, the Unorthodox martial artists stuck to the corners, holding their weapons tightly and bated their breaths.

Clang clang clang. The sound of something flying and hitting the paper door was loud.

Some even pierced through the paper and broke inside the room, instantly filling it with a pungent smell of oil.

Anyone could tell at once that the word ‘fire' had passed through their minds, as well as the fact that these bastards intended to burn them alive.

At this, the martial artists of the Killing Moon Squad exchanged glances and simultaneously kicked off the floor, rushing out.

As Qing listened carefully, she noticed that one of them was searching a separate room, while the other five rushed into the bedroom.

Qing melted into the darkness, unseen by others.

Of course, she was far from being an actual ‘Stealth Master'.

It wasn't because her Stealth training was lacking, but rather because her natural disposition was to move in large, boisterous motions, making it hard for her to move stealthily.

However, the fact that her presence was barely noticeable even without actively trying to hide it proved that her Stealth training was actually effective.

How big could a detached house be?

She soon found the Unorthodox Faction bastard searching the house.

"Fuck, it's all fucking empty."

He was opening every cabinet and feeling around, but what could possibly be found in an empty detached house in the first place?

But he didn't give up and continued to open drawers and cabinets with an indomitable will. As such, he didn't notice Qing approaching right behind him, holding up a hammer.

If anyone were to observe this, they would probably shout ‘Behind you, behind you!'.

Meanwhile, Qing was carefully following him from behind, wondering when he would notice her.

Then, cling-clang……!

Upon hearing the sound of bells, Qing's lips stretched wide to the side.

Ding. Unfortunately, time's up.

"Hey. Disturbing a shrine like this… You're going to be punished by the heavens. No, by Qing."

"Eheok!"

The bastard startled and turned his body, but the hammerhead had already sliced through the air with a sharp swoosh.

It struck his instep slightly diagonally!

Crack! A ghastly sound of meat being crushed.

In that brief moment of the blink of an eye, flesh burst and bones were crushed, conveying the sensation of squashing something living.

Without any Inner Qi, it was the pure essence of the enchanting sensation of tightly compressed meat, piercing through the palm with just physical strength.

Haeuuut. A sweet exhale escaped Qing's mouth without her realizing it, but it was buried by a much louder scream.

"Ahhhhhhk!"

The hammerhead that struck the instep had slightly dug into the hard wooden floor, so what could possibly become of the flesh caught in between?

Qing looked down at the Unorthodox martial artist, who was screaming at the top of his lungs and writhing.

The shadowy eyeholes sparkled with an ominous glint.

Hm. It's a shame, but I guess this is all I get.

After all, the Jin Clan members should be allowed to enjoy themselves too.

Qing licked her lips and then suddenly changed her expression, entering a mode of immersive acting.

"Oh no! Mister! Your foot! Your foot!"

"Ahhhhk! Ahhhhhk!"

"Mister! Try to get a hold of yourself! Get a hold of yourself!"

"Ahhhhhk! Ahk, Ahk, Ahk, Ahk!"

Qing slapped the cheeks of the Unorthodox martial artist, who was just opening and closing his mouth, screaming his lungs out.

However, despite the shock therapy, it had no effect. In fact, the Unorthodox martial artist seemed to be even more terrified, flailing his hands and hitting Qing.

Of course, this was the same Qing who would rush towards a blade if she thought she could get away with it.

So, the feeble flailing of a mere Unorthodox Faction member was hardly a threat.

After leaving the utterly confused Unorthodox martial artist's neck, Qing wondered how she could make him get a hold of himself.

If slapping his cheeks didn't work…

Then that meant the shock was too weak.

A greater shock would overcome a greater fear!

A nuclear headbutt fell towards the Unorthodox martial artist's head.

It was a complete act of violence, the very definition of destruction of the world, as well as an irresistible, overwhelming force.

Thwack!!!

The Unorthodox martial artist's eyes rolled up as if they would turn inside out. Then, they barely came back down.

"Haeueok."

If one was in enough pain, they couldn't even scream.

It seemed like he had come to his senses, so Qing squatted in front of him and spoke kindly.

"Hey. You don't seem to understand the situation right now, do you? You've been ambushed, you see? Your right foot has been completely turned into jerky. So, is it time for you to be screaming like this? With that appearance, do you think you can beat me? So, what should you do now?"

"S-Spare-"

"Do you have any history of sparing those who asked for their lives? Not even once-"

"I have!"

"That's a bit too quick of an answer, don't you think? When? Where, and to whom did you spare and for what reason? Answer. One. Two. Three. Four……"

Qing folded her fingers one by one, speaking like a child would.

The Unorthodox martial artist could not answer.

"Now. Begging for your life won't work, right? So, what to do? You have to run. Now. Try to run."

"What? What?"

"Run. Hop on one foot, can you?"

Qing said, revealing her white teeth.

What if, when one wanted to cry, they were slapped on the cheek?

Then, they might just think, ‘Now is the time. Now is the time to let it all out and weep to my heart's content', and burst into tears, completely opening the floodgates.

The Jin Clan members wanted to vent their hatred.

Their family, their relatives, with whom they had lived under one roof, had been brutally murdered, but their enemies had escaped.

So, what if, at a time when they were filled with such resentment, unable to move on, robbers appeared to overturn their funeral and steal the funeral offerings?

Your Honor, no, Magistrate. I believe you would acknowledge that ‘Those who should have been beaten to death were beaten to death, so isn't this just a natural cause of death?'

The Unorthodox Faction martial artist who had escaped through the paper door suddenly felt a gentle force lift him as an imposing figure blocked his path.

A trajectory of the sword that split at the end, extending in two directions.

The white hand, like that of a scholar, seemed as if it would be split apart in front of such an excellent display of Sword Qi.

However, after just a moment, the Unorthodox Faction martial artist felt a gentle force lift him.

Without realizing it, his body floated up. Then, after naturally turning a full circle on the flat back, the world spun once, twice, and then, thud!

As the Unorthodox Faction martial artist, who had been slammed to the ground, looked down at his shoulder in sudden, excruciating pain…

He saw his own broken arm, twisted one and a half turns at the shoulder, with the bone protruding. He was then greeted by his own ulna and radius for the first time in his life.

Hello, dear owner. I am your right humerus. It is a great shame to see you like this, with bone marrow leaking out messily.

"Ahhhhhk!"

When a person actually sees their own injury, they tend to feel twice as much pain. As such, a terrible scream belatedly burst forth due to the horrific pain.

The same thing happened here and there.

Of course, not everyone could perform the feat of turning an arm one and a half turns and extracting the bone like Clan Lord Jin. Such a technique was only possible for a true expert.

As a result, other Unorthodox Faction martial artists were not as severely injured.

It could be said that they were rather unlucky because of that.

Since they were in a seemingly better state, the enraged Jin Clan martial artists started beating them up even more.

Ahhk! Agh! Ahhhhhk! Spare! Ssss!

In the middle of the night, screams and pleas rang out.

It was around this time that Qing returned to the yard, dragging an Unorthodox Faction martial artist.

Seeing the brutal assault being carried out in the detached house's yard, Qing, startled, dropped the hair she was holding and rushed over, jumping in excitement.

"Wait! Don't left me out! Let's do it together!"

Thus, Qing also joined in on the beating.

Kicking, stomping with her feet, striking with her palms, hitting the head, kicking the cheeks and making teeth fly out, stepping on hands, and snapping fingers back.

Since there were more Jin Clan martial artists, they beat them in groups of two, making it an even more enjoyable time.

If people saw this, they would think it was some Blood Cult's fiends, not members of an Orthodox Faction.

Then, suddenly, Qing spoke.

"Huh? Clan Lord. One of them is missing, though? There were definitely five of them, but there's only four here?"

"Hm?"

At that, the Jin Clan martial artists stopped beating the Unorthodox Faction members and looked towards the detached house, where the paper door had been completely destroyed, revealing the bedroom inside.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Mangchi used his head.

When his subordinates rushed out, Mangchi quietly crawled under the bed alone.

Then, he heard sounds.

Unceasing screams, the thumping sounds of flesh being beaten, and groans that were cut off abruptly.

It was a sound very familiar to an Unorthodox Faction member, so he had a rough idea of what kind of scene was unfolding.

Who the hell are they?

How dare they interfere with the great Killing Moon Sect's business?

Since the other side had more numbers, he decided to endure for now, but he would definitely repay this humiliation.

Then, a particularly piercing female voice reached his ears.

It was either because she was a woman, or because her voice was so beautiful that it stuck in his ears.

- Clan Lord, one of them is missing, though.

Mangchi's heart sank.

The Jin Clan, it's the Jin Clan's bastards!

Even though they were a tiger with its teeth pulled out, it didn't mean that the direct line had been annihilated.

Moreover, Clan Lord?

If the Jin Clan Lord had stepped forward himself, even if it wasn't his older brother, the Great Clan Lord, but his other older brother, the Sect Leader, there would be no chance of winning one-on-one.

So, Mangchi suppressed his breath.

He would die if he went out anyway.

So, he decided to just stay hidden.

Maybe they'll think he got away and disperse.

Then, he heard footsteps approaching.

- It's strange. Where did he run off to?

- Did he already escape?

- Hm, should we have guarded the back door?

- We need to hurry up and track him down. Hurry. If we miss even one, it'll be a hassle.

- Yes, Clan Lord!

Then, the footsteps hurriedly moved away.

Mangchi felt a brief moment of relief, but he didn't even dare to exhale.

Then, a once-in-a-lifetime conflict surged within him.

If he left too quickly, he might be discovered. But if he lingered too long, they might come back.

A single moment felt like a year.

The surroundings were quiet.

It was winter, so not even the usual insects were chirping.

It was so quiet that his own heartbeat sounded loud.

Time passed. Sweat dripped.

Time did not pass. Sweat formed droplets and fell.

How much time had passed?

His extremely heightened nerves stretched the time out endlessly.

After a long, long while…

Mangchi carefully extended his arm and moved his body, which was stuck to the floor.

Creeeaaak, his body scraped against the floor, causing his heart to sink.

He used his fingertips and toes to lift his body, moving slowly and carefully outside, trying not to make even the sound of his clothes rustling.

At that moment, a voice was heard.

"Wow. You're finally crawling out now?"

Thump!

Mangchi tried to stand up abruptly, but ended up hitting the bed with his back.

It was such a rough movement that the bed lifted slightly. As such, there was a loud thunk! followed by a creak! as the bed shook.

Then, he finally met ten pairs of eyes looking at him. 