\chapter{On the Plains and Hills, One Food and Two Hammers (8)}

Qing asked with a voice full of laughter.

"Why are you crawling out from under a woman's bed like a rat? Are you a pervert facing the death penalty?"

"I-It's just that."

Looking down at the flustered Hammer, who was at a loss for words, Qing added another word.

"Answer."

It was truly a word worthy of a great man.

If you are a great man, you must be able to convey your meaning with a single word.

At this display of dignity, Hammer was overwhelmed and immediately prostrated himself.

"I have committed a grave sin!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Among the martial artists of the Jin Family, there were some who had particularly refreshed expressions.

They looked as lighthearted as if they had shaken off some burden, just like people greeting a new morning.

And as much as they were lighthearted, the screams, or rather the cries, resounded far and wide in the Hall of the Enchanting Beauties last night.

The commoners who heard the sounds lit up their eyes and gossiped until their lips were chapped.

Did you hear the sounds last night? Do you know what they were? They were horrifying, the terrible screams of a person desperately crying out. But do you know where I heard them?

Ahem, I'm getting thirsty.

Ah, I could use a drink. Alright, alright, stop pestering me. It was the Hall of the Enchanting Beauties. A curse has been placed on the Geomok Fairy. It's the work of vengeful spirits of the Jin Family who died unjustly.

Yes. Ghostly wails. Just thinking about it sends shivers down my spine. It was a terrible sound.

Geomok Fairy? I don't know. If she's a truly powerful shaman, wouldn't she just show up alive?

Where else could there be such an interesting story in this boring Zhongyuan?

Those who had quickly bought drinks and heard the story would then say, ‘Have you heard the story?' as if it was their turn to be treated.

Of course, there were many who had heard it for free, not buying drinks but just eavesdropping at someone else's table.

At any rate, this was why rumors spread thoroughly within a city in just one day in Zhongyuan.

As a side note, rumors did not travel well outside the city. First, the person carrying the rumor had to go outside the city, and the listener in another village wouldn't be that curious about the rumors of another village. Furthermore, it was difficult for the person explaining to make it interesting.

I heard there was a shaman called Geomok Fairy in our village who served a general called Xiang Yu, and ah, before that, I should tell you about the tragedy of the Jin family. That was……

Anyway, the market was abuzz with talk of Geomok Fairy versus the curse of the Jin Family.

In the true spirit of Zhongyuan, it was common for betting pools to spring up here and there, wondering whether Geomok Fairy had won or if the curse had won.

Since there was nothing to do in this dull winter, the voices of idle people making idle chatter were loud, so it was natural that such news would reach the ears of the members of the Killing Moon Squad.

"What the fuck? Hey, hey, bring Wang Wu, that son of a bitch, here!"

As soon as the head of the Killing Moon Squad, Wang Wu, entered, a sandglass flew at him.

Should I dodge it? Or not?

Wang Wu briefly considered before simply crouching his neck to prepare for the impact.

If it were an inkstone, he would have considered dodging, but a sandglass was something he could take.

Crack!

A sandglass was a device used to hold water for grinding ink when writing.

Naturally, it contained water, so when the sandglass shattered, water splashed out.

Immediately after, the leader of the Killing Moon Squad, Yi Wangchul, unleashed his livid anger.

"You, you! What the fuck are you doing, you son of a bitch?! I told you to go and take care of it yourself! But you're still sitting on your ass after sending the kids? When did you start to just ignore what I said?!"

"……I apologize."

Wang Wu bowed his head.

The water that had soaked his head trickled down his forehead, collected at the tip of his nose, and then dripped down.

Although Wang Wu was a master in his own right, his head would not be split open from getting hit by a sandglass. Nevertheless, he felt utterly miserable.

If there had been self-help books in Zhongyuan, the leader of the Killing Moon Squad, Yi Wangchul, would not have done such a foolish thing.

This kind of interrogation only resulted in resentment and resistance from subordinates. There was no way they would sincerely reflect on their actions.

This could be seen just by looking at Qing's hometown.

How many people, if they could kill through imagination, would have died many times over due to the numerous office workers thinking, ‘Fuck this shit, I'm done. But I have to put up with it to make a living'.

So, Wang Wu was honestly upset.

It was separate from the fact that he had disobeyed orders, so such an interrogation was completely ineffective.

Goddamn it. Honestly, isn't this going too far?

I've lost seven of my brothers, and instead of consolation, I'm being treated like this.

And didn't my lord know that I cherished Hammer like a brother?

Besides, Advisor Bang's faction was growing larger by the day.

At a time like this, shouldn't he at least console me for losing my right-hand man?

"Would you please calm down? Leader. Wouldn't the Chief Manager have ordered a trusted subordinate to carry out the task? Isn't that right, Chief Manager Wang?"

"……That is so."

Why is this fucker taking my side? Wang Wu momentarily looked at Advisor Bang with new eyes, only to realize he was being subtly mocked by seeming to take his side.

"Seven were sent, but not a single one returned, which means the enemy was formidable, was it not? Chief Manager Wang might have been in danger as well. Of course, it's unknown what would have happened if Chief Manager Wang had gone in person. If Chief Manager Wang's skills were lacking, he might have died. If they were outstanding, he might have succeeded. But at least he saved his body by staying safe, didn't he?"

"Ha, he should have just died then! Get out! I don't even want to see your face!"

Wang Wu was resentful and furious.

After the Chief Manager left, Yi Wangchul grabbed the advisor, Bang Jeommyeong.

"Advisor Bang, was that Geomok Fairy really such a master? Could there be a sect or something behind her, coming to take revenge?"

After making a fuss and failing, the saying of Wulin came to mind.

(Omitted) Be careful in Wulin.

However, Bang Jeommyeong shook his head.

"Rather than that, there's a higher possibility that the Jin family intervened."

"What? Then, did the Jin family realize what we were up to?!"

"There's no need to worry."

"How so?"

"The Jin family would have already had their suspicions. Now they've just obtained physical evidence, but what can they do? You didn't know about it, Leader."

"Hmm?"

"Wasn't it something that Chief Manager Wang did on his own initiative? Did you order it, Leader? Or did I?"

At this, Yi Wangchul had an expression of realization.

"I see!"

I didn't order it.

It was Wang Wu who made the decision and acted on his own.

"It will be resolved nicely by handing over Chief Manager Wang. We can't use the curse anymore, but we've already enjoyed it quite a bit, haven't we?"

Then, Advisor Bang chuckled.

"The Jin family can't attack us anyway."

"Why is that?"

"The Jin family has no warriors. Even if only the direct-line masters come, there are only about ten, right? Then the Jin family will surely perish."

"But wouldn't we also perish?"

"Didn't the Geumjeok Gang and Gwangju Seonbang also participate in this matter? If the three prominent families of the Four Paths combine their strengths, what could even the Jin Family Head, who is an Unrestrained Realm Master, do?"

"But if the Wulin Alliance makes a move……"

"You must trust our Four Paths Alliance then. Doesn't the fact that I was dispatched to the Killing Moon Sect show how much the Four Paths Alliance values you, Leader? The Four Paths Alliance has high expectations for you."

Advisor Bang was a person sent by the Four Paths Alliance.

Otherwise, no matter how capable an advisor was, how could a weak scholar integrate into a group without any friction?

No matter how much a leader protected someone, a weakling would inevitably be challenged, but no one could carelessly confront someone backed by the Four Paths Alliance.

"Indeed, you are my Zhuge Liang1!"

"Hehe, you flatter me."

Zhang Liang, whose courtesy name was Zifang, was a strategist and advisor during the Chu-Han Contention, considered the greatest strategist of all time, even surpassing Zhuge Liang.

Therefore, in Zhongyuan, the expression ‘You are my Zhang Liang' was the highest praise one could give to a strategist.

‘You ignorant fucks, just you wait and see.'

And beyond the closed door, hiding under the eaves, Wang Wu, who had overheard the conversation, gritted his teeth.

It was fortunate that he had eavesdropped on what was being said, otherwise, he would have been handed over to the Jin family, not knowing anything, like a discarded tail.

This was why it was said that one should always be careful, as ‘birds hear the words spoken in the day, and rats hear the words spoken at night'.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Now that the scoundrels' interrogation was over, the Jin Family Head's complexion was as pale as a sheet.

What in the world am I seeing?

How, in the world, how. I have never seen such a terrible sight in over fifty years.

I thought my Cheonhwageom was a decent and well-mannered child, but how could this be.

The Jin Family Head couldn't continue his words, his lips merely twitching at the gruesome and horrific acts.

At this, Qing smiled bashfully.

It was a truly lovely smile, but as a senior of the Orthodox Faction, there were words he had to say.

"Ahem, Cheonhwageom. Tea should be hot. How can you drink tea cold?"

"Ah. But cold tea has its own charm, you know?"

"Cold tea is not tea. One should not make tea cold."

Although there was such a thing as iced tea, strictly speaking, it was not made with tea.

Only fake teas made by infusing fruit preserves, fruits, flowers, or roasted grains could be consumed cold.

Real tea made from infusing actual tea leaves was not meant to be drunk cold.

"Ehh, it's really good though."

"Ahem."

Even the gentle Jin Family Head couldn't help but turn his head away.

To think that such a perfect person had this terrible quirk.

No, perhaps it was necessary for such an outstanding Divine Dragon to have such a terrible flaw!

How could the heavens bestow such a wonderful child with such a dreadful taste!

The Jin Family Head lamented, cursing the heavens.

Regardless, Qing asked.

"So, are you going to strike when the Wulin Alliance's support troops arrive?"

"Hmm. Unfortunately, that won't be possible."

Jin Jaggang shook his head.

"But those bastards killed innocent people and blamed it on an unfortunate curse."

The Jin Family Head wore a bitter smile at this.

"We knew it was the scoundrels' doing from the start. Even if a witness has come forward now, it wouldn't change anything. At most, they'll just cut their tails, saying they didn't order such a thing."

The Jin Family Head explained it to Qing.

It was exactly as had been discussed in the Killing Moon Sect's leader's room, so it was clear that the heads of great families were well-versed in such political strategies.

"Then, are we just going to let this go? Those bastards?"

Jin Jaggang looked at Qing, who was fuming, with a warm and gentle gaze.

It was truly gracious and grateful that she was getting angry on their behalf.

He wished he could make her his daughter-in-law, but honestly, none of his sons were good enough for her.

It was also impossible to adopt the disciple that Senior Yeogwanggyeon cherished like a daughter.

"Now they won't be able to interfere with the reconstruction work anymore, so the Jin Clan will eventually regain its former glory. Is it not said that a gentleman's revenge is never late, no matter how long it takes? When that time comes, I will personally take the lead and grind those bastards to dust."

Qing recalled the interrogation of those bastards.

How could those of the Unorthodox Faction have any sense of loyalty? There was none whatsoever.

They confessed everything from the start, and what followed was merely the Jin family's cathartic release under the pretext of confirming the truth.

Hmm. That was actually quite fun.

I didn't think they would be so skilled at that, those of the Jin family.

But Qing was still dissatisfied.

The Jin Family Head smiled at her expression.

How dazzling is the vigor of youth to an old man's eyes.

"The Wulin Alliance's support troops might come to attack, but if they do, the warriors of the Murim Alliance will be harmed, will they not? I cannot force the young talents of the Murim Alliance to shed blood for the sake of the Jin family's vengeance."

It was truly an admirable statement.

Those bastards were impressive when they were grinding people with their bare hands, but realistically, if a war were to break out, there would inevitably be people getting hurt and dying.

But what was Qing like?

When it came to tormenting evil people, she was the most persistent and vicious villainess in the world.

"Clan Lord. So, we are not attacking. But I have an idea……"