\chapter{On the Plains and Hills, One Food and Two Hammers (1)}

In front of the government office, the disciples of Guilin and Zhangshan formed a line and beheaded the unorthodox martial artists as they emerged. Some might criticize this as cowardly.

However, the official stance of Guilin and Zhangshan is as follows.

We went there with the intention of righteously demanding the price of blood.

But what could we do when they came out one by one instead of all at once?

Or were we supposed to wait for the enemies to gather and form their ranks while trying to avenge our disciples?

That's not righteousness, that's what an utter fool would do.

Or perhaps, you might ask about the suspicious collusion with the government.

But again, the official stance is this.

Don't you know that the government and martial world should not interfere with each other?

The government must have had their reasons for separating them and not letting them out all at once.

They might not have wanted those bastards who caused trouble to gather together.

Or do you think mere martial arts instructors have the power to manipulate the government?

The fact that Gang Suyang, the head of the Guilin Sword School, had received an imperial decree from His Highness, the Prince of Suxi, was known only to a very few. And in truth, the Guilin Sword School had done nothing behind the scenes.

If the Prince wishes to bestow his grace, we commoners can only be grateful.

Thus, in recent days, the number of unorthodox businesses in Guangxi Province began to decline rapidly.

The most prominent orthodox sects in each city of Guangxi Province suddenly went wild, crying out, ‘Now is the time! The time for business expansion!' and launched aggressive campaigns.

After seeing the combat unit of the Four Links Gang get utterly destroyed, there was no unorthodox faction that was unaware of the fact that the Wulin Alliance's combat unit was on its way to provide support.

Moreover, even the officials who had been bribed so much had changed their faces and turned strict. At least, the ones who were somewhat emotionally close (or had their weaknesses caught) gave them a heads-up.

That the higher-ups, the real higher-ups, were trying to support the Orthodox Faction.

Now was the time to lie low and avoid the storm.

Or take this opportunity to stop being unorthodox and shift to the ambiguous area between orthodox and unorthodox.

With the atmosphere like this, in early February, when Qing announced that she was going to visit the Guangdong Jin Clan, Gang Suyang nodded readily, though with a somewhat wistful expression.

"Even though we haven't properly shown our gratitude to our benefactor, you are leaving already?"

"Hey, being treated as a VIP is only special for a day or two. If this goes on, I'll really start to take it for granted. I might even start pointing fingers and causing a scene, saying, ‘How dare you treat the Heavenly Blossom Sword like this?'"

Qing's carefree nature was well known to Gang Suyang, who was almost like a beggar. What should he even call it? Anyway.

He just chuckled and replied, "You speak such pretty words."

"Sect Leader! Lady Xiamen! I have something to-!"

"No."

The head disciple, Do Daljeon, cut off Unaram's words.

"Gasp! But the Junior Sister hasn't even-!"

"Isn't it that you want to follow the Heavenly Blossom Sword?"

"Indeed! You read your disciple's mind! How can you understand so clearly!"

"Haaa. If it were any other time, perhaps. But the unorthodox bastards are looking for any excuse to cause trouble. At a time like this, for a Guilin disciple, that too the Great Senior Sister, to enter Guangdong is not a good idea."

"Yes……."

Unaram's shoulders slumped.

"Senior Sister! Next time! Definitely! Definitely! Definitely again!"

Cutting off Unaram's words, Do Daljeon bowed deeply.

"Young Lady Ximen. We have been greatly indebted to you. As soon as the Alliance's support unit arrives, we will send them to the Guangdong Jin Clan. Although the Jin Clan is not currently facing any physical threats, the schemes of the unorthodox bastards can be quite wicked, so please take care."

Qing stopped by the Guilin Sword School's finest guest room.

It was for a farewell.

"Hmm? You're leaving?"

"I've had my fill of Guangxi cuisine, so I'm off to try Guangdong's. I heard Guangdong and Hangzhou are the closest to having the best cuisine under the heavens?"

The five great cuisines of Zhongyuan were divided by regional characteristics, which was a bit different from simply being about gastronomy.

When it comes to the four great cuisines of Zhongyuan, Guangdong and Hangzhou are mentioned first.

Even in the souls of the people of Zhongyuan who insist their region is the best, when excluding their hometown's special score and grading honestly, they would choose one of these two as the most delicious regional cuisine.

"Aigoo, Young Lady. Why not spend some quality time together? Where are you going?"

"What, did I move to Namneung? Jayu has to go home eventually, you know."

"Ahem."

Jayu could sense a feeling of wistfulness.

He knew that Qing was someone who was very nonchalant about meetings and partings, but he thought she could have at least told him in advance.

"Well then, see you later."

"See you later."

As soon as she finished greeting him, someone rushed to her side.

"Aigoooo, if you leave now, when will I ever see your brilliant visage again? T-That, although it's a small token, I hope it will be of some help on your journey-"

But before Qing could even open the box, she was dragged away by Lady Chang.

"Where does this motherfucker keep finding gold and silver to bribe people with?"

"I just found it on the road, so you don't have to worry about iiiiiit."

The voice of the katydid gradually faded away.

When Qing opened the box, lo and behold.

It contained a hairpin adorned with seven jewels and coral, creating a rainbow of colors.

Even if one had gold and silver, it was a luxury item that was hard to obtain.

Seriously, where does he keep finding these things?

Could it be that there's something similar to a thief or a similar profession in Zhongyuan who goes around picking things up from other people's houses?

Qing snorted lightly.

Honestly, that was highly unlikely.

It must be Jayu who gave it to him to give to her.

He was probably too embarrassed to hand it over himself.

"My Teddy Bear. Jagi, see you later."

"I don't think we'll need to see each other again."

"Nanzhou isn't far from the Divine Maiden Sect, you know? I'll report to the elders of my sect first and then come back to you. My love."

"I'm not your love."

Na Yanggyeol's protection of Qing wasn't just about that.

Na Yanggyeol was the very person who was harassed by the unorthodox martial artists.

Although classified as White Path, the Heavenly Blossom Hall was not officially affiliated with the Wulin Alliance.

Therefore, for her own and her sect's honor, she had to participate in the battle.

Otherwise, it would seem as if they had unilaterally received help from the Wulin Alliance.

In the same vein, it was a bit difficult for her to follow Qing to Guangdong.

Of course, the fact that she still insisted on protecting Qing and even brought a special detachment was quite impressive, or perhaps fearless.

Considering that she volunteered to stick around without knowing about the Royal Household's Masters, one could give her some credit for her love that defied even the fear of death.

"Well then, see you later."

Na Yanggyeol kissed her own lips and blew.

Qing responded by flicking her hand as if shooing away a fly.

And with that, the farewells were over.

"Young Lady Ximen, be careful!"

"Do visit again next time!"

"We must have another bout to determine the best drinker in Guangxi!"

After waving to the crowd that had come to see her off, Qing turned around without any regrets and kicked off the ground.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Guangdong Jin Clan.

This clan, which was not one of the Five Noble Clans but was among the Ten Great Clans of Zhongyuan, was, in terms of fame, not inferior to the Five Noble Clans.

This was because of the famous Tai Chi.

The founder of Tai Chi, Jin, did not withhold his teachings of Tai Chi from anyone who knocked on the doors of the Jin Clan.

Therefore, the founder of the Wudang Sect, Zhang Sanfeng, gained great enlightenment from the Jin Clan's Tai Chi and created the Wudang Sect's exclusive Zhang Clan Tai Chi and Tai Chi Sword.

Of course, Jin did not pass on the entire essence of Tai Chi.

The Tai Chi that was taught was closer to a health-promoting Daoist exercise rather than a practical martial art.

It was a mystical exercise that enhanced the body's potential, increased flexibility and strength, and imbued the body with Qi through its dynamic effects.

Of course, it had minimal effects, requiring at least ten years of consistent practice to see significant results.

However, due to its widespread popularity, commoners practiced it every morning and evening for their health.

So the Guangdong Jin Clan?

Ah, the Jin Clan of the Jin Clan Tai Chi?

Thus, it was a famous household known to everyone under the heavens.

But if it was such a famous clan known throughout the world, why wasn't it included among the Five Noble Clans?

This was due to the limitations of martial artists.

Regarding the limitations of an individual martial artist, those foolish apes, who didn't even know how to use tools, would uniformly bring up Shaolin or the Martial Great Emperor.

Didn't they rise to the top of the world through martial arts?

This could be proven to be a severe fallacy scientifically, logically, philosophically, and even mathematically.

Even if there were Masters who spoke like this, there were very few Masters of martial arts to begin with. Let's say they somehow overcame life and death.

Between Formless Fist and Formless Sword, Mind Fist and Mind Sword, there would be no need to ask which one would hurt more.

Did they have to cut off their arms to use Igi어 Fist?

However, the true weakness of a martial artist was-

That they suffered losses when clashing their bare body against their opponent's weapon-

That they couldn't clash weapons and had to evade, so they couldn't counterattack-

That their reach was too short, so they had to evade until they were exhausted and eventually collapsed on their own-

None of these.

It was the fact that they were incompetent alone, but even more incompetent when gathered together.

The difference was significant between a martial artist versus a swordsman and martial artists versus swordsmen.

It was one thing to be able to win in a one-on-one fight by adjusting the distance well, dodging attacks well, sticking close, and striking well.

However, group battles revealed the true essence of martial artists.

When they gathered, they interfered with each other's evasion, getting hit by swords.

And if they dispersed?

Originally, in group fights, dispersing meant death.

Therefore, regardless of the martial prowess of individual Masters from the Guangdong Jin Clan, their combat unit was hard to evaluate highly.

Moreover, when combined with the Tai Chi footwork that drew large changes from left to right, it was quite a mess.

Rather, despite these critical weaknesses, the fact that they were included in the Ten Great Clans was a testament to the benefits of their fame.

However, even that was not to last much longer.

When the Jin Clan members returned from the Wulin competition, all that remained were the decaying servants of the manor.

If a house is not inhabited by people, it rapidly loses its vitality.

It would have been fortunate if no one lived there, but when dead bodies were left lying around, the damage was even greater.

Since it was entangled with the Blood Cult, even petty thieves avoided entering, and the abandoned manor was practically in ruins.

But the Jin Clan did not collapse.

Since the direct line had made a rare trip to Zhongyuan for a major event, the deceased were regrettable, but they believed they could overcome this.

They would refurbish the declining manor, and even if the clan took on more of the character of a martial arts school, they would accept many disciples and regain their former glory.

Then the Four Links Gang intervened.

Even if they were unorthodox, they could not invade the Jin Clan's manor, which had suffered at the hands of the Blood Cult.

It wasn't out of the goodness of their hearts or any sense of morality, but because the orthodox martial world would never stand for it.

So the unorthodox approached from a different direction.

It began with the workers mobilized for the manor's reconstruction being found dead one by one.

And so it went on for a day. Two days. Three days…….

The workers continued to die, and eventually, when the reconstruction work was halted, the incidents ceased as if they had never happened.

But when the reconstruction work resumed, the workers started dying again as if on cue.

No matter how much money they received, not many were willing to risk their lives for it.

The Jin Clan, with its income cut off, couldn't afford to offer enough to make someone risk their life for the reconstruction work.

So what could they do?

The reconstruction work was halted.

The Jin Clan's manor remained half in ruins.

Who would want to become a disciple of a martial arts school that was half in ruins?

Of course, due to the fame of the Jin Clan Tai Chi, there were those who wanted to join.

However, the unorthodox factions waited for this moment and simultaneously began recruiting disciples, offering generous incentives like ‘Join now and get one plus one, Divine Arts plus Elixirs for free'.

They couldn't reconstruct the manor.

They couldn't recruit new manpower.

Despite occupying the best spot in the middle of Guangzhou, it was in a state not much better than a haunted house.

People were gossiping, saying that the Jin Clan had fallen, which was not far from the truth.

In the past, commoners wouldn't dare to even casually utter the Jin Clan's name.

Thus, the once-prominent Jin Clan's reputation declined.

The gold-painted signboard was now tilted.

And everyone was gossiping about such things.

Now that the Jin Clan had become a laughingstock…

A woman was traversing Guangdong. 