\chapter{On the Plains and Hills, One Food and Two Hammers (10)}

Qing was someone who always showed a sincere heart and a noticeable increase in intelligence when it came to dealing with bad guys.

However, her origins should have spoken for themselves.

Qing was someone who had lived and grown up in the modern era. In a society where there were no life-or-death feuds or vendettas that required killing, she had no history of plotting schemes.

So, even when it came to Qing's schemes, they were not particularly sophisticated.

The gods have granted me three more bottles of poison!

The naive snake grandfather had gifted her three bottles of deadly poison.

Moreover, it was a pure gift of goodwill, without any coercion or trickery.

How could Qing's schemes be anything but simplistic?

She planned to sneak in at night and sprinkle poison everywhere.

Since he couldn't let a guest do such dangerous work alone, Clan Leader Jin decided to accompany her.

If the Salwol Gate ended up with a series of funerals, everyone in Guangzhou would think that the Salwol Gate had done something to deserve it.

In Jin Clan Leader's opinion, that wasn't a bad outcome.

Once the rumor spread, the Salwol Gate would have to lie low, which would be a welcome development for the Jin family, who needed a lot of time.

If the poisoning was fatal, they could even consider wiping them out entirely.

Or, if they could eliminate the leader or his close aides, the Salwol Gate might self-destruct due to internal fighting, given the nature of Unorthodox Factions.

But what was this?

"The Geumjeok Gang is ruined?"

Suddenly, the Geumjeok Gang was said to have collapsed overnight.

"Tell me more, in detail."

"I do not know. I heard that when the fire brigade rushed over after seeing flames rise at dawn, it was already a field of corpses. They fled back in terror. There are widespread rumors throughout Guangzhou that a curse has been cast and divine punishment has been brought down."

"Hmm."

Jin Clan Leader rubbed his chin.

Could it be the work of that child, Cheonhwa Sword?

But how?

Thus, Jin Clan Leader headed to the guest quarters.

Of course, Qing, who had established her own hall, was not staying in the guest quarters, but was preparing for the Second Jin Clan Restoration Conference.

As Qing was hanging words on a string, she saw Jin Clan Leader and ran over to greet him.

"Oh! Clan Leader, you've come?"

How can she smile so brightly?

Seeing her like this, Jin Jagang was filled with a truly joyful heart.

Come to think of it, his own children had never greeted him so warmly. They said that raising children was all for naught, but why was someone else's daughter greeting someone else's father so warmly?

If only Jin Seol was half as warm as her.

Today, Qing accumulated another point of an elder's affection.

"Have you heard the news, Cheonhwa Sword? The Geumjeok Gang is ruined- Hmm. Yes. You haven't heard."

"Huh?"

Qing's expression was incredibly honest.

Jin Jagang, who was about to ask if the destruction of the Geumjeok Gang was Cheonhwa Sword's doing, immediately came to a conclusion.

This had nothing to do with this child.

"The Geumjeok Gang is ruined?"

"There was a bloodbath last night. It's said that the manor was filled with corpses. Except for those who were staying outside, they were all annihilated."

The way he spoke was soft and gentle like a professor's, but the content was quite brutal.

"Hmm. Anyway, that's good, isn't it?"

"It is, but it's also concerning."

Jin Jagang also agreed that it was good that they were ruined.

The Geumjeok Gang was a coalition of loan sharks.

Loan sharks were basically what modern people would call private lenders or loan sharks, and this was a gang formed by the moneylenders of Guangzhou.

Wasn't it common for those who squeezed people dry to be so tyrannical once they gained power?

At this, Qing made a carefree remark.

"Well, isn't it a good thing? It's natural for those who've made many enemies to die, isn't it? If the ones we need to get rid of are gone, that's good. Maybe they were reckless and messed with the wrong person, right?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

All of Guangzhou was abuzz with talk of the Jin Clan's curse.

Didn't the Earth-Shaking Divine Maiden say so?

She had broken the curse of the Jin Clan herself, so the curse would return to its owner with a vengeance.

And the perfectly fine Geumjeok Gang was suddenly wiped out overnight.

It's the curse, it must be the curse! The curse has returned!

Since a grand betting pool had already been established in Guangzhou, it was a moment where the joy and sorrow of countless ordinary people intersected.

Nevertheless, there were two opinions that both those who won and lost money agreed upon.

The Geumjeok Gang bastards deserved to die.

And, the Earth-Shaking Divine Maiden was incredibly powerful and accurate.

However, there was one bold child who challenged these opinions.

"No! It's not a curse! It was all done by the Great Hero!"

At this, people who were whispering amongst themselves became interested in this new approach to the incident.

"A Great Hero, you say? What do you mean?"

Then, the girl, with a somewhat dreamy look on her face, clasped her hands together and began to tell the story of the previous night.

In Wulin, one should always be wary of passersby.

For example, if a dining table was overturned as collateral damage during a fight in an inn, one might get punched by the owner of the table who was enraged by such a disturbance.

Or, it wasn't uncommon for a prey that was almost caught to be snatched away by a passerby, or even worse, for one to become the hunted instead.

But there were so many passersby.

Everyone knew the danger of passersby, but if they were always cautious, they wouldn't be able to do anything but quietly breathe.

So the Geumjeok Gang warriors had to work to make a living.

If all they did was quietly breathe, what would they eat and how would they live?

So, they were just carrying out their duties of collecting from a delinquent debtor.

However, it was admittedly a bit of a nasty job.

"P-Please, no! No!"

"What do you mean, no? So you were planning to rip off the Geumjeok Gang?"

"I'll do whatever I can to gather the money, please! Just not my daughter, please!"

"Heh. We've been more than patient already. It's not that bad, you know? Since you can't pay the money, we're helping you find a way to pay. It's all thanks to this old man's mercy, introducing you to a good job."

"I'd rather, ugh."

The woman was kicked and rolled on the ground.

"Mom!"

A young child tried to run to her mother, but her wrist was caught, and she could only struggle with her arm held back.

"Let, let go! You bad man!"

A Geumjeok Gang warrior spat on the ground.

"What a nag this old hag is. Do old hags even sell for anything? Will you even earn a few silvers if you sell your body? Will you even be able to pay the interest if you spend your whole life spreading your legs? Look here, isn't it good to have children? Originally, daughters are meant to be sold off to a family. You were all over each other when you borrowed the money, saying you'd do anything, but now that it's time to pay up, you're all making a fuss. Am I the bad guy!? Am I the bad guy?!"

The Geumjeok Gang warrior shouted roughly.

It sounded like a question, but it wasn't really a question.

However, a completely unexpected answer came back.

"You seem like a bad guy. Hey. How much does this woman owe you that you're taking her child away right in front of her?"

The Geumjeok Gang warrior turned his head to look at the speaker.

He looked to be in his mid-twenties.

He had a smooth face, but his eye patch took away from his appearance. He was a one-eyed young man.

The Geumjeok Gang warrior flinched and hunched his shoulders, carefully examining the young man from top to bottom.

He wasn't carrying any weapons, his hands were smooth as if they hadn't touched water, and his clothes didn't have any patterns indicating his affiliation.

The Geumjeok Gang warrior's shoulders relaxed.

"What's this now? Do you not know that it's not fun to meddle in other people's affairs? Why? You gonna pay it back for her or something?"

"I can't say it's impossible."

"Ah. Is that so? It's one hundred Gold."

At this, the passing young man looked down at the fallen woman.

"How much did you originally borrow?"

"Ten silver! It was ten silver! And they told us to pay forty Gold!"

The girl, who had been held by the arm by the Geumjeok Gang warrior, shouted sharply.

"Well, if you sell that woman, you'd get one hundred Gold, so if you only take forty, aren't we losing sixty Gold? You have to pay the right price."

"Hoo. That's a miraculous calculation method."

Then the young man smiled brightly.

If it weren't for the eye patch, it would have been a radiant smile that would make women swoon.

"You borrow ten silver and have to pay back one hundred Gold? Did I hear that right? How many times is that? Twelve silver is one Gold, so, um, um. Anyway, aren't you just a bunch of robbers?"

"What, robbers? Do you have any idea who you're talking to? Do you think you'll be safe after insulting our Geumjeok Gang in Guangzhou!"

"Thank you. Thank you. From the bottom of my heart."

It was an unexpected remark.

The young man wasn't insane, so why would he suddenly express his gratitude?

But as unease gradually rose, the guy was just too relaxed.

"What? What are you thankful for?"

"I'm thankful that you're living as villains."

"What's that nonsen, urk."

The Geumjeok Gang warrior was about to ask what that nonsense was when he gasped in shock.

It was because of the shaded, flesh-colored pillars that suddenly rose up and covered his field of vision.

It was the one-eyed young man who had suddenly approached, grabbing his face with his large hand.

At the same time, a sharp pain pricked his shoulder blades and his arms lost all strength, dangling limply.

Only then did he recall the saying of Jianghu, ‘Beware of passersby!'

"Y-Y-You, Great E-Ex, s-spare……."

"Well. Hey, there, little one. These loan sharks wouldn't just not collect interest, would they? How much interest did you pay? It must be more than the principal by now."

As soon as she was released, the child, who ran to hug her mother, shouted boldly.

"Together, it's over one Gold!"

"That's quite wicked, isn't it? So, do you want this guy dead? If you want, I'll kill him."

At this, the girl's eyes widened.

Then, she tightly hugged her moaning mother, and a fierce glint appeared in her eyes.

"Bastard! Kill him! Kill him!"

"‘Kill him' is a bit rude to say to an elder."

The young man lifted the Geumjeok Gang warrior by the scruff of his neck with his other hand.

"Keo, keoheok, keook."

If Qing had seen this, she would have advised him to grab the neck a bit tighter to completely block the airway, as she could hear his breath leaking.

Of course, most people weren't Qing, so instead of interfering, they just kept quiet, awed by the prowess of this expert.

Then the one-eyed young man looked around at the crowd.

"What do you all think? Is this guy someone who deserves to die? Is he a useless piece of trash that would be a waste to even compost?"

The warrior, dangling in the air, desperately scanned the crowd with his eyes.

However…

"Kill him! That bastard has sold off more than a handful of people!"

"He was a rotten egg ever since he was a kid! He was a gambler who bankrupted his family! He killed his own parents when they collapsed from anger!"

In the end, grudges returned as grudges.

The Geumjeok Gang warrior's eyes were filled with despair.

If he had known this would happen, he would have lived a better life.

However, regret right before death was just regret, not repentance.

The one-eyed young man's expression was one of great satisfaction.

And the next morning, the Geumjeok Gang was ruined.

The girl's argument was met with skepticism.

"So, that one-eyed young man destroyed the Geumjeok Gang? Come on, is he some kind of Reincarnated Master? I've never even heard of a one-eyed young Master."

At this, the girl yelled.

"He's not one-eyed! Don't be rude to the Great Hero! He has a patch! A patch, you know!?" 