\chapter{On the Plains and Hills, One Food and Two Hammers (3)}

She had spoken so boldly, but alas.

Qing felt a sense of awkwardness.

She had learned carpentry in Naknyeong.

And in Naknyeong, they built houses with wood.

But when she tried to repair Jin Ga-jang, ah, why are there only bricks in sight…….

Of course, it wouldn't all be built with bricks.

The frame would be made of wood, and the bricks would fill in, that was obvious.

But were these bricks just stacked? What were they attached with?

Are there wooden walls on the inside?

I'll only know if I dismantle a house…….

If she wanted to build in the style of Henan Province, Qing had already participated in dismantling several submerged houses and rebuilding them from the foundation.

"Lord, may I dismantle a house?"

"Of course. Mmm. Try dismantling the lower west wing. That one is severely damaged."

Jin Ja-gang, the head of the Jin Clan, readily agreed.

In truth, he had doubts about Qing's carpentry skills.

After all, she was a young talent who had significantly shortened the record for the youngest Transcendent Realm Master in Wulin.

He was certain that she had spent day and night diligently practicing martial arts, barely sleeping and eating in a hurry.

(In reality, she slept a lot and ate a lot in a hurry while freeloading her martial arts, but…)

So, even if she knew carpentry, he could only think that it was a skill she had picked up by watching over someone's shoulder when she was young.

It was only natural to think so.

She was only twenty-one this year, not enough time in her life to master another skill.

Perhaps if it was a sixty or seventy-year-old Master who said they could do carpentry work when they were bored, then maybe.

So, he didn't have high expectations for the reconstruction work.

He was just pleased with the idea of breaking this curse by replicating the same method of revenge.

And what was a curse?

The cause might have been the work of the Unorthodox Faction, but now it had become a real curse.

If the Heavenly Sword could provide even a small opportunity to grasp onto in this quagmire, he would be grateful.

Qing wandered around Jin Ga-jang.

It would be rude for a guest to roam around the manor alone, and people would question the hospitality, but the head of the Jin Clan had asked for understanding due to lack of hands, even bowing his head to a junior (though senior in terms of generation). So it wasn't that big of a deal.

Still, it was a sight that would make others click their tongues.

But Qing was someone who didn't care at all about such etiquette, and it was more awkward to have someone tagging along when the clan was so busy.

So, she was wandering the manor to find the lower west wing to dismantle, actually physically dismantle it.

The Jin Clan, unable to hire even new servants due to being a cursed manor, let alone construction workers.

There was no sign of people, the surroundings were quiet, and a subtle, unpleasant smell of decay lingered, making it truly eerie.

Despite the clear and bright weather, the low saturation made it feel like a pale, gloomy, and shadowy scene.

This is probably why they were reluctant to accept help, thinking it was embarrassing to show this to guests.

But still, face is one thing, and the manor is in this state. Shouldn't they have gotten help and done something?

Even now, the current members were struggling to take care of the business, leaving a guest alone to wander around the manor.

At least Qing had visited due to the rumors of difficulty, but if it weren't for that, how long were they planning to slowly decline in this cursed manor?

The lord seemed like a gentle and kind person, but was he a bit slow on the uptake?

They should have at least torn down the buildings where the stench leaks even when closed.

It was when Qing was having such irreverent thoughts.

Suddenly, a strange sound reached Qing's superhuman hearing.

Kkeu-heuk, heuk, kkeu-heuk. The sound of muffled sobs.

"Ooh."

Qing rubbed her forearm.

What is it? A ghost? Does it really exist?

There are Daoist temples, Qi, and even Buddha's Palm that manifests a Buddha, so why not ghosts?

Can the Buddha's Palm, with its exorcising energy, also beat up ghosts?

Qing cautiously approached the sound.

Why is it that when watching horror stories, people wonder why the characters would open the door and enter a haunted place despite feeling uneasy and scared, trembling and swallowing nervously?

But when faced with such a situation, she understood.

It was much scarier to run away without confirming what it was, whether it really existed or not.

So, following the sound, Qing gently opened the door of a building that smelled particularly bad.

Creak.

Since the surroundings were quiet, the sound of the door opening was especially grating.

And inside the dim building, in the distance, the back of a boy sitting alone.

Hmm. It's a person. Well. Of course, it is.

"Who's there?"

"Ah, Young Lady Ximen. Sniff, what brings you here?"

"Ah, you. Hwacheon, was it?"

Jin Hwacheon. She heard he was the something-th son of the Jin family, but with fourteen or fifteen children in total, she couldn't remember all their names.

"What are you doing here? Why are you crying?"

"I wasn't crying."

Jin Hwacheon said this with swollen eyes.

"Your eyes are red."

"Y-You must have seen wrong."

Jin Hwacheon said this and then wiped his eyes with his sleeve.

"Sure. If you say so."

"I wasn't crying."

"Yeah, yeah. I didn't see anything."

At this, Jin Hwacheon's youthful face twitched.

But Qing just raised the corners of her mouth.

What can you do even if you twitch?

"What are you doing here?"

"Me? I was looking for the lower west wing. It all looks the same, so I don't know where it is. You, if you're free, want to guide me?"

At this, Jin Hwacheon made an incredulous expression.

"This is the lower west wing."

"Ah. It is? I arrived correctly? Why am I so good at finding my way? The path I walk is the way. Kyaaa."

Jin Hwacheon's expression changed.

Qing realized that a person's expression could change from incredulous to even more incredulous.

"So, what brings you here?"

"Ah. I'm going to do some construction, but I don't know how things are in Guangdong, so I was going to dismantle a house and examine it slowly."

"Dismantle, as in, take apart the house……?"

"Yeah."

At this, Jin Hwacheon's expression darkened.

"You can't."

"Huh? What?"

"You can't. You shouldn't. You can't do that."

"Eh. I already got the Clan Lord's permission, though?"

"But."

"Give it up, kid. No one can stop my destruction. I will demolish everything and rebuild. Destruction is the mother of creation. Have you ever seen a phoenix rising from ashes?"

Qing just spouted nonsense.

It was meant to sound ridiculous.

"You can't!"

Jin Hwacheon shouted back.

"If you demolish the house, then, sniff, then."

And then tears streamed down, his nostrils flared, heeeeuuuup, he took a deep breath.

Ah. He's going to cry.

Qing realized it too late.

K-Heung-heong, the boy burst into tears.

It took quite some time for the boy to calm down.

"This was Hyewoon's house, but if it's demolished, I won't be able to remember again. I couldn't even say goodbye."

From what she heard, it seemed to be the house of his closest friend.

Since the children of a clan wouldn't play outside the clan, the friends they grew up with, playing and fighting, were ultimately their relatives from collateral lines.

"Hmm."

Qing reflected deeply.

Of course, not on the fact that she made a boy cry.

Why would a man cry?

Crying is a woman's exclusive special move, so men shouldn't cry.

It was a reflection on her own lack of understanding for not realizing why the family was in such a state and doing nothing.

The Jin Clan was a noble clan.

Since they were a collection of people with the surname Jin, even the collateral lines were ultimately close, like fourth or fifth cousins, and even the distant collateral lines grew up together from a young age like neighbors and friends.

And they were family.

It would have taken about two months to slowly travel from Henan to Guangdong, and if they discovered this tragedy around mid-August, it would have been just over three months since the forty-ninth day memorial, the last of Zhongyuan' ancestral rites.

It was too short a time to forget the loss of family.

Moreover, it wasn't a gradual farewell with time to prepare the heart due to illness or old age, but a tragic and unjust disaster caused by the Blood Cult's surprise attack.

Moreover, when the Jin Clan members found the bodies, they must have been in a terrible state, closer to liquid than solid, left in the humid and hot Guangdong weather of midsummer.

And to think they were happily playing at the Martial Arts Tournament while the bodies were rotting away like that.

To demolish it, no less.

To the people of the Jin Clan, each house was like a memorial.

Though she could only guess, Qing had no way of truly knowing how they felt.

But if that was the case, shouldn't they have been doing something instead of just being beaten?

Just in time, there were plenty of bastards in the city trying to somehow take down this family, which was grieving the tragedy.

And those sons of bitches were doing whatever they could, even brutally harming innocent workers.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Dressed in attire befitting the title of a Soil Fairy, Qing headed to the city of Guangzhou.

It was truly the appearance of a peculiar person, attracting the attention of everyone in the entire city.

A colorful shaman's staff adorned with five-colored cloth strips, a straw rope around her waist tied with dozens of geogeo (clams) that scattered a rainbow-like glow, and a clattering sound of shells colliding with each step.

On top of that, she wore a bamboo hat with talismans written in cinnabar on yellow paper, not only stuck all over but also hanging long on the left, right, and back, reaching her shoulders and back.

With only her face covered by a thick veil, it truly looked like a divine shaman had appeared in the marketplace.

But if she's a shaman, that doesn't make her a carpenter.

In fact, that was why she came out.

She needed some special tool that looked like it was for carpentry so that everyone would immediately think, ‘Ah, the Soil Fairy has arrived'.

A saw? I can just use Sword Force. A plane? I can just use Sword Force. A chisel? An awl? Sword Force is invincible.

But I should have a hammer.

The Moonlight Sword was a five-geun heavy sword, but its well-balanced center of gravity made it a bit ambiguous to use as a hammer.

Thus, Qing, dressed in that outfit, stepped into the blacksmiths' district.

Amidst the rhythmic clanging of iron and the thick smell of burning coal, Qing strolled around, pretending to examine the iron tools displayed on the stalls.

In truth, she hadn't done blacksmithing, so she didn't know much just by looking at the exterior.

For now, it was a ploy to make people think of her as the Soil Fairy.

Then, Qing approached the largest blacksmith's stall and casually asked in a blunt tone.

It was her attempt at imitating Wudang.

"Hey, I'm looking for a jangchoo (sledgehammer)."

"What weight are you looking for?"

"Fifteen geun."

"Eigh, what? There's no such thing."

"That's strange. They use it in Henan."

Of course, they don't.

If someone were to swing a fifteen-geun hammer, they would surely collapse from exhaustion within a quarter of an hour.

Moreover, a hammer wasn't just about being heavy. If it was that heavy, it would be closer to breaking materials than hammering.

Even when driving a stake, it would crack from the inside rather than being driven in.

"Then what is the biggest hammer in Guangdong?"

"Eight geun. Seriously, they forge fifteen-geun hammers in Henan? What in the world do they use that for?"

"Where else would you use a hammer but in construction? Are you trying to smash some random person's head?"

"Hah. Even with an eight-geun hammer, people collapse from exhaustion within a quarter of an hour. Only ten or so sledgehammers are found in the entire street. What's this about a fifteen-geun sledgehammer?"

"This lady worships Xiang Yu as her divine deity. Fifteen geun is light, and it's a great regret that the twenty-geun hammer I used to use broke."

"Twenty geun? Hah, then you must wield an eight-geun hammer like chopsticks, right? How about showing us that spectacular hammering?"

"Tsk. I don't mind showing you, but you doubted my words, so you'll suffer greatly. Are you still okay with that?"

"Hmph. You shamans are all the same, always trying to trick people with such words. Get lost, you quack who looks like a quack."

The blacksmith's words, which had been snorting, suddenly stopped.

It was because a long, slender, and delicate hand picked up the eight-geun hammer with ease.

And then, it was twirled up and down as if it were a mere twig.

"The weight doesn't feel right."

Then, she casually tossed aside the iron awl and kept hitting it up with the hammerhead.

A hammer's weight was measured differently from other tools, with eight geun referring to the weight of the hammerhead alone.

With one hand holding the end of a four-cheok hammer handle, she kept hitting an elongated, heavy iron awl up to half a zhang.

The blacksmith's mouth fell open, and his gaze followed the iron awl flying up into the sky and falling back down.

Clang clang clang, the sound of the iron awl being hit.

Because of Qing's self-proclaimed divine shaman attire, which already attracted attention, blacksmiths and customers alike in the blacksmiths' district were captivated by the spectacle, watching with their souls entranced. 