\chapter{On the Plains and Hills, One Food and Two Hammers (5)}

Today, there was no need for patrol, so they were told to gather at the eastern Jin Fortress by 10 AM.

By the time Jinseol set foot in Jin Fortress, no, even before she set foot inside, she could hear the clamor of her family's voices.

It was a sound she hadn't heard in a very long time.

Without realizing it, a faint smile crept onto Jinseol's face as she quickened her steps.

And so, she arrived in front of Jin Fortress.

A long banner, with one character written on each large cloth, strung together, caught her eye first.

THE FIRST JIN CLAN RECONSTRUCTION COMPETITION.

But more than the content, the majestic calligraphy caught her eye first.

She didn't know much about calligraphy, but she had never seen such a… how should she put it… very organized, powerful, and vigorous, perfectly square characters that were so magnificent.

And then, she was surprised again to see such precious writing on a shabby, worn-out cloth.

What a waste of such valuable calligraphy on such a humble thing!

It was obvious that the writing was worth quite a lot of gold, so why was it wasted there?

"Oh. Young Lady Jin has arrived?"

"Young Lady Ximen? No, what in the world is that getup!?"

Jinseol was doubly surprised before becoming appalled.

The members of the Lily of the Valley Society half-jokingly said that lilies had nothing to show off, so they went around exposing their chests, but in truth, among the female disciples of the Orthodox Wulin, there were none who dressed as well as Jinseol.

In fact, the members of Jinseol's Lily of the Valley Society were a group that had gathered due to their keen interest in clothing.

"I'm the Earth-Moving Fairy. How is it? Do I look like a shaman?"

"What is this strange getup? This is not right! You can't wear something like this! This is completely absurd!"

"Ah. Why not?"

"A woman should not have seven colors on her at once! That's something only children under ten can do! Is Young Lady Ximen a child!? Are you going around dressed in colorful clothes!?"

"Oing? Is that like, a law or something?"

"Decorum! Clothing is also a part of decorum! Goodness! How could you! And it's fluttering so much! No, oh my. KYAAAH! What is this stitching! It's all straight lines! You already have such a large chest, and now this!"

Jinseol was practically spitting fire.

"Um. Calm down."

"How can I be calm!? It's not even clothes, it's just, what should I even call this?"

"Uh……… Shaman's robe?"

"Young Lady Ximen, have you ever seen a shaman? And what is that thing you're wearing on your head? Are you catching bees? Going to collect honey? Why are there so many talismans, tsk."

Jinseol grabbed Qing's veil and pulled it up.

Then, Qing's beauty went, ‘Boop!'. Her beauty went, ‘Pop!'.

Jinseol was momentarily at a loss for words.

It seemed that the saying ‘face is the completion of fashion' was true after all. She was wearing the most unfashionable, worst, and strangest outfit, yet somehow, it looked good on her.

"Hehe."

A bashful smile spread across Qing's face.

That embarrassing smile was a one-line message.

-I really don't know what's wrong at all.

At that, Jinseol let out a deep sigh.

"Haaaaa. Have you been going around like that all this time? I really can't stand it. I'll make you a proper outfit. This is not it. It's really not it."

"It's only a few more days until the Earth-Moving Fairy has to make her appearance. There's no need to go that far."

"Even if it's just one day, it's a no. I'll stay up all night to make one, so that strange outfit… um, but the sewing is meticulously done, which is annoying……"

"Hehe. I've always had a bit of a knack for handicrafts."

"Don't laugh. Hmm. By the way, what's going on here? The First Jin Clan Reconstruction Competition?"

At that, Qing grinned mischievously.

"We're rebuilding the house now. Ah, by the way, Young Lady Jin, do you prefer the Big Dipper or the Arisaema Star?"

Jinseol's expression turned strange.

The Big Dipper versus the Arisaema Star?

The Big Dipper was a large constellation in the northern sky, and Arisaema (天南星) was a flower, and a sinister one at that, containing deadly poison.

Asking her to choose between two completely different things.

What kind of bizarre question was that?

Qing didn't give her time to think.

"Now. You have five seconds to answer. One. Two. Three-"

"Big Dipper, Big Dipper."

"Too bad. Unfortunately, the Big Dipper is already full. Young Lady Jin is Arisaema."

"……Then why did you ask?"

"There were people who were looking forward to it? Congratulations! Team Arisaema, applause!"

At that, some of the clan members who were already there clapped with slightly twisted smiles.

"No, what is going on here?"

"Ah. It's a reconstruction competition. We're splitting into two teams, North and South, to compete based on time, craftsmanship, and artistic points. The North Team is the Big Dipper, the South Team is Arisaema."

"Now, now. Get your armbands. Perfect timing. Young Lady Jin is the team leader."

"Me?"

"It fits perfectly, doesn't it? The Clan Lord is a giant of the Orthodox Wulin, so he's the leader of the Big Dipper Team, and Young Lady Jin is one of the Five Beauties of Murim, so you're the leader of the Arisaema Team."

"Then shouldn't I be Arisaema?"

Arisaema was a poisonous plant, and due to its color and bizarre appearance, it was considered a very ominous flower.

"Eh, let's not worry about the small things. Now then, let's begin the First Jin Clan Reconstruction Competition! Now, applause!"

And then, clap clap clap. A somewhat reluctant applause, as if they were being forced to clap, resounded.

They tore down the bricks, removed the exterior, and even removed the jade stones laid on the floor. In one area, two teams were mixing lime and ash to make mortar.

After tearing up the floor, they found blackened, rotten bloodstains on the wooden structure underneath.

In fact, it was worse than bloodstains, as it was the result of decomposed flesh seeping in.

No wonder the stench of corpses lingered.

Carefully, they sawed through the joints, removed the decaying wood, dug out the rotten soil from the foundation, and laid down new soil.

Although the people of the Jin Clan were martial artists, they were still martial artists.

This meant they were physically superior.

People usually find joy in new experiences, and if their bodies aren't too tired, they enjoy it even more.

And above all, it's even more enjoyable when done together.

"When I went on patrol to Samhapru, you know, they were talking openly now. Like, if you can't manage it, just sell it and leave, why are you sticking around? If it were me, I would have immediately roared, ‘Who dares to speak of the Jin Clan in broad daylight!', but."

"My goodness. Did you really just let that slide?"

"What can you do about commoners who don't know any better? It only makes you look bad if you get angry there."

"Still, the world's morals are really."

Since their schedules were packed with patrols of their respective businesses, they hardly had time to see each other's faces and talk.

So now, they were chattering away while removing bricks, mixing lime, moving wood, and holding things together. It was as if they were making up for lost time with stories only they knew.

As such, their mouths were busier than their hands, and after more than two hours, it was past noon.

Since it was well past lunchtime, everyone was bound to be hungry.

Only then did the women, children, and elderly of the Jin Clan, who couldn't be of much help, bring out simple meals on low tables.

It was a simple meal of multigrain rice, stir-fried vegetables, and dried fish that had been fried and seasoned. They also brought out large bowls filled with yellow wine.

Was this a meal or a drinking party?

The yellow wine was sweet, and after labor, alcohol tasted even sweeter.

People have a habit of becoming strangely carefree when they've ruined their clothes, and already covered in dust and dirt, they didn't care about the dignity of a noble clan and just plopped down on the ground, gulping down the warm yellow wine.

"Kyaaa. Has this always been such a good wine? I never really drank yellow wine."

"It must be because of the weather, right? It's going down so smoothly."

They looked as if they had just finished some autumn military construction project.

Though it seemed more like they were having fun chatting rather than working, they were still martial artists using Inner Qi, so their hands never rested and the progress wasn't bad.

Besides, whenever they found graffiti, they would gather around and speculate about who drew it, reminisce about how that person was, and then slowly return to work. Honestly, if Qing had done it alone, she would have probably gotten more done, though.

"Uncle, is that tasty?"

"Why are you coming to your uncle? Go over there and snatch some from your father."

"Little Brother. How much can a child drink? One should learn how to drink from an adult. I'm too soft on my own children to teach them properly, so I'll have to rely on you this time, Uncle."

And so, a cup of yellow wine reached the youngest member of the family, ten-year-old Jin Chu.

With the adults watching with expectant eyes, the little lady emptied the bowl in one go and wiped her mouth, expressing her opinion.

"It's delicious."

A great tree can be told apart from the time it is a sapling, so perhaps this was the moment a great future drinker was born.

The ten-year-old little lady, her face instantly turning as red as a radish, staggered around, which everyone found amusing, thus laughing and calling out to her, ‘Achu-ya, Achu-ya, come here'.

"Now, now. It's getting chilly, so let's get back to the second half. Let's see. How far have the bricks of the Big Dipper Team gotten? Forty tiers already? Oh. Arisaema Team, ah. Yes, Arisaema, anyway, you need to work harder. At this rate, will you be able to raise it to the ears by the end of the day?"

After playing for nearly half an hour, they started working again.

Since it was a small annex to begin with, it didn't take much effort to tear it down and rebuild the interior and exterior.

Thus, as the sun set, the bricks were almost all stacked up.

Qing was busy hammering the newly attached roof planks.

With a light tap of the eight-geun hammer held just below its head, a nail would disappear neatly in one hit. This was the One-Hit Nail Remover, the very skill that made the carpenters of Guangzhou shudder in awe.

Of course, since everyone else was an amateur when it came to carpentry, they didn't realize how amazing Qing's skill was.

When Qing held out her hand, someone would place a nail in it.

Although not as good as Qing's, their hands were still quite pretty.

Even if the appearance of a woman's hands was a matter of preference, beautiful hands were universally considered to be white, slender, long, and sleek.

Therefore, though Jinseol's hands might not be as perfect as Qing's, one should be grateful that they could even be compared.

Then, at some point, along with the nail, a word was passed.

"Thank you."

"Eh? For what?"

"This event, you planned it all, didn't you? And lunch too. Was it some kind of commoner experience?"

"Eh, it's no big deal."

At that, Jinseol looked at Qing.

Even under the sunset, her skin was clear and her face truly beautiful.

"I should have refused the Wulin Alliance's help. When people are sad and in pain, they should stick together, or else they'll just continue to be sad and in pain. It's really fortunate that Young Lady Ximen came. Really."

Jinseol said this while looking around at the Jin Clan members, still tipsy and chatting under the sunset.

It was a scene that made one's lips loosen without realizing it.

"It's been a while since it's been this lively."

"Then, why don't you send a letter now? The guest rooms can be quickly fixed up."

"Daddy, no."

Jinseol blushed.

So Young Lady Jin still calls the Clan Lord ‘Daddy'.

Qing acquired a piece of meaningless information.

"I'll have to talk to Father about it. Actually, when I realized that the Unorthodox Faction was interfering, I should have asked for support then. Since the situation wasn't good, I kept putting it off because I was embarrassed to show such a state to others. I should have been stronger. How pathetic."

Jinseol bit her pretty lips slightly.

In response, Qing held out her hand instead of answering.

Jinseol hesitated for a moment, then carefully took and held that hand tightly.

Qing's hands were always cold, so other people's touch always felt warm.

Feeling the warmth transmitted to her palm, Qing quietly withdrew her hand and answered.

"I meant to ask for a nail, not your hand…"

The First Jin Clan Reconstruction Competition ended with the victory of the Big Dipper Team.

Anyway, since they finished the work before it got dark, both teams received the same score for speed.

There were no flaws anywhere, so the artistic score was also the same.

There were no safety accidents, so the ‘Safety is Good' score was also the same (although everyone wondered why it was called the ‘Safety is Good' score and not just the safety score).

Thus, what determined the victory was the height of the ears.

In the Guangdong style, there was a unique decoration where the front and back of the roof were built up high with bricks to make them look like pretty ears.

It was a style called Hwog'i(鑊耳), using the characters for ‘pot' and ‘ear', said to resemble a pot or an ear.

Carpenters said that this made houses cooler in the summer, so there must be some great scientific principle behind it.

But Qing didn't want to analyze it scientifically, so she just accepted it as it was.

It's an ancestral tradition passed down.

Not my ancestors, but still, their ancestors.

So yeah. If they say so, then they're probably right.

The Big Dipper Team had stacked their Hwog'i about five tiers higher, so they received a generous bonus to their ‘Spirit to the Sky' score, thus winning.

The poor Jin Fortress ended up with mismatched ears.

There were some controversies about the fairness of the judging, such as ‘What do you mean by that?', ‘Is it only about how high the ears are?', and ‘Was there a special bonus for the Clan Lord or something?'. (Even the usually composed Clan Lord Jin's eyebrows twitched at this.)

However, since it was all for fun, the atmosphere wasn't too serious.

Of course, the latter was just Qing's personal opinion.

The martial artists' desire for competition and victory was underestimated, so it seemed that the Second Jin Clan Reconstruction Competition would inevitably have a donkey's ear, not a king's, but Qing was not aware of this.

The leftover materials after the construction were dumped next to the main gate of the Jin Fortress, and a notice was posted.

\begin{quotation}
	「The wood is contaminated and unusable except for firewood. The bricks are dirty and need to be cleaned before use. The Earth-Moving Fairy has purified them with her divine power. They will be removed after ten days.」
\end{quotation}

This was a common way to dispose of waste materials in Zhongyuan, and it meant the following.

Take it if you want to use it as firewood.

Take the bricks if you want to clean and use them.

Are you skeptical? The Earth-Moving Fairy has already purified them, so they're safe.

If you don't take them, they will be discarded after ten days.

Thus, passing commoners eagerly began to take as much as they could carry.

It was truly a win-win, eco-friendly construction that minimized waste.

And so, news spread throughout Guangzhou.

The Earth-Moving Fairy is said to be quite effective, and it seems she has finally laid her hands on the Jin Clan.

I heard she serves a Xiang Yu, right? I know she has the strength of a Xiang Yu, but isn't she a bit ambiguous when it comes to curses?

And so, they whispered.

They wondered just how long the Earth-Moving Fairy could withstand the curse of the Jin Clan. 