\chapter{On the Plains and Hills, One Food and Two Hammers (11)}

Defeat was painful.

The people of the Jin Clan had sharpened their swords, preparing for the next battle with this experience.

And so, today was the day to repay that humiliation.

The Second Jin Clan Reconstruction Tournament!

Jin Seol and Cheon Namseong had waited for this day.

They had secretly gathered and practiced carrying and stacking bricks, and they had also developed a plausible strategy of minimizing the number of people working on internal structure repairs and concentrating on artistic scores.

Effort does not betray, mostly.

(Sometimes it does.)

And so, the result!

Behold, this large and beautiful work of art!

"Agh, what is this?!"

Qing had a face as if she had eaten a bitter root.

A bitter root was the bark of the Gomu (苦木) tree in Zhongyuan. As the Chinese characters literally implied, it was a bitter tasting tree.

It was so bitter that even flies would run away from it (because insects have taste receptors on their legs), and it wasn't even a food ingredient or a medicinal herb, just a tree.

What would one's expression be after chewing on the most bitter bark in the world?

Qing, with a completely distorted face, gazed at the unique feature of the Guangju architectural style: the ears on the roof.

After Jin Seol's group had been judged the winner last time for stacking the ears a few levels higher, they had clearly set out to build a tower as high as they possibly could.

The form of the ears was like a large circle with a small circle on the left and right (oOo).

If the middle circle was made into a tall, very long ellipse, what form would it become?

"No, didn't you realize something was wrong while stacking this? What is this? Is this an ear? Anyone can see that this is… Agh. What are you going to do about this?"

Qing barely swallowed the ‘dick' that had reached the tip of her tongue.

After all, she couldn't say ‘dick' in front of all the elders, right?

But she could have said it.

Because everyone else participating in the Reconstruction Tournament thought the same.

Hmm, now that it's stacked up so high, doesn't it look a bit… fucked up?

Yeah. It looks like a very angry cock.

The ladies of the Jin Clan looked at the towering phallic structure with a mix of embarrassment and curiosity, while the children couldn't suppress their giggles.

"W-Well, as we were stacking it……"

"As you were stacking it? No, is Miss Jin a child? How could you make a house like this? What would guests think when they see it? I'm sure they'll say something like, ‘My goodness, that guest house is so ugly. What does it mean to give me such an ugly guest house!'"

Qing spat out fire.

It wasn't her house, but she still had the professional pride of a head carpenter who had led the construction.

"Pfft, n-no, that…"

Jin Seol bowed her head deeply.

However, she showed no sign of remorse, causing Qing's eyebrows to twitch.

"Do not be too angry. Hmm. It might be good to change the name of the guest house while we're at it. Mmm. Let's call it Center, Center, yeah, let's call it Center."

The Jin Clan Lord, feeling sorry for his shrinking daughter, tried to lighten the mood with a smile.

But like father, like daughter.

On the opposite side, a magnificent brick tower stood tall, making it look like two massive cannons pointed to the sky.

It was literally a double-barreled cannon aimed at the universe.

"How is Center Hall? Perhaps the Sword of Heavenly Flowers could write the signboard… Hmm. It's been a while since I've written a signboard, so I think I should practice a bit. I feel like I saw a large brush somewhere."

Seeing Qing's expression, the Jin Clan Lord naturally changed the subject and turned away.

"Agh, I don't care. It's Miss Jin's house, not mine. The homeowner said she's fine with it. Just don't go around saying I built it. Agh, I'm hungry. Let's go eat."

Qing threw down the hammer as if to say she didn't care.

At this, the people of the Jin Clan looked at Jin Jagang and Jin Seol hesitantly.

Qing, wondering what this was all about, snorted, and then, Jin Seol finally opened her mouth with difficulty.

"Young Lady Ximen, so who is the winner……?"

"What winner are you talking about?! You two were fighting tooth and nail, and the only thing that got damaged was that perfectly fine guest house! If I had to pick, it'd be the brick vendor because they're the ones who will sold more bricks!"

The Northern Star Clan: One Loss. The Southern Sky Clan: Two Losses.

And it was the moment the brick vendor won a mysterious victory.

At that, Jin Seol's shoulders drooped.

But she had said all that she wanted to say.

"Th-That's not quite right. From the context, it's not ‘mutual destruction' but ‘mutual loss'-"

"It's all the same! From now on, you better learn how to use people!"

Qing yelled out loud.

Qing also had one loss recorded to her name.

It could be said that everyone was a loser that day.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was not the type to hold a grudge.

Therefore, after filling her stomach with a furious feast, she quickly dispelled her frustration.

Hmmm, but still, that thing is a bit infuriating every time I look at it. Do they think architecture is a joke?

Anyway, she was about to change her clothes to return to the Umi's Beauty Hall, but she couldn't even close her clothes because her stomach was so bloated.

Because the more uncomfortable clothing was, the more beautiful it was, the full version of the miko outfit that Jin Seol had modified became a garment that emphasized Qing's slender waist, even when she was on an empty stomach.

"Miss Jin? My, the clothes won't go in……."

"What is this!? What, what is this stomach!?"

"Well, it's the source of my Transcendent Realm martial arts, right?"

"No, what kind of person eats until their stomach becomes like this!? To a woman, clothing is like a weapon! Would Young Lady Ximen go out to fight without a sword!? How could you be so……!"

This time, Jin Seol spat out fire.

Everyone had a sore spot.

If Qing was thorough with her work ethic as a head carpenter, Jin Seol had pride in being the top clothing designer (or so she thought), leading the trends of Zhongyuan.

Even if it wasn't Zhongyuan, she did lead the trends of the Dragon Phoenix Assembly, so she wasn't exactly wrong.

After working through the entire night to make clothes, for her to say that she couldn't wear them because she had eaten too much!

Qing just laughed and mumbled.

"Well, I do occasionally go out without it, though…"

"WHAT?!"

As Jin Seol's eyes turned into axe blades, Qing flinched.

She was just speaking the truth, but…

As expected, the truth was always oppressed, so she had no choice but to swallow a sigh inwardly.

Fortunately, the belts of Zhongyuan came in various thicknesses. There was something that covered the area from her sternum to her hips, like a shapewear from Qing's homeworld.

With that, she wrapped her stomach and was able to avoid a major disaster of showing her bare skin.

As she returned to the Umi's Beauty Hall, she thought, ‘What the hell is this?', for there was a long line of people standing along the wall of the villa.

After all, only a very small minority believed in the theory of the righteous deeds of the handsome-yet-evil-looking-one-eyed youth (as strongly asserted by the vegetable store's little daughter).

The majority of the people in Guangju did not believe the claims of the vegetable store's daughter that the one-eyed youth had upended the Gold Debt Hall.

Even if the Gold Debt Hall was referred to as a ‘Hall', after all.

Originally, groups like the Gold Debt Hall were a group of professionals or a gathering of local patrons, so even if they had a manor, it wasn't the same as other sects.

In Qing's homeworld's terms, it was like an expanded concept of the offices of some kind of association.

Of course, it wasn't exactly an office. The manor building was the pride of the Hall, so it was quite magnificent and served as a group dormitory for the martial artists belonging to it.

Moreover, the moneylenders were those who were incredibly protective of their own safety.

The executives would take all the elite martial artists from their homes and businesses, so at night, it was practically an empty house, leaving behind only the dregs.

But even so, he was just a young man who seemed to be in his mid to late twenties.

It was hard to imagine he had done it all by himself.

Moreover, he was one-eyed.

If one had only one eye, it was harder to gauge distance, causing them to lean towards the side where their eye was. So, although they looked cool, one-armed, one-legged, or one-eyed martial artists were not as skilled as those with a full set of limbs.

They only looked cool.

Therefore, wasn't it more logical and reasonable to think that the Gold Debt Hall's calamity was the result of a curse?

This was the culture of Zhongyuan.

And a true miko, no, a divine maiden, had appeared, having single-handedly repelled that terrible curse.

In a Zhongyuan overrun with fake shamans, such a genuine divine maiden was truly a precious and rare guest.

After all, everyone had only ever heard rumors of a real one, but no one had actually ever seen one.

And as a result, a long line formed in front of the Umi's Beauty Hall.

Qing was greatly bewildered by this.

What is this? What are these people lined up for like they are at a famous restaurant or something?

"Divine Maiden! My wife is about to give birth, so please write a charm for a son!"

"My son is preparing for the Imperial Examination, so please write a divine charm……"

"Aigo, Divine Maiden, misfortune has come into my house and my first, second, and third sons have all fallen sick one after another. It's like we've been cursed, so please, thinking of how you'll save many people, can you perform a ritual just once!"

"My son has a wedding this time, but since they're bringing over a widow, can you please check if she's the kind of woman who eats men? Please?"

"Ahem, I plan to build a villa this time, and since it's said that the Soil and Wood Divine Maiden is so efficacious, I will pay you the highest rate in the industry."

Etc, etc.

Even if you were to open just a store, it was normal to set up a sacrificial altar and pray for fortune in Zhongyuan.

Since a real shaman, who had only been a rumor, had appeared, people from all over the city were praying for miracles.

With requests for all kinds of rituals, buildings, and even palm readings, fortune-telling, and future predictions, Qing immediately grasped the situation.

Being a shaman also seems like it could be fun.

But at this rate, I would only be playing the role of a shaman for as long as I stayed in Guangju.

Moreover, wouldn't being a shaman be something where you didn't learn anything new?

Being a carpenter was fun, and being a physician was something that saved lives, so she worked hard at them.

But what was the point in being a shaman? It was just a religious profession where you give comfort to people and get paid.

"No, what is all this? Why are you all creating such a ruckus in front of the Hall! Can't you all just get lost?"

However, people hesitated and looked at each other, not showing any signs of leaving.

It was then.

"Sister-in-Law! You're Sister-in-Law, right!?"

"Oing?"

A familiar voice reached Qing's ear.

Actually, rather than the voice itself, the two words ‘Sister-in-Law' were enough to make Qing's head spin around.

After all, Kyeon Pohui's voice wasn't all that unique, so it had been quite a while since she last heard it. It was more than that; it was as if the voice was imbued with happiness, laughter, a sense of urgency, and a whole range of emotions that exceeded a hundred and fifty one at the same time. How else would you describe the person who was shouting ‘Sister-in-Law' with such passion?

"Ah? Sister-in-Law? It's Sister-in-Law!"

Qing's voice also became tinged with delight.

From afar, the veiled woman, who was standing awkwardly, immediately rushed over at Qing's answer.

Qing spread her arms wide to welcome her.

A sudden and rough hug.

Qing hugged Kyeon Pohui back just as tightly.

But wait? Why?

Qing blinked her eyes.

Suddenly, something curved into the back of her knees and she was lifted up into the air.

"Eh. Sister-in-Law?"

"Sister-in-Law's legs are weak, you know? It feels so good to be like this. Now that I'm here, you don't have to walk around so painfully anymore."

"My legs are weak? Me?"

Qing was one of the best at Qinggong.

Even without that, her body that transcended humans was the very embodiment of health, possessing arms of steel, legs of steel, and a nearly indestructible state of having the power to withstand Sword Force below her elbows.

But, hmm…….

Maybe it's because it's been so long since I was hugged?

This is actually quite comfortable…….

"Well, if Sister-in-Law says so, then I guess it's so. But what brings you here? Did Gramps send you on an errand all the way to Guangju? No way, was it about the Guild business? No, what more is Gramps trying to do, sending people all the way to Guangju like this?"

"Huh? No. I came because I wanted to see Sister-in-Law. Oh, right, I came with my nephew too. He said he had some things to take care of. Have you met him already?"

At that, Qing's eyes widened.

"Oing? Nephew? When did Sister-in-Law get a nephew, no, wait, if he can move around alone, then that means he's old enough, so does that mean you were already a mom when we first met? Who's the dad? Why didn't you show him to me?"

At that, Kyeon Pohui cocked her head.

"A mom? No, I'm not. And I don't know who the dad is. Sister-in-Law should know, not me."

"……? I know?"

"Yeah. Because he's your nephew."

"Yeah. He's my nephew? So?"

What the hell? Why did the conversation suddenly enter a maze?

As expected, was Kyeon Pohui just being Kyeon Pohui again?

Should I just understand her because my Sister-in-Law is just being her usual self?

"So, how old is your nephew? Is he old enough to move around alone already? So is he ten? Eleven?"

"Ah. I know that much. He's fifty this year."

"……?"

What the fuck?

If it's a normal conversation, shouldn't it be a give-and-take?

In that sense, can what we're doing right now even be defined as a conversation?

It's been a long time since I've tasted Kyeon Pohui's special brand of nonsense. It only took a few words for my mind to go dizzy and become discombobulated.

Come to think of it, my Sister-in-Law was a little, a little bit like this from the beginning.

But what can I do? She's already my Sister-in-Law.

I should embrace her with love.

"Hey, Sister-in-Law. Listen-"

It was then.

A thunderous voice cut off Qing's words!

"Mother!! I! Your good son has arrived!!"

And so it went.