\chapter{On the Plains and Hills, One Food and Two Hammers (4)}

It was an unexpected spectacle, a jackpot for those who roamed the streets of Cheolbang.

Unlike Qing's hometown, where people were glued to small screens, watching the antics of clowns in real-time, such sights were rare in this primitive, ancient era.

Thus, following the light, weightless clanging of hammers, iron wedges bobbed up and down.

And people's gazes bobbed up and down along with them.

People of this era were much more sociable than modern folks, so those who arrived later would ask those who were already watching.

"Hey, what kind of medicine are they selling? My body's been feeling weak lately, so I'm thinking of buying a bottle."

"They're not selling medicine, they say she's a ‘Tomok Fairy'."

"Tomok Fairy? Why, is she going to build a house or something? Ah. So she's really going to build a house. Well, seeing how she's handling that hammer, she must be good at building houses."

"Is that for real? Isn't she just trying to scam people with an empty hammer and wooden pegs?"

"The weight and sound are different. And they say she's not selling medicine, but that she's possessed by the spirit of General Xiang Yu. When that guy over there doubted her, she showed him her skills."

"Even General Xiang Yu would be surprised."

"What do you mean, selling medicine? Wow, look at her chest. It must weigh at least ten geun1. I wonder if she's selling medicine to enlarge breasts? I should buy some for my wife."

"She's not a medicine seller, she's the ‘Tomok Fairy', the ‘Number One Carpenter of Henan'. Jeez. What the hell, am I some kind of assistant to a medicine seller? Why is everyone asking me? And listen when someone tells you something! How many times do I have to say she's not selling medicine?!"

Well, it was because he had an approachable face that made people want to ask him questions.

Then, Qing struck the iron wedge hard.

The iron wedge flew up to the sky.

Then Qing raised the eight-geun hammer high, and brought it down with all her might.

KA-BOOM!

Along with the dull vibration felt through their feet, the iron wedge was driven into the frozen winter ground until only its round head was visible.

The spectators' eyes widened collectively, wondering what they had just witnessed, craning their necks to examine the ground, questioning if such a feat was humanly possible.

Qing spoke to the skeptic.

"Tsk. I must be renowned as the Number One Carpenter of Henan because I serve a great spirit. Still doubting me? Don't you know that doubt is a disease worse than madness? I don't know what misfortune may befall you."

The skeptic rushed over and touched the iron wedge embedded in the ground, its round head barely visible above the surface.

And then the poor skeptic trembled.

"Oh my, oh my, my eyes have failed me. I couldn't recognize a divine being. Please, do not be angry."

"Hmm. It's alright. The spirit says he has loosened up his body. So there's no need to tremble like that. You'll cause an earthquake if you keep trembling like that."

"Oh, thank you, thank you!"

The skeptic bowed deeply.

Hmm. I feel a bit bad.

Qing felt a pang of guilt.

Wasn't it too much to get angry at him for not recognizing her when she had deliberately hidden her strength?

"Alright then. Ah, General! Yes, do you like it? Yes. Yes. Then I will take payment. Yes. Twenty silver coins? For this? Ah. Yes."

Qing, acting as if she was having a conversation with herself, took out a silver ingot from her money pouch.

"The spirit says he likes it, so I must pay. Is this not enough?"

"Oh, how could I take money from a spirit? I will offer it as a tribute-"

"You fool! The spirit is not a robber! If the Great King says it's twenty nyang, then it's twenty nyang. How dare you try to change that? If the spirit gives, you should just accept it with gratitude."

"Aigoo, my thoughts were shallow. Please, withdraw your anger."

Qing left, dragging the hammer behind her.

Then, the spectators rushed towards the skeptic, or rather, towards the hammer mark at the skeptic's feet, to examine it.

Wow. It's really in there. There's no grip, so you can't even pull it out.

Number One Carpenter of Henan? Do they have to be this good to be called the best there? Can the Number One Carpenter of Guangdong not do this?

She's said to be a shaman possessed by the spirit of General Xiang Yu. It's said he had the strength to uproot mountains and an indomitable spirit, and she swings that heavy eight-geun hammer like it's a chopstick.

By now, she had sufficiently achieved her goal.

While it was a pity for the skeptic who had to kneel, she had given him double the price, so she had paid him well for the kneeling.

Qing dragged the hammerhead on the ground and left the scene.

With her colorful clothes that attracted attention and the sound of the hammerhead dragging, how could she not draw attention?

Wondering if there would be more interesting things to see, idle commoners followed her in a throng during the slow winter season.

And so, with a crowd in tow, the ‘Tomok Fairy' arrived at a construction site where they were raising wooden frames.

It wasn't that she had specifically sought it out, but rather that she had followed the sounds of hammering, sawing, and the chants of workers, focusing her superhuman hearing.

Seeing the crowd, the carpenters stopped their work and stared blankly at the approaching spectacle, wondering what was going on and why a shaman was coming to a construction site with a hammer.

Then Qing casually twirled her hammer, thumped it on the ground, leaned on the handle, and spoke.

"Hey there. Are you short on hands? This lady is the Tomok Fairy, the Number One Carpenter of Henan, and I've come to learn a thing or two from the carpenters of Guangdong, who are said to be quite skilled."

"Carpenters? Seeing how you hold that hammer, you don't seem like a novice. But what kind of carpenter has such an appearance?"

"This lady is a carpenter, but also a shaman. It is my duty to learn all the carpentry under the heavens."

"Well, what does carpentry have to do with being a shaman-"

"Ahem! Did I not say carpentry? ‘To' is earth and ‘Mok' is wood. A carpenter connects earth and wood to, um, create dwellings? Thus, it's a profession, um, that benefits the world widely, roughly. Ah, that's right. This lady will later build a shrine for the Great King who will unite all under the heavens."

Wasn't that a bit too desperate and forced of an explanation?

The carpenters tilted their heads.

I don't know what kind of trick she's playing, but I wonder if it's bad luck to have her around while building a house?

But they couldn't just chase her away. They didn't know if chasing away a shaman while building a house would anger the spirits of the land or not, since they had never experienced such a thing before.

Then, Qing added a line.

"I don't need a wage, I just want to learn."

That was a truly miraculous and gracious offer! Free labor!

At that, the carpenters nodded in unison.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The names of Orthodox and Unorthodox sects differed from the start.

Unlike the Orthodox, who named themselves after regions, famous mountains in the area, or a collection of auspicious characters, the Unorthodox sects had names that were ominous at a glance.

This wasn't because the founders of the Black Path gangs had all gone through a delayed puberty.

Originally, gangs tended to have names that made them seem stronger than others, and when such gangs overpowered others and grew in size until they took over a large estate, that was the moment a new Black Path gang was born.

Therefore, the fact that the organization's name was quite suspicious and ominous was actually a kind of reward among the Unorthodox.

Doesn't the name itself suggest they're not a force to be reckoned with?

Of course, the ‘gang' in Black Path gangs was different from the ‘sect' in Orthodox sects.

The ‘sect' in Orthodox sects referred to religious sects with roots in Daoism like the Mount Hua Sect, Zhongnan Sect, and Wudang Sect, while the ‘gang' in Unorthodox sects meant ‘our group'.

At any rate, Guangzhou was tightly controlled under the influence of the Guangdong Jin Clan, but during the three months from the martial arts tournament to their return, the Jin Clan was practically nonexistent in Guangzhou.

Thus, a Warring States period of Black Path gangs quickly unfolded, and now three Black Path gangs, the Black Moon Gang, Guangzhou Boat Clan, and Gold Dagger Gang, had a firm grip on Guangzhou.

Even after the Jin Clan returned, they were busy with funerals and recovering their spirit to deal with this situation. As such, the Unorthodox were determined to solidify their power, their eyes burning with ambition.

And now, the object of their keen observation was, of course, the suddenly appeared, unidentified carpenter-shaman, the Tomok Fairy.

The leader of the Black Moon Gang, Yi Wangchul, was also paying attention.

"What is that Tomok Fairy doing now? It doesn't seem like she's doing construction for the Jin Manor?"

"It is said that she is going around the construction sites in Guangzhou, working for free."

At that, Yi Wangchul's expression turned to one of disbelief.

"For free? Why?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was good at any kind of manual labor.

Whether it was due to innate talent or her superhuman physique, which was unmatched in strength, balance, and keen senses, was unknown.

"Hey, Mister Kim. Hold that up straight. No, what kind of man can't even hold something up properly? Look at the shaman over there. She holds it up straight as a rod once she grabs it, doesn't she?"

"Well, she's a woman, so of course she'd hold it up straight. Men don't do that."

At that, laughter erupted.

Qing chuckled and said.

"You're just flapping your mouth without knowing what to do with it. Want me to nail you? I saw a forearm-sized stake lying around."

"If you're going to nail me, at least make sure I can still use the toilet."

"If I nail you, I'll nail you in the front. What's the use of a toilet then? Just wrap it up in thick cotton cloth and change it twice a day."

At that, Carpenter Yeom's expression contorted.

Laughter erupted again, and Yeom, having nothing to say, grumbled.

"She's a shaman, but her voice never rests."

"Well, with that face, there's no chance. Flirting only works if you're pretty."

Laughter erupted once more.

The Tomok Fairy, good at her work and quick with her wit, had taken over the construction sites of Guangzhou in just five days.

After all, how could she not be good at her work?

She could do the work of ten people all by herself, which wasn't just saving the effort of ten people.

To erect a single pillar required ten people, which took time to gather, time to coordinate their efforts and breathing, and each of those people had their own tasks they were supposed to be doing.

So other tasks would be interrupted, some would be idle, some would be working, and then after exerting themselves, they would need to rest because they were tired…….

If such tasks requiring collective effort were handled single-handedly by the self-proclaimed Xiang Yu, the work speed would increase by more than just the help of ten people.

Thus, if she helped for a day, the completion would be advanced by ten days.

Now, whenever the Tomok Fairy appeared, all the owners of the construction sites would rush over.

They pleaded for her to work for them, even offering their gold and silver.

"Alright. Is there any house where we're raising the ridgepole today? I'm trying to learn how to raise a round ridgepole."

"Shaman, we're raising the roof this afternoon! I'll entrust you with an entire house, so please work with us?"

"Oh. Alright. Where is it? The Bangseon Family? Okay."

What Qing felt these days was that carpentry might suit her aptitude.

The way they assembled things here was fundamentally different from what she had learned in Nakseong, so even though it was all carpentry, the methods varied greatly across the vast land.

"What's this? You assemble wood like this? Won't it shake later?"

"The front and back are walled with stone anyway, so it'll be fine. Why, how do they do it in Henan?"

"Like this?"

"Ooh. What's this? This is… My goodness. How ingenious."

Using only wood without any nails, not even a single iron nail, was a new world for the Guangdong carpenters.

Since wood was not exposed to the outside in Guangdong, they just hammered in nails.

So when Qing demonstrated Henan-style techniques, the Guangdong carpenters didn't just sit idly by.

"I haven't even shown this to my own son yet, but here, where the glue is applied……."

"We press the loess and clay deep like this for the flooring here. Since it's a place where water collects, this way it won't tilt later."

"You're going to put up a pillar? Aigoo, you'll have to take down all the bricks if you do that. It's better to do it like this. Lift it separately and put in twin beams."

"Ah, then what do you do with that space? Wouldn't it be better to temporarily support it, cut it out, and then piece it together?"

"But for the flooring… Maybe if we do it the other way around?"

"Do we need to go all the way to the bluestone?"

When Qing asked the carpenters about methods to replace materials without demolishing the house, they would discuss among themselves, and bright ideas would pop out.