\chapter{It is easy to forget a favor, but it is hard to forget a grudge (1)}

Originally, Qing thought that dealing with adults was much easier.

In Qing's opinion, among opponents, those who were similar were more comfortable to deal with than those inferior to her, and adults were far more comfortable to deal with than those who were similar.

After all, if you acted affectionately towards an adult, they would readily open their hearts and cherish you. So who could be an easier opponent than that?

However, this time, her steps were heavy.

This isn't easy…….

Before all, she was undoubtedly her biological mother.

It was not as if, in this primitive, ancient, and uncivilized Zhongyuan, unlike Qing's hometown, one could just snip off some hair and send it somewhere to conveniently receive a notification a few days later that would go, 'Behold! This child is yours! I shall inform you after thirty seconds', with a suspenseful pause in between.

However, since the mission window had clearly stated to 'know your roots', it was evident that she was the woman who gave birth to this body.

But still, what am I supposed to do?

What if there really is something like a soul?

If only I knew what kind of person Princess Yeonsul was in life, I could at least make some sort of judgment.

If she was a filial daughter who, even after death, was worried about her mother and would have said, 'Please take care of my mother', then I could fulfill her wishes for the sake of the deceased.

But what if it was the opposite?

What if she was someone who gritted her teeth, saying, 'That bitch took my body and is now deceiving my mother'?

And in truth, Qing's reluctance was closer to the latter.

What if consciousness was something that could succeed?

What if the real Princess Yeonsul went to the afterlife, whether it be heaven or hell, all because I intervened, or maybe just a signal system of a brain with a certain personality ceased to exist on this earth?

Therefore, pretending to be close to her mother was, in fact, a very sinful and embarrassing thing to do.

And let's say I do pretend to be her daughter.

What happens if the situation changes later?

What if the fake Princess Yeonsul in the Imperial Palace was actually the real one and the mole was just somewhere else, or it fell off, or it disappeared on its own?

Then wouldn't I be a fraud? Moreover, if she was the Empress, wouldn't that make me a traitor?

Qing usually ran away at times like this.

What's wrong with running away?

If you can't do this or that, you just have to step back.

But where can I run when this is my home?

Thus, her increasingly heavy footsteps finally reached the guest hall.

At the entrance, she saw a man in the exact eunuch posture, with both hands hidden inside the opposite sleeves.

It felt strange to see a man inside the Divine Maiden Sect, but since he entered so confidently, it seemed eunuchs were treated as neither men nor women.

Hmm. So if I cut it off, I can go to both Shaolin and Emei?

Wow. I'm really not envious. Not one bit.

Qing had such rude thoughts as she looked at that, um, who was it, anyway, some eunuch.

Unaware of this, Eunuch Gyeongsa, Manrihyeong, bowed deeply and slowly upon seeing Qing.

His neck bent at such an angle that it seemed like it would snap, showing the depth of his respect and reverence.

Then, without a word, he just smiled warmly, full of affection, which seemed to signal for her to enter.

Thus, Qing took off her shoes and lightly stepped into the guest hall, entering the hallway.

The structure of the guest halls for distinguished guests in Zhongyuan was similar, regardless of size. At the end of the hallway was the largest room for the most important guest, to the right were rooms for the entourage, and to the left were several smaller rooms for servants.

As such, the two palace maids standing in front of the main room turned their gazes at the sound of the door opening, then suddenly, their eyes widened and their pupils trembled violently.

The emotions contained within, perhaps affection? Or joy, surged within, making Qing feel even more awkward.

"Your Highness, I am Ximen Qing, a disciple of the Divine Maiden Sect. I have come to greet you, as I will be attending to you during your ancestral rites."

-Is that so? Then we shall see each other for a long while, shall we not? Come in. Let us have some tea.

"Then, I shall prepare the tea."

-No. How can I make the people of the host household do work when I am a guest? I have brought my own attendants, so there is no need for a disciple of the Divine Maiden Sect to trouble themselves. Come in.

"Yes."

Thus, she entered the VIP room and saw a noblewoman sitting on a wide chair to the left and right of a red cushion, leaning to the side with her elbow on the knee of her bent leg, supporting her chin.

Considering the extreme display of maternal love she had seen the other day, Qing thought she would rush over and embrace her in a flurry, but surprisingly, she showed no particular reaction even after seeing her.

Or so she thought.

Thud. As soon as the maids standing outside closed the door, the Empress practically shot forward.

Hmm. Should I play along for now?

It seemed like a touching moment of a mother-daughter reunion, so Qing decided to embrace her and opened her arms wide, ready to accept he-

"Gasp."

Qing was startled.

Instead of hugging her, the Empress, who had rushed over, roughly pulled open Qing's clothes and pushed aside her chest covering, grabbing her bare breast.

"Y-Your, Your Highness, if you do this."

"Phew. It wasn't, it wasn't a dream. It wasn't a dream. It wasn't a dream……"

Fortunately, it seemed she wanted to check the twin moles hidden beneath her chest, not some sinister intention like Tang Nanah.

After confirming with her eyes, the Empress seemed to lose all her strength, staggering, so Qing had no choice but to hurriedly embrace and support her.

"My child. My Flower Piglet."

"Flower Piglet…… you say?"

Flower Piglet was the most affectionate, or rather, cringeworthy nickname in Zhongyuan.

It might have originated from the custom of raising piglets fondly until they grew up to be slaughtered, or perhaps not. The exact reason was unclear.

It could have been that the clear explanation was burned as an old custom under the red flag of the new era.

Regardless, the Empress now began to caress Qing's face.

She rubbed her cheeks, swept her bangs to reveal her forehead, and traced her prominent, elegant nose with her fingers.

Qing was at a loss due to the affectionate display of love.

Wow. This. This is really, the burden is, it's seriously a lot.

"My child, why do you not show any joy at seeing this mother? After sending you away, this mother wondered if I was just longing for you in a dream, if I was merely seeing illusions, if I had truly gone mad. Even if I had gone mad, I wished I could see you again, hug you, touch you, and I have been waiting with bated breath until now. Hm?"

The love is heavy! It's too heavy!

Qing's face lost all color.

Luckily, her face was originally transparent, clear, and white, so it didn't show, which was fortunate, or else the Empress would have been deeply hurt and heartbroken.

Now, she had to decide on a stance.

Whether to act coy and affectionate, playing the role of a daughter.

Or…

"Your Highness. With all due respect, I do not have any memories before my illness, and now I am a disciple of the Daoist Sect, having left the secular world. The Princess has already……"

Qing's words caught in her throat.

Already what? Dead? Gone? No longer in this world?

"How can you say such a thing? No matter what anyone says, you are my daughter. Even if everyone in the world denies it, you are my daughter. The more I look at you, the more I see my daughter. How can you say such words? Memories can return, and even if they do not, it is fine. Even so, this mother is your mother."

"But, Your Highness, you will eventually face a very unfamiliar person while I attend to you."

"Even with your beauty blossomed like this, I still recognize you as my daughter. Unfamiliar, you say? Even if you were to make that little pucker with your lower lip, as if troubled by something, I would still know it is you, Sohal."

It was just a coincidence, though.

It was a habit she had before leaving her hometown, so how could she have known that the original owner of this body also did the same?

But the Princess was the Princess, and Qing was a stranger with roots left in a completely different land, with the foundation of her life and values being entirely different.

Therefore, Qing thought that as they spent time together, attending to her closely, the Empress would eventually have to accept that her daughter and Ximen Qing were different people.

……Or so she thought?

Why? Why is that?

"Why do you look like you are not feeling well? Why are you just poking at the food? This stir-fried eggplant is exactly to your taste, isn't it? Here. Don't mind others and just eat."

"Uh, it is to my taste. How did you know?"

"How did I know, you ask? How could a mother not know her daughter's favorite food?"

Then she rattled off a list of dishes.

What the hell?

Why do the Princess and I have the exact same taste in food?

But Qing soon accepted it.

Originally, she didn't like sweets that much, but after coming here, she became like a ghost who died without ever tasting sugar.

They say that taste is also genetic. Since her body had changed, perhaps her food preferences had changed accordingly.

"If you tell me to eat more, then……"

"When you were young, your body was already quite robust, so that damn father of yours, that wretched man, would scold you, telling you that you were a girl who grew straight up like bamboo and that you should stop eating so much. So you couldn't eat according to your true appetite and ended up just nibbling, always minding others. How could I not recognize that?"

"It's not like that. It's a method of eating like a beauty that my teacher taught me……"

"Her Ladyship is indeed amazing. But this mother's heart feels full just by watching you eat heartily, so don't bother with that and just eat as you please."

"Well, the way I eat might look a bit unsightly……"

"How could a daughter's eating be unsightly? Don't be shy."

Since she insisted this much…

And after thinking about it, acting like a beauty was just acting like the Princess.

She had already shown her true self, so whatever.

Thus, Qing changed her posture and began to eat in earnest, causing the Empress's expression to become wistful, with tears welling up in her eyes.

"Look at that. You're exactly the same. How could I not recognize you?"

It meant that Princess Yeonsul also used to stuff her mouth full of food until her cheeks bulged.

And then?

"Now that you've eaten, it's time to lie down, right? Come here."

"Huh? Did Princess Yeonsul also lie down after eating?"

"That's why you grew so well. Our Flower Piglet caused many palace maids to burst their skirts. They thought that if they ate and immediately lay down to sleep, they would become as buxom as you."

And so, while attending to the Empress, Qing gradually learned more about the woman called Princess Yeonsul.

She's exactly like me?

What's with this princess, acting like a street ruffian, being vulgar, yet also bold and courageous like a man, and even clinging onto others while displaying her frivolousness?

She was even said to have a talent for music, remembering any tune she heard just once, whether it was played on a zither or a flute, and skillfully playing it back.

Based on what she had found out so far, the only difference was their handwriting.

Thus, Qing concluded.

The Empress must be in a bad state.

Not just a little, but a lot.

Why else would she say that even the bad habits Qing brought from her hometown were the same as the Princess's?

As if a princess would ever subtly pull at her underwear, claiming it was stuck to her body?

The Empress must have missed her daughter so much that now, no matter what I do, she just sees me as her daughter.

And it was understandable.

Ever since the fake Princess Yeonsul returned, the Empress had been on edge, suspecting solely based on her intuition that 'that is not my daughter'.

She had been alone in her suspicion, unable to express it and secretly suffering, for over four years, almost five.

If she had voiced her doubts, in Qing's hometown, it would have been recorded as a mental illness called paranoia.

So the Empress must not be in her right mind…….

But that made it even more unsettling.

Wasn't this like preying on someone who was mentally ill and pretending to be someone else?

For the sake of the real Princess Yeonsul, it felt like something she shouldn't do.

So she had to distance herself, showing that Princess Yeonsul no longer existed in this world, and that only Ximen Qing, a complete stranger, was here.

Qing made up her mind.

And so, a month and a half passed.

And sincerity always finds a way to be conveyed.

It was a short time, but since they were always together, the effort accumulated, and the sincerity eventually got through.

So what could she do?

Now, she had no choice but to accept it.

Thus, Qing was defeated.

For Qing, who was hungry for affection, the Empress's love was vast, immense, and infinitely pouring, an embrace she could not avoid.

"Ah."

As Qing lay on her lap with her mouth open, the Empress gently placed a grape into it.

As Qing munched, the Empress's palm once brushed Qing's cheek, then rested on her lips, creating a support.

Then, a grape seed popped out of Qing's lips and fell into the Empress's hand.

If anyone saw this, they would exclaim, 'What an unholy sight!'.

And even if this woman was not the Empress but an ordinary mother, it would still be the same.

It was a scene that would make one say, 'What a terrible act of filial impiety!'.

But what can I do? Her Highness wishes it.

It's not like I'm doing this because it's comfortable for me. This is all for Her Highness's peace of mind, see, she's smiling so widely.

If I sacrifice myself to bring her peace of mind, isn't that a good deed?

The late Princess Yeonsul would surely understand if she saw that expression.

After all, she was said to be a woman with a heart as fine as silk, beloved by everyone, though her behavior had some serious flaws.

But after she fell ill, her behavior became subdued as she was bedridden, but it seemed her heart had developed flaws.

Still, since her heart was so beautiful before, people sympathized, saying she must have become like that because she was so sick.

Of course, this part was the opinion of her mother, the Empress, so it should be taken with a grain of salt.

Anyway, Princess Yeonsul would surely understand, and…

Qing, who was not used to being so pampered, especially by the most noble woman under the heavens, found this situation to be not very comfortable. To be precise, it was very comfortable.

Just a tiny bit, honestly, it was a little bit comfortable……. 