\chapter{It is easy to forget a favor, but it is hard to forget a grudge (7)}

"Ugh, these good-for-nothings."

Qing flicked her hands.

However, the greasy flesh remnants clung to her hands instead, making them even dirtier.

Qing frowned, looked around, and thought, 'Why are these bastards all shirtless?'

She found a relatively intact and bloodless pair of pants, tore off a piece, and wiped her hands. But the makeshift towel was soaked in sweat or something, making it extremely damp.

She was wiping off the sticky blood and grease with it, but could this really be called clean?

Ugh, it's so gross.

Qing was casually pushing the sprawled corpses with her foot when she suddenly brightened, thanks to discovering a waist with a water pouch.

That's it.

Uncharacteristically, trying to be clean, Qing uncapped the pouch and poured it over her hands, but alas.

The smell of stale alcohol stung her nose.

Hmm. Can this be considered some sort of disinfectant?

I'd like a sip, but it's so gross since I don't know who the owner is.

Qing wiped her hands, still dripping with alcohol, on her pants.

Then, she retrieved the Moonlight Sword and slid it into its sheath.

It's great and all, but the fact that the sword is so long makes it really annoying to sheath.

And then she noticed the vice commander, still groaning softly.

"Alright. Reflection time is over. Did you wish you had lived a good life, knowing this would happen?"

"What, what are you talking about? What grudge does the Green Forest have that you're doing this to us?!"

"Huh? What are you talking about? You started it first when I was just passing by. You demanded money for just passing by. I was even willing to pay a reasonable amount. Look how pretty it is here. It's worth paying for the view."

"What are you talking about, coming all the way here?!"

"Who came all the way here? Do you think every mountain in Zhongyuan belongs to the Green Forest? You started a fight while I was passing by."

The vice commander, wondering what this was all about, suddenly had a thought.

"You, did you step foot here not knowing where this place was?"

"Hmm? Zhangjiajie?"

Zhangjiajie was the name of a small town that one had to pass two ridges over Tianzi Mountain, past the strange rock formations.

At this, the vice commander immediately realized.

Fuck. So, it wasn't an invasion of the Green Forest. She was really just passing by, not knowing anything.

As Qing had said, they had been the ones to start a fight and ended up utterly destroyed.

"Now then. If you have any last words, try to make them cool."

"……Spare me!"

The vice commander, trying to beg for his life, was kicked in the head by a flying boot, letting out a desperate scream.

His nose caved in, and the vice commander asked in an aggrieved tone.

"Why, why……?"

"I told you to say your last words, but I didn't say I'd listen to them."

"Is that something you should say right now?!"

"Have you ever listened to the last words of the people you've killed while banditry? Not counting the times you listened and scoffed. I'll spare your life if you have."

"That's…"

The vice commander's words were instantly cut off.

That alone was as good as an answer.

"T-There is!"

"Hmm. I can't believe you. But a promise is a promise."

In an instant, as she drew her sword, she slashed upwards and then downwards.

The vice commander's shoulders were neatly severed, and his two arms fell to either side.

"I spared your life. You seem to be at least at the peak realm, so you should know how to stop the bleeding. If you die now, you know it's on you, right?"

"What nonsense is this, s-spare me, spare me!"

Stopping the bleeding requires hands to apply pressure or wrap the wounds.

However, there was no need for Qing to concern herself with that.

If he wanted to live, he had to figure it out himself. Whether by using his feet or his mouth.

"Hmm. I'm leaving now. It was fun. Bye, then."

Having had her fun, Qing leaped away without any lingering attachment.

She had seen some signal flares earlier, and if she stayed, she might get swarmed, which would be annoying.

Knowing her own agility was excellent, Qing was confident in her ability to escape at any time.

So Qing thought, 'I should escape now'.

From the top of Liuluo Peak, the mountain paths stretched east and west.

To the west, the path from Mount Yongsan extended all the way to Tianzi Mountain.

And Qing did not choose either direction.

Isn't it fine to just go south even if there's no path?

Southward.

She thought she would just descend the mountain.

However, there was something Qing did not know.

The people of her homeland tended to underestimate mountains.

This was because the mountains of the Korean Peninsula were indeed underestimated.

In the first place, the terrain was not rugged, so there were no mazes formed by canyons. In fact, it was rare for bedrock to even block the way.

Moreover, the trees were not tall and the density was low, allowing sunlight to filter in, making the inside bright and not significantly limiting visibility.

However, to the rest of humanity, mountains were a terror.

Deep mountains were densely packed with trees, making it dark even during the day. And once the sun set, it turned into a world of complete darkness where one couldn't see anything at all, whether with their eyes closed or open.

In addition, the terrain was unpredictable, with steep slopes blocking the way. Cliffs just a couple of yards high were not even considered cliffs.

Therefore, to the people of Zhongyuan, mountains were forbidden areas where one could not return alive if they entered carelessly.

Moreover, they were terrains where Qinggong could not be used.

The Qinggong that Qing had learned was specialized for running fast and long.

It was a miraculous technique that allowed one to leap more than three yards with each step at top speed.

However, on a pathless mountain, there was no clear space to leap, not even within two yards, let alone three.

The path was blocked by trees, or it dropped off, making it impossible to tell if it was a cliff or a slope beyond, or it was obstructed by bedrock or cliffs. Thus, leaping would be no different from challenging nature like that bastard called the commander earlier, or saying something like, 'Here I come, Ximen Qing, to ram my body against you!'

Moreover, the ground was not properly visible due to the thick layer of fallen leaves.

It was impossible to know if stepping carelessly would cause one to sink or slip.

This was why even the most skilled land and herb gatherers, or those who hunted for rock cheongs, could not dare to run in the mountains.

So, instead of using Qinggong, Qing traversed the rugged mountain terrain at a brisk pace.

However, Qing's physical abilities had already long surpassed that of humans.

Despite her surprisingly nimble and agile movements, Qing showed no signs of fatigue.

Because, after all, she wasn't particularly tired.

Thus, she thought.

I can't use Qinggong, but even so, what about it?

I'll just keep going south.

Sheesh. Climbing mountains isn't all that hard.

……That was what I thought, at least for a time.

It was when Qing felt good, at least until an endless cliff blocked her path.

I'm going the way I want to go. I thought I was creating my own path, full of spirit and vigor as she traversed the mountain terrain.

Suddenly, her view opened up, revealing a breathtaking panorama hundreds of yards below.

Wow. That's really stunning.

All those tiny green things the size of fingernails below were actually enormous trees, weren't they?

But a moment's sightseeing was all it took.

But like, how do I get down from here?

Qing stepped on the edge of the cliff a few times to confirm it was solid bedrock, then carefully, despite being a Transcendent Realm Master, she crawled on all fours like a coward to the very edge and stuck her head out.

"Gasp."

Startled, Qing quickly crawled back.

It was a sheer cliff without any kind of fencing.

It seemed to be well over a hundred yards high. Looking down at the distant ground made her heart sink and her knees go weak, causing her to tremble uncontrollably.

Even though her body's sturdiness had transcended human limits and she could wrap herself in a Protective Aura, a person could not survive a fall from over a hundred yards.

It might not be impossible to climb down the bedrock, but no, seriously, that was just not it. I might be in the Transcendent Realm, but I'm not a professional cliff climber, you know?

Moreover, a huge cliff blocked the way on the other side to the south as well.

Even if she managed to climb down, there was no way to climb up the opposite cliff.

So what now? I have to make a detour.

Qing looked left and right, before deciding to head west for now.

And after following the cliff at this angle for a while, the angle gradually shifted until she faced a cliff that completely blocked the west.

If she continued to follow the cliff, she would end up returning to the spot where she had fought the bandits.

Qing turned in the opposite direction.

After heading straight east for about half an hour, her view opened up once more, revealing the most spectacular scenery of Zhangjiajie!

There was a moderate amount of fog, creating a dreamy landscape where islands seemed to float on clouds. It was a view that made it seem as if she had arrived in a Daoist paradise, known as Wuling Daoyuan.

In other words, it was a dead end.

Only then did Qing realize why there had been no path to the south.

Ah shit. The south is completely blocked by cliffs, so of course there's no path.

However, it was not fair to criticize Qing for being foolish.

This was because people from Qing's roots, the Korean people, were those who found their way based on cardinal directions.

Even if it was a forest or a mountain, it didn't matter. Furthermore, even cities were built like that, so if one knew the geography of east, west, south, and north, they could somehow reach their destination.

However, this was a characteristic of planned cities. In older cities, going by cardinal directions alone would often lead to dead ends.

But since the norms of a culture could not escape the boundaries of that culture…

Fortunately, after following the path north for a while, a steep but not cliff-like slope appeared.

Hmm, it's a bit too steep, but would it be okay……?

But if I go further, I'll just end up back there.

The time has already been delayed. Ugh, I hate the Net of Heaven and Earth.

Having been severely traumatized by it, Qing had a strong aversion to being tracked.

Qing made up her mind.

And her outstanding execution did not know hesitation.

Of course, because of that excellent execution, she spent nearly an hour just skirting the southern cliff of Liuluo Peak, but whatever.

If she had just followed the path, she could have descended the mountain in one go. However, she insisted on taking several times the effort, facing much more difficulty and danger, and even taking dozens of times longer to do so.

Qing carefully stepped onto the slope.

She practically laid down on her back, sticking close to the ground with her back and hands, carefully sliding down.

Naturally, it was slow.

And if she slipped, even Qing couldn't avoid serious injuries.

But what else could she do?

This was the path Qing had chosen.

She had to endure it with sheer fucking willpower.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Upon receiving the urgent request for support from the summit of Liuluo Peak, the first to arrive were none other than those of the Mount Liang Bastards.

Mount Liang was the greatest idol for those of the Green Forest, as well as the one they should all emulate.

And as one would expect from a combat unit that had taken that name, they were also the most elite combat unit of the Green Forest, based at the main headquarters.

Thus, the members of the Mount Liang Bastards frowned upon seeing the carnage at the top of Liuluo Peak.

Since parts of human bodies were scattered around in a mess, there wasn't a single corpse with all its limbs intact.

The best-preserved one was a body with only its head separated. How gruesome.

Among the dead, that was the case.

Among the living, there were also those with their limbs attached.

"S-Sir, y-young ma-master!"

"Do not touch him! His neck is broken. If you shake him, he might really die!"

Since the elite unit naturally included a medic, the Mount Liang Bastards' medic carefully examined the unconscious young master.

"How is the Young Master?"

"The neck is one thing, but blood has pooled in his head. Even if we were just a few moments late, he would have already passed away. We need to treat him, but there is a risk……"

"It's better than dying on the spot. If something goes wrong, we can just say he was already dead. Hurry."

"Yes, sir."

Meanwhile, the members surveyed the surroundings.

There was no need to examine the identities of the corpses in detail.

After all, the Second Young Master led the Fierce Tiger Unit and the vice commander was also found dead without both of his arms.

"How many were in the Fierce Tiger Unit?"

"Forty-seven, I believe."

"But there are only twenty-four corpses."

The commander murmured grimly.

It was obvious that the rest had turned their backs and fled since the scene was so gruesome.

When those who claimed to be heroes of the Green Forest were just a bunch of nobodies who hadn't even risked their lives. How many of them would actually do so?

"Any survivors?"

"None, sir."

"The rest ran away, then. But who did this? It's such a spiteful act, full of resentment."

The commander of the Mount Liang Bastards, Dou Sam, tried to make some semblance of a deduction.

And the conclusion was… he didn't fucking know.

There were way too many people who held grudges against the Green Forest.

If the intensity of the grudges translated to actual power, then the Green Forest as a force would have long been wiped out from this world.

"How is the Young Master?"

"For now, his life is not in danger, but…"

Due to being left unattended with a broken neck, he was completely paralyzed below the neck, unable to move even a single strand of hair.

Moreover, the likelihood of him being intact above the neck was also low.

There was a high probability that he would become an idiot or a fool with some kind of brain damage, like being mute, retarded, deaf, or the like.

Dou Sam frowned.

"It would be better if he were a fool. To live a sane life with total paralysis… If it were me, I'd rather you just cut off my breath. Anyway, that's a cruel way to handle things. Who did…."

Dou Sam's question was soon answered.

Not long after, the bandits of Mount Yong, who had appeared, were dragging captured deserters of the Fierce Tiger Unit, all tied up.

"I wasn't running away, I was just requesting support, kuheok, aak, aak!!"

The deserter, desperately trying to swallow his excuses, was kicked and sent rolling, screaming as his wrist was then stomped on.

"A runaway bastard has a lot to say. If you want to live, you better have a lot to say. Who did this? Who are the bastards?"

Then, without a moment's delay, a scream-like reply burst forth.

"XIMEN QING! IT WAS THAT BITCH, XIMEN QING!" 