\chapter{It is easy to forget a favor, but it is hard to forget a grudge (3)}

The Wulin Alliance was not a superior organization to each individual martial arts sect, so when a mission letter arrived, it wasn't necessary to unconditionally accept and obey the orders.

However, it was not easy to refuse the very first mission after the Wulin Competition.

In Zhongyuan, face was as important as life itself.

Of course, if one had to choose between life and face, a hundred out of a hundred would choose life, but that's beside the point.

So, if one were to refuse a mission right after the Wulin Competition ended, it would be a stain on the face of the Murim Alliance.

Moreover, Qing was the winner of the Hidden Dragon's Martial Arts Tournament.

As the representative who stood at the forefront of the younger generation of the Orthodox Faction, if Qing ignored the mission, who in the world would follow?

Besides, even if it was called a mission, it didn't involve risking one's life in battle.

It was just a request to stay in a somewhat distant region until the end of winter.

Moreover, it wasn't a task that would cause hardship but rather one where she would be treated with great hospitality.

So, what could be done? She had to do it.

Especially since there were certain individuals who couldn't avoid the mission.

Among them was Seol Ri, who had been dispatched to the Wulin Alliance as a representative of the Ice Palace.

The Wulin Alliance had no way of tracking Seol Ri's location.

However, the Vice-Commander, Sama Chunbong, was an eccentric who, despite her odd personality, was meticulous in her work. She had attached a document to each mission letter, requesting that if there was anyone named among them, the mission should be delivered to them.

Thus, Seol Ri, who was either going through puberty or a rebellious phase, making her incredibly disobedient, yet had suddenly become obsessed with training, firmly grasped Qing's hand.

"Young Lady Ximen. I will definitely return."

Seol Ri's eyes were resolute as she spoke.

Just by looking at her expression, one might think she was someone heading into a life-threatening situation, vowing to return.

"Didn't you say it was Soju? Soju, hmm. That suddenly sounds appealing. Fish sashimi with a shot of soju, yum."

This won't do. I can't take it anymore.

Qing gathered her Inner Qi and started poking around inside her body, somewhere in her internal organs.

As such, the creature Qing harbored within her was stimulated and thrashed about, causing a spicy and pungent sensation to rise, warming her insides.

Indeed, it was quite the alcohol craving. It was effective.

It was just a shame that the parasitic newt, now a blood-infused liquor bottle, was the only one suffering, being constantly beaten by True Qi after sucking on toxic energy.

It was a creature that was supposed to be an internal pet that detoxified the body, but who knew what would become of it.

"Ahhhh, this is it. But if it's Soju, isn't that a nice place? I heard the food there is delicious. Ah. Does Gunyeong need some pocket money?"

"Yes. No. That's…… um. And I don't like being called Gunyeong."

You said it was Soju? Yes.

Isn't that a nice place to go? No.

Do you need pocket money? Um.

Come to think of it, no matter how poor and beggar-like Seol Ri's financial situation was, how could she readily say, 'Yes, please give me some money'?

She might accept it if offered, but it seemed Seol Ri was subtly reading Qing's mood, at least when it came to this.

"Ah. I was being inconsiderate. Just a moment, I'll get you something."

Qing quickly brought out a silk money pouch.

"Don't spend it recklessly just because you have money. You have to be thrifty to live well. But don't be too stingy either. A person needs to have a full money pouch to walk confidently wherever they go."

Seol Ri accepted the money pouch, bowed her head, and then looked back at Qing.

"I will become much stronger and protect you."

"Sure, sure. This daddy is already deeply moved, hearing such a dutiful sentiment from our Gunyeong."

At that, Seol Ri tilted her head, about to say something about the name Gunyeong again.

"Why daddy?"

"Huh? Should I be mommy then?"

"……?"

"……?"

They exchanged confused glances.

Seol Ri tilted her head for a moment, then decided to let it go as just another one of Qing's nonsensical remarks, and said her farewells again.

"I will definitely return."

"Didn't you say that already? But why are you coming to the Divine Maiden Sect? Shouldn't you be going to the Wulin Alliance?"

"Yes. I said I would protect you. I did."

"Sure, sure. Now, go. You have to catch your boat on time."

"I will, definitely, return."

Qing burst into laughter at Seol Ri's resolute gaze.

The journey from the Divine Maiden Sect to Soju was not only not difficult or dangerous, but it was also a very comfortable and easy trip.

Just take a boat from Jagwi and keep going until you reach the sea, and Soju would be right in front of you.

In fact, this was Sama Chunbong's consideration, arranging for Seol Hwa, who was likely unfamiliar with the lay of the land in Zhongyuan, to be placed where she absolutely couldn't get lost.

After that, she had to inform the Empress that she was leaving the mountain.

Hmm, it's hard to bring this up.

What if she tries to stop me?

The ceremony would be over in fifteen days, and she would leave on her own, but what if she asked her to stay longer?

I don't have the confidence to refuse her harshly.

But the Empress was surprisingly nonchalant.

"Yes. A child should not see their mother off, but the other way around. Be careful, don't pick up and eat just anything, don't sleep just anywhere because you're tired, don't neglect to wash up just because there's no bath, and don't follow strangers. Also, don't chase after cute animals just because you see them."

"What do you take me for, a child?"

"What else would a twenty-year-old girl be but a child? Above all, be careful. If I hear that something happened to you, this mother will also end my life."

"Don't say such things."

"The reason I didn't take my life even after losing you was that I could not die before seeing your corpse with my own eyes. Just in case you were still alive. I will live as a martial artist and die as one, but if you happen to die, do not be too afraid. This mother will accompany our Flower Pig on her journey to the underworld. Think of it as having one more life added to yours, so you must cherish it."

It meant that if you die, I'll follow you to the afterlife.

No matter how one looked at it, it didn't sound like a joke.

It's seriously too heavy! Seriously!

At any rate, the Empress surprisingly let Qing go quite easily.

Ximen Surin was as nonchalant as ever.

"Take care on your journey. Since you're going to a land bordering the sea, eat plenty of the seafood you love. You were so eager to find saltwater fish sashimi, so this is your chance to fulfill your wish."

"Hehe. Ah. That's right. Now that I've reached the Transcendent Realm, shouldn't we postpone the Wisdom Sword of Tai Chi and the Four Manifestations Sword? Are there any other martial arts worth learning?"

"Hmm."

Ximen Surin, who had wondered where Qing kept learning such precious and rare martial arts, had come to an understanding after hearing that she was actually a princess.

If the Imperial Palace's Martial Vault had collected all the martial arts of Wulin, then it seemed she had someone who could acquire what she needed.

However, judging by the fact that she hadn't yet learned the two types of martial arts she had told her to learn, it didn't seem like she could acquire them as quickly as she wanted.

Perhaps the process of acquiring them was difficult or time-consuming.

"Having reached the Transcendent Realm, it is time to refine your own martial path. Therefore, do you really need to covet the martial arts of others? But if you insist on learning, since the more Inner Qi is the better, it would be good to learn a difficult form of Qi cultivation that focuses on Qigong."

"Qigong. Yes."

Ximen Surin burst into laughter.

Wasn't telling a disciple to learn someone else's martial arts something a teacher shouldn't say?

But since the disciple was now a Divine Thief, maybe it wasn't such a bad idea.

When the thought of the Divine Thief came to mind, Ximen Surin spoke.

"Write a letter to the Hanlin Academy. Explain your situation and let him know that you won't be able to make it this winter. Since your second teacher is also not present, is he not?"

"Ah. You're right."

"If the plan is to stay in Namnyeong until this winter, you will return in the spring. So ask that Hanlin Lecturer via letter if it would be acceptable to arrive in late spring. Didn't you say you had training to do?"

"Ah. That's right. Master, if permission is granted, may I take Jangmyeong with me? I promised to tour Jianghu together after the Wulin Competition, but things turned out this way."

"Taiyuan, you say? That wouldn't be so bad."

Wasn't it when the Hanlin Academy, pushed out of direct politics, moved away from Beijing to Taiyuan?

Thanks to that, Taiyuan became known as the headquarters of Confucianism, so she thought it would be a good place to learn.

Moreover, while a Divine Thief was nothing more than a thief, a Lecturer at the Hanrim Academy was a giant who oversaw the education of Confucian scholars.

This was why Ximen Surin had readily accepted the second teacher; the path of Orthodox martial arts followed the principles of Confucianism, Buddhism, and Daoism.

She had taught Qing the scriptures of Buddhism and Daoism, but Confucianism was somewhat unfamiliar and distant to Ximen Surin.

It was because she had burned all the Confucian scriptures she had, due to her disgust at how that damned Confucianism treated women so harshly.

And so, she bid farewell to her master.

Jin Jangmyeong, upon hearing that Qing was leaving, pouted like a spoiled child, showing a displeased expression. However, when she heard that they would spend a season together in Taiyuan after Qing returned, her expression suddenly brightened.

"It's a promise. Don't be late."

"How far could it be to be late?"

"It's not far?"

"Isn't it just a little shorter than the round trip to Luoyang?"

"……?"

In terms of straight-line distance, that was true.

Without any particularly difficult obstacles between the Divine Maiden Sect and Luoyang, one could practically just follow a straight line drawn on a map and ride a horse without being blocked.

It might be a nuisance to trample through fields and paddies, but it wasn't entirely impossible.

However, the road to Gwangseo Province was different.

In the geography of Zhongyuan, the west was very high and the east was low, and the north was very high and the south was also high.

When high areas overlapped, they didn't disappear but stacked, becoming even higher.

So, to go to Gwangseo Province, one had to first go east until they reached Dongting Lake, and then take a detour along the southern part of Hunan Province all the way down to Guangdong Province.

Only when reaching Guangdong could one head west, which was considered the proper route.

This would double the travel distance.

"Well, that's if you're pulling a carriage."

Of course, Qing had no intention of taking such a detour.

Why go the long way when you can just take a shortcut through the mountains?

Why take a detour just to travel on flat roads?

Why not just go south?

After all, even if you get a bit lost, if you just keep heading south, you'll eventually get there.

She possessed unparalleled Qinggong, an astonishing digestive system that could handle almost anything, and the ability to sleep anywhere without issue.

And she heard there were roads, even if they weren't obvious. So, what's the problem?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The shape of the administrative provinces of Zhongyuan was quite irregular, some long to the left, some to the right, and among them, the boundary of Gansu Province was particularly bizarre, shaped like a long snake.

Why did the boundaries end up like this?

Well, it was because there were obstacles there.

In a distant past, even more primitive than the current uncivilized Zhongyuan, there was a time when people were even more uncultured.

During those times, primitive people couldn't conquer high mountains, deep forests, and wetlands, so they were natural obstacles they couldn't dare to enter, as they wouldn't come out alive.

In other words, the boundaries of the administrative provinces of Zhongyuan were formed by mountain ranges, following the ridges that connected the peaks on either side, or by very dense forests, wetlands, or jungles.

Among these, wetlands were eventually conquered.

The southern part of Zhongyuan was originally a barren land where people couldn't live due to the wetlands, but now it had become such a valuable area that the country's capital had moved east to Beijing.

However, the straight path Qing aimed for was still, in the current and even in the future Zhongyuan, considered one of the most remote and undeveloped areas.

However, there was one place along this straight path that would be developed in the future.

That was the very place that was considered the sacred land of the Korean people, a place of pilgrimage, the origin and end of filial piety tourism, the holy mountain of the supreme people.

Its name was Zhangjiajie!

Of course, Zhangjiajie being conquered by Koreans was still far in the future.

Currently, a different force occupied Zhangjiajie.

To be precise, the name Zhangjiajie was not yet well-known, merely a small, insignificant city nearby. In the current Zhongyuan, it was called Mount Cheonja, a name with a very lofty meaning.

And on Mount Cheonja, a large group of people resided.

They were the Lulin, a labor union engaged in bountiful activities such as forestry, robbery, murder, kidnapping, and looting.