\chapter{It is easy to forget a favor, but it is hard to forget a grudge (4)}

Basically, Qing is fundamentally someone who lacks awareness towards safety.

It was like that from the start. In the nation where Qing was born and raised, it was rare to seriously ponder about survival. In fact, it was safe to say that such a thing was practically nonexistent, except for a few exceptions.

After all, the gap between how to make a living and how to not die was a disparity that the people of Qing's ethnicity could not truly feel.

Even if it wasn't for that, it was also because she had splendidly endured her first year in Zhongyuan as a newcomer to Wulin.

After all, she thought, 'I survived by picking up and eating trash. Would there be anything worse than that?'

On top of that, her Qinggong was unparalleled, so if push came to shove, she could just run away. As such, she never really thought that she would be in danger, no matter what she did.

That was why she fearlessly set foot on a secluded, rugged, and untraveled mountain path as a lone woman.

It's not without reason that people use well-maintained roads that are frequented by many.

After all, there are many dangers that come with mountain paths.

First, there are the creatures of the mountain.

A Transcendent Realm Master wouldn't fear wild beasts. Charging beasts with their teeth bared would just be turned into a meal that was extremely lacking in both nutrition and taste after being sliced and diced with Sword Qi.

Wild animals stank, were gamey, could have all sorts of parasites and poisons, and even if they weren't poisonous, they could still be ridden with disease.

However, snakes and venomous insects were a bit more frightening.

If one was quietly bitten while sleeping and had to deal with it while camping in a secluded mountain, the situation could become very difficult.

But Qing was immune.

And then there was also the absence of villages.

Along well-maintained roads, there were small towns and villages that catered to outsiders. However, it was extremely rare for villages to be built in places where it was uncertain whether a path was a path or just a trace of one.

This meant that resupplying things like food and daily necessities during the journey was impossible. On a smaller scale, it became a matter of human dignity.

But Qing was a woman who would shove anything into her mouth when she was hungry, and she had already thrown away her dignity during her first year.

There was also the issue of getting lost.

But it was Qing who ate dirt for food and slept on the streets.

If you threw her a ball, she could probably live well on a deserted island for a thousand years.

When you look at it point by point, there was actually a logical basis for Qing's apathy towards danger.

She hadn't intended to travel alone from the start.

She left Divine Maiden Peak and stopped by Zigui, but Choi Leeong and her sworn sister weren't there, so what could she do?

Come to think of it, everyone's living their own lives now, so why would I stop what they're doing and tell them to come with me?

Gramps and my sworn sister will live their own lives, meet, play, and separate.

Even if it wasn't a sworn sister but a real sister, people don't stick together for every single thing.

That's how Qing cleanly gave up and hit the road alone.

With a veil on.

Wow, the veil! It's back!

Men were not as blatant as women, but it wasn't all that pleasant to see the same faces going around in circles in the same area with such mysterious movements.

Ximen Surin, who had unofficially received a government position, told her it was okay to wear it in case she was worried about her identity being revealed after hearing about Qing's background.

She had lowered the wearing restriction by one level, telling her to only take it off when she was Ximen Qing, a disciple of the Divine Maiden Sect.

Thus, liberated from the fervent gazes of men and the occasional bold advances from courageous ones, Qing headed southwest along the road, passing through Enshi County.

By now, Qing had at least a basic understanding of the geography of Zhongyuan.

If she just followed the road right now and headed towards Chongqing, she would have to climb a cliff to cross the plateau of Guizhou Province instead of a mountain path.

So, she headed south to Yongsan County of Hunan Province.

Originally, if there were no other cities or villages nearby, the merchants catering to outsiders would be vicious.

Their reasoning was that there was nowhere else to buy.

Yongsan County was like that, so Qing clicked her tongue at the price gouging. But when a group colluded to raise prices, what could you do?

Is it called Yongsan because the prices are terrible?

They're not even kind. Seriously, I want to punch them in the face.

The merchants would say that the nearest towns were either Sangshik County or Zhangjiajie, and the roads were too rough for carriages.

Otherwise, they would have to bring goods from Eunseo County to the north or Ilsu County to the south, which would take at least half a month to go and come back. So it was only natural for prices to be high.

Anyway, since it was a merchant talking, Qing naturally filtered it through one ear and out the other, leaving only one word behind.

Zhangjiajie!

Where is Zhangjiajie…(omitted)…that's the place!

Come to think of it, I've never been to the famed Zhangjiajie. In this chance, why not check out why it's so popular among the middle-aged and above?

It was like stepping into the tiger's den with her own feet, but how could Qing possibly know that it was the location of the headquarters for the Wulin's Bandit Alliance?

In the first place, since the relationship between the martial artists of the prestigious sects and the Nokrim was akin to seeing a cow looking at a chicken or a chicken looking at a cow, Ximen Surin didn't particularly warn her about it.

On top of that, Qing had never even joked about the Nokrim because she was worried that her acquaintances might get caught up in it, so she had never heard of their infamous names in passing either.

Thus, after crossing a few ridges, Qing went, 'Wow!'

So this is why everyone goes on and on about Zhangjiajie, Zhangjiajie!

If someone else saw this, they would have thought she was a strange woman shouting 'Zhangjiajie' at Mount Cheonja.

To use Qing's hometown as an analogy, it was as if a Korean, not even a foreigner, was standing on Namsan Mountain and shouting, "Wow Jung-gu! Wow Jung-gu! What a great mountain." That was how they would understand the situation.

The scenery of Zhangjiajie was truly dreamlike.

Hundreds of rock formations stood hundreds of zhangs tall, supporting the sky like pillars. The view from the entrance at about the tenth ridge was truly a strange and unfamiliar scene of another world.

As someone from a different world, Qing thought it was like being on an alien planet from a movie.

But the people of Zhongyuan were no different. Upon seeing the scenery of Zhangjiajie, they thought, 'This is not our world, but another world. This is what the heavens must look like, not the earth.'

Thus, it was said that the immortal's paradise, known as the Peach Blossom Spring of Wuling, was another name for Zhangjiajie.

Thus, Qing, who had taken in the fantastic scenery of Zhangjiajie, thought.

Hm. It was nice to look at.

It's cool to look at, but there's no real need to go there.

It'll probably just look like a normal canyon from below.

There's no need to go over several more mountains for no reason.

She was about to continue on her way.

"Hey there. You're not allowed to look around the terrain without the Lord of the Mountain's permission, you know? Are you thinking of just looking and running without paying for this spectacular view?"

Heads popped up along the mountain path she had climbed (although it was in such a bad state that it was hard to tell if it was a mountain path or an animal trail), followed by necks, shoulders, and chests, as if they were growing from below.

"Extorting money without paying is a crime. Right? Hmm. It's not extortion, but should it be called sightseeing without payment? Or maybe viewing without payment?"

"Keke, you are as brilliant as ever, sir!"

A burly man who appeared from behind flattered him.

All the men who appeared, filling the path, had their upper bodies exposed.

However, in Zhongyuan, it was very natural and common for men to take off their tops in the summer, so one should not be prejudiced just because they had taken off their tops.

But at the same time, they were all carrying cheap-looking weapons, specifically ones that were large, and they had high Evil Karma, so it was easy to tell that they were bandits.

"Have you ever seen a toll booth here?"

"Hmm? Another woman in a veil? Goodness, everyone and their mother is wearing a veil these days. Ah. I'm not talking about you, guest. With the Heavenly Flower Style and the Beggar Girl Style, it's all a mess because of the trends these days."

When talking about trends in Zhongyuan, they would say 'Style'.

The Heavenly Flower Style was literally the trend of Ximen Qing wearing a veil, as the Heavenly Flower Among Flowers.

The Beggar Girl Style was a trend of beggar-like clothing, entirely the doing of Peng Daesan, the Most Handsome Man Under the Heavens.

"Hehe, but I'm glad the Bared Chest Style isn't popular, sir."

"That's a good thing. But if you're going to go with the Bared Chest, you need to show your face to tell if it's a beauty's breast or an ugly woman's lump of flesh. And if you add the Beggar Girl Style to that, you can't even tell if it's worth thirty coins or not."

Qing's eyes flashed.

What? Bared Chest Style? It's popular to bare chests?

Since when?

Come to think of it, why was I stuck in the Divine Maiden Sect without even getting to see while everyone else was baring their chests?

It was early October, so the mornings and evenings were starting to get chilly, and the nights were cold.

If it's Bared Chest or whatever, by the time I reach South, they'll all be wearing winter clothes…….

"Hey hey. We're talking amongst ourselves while a guest is waiting. Now then. You have to pay for the viewing."

"How much is it?"

"Since you have to pay for the view with a view, just take off that veil for a moment. Let's have a look and if it's a spectacular view, we'll let it slide. If it's not, we'll take your money pouch as payment for the viewing, and as punishment for viewing without paying, we'll take all your underwear too."

Saying that if she's ugly, they'll strip her naked and kick her out. Since they're on a mountaintop, it was the same as telling her to die.

Looking at their Evil Karma, it seemed they had done this before. Hmm. They're already on the list for the death penalty.

I was going to pass by quietly, but this changes things.

But shouldn't they at least be a little wary of a woman standing alone on a mountaintop with a sword?

Do they have as many heads as their skills?

Anyway, it was obvious that a quarrel would start no matter what.

Qing smiled and lifted her veil.

"Oh……."

"Wow……."

"Fuck……."

Various exclamations burst out simultaneously.

It was an inevitable conditioned reflex as a man, having witnessed the harmful beauty of Qing, the most likely candidate for the Most Beautiful Under the Heavens.

Qing asked, lowering her veil again.

"Would this be enough to pay the price?"

"Hmm. It's definitely a spectacular view. But I'm still not sure. You'll have to take off your clothes for me to know."

Well. I knew you'd say that.

Qing chuckled and asked.

"And after taking off my clothes? You'll want to touch a bit, and then what? Just the tip?"

"Keke, you know it well?"

"Sure. I like touching and putting in too. But I don't have a dick, so I use a sword instead. Can I try poking you just a little bit? Huh?"

Qing smiled ominously as she drew Moonlight Sword (10th).

At that, the bandits flinched.

Of course, it wasn't because Qing had lowered her veil again, thus making her deadly smile visible.

It was because Qing's Moonlight Sword was just too big and beautiful.

The blade alone was three and a half zhangs long and as wide as the longest finger. Just from its appearance, even a man with great strength couldn't possibly draw it so lightly with one hand.

In fact, it was an absurdly heavy weapon, weighing five geuns with a large counterweight attached to the end of the hilt, made to order to be as heavy as possible.

It was just the right weight for Qing, who had become even stronger with the Dragon Elephant Prajna.

Only then did the bandits feel a sense of foreboding.

Although Yuknak Peak faced the main mountain of Cheonja on the opposite ridge, it was still right in front of the Nokrim's main base.

They never imagined that someone would dare to draw a sword right in front of the Nokrim's main base.

And usually, those who draw swords have a reason for doing so.

"Hmm. Young Lady? Perhaps your sect is……"

"Why ask about my sect? You can just tell Yama that that bitch sent you when you die."

"Damn it! Ximen Qing! Boss, we have to escape!"

Oho, they know me?

Since I had missed that rat last time, I expected the Nokrim to be grinding their teeth, waiting for me.

"Fuck! Why is Ximen Qing here! Is it an ambush, an ambush!? She came to kill me!"

At that, Qing's lips stretched into a wide grin, almost reaching her ears.

But an ambush is an ambush, but what's this about coming to kill him?

That means he's a big shot, doesn't it?

"Break through! Make way!"

Then they all rushed forward, hiding their boss from view.

It's nice of them to come to me, but…

Why are they breaking through towards me instead of running away?

Well, it was because the Nokrim's main base was behind Qing.

But Qing didn't know that.

She just thought there was a bandit's den or something on this side.

That's why she didn't bother to stop the one who took out a signal flare.

If anything, she thought, 'Yeah, bring as many bandits as you can. Bring them all.'

'Today, I'm going to thoroughly clean up this tourist spot.'