\chapter{It is easy to forget a favor, but it is hard to forget a grudge (7)}

To err is human, but to persist in error is diabolical.

The characteristic of a person who informs on others is that they insist they are never at fault, no matter what.

So, if you ever find yourself in a situation where you're informing on someone and you start with something like, 'I might be a little at fault too,' you can interpret that as objectively having made a huge mistake, on the level of a Public Enemy of Wulin.

"Ximen Qing? Wasn't there a ban on gold issued-?"

"Yes! That bitch suddenly drew her sword and started attacking!"

Dao Wusan frowned.

First of all, he was annoyed that a bastard had interrupted him, and the content that followed the interruption was not very pleasant either.

"Ximen Qing, you say. What kind of grudge does she have to come all the way here? Anyway, how many of them are there? What's their strength? Are there many Masters?"

"That bitch is alone! She came alone!"

"Alone? By herself? Are you saying that a combat unit of the Green Forest was just annihilated by a single young woman?"

Dao Wusan's eyebrows twitched.

It was true that it was a nominal unit meant to give merits to the Young Master, who led the unit in name, and to serve as his guard. But it was also a combat unit nonetheless.

Still, it was just one young woman.

Although he had heard later that she had reached the Transcendent Realm, she had just entered the initial stage. How well, how long, and how skillfully could she use Sword Force?

Looking back on his own entry into the Transcendent Realm twenty years ago, Dao Wusan had almost died from exhaustion when he tried to forcefully create Sword Force with his meager Inner Qi as someone in the Early-Stage Transcendent Realm.

The Early-Stage Transcendent Realm was such a vulnerable state that it could also be called a half-crippled state, where one would collapse from exhaustion after overusing a new toy they couldn't even handle properly.

"Hmm. She knows how to fight."

"Great Leader?"

"Look at this cruel handiwork. Would a righteous female warrior of the Orthodox Faction feel joy from slicing people up like a butcher? She must have acted cruelly to instill fear. Look at the results. Half ran away, and the other half must have hesitated in fear, watching each other's backs. It's all so obvious."

Half right and half wrong.

It was true that Qing had acted more cruelly for that purpose.

But it was also true that she had a butcherous nature.

It was regrettable that the term 'pleasure murderer' did not yet exist in the primitive, ancient, and barbaric Zhongyuan, or else it would have described her perfectly.

Dao Wusan spoke to his subordinates.

"You should all take this to heart. See how powerful cruelty can be as a weapon? She's just a fledgling who has barely reached the Transcendent Realm. She's only twenty. How much actual combat experience could a twenty-year-old woman have? If you hadn't been afraid, if you hadn't run away, if you had all rushed in at once, the number of corpses would have been the same, but wouldn't she have been captured and tied naked in front of the Chieftain by now?"

"Yes, Great Leader."

"But isn't it strange? I definitely heard that the order was to kill any bastard who tried to run away, that they should never retreat, and that they should definitely capture and kill her."

"I, I didn't run away-"

"Fear begets fear. I want you to kill this bastard in the most gruesome way possible and hang him up there. Put a big sign with his crime too. Soon, all the nearby mountain寨s will gather, and we need to show them what happens to those who run away, so they will get their act together."

"Yes, Great Leader."

"Wait. No."

Dao Wusan grinned, a sinister smile.

It was a ghastly smile full of anticipation, similar to the one Qing often made.

"I'll do it myself. It's been a while since I've seen such a blood-boiling sight."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

From the sixth peak of Mount Tianmen, if you descend to the east, you will come across a primeval forest called Yuanjiajie.

The majestic scenery, with hundreds of vertical pillars and irregular cliffs rising above the dense forest, is the image that usually comes to mind when one thinks of Zhangjiajie.

However, if one actually sets foot on the ground of Yuanjiajie, the spectacular view is not visible.

It is somewhere between a jungle and a forest, with dense trees forming a thick canopy, making it impossible to see above.

As a result, even on the brightest summer day, it is dim because the sunlight does not reach the ground.

By the time Qing descended the steep slope, the already short November sun had set.

What in the world? Even during the day, it would have been this dark?

I can't even see a single thing in front of me.

She wondered if she had closed her eyes by mistake, but when she did close them, it was as if she could see even better.

At least when her eyes were closed, she felt like she could see the faint, flickering afterimages behind her eyelids.

When she opened her eyes, it was a world of complete darkness where absolutely nothing, truly nothing, could be seen.

Since Zhangjiajie was humid all year round, when the sun set and the ground cooled, a thick night fog rose.

Even though Qing had transcendent eyesight, far beyond that of ordinary humans, when there was no light source to reflect and illuminate, nothing could be seen.

However, even though she couldn't see anything, Qing walked slowly but surely without any obstruction.

This was thanks to the Awakening Divine Arts.

The flow of water vapor was much clearer than the wind.

Thus, her spatial awareness was expanded to about twice its usual range, allowing her to walk slowly without bumping into anything or falling, almost as if she were taking a leisurely stroll.

And Qing knew that her physical abilities had transcended the human condition.

She knew that her eyesight was also like that.

So, if she couldn't see anything, how much worse would it be for the bandits?

It would be enough to just slip away under the cover of night.

Qing felt proud of herself for this.

Good. That's right, this is how I expected it to play out.

There are no gaps anywhere.

Despite having gotten lucky by chance, she was still very smug and proud of herself.

Thus, all that was left was to escape to the south, to the south…….

Hmm. But which way is south?

Of course, Qing had lived in a world without maps in her hands for a long time, so she had learned some basic orientation skills.

For starters, she could tell just by looking at the sky without much worry.

But I can't see the sky…….

If the sky wasn't visible, another method was to observe the trees.

Trees tend to have branches that extend towards the south, so the side with more lush growth would be south.

But, um, I also can't see the trees…….

Qing didn't know, but even if she could see, she wouldn't have been able to tell.

In a virgin forest that was practically a jungle, trees grew upwards, competing with each other to reach even higher. As such, they didn't particularly grow in any one of the cardinal directions.

Other methods included tree stumps, um, can't see them.

Moss on the rocks, um, it's so humid that there's moss everywhere.

"Ah shit. I'm lost……"

Only then did Qing acknowledge the fact that she was stranded.

Of course, that didn't mean she was overcome with fear or anything.

It just meant she couldn't immediately determine her direction. If she waited until sunrise, wouldn't that solve it?

So, in this situation, the wisest course of action would be to conserve her energy and replenish her stamina by sleeping soundly through the night, using her body's optimization for sleeping outdoors. And then, when the sun rose in the morning, she could determine her direction and escape.

However, this time, her thoughtless impulsiveness held her back.

The Green Forest bastards would obviously be chasing after her with burning eyes, so how could she sleep peacefully in such a situation?

Besides, it's not like I can't find my way.

It's just that I can't determine the direction for now.

If I keep walking, I might be able to get out of the forest. If not, oh well.

If I get out before sunrise, that's a win.

If the sun rises before then, I can just use the sun to determine the direction and get out.

So if I fail, there's no loss, and if I succeed, it's a win, right?

Then, isn't it a loss if I don't move now?

Besides, it's not like the forest continues indefinitely. If I just keep walking in a straight line, I'll be able to get out in the long, long night, won't I?

Of course, that would only be possible if she could walk in a straight line.

What Qing overlooked was that humans could never walk in a straight line in a forest.

And failing to get out didn't mean there was no loss, but rather that there was indeed a loss. In fact, there was even a chance that she would just walk deeper into the forest.

Wouldn't people say not to move from your spot and to calmly send signals when stranded in a mountain for a reason?

Thus, Qing's full-scale jungle expedition began.

It was a completely useless endeavor, but if one had to put a positive spin on it, the act of exploration itself was usually not very useful.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

During the battle, Qing had been splashed with a icky liquid when she was hit in the back by something that was presumed to be her own weapon, or at least something that had shattered with a ‘clang'.

Fortunately, it was nothing to be concerned about.

It was just a type of oil with a scent that humans could not detect, called a perfumed oil.

Unfortunately for Qing, the Green Forest kept many dogs trained to track this perfumed oil.

Thus, several dogs sniffed and followed the scent, traversing around the cliff on the south side of the sixth peak before climbing up the east end, where they found a steep earthen slope. Unable to descend, they barked ferociously.

Dao Wusan was dumbfounded.

So, after causing that bloodbath, she didn't even run away. Instead, she slowly admired the scenic views of the so-called Six Wonders of the Sixth Peak before hiding in the Yuanjiajie jungle.

"This is one clever bitch. And she really is bold, too. If it wasn't for the tracking scent, we would have missed her with our eyes wide open."

They would have heard the sound of the signal flares and assumed she had run away somewhere, thus heading out in pursuit along the trails.

Since she would have to wait anyway, it seemed she had leisurely enjoyed the sights. How could a mere twenty-year-old girl have such audacity?

Dao Wusan was genuinely impressed.

This beautiful act of killing, this meticulous mind, and this bold courage.

If only she wasn't an enemy who had to be killed, wouldn't she be so attractive that he would have asked her to bear his child?

Of course, since she had harmed two of the Chieftain's sons, she could never survive.

At any rate, because of this, the combat teams from each mountain寨 that had arrived at the sixth peak returned to their respective bases after witnessing the fugitive's splendid end.

It was getting late.

The bandits of the Green Forest knew all too well how deadly the mountain could be at night.

They could not enter Yuanjiajie in their current state of urgency.

The real hunt would begin tomorrow.

Instead, there was another matter of concern.

They had to inform the Chieftain of this fact.

If a subordinate was sent, what were the odds of them coming back alive, considering the Chieftain's temper?

But since he couldn't bring himself to harm a Great Leader of the Yangsanbak, he would have to report it in person.

Thus, Dao Wusan's steps were heavy as he entered the main stronghold of the Green Forest Alliance, the Chieftain's manor.

And as expected…

When the report was heard, the Chieftain raised his hand.

If he had dodged, he would have been hit even more.

So, Dao Wusan just stiffened his neck as he waited for the blow to land.

"No, it's not your fault. Huuek."

Surprisingly, the Chieftain actually managed to hold back!

Dao Wusan's eyes widened.

It was an astonishing sight for the Chieftain to suppress his temper, but what was even more astonishing-

The Chieftain was crying, no, he was shedding tears of blood.

"Brother."

"That bitch, that bitch will be used to perform ancestral rites. No, I will chew her up alive. I will keep her alive and chew on her, starting from her fingertips and toes. When she begs me to kill her, I will throw her in the piss pot. Hey, brother. What will happen to that bitch then? Will she drown in piss? Will she drown? Or will she be too scared of drowning that she'll drink it all up and burst? Or will the poison in the piss kill her first? I'm curious, aren't you curious?"

It was the resentment of a father who had lost two children.

The words he spat out while shedding tears of blood, with burst blood vessels in his eyes, were filled with deep-seated venomous spite.

"No, there must be something more miserable, right? Yes, since she's a woman, I'll just hang her up during the day. What do you think? Will those bandit bastards try to fuck a dirty woman, soaked in piss and reeking of urine, just because she's pretty? Aren't you curious?"

"Brother."

"Yes. I know. If we capture her, many will die. But Wusam, I have a favor to ask of you. Okay?"

Dao Wusan looked at the Chieftain's trembling hands and the tears mixed with blood dripping from his chin.

So what other answer could he possibly give?

"……I will follow your orders."

It was something that happened while Qing was wandering through the virgin forest, completely unaware.

Thus, the eve of the decisive battle.