\chapter{It is easy to forget a favor, but it is hard to forget a grudge (5)}

In the past, there was a time when everyone in Zhongyuan was a
bandit.

It was a turbulent time when Zhongyuan was divided and various
factions fought against each other.

Armies fought amongst themselves.

Sects aligned themselves with the Orthodox, Righteous, and Demonic
factions, but as soon as they drove someone out of a region, they would
change their stance and fight amongst themselves.

Even the common people banded together in villages to raid
neighboring villages, looting their warehouses and women. And the
men would be castrated and enslaved, as if this was a completely
normal occurrence.

Banditry was so commonplace then.

And those who were not bandits were considered abnormal.

At that time, there were bandits in the mountains, water bandits in the
rivers.

There were horse bandits in the plains and pirates in the sea.

It was an era of turmoil throughout the world, where everyone fought
against everyone else, biting and clawing for survival.

As such, it was only natural for the great minds of antiquity to view
humans as the most savage, cruel, and wicked of all beasts.

And they had no choice but to acknowledge the importance of the Son
of Heaven, or more precisely, the importance of a unified dynasty.

Therefore, the philosophy of Zhongyuan fundamentally
regarded people as evil, and the existence of the Emperor as an
unavoidable and necessary element to control this evil.

If the Emperor did not rule with benevolence, the people of the world
would become endlessly selfish and wicked, never ceasing to devour
one another.

The people of Qing’s hometown might not understand this, but if the
Emperor was replaced with a lawful government recognized by the
international community, it might become a bit more relatable.

At any rate, when a dynasty unified Zhongyuan, these bandit
groups gradually subsided, and the world found stability.

However, just like the five characters that make up the saying, ‘No
flower blooms red for ten days’, when a dynasty lasted long, the world
would once again be infested with bandits.

It was an omen of the dynasty’s downfall.

Fortunately, the current dynasty was given a chance, as the Celestial
Martial Emperor, praised as the Greatest Under Heaven, had crushed
all the major bandits in the world.

Now, horse bandits were hard to find.

Unless they were barbarian raiders from the north on horseback, no
one in Zhongyuan dared to ride horses in groups while carrying
weapons. After all, doing so would only attract the attention of
government officials who were eager for a chance to seize such
expensive horses.

And water bandits had given up being water bandits.

According to Bok Haun, the leader of the Forts of the Yangtze River
Waterway, they would give up being water bandits! And transcend
beyond being mere water bandits!

But at their core, bandit groups were nothing but a bunch of bastards
driven by their primal desire to do whatever the fuck they wanted.

As the Forts of the Yangtze River Waterway transitioned from a band of
robbers to a legitimate business managing the Yangtze River, such
individuals were expelled. And recently, even those who were on the
fence had revealed their true colors, leading to a bloodbath.

As a result, their combat capabilities had drastically weakened a long
time ago, but due to the unique nature of naval warfare, they were still
barely able to maintain control of the Yangtze River.

It could also be said that Bok Haun had foresight, as the gap between
the shipbuilding technology of the private sector and that of the
government was gradually widening. If things continued, just a few
warships would be enough to annihilate the entire fleet of the
Waterway Forts’ warships.

Pirates were just pirates.

They were like swarms of locusts, pests that kept coming back no
matter how many times they were dealt with. They were incorrigible
vermin that everyone just accepted as a fact of life.

And then there were mountain bandits.

Mountain bandits still boasted great prosperity.

First of all, there were no expeditions to subdue them.

Since there was no particular benefit to suppressing them, the
government did not mobilize. In fact, they saw it as a loss because if
the roads in Zhongyuan became safer and the common people
could move freely, it would only make it harder for the government to
rule.

Secondly, their numbers were vast.

It was incredibly easy to become a mountain bandit. If a group of
travelers crossed a mountain pass together, drugging, backstabbing,
killing, and looting was enough to make it a successful career change.

Moreover, if one expressed the slightest desire to become a bandit,
they would be welcomed into the fold without any questions asked. It
would not be an exaggeration to say that joining the Greens was more
of an announcement than an application.

Thirdly, there were unexpectedly many Masters among them.

One might ask why someone would resort to banditry when they could
be respected and live well as a Master.

However, first, there were many evil souls who wanted to wield their
power as they pleased, as much as they were strong.

And most importantly, where else would fugitives go, those whose
faces and names were known and who would be killed on sight if they
roamed Zhongyuan?

The Unorthodox Faction didn’t accept just anyone, as they knew how
terrifying grudges, especially those from Zhongyuan, could be.

And the Demonic Cult was too far.

The Blood Cult… Well, even they had their limits.

So, all that was left were the mountain bandits.

Build a house in a place blessed by nature with good water and fresh
air, lead some underlings, and live like a king in a small kingdom.

What a splendid plan it was.

It was easy to find underlings who would lick anyone’s boots if they
were taught a bit of martial arts.

Just by showing a little bit of sincerity to the Greens, one could also
easily acquire a banner.

Thus, the Greens flourished.

This was the rise and fall of the Greens.

As they flourished, their audacity grew and their misdeeds increased.

Then, when they crossed the line, they would be thoroughly
suppressed and scattered, after which they would disband, go
independent, and enter a dark age where they struggled to survive.

Then, when some Master shouted, “Greens, assemble!”, a new Greens
would emerge. And so on and so forth.

In that sense, the current Greens were in their golden age.

Since the Celestial Martial Emperor did not bother to deal with
insignificant mountain bandits, they had actually grown in power while
the Imperial Palace, the Unorthodox Faction, the Demonic Cult, and
the Blood Cult were all weakened.

Many of those who had fled from the Celestial Martial Emperor joined
the Greens, significantly raising the level of their martial arts.

Of course, if the Celestial Martial Emperor heard this, he would have
immediately punched whoever said it.

Aren’t the Greens also part of the Unorthodox Faction?

If I crushed the Four Pillars, then I crushed them as well, so why would I
bother to deal with each and every small fry?

Should I have sought out every single Unorthodox Faction sect and
eradicated their lineage?

Aside from the old stories, in recent times, those who lost their jobs due
to the Waterway Forts’ business transition had flocked to them in large
numbers, providing them with a significant boost in usable manpower.

In such a situation, how high would the prestige of the Greens’ leader
and Chief Inspector be?

And yet, a mere young girl from the Divine Maiden Sect, a sect they had
barely even heard of, dared to kill his son.

It was only natural for him to feel a sense of audacity.

Moreover, she had looted gold and silver from the bandits.

This was also a serious challenge to the authority of the Chief Inspector.

But how could Qing know about such circumstances?

Even if it wasn’t Qing, it was a time when no one cared about the
current state of the Greens.

Everyone just thought of them as bandits who would appear again even
if they were removed, so of course, their power had to be at an all-time
high.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Honk!!

Hoooooooonk!!

Amidst the sound of a horn being blown with all his might, Qing yelled
out excitedly.

“Let’s go, Moonlight Sword! Our first customer since starting our Wulin
journey!”

Qing’s Moonlight Sword (No. 10) received its first customer.

The first victim of the new sword was split in half at the heart.

If one asked how the blade, which entered through the crown of the
head, could split the heart in half, Qing would answer as such.

With great strength, a good sword, and Sword Force!

The bandits doubted their eyes at such a brutal display.

Of course, 80\% of Qing’s cruelty was because she enjoyed it. It was the
only drug that the nation had allowed (it hadn’t), so she couldn’t stop
herself from indulging in its thrilling pleasure.

The remaining 20\% was because, having lived in Wulin, she knew that
being cruel was a good way to gain an advantage in the early stages of a
fight.

It made the entire battle much more favorable.

Among the rules Qing had set for herself was that once the sword
entered, it could not exit the same way.

The sword that entered through the crown and split the heart exited
through the side.

Half of a half of the body fell to the ground.

The remaining half and a half of the body seemed to kneel, collapsing
limply.

“Hiiieeeek! A-A monster!”

There was someone among them with a weak stomach, so his morale
was instantly shattered, causing him to turn and run.

However, it seemed he was far too afraid.

He was so terrified that he left his body behind and only his head flew
into the sky in an attempt to escape.

The bandit leader? The one who helped the head escape, swung his
broadsword, flicking away the blood, before shouting.

“Anyone who flees will die by my hand! Kill her! If you don’t kill her,
you’ll die anyway!”

It seemed that the leader was just a figurehead, a precious person who
was useless in battle, and that this guy was the real deal.

Well then, let’s have some fun.

Qing dashed forward, leading with her long sword.

Stab, one guy. Stab, another guy.

Qing continued to push forward, skewering two men on her sword.

Suddenly, she felt a grip.

The guy skewered in the front grabbed Qing’s hand.

At the same time, there was a desperate look in his eyes!

Thud!! Qing headbutted him.

Aaaagh! The sweet scream that followed. Crunch. The sensation of
the nose bone being crushed. Wow, wow, wow.

I never knew headbutting was this good…….

Since two men were skewered, Qing’s speed was halved. But it was
already fast to begin with. The valor of charging forward with two
people skewered remained the same.

The two skewered were nothing but a burden, as well as a shield.

The bandits attacked, but there was a human shield in front, while
attacks came from the left and right.

Thump. A blade struck her shoulder, stinging.

But it would probably just be a scratch.

Ignoring it, Qing gritted her teeth and accelerated further.

From the Vice-Leader’s perspective, it was quite a sight.

The blade, protruding from the back of his subordinate, was
approaching.

He had managed to stop one of his men from fleeing by cutting his
head off.

But the sight of the others, who were just standing around, looking at
each other and maintaining their distance, was not very proactive.

The Vice-Leader pushed the leader roughly.

“Go!”

“Uh, okay.”

At the same time, the Vice-Leader drew upon his Dao, summoning his
Inner Qi with all his might.

Against a Transcendent Expert, it was meaningless to have many
people.

However, if he let the leader die, he wouldn’t be able to live in the
mountains and would have to flee down below, only to be killed.

If he could just buy some time, just buy some time…

Thus, the sword impaling two people was right before him.

Only then did the Vice-Leader realize a major problem.

Where should he even cut?

To slice a person like tofu, a Divine Weapon or at least Sword Force was
needed.

A broadsword with just Dao Qi could not cut through three people at
once.

“Damn it! The net! Throw the net!”

The Vice-Leader shouted as he flew to the right.

Since the sword was charging straight ahead, the sides were wide open.

He barely managed to slip past his subordinates’ shoulders and swung
his raised broadsword downward-

Whooosh!

The sound of cutting through the air was vicious.

However, the broadsword cut through only empty air.

Oh shit.

In the Vice-Leader’s eyes, he could see his two subordinates impaled
and collapsing.

Ximen Qing, that wicked bitch, had just dropped her sword.

Dropped it? Where?

In that instant, time slowed down, a testament to his concentration as a
Peak Expert.

Above the head of his collapsing subordinate (the one in the back).

He could now see an oddly shaped shoe with only a thin front sole
suddenly coming down.

And in an instant, a thick, black Inner Qi gathered at the tip of the foot,
exploding the head like a watermelon. Amidst the slowly scattering
fragments of the shattered head, the figure was already flying away,
having used a person’s head as a stepping stone to trample on with
Stomping.

In the slowly flowing time, only Qing flew swiftly through the air.

The leader, who had turned to run, looked back, perhaps sensing
something. An expression of terror gradually spread across his face.

“Aheuuuun---”

The Vice-Leader let out a slow scream.

In an instant, thud, the leader’s foot caught on a rock.

The leader, who had been running desperately, tripped and flew
forward, headfirst.

This was why one should always look ahead while running.

As a result, Qing’s hand, instead of pushing her back, pushed the empty
air.

It was a good thing to look back every now and then.

At this, Qing’s left hand quickly reached for the back of her head,
grabbing a binyeo and throwing it.

The flying binyeo struck the leader’s calf. It missed!

Whether the miss was due to a lack of aim from throwing it in a hurry
or whether Qing’s skill with throwing weapons had reached the level of
precision that only the most elite of the human race could achieve was
unknown.

I got him! The leader can escape!

At the same time, time finally regained its speed. The Vice-Leader’s
scream, which had been filled with tension, now burst out in a joyful
roar.

“--die!”

But the problem wasn’t the binyeo.

The leader was a human projectile launched headfirst, a 13,333-geun
cart rapidly descending a steep downhill with no brakes.

At the end of that trajectory was a massive boulder.

It was a beautiful flight, almost like a performance art expressing the
human will to resist nature by trying to smash a rock with one’s head.

However, it was clear that one should always look ahead while running.

And they should never look back, even occasionally.
