\chapter{It is easy to forget a favor, but it is hard to forget a grudge (6)}

Nokrim spread its influence throughout the entirety of Zhongyuan, and thus, their numbers were vast.

Moreover, they had quite a few experts in their ranks, which allowed them to collect a variety of martial arts.

Even with just this, they were acknowledged as a force to be reckoned with in Zhongyuan, but…?

However, the reality was that they were not.

First of all, they were a group of lowly villains, just a bunch of bandits. Furthermore, Nokrim had a critical problem unique to them.

A wise person would not engage in banditry.

Conversely, this meant that those who engaged in banditry were either born with an unfavorable disposition or were fugitives due to their lack of wisdom, ultimately making them all good-for-nothings.

And wisdom usually came with intelligence.

Of course, it wasn’t always the case, but generally, it was so.

“So, tweet tweet tweet tweet, attention, tweeeet tweet, tweeeet tweet, right, tweet, tweeeeet, tweet, tweeeeet, is this left? Tweeeetweeettweeettweeetweeet, uh, what was it again? Was it wrong? Tweeeettweeettweeettweeetweeet?”

“Was right tweet tweeeeet? Or was it tweet tweet tweeeet?”

“Fuck, can’t he just shout tweet tweet tweet tweet right!? Why make it so complicated when everyone can hear if their ears are open?”

Flag signals or hand signals were discreet but had the drawback of needing to be seen.

Sound signals like whistles and drums were noisy, but they had the advantage of being able to convey information as long as one’s ears were open.

However, both had a major drawback; both the sender and receiver of the signal had to memorize a prearranged signal system.

It made those teaching it want to burst a blood vessel.

“Fuck! These thick-headed bastards! This won’t do!”

Thus, Nokrim’s signal system gradually became simpler and more crude so that it could be memorized more easily.

As such, the most important signal for requesting support during an enemy attack, meaning ‘a very, very big incident has occurred’ and ‘help’, had also become crude.

“Just blow the fucking thing as hard as you can! Blow it with all your might, with all the strength you’ve been saving since sucking on your mom’s tits, so that anyone who hears it will know that something has happened.”

Thus, the violent sound of a whistle, Tweeeeeeet! Tweeeeeeeeet!, continued to ring out from the moment Qing initiated her rampage with the very first display of Moonlight Sword Form Ten.

It was understandable that those in the midst of battle would be desensitized to noise, but to the bandits lazing around in the stronghold, the sound was quite annoying and bothersome.

“Jeez, which bastard is making so much noise?”

“He must be bored.”

“Fuck, does he think people only sleep at night? What about those who sleep during the day? Shouldn’t he be more considerate?”

Originally, the long-standing tradition of Nokrim was for the senior to sleep while the junior remained quiet in a two-man team for the daytime watch.

So, shouldn’t he be considerate of those who sleep during the day, following tradition?

Which bastard was disturbing the sleep of his fellow bandit?

And as such, it took quite a while for them to realize that it was an emergency signal.

The lookout frowned, thinking, Tweeeeeeet, it seems to be coming from the direction of Six Mounds Peak. Who’s there? Which bastard is it?

Then, suddenly…

“Isn’t this… an emergency signal? The enemy has attacked.”

“Eh? No way. Who would be bored enough to…….”

Tweeeeeeeeeeeet!

The senior bandit’s complexion darkened.

“Fuck, something must have happened. What should we do? What are we supposed to do again?”

“Should we ring the bell first?”

“What if it’s nothing? No, ring it. But I’m not taking any responsibility.”

“Uh, then should I wait and see how the situation develops first-“

“Are you trying to goof off, you bastard? Are you not going to ring it right now? Do you want me to ring your head instead?”

In this order, the warning bell rang, Clang clang clang, hurry and gather, what’s with all the noise, do you want to die, that’s not it, it’s the whistle, what whistle, um? A whistle?

Oh shit, something must have happened!

If a signal was received, a response had to be sent.

Either ‘Going now’ or ‘Not going’.

Unless there was an unavoidable reason, a request could not be refused, so naturally, a signal had to be returned, saying that they would go, so hold on.

Thus, a signal firework was shot.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Thwack!!!

A painful sound rang out.

At this moment, everyone had to flinch, grimacing at the sound.

Even the one blowing the whistle with bulging eyes was momentarily distracted by the magnificent challenge against nature, thus looking at the outcome of the battle between man and rock.

However, the era was still primitive and ancient.

It was still too early for humans to triumph over nature.

If humans were to conquer nature, uprooting forests, destroying mountains, raising the earth’s temperature, devastating green lands into deserts, and etc…

Nature, this is the greatness of man. If you don’t listen, the ecosystem will die. Just now, because you caused a tsunami, I raised the sea temperature by two decimal points. If you want to save the environment, you better lower the temperature yourself and obey humans.

It would still take some time before such aggressive environmental protection would arrive.

At any rate, the result was, um… A draw?

The Headman was slumped over, but his limbs were twitching faintly, so it seemed his windpipe hadn’t been severed.

And since the rock was also unharmed, it was appropriate to call this duel a draw with both surviving.

At this, Qing, who had suddenly drawn everyone’s attention, reflexively denied it.

“I, I didn’t do it. You all saw it too, right? He was cowardly and tried to run away on his own, then tripped over his own feet like an idiot. I didn’t push him. I’m not someone who shoots palm strikes from my hands, I mean, I do shoot palm strikes, but I didn’t this time. I threw a dart, but it missed. And I didn’t really intend to kill him, I was just going to use him as a hostage until I could escape and play with him a bit-“

“Young Master!”

The Vice Headman, who had snapped out of his daze at her babbling, rushed to the Headman and held him.

Seeing the Headman’s head slumped over, Qing urgently advised.

“Wait! His neck bone is broken! If you touch him now, he’s going to die? You need to fix it with a splint and carry him carefully on a stretcher.”

Qing was a skilled physician recognized by Physician Wang.

In fact, if a physician was recognized by someone of Physician Wang’s level, they would be considered a decent doctor, good enough to open a clinic in some rural area.

However, the customs of Zhongyuan did not permit female physicians, and Physician Wang was also a man of the Central Plains who could not help but be bound by such customs, so he did not recognize Qing as a physician.

As such, only female physicians whose status was higher than the customs of Zhongyuan could be born.

Like Tang Nanah, who was supported by the Sichuan Tang Clan.

Anyway, upon hearing the medical advice that he would die, the Vice Headman immediately laid the Headman down.

The Headman’s head was swollen like a mountain, with his head twisted in a funny, asymmetrical manner. He needed treatment quickly.

The Vice Headman hurriedly asked in his urgency.

“Ah. Then, how should we apply the splint?”

“You need to figure that out on your own. Do I have to do everything from one to ten for you? Are we even that close?”

“Wait, this person is actually-”

“Agh! So frustrating! Why does no one do anything by themselves? What do you even think of me? I came here to fight you, not to play mom! I’m tired of this now. Let’s just end it he-”

“Wait! Hear me out-“

“Martial artists speak with their swords! I’ll tell you how to apply a splint with my sword! Open your ears and listen! Sword, come here, no, my sword. I mean, hand, come here!”

It was at the very moment when Qing raised her knee high to stomp the ground with True Qi.

Piiiiiiiiiiing-!

An unusual sound that she had never heard before pierced Qing’s ears.

It was the sound of a signal arrow, also known as a sounding arrow.

It was made by attaching something similar to a whistle to the arrowhead or by making a hollow arrowhead to produce a whistling sound as the wind entered.

What’s this? I have a bad feeling-

Piiiiiiiiiiing-! Piiiiiiiiiiing-! Piiiiiiiiiiing-! Piiiiiiiiiiing-!

Before Qing could finish her thoughts, the loud sounds of arrows flying from all directions, east, west, south, north, everywhere, were linked together endlessly like a trail of tails.

Qing let go of the posture that made her seem like she would charge at any second and slowly took a step back, asking.

“Um. Just in case I’m wrong, that’s not something like a whistle, is it? Net of Heaven and Earth? Something like that? With people saying they’re coming here?”

“Th-That’s right! Surrender the Young Master right now! Then you might be able to keep your life-“

“Ah shit. It seems like it’s for real.”

It was too many sounds to ignore.

And it was coming from all directions.

If she stayed here, she would really be surrounded by hundreds of people.

It was a shame, but the game was over. She couldn’t even have a proper party and had to end it here.

Qing made up her mind.

It was a moment for a strategic withdrawal!

Qing threw herself back.

At this, the Vice Headman urgently shouted.

“Damn it! Catch her!”

Qing pulled out a skewer from a person lying on the ground.

Come back! Moonlight Sword!

Qing held the Moonlight Sword (X) in her hand and slashed at the approaching enemies.

The absurdly heavy weapon, weighing as much as five geun1, sliced through human torsos cleanly.

Five geun might not seem like much, but for a melee weapon, it was an enormous weight.

Even the large two-handed greatswords used by Westerners did not exceed four geun.

And this was a long, one-handed weapon weighing five geun.

When Sword Force was added, its destructive power swept through the space, as violent as its length.

If an arm was caught, an arm was severed. If a leg was caught, a leg was severed. If a torso was caught, a torso was severed.

Even if weapons were caught, the weapons were cut through. As such, a man who had raised a battle-axe with both hands was split in half along with the axe’s handle, spilling out to the left and right.

Wow, why is it cutting so well?

Was it because Old Man Ban stopped making weapons or whatever? Did he hide such skill until now?

As the sword cut so well, a subtle excitement and joy surged within her.

She swung the sword downwards and upwards in simple motions.

A bandit stood staggering, and a precise strike thinly sliced off his arm, as if he was a piece of meat being prepared for display.

Clack clack clack clack. Thin slices of a human, that should have been exhibited in some mysterious exhibition, piled up neatly on the ground.

This is, ah, seriously. Phew, phew.

It was at that moment when Qing felt a bit dizzy and staggered slightly.

Whoooosh, something flew in from all directions, wrapping around Qing’s senses that encompassed all directions. Uh, is there no way to avoid this?

Powerful Sword Force split the air.

Tududuk, there was a continuous sensation of something being caught and cut.

But that was it. As she wrapped herself with her arms, she suddenly felt familiar. Ah shit, a net.

However, this was not the same Qing who had floundered helplessly in a net in the past.

As she thrashed around, wrapped in the net, she stomped her foot and scattered her White Hand, causing the shoulder of a bandit who had rushed in, thinking this was his chance, to collapse as his arm fell limp.

But it was cumbersome.

Every time she moved, there was a loud Tududuk sound of something being torn, but the net, seemingly coated in tough glue, stuck to her, making it difficult to move.

She stomped the ground roughly, but her next step was caught in the net.

Suddenly, a force yanked at her shoulder; she had pulled her own shoulder with her monstrous strength.

She staggered but barely managed not to fall thanks to the monstrous strength of a Demonic Adept. As she steadied herself, tearing the net with a Tududuk sound, something else flew in and struck her back.

Clang, the sound of porcelain breaking, and her back felt damp as if some liquid had been poured on her.

What the! What’s this sticky, gross feeling? What is this? What’s going on! What is this?!

Qing’s eyes flashed with a ferocious glint.

What did these fuckers just pour on me?

Letting go of the sword entirely, Qing grabbed the net with both hands and tore it apart with a Tududuk sound.

It was an astonishing sight to see someone tearing apart a tightly woven net as if pulling apart long strands of grass.

“Damn it! Throw more nets!”

“We’re out of nets!”

“Why are we out?! You’re supposed to bring three!”

Originally, according to the regulations, each patrol team was supposed to carry three nets, but who would carry three of those heavy things around?

If they carried all three nets, they would be ridiculed, just like a soldier in Qing’s homeland being mocked for carrying a full FM loadout.

“Attack! Attack, I said!”

“But…”

The fragments of people scattered around the net-tearing monster made it a terrifying sight that no one dared to approach recklessly.

“Attack together!”

The Vice Headman shouted and charged.

His momentum was impressive.

But no subordinates followed him.

To Qing, it seemed like the loyalty of bandits was just about this level.

However, the Vice Headman was oblivious to this fact.

Sword Qi was imbued in the blade, and a powerful strike from a Peak Realm martial artist, filled with all his might, rushed towards Qing.

The moment the greatsword rushed towards Qing…

The Vice Headman could almost hear the triumphant declaration of his Chieftain.

He might even be willing to listen to anything.

Perhaps he could ask to be promoted to Senior Patrolman? Or perhaps he could say he wanted to leave this place and set up an independent stronghold? Or maybe gold? Women? His daughter was quite beautiful, wasn’t she?

But the happy imagination was short-lived.

Crack!

The Vice Headman doubted his eyes.

It was the blade of a Peak Realm martial artist, imbued with Sword Qi. Moreover, it was a strike from a muscular man, swinging with all his might and adding his body weight to it.

The greatsword slid along the tilted back of her hand, and sparks flew with a metallic scraping sound.

It was only then that his heart sank.

He should have realized the moment she casually reached for the blade without a moment’s hesitation.

And then, a white hand grasped his wrist.

The Vice Headman looked at Qing with trembling eyes.

Qing’s eyes, shining with an ominous, flickering light beyond the veil, met the Vice Headman’s gaze.

“Argh!!”

Suddenly, there was an absurd amount of force squeezing his wrist.

He screamed without realizing it.

Could mere flesh and bone withstand such a grip that could crush even iron?

Qing clenched her fist completely.

As she did so, the sensation of pulp oozing out between her fingers was, ah, truly indescribable.

The Vice Headman’s greatsword fell to the ground, and his right hand, severed at the wrist, tumbled beside it.

The Vice Headman screamed, clutching his mangled wrist, and the bandits, horrified, all turned to flee at once. 