\chapter{It is easy to forget a favor, but it is hard to forget a grudge (2)}

News in Zhongyuan traveled slowly.

The fastest way to deliver news was to send a person directly, and the less fast method was to entrust a letter to a merchant or acquaintance heading in that direction.

Other than that, one should expect the news to be delayed.

News could be delivered without a person.

However, it spread from mouth to mouth, and only after hearing the rumors would someone go to confirm the facts. Then, one had to account for the time it took to return after confirming the information.

Thus, this was the plight of large organizations in Zhongyuan.

The news was slow.

So, did the Wulin Alliance have any special measures?

No, not really.

Unusual events were taking place in the southeastern part of Zhongyuan, but they needed to hear the news first before they could decide whether to respond or not.

Separately, an agenda to help the Orthodox Factions in the southeastern region of Zhongyuan was adopted at the Wulin Assembly.

And through the meeting, it was decided that the method would be to dispatch the Rising Stars of prestigious families to each region.

Just having the Rising Stars of prestigious families stay at the Orthodox Faction's sects in the southeastern part of Wulin would put great pressure on the local Unorthodox Factions.

After all, most Unorthodox Factions were just gatherings of vagrants without any foundation, lacking tradition and history.

To put it more harshly, it would not be an exaggeration to say that they were just clubs formed around a high-level martial art that they happened to acquire by chance. And even then, they were just clubs of thugs.

Therefore, even if they exerted some power in the local area, they were no match for the Nine Great Sects and Ten Great Families.

So, if the Rising Stars of prestigious families appeared, they would have no choice but to lie low and watch their steps.

Moreover, this allowed the Wulin Alliance to show off and make a good impression.

When the disciples of the most prestigious Orthodox Factions in Zhongyuan, whose names alone made hearts flutter, stepped forward, how could the local sects not be delighted?

If the dispatched local sects had to choose between a combat unit and a single Rising Star, they would naturally choose the latter.

After all, what was the point of being a local sect if you couldn't even handle that much?

If there were too many people, it would be quite burdensome for a small sect, and it would be difficult to accommodate them for a long time.

However, one or two Rising Stars were not that burdensome, and it was all about connections! A chance to make some!

So it was good for the Wulin Alliance and good for the local sects.

Though, the opinions of the dispatched Rising Stars should also be considered.

However, even if they voiced their opinions, the elders would just think, 'What's the problem? You'll be well taken care of and have fun. Why are you even complaining?', thus making it pointless for the Rising Stars to open their mouths.

However, from the perspective of the Unorthodox Factions, it was ridiculous.

Of course, they had no intention of touching the Rising Stars and getting themselves utterly destroyed, but what if they went crazy and decided to go down fighting?

Do you think we're that much of a pushover?

That's right. They were pushovers.

Peace had lasted for a long time, and it was because the Unorthodox Factions dared to act out, underestimating and looking down on them.

Most tragedies in history were caused by complacency.

However, humans were foolish and stubborn creatures who only realized they were complacent after a tragedy had already occurred.

At any rate.

For these reasons, it was decided that the prestigious families and renowned Rising Stars would be dispatched to the southeastern part of Zhongyuan.

The Wulin Alliance's Military Advisor Division's Assistant Advisor, Sama Chunbong, who was in charge of creating the dispatch list, began to write down names with swift strokes.

Although it seemed like she was writing carelessly,she was not doing her job carelessly.

Individual's martial prowess, their importance within their sect, the convenience of the travel route, whether their personality would match well with the dispatched sect, and whether they had the intelligence to handle unexpected situations, and so on.

She was matching all sorts of information stored in her head to assign the best locations.

In fact, Sama Chunbong was a capable person who could do just that.

However, her behavior was eccentric and bizarre, and she had not an ounce of dignity, being as light as a feather, so she was treated poorly.

While writing down names, Sama Chunbong paused.

Let's see, Ximen Qing, Young Lady Ximen.

The lifelong rival who would contend for the position of the most talented woman in Wulin, no, Zhongyuan, no, all under the Heavens. No, not a rival, but a training partner. Yes, that's right, a training partner!

Of course, in terms of beauty, it's a narrow victory for me.

Young Lady Ximen is quite tall for a woman, so I win by a finger's length.

Yet, when sitting, I am taller, so the advantage in terms of authority and dignity that comes from the sitting posture and the visible field of view is also my victory.

However, as for the lumps of flesh on her chest, well, if it was the me of the past, I would have declared defeat. But now that I know those things are just pockets of talent, it's also my victory.

In terms of the schemes in my head, there is no need to even mention that it's my victory, and as for our backgrounds, if we compare the Divine Maiden Sect to the Sama Clan, it's my victory as well, though only by a short length since we were once a dynasty.

Only in individual martial prowess did I concede defeat, but since strategists command generals, strictly speaking, this is also my victory.

"Huhu. Young Lady Ximen. You are still no match for this young lady of Sama in all aspects. You must strive harder. At this rate, you might be dropped from being my training partner."

If Qing had heard this, she would have been utterly disgusted.

The problem was beyond the fairness of the criteria for determining victory or defeat.

She wouldn't want to be friends, much less even be involved, with a bitch who cackles ominously to herself in an empty room.

Anyway, Sama Chunbong, who had briefly thought of her only acknowledged competitor-

"No, no. A competitor, you say? Since she's not yet my match, I should call her my follower. But this feeling of someone chasing after me. Huhu, it's not so bad."

If the Military Advisor Division's Advisor, Assistant Advisor, and Vice Advisor had seen and heard this, they would have said, 'That bitch is at it again.'.

And if the Military Advisor Division's staff members, who were technically Sama Chunbong's subordinates, had seen and heard this, they would have thought to themselves, 'That bitch is at it again.'.

They just put up with her because she was good at her job and had a relatively good nature.

She was treated like a younger sister who was strange but kind, though her condition was quite severe, thus making her seem a bit crazy.

Anyway, Sama Chunbong, who had briefly thought of the only competitor she acknowledged, wrote down Qing's name.

「Guangxi Province, Nanning County, Guilin Sword Sect - Ximen Qing」

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Her daughter was not suited for the Imperial Palace from the start.

She never got used to the etiquette, and she always said that the palace ceremonies were stuffy, dreary, and boring. She couldn't stay still for even a moment.

On the other hand, she was so kind that she feared the fear of her subordinates, who would turn pale and beg for mercy at the slightest mistake. And yet, she had a surprisingly sharp eye for people, thus growing disgusted with those who hid their true intentions and flattered her.

From the way she ate to every single movement, it was all like the rough and tumble martial artists of Jianghu; her movements were large, bold, and spirited.

If she had been a man, her personality would have been praised as manly. But because she was a woman, she was scolded for not being feminine, receiving a scolding almost every single day.

That was probably why she had fallen ill.

Since the palace was her home, but she could never be comfortable in her own home, it was only natural for the young girl's heart to become sick and bedridden.

Her illness grew worse, and her once beautiful face became so twisted and distorted that it was unrecognizable. Moreover, she was conscious for fewer and fewer hours a day.

Then, perhaps sensing something herself, just before she lost consciousness altogether, she desperately called for her mother and managed to utter one last sentence before rolling her eyes back and fainting.

'Mom, just have one more daughter. Then I'll be reborn and be your daughter again. Thank you, and I love you.'

And yet, that very daughter had returned.

They had met in front of the largest Buddhist temple under the heavens, so was this the work of Buddha's benevolence? Or was it because she had registered in a Daoist sect and her expression was bright, thus indicating that the Daoist Immortals had helped? Perhaps they had all helped.

Thus, the Empress' affection for her was so deep that it could not be described with mere words.

Drrr, Qing, who was sleeping on her lap, snored quite loudly.

She found it endearing that her daughter snored like a man, almost to the point of tears.

Indeed. It was this very aspect of her.

Her returned daughter didn't seem much like her daughter at all.

Now, she knew what it was.

Every gesture, every smile, every little detail, such very trivial details were off, so her mother could not help but feel strange.

And so, she resolved once again.

She wanted to live as Ximen Qing, the female martial artist of Wulin?

Then so be it.

As a mother, how could she force her daughter to live in the uncomfortable Imperial Palace again just to keep her close?

But…

No matter how stifling and difficult the Imperial Palace was, it was still a palace that soared above the sky.

Even if one said they were free, it was only on the ground under the sky, so how long could a noble from the heavens enjoy herself among the lowly?

You will surely change your mind. So, I must prepare so that you can return to your place, your original place, at any time.

The Empress' eyes flashed ominously.

The Empress was also the mother of all people under the heavens, who had seized the position of being below only one but above all others through the well-worn power struggles of the Imperial Palace.

But soon, the look in her eyes disappeared, replaced by an affection that seemed as if she could not love her daughter enough.

The Empress stroked Qing's hair.

The date announced to the Imperial Court for the ancestral rites had almost passed, so they would have to part soon.

Why did happy times pass by so quickly?

It is fine even if you never remember.

Even so, that you are alive and breathing is the greatest grace to me. My daughter.

The Empress' sincerity was such that just Qing breathing was enough to make her feel happy and blissful.

If Qing had hit and beaten the Empress, committing an act of great disrespect, she would have just laughed and said, 'My little piglet's slaps are quite spicy. Well done, my daughter.'

So how could Qing possibly resist and not fall for her?

Moreover, the more she was like Princess Yeonseol, the more unstable Qing's mind became.

Why is Princess Yeonseol like me? Is this world created by someone?

Or was the Empress designed and made that way?

Design? What is this world? Where am I?

What am I?

But she couldn't bring herself to push away the Empress.

When she felt uneasy, she naturally relied on the motherly figure who clung to her closely and devoted herself to her.

Besides, Qing was originally weak to affection.

She was a pushover who had fallen for the Great Demonic Adept Choi Leeong, who was full of Evil Karma, and even for Gyeon Pohui, an idiot who accumulated Evil Karma because she was stupid.

And as could be seen from the time with Gyeon Pohui, under boundless affection, Qing's manners plummeted in inverse proportion.

Qing's attitude towards the Empress gradually relaxed until she reached a point where she didn't even lift a finger.

Even at the dining table, she would stick a chair right next to the Empress, lie on her lap, and just eat whatever was fed to her.

So, the grown-up daughter, and in many ways, an excessively grown-up daughter, acted like a spoiled baby.

She didn't do anything on her own, so she had to be fed, dressed, washed, and put to sleep, acting spoiled and throwing tantrums.

In fact, it wasn't an unfamiliar experience for Qing.

Previously, at the Demonic Cult, Support Unit Yi Ho had done exactly that. Though back then, she at least had the excuse of being disabled.

Thus, it was disrespectful, but it could be called Support Unit Sam Ho.

It would be a huge win for Gyeon Pohui.

She had suddenly become the sworn sister of a princess and now had the Empress, the mother of all under the Heavens, as her direct junior.

And it wasn't as if there was no one who suffered because Qing had become a completely useless human being.

The Empress was having the happiest moments of her life taking care of her daughter.

So, it could be said to be an act of filial piety that was quite unfilial.

However, there was indeed someone who suffered.

It was Jin Jangmyeong, who had her older sister, whom she had just gotten back, stolen from her.

However, Qing would spare an hour a day to play with her, saying she would check her martial arts, so at least that was something.

If it wasn't for that, a villain who hated the Imperial Family might have been born in the Divine Maiden Sect.

And Seol Riri was, um. She was truly tenacious. So very tenacious.

Seol Riri was incredibly popular among the disciples of the Divine Maiden Sect.

To be precise, it was more respect than popularity.

Every day, except for meal times, she would sit in the lotus position and meditate.

Since the Divine Maiden Sect did not allow anyone other than honored guests to use individual rooms, disciples who shared rooms with her testified that she didn't even sleep.

Of course, there were levels to meditation, and among them was the least efficient one, which was akin to taking a nap. So, strictly speaking, she was just replacing sleep.

Anyway, the sight of the beautiful woman with mysterious silver hair, who spoke very few words, devoting herself to training all day long made a deep impression on the Divine Maiden Sect disciples.

Moreover, her training was so intense that she would sweat profusely, making her appearance quite seductive and her clothes damp. Wow, just dripping with sweat.

It seems that she is quite seductive, as expected of our Grand Master's friend.

At any rate, after seeing the desperate efforts of the truly, truly, truly determined Wulin's Ohwa, everyone was impressed. So much so that everyone's enthusiasm for training was burning and overflowing.

Good times always pass quickly.

After acting like a baby for most of the day, Qing's meridians were now completely healed.

As per Practitioner Jinjeong's words, her meridians had become wider and sturdier than before.

And it was around this time that the Wulin Alliance's mission letter arrived.